### 2020-03-26 Proposal/aws_325ghz.tex
Moved the draft proposal to this repository.

\documentclass[BCOR=1cm,12pt,bibliography=totoc]{article}

% Overall formatting
\sloppy
\let\cleardoublepage\clearpage % do not force chapters to start on odd pages

% Graphics
\usepackage{graphicx}
\DeclareGraphicsExtensions{.png,.pdf,.jpg}
\graphicspath{{Figures/}}

\usepackage[a4paper, total={16cm,25cm}]{geometry}

% Tables
\newlength{\mytabskip}   
\setlength{\mytabskip}{-1.5ex}
\newcommand{\tabrule}{\rule[\mytabskip]{0ex}{0ex}}
\usepackage{tabularx}
%\usepackage{longtable}

% bibliography stuff 
\usepackage{natbib}
\bibliographystyle{plainnat} % to display the URLs

\newcommand{\unit}[1]{\ensuremath{\mathrm{#1}}}
\newcommand{\degree}{\ensuremath{\mathrm{^\circ}}}

%\newcommand{\FIXME}[1]{{\sffamily \bfseries #1}}
\newcommand{\FIXME}[1]{{\sffamily {\bfseries \textcolor{red}{FIXME:} #1}}}

\hyphenation{EUMETSAT}
\hyphenation{Metop}

\begin{document}

\noindent
\textbf{{\LARGE Arctic Weather Satellite (AWS) channels\\definition: Work plan}}  \vspace{5mm}\\
{\bf Patrick Eriksson}\\
Dept.\ of Space, Earth and Environment\\
Chalmers University of Technology\\
SE-412\,96, Gothenburg, Sweden \vspace{10mm}

\section{Objectives}
\label{sec:objectives}
%
Our understanding is that the main objectives of the study are:
\begin{itemize}
\item Demonstrate that channels around 325.15\,GHz provides a basis for cloud
  filtering/correction of data measured around 183\,GHz, that is equivalent
  or better than what can be achieved with a channel at 229\,GHz (as found on
  the MicroWave Sounder, MWS). 
\item Suggest specifications of 325\,GHz channels considering the specific
  constraints of the AWS project. Matching in terms of weighting functions between
  183 and 325\,GHz channels could be relevant in this context.
\end{itemize}
If feasible, other ways to compare the 229 and 325\,GHz options should be
considered, such as degree of freedom in the measurements.

\section{Reference documents and data}
\label{sec:info}
%
The study report by \citet{rekha2012potential} will be used as reference with
respect to cloud filtering using 229\,GHz through a scattering index (SI)
approach. It should be considered if the specifications of the 325\,GHz
channels could be the same as applied for ICI (Ice Cloud Imager), that are
based on \citet{buehler:obser:12}.

Omnisys will be consulted when it comes to technical assumptions and
constraints. It is assumed that channels at 89, 166 and 183\,GHz will be placed
as for MWS, except that AWS 183\,GHz channels will be single sideband (covering
the lower MWS band). If needed, assumptions for a 229\,GHz channel will be
taken from the MWS science plan. Required input from Omnisys includes: minimum
and maximum intermediate frequency (IF) for 325\,GHz channels, maximum number
of channels inside this range and expected receiver noise temperature at 166,
183 and 325\,GHz.

\section{Cloud filtering and correction}
\label{sec:clouds}
%
As mentioned, \citet{rekha2012potential} suggested a SI-based cloud filtering
approach for MWS, using data from 229\,GHz. SI-type cloud filtering based on
183\,GHz data alone can also be performed \citep{buehler:aclou:07}. However,
the cloud filtering performed operationally for NWP (numerical weather
prediction) seems to mainly be based on deviations between observations and
clear-sky simulations based on the background field (e.g.\
\citet{chambon2015investigating}). The aim of both these approaches is just to
reject data with a cloud impact exceeding some brightness temperature
threshold. This means that even if these cloud filtering methods would work
perfectly, they will still cause a bias in filtered data. This is the case as
the presence of clouds gives throughout a decrease in 183\,GHz radiances (maybe
except for outermost channels and very dry conditions). Expressed differently,
compared to the true cloud and noise free brightness temperature, the filtered
data will have an uncertainty distribution that is non-Gaussian. On one side
the distribution will be determined by the measurement noise. On the other
side, the distribution will be a combination of measurement noise and the cloud
impacts that are below the threshold value. The mean of this distribution will
deviate from zero. This is not optimal but likely the best that can be achieved
with present sensors.

The 325\,GHz transition is of similar strength as the 183\,GHz one (though a
bit weaker and more highly affected by continuum absorption). On the other
hand, the impact of high altitude cirrus clouds should be considerably higher.
Weak cloud impact should mainly end up in the Rayleigh domain, where
scattering follows $\lambda^4$. For 325 vs.\ 183\,GHz, this gives a factor very
close to 10. That is, if a high cloud gives a 5\,K impact on a channel around
325\,GHz the impact for a channel around 183\,GHz with similar (clear-sky)
weighting function should be about 0.5\,K. The impact at 183\,GHz can not be
detected, due to thermal noise and modelling uncertainties, while the impact at
325\,GHz should be possible to estimate. Further, the estimated 325\,GHz cloud
impact could even be used to compensate for the cloud impact at 183\,GHz.

This later approach, i.e.\ to perform a cloud correction of 183\,GHz data, will
be the primary option for this study. If successful, this will provide 183\,GHz
data that are more useful for NWP and stand-alone 1DVAR that rely on
``clear-sky'' data. At least the resulting data should have a lower bias than
the existing approaches. The precision will depend on situation and the method
for cloud correction should preferably also provide a case-specific uncertainty
estimate.

The suggested cloud correction scheme could be seen as forming clear-sky
``super-channels'' by combining measurements at 183 and 325\,GHz. This would
have the advantage that NWP systems not yet prepared for 325\,GHz, could still
make use of these data early on. For situations where 325\,GHz lacks cloud
impacts, theoretically the super-channels could have a resulting NEDT (Noise
Equivalent Delta Temperature) lower than the one of 183\,GHz, as the
combination of 183 and 325\,GHz together gives a higher effective bandwidth. In
practice this can be hard to achieve due to a higher noise at 325\,GHz and
modelling uncertainties, and the comment was added mainly to illustrate the
approach.

\section{Work plan}
\label{sec:wp}
%
For clarity, the work as divided into a number of work packages (WPs). See
next page. The work will be performed by (with WP responsibilities inside
parenthesises):
\begin{itemize}
\item Patrick Eriksson (WP 1.1 and 3.3)
\item Simon Pfreundschuh (WP 1.2 and 3.2)
\item Inderpreet Kaur (WP 2.1, 2.2, and 3.1)
\end{itemize}

\newpage
\subsection*{WP1}
%
\subsubsection*{WP1.1: Basic preparations}
%
\begin{itemize}
\item Contact Omnisys to obtain required technical information.
\item Determine the number of monochromatic frequencies needed to represent each
  channel with sufficient accuracy. 
\item Compare 183, 229 and 325\,GHz brightness temperatures and weighting
  functions (clear-sky), for a set of climatological atmospheres. Based on
  this, define preliminary specifications of 325\,GHz channels.
\end{itemize}

\subsubsection*{WP1.2: Setting up bulk simulations}
%
The task of this WP is to prepare and implement functions for creating a
diverse set of simulations, to be used in later WPs. The simulations will be
based on CloudSat reflectivities and ERA5 data, and largely follow the
``dBZ-based model system'' introduced in \citet{ekelund:using:20}. The main
deviations to \citet{ekelund:using:20} is that some along-track averaging of
CloudSat data will be performed, the mapping from reflectivities will be
performed by 1DVAR (and not by ``onion-peeling'') and that each footprint will
be represented with a single pencil beam. To make it easier to streamline the
calculations, a switch from Matlab to Python will also be made. Both clear-sky
and all-sky data will be generated, using ARTS and its interface to the RT4
scattering solver.

\subsection*{WP2}
%
\subsubsection*{WP2.1: Bulk simulations}
%
Perform the required number of simulations. Data will be generated for randomly
sampled positions, for latitudes up to  60$^\circ$N/S. Higher latitudes
will be avoided initially as that require more care about surface emissivity.
Both land and ocean areas will be considered but for land an altitude threshold
will be applied, again due to limitations in the knowledge of surface
emissivities.

Simulations covering channels at 89, 166, 183, 229 and 325\,GHz will be made. A
number of scan angles, between nadir and swath edge, will be covered. A first
batch of 100\,000 simulations will be made. If found necessary, adding more
simulations could be possible. If time permits, extending the simulations to
higher latitudes could also be considered.

\subsubsection*{WP2.2: Post-processing of data}
%
Monochromatic data are weighted together to form channel antenna temperatures.
For 325\,GHz channel data should be formed for some alternative channel
specifications, for later comparison between the alternatives. Position,
land/ocean, IWP and other data are added, to form a database suitable for the
analysis in WP3.

\subsection*{WP3}
%
\subsubsection*{WP3.1: Cloud correction}
%
A cloud correction scheme of 183\,GHz data is developed. The main task if to
find a suitable regression approach. In short, the regression shall, based on
the simulated 325\,GHz data and the antenna temperature of the 183\,GHz channel
of concern, predict the clear-sky, noise free, value. Different regression
schemes and 325\,GHZ channel alternatives will be compared by assessing the
error of the prediction. The error shall have as low bias and spread as
possible. An error model will also be devised and assessed. Tests will be made
for lower and higher assumed NEDT, to assess if there is any critical value
that should be reflected in the requirements of AWS.

A similar regression will be tested for 229\,GHz. If not working well, a
perfect version of the approach by \citet{rekha2012potential} will be used
instead for 229\,GHz. That is, the assumed error distribution is the one
described in Sec.~\ref{sec:clouds},

\subsubsection*{WP3.2: Measurements’ degrees of freedom (DoF)}
%
An analysis following the one in Sec.~4.3.2 of \citet[][]{eriksson:towar:20}
for ICI will be made, based on the database of simulations. This WP requires
that the database contains data for 89 and 166\,GHz, to give a correct view on
the value of 229\,GHz. This is the case as 229\,GHz is a window channel (as 89
and 166\,GHz) and there should be redundancy between 229\,GHz and the other
window channels. In a similar way, 325\,GHz will give small increase in the DoF
for clear clear-sky situations, due to redundancy with 183\,GHz, but should
increase the DoF significantly in the presence of ice clouds.

\subsubsection*{WP3.3: Meetings and reporting}
%
This WP covers to analyse the results to reach a conclusion, as well as
reporting the results.

\bibliography{j_abbr,references}

\end{document}

### 2020-03-26 aws/data.py
Added aws Python package and code to read input data.

@@ -1,0 +1,71 @@
+from h5py import File
+
+class Profiles:
+    """
+    Data provider class that provides the parts interface for an
+    input data file in HDF5 (matlab) format.
+
+    Attributes:
+        self.path: The filename of the input data
+        self.data: HDF5 group object containing the data
+
+    """
+    def __init__(self, path):
+        """
+        Create data provider from given input file.
+
+        Args:
+            path(:code:`str`): The path to the input file.
+        """
+        self.path = path
+        self.file = File(path)
+
+    def get_y_cloudsat(self, i):
+        r = self.file["C"]["dBZ"][i][0]
+        data = self.file[r][0, :]
+        return data
+
+    def get_pressure(self, i):
+        r = self.file["C"]["p_grid"][i][0]
+        data = self.file[r][0, :]
+        return data
+
+    def get_temperature(self, i):
+        r = self.file["C"]["t_field"][i][0]
+        data = self.file[r][0, :]
+        return data
+
+    def get_temperature(self, i):
+        r = self.file["C"]["t_field"][i][0]
+        data = self.file[r][0, :]
+        return data
+
+    def get_altitude(self, i):
+        r = self.file["C"]["z_field"][i][0]
+        data = self.file[r][0, :]
+        return data
+
+    def get_H2O(self, i):
+        r = self.file["C"]["h2o"][i][0]
+        data = self.file[r][0, :]
+        return data
+
+    def get_lwc(self, i):
+        r = self.file["C"]["lwc"][i][0]
+        data = self.file[r][0, :]
+        return data
+
+    def get_surface_altitude(self, i):
+        r = self.file["C"]["z_surface"][i][0]
+        data = self.file[r][0, :]
+        return data
+
+    def get_surface_wind_speed(self, i):
+        r = self.file["C"]["wind_speed"][i][0]
+        data = self.file[r][0, :]
+        return data
+
+    def get_surface_wind_direction(self, i):
+        r = self.file["C"]["wind_dir"][i][0]
+        data = self.file[r][0, :]
+        return data

### 2020-03-26 Matlab/CaseGeneration/init_aws325ghz.m
adapted path for IK

@@ -13,6 +13,9 @@ function init_aws325ghz
 switch whoami
   case 'patrick'
     run( '~/SVN/opengem/patrick/Projects/CloudArts/addpath_cloudarts' );
+  case 'inderpreet'
+    run( '~/SVN/CloudArts/addpath_cloudarts' );
+    atmlab( 'ATMLAB_DATA_PATH',   '~/SVN/atmlab-data');
   otherwise
     error( 'Unknown user' );
 end

### 2020-03-26 Matlab/CaseGeneration/test.m
adpated path for IK

@@ -3,6 +3,8 @@
 switch whoami
   case 'patrick'
     workfolder = '/home/patrick/WORKAREA';
+  case 'inderpreet'
+    workfolder = 'home/inderpreet/Projects/AWS'
   otherwise
     error( 'Unknown user' );
 end  

### 2020-04-07 aws/hydrometeors.py
Make AB12 work in retrieval.

@@ -45,6 +45,21 @@ class D14(D14MN):
     def moment_names(self):
         return ["water_content", "n0"]
 
+class Abel(AB12):
+    """
+    Specialized class implementing a normalized modified gamma distribution
+    parametrized using mass density and mass weighted mean diameter (D_m).
+    The shape is the same as the one used for the DARDAR v3 retrievals.
+    """
+    def __init__(self):
+        super().__init__()
+        self.name = "ab12"
+
+    @property
+    def moment_names(self):
+        return ["water_content"]
+
+
 
 
 
@@ -73,7 +88,7 @@ class Rain(ScatteringSpecies):
         # PSD, same as DARDAR V3
         alpha = 0.0
         beta = 1.0
-        psd = D12()
+        psd = Abel()
         psd.t_min = 270.0
 
         scattering_data = os.path.join(data_path, "StandardHabits", "LiquidSphere.xml")

### 2020-04-07 aws/sensor.py

@@ -18,7 +18,7 @@ class CloudSat(ActiveSensor):
                          stokes_dimension = 1)
         self.instrument_pol       = [1]
         self.instrument_pol_array = [[1]]
-        self.extinction_scaling   = 1.0
+        self.extinction_scaling   = 0.0
         self.y_min = -30.0
         self.sensor_position = np.array([[600e3]])
         self.sensor_line_of_sight = np.array([[180.0]])

### 2020-04-07 Matlab/BasicAnalysis/apply_channels.m
Script to make figures of spectra, Jacobian and transmission to space ready.

@@ -1,9 +1,18 @@
+% FORMAT  weighted = apply_channels(f_mono,monochrom,channels)
+%
+% OUT  weighted   Channel weighted values
+% IN   f_mono     Monochromatic frequency grid
+%      monochrom  Monochromatic values (nf,nx)  
+%      channels   As return by eg. *channels_fixed*
+
+% 2020-04-07 Patrick Eriksson
+
 function weighted = apply_channels(f_mono,monochrom,channels)
 
 n        = size( channels, 1 );
-weighted = zeros( size(monochrom,1), n );
+weighted = zeros( n, size(monochrom,2) );
 
 for c = 1 : n
   ind = find( f_mono >= channels(c,1) & f_mono <= channels(c,2) ); 
-  weighted(:,c) = mean( monochrom(:,ind), 2 );
+  weighted(c,:) = mean( monochrom(ind,:), 1 );
 end

### 2020-04-07 Matlab/BasicAnalysis/channels_aws325ghz.m

@@ -1,15 +1,31 @@
-function chs325 = channels_aws325ghz(only3)
+% Returns limits for some AWS 325 GHz channels options
 %
-if nargin == 0, only3 = false; end
+%    Limits for lower sideband returned
+%
+% FORMAT chs325 = channels_aws325ghz([option])
+%
+% OUT   chs325  Limits for lower sideband of ICI 325 GHz channels
+% OPT   option  Option string.
 
+% 2020-04-07 Patrick Eriksson
 
-if only3
-  chs325 = 325.15e9 + [-9.00 -5.00;
-                       -4.70 -2.30;
-                       -2.30 -0.80 ] * 1e9;
-else    
-  chs325 = 325.15e9 + [-9.00 -6.00;
-                       -6.00 -3.60;
-                       -3.60 -1.80;
-                       -1.80 -0.80 ] * 1e9;
+function chs325 = channels_aws325ghz(option)
+%
+if nargin == 0, option = '3'; end
+
+switch option
+  
+  case '3'
+    chs325 = 325.15e9 + [-9.00 -5.00;
+                         -4.70 -2.30;
+                         -2.30 -0.80 ] * 1e9;
+  
+  case '4'
+    chs325 = 325.15e9 + [-9.00 -6.00;
+                         -6.00 -3.60;
+                         -3.60 -1.80;
+                         -1.80 -0.80 ] * 1e9;
+  
+  otherwise
+    error( 'Unknown option' );
 end

### 2020-04-07 Matlab/BasicAnalysis/channels_fixed.m

@@ -1,3 +1,12 @@
+% Returns limits for fixed chanels
+%
+% FORMAT [chs183,ch229] = channels_fixed
+%
+% OUT   chs183  Limits for lower sideband of MWS 183 GHz channels
+%       chs229  Limits  of MWS 229 GHz channel
+
+% 2020-04-07 Patrick Eriksson
+
 function [chs183,ch229] = channels_fixed
 
 chs183 = 183.31e9 + [-8.00 -6.00;

### 2020-04-07 Matlab/BasicAnalysis/channels_ici325ghz.m

@@ -1,3 +1,13 @@
+% Returns limits for ICI 325 GHz channels
+%
+%    Limits for lower sideband returned
+%
+% FORMAT chs325 = channels_ici325ghz
+%
+% OUT   chs325  Limits for lower sideband of ICI 325 GHz channels
+
+% 2020-04-07 Patrick Eriksson
+
 function chs325 = channels_ici325ghz
 
 chs325 = 325.15e9 + [-11.0 -8.00;

### 2020-04-07 Matlab/BasicAnalysis/mkfigs_spectra_wfuns.m

@@ -1,4 +1,11 @@
-function compare_spectra(r_surface,chs183,chs229,chs325)
+% Makes figures with spectra, weighting functions and transmissivity to
+% space for all five Fascod atmospheres.
+%
+% FORMAT  mkfigs_spectra_wfuns(r_surface,chs183,chs229,chs325)
+
+% 2020-04-07 Patrick Eriksson
+
+function mkfigs_spectra_wfuns(r_surface,chs183,chs229,chs325)
 
 df = linspace( -10e9, -0.5e9, 50 );
 nf = length( df );
@@ -19,7 +26,8 @@ ftmp = c325 + [df sort(-df) ];
 [Y325,J325,T325] = calc_atms( ftmp, r_surface );
 %
 Y325 = ( Y325(1:nf,:) + Y325(nf*2:-1:nf+1,:) ) / 2;
-T325 = ( T325(:,1:nf,:) + T325(:,nf*2:-1:nf+1,:) ) / 2;
+T325 = ( T325(1:nf,:,:) + T325(nf*2:-1:nf+1,:,:) ) / 2;
+J325 = ( J325(1:nf,:,:) + J325(nf*2:-1:nf+1,:,:) ) / 2;
 
 %- 229 GHz
 %
@@ -45,25 +53,65 @@ h2 = plot( (f325-c325)/1e9, Y325, '--', 'LineWidth', 1 );
 set( gca, 'ColorOrderIndex', 1 );
 h3 =plot( (f229-c229)/1e9, Y229, '-.', 'LineWidth', 1 );
 xlabel( 'Distance from centre/LO frequency [GHz]' );
-ylabel( 'Tb [K]' )
+ylabel( 'Tb [K]' );
+grid on
 %
 l        = upper( atms );
 l{1}     = [ l{1}, ', 183 GHz'];
 l{end+1} = '325 GHz';
 l{end+1} = '229 GHz';
 %
-legend( [h1;h2(1);h3(1)], l, 'Location', 'SouthWest' );
+legend( [h1;h2(1);h3(1)], l, 'Location', 'South' );
 hold off
 %
 axis([ -10 0 230 286 ])
 
 
+% Wfuns plots
+%
+dz = diff( p2z_simple( Q.P_GRID(4:5) ) ) / 1e3;
+%
+for i = 1 : length(atms)
+  figure( get(gcf,'Number') + 1 );
+  clf;
+  n = size( T183, 2 );
+  l = {};
+  %
[…]

### 2020-04-07 Matlab/BasicAnalysis/q_basic.m

@@ -66,7 +66,7 @@ Q.SENSOR_POS            = 600e3;
 Q.SENSOR_LOS            = 170;
 %
 Q.F_GRID                = vec2col( f_grid );
-Q.P_GRID                = z2p_simple( -500:250:50e3 )';
+Q.P_GRID                = z2p_simple( -500:500:50e3 )';
 
 
 %- External version

### 2020-04-07 Report/aws_325ghz_study.tex
Started folder for study report.

--- 2020-03-26 Proposal/aws_325ghz.tex
@@
-\documentclass[BCOR=1cm,12pt,bibliography=totoc]{article}
+\documentclass[12pt]{article}
 
@@
 \usepackage{natbib}
-\bibliographystyle{plainnat} % to display the URLs
+\bibliographystyle{kluwer}
 
@@
 \noindent
-\textbf{{\LARGE Arctic Weather Satellite (AWS) channels\\definition: Work plan}}  \vspace{5mm}\\
-{\bf Patrick Eriksson}\\
-Dept.\ of Space, Earth and Environment\\
+\textbf{\LARGE Arctic Weather Satellite: Cloud ...}  \vspace{5mm}\\
+{\bf Patrick Eriksson, Simon Pfreundschuh and Inderpreet Kaur}\\
+Department of Space, Earth and Environment\\
 Chalmers University of Technology\\
@@
 
-\section{Objectives}
-\label{sec:objectives}
+\section{Introduction}
 %
-Our understanding is that the main objectives of the study are:
-\begin{itemize}
-\item Demonstrate that channels around 325.15\,GHz provides a basis for cloud
-  filtering/correction of data measured around 183\,GHz, that is equivalent
-  or better than what can be achieved with a channel at 229\,GHz (as found on
-  the MicroWave Sounder, MWS). 
-\item Suggest specifications of 325\,GHz channels considering the specific
-  constraints of the AWS project. Matching in terms of weighting functions between
-  183 and 325\,GHz channels could be relevant in this context.
-\end{itemize}
-If feasible, other ways to compare the 229 and 325\,GHz options should be
-considered, such as degree of freedom in the measurements.
-
-\section{Reference documents and data}
-\label{sec:info}
-%
-The study report by \citet{rekha2012potential} will be used as reference with
-respect to cloud filtering using 229\,GHz through a scattering index (SI)
-approach. It should be considered if the specifications of the 325\,GHz
-channels could be the same as applied for ICI (Ice Cloud Imager), that are
-based on \citet{buehler:obser:12}.
-
-Omnisys will be consulted when it comes to technical assumptions and
-constraints. It is assumed that channels at 89, 166 and 183\,GHz will be placed
-as for MWS, except that AWS 183\,GHz channels will be single sideband (covering
-the lower MWS band). If needed, assumptions for a 229\,GHz channel will be
-taken from the MWS science plan. Required input from Omnisys includes: minimum
-and maximum intermediate frequency (IF) for 325\,GHz channels, maximum number
-of channels inside this range and expected receiver noise temperature at 166,
-183 and 325\,GHz.
-
-\section{Cloud filtering and correction}
-\label{sec:clouds}
-%
-As mentioned, \citet{rekha2012potential} suggested a SI-based cloud filtering
-approach for MWS, using data from 229\,GHz. SI-type cloud filtering based on
-183\,GHz data alone can also be performed \citep{buehler:aclou:07}. However,
-the cloud filtering performed operationally for NWP (numerical weather
-prediction) seems to mainly be based on deviations between observations and
-clear-sky simulations based on the background field (e.g.\
-\citet{chambon2015investigating}). The aim of both these approaches is just to
-reject data with a cloud impact exceeding some brightness temperature
-threshold. This means that even if these cloud filtering methods would work
-perfectly, they will still cause a bias in filtered data. This is the case as
-the presence of clouds gives throughout a decrease in 183\,GHz radiances (maybe
-except for outermost channels and very dry conditions). Expressed differently,
-compared to the true cloud and noise free brightness temperature, the filtered
-data will have an uncertainty distribution that is non-Gaussian. On one side
-the distribution will be determined by the measurement noise. On the other
-side, the distribution will be a combination of measurement noise and the cloud
-impacts that are below the threshold value. The mean of this distribution will
-deviate from zero. This is not optimal but likely the best that can be achieved
-with present sensors.
-
-The 325\,GHz transition is of similar strength as the 183\,GHz one (though a
-bit weaker and more highly affected by continuum absorption). On the other
-hand, the impact of high altitude cirrus clouds should be considerably higher.
-Weak cloud impact should mainly end up in the Rayleigh domain, where
-scattering follows $\lambda^4$. For 325 vs.\ 183\,GHz, this gives a factor very
-close to 10. That is, if a high cloud gives a 5\,K impact on a channel around
-325\,GHz the impact for a channel around 183\,GHz with similar (clear-sky)
-weighting function should be about 0.5\,K. The impact at 183\,GHz can not be
-detected, due to thermal noise and modelling uncertainties, while the impact at
-325\,GHz should be possible to estimate. Further, the estimated 325\,GHz cloud
-impact could even be used to compensate for the cloud impact at 183\,GHz.
-
-This later approach, i.e.\ to perform a cloud correction of 183\,GHz data, will
-be the primary option for this study. If successful, this will provide 183\,GHz
-data that are more useful for NWP and stand-alone 1DVAR that rely on
-``clear-sky'' data. At least the resulting data should have a lower bias than
-the existing approaches. The precision will depend on situation and the method
-for cloud correction should preferably also provide a case-specific uncertainty
-estimate.
-
-The suggested cloud correction scheme could be seen as forming clear-sky
-``super-channels'' by combining measurements at 183 and 325\,GHz. This would
-have the advantage that NWP systems not yet prepared for 325\,GHz, could still
-make use of these data early on. For situations where 325\,GHz lacks cloud
-impacts, theoretically the super-channels could have a resulting NEDT (Noise
-Equivalent Delta Temperature) lower than the one of 183\,GHz, as the
-combination of 183 and 325\,GHz together gives a higher effective bandwidth. In
-practice this can be hard to achieve due to a higher noise at 325\,GHz and
-modelling uncertainties, and the comment was added mainly to illustrate the
-approach.
-
-\section{Work plan}
-\label{sec:wp}
-%
-For clarity, the work as divided into a number of work packages (WPs). See
-next page. The work will be performed by (with WP responsibilities inside
-parenthesises):
-\begin{itemize}
-\item Patrick Eriksson (WP 1.1 and 3.3)
-\item Simon Pfreundschuh (WP 1.2 and 3.2)
-\item Inderpreet Kaur (WP 2.1, 2.2, and 3.1)
-\end{itemize}
-
-\newpage
-\subsection*{WP1}
-%
-\subsubsection*{WP1.1: Basic preparations}
-%
-\begin{itemize}
-\item Contact Omnisys to obtain required technical information.
-\item Determine the number of monochromatic frequencies needed to represent each
-  channel with sufficient accuracy. 
-\item Compare 183, 229 and 325\,GHz brightness temperatures and weighting
-  functions (clear-sky), for a set of climatological atmospheres. Based on
-  this, define preliminary specifications of 325\,GHz channels.
-\end{itemize}
-
-\subsubsection*{WP1.2: Setting up bulk simulations}
-%
-The task of this WP is to prepare and implement functions for creating a
-diverse set of simulations, to be used in later WPs. The simulations will be
-based on CloudSat reflectivities and ERA5 data, and largely follow the
-``dBZ-based model system'' introduced in \citet{ekelund:using:20}. The main
-deviations to \citet{ekelund:using:20} is that some along-track averaging of
-CloudSat data will be performed, the mapping from reflectivities will be
-performed by 1DVAR (and not by ``onion-peeling'') and that each footprint will
-be represented with a single pencil beam. To make it easier to streamline the
-calculations, a switch from Matlab to Python will also be made. Both clear-sky
-and all-sky data will be generated, using ARTS and its interface to the RT4
-scattering solver.
-
-\subsection*{WP2}
-%
-\subsubsection*{WP2.1: Bulk simulations}
-%
-Perform the required number of simulations. Data will be generated for randomly
-sampled positions, for latitudes up to  60$^\circ$N/S. Higher latitudes
-will be avoided initially as that require more care about surface emissivity.
-Both land and ocean areas will be considered but for land an altitude threshold
-will be applied, again due to limitations in the knowledge of surface
-emissivities.
-
-Simulations covering channels at 89, 166, 183, 229 and 325\,GHz will be made. A
-number of scan angles, between nadir and swath edge, will be covered. A first
-batch of 100\,000 simulations will be made. If found necessary, adding more
-simulations could be possible. If time permits, extending the simulations to
-higher latitudes could also be considered.
-
-\subsubsection*{WP2.2: Post-processing of data}
-%
-Monochromatic data are weighted together to form channel antenna temperatures.
-For 325\,GHz channel data should be formed for some alternative channel
-specifications, for later comparison between the alternatives. Position,
-land/ocean, IWP and other data are added, to form a database suitable for the
-analysis in WP3.
-
-\subsection*{WP3}
-%
-\subsubsection*{WP3.1: Cloud correction}
-%
-A cloud correction scheme of 183\,GHz data is developed. The main task if to
-find a suitable regression approach. In short, the regression shall, based on
-the simulated 325\,GHz data and the antenna temperature of the 183\,GHz channel
-of concern, predict the clear-sky, noise free, value. Different regression
-schemes and 325\,GHZ channel alternatives will be compared by assessing the
-error of the prediction. The error shall have as low bias and spread as
-possible. An error model will also be devised and assessed. Tests will be made
-for lower and higher assumed NEDT, to assess if there is any critical value
-that should be reflected in the requirements of AWS.
-
-A similar regression will be tested for 229\,GHz. If not working well, a
-perfect version of the approach by \citet{rekha2012potential} will be used
-instead for 229\,GHz. That is, the assumed error distribution is the one
-described in Sec.~\ref{sec:clouds},
-
-\subsubsection*{WP3.2: Measurements’ degrees of freedom (DoF)}
-%
-An analysis following the one in Sec.~4.3.2 of \citet[][]{eriksson:towar:20}
-for ICI will be made, based on the database of simulations. This WP requires
-that the database contains data for 89 and 166\,GHz, to give a correct view on
-the value of 229\,GHz. This is the case as 229\,GHz is a window channel (as 89
-and 166\,GHz) and there should be redundancy between 229\,GHz and the other
-window channels. In a similar way, 325\,GHz will give small increase in the DoF
-for clear clear-sky situations, due to redundancy with 183\,GHz, but should
-increase the DoF significantly in the presence of ice clouds.
-
-\subsubsection*{WP3.3: Meetings and reporting}
-%
-This WP covers to analyse the results to reach a conclusion, as well as
-reporting the results.
+\dots
 

### 2020-04-08 Report/aws_325ghz_study.tex
A small start on the report.

@@
 \noindent
-\textbf{\LARGE Arctic Weather Satellite: Cloud ...}  \vspace{5mm}\\
+\textbf{\Large Arctic Weather Satellite: ???}  \vspace{8mm}\\
 {\bf Patrick Eriksson, Simon Pfreundschuh and Inderpreet Kaur}\\
@@
 
+\section{Data and methods}
+
+\subsection{Fascod}
+%
+The Fascod dataset \citep{anderson1986afgl} is used to represent different
+climate zones in overview calculations. The dataset consists of profiles of
+pressure, temperature and volume mixing ratio profiles of various atmospheric
+gases. Five climatoligies are used: tropical (TRO), mid-latitude summer (MLS),
+mid-latitude winter (MLW), sub-arctic summer (SAS), and sub-arctic winter
+(SAW). No hydrometeors are included in simulations involving Fascod.
+
+\subsection{Bulk atmospheric profile database}
+%
+Refer to ICI and Robin's article.
+
+\subsection{AWS}
+%
+Channels
+
+The satellite is assumed to be at an altitude of 600\,km.
+
+\subsection{Radiative transfer simulations}
+%
+\subsubsection{ARTS}
+%
+All radiative transfer calculations are made by the Atmospheric Radiative
+Transfer System (ARTS, \citet{eriksson:arts2:11,buehler:artst:18}), version
+arts-2.3.????. Models and input used for absorption and hydrometeor properties
+are described below. ARTS considers a spherical Earth by default. Scattering
+calculations were made by ARTS's interface to the RT4 solver
+\citep{evans1995microwavec}. Ocean/water and land emissivities ae taken from
+TESSEM \citet{prigent2017sea} and TELSEM \citet{aires2011tool}, respectively.
+
+\subsubsection{Absorption models}
+%
+The absorption of nitrogen is modelled following \citet{pwr:93}. Nitrogen has a
+significant impact at least around 325\,GHz at dry conditions. Also oxygen
+absorption follows \citet{pwr:93}. Oxygen is in this study mainly of concern
+for the 89\,GHz CloudSat simulations. Liquid cloud water (LCW) is treated
+purely absorbing, based on \citet{ellison2007permittivity}.
+
+For water vapour the present settings in RTTOV are applied. That is, largely
+MPM89 \citep{liebe:89} is followed, but some parameters for the 22 and 183\,GHz
+transitions are replaced \citep{saunders2018update,turner2019amsutran}. A basic
+comparison to RTTOV (12.?) was made (with MHS as assumed sensor) and an
+agremment around or better than 0.?\,K was found.
+
+\subsubsection{Hydrometeor properties}
+%
+\dots
+
+\section{Results}
+
+\subsection{Overview of the frequency bands}
+%
+The simulations involving Fascode were done using a fixed satellite observation
+angle of 155$^\circ$ (from zenith) and a
+
+\begin{figure}[p]
+  \centering
+  \includegraphics[width=0.7\textwidth]{fascod_tb_r000}
+  \caption{dd}
+  \label{fig:tb:r00}
+\end{figure}
+\begin{figure}[p]
+  \centering
+  \includegraphics[width=0.7\textwidth]{fascod_tb_r050}
+  \caption{Same as figure above, but with a surface reflectivity of 0.5.}
+  \label{fig:tb:r00}
+\end{figure}
+
 \bibliography{j_abbr,references}

### 2020-04-08 Matlab/BasicAnalysis/mkfigs_spectra_wfuns.m

@@ -7,7 +7,7 @@
 
 function mkfigs_spectra_wfuns(r_surface,chs183,chs229,chs325)
 
-df = linspace( -10e9, -0.5e9, 50 );
+df = linspace( -10e9, -0.5e9, 100 );
 nf = length( df );
 
 %- 183 GHz
@@ -31,7 +31,7 @@ J325 = ( J325(1:nf,:,:) + J325(nf*2:-1:nf+1,:,:) ) / 2;
 
 %- 229 GHz
 %
-df   = linspace( -1e9, -0.1, 5 );
+df   = linspace( -1e9, -0.1, 10 );
 nf   = length( df );
 c229 = 229e9;
 f229 = c229 + df;
@@ -40,6 +40,8 @@ ftmp = c229 + [df sort(-df) ];
 [Y229,J229,T229] = calc_atms( ftmp, r_surface );
 %
 Y229 = ( Y229(1:nf,:) + Y229(nf*2:-1:nf+1,:) ) / 2;
+T229 = ( T229(1:nf,:,:) + T229(nf*2:-1:nf+1,:,:) ) / 2;
+J229 = ( J229(1:nf,:,:) + J229(nf*2:-1:nf+1,:,:) ) / 2;
 
 
 %- Spectrum plot
@@ -52,7 +54,7 @@ set( gca, 'ColorOrderIndex', 1 );
 h2 = plot( (f325-c325)/1e9, Y325, '--', 'LineWidth', 1 );
 set( gca, 'ColorOrderIndex', 1 );
 h3 =plot( (f229-c229)/1e9, Y229, '-.', 'LineWidth', 1 );
-xlabel( 'Distance from centre/LO frequency [GHz]' );
+xlabel( 'Distance from reference frequency [GHz]' );
 ylabel( 'Tb [K]' );
 grid on
 %

### 2020-04-08 Matlab/BasicAnalysis/q_basic.m

@@ -63,7 +63,7 @@ Q.PPATH_LMAX            = -1;
 Q.YCALC_WSMS            = { 'yCalc' };
 %
 Q.SENSOR_POS            = 600e3;
-Q.SENSOR_LOS            = 170;
+Q.SENSOR_LOS            = 155;
 %
 Q.F_GRID                = vec2col( f_grid );
 Q.P_GRID                = z2p_simple( -500:500:50e3 )';

### 2020-04-08 Report/aws_325ghz_study.tex
Some work on report.

@@
 \noindent
-\textbf{\Large Arctic Weather Satellite: ???}  \vspace{8mm}\\
+\textbf{\Large Study to support the definition of Arctic Weather \vspace{1mm}\\
+Satellite (AWS) high frequency channels} \vspace{8mm}\\
 {\bf Patrick Eriksson, Simon Pfreundschuh and Inderpreet Kaur}\\
@@
 
-\subsection{Fascod}
+\subsection{Atmospheric scenarios}
+
+\subsubsection{Fascod}
 %
-The Fascod dataset \citep{anderson1986afgl} is used to represent different
+The Fascod dataset \citep{anderson1986afgl} was used to represent different
 climate zones in overview calculations. The dataset consists of profiles of
 pressure, temperature and volume mixing ratio profiles of various atmospheric
-gases. Five climatoligies are used: tropical (TRO), mid-latitude summer (MLS),
+gases. Five climatoligies were used: tropical (TRO), mid-latitude summer (MLS),
 mid-latitude winter (MLW), sub-arctic summer (SAS), and sub-arctic winter
-(SAW). No hydrometeors are included in simulations involving Fascod.
+(SAW). No hydrometeors were included in simulations involving Fascod.
 
-\subsection{Bulk atmospheric profile database}
+\subsubsection{Bulk profile database}
 %
-Refer to ICI and Robin's article.
+A database of atmospheric cases was created based on data from CloudSat and
+ERA-Interim. The core idea of the approach is to use CloudSat reflectivities to
+obtain as realistic vertical profiles of ice hydrometeors and rain as
+possible. No external CloudSat retrievals are involved. Instead the CloudSat
+reflectivites are mapped to properties for the passive simulations by assuming
+a particle size distribution (PSD) and a particle habit, together denoted as
+the particle model. The process involves an inversion of the radar data, but as
+the same particle model is used for that inversion and to map ice water content
+(IWC) and rain water content (RWC) to single scattering data when performing
+the passive radiative transfer calculations, the impact of clouds on the
+simulated AWS data is as realistic as possible. The thin clouds not detected by
+CloudSat should not be of relevance for passive measurements frequencies
+350\,GHz. Background data (temperature, humidity, 10\,m wind speed, \dots) were
+taken from ERA-Interim, for the time and location of the CloudSat data. Liquid
+water content (LWC) was taken from ERA-Interim, as CloudSat has no sensitivity
+to the hydrometeor category.
 
-\subsection{AWS}
-%
-Channels
+This approach for generating atmospheric scenarios has been used by us since
+\citet{rydberg:nonga:09}, and more recently in e.g.\
+citet{eriksson:towar:20,barlakas:three:20}. It is also used in
+\citet{ekelund:using:20}, where the approach is described more in detail. In
+the cited articles, the sensor's footprint has been considered in varying
+degree, as ``beam filling'' must be considered at high impact of hydrometeors.
+As clear-sky and weak cloud interference are in focus in this study, and to
+save calculation time, instead CloudSat data were averaged over 10\,km to form
+the atmospheric cases and standard 1D radiative transfer calculations are
+applied on each case (instead of applying an independent beam approximation
+inside a 2D or 3D atmosphere as done in cited works).
 
-The satellite is assumed to be at an altitude of 600\,km.
+[* Do we show comparison to ATMS, or do we refer to articles for ``validation''? ]
+[* Add time and latitude ranges used * ]
 
@@
 arts-2.3.????. Models and input used for absorption and hydrometeor properties
-are described below. ARTS considers a spherical Earth by default. Scattering
-calculations were made by ARTS's interface to the RT4 solver
-\citep{evans1995microwavec}. Ocean/water and land emissivities ae taken from
+are described below. Ocean/water and land emissivities are taken from
 TESSEM \citet{prigent2017sea} and TELSEM \citet{aires2011tool}, respectively.
+
+The calculations were performed for each atmospheric cases. One ''clear-sky''
+where all hydrometeors contents were set to zero, and one ``all-sky'' where IWC
+and RWC derived from CloudSat reflectivities and LWC from ERA-Interim were
+included. Both sets of calculations were were made by ARTS's interface to the
+RT4 solver \citep{evans1995microwavec}. This ``scattering solver'' was used
+also for clear-sky, to avoid a possible bias between clear-sky and all-sky for
+insignificant hydrometeor contents. RT4 handles the first two elements of the
+Stokes vector, that were converted to brightness temperatures for H- and V-
+polarisation.
 
@@
 absorption follows \citet{pwr:93}. Oxygen is in this study mainly of concern
-for the 89\,GHz CloudSat simulations. Liquid cloud water (LCW) is treated
+for the 89\,GHz CloudSat simulations. LWC was treated to be
 purely absorbing, based on \citet{ellison2007permittivity}.
@@
 comparison to RTTOV (12.?) was made (with MHS as assumed sensor) and an
-agremment around or better than 0.?\,K was found.
+agreement around or better than 0.?\,K was found.
 
@@
 %
-\dots
+[* Write later, Simon? TRO only! *]
+
+\subsection{Sensor characteristics}
+%
+The AWS satellite was assumed to be at an altitude of 600\,km. Data were
+generated for sensor viewing angles (the angle from nadir) from 0$^\circ$ to
+45$^\circ$, in steps of 5$^\circ$.
+
+AWS channels that were included, and considered as fixed in terms of positions
+and widths, are found in Table\dots [* Finish after talking to Anders at
+Omnisys. * ]
+
+[* Clarify what polarisation we assume for the different channels *]
+
+[* Inderpreet: Add equation and text about polarisation rotation (ie equations
+in the Sow) *]
+
+[* Describe settings for ATMS together with results, if included *)
 
@@
 %
-The simulations involving Fascode were done using a fixed satellite observation
-angle of 155$^\circ$ (from zenith) and a
+The simulations involving Fascod were done using a fixed satellite observation
+angle of 155$^\circ$ (from zenith) \dots
 

### 2020-04-08 aws/sensor.py
Added ATMS sensor class.

@@ -10,6 +10,18 @@ class AWS(PassiveSensor):
         self.sensor_position = np.broadcast_to(np.array([[600e3]]),
                                                self.sensor_line_of_sight.shape)
 
+class ATMS(PassiveSensor):
+
+    def __init__(self):
+        f_grid = np.array([166.5,])
+        f_grid = np.concatenate(f_grid, 183.31 + np.array([-7,-4.5,-3.0,-1.8,-1.0]))
+        f_grid *= 1e9
+        super().__init__("atms", f_grid, stokes_dimension=2)
+        self.sensor_line_of_sight = np.arange(135, 181, 5).reshape(-1, 1)
+        self.sensor_position = np.broadcast_to(np.array([[830e3]]),
+                                               self.sensor_line_of_sight.shape)
+
+
 class CloudSat(ActiveSensor):
     def __init__(self):
         range_bins = np.arange(500.0, 18e3 + 1.0, 500.0)
@@ -25,7 +37,7 @@ class CloudSat(ActiveSensor):
         self.nedt = 1.0
 
 band_166  = 166.50e9 + np.array([-0.8, 0.8]) * 1e9
-band_183l = 183.31e9 + np.linspace(-8.0, -0.8, 8.0) * 1e9;
+band_183l = 183.31e9 + np.arange(-8.0, -0.8, 8.0) * 1e9;
 band_229  = 229.00e9 + np.array([-1.0, 1.0]) * 1e9;
-band_325l = 325.15e9 + np.linspace(-9.0, -0.75, 8.0) * 1e9;
-band_325u = 325.15e9 + np.linspace(0.75, 9.0, 8.0) * 1e9;
+band_325l = 325.15e9 + np.arange(-9.0, -0.75, 8.0) * 1e9;
+band_325u = 325.15e9 + np.arange(0.75, 9.0, 8.0) * 1e9;

### 2020-04-08 aws/simulation.py

@@ -24,7 +24,9 @@ class Simulation(ArtsSimulation):
                  data_provider,
                  ice_shape = "8-Column-Aggregate"):
         scatterers = [Ice(ice_shape), Rain()]
-        absorbers = [H2O(), CloudWater()]
+        absorbers = [H2O(from_catalog=True),
+                     CloudWater(from_catalog=True),
+                     N2()]
         surface = Tessem()
         scattering_solver = RT4(nstreams=32)
         atmosphere = Atmosphere1D(absorbers=absorbers,
@@ -32,12 +34,12 @@ class Simulation(ArtsSimulation):
                                   surface=surface,
                                   catalog=LineCatalog("abs_lines_h2o_rttov.xml"))
 
+        super().__init__(atmosphere=atmosphere,
+                         data_provider=data_provider,
+                         sensors=[sensor],
+                         scattering_solver=scattering_solver)
 
         self.includes = ["general/general.arts",
                          "include_mpm89_cont.arts",
                          "general/planet_earth.arts"]
 
-        super().__init__(atmosphere=atmosphere,
-                         data_provider=data_provider,
-                         sensors=[sensor],
-                         scattering_solver=scattering_solver)

### 2020-04-08 Proposal/aws_325ghz_proposal.tex

--- 2020-03-26 Proposal/aws_325ghz.tex
@@
 \noindent
-\textbf{{\LARGE Arctic Weather Satellite (AWS) channels\\definition: Work plan}}  \vspace{5mm}\\
+\textbf{{\Large Arctic Weather Satellite (AWS) channels definition:\\Work plan}}  \vspace{5mm}\\
 {\bf Patrick Eriksson}\\
@@
 
-\bibliography{j_abbr,references}
+{\footnotesize
+ \bibliography{j_abbr,references}}
 

### 2020-04-08 Report/aws_325ghz_study.tex
A bit of new report text.

@@
 \subsubsection{Fascod}
+\label{sec:fascod}
 %
@@
 \citet{rydberg:nonga:09}, and more recently in e.g.\
-citet{eriksson:towar:20,barlakas:three:20}. It is also used in
+\citet{eriksson:towar:20,barlakas:three:20}. It is also used in
 \citet{ekelund:using:20}, where the approach is described more in detail. In
@@
 
-\subsection{Overview of the frequency bands}
+\subsection{Overview of the 183, 229 and 325\,GHz bands}
 %
-The simulations involving Fascod were done using a fixed satellite observation
-angle of 155$^\circ$ (from zenith) \dots
+The simulations in this sction are based on five Fascod climate scenarios
+(Sec.~\ref{sec:fascod}), and performed with a fixed sensor viewing angle of
+25$^\circ$. No hydrometeors are included. For simpler interpretetation of the
+results, the reflectivity is set to have no frequency variation, i.e.\ the same
+value is applied for all bands. The reflective is varied between 0 and 0.5.
+
+\subsubsection{Clear-sky brightness temperatures}
+%
+Figure~\ref{fig:tb:r00} shows brightness temperatures over the three bands, for
+a reflectivity of 0 (i.e.\ a blackbody surface). The figure takes into account
+that the 183\,GHz channels of AWS are of single-sideband character, while for
+229 and 325\,GHz averages of upper and lower sidebands are shown, plotted as
+a function from the centre frequency on the lower side.
 
@@
   \centering
-  \includegraphics[width=0.7\textwidth]{fascod_tb_r000}
-  \caption{dd}
+  \includegraphics[width=0.75\textwidth]{fascod_tb_r000}
+  \caption{Solid lines show brightness temperatures for the lower wing of the
+    183.31\,GHz transition. Dashed lines represent double-sideband measurements
+    around 325.15\,GHz, with the mean of upper and lower band shown on the low
+    side. Dash-dotted lines represent double-sideband measurements around
+    229.00\,GHz in the same manner, but only over the bandwidth of the
+    potential channel. For all three bands, spectra for all five
+    Fascod scenarios are included.}
   \label{fig:tb:r00}
@@
   \centering
-  \includegraphics[width=0.7\textwidth]{fascod_tb_r050}
+  \includegraphics[width=0.75\textwidth]{fascod_tb_r050}
   \caption{Same as figure above, but with a surface reflectivity of 0.5.}
@@
 
+For 183 and 325\,GHz the brightness temperatures increase when moving away from
+the centre frequency of the transition. The ``kinks'' in the spectra correspond
+to ozone transitions, that are both more frequent and stronger in the 325\,GHz
+range than in the 183\,GHz one. See Fig.~1 of \citet{eriksson:towar:20} for how
+the ozone transitions are distribbuted between the lower and uper 325\,GHz sideband. 
+The spectra of 183 and 325\,GHz deviate little close to the trasition
+frequency, showing that the two frequencies are of similar strength, though the
+325\,GHz one is slightly weaker. The higher deviation further out in the wings
+is due to different contribution of far wing and continuum absorption. This
+contribution is higher at 325\,GHz. The 229\,GHz brightness temperatures is
+higher than any value around 183 and 325\,GHz, as expected 229\,GHz being a
+window channel.
+
+In Figure~\ref{fig:tb:r00} the surface reflectivity is changed to 0.5, which
+should roughly correspond to the highest reflectivity encountered at these
+frequencies. The differences between the two figures are small for 183 and
+325\,GHz tor the tropical and the two summer scenarios. On the other hand,
+there is a clear impact in the wing part of 183\,GHz for the two winter
+scenarios. The same is true for 340\,GHz, but the influence of the surface
+reflectivity is considerably lower. [* Comment somewhere on the implications of
+this for retrievals at high latitudes *] Beside for the tropical case, for
+229\,GHz there is a pronounced dependendency of the surface reflectivity, e.g.\
+about 35\,K for mid-latitude winter.
+
+\subsubsection{Clear-sky relative humidity weighting functions}
+%
+\dots
+
+\subsubsection{Clear-sky transmissivities to space}
+%
+\dots
+
 \bibliography{j_abbr,references}

### 2020-04-08 aws/data.py
Random access data provider.

@@ -1,5 +1,7 @@
 import os
 import numpy as np
+import re
+import glob
 from h5py import File
 from artssat.data_provider import DataProviderBase
 
@@ -131,3 +133,50 @@ class Profiles(DataProviderBase):
             r = self.file["C"]["rwc"][i][0]
             iwc += [self.file[r][0, :]]
         return np.stack(iwc)
+
+pattern = re.compile(".*c_of_[\d]*_[\d]*_[\d]*.mat")
+
+class RandomProfile(DataProviderBase):
+    """
+    Data provider returning a random profile from a folder of orbit files.
+
+    Attributes:
+        self.path: The folder containing the input orbits.
+    """
+    def __init__(self, path):
+        """
+        """
+        super().__init__()
+        files = glob.glob(os.path.join(path, "*.mat"))
+        self.files = [f for f in files if pattern.match(f)]
+
+        def make_getter(name):
+            def getter(self, *args, **kwargs):
+                profiles = self._get_random_file()
+                index = self._get_random_index(profiles)
+                fget = getattr(profiles, "get_" + name)
+                return fget(index)
+            return getter
+
+        getters = ["y_cloudsat",
+                   "cloudsat_range_bins",
+                   "pressure",
+                   "temperature",
+                   "surface_temperature",
+                   "altitude",
+                   "H2O",
+                   "cloud_water",
+                   "surface_altitude",
+                   "surface_windspeed",
+                   "surface_wind_direction",
+                   "latitude",
+                   "longitude"]
+
+        for g in getters:
+            self.__dict__["get_" + g] = make_getter(g).__get__(self)
+
+    def _get_random_file(self):
+        return Profiles(self.files[np.random.randint(len(self.files))])
+
+    def _get_random_index(self, profiles):
+        return np.random.randint(profiles.n_profiles)

### 2020-04-08 aws/retrieval.py

@@ -114,3 +114,7 @@ class Retrieval(Simulation, DataProviderBase):
         if self.rwc[i] is None:
             self.run(i, silent=True)
         return self.rwc[i]
+
+    def __setstate__(self, state):
+        self.__dict__ = state
+        self.setup()

### 2020-04-08 aws/simulation.py

@@ -43,3 +43,4 @@ class Simulation(ArtsSimulation):
                          "include_mpm89_cont.arts",
                          "general/planet_earth.arts"]
 
+

### 2020-04-09 Report/aws_325ghz_study.tex
A first versio of Sec 3.1.

@@
 
+[* Tbs, transmissivities and Jacobians are averaged over the channels *]
+
 [* Describe settings for ATMS together with results, if included *)
@@
 %
-The simulations in this sction are based on five Fascod climate scenarios
+The simulations in this section are based on five Fascod climate scenarios
 (Sec.~\ref{sec:fascod}), and performed with a fixed sensor viewing angle of
-25$^\circ$. No hydrometeors are included. For simpler interpretetation of the
+25$^\circ$. No hydrometeors are included. For simpler interpretation of the
 results, the reflectivity is set to have no frequency variation, i.e.\ the same
@@
 
+In the figures covering transmissivities and Jacobians, ICI's 325\,GHz channels
+are applied (Table~?).
+
 \subsubsection{Clear-sky brightness temperatures}
 %
-Figure~\ref{fig:tb:r00} shows brightness temperatures over the three bands, for
+Figure~\ref{fig:tb:r000} shows brightness temperatures over the three bands, for
 a reflectivity of 0 (i.e.\ a blackbody surface). The figure takes into account
@@
     Fascod scenarios are included.}
-  \label{fig:tb:r00}
+  \label{fig:tb:r000}
 \end{figure}
@@
   \caption{Same as figure above, but with a surface reflectivity of 0.5.}
-  \label{fig:tb:r00}
+  \label{fig:tb:r050}
+\end{figure}
+\begin{figure}[p]
+  \centering
+  \includegraphics[width=0.75\textwidth]{fascod_tr_mls}
+  \caption{Transmissivity to space as a function of altitude, for the
+    mid-latitude summer scenario. Solid lines represent 183\,GHz channels,
+    dashed lines 325\,GHz channels (ICI-5/6/7) and dashed-dotted the 229\,GHz
+    channel. These transmissivities are independent of surface reflectivity.}
+  \label{fig:tr:mls}
+\end{figure}
+\begin{figure}[p]
+  \centering
+  \includegraphics[width=0.75\textwidth]{fascod_wf_mls_025}
+  \caption{Jacobians for relative humidity. Line symbols as in Fig.~\ref{fig:tr:mls}.
+    Surface reflectivity is set to 0.25.}
+  \label{fig:wf:mls:025}
 \end{figure}
@@
 range than in the 183\,GHz one. See Fig.~1 of \citet{eriksson:towar:20} for how
-the ozone transitions are distribbuted between the lower and uper 325\,GHz sideband. 
-The spectra of 183 and 325\,GHz deviate little close to the trasition
+the ozone transitions are distributed between the lower and upper 325\,GHz
+sideband. The spectra of 183 and 325\,GHz deviate little close to the transition
 frequency, showing that the two frequencies are of similar strength, though the
-325\,GHz one is slightly weaker. The higher deviation further out in the wings
-is due to different contribution of far wing and continuum absorption. This
-contribution is higher at 325\,GHz. The 229\,GHz brightness temperatures is
-higher than any value around 183 and 325\,GHz, as expected 229\,GHz being a
-window channel.
+325\,GHz one is slightly weaker. The higher deviations further out in the wings
+are due to different contribution of far wing and continuum absorption, that is
+higher at 325\,GHz. The 229\,GHz brightness temperatures is higher than any
+value around 183 and 325\,GHz, as expected 229\,GHz being a window channel.
 
-In Figure~\ref{fig:tb:r00} the surface reflectivity is changed to 0.5, which
+In Figure~\ref{fig:tb:r050} the surface reflectivity is changed to 0.5, which
 should roughly correspond to the highest reflectivity encountered at these
-frequencies. The differences between the two figures are small for 183 and
-325\,GHz tor the tropical and the two summer scenarios. On the other hand,
+frequencies. The differences to Fig.~\ref{fig:tb:r000}  are small for 183 and
+325\,GHz for the tropical and the two summer scenarios. On the other hand,
 there is a clear impact in the wing part of 183\,GHz for the two winter
@@
 this for retrievals at high latitudes *] Beside for the tropical case, for
-229\,GHz there is a pronounced dependendency of the surface reflectivity, e.g.\
+229\,GHz there is a pronounced dependency of the surface reflectivity, e.g.\
 about 35\,K for mid-latitude winter.
+
+\subsubsection{Clear-sky transmissivities to space}
+%
+Assuming that a cloud layer can be moved in altitude, its impact on measured
+brightness temperatures will roughly follow the transmissivity to space for the
+cloud altitude. In short, where the transmissivity is zero the cloud will have
+no impact, while where the transmissivity is unity the influence will be close
+to constant with altitude (especially when the single scattering albedo is
+high). This relationship just refers to the relative impact for a
+given frequency, the absolute impact (at transmissivity 1) increases in general
+with frequency.
+
+Figure~\ref{fig:tr:mls} displays examples on transmissivities to space. The
+transmissivities refers to the up-welling radiation. The contribution from
+reflected down-welling is neglected and the considered transmissivity does not
+depend on surface reflectivity.
+
+The altitude variation of transmissivity exhibits same basic shape between all
+the 183 and 325\,GHz channels, but the altitude of optical thickness of 1
+(transmissivity of $e^{-1}\approx0.37$) varies. The curves of the end 183\,GHz
+channels brackets the ones corresponding to the ICI 325\,GHZ channels. The later
+channels show a higher deviation from 1 at 150\,hPa, due to some (weak) ozone
+attenuation in the stratosphere. The 229\,GHz has the highest transmissivities.
 
@@
 %
-\dots
+The sensitivity to humidity is most easily compared by the channels' weighting
+functions (i.e.\ the Jacobian), and examples are found in
+Fig.~\ref{fig:wf:mls:025}. The shape of the weighting functions depends on the
+unity selected for representing water vapour. As the absolute amount of water
+vapour varies with orders of magnitude from the surface to the tropopause, it
+is difficult to interpret weighting functions for absolute humidity units and
+it is more suitable to use a relative one. In Fig.~\ref{fig:wf:mls:025} the
+weighting functions correspond to an increase of relative humidity (RH) with one
+percent unit over 1\,km. RH with respect liquid/ice is applied above/below
+0$^\circ$C.
 
-\subsubsection{Clear-sky transmissivities to space}
-%
-\dots
+The basic shape of the Jacobian is similar for all 183 and 325\,GHz channels,
+but the peak altitude varies. The end 183\,GHz channels brackets the 325\,GHz
+ICI ones, as for transmissivity. These Jacobians are negative, meaning that a
+change towards higher humidity results in decreased brightness temperatures.
+The 229\,GHz Jacobian is positive close to the surface, as this channel has
+sensitivity all the way down to the surface and more water vapour just above a
+reflecting surface results in higher brightness temperatures. The switch from
+negative to positive Jacobian depends on atmospheric scenario and surface
+reflectivity. For dry conditions also the outer 183 and 325\,GHz channels can
+have a positive part, as long as the reflectivity is not close to 0.
 

### 2020-04-13 aws/data.py
Simulations seem to be finally running.

@@ -84,6 +84,14 @@ class Profiles(DataProviderBase):
         data = self.file[r][0, :]
         return data
 
+    def get_N2(self, i):
+        z = self.get_altitude(i)
+        return 0.781 * np.ones(z.shape)
+
+    def get_O2(self, i):
+        z = self.get_altitude(i)
+        return 0.209 * np.ones(z.shape)
+
     def get_cloud_water(self, i):
         r = self.file["C"]["lwc"][i][0]
         data = self.file[r][0, :]
@@ -102,6 +110,11 @@ class Profiles(DataProviderBase):
     def get_surface_wind_direction(self, i):
         r = self.file["C"]["wind_dir"][i][0]
         data = self.file[r][0, :]
+        return data
+
+    def get_surface_type(self, i):
+        r = self.file["C"]["i_surface"][i][0]
+        data = np.round(self.file[r][0, :])
         return data
 
     def get_latitude(self, i):
@@ -134,7 +147,7 @@ class Profiles(DataProviderBase):
             iwc += [self.file[r][0, :]]
         return np.stack(iwc)
 
-pattern = re.compile(".*c_of_[\d]*_[\d]*_[\d]*.mat")
+pattern = re.compile(".*c_of_([\d]*)_([\d]*)_([\d]*).mat")
 
 class RandomProfile(DataProviderBase):
     """
@@ -148,35 +161,60 @@ class RandomProfile(DataProviderBase):
         """
         super().__init__()
         files = glob.glob(os.path.join(path, "*.mat"))
+        self.path = path
         self.files = [f for f in files if pattern.match(f)]
 
+        self.cycle = 1000000
+        np.random.seed(666)
+        self.file_indices = np.random.randint(0, len(files), size=self.cycle)
+        self.profile_indices = np.random.randint(0, len(files), size=self.cycle)
+
         def make_getter(name):
-            def getter(self, *args, **kwargs):
-                profiles = self._get_random_file()
-                index = self._get_random_index(profiles)
+            def getter(self, i):
+                profiles = self._get_random_file(i)
+                ri = self._get_random_index(profiles, i)
                 fget = getattr(profiles, "get_" + name)
-                return fget(index)
+                return fget(ri)
             return getter
 
         getters = ["y_cloudsat",
                    "cloudsat_range_bins",
                    "pressure",
                    "temperature",
-                   "surface_temperature",
                    "altitude",
-                   "H2O",
-                   "cloud_water",
-                   "surface_altitude",
-                   "surface_windspeed",
[…]

### 2020-04-13 aws/retrieval.py

@@ -3,7 +3,9 @@ import numpy as np
 from aws.simulation import Simulation
 from aws.sensor import CloudSat
 from artssat.jacobian import Log10
+from artssat.atmosphere.surface import Tessem
 from artssat.data_provider import DataProviderBase
+from artssat.atmosphere.absorption import O2
 
 class RainAPriori(DataProviderBase):
     def __init__(self):
@@ -77,7 +79,10 @@ class Retrieval(Simulation, DataProviderBase):
                             data_provider,
                             ice_shape=ice_shape)
 
+        self.atmosphere.absorbers += [O2(model="PWR98")]
+
         scatterers = self.atmosphere.scatterers
+        self.atmosphere._surface = Tessem()
         # Add first moment ice to retrieval and set transform
         ice = [s for s in scatterers if s.name == "ice"][0]
         self.retrieval.add(ice.moments[0])
@@ -90,30 +95,32 @@ class Retrieval(Simulation, DataProviderBase):
         rain.moments[0].transformation = Log10()
         self._rain_water_content = rain.moments[0]
 
-        self.iwc = [None] * data_provider.n_profiles
-        self.rwc = [None] * data_provider.n_profiles
-
         self.retrieval.settings["stop_dx"] = 1e-6
         self.setup()
+        self.cache_index = None
+
+        self.iwc = None
+        self.rwc = None
 
     def run(self, i, silent=False):
 
         self.retrieval.settings["display_progress"] = int(not silent)
         Simulation.run(self, i)
-        self.iwc[i] = self.retrieval.results.get_result(self._ice_water_content,
-                                                        transform_back=True)
-        self.rwc[i] = self.retrieval.results.get_result(self._rain_water_content,
-                                                        transform_back=True)
+        self.cache_index = i
+        self.iwc = self.retrieval.results.get_result(self._ice_water_content,
+                                                     transform_back=True)
+        self.rwc = self.retrieval.results.get_result(self._rain_water_content,
+                                                     transform_back=True)
 
     def get_ice_water_content(self, i):
-        if self.iwc[i] is None:
+        if not self.cache_index == i:
             self.run(i, silent=True)
-        return self.iwc[i]
+        return self.iwc
 
     def get_rain_water_content(self, i):
-        if self.rwc[i] is None:
+        if not self.cache_index == i:
             self.run(i, silent=True)
-        return self.rwc[i]
+        return self.rwc
 
     def __setstate__(self, state):
         self.__dict__ = state

### 2020-04-13 aws/sensor.py

@@ -14,7 +14,7 @@ class ATMS(PassiveSensor):
 
     def __init__(self):
         f_grid = np.array([166.5,])
-        f_grid = np.concatenate(f_grid, 183.31 + np.array([-7,-4.5,-3.0,-1.8,-1.0]))
+        f_grid = np.concatenate([f_grid, 183.31 + np.array([-7,-4.5,-3.0,-1.8,-1.0])])
         f_grid *= 1e9
         super().__init__("atms", f_grid, stokes_dimension=2)
         self.sensor_line_of_sight = np.arange(135, 181, 5).reshape(-1, 1)

### 2020-04-13 aws/simulation.py

@@ -3,10 +3,10 @@ import os
 from artssat import ArtsSimulation
 from artssat.atmosphere import Atmosphere1D
 from artssat.atmosphere.absorption import H2O, CloudWater, O2, N2
-from artssat.atmosphere.surface import Tessem
+from artssat.atmosphere.surface import CombinedSurface, Tessem, Telsem
 from artssat.scattering.solvers import RT4
 from artssat.atmosphere.catalogs import LineCatalog
-from pyarts.workspace.api import include_path_push
+from pyarts.workspace.api import include_path_push, arts_include_path
 
 from aws.hydrometeors import Ice, Rain
 from aws.sensor import AWS
@@ -15,20 +15,26 @@ try:
     aws_path = os.path.dirname(__file__)
 except:
     aws_path = "."
+
 include_path_push(os.path.join(aws_path, "include"))
+arts_include_path += [os.path.join(aws_path, "include")]
 
 
 class Simulation(ArtsSimulation):
     def __init__(self,
                  sensor,
                  data_provider,
-                 ice_shape = "8-Column-Aggregate"):
+                 ice_shape = "8Column-Aggregate"):
         scatterers = [Ice(ice_shape), Rain()]
-        absorbers = [H2O(from_catalog=True),
-                     CloudWater(from_catalog=True),
+        absorbers = [H2O(from_catalog=True,
+                         model="MPM89"),
+                     CloudWater(from_catalog=True,
+                                model="ELL07"),
                      N2()]
-        surface = Tessem()
-        scattering_solver = RT4(nstreams=32)
+        telsem = Telsem("/home/simonpf/src/aws/data/")
+        telsem.d_max = 100e3
+        surface = CombinedSurface(Tessem(), telsem)
+        scattering_solver = RT4(nstreams=16)
         atmosphere = Atmosphere1D(absorbers=absorbers,
                                   scatterers=scatterers,
                                   surface=surface,
@@ -41,6 +47,7 @@ class Simulation(ArtsSimulation):
 
         self.includes = ["general/general.arts",
                          "include_mpm89_cont.arts",
+                         "general/agendas.arts",
                          "general/planet_earth.arts"]
 
 

### 2020-04-13 test/simulation.py

@@ -4,10 +4,9 @@ import os
 import os
 
 from aws.retrieval import Simulation, Retrieval
-from aws.data import Profiles
-from aws.sensor import AWS, band_166, band_183l, band_229, band_325l, band_325u
+from aws.sensor import ATMS
 from aws.retrieval import Retrieval
-from aws.data import Profiles
+from aws.data import RandomProfile
 
 try:
     from IPython import get_ipython
@@ -22,20 +21,14 @@ try:
 except:
     path = "."
 
-data_provider = Profiles(os.path.join(path, "..", "data", "testdata.mat"))
+data_provider = RandomProfile("/home/simonpf/Dendrite/Projects/AWS-325GHz/CasesV1")
 
 # Create the retrieval and let it act as data provider to simulations.
 retrieval = Retrieval(data_provider, "Perpendicular3BulletRosette")
 data_provider.add(retrieval)
 
 
-# Simulation
-frequencies = np.concatenate([band_166,
-                              band_183l,
-                              band_229,
-                              band_325l,
-                              band_325u])
-sensor = AWS(frequencies)
+sensor = ATMS()
 simulation = Simulation(sensor, data_provider, "Perpendicular3BulletRosette")
 simulation.setup()
-simulation.run(0)
+simulation.run(28)

### 2020-04-13 Proposal/aws_325ghz_proposal.tex

@@
 \graphicspath{{Figures/}}
+\usepackage{pdfpages}
 
@@
 
-%\newcommand{\FIXME}[1]{{\sffamily \bfseries #1}}
 \newcommand{\FIXME}[1]{{\sffamily {\bfseries \textcolor{red}{FIXME:} #1}}}
@@
 \noindent
-\textbf{{\Large Arctic Weather Satellite (AWS) channels definition:\\Work plan}}  \vspace{5mm}\\
+\textbf{{\Large Activity on the definition of the AWS
+high frequency\vspace{0.5ex}\\channels: Proposal}}  \vspace{5mm}\\
 {\bf Patrick Eriksson}\\
@@
 
+\includepdf[pages={1}]{cv_pe_1page}
+\includepdf[pages={1}]{CV_IKaur_1Page}
+
 \end{document}

### 2020-04-14 aws/retrieval.py
Avoid memory leak when pickling simulations.

@@ -68,15 +68,15 @@ class Retrieval(Simulation, DataProviderBase):
                  ice_shape = "8-ColumnAggregate"):
         sensor = CloudSat()
 
-        data_provider.add(IceAPriori())
-        data_provider.add(RainAPriori())
-        data_provider.add(ObservationErrors())
-        self.data_provider = data_provider
-
         DataProviderBase.__init__(self)
+        self.add(IceAPriori())
+        self.add(RainAPriori())
+        self.add(ObservationErrors())
+        self.add(data_provider)
+
         Simulation.__init__(self,
                             sensor,
-                            data_provider,
+                            self,
                             ice_shape=ice_shape)
 
         self.atmosphere.absorbers += [O2(model="PWR98")]
@@ -96,13 +96,14 @@ class Retrieval(Simulation, DataProviderBase):
         self._rain_water_content = rain.moments[0]
 
         self.retrieval.settings["stop_dx"] = 1e-6
-        self.setup()
         self.cache_index = None
 
         self.iwc = None
         self.rwc = None
 
     def run(self, i, silent=False):
+        if not self._setup:
+            self.setup()
 
         self.retrieval.settings["display_progress"] = int(not silent)
         Simulation.run(self, i)
@@ -121,7 +122,3 @@ class Retrieval(Simulation, DataProviderBase):
         if not self.cache_index == i:
             self.run(i, silent=True)
         return self.rwc
-
-    def __setstate__(self, state):
-        self.__dict__ = state
-        self.setup()

### 2020-04-14 aws/sensor.py

@@ -21,7 +21,6 @@ class ATMS(PassiveSensor):
         self.sensor_position = np.broadcast_to(np.array([[830e3]]),
                                                self.sensor_line_of_sight.shape)
 
-
 class CloudSat(ActiveSensor):
     def __init__(self):
         range_bins = np.arange(500.0, 18e3 + 1.0, 500.0)

### 2020-04-14 test/simulation.py

@@ -22,13 +22,21 @@ except:
     path = "."
 
 data_provider = RandomProfile("/home/simonpf/Dendrite/Projects/AWS-325GHz/CasesV1")
+data_provider_2 = RandomProfile("/home/simonpf/Dendrite/Projects/AWS-325GHz/CasesV1")
 
 # Create the retrieval and let it act as data provider to simulations.
 retrieval = Retrieval(data_provider, "Perpendicular3BulletRosette")
-data_provider.add(retrieval)
-
+retrieval.add(data_provider)
 
 sensor = ATMS()
 simulation = Simulation(sensor, data_provider, "Perpendicular3BulletRosette")
-simulation.setup()
-simulation.run(28)
+#simulation.setup()
+#simulation.run(28)
+
+import dill
+dill.dump(simulation, open("sim.pckl", "wb"))
+
+for i in range(100):
+    print(i)
+    sim = dill.load(open("sim.pckl", "rb"))
+    sim.data_provider = None

### 2020-04-14 Proposal/aws_325ghz_proposal.tex

@@
 \noindent
-\textbf{{\Large Activity on the definition of the AWS
-high frequency\vspace{0.5ex}\\channels: Proposal}}  \vspace{5mm}\\
+\textbf{{\Large Proposal for activity on the definition of the AWS\vspace{0.5ex}\\
+high frequency channels}}  \vspace{5mm}\\
 {\bf Patrick Eriksson}\\
@@
 \begin{itemize}
-\item Demonstrate that channels around 325.15\,GHz provides a basis for cloud
+\item Demonstrate that channels around 325.15\,GHz provide a basis for cloud
   filtering/correction of data measured around 183\,GHz, that is equivalent
@@
   constraints of the AWS project. Matching in terms of weighting functions between
-  183 and 325\,GHz channels could be relevant in this context.
+  183 and 325\,GHz channels and degree of freedom in the measurements should be
+  considered in the process.
 \end{itemize}
-If feasible, other ways to compare the 229 and 325\,GHz options should be
-considered, such as degree of freedom in the measurements.
 
@@
 
-Omnisys will be consulted when it comes to technical assumptions and
-constraints. It is assumed that channels at 89, 166 and 183\,GHz will be placed
-as for MWS, except that AWS 183\,GHz channels will be single sideband (covering
-the lower MWS band). If needed, assumptions for a 229\,GHz channel will be
-taken from the MWS science plan. Required input from Omnisys includes: minimum
-and maximum intermediate frequency (IF) for 325\,GHz channels, maximum number
-of channels inside this range and expected receiver noise temperature at 166,
-183 and 325\,GHz.
+Table~1 in Statement of Work will be followed for channels around 89, 166, 183
+and 229\,GHz. Omnisys will be consulted for further input on technical
+assumptions and constraints. Required input from Omnisys is: minimum and
+maximum intermediate frequency (IF) for 325\,GHz channels, maximum number of
+channels inside this range and expected receiver noise temperature at 166, 183,
+and 325\,GHz. We will also ask Omnisys for a confirmation on that 183\,GHz
+will be implemented as single-band channels (we will only consider one option
+for the 183\,GHz channels).
 
@@
 clear-sky simulations based on the background field (e.g.\
-\citet{chambon2015investigating}). The aim of both these approaches is just to
+\citet{chambon2015investigating}). The aim of these approaches is just to
 reject data with a cloud impact exceeding some brightness temperature
@@
 compared to the true cloud and noise free brightness temperature, the filtered
-data will have an uncertainty distribution that is non-Gaussian. On one side
+data will have an uncertainty distribution that is non-Gaussian. On one side,
 the distribution will be determined by the measurement noise. On the other
@@
 hand, the impact of high altitude cirrus clouds should be considerably higher.
-Weak cloud impact should mainly end up in the Rayleigh domain, where
+Weak cloud impact mainly end up in the Rayleigh domain, where
 scattering follows $\lambda^4$. For 325 vs.\ 183\,GHz, this gives a factor very
@@
 practice this can be hard to achieve due to a higher noise at 325\,GHz and
-modelling uncertainties, and the comment was added mainly to illustrate the
+modelling uncertainties, and the comment is mainly made to illustrate the
 approach.
@@
 %
-For clarity, the work as divided into a number of work packages (WPs). See
-next page. The work will be performed by (with WP responsibilities inside
-parenthesises):
+For clarity, the work as divided into a number of work packages (WPs). See next
+page. The work will be performed by, with acronym and mean activity during the
+2 month study period inside parenthesis:
 \begin{itemize}
-\item Patrick Eriksson (WP 1.1 and 3.3)
-\item Simon Pfreundschuh (WP 1.2 and 3.2)
-\item Inderpreet Kaur (WP 2.1, 2.2, and 3.1)
+\item Patrick Eriksson (PE, 25\%)
+\item Inderpreet Kaur (OK, 35\%)
+\item Simon Pfreundschuh (SP, 10\%)
 \end{itemize}
+CVs of Patrick Eriksson and Inderpreet Kaur are attached (Simon Pfreundschuh is
+PhD student).
 
@@
 \begin{itemize}
+\item Overall planning
 \item Contact Omnisys to obtain required technical information.
@@
   channel with sufficient accuracy. 
-\item Compare 183, 229 and 325\,GHz brightness temperatures and weighting
-  functions (clear-sky), for a set of climatological atmospheres. Based on
+\item Compare 183, 229 and 325\,GHz brightness temperatures, weighting
+  functions (clear-sky) and transmissivity to space (following Fig.~4 in
+  \citet{eriksson:towar:20}), for a set of climatological atmospheres.
+  Based on
   this, define preliminary specifications of 325\,GHz channels.
@@
 ``dBZ-based model system'' introduced in \citet{ekelund:using:20}. The main
-deviations to \citet{ekelund:using:20} is that some along-track averaging of
+deviations to \citet{ekelund:using:20} are that some along-track averaging of
 CloudSat data will be performed, the mapping from reflectivities will be
@@
 
-Simulations covering channels at 89, 166, 183, 229 and 325\,GHz will be made. A
+Simulations covering channels at 166, 183, 229 and 325\,GHz will be made. A
 number of scan angles, between nadir and swath edge, will be covered. A first
-batch of 100\,000 simulations will be made. If found necessary, adding more
-simulations could be possible. If time permits, extending the simulations to
-higher latitudes could also be considered.
+batch of simulations (about 100\,000, exact number TBD) will be made. If found
+necessary, adding more simulations could be possible. If time permits,
+extending the simulations to higher latitudes could also be considered.
 
@@
 A similar regression will be tested for 229\,GHz. If not working well, a
-perfect version of the approach by \citet{rekha2012potential} will be used
-instead for 229\,GHz. That is, the assumed error distribution is the one
-described in Sec.~\ref{sec:clouds},
+perfect version of the approach by \citet{rekha2012potential} will instead be
+used as reference for 229\,GHz. That is, the assumed error distribution is the
+one described in Sec.~\ref{sec:clouds},
 
@@
 
+\newpage
+\section{Financial proposal}
+%
+\subsection{Fit to engage}
+%
+We (the bidder) confirm the following;
+\begin{itemize}
+\item that the Bidder has the legal capacity to enter into the procurement contract;
+\item that the Bidder is not bankrupt or being wound up, is not having its affairs
+administered by the courts, have not entered into a judicial arrangement with creditors,
+have not suspended business activities, is not the subject of proceedings concerning
+those matters, or is not in any analogous situation arising from a similar procedure
+provided for in national legislation or regulations;
+\item that the Bidder and its key persons have not been convicted of an offence
+concerning their professional conduct by a judgement which has the force of res judicata;
+\item that the Bidder and its key persons have not been found guilty of grave
+professional misconduct;
+\item that the Bidder and its key persons have fulfilled its obligations relating to the
+payment of social security contributions or the payment of taxes in accordance with the
+legal provisions of the country in which it is established or those of the country where
+the contract is to be performed;
+\item that the Bidder and its key persons have not been the subject of a judgement which
+has the force of res judicata for fraud, corruption, involvement in a criminal organisation
+or any other illegal activity detrimental to the EUMETSAT’s interests; and,
+\item that the Bidder and its key persons are not currently subject to a suspension
+having been found guilty of misrepresentation in supplying the information required
+under the bullets hereinabove, or having failed to supply this information.
+\end{itemize}
+
+\subsection{Total overall binding price}
+%
+Department of Space, Earth and Environment at Chalmers University of Technology
+(Sweden) offers to execute the project at the Firm fixed price 14\,667 EUR. The
+price is broken down for the individual parts in the table below. There are
+only salary costs. We assume that no travelling to visit meetings will be
+requested by EUMETSAT.
+The offer is valid until end of June 2020.\\
+
+\begin{tabular}[h]{c|cccc|c}
+ WP& PE [h] & IK [h] & SP [h] & Total [h] & Cost [EUR] \\
+\hline
+1.1&	20&	4&	0&	24&	2,092 \\
+1.2&	8&	8&	16&	32&	1,863  \\
+2.1&	8&	24&	2&	34&	2,068 \\
+2.2&	4&	16&	0&	20&	1,194 \\
+3.1&	16&	44&	4&	64&	3,931 \\
+3.2&	8&	0&	8&	16&	1,105 \\
+  3.3&	16&	16&	2&	34&	2,414 \\
+  \hline
+Total&	80&	112&32&	224& 14,667 \\
+
+\end{tabular}
+
+\newpage
 {\footnotesize

### 2020-04-15 Validation/ATMS_nc.py
scripts to read ATMS data and plot the distributions of ARTS simulations and ATMS data

@@ -1,0 +1,85 @@
+"""Module for processing ATMS files
+"""
+import os
+import numpy as np
+import netCDF4 as nc
+import pandas as pd
+from parse import parse
+import datetime as dt
+import pickle
+
+class ATMS:
+    
+	def __init__(self, filePath, fileName):
+        
+		totalPath = os.path.join(filePath, fileName)
+
+#	self.fileName = 'SNDR.SNPP.ATMS.20150907T0000.m06.g001.L1B.std.v02_05.G.180910082449.nc'
+		self.dataset = nc.Dataset(totalPath, 'r+')
+
+		self.lat = self.dataset.variables["lat"][:]
+		self.lon = self.dataset.variables["lon"][:]
+		self.surf_alt = self.dataset.variables["surf_alt"][:]
+		self.antenna_temp = self.dataset.variables["antenna_temp"][:]
+		self.view_angle = self.dataset.variables["sat_zen"][:]
+
+	def doMask(self, latlims, height):
+		""" Arguments: latlims (tuple)- provide the min and max latitude limits
+#                       height- max height above which no values are to be considered
+#            returns: mask - np.array (boolean), mask based on latitude and height limits             
+		 """
+		mask_lat = (self.lat >= latlims[0]) & (self.lat <= latlims[1])
+		mask_height = (self.surf_alt < height) & (self.surf_alt >=0.0)  	
+		mask = np.logical_and(mask_lat, mask_height)
+		return mask
+        
+	def extractBT(self, mask):
+		""" arguments: mask
+		"""
+		BT_17 = self.antenna_temp[:,:,16][mask]
+		BT_18 = self.antenna_temp[:,:,17][mask]
+		BT_19 = self.antenna_temp[:,:,18][mask]
+		BT_20 = self.antenna_temp[:,:,19][mask]
+		BT_21 = self.antenna_temp[:,:,20][mask]
+		BT_22 = self.antenna_temp[:,:,21][mask]
+		lat_subset = self.lat[mask]
+		lon_subset = self.lon[mask]
+		alt_subset = self.surf_alt[mask]
+		vza_subset = self.view_angle[mask]
+		lat = pd.DataFrame(lat_subset, columns =  ['lat'])
+		lon = pd.DataFrame(lon_subset, columns =  ['lon'])
[…]

### 2020-04-15 Matlab/SetupTesting/create_fgrid.m
Work on selecting frequencies.

@@ -1,0 +1,31 @@
+% Compiles the f_grid to apply in ARTS
+%
+% FORMAT f_grid = create_fgrid
+
+% 2020-04-15 Patrick Eriksson
+
+function f_grid = create_fgrid
+
+r        = 0.5;
+n_window = 1;
+n_wing   = 5;
+
+[f_grid,f_lims,f_chs,f0] = test_f_input( '89' );
+f89 = test_f_interp(f_grid,f_lims,f_chs,r,n_window,n_window);
+
+[f_grid,f_lims,f_chs,f0] = test_f_input( '166' );
+f166 = test_f_interp(f_grid,f_lims,f_chs,r,n_window,n_window);
+
+[f_grid,f_lims,f_chs,f0] = test_f_input( '229' );
+f229 = test_f_interp(f_grid,f_lims,f_chs,r,n_window,n_window);
+
+[f_grid,f_lims,f_chs,f0] = test_f_input( '183l' );
+f183l = test_f_interp(f_grid,f_lims,f_chs,r,n_wing,n_wing);
+
+[f_grid,f_lims,f_chs,f0] = test_f_input( '325l' );
+f325l = test_f_interp(f_grid,f_lims,f_chs,r,n_wing,n_wing);
+
+[f_grid,f_lims,f_chs,f0] = test_f_input( '325u' );
+f325u = test_f_interp(f_grid,f_lims,f_chs,r,n_wing,n_wing);
+
+f_grid = [f89,f166,f183l,f229,f325l,f325u]';

### 2020-04-15 Matlab/SetupTesting/test_f_input.m

@@ -1,42 +1,58 @@
+% Provides input for test_f_interp
+%
+% FORMAT [f_grid,f_lims,f_chs,f0] = test_f_input(band)
+%
+% OUT   See test_f_interp
+% IN    band   Strng with band name.
+
+% 2020-04-15 Patrick Eriksson
+
 function [f_grid,f_lims,f_chs,f0] = test_f_input(band)
 
 
 switch band
   
+  case '89'
+    %
+    f0     = 89e9;
+    f_grid = f0 + [ -2 : 0.1 : 2 ]*1e9;
+    f_lims = f0 + [ -1 1 ]*1e9;
+    f_chs  = f0 + [ -2 2 ]*1e9; 
+  
   case '166'
     %
-    f0     = 166.5e9;
+    f0     = 165.5e9;
     f_grid = f0 + [ -1.4 : 0.05 : 1.4 ]*1e9;
-    f_lims = f0 + [ -0.8 0.8]*1e9;
-    f_chs  = f0 + [ -1.4 1.4]*1e9; 
+    f_lims = f0 + [ -0.7 0.7 ]*1e9;
+    f_chs  = f0 + [ -1.4 1.4 ]*1e9; 
   
   case '183l'
     %
-    f0     = 183.31e9;
+    f0     = 183.311e9;
     f_grid = f0 + [ -8 : 0.05 : -0.75 ]*1e9;
-    f_lims = f0 + [ -8 -0.8]*1e9;
+    f_lims = f0 + [ -7.5 -1 ]*1e9;
     f_chs  = f0 + [ -8.0 -6.0; -5.5 -3.5; -3.5 -2.5; -2.3 -1.3; -1.25 -0.75]*1e9; 
 
   case '229'
     %
     f0     = 229e9;
     f_grid = f0 + [ -1 : 0.05 : 1 ]*1e9;
-    f_lims = f0 + [ -0.8 0.8]*1e9;
+    f_lims = f0 + [ -0.5 0.5 ]*1e9;
     f_chs  = f0 + [ -1 1 ]*1e9; 
   
   case '325l'
     %
     f0     = 325.15e9;
-    f_grid = f0 + [ -9 : 0.05 : -0.7 ]*1e9;
-    f_lims = f0 + [ -9 -0.75]*1e9;
[…]

### 2020-04-15 Matlab/SetupTesting/test_f_interp.m

@@ -1,24 +1,50 @@
-function f_opt = test_f_interp(f_grid,f_lims,f_chs,r_surface,nmax,nout)
+% Testing of frequencies to apply
+%
+% FORMAT f_n = test_f_interp(f_grid,f_lims,f_chs,r_surface,nmax,nout)
+%
+% OUT   f_n      Frequency grid applied for nout
+% IN    f_grid   Fine grid. Data on this grid represents the truth. Should
+%                cover all other frequencies.
+%       f_lims   Frequency limits for equidistant sparse grid.
+%       f_chs    Edge frequencies for each channel to evaluate. One row per channel.
+%       r_surface  Surface reflectivity.
+%       nmax     Max points in sparse grid to consider
+%       nout     Return f_n and make plot for this n.
+
+% 2020-04-15 Patrick Eriksson
+
+function f_n = test_f_interp(f_grid,f_lims,f_chs,r_surface,nmax,nout)
 
 %- Get reference spectrum
 %
 Y0 = calc_atms( f_grid, r_surface );
 
 
+%- Special case of empty f_lims
+%
+if isempty(f_lims)
+  [nstart,nmax,nout] = deal( size(f_chs,1) );
+else
+  nstart = 1;
+end
+    
+
 %- Test with different n
 %
-fprintf('\n             Full band         Channel\n')
-fprintf(' n    mean      std      mex      max\n')
-fprintf('-------------------------------------\n')
+fprintf('\n             Full band                   Channel\n')
+fprintf(' n    mean      std      max     mean      std      max\n')
+fprintf('-------------------------------------------------------\n')
 %
-for n = 1 : nmax
-  if n == 1
+for n = nstart : nmax
+  if isempty(f_lims)
+    f_test    = mean( f_chs, 2 )';
+  elseif n == 1
     f_test   = (f_lims(1) + f_lims(end)) / 2;
   else
     f_test   = linspace( f_lims(1), f_lims(end), n );
   end
   [Y,atms] = calc_atms( f_test, r_surface );
-  if 1
+  if 0
     imethod = 'spline';
     if n == 1
       dY      = repmat( Y, length(f_grid), 1 );
@@ -44,24 +70,28 @@ for n = 1 : nmax
   dY     = dY - Y0;
   %
   if n == nout
-    f_opt = f_test;
-    plot( f_grid/1e9, dY );
[…]

### 2020-04-15 aws/data.py
Added option to provide clearsky data.

@@ -32,13 +32,13 @@ class Profiles(DataProviderBase):
     def n_profiles(self):
         return self.file["C"]["dBZ"].shape[0]
 
-    def get_y_cloudsat(self, i):
+    def get_y_cloudsat(self, i, **kwargs):
         r = self.file["C"]["dBZ"][i][0]
         data = self.file[r][0, :]
         data = np.maximum(data, -30.0)
         return data
 
-    def get_cloudsat_range_bins(self, i):
+    def get_cloudsat_range_bins(self, i, **kwargs):
         r = self.file["C"]["z_field"][i][0]
         z = self.file[r][0, :]
         range_bins = np.zeros(z.size + 1)
@@ -47,12 +47,12 @@ class Profiles(DataProviderBase):
         range_bins[-1] = 2 * range_bins[-2] - range_bins[-3]
         return range_bins
 
-    def get_pressure(self, i):
+    def get_pressure(self, i, **kwargs):
         r = self.file["C"]["p_grid"][i][0]
         data = self.file[r][0, :]
         return data
 
-    def get_temperature(self, i):
+    def get_temperature(self, i, **kwargs):
         r = self.file["C"]["t_field"][i][0]
         data = self.file[r][0, :]
         return data
@@ -63,12 +63,12 @@ class Profiles(DataProviderBase):
             t += [self.get_temperature(i)]
         return np.stack(t)
 
-    def get_surface_temperature(self, i):
+    def get_surface_temperature(self, i, **kwargs):
         r = self.file["C"]["t_surface"][i][0]
         data = self.file[r][0, 0]
         return data
 
-    def get_altitude(self, i):
+    def get_altitude(self, i, **kwargs):
         r = self.file["C"]["z_field"][i][0]
         data = self.file[r][0, :]
         return data
@@ -79,56 +79,56 @@ class Profiles(DataProviderBase):
             z += [self.get_altitude(i)]
         return np.stack(z)
 
-    def get_H2O(self, i):
+    def get_H2O(self, i, **kwargs):
         r = self.file["C"]["h2o"][i][0]
         data = self.file[r][0, :]
         return data
 
-    def get_N2(self, i):
+    def get_N2(self, i, **kwargs):
         z = self.get_altitude(i)
         return 0.781 * np.ones(z.shape)
 
-    def get_O2(self, i):
+    def get_O2(self, i, **kwargs):
         z = self.get_altitude(i)
         return 0.209 * np.ones(z.shape)
 
-    def get_cloud_water(self, i):
[…]

### 2020-04-15 aws/retrieval.py

@@ -113,12 +113,18 @@ class Retrieval(Simulation, DataProviderBase):
         self.rwc = self.retrieval.results.get_result(self._rain_water_content,
                                                      transform_back=True)
 
-    def get_ice_water_content(self, i):
+    def get_ice_water_content(self, i, clearsky=False):
+        if clearsky:
+            z = self.data_provider.get_altitude(i)
+            return np.zeros(z.shape)
         if not self.cache_index == i:
             self.run(i, silent=True)
         return self.iwc
 
-    def get_rain_water_content(self, i):
+    def get_rain_water_content(self, i, clearsky=False):
+        if clearsky:
+            z = self.data_provider.get_altitude(i)
+            return np.zeros(z.shape)
         if not self.cache_index == i:
             self.run(i, silent=True)
         return self.rwc

### 2020-04-15 aws/hydrometeors.py
Use sub-sampled scattering data.

@@ -79,8 +79,8 @@ class Ice(ScatteringSpecies):
             raise ValueError("{} is not a known shape. Available shapes are {}".
                              format(shape, particle_names))
 
-        scattering_data = os.path.join(data_path, "StandardHabits", name_data)
-        scattering_meta_data = os.path.join(data_path, "StandardHabits", name_meta)
+        scattering_data = os.path.join(data_path, "StandardHabits_small", name_data)
+        scattering_meta_data = os.path.join(data_path, "StandardHabits_small", name_meta)
         super().__init__("ice", psd, scattering_data, scattering_meta_data)
 
 class Rain(ScatteringSpecies):
@@ -91,6 +91,6 @@ class Rain(ScatteringSpecies):
         psd = Abel()
         psd.t_min = 270.0
 
-        scattering_data = os.path.join(data_path, "StandardHabits", "LiquidSphere.xml")
-        scattering_meta_data = os.path.join(data_path, "StandardHabits", "LiquidSphere.meta.xml")
+        scattering_data = os.path.join(data_path, "StandardHabits_small", "LiquidSphere.xml")
+        scattering_meta_data = os.path.join(data_path, "StandardHabits_small", "LiquidSphere.meta.xml")
         super().__init__("rain", psd, scattering_data, scattering_meta_data)

### 2020-04-15 Report/aws_325ghz_study.tex

@@
 
-\section{Data and methods}
+\section{Assumptions on AWS characteristics}
+%
+The assumption listed below are primarily taken for the Statement of Work
+(SoW), complemented with information provided by Anders Emrich at Omnisys
+(private communication, April 14 2020). The later data represent what Omnisys
+considers to be technically feasible inside the budget of the project.
+
+\subsection{Channel specifications}
+%
+Channels around 89, 166, 183 and 229\,GHz are assumed to be fixed, with name,
+position and widths defined in Table~\ref{tab:fixed:chs}. AWS channels 31 to 36
+will be implemented as a single front-end, but are here still considered as two
+``bands'', denoted as 166 and 183\,GHz.
+
+For 325\,GHz, it will be assumed that channels can be placed between 0.75 and
+8.0\,GHz in terms of intermediate frequency (IF), and that up to 4 channels
+inside this range can be implemented. There should be some gap between these
+channels, above 100\,-\,200\,MHz, to facilitate the technical implementation.
+For comparison, Table~\ref{tab:fixed:chs} includes also the position of the ICI
+325\,GHz channels. As the ICI channels extend to 11\,GHz in IF, they will not
+be considered for AWS but will be applied for demonstration and reference
+purposes.
+
+For simplicity, the frequency variation of all channel responses is assumed to
+be rectangular. This selection shall not be interpreted as any opinion on the
+optimal shape of these responses; a significant deviation from a rectangular
+shape should be of no concern as long as the actual shape is well
+characterised.
+
+\begin{table}[!bt]
+  \begin{minipage}[b]{0.5\linewidth}
+  \centering  
+  \begin{tabular}[c]{c|c|c}
+    Channel & Frequency   & Bandwidth \\
+    name    & [GHz] &  [MHz] \\
+    \hline
+    AWS-21  & \phantom{0}89.000 & 4000\\
+    AWS-31  & 165.500 & 2800\\
+    AWS-32  & 176.311 & 2000\\
+    AWS-33  & 178.811 & 2000\\
+    AWS-34  & 180.311 & 1000\\
+    AWS-35  & 181.511 & 1000\\
+    AWS-36  & 182.311 & \phantom{0}500\\
+    AWS-41  & 229.000 & 2000\\
+    \hline
+  \end{tabular}
+  \end{minipage}%
+  \begin{minipage}[b]{0.5\linewidth}
+  \centering  
+  \begin{tabular}[c]{c|c|c}
+    Channel & Frequency   & Bandwidth \\
+    name    & [GHz] &  [MHz] \\
+    \hline
+    ICI-5  & 325.15$\pm$9.50 & 3000\\
+    ICI-6  & 325.15$\pm$3.50 & 2400\\
+    ICI-7  & 325.15$\pm$1.50 & 1600\\
+    \hline
+  \end{tabular}
+  \end{minipage}  
+  \caption{Fixed channel position and widths. The left table covers channels of
+    AWS, with values taken from SoW. Channels AWS-21 to AWS-36 are at this
+    moment mandatory for AWS, while AWS-41 is so far tentative. The right table
+    lists the values of some channels of ICI \citep{eriksson:towar:20}.}
+  \label{tab:fixed:chs}
+\end{table}
+
+\subsection{Noise}
+%
+The nominal reciever noise temperature, $T_r$ of each band is listed in
+Table~\ref{tab:trec}. The noise of data for individual channels is calculated
+as
+\begin{equation}
+  \sigma^i = c \frac{T^i_r+T^i_a}{\sqrt{\Delta\!f^i\Delta t}}
+\end{equation}
+where $\sigma^i$ is the noise standard deviation of channel $i$, $c$ is a
+scaling factor (see below), $T^i_r$ is the reciever noise temperature of the
+channel, $T^i_a$ is the antenna temperature of the channel, $\Delta\!f^i$ is the
+bandwidth of channel and $\Delta t$ is the integration time.
+
+The factor $c$ is set to 1.2 to incorporate the additional noise caused by the
+calibration process. The bandwith applied is the one found in columns 3 of
+Table~\ref{tab:fixed:chs}. The integration time is set to match an effective
+15\,km resolution at 183\,GHz. This time was estimated to 3\,ms.
+
+\begin{table}[!bt]
+  \centering
+  \begin{tabular}[b]{c|ccccc}
+    Band [GHz]   & 89 & 166 & 183 & 229 & 325 \\
+    \hline
+    $T_r$ [K]    & 390 & 650 & 650 & {\it 1000}  & 1200 \\
+    \hline
+  \end{tabular}
+  \caption{Assumed reciever noise temperatures. The value for 229\,GHz is
+    selected by us, remaining values are present assumptions at Omnisys.}
+  \label{tab:trec}
+\end{table}
+
+\subsection{Various}
+%
+The AWS satellite is assumed to be at an altitude of 600\,km. Data were
+generated for sensor viewing angles (the angle from nadir) from 0$^\circ$ to
+45$^\circ$, in steps of 5$^\circ$.
+
+The polarisation response of the bands is not yet determined and for simplicity
+``quasi-horisontal'' (defined in same way as for e.g.\ MWS) is throughout
+assumed. Antenna temperatures are obtained as:
+\begin{equation}
+  \label{eq:polrot}
+  T_a = T_b^V\sin^2(\theta) + T_b^H\cos^2(\theta)
+\end{equation}
+where $T_b^V$/$T_b^H$ is the brightness temprature at vertical/horisontal
+polarisation, respectively, and $\theta$ is the viewing angle (from nadir).
+
+\section{Input data and software}
 
@@
 
-\subsection{Sensor characteristics}
-%
-The AWS satellite was assumed to be at an altitude of 600\,km. Data were
-generated for sensor viewing angles (the angle from nadir) from 0$^\circ$ to
-45$^\circ$, in steps of 5$^\circ$.
-
-AWS channels that were included, and considered as fixed in terms of positions
-and widths, are found in Table\dots [* Finish after talking to Anders at
-Omnisys. * ]
-
-[* Clarify what polarisation we assume for the different channels *]
-
-[* Inderpreet: Add equation and text about polarisation rotation (ie equations
-in the Sow) *]
-
-[* Tbs, transmissivities and Jacobians are averaged over the channels *]
-
-[* Describe settings for ATMS together with results, if included *)
-
 \section{Results}
@@
 value is applied for all bands. The reflective is varied between 0 and 0.5.
-
-In the figures covering transmissivities and Jacobians, ICI's 325\,GHz channels
-are applied (Table~?).
+In the figures covering transmissivities and Jacobians, the specifications
+of ICI is applied for 325\,GHz channels (Table~\ref{tab:fixed:chs}).
 
@@
     mid-latitude summer scenario. Solid lines represent 183\,GHz channels,
-    dashed lines 325\,GHz channels (ICI-5/6/7) and dashed-dotted the 229\,GHz
-    channel. These transmissivities are independent of surface reflectivity.}
+    dashed lines 325\,GHz channels and dashed-dotted the 229\,GHz channel
+    (Table~\ref{tab:fixed:chs}). These transmissivities are independent of
+    surface reflectivity.}
   \label{fig:tr:mls}
@@
 the 183 and 325\,GHz channels, but the altitude of optical thickness of 1
-(transmissivity of $e^{-1}\approx0.37$) varies. The curves of the end 183\,GHz
-channels brackets the ones corresponding to the ICI 325\,GHZ channels. The later
-channels show a higher deviation from 1 at 150\,hPa, due to some (weak) ozone
-attenuation in the stratosphere. The 229\,GHz has the highest transmissivities.
+(transmissivity of $e^{-1}\approx0.37$) varies. The curves of the edge 183\,GHz
+channels (AWS-32 and 36) brackets the ones corresponding to the ICI 325\,GHZ
+channels. The later channels show a higher deviation from 1 at 150\,hPa, due to
+some (weak) ozone attenuation in the stratosphere. The 229\,GHz has the highest
+transmissivities.
 
@@
 The basic shape of the Jacobian is similar for all 183 and 325\,GHz channels,
-but the peak altitude varies. The end 183\,GHz channels brackets the 325\,GHz
-ICI ones, as for transmissivity. These Jacobians are negative, meaning that a
-change towards higher humidity results in decreased brightness temperatures.
-The 229\,GHz Jacobian is positive close to the surface, as this channel has
-sensitivity all the way down to the surface and more water vapour just above a
-reflecting surface results in higher brightness temperatures. The switch from
-negative to positive Jacobian depends on atmospheric scenario and surface
-reflectivity. For dry conditions also the outer 183 and 325\,GHz channels can
-have a positive part, as long as the reflectivity is not close to 0.
+but the peak altitude varies. Again the edge 183\,GHz channels brackets the
+325\,GHz ICI ones, as for transmissivity. These Jacobians are negative, meaning
+that a change towards higher humidity results in decreased brightness
+temperatures. The 229\,GHz Jacobian is positive close to the surface, as this
+channel has sensitivity all the way down to the surface and more water vapour
+just above a reflecting surface results in higher brightness temperatures. The
+switch from negative to positive Jacobian depends on atmospheric scenario and
+surface reflectivity. For dry conditions also the outer 183 and 325\,GHz
+channels can have a positive part, as long as the reflectivity is not close to
+0.
+
+\section{Notes}
+\begin{itemize}
+\item Discuss selection of polarisation
+\end{itemize}
 

### 2020-04-16 Report/aws_325ghz_study.tex
Another script for figures of wfund and transmissivities.

@@
 
+\thispagestyle{empty}
 \noindent
@@
 SE-412\,96, Gothenburg, Sweden \vspace{10mm}
+
+\section*{Summary}
+%
+To written \dots
+
+\setcounter{tocdepth}{1} 
+\tableofcontents
+
+\newpage
+\setcounter{page}{1}
 
@@
 
-\begin{table}[!bt]
+\begin{table}[!b]
   \begin{minipage}[b]{0.5\linewidth}
@@
 
-\section{Results}
-
-\subsection{Overview of the 183, 229 and 325\,GHz bands}
+\section{Overview of the 183, 229 and 325\,GHz bands}
 %
@@
 
-\subsubsection{Clear-sky brightness temperatures}
+\subsection{Clear-sky brightness temperatures}
 %
@@
 
-\subsubsection{Clear-sky transmissivities to space}
+\subsection{Clear-sky transmissivities to space}
 %
@@
 
-\subsubsection{Clear-sky relative humidity weighting functions}
+\subsection{Clear-sky relative humidity weighting functions}
 %
@@
 
+\section{Preliminary options for 325\,GHz channels}
+
+\subsection{...}
+%
+\dots Fig.~\ref{fig:wfuns:325ul}
+
+\begin{figure}[!tb]
+  \centering
+  \includegraphics[height=65mm]{fascod_wf_325l_tro}\hspace{5mm}% 
+  \includegraphics[clip,trim=43 0 0 0,height=65mm]{fascod_wf_325u_tro}
+ \caption{...}
+  \label{fig:wfuns:325ul}
+\end{figure}
+
 \section{Notes}
@@
 
+{\footnotesize
 \bibliography{j_abbr,references}
+}
 

### 2020-04-16 Matlab/BasicAnalysis/mkfigs_compare_chs.m

@@ -1,0 +1,92 @@
+% Makes figures weighting functions and transmissivity to
+% space for specified channels and Fascod scenario.
+%
+% FORMAT  mkfigs_compare_chs(atm,r_surface,chs)
+
+% 2020-04-16 Patrick Eriksson
+
+function mkfigs_compare_chs(atm,r_surface,chs)
+
+
+%- Calculate spectra etc
+%
+f_fine = min(chs(:)) : 5e6 : max(chs(:))+5e6;
+%
+[~,J,T2S,Q] = calc_atms( atm, f_fine, r_surface );
+
+
+% Channel values
+%
+dz = diff( p2z_simple( Q.P_GRID(4:5) ) ) / 1e3;
+%
+J = apply_channels( f_fine, J/(100*dz), chs );
+%
+T2S = apply_channels( f_fine, T2S, chs );
+
+
+%- Legend texts
+%
+l = [];
+%
+for c = 1 : size(chs,1)
+  l{end+1} = sprintf( '%.2f GHz', mean(chs(c,:),2)/1e9 );
+end
+
+
+% Plot wfuns
+%
+figure(1)
+semilogy( J, Q.P_GRID/1e2, '-', 'LineWidth', 1 );
+%
+set( gca, 'YDir', 'rev' );
+xlabel( 'Jacobian [K/%RH/km]' );
+ylabel( 'Pressure [hPa]' );
+title( upper( atm ) );
+grid on;
+legend( l, 'Location', 'NorthWest' );
+axis([-0.025 .025 150 1000])
+
+
+% Plot transmissivities
+%
+n = size( T2S, 2 );
+%
+figure(2)
+semilogy( T2S, Q.P_GRID(end:-1:end-n+1)/1e2, '-', 'LineWidth', 1 );
+%
+set( gca, 'YDir', 'rev' );
+xlabel( 'Transmissivity to space [-]' );
+ylabel( 'Pressure [hPa]' );
+title( upper( atm ) );
+set(gca,'XTick',[0:0.1:1]);
+grid on;
+legend( l, 'Location', 'NorthWest' );
+axis([0 1 150 1000])
+
+return
+
+
+
+function [Y,J,T2S,Q] = calc_atms( atm, f_grid, r_surface )
+  %
+  Q = q_basic( atm, f_grid, r_surface );
+  %
+  % Activate Jacobian for H2O
+  Q.ABS_SPECIES(2).RETRIEVE = true;
[…]

### 2020-04-16 Matlab/SetupTesting/test_f_input.m

@@ -45,14 +45,14 @@ switch band
     f0     = 325.15e9;
     f_grid = f0 + [ -9 : 0.05 : -0.75 ]*1e9;
     f_lims = f0 + [ -8.5 -1]*1e9;
-    f_chs  = f0 + [ -8 -5.5; -5.5 -3.5; -3.5 -1.5; -1.5 -0.75]*1e9; 
+    f_chs  = f0 + [ -9 -6; -5.5 -3.5; -3.5 -1.5; -1.5 -0.75]*1e9; 
 
   case '325u'
     %
     f0     = 325.15e9;
     f_grid = f0 + [ 0.7 : 0.05 : 9 ]*1e9;
     f_lims = f0 + [ 1 8.5]*1e9;
-    f_chs  = f0 + [ 5.5 8.0; 3.5 5.5; 1.5 3.5; 0.75 1.5]*1e9; 
+    f_chs  = f0 + [ 6 9.0; 3.5 5.5; 1.5 3.5; 0.75 1.5]*1e9; 
     
   otherwise
     error( 'Unknow selectio for *band*.' );

### 2020-04-16 aws/hydrometeors.py
Added documentation describing how to launch cluster on gold servers.

@@ -59,10 +59,6 @@ class Abel(AB12):
     def moment_names(self):
         return ["water_content"]
 
-
-
-
-
 class Ice(ScatteringSpecies):
     def __init__(self,
                  shape):
@@ -79,8 +75,12 @@ class Ice(ScatteringSpecies):
             raise ValueError("{} is not a known shape. Available shapes are {}".
                              format(shape, particle_names))
 
-        scattering_data = os.path.join(data_path, "StandardHabits_small", name_data)
-        scattering_meta_data = os.path.join(data_path, "StandardHabits_small", name_meta)
+        scattering_data = os.path.join(data_path,
+                                       "StandardHabits_small",
+                                       name_data)
+        scattering_meta_data = os.path.join(data_path,
+                                            "StandardHabits_small",
+                                            name_meta)
         super().__init__("ice", psd, scattering_data, scattering_meta_data)
 
 class Rain(ScatteringSpecies):
@@ -91,6 +91,10 @@ class Rain(ScatteringSpecies):
         psd = Abel()
         psd.t_min = 270.0
 
-        scattering_data = os.path.join(data_path, "StandardHabits_small", "LiquidSphere.xml")
-        scattering_meta_data = os.path.join(data_path, "StandardHabits_small", "LiquidSphere.meta.xml")
+        scattering_data = os.path.join(data_path,
+                                       "StandardHabits_small",
+                                       "LiquidSphere.xml")
+        scattering_meta_data = os.path.join(data_path,
+                                            "StandardHabits_small",
+                                            "LiquidSphere.meta.xml")
         super().__init__("rain", psd, scattering_data, scattering_meta_data)

### 2020-04-16 docs/source/conf.py

@@ -1,0 +1,74 @@
+import sphinx_rtd_theme
+# Configuration file for the Sphinx documentation builder.
+#
+# This file only contains a selection of the most common options. For a full
+# list see the documentation:
+# https://www.sphinx-doc.org/en/master/usage/configuration.html
+
+# -- Path setup --------------------------------------------------------------
+
+# If extensions (or modules to document with autodoc) are in another directory,
+# add these directories to sys.path here. If the directory is relative to the
+# documentation root, use os.path.abspath to make it absolute, like shown here.
+#
+# import os
+# import sys
+# sys.path.insert(0, os.path.abspath('.'))
+
+
+# -- Project information -----------------------------------------------------
+
+project = 'AWS'
+copyright = '2020, Simon Pfreundschuh, Inderpreet Kaur, Patrick Eriksson'
+author = 'Simon Pfreundschuh, Inderpreet Kaur, Patrick Eriksson'
+
+# The full version, including alpha/beta/rc tags
+release = '0.1'
+
+
+# -- General configuration ---------------------------------------------------
+
+# Add any Sphinx extension module names here, as strings. They can be
+# extensions coming with Sphinx (named 'sphinx.ext.*') or your custom
+# ones.
+extensions = [
+    "sphinx_rtd_theme",
+    "sphinx.ext.autodoc",
+    "sphinx.ext.autosummary",
+    "sphinx.ext.napoleon",
+    "nbsphinx"
+]
+
+# Add any paths that contain templates here, relative to this directory.
+templates_path = ['_templates']
+
+# List of patterns, relative to source directory, that match files and
+# directories to ignore when looking for source files.
+# This pattern also affects html_static_path and html_extra_path.
+exclude_patterns = []
+
+
+# -- Options for HTML output -------------------------------------------------
+
+# The theme to use for HTML and HTML Help pages.  See the documentation for
+# a list of builtin themes.
+#
+html_theme = 'sphinx_rtd_theme'
+html_theme_options = {
+    'logo_only': False,
+    'display_version': True,
+    'prev_next_buttons_location': 'bottom',
+    'style_external_links': False,
+    'vcs_pageview_mode': '',
+    # Toc options
+    'collapse_navigation': False,
+    'sticky_navigation': False,
+    'navigation_depth': 2,
+    'includehidden': True,
+    'titles_only': False
+}
+
+# Add any paths that contain custom static files (such as style sheets) here,
[…]

### 2020-04-16 aws/data.py
Some cleaning up.

@@ -23,6 +23,7 @@ class Profiles(DataProviderBase):
             path(:code:`str`): The path to the input file.
         """
         super().__init__()
+        path = os.path.expanduser(path)
         if not os.path.exists(path):
             raise ValueError("Could not find file {}.".format(path))
         self.path = path
@@ -159,6 +160,7 @@ class RandomProfile(DataProviderBase):
     def __init__(self, path):
         """
         """
+        path = os.path.expanduser(path)
         super().__init__()
         files = glob.glob(os.path.join(path, "*.mat"))
         self.path = path

### 2020-04-16 aws/hydrometeors.py
Removed absolute paths from code.

@@ -76,10 +76,10 @@ class Ice(ScatteringSpecies):
                              format(shape, particle_names))
 
         scattering_data = os.path.join(data_path,
-                                       "StandardHabits_small",
+                                       "StandardHabits",
                                        name_data)
         scattering_meta_data = os.path.join(data_path,
-                                            "StandardHabits_small",
+                                            "StandardHabits",
                                             name_meta)
         super().__init__("ice", psd, scattering_data, scattering_meta_data)
 
@@ -92,9 +92,9 @@ class Rain(ScatteringSpecies):
         psd.t_min = 270.0
 
         scattering_data = os.path.join(data_path,
-                                       "StandardHabits_small",
+                                       "StandardHabits",
                                        "LiquidSphere.xml")
         scattering_meta_data = os.path.join(data_path,
-                                            "StandardHabits_small",
+                                            "StandardHabits",
                                             "LiquidSphere.meta.xml")
         super().__init__("rain", psd, scattering_data, scattering_meta_data)

### 2020-04-16 aws/simulation.py

@@ -10,6 +10,7 @@ from pyarts.workspace.api import include_path_push, arts_include_path
 
 from aws.hydrometeors import Ice, Rain
 from aws.sensor import AWS
+from aws import aws_path
 
 try:
     aws_path = os.path.dirname(__file__)
@@ -31,7 +32,7 @@ class Simulation(ArtsSimulation):
                      CloudWater(from_catalog=True,
                                 model="ELL07"),
                      N2()]
-        telsem = Telsem("/home/simonpf/src/aws/data/")
+        telsem = Telsem(os.path.join(aws_path, "data"))
         telsem.d_max = 100e3
         surface = CombinedSurface(Tessem(), telsem)
         scattering_solver = RT4(nstreams=16)

### 2020-04-16 aws/hydrometeors.py
Fixed simulation test.

@@ -79,7 +79,7 @@ class Ice(ScatteringSpecies):
                                        "StandardHabits",
                                        name_data)
         scattering_meta_data = os.path.join(data_path,
-                                            "StandardHabits",
+                                            "StandardHabits_small",
                                             name_meta)
         super().__init__("ice", psd, scattering_data, scattering_meta_data)
 
@@ -95,6 +95,6 @@ class Rain(ScatteringSpecies):
                                        "StandardHabits",
                                        "LiquidSphere.xml")
         scattering_meta_data = os.path.join(data_path,
-                                            "StandardHabits",
+                                            "StandardHabits_small",
                                             "LiquidSphere.meta.xml")
         super().__init__("rain", psd, scattering_data, scattering_meta_data)

### 2020-04-16 aws/simulation.py

@@ -12,13 +12,9 @@ from aws.hydrometeors import Ice, Rain
 from aws.sensor import AWS
 from aws import aws_path
 
-try:
-    aws_path = os.path.dirname(__file__)
-except:
-    aws_path = "."
 
-include_path_push(os.path.join(aws_path, "include"))
-arts_include_path += [os.path.join(aws_path, "include")]
+include_path_push(os.path.join(aws_path, "aws", "include"))
+arts_include_path += [os.path.join(aws_path, "aws", "include")]
 
 
 class Simulation(ArtsSimulation):

### 2020-04-16 test/simulation.py

@@ -26,17 +26,8 @@ data_provider_2 = RandomProfile("/home/simonpf/Dendrite/Projects/AWS-325GHz/Case
 
 # Create the retrieval and let it act as data provider to simulations.
 retrieval = Retrieval(data_provider, "Perpendicular3BulletRosette")
-retrieval.add(data_provider)
 
 sensor = ATMS()
-simulation = Simulation(sensor, data_provider, "Perpendicular3BulletRosette")
-#simulation.setup()
-#simulation.run(28)
-
-import dill
-dill.dump(simulation, open("sim.pckl", "wb"))
-
-for i in range(100):
-    print(i)
-    sim = dill.load(open("sim.pckl", "rb"))
-    sim.data_provider = None
+simulation = Simulation(sensor, retrieval, "Perpendicular3BulletRosette")
+simulation.setup()
+simulation.run(0)

### 2020-04-20 Report/aws_325ghz_study.tex
Work on the report. Polishing of text and figures. Added part in tentative channel options.

@@
 %
-Channels around 89, 166, 183 and 229\,GHz are assumed to be fixed, with name,
-position and widths defined in Table~\ref{tab:fixed:chs}. AWS channels 31 to 36
-will be implemented as a single front-end, but are here still considered as two
-``bands'', denoted as 166 and 183\,GHz.
+The specifications of channels around 89, 166, 183 and 229\,GHz are assumed to
+be fixed, with name, position and widths defined in Table~\ref{tab:fixed:chs}.
+AWS channels 31 to 36 will be implemented as a single front-end, but are here
+still considered as two ``bands'', denoted as 166 and 183\,GHz, to more easily
+separate the channels in the text.
 
@@
 channels, above 100\,-\,200\,MHz, to facilitate the technical implementation.
-For comparison, Table~\ref{tab:fixed:chs} includes also the position of the ICI
-325\,GHz channels. As the ICI channels extend to 11\,GHz in IF, they will not
+For comparison, Table~\ref{tab:fixed:chs} includes also the position of 
+325\,GHz channels of ICI. As the ICI channels extend to 11\,GHz in IF, they will not
 be considered for AWS but will be applied for demonstration and reference
@@
     AWS-36  & 182.311 & \phantom{0}500\\
-    AWS-41  & 229.000 & 2000\\
+    AWS-4X  & 229.000 & 2000\\
     \hline
@@
     AWS, with values taken from SoW. Channels AWS-21 to AWS-36 are at this
-    moment mandatory for AWS, while AWS-41 is so far tentative. The right table
+    moment mandatory for AWS, while AWS-4X is so far tentative. The right table
     lists the values of some channels of ICI \citep{eriksson:towar:20}.}
@@
 scaling factor (see below), $T^i_r$ is the reciever noise temperature of the
-channel, $T^i_a$ is the antenna temperature of the channel, $\Delta\!f^i$ is the
-bandwidth of channel and $\Delta t$ is the integration time.
+channel, $T^i_a$ is the antenna temperature of the channel, $\Delta\!f^i$ is
+the bandwidth (in terms of IF) of channel and $\Delta t$ is the integration
+time.
 
@@
 a particle size distribution (PSD) and a particle habit, together denoted as
-the particle model. The process involves an inversion of the radar data, but as
+the particle model. The process involves an inversion of the radar data, but as,
 the same particle model is used for that inversion and to map ice water content
@@
 \citet{rydberg:nonga:09}, and more recently in e.g.\
-\citet{eriksson:towar:20,barlakas:three:20}. It is also used in
+\citet{eriksson:towar:20} and \citet{barlakas:three:20}. It is also used in
 \citet{ekelund:using:20}, where the approach is described more in detail. In
@@
 are described below. Ocean/water and land emissivities are taken from
-TESSEM \citet{prigent2017sea} and TELSEM \citet{aires2011tool}, respectively.
+TESSEM \citep{prigent2017sea} and TELSEM \citep{aires2011tool}, respectively.
 
-The calculations were performed for each atmospheric cases. One ''clear-sky''
+Two calculations were performed for each atmospheric cases. One ''clear-sky''
 where all hydrometeors contents were set to zero, and one ``all-sky'' where IWC
@@
 absorption follows \citet{pwr:93}. Oxygen is in this study mainly of concern
-for the 89\,GHz CloudSat simulations. LWC was treated to be
+for the 94\,GHz CloudSat simulations. LWC was treated to be
 purely absorbing, based on \citet{ellison2007permittivity}.
@@
 comparison to RTTOV (12.?) was made (with MHS as assumed sensor) and an
-agreement around or better than 0.?\,K was found.
+agreement around or better than 0.?\,K was found [* expand *].
 
@@
 are due to different contribution of far wing and continuum absorption, that is
-higher at 325\,GHz. The 229\,GHz brightness temperatures is higher than any
+higher at 325\,GHz. The 229\,GHz brightness temperatures are higher than any
 value around 183 and 325\,GHz, as expected 229\,GHz being a window channel.
@@
 there is a clear impact in the wing part of 183\,GHz for the two winter
-scenarios. The same is true for 340\,GHz, but the influence of the surface
+scenarios. The same is true for 325\,GHz, but the influence of the surface
 reflectivity is considerably lower. [* Comment somewhere on the implications of
@@
 
-\subsection{...}
+\subsection{Impact of upper end of IF band}
 %
-\dots Fig.~\ref{fig:wfuns:325ul}
+Figure~\ref{fig:wfuns:325ul} assumes that the channel placed at the high end of
+the IF band is 3\,GHz wide (as for ICI, Table~\ref{tab:fixed:chs}), and shows
+the RH weighting function if the outer channel ends at 11, 10, 9 or 8\,GHz. The
+weighting functions for each sideband are here kept separated.
 
@@
   \includegraphics[clip,trim=43 0 0 0,height=65mm]{fascod_wf_325u_tro}
- \caption{...}
+  \caption{RH weighting functions for the lower (left) and upper (right) side
+    of the 325.15\,GHz transition. All weighting functions are for a 3\,GHz
+    bandwidth. The stated frequencies are the centre frequency of each. In
+    terms of IF range, the channels cover 8-11, 7-10, 6-9 and 5-8\,GHz (from
+    top-to-bottom in the order given in the legends). }
   \label{fig:wfuns:325ul}
 \end{figure}
+
+As expected, when the channel is moved away the centre frequency, the weighting
+function moves downwards. However, moving the channel from 5\,-\,8\,GHz to
+8\,-\,11\,GHz (in IF) results only a small shift, about 400 and 200\,m for the
+lower and upper side, respectively. In terms of the resulting double sideband
+channel the the shift would be 300\,m. Accordingly, there is little gain
+inforcing the IF range to go above 8\,GHz. As a rule of thumb, a higher ratio
+between highest and lowest IF is more costly to implement. Albeit small, a
+negative consequence of a 8\,-\,11\,GHz channel, compared to 5\,-\,8\,GHz, is
+some assymetry in the altitude response between lower and upper sideband. This
+assymetry is caused by higher continuum and far wing absorption on the upper
+side.
+
+In summary, the benefit of extending the IF band above 8\,GHz is small and
+placing channels above 8\,GHz seems unnecessary considering the limited budget
+and development time of AWS.
+
+\subsection{A three channel option}
+%
+The ICI channels give a rough RH weighting functions matching with AWS-32,
+AWS-33 and AWS-34 (Fig.~\ref{fig:wf:mls:025}), and to find a tentative three
+channel option for the AWS 325\,GHz channels specifications providing an even
+better matching were tried out. The resulting specifications are found in
+Table~\ref{tab:chs:prel} and example weighting functions are displayed in
+Fig.~\ref {fig:3ch:prel}. This option has a IF range of 1.0 to 8.0\,GHz, and
+leaves a 100\,MHz space between AWS-42 and AWS-43, and 200\,MHz space between
+AWS-41 and AWS-42.
+
+\begin{table}[!b]
+  \begin{minipage}[b]{0.5\linewidth}
+  \centering  
+  \begin{tabular}[c]{c|c|c}
+    Channel & Frequency   & Bandwidth \\
+    name    & [GHz] &  [MHz] \\
+    \hline
+    AWS-41  & 325.15$\pm$6.50 & 3000\\
+    AWS-42  & 325.15$\pm$3.55 & 2500\\
+    AWS-43  & 325.15$\pm$1.60 & 1200\\
+    \hline
+  \end{tabular}
+  \end{minipage}%
+  \begin{minipage}[b]{0.5\linewidth}
+  \centering  
+  \begin{tabular}[c]{c|c|c}
+    Channel & Frequency   & Bandwidth \\
+    name    & [GHz] &  [MHz] \\
+    \hline
+    AWS-41  & 325.15$\pm$6.60 & 2800\\
+    AWS-42  & 325.15$\pm$4.05 & 1900\\
+    AWS-43  & 325.15$\pm$2.35 & 1300\\
+    AWS-44  & 325.15$\pm$1.20 & \phantom{0}800\\
+    \hline
+  \end{tabular}
+  \end{minipage}  
+  \caption{Preliminary specifications of AWS 325\,GHz channels, in the case of
+    of three (left) and four (right) channels.}
+  \label{tab:chs:prel}
+\end{table}
+
+\begin{figure}[!tb]
+  \centering
+  \includegraphics[height=64mm]{fascod_3chopt_tro}\hspace{5mm}% 
+  \includegraphics[clip,trim=43 0 0 0,height=64mm]{fascod_3chopt_mlw}
+  \caption{RH weighting functions of the three channel option in
+    Table~\ref{tab:chs:prel}, for the Fascod tropical (left) and mid-latiude
+    winter (right) scenarios.}
+  \label{fig:3ch:prel}
+\end{figure}
+\begin{figure}[!tb]
+  \centering
+  \includegraphics[height=64mm]{fascod_4chopt_tro}\hspace{5mm}% 
+  \includegraphics[clip,trim=43 0 0 0,height=64mm]{fascod_4chopt_mlw}
+  \caption{RH weighting functions of the four channel option in
+    Table~\ref{tab:chs:prel}, for the Fascod tropical (left) and mid-latiude
+    winter (right) scenarios.}
+  \label{fig:4ch:prel}
+\end{figure}
+
+\subsection{A four channel option}
+%
+The tentative four channel option in Table~\ref{tab:chs:prel} gives a broader
+altitude coverage, towards higher altitudes, and offers weighting functions
+roughly equally spaced in altitude (Fig.~\ref {fig:4ch:prel}). This option has
+a IF range of 0.7 to 8.0\,GHz, and leaves 200\,MHz space between AWS-41 and
+AWS-42 and has 100\,MHz between the other channels.
 

### 2020-04-20 Matlab/BasicAnalysis/dofigs_fascod.m

@@ -8,35 +8,34 @@ if 0
 %
 [chs183,ch229] = channels_fixed;
 chs325         = channels_ici325ghz;
+is_ici         = true;
 
 % Results for r = 0
 %
-mkfigs_spectra_wfuns( 0, chs183, ch229, chs325 );
+mkfigs_spectra_wfuns( 0, chs183, ch229, chs325, is_ici );
 %
 print -f1 fascod_tb_r000.pdf -dpdf
 
 
 % Results for r = 0.5
 %
-mkfigs_spectra_wfuns( 0.5, chs183, ch229, chs325 );
+mkfigs_spectra_wfuns( 0.5, chs183, ch229, chs325, is_ici );
 %
 print -f1 fascod_tb_r050.pdf -dpdf
 
 % Results for r = 0.25
 %
-mkfigs_spectra_wfuns( 0.25, chs183, ch229, chs325 );
+mkfigs_spectra_wfuns( 0.25, chs183, ch229, chs325, is_ici );
 %
 print -f3 fascod_wf_mls_025.pdf -dpdf
 print -f8 fascod_tr_mls.pdf -dpdf
-
-end
 
 
 %----------------------------------------------
 %--- Wfuns in wingds of 183 and 325 GHz
 %----------------------------------------------
 
-chs=325.15e9+[-12 -10;-10 -8;-8 -6;-6 -4;-4 -2;-2 -1]*1e9;
+chs=325.15e9+[-11 -8;-10 -7;-9 -6;-8 -5]*1e9;
 %
 mkfigs_compare_chs( 'tro', 0.1, chs );
 %
@@ -45,7 +44,7 @@ axis([-0.025 0 150 1000])
 %
 print -f1 fascod_wf_325l_tro.pdf -dpdf
 
-chs=325.15e9+[10 12;8 10;6 8;4 6; 2 4;1 2]*1e9;
+chs=325.15e9+[8 11;7 10;6 9;5 8]*1e9;
 %
 mkfigs_compare_chs( 'tro', 0.1, chs );
 %
@@ -54,5 +53,33 @@ axis([-0.025 0 150 1000])
 %
 print -f1 fascod_wf_325u_tro.pdf -dpdf
 
+end
+
+
+% 3-channel set
+%
+chs183 = channels_fixed;
+ch229  = [];
[…]

### 2020-04-20 Matlab/BasicAnalysis/mkfigs_spectra_wfuns.m

@@ -1,12 +1,21 @@
 % Makes figures with spectra, weighting functions and transmissivity to
 % space for all bands and all five Fascod atmospheres.
 %
-% FORMAT  mkfigs_spectra_wfuns(r_surface,chs183,chs229,chs325)
+% FORMAT  mkfigs_spectra_wfuns(r_surface,chs183,chs229,chs325,is_ici)
+%
+% IN   r_surface   Surface reflectivity
+%      chs183      183 GHz chanels
+%      chs229      229 GHz channels. Can be empty.
+%      chs325      325 GHz chanels
+% OPT  is_ici      Set to true if ICI channels are given. Default is false.
 
 % 2020-04-07 Patrick Eriksson
 
-function mkfigs_spectra_wfuns(r_surface,chs183,chs229,chs325)
-
+function mkfigs_spectra_wfuns(r_surface,chs183,chs229,chs325,is_ici)
+%
+if nargin < 5, is_ici = false; end
+    
+    
 df = linspace( -10e9, -0.5e9, 100 );
 nf = length( df );
 
@@ -31,18 +40,19 @@ J325 = ( J325(1:nf,:,:) + J325(nf*2:-1:nf+1,:,:) ) / 2;
 
 %- 229 GHz
 %
-df   = linspace( -1e9, -0.1, 10 );
-nf   = length( df );
-c229 = 229e9;
-f229 = c229 + df;
-ftmp = c229 + [df sort(-df) ];
-%
-[Y229,J229,T229] = calc_atms( ftmp, r_surface );
-%
-Y229 = ( Y229(1:nf,:) + Y229(nf*2:-1:nf+1,:) ) / 2;
-T229 = ( T229(1:nf,:,:) + T229(nf*2:-1:nf+1,:,:) ) / 2;
-J229 = ( J229(1:nf,:,:) + J229(nf*2:-1:nf+1,:,:) ) / 2;
-
+if ~isempty(chs229)
+  df   = linspace( -1e9, -0.1, 10 );
+  nf   = length( df );
+  c229 = 229e9;
+  f229 = c229 + df;
+  ftmp = c229 + [df sort(-df) ];
+  %
+  [Y229,J229,T229] = calc_atms( ftmp, r_surface );
+  %
+  Y229 = ( Y229(1:nf,:) + Y229(nf*2:-1:nf+1,:) ) / 2;
[…]

### 2020-04-21 Report/aws_325ghz_study.tex

@@
 reflectivites are mapped to properties for the passive simulations by assuming
-a particle size distribution (PSD) and a particle habit, together denoted as
+a particle size distribution and a particle habit, together denoted as
 the particle model. The process involves an inversion of the radar data, but as,
@@
 %
-[* Write later, Simon? TRO only! *]
+As mentioned above, LWC is taken from ERA-Interim and is assumed to be totally
+absorbing. LWC is allowed to exist at temperatures below 0$^\circ$C, i.e.\
+super-cooled liquid cloud droplets are present in the simulations. In the
+mapping of CloudSat reflectivities to RWC and IWC a total separation between
+liquid and ice phase is assumed. All scattering hydrometeors at temperatures
+above 0$^\circ$C are assumed to be rain, and all below 0$^\circ$C are assumed
+to be ice hydrometeors.
+
+For RWC the particle size distribution of \citet{abel2012improved} is applied.
+The PSD of IWC follows the basic formulation applied in DARDAR, using latest
+parameter values (i.e.\ $\alpha$ and $\beta$) as given by
+\citet{amt-12-2819-2019}. This PSD can be considered as a ``two moment''
+scheme, but is here applied in a one moment manner by setting $N_0^*$ (as a
+function of temperature) following Table~5 of \citet{delanoe2014normalized},
+and letting the radar reflectivity set the remaining moment.
+
+Single scattering data are taken from \citet{eriksson:agene:18}. For ice
+hydrometeors, three habits are applied: Perpendicular 3-bullet rosette, Large
+plate aggregate and Large column aggregate. In the two later cases, the
+aggregates are complemented with single crystal data to also cover smaller
+sizes. These data describe particles assumed to have a totally random
+orientation. To apply oriented particles is much more computationally costly
+and could not be accommodated inside the study.
 
@@
 lower and upper side, respectively. In terms of the resulting double sideband
-channel the the shift would be 300\,m. Accordingly, there is little gain
+channel the the shift would be 300\,m. Accordingly, there is little gain by
 inforcing the IF range to go above 8\,GHz. As a rule of thumb, a higher ratio
@@
 AWS-33 and AWS-34 (Fig.~\ref{fig:wf:mls:025}), and to find a tentative three
-channel option for the AWS 325\,GHz channels specifications providing an even
-better matching were tried out. The resulting specifications are found in
-Table~\ref{tab:chs:prel} and example weighting functions are displayed in
-Fig.~\ref {fig:3ch:prel}. This option has a IF range of 1.0 to 8.0\,GHz, and
-leaves a 100\,MHz space between AWS-42 and AWS-43, and 200\,MHz space between
-AWS-41 and AWS-42.
+channel option an even better matching was used as constrain to set the
+specifications. The resulting values are found in Table~\ref{tab:chs:prel} and
+example weighting functions are displayed in Fig.~\ref {fig:3ch:prel}. This
+option has a IF range of 1.0 to 8.0\,GHz, and leaves a 100\,MHz space between
+AWS-42 and AWS-43, and 200\,MHz space between AWS-41 and AWS-42. That is, the
+suggestion uses the complete IF bandwidth as far as possible, that is
+technically possible.
 
@@
 a IF range of 0.7 to 8.0\,GHz, and leaves 200\,MHz space between AWS-41 and
-AWS-42 and has 100\,MHz between the other channels.
+AWS-42 and has 100\,MHz between the other channels. Also this suggestion uses
+the complete IF bandwidth.
 
-\section{Notes}
-\begin{itemize}
-\item Discuss selection of polarisation
-\end{itemize}
+\section{Discussion}
+
+\subsection{Shape of channel response functions}
+%
+The simulations have assumed rectangularly shaped response functions, for
+simplicity. We have left some frequency gaps between the channels to simplify
+the technical implementation, i.e.\ to decrease the demand on very sharp
+ransitions from high to low response. We have assumed that 100\,MHz is
+sufficient in the lower end of the IF-range and 200\,MHz in the upper part. If
+found necessary we don't see any problem in increasing the gaps, beside that
+the bandwidth decreases and the NE$\Delta$T of the channel will somewhat
+increase.
+
+\subsection{Polarisation response}
+%
+Polarisation aspects have not been considered in full detail. Some polarisation
+is induced by the surface in the simulations, but hydrometeors are assumed to
+be totally randomly oriented and do not cause polarisation. To involve oriented
+particles was not possible due to the limited time allocated for the study.
+
+The basic recommendation would be to use the same polarisation response as far
+as possible. If both quasi-horisontal and quasi-vertical bands must be applied,
+the recommedation prioritize to use the polarisation option for 183 and
+325\,GHz, to maintain a similar influence of polarisation between the bands.
+
+\section{Conclusion}
+%
+\dots
 

### 2020-05-12 Report/aws_325ghz_study.tex
short description of distribution figures

@@
 
+\subsection{Statistical comparison of simulations and ATMS}
+\begin{figure}[p]
+	\centering
+	\includegraphics[height=62mm]{ATMS_C16_distribution}\hspace{5mm}% 
+	\includegraphics[height=62mm]{ATMS_C17_distribution}
+	\includegraphics[height=62mm]{ATMS_C18_distribution}\hspace{5mm}% 
+	\includegraphics[height=62mm]{ATMS_C19_distribution}
+	\includegraphics[height=62mm]{ATMS_C20_distribution}\hspace{5mm}% 
+	\includegraphics[height=62mm]{ATMS_C21_distribution}
+	\includegraphics[height=62mm]{ATMS_C22_distribution}
+	\caption{Distributions of simulated and observed ATMS channels brightness temperatures for channels 16 - 22 and nadir viewing angle.
+The data covers latitude range $60^{\degree}$S to $60^{\degree}$N.
+Simulation "all-sky thinned" refers to the simulation dataset from which 50\% of the clear-sky simulations are removed.
+Both land and ocean measurements are considered and only daytime ATMS data is included.}
+	\label{fig:pdf:c16-22}
+\end{figure}
+Following the simulation setup described in Section 3, around 77000 cases were simulated based on randomly selected CloudSat orbits during August 2015.
+The input data was restricted between $60^{\degree}$S to $60^{\degree}$N and no differentiation was made between the observations over water and land.
+The statistical comparison of the simulations to actual ATMS data at nadir (zenith angle = $180^{\degree}$) for channels 16-22 is shown in Figure~\ref{fig:pdf:c16-22}.
+For the comparison, the daytime ATMS observations were selected.
+ For 183 GHz channels (Channels 18-22), the simulations and observations have a good agreement for clear-sky conditions although, the peak of distribution is higher than the observations.
+The fraction of cloudy observations is lower in ATMS in comparison to simulations, but in the transitional region (left of the clear sky peak), the occurence frequency of ATMS is higher.
+For example, for Channel 19 (183.31 $\pm$ 4.5GHz), the occurence rate of simulations is almost 3 times lower than the observations.
+In the present study, this transitional region is of high interest, so the fraction of cloudy simulations in the database was effectively increased by removing a fraction of the clear sky simulations.
+After testing various values of 'clear-sky removal fraction', it was found that removing 50\% of the total clear sky simulations gave a comparable match with the occurence rate of ATMS in this region.
+ This smaller dataset was used to correct the cloud impact in the simulations, discussed in the next section.
+
+\subsection{}
+
 \section{Conclusion}

### 2020-05-12 Report/aws_325ghz_study.tex
Some rearrangement of the comparison with ATMS.

--- 2020-04-21 Report/aws_325ghz_study.tex
@@
 
-[* Do we show comparison to ATMS, or do we refer to articles for ``validation''? ]
-[* Add time and latitude ranges used * ]
-
 \subsection{Radiative transfer simulations}
@@
 MPM89 \citep{liebe:89} is followed, but some parameters for the 22 and 183\,GHz
-transitions are replaced \citep{saunders2018update,turner2019amsutran}. A basic
-comparison to RTTOV (12.?) was made (with MHS as assumed sensor) and an
-agreement around or better than 0.?\,K was found [* expand *].
+transitions are replaced \citep{saunders2018update,turner2019amsutran}.
 
@@
 and could not be accommodated inside the study.
+
+\subsection{Validation of simulations}
+%
+Using the simulation setup described above, around 77000 cases were simulated
+based on randomly selected CloudSat orbits during August 2015. The input data
+were restricted between $60^{\degree}$S to $60^{\degree}$N. No differentiation
+was made between the observations over water and land.
+
+\begin{figure}[p]
+	\centering
+	\includegraphics[height=60mm]{ATMS_C16_distribution}\hspace{5mm}% 
+	\includegraphics[height=60mm]{ATMS_C17_distribution}
+	\includegraphics[height=60mm]{ATMS_C18_distribution}\hspace{5mm}% 
+	\includegraphics[height=60mm]{ATMS_C19_distribution}
+	\includegraphics[height=60mm]{ATMS_C20_distribution}\hspace{5mm}% 
+	\includegraphics[height=60mm]{ATMS_C21_distribution}
+	\includegraphics[height=60mm]{ATMS_C22_distribution}
+	\caption{Probability distribution functions (PDFs) of simulated and
+      observed ATMS channels brightness temperatures for channels 16 - 22 and
+      nadir viewing angle. The data covers latitude range $60^{\degree}$S to
+      $60^{\degree}$N. Both land and ocean measurements are considered and only
+      daytime ATMS data are included. See further the text.}
+	\label{fig:pdf:c16-22}
+\end{figure}
+
+A statistical comparison of the simulations to actual ATMS data, for channels
+16-22 at nadir (zenith angle = $180^{\degree}$), is shown in
+Figure~\ref{fig:pdf:c16-22}. For the comparison, the daytime ATMS observations
+were selected as CloudSat operates only during the day part of the orbit since
+2011. For the channels around 183\,GHz, the ATMS characteristics are not fully
+simulated. The ATMS channel widths are considered, but as AWS is only covering
+the lower wing of the 183\,GHz transition the upper sideband of ATMS is not
+included.
+
+The overall agreement is good for channels. For 183 GHz channels (Channels
+18-22), the simulations and observations have a good agreement for the part of
+the PDFs matching clear-sky conditions (the main peak of the distribution),
+albeit the simulations have a more sharp peak. This could either be caused by a
+different geographical sampling of ATMS and CloudSat or to shortcomings in the
+ERA-Interim input data. The fraction of cloudy observations is lower in ATMS in
+comparison to simulations, for brightness temperatures below about 240\.K. This
+is due to the fact that the antenna pattern is not considered in the
+simulations.
+
+In the intermediate region, the simulations have a lower occurance rate. The
+impact of hydrometeors should be somewhat higher in the upper sideband of ATMS,
+which is not reflected in the simulations, but this is not sufficient to
+explain the deviation. As this region is well covered in the simulations
+reported in Fig.~7 of \citep{eriksson:towar:20}, the deviation of concern is
+presumably also a consequence of the neglected antenna pattern. In this study,
+this transitional region is of high interest. For this reason, the PDF for a
+50\% random rejection of cases with an insignificant cloud impact is also
+shown. This PDF gives a fair match in the intermediate region (but gives an
+even higher overrepresentation at more strong cloud impacts). This smaller
+dataset will be considered in parallel below, to ensure that no fraction of the
+``cloudy'' cases is not underrepresentated in the results.
 
@@
 
+\section{Cloud correction by a simple scheme}
+%
+\dots
+
+\section{Cloud correction by QRNN}
+%
+\dots
+
 \section{Discussion}

### 2020-05-13 Report/aws_325ghz_study.tex
updated text correction scheme

@@
   \sigma^i = c \frac{T^i_r+T^i_a}{\sqrt{\Delta\!f^i\Delta t}}
+  \label{eq:noise}
 \end{equation}
@@
 %
-\dots
+
+\begin{figure}[!tb]
+	\centering
+	\includegraphics[height=65mm]{fit_C34_C42}\hspace{5mm}% 
+	\caption{Brightness temperature difference of channel-34 from channel-42 plotted against cloud impact in channel-34 (TB allsky - TB cleasky).
+The black curve represents the line of best fit as a third order polynomial.
+}
+	\label{fig:fit:c34-42}
+\end{figure}
+
+\begin{figure}[!th]
+	\centering
+	\includegraphics[height=85mm]{PDF_corrected_C34_C42}
+	\caption{Deviation of channel-34 measurements to noise free clear-sky cases.
+The various curves represent the measurements before and after correction.
+The correction according to \cite{rekha2012potential} is also shown.
+The two curves with label ``after correction'' are for two different values of noise threshold.
+}
+	\label{fig:correction:c34-42}
+\end{figure}
+
+In this section, the 325GHz three channel option  is evaluated for ice cloud correction for 183 GHz channels.
+We predict the clears-sky value for 183GHz channel based on the brightness temperatures of simulated 325GHz channel data.
+For correction, the channels from the three option 325GHz and 183GHz are matched according to their weighting functions(Figure~\ref{fig:3ch:prel}).
+From the five  183 GHz and 325 GHz combinations possible, the weighting functions for channel- 34 and channel-42 have the best match, thus we use this combination for the development of the correction scheme.
+
+A simple regression approach is implemented to estimate the clear-sky values from the measurements.
+From the simulation dataset, 40000 clear-sky and the corresponding all-sky simulations are selected to develop the correction scheme.
+Without the availability of actual data, an identical simulation dataset but with noise is used mimic the measurements.
+The noise for individual channels is calculated according to Equation~\ref{eq:noise}.
+Before deriving any relationship between the different variables, 50\% of the clear-sky simulations are removed from the dataset.
+This clear-sky removal is to remove any under-representation of cloudy simulations, as discussed in the Validation section.
+Further, the simulations from channel-34 with cloud impact greater than 25 K are considered as "too cloudy" and are not included in the correction.
+
+Among the various possible combinations of clear-sky and all-sky pairs for channel-34 and channel-43, the brightness temperature (TB)  differences of channels-34 and 42 are found to be reasonably well correlated against the channel-34 cloud impact (TB clear-sky minus all-sky ).
+Figure ~\ref{fig:fit:c34-42}  shows the scatter plot of the TB channel-34 minus TB channel-42 against the channel-34 cloud impact.
+The regression between the two variables gives the correction estimate for channel-34 all-sky measurements :
+\begin{equation}
+correction = tb^{34} + f(tb0^{42}_{as} - tb0^{32}_{cs})   
+\end{equation}
+where, $ tb^{34}$ are channel-34 measurements, and $tb0^{42}_{as}$ and $tb0^{32}_{cs}$ are channel-42 and channel-34 simulations for all-sky and clear-sky respectively. 
+The correction is applied only to cloudy measurements.
+All cases with cloud impact less than 0.2 K or greater than 25 K are termed as ``clear'' or ``too cloudy''  respectively and are not corrected.
+Further, all measurements with TB differences between channel-34 and channel-42 greater than a ``noise-index'' are not adjusted.
+This check is introduced to avoid correction of clear-sky measurements which are falsely classified as cloudy.
+the ``noise-index'' is defined as a factor the standard deviation of noise for 183GHz.
+
+The error in the predicted measurements is assessed by calculating the deviation to noise-free clear-sky observations.
+The occurrence frequency of the deviations is shown in Figure~\ref{fig:correction:c34-42}.
+When all measurements are corrected for cloud impact, the deviations should follow a gaussian distribution with zero mean.
+However, without any correction, the measurements show a strong cloud impact, which is indicated by the non-zero values to the left of the peak (orange line).
+Removing measurements with cloud impact greater than 25 K (green line) reduces the cloud impact far left but not in the intermediate region indicating that it effectively removes the ``too cloudy'' measurements.
+After adjustment, the cloudy impact in the measurements is considerably reduced, though the spread increases.
+The sensitivity of the algorithm to correctly adjust the cloudy cases is tested through two different values of the noise-index: $1 \sigma$ and $2\sigma$.
+As evident from the figure, both values gave almost similar results indicating that the algorithm can correctly identify and adjust most of the cloudy measurements.
+
+For completeness, we also include results from the cloud filtering approach described by \cite{rekha2012potential}.
+In the report, they describe the usability of 229 GHz (channel-4x) to identify the ice clouds, and filter out all measurements with TB difference between channel-32 and channel-4x greater than 4K.
+The correction approach when applied to channel-34 is also shown in the Figure (brown curve).
+The performance of cloud filtering by \cite{rekha2012potential} seems comparable with the regression approach described in this report, however they risk rejecting more than 50\% of the clear cases.
+With the regression approach, only 2-4\% of the total cases are rejected.
+
+\begin{figure}[!tb]
+	\centering
+	\includegraphics[height=70mm]{PDF_corrected_C32_C41}\hspace{5mm}% 
+	\includegraphics[height=70mm]{PDF_corrected_C33_C41}
+	\includegraphics[height=70mm]{PDF_corrected_C35_C43}\hspace{5mm}% 
+	\includegraphics[height=70mm]{PDF_corrected_C36_C43}
+	\caption{Same as for Figure~\ref{fig:correction:c34-42}, but for other possible combinations of 183GHz and 325 GHz. }
+	\label{fig:correction:allchannels}
+\end{figure}
+
+The regression approach described above is also extended to other four channel combinations and the results are shown in Figure\ref{fig:correction:allchannels}.
 

### 2020-05-14 Report/aws_325ghz_study.tex
updated correction section

@@
 %
-
 \begin{figure}[!tb]
@@
 	\includegraphics[height=85mm]{PDF_corrected_C34_C42}
-	\caption{Deviation of channel-34 measurements to noise free clear-sky cases.
+	\caption{Deviation of channel-34 measurements to noise free clear-sky simulations.
 The various curves represent the measurements before and after correction.
 The correction according to \cite{rekha2012potential} is also shown.
-The two curves with label ``after correction'' are for two different values of noise threshold.
+The two curves with label ``after correction'' are for two different values of clear-sky threshold.
+The fraction of cases rejected by the regression approach are given as ``fraction rejected'' in the title, while the number in the parentheses is fraction of cases rejected according  to \cite{rekha2012potential}.
+The average deviation for each dataset is also provided in the legend.
 }
@@
 For correction, the channels from the three option 325GHz and 183GHz are matched according to their weighting functions(Figure~\ref{fig:3ch:prel}).
-From the five  183 GHz and 325 GHz combinations possible, the weighting functions for channel- 34 and channel-42 have the best match, thus we use this combination for the development of the correction scheme.
+From the five  183 GHz and 325 GHz combinations possible, the weighting functions for channel-34 and channel-42 have the best match, thus we use this combination for the development of the correction scheme.
 
@@
 This clear-sky removal is to remove any under-representation of cloudy simulations, as discussed in the Validation section.
-Further, the simulations from channel-34 with cloud impact greater than 25 K are considered as "too cloudy" and are not included in the correction.
+Further, the simulations from channel-34 with cloud impact (clear - allsky) greater than 25 K are considered as "too cloudy" and are not included in the correction.
 
@@
 The correction is applied only to cloudy measurements.
-All cases with cloud impact less than 0.2 K or greater than 25 K are termed as ``clear'' or ``too cloudy''  respectively and are not corrected.
-Further, all measurements with TB differences between channel-34 and channel-42 greater than a ``noise-index'' are not adjusted.
-This check is introduced to avoid correction of clear-sky measurements which are falsely classified as cloudy.
-the ``noise-index'' is defined as a factor the standard deviation of noise for 183GHz.
+If TB differences between the measurements from channel-34 and channel-42 are less than 0.2 K or are greater than 25 K, they are considered as ``clear'' or ``too cloudy''  respectively and are not corrected.
+Further, it is also important to not to correct the cases which are classified as cloudy, but are clear instead.
+To avoid correcting such cases, another check is introduced.
+Assuming cloud impact for clear-sky cases in channel-34 to be twice the standard deviation of noise, the corresponding TB difference between measurements from channel-34 and 42 is interpolated from the fit.
+This value is assumed to be an estimate of the ``clear-sky threshold''.
+All measurements with TB differences between channel-34 and 42 less than this threshold are assumed to be true cloudy cases and are corrected.
 
@@
 The occurrence frequency of the deviations is shown in Figure~\ref{fig:correction:c34-42}.
-When all measurements are corrected for cloud impact, the deviations should follow a gaussian distribution with zero mean.
-However, without any correction, the measurements show a strong cloud impact, which is indicated by the non-zero values to the left of the peak (orange line).
-Removing measurements with cloud impact greater than 25 K (green line) reduces the cloud impact far left but not in the intermediate region indicating that it effectively removes the ``too cloudy'' measurements.
-After adjustment, the cloudy impact in the measurements is considerably reduced, though the spread increases.
-The sensitivity of the algorithm to correctly adjust the cloudy cases is tested through two different values of the noise-index: $1 \sigma$ and $2\sigma$.
-As evident from the figure, both values gave almost similar results indicating that the algorithm can correctly identify and adjust most of the cloudy measurements.
+The value in parentheses in the legend is the average bias for each dataset.
+If all measurements are correctly adjusted for cloud impact, the deviations should follow the gaussian distribution of noise.
+However, without any correction, the distribution function is skewed towards the left, indicating the presence of clouds (orange line).
+This cloudy impact is slightly reduced when cases with cloud impact greater than 25 K  are removed (green line).
+The reduction is mostly for cases with low TBs, indicating ``too cloudy'' measurements.
+When the regression approach is applied to adjust the remaining cloudy cases, the cloud impact in the measurements is considerably reduced, though the spread increases (red line).
+The sensitivity of the algorithm to correctly adjust the cloudy cases two different values of the noise-index: $1 \sigma$ and $2\sigma$.
+As evident from the figure, both values give almost similar results indicating that the algorithm can correctly identify and adjust most of the cloudy measurements.
 

### 2020-05-15 Report/aws_325ghz_study.tex
updated text for cloud correction

--- 2020-05-12 Report/aws_325ghz_study.tex
@@
 %
-\dots
+\subsection{Formulation of correction scheme}
+%
+\begin{figure}[!tb]
+	\centering
+	\includegraphics[height=65mm]{fit_C34_C42}\hspace{5mm}% 
+	\caption{Brightness temperature difference of channel-34 from channel-42 plotted against cloud impact in channel-34 (TB allsky - TB cleasky).
+The black curve represents the line of best fit as a third order polynomial.
+}
+	\label{fig:fit:c34-42}
+\end{figure}
+%
+In this section, the 325GHz three channel option is evaluated for detection and correction of the ice-cloud cases in 183 GHz channels.
+Combinations of brightness temperature (TB) differences between 183 GHz and 325 Ghz are used as a measure of the cloud impact.
+A regression based approach is used to estimate the adjustment need to predict the clear-sky values.
+
+Let C1 and C2 represent the one of the channels each from 183 GHz and 325 GHz respectively, and Tb1 and Tb2 represent the corresponding TB.
+The correction scheme formulates a relationship between the cloud impact in C1 to the TB differences between C1 and C2:
+\begin{equation}
+Tb1_{as}-Tb2_{cs} = f(Tb2_{as} - Tb1_{as})
+\end{equation}
+where, the subscripts ``as'' and ``cs'' denote the all-sky and clear-sky cases respectively.
+
+The combinations of C1 and C2 are selected by matching their weighting functions as shown in  Figure~\ref{fig:3ch:prel}.
+Five  183 GHz and 325 GHz paired combinations are possible, for example one such paired combination is channel-34(180.311 GHz) and channel-42 (325$\pm$3.55 GHz).
+For each of the five 183 GHz channels, the correction scheme is derived from its corresponding counterpart in 325 GHz channel.
+
+As an example, the relationship between the TB differences for C1 and C2 and the cloud impact in C1 is shown in  Figure~\ref{fig:fit:c34-42}.
+For this particular case, C1 is 180.311 GHz and C2 is 325$\pm$3.55 GHz, and around 40000 simulations are used.
+The two variables have a reasonably strong correlation for small TB differences, but as the impact of cloud increases the correlations are poor.
+The data can be fitted to linear or non-linear models.
+The fitted model can be used to interpolate the adjustment required to compensate the brightness temperature for cloudy cases.
+To avoid fitting the ``too cloudy'' cases which do not show any reasonable correlation, cases with cloud impact greater than 25 K are excluded in the fit.
+
+\subsection{Application of correction scheme}
+\begin{figure}[!th]
+	\centering
+	\includegraphics[clip,trim=0 0 0 0,height=85mm]{PDF_corrected_C34_C42}
+	\caption{Deviation of 180.311 GHz measurements to noise free clear-sky simulations before and after correction corrected using a linear, quadratic and cubic model.
+The spread of noise is also shown as reference.
+The measurements have been corrected using brightness temperatures from 325$\pm$3.55 GHz.
+}
+	\label{fig:correction:c34-42}
+\end{figure}
+%
+In this section, we test the applicability of the correction scheme in detail.
+To analyse the performance of the approach, we apply it to correct the measurements from C1.
+Without the availability of actual data, the simulation dataset but with noise is used mimic the measurements.
+The noise for individual channels is calculated according to Equation~\ref{eq:noise}.
+Since, the fit is not valid for ``too cloudy'' cases, such cases are not corrected.
+Among the measurements, cases with TB difference between C1 and C2 greater than 25 K were classifed as ``too cloudy''.
+As an initial step, no other filter is introduced in the measurements.
+
+To test the efficacy of the correction scheme, three different models :linear, quadratic and cubic are evaluated to fit the TB differences between C1 and C2. 
+The clear-sky adjustment for each measurement is calculated from all three models, and the three predicted datasets are compared.
+The error in the predicted measurements is assessed by calculating the deviation to noise-free clear-sky observations.
+The occurrence frequency of the deviations is shown in Figure~\ref{fig:correction:c34-42}.
+In this example, channel 180.311 GHz has been corrected with 325$\pm$3.55 GHz channel.
+The occurence frequency of the all measurement without any filtering/corection is also plotted as reference (orange color).
+If all measurements are devoid of any cloud impact, the deviations should follow the gaussian distribution of noise.
+However, in real scenarios, measurements are not free from the impact of clouds, which is also evident from the large skewness in the distribution.
+
+All three models are able to reduce the skewness of the distribution curve indicating similar performance for cases with high cloud impact.
+
+[** incomplete - to be added - disussion of results from three models**]
+
+The total bias in the measurements is -0.81 K, however after correction with a cubic model the bias is reduced to 0.05 K. 
+%
+\begin{figure}[!tb]
+	\centering
+	\includegraphics[height=85mm]{PDF_corrected_C34_C42_thinned}
+	\caption{Same as Figure~\ref{fig:correction:c34-42}, but for different subsets of the measurement dataset.
+The different datasets are: thinned measurements (50\% of the clear-sky cases removed), corrected measurements 1$\sigma$ (cloudy measurements are filtered with noise-threshold = 1$\sigma$), corrected measurements 2$\sigma$(cloudy measurements are filtered with noise-threshold = 2$\sigma$), sreerekha et al (cloud filtering according to criteria described in \cite{rekha2012potential}) }
+	\label{fig:correction:c34-42:thinned}
+\end{figure}
+%
+The results from the correction approach using the cubic  model are promising, however they lack a clear-sky check.
+From Figure\ref{fig:correction:c34-42} it is evident that the majority of the measurements do not have any cloud impact.
+It is important to classify such cases correctly to avoid any undesirable adjustment.
+To avoid this two filters are introduced in the measurement dataset.
+
+In the first filter, 50\% of all measurements with noise free $Tb1_{as} - TB1_{cs} < 0.2$ are removed.
+The clear-sky thinning has two effects.
+Firstly, it helps to flag measurements without any cloud impact, and secondly it improves the representation of the cloudy cases in the database as already shown in validation against ATMS data(Figure\ref{fig:pdf:c16-22}).
+In the second filter, only measurements with cloudy adjustment greater than ``noise-threshold'' are corrected.
+The value of the noise-threshold is assumed to be of the order of the standard deviation of the noise.
+This filter is tested with two values of the noise-threshold :  $1\sigma$ and  $2\sigma$, where $\sigma$ is the standard deviation of noise.
+
+Figure~\ref{fig:correction:c34-42:thinned} shows the results when the filtered cloudy cases are corrected.
+Various metrics from the corrected measurements are also shown in Table~\ref{tab:correction:stats}.
+When cloudy measurements are filtered with noise-threshold = 1$\sigma$, around 14\% cases of the thinned dataset are classified as corrected and the average deviation in the corrected dataset is -0.069 K.
+Whereas, with noise-threshold= 2$\sigma$, only 9\% are classfied as cloudy and the average deviation is -0.117 K.
+This indicates that a larger value of noise threshold can incorrectly classify some cloudy cases as clear.
+
+\begin{table}[!bt]
+	\centering
+	\begin{tabular}[b]{c|c|c|c}
+		 Dataset & Bias & Standard & Measure\\
+		 		 & [K] & deviation[K] & skewness [K]\\	
+		\hline
+		noise & 0.006& 0.628& -0.006\\
+		all& -0.818& 4.699& -10.385\\
+		thinned& -0.465& 1.556& -5.007\\
+		$1\sigma$& -0.069& 0.904& -2.543\\
+		$2\sigma$& -0.117& 0.903& -2.597\\
+		sreerekha& -0.181& 0.731& -0.506\\
+		\hline
+	\end{tabular}
+	\caption{Various metrics for different subsets of the measurement dataset.
+The different datasets are: noise(simulation dataset),  All (all measurements are considered), thinned (50\% of clear sky measurements are removed), $1\sigma$ (cloudy measurements are filtered with noise-index = 1$\sigma$), $2\sigma$ (cloudy measurements are filtered with noise-index = 2$\sigma$), sreerekha (measurements are filtered according to criteria described in \cite{rekha2012potential})   }
+	\label{tab:correction:stats}
+\end{table}
+%
+In past, \cite{rekha2012potential} have highlighted the applicability of 229 GHz channel to identify the ice clouds.
+In the report, they use 229 GHz (channel-4x) to identify the ice clouds in 183.31$\pm$7 GHz.
+In their approach, all cases with TB difference between 229 Ghz and 183.31$\pm$7 GHz greater than 4 K as classified as cloudy.
+This information can be used to filter out the cloudy cases in all other 183 GHz channels.
+No correction is provided to the cloudy cases.
+In order to compare the performance of the correction scheme described here, the filtering scheme by \cite{rekha2012potential} is used a reference.
+The results from approach are also shown in Figure\ref{fig:correction} and Table~\ref{tab:correction:stats}.
+The performance of cloud filtering by \cite{rekha2012potential} seems comparable with the regression approach described in this report, albeit they risk rejecting more than 50\% of the clear cases.
+
+The regression approach described above is also extended to other four channel combinations and the results are shown in Figure\ref{fig:correction:allchannels}.
+ [** incomplete to be added ** add tables or figures? **]
 

### 2020-05-15 Report/aws_325ghz_study.tex
updated text for cloud correction, fixed few typos

@@
 Various metrics from the corrected measurements are also shown in Table~\ref{tab:correction:stats}.
-When cloudy measurements are filtered with noise-threshold = 1$\sigma$, around 14\% cases of the thinned dataset are classified as corrected and the average deviation in the corrected dataset is -0.069 K.
+When cloudy measurements are filtered with noise-threshold = 1$\sigma$, around 14\% cases of the thinned dataset are classified as cloudy and the average deviation in the corrected dataset is -0.069 K.
 Whereas, with noise-threshold= 2$\sigma$, only 9\% are classfied as cloudy and the average deviation is -0.117 K.
@@
 		$2\sigma$& -0.117& 0.903& -2.597\\
-		sreerekha& -0.181& 0.731& -0.506\\
+		sreerekha et al& -0.181& 0.731& -0.506\\
 		\hline
@@
 	\caption{Various metrics for different subsets of the measurement dataset.
-The different datasets are: noise(simulation dataset),  All (all measurements are considered), thinned (50\% of clear sky measurements are removed), $1\sigma$ (cloudy measurements are filtered with noise-index = 1$\sigma$), $2\sigma$ (cloudy measurements are filtered with noise-index = 2$\sigma$), sreerekha (measurements are filtered according to criteria described in \cite{rekha2012potential})   }
+The different datasets are: noise(simulation dataset),  All (all measurements are considered), thinned (50\% of clear sky measurements are removed), $1\sigma$ (cloudy measurements are filtered with noise-threshold = 1$\sigma$), $2\sigma$ (cloudy measurements are filtered with noise-threshold = 2$\sigma$), sreerekha (measurements are filtered according to criteria described in \cite{rekha2012potential})   }
 	\label{tab:correction:stats}

### 2020-05-18 Report/aws_325ghz_study.tex
Made a first version of the report's introduction section.

@@
 %
-\dots
+\subsection{Background}
+The Arctic Weather Satellite (AWS) is a small platform carrying a single
+radiometer package. This instrument is an across-track scanning microwave
+radiometer. The exact channel configuration of AWS is not yet set. The main
+issue for this report is that AWS will have channels at 183\,GHz, but also one
+or several channels a higher frequencies. A number of channels around 325\,GHz
+was considered as the main option before AWS became an ESA/EUMETSAT mission,
+but it has now also been suggested to have a single channel at 229\,GHz. This
+suggestion is based on MWS (MicroWave Sounder), one of the instruments onboard
+the next generation of Metop satellites. The 229\,GHz was added to MWS as an
+help for performing cloud screening of 183\,GHz data
+\citep{rekha2012potential}. For comparison, it can be mentioned that ICI (Ice
+Cloud Imager), another new Metop sensor, will include 325\,GHz channels.
+
+\subsection{Aim}
+%
+To support the selection between 229 and 325\,GHz channels for AWS, this report
+investigates the possibility to use the later range in forming 183\,GHz data of
+``clear-sky'' character. That is, following \citet{rekha2012potential}, the
+assumption, is that the 183\,GHz data will be used in an system not yet
+capable of doing ``all -sky'' assimilation.
+
+In \citet{rekha2012potential} the task was defined to screen out observations
+having a cloud impact exceeding 4\,K at 183$\pm$7\,GHz. Their final suggestion
+for screening does not involve data from any other channel than 229\,GHz, but
+requires radiative transfer calculations (as a ``B-O test'' is made). Only 
+screening of 183$\pm$7\,GHz was discussed.
+
+In this report, the task is defined in a somewhat different manner. The aim is
+not just to estimate the cloud impact, but also to investigate to which degree
+the cloud impact can be removed, i.e.\ to make a cloud correction. Further, in
+this report only schemes that can be based directly on AWS data will be
+considered and versions involving ``B-O tests'' are left for possible future
+studies. On the other hand, cloud correction of all AWS 183\,GHz channels are
+investigated. Another important difference is that our simulations aim to be a
+random sample of real situations, while the simulations of
+\citet{rekha2012potential} have a strong over-representation of cloudy
+cases.
+
+\subsection{Comparison to \citet{rekha2012potential}}
+%
+Results from \citet{rekha2012potential} will be used as reference. They did not
+suggest specific settings of their algorithm. The main consideration of the
+scheme is a threshold value. We assume below 6\,K for
+this value, as it used most frequently as example in
+\citet{rekha2012potential}. According to their Table~3, this results in that
+2.4\% of the ``cloudy'' cases are miss-classified as ``clear''. We assume that
+these cases have a cloud impact of 4 to 8\,K (i.e.\ the screening is 100\%
+successful for cloud impact above 8\,K). For a 6\,K threshold 41\% of the
+``clear'' cases are classified as ``cloudy'' and a removed in the screening
+process.
+
+The selected threshold value is towards the high side of the ones considered by 
+\citet{rekha2012potential}. A lower value improves the removal of ``cloudy'' cases,
+but the fraction of incorrectly removed ``clear'' cases increases quickly. For
+example, a threshold of 3\,K decreases the miss-classification of ``cloudy''
+cases to 0.6\%, but increases the miss-classification for ``clear'' cases to 77\%.
+If 183$\pm$7\,GHz is classified as cloudy, we assume that also the data from
+other 183\,GHz channels are rejected.
 
@@
 insignificant hydrometeor contents. RT4 handles the first two elements of the
-Stokes vector, that were converted to brightness temperatures for H- and V-
-polarisation.
+Stokes vector, that were converted to brightness temperatures for H- and
+V-polarisation.
 
@@
 MPM89 \citep{liebe:89} is followed, but some parameters for the 22 and 183\,GHz
-transitions are replaced \citep{saunders2018update,turner2019amsutran}.
+transitions are replaced \citep{saunders2018update,turner2019amsutran}. A
+smaller comparison to RTTOV has been made, that indciated an agreement better
+than 0.1\,K in general. Deviations between 0.1 and 0.2\,K were found for some
+channels at incidence angles above 40$^\circ$.
 
@@
 
-\begin{figure}[!tb]
-  \centering
-  \includegraphics[height=65mm]{fascod_wf_325l_tro}\hspace{5mm}% 
-  \includegraphics[clip,trim=43 0 0 0,height=65mm]{fascod_wf_325u_tro}
-  \caption{RH weighting functions for the lower (left) and upper (right) side
-    of the 325.15\,GHz transition. All weighting functions are for a 3\,GHz
-    bandwidth. The stated frequencies are the centre frequency of each. In
-    terms of IF range, the channels cover 8-11, 7-10, 6-9 and 5-8\,GHz (from
-    top-to-bottom in the order given in the legends). }
-  \label{fig:wfuns:325ul}
-\end{figure}
-
 As expected, when the channel is moved away the centre frequency, the weighting
@@
 
+\begin{figure}[!p]
+  \centering
+  \includegraphics[height=61mm]{fascod_wf_325l_tro}\hspace{5mm}% 
+  \includegraphics[clip,trim=43 0 0 0,height=61mm]{fascod_wf_325u_tro}
+  \caption{RH weighting functions for the lower (left) and upper (right) side
+    of the 325.15\,GHz transition. All weighting functions are for a 3\,GHz
+    bandwidth. The stated frequencies are the centre frequency of each. In
+    terms of IF range, the channels cover 8-11, 7-10, 6-9 and 5-8\,GHz (from
+    top-to-bottom in the order given in the legends). }
+  \label{fig:wfuns:325ul}
+\end{figure}
+\begin{figure}[!p]
+  \centering
+  \includegraphics[height=61mm]{fascod_3chopt_tro}\hspace{5mm}% 
+  \includegraphics[clip,trim=43 0 0 0,height=61mm]{fascod_3chopt_mlw}
+  \caption{RH weighting functions of the three channel option in
+    Table~\ref{tab:chs:prel}, for the Fascod tropical (left) and mid-latiude
+    winter (right) scenarios.}
+  \label{fig:3ch:prel}
+\end{figure}
+\begin{figure}[!p]
+  \centering
+  \includegraphics[height=61mm]{fascod_4chopt_tro}\hspace{5mm}% 
+  \includegraphics[clip,trim=43 0 0 0,height=61mm]{fascod_4chopt_mlw}
+  \caption{RH weighting functions of the four channel option in
+    Table~\ref{tab:chs:prel}, for the Fascod tropical (left) and mid-latiude
+    winter (right) scenarios.}
+  \label{fig:4ch:prel}
+\end{figure}
+
 \subsection{A three channel option}
@@
 
-\begin{table}[!b]
+\begin{table}[!t]
   \begin{minipage}[b]{0.5\linewidth}
@@
 \end{table}
-
-\begin{figure}[!tb]
-  \centering
-  \includegraphics[height=64mm]{fascod_3chopt_tro}\hspace{5mm}% 
-  \includegraphics[clip,trim=43 0 0 0,height=64mm]{fascod_3chopt_mlw}
-  \caption{RH weighting functions of the three channel option in
-    Table~\ref{tab:chs:prel}, for the Fascod tropical (left) and mid-latiude
-    winter (right) scenarios.}
-  \label{fig:3ch:prel}
-\end{figure}
-\begin{figure}[!tb]
-  \centering
-  \includegraphics[height=64mm]{fascod_4chopt_tro}\hspace{5mm}% 
-  \includegraphics[clip,trim=43 0 0 0,height=64mm]{fascod_4chopt_mlw}
-  \caption{RH weighting functions of the four channel option in
-    Table~\ref{tab:chs:prel}, for the Fascod tropical (left) and mid-latiude
-    winter (right) scenarios.}
-  \label{fig:4ch:prel}
-\end{figure}
 

### 2020-05-18 Report/aws_325ghz_study.tex
updated figures and tables, some text

@@
 	\centering
-	\includegraphics[height=65mm]{fit_C34_C42}\hspace{5mm}% 
-	\caption{Brightness temperature difference of channel-34 from channel-42 plotted against cloud impact in channel-34 (TB allsky - TB cleasky).
+	\includegraphics[height=65mm]{fit_AWS-34_AWS-42}\hspace{5mm}% 
+	\caption{Brightness temperature difference of AWS-34 from AWS-42 plotted against cloud impact in AWS-34.
 The black curve represents the line of best fit as a third order polynomial.
-}
+Red and green color represent the clear and cloudy cases respectively in the simulation dataset.
+The blue vertical line represents the clear-sky screening threshold in the measurements for noise-threshold = 0.2\,K   }
 	\label{fig:fit:c34-42}
@@
 \begin{equation}
-Tb1_{as}-Tb2_{cs} = f(Tb2_{as} - Tb1_{as})
+Tb1_{as}-Tb2_{cs} = f(x_m)
+\label{eq:TB:diff}
 \end{equation}
-where, the subscripts ``as'' and ``cs'' denote the all-sky and clear-sky cases respectively.
+where, $x_m = Tb2_{as} - Tb1_{as}$, and the subscripts ``as'' and ``cs'' denote the all-sky and clear-sky cases respectively.
 
 The combinations of C1 and C2 are selected by matching their weighting functions as shown in  Figure~\ref{fig:3ch:prel}.
-Five  183 GHz and 325 GHz paired combinations are possible, for example one such paired combination is channel-34(180.311 GHz) and channel-42 (325$\pm$3.55 GHz).
+Five  183 GHz and 325 GHz paired combinations are possible, for example one such paired combination is AWS-34(180.311 GHz) and AWS-42 (325$\pm$3.55 GHz).
 For each of the five 183 GHz channels, the correction scheme is derived from its corresponding counterpart in 325 GHz channel.
@@
 As an example, the relationship between the TB differences for C1 and C2 and the cloud impact in C1 is shown in  Figure~\ref{fig:fit:c34-42}.
-For this particular case, C1 is 180.311 GHz and C2 is 325$\pm$3.55 GHz, and around 40000 simulations are used.
+For this particular case, C1 is AWS-34 and C2 is AWS-42, and around 40000 simulations are used.
 The two variables have a reasonably strong correlation for small TB differences, but as the impact of cloud increases the correlations are poor.
@@
 The fitted model can be used to interpolate the adjustment required to compensate the brightness temperature for cloudy cases.
-To avoid fitting the ``too cloudy'' cases which do not show any reasonable correlation, cases with cloud impact greater than 25 K are excluded in the fit.
+To avoid fitting the ``too cloudy'' cases which do not show any reasonable correlation, cases with $Tb2-Tb1$< -40\,K  are excluded in the fit.
+Also, cases with $Tb2-Tb1$ < 0.2\,K (red color dots) are assumed to be clear are not included in the model.
 
+Before correcting the measurements, it is important to correctly classify all the cases into clear or cloudy.
+To avoid any undesirable adjustment of the clear cases, a clear-sky screening is added  to the correction scheme.
+In this screening, we assume that for clear cases, the average differences of the measurements to their noise-free clear-sky values are of the order of the instrument noise.
+Further in the text, we refer this value of noise as ``noise-index''.
+Assuming the function $f$ in eqn~\ref{eq:TB:diff} to be invertible, and if $x_{cs}$  represents the noise-index, the TB difference between the measurements from C1 and C2 for the noise-index can be used as a measure of clear-sky screening: ($dtb_{cs}$):
+\begin{equation}
+dtb_{cs}= f_{cs}^{-1}(x_{cs}) 
+\label{eq:dtb}
+\end{equation}
+The value of $dtb_{cs}$ is not constant and shall depend on the the combination of 183 GHz and 325 GHz used.
+The measurements with TB difference between C2 and C1 less than $dtb_{cs}$ are considered cloudy and are corrected.
+In Figure~\ref{fig:correction:c34-42}, the blue dotted line represents the clear-sky screening cut-off when noise-index = 0.2\,K.
+All measurements to the left of this line are classified as cloudy, and vice-versa.
+For the dataset shown in the figure, around 15\% of the total cases were classified as clear.
+The sensitivity of noise-index is discussed in detail in the next section.
 \subsection{Application of correction scheme}
@@
 	\centering
-	\includegraphics[clip,trim=0 0 0 0,height=85mm]{PDF_corrected_C34_C42}
-	\caption{Deviation of 180.311 GHz measurements to noise free clear-sky simulations before and after correction corrected using a linear, quadratic and cubic model.
+	\includegraphics[clip,trim=0 0 0 0,height=85mm]{PDF_corrected_AWS-34_AWS-42}
+	\caption{Deviation of AWS-34 measurements to noise free clear-sky simulations before and after correction corrected using a linear, quadratic and cubic model.
 The spread of noise is also shown as reference.
-The measurements have been corrected using brightness temperatures from 325$\pm$3.55 GHz.
+The measurements have been corrected using brightness temperatures from AWS-42.
 }
@@
 The noise for individual channels is calculated according to Equation~\ref{eq:noise}.
-Since, the fit is not valid for ``too cloudy'' cases, such cases are not corrected.
-Among the measurements, cases with TB difference between C1 and C2 greater than 25 K were classifed as ``too cloudy''.
-As an initial step, no other filter is introduced in the measurements.
+As an example, the results from the channel combination AWS-34 and AWS-42 are shown.
 
 To test the efficacy of the correction scheme, three different models :linear, quadratic and cubic are evaluated to fit the TB differences between C1 and C2.
-The clear-sky adjustment for each measurement is calculated from all three models, and the three predicted datasets are compared.
+For all three models, cases with $Tb2-Tb1 < $ -15\,K are assumed to be ``too cloudy'' and are not corrected.
+The clear-sky adjustment for all eligible measurements (without clear-sky screening) is calculated from all three models, and the three predicted datasets are compared.
 The error in the predicted measurements is assessed by calculating the deviation to noise-free clear-sky observations.
-The occurrence frequency of the deviations is shown in Figure~\ref{fig:correction:c34-42}.
-In this example, channel 180.311 GHz has been corrected with 325$\pm$3.55 GHz channel.
-The occurence frequency of the all measurement without any filtering/corection is also plotted as reference (orange color).
+The occurrence frequency of the deviations from three models is shown in Figure~\ref{fig:correction:c34-42}.
+The occurence frequency of the all measurement without any filtering or correction is also plotted as reference (orange color).
 If all measurements are devoid of any cloud impact, the deviations should follow the gaussian distribution of noise.
-However, in real scenarios, measurements are not free from the impact of clouds, which is also evident from the large skewness in the distribution.
+However, in real scenarios, the distribution is skewed due to the impact of clouds.
+It should also be noted that since no clear-sky screening was included in the measurements, the measurements with zero deviation to noise-free clear-sky were reduced.
+This indicates that it is extremely important to correctly classify the cases as clear/cloudy.
+Among the three models, the quadratic and cubic models work better than a liner model.
+Both quadratic and cubic models are able to correct the cloud impact in the measurements, however the values of average bias indicates that the cubic model performs better.
+The average deviation in the dataset is -0.82\,K and after correction with a cubic model, it reduces to -0.02\,K, while for quadratic model, the average bias after correction is 0.24\,K.
+For all other results described in this section, a cubic model is used.
 
-All three models are able to reduce the skewness of the distribution curve indicating similar performance for cases with high cloud impact.
+********
 
-[** incomplete - to be added - disussion of results from three models**]
+TEXT NOT UPDATED BELOW 
+Before applying the clear-sky screening, the measurement dataset was also thinned in order to improve the representation of the cloudy cases.
+Validation of the simulations against ATMS data(Figure\ref{fig:pdf:c16-22}) showed that the cloudy cases were a bit underrepreseneted than the observations.
+Removing 50\% of the clear-sky cases, helped in improving the percentage of total cloudy cases in the database.
 
-The total bias in the measurements is -0.81 K, however after correction with a cubic model the bias is reduced to 0.05 K. 
+To implement the clear-sky screening as discussed in the previous section, two different values of the noise-index are tested : $1\sigma$ and  $2\sigma$, where $\sigma$ is the standard deviation of noise.
+For both values of noise-index the corresponding clear-sky cut-off is calculated using Eq~\ref{eq:dtb}.
+Figure~\ref{fig:correction:c34-42:thinned} shows the results when only the screened cloudy cases are corrected.
+Various metrics from the corrected measurements are also shown in Table~\ref{tab:correction:stats}.
+When cloudy measurements are filtered with noise-index = 1$\sigma$, around 13.5\% cases of the thinned dataset are classified as cloudy and the average deviation in the corrected dataset is -0.069 K.
+Whereas, with noise-threshold= 2$\sigma$, only 7.5\% are classified as cloudy and the average deviation is -0.117 K.
+This indicates that a larger value of noise threshold can incorrectly classify some cloudy cases as clear.
 %
@@
 	\centering
-	\includegraphics[height=85mm]{PDF_corrected_C34_C42_thinned}
+	\includegraphics[height=85mm]{PDF_corrected_AWS-34_AWS-42_thinned}
 	\caption{Same as Figure~\ref{fig:correction:c34-42}, but for different subsets of the measurement dataset.
@@
 %
-The results from the correction approach using the cubic  model are promising, however they lack a clear-sky check.
-From Figure\ref{fig:correction:c34-42} it is evident that the majority of the measurements do not have any cloud impact.
-It is important to classify such cases correctly to avoid any undesirable adjustment.
-To avoid this two filters are introduced in the measurement dataset.
-
-In the first filter, 50\% of all measurements with noise free $Tb1_{as} - TB1_{cs} < 0.2$ are removed.
-The clear-sky thinning has two effects.
-Firstly, it helps to flag measurements without any cloud impact, and secondly it improves the representation of the cloudy cases in the database as already shown in validation against ATMS data(Figure\ref{fig:pdf:c16-22}).
-In the second filter, only measurements with cloudy adjustment greater than ``noise-threshold'' are corrected.
-The value of the noise-threshold is assumed to be of the order of the standard deviation of the noise.
-This filter is tested with two values of the noise-threshold :  $1\sigma$ and  $2\sigma$, where $\sigma$ is the standard deviation of noise.
-
-Figure~\ref{fig:correction:c34-42:thinned} shows the results when the filtered cloudy cases are corrected.
-Various metrics from the corrected measurements are also shown in Table~\ref{tab:correction:stats}.
-When cloudy measurements are filtered with noise-threshold = 1$\sigma$, around 14\% cases of the thinned dataset are classified as cloudy and the average deviation in the corrected dataset is -0.069 K.
-Whereas, with noise-threshold= 2$\sigma$, only 9\% are classfied as cloudy and the average deviation is -0.117 K.
-This indicates that a larger value of noise threshold can incorrectly classify some cloudy cases as clear.
-
 \begin{table}[!bt]
@@
 		\hline
-		noise & 0.006& 0.628& -0.006\\
-		all& -0.818& 4.699& -10.385\\
-		thinned& -0.465& 1.556& -5.007\\
-		$1\sigma$& -0.069& 0.904& -2.543\\
-		$2\sigma$& -0.117& 0.903& -2.597\\
-		sreerekha et al& -0.181& 0.731& -0.506\\
+		Noise& 0.005& 0.633& -0.008\\
+		%all& -0.818& 4.699& -10.392\\
+		thinned& -0.303& 0.981& -2.318\\
+		1$\sigma$& -0.067& 0.756& -0.303\\
+		2$\sigma$& -0.119& 0.747& -0.519\\
+		sreerekha et al & -0.224& 0.798& -0.996\\
 		\hline
@@
 	\caption{Various metrics for different subsets of the measurement dataset.
-The different datasets are: noise(simulation dataset),  All (all measurements are considered), thinned (50\% of clear sky measurements are removed), $1\sigma$ (cloudy measurements are filtered with noise-threshold = 1$\sigma$), $2\sigma$ (cloudy measurements are filtered with noise-threshold = 2$\sigma$), sreerekha (measurements are filtered according to criteria described in \cite{rekha2012potential})   }
+The different datasets are: noise(simulation dataset), thinned (50\% of clear sky measurements are removed), $1\sigma$ (cloudy measurements are filtered with noise-index = 1$\sigma$), $2\sigma$ (cloudy measurements are filtered with noise-index = 2$\sigma$), sreerekha (measurements are filtered according to criteria described in \cite{rekha2012potential})   }
 	\label{tab:correction:stats}

### 2020-05-20 Report/aws_325ghz_study.tex
new text and tables in correction scheme

@@
 
-********
-
-TEXT NOT UPDATED BELOW 
 Before applying the clear-sky screening, the measurement dataset was also thinned in order to improve the representation of the cloudy cases.
-Validation of the simulations against ATMS data(Figure\ref{fig:pdf:c16-22}) showed that the cloudy cases were a bit underrepreseneted than the observations.
+Validation of the simulations against ATMS data(Figure\ref{fig:pdf:c16-22}) showed that the cloudy cases were a bit underrepresented than the observations.
 Removing 50\% of the clear-sky cases, helped in improving the percentage of total cloudy cases in the database.
@@
 For both values of noise-index the corresponding clear-sky cut-off is calculated using Eq~\ref{eq:dtb}.
-Figure~\ref{fig:correction:c34-42:thinned} shows the results when only the screened cloudy cases are corrected.
-Various metrics from the corrected measurements are also shown in Table~\ref{tab:correction:stats}.
-When cloudy measurements are filtered with noise-index = 1$\sigma$, around 13.5\% cases of the thinned dataset are classified as cloudy and the average deviation in the corrected dataset is -0.069 K.
-Whereas, with noise-threshold= 2$\sigma$, only 7.5\% are classified as cloudy and the average deviation is -0.117 K.
+The ``too cloudy'' screening ($Tb2-Tb1 < $ -15\,K) rejects almost 50\% of the cases in the measurement dataset.
+When the clear-sky screening is applied to this dataset, around 13.5\% of the cases are classfied as cloudy by noise-index = 1$\sigma$, while with 2$\sigma$ around 7.5\% are classified as cloudy.
+These cloudy cases are corrected according to the cubic model.
+Figure~\ref{fig:correction:c34-42:thinned} shows the results when only the screened cloudy cases are corrected/rejected.
+Various metrics from the corrected measurements are also shown in Table~\ref{tab:correction:stats:34:42}.
+The results from \cite{rekha2012potential} are also shown as reference.
+In their approach, the cases with TB difference between AWS-4x and AWS-32 greater than 6\,K are classified as cloudy and are rejected.
+Assuming that the measuremnt is cloudy in AWS-32, the corresponding measuremnt in other 183GHz channels is also rejected.
+In order to have a fair comparison of our approach with  \cite{rekha2012potential}, we also include a dataset where all the cloudy cases according to the clear-ksy screening are filtered out from the measurements.
+The metrics from this dataset are also provided in under label ``filtered''.
+
+With noise-index = 1$\sigma$, the average bias in the corrected dataset in -0.067\,K, while with 2$\sigma$, the average bias is -0.119\,K.
 This indicates that a larger value of noise threshold can incorrectly classify some cloudy cases as clear.
+%
 %
@@
 	\caption{Same as Figure~\ref{fig:correction:c34-42}, but for different subsets of the measurement dataset.
-The different datasets are: thinned measurements (50\% of the clear-sky cases removed), corrected measurements 1$\sigma$ (cloudy measurements are filtered with noise-threshold = 1$\sigma$), corrected measurements 2$\sigma$(cloudy measurements are filtered with noise-threshold = 2$\sigma$), sreerekha et al (cloud filtering according to criteria described in \cite{rekha2012potential}) }
+The different datasets are:- thinned: 50\% of the clear-sky cases removed, filtered (1$\sigma$): cloudy measurements are filtered with noise-threshold = 1$\sigma$,   corrected (1$\sigma$): cloudy measurements are corrected with noise-threshold = 1$\sigma$, sreerekha et al: cloud filtering according to criteria described in \cite{rekha2012potential} }
 	\label{fig:correction:c34-42:thinned}
@@
 %
+
 \begin{table}[!bt]
@@
 	\begin{tabular}[b]{c|c|c|c}
-		 Dataset & Bias & Standard & Measure\\
-		 		 & [K] & deviation[K] & skewness [K]\\	
+		Dataset  		  &   bias &   std &   measure  \\
+		&   [K]  &   [K] & skewness[K]\\
 		\hline
-		Noise& 0.005& 0.633& -0.008\\
-		%all& -0.818& 4.699& -10.392\\
-		thinned& -0.303& 0.981& -2.318\\
-		1$\sigma$& -0.067& 0.756& -0.303\\
-		2$\sigma$& -0.119& 0.747& -0.519\\
-		sreerekha et al & -0.224& 0.798& -0.996\\
+		Noise            &   0.00 &  0.63 &              -0.00 \\
+		all               &  -0.75 &  4.62 &             -11.78 \\
+		thinned           &  -0.30 &  1.00 &              -2.63 \\
+		corrected(2$\sigma$) &  -0.11 &  0.75 &              -0.70 \\
+		corrected(1$\sigma$) &  -0.06 &  0.76 &              -0.47 \\
+		sreerekha et al   &  -0.21 &  0.79 &              -1.02 \\
+		filtered(1$\sigma$)   &  -0.13 &  0.68 &              -0.25 \\
 		\hline
@@
 	\caption{Various metrics for different subsets of the measurement dataset.
-The different datasets are: noise(simulation dataset), thinned (50\% of clear sky measurements are removed), $1\sigma$ (cloudy measurements are filtered with noise-index = 1$\sigma$), $2\sigma$ (cloudy measurements are filtered with noise-index = 2$\sigma$), sreerekha (measurements are filtered according to criteria described in \cite{rekha2012potential})   }
-	\label{tab:correction:stats}
+The different datasets are: noise(simulation dataset), thinned (50\% of clear sky measurements are removed), filtered $1\sigma$ (cloudy measurements are filtered with noise-index = 1$\sigma$), corrected $1\sigma$ (cloudy measurements are corrected with noise-index = 1$\sigma$), corrected $2\sigma$ (cloudy measurements are corrected with noise-index = 2$\sigma$), sreerekha (measurements are filtered according to criteria described in \cite{rekha2012potential})   }
+	\label{tab:correction:stats:34:42}
 \end{table}
-%
-In past, \cite{rekha2012potential} have highlighted the applicability of 229 GHz channel to identify the ice clouds.
-In the report, they use 229 GHz (channel-4x) to identify the ice clouds in 183.31$\pm$7 GHz.
-In their approach, all cases with TB difference between 229 Ghz and 183.31$\pm$7 GHz greater than 4 K as classified as cloudy.
-This information can be used to filter out the cloudy cases in all other 183 GHz channels.
-No correction is provided to the cloudy cases.
-In order to compare the performance of the correction scheme described here, the filtering scheme by \cite{rekha2012potential} is used a reference.
-The results from approach are also shown in Figure\ref{fig:correction} and Table~\ref{tab:correction:stats}.
-The performance of cloud filtering by \cite{rekha2012potential} seems comparable with the regression approach described in this report, albeit they risk rejecting more than 50\% of the clear cases.
+
+\begin{figure}[!tb]
+	\centering
+	\includegraphics[height=85mm]{PDF_corrected_AWS-32_AWS-4X_thinned}
+	\caption{Same as Figure~\ref{fig:correction:c34-42:thinned}, but for channel combinations: AWS-32 and AWS-4X.}
+	\label{fig:correction:c32-4X:thinned}
+\end{figure}
+
+\begin{table}[!bt]
+	\centering
+	\begin{tabular}[b]{c|c|c|c}
+		Dataset  		  &   bias &   std &   measure  \\
+		&   [K]  &   [K] & skewness[K]\\
+		\hline
+	Noise             &   0.00 &  0.45 &              -0.00 \\
+	all               &  -1.37 &  6.98 &              -8.92 \\
+	thinned           &  -0.62 &  1.77 &              -4.60 \\
+	filtered(1$\sigma$)   &  -0.22 &  0.52 &              -0.65 \\
+	corrected(1$\sigma$) &   0.87 &  1.75 &              -1.31 \\
+	corrected(2$\sigma$) &   0.76 &  1.80 &              -1.08 \\
+	sreerekha et al   &  -0.41 &  1.00 &              -2.54 \\
+		\hline
+	\end{tabular}
+	\caption{Same as Table~\ref{tab:correction:stats:34:42}, but for channel combinations: AWS-32 and AWS-4X.   }
+	\label{tab:correction:stats:32:4X}
+\end{table}
+
+\begin{table}[!bt]
+	\centering
+	\begin{tabular}[b]{c|c|c|c}
+		Dataset  		  &   bias &   std &   measure  \\
+		&   [K]  &   [K] & skewness[K]\\
+		\hline
+Noise             &   0.00 &  0.45 &               0.01 \\
+all               &  -1.37 &  6.98 &              -8.92 \\
+thinned           &  -0.48 &  1.82 &             -14.92 \\
+filtered(1$\sigma$)   &  -0.21 &  0.55 &              -0.62 \\	
+corrected(1$\sigma$) &   0.47 &  1.68 &             -15.20 \\
+corrected(2$\sigma$) &   0.47 &  1.68 &             -15.16 \\
+sreerekha et al   &  -0.41 &  1.00 &              -2.54 \\		
+		\hline
+	\end{tabular}
+	\caption{Same as Table~\ref{tab:correction:stats:34:42}, but for channel combinations: AWS-32 and AWS-41.   }
+	\label{tab:correction:stats:32:41}
+\end{table}
+
+\begin{table}[!bt]
+	\centering
+	\begin{tabular}[b]{c|c|c|c}
+		Dataset  		  &   bias &   std &   measure  \\
+		&   [K]  &   [K] & skewness[K]\\
+		\hline
+Noise             &  -0.00 &  0.45 &               0.01 \\
+all               &  -1.04 &  5.74 &             -10.19 \\
+thinned           &  -0.33 &  0.91 &              -3.15 \\
+filtered(1$\sigma$)   &  -0.13 &  0.49 &          -0.39 \\
+corrected(1$\sigma$) &  -0.04 &  0.59 &           -0.85 \\
+corrected(2$\sigma$) &  -0.11 &  0.57 &           -1.17 \\
+sreerekha et al   &  -0.29 &  0.79 &              -2.21 \\		
+		\hline
+	\end{tabular}
+	\caption{Same as Table~\ref{tab:correction:stats:34:42}, but for channel combinations: AWS-33 and AWS-41.   }
+	\label{tab:correction:stats:33:41}
+\end{table}
+
+\begin{table}[!bt]
+	\centering
+	\begin{tabular}[b]{c|c|c|c}
+		Dataset  		  &   bias &   std &   measure  \\
+		&   [K]  &   [K] & skewness[K]\\
+		\hline
+Noise             &  -0.00 &  0.63 &              -0.00 \\
+all               &  -0.48 &  3.40 &              -14.25 \\
+thinned           &  -0.27 &  1.05 &              -4.43 \\
+filtered(1$\sigma$)   &  -0.13 &  0.68 &          -0.47 \\
+corrected(1$\sigma$) &   0.01 &  0.90 &           -1.66 \\
+corrected(2$\sigma$) &  -0.09 &  0.83 &           -2.37 \\
+sreerekha et al   &  -0.13 &  0.70 &              -0.58 \\
+
+		\hline
+	\end{tabular}
+	\caption{Same as Table~\ref{tab:correction:stats:34:42}, but for channel combinations: AWS-35 and AWS-43.   }
+	\label{tab:correction:stats:35:43}
+\end{table}
+
+\begin{table}[!bt]
+	\centering
+	\begin{tabular}[b]{c|c|c|c}
+		Dataset  		  &   bias &   std &   measure  \\
+		&   [K]  &   [K] & skewness[K]\\
+		\hline
+	Noise             &  -0.00 &  0.88 &              -0.00 \\
+	all               &  -0.31 &  2.59 &             -15.34 \\
+	thinned           &  -0.16 &  1.02 &              -0.87 \\
+	fitered(1$\sigma$)   &  -0.11 &  0.92 &              -0.14 \\
+	corrected(1$\sigma$) &  -0.07 &  0.93 &              -0.08 \\
+	corrected(2$\sigma$) &  -0.11 &  0.94 &              -0.19 \\
+	sreerekha et al   &  -0.09 &  0.91 &              -0.12 \\
+
+		\hline
+	\end{tabular}
+	\caption{Same as Table~\ref{tab:correction:stats:34:42}, but for channel combinations: AWS-36 and AWS-43.   }
+	\label{tab:correction:stats:36:43}
+\end{table}
 

### 2020-05-20 Report/aws_325ghz_study.tex
cloud correction, added fractions and new text

@@
 Red and green color represent the clear and cloudy cases respectively in the simulation dataset.
-The blue vertical line represents the clear-sky screening threshold in the measurements for noise-threshold = 0.2\,K   }
+The blue vertical line represents the clear-sky screening threshold in the measurements for noise-index = 0.2\,K   }
 	\label{fig:fit:c34-42}
@@
 %
-In this section, the 325GHz three channel option is evaluated for detection and correction of the ice-cloud cases in 183 GHz channels.
-Combinations of brightness temperature (TB) differences between 183 GHz and 325 Ghz are used as a measure of the cloud impact.
+In this section, the 325\,GHz three channel option is evaluated for detection and correction of the ice-cloud cases in 183\,GHz channels.
+Combinations of brightness temperature (TB) differences between 183\,GHz and 325\,GHz are used as a measure of the cloud impact.
 A regression based approach is used to estimate the adjustment need to predict the clear-sky values.
 
-Let C1 and C2 represent the one of the channels each from 183 GHz and 325 GHz respectively, and Tb1 and Tb2 represent the corresponding TB.
+Let C1 and C2 represent the one of the channels each from 183\,GHz and 325\,GHz respectively, and Tb1 and Tb2 represent the corresponding TB.
 The correction scheme formulates a relationship between the cloud impact in C1 to the TB differences between C1 and C2:
@@
 The combinations of C1 and C2 are selected by matching their weighting functions as shown in  Figure~\ref{fig:3ch:prel}.
-Five  183 GHz and 325 GHz paired combinations are possible, for example one such paired combination is AWS-34(180.311 GHz) and AWS-42 (325$\pm$3.55 GHz).
-For each of the five 183 GHz channels, the correction scheme is derived from its corresponding counterpart in 325 GHz channel.
+Five  183 and 325\,GHz paired combinations are possible, for example one such paired combination is AWS-34 and AWS-42.
+For each of the five 183\,GHz channels, the correction scheme is derived from its corresponding counterpart in 325\,GHz channel.
 
 As an example, the relationship between the TB differences for C1 and C2 and the cloud impact in C1 is shown in  Figure~\ref{fig:fit:c34-42}.
-For this particular case, C1 is AWS-34 and C2 is AWS-42, and around 40000 simulations are used.
+For this particular case, C1 is AWS-34 and C2 is AWS-42, and around 125000 simulations are used.
 The two variables have a reasonably strong correlation for small TB differences, but as the impact of cloud increases the correlations are poor.
@@
 	\includegraphics[clip,trim=0 0 0 0,height=85mm]{PDF_corrected_AWS-34_AWS-42}
-	\caption{Deviation of AWS-34 measurements to noise free clear-sky simulations before and after correction corrected using a linear, quadratic and cubic model.
+	\caption{Deviation of AWS-34 measurements to noise free clear-sky simulations before and after correction, corrected using a linear, quadratic and cubic model.
 The spread of noise is also shown as reference.
@@
 %
+
+\begin{figure}[!tb]
+	\centering
+	\includegraphics[height=85mm]{PDF_corrected_AWS-34_AWS-42_thinned}
+	\caption{Deviation of AWS-34 measurements to noise free clear-sky simulations before and after correction.
+The measurements have been corrected using a cubic model.
+The different datasets are:- thinned: 50\% of the clear-sky cases removed, filtered (1$\sigma$): cloudy measurements are filtered with noise-index = 1$\sigma$,   corrected (1$\sigma$): cloudy measurements are corrected with noise-index = 1$\sigma$, sreerekha et al: cloud filtering according to criteria described in \cite{rekha2012potential}.}
+	\label{fig:correction:c34-42:thinned}
+\end{figure}
+%
+
+\begin{table}[!bt]
+	\centering
+	\begin{tabular}[b]{c|c|c|c|c}
+		Dataset  		  &   bias &   std &   measure  & fraction  \\
+		&   [K]  &   [K] & skewness[K] & filtered/corrected [\%]\\
+		\hline
+Noise             &   0.00 &  0.63 &              -0.01 &                - \\
+uncorrected       &  -0.30 &  1.00 &              -2.64 &                - \\
+filtered(1$\sigma$)   &  -0.13 &  0.68 &              -0.25 &             13.05 \\
+corrected(1$\sigma$) &  -0.06 &  0.76 &              -0.48 &               13.05 \\
+corrected(2$\sigma$) &  -0.11 &  0.75 &              -0.69 &                7.21 \\
+sreerekha et al   &  -0.21 &  0.78 &              -1.02 &               62.15 \\
+
+		\hline
+	\end{tabular}
+	\caption{Various metrics for different subsets of the measurement dataset.
+The different datasets are: noise (simulation dataset), uncorrected (measurment dataset), filtered $1\sigma$ (cloudy measurements are filtered with noise-index = 1$\sigma$), corrected $1\sigma$ (cloudy measurements are corrected with noise-index = 1$\sigma$), corrected $2\sigma$ (cloudy measurements are corrected with noise-index = 2$\sigma$), sreerekha (measurements are filtered according to criteria described in \cite{rekha2012potential})   }
+	\label{tab:correction:stats:34:42}
+\end{table}
+%
 In this section, we test the applicability of the correction scheme in detail.
-To analyse the performance of the approach, we apply it to correct the measurements from C1.
+To analyse the performance of the approach, we apply it to correct the measurements from C1 using data from C2.
 Without the availability of actual data, the simulation dataset but with noise is used mimic the measurements.
@@
 This indicates that it is extremely important to correctly classify the cases as clear/cloudy.
-Among the three models, the quadratic and cubic models work better than a liner model.
+Among the three models, the quadratic and cubic models work better than the linear model.
 Both quadratic and cubic models are able to correct the cloud impact in the measurements, however the values of average bias indicates that the cubic model performs better.
@@
 Before applying the clear-sky screening, the measurement dataset was also thinned in order to improve the representation of the cloudy cases.
-Validation of the simulations against ATMS data(Figure\ref{fig:pdf:c16-22}) showed that the cloudy cases were a bit underrepresented than the observations.
+Validation of the simulations against ATMS data(Figure\ref{fig:pdf:c16-22}) showed that the cloudy cases were underrepresented than the observations.
 Removing 50\% of the clear-sky cases, helped in improving the percentage of total cloudy cases in the database.
+Further in the text, results from only thinned dataset are described.
 
 To implement the clear-sky screening as discussed in the previous section, two different values of the noise-index are tested : $1\sigma$ and  $2\sigma$, where $\sigma$ is the standard deviation of noise.
-For both values of noise-index the corresponding clear-sky cut-off is calculated using Eq~\ref{eq:dtb}.
-The ``too cloudy'' screening ($Tb2-Tb1 < $ -15\,K) rejects almost 50\% of the cases in the measurement dataset.
-When the clear-sky screening is applied to this dataset, around 13.5\% of the cases are classfied as cloudy by noise-index = 1$\sigma$, while with 2$\sigma$ around 7.5\% are classified as cloudy.
-These cloudy cases are corrected according to the cubic model.
+For both values of noise-index the corresponding clear-sky cut-off ($dtb_{cs}$) is calculated using Eq~\ref{eq:dtb}.
 Figure~\ref{fig:correction:c34-42:thinned} shows the results when only the screened cloudy cases are corrected/rejected.
@@
 In their approach, the cases with TB difference between AWS-4x and AWS-32 greater than 6\,K are classified as cloudy and are rejected.
-Assuming that the measuremnt is cloudy in AWS-32, the corresponding measuremnt in other 183GHz channels is also rejected.
-In order to have a fair comparison of our approach with  \cite{rekha2012potential}, we also include a dataset where all the cloudy cases according to the clear-ksy screening are filtered out from the measurements.
+Assuming that the measurement is cloudy in AWS-32, the corresponding measuremnt in other 183GHz channels is also rejected.
+In order to have a fair comparison of our approach with  \cite{rekha2012potential}, we also include a dataset where all the cloudy cases according to the clear-sky screening are filtered out from the measurements.
 The metrics from this dataset are also provided in under label ``filtered''.
+For all datasets shown in the table, we assume that cases with $Tb2-Tb1 < $ -15\,K are ``too-cloudy''.
+Such cases form 5\% of the thinned dataset and are not included in the statistics.
 
-With noise-index = 1$\sigma$, the average bias in the corrected dataset in -0.067\,K, while with 2$\sigma$, the average bias is -0.119\,K.
-This indicates that a larger value of noise threshold can incorrectly classify some cloudy cases as clear.
+The distribution of the deviations in the filtered data (both with approach described by sreerekha et al and the clear-sky screening) is non-Gaussian.
+The right side of the distribution follows the measurement noise while the left side is skewed.
+The skewness in the distribution is due to cloud impacts which go undetected.
+These cases have cloud impact less than the threshold value and are misclassfied as clear.
+The frequency of such cases is higher in Sreerekha et al approach than the clear-ksy screening presented here.
+The measure of skewness is also smaller for the clear-sky screening.
+In the report by \cite{rekha2012potential} they mention that for 6\,K threshold value, around 2.4\% of the cloudy cases are misclassfied as clear.
+For this value of threshold, 41\% of the clear cases are also classfied as cloudy and rejected.
+
+The regression approach described here does not provide any way to correct the misclassfied cases, but the frequency of such cases can be controlled through clear-sky cutoff ($dtb_{cs}$).
+When the clear-sky screening is applied to this dataset, around 13.05\% of the cases are classified as cloudy when $dtb_{cs}$ corresponds to noise-index = 1$\sigma$, while with 2$\sigma$ around 7.2\% are classified as cloudy.
+These cloudy cases are corrected according to the cubic model.
+After correction, the average deviation to the clear-sky noise-free values in the corrected measurements should be closer to zero than uncorrected measurements.
+Before correction, the average bias for measurements is -0.30\,K but after correction it reduces to -0.06\,K and -0.11\,K for the two values of the noise-index respectively.
+This indicates that a larger value of noise-index increases the probability of falsely classifying clear cases as cloudy.
 %
+\subsection{Application of correction scheme using AWS-4X}
 %
-\begin{figure}[!tb]
-	\centering
-	\includegraphics[height=85mm]{PDF_corrected_AWS-34_AWS-42_thinned}
-	\caption{Same as Figure~\ref{fig:correction:c34-42}, but for different subsets of the measurement dataset.
-The different datasets are:- thinned: 50\% of the clear-sky cases removed, filtered (1$\sigma$): cloudy measurements are filtered with noise-threshold = 1$\sigma$,   corrected (1$\sigma$): cloudy measurements are corrected with noise-threshold = 1$\sigma$, sreerekha et al: cloud filtering according to criteria described in \cite{rekha2012potential} }
-	\label{fig:correction:c34-42:thinned}
-\end{figure}
-%
-
-\begin{table}[!bt]
-	\centering
-	\begin{tabular}[b]{c|c|c|c}
-		Dataset  		  &   bias &   std &   measure  \\
-		&   [K]  &   [K] & skewness[K]\\
-		\hline
-		Noise            &   0.00 &  0.63 &              -0.00 \\
-		all               &  -0.75 &  4.62 &             -11.78 \\
-		thinned           &  -0.30 &  1.00 &              -2.63 \\
-		corrected(2$\sigma$) &  -0.11 &  0.75 &              -0.70 \\
-		corrected(1$\sigma$) &  -0.06 &  0.76 &              -0.47 \\
-		sreerekha et al   &  -0.21 &  0.79 &              -1.02 \\
-		filtered(1$\sigma$)   &  -0.13 &  0.68 &              -0.25 \\
-		\hline
-	\end{tabular}
-	\caption{Various metrics for different subsets of the measurement dataset.
-The different datasets are: noise(simulation dataset), thinned (50\% of clear sky measurements are removed), filtered $1\sigma$ (cloudy measurements are filtered with noise-index = 1$\sigma$), corrected $1\sigma$ (cloudy measurements are corrected with noise-index = 1$\sigma$), corrected $2\sigma$ (cloudy measurements are corrected with noise-index = 2$\sigma$), sreerekha (measurements are filtered according to criteria described in \cite{rekha2012potential})   }
-	\label{tab:correction:stats:34:42}
-\end{table}
-
-\begin{figure}[!tb]
+\begin{figure}[!t]
 	\centering
@@
 \end{figure}
+%
 
-\begin{table}[!bt]
+As a reference, we also apply the correction scheme described above to correct AWS-32 using AWS-4X.
+In this case, C1 and C2 are AWS-32 and AWS-4X.
+The TB correlations between AWS-32 and AWS-4X are poor and show a large spread particularly for large cloud impacts [figure not shown].
+We fit the data to a cubic model, but exclude cases with $Tb2-Tb1 <$ -20\,K.
+Also cases with TB difference less than 0.2\,K are classified as clear and are not included in the fit.
+The clear-sky screening is also  evaluated for noise-index = 1$\sigma$ and $2\sigma$.
+Figure~\ref{fig:correction:c32-4X:thinned} shows the deviations to clear-sky values before and after correction, and the corresponding metrics are provided in Table~\ref{tab:correction:stats:32:4X}.
+As evident from the figure, \cite{rekha2012potential} classifies all measurements with cloud impact greater than 6\,K as cloudy, but a significant skewness in the distribution indicates misclassfication of cloudy cases.
+However, the frequency of misclassfied cases is significantly lower for our clear-sky screening.
+With \cite{rekha2012potential}'s approach, around 62\% of the measurements are rejected as cloudy, but in our approach, 84\% of the cases are classified as cloudy.
+This clearly indicates a high rate of misclassification of the clear cases.
+\begin{table}[!h]
 	\centering
-	\begin{tabular}[b]{c|c|c|c}
-		Dataset  		  &   bias &   std &   measure  \\
-		&   [K]  &   [K] & skewness[K]\\
+	\begin{tabular}[b]{c|c|c|c|c}
+		Dataset  		  &   bias &   std &   measure & fraction \\
+		&   [K]  &   [K] & skewness[K] 		& filtered/corrected [\%]\\
 		\hline
-	Noise             &   0.00 &  0.45 &              -0.00 \\
-	all               &  -1.37 &  6.98 &              -8.92 \\
-	thinned           &  -0.62 &  1.77 &              -4.60 \\
-	filtered(1$\sigma$)   &  -0.22 &  0.52 &              -0.65 \\
-	corrected(1$\sigma$) &   0.87 &  1.75 &              -1.31 \\
-	corrected(2$\sigma$) &   0.76 &  1.80 &              -1.08 \\
-	sreerekha et al   &  -0.41 &  1.00 &              -2.54 \\
+Noise             &  -0.00 &  0.45 &               0.02 &                - \\
+uncorrected       &  -0.62 &  1.76 &              -4.61 &                - \\
+filtered($1\sigma$)  &  -0.21 &  0.52 &              -0.65 &               84.49 \\
+corrected($1\sigma$) &   0.88 &  1.76 &              -1.29 &               84.49 \\
+corrected($2\sigma$) &   0.76 &  1.80 &              -1.06 &               68.00 \\
+sreerekha et al   &  -0.40 &  1.00 &              -2.54 &               62.02 \\
 		\hline
@@
 
+\subsection{Application of correction scheme to AWS-32, AWS-33, AWS-35 and AWS-36}
+The correction scheme can also be extended to other combinations of 183GHz and 325GHz.
+The other possible combinations for clear-sky screening are: AWS-32 and AWS-41; AWS-33 and AWS-41; AWS-35 and AWS-43; AWS-36 and AWS-43.
+% 
+Table~\ref{tab:correction:stats:32:41}  shows the statistics when AWS-32 is corrected using AWS-41.
+The statistics of the filtered dataset are better than the approach by \cite{rekha2012potential}.
+However, a very high rejection fraction (85\%) indicates that a large percentage of clear cases are misclassfied as cloudy.
+
+Table~\ref{tab:correction:stats:33:41} shows the statistics when AWS-33 is corrected using AWS-41.
+These TB differences for this combination and the cloud impact in AWS-33 are highly correlated and using a cubic model, approximately 20\% of the observations are corrected, which reduces the average bias in the measurements from -0.33\,K to -0.05\,K.
+
+A similar performance is seen for the combination AWS-35 and AWS-43, where 19\% of the measurements are classfied as cloudy.
+Correcting these measurements for the cloud impact reduces the average bias in the measurements from -0.33\,K to -0.05\,K.
+Table~\ref{tab:correction:stats:35:43}  shows the statistics obtained from this combination.
+The statistics from the channel combination AWS-36 and AWS-42 are shown in Table~\ref{tab:correction:stats:36:43}.
 \begin{table}[!bt]
 	\centering
-	\begin{tabular}[b]{c|c|c|c}
-		Dataset  		  &   bias &   std &   measure  \\
-		&   [K]  &   [K] & skewness[K]\\
+	\begin{tabular}[b]{c|c|c|c|c}
+		Dataset  		  &   bias &   std &   measure & fraction \\
+		&   [K]  &   [K] & skewness[K] & filtered/corrected [\%]\\
 		\hline
-Noise             &   0.00 &  0.45 &               0.01 \\
-all               &  -1.37 &  6.98 &              -8.92 \\
-thinned           &  -0.48 &  1.82 &             -14.92 \\
-filtered(1$\sigma$)   &  -0.21 &  0.55 &              -0.62 \\	
-corrected(1$\sigma$) &   0.47 &  1.68 &             -15.20 \\
-corrected(2$\sigma$) &   0.47 &  1.68 &             -15.16 \\
-sreerekha et al   &  -0.41 &  1.00 &              -2.54 \\		
+ Noise             &  -0.00 &  0.45 &               0.01 &               - \\
+uncorrected       &  -0.48 &  1.82 &             -14.94 &                - \\
+filtered(1sigma)  &  -0.20 &  0.55 &              -0.61 &               92.99 \\
+corrected(1sigma) &   0.48 &  1.68 &             -15.20 &               92.99 \\
+corrected(2sigma) &   0.47 &  1.68 &             -15.16 &               94.75 \\
+sreerekha et al   &  -0.41 &  1.00 &              -2.55 &               62.02 \\	
 		\hline
@@
 	\centering
-	\begin{tabular}[b]{c|c|c|c}
-		Dataset  		  &   bias &   std &   measure  \\
-		&   [K]  &   [K] & skewness[K]\\
+	\begin{tabular}[b]{c|c|c|c|c}
+		Dataset  		  &   bias &   std &   measure  & fraction\\
+		&   [K]  &   [K] & skewness[K]                   & filtered/corrected [\%]\\
 		\hline
-Noise             &  -0.00 &  0.45 &               0.01 \\
-all               &  -1.04 &  5.74 &             -10.19 \\
-thinned           &  -0.33 &  0.91 &              -3.15 \\
-filtered(1$\sigma$)   &  -0.13 &  0.49 &          -0.39 \\
-corrected(1$\sigma$) &  -0.04 &  0.59 &           -0.85 \\
-corrected(2$\sigma$) &  -0.11 &  0.57 &           -1.17 \\
-sreerekha et al   &  -0.29 &  0.79 &              -2.21 \\		
+	Noise             &  -0.00 &  0.45 &               0.01 &               - \\
+	uncorrected       &  -0.33 &  0.91 &              -3.15 &                - \\
+	filtered(1$\sigma$)  &  -0.13 &  0.49 &              -0.39 &               20.60 \\
+	corrected(1$\sigma$) &  -0.05 &  0.59 &              -0.85 &               20.60 \\
+	corrected(2$\sigma$) &  -0.11 &  0.57 &              -1.17 &               10.19 \\
+	sreerekha et al   &  -0.30 &  0.79 &              -2.21 &               62.10 \\
 		\hline
@@
 	\centering
-	\begin{tabular}[b]{c|c|c|c}
-		Dataset  		  &   bias &   std &   measure  \\
-		&   [K]  &   [K] & skewness[K]\\
+	\begin{tabular}[b]{c|c|c|c|c}
+		Dataset  		  &   bias &   std &   measure & fraction \\
+		&   [K]  &   [K] & skewness[K] & filtered/corrected [\%]\\
 		\hline
-Noise             &  -0.00 &  0.63 &              -0.00 \\
-all               &  -0.48 &  3.40 &              -14.25 \\
-thinned           &  -0.27 &  1.05 &              -4.43 \\
-filtered(1$\sigma$)   &  -0.13 &  0.68 &          -0.47 \\
-corrected(1$\sigma$) &   0.01 &  0.90 &           -1.66 \\
-corrected(2$\sigma$) &  -0.09 &  0.83 &           -2.37 \\
-sreerekha et al   &  -0.13 &  0.70 &              -0.58 \\
-
+ Noise             &  -0.00 &  0.63 &              -0.01 &                - \\
+uncorrected       &  -0.27 &  1.06 &              -4.44 &                - \\
+filtered(1$\sigma$)  &  -0.13 &  0.68 &              -0.47 &               19.02 \\
+corrected(1$\sigma$) &   0.01 &  0.90 &              -1.67 &               19.02 \\
+corrected(2$\sigma$) &  -0.09 &  0.83 &              -2.39 &                6.37 \\
+sreerekha et al   &  -0.13 &  0.70 &              -0.58 &               62.24 \\
 		\hline
@@
 	\centering
-	\begin{tabular}[b]{c|c|c|c}
-		Dataset  		  &   bias &   std &   measure  \\
-		&   [K]  &   [K] & skewness[K]\\
+	\begin{tabular}[b]{c|c|c|c|c}
+		Dataset  		  &   bias &   std &   measure & fraction  \\
+		&   [K]  &   [K] & skewness[K] &				filtered/corrected [\%]\\
 		\hline
-	Noise             &  -0.00 &  0.88 &              -0.00 \\
-	all               &  -0.31 &  2.59 &             -15.34 \\
-	thinned           &  -0.16 &  1.02 &              -0.87 \\
-	fitered(1$\sigma$)   &  -0.11 &  0.92 &              -0.14 \\
-	corrected(1$\sigma$) &  -0.07 &  0.93 &              -0.08 \\
-	corrected(2$\sigma$) &  -0.11 &  0.94 &              -0.19 \\
-	sreerekha et al   &  -0.09 &  0.91 &              -0.12 \\
-
+Noise             &  -0.00 &  0.88 &              -0.01 &                - \\
+uncorrected       &  -0.16 &  1.01 &              -0.86 &                - \\
+filtered(1$\sigma$)  &  -0.11 &  0.92 &              -0.12 &                4.98 \\
+corrected(1$\sigma$) &  -0.07 &  0.93 &              -0.07 &                4.98 \\
+corrected(2$\sigma$) &  -0.11 &  0.94 &              -0.18 &                2.06 \\
+sreerekha et al   &  -0.09 &  0.91 &              -0.10 &               62.20 \\
 		\hline
@@
 \end{table}
-
-The regression approach described above is also extended to other four channel combinations and the results are shown in Figure\ref{fig:correction:allchannels}.
- [** incomplete to be added ** add tables or figures? **]
 

### 2020-05-21 Report/aws_325ghz_study.tex
Some polishing of Sec 6 in the report.

@@
 Satellite (AWS) high frequency channels} \vspace{8mm}\\
-{\bf Patrick Eriksson, Simon Pfreundschuh and Inderpreet Kaur}\\
+{\bf Patrick Eriksson, Inderpreet Kaur and Simon Pfreundschuh}\\
 Department of Space, Earth and Environment\\
 Chalmers University of Technology\\
-SE-412\,96, Gothenburg, Sweden \vspace{10mm}
+SE-412\,96, Gothenburg, Sweden\vspace{10mm}
 
@@
 %
-To written \dots
+To be written \dots
 
@@
 \subsection{Comparison to \citet{rekha2012potential}}
+\label{sec:rekha}
 %
@@
 16-22 at nadir (zenith angle = $180^{\degree}$), is shown in
-Figure~\ref{fig:pdf:c16-22}. For the comparison, the daytime ATMS observations
+Fig.~\ref{fig:pdf:c16-22}. For the comparison, the daytime ATMS observations
 were selected as CloudSat operates only during the day part of the orbit since
@@
 
-In Figure~\ref{fig:tb:r050} the surface reflectivity is changed to 0.5, which
+In Fig.~\ref{fig:tb:r050} the surface reflectivity is changed to 0.5, which
 should roughly correspond to the highest reflectivity encountered at these
@@
 %
+In this section, the 325\,GHz three channel option is evaluated for detection
+and correction of cloud interference in 183\,GHz channels. Combinations of
+brightness temperature (TB) differences between 183\,GHz and 325\,GHz are used
+as a measure of the cloud impact. A regression based approach is used to
+estimate the adjustment needed to predict the clear-sky values.
+
 \subsection{Formulation of correction scheme}
 %
-\begin{figure}[!tb]
-	\centering
-	\includegraphics[height=65mm]{fit_AWS-34_AWS-42}\hspace{5mm}% 
-	\caption{Brightness temperature difference of AWS-34 from AWS-42 plotted against cloud impact in AWS-34.
-The black curve represents the line of best fit as a third order polynomial.
-Red and green color represent the clear and cloudy cases respectively in the simulation dataset.
-The blue vertical line represents the clear-sky screening threshold in the measurements for noise-index = 0.2\,K   }
-	\label{fig:fit:c34-42}
-\end{figure}
-%
-In this section, the 325\,GHz three channel option is evaluated for detection and correction of the ice-cloud cases in 183\,GHz channels.
-Combinations of brightness temperature (TB) differences between 183\,GHz and 325\,GHz are used as a measure of the cloud impact.
-A regression based approach is used to estimate the adjustment need to predict the clear-sky values.
-
-Let C1 and C2 represent the one of the channels each from 183\,GHz and 325\,GHz respectively, and Tb1 and Tb2 represent the corresponding TB.
-The correction scheme formulates a relationship between the cloud impact in C1 to the TB differences between C1 and C2:
+Let C1 and C2 represent the one of the channels each from 183\,GHz and 325\,GHz
+respectively, and Tb1 and Tb2 represent the corresponding TB. The correction
+scheme formulates a relationship between the cloud impact in C1 to the TB
+differences between C1 and C2:
 \begin{equation}
@@
 
-The combinations of C1 and C2 are selected by matching their weighting functions as shown in  Figure~\ref{fig:3ch:prel}.
-Five  183 and 325\,GHz paired combinations are possible, for example one such paired combination is AWS-34 and AWS-42.
-For each of the five 183\,GHz channels, the correction scheme is derived from its corresponding counterpart in 325\,GHz channel.
+The combinations of C1 and C2 are selected by matching their weighting
+functions as shown in Fig.~\ref{fig:3ch:prel}. Five 183 and 325\,GHz paired
+combinations are possible, for example one such paired combination is AWS-34
+and AWS-42. For each of the five 183\,GHz channels, the correction scheme is
+derived from its corresponding counterpart in 325\,GHz channel.
 
-As an example, the relationship between the TB differences for C1 and C2 and the cloud impact in C1 is shown in  Figure~\ref{fig:fit:c34-42}.
-For this particular case, C1 is AWS-34 and C2 is AWS-42, and around 125000 simulations are used.
-The two variables have a reasonably strong correlation for small TB differences, but as the impact of cloud increases the correlations are poor.
-The data can be fitted to linear or non-linear models.
-The fitted model can be used to interpolate the adjustment required to compensate the brightness temperature for cloudy cases.
-To avoid fitting the ``too cloudy'' cases which do not show any reasonable correlation, cases with $Tb2-Tb1$< -40\,K  are excluded in the fit.
-Also, cases with $Tb2-Tb1$ < 0.2\,K (red color dots) are assumed to be clear are not included in the model.
+\begin{figure}[!tb]
+	\centering
+	\includegraphics[height=85mm]{fit_AWS-34_AWS-42}\hspace{5mm}% 
+	\caption{Brightness temperature difference of AWS-34 from AWS-42 plotted
+      against cloud impact in AWS-34. The black curve represents the line of
+      best fit as a third order polynomial. Red and green color represent the
+      clear and cloudy cases respectively in the simulation dataset. The blue
+      vertical line represents a clear-sky screening threshold of 0.2\,K. }
+	\label{fig:fit:c34-42}
+\end{figure}
+%
 
-Before correcting the measurements, it is important to correctly classify all the cases into clear or cloudy.
-To avoid any undesirable adjustment of the clear cases, a clear-sky screening is added  to the correction scheme.
-In this screening, we assume that for clear cases, the average differences of the measurements to their noise-free clear-sky values are of the order of the instrument noise.
-Further in the text, we refer this value of noise as ``noise-index''.
-Assuming the function $f$ in eqn~\ref{eq:TB:diff} to be invertible, and if $x_{cs}$  represents the noise-index, the TB difference between the measurements from C1 and C2 for the noise-index can be used as a measure of clear-sky screening: ($dtb_{cs}$):
+As an example, the relationship between the TB differences for C1 and C2 and
+the cloud impact in C1 is shown in Fig.~\ref{fig:fit:c34-42}. For this
+particular case, C1 is AWS-34 and C2 is AWS-42, and around 125\,000 simulations
+are used. The two variables have a reasonably strong correlation for small TB
+differences, but as the impact of cloud increases the correlations gets poorer.
+The data can be fitted to linear or non-linear models. The fitted model can be
+used to interpolate the adjustment required to compensate the brightness
+temperature for cloudy cases. To avoid fitting the ``too cloudy'' cases which
+do not show any reasonable correlation, cases with $Tb2-Tb1< -40$\,K are
+excluded in the fit. Also, cases with $Tb2-Tb1 < 0.2$\,K (red color dots) are
+assumed to be clear-sky are not included in the model.
+
+It is also important to have a manner for making a clear/cloudy classification.
+This is useful for making a filtering in line with \citep{rekha2012potential},
+but is also needed in the correction scheme. The later is the case as the
+polynomial fit derived gives a non-zero correction for clear-sky cases. In
+Fig.~\ref{fig:fit:c34-42} the difference between clear-sky values of channel C1
+and C2 (red dots) have a mean close to zero (as the weighting functions are
+well matched), but this is not the case for all channel combinations and some
+general rule for finding a threshold value (with respect to $x_m$) must be
+formulated. The polynomial fit will be used also for this part.
+
+%Before correcting the measurements, it is important to correctly classify all
+%the cases into clear or cloudy. To avoid any undesirable adjustment of the
+%clear cases, a clear-sky screening is added  to the correction scheme. In this
+%screening, we assume that for clear cases, the average differences of the
+%measurements to their noise-free clear-sky values are of the order of the
+%instrument noise. Further in the text, we refer this value of noise as
+%``noise-index''.
+%Assuming the function $f$ in eqn~\ref{eq:TB:diff} to be invertible, and if $x_{cs}$  represents the noise-index, the TB difference between the measurements from C1 and C2 for the noise-index can be used as a measure of clear-sky screening: ($dtb_{cs}$):
+
+We will simply treat cases that matches a correction below a certain value as
+``clear-sky''. If the correction limit is denoted as $dtb_{cs}$, the threshold
+value, $x_{cs}$, is obtained by inverting the polynomial fit:
 \begin{equation}
@@
 \end{equation}
-The value of $dtb_{cs}$ is not constant and shall depend on the the combination of 183 GHz and 325 GHz used.
-The measurements with TB difference between C2 and C1 less than $dtb_{cs}$ are considered cloudy and are corrected.
-In Figure~\ref{fig:correction:c34-42}, the blue dotted line represents the clear-sky screening cut-off when noise-index = 0.2\,K.
-All measurements to the left of this line are classified as cloudy, and vice-versa.
-For the dataset shown in the figure, around 15\% of the total cases were classified as clear.
-The sensitivity of noise-index is discussed in detail in the next section.
+That is, if $x_m>x_{cs}$ a measurement is classified as clear-sky. If
+$x_m\leq x_{cs}$, the measurement is rejected if a pure filtering is made, or
+it is adjusted if the correction scheme is applied. We will largely set
+$dtb_{cs}$ based on the noise level of the 183\,GHz channel involved, to be
+1$\sigma$ or 2$\sigma$ where $\sigma$ refers to the magnitide of measurement
+noise (Eq.~\ref{eq:noise}, often called NE$\Delta$T).
+
+%The value of $dtb_{cs}$ is not constant and shall depend on the the combination
+%of 183 GHz and 325 GHz used. The measurements with TB difference between C2 and
+%C1 less than $dtb_{cs}$ are considered cloudy and are corrected. In
+%Fig.~\ref{fig:correction:c34-42}, the blue dotted line represents the clear-sky
+%screening cut-off when noise-index = 0.2\,K. All measurements to the left of
+%this line are classified as cloudy, and vice-versa. For the dataset shown in
+%the figure, around 15\% of the total cases were classified as clear. The
+%sensitivity of noise-index is discussed in detail in the next section.
+
 \subsection{Application of correction scheme}
-\begin{figure}[!th]
+\begin{figure}[!p]
 	\centering
-	\includegraphics[clip,trim=0 0 0 0,height=85mm]{PDF_corrected_AWS-34_AWS-42}
-	\caption{Deviation of AWS-34 measurements to noise free clear-sky simulations before and after correction, corrected using a linear, quadratic and cubic model.
-The spread of noise is also shown as reference.
-The measurements have been corrected using brightness temperatures from AWS-42.
-}
+	\includegraphics[clip,trim=0 0 0 0,height=90mm]{PDF_corrected_AWS-34_AWS-42}
+	\caption{Deviation of AWS-34 measurements to noise free clear-sky
+      simulations before and after correction, corrected using a linear,
+      quadratic and cubic model. The spread of noise is also shown as
+      reference. The measurements have been corrected using brightness
+      temperatures from AWS-42. }
 	\label{fig:correction:c34-42}
@@
 
-\begin{figure}[!tb]
+\begin{figure}[!]
 	\centering
-	\includegraphics[height=85mm]{PDF_corrected_AWS-34_AWS-42_thinned}
-	\caption{Deviation of AWS-34 measurements to noise free clear-sky simulations before and after correction.
-The measurements have been corrected using a cubic model.
-The different datasets are:- thinned: 50\% of the clear-sky cases removed, filtered (1$\sigma$): cloudy measurements are filtered with noise-index = 1$\sigma$,   corrected (1$\sigma$): cloudy measurements are corrected with noise-index = 1$\sigma$, sreerekha et al: cloud filtering according to criteria described in \cite{rekha2012potential}.}
+	\includegraphics[height=90mm]{PDF_corrected_AWS-34_AWS-42_thinned}
+	\caption{Deviation of AWS-34 measurements to noise free clear-sky
+      simulations before and after correction. The measurements have been
+      corrected using a cubic model. The different datasets are: thinned: 50\%
+      of the clear-sky cases removed, filtered (1$\sigma$): cloudy measurements
+      are filtered with noise-index = 1$\sigma$, corrected (1$\sigma$): cloudy
+      measurements are corrected with noise-index = 1$\sigma$, Sreerekha et al:
+      cloud filtering according to criteria described in
+      \cite{rekha2012potential}.}
 	\label{fig:correction:c34-42:thinned}
@@
 corrected(2$\sigma$) &  -0.11 &  0.75 &              -0.69 &                7.21 \\
-sreerekha et al   &  -0.21 &  0.78 &              -1.02 &               62.15 \\
+Sreerekha et al   &  -0.21 &  0.78 &              -1.02 &               62.15 \\
 
@@
 	\caption{Various metrics for different subsets of the measurement dataset.
-The different datasets are: noise (simulation dataset), uncorrected (measurment dataset), filtered $1\sigma$ (cloudy measurements are filtered with noise-index = 1$\sigma$), corrected $1\sigma$ (cloudy measurements are corrected with noise-index = 1$\sigma$), corrected $2\sigma$ (cloudy measurements are corrected with noise-index = 2$\sigma$), sreerekha (measurements are filtered according to criteria described in \cite{rekha2012potential})   }
+The different datasets are: noise (simulation dataset), uncorrected (measurment dataset), filtered $1\sigma$ (cloudy measurements are filtered with noise-index = 1$\sigma$), corrected $1\sigma$ (cloudy measurements are corrected with noise-index = 1$\sigma$), corrected $2\sigma$ (cloudy measurements are corrected with noise-index = 2$\sigma$), Sreerekha (measurements are filtered according to criteria described in \cite{rekha2012potential})   }
 	\label{tab:correction:stats:34:42}
@@
 
-To test the efficacy of the correction scheme, three different models :linear, quadratic and cubic are evaluated to fit the TB differences between C1 and C2.
-For all three models, cases with $Tb2-Tb1 < $ -15\,K are assumed to be ``too cloudy'' and are not corrected.
-The clear-sky adjustment for all eligible measurements (without clear-sky screening) is calculated from all three models, and the three predicted datasets are compared.
-The error in the predicted measurements is assessed by calculating the deviation to noise-free clear-sky observations.
-The occurrence frequency of the deviations from three models is shown in Figure~\ref{fig:correction:c34-42}.
-The occurence frequency of the all measurement without any filtering or correction is also plotted as reference (orange color).
-If all measurements are devoid of any cloud impact, the deviations should follow the gaussian distribution of noise.
-However, in real scenarios, the distribution is skewed due to the impact of clouds.
-It should also be noted that since no clear-sky screening was included in the measurements, the measurements with zero deviation to noise-free clear-sky were reduced.
-This indicates that it is extremely important to correctly classify the cases as clear/cloudy.
-Among the three models, the quadratic and cubic models work better than the linear model.
-Both quadratic and cubic models are able to correct the cloud impact in the measurements, however the values of average bias indicates that the cubic model performs better.
-The average deviation in the dataset is -0.82\,K and after correction with a cubic model, it reduces to -0.02\,K, while for quadratic model, the average bias after correction is 0.24\,K.
-For all other results described in this section, a cubic model is used.
+To test the efficacy of the correction scheme, three different models: linear,
+quadratic and cubic are evaluated to fit the TB differences between C1 and C2.
+For all three models, cases with $Tb2-Tb1 < $ -15\,K are assumed to be ``too
+cloudy'' and are not corrected. The clear-sky adjustment for all eligible
+measurements (without clear-sky screening) is calculated from all three models,
+and the three predicted datasets are compared. The error in the predicted
+measurements is assessed by calculating the deviation to noise-free clear-sky
+observations. The occurrence frequency of the deviations from three models is
+shown in Fig.~\ref{fig:correction:c34-42}. The occurence frequency of the all
+measurement without any filtering or correction is also plotted as reference
+(orange color). If all measurements are devoid of any cloud impact, the
+deviations should follow the gaussian distribution of noise. However, in real
+scenarios, the distribution is skewed due to the impact of clouds. It should
+also be noted that since no clear-sky screening was included in the
+measurements, the measurements with zero deviation to noise-free clear-sky were
+reduced. This indicates that it is extremely important to correctly classify
+the cases as clear/cloudy. Among the three models, the quadratic and cubic
+models work better than the linear model. Both quadratic and cubic models are
+able to correct the cloud impact in the measurements, however the values of
+average bias indicates that the cubic model performs better. The average
+deviation in the dataset is -0.82\,K and after correction with a cubic model,
+it reduces to -0.02\,K, while for quadratic model, the average bias after
+correction is 0.24\,K. For all other results described in this section, a cubic
+model is used.
 
-Before applying the clear-sky screening, the measurement dataset was also thinned in order to improve the representation of the cloudy cases.
-Validation of the simulations against ATMS data(Figure\ref{fig:pdf:c16-22}) showed that the cloudy cases were underrepresented than the observations.
-Removing 50\% of the clear-sky cases, helped in improving the percentage of total cloudy cases in the database.
-Further in the text, results from only thinned dataset are described.
+Before applying the clear-sky screening, the measurement dataset was also
+thinned in order to improve the representation of the cloudy cases. Validation
+of the simulations against ATMS data (Fig.\ref{fig:pdf:c16-22}) showed that the
+cloudy cases were underrepresented than the observations. Removing 50\% of the
+clear-sky cases, helped in improving the percentage of total cloudy cases in
+the database. Further in the text, results from only thinned dataset are
+described.
 
-To implement the clear-sky screening as discussed in the previous section, two different values of the noise-index are tested : $1\sigma$ and  $2\sigma$, where $\sigma$ is the standard deviation of noise.
-For both values of noise-index the corresponding clear-sky cut-off ($dtb_{cs}$) is calculated using Eq~\ref{eq:dtb}.
-Figure~\ref{fig:correction:c34-42:thinned} shows the results when only the screened cloudy cases are corrected/rejected.
-Various metrics from the corrected measurements are also shown in Table~\ref{tab:correction:stats:34:42}.
-The results from \cite{rekha2012potential} are also shown as reference.
-In their approach, the cases with TB difference between AWS-4x and AWS-32 greater than 6\,K are classified as cloudy and are rejected.
-Assuming that the measurement is cloudy in AWS-32, the corresponding measuremnt in other 183GHz channels is also rejected.
-In order to have a fair comparison of our approach with  \cite{rekha2012potential}, we also include a dataset where all the cloudy cases according to the clear-sky screening are filtered out from the measurements.
-The metrics from this dataset are also provided in under label ``filtered''.
-For all datasets shown in the table, we assume that cases with $Tb2-Tb1 < $ -15\,K are ``too-cloudy''.
-Such cases form 5\% of the thinned dataset and are not included in the statistics.
+To implement the clear-sky screening as discussed in the previous section, two
+different values of the noise-index are tested: $1\sigma$ and $2\sigma$, where
+$\sigma$ is the standard deviation of noise. For both values of noise-index the
+corresponding clear-sky cut-off ($dtb_{cs}$) is calculated using
+Eq~\ref{eq:dtb}. Figure~\ref{fig:correction:c34-42:thinned} shows the results
+when only the screened cloudy cases are corrected/rejected. Various metrics
+from the corrected measurements are also shown in
+Table~\ref{tab:correction:stats:34:42}. The results from
+\cite{rekha2012potential} are also shown as reference (see Sec.~\ref{sec:rekha}
+for our assumptions). In their approach, the cases with TB difference between
+AWS-4x and AWS-32 greater than 6\,K are classified as cloudy and are rejected.
+Assuming that the measurement is cloudy in AWS-32, the corresponding measuremnt
+in other 183GHz channels is also rejected. In order to have a fair comparison
+of our approach with \cite{rekha2012potential}, we also include a dataset where
+all the cloudy cases according to the clear-sky screening are filtered out from
+the measurements. The metrics from this dataset are also provided in under
+label ``filtered''. For all datasets shown in the table, we assume that cases
+with $Tb2-Tb1 < $ -15\,K are ``too-cloudy''.
+%Such cases form 5\% of the thinned
+%dataset and are not included in the statistics.
 
-The distribution of the deviations in the filtered data (both with approach described by sreerekha et al and the clear-sky screening) is non-Gaussian.
-The right side of the distribution follows the measurement noise while the left side is skewed.
-The skewness in the distribution is due to cloud impacts which go undetected.
-These cases have cloud impact less than the threshold value and are misclassfied as clear.
-The frequency of such cases is higher in Sreerekha et al approach than the clear-ksy screening presented here.
-The measure of skewness is also smaller for the clear-sky screening.
-In the report by \cite{rekha2012potential} they mention that for 6\,K threshold value, around 2.4\% of the cloudy cases are misclassfied as clear.
-For this value of threshold, 41\% of the clear cases are also classfied as cloudy and rejected.
+The distribution of the deviations in the filtered data (both with approach
+described by Sreerekha et al and the clear-sky screening) is non-Gaussian. The
+right side of the distribution follows the measurement noise while the left
+side is skewed. The skewness in the distribution is due to cloud impacts which
+go undetected. These cases have cloud impact less than the threshold value and
+are misclassfied as clear. The frequency of such cases is higher in Sreerekha
+et al approach than the clear-ksy screening presented here. The measure of
+skewness is also smaller for the clear-sky screening. 
+%In the report by
+%\cite{rekha2012potential} they mention that for 6\,K threshold value, around
+%2.4\% of the cloudy cases are misclassfied as clear. For this value of
+%threshold, 41\% of the clear cases are also classfied as cloudy and rejected.
 
-The regression approach described here does not provide any way to correct the misclassfied cases, but the frequency of such cases can be controlled through clear-sky cutoff ($dtb_{cs}$).
-When the clear-sky screening is applied to this dataset, around 13.05\% of the cases are classified as cloudy when $dtb_{cs}$ corresponds to noise-index = 1$\sigma$, while with 2$\sigma$ around 7.2\% are classified as cloudy.
-These cloudy cases are corrected according to the cubic model.
-After correction, the average deviation to the clear-sky noise-free values in the corrected measurements should be closer to zero than uncorrected measurements.
-Before correction, the average bias for measurements is -0.30\,K but after correction it reduces to -0.06\,K and -0.11\,K for the two values of the noise-index respectively.
-This indicates that a larger value of noise-index increases the probability of falsely classifying clear cases as cloudy.
+The regression approach described here does not provide any way to correct the
+misclassfied cases, but the frequency of such cases can be controlled through
+clear-sky cutoff ($dtb_{cs}$). When the clear-sky screening is applied to this
+dataset, around 13.05\% of the cases are classified as cloudy when $dtb_{cs}$
+corresponds to noise-index = 1$\sigma$, while with 2$\sigma$ around 7.2\% are
+classified as cloudy. These cloudy cases are corrected according to the cubic
+model. After correction, the average deviation to the clear-sky noise-free
+values in the corrected measurements should be closer to zero than uncorrected
+measurements. Before correction, the average bias for measurements is -0.30\,K
+but after correction it reduces to -0.06\,K and -0.11\,K for the two values of
+the noise-index respectively. This indicates that a larger value of noise-index
+increases the probability of falsely classifying clear cases as cloudy.
 %
@@
 	\includegraphics[height=85mm]{PDF_corrected_AWS-32_AWS-4X_thinned}
-	\caption{Same as Figure~\ref{fig:correction:c34-42:thinned}, but for channel combinations: AWS-32 and AWS-4X.}
+	\caption{Same as Fig.~\ref{fig:correction:c34-42:thinned}, but for channel combinations: AWS-32 and AWS-4X.}
 	\label{fig:correction:c32-4X:thinned}
@@
 
-As a reference, we also apply the correction scheme described above to correct AWS-32 using AWS-4X.
-In this case, C1 and C2 are AWS-32 and AWS-4X.
-The TB correlations between AWS-32 and AWS-4X are poor and show a large spread particularly for large cloud impacts [figure not shown].
-We fit the data to a cubic model, but exclude cases with $Tb2-Tb1 <$ -20\,K.
-Also cases with TB difference less than 0.2\,K are classified as clear and are not included in the fit.
-The clear-sky screening is also  evaluated for noise-index = 1$\sigma$ and $2\sigma$.
-Figure~\ref{fig:correction:c32-4X:thinned} shows the deviations to clear-sky values before and after correction, and the corresponding metrics are provided in Table~\ref{tab:correction:stats:32:4X}.
-As evident from the figure, \cite{rekha2012potential} classifies all measurements with cloud impact greater than 6\,K as cloudy, but a significant skewness in the distribution indicates misclassfication of cloudy cases.
-However, the frequency of misclassfied cases is significantly lower for our clear-sky screening.
-With \cite{rekha2012potential}'s approach, around 62\% of the measurements are rejected as cloudy, but in our approach, 84\% of the cases are classified as cloudy.
-This clearly indicates a high rate of misclassification of the clear cases.
+As a reference with respect to having a channel at 229\,GHz, we also apply the
+correction scheme described above to correct AWS-32 using AWS-4X (following
+\citet{rekha2012potential}). In this case, C1 and C2 are AWS-32 and AWS-4X. The
+TB correlations between AWS-32 and AWS-4X are poor and show a large spread
+particularly for large cloud impacts (not shown). We fit the data to a
+cubic model, but exclude cases with $Tb2-Tb1 <$ -20\,K. Also cases with TB
+difference less than 0.2\,K are classified as clear and are not included in the
+fit. The clear-sky screening is also evaluated for noise-index = 1$\sigma$ and
+$2\sigma$. Fig.~\ref{fig:correction:c32-4X:thinned} shows the deviations to
+clear-sky values before and after correction, and the corresponding metrics are
+provided in Table~\ref{tab:correction:stats:32:4X}. As evident from the figure,
+\cite{rekha2012potential} classifies all measurements with cloud impact greater
+than 6\,K as cloudy, but a significant skewness in the distribution indicates
+misclassfication of cloudy cases. However, the frequency of misclassfied cases
+is significantly lower for our clear-sky screening. With
+\cite{rekha2012potential}'s approach, around 62\% of the measurements are
+rejected as cloudy, but in our approach, 84\% of the cases are classified as
+cloudy. This clearly indicates a high rate of misclassification of the clear
+cases.
 \begin{table}[!h]
@@
 corrected($2\sigma$) &   0.76 &  1.80 &              -1.06 &               68.00 \\
-sreerekha et al   &  -0.40 &  1.00 &              -2.54 &               62.02 \\
+Sreerekha et al   &  -0.40 &  1.00 &              -2.54 &               62.02 \\
 		\hline
@@
 \subsection{Application of correction scheme to AWS-32, AWS-33, AWS-35 and AWS-36}
-The correction scheme can also be extended to other combinations of 183GHz and 325GHz.
-The other possible combinations for clear-sky screening are: AWS-32 and AWS-41; AWS-33 and AWS-41; AWS-35 and AWS-43; AWS-36 and AWS-43.
-% 
-Table~\ref{tab:correction:stats:32:41}  shows the statistics when AWS-32 is corrected using AWS-41.
-The statistics of the filtered dataset are better than the approach by \cite{rekha2012potential}.
-However, a very high rejection fraction (85\%) indicates that a large percentage of clear cases are misclassfied as cloudy.
+The correction scheme can also be extended to other combinations of 183GHz and
+325GHz. The most relevant combinations for clear-sky screening are: AWS-32 and
+AWS-41; AWS-33 and AWS-41; AWS-35 and AWS-43; AWS-36 and AWS-43.
 
-Table~\ref{tab:correction:stats:33:41} shows the statistics when AWS-33 is corrected using AWS-41.
-These TB differences for this combination and the cloud impact in AWS-33 are highly correlated and using a cubic model, approximately 20\% of the observations are corrected, which reduces the average bias in the measurements from -0.33\,K to -0.05\,K.
+Table~\ref{tab:correction:stats:32:41} shows the statistics when AWS-32 is
+corrected using AWS-41. The statistics of the filtered dataset are better than
+the approach by \cite{rekha2012potential}, while the corrected data have poorer
+statistics. This is not surprising as the weighting function match between 
+AWS-32 and  AWS-41 is poor.
+%However, a very high rejection
+%fraction (85\%) indicates that a large percentage of clear cases are
+%misclassfied as cloudy.
 
-A similar performance is seen for the combination AWS-35 and AWS-43, where 19\% of the measurements are classfied as cloudy.
-Correcting these measurements for the cloud impact reduces the average bias in the measurements from -0.33\,K to -0.05\,K.
-Table~\ref{tab:correction:stats:35:43}  shows the statistics obtained from this combination.
-The statistics from the channel combination AWS-36 and AWS-42 are shown in Table~\ref{tab:correction:stats:36:43}.
+Table~\ref{tab:correction:stats:33:41} shows the statistics when AWS-33 is
+corrected using AWS-41. These TB differences for this combination and the cloud
+impact in AWS-33 are highly correlated and using a cubic model, approximately
+20\% of the observations are corrected, which reduces the average bias in the
+measurements from -0.33\,K to -0.05\,K.
+
+A similar performance is seen for the combination AWS-35 and AWS-43, where 19\%
+of the measurements are classfied as cloudy. Correcting these measurements for
+the cloud impact reduces the average bias in the measurements from -0.33\,K to
+-0.05\,K. Table~\ref{tab:correction:stats:35:43} shows the statistics obtained
+from this combination. The statistics from the channel combination AWS-36 and
+AWS-42 are shown in Table~\ref{tab:correction:stats:36:43}.
 \begin{table}[!bt]
@@
 corrected(2sigma) &   0.47 &  1.68 &             -15.16 &               94.75 \\
-sreerekha et al   &  -0.41 &  1.00 &              -2.55 &               62.02 \\	
+Sreerekha et al   &  -0.41 &  1.00 &              -2.55 &               62.02 \\	
 		\hline
@@
 	corrected(2$\sigma$) &  -0.11 &  0.57 &              -1.17 &               10.19 \\
-	sreerekha et al   &  -0.30 &  0.79 &              -2.21 &               62.10 \\
+	Sreerekha et al   &  -0.30 &  0.79 &              -2.21 &               62.10 \\
 		\hline
@@
 corrected(2$\sigma$) &  -0.09 &  0.83 &              -2.39 &                6.37 \\
-sreerekha et al   &  -0.13 &  0.70 &              -0.58 &               62.24 \\
+Sreerekha et al   &  -0.13 &  0.70 &              -0.58 &               62.24 \\
 		\hline
@@
 corrected(2$\sigma$) &  -0.11 &  0.94 &              -0.18 &                2.06 \\
-sreerekha et al   &  -0.09 &  0.91 &              -0.10 &               62.20 \\
+Sreerekha et al   &  -0.09 &  0.91 &              -0.10 &               62.20 \\
 		\hline
@@
 \section{Discussion}
+
+(Just a start, to not forget these points)
 
@@
 %
+This study compares the options of having a channel at 229\,GHz or having some
+around 325\,GHz from a single perspective, cloud filtering(corection of
+183\,GHz data. There could be other important reasons to consider for the
+selection.
+
 \dots

### 2020-05-25 Report/aws_325ghz_study.tex
updated section 6

@@
 \subsection{Validation of simulations}
+\label{sec:validation}
 %
@@
 \subsection{Formulation of correction scheme}
+\label{sec:correction:scheme}
 %
@@
 The combinations of C1 and C2 are selected by matching their weighting
-functions as shown in Fig.~\ref{fig:3ch:prel}. Five 183 and 325\,GHz paired
+functions as shown in Fig.~\ref{fig:3ch:prel}. Five 183\,GHz and 325\,GHz paired
 combinations are possible, for example one such paired combination is AWS-34
@@
 This is useful for making a filtering in line with \citep{rekha2012potential},
-but is also needed in the correction scheme. The later is the case as the
+but is also needed in the correction scheme. The latter is the case as the
 polynomial fit derived gives a non-zero correction for clear-sky cases. In
@@
 \begin{equation}
-dtb_{cs}= f_{cs}^{-1}(x_{cs}) 
+x_{cs} = f_{cs}^{-1}(dtb_{cs}) 
 \label{eq:dtb}
@@
 $dtb_{cs}$ based on the noise level of the 183\,GHz channel involved, to be
-1$\sigma$ or 2$\sigma$ where $\sigma$ refers to the magnitide of measurement
+1$\sigma$ or 2$\sigma$ where $\sigma$ refers to the magnitude of measurement
 noise (Eq.~\ref{eq:noise}, often called NE$\Delta$T).
@@
       reference. The measurements have been corrected using brightness
-      temperatures from AWS-42. }
+      temperatures from AWS-42.
+The average bias values are given in parenthesis in the legend.
+No clear/cloudy classification based on the fit is applied, but cases with $Tb2 - Tb1 > 15$\,K are rejected.}
 	\label{fig:correction:c34-42}
@@
 		Dataset  		  &   bias &   std &   measure  & fraction  \\
-		&   [K]  &   [K] & skewness[K] & filtered/corrected [\%]\\
-		\hline
-Noise             &   0.00 &  0.63 &              -0.01 &                - \\
-uncorrected       &  -0.30 &  1.00 &              -2.64 &                - \\
-filtered(1$\sigma$)   &  -0.13 &  0.68 &              -0.25 &             13.05 \\
-corrected(1$\sigma$) &  -0.06 &  0.76 &              -0.48 &               13.05 \\
-corrected(2$\sigma$) &  -0.11 &  0.75 &              -0.69 &                7.21 \\
-Sreerekha et al   &  -0.21 &  0.78 &              -1.02 &               62.15 \\
-
-		\hline
-	\end{tabular}
-	\caption{Various metrics for different subsets of the measurement dataset.
-The different datasets are: noise (simulation dataset), uncorrected (measurment dataset), filtered $1\sigma$ (cloudy measurements are filtered with noise-index = 1$\sigma$), corrected $1\sigma$ (cloudy measurements are corrected with noise-index = 1$\sigma$), corrected $2\sigma$ (cloudy measurements are corrected with noise-index = 2$\sigma$), Sreerekha (measurements are filtered according to criteria described in \cite{rekha2012potential})   }
+							&   [K]  &   [K] & skewness[K] & rejected [\%]\\
+		\hline
+		noise             		&   0.00 &  0.63 &              -0.00 &                - \\
+		uncorrected       		&  -0.19 &  0.87 &              -2.42 &                - \\
+		filtered($1\sigma$ ) 	&  -0.10 &  0.66 &              -0.15 &               10.56 \\
+		corrected($1\sigma$) 	&  -0.05 &  0.72 &              -0.23 &                2.84 \\
+		corrected($2\sigma$) 	&  -0.09 &  0.70 &              -0.49 &                2.84 \\
+		sreerekha et al   		&  -0.14 &  0.73 &              -0.76 &               61.73 \\
+		\hline
+	\end{tabular}
+	\caption{Bias, standard deviation(std), and measure of skewness of deviations of the measurements to noise-free clear-sky cases.
+The fraction rejected describes the percentage of cases which are removed.
+The different datasets are: noise (simulation dataset), uncorrected (measurement dataset), filtered $1\sigma$ (cloudy measurements are filtered with $dtb_{cs}$ = 1$\sigma$), corrected $1\sigma$ (cloudy measurements are corrected with $dtb_{cs}$ = 1$\sigma$), corrected $2\sigma$ (cloudy measurements are corrected with $dtb_{cs}$ = 2$\sigma$), Sreerekha (measurements are filtered according to criteria described in \cite{rekha2012potential}).
+}
 	\label{tab:correction:stats:34:42}
+\end{table}
+%
+\begin{table}[!bt]
+	\centering
+	\begin{tabular}[b]{c|c|c|c|c}
+		Dataset  		  &   bias &   std &   measure  & fraction  \\
+		&   [K]  &   [K] & skewness[K] & rejected [\%]\\
+		\hline
+noise             		&   0.00 &  0.63 &              -0.01 &                - \\
+uncorrected       		&  -0.29 &  1.00 &              -2.62 &                - \\
+filtered($1\sigma$)  	&  -0.13 &  0.68 &              -0.24 &               17.49 \\
+corrected($1\sigma$) 	&  -0.06 &  0.76 &              -0.46 &                4.97 \\
+corrected($2\sigma$) 	&  -0.11 &  0.75 &              -0.69 &                4.97 \\
+sreerekha et al   		&  -0.20 &  0.79 &              -1.01 &               63.09 \\
+		\hline
+\end{tabular}
+\caption{Same as Table~\ref{tab:correction:stats:34:42}, but for thinned dataset. 50\% of the clear cases are removed to improve the improve the representation of cloudy cases }
+\label{tab:correction:stats:34:42:thinned}
 \end{table}
@@
 cloudy'' and are not corrected. The clear-sky adjustment for all eligible
-measurements (without clear-sky screening) is calculated from all three models,
+measurements (without clear/cloudy classification) is calculated from all three models,
 and the three predicted datasets are compared. The error in the predicted
@@
 observations. The occurrence frequency of the deviations from three models is
-shown in Fig.~\ref{fig:correction:c34-42}. The occurence frequency of the all
+shown in Fig.~\ref{fig:correction:c34-42}. The occurence frequency of the
 measurement without any filtering or correction is also plotted as reference
@@
 
-Before applying the clear-sky screening, the measurement dataset was also
-thinned in order to improve the representation of the cloudy cases. Validation
-of the simulations against ATMS data (Fig.\ref{fig:pdf:c16-22}) showed that the
-cloudy cases were underrepresented than the observations. Removing 50\% of the
-clear-sky cases, helped in improving the percentage of total cloudy cases in
-the database. Further in the text, results from only thinned dataset are
-described.
-
-To implement the clear-sky screening as discussed in the previous section, two
-different values of the noise-index are tested: $1\sigma$ and $2\sigma$, where
-$\sigma$ is the standard deviation of noise. For both values of noise-index the
-corresponding clear-sky cut-off ($dtb_{cs}$) is calculated using
-Eq~\ref{eq:dtb}. Figure~\ref{fig:correction:c34-42:thinned} shows the results
-when only the screened cloudy cases are corrected/rejected. Various metrics
-from the corrected measurements are also shown in
-Table~\ref{tab:correction:stats:34:42}. The results from
+To implement the clear/cloudy classification as discussed in the previous section, two
+different values of $dtb_{cs}$ are tested: $1\sigma$ and $2\sigma$. For both values of $dtb_{cs}$ the
+corresponding clear-sky cut-off ($x_{cs}$) is calculated using
+Eq~\ref{eq:dtb}. Figure~\ref{fig:correction:c34-42} shows the deviation of the uncorrected and corrected measurements to their noise-free clear-sky values. The results from
 \cite{rekha2012potential} are also shown as reference (see Sec.~\ref{sec:rekha}
-for our assumptions). In their approach, the cases with TB difference between
-AWS-4x and AWS-32 greater than 6\,K are classified as cloudy and are rejected.
-Assuming that the measurement is cloudy in AWS-32, the corresponding measuremnt
-in other 183GHz channels is also rejected. In order to have a fair comparison
-of our approach with \cite{rekha2012potential}, we also include a dataset where
-all the cloudy cases according to the clear-sky screening are filtered out from
-the measurements. The metrics from this dataset are also provided in under
-label ``filtered''. For all datasets shown in the table, we assume that cases
-with $Tb2-Tb1 < $ -15\,K are ``too-cloudy''.
-%Such cases form 5\% of the thinned
-%dataset and are not included in the statistics.
-
-The distribution of the deviations in the filtered data (both with approach
-described by Sreerekha et al and the clear-sky screening) is non-Gaussian. The
+for our assumptions). In order to have a fair comparison
+of our approach with \cite{rekha2012potential}, we also include the dataset,``Filtered'', where all cloudy cases are rejected.
+Apart from the fit based cloudy classfication, it is also assumed that cases with $Tb2-Tb1 < $ -15\,K are ``too-cloudy'', and are rejected.
+Various metrics corresponding to the Figure~\ref{fig:correction:c34-42} are shown in
+Table~\ref{tab:correction:stats:34:42}.
+
+The distribution of the deviations in the pure-filtered data is non-Gaussian. The
 right side of the distribution follows the measurement noise while the left
 side is skewed. The skewness in the distribution is due to cloud impacts which
-go undetected. These cases have cloud impact less than the threshold value and
-are misclassfied as clear. The frequency of such cases is higher in Sreerekha
-et al approach than the clear-ksy screening presented here. The measure of
-skewness is also smaller for the clear-sky screening. 
-%In the report by
-%\cite{rekha2012potential} they mention that for 6\,K threshold value, around
-%2.4\% of the cloudy cases are misclassfied as clear. For this value of
-%threshold, 41\% of the clear cases are also classfied as cloudy and rejected.
-
-The regression approach described here does not provide any way to correct the
-misclassfied cases, but the frequency of such cases can be controlled through
-clear-sky cutoff ($dtb_{cs}$). When the clear-sky screening is applied to this
-dataset, around 13.05\% of the cases are classified as cloudy when $dtb_{cs}$
-corresponds to noise-index = 1$\sigma$, while with 2$\sigma$ around 7.2\% are
-classified as cloudy. These cloudy cases are corrected according to the cubic
-model. After correction, the average deviation to the clear-sky noise-free
+go undetected.
+The frequency of such cases is higher in Sreerekha in comparison to the correction scheme presented here.
+The regression approach described here does not provide any way to correct the misclassfied cases, but the frequency of such cases can be controlled through $dtb_{cs}$.
+With a fit based cloudy classification, around 7\% of the cases are classified as cloudy when $dtb_{cs}$
+= 1$\sigma$.  After correction, the average deviation to the clear-sky noise-free
 values in the corrected measurements should be closer to zero than uncorrected
-measurements. Before correction, the average bias for measurements is -0.30\,K
-but after correction it reduces to -0.06\,K and -0.11\,K for the two values of
-the noise-index respectively. This indicates that a larger value of noise-index
-increases the probability of falsely classifying clear cases as cloudy.
+measurements. Before correction, the average bias for measurements is -0.19\,K
+but after correction it reduces to -0.05\,K and -0.09\,K for the two values of
+the $dtb_{cs}$ respectively.
+
+In Sec.~\ref{sec:validation} the validation of simulations against ATMS data (Fig.\ref{fig:pdf:c16-22}) showed that the cloudy cases in the simulations were underrepresented in comparison to the observations.
+In order to have a better representation of the cloudy cases, we thin the measurement dataset by rejecting 50\% of the clear-sky cases.
+Results from this smaller dataset are shown in Table~\ref{fig:correction:c34-42:thinned}.
+In comparison to the original dataset, the statistics in the thinned dataset is slightly worse, as expected.
+But overall the performance of the correction scheme is comparable.
+For all further analysis presented in this report, we use the thinned dataset.
 %
@@
 TB correlations between AWS-32 and AWS-4X are poor and show a large spread
-particularly for large cloud impacts (not shown). We fit the data to a
-cubic model, but exclude cases with $Tb2-Tb1 <$ -20\,K. Also cases with TB
-difference less than 0.2\,K are classified as clear and are not included in the
-fit. The clear-sky screening is also evaluated for noise-index = 1$\sigma$ and
-$2\sigma$. Fig.~\ref{fig:correction:c32-4X:thinned} shows the deviations to
+particularly for large cloud impacts (not shown). We fit the data to a polynomial model as described in Sec.~\ref{sec:correction:scheme} but exclude cases with $Tb2-Tb1 <$ -20\,K in the fit.
+
+Fig.~\ref{fig:correction:c32-4X:thinned} shows the deviations of the measurements to
 clear-sky values before and after correction, and the corresponding metrics are
-provided in Table~\ref{tab:correction:stats:32:4X}. As evident from the figure,
-\cite{rekha2012potential} classifies all measurements with cloud impact greater
-than 6\,K as cloudy, but a significant skewness in the distribution indicates
-misclassfication of cloudy cases. However, the frequency of misclassfied cases
-is significantly lower for our clear-sky screening. With
-\cite{rekha2012potential}'s approach, around 62\% of the measurements are
-rejected as cloudy, but in our approach, 84\% of the cases are classified as
-cloudy. This clearly indicates a high rate of misclassification of the clear
-cases.
+provided in Table~\ref{tab:correction:stats:32:4X}.
+Rejecting all the cloudy cases reduces the average bias in the measurements from -0.62\,K to -0.22\,K, but when these cases are corrected, the total bias increases to 0.87\,K.
+This indicates that the relationship between AWS-32 and AWS-4X is inadequate to estimate the cloud impact in AWS-32.
+% 
 \begin{table}[!h]
@@
 		Dataset  		  &   bias &   std &   measure & fraction \\
-		&   [K]  &   [K] & skewness[K] 		& filtered/corrected [\%]\\
-		\hline
-Noise             &  -0.00 &  0.45 &               0.02 &                - \\
-uncorrected       &  -0.62 &  1.76 &              -4.61 &                - \\
-filtered($1\sigma$)  &  -0.21 &  0.52 &              -0.65 &               84.49 \\
-corrected($1\sigma$) &   0.88 &  1.76 &              -1.29 &               84.49 \\
-corrected($2\sigma$) &   0.76 &  1.80 &              -1.06 &               68.00 \\
-Sreerekha et al   &  -0.40 &  1.00 &              -2.54 &               62.02 \\
+						&   [K]  &   [K] & skewness[K] 		& rejected [\%]\\
+		\hline
+Noise             		&  -0.00 &  0.45 &               0.01 &                - \\
+uncorrected       		&  -0.62 &  1.77 &              -4.61 &                - \\
+filtered($1\sigma$)  	&  -0.22 &  0.51 &              -0.65 &               85.37 \\
+corrected($1\sigma$) 	&   0.87 &  1.75 &              -1.31 &                5.35 \\
+corrected($2\sigma$) 	&   0.76 &  1.80 &              -1.08 &                5.35 \\
+sreerekha et al   		&  -0.41 &  1.00 &              -2.54 &               62.95 \\
 		\hline
@@
 \subsection{Application of correction scheme to AWS-32, AWS-33, AWS-35 and AWS-36}
+%
 The correction scheme can also be extended to other combinations of 183GHz and
@@
 AWS-32 and  AWS-41 is poor.
-%However, a very high rejection
-%fraction (85\%) indicates that a large percentage of clear cases are
-%misclassfied as cloudy.
 
 Table~\ref{tab:correction:stats:33:41} shows the statistics when AWS-33 is
-corrected using AWS-41. These TB differences for this combination and the cloud
-impact in AWS-33 are highly correlated and using a cubic model, approximately
-20\% of the observations are corrected, which reduces the average bias in the
-measurements from -0.33\,K to -0.05\,K.
-
-A similar performance is seen for the combination AWS-35 and AWS-43, where 19\%
-of the measurements are classfied as cloudy. Correcting these measurements for
-the cloud impact reduces the average bias in the measurements from -0.33\,K to
--0.05\,K. Table~\ref{tab:correction:stats:35:43} shows the statistics obtained
-from this combination. The statistics from the channel combination AWS-36 and
-AWS-42 are shown in Table~\ref{tab:correction:stats:36:43}.
+corrected using AWS-41. The TB differences for this combination and the cloud
+impact in AWS-33 are highly correlated.
+Rejecting the cloudy cases reduces the average bias in the measurements from -0.33\,K to -0.13\,K, while a correction of cloudy cases according to the correction scheme reduces the bias further to 0.01\,K.
+
+A similar performance is seen for the combination AWS-35 and AWS-43, where 21\%
+of the measurements are classfied as cloudy.
+Table~\ref{tab:correction:stats:35:43} shows the statistics obtained from this combination.
+The statistics from the channel combination AWS-36 and AWS-42 are shown in Table~\ref{tab:correction:stats:36:43}.
+%
 \begin{table}[!bt]
@@
 		Dataset  		  &   bias &   std &   measure & fraction \\
-		&   [K]  &   [K] & skewness[K] & filtered/corrected [\%]\\
-		\hline
- Noise             &  -0.00 &  0.45 &               0.01 &               - \\
-uncorrected       &  -0.48 &  1.82 &             -14.94 &                - \\
-filtered(1sigma)  &  -0.20 &  0.55 &              -0.61 &               92.99 \\
-corrected(1sigma) &   0.48 &  1.68 &             -15.20 &               92.99 \\
-corrected(2sigma) &   0.47 &  1.68 &             -15.16 &               94.75 \\
-Sreerekha et al   &  -0.41 &  1.00 &              -2.55 &               62.02 \\	
+							&   [K]  &   [K] & skewness[K] & rejected [\%]\\
+		\hline
+noise             		&   0.00 &  0.45 &               0.00 &                - \\
+uncorrected       		&  -0.48 &  1.82 &             -14.89 &                - \\
+filtered($1\sigma$)  	&  -0.26 &  0.77 &             -16.30 &               72.27 \\
+corrected($1\sigma$) 	&   0.44 &  1.70 &             -14.68 &                7.93 \\
+corrected($2\sigma$) 	&   0.25 &  1.72 &             -13.85 &                7.93 \\
+sreerekha et al   		&  -0.41 &  1.00 &              -2.54 &               62.04 \\
 		\hline
@@
 		Dataset  		  &   bias &   std &   measure  & fraction\\
-		&   [K]  &   [K] & skewness[K]                   & filtered/corrected [\%]\\
-		\hline
-	Noise             &  -0.00 &  0.45 &               0.01 &               - \\
+						&   [K]  &   [K] & skewness[K]  & rejected [\%]\\
+		\hline
+	noise       	    	&  -0.00 &  0.45 &               0.00 &               - \\
 	uncorrected	    		&  -0.33 &  0.91 &              -3.15 &                - \\
-	filtered(1$\sigma$)  &  -0.13 &  0.49 &              -0.39 &               20.60 \\
-	corrected(1$\sigma$) &  -0.05 &  0.59 &              -0.85 &               20.60 \\
-	corrected(2$\sigma$) &  -0.11 &  0.57 &              -1.17 &               10.19 \\
-	Sreerekha et al   &  -0.30 &  0.79 &              -2.21 &               62.10 \\
+	filtered($1\sigma$)  	&  -0.13 &  0.49 &              -0.40 &               26.13 \\
+	corrected($1\sigma$) 	&  -0.05 &  0.59 &              -0.85 &                6.87 \\
+	corrected($2\sigma$) 	&  -0.11 &  0.57 &              -1.17 &                6.87 \\
+	sreerekha et al   		&  -0.30 &  0.79 &              -2.21 &               62.99 \\
+
 		\hline
@@
 		Dataset  		  &   bias &   std &   measure & fraction \\
-		&   [K]  &   [K] & skewness[K] & filtered/corrected [\%]\\
-		\hline
- Noise             &  -0.00 &  0.63 &              -0.01 &                - \\
-uncorrected       &  -0.27 &  1.06 &              -4.44 &                - \\
-filtered(1$\sigma$)  &  -0.13 &  0.68 &              -0.47 &               19.02 \\
-corrected(1$\sigma$) &   0.01 &  0.90 &              -1.67 &               19.02 \\
-corrected(2$\sigma$) &  -0.09 &  0.83 &              -2.39 &                6.37 \\
-Sreerekha et al   &  -0.13 &  0.70 &              -0.58 &               62.24 \\
+							&   [K]  &   [K] & skewness[K] & rejected [\%]\\
+		\hline
+ Noise           	  &  -0.00 &  0.63 &               0.00 &                -\\
+uncorrected     	  &  -0.27 &  1.06 &              -4.42 &                - \\
+filtered($1\sigma$)	  &  -0.13 &  0.68 &              -0.46 &               21.42 \\
+corrected($1\sigma$)  &   0.01 &  0.90 &              -1.66 &                2.87 \\
+corrected($2\sigma$)  &  -0.09 &  0.83 &              -2.37 &                2.87 \\
+sreerekha et al  	  &  -0.13 &  0.70 &              -0.58 &               63.10 \\
+
 		\hline
@@
 		Dataset  		  &   bias &   std &   measure & fraction  \\
-		&   [K]  &   [K] & skewness[K] &				filtered/corrected [\%]\\
+							&   [K]  &   [K] & skewness[K] & rejected [\%]\\
 		\hline
  Noise            	 &  -0.00 &  0.88 &              -0.01 &               - \\
-uncorrected       &  -0.16 &  1.01 &              -0.86 &                - \\
-filtered(1$\sigma$)  &  -0.11 &  0.92 &              -0.12 &                4.98 \\
-corrected(1$\sigma$) &  -0.07 &  0.93 &              -0.07 &                4.98 \\
-corrected(2$\sigma$) &  -0.11 &  0.94 &              -0.18 &                2.06 \\
-Sreerekha et al   &  -0.09 &  0.91 &              -0.10 &               62.20 \\
+uncorrected      	 &  -0.16 &  1.02 &              -0.86 &                - \\
+filtered($1\sigma$)  &  -0.11 &  0.92 &              -0.13 &                7.39 \\
+corrected($1\sigma$) &  -0.07 &  0.93 &              -0.07 &                2.50 \\
+corrected($2\sigma$) &  -0.11 &  0.94 &              -0.19 &                2.50 \\
+sreerekha et al 	 &  -0.09 &  0.91 &              -0.11 &               63.11 \\
 		\hline

### 2020-05-26 Report/aws_325ghz_study.tex
A few changes and comments in the report file.

@@
       against cloud impact in AWS-34. The black curve represents the line of
-      best fit as a third order polynomial. Red and green color represent the
-      clear and cloudy cases respectively in the simulation dataset. The blue
-      vertical line represents a clear-sky screening threshold of 0.2\,K. }
+      best fit (of green points) as a third order polynomial. Red and green
+      color represent the clear and cloudy cases respectively in the simulation
+      dataset. The blue vertical line represents a clear-sky screening
+      threshold of 0.2\,K. }
 	\label{fig:fit:c34-42}
@@
 differences, but as the impact of cloud increases the correlations gets poorer.
-The data can be fitted to linear or non-linear models. The fitted model can be
-used to interpolate the adjustment required to compensate the brightness
+The data can be fitted by linear or non-linear models. The fitted model can be
+used to obtain the adjustment required to compensate the brightness
 temperature for cloudy cases. To avoid fitting the ``too cloudy'' cases which
@@
 It is also important to have a manner for making a clear/cloudy classification.
-This is useful for making a filtering in line with \citep{rekha2012potential},
+This is useful for making a filtering in line with \citet{rekha2012potential},
 but is also needed in the correction scheme. The latter is the case as the
@@
 	\centering
-	\includegraphics[clip,trim=0 0 0 0,height=90mm]{PDF_corrected_AWS-34_AWS-42}
+	\includegraphics[clip,trim=0 0 0 0,height=80mm]{PDF_corrected_AWS-34_AWS-42}
 	\caption{Deviation of AWS-34 measurements to noise free clear-sky
@@
 
-\begin{figure}[!]
-	\centering
-	\includegraphics[height=90mm]{PDF_corrected_AWS-34_AWS-42_thinned}
+\begin{figure}[!p]
+	\centering
+	\includegraphics[height=80mm]{PDF_corrected_AWS-34_AWS-42_thinned}
 	\caption{Deviation of AWS-34 measurements to noise free clear-sky
@@
 cloudy'' and are not corrected. The clear-sky adjustment for all eligible
-measurements (without clear/cloudy classification) is calculated from all three models,
-and the three predicted datasets are compared. The error in the predicted
-measurements is assessed by calculating the deviation to noise-free clear-sky
-observations. The occurrence frequency of the deviations from three models is
-shown in Fig.~\ref{fig:correction:c34-42}. The occurence frequency of the
-measurement without any filtering or correction is also plotted as reference
-(orange color). If all measurements are devoid of any cloud impact, the
-deviations should follow the gaussian distribution of noise. However, in real
-scenarios, the distribution is skewed due to the impact of clouds. It should
-also be noted that since no clear-sky screening was included in the
-measurements, the measurements with zero deviation to noise-free clear-sky were
-reduced. This indicates that it is extremely important to correctly classify
-the cases as clear/cloudy. Among the three models, the quadratic and cubic
-models work better than the linear model. Both quadratic and cubic models are
-able to correct the cloud impact in the measurements, however the values of
-average bias indicates that the cubic model performs better. The average
-deviation in the dataset is -0.82\,K and after correction with a cubic model,
-it reduces to -0.02\,K, while for quadratic model, the average bias after
-correction is 0.24\,K. For all other results described in this section, a cubic
-model is used.
-
-To implement the clear/cloudy classification as discussed in the previous section, two
-different values of $dtb_{cs}$ are tested: $1\sigma$ and $2\sigma$. For both values of $dtb_{cs}$ the
-corresponding clear-sky cut-off ($x_{cs}$) is calculated using
-Eq~\ref{eq:dtb}. Figure~\ref{fig:correction:c34-42} shows the deviation of the uncorrected and corrected measurements to their noise-free clear-sky values. The results from
+measurements (without clear/cloudy classification) is calculated from all three
+models, and the three predicted datasets are compared. The error in the
+predicted measurements is assessed as the deviation to corresponding noise-free
+clear-sky value.
+
+The occurrence frequency of the deviations from three models is shown in
+Fig.~\ref{fig:correction:c34-42}. The occurence frequency of the measurement
+without any filtering or correction is also plotted as reference (orange
+color). If all measurements are devoid of any cloud impact, the deviations
+should follow the gaussian distribution of noise. However, in real scenarios,
+the distribution is skewed due to the impact of clouds. It should also be noted
+that since no clear-sky screening was included in the measurements, the
+measurements with zero deviation to noise-free clear-sky were reduced. [* Don't
+get what you mean here * ] This
+indicates that it is extremely important to correctly classify the cases as
+clear/cloudy. Among the three models, the quadratic and cubic models work
+better than the linear model. Both quadratic and cubic models are able to
+correct the cloud impact in the measurements, however the values of average
+bias indicates that the cubic model performs better. The average deviation in
+the dataset is -0.82\,K and after correction with a cubic model, it reduces to
+-0.02\,K, while for quadratic model, the average bias after correction is
+0.24\,K. For all other results described in this section, a cubic model is
+used.
+
+[* The text seems to indicate that you here move to Fig 11, but you refer to
+Fig 10. *]
+
+To implement the clear/cloudy classification as discussed in the previous
+section, two different values of $dtb_{cs}$ are tested: $1\sigma$ and
+$2\sigma$. For both values of $dtb_{cs}$ the corresponding clear-sky cut-off
+($x_{cs}$) is calculated using Eq~\ref{eq:dtb}.
+Figure~\ref{fig:correction:c34-42} shows the deviation of the uncorrected and
+corrected measurements to their noise-free clear-sky values. The results from
 \cite{rekha2012potential} are also shown as reference (see Sec.~\ref{sec:rekha}
-for our assumptions). In order to have a fair comparison
-of our approach with \cite{rekha2012potential}, we also include the dataset,``Filtered'', where all cloudy cases are rejected.
-Apart from the fit based cloudy classfication, it is also assumed that cases with $Tb2-Tb1 < $ -15\,K are ``too-cloudy'', and are rejected.
-Various metrics corresponding to the Figure~\ref{fig:correction:c34-42} are shown in
+for our assumptions). In order to allow a more direct comparison of our
+approach with \cite{rekha2012potential}, we also include the
+dataset,``Filtered'', where all cloudy cases are rejected. Apart from the fit
+based cloudy classfication, it is also assumed that cases with $Tb2-Tb1 < $
+-15\,K are ``too-cloudy'', and are rejected. Various metrics corresponding to
+the Figure~\ref{fig:correction:c34-42} are shown in
 Table~\ref{tab:correction:stats:34:42}.
@@
 
-In Sec.~\ref{sec:validation} the validation of simulations against ATMS data (Fig.\ref{fig:pdf:c16-22}) showed that the cloudy cases in the simulations were underrepresented in comparison to the observations.
-In order to have a better representation of the cloudy cases, we thin the measurement dataset by rejecting 50\% of the clear-sky cases.
-Results from this smaller dataset are shown in Table~\ref{fig:correction:c34-42:thinned}.
-In comparison to the original dataset, the statistics in the thinned dataset is slightly worse, as expected.
-But overall the performance of the correction scheme is comparable.
+In Sec.~\ref{sec:validation} the validation of simulations against ATMS data
+(Fig.\ref{fig:pdf:c16-22}) showed that the cloudy cases in the simulations were
+underrepresented in comparison to the observations. In order to have a better
+representation of the cloudy cases, we thin the measurement dataset by
+rejecting 50\% of the clear-sky cases. Results from this smaller dataset are
+shown in Table~\ref{fig:correction:c34-42:thinned}. [* You mean FIgure? But you
+should the also refer to Table 5. *]In comparison to the
+original dataset, the statistics in the thinned dataset is slightly worse, as
+expected. But overall the performance of the correction scheme is comparable.
 For all further analysis presented in this report, we use the thinned dataset.
@@
 
-Fig.~\ref{fig:correction:c32-4X:thinned} shows the deviations of the measurements to
-clear-sky values before and after correction, and the corresponding metrics are
-provided in Table~\ref{tab:correction:stats:32:4X}.
-Rejecting all the cloudy cases reduces the average bias in the measurements from -0.62\,K to -0.22\,K, but when these cases are corrected, the total bias increases to 0.87\,K.
-This indicates that the relationship between AWS-32 and AWS-4X is inadequate to estimate the cloud impact in AWS-32.
+Fig.~\ref{fig:correction:c32-4X:thinned} shows the deviations of the
+measurements to clear-sky values before and after correction, and the
+corresponding metrics are provided in Table~\ref{tab:correction:stats:32:4X}.
+Rejecting all the cloudy cases reduces the average bias in the measurements
+from -0.62\,K to -0.22\,K, but when these cases are corrected, the total bias
+increases to 0.87\,K. This indicates that the relationship between AWS-32 and
+AWS-4X is inadequate to estimate the cloud impact in AWS-32.
+[* You should discuss the high fraction reject we get for ``filtered'', but is
+this the best we can do? *]
+
 %
@@
 corrected using AWS-41. The TB differences for this combination and the cloud
-impact in AWS-33 are highly correlated.
-Rejecting the cloudy cases reduces the average bias in the measurements from -0.33\,K to -0.13\,K, while a correction of cloudy cases according to the correction scheme reduces the bias further to 0.01\,K.
+impact in AWS-33 are highly correlated. Rejecting the cloudy cases reduces the
+average bias in the measurements from -0.33\,K to -0.13\,K, while a correction
+of cloudy cases according to the correction scheme reduces the bias further to
+0.01\,K. [* Last value not consistent with table *]
 
@@
 of the measurements are classfied as cloudy.
-Table~\ref{tab:correction:stats:35:43} shows the statistics obtained from this combination.
-The statistics from the channel combination AWS-36 and AWS-42 are shown in Table~\ref{tab:correction:stats:36:43}.
-%
+Table~\ref{tab:correction:stats:35:43} shows the statistics obtained from this
+combination. The statistics from the channel combination AWS-36 and AWS-42 are
+shown in Table~\ref{tab:correction:stats:36:43}. [* Add a bit of discussion for
+both combiniations. *]
+
+[* Should not the fraction of rejected for Sreerekha et al be the same for all
+channel combinations? *]
+
 \begin{table}[!bt]

### 2020-05-27 Report/aws_325ghz_study.tex
addressed comments in section 6

@@
 \begin{equation}
-Tb1_{as}-Tb2_{cs} = f(x_m)
+Tb1_{as}-Tb1_{cs} = f(x_m)
 \label{eq:TB:diff}
@@
       color represent the clear and cloudy cases respectively in the simulation
-      dataset. The blue vertical line represents a clear-sky screening
-      threshold of 0.2\,K. }
+      dataset. The blue vertical line represents correction threshold, $x_{cs}$, for $dtb_{cs} =$
+      0.2\,K. }
 	\label{fig:fit:c34-42}
@@
 are used. The two variables have a reasonably strong correlation for small TB
-differences, but as the impact of cloud increases the correlations gets poorer.
+differences, but as the impact of cloud increases, the correlations gets poorer.
 The data can be fitted by linear or non-linear models. The fitted model can be
@@
 excluded in the fit. Also, cases with $Tb2-Tb1 < 0.2$\,K (red color dots) are
-assumed to be clear-sky are not included in the model.
+assumed to be clear-sky, are not included in the model.
 
 It is also important to have a manner for making a clear/cloudy classification.
-This is useful for making a filtering in line with \citet{rekha2012potential},
+This is useful for making filtering in line with \citet{rekha2012potential},
 but is also needed in the correction scheme. The latter is the case as the
@@
 formulated. The polynomial fit will be used also for this part.
-
-%Before correcting the measurements, it is important to correctly classify all
-%the cases into clear or cloudy. To avoid any undesirable adjustment of the
-%clear cases, a clear-sky screening is added  to the correction scheme. In this
-%screening, we assume that for clear cases, the average differences of the
-%measurements to their noise-free clear-sky values are of the order of the
-%instrument noise. Further in the text, we refer this value of noise as
-%``noise-index''.
-%Assuming the function $f$ in eqn~\ref{eq:TB:diff} to be invertible, and if $x_{cs}$  represents the noise-index, the TB difference between the measurements from C1 and C2 for the noise-index can be used as a measure of clear-sky screening: ($dtb_{cs}$):
 
@@
 
-%The value of $dtb_{cs}$ is not constant and shall depend on the the combination
-%of 183 GHz and 325 GHz used. The measurements with TB difference between C2 and
-%C1 less than $dtb_{cs}$ are considered cloudy and are corrected. In
-%Fig.~\ref{fig:correction:c34-42}, the blue dotted line represents the clear-sky
-%screening cut-off when noise-index = 0.2\,K. All measurements to the left of
-%this line are classified as cloudy, and vice-versa. For the dataset shown in
-%the figure, around 15\% of the total cases were classified as clear. The
-%sensitivity of noise-index is discussed in detail in the next section.
-
 \subsection{Application of correction scheme}
+%
 \begin{figure}[!p]
 	\centering
-	\includegraphics[clip,trim=0 0 0 0,height=80mm]{PDF_corrected_AWS-34_AWS-42}
+	\includegraphics[clip,trim=0 0 0 0,height=80mm]{PDF_corrected_AWS-34_AWS-42_allfits}
 	\caption{Deviation of AWS-34 measurements to noise free clear-sky
@@
 The average bias values are given in parenthesis in the legend.
-No clear/cloudy classification based on the fit is applied, but cases with $Tb2 - Tb1 > 15$\,K are rejected.}
+No clear/cloudy classification based on the fit is applied, but cases with $Tb2 - Tb1 > -15$\,K are rejected.}
+	\label{fig:correction:c34-42:fit}
+\end{figure}
+%
+\begin{figure}[!p]
+	\centering
+	\includegraphics[height=80mm]{PDF_corrected_AWS-34_AWS-42_all}
+	\caption{Deviation of AWS-34 measurements to noise free clear-sky simulations before and after correction.
+The measurements have been corrected using a cubic model.
+The different datasets are: noise (simulation dataset), uncorrected-all (measurement dataset without clear/cloudy classification), filtered $1\sigma$ (cloudy measurements are filtered with $dtb_{cs}$ = 1$\sigma$), corrected $1\sigma$ (cloudy measurements are corrected with $dtb_{cs}$ = 1$\sigma$), corrected $2\sigma$ (cloudy measurements are corrected with $dtb_{cs}$ = 2$\sigma$), Sreerekha (measurements are filtered according to criteria described in \cite{rekha2012potential}).
+      \cite{rekha2012potential}.}
 	\label{fig:correction:c34-42}
-\end{figure}
-%
-
-\begin{figure}[!p]
-	\centering
-	\includegraphics[height=80mm]{PDF_corrected_AWS-34_AWS-42_thinned}
-	\caption{Deviation of AWS-34 measurements to noise free clear-sky
-      simulations before and after correction. The measurements have been
-      corrected using a cubic model. The different datasets are: thinned: 50\%
-      of the clear-sky cases removed, filtered (1$\sigma$): cloudy measurements
-      are filtered with noise-index = 1$\sigma$, corrected (1$\sigma$): cloudy
-      measurements are corrected with noise-index = 1$\sigma$, Sreerekha et al:
-      cloud filtering according to criteria described in
-      \cite{rekha2012potential}.}
-	\label{fig:correction:c34-42:thinned}
 \end{figure}
@@
 		\hline
-		noise             		&   0.00 &  0.63 &              -0.00 &                - \\
-		uncorrected       		&  -0.19 &  0.87 &              -2.42 &                - \\
+		noise             		&   0.00 &  0.63 &               0.00 &                - \\
+		uncorrected-all       	&  -0.19 &  0.87 &              -2.42 &                - \\
 		filtered($1\sigma$ ) 	&  -0.10 &  0.66 &              -0.15 &               10.56 \\
@@
 		corrected($2\sigma$) 	&  -0.09 &  0.70 &              -0.49 &                2.84 \\
-		sreerekha et al   		&  -0.14 &  0.73 &              -0.76 &               61.73 \\
+		sreerekha et al   		&  -0.14 &  0.73 &              -0.76 &               43.60 \\
 		\hline
@@
 The fraction rejected describes the percentage of cases which are removed.
-The different datasets are: noise (simulation dataset), uncorrected (measurement dataset), filtered $1\sigma$ (cloudy measurements are filtered with $dtb_{cs}$ = 1$\sigma$), corrected $1\sigma$ (cloudy measurements are corrected with $dtb_{cs}$ = 1$\sigma$), corrected $2\sigma$ (cloudy measurements are corrected with $dtb_{cs}$ = 2$\sigma$), Sreerekha (measurements are filtered according to criteria described in \cite{rekha2012potential}).
+The different datasets are: noise (simulation dataset), uncorrected-all (measurement dataset without clear/cloudy classification), filtered $1\sigma$ (cloudy measurements are filtered with $dtb_{cs}$ = 1$\sigma$), corrected $1\sigma$ (cloudy measurements are corrected with $dtb_{cs}$ = 1$\sigma$), corrected $2\sigma$ (cloudy measurements are corrected with $dtb_{cs}$ = 2$\sigma$), Sreerekha (measurements are filtered according to criteria described in \cite{rekha2012potential}).
 }
@@
 	uncorrected       		&  -0.29 &  1.00 &              -2.62 &                - \\
-filtered($1\sigma$)  	&  -0.13 &  0.68 &              -0.24 &               17.49 \\
-corrected($1\sigma$) 	&  -0.06 &  0.76 &              -0.46 &                4.97 \\
-corrected($2\sigma$) 	&  -0.11 &  0.75 &              -0.69 &                4.97 \\
-sreerekha et al   		&  -0.20 &  0.79 &              -1.01 &               63.09 \\
-		\hline
-\end{tabular}
-\caption{Same as Table~\ref{tab:correction:stats:34:42}, but for thinned dataset. 50\% of the clear cases are removed to improve the improve the representation of cloudy cases }
+	filtered($1\sigma$)  	&  -0.13 &  0.68 &              -0.25 &               17.54 \\
+	corrected($1\sigma$) 	&  -0.06 &  0.76 &              -0.46 &                4.99 \\
+	corrected($2\sigma$) 	&  -0.11 &  0.75 &              -0.69 &                4.99 \\
+	sreerekha et al   		&  -0.20 &  0.78 &              -1.00 &               45.36 \\	
+		\hline
+\end{tabular}
+\caption{Same as Table~\ref{tab:correction:stats:34:42}, but for thinned dataset. 50\% of the clear cases are removed to improve the representation of cloudy cases }
 \label{tab:correction:stats:34:42:thinned}
@@
 The occurrence frequency of the deviations from three models is shown in
-Fig.~\ref{fig:correction:c34-42}. The occurence frequency of the measurement
+Fig.~\ref{fig:correction:c34-42:fit}. The occurence frequency of the measurement
 without any filtering or correction is also plotted as reference (orange
@@
 should follow the gaussian distribution of noise. However, in real scenarios,
-the distribution is skewed due to the impact of clouds. It should also be noted
-that since no clear-sky screening was included in the measurements, the
-measurements with zero deviation to noise-free clear-sky were reduced. [* Don't
-get what you mean here * ] This
-indicates that it is extremely important to correctly classify the cases as
-clear/cloudy. Among the three models, the quadratic and cubic models work
+the distribution is skewed due to the impact of clouds. Among the three models, the quadratic and cubic models work
 better than the linear model. Both quadratic and cubic models are able to
@@
 bias indicates that the cubic model performs better. The average deviation in
-the dataset is -0.82\,K and after correction with a cubic model, it reduces to
--0.02\,K, while for quadratic model, the average bias after correction is
-0.24\,K. For all other results described in this section, a cubic model is
-used.
-
-[* The text seems to indicate that you here move to Fig 11, but you refer to
-Fig 10. *]
+the dataset is -0.75\,K and after correction with a cubic model, it reduces to
+-0.05\,K, while for quadratic model, the average bias after correction is
+0.22\,K. For all other results described further, a cubic model is
+used. It should also be noted
+that since no clear/cloudy classification is included, the peak of the distributions (representing the clear-sky cases) is reduced in the corrected datasets. 
+To avoid correcting the clear cases, implementation of clear/cloudy classification is extremely important.
 
@@
 The distribution of the deviations in the pure-filtered data is non-Gaussian. The
-right side of the distribution follows the measurement noise while the left
+right side of the distribution follows measurement noise while the left
 side is skewed. The skewness in the distribution is due to cloud impacts which
-go undetected.
-The frequency of such cases is higher in Sreerekha in comparison to the correction scheme presented here.
+pass through the clear-sky threshold.
+A larger skewness in the dataset ``Sreerekha et al'' in comparsion to ``Filtered'' shows that the frequency of misclassfied cases is higher in the approach by \cite{rekha2012potential}.
 The regression approach described here does not provide any way to correct the misclassfied cases, but the frequency of such cases can be controlled through $dtb_{cs}$.
-With a fit based cloudy classification, around 7\% of the cases are classified as cloudy when $dtb_{cs}$
-= 1$\sigma$.  After correction, the average deviation to the clear-sky noise-free
-values in the corrected measurements should be closer to zero than uncorrected
-measurements. Before correction, the average bias for measurements is -0.19\,K
+After correction, the average deviation to the clear-sky noise-free values in the corrected measurements should be closer to zero than uncorrected.
+With a fit based cloudy classification, 10.56\% of the cases are classified as cloudy when $dtb_{cs}$
+= 1$\sigma$.  Before correction, the average bias for measurements is -0.19\,K
 but after correction it reduces to -0.05\,K and -0.09\,K for the two values of
@@
 representation of the cloudy cases, we thin the measurement dataset by
-rejecting 50\% of the clear-sky cases. Results from this smaller dataset are
-shown in Table~\ref{fig:correction:c34-42:thinned}. [* You mean FIgure? But you
-should the also refer to Table 5. *]In comparison to the
+removing 50\% of the clear-sky cases. The results from this smaller dataset, before and after filtering/correction are shown in Table~\ref{tab:correction:stats:34:42:thinned}. In comparison to the
 original dataset, the statistics in the thinned dataset is slightly worse, as
 expected. But overall the performance of the correction scheme is comparable. 
-For all further analysis presented in this report, we use the thinned dataset.
+For all further analysis presented in this report, the thinned dataset is used.
 %
@@
 	\includegraphics[height=85mm]{PDF_corrected_AWS-32_AWS-4X_thinned}
-	\caption{Same as Fig.~\ref{fig:correction:c34-42:thinned}, but for channel combinations: AWS-32 and AWS-4X.}
+	\caption{Same as Fig.~\ref{fig:correction:c34-42}, but for channel combinations: AWS-32 and AWS-4X.}
 	\label{fig:correction:c32-4X:thinned}
@@
 corresponding metrics are provided in Table~\ref{tab:correction:stats:32:4X}.
-Rejecting all the cloudy cases reduces the average bias in the measurements
-from -0.62\,K to -0.22\,K, but when these cases are corrected, the total bias
-increases to 0.87\,K. This indicates that the relationship between AWS-32 and
-AWS-4X is inadequate to estimate the cloud impact in AWS-32.
-[* You should discuss the high fraction reject we get for ``filtered'', but is
-this the best we can do? *]
+With clear/cloudy classification for $dtb_{cs} = 1\sigma$, around 85\% of the total measurements are classified as cloudy and are rejected in pure-filtering.
+Rejecting all the cloudy cases reduces the average bias in the measurements from -0.62\,K to -0.21\,K,  while with the approach from \citet{rekha2012potential} only 45\% of the data is rejected and the average bias reduces to  -0.41\,K.
+When all the cloudy cases, except the ``too cloudy'', are corrected, the total bias increases to 0.88\,K.
+The unusually high fraction of cloudy cases and an increase in bias on correction suggests misclassfication of clear cases as cloudy.
+Since, the weighting functions of AWS-32 and AWS-4X are poorly matched, their relationship is inadequate to estimate the cloud impact in AWS-32.
+Without any additional information, the regression approach can only provide a successful filtering in comparison to the original approach described by \citet{rekha2012potential},  although at the cost of high rejection fraction.
+Additional information e.g., TB from other channels, is necessary improve the accuracy of cloudy correction.
 
@@
 uncorrected       		&  -0.62 &  1.77 &              -4.61 &                - \\
-filtered($1\sigma$)  	&  -0.22 &  0.51 &              -0.65 &               85.37 \\
-corrected($1\sigma$) 	&   0.87 &  1.75 &              -1.31 &                5.35 \\
-corrected($2\sigma$) 	&   0.76 &  1.80 &              -1.08 &                5.35 \\
-sreerekha et al   		&  -0.41 &  1.00 &              -2.54 &               62.95 \\
-		\hline
-	\end{tabular}
-	\caption{Same as Table~\ref{tab:correction:stats:34:42}, but for channel combinations: AWS-32 and AWS-4X.   }
+filtered($1\sigma$)  	&  -0.21 &  0.51 &              -0.65 &               85.43 \\
+corrected($1\sigma$) 	&   0.88 &  1.76 &              -1.30 &                5.35 \\
+corrected($2\sigma$) 	&   0.76 &  1.80 &              -1.07 &                5.35 \\
+sreerekha et al   		&  -0.41 &  1.00 &              -2.54 &               45.36 \\
+		\hline
+	\end{tabular}
+	\caption{Same as Table~\ref{tab:correction:stats:34:42:thinned}, but for channel combinations: AWS-32 and AWS-4X.   }
 	\label{tab:correction:stats:32:4X}
@@
 AWS-32 and  AWS-41 is poor. 
-
 Table~\ref{tab:correction:stats:33:41} shows the statistics when AWS-33 is
@@
 average bias in the measurements from -0.33\,K to -0.13\,K, while a correction
-of cloudy cases according to the correction scheme reduces the bias further to
-0.01\,K. [* Last value not consistent with table *]
-
-A similar performance is seen for the combination AWS-35 and AWS-43, where 21\%
-of the measurements are classfied as cloudy.
-Table~\ref{tab:correction:stats:35:43} shows the statistics obtained from this
-combination. The statistics from the channel combination AWS-36 and AWS-42 are
-shown in Table~\ref{tab:correction:stats:36:43}. [* Add a bit of discussion for
-both combiniations. *]
-
-[* Should not the fraction of rejected for Sreerekha et al be the same for all
-channel combinations? *]
+of cloudy cases reduces the bias further to 0.05\,K.
+A similar performance is seen for the combination AWS-35 and AWS-43, and Table~\ref{tab:correction:stats:35:43} shows the statistics from this combination.
+After correction the bias due to cloudy measurements reduces -0.33\,K to -0.05\,K while rejecting only 6.88\% of the total cases.
+
+Table~\ref{tab:correction:stats:36:43} shows the statistics when AWS-36 is corrected using AWS-43.
+For this combination, the weighting functions have a poor match, but the TB differences and the cloud impact are strongly correlated, as the cloud impact in AWS-36 is relatively low in comparison to other 183\,GHz channels.
+The low fraction of rejection (7.38\%) also shows that most of the measurements are without cloud impact.
+However, the small fraction of cloudy cases which are corrected helps in successfully reducing the average bias from -0.16\,K to 0.07\,K.
 
@@
 uncorrected       		&  -0.48 &  1.82 &             -14.89 &                - \\
-filtered($1\sigma$)  	&  -0.26 &  0.77 &             -16.30 &               72.27 \\
-corrected($1\sigma$) 	&   0.44 &  1.70 &             -14.68 &                7.93 \\
-corrected($2\sigma$) 	&   0.25 &  1.72 &             -13.85 &                7.93 \\
-sreerekha et al   		&  -0.41 &  1.00 &              -2.54 &               62.04 \\
-		\hline
-	\end{tabular}
-	\caption{Same as Table~\ref{tab:correction:stats:34:42}, but for channel combinations: AWS-32 and AWS-41.   }
+filtered($1\sigma$)  	&  -0.26 &  0.77 &             -16.33 &               72.06 \\
+corrected($1\sigma$) 	&   0.43 &  1.70 &             -14.68 &                7.93 \\
+corrected($2\sigma$) 	&   0.25 &  1.72 &             -13.86 &                7.93 \\
+sreerekha et al   		&  -0.41 &  1.00 &              -2.54 &               45.36 \\
+		\hline
+	\end{tabular}
+	\caption{Same as Table~\ref{tab:correction:stats:34:42:thinned}, but for channel combinations: AWS-32 and AWS-41.   }
 	\label{tab:correction:stats:32:41}
@@
 	uncorrected	    		&  -0.33 &  0.91 &              -3.15 &                - \\
-	filtered($1\sigma$)  	&  -0.13 &  0.49 &              -0.40 &               26.13 \\
-	corrected($1\sigma$) 	&  -0.05 &  0.59 &              -0.85 &                6.87 \\
-	corrected($2\sigma$) 	&  -0.11 &  0.57 &              -1.17 &                6.87 \\
-	sreerekha et al   		&  -0.30 &  0.79 &              -2.21 &               62.99 \\
-
-		\hline
-	\end{tabular}
-	\caption{Same as Table~\ref{tab:correction:stats:34:42}, but for channel combinations: AWS-33 and AWS-41.   }
+	filtered($1\sigma$)  	&  -0.13 &  0.49 &              -0.40 &               26.18 \\
+	corrected($1\sigma$) 	&  -0.05 &  0.59 &              -0.85 &                6.88 \\
+	corrected($2\sigma$) 	&  -0.11 &  0.57 &              -1.17 &                6.88 \\
+	sreerekha et al   		&  -0.29 &  0.78 &              -2.22 &               45.36 \\
+		\hline
+	\end{tabular}
+	\caption{Same as Table~\ref{tab:correction:stats:34:42:thinned}, but for channel combinations: AWS-33 and AWS-41.   }
 	\label{tab:correction:stats:33:41}
@@
 uncorrected     	  &  -0.27 &  1.06 &              -4.42 &                - \\
-filtered($1\sigma$)	  &  -0.13 &  0.68 &              -0.46 &               21.42 \\
-corrected($1\sigma$)  &   0.01 &  0.90 &              -1.66 &                2.87 \\
-corrected($2\sigma$)  &  -0.09 &  0.83 &              -2.37 &                2.87 \\
-sreerekha et al  	  &  -0.13 &  0.70 &              -0.58 &               63.10 \\
-
-		\hline
-	\end{tabular}
-	\caption{Same as Table~\ref{tab:correction:stats:34:42}, but for channel combinations: AWS-35 and AWS-43.   }
+filtered($1\sigma$)	  &  -0.13 &  0.68 &              -0.46 &               21.30 \\
+corrected($1\sigma$)  &   0.01 &  0.90 &              -1.65 &                2.86 \\
+corrected($2\sigma$)  &  -0.09 &  0.83 &              -2.35 &                2.86 \\
+sreerekha et al  	  &  -0.13 &  0.70 &              -0.54 &               45.36 \\
+		\hline
+	\end{tabular}
+	\caption{Same as Table~\ref{tab:correction:stats:34:42:thinned}, but for channel combinations: AWS-35 and AWS-43.   }
 	\label{tab:correction:stats:35:43}
@@
 uncorrected      	 &  -0.16 &  1.02 &              -0.86 &                - \\
-filtered($1\sigma$)  &  -0.11 &  0.92 &              -0.13 &                7.39 \\
+filtered($1\sigma$)  &  -0.11 &  0.92 &              -0.13 &                7.38 \\
 corrected($1\sigma$) &  -0.07 &  0.93 &              -0.07 &                2.50 \\
 corrected($2\sigma$) &  -0.11 &  0.94 &              -0.19 &                2.50 \\
-sreerekha et al 	 &  -0.09 &  0.91 &              -0.11 &               63.11 \\
-		\hline
-	\end{tabular}
-	\caption{Same as Table~\ref{tab:correction:stats:34:42}, but for channel combinations: AWS-36 and AWS-43.   }
+sreerekha et al 	 &  -0.09 &  0.91 &              -0.10 &               45.36 \\
+		\hline
+	\end{tabular}
+	\caption{Same as Table~\ref{tab:correction:stats:34:42:thinned}, but for channel combinations: AWS-36 and AWS-43.   }
 	\label{tab:correction:stats:36:43}

### 2020-05-28 Report/aws_325ghz_study.tex
Work on the report. Extended the discussion section.

@@
 %
-The nominal reciever noise temperature, $T_r$ of each band is listed in
+The nominal receiver noise temperature, $T_r$ of each band is listed in
 Table~\ref{tab:trec}. The noise of data for individual channels is calculated
@@
 where $\sigma^i$ is the noise standard deviation of channel $i$, $c$ is a
-scaling factor (see below), $T^i_r$ is the reciever noise temperature of the
+scaling factor (see below), $T^i_r$ is the receiver noise temperature of the
 channel, $T^i_a$ is the antenna temperature of the channel, $\Delta\!f^i$ is
@@
 The factor $c$ is set to 1.2 to incorporate the additional noise caused by the
-calibration process. The bandwith applied is the one found in columns 3 of
+calibration process. The bandwidth applied is the one found in columns 3 of
 Table~\ref{tab:fixed:chs}. The integration time is set to match an effective
@@
   \end{tabular}
-  \caption{Assumed reciever noise temperatures. The value for 229\,GHz is
+  \caption{Assumed receiver noise temperatures. The value for 229\,GHz is
     selected by us, remaining values are present assumptions at Omnisys.}
@@
 The polarisation response of the bands is not yet determined and for simplicity
-``quasi-horisontal'' (defined in same way as for e.g.\ MWS) is throughout
+``quasi-horizontal'' (defined in same way as for e.g.\ MWS) is throughout
 assumed. Antenna temperatures are obtained as:
@@
 \end{equation}
-where $T_b^V$/$T_b^H$ is the brightness temprature at vertical/horisontal
+where $T_b^V$/$T_b^H$ is the brightness temperature at vertical/horizontal
 polarisation, respectively, and $\theta$ is the viewing angle (from nadir).
@@
 possible. No external CloudSat retrievals are involved. Instead the CloudSat
-reflectivites are mapped to properties for the passive simulations by assuming
+reflectivities are mapped to properties for the passive simulations by assuming
 a particle size distribution and a particle habit, together denoted as
@@
 transitions are replaced \citep{saunders2018update,turner2019amsutran}. A
-smaller comparison to RTTOV has been made, that indciated an agreement better
+smaller comparison to RTTOV has been made, that indicated an agreement better
 than 0.1\,K in general. Deviations between 0.1 and 0.2\,K were found for some
@@
 
-In the intermediate region, the simulations have a lower occurance rate. The
+In the intermediate region, the simulations have a lower occurrence rate. The
 impact of hydrometeors should be somewhat higher in the upper sideband of ATMS,
@@
 \section{Overview of the 183, 229 and 325\,GHz bands}
+\label{sec:overview}
 % 
@@
 scenarios. The same is true for 325\,GHz, but the influence of the surface
-reflectivity is considerably lower. [* Comment somewhere on the implications of
-this for retrievals at high latitudes *] Beside for the tropical case, for
+reflectivity is considerably lower.  Beside for the tropical case, for
 229\,GHz there is a pronounced dependency of the surface reflectivity, e.g.\
@@
 channel the the shift would be 300\,m. Accordingly, there is little gain by
-inforcing the IF range to go above 8\,GHz. As a rule of thumb, a higher ratio
+enforcing the IF range to go above 8\,GHz. As a rule of thumb, a higher ratio
 between highest and lowest IF is more costly to implement. Albeit small, a
 negative consequence of a 8\,-\,11\,GHz channel, compared to 5\,-\,8\,GHz, is
-some assymetry in the altitude response between lower and upper sideband. This
-assymetry is caused by higher continuum and far wing absorption on the upper
+some asymmetry in the altitude response between lower and upper sideband. This
+asymmetry is caused by higher continuum and far wing absorption on the upper
 side.
@@
   \caption{RH weighting functions of the three channel option in
-    Table~\ref{tab:chs:prel}, for the Fascod tropical (left) and mid-latiude
+    Table~\ref{tab:chs:prel}, for the Fascod tropical (left) and mid-latitude
     winter (right) scenarios.}
@@
   \caption{RH weighting functions of the four channel option in
-    Table~\ref{tab:chs:prel}, for the Fascod tropical (left) and mid-latiude
+    Table~\ref{tab:chs:prel}, for the Fascod tropical (left) and mid-latitude
     winter (right) scenarios.}
@@
 \section{Cloud correction by a simple scheme}
+\label{sec:simple}
 %
@@
 %
-Let C1 and C2 represent the one of the channels each from 183\,GHz and 325\,GHz
+Let C1 and C2 represent one of the channels each from 183\,GHz and 325\,GHz,
 respectively, and Tb1 and Tb2 represent the corresponding TB. The correction
@@
 combinations are possible, for example one such paired combination is AWS-34
-and AWS-42. For each of the five 183\,GHz channels, the correction scheme is
-derived from its corresponding counterpart in 325\,GHz channel.
+and AWS-42.
 
@@
 	\caption{Brightness temperature difference of AWS-34 from AWS-42 plotted
-      against cloud impact in AWS-34. The black curve represents the line of
-      best fit (of green points) as a third order polynomial. Red and green
-      color represent the clear and cloudy cases respectively in the simulation
-      dataset. The blue vertical line represents correction threshold, $x_{cs}$, for $dtb_{cs} =$
-      0.2\,K. }
+      against cloud impact in AWS-34. Red and green colour represent the clear
+      and cloudy cases respectively in the simulation dataset. The black curve
+      represents the line of best fit (of green points) as a third order
+      polynomial. The blue vertical line represents the correction threshold,
+      $x_{cs}$, for $dtb_{cs} =$ 0.2\,K. }
 	\label{fig:fit:c34-42}
@@
 are used. The two variables have a reasonably strong correlation for small TB
-differences, but as the impact of cloud increases, the correlations gets poorer.
-The data can be fitted by linear or non-linear models. The fitted model can be
-used to obtain the adjustment required to compensate the brightness
+differences, but as the impact of cloud increases, the correlations gets
+poorer. The data can be fitted by linear or non-linear models. The fitted model
+can be used to obtain the adjustment required to compensate the brightness
 temperature for cloudy cases. To avoid fitting the ``too cloudy'' cases which
 do not show any reasonable correlation, cases with $Tb2-Tb1< -40$\,K are
-excluded in the fit. Also, cases with $Tb2-Tb1 < 0.2$\,K (red color dots) are
-assumed to be clear-sky, are not included in the model.
-
-It is also important to have a manner for making a clear/cloudy classification.
-This is useful for making filtering in line with \citet{rekha2012potential},
-but is also needed in the correction scheme. The latter is the case as the
-polynomial fit derived gives a non-zero correction for clear-sky cases. In
-Fig.~\ref{fig:fit:c34-42} the difference between clear-sky values of channel C1
-and C2 (red dots) have a mean close to zero (as the weighting functions are
-well matched), but this is not the case for all channel combinations and some
-general rule for finding a threshold value (with respect to $x_m$) must be
-formulated. The polynomial fit will be used also for this part.
+excluded in the fit. Also, cases with a cloud impact below 0.2\,K (red colour
+dots) can be considered as clear-sky, are not included in the model.
+
+It is also important to have a manner for making a clear/cloudy classification
+that can be derived from actual measurement data. This is useful for making
+filtering in line with \citet{rekha2012potential}, but is also needed in the
+correction scheme. The latter is the case as the polynomial fit derived gives a
+non-zero correction for clear-sky cases. In Fig.~\ref{fig:fit:c34-42} the
+difference between clear-sky values of channel C1 and C2 (red dots) have a mean
+close to zero (as the weighting functions are well matched), but this is not
+the case for all channel combinations and some general rule for finding a
+threshold value (with respect to $x_m$) must be formulated. The polynomial fit
+will be used also for this part.
 
@@
 %
-\begin{figure}[!p]
-	\centering
-	\includegraphics[clip,trim=0 0 0 0,height=80mm]{PDF_corrected_AWS-34_AWS-42_allfits}
-	\caption{Deviation of AWS-34 measurements to noise free clear-sky
-      simulations before and after correction, corrected using a linear,
-      quadratic and cubic model. The spread of noise is also shown as
-      reference. The measurements have been corrected using brightness
-      temperatures from AWS-42.
-The average bias values are given in parenthesis in the legend.
-No clear/cloudy classification based on the fit is applied, but cases with $Tb2 - Tb1 > -15$\,K are rejected.}
-	\label{fig:correction:c34-42:fit}
-\end{figure}
-%
-\begin{figure}[!p]
-	\centering
-	\includegraphics[height=80mm]{PDF_corrected_AWS-34_AWS-42_all}
-	\caption{Deviation of AWS-34 measurements to noise free clear-sky simulations before and after correction.
-The measurements have been corrected using a cubic model.
-The different datasets are: noise (simulation dataset), uncorrected-all (measurement dataset without clear/cloudy classification), filtered $1\sigma$ (cloudy measurements are filtered with $dtb_{cs}$ = 1$\sigma$), corrected $1\sigma$ (cloudy measurements are corrected with $dtb_{cs}$ = 1$\sigma$), corrected $2\sigma$ (cloudy measurements are corrected with $dtb_{cs}$ = 2$\sigma$), Sreerekha (measurements are filtered according to criteria described in \cite{rekha2012potential}).
-      \cite{rekha2012potential}.}
-	\label{fig:correction:c34-42}
-\end{figure}
-%
-
-\begin{table}[!bt]
-	\centering
-	\begin{tabular}[b]{c|c|c|c|c}
-		Dataset  		  &   bias &   std &   measure  & fraction  \\
-							&   [K]  &   [K] & skewness[K] & rejected [\%]\\
-		\hline
-		noise             		&   0.00 &  0.63 &               0.00 &                - \\
-		uncorrected-all       	&  -0.19 &  0.87 &              -2.42 &                - \\
-		filtered($1\sigma$ ) 	&  -0.10 &  0.66 &              -0.15 &               10.56 \\
-		corrected($1\sigma$) 	&  -0.05 &  0.72 &              -0.23 &                2.84 \\
-		corrected($2\sigma$) 	&  -0.09 &  0.70 &              -0.49 &                2.84 \\
-		sreerekha et al   		&  -0.14 &  0.73 &              -0.76 &               43.60 \\
-		\hline
-	\end{tabular}
-	\caption{Bias, standard deviation(std), and measure of skewness of deviations of the measurements to noise-free clear-sky cases.
-The fraction rejected describes the percentage of cases which are removed.
-The different datasets are: noise (simulation dataset), uncorrected-all (measurement dataset without clear/cloudy classification), filtered $1\sigma$ (cloudy measurements are filtered with $dtb_{cs}$ = 1$\sigma$), corrected $1\sigma$ (cloudy measurements are corrected with $dtb_{cs}$ = 1$\sigma$), corrected $2\sigma$ (cloudy measurements are corrected with $dtb_{cs}$ = 2$\sigma$), Sreerekha (measurements are filtered according to criteria described in \cite{rekha2012potential}).
-}
-	\label{tab:correction:stats:34:42}
-\end{table}
-%
-\begin{table}[!bt]
-	\centering
-	\begin{tabular}[b]{c|c|c|c|c}
-		Dataset  		  &   bias &   std &   measure  & fraction  \\
-		&   [K]  &   [K] & skewness[K] & rejected [\%]\\
-		\hline
-	noise             		&   0.00 &  0.63 &              -0.01 &                - \\
-	uncorrected       		&  -0.29 &  1.00 &              -2.62 &                - \\
-	filtered($1\sigma$)  	&  -0.13 &  0.68 &              -0.25 &               17.54 \\
-	corrected($1\sigma$) 	&  -0.06 &  0.76 &              -0.46 &                4.99 \\
-	corrected($2\sigma$) 	&  -0.11 &  0.75 &              -0.69 &                4.99 \\
-	sreerekha et al   		&  -0.20 &  0.78 &              -1.00 &               45.36 \\	
-		\hline
-\end{tabular}
-\caption{Same as Table~\ref{tab:correction:stats:34:42}, but for thinned dataset. 50\% of the clear cases are removed to improve the representation of cloudy cases }
-\label{tab:correction:stats:34:42:thinned}
-\end{table}
-%
 In this section, we test the applicability of the correction scheme in detail.
-To analyse the performance of the approach, we apply it to correct the measurements from C1 using data from C2.
-Without the availability of actual data, the simulation dataset but with noise is used mimic the measurements.
-The noise for individual channels is calculated according to Equation~\ref{eq:noise}.
-As an example, the results from the channel combination AWS-34 and AWS-42 are shown.
+To analyse the performance of the approach, we apply it to correct the
+measurements from C1 using data from C2. Without the availability of actual
+data, the simulation dataset but with noise added is used mimic the measurements. The
+noise for individual channels is calculated according to
+Equation~\ref{eq:noise}. As an example, the results from the channel
+combination AWS-34 and AWS-42 are shown.
 
@@
 The occurrence frequency of the deviations from three models is shown in
-Fig.~\ref{fig:correction:c34-42:fit}. The occurence frequency of the measurement
-without any filtering or correction is also plotted as reference (orange
-color). If all measurements are devoid of any cloud impact, the deviations
-should follow the gaussian distribution of noise. However, in real scenarios,
-the distribution is skewed due to the impact of clouds. Among the three models, the quadratic and cubic models work
-better than the linear model. Both quadratic and cubic models are able to
-correct the cloud impact in the measurements, however the values of average
-bias indicates that the cubic model performs better. The average deviation in
-the dataset is -0.75\,K and after correction with a cubic model, it reduces to
--0.05\,K, while for quadratic model, the average bias after correction is
-0.22\,K. For all other results described further, a cubic model is
-used. It should also be noted
-that since no clear/cloudy classification is included, the peak of the distributions (representing the clear-sky cases) is reduced in the corrected datasets. 
-To avoid correcting the clear cases, implementation of clear/cloudy classification is extremely important.
+Fig.~\ref{fig:correction:c34-42:fit}. The occurrence frequency of the
+measurements without any filtering or correction is also plotted as reference
+(orange colour). If all measurements are devoid of any cloud impact, the
+deviations should follow the Gaussian distribution of noise. However, in real
+scenarios, the distribution is skewed due to the impact of clouds. Among the
+three models, the quadratic and cubic models work better than the linear model.
+Both quadratic and cubic models are able to correct the cloud impact in the
+measurements, however the values of average bias indicates that the cubic model
+performs better. The average deviation in the dataset is -0.75\,K and after
+correction with a cubic model, it reduces to -0.05\,K, while for quadratic
+model, the average bias after correction is 0.22\,K. For all other results
+described further, a cubic model is used. It should also be noted that since no
+clear/cloudy classification is included, the peak of the distributions
+(representing the clear-sky cases) is reduced in the corrected datasets. To
+avoid correcting the clear cases, implementation of clear/cloudy classification
+is extremely important. [* I still don't get the last part. Do you mean that you
+apply the correction on all data? *]
 
@@
 dataset,``Filtered'', where all cloudy cases are rejected. Apart from the fit
-based cloudy classfication, it is also assumed that cases with $Tb2-Tb1 < $
+based cloudy classification, it is also assumed that cases with $Tb2-Tb1 < $
 -15\,K are ``too-cloudy'', and are rejected. Various metrics corresponding to
 the Figure~\ref{fig:correction:c34-42} are shown in
-Table~\ref{tab:correction:stats:34:42}.
-
-The distribution of the deviations in the pure-filtered data is non-Gaussian. The
-right side of the distribution follows measurement noise while the left
-side is skewed. The skewness in the distribution is due to cloud impacts which
-pass through the clear-sky threshold.
-A larger skewness in the dataset ``Sreerekha et al'' in comparsion to ``Filtered'' shows that the frequency of misclassfied cases is higher in the approach by \cite{rekha2012potential}.
-The regression approach described here does not provide any way to correct the misclassfied cases, but the frequency of such cases can be controlled through $dtb_{cs}$.
-After correction, the average deviation to the clear-sky noise-free values in the corrected measurements should be closer to zero than uncorrected.
-With a fit based cloudy classification, 10.56\% of the cases are classified as cloudy when $dtb_{cs}$
-= 1$\sigma$.  Before correction, the average bias for measurements is -0.19\,K
-but after correction it reduces to -0.05\,K and -0.09\,K for the two values of
-the $dtb_{cs}$ respectively.
+Table~\ref{tab:correction:stats:34:42}. [* Why are the yellow lines so
+different in Figs.~10 and 11? Maybe we discussed it, but I have then forgot. *]
+
+\begin{figure}[!p]
+	\centering
+	\includegraphics[height=85mm]{PDF_corrected_AWS-34_AWS-42_allfits}
+	\caption{Deviation of AWS-34 measurements to noise free clear-sky
+      simulations before and after correction, corrected using a linear,
+      quadratic and cubic model. The distribution of noise alone is also shown
+      as reference. The measurements have been corrected using brightness
+      temperatures from AWS-42. The mean value of each distribution is given in
+      parenthesis in the legend. Cases with $Tb2 - Tb1 > -15$\,K are rejected.}
+	\label{fig:correction:c34-42:fit}
+\end{figure}
+%
+\begin{figure}[!p]
+	\centering
+	\includegraphics[height=85mm]{PDF_corrected_AWS-34_AWS-42_all}
+	\caption{Deviation of AWS-34 measurements to noise free clear-sky
+      simulations before and after correction. The measurements have been
+      corrected using a cubic model. The different datasets are: noise
+      (simulation dataset), uncorrected-all (measurement dataset without
+      clear/cloudy classification), filtered $1\sigma$ (cloudy measurements are
+      filtered with $dtb_{cs}$ = 1$\sigma$), corrected $1\sigma$ (cloudy
+      measurements are corrected with $dtb_{cs}$ = 1$\sigma$), corrected
+      $2\sigma$ (cloudy measurements are corrected with $dtb_{cs}$ =
+      2$\sigma$), Sreerekha (measurements are filtered according to criteria
+      described in \citet{rekha2012potential}).}
+	\label{fig:correction:c34-42}
+\end{figure}
+%
+
+\begin{table}[!bt]
+	\centering
+	\begin{tabular}[b]{c|c|c|c|c}
+		Dataset  		  &   bias &   std &   skewness  & fraction  \\
+							&   [K]  &   [K] & [K] & rejected [\%]\\
+		\hline
+		noise             		&   0.00 &  0.63 &               0.00 &                - \\
+		uncorrected-all       	&  -0.19 &  0.87 &              -2.42 &                - \\
+		filtered($1\sigma$ ) 	&  -0.10 &  0.66 &              -0.15 &               10.56 \\
+		corrected($1\sigma$) 	&  -0.05 &  0.72 &              -0.23 &                2.84 \\
+		corrected($2\sigma$) 	&  -0.09 &  0.70 &              -0.49 &                2.84 \\
+		sreerekha et al   		&  -0.14 &  0.73 &              -0.76 &               43.60 \\
+		\hline
+	\end{tabular}
+	\caption{Bias, standard deviation (std), and measure of skewness of
+      deviations of the measurements to noise-free clear-sky cases. The
+      fraction rejected describes the percentage of cases which are removed.
+      The different datasets are: noise (simulation dataset), uncorrected-all
+      (measurement dataset without clear/cloudy classification), filtered
+      $1\sigma$ (cloudy measurements are filtered with $dtb_{cs}$ = 1$\sigma$),
+      corrected $1\sigma$ (cloudy measurements are corrected with $dtb_{cs}$ =
+      1$\sigma$), corrected $2\sigma$ (cloudy measurements are corrected with
+      $dtb_{cs}$ = 2$\sigma$), Sreerekha (measurements are filtered according
+      to criteria described in \cite{rekha2012potential}). }
+	\label{tab:correction:stats:34:42}
+\end{table}
+%
+\begin{table}[!bt]
+	\centering
+	\begin{tabular}[b]{c|c|c|c|c}
+		Dataset  		  &   bias &   std &   skewness  & fraction  \\
+		&   [K]  &   [K] & [K] & rejected [\%]\\
+		\hline
+	noise             		&   0.00 &  0.63 &              -0.01 &                - \\
+	uncorrected       		&  -0.29 &  1.00 &              -2.62 &                - \\
+	filtered($1\sigma$)  	&  -0.13 &  0.68 &              -0.25 &               17.54 \\
+	corrected($1\sigma$) 	&  -0.06 &  0.76 &              -0.46 &                4.99 \\
+	corrected($2\sigma$) 	&  -0.11 &  0.75 &              -0.69 &                4.99 \\
+	sreerekha et al   		&  -0.20 &  0.78 &              -1.00 &               45.36 \\	
+		\hline
+\end{tabular}
+\caption{Same as Table~\ref{tab:correction:stats:34:42}, but for thinned dataset. 50\% of the clear cases are removed to improve the representation of cloudy cases }
+\label{tab:correction:stats:34:42:thinned}
+\end{table}
+
+The distributions of filtered data are non-Gaussian. The right side of the
+distribution follows measurement noise while the left side is skewed. The
+skewness in the distribution is due to cloud impacts which pass through the
+clear-sky threshold. The higher skewness in ``Sreerekha et al'' is mainly
+caused by that their method only aims at removing cloud impacts above 4\,K.
+Their approach also leads to a high rejection fraction (43.6\%). The filtering
+method introduced here leads to a considerable lower rejection of data
+(10.6\%).
+
+[* The unit for skewness is said to K. Is that correct? In any case I suggest
+to add an equation/description of skewness *]
+
+If the correction part is added, the rejection is decreased even further (28\%)
+and the bias is also improved (from -0.10 to -0.05\,K). On the other hand, the
+correction gives some increase in standard deviation and skewness, compared to
+filtering alone. A correction using $2\sigma$ as threshold between clear/cloudy
+gives poorer performance, in particular the skewness is increased.
 
@@
 (Fig.\ref{fig:pdf:c16-22}) showed that the cloudy cases in the simulations were
-underrepresented in comparison to the observations. In order to have a better
-representation of the cloudy cases, we thin the measurement dataset by
-removing 50\% of the clear-sky cases. The results from this smaller dataset, before and after filtering/correction are shown in Table~\ref{tab:correction:stats:34:42:thinned}. In comparison to the
-original dataset, the statistics in the thinned dataset is slightly worse, as
-expected. But overall the performance of the correction scheme is comparable. 
-For all further analysis presented in this report, the thinned dataset is used.
+underrepresented in comparison to the observations. In order to have a higher
+representation of cloudy cases, we thinned the measurement dataset by removing
+50\% of the clear-sky cases. The results from this smaller dataset, before and
+after filtering/correction are shown in
+Table~\ref{tab:correction:stats:34:42:thinned}. In comparison to the original
+dataset, the statistics in the thinned dataset is slightly worse, as expected.
+But overall the performance of the correction scheme is comparable. For all
+further analysis presented in this report, the thinned dataset is used.
 %
@@
 	\includegraphics[height=85mm]{PDF_corrected_AWS-32_AWS-4X_thinned}
-	\caption{Same as Fig.~\ref{fig:correction:c34-42}, but for channel combinations: AWS-32 and AWS-4X.}
+	\caption{Same as Fig.~\ref{fig:correction:c34-42}, but for channel combinations AWS-32 and AWS-4X.}
 	\label{fig:correction:c32-4X:thinned}
@@
 corresponding metrics are provided in Table~\ref{tab:correction:stats:32:4X}.
-With clear/cloudy classification for $dtb_{cs} = 1\sigma$, around 85\% of the total measurements are classified as cloudy and are rejected in pure-filtering.
-Rejecting all the cloudy cases reduces the average bias in the measurements from -0.62\,K to -0.21\,K,  while with the approach from \citet{rekha2012potential} only 45\% of the data is rejected and the average bias reduces to  -0.41\,K.
-When all the cloudy cases, except the ``too cloudy'', are corrected, the total bias increases to 0.88\,K.
-The unusually high fraction of cloudy cases and an increase in bias on correction suggests misclassfication of clear cases as cloudy.
-Since, the weighting functions of AWS-32 and AWS-4X are poorly matched, their relationship is inadequate to estimate the cloud impact in AWS-32.
-Without any additional information, the regression approach can only provide a successful filtering in comparison to the original approach described by \citet{rekha2012potential},  although at the cost of high rejection fraction.
-Additional information e.g., TB from other channels, is necessary improve the accuracy of cloudy correction.
-
-%
+With clear/cloudy classification for $dtb_{cs} = 1\sigma$, around 85\% of the
+total measurements are classified as cloudy and are rejected in pure-filtering.
+Rejecting all the cloudy cases reduces the average bias in the measurements
+from -0.62\,K to -0.21\,K, while with the approach from
+\citet{rekha2012potential} only 45\% of the data is rejected and the average
+bias reduces to -0.41\,K. When all the cloudy cases, except the ``too cloudy'',
+are corrected, the total bias increases to 0.88\,K. The unusually high fraction
+of cloudy cases and an increase in bias on correction suggests misclassification
+of clear cases as cloudy. Since, the weighting functions of AWS-32 and AWS-4X
+are poorly matched, their relationship is inadequate to estimate the cloud
+impact in AWS-32. Without any additional information, the regression approach
+can only provide a successful filtering in comparison to the original approach
+described by \citet{rekha2012potential}, although at the cost of high rejection
+fraction. Additional information e.g., TB from other channels, is necessary
+improve the accuracy of the correction.
+
 \begin{table}[!h]
@@
 	\begin{tabular}[b]{c|c|c|c|c}
-		Dataset  		  &   bias &   std &   measure & fraction \\
-						&   [K]  &   [K] & skewness[K] 		& rejected [\%]\\
+		Dataset  		  &   bias &   std & skewness & fraction \\
+						&   [K]  &   [K] & [K] 		& rejected [\%]\\
 		\hline
@@
 The correction scheme can also be extended to other combinations of 183GHz and
-325GHz. The most relevant combinations for clear-sky screening are: AWS-32 and
+325GHz channels. The most relevant combinations for clear-sky screening are: AWS-32 and
 AWS-41; AWS-33 and AWS-41; AWS-35 and AWS-43; AWS-36 and AWS-43.
+
+[* The values for uncorrected differ between Table 6 and 7? Can't be correct. *]
 
@@
 statistics. This is not surprising as the weighting function match between
-AWS-32 and  AWS-41 is poor. 
+AWS-32 and AWS-41 is poor. The correction using $2\sigma$ as threshold works
+better $1\sigma$. This is an exception, the reversed is valid for AWS-34/42 (as
+mentioned) and the channel combinations discussed below.
+
 Table~\ref{tab:correction:stats:33:41} shows the statistics when AWS-33 is
@@
 average bias in the measurements from -0.33\,K to -0.13\,K, while a correction
-of cloudy cases reduces the bias further to 0.05\,K.
-A similar performance is seen for the combination AWS-35 and AWS-43, and Table~\ref{tab:correction:stats:35:43} shows the statistics from this combination.
-After correction the bias due to cloudy measurements reduces -0.33\,K to -0.05\,K while rejecting only 6.88\% of the total cases.
-
-Table~\ref{tab:correction:stats:36:43} shows the statistics when AWS-36 is corrected using AWS-43.
-For this combination, the weighting functions have a poor match, but the TB differences and the cloud impact are strongly correlated, as the cloud impact in AWS-36 is relatively low in comparison to other 183\,GHz channels.
-The low fraction of rejection (7.38\%) also shows that most of the measurements are without cloud impact.
-However, the small fraction of cloudy cases which are corrected helps in successfully reducing the average bias from -0.16\,K to 0.07\,K.
-
-\begin{table}[!bt]
+of cloudy cases reduces the bias further to 0.05\,K. A similar performance is
+seen for the combination AWS-35 and AWS-43, and
+Table~\ref{tab:correction:stats:35:43} shows the statistics from this
+combination. After correction the bias due to cloudy measurements reduces
+-0.33\,K to -0.05\,K while rejecting only 6.88\% of the total cases.
+
+Table~\ref{tab:correction:stats:36:43} shows the statistics when AWS-36 is
+corrected using AWS-43. For this combination, the weighting functions have a
+poor match, but the TB differences and the cloud impact are strongly
+correlated, as the cloud impact in AWS-36 is relatively low in comparison to
+other 183\,GHz channels. The low fraction of rejection (7.38\%) also shows that
+most of the measurements are without cloud impact. However, the small fraction
+of cloudy cases which are corrected helps in successfully reducing the average
+bias from -0.16\,K to 0.07\,K.
+
+\begin{table}[!p]
 	\centering
 	\begin{tabular}[b]{c|c|c|c|c}
-		Dataset  		  &   bias &   std &   measure & fraction \\
-							&   [K]  &   [K] & skewness[K] & rejected [\%]\\
+		Dataset  		  &   bias &   std & skewness & fraction \\
+							&   [K]  &   [K] & [K] & rejected [\%]\\
 		\hline
@@
 	\end{tabular}
-	\caption{Same as Table~\ref{tab:correction:stats:34:42:thinned}, but for channel combinations: AWS-32 and AWS-41.   }
+	\caption{Same as Table~\ref{tab:correction:stats:34:42:thinned}, but for channel combination: AWS-32 and AWS-41.   }
 	\label{tab:correction:stats:32:41}
@@
 
-\begin{table}[!bt]
+\begin{table}[!p]
 	\centering
 	\begin{tabular}[b]{c|c|c|c|c}
-		Dataset  		  &   bias &   std &   measure  & fraction\\
-						&   [K]  &   [K] & skewness[K]  & rejected [\%]\\
+		Dataset  		  &   bias &   std &  skewness  & fraction\\
+						&   [K]  &   [K] & [K]  & rejected [\%]\\
 		\hline
@@
 	\end{tabular}
-	\caption{Same as Table~\ref{tab:correction:stats:34:42:thinned}, but for channel combinations: AWS-33 and AWS-41.   }
+	\caption{Same as Table~\ref{tab:correction:stats:34:42:thinned}, but for channel combination: AWS-33 and AWS-41.   }
 	\label{tab:correction:stats:33:41}
@@
 
-\begin{table}[!bt]
+\begin{table}[!p]
 	\centering
 	\begin{tabular}[b]{c|c|c|c|c}
-		Dataset  		  &   bias &   std &   measure & fraction \\
-							&   [K]  &   [K] & skewness[K] & rejected [\%]\\
+		Dataset  		  &   bias &   std &   skewness & fraction \\
+							&   [K]  &   [K] & [K] & rejected [\%]\\
 		\hline
@@
 	\end{tabular}
-	\caption{Same as Table~\ref{tab:correction:stats:34:42:thinned}, but for channel combinations: AWS-35 and AWS-43.   }
+	\caption{Same as Table~\ref{tab:correction:stats:34:42:thinned}, but for channel combination: AWS-35 and AWS-43.   }
 	\label{tab:correction:stats:35:43}
@@
 
-\begin{table}[!bt]
+\begin{table}[!p]
 	\centering
 	\begin{tabular}[b]{c|c|c|c|c}
-		Dataset  		  &   bias &   std &   measure & fraction  \\
-							&   [K]  &   [K] & skewness[K] & rejected [\%]\\
+		Dataset  		  &   bias &   std &   skewness & fraction  \\
+							&   [K]  &   [K] & [K] & rejected [\%]\\
 		\hline
@@
 	\end{tabular}
-	\caption{Same as Table~\ref{tab:correction:stats:34:42:thinned}, but for channel combinations: AWS-36 and AWS-43.   }
+	\caption{Same as Table~\ref{tab:correction:stats:34:42:thinned}, but for channel combination: AWS-36 and AWS-43.   }
 	\label{tab:correction:stats:36:43}
@@
 
-(Just a start, to not forget these points)
-
-\subsection{Shape of channel response functions}
-%
-The simulations have assumed rectangularly shaped response functions, for
-simplicity. We have left some frequency gaps between the channels to simplify
-the technical implementation, i.e.\ to decrease the demand on very sharp
-ransitions from high to low response. We have assumed that 100\,MHz is
-sufficient in the lower end of the IF-range and 200\,MHz in the upper part. If
-found necessary we don't see any problem in increasing the gaps, beside that
-the bandwidth decreases and the NE$\Delta$T of the channel will somewhat
-increase.
-
-\subsection{Polarisation response}
+\subsection{229 vs.\ 325\,GHz}
+
+\subsubsection{Altitude coverage}
+%
+This discussion is based on figures and text found in Sec.~\ref{sec:overview}.
+A basic remark is that a channel at 229\,GHz channel has a lower sounding
+altitude than all the 183\GHz channels for clear-sky conditions. Accordingly,
+there are no matching RH weighting functions between 229\,GHz and 183\,GHz
+channels. On the other hand, channels around 325\,GHz have quite similar
+characteristics as some of the 183\,GHz channels (for clear-sky), but
+consistently have a sounding altitude above the one of AWS-32.
+
+With respect to sensitivity to hydrometeors, 229\,GHz will react on rain and
+clouds at lower altitudes than the 183\,GHz channels. Due to the lower sounding
+altitude, 229\,GHz is also more influenced by the surface. Both these aspects
+could be beneficial in a wider perspective, but are not ideal for cloud
+filtering of 183\,GHz data. With respect to this application, the main drawback
+of the 325\,GHz region is the lack of a full coverage for AWS-32. There exists
+an altitude range where hydrometeors have an impact on AWS-32 but will largely
+be undetected by the 325\,GHz channels.
+
+\subsubsection{Performance of the basic scheme}
+%
+A simple approach for cloud filtering/correction based on 325\,GHz data is
+tested in Sec.~\ref{sec:simple}. The approach requires simulations for deriving
+some parameters (in the form of a polynomial fit), while the application only
+involves measurement data. Another advantage of the approach is that it is
+channel specific. That is, it could result in that e.g.\ AWS-32 and 33 are
+rejected, while that data for the higher peaking channels still can be used.
+
+The results for AWS-33, 34, 35 and 36 should be considered as satisfactorily.
+In short, a relatively low rejection rate is achieved and still data with
+relatively narrow and symmetric error distributions are provided. The lowest
+standard deviation and skewness are obtained by just performing a filtering.
+Activating the correction part (with $1\sigma$ as threshold value) decreases
+the bias and rejection rates significantly, but comes with the cost of
+increased standard deviation and skewness. However, the increase in standard
+deviation is throughout below 50\% (compared to the ideal case of that the
+error distribution only consists of noise).
+
+[* Finish when Tables 6 and 7 have been checked/corrected. *]
+
+\subsubsection{Comparison to \citet{rekha2012potential}}
+%
+Results from \citet{rekha2012potential} has been used as reference, but the
+comparison should only be considered as being qualitative. A more detailed
+comparison is not possible as the selection of atmospheric cases is very
+different between the studies. While in this study we aim to have a statistical
+distribution as close as possible to real conditions, there is a strong focus on
+cloudy conditions in the simulations used by \citet{rekha2012potential}. Our
+translation of the performance reported in \citet{rekha2012potential} to our
+conditions is found in Sec.~\ref{sec:rekha}.
+
+The results of \citet{rekha2012potential} is better than ours for AWS-32 [*
+check when tables been updated *], while for the other 183\,GHz channels better
+results are obtained by using 325\,GHz data. The main difference for these
+later channels is the high rejection rate for \citet{rekha2012potential}.
+
+It should be noted that the approach of \citet{rekha2012potential} involves
+simulations for every case, to obtain a ``background minus observation''
+difference, while in this study a similar or better performance is obtained
+from using measurement data alone.
+
+\subsection{Technical implementation}
+
+\subsubsection{Shape of channel response functions}
+%
+The simulations have assumed rectangularly shaped response functions. This was
+done for simplicity and shall in no way be taken as an indication on that this
+shape is required.
+
+We have left some frequency gaps between the channels to simplify the technical
+implementation, i.e.\ to decrease the demand on very sharp transitions from high
+to low response. We have assumed that 100\,MHz is sufficient in the lower end
+of the IF-range and 200\,MHz in the upper part. If found necessary we don't see
+any problem in increasing the gaps, beside that the bandwidth decreases and the
+NE$\Delta$T of the channel will somewhat increase.
+
+\subsubsection{Polarisation response}
 %
@@
 The basic recommendation would be to use the same polarisation response as far
-as possible. If both quasi-horisontal and quasi-vertical bands must be applied,
-the recommedation prioritize to use the polarisation option for 183 and
+as possible. If both quasi-horizontal and quasi-vertical bands must be applied,
+the recommendation prioritise to use the polarisation option for 183 and
 325\,GHz, to maintain a similar influence of polarisation between the bands.
@@
 This study compares the options of having a channel at 229\,GHz or having some
-around 325\,GHz from a single perspective, cloud filtering(corection of
+around 325\,GHz from a single perspective, cloud filtering/correction of
 183\,GHz data. There could be other important reasons to consider for the

### 2020-05-29 Report/aws_325ghz_study.tex
new updates in Sec6 and 8

@@
 noise (Eq.~\ref{eq:noise}, often called NE$\Delta$T).
+We will use $1\sigma$ for the development of the scheme, however, the sensitivity of the scheme to 1$\sigma$ and 2$\sigma$  threshold is also provided later in the text.
 
@@
 Equation~\ref{eq:noise}. As an example, the results from the channel
-combination AWS-34 and AWS-42 are shown.
+combination AWS-34 and AWS-42 are shown. The error in the
+predicted measurements is assessed as the deviation to corresponding noise-free
+clear-sky value.
+The average bias, standard deviation and the measure of skewness, of the deviations are also calculated.
+Skewness gives a measure of asymmetry of the probability distribution of deviations around its mean.
 
@@
 For all three models, cases with $Tb2-Tb1 < $ -15\,K are assumed to be ``too
-cloudy'' and are not corrected. The clear-sky adjustment for all eligible
-measurements (without clear/cloudy classification) is calculated from all three
-models, and the three predicted datasets are compared. The error in the
-predicted measurements is assessed as the deviation to corresponding noise-free
-clear-sky value.
+cloudy'' and are not corrected. Also, cases classified as clear according to $1\sigma$ threshold are not corrected. The clear-sky adjustment for all eligible
+measurements is calculated from all three
+models, and the three predicted datasets are compared.
 
 The occurrence frequency of the deviations from three models is shown in
-Fig.~\ref{fig:correction:c34-42:fit}. The occurrence frequency of the
+Fig.~\ref{fig:correction:c34-42:fit} and their corresponding statistics are shown in Table~\ref{tab:correction:stats:34:42:allfits}. The occurrence frequency of the
 measurements without any filtering or correction is also plotted as reference
-(orange colour). If all measurements are devoid of any cloud impact, the
-deviations should follow the Gaussian distribution of noise. However, in real
-scenarios, the distribution is skewed due to the impact of clouds. Among the
-three models, the quadratic and cubic models work better than the linear model.
-Both quadratic and cubic models are able to correct the cloud impact in the
-measurements, however the values of average bias indicates that the cubic model
-performs better. The average deviation in the dataset is -0.75\,K and after
-correction with a cubic model, it reduces to -0.05\,K, while for quadratic
-model, the average bias after correction is 0.22\,K. For all other results
-described further, a cubic model is used. It should also be noted that since no
-clear/cloudy classification is included, the peak of the distributions
-(representing the clear-sky cases) is reduced in the corrected datasets. To
-avoid correcting the clear cases, implementation of clear/cloudy classification
-is extremely important. [* I still don't get the last part. Do you mean that you
-apply the correction on all data? *]
-
-To implement the clear/cloudy classification as discussed in the previous
-section, two different values of $dtb_{cs}$ are tested: $1\sigma$ and
-$2\sigma$. For both values of $dtb_{cs}$ the corresponding clear-sky cut-off
-($x_{cs}$) is calculated using Eq~\ref{eq:dtb}.
-Figure~\ref{fig:correction:c34-42} shows the deviation of the uncorrected and
-corrected measurements to their noise-free clear-sky values. The results from
+(orange colour). If all measurements are devoid of cloud impact, the
+deviations should follow the Gaussian distribution of noise.
+In such a case, the skewness of the deviations is close to zero.
+However, in real conditions, the distribution has a large negative skewness due to the impact of clouds.
+After correction, all the three models are successful in reducing the cloud impact in the
+measurements.
+The linear model has the lowest reduction in bias (from  -0.75\,K to -0.03\,K) but the highest values for skewness and standard deviation, in comparison to the other two models.
+With the linear model, the error distribution of the corrected dataset has a relatively high positive skewness, which is undesirable.
+The positive skewness can be due to over-correction of cloudy cases, or erroneous correction of clear cases.
+The cubic  and quadratic models have almost similar statistics for bias and standard deviation, but the skewness in the cubic model is lower.
+Overall, the cubic model can be said to have the best performance, thus for all the results shown further, a cubic model is used.
+
+In Sec.~\ref{sec:validation} the validation of simulations against ATMS data
+(Fig.\ref{fig:pdf:c16-22}) showed that the cloudy cases in the simulations were
+underrepresented in comparison to the observations. In order to have a higher
+representation of cloudy cases, we thinned the measurement dataset by removing
+50\% of the clear-sky cases. Since the distribution of thinned dataset is more closer to real conditions, all the analyses presented further in this section are based on the thinned dataset.
+
+Figure~\ref{fig:correction:c34-42:thinned} shows the deviation of the uncorrected and
+corrected measurements to their noise-free clear-sky values for the thinned dataset. The results from
 \cite{rekha2012potential} are also shown as reference (see Sec.~\ref{sec:rekha}
@@
 approach with \cite{rekha2012potential}, we also include the
-dataset,``Filtered'', where all cloudy cases are rejected. Apart from the fit
+dataset, ``Filtered'', where all cloudy cases are rejected. Apart from the fit
 based cloudy classification, it is also assumed that cases with $Tb2-Tb1 < $
--15\,K are ``too-cloudy'', and are rejected. Various metrics corresponding to
-the Figure~\ref{fig:correction:c34-42} are shown in
-Table~\ref{tab:correction:stats:34:42}. [* Why are the yellow lines so
-different in Figs.~10 and 11? Maybe we discussed it, but I have then forgot. *]
-
-\begin{figure}[!p]
+-15\,K are ``too-cloudy'' and are rejected.
+To analyse the sensitivity of our scheme to noise threhold, as discussed in the previous section, results from two different values of $dtb_{cs}$ are shown.
+For both values of $dtb_{cs}$ the corresponding clear-sky cut-off
+($x_{cs}$) is calculated using Eq~\ref{eq:dtb}. Various metrics corresponding to
+the Figure~\ref{fig:correction:c34-42:thinned} are shown in
+Table~\ref{tab:correction:stats:34:42:thinned}.
+
+\begin{figure}[!tb]
 	\centering
@@
       as reference. The measurements have been corrected using brightness
-      temperatures from AWS-42. The mean value of each distribution is given in
-      parenthesis in the legend. Cases with $Tb2 - Tb1 > -15$\,K are rejected.}
+      temperatures from AWS-42. The clear/cloudy classification is made with $dtb_{cs} = 1\sigma$ and also cases with $Tb2 - Tb1 > -15$\,K are rejected.}
 	\label{fig:correction:c34-42:fit}
@@
 %
-\begin{figure}[!p]
-	\centering
-	\includegraphics[height=85mm]{PDF_corrected_AWS-34_AWS-42_all}
+\begin{table}[!tb]
+	\centering
+	\begin{tabular}[b]{c|c|c|c|c}
+		Dataset  		  &   bias &   std &   skewness  & fraction  \\
+		&   [K]  &   [K] & [-] & rejected [\%]\\
+		\hline
+		noise                     &   0.00 &  0.63 &               0.00 &                - \\
+		uncorrected-all           &  -0.75 &  4.62 &             -11.78 &                - \\
+		corrected-linear model    &  -0.03 &  0.75 &               0.48 &                2.84 \\
+		corrected-quadratic model &  -0.06 &  0.71 &              -0.34 &                2.84 \\
+		corrected-cubic model     &  -0.05 &  0.72 &              -0.23 &                2.84 \\
+		\hline
+	\end{tabular}
+	\caption{Bias, standard deviation (std), and measure of skewness of error distributions
+		shown in Figure~\ref{fig:correction:c34-42:fit}.The fraction rejected describes the percentage of cases which are removed.
+Results from three different fit models are shown: linear, quadratic and cubic.}
+	\label{tab:correction:stats:34:42:allfits}
+\end{table}
+%
+\begin{figure}[!tb]
+	\centering
+	\includegraphics[height=85mm]{PDF_corrected_AWS-34_AWS-42_thinned}
 	\caption{Deviation of AWS-34 measurements to noise free clear-sky
@@
       corrected using a cubic model. The different datasets are: noise
-      (simulation dataset), uncorrected-all (measurement dataset without
-      clear/cloudy classification), filtered $1\sigma$ (cloudy measurements are
-      filtered with $dtb_{cs}$ = 1$\sigma$), corrected $1\sigma$ (cloudy
-      measurements are corrected with $dtb_{cs}$ = 1$\sigma$), corrected
-      $2\sigma$ (cloudy measurements are corrected with $dtb_{cs}$ =
-      2$\sigma$), Sreerekha (measurements are filtered according to criteria
-      described in \citet{rekha2012potential}).}
-	\label{fig:correction:c34-42}
+      (simulation dataset), uncorrected (thinned measurements), filtered $1\sigma$ (cases classified as cloudy according to $dtb_{cs}$ = 1$\sigma$ are rejected), corrected $1\sigma$ (cases classified as cloudy according to $dtb_{cs}$ = 1$\sigma$ are corrected), corrected
+      $2\sigma$ (cases classified as cloudy according to $dtb_{cs}$ = 2$\sigma$ are corrected), Sreerekha et al (cloudy cases are filtered according to \citet{rekha2012potential}).}
+	\label{fig:correction:c34-42:thinned}
 \end{figure}
 %
-
-\begin{table}[!bt]
+\begin{table}[!tb]
 	\centering
@@
 		Dataset  		  &   bias &   std &   skewness  & fraction  \\
-							&   [K]  &   [K] & [K] & rejected [\%]\\
-		\hline
-		noise             		&   0.00 &  0.63 &               0.00 &                - \\
-		uncorrected-all       	&  -0.19 &  0.87 &              -2.42 &                - \\
-		filtered($1\sigma$ ) 	&  -0.10 &  0.66 &              -0.15 &               10.56 \\
-		corrected($1\sigma$) 	&  -0.05 &  0.72 &              -0.23 &                2.84 \\
-		corrected($2\sigma$) 	&  -0.09 &  0.70 &              -0.49 &                2.84 \\
-		sreerekha et al   		&  -0.14 &  0.73 &              -0.76 &               43.60 \\
-		\hline
-	\end{tabular}
-	\caption{Bias, standard deviation (std), and measure of skewness of
-      deviations of the measurements to noise-free clear-sky cases. The
-      fraction rejected describes the percentage of cases which are removed.
-      The different datasets are: noise (simulation dataset), uncorrected-all
-      (measurement dataset without clear/cloudy classification), filtered
-      $1\sigma$ (cloudy measurements are filtered with $dtb_{cs}$ = 1$\sigma$),
-      corrected $1\sigma$ (cloudy measurements are corrected with $dtb_{cs}$ =
-      1$\sigma$), corrected $2\sigma$ (cloudy measurements are corrected with
-      $dtb_{cs}$ = 2$\sigma$), Sreerekha (measurements are filtered according
-      to criteria described in \cite{rekha2012potential}). }
-	\label{tab:correction:stats:34:42}
-\end{table}
-%
-\begin{table}[!bt]
-	\centering
-	\begin{tabular}[b]{c|c|c|c|c}
-		Dataset  		  &   bias &   std &   skewness  & fraction  \\
-		&   [K]  &   [K] & [K] & rejected [\%]\\
+		&   [K]  &   [K] & [-] & rejected [\%]\\
 		\hline
 	noise             		&   0.00 &  0.63 &              -0.01 &                - \\
-	uncorrected       		&  -0.29 &  1.00 &              -2.62 &                - \\
+	uncorrected     		&  -1.27 &  6.05 &              -8.97 &                - \\
 	filtered($1\sigma$)  	&  -0.13 &  0.68 &              -0.25 &               17.54 \\
@@
 \end{tabular}
-\caption{Same as Table~\ref{tab:correction:stats:34:42}, but for thinned dataset. 50\% of the clear cases are removed to improve the representation of cloudy cases }
+\caption{Bias, standard deviation (std), and measure of skewness of the
+	error distributions of datasets shown in Figure~\ref{fig:correction:c34-42:thinned}.}
 \label{tab:correction:stats:34:42:thinned}
@@
 clear-sky threshold. The higher skewness in ``Sreerekha et al'' is mainly
-caused by that their method only aims at removing cloud impacts above 4\,K.
-Their approach also leads to a high rejection fraction (43.6\%). The filtering
+beacuse their method only aims at removing cloud impacts above 4\,K.
+Their approach also leads to a high rejection fraction (45.36\%). The filtering
 method introduced here leads to a considerable lower rejection of data
-(10.6\%).
-
-[* The unit for skewness is said to K. Is that correct? In any case I suggest
-to add an equation/description of skewness *]
-
-If the correction part is added, the rejection is decreased even further (28\%)
-and the bias is also improved (from -0.10 to -0.05\,K). On the other hand, the
+(17.54\%).
+
+If the correction part for $1\sigma$ is added, the rejection is decreased even further (4.99\%)
+and the bias is also improved (from -1.27 to -0.06\,K). On the other hand, the
 correction gives some increase in standard deviation and skewness, compared to
-filtering alone. A correction using $2\sigma$ as threshold between clear/cloudy
-gives poorer performance, in particular the skewness is increased.
-
-In Sec.~\ref{sec:validation} the validation of simulations against ATMS data
-(Fig.\ref{fig:pdf:c16-22}) showed that the cloudy cases in the simulations were
-underrepresented in comparison to the observations. In order to have a higher
-representation of cloudy cases, we thinned the measurement dataset by removing
-50\% of the clear-sky cases. The results from this smaller dataset, before and
-after filtering/correction are shown in
-Table~\ref{tab:correction:stats:34:42:thinned}. In comparison to the original
-dataset, the statistics in the thinned dataset is slightly worse, as expected.
-But overall the performance of the correction scheme is comparable. For all
-further analysis presented in this report, the thinned dataset is used.
+filtering alone. A correction using $2\sigma$ gives poorer performance, in particular the reduction in bias is smaller and the skewness is increased.
+
 %
@@
 	\includegraphics[height=85mm]{PDF_corrected_AWS-32_AWS-4X_thinned}
-	\caption{Same as Fig.~\ref{fig:correction:c34-42}, but for channel combinations AWS-32 and AWS-4X.}
+	\caption{Same as Fig.~\ref{fig:correction:c34-42:thinned}, but for channel combinations AWS-32 and AWS-4X. The dataset ``corrected 2$\sigma$'' is not shown.  }
 	\label{fig:correction:c32-4X:thinned}
@@
 Rejecting all the cloudy cases reduces the average bias in the measurements
-from -0.62\,K to -0.21\,K, while with the approach from
-\citet{rekha2012potential} only 45\% of the data is rejected and the average
+from -2.25\,K to -0.21\,K, while with the approach from
+\citet{rekha2012potential} only 45.36\% of the data is rejected and the average
 bias reduces to -0.41\,K. When all the cloudy cases, except the ``too cloudy'',
@@
 		Dataset  		  &   bias &   std & skewness & fraction \\
-						&   [K]  &   [K] & [K] 		& rejected [\%]\\
-		\hline
-Noise             		&  -0.00 &  0.45 &               0.01 &                - \\
-uncorrected       		&  -0.62 &  1.77 &              -4.61 &                - \\
+						&   [K]  &   [K] & [-] 		& rejected [\%]\\
+		\hline
+Noise             		&  0.00 &  0.45 &               0.01 &                - \\
+uncorrected       		&  -2.25 &  8.94 &              -6.85 &                - \\
 filtered($1\sigma$)  	&  -0.21 &  0.51 &              -0.65 &               85.43 \\
@@
 AWS-41; AWS-33 and AWS-41; AWS-35 and AWS-43; AWS-36 and AWS-43.
-
-[* The values for uncorrected differ between Table 6 and 7? Can't be correct. *]
 
@@
 AWS-32 and AWS-41 is poor. The correction using $2\sigma$ as threshold works
-better $1\sigma$. This is an exception, the reversed is valid for AWS-34/42 (as
+better $1\sigma$. This is an exception, the reverse is valid for AWS-34/42 (as
 mentioned) and the channel combinations discussed below.
@@
 impact in AWS-33 are highly correlated. Rejecting the cloudy cases reduces the
-average bias in the measurements from -0.33\,K to -0.13\,K, while a correction
-of cloudy cases reduces the bias further to 0.05\,K. A similar performance is
-seen for the combination AWS-35 and AWS-43, and
-Table~\ref{tab:correction:stats:35:43} shows the statistics from this
-combination. After correction the bias due to cloudy measurements reduces
--0.33\,K to -0.05\,K while rejecting only 6.88\% of the total cases.
+average bias in the measurements from -1.74\,K to -0.13\,K, while a correction
+of cloudy cases reduces the bias further to 0.05\,K.
+The standard deviation and skewness of the corrected dataset are higher than pure-filtering, but smaller than the approach by  ``sreerekha et al''.
+Using $2\sigma$ threshold corrects a smaller fraction of cases than $1\sigma$ but the overall statistics are poorer in comparison to $1\sigma$, but still better than the ``sreerekha et al''.
+
+Table~\ref{tab:correction:stats:35:43} shows the statistics for the combination AWS-35 and AWS-43.
+Here the two filtered datasets have a comparable performance, while on correction, the bias is reduced, but skewness and standard deviation are increased.
+After correction ($1\sigma$) the bias due to cloudy measurements reduces from -0.83\,K to 0.01\,K while rejecting only 2.86\% of the total cases.
+The performance of $1\sigma$ threshold in this case is also better than $2\sigma$.
 
@@
 most of the measurements are without cloud impact. However, the small fraction
-of cloudy cases which are corrected helps in successfully reducing the average
-bias from -0.16\,K to 0.07\,K.
+of cloudy cases which are corrected, helps in successfully reducing the average
+bias from -0.54\,K to -0.07\,K.
 
@@
 		Dataset  		  &   bias &   std & skewness & fraction \\
-							&   [K]  &   [K] & [K] & rejected [\%]\\
+							&   [K]  &   [K] & [-] & rejected [\%]\\
 		\hline
 noise             		&   0.00 &  0.45 &               0.00 &                - \\
-uncorrected       		&  -0.48 &  1.82 &             -14.89 &                - \\
+uncorrected       		&  -2.25 &  8.94 &              -6.85 &                 - \\
 filtered($1\sigma$)  	&  -0.26 &  0.77 &             -16.33 &               72.06 \\
@@
 		Dataset  		  &   bias &   std &  skewness  & fraction\\
-						&   [K]  &   [K] & [K]  & rejected [\%]\\
-		\hline
-	noise       	    	&  -0.00 &  0.45 &               0.00 &               - \\
-	uncorrected	    		&  -0.33 &  0.91 &              -3.15 &                - \\
+						&   [K]  &   [K] & [-]  & rejected [\%]\\
+		\hline
+	noise       	    	&  0.00 &  0.45 &               0.00 &               - \\
+	uncorrected	    		&  -1.74 &  7.45 &              -7.77 &                - \\
 	filtered($1\sigma$)  	&  -0.13 &  0.49 &              -0.40 &               26.18 \\
@@
 		Dataset  		  &   bias &   std &   skewness & fraction \\
-							&   [K]  &   [K] & [K] & rejected [\%]\\
-		\hline
- Noise           	  &  -0.00 &  0.63 &               0.00 &                -\\
-uncorrected     	  &  -0.27 &  1.06 &              -4.42 &                - \\
+							&   [K]  &   [K] & [-] & rejected [\%]\\
+		\hline
+ Noise           	  &  0.00 &  0.63 &               0.00 &                -\\
+uncorrected     	  &  -0.83 &  4.50 &             -10.85 &                - \\
 filtered($1\sigma$)	  &  -0.13 &  0.68 &              -0.46 &               21.30 \\
@@
 	\end{tabular}
-	\caption{Same as Table~\ref{tab:correction:stats:34:42:thinned}, but for channel combination: AWS-35 and AWS-43.   }
+	\caption{Same as Table~\ref{tab:correction:stats:34:42:thinned}, but for channel combination: AWS-35 and AWS-43.}
 	\label{tab:correction:stats:35:43}
@@
 		Dataset  		  &   bias &   std &   skewness & fraction  \\
-							&   [K]  &   [K] & [K] & rejected [\%]\\
-		\hline
- Noise            	 &  -0.00 &  0.88 &              -0.01 &               - \\
-uncorrected      	 &  -0.16 &  1.02 &              -0.86 &                - \\
+							&   [K]  &   [K] & [-] & rejected [\%]\\
+		\hline
+ Noise            	 &  0.00 &  0.88 &              -0.01 &               - \\
+uncorrected      	 &  -0.54 &  3.40 &             -12.26 &                - \\
 filtered($1\sigma$)  &  -0.11 &  0.92 &              -0.13 &                7.38 \\
@@
 A basic remark is that a channel at 229\,GHz channel has a lower sounding
-altitude than all the 183\GHz channels for clear-sky conditions. Accordingly,
+altitude than all the 183\,GHz channels for clear-sky conditions. Accordingly,
 there are no matching RH weighting functions between 229\,GHz and 183\,GHz
@@
 
-[* Finish when Tables 6 and 7 have been checked/corrected. *]
+For AWS-32, filtering based either AWS-4X or AWS-41 has a very high rejection rate, though the resulting dataset has low error.
+The high fraction of rejection can increase the probability of removing ``true'' clear cases.
+After correction, the error distributions are asymmetric and have large bias and standard deviation.
+Among the two combinations, the dataset corrected with AWS-41 has slightly better bias and standard deviation.
+As an exception to other 183\,GHz channels, the correction scheme for AWS-32 works better for $2\sigma$ threshold, as with a larger value of noise, relatively smaller number of cases are corrected.
+The effect of mismatch between weighting functions for AWS-32 and AWS-4X/41 is reflected in the performance of our correction scheme.
 
@@
 
-The results of \citet{rekha2012potential} is better than ours for AWS-32 [*
-check when tables been updated *], while for the other 183\,GHz channels better
-results are obtained by using 325\,GHz data. The main difference for these
-later channels is the high rejection rate for \citet{rekha2012potential}.
+The results of \citet{rekha2012potential} is better than ours for AWS-32, while for the other 183\,GHz channels better results are obtained by using 325\,GHz data.
+However, when only pure-filtering is considered, our scheme performs better for AWS-32, albeit with a high rejection rate.
+For all later channels of 183\,GHz,  we reject only a small fraction of cases in comparison to \citet{rekha2012potential}, but the corrected datasets have symmetric error distributions with lower bias, standard deviations.
+Only for AWS-35 and AWS-36, the standard deviation and skewness of the corrected dataset is higher.
 

### 2020-05-29 Report/aws_325ghz_study.tex
Smaller updates of the report.

@@
 
+[* Anders just informed us (May 29) that it would be good to avoid an IF of 1.7\,GHz, as that frequency could be used for downlink and there is a risk for
+interference. The four channel option can easily be adopted to this, but what
+do with the three channel one? *]
+
 \subsection{Impact of upper end of IF band}
@@
 1$\sigma$ or 2$\sigma$ where $\sigma$ refers to the magnitude of measurement
-noise (Eq.~\ref{eq:noise}, often called NE$\Delta$T).
-We will use $1\sigma$ for the development of the scheme, however, the sensitivity of the scheme to 1$\sigma$ and 2$\sigma$  threshold is also provided later in the text.
+noise (Eq.~\ref{eq:noise}, often called NE$\Delta$T). We will use $1\sigma$ for
+the development of the scheme, however, the sensitivity of the scheme to
+a 1$\sigma$ or 2$\sigma$ threshold is also provided later in the text.
 
@@
 For all three models, cases with $Tb2-Tb1 < $ -15\,K are assumed to be ``too
-cloudy'' and are not corrected. Also, cases classified as clear according to $1\sigma$ threshold are not corrected. The clear-sky adjustment for all eligible
-measurements is calculated from all three
-models, and the three predicted datasets are compared.
+cloudy'' and are not corrected. Also, cases classified as clear according to
+the $1\sigma$ threshold are not corrected. The clear-sky adjustment for all
+eligible measurements is calculated from all three models, and the three
+predicted datasets are compared.
 
@@
 representation of cloudy cases, we thinned the measurement dataset by removing
-50\% of the clear-sky cases. Since the distribution of thinned dataset is more closer to real conditions, all the analyses presented further in this section are based on the thinned dataset.
+50\% of the clear-sky cases. The distribution of thinned dataset is more closer
+to real conditions in the region matching weak cloud impacts and all the
+analyses presented further in this section are based on the thinned dataset.
 
@@
 average bias in the measurements from -1.74\,K to -0.13\,K, while a correction
-of cloudy cases reduces the bias further to 0.05\,K.
-The standard deviation and skewness of the corrected dataset are higher than pure-filtering, but smaller than the approach by  ``sreerekha et al''.
-Using $2\sigma$ threshold corrects a smaller fraction of cases than $1\sigma$ but the overall statistics are poorer in comparison to $1\sigma$, but still better than the ``sreerekha et al''.
+of cloudy cases reduces the bias further to 0.05\,K. The standard deviation and
+skewness of the corrected dataset are higher than pure-filtering, but smaller
+than the approach by Sreerekha et al. Using $2\sigma$ threshold corrects a
+smaller fraction of cases than $1\sigma$ but the overall statistics are poorer
+in comparison to $1\sigma$, but still better than Sreerekha et al.
 
@@
 %
+There are two main drawbacks of the simple scheme introdoced in the previous
+section. The filtering/correction only involves a single 325\,GHz channel. The
+scheme could be extended to consider a higher number of channels, but there is
+no obvious formulation of the expressions to apply. The second problem is that
+no case-specific uncertainty estimate is provided, only the overal bias and
+standard deviations are known. The first drawback hints towards using a machine
+learning approach, and the second one suggests to use the special form denoted
+QRNN (Quantile Regression Neural Network), that was introduced for ratmospheric
+retrievals by \citet{pfreundschuh:aneur:18}.
+
 \dots

### 2020-06-05 Report/aws_325ghz_study.tex
added few tables and figures for QRNN, but no text

@@
 %
-There are two main drawbacks of the simple scheme introdoced in the previous
+There are two main drawbacks of the simple scheme introduced in the previous
 section. The filtering/correction only involves a single 325\,GHz channel. The
@@
 learning approach, and the second one suggests to use the special form denoted
-QRNN (Quantile Regression Neural Network), that was introduced for ratmospheric
+QRNN (Quantile Regression Neural Network), that was introduced for atmospheric
 retrievals by \citet{pfreundschuh:aneur:18}.
@@
 
+\subsection{QRNN model}
+%
+\begin{figure}[!ht]
+	\centering
+	\includegraphics[height=85mm]{quantile_loss_median.png}
+	\caption{The mean quantile loss for $\tau = 0.5$ with different configurations of layer width and hidden layers ($n_h$).}
+	\label{fig:quantile_loss_median}
+\end{figure}
+
+\subsection{Prediction accuracy}
+%
+\begin{figure}[!tb]
+	\centering
+	\includegraphics[height=60mm]{distribution_predicted_C32}\hspace{5mm}% 
+	\includegraphics[height=60mm]{distribution_predicted_C33}
+	\includegraphics[height=60mm]{distribution_predicted_C34}\hspace{5mm}% 
+	\includegraphics[height=60mm]{distribution_predicted_C35}
+	\includegraphics[height=60mm]{distribution_predicted_C36}
+	\caption{ Probability distribution functions (PDFs) of predicted and observed noise free brightness temperatures for all 183\,GHz channels of AWS.  }
+	\label{fig:pdf:qrnn}
+\end{figure}
+
+\begin{figure}[!tb]
+	\centering
+	\includegraphics[height=85mm]{Channel_C34.png}
+	\caption{Deviation of AWS-34 measurements to noise free clear-sky
+		simulations before and after correction with QRNNs. Predictions from both three channel and four channel options for 325 GHz are shown. }
+	\label{fig:qrnn_C34:deviations}
+\end{figure}
+
+\begin{table}[!tb]
+	\centering
+	\begin{tabular}[b]{c|c|c|c|c}
+	Dataset  		  &   bias &   std &   skewness & fraction  \\
+	&   [K]  &   [K] & [-] & rejected [\%]\\
+		\hline
+Noise                     & -0.006 & 0.634 &              0.008 &      - \\
+uncorrected               & -0.678 & 3.678 &            -10.320 &     - \\
+corrected (three channel) &  0.050 & 0.617 &             -0.506 &      2.730 \\
+corrected (four channel)  &  0.077 & 0.608 &             -0.446 &      2.957 \\
+		\hline
+	\end{tabular}
+	\caption{ Bias, standard deviation and measure of skewness for the error distributions of the dataset shown in Figure~\ref{fig:qrnn_C34:deviations}}
+	\label{tab:qrnn:C34}
+\end{table}
+
+\begin{table}[!tb]
+	\centering
+	\begin{tabular}[b]{c|c|c|c|c}
+	Dataset  		  &   bias &   std &   skewness & fraction  \\
+	&   [K]  &   [K] & [-] & rejected [\%]\\
+		\hline
+Noise                     &  0.004 & 0.455 &              0.006 &      - \\
+uncorrected               & -1.341 & 5.905 &             -7.482 &      - \\
+corrected (three channel) & -0.065 & 0.820 &             -2.312 &      4.902 \\
+corrected (four channel)  & -0.003 & 0.821 &             -2.158 &      4.906 \\
+		\hline
+	\end{tabular}
+	\caption{ Same as Table~\ref{tab:qrnn:C34}, but for channel AWS-32.}
+	\label{tab:qrnn:C32}
+\end{table}
+
+\begin{table}[!tb]
+	\centering
+	\begin{tabular}[b]{c|c|c|c|c}
+	Dataset  		  &   bias &   std &   skewness & fraction  \\
+	&   [K]  &   [K] & [-] & rejected [\%]\\
+		\hline
+Noise                     &  0.002 & 0.451 &             -0.017 &     - \\
+uncorrected               & -0.981 & 4.706 &             -8.755 &     - \\
+corrected (three channel) &  0.048 & 0.578 &             -0.596 &      4.189 \\
+corrected (four channel)  &  0.044 & 0.573 &             -0.603 &      4.280 \\
+		\hline
+	\end{tabular}
+	\caption{ Same as Table~\ref{tab:qrnn:C34}, but for channel AWS-33.}
+	\label{tab:qrnn:C33}
+\end{table}
+
+\begin{table}[!tb]
+	\centering
+	\begin{tabular}[b]{c|c|c|c|c}
+	Dataset  		  &   bias &   std &   skewness & fraction  \\
+	&   [K]  &   [K] & [-] & rejected [\%]\\
+		\hline
+Noise                      &  0.002 & 0.626 &             -0.003 &      - \\
+uncorrected                & -0.428 & 2.661 &            -12.451 &      - \\
+corrected (three channel)  &  0.036 & 0.601 &             -0.202 &      1.451 \\
+corrected (four channel)   &  0.017 & 0.572 &             -0.279 &      1.781 \\
+		\hline
+	\end{tabular}
+	\caption{ Same as Table~\ref{tab:qrnn:C34}, but for channel AWS-35.}
+	\label{tab:qrnn:C35}
+\end{table}
+
+\begin{table}[!tb]
+	\centering
+	\begin{tabular}[b]{c|c|c|c|c}
+	Dataset  		  &   bias &   std &   skewness & fraction  \\
+	&   [K]  &   [K] & [-] & rejected [\%]\\
+		\hline
+Noise                     & -0.000 & 0.888 &              0.005 &      - \\
+uncorrected               & -0.269 & 2.059 &            -11.899 &      - \\
+corrected (three channel) &  0.053 & 0.797 &             -0.143 &      1.263 \\
+corrected (four channel)  &  0.033 & 0.763 &             -0.140 &      1.148 \\
+		\hline
+	\end{tabular}
+	\caption{ Same as Table~\ref{tab:qrnn:C34}, but for channel AWS-36.}
+	\label{tab:qrnn:C36}
+\end{table}
+
+\subsection{Uncertainity estimation}
 \section{Discussion}

### 2020-06-10 Report/aws_325ghz_study.tex
Few changes as response to questions fro Christophe.
Small change of 4ch-option and defined a second 3ch one.

@@
 results, the reflectivity is set to have no frequency variation, i.e.\ the same
-value is applied for all bands. The reflective is varied between 0 and 0.5.
+value is applied for all bands. The reflectivity is varied between 0 and 0.5
+(these fixed values are only applied in this section, the bulk simulations are
+using TESSEM and TELSEM for seting the surface properties).
 In the figures covering transmissivities and Jacobians, the specifications
@@
 
-[* Anders just informed us (May 29) that it would be good to avoid an IF of 1.7\,GHz, as that frequency could be used for downlink and there is a risk for
-interference. The four channel option can easily be adopted to this, but what
-do with the three channel one? *]
-
 \subsection{Impact of upper end of IF band}
@@
     AWS-41  & 325.15$\pm$6.60 & 2800\\
-    AWS-42  & 325.15$\pm$4.05 & 1900\\
-    AWS-43  & 325.15$\pm$2.35 & 1300\\
+    AWS-42  & 325.15$\pm$4.10 & 1800\\
+    AWS-43  & 325.15$\pm$2.40 & 1200\\
     AWS-44  & 325.15$\pm$1.20 & \phantom{0}800\\
@@
   \end{tabular}
+%  \begin{tabular}[c]{c|c|c}
+%    Channel & Frequency   & Bandwidth \\
+%    name    & [GHz] &  [MHz] \\
+%    \hline
+%    AWS-41  & 325.15$\pm$6.60 & 2800\\
+%    AWS-42  & 325.15$\pm$4.05 & 1900\\
+%    AWS-43  & 325.15$\pm$2.35 & 1300\\
+%    AWS-44  & 325.15$\pm$1.20 & \phantom{0}800\\
+%    \hline
+%  \end{tabular}
   \end{minipage}  
@@
 roughly equally spaced in altitude (Fig.~\ref {fig:4ch:prel}). This option has
-a IF range of 0.7 to 8.0\,GHz, and leaves 200\,MHz space between AWS-41 and
-AWS-42 and has 100\,MHz between the other channels. Also this suggestion uses
-the complete IF bandwidth.
+a IF range of 0.7 to 8.0\,GHz, and leaves 200\,MHz space between all the
+325\,GHz channels. Also this suggestion uses the complete IF bandwidth.
+
+\subsection{A second three channel option}
+%
+Relatively late in the study Omnisys informed us about that an IF of 1.7\,GHz
+should be avoided, as this frequency likely will be used for downlink of data.
+The four channel option needed just a marginal change to adopt to this
+constrain, while 1.7\,GHz is more or less at the centre of the three channel
+option. It was then decided to formulate second three channel option avoiding 
+1.7\,GHz, and the suggestion is found in Table~\ref{tab:chs:3b}.
+
+\begin{table}[!h]
+  \centering  
+  \begin{tabular}[c]{c|c|c}
+    Channel & Frequency   & Bandwidth \\
+    name    & [GHz] &  [MHz] \\
+    \hline
+    AWS-41  & 325.15$\pm$6.50 & 3000\\
+    AWS-42  & 325.15$\pm$3.30 & 3000\\
+    AWS-43  & 325.15$\pm$1.20 & \phantom{0}800\\
+    \hline
+  \end{tabular}
+  \caption{The second three channel suggestion.}
+  \label{tab:chs:3b}
+\end{table}
+
+AWS-41 is identical between the two three channel options. In this second
+option, AWS-43 is set to have the same limits as AWS-44 in the four channel
+option. AWS-42 was then allowed to fill the frequency range between the two
+other channels, but keeping a gap of 200\,MHz on each side.
+
+The resulting weighting functions are exemplified in Fig.~\ref{fig:3bch:prel}.
+As expected, there is now a somewhat poorer match to 183\,GHz, most importantly
+the weighting function of AWS-43 ends up between the ones of AWS-35 and 36. The
+weighting function of AWS-42 is slightly moved upwards compared to the first
+three channel option.
+
+\begin{figure}[!tb]
+  \centering
+  \includegraphics[height=61mm]{fascod_3bchopt_tro}\hspace{5mm}% 
+  \includegraphics[clip,trim=43 0 0 0,height=61mm]{fascod_3bchopt_mlw}
+  \caption{RH weighting functions of the second three channel option
+    (Table~\ref{tab:chs:3b}), for the Fascod tropical (left) and mid-latitude
+    winter (right) scenarios.}
+  \label{fig:3bch:prel}
+\end{figure}
 

### 2020-06-10 Report/aws_325ghz_study.tex
added some text for QRNN

--- 2020-06-05 Report/aws_325ghz_study.tex
@@
 %\usepackage{longtable}
+\usepackage{mathtools}
 
@@
 no obvious formulation of the expressions to apply. The second problem is that
-no case-specific uncertainty estimate is provided, only the overal bias and
+no case-specific uncertainty estimate is provided, only the overall bias and
 standard deviations are known. The first drawback hints towards using a machine
@@
 
-\dots
-
 \subsection{QRNN model}
+%
+The neural network training is a process of learning to predict the outputs {$y_i$} from inputs {$x_i$} through a series of learnable transformations.
+While training, neural networks seek to minimize the model error through a loss function.
+The choice of the loss function depends on the predictive problem.
+When a neural network is trained to minimize the mean of the quantile loss function to predict the quantiles of the distribution, it is called a Quantile Regression Neural Network (QRNN).
+
+If $X$ is a random variable with cumulative distribution function $F(X)$, and $x_{\tau}$ is its $\tau$th quantile, the quantile loss function is defined as:
+\begin{equation}
+\mathcal{L}_\tau(y_\tau, y_{true}) =
+\begin{cases*}
+(1 - \tau)|y_\tau - y_{true}| &\text{if}  $y_\tau < y_\text{true}$\\
+\tau |y_\tau - y_\text{true}| & \text{ otherwise, }
+\end{cases*}
+\label{loss_function}
+\end{equation}
+
+A detailed description of QRNN can be found in \citet{pfreundschuh:aneur:18}.
+
+\subsubsection{Training}
+%  
+In this section, QRNNs are used to correct the cloud impact in each of 183\,GHz channels using TBs from all available channels of 325\,GHz.
+We assess the performance of the scheme using both three channel and four channel options of 325\,GHz.
+A separate QRNN is used for each of the 183\,GHz channels.
+For example, to predict clear-sky TBs from AWS-34, the training data is TBs from all channels of 325\,GHz.
+
+To develop the QRNN based correction scheme, we use the same dataset as in the simple scheme .
+Out of 125\,000 simulations, 90\% are used to train the model, while the rest 10\% is used to evaluate the model's performance during training.
+In the training process, noise is added to the input according to Eqn~\ref{eq:noise}, every time the training data is exposed to the model.
+This ensures that the model is exposed to a new dataset on every iteration.
+Before training, the input data is normalized with mean and standard deviation.
+
+The structure of the QRNN is defined by various hyper-parameters which are tuned to achieve a high-performing model.
+These parameters determine the structure of the neural network and how the network is trained.
+We performed a grid search to determine structural parameters: depth (number of hidden layers) and width (number of neurons).
+The quantile loss for the $\tau = 0.5$ (median) is used to compare the performance of different hyper-parameter configurations.
+Figure~\ref{fig:quantile_loss_median} shows the mean quantile loss when QRNN is trained for predicting clear-sky values for AWS-34.
+Increasing both layer width and depth has a positive impact on performance of the network, however for four hidden layers, increasing the layer width leads to only small performance gains.
+On basis of these results, a neural network with four hidden layer and 128 neurons was chosen for training.
+
+For the training, we obtained the best performance when trained with a multiple learning rate schedule.
+We start the training process with a initial learning rate and after a certain number of epochs, the training is updated with a new initial learning rate.
+We chose the three training schedules with initial learning rates = 0.01, 0.001, 0.0001 respectively, updated after 20 epochs.
+The batch size was set to 256 samples.
 %
@@
 \end{figure}
-
+%
 \subsection{Prediction accuracy}
 %
+We train the QRNN to predict the quantiles $x_{\tau}$, for median, $\pm 1\sigma$ and $\pm 2 \sigma$ ($\tau$ = 0.05, 0.32, 0.5 , 0.68, 0.95).
+The expectation value of the posterior distribution is assumed to be the best estimate for the predicted clear-sky value.
+
+To analyse the prediction accuracy, a testing dataset is constructed by randomly drawing 25\,000 cases from the simulation dataset.
+Noise is added to each simulation to mimic a new measurement dataset.
+The distributions of the predicted clear-sky noise-free values for each of the 183\, GHz channels are shown in Figure~\ref{fig:pdf:qrnn}.
+The simulated clear-sky distributions are also plotted for reference.
+It is evident from these results that QRNN is successful in predicting the clear-sky values from measurements.
+
+Figure~\ref{fig:qrnn_C34:deviations} shows the error distributions of the measurements and predicted clear-sky TBs for AWS-34 using both three and four channel options of 325\,GHz.
+Measurements with cases with $Tb2 - Tb1 > -15$\,K are assumed to be too-cloudy and are filtered out.
+Both the three channel and four channel QRNN model are successful in predicting the clear-sky noise-free value for AWS-34, and the resulting error distribution is symmetric.
+The statistics corresponding to these distributions are provided in Table~\ref{tab:qrnn:C34}.
+For AWS-34, the performance of both three and four option 325\,GHz is comparable.
+The average bias, standard
+
+The fraction of cases rejected as "too-cloudy" is also provided under ``fraction rejected''. 
+   c
+
 \begin{figure}[!tb]
@@
 uncorrected               & -0.678 & 3.678 &            -10.320 &     - \\
-corrected (three channel) &  0.050 & 0.617 &             -0.506 &      2.730 \\
-corrected (four channel)  &  0.077 & 0.608 &             -0.446 &      2.957 \\
+corrected (three channel) &  0.079 & 0.620 &             -0.414 &      2.730 \\
+corrected (four channel)  &  0.075 & 0.619 &             -0.416 &      2.957 \\
 		\hline
@@
 uncorrected               & -1.341 & 5.905 &             -7.482 &      - \\
-corrected (three channel) & -0.065 & 0.820 &             -2.312 &      4.902 \\
-corrected (four channel)  & -0.003 & 0.821 &             -2.158 &      4.906 \\
+corrected (three channel) & -0.026 & 0.829 &             -2.110 &      4.902 \\
+corrected (four channel)  & -0.027 & 0.828 &             -2.187 &      4.906 \\
 		\hline
@@
 uncorrected               & -0.981 & 4.706 &             -8.755 &     - \\
-corrected (three channel) &  0.048 & 0.578 &             -0.596 &      4.189 \\
-corrected (four channel)  &  0.044 & 0.573 &             -0.603 &      4.280 \\
+ corrected (three channel)&  0.053 & 0.573 &             -0.593 &      4.189 \\
+corrected (four channel)  &  0.035 & 0.572 &             -0.554 &      4.280 \\
+
 		\hline
@@
 uncorrected                & -0.428 & 2.661 &            -12.451 &      - \\
-corrected (three channel)  &  0.036 & 0.601 &             -0.202 &      1.451 \\
-corrected (four channel)   &  0.017 & 0.572 &             -0.279 &      1.781 \\
+corrected (three channel)  &  0.031 & 0.600 &             -0.303 &      1.451 \\
+corrected (four channel)   &  0.049 & 0.581 &             -0.335 &      1.781 \\
 		\hline
@@
 uncorrected               & -0.269 & 2.059 &            -11.899 &      - \\
-corrected (three channel) &  0.053 & 0.797 &             -0.143 &      1.263 \\
-corrected (four channel)  &  0.033 & 0.763 &             -0.140 &      1.148 \\
+ corrected (three channel)&  0.064 & 0.797 &             -0.138 &      1.263 \\
+corrected (four channel)  &  0.057 & 0.765 &             -0.120 &      1.148 \\
 		\hline

### 2020-06-11 Report/aws_325ghz_study.tex
updated tables, figures with new channel configurations

@@
 In this section, QRNNs are used to correct the cloud impact in each of 183\,GHz channels using TBs from all available channels of 325\,GHz.
-We assess the performance of the scheme using both three channel and four channel options of 325\,GHz.
 A separate QRNN is used for each of the 183\,GHz channels.
 For example, to predict clear-sky TBs from AWS-34, the training data is TBs from all channels of 325\,GHz.
+We assess the performance of the scheme using both three channel and four channel options of 325\,GHz.
+Two configurations for three channel option are described in Sec.~\ref{sec:}, and both have been used to train QRNN separately.
+Thus, for each channel of 183\,GHz, we have a set of three predictions: one from four channel option, and two from the old and new configurations of the three channel option.
+Further in the text, the old and new three channel configurations are labeled as "three-a" and "three-b".
 
@@
 We performed a grid search to determine structural parameters: depth (number of hidden layers) and width (number of neurons).
-The quantile loss for the $\tau = 0.5$ (median) is used to compare the performance of different hyper-parameter configurations.
-Figure~\ref{fig:quantile_loss_median} shows the mean quantile loss when QRNN is trained for predicting clear-sky values for AWS-34.
+The mean quantile loss is used to compare the performance of different hyper-parameter configurations.
+Figure~\ref{fig:quantile_loss} shows the mean quantile loss when QRNN is trained for predicting clear-sky values for AWS-34 using four channel option.
 Increasing both layer width and depth has a positive impact on performance of the network, however for four hidden layers, increasing the layer width leads to only small performance gains.
 On basis of these results, a neural network with four hidden layer and 128 neurons was chosen for training.
-
 For the training, we obtained the best performance when trained with a multiple learning rate schedule.
@@
 The batch size was set to 256 samples.
+
+The grid search was also conducted for both three channel options, and an identical QRNN structure, as described for the four channel option, was found to have the best performance. 
 %
@@
 	\centering
-	\includegraphics[height=85mm]{quantile_loss_median.png}
+	\includegraphics[height=85mm]{quantile_loss.png}
 	\caption{The mean quantile loss for $\tau = 0.5$ with different configurations of layer width and hidden layers ($n_h$).}
-	\label{fig:quantile_loss_median}
+	\label{fig:quantile_loss}
 \end{figure}
@@
 %
-We train the QRNN to predict the quantiles $x_{\tau}$, for median, $\pm 1\sigma$ and $\pm 2 \sigma$ ($\tau$ = 0.05, 0.32, 0.5 , 0.68, 0.95).
+We train the QRNN to predict the quantiles $x_{\tau}$, for median, $\pm 1\sigma$, $\pm 2 \sigma$ and  $\pm 3 \sigma$ ($\tau$ = 0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998).
 The expectation value of the posterior distribution is assumed to be the best estimate for the predicted clear-sky value.
-
 To analyse the prediction accuracy, a testing dataset is constructed by randomly drawing 25\,000 cases from the simulation dataset.
 Noise is added to each simulation to mimic a new measurement dataset.
+
 The distributions of the predicted clear-sky noise-free values for each of the 183\, GHz channels are shown in Figure~\ref{fig:pdf:qrnn}.
 The simulated clear-sky distributions are also plotted for reference.
-It is evident from these results that QRNN is successful in predicting the clear-sky values from measurements.
-
-Figure~\ref{fig:qrnn_C34:deviations} shows the error distributions of the measurements and predicted clear-sky TBs for AWS-34 using both three and four channel options of 325\,GHz.
+For these results, the four channel option was used to train the QRNN.
+The distributions show that QRNN is overall successful in predicting the clear-sky cases.
+For all channels, the simulations and predictions have a good agreement for the main peak of the distribution.
+However, for AWS-32, AWS-33 and  AWS-34, QRNN seems to predict slightly colder TBs.
+These results give an indication of the behavior of QRNN, but for a detailed analysis of the prediction accuracy, we make a quantitative assessment of the errors.
+
+Figure~\ref{fig:qrnn_C34:deviations} shows the error distributions of the measurements and predicted clear-sky TBs for AWS-34 using three (three-b) and four channel options of 325\,GHz.
 Measurements with cases with $Tb2 - Tb1 > -15$\,K are assumed to be too-cloudy and are filtered out.
@@
 The statistics corresponding to these distributions are provided in Table~\ref{tab:qrnn:C34}.
-For AWS-34, the performance of both three and four option 325\,GHz is comparable.
-The average bias, standard
-
+.
 The fraction of cases rejected as "too-cloudy" is also provided under ``fraction rejected''.
-   c
+For AWS-34, the predictions from all three QRNN models are comparable.
 
@@
 		\hline
-Noise                     & -0.006 & 0.634 &              0.008 &      - \\
-uncorrected               & -0.678 & 3.678 &            -10.320 &     - \\
-corrected (three channel) &  0.079 & 0.620 &             -0.414 &      2.730 \\
-corrected (four channel)  &  0.075 & 0.619 &             -0.416 &      2.957 \\
-		\hline
-	\end{tabular}
-	\caption{ Bias, standard deviation and measure of skewness for the error distributions of the dataset shown in Figure~\ref{fig:qrnn_C34:deviations}}
+Noise                       &  0.003 & 0.641 &             -0.001 &      - \\
+uncorrected                 & -0.677 & 3.673 &            -10.321 &      - \\
+corrected (three-a) 		&  0.094 & 0.624 &             -0.629 &      2.750 \\
+corrected (three-b) 		&  0.100 & 0.652 &             -0.543 &      2.582 \\
+corrected (four)   			&  0.111 & 0.620 &             -0.659 &      2.985 \\
+
+		\hline
+	\end{tabular}
+	\caption{ Bias, standard deviation and measure of skewness for the error distributions of the dataset (AWS-34) shown in Figure~\ref{fig:qrnn_C34:deviations}}
 	\label{tab:qrnn:C34}
@@
 		\hline
-Noise                     &  0.004 & 0.455 &              0.006 &      - \\
-uncorrected               & -1.341 & 5.905 &             -7.482 &      - \\
-corrected (three channel) & -0.026 & 0.829 &             -2.110 &      4.902 \\
-corrected (four channel)  & -0.027 & 0.828 &             -2.187 &      4.906 \\
+Noise                       & -0.004 & 0.450 &             -0.030 &      - \\
+uncorrected                 & -1.343 & 5.908 &             -7.484 &      - \\
+corrected (three-a)  		&  0.019 & 0.889 &             -3.519 &      4.906 \\	 
+corrected (three-b)  		& -0.008 & 0.850 &             -3.326 &      4.926 \\			
+corrected (four)    		& -0.011 & 0.878 &             -3.030 &      4.930 \\
+
 		\hline
@@
 		\hline
-Noise                     &  0.002 & 0.451 &             -0.017 &     - \\
-uncorrected               & -0.981 & 4.706 &             -8.755 &     - \\
- corrected (three channel)&  0.053 & 0.573 &             -0.593 &      4.189 \\
-corrected (four channel)  &  0.035 & 0.572 &             -0.554 &      4.280 \\
-
-		\hline
+Noise                       & -0.005 & 0.450 &             -0.004 &      - \\
+uncorrected                 & -0.982 & 4.703 &             -8.778 &      - \\
+corrected (three-a) 		&  0.088 & 0.583 &             -0.959 &      4.197 \\
+corrected (three-b)  		& -0.030 & 0.612 &             -0.756 &      4.205 \\
+corrected (four)            &  0.106 & 0.591 &             -1.006 &      4.212 \\
+		\hline
+
 	\end{tabular}
@@
 		\hline
-Noise                      &  0.002 & 0.626 &             -0.003 &      - \\
-uncorrected                & -0.428 & 2.661 &            -12.451 &      - \\
-corrected (three channel)  &  0.031 & 0.600 &             -0.303 &      1.451 \\
-corrected (four channel)   &  0.049 & 0.581 &             -0.335 &      1.781 \\
+
+Noise                      &  0.003 & 0.626 &             -0.009 &      - \\
+uncorrected                & -0.428 & 2.653 &            -12.492 &      - \\
+corrected (three-a) 	   &  0.060 & 0.610 &             -0.281 &      1.439 \\
+corrected (three-b) 	   &  0.097 & 0.618 &              0.011 &      1.331 \\
+corrected (four)   		   &  0.042 & 0.591 &             -0.351 &      1.821 \\
 	\hline
@@
 		\hline
-Noise                     & -0.000 & 0.888 &              0.005 &      - \\
+Noise                       & 0.000 & 0.888 &              0.005 &      - \\
 uncorrected                 & -0.269 & 2.059 &            -11.899 &      - \\
- corrected (three channel)&  0.064 & 0.797 &             -0.138 &      1.263 \\
-corrected (four channel)  &  0.057 & 0.765 &             -0.120 &      1.148 \\
+corrected (three-a) 		&  0.062 & 0.797 &             -0.139 &      1.279 \\
+corrected (three-b) 		&  0.092 & 0.770 &             -0.075 &      1.124 \\
+corrected (four)   			&  0.056 & 0.779 &             -0.172 &      1.156 \\
+
 		\hline
@@
 
-\subsection{Uncertainity estimation}
+\subsection{Uncertainty estimation}
+%
+\begin{figure}[!ht]
+	\centering
+	\includegraphics[height=85mm]{prediction_uncertainty.png}
+	\caption{The prediction uncertainty with respect to quantiles for randomly selected 2400 cases.}
+	\label{fig:prediction_uncertainty}
+\end{figure}
+
 \section{Discussion}

### 2020-06-11 QRNN/random_split.py

@@ -1,0 +1,88 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Mon Jun  1 13:18:09 2020
+
+@author: inderpreet
+"""
+
+
+import numpy as np
+import xarray
+import os
+import matplotlib.pyplot as plt
+
+def get_TB(TB, TB0, ic, cases):
+    
+    x_train = TB[:, :, cases[:int(0.9*ic.shape[0])]]
+    x_train0 = TB0[:, :, cases[:int(0.9*ic.shape[0])]]
+    
+    x_test  = TB[:, :, cases[int(0.8*ic.shape[0]):]]
+    x_test0 = TB0[:, :, cases[int(0.8*ic.shape[0]):]]
+    
+    
+    x_val0 = TB0[:, :, cases[int(0.9*ic.shape[0]):]]
+    x_val = TB[:, :, cases[int(0.9*ic.shape[0]):]]
+    
+    return x_test0, x_test
+
+
+y = xarray.open_dataset(os.path.expanduser('~/Dendrite/Projects/AWS-325GHz/TB_AWS/TB_AWS_m60_p60_four.nc'))
+TB0 = y.TB
+cases = TB0.cases.values
+
+y = xarray.open_dataset(os.path.expanduser('~/Dendrite/Projects/AWS-325GHz/TB_AWS/TB_AWS_m60_p60_noise_four.nc'))
+TB = y.TB_noise
+
+ic = np.arange(0, len(cases), 1)
+np.random.shuffle(ic)
+
+x_test0, x_test = get_TB(TB, TB0, ic, cases)
+
+x_test.to_netcdf(os.path.expanduser('~/Dendrite/Projects/AWS-325GHz/TB_AWS/testing_data_noise_four.nc'), 'w')
+x_test0.to_netcdf(os.path.expanduser('~/Dendrite/Projects/AWS-325GHz/TB_AWS/testing_data_four.nc'), 'w')
+
+
+#=====================================================================================================
+#Repeat same for three channel option A with same shuffled indices
+#=====================================================================================================
+
+y = xarray.open_dataset(os.path.expanduser('~/Dendrite/Projects/AWS-325GHz/TB_AWS/TB_AWS_m60_p60_three_a.nc'))
+TB0 = y.TB
+
[…]

### 2020-06-12 QRNN/aws.py
added second conf of 3 channel option

@@ -8,7 +8,7 @@ class awsData(Dataset):
     Pytorch dataset for the AWS training data.
 
     """
-    def __init__(self, path, inChannels, batch_size = None):
+    def __init__(self, path, inChannels, option, T_rec = None, batch_size = None):
         """
         Create instance of the dataset from a given file path.
 
@@ -19,43 +19,47 @@ class awsData(Dataset):
         """
         super().__init__()
         self.batch_size = batch_size
-
+        self.T_rec = T_rec
         self.file = netCDF4.Dataset(path, mode = "r")
-
+        
 #        TB = self.file.variables["TB_noise"][:]
         TB = self.file.variables["TB"][:]
         channels = self.file.variables["channels"][:]
 
  #       print (channels)
         self.channels = inChannels
+        self.option = option
+#       find index for input channels
+        
+
         i1, = np.argwhere(channels == inChannels[0])[0] 
         i2, = np.argwhere(channels == inChannels[1])[0]     
         i3, = np.argwhere(channels == inChannels[2])[0]     
         i4, = np.argwhere(channels == inChannels[3])[0]
         
-        self.index = [i1, i2, i3, i4]
+        if self.option == 4:
+            i5, = np.argwhere(channels == inChannels[4])[0]        
+            self.index = [i1, i2, i3, i4, i5]
+        else:
+            self.index = [i1, i2, i3, i4]
         
+
         C1 = TB[i1, 1, :]        
         C2 = TB[i2, 1, :]
         C3 = TB[i3, 1, :]
         C4 = TB[i4, 1, :]
+        if self.option == 4:
+            C5 = TB[i5, 1, :]
 
-        #store mean and std to normalise data  
-        
         self.x = np.float32(np.stack([C1, C2, C3, C4], axis = 1))
+        if self.option == 4:
+            self.x = np.float32(np.stack([C1, C2, C3, C4, C5], axis = 1))
         
+        #store mean and std to normalise data  
         x_noise = self.add_noise(self.x)
   
         self.std = np.std(x_noise, axis = 0)
         self.mean = np.mean(x_noise, axis = 0)   
-#        print (self.mean, self.std)
-
-        
-#        path = path.replace("_noise", "")
-        
-#        self.file = netCDF4.Dataset(path, mode = "r")
-
-#        TB = self.file.variables["TB"][:]
         
         self.y = np.float32(TB[i1, 0, :])
         
@@ -85,6 +89,7 @@ class awsData(Dataset):
             i: The index of the sample to return
         """
         if (i == 0):
+
[…]

### 2020-06-12 QRNN/random_split.py

@@ -31,7 +31,7 @@ y = xarray.open_dataset(os.path.expanduser('~/Dendrite/Projects/AWS-325GHz/TB_AW
 TB0 = y.TB
 cases = TB0.cases.values
 
-y = xarray.open_dataset(os.path.expanduser('~/Dendrite/Projects/AWS-325GHz/TB_AWS/TB_AWS_m60_p60_noise_four.nc'))
+y = xarray.open_dataset(os.path.expanduser('~/Dendrite/Projects/AWS-325GHz/TB_AWS/TB_AWS_m60_p60_noise_four_Trec1.nc'))
 TB = y.TB_noise
 
 ic = np.arange(0, len(cases), 1)
@@ -39,8 +39,8 @@ np.random.shuffle(ic)
 
 x_test0, x_test = get_TB(TB, TB0, ic, cases)
 
-x_test.to_netcdf(os.path.expanduser('~/Dendrite/Projects/AWS-325GHz/TB_AWS/testing_data_noise_four.nc'), 'w')
-x_test0.to_netcdf(os.path.expanduser('~/Dendrite/Projects/AWS-325GHz/TB_AWS/testing_data_four.nc'), 'w')
+x_test.to_netcdf(os.path.expanduser('~/Dendrite/Projects/AWS-325GHz/TB_AWS/testing_data_noise_four_Trec1.nc'), 'w')
+x_test0.to_netcdf(os.path.expanduser('~/Dendrite/Projects/AWS-325GHz/TB_AWS/testing_data_four_Trec1.nc'), 'w')
 
 
 #=====================================================================================================
@@ -50,13 +50,13 @@ x_test0.to_netcdf(os.path.expanduser('~/Dendrite/Projects/AWS-325GHz/TB_AWS/test
 y = xarray.open_dataset(os.path.expanduser('~/Dendrite/Projects/AWS-325GHz/TB_AWS/TB_AWS_m60_p60_three_a.nc'))
 TB0 = y.TB
 
-y = xarray.open_dataset(os.path.expanduser('~/Dendrite/Projects/AWS-325GHz/TB_AWS/TB_AWS_m60_p60_noise_three_a.nc'))
+y = xarray.open_dataset(os.path.expanduser('~/Dendrite/Projects/AWS-325GHz/TB_AWS/TB_AWS_m60_p60_noise_three_a_Trec1.nc'))
 TB = y.TB_noise
 
[…]

### 2020-06-12 Report/aws_325ghz_study.tex
added stats for T_rec = 1800, and T_rec = 2400

@@
 %
+
+\begin{table}[!p]
+	\centering
+	\begin{tabular}[b]{c|c|c|c|c}
+		Dataset  		  &   bias &   std & skewness & fraction \\
+		&   [K]  &   [K] & [-] & rejected [\%]\\
+		\hline
+		noise             		&   0.00 &  0.45 &               0.00 &                - \\
+		uncorrected       		&  -2.25 &  8.94 &              -6.85 &                 - \\
+		filtered($1\sigma$)  	&  -0.26 &  0.77 &             -16.33 &               72.06 \\
+		corrected($1\sigma$) 	&   0.43 &  1.70 &             -14.68 &                7.93 \\
+		corrected($2\sigma$) 	&   0.25 &  1.72 &             -13.86 &                7.93 \\
+		sreerekha et al   		&  -0.41 &  1.00 &              -2.54 &               45.36 \\
+		\hline
+	\end{tabular}
+	\caption{Same as Table~\ref{tab:correction:stats:34:42:thinned}, but for channel combination: AWS-32 and AWS-41.   }
+	\label{tab:correction:stats:32:41}
+\end{table}
+
+\begin{table}[!p]
+	\centering
+	\begin{tabular}[b]{c|c|c|c|c}
+		Dataset  		  &   bias &   std &  skewness  & fraction\\
+		&   [K]  &   [K] & [-]  & rejected [\%]\\
+		\hline
+		noise       	    	&  0.00 &  0.45 &               0.00 &               - \\
+		uncorrected	    		&  -1.74 &  7.45 &              -7.77 &                - \\
+		filtered($1\sigma$)  	&  -0.13 &  0.49 &              -0.40 &               26.18 \\
+		corrected($1\sigma$) 	&  -0.05 &  0.59 &              -0.85 &                6.88 \\
+		corrected($2\sigma$) 	&  -0.11 &  0.57 &              -1.17 &                6.88 \\
+		sreerekha et al   		&  -0.29 &  0.78 &              -2.22 &               45.36 \\
+		\hline
+	\end{tabular}
+	\caption{Same as Table~\ref{tab:correction:stats:34:42:thinned}, but for channel combination: AWS-33 and AWS-41.   }
+	\label{tab:correction:stats:33:41}
+\end{table}
+
+\begin{table}[!p]
+	\centering
+	\begin{tabular}[b]{c|c|c|c|c}
+		Dataset  		  &   bias &   std &   skewness & fraction \\
+		&   [K]  &   [K] & [-] & rejected [\%]\\
+		\hline
+		Noise           	  &  0.00 &  0.63 &               0.00 &                -\\
+		uncorrected     	  &  -0.83 &  4.50 &             -10.85 &                - \\
+		filtered($1\sigma$)	  &  -0.13 &  0.68 &              -0.46 &               21.30 \\
+		corrected($1\sigma$)  &   0.01 &  0.90 &              -1.65 &                2.86 \\
+		corrected($2\sigma$)  &  -0.09 &  0.83 &              -2.35 &                2.86 \\
+		sreerekha et al  	  &  -0.13 &  0.70 &              -0.54 &               45.36 \\
+		\hline
+	\end{tabular}
+	\caption{Same as Table~\ref{tab:correction:stats:34:42:thinned}, but for channel combination: AWS-35 and AWS-43.}
+	\label{tab:correction:stats:35:43}
+\end{table}
+
+\begin{table}[!p]
+	\centering
+	\begin{tabular}[b]{c|c|c|c|c}
+		Dataset  		  &   bias &   std &   skewness & fraction  \\
+		&   [K]  &   [K] & [-] & rejected [\%]\\
+		\hline
+		Noise            	 &  0.00 &  0.88 &              -0.01 &               - \\
+		uncorrected      	 &  -0.54 &  3.40 &             -12.26 &                - \\
+		filtered($1\sigma$)  &  -0.11 &  0.92 &              -0.13 &                7.38 \\
+		corrected($1\sigma$) &  -0.07 &  0.93 &              -0.07 &                2.50 \\
+		corrected($2\sigma$) &  -0.11 &  0.94 &              -0.19 &                2.50 \\
+		sreerekha et al 	 &  -0.09 &  0.91 &              -0.10 &               45.36 \\
+		\hline
+	\end{tabular}
+	\caption{Same as Table~\ref{tab:correction:stats:34:42:thinned}, but for channel combination: AWS-36 and AWS-43.   }
+	\label{tab:correction:stats:36:43}
+\end{table}
+
 The correction scheme can also be extended to other combinations of 183GHz and
@@
 
-\begin{table}[!p]
-	\centering
-	\begin{tabular}[b]{c|c|c|c|c}
-		Dataset  		  &   bias &   std & skewness & fraction \\
-							&   [K]  &   [K] & [-] & rejected [\%]\\
-		\hline
-noise             		&   0.00 &  0.45 &               0.00 &                - \\
-uncorrected       		&  -2.25 &  8.94 &              -6.85 &                 - \\
-filtered($1\sigma$)  	&  -0.26 &  0.77 &             -16.33 &               72.06 \\
-corrected($1\sigma$) 	&   0.43 &  1.70 &             -14.68 &                7.93 \\
-corrected($2\sigma$) 	&   0.25 &  1.72 &             -13.86 &                7.93 \\
-sreerekha et al   		&  -0.41 &  1.00 &              -2.54 &               45.36 \\
-\hline
-	\end{tabular}
-	\caption{Same as Table~\ref{tab:correction:stats:34:42:thinned}, but for channel combination: AWS-32 and AWS-41.   }
-	\label{tab:correction:stats:32:41}
-\end{table}
-
-\begin{table}[!p]
-	\centering
-	\begin{tabular}[b]{c|c|c|c|c}
-		Dataset  		  &   bias &   std &  skewness  & fraction\\
-						&   [K]  &   [K] & [-]  & rejected [\%]\\
-		\hline
-	noise       	    	&  0.00 &  0.45 &               0.00 &               - \\
-	uncorrected	    		&  -1.74 &  7.45 &              -7.77 &                - \\
-	filtered($1\sigma$)  	&  -0.13 &  0.49 &              -0.40 &               26.18 \\
-	corrected($1\sigma$) 	&  -0.05 &  0.59 &              -0.85 &                6.88 \\
-	corrected($2\sigma$) 	&  -0.11 &  0.57 &              -1.17 &                6.88 \\
-	sreerekha et al   		&  -0.29 &  0.78 &              -2.22 &               45.36 \\
-		\hline
-	\end{tabular}
-	\caption{Same as Table~\ref{tab:correction:stats:34:42:thinned}, but for channel combination: AWS-33 and AWS-41.   }
-	\label{tab:correction:stats:33:41}
-\end{table}
-
-\begin{table}[!p]
-	\centering
-	\begin{tabular}[b]{c|c|c|c|c}
-		Dataset  		  &   bias &   std &   skewness & fraction \\
-							&   [K]  &   [K] & [-] & rejected [\%]\\
-		\hline
- Noise           	  &  0.00 &  0.63 &               0.00 &                -\\
-uncorrected     	  &  -0.83 &  4.50 &             -10.85 &                - \\
-filtered($1\sigma$)	  &  -0.13 &  0.68 &              -0.46 &               21.30 \\
-corrected($1\sigma$)  &   0.01 &  0.90 &              -1.65 &                2.86 \\
-corrected($2\sigma$)  &  -0.09 &  0.83 &              -2.35 &                2.86 \\
-sreerekha et al  	  &  -0.13 &  0.70 &              -0.54 &               45.36 \\
-		\hline
-	\end{tabular}
-	\caption{Same as Table~\ref{tab:correction:stats:34:42:thinned}, but for channel combination: AWS-35 and AWS-43.}
-	\label{tab:correction:stats:35:43}
-\end{table}
-
-\begin{table}[!p]
-	\centering
-	\begin{tabular}[b]{c|c|c|c|c}
-		Dataset  		  &   bias &   std &   skewness & fraction  \\
-							&   [K]  &   [K] & [-] & rejected [\%]\\
-		\hline
- Noise            	 &  0.00 &  0.88 &              -0.01 &               - \\
-uncorrected      	 &  -0.54 &  3.40 &             -12.26 &                - \\
-filtered($1\sigma$)  &  -0.11 &  0.92 &              -0.13 &                7.38 \\
-corrected($1\sigma$) &  -0.07 &  0.93 &              -0.07 &                2.50 \\
-corrected($2\sigma$) &  -0.11 &  0.94 &              -0.19 &                2.50 \\
-sreerekha et al 	 &  -0.09 &  0.91 &              -0.10 &               45.36 \\
-		\hline
-	\end{tabular}
-	\caption{Same as Table~\ref{tab:correction:stats:34:42:thinned}, but for channel combination: AWS-36 and AWS-43.   }
-	\label{tab:correction:stats:36:43}
-\end{table}
-
 \section{Cloud correction by QRNN}
@@
 %  
+\begin{figure}[!ht]
+	\centering
+	\includegraphics[height=85mm]{quantile_loss.png}
+	\caption{The mean quantile loss for $\tau = 0.5$ with different configurations of layer width and hidden layers ($n_h$).}
+	\label{fig:quantile_loss}
+\end{figure}
 In this section, QRNNs are used to correct the cloud impact in each of 183\,GHz channels using TBs from all available channels of 325\,GHz.
@@
 %
-\begin{figure}[!ht]
-	\centering
-	\includegraphics[height=85mm]{quantile_loss.png}
-	\caption{The mean quantile loss for $\tau = 0.5$ with different configurations of layer width and hidden layers ($n_h$).}
-	\label{fig:quantile_loss}
-\end{figure}
+
 %
@@
 %
+\begin{figure}[!p]
+	\centering
+	\includegraphics[height=60mm]{distribution_predicted_C32}\hspace{5mm}% 
+	\includegraphics[height=60mm]{distribution_predicted_C33}
+	\includegraphics[height=60mm]{distribution_predicted_C34}\hspace{5mm}% 
+	\includegraphics[height=60mm]{distribution_predicted_C35}
+	\includegraphics[height=60mm]{distribution_predicted_C36}
+	\caption{ Probability distribution functions (PDFs) of predicted and observed noise free brightness temperatures for all 183\,GHz channels of AWS.  }
+	\label{fig:pdf:qrnn}
+\end{figure}
 We train the QRNN to predict the quantiles $x_{\tau}$, for median, $\pm 1\sigma$, $\pm 2 \sigma$ and  $\pm 3 \sigma$ ($\tau$ = 0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998).
@@
 
+In an analogy between the results from the simple correction scheme and QRNN, we perform a similar error distribution analysis as in Section~\ref{sec:}.
 Figure~\ref{fig:qrnn_C34:deviations} shows the error distributions of the measurements and predicted clear-sky TBs for AWS-34 using three (three-b) and four channel options of 325\,GHz.
@@
 The fraction of cases rejected as "too-cloudy" is also provided under ``fraction rejected''.
-For AWS-34, the predictions from all three QRNN models are comparable.
-
-\begin{figure}[!tb]
-	\centering
-	\includegraphics[height=60mm]{distribution_predicted_C32}\hspace{5mm}% 
-	\includegraphics[height=60mm]{distribution_predicted_C33}
-	\includegraphics[height=60mm]{distribution_predicted_C34}\hspace{5mm}% 
-	\includegraphics[height=60mm]{distribution_predicted_C35}
-	\includegraphics[height=60mm]{distribution_predicted_C36}
-	\caption{ Probability distribution functions (PDFs) of predicted and observed noise free brightness temperatures for all 183\,GHz channels of AWS.  }
-	\label{fig:pdf:qrnn}
-\end{figure}
+For AWS-34, average deviation in the predictions from all three QRNN models are comparable.
+The cloud impact in the uncorrected measurements is reflected in the high negative skewness (-10.32), however with QRNN the skewness is largely reduced and the symmetry in the distributions is reflected in the low skewness values.
+Among the three set of predictions, option three-b has the most symmetric error distribution but with a relatively large spread.
+Predictions from option four have the lowest standard deviation (0.620\,K), which is interestingly smaller than the standard deviation of noise (0.641\,K).
+Though, all three options of 325\,GHz provide a full coverage to the hydrometer impact in AWS-34, predictions from four channel option are slightly more accurate.
+
+Similar error statistics are also estimated for other 183\,GHz channels.
+Table~\ref{tab:qrnn:C32} provides the statistics for AWS-32.
+Before correction, the average bias and standard deviation with respect to noise free simulations is -1.343\,K and 5.908\,K respectively.
+However, after correction(four channel), the bias and standard deviation are -0.011\,K and 0.878\,K.
+The skewness in the error distributions is also reduced in the predictions (from -7.48 to -3.03).
+But a relatively high negative skewness in the predicted dataset indicates presence of uncorrected cloud impact.
+
+Table~\ref{tab:qrnn:C33} shows the statistics for AWS-33.
+The standard deviation in the four channel option (0.591\,K) is slighly lower than three-b(0.612\,K), but the skewness in three-b in lower.
+This indicates that with four channel option, the QRNN predictions are mostly closer to the simulations, but few cases with large cloud impact are under predicted.
+
+For AWS-35 (Table~\ref{tab:qrnn:C35}), the four channel option has the best performance.
+The average bias in QRNN predictions (four) is only 0.04\,K in comparsion to -0.42\,K for the measurements.
+Option three-b has lower skewness than option four, but the standard deviation is higher.
+It is interesting to note that the standard deviation in all three predicted datasets is always lower than noise.
+Similar results are also seen for AWS-36 (Table~\ref{tab:qrnn:C36}).
+The four channel combination reduces the average bias from -0.269\,K to 0.056\,K and the standard deviation from 2.059\,K to 0.779\,K.
+Also for this channel, the spread of the predictions is narrower than noise.
 
@@
 corrected (four)   			&  0.111 & 0.620 &             -0.659 &      2.985 \\
-
 		\hline
@@
 corrected (four)    		& -0.011 & 0.878 &             -3.030 &      4.930 \\
-
 		\hline
@@
 %
+
 \begin{figure}[!ht]
@@
 	\includegraphics[height=85mm]{prediction_uncertainty.png}
-	\caption{The prediction uncertainty with respect to quantiles for randomly selected 2400 cases.}
+	\caption{The prediction uncertainty in AWS-34 with respect to quantiles for randomly selected 2400 cases.
+The red line represents the uncertainty if underlying distribution is purely Gaussian with standard deviation 0.62\,K.
+}
 	\label{fig:prediction_uncertainty}
@@
 
+\section{Sensitivity to different receiver noise temperatures}
+
+\subsection{T rec = 1800}
+%
+\begin{table}[!tb]
+	\centering
+	\begin{tabular}[b]{c|c|c|c|c}
+		Dataset  		  &   bias &   std &   skewness & fraction  \\
+		&   [K]  &   [K] & [-] & rejected [\%]\\
+		\hline
+	Noise                      & -0.001 & 0.451 &              0.020 &      0.000 \\
+	uncorrected                & -1.342 & 5.908 &             -7.479 &      0.000 \\
+	corrected (three channela) & -0.009 & 0.893 &             -3.092 &      4.990 \\
+    corrected (three channelb) &  0.009 & 0.888 &             -3.197 &      4.902 \\	
+	corrected (four channel)   &  0.006 & 0.860 &             -2.943 &      4.954 \\
+		\hline
+	\end{tabular}
+	\caption{ AWS-32 , Trec = 1800}
+	\label{tab:qrnn:C36}
+\end{table}
+
+\begin{table}[!tb]
+	\centering
+	\begin{tabular}[b]{c|c|c|c|c}
+		Dataset  		  &   bias &   std &   skewness & fraction  \\
+		&   [K]  &   [K] & [-] & rejected [\%]\\
+		\hline
+	Noise                      & -0.001 & 0.452 &              0.015 &      0.000 \\
+	uncorrected                & -0.975 & 4.703 &             -8.763 &      0.000 \\
+	corrected (three channela) &  0.085 & 0.587 &             -0.640 &      4.209 \\
+	corrected (three channelb) &  0.062 & 0.605 &             -0.845 &      4.205 \\
+	corrected (four channel)   &  0.048 & 0.606 &             -1.112 &      4.264 \\
+		\hline
+	\end{tabular}
+	\caption{ AWS-33, Trec = 1800 }
+	\label{tab:qrnn:C36}
+\end{table}
+
+\begin{table}[!tb]
+	\centering
+	\begin{tabular}[b]{c|c|c|c|c}
+		Dataset  		  &   bias &   std &   skewness & fraction  \\
+		&   [K]  &   [K] & [-] & rejected [\%]\\
+		\hline
+	Noise                      &  0.001 & 0.632 &              0.021 &      0.000 \\
+	uncorrected                & -0.676 & 3.686 &            -10.301 &      0.000 \\
+	corrected (three channela) &  0.079 & 0.646 &             -0.344 &      2.730 \\
+    corrected (three channelb) &  0.090 & 0.639 &             -0.405 &      2.582 \\
+	corrected (four channel)   &  0.079 & 0.630 &             -0.399 &      2.981 \\
+		\hline
+	\end{tabular}
+	\caption{ AWS-34, Trec = 1800 }
+	\label{tab:qrnn:C36}
+\end{table}
+
+\begin{table}[!tb]
+	\centering
+	\begin{tabular}[b]{c|c|c|c|c}
+		Dataset  		  &   bias &   std &   skewness & fraction  \\
+		&   [K]  &   [K] & [-] & rejected [\%]\\
+		\hline
+Noise                       &  0.001 & 0.629 &              0.007 &      0.000 \\
+uncorrected                 & -0.417 & 2.654 &            -12.446 &      0.000 \\
+corrected (three channela)  &  0.045 & 0.636 &             -0.188 &      1.431 \\
+corrected (three channelb)  &  0.081 & 0.640 &             -0.458 &      1.299 \\
+corrected (four channel)    &  0.058 & 0.617 &             -0.007 &      1.801 \\
+		\hline
+	\end{tabular}
+	\caption{ AWS-35, Trec = 1800 }
+	\label{tab:qrnn:C36}
+\end{table}
+
+\begin{table}[!tb]
+	\centering
+	\begin{tabular}[b]{c|c|c|c|c}
+		Dataset  		  &   bias &   std &   skewness & fraction  \\
+		&   [K]  &   [K] & [-] & rejected [\%]\\
+		\hline
+Noise                      &  0.002 & 0.882 &             -0.006 &      0.000 \\
+uncorrected                & -0.268 & 2.063 &            -12.003 &      0.000 \\
+corrected (three channela) &  0.075 & 0.831 &             -0.130 &      1.283 \\
+corrected (three channelb) &  0.105 & 0.807 &             -0.080 &      1.136 \\
+corrected (four channel)   &  0.093 & 0.826 &             -0.175 &      1.120 \\
+		\hline
+	\end{tabular}
+	\caption{ AWS-36, Trec = 1800 }
+	\label{tab:qrnn:C36}
+\end{table}
+
+\subsection{T rec = 2400}
+%
+\begin{table}[!tb]
+	\centering
+	\begin{tabular}[b]{c|c|c|c|c}
+		Dataset  		  &   bias &   std &   skewness & fraction  \\
+		&   [K]  &   [K] & [-] & rejected [\%]\\
+		\hline
+Noise                       &  0.002 & 0.454 &              0.003 &      0.000 \\
+uncorrected                 & -1.343 & 5.907 &             -7.483 &      0.000 \\
+corrected (three channela)  & -0.017 & 0.877 &             -3.381 &      4.934 \\
+corrected (three channelb)  & -0.015 & 0.882 &             -3.177 &      4.974 \\
+corrected (four channel)    &  0.028 & 0.876 &             -3.638 &      4.978 \\
+		\hline
+	\end{tabular}
+	\caption{ AWS-32, Trec = 2400 }
+	\label{tab:qrnn:C36}
+\end{table}
+
+\begin{table}[!tb]
+	\centering
+	\begin{tabular}[b]{c|c|c|c|c}
+		Dataset  		  &   bias &   std &   skewness & fraction  \\
+		&   [K]  &   [K] & [-] & rejected [\%]\\
+		\hline
+ Noise                     & -0.003 & 0.448 &              0.005 &      0.000 \\
+uncorrected                & -0.979 & 4.709 &             -8.762 &      0.000 \\
+corrected (three channela) &  0.057 & 0.628 &             -0.728 &      4.232 \\
+corrected (three channelb) &  0.040 & 0.614 &             -0.786 &      4.205 \\
+corrected (four channel)   &  0.043 & 0.614 &             -0.798 &      4.232 \\
+		\hline
+	\end{tabular}
+	\caption{ AWS-33, Trec = 2400  }
+	\label{tab:qrnn:C36}
+\end{table}
+
+\begin{table}[!tb]
+	\centering
+	\begin{tabular}[b]{c|c|c|c|c}
+		Dataset  		  &   bias &   std &   skewness & fraction  \\
+		&   [K]  &   [K] & [-] & rejected [\%]\\
+		\hline
+ Noise                      & -0.001 & 0.638 &              0.006 &      0.000 \\
+uncorrected                 & -0.676 & 3.688 &            -10.299 &      0.000 \\
+ corrected (three channela) &  0.069 & 0.655 &             -0.396 &      2.666 \\
+corrected (three channelb)  &  0.090 & 0.648 &             -0.310 &      2.594 \\
+corrected (four channel)    &  0.059 & 0.643 &             -0.340 &      2.937 \\
+		\hline
+	\end{tabular}
+	\caption{ AWS-34, Trec = 2400 }
+	\label{tab:qrnn:C36}
+\end{table}
+
+\begin{table}[!tb]
+	\centering
+	\begin{tabular}[b]{c|c|c|c|c}
+		Dataset  		  &   bias &   std &   skewness & fraction  \\
+		&   [K]  &   [K] & [-] & rejected [\%]\\
+		\hline
+Noise                      & -0.004 & 0.633 &              0.021 &      0.000 \\
+uncorrected                & -0.420 & 2.654 &            -12.449 &      0.000 \\
+corrected (three channela) &  0.034 & 0.646 &             -0.389 &      1.479 \\
+corrected (three channelb) &  0.076 & 0.647 &             -0.148 &      1.291 \\
+corrected (four channel)   &  0.044 & 0.632 &             -0.188 &      1.809 \\
+		\hline
+	\end{tabular}
+	\caption{ AWS-35, Trec = 2400}
+	\label{tab:qrnn:C36}
+\end{table}
+
+\begin{table}[!tb]
+	\centering
+	\begin{tabular}[b]{c|c|c|c|c}
+		Dataset  		  &   bias &   std &   skewness & fraction  \\
+		&   [K]  &   [K] & [-] & rejected [\%]\\
+		\hline
+Noise                      &  0.005 & 0.884 &             -0.026 &      0.000 \\
+uncorrected                & -0.268 & 2.057 &            -11.977 &      0.000 \\
+corrected (three channela) &  0.039 & 0.854 &             -0.131 &      1.283 \\
+corrected (three channelb) &  0.090 & 0.839 &             -0.096 &      1.108 \\
+corrected (four channel)   &  0.059 & 0.850 &             -0.140 &      1.140 \\
+		\hline
+	\end{tabular}
+	\caption{ AWS-36, Trec = 2400 }
+	\label{tab:qrnn:C36}
+\end{table}
+
 \section{Discussion}
@@
 \subsection{229 vs.\ 325\,GHz}
-
 \subsubsection{Altitude coverage}
@@
 
+\subsection{Performance of QRNN}
+%
+\dots
+
 \subsection{Technical implementation}

### 2020-06-15 Report/aws_325ghz_study.tex
added AWS-4X, and some new text

@@
 Table~\ref{tab:fixed:chs}. The integration time is set to match an effective
-15\,km resolution at 183\,GHz. This time was estimated to 3\,ms.
+10\,km resolution at 183\,GHz. This time was estimated to 3\,ms.
 
@@
   \caption{RH weighting functions of the three channel option in
-    Table~\ref{tab:chs:prel}, for the Fascod tropical (left) and mid-latitude
+    Table~\ref{tab:chs:prel3}, for the Fascod tropical (left) and mid-latitude
     winter (right) scenarios.}
@@
   \caption{RH weighting functions of the four channel option in
-    Table~\ref{tab:chs:prel}, for the Fascod tropical (left) and mid-latitude
+    Table~\ref{tab:chs:prel4}, for the Fascod tropical (left) and mid-latitude
     winter (right) scenarios.}
@@
 channel option an even better matching was used as constrain to set the
-specifications. The resulting values are found in Table~\ref{tab:chs:prel} and
+specifications. The resulting values are found in Table~\ref{tab:chs:prel3} and
 example weighting functions are displayed in Fig.~\ref {fig:3ch:prel}. This
@@
 \begin{table}[!t]
-  \begin{minipage}[b]{0.5\linewidth}
-  \centering  
-  \begin{tabular}[c]{c|c|c}
-    Channel & Frequency   & Bandwidth \\
-    name    & [GHz] &  [MHz] \\
-    \hline
-    AWS-41  & 325.15$\pm$6.50 & 3000\\
-    AWS-42  & 325.15$\pm$3.55 & 2500\\
-    AWS-43  & 325.15$\pm$1.60 & 1200\\
-    \hline
-  \end{tabular}
-  \end{minipage}%
-  \begin{minipage}[b]{0.5\linewidth}
-  \centering  
-  \begin{tabular}[c]{c|c|c}
-    Channel & Frequency   & Bandwidth \\
-    name    & [GHz] &  [MHz] \\
-    \hline
-    AWS-41  & 325.15$\pm$6.60 & 2800\\
-    AWS-42  & 325.15$\pm$4.10 & 1800\\
-    AWS-43  & 325.15$\pm$2.40 & 1200\\
-    AWS-44  & 325.15$\pm$1.20 & \phantom{0}800\\
-    \hline
-  \end{tabular}
-%  \begin{tabular}[c]{c|c|c}
-%    Channel & Frequency   & Bandwidth \\
-%    name    & [GHz] &  [MHz] \\
-%    \hline
-%    AWS-41  & 325.15$\pm$6.60 & 2800\\
-%    AWS-42  & 325.15$\pm$4.05 & 1900\\
-%    AWS-43  & 325.15$\pm$2.35 & 1300\\
-%    AWS-44  & 325.15$\pm$1.20 & \phantom{0}800\\
-%    \hline
-%  \end{tabular}
-  \end{minipage}  
-  \caption{Preliminary specifications of AWS 325\,GHz channels, in the case of
-    of three (left) and four (right) channels.}
-  \label{tab:chs:prel}
+  \centering  
+  \begin{tabular}[c]{c|c|c|ccc}
+    Channel & Frequency   & Bandwidth & $T_r=1200$\,K
+    & $T_r=1800$\,K & $T_r=2400$\,K\\
+    name    & [GHz] &  [MHz] & [K]  & [K] & [K]\\
+    \hline
+    AWS-41  & 325.15$\pm$6.50 & 3000 & 0.58 & 0.82 & 1.06 \\
+    AWS-42  & 325.15$\pm$3.55 & 2500 & 0.64 & 0.90 & 1.16 \\
+    AWS-43  & 325.15$\pm$1.60 & 1200 & 0.92 & 1.30 & 1.68 \\
+    \hline
+  \end{tabular}
+  \caption{Tentative suggestion for a three 325\,GHz channels option. The
+    values in the three last columns is the 1$\sigma$ noise level according to
+    Eq.~\ref{eq:noise}, for $T_a=300$\,K and  $T_r$ }
+  \label{tab:chs:prel3}
+\end{table}
+
+\begin{table}[!t]
+  \centering  
+  \begin{tabular}[c]{c|c|c|ccc}
+    Channel & Frequency   & Bandwidth & $T_r=1200$\,K
+    & $T_r=1800$\,K & $T_r=2400$\,K\\
+    name    & [GHz] &  [MHz] & [K]  & [K] & [K]\\
+    \hline
+    AWS-41  & 325.15$\pm$6.60 & 2800 & 0.60 & 0.85 & 1.10 \\
+    AWS-42  & 325.15$\pm$4.10 & 1800 & 0.75 & 1.06 & 1.37 \\
+    AWS-43  & 325.15$\pm$2.40 & 1200 & 0.92 & 1.30 & 1.68 \\
+    AWS-44  & 325.15$\pm$1.20 & \phantom{0}800 & 1.12 & 1.59 & 2.06\\
+    \hline
+  \end{tabular}
+  \caption{Tentative suggestion for a four 325\,GHz channels option. Else as
+    Table~\ref{tab:chs:prel4}.}
+  \label{tab:chs:prel4}
 \end{table}
@@
 %
-The tentative four channel option in Table~\ref{tab:chs:prel} gives a broader
+The tentative four channel option in Table~\ref{tab:chs:prel4} gives a broader
 altitude coverage, towards higher altitudes, and offers weighting functions
@@
   \centering  
-  \begin{tabular}[c]{c|c|c}
-    Channel & Frequency   & Bandwidth \\
-    name    & [GHz] &  [MHz] \\
-    \hline
-    AWS-41  & 325.15$\pm$6.50 & 3000\\
-    AWS-42  & 325.15$\pm$3.30 & 3000\\
-    AWS-43  & 325.15$\pm$1.20 & \phantom{0}800\\
+  \begin{tabular}[c]{c|c|c|ccc}
+    Channel & Frequency   & Bandwidth & $T_r=1200$\,K
+    & $T_r=1800$\,K & $T_r=2400$\,K\\
+    name    & [GHz] &  [MHz] & [K]  & [K] & [K]\\
+    \hline
+    AWS-41  & 325.15$\pm$6.50 & 3000  & 0.58 & 0.82 & 1.06\\
+    AWS-42  & 325.15$\pm$3.30 & 3000  & 0.58 & 0.82 & 1.06\\
+    AWS-43  & 325.15$\pm$1.20 & \phantom{0}800 & 1.12 & 1.59 & 2.06\\
     \hline
@@
 %  
+\label{sec:qrnn:training}
 \begin{figure}[!ht]
@@
 
-\begin{table}[!tb]
+\begin{table}[!p]
 	\centering
@@
 %
-
-\begin{figure}[!ht]
-	\centering
-	\includegraphics[height=85mm]{prediction_uncertainty.png}
+Quantile regression can be used to construct a probability distribution of the predictions in comparison to simple regression models, which predict only a point estimate of the target.
+The outputs from QRNN model are subject to uncertainty which can be modeled by the prediction intervals.
+
+In our QRNN model, we estimate the conditional quantiles for  median, $\pm 1\sigma$, $\pm 2\sigma$, and $\pm 3\sigma$.
+The predictions for each quantile are used to construct the confidence intervals.
+The confidence interval for each point estimate is a way to quantify its uncertainty.
+For example, the predicted quantiles for $\pm 1 \sigma$ give 68\% probability that the true value will lie between the range.
+
+If the posterior distribution from QRNN follow normal distribution, the uncertainty can be estimated as a gaussian distribution centered around the median and standard deviation equal to the estimated error.
+To inspect if the predictions follow a normal distribution we evaluate the length of confidence intervals with respect to the median.
+Figure~\ref{fig:prediction_uncertainty} shows the prediction uncertainty in AWS-34 (using four channel option).
+The uncertainty with respect to the median for 1000 randomly selected cases is shown.
+The red line represents the uncertainty in a hypothetical Gaussian distribution  of $270\pm0.62$\,K.
+If the underlying distribution is Gaussian, the prediction uncertainty should be symmetric around the median, and the uncertainties should be equally spaced for $1\sigma$, $2\sigma$ and so on.
+The predictions from our QRNN model seem to be symmetric around the median for the 95\% confidence interval ($\pm 2 \sigma$).
+In other words, around 95\% of the true cases lie in the confidence interval given by $\pm 2\sigma$, and only 6\% of predictions are either too low or too high than the true value.
+
+A similar uncertainty quantification for other 183\,GHz channels also gives similar results.
+Thus, assuming the posterior distribution to be gaussian between $\pm 2 \sigma$, the median is the measure of mean of the gaussian distribution, and the estimated error with respect to the true-value gives the spread of the distribution.
+\begin{figure}[!tb]
+	\centering
+	\includegraphics[height=80mm]{prediction_uncertainty.png}
 	\caption{The prediction uncertainty in AWS-34 with respect to quantiles for randomly selected 2400 cases.
@@
 
+\subsection{QRNN using AWS-4X}
+%
+\begin{figure}[!tb]
+	\centering
+	\includegraphics[height=80mm]{Channel_C32_C4X.png}
+	\caption{ }
+	\label{fig:qrnn_C32_C4X:deviations}
+\end{figure}
+
+\begin{table}[!tb]
+	\centering
+	\begin{tabular}[b]{c|c|c|c|c}
+		Dataset  		  &   bias &   std &   skewness & fraction  \\
+		&   [K]  &   [K] & [-] & rejected [\%]\\
+		\hline
+		Noise                      & -0.001 & 0.451 &              0.020 &      - \\
+		uncorrected                & -1.343 & 5.908 &             -7.484 &      - \\
+		corrected (AWS-4X)         &  0.008 & 1.514 &             -4.085 &      3.678 \\
+		corrected (four channel)   & -0.011 & 0.878 &             -3.030 &      4.930 \\
+		\hline
+	\end{tabular}
+	\caption{ AWS-32 with AWS-4X}
+	\label{tab:qrnn:C32:C4X}
+\end{table} 
+We also tested the QRNN model to predict cloud-free TBs using AWS-4X.
+In this case, we trained QRNN with measurements from AWS-32 and AWS-4X, to predict the clear-sky cloud free TBs for AWS-32.
+The model was trained as described in Section~\ref{sec:qrnn:training}, but the width of the network was chosen to be 256 neurons.
+Other structural and training parameters remain unchanged.
+
+Figure~\ref{fig:qrnn_C32_C4X:deviations} shows the error distributions for the differences between the predicted values and clear-sky simulations for AWS-32.
+The corresponding statistics are shown in Table~\ref{tab:qrnn:C32:C4X}.
+The results from QRNN model trained with four channel option of 325\,GHz are also shown for comparison.
+
 \section{Sensitivity to different receiver noise temperatures}
 
-\subsection{T rec = 1800}
-%
-\begin{table}[!tb]
-	\centering
-	\begin{tabular}[b]{c|c|c|c|c}
-		Dataset  		  &   bias &   std &   skewness & fraction  \\
-		&   [K]  &   [K] & [-] & rejected [\%]\\
-		\hline
-	Noise                      & -0.001 & 0.451 &              0.020 &      0.000 \\
-	uncorrected                & -1.342 & 5.908 &             -7.479 &      0.000 \\
+%
+\begin{table}[!p]
+	\centering
+	\begin{tabular}[b]{c|c|c|c|c}
+		Dataset  		  &   bias &   std &   skewness & fraction  \\
+		&   [K]  &   [K] & [-] & rejected [\%]\\
+		\hline
+	Noise                      & -0.001 & 0.451 &              0.020 &      - \\
+	uncorrected                & -1.342 & 5.908 &             -7.479 &      - \\
 	corrected (three channela) & -0.009 & 0.893 &             -3.092 &      4.990 \\
@@
 
-\subsection{T rec = 2400}
-%
-\begin{table}[!tb]
+%
+\begin{table}[!p]
 	\centering

### 2020-06-16 Report/aws_325ghz_study.tex
added text for AWS-4X and T_r & some polishing

@@
 \section{Preliminary options for 325\,GHz channels}
+
+\label{sec:channel:configurations}
 
@@
 \label{sec:qrnn:training}
-\begin{figure}[!ht]
+\begin{figure}[!tb]
 	\centering
 	\includegraphics[height=85mm]{quantile_loss.png}
-	\caption{The mean quantile loss for $\tau = 0.5$ with different configurations of layer width and hidden layers ($n_h$).}
+	\caption{The mean quantile loss with different configurations of layer width and hidden layers ($n_h$).}
 	\label{fig:quantile_loss}
@@
 A separate QRNN is used for each of the 183\,GHz channels.
-For example, to predict clear-sky TBs from AWS-34, the training data is TBs from all channels of 325\,GHz.
+For example, to predict clear-sky TBs from AWS-34, the training data is measurements from all channels of 325\,GHz and measurements from the 183\,GHz to be predicted.
 We assess the performance of the scheme using both three channel and four channel options of 325\,GHz.
-Two configurations for three channel option are described in Sec.~\ref{sec:}, and both have been used to train QRNN separately.
+Two suggestions for three channel option are described in Sec.~\ref{sec:channel:configurations}, and both have been used to train QRNN separately.
 Thus, for each channel of 183\,GHz, we have a set of three predictions: one from four channel option, and two from the old and new configurations of the three channel option.
@@
 Out of 125\,000 simulations, 90\% are used to train the model, while the rest 10\% is used to evaluate the model's performance during training.
+Presently we train QRNN for only nadir sensor viewing angle and the receiver noise $T_r$ = 1200\,K.
 In the training process, noise is added to the input according to Eqn~\ref{eq:noise}, every time the training data is exposed to the model.
@@
 We performed a grid search to determine structural parameters: depth (number of hidden layers) and width (number of neurons).
-The mean quantile loss is used to compare the performance of different hyper-parameter configurations.
+The quantile loss on the validation set averaged over all predicted quantiles is used to compare the performance of different hyper-parameter configurations.
 Figure~\ref{fig:quantile_loss} shows the mean quantile loss when QRNN is trained for predicting clear-sky values for AWS-34 using four channel option.
@@
 We chose the three training schedules with initial learning rates = 0.01, 0.001, 0.0001 respectively, updated after 20 epochs.
-The batch size was set to 256 samples.
 
 The grid search was also conducted for both three channel options, and an identical QRNN structure, as described for the four channel option, was found to have the best performance.
-%
-
+For QRNN models presented here, we did not optimize the type of activation function and batch size.
+Rectified Linear Unit (ReLU) was used as the activation function  and the batch size was set to 256 samples for all QRNN models.
 %
@@
 \end{figure}
+\begin{figure}[!p]
+	\centering
+	\includegraphics[height=85mm]{Channel_C34.png}
+	\caption{Deviation of AWS-34 measurements to noise free clear-sky
+		simulations before and after correction with QRNNs. Predictions from three channel (three-b) and four channel options for 325 GHz are shown. }
+	\label{fig:qrnn_C34:deviations}
+\end{figure}
+
+\begin{table}[!p]
+	\centering
+	\begin{tabular}[b]{c|c|c|c|c}
+		Dataset  		  &   bias &   std &   skewness & fraction  \\
+		&   [K]  &   [K] & [-] & rejected [\%]\\
+		\hline
+		Noise                       &  0.003 & 0.641 &             -0.001 &      - \\
+		uncorrected                 & -0.677 & 3.673 &            -10.321 &      - \\
+		corrected (three-a) 		&  0.094 & 0.624 &             -0.629 &      2.750 \\
+		corrected (three-b) 		&  0.100 & 0.652 &             -0.543 &      2.582 \\
+		corrected (four)   			&  0.111 & 0.620 &             -0.659 &      2.985 \\
+		\hline
+	\end{tabular}
+	\caption{ Bias, standard deviation and measure of skewness for the error distributions of the dataset (AWS-34) shown in Figure~\ref{fig:qrnn_C34:deviations}.
+The labels "three-a", "three-b" correspond to the old and new suggestions of three channels options of 325\,GHz, and the label "four" represents the four channels option.}
+	\label{tab:qrnn:C34}
+\end{table}
+
+\begin{table}[!p]
+	\centering
+	\begin{tabular}[b]{c|c|c|c|c}
+		Dataset  		  &   bias &   std &   skewness & fraction  \\
+		&   [K]  &   [K] & [-] & rejected [\%]\\
+		\hline
+		Noise                       & -0.004 & 0.450 &             -0.030 &      - \\
+		uncorrected                 & -1.343 & 5.908 &             -7.484 &      - \\
+		corrected (three-a)  		&  0.019 & 0.889 &             -3.519 &      4.906 \\	 
+		corrected (three-b)  		& -0.008 & 0.850 &             -3.326 &      4.926 \\			
+		corrected (four)    		& -0.011 & 0.878 &             -3.030 &      4.930 \\
+		\hline
+	\end{tabular}
+	\caption{ Same as Table~\ref{tab:qrnn:C34}, but for channel AWS-32.}
+	\label{tab:qrnn:C32}
+\end{table}
+
+\begin{table}[!p]
+	\centering
+	\begin{tabular}[b]{c|c|c|c|c}
+		Dataset  		  &   bias &   std &   skewness & fraction  \\
+		&   [K]  &   [K] & [-] & rejected [\%]\\
+		\hline
+		Noise                       & -0.005 & 0.450 &             -0.004 &      - \\
+		uncorrected                 & -0.982 & 4.703 &             -8.778 &      - \\
+		corrected (three-a) 		&  0.088 & 0.583 &             -0.959 &      4.197 \\
+		corrected (three-b)  		& -0.030 & 0.612 &             -0.756 &      4.205 \\
+		corrected (four)            &  0.106 & 0.591 &             -1.006 &      4.212 \\
+		\hline
+
+	\end{tabular}
+	\caption{ Same as Table~\ref{tab:qrnn:C34}, but for channel AWS-33.}
+	\label{tab:qrnn:C33}
+\end{table}
+
+\begin{table}[!p]
+	\centering
+	\begin{tabular}[b]{c|c|c|c|c}
+		Dataset  		  &   bias &   std &   skewness & fraction  \\
+		&   [K]  &   [K] & [-] & rejected [\%]\\
+		\hline
+
+		Noise                      &  0.003 & 0.626 &             -0.009 &      - \\
+		uncorrected                & -0.428 & 2.653 &            -12.492 &      - \\
+		corrected (three-a) 	   &  0.060 & 0.610 &             -0.281 &      1.439 \\
+		corrected (three-b) 	   &  0.097 & 0.618 &              0.011 &      1.331 \\
+		corrected (four)   		   &  0.042 & 0.591 &             -0.351 &      1.821 \\
+		\hline
+	\end{tabular}
+	\caption{ Same as Table~\ref{tab:qrnn:C34}, but for channel AWS-35.}
+	\label{tab:qrnn:C35}
+\end{table}
+
+\begin{table}[!p]
+	\centering
+	\begin{tabular}[b]{c|c|c|c|c}
+		Dataset  		  &   bias &   std &   skewness & fraction  \\
+		&   [K]  &   [K] & [-] & rejected [\%]\\
+		\hline
+		Noise                       &  0.000 & 0.888  &              0.005 &      - \\
+		uncorrected                 & -0.269 & 2.059 &            -11.899 &      - \\
+		corrected (three-a) 		&  0.062 & 0.797 &             -0.139 &      1.279 \\
+		corrected (three-b) 		&  0.092 & 0.770 &             -0.075 &      1.124 \\
+		corrected (four)   			&  0.056 & 0.779 &             -0.172 &      1.156 \\
+
+		\hline
+	\end{tabular}
+	\caption{ Same as Table~\ref{tab:qrnn:C34}, but for channel AWS-36.}
+	\label{tab:qrnn:C36}
+\end{table}
+
 We train the QRNN to predict the quantiles $x_{\tau}$, for median, $\pm 1\sigma$, $\pm 2 \sigma$ and  $\pm 3 \sigma$ ($\tau$ = 0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998).
@@
 
-In an analogy between the results from the simple correction scheme and QRNN, we perform a similar error distribution analysis as in Section~\ref{sec:}.
+In an analogy between the results from the simple correction scheme and QRNN, we perform a similar error distribution analysis as in Section~\ref{sec:simple}.
 Figure~\ref{fig:qrnn_C34:deviations} shows the error distributions of the measurements and predicted clear-sky TBs for AWS-34 using three (three-b) and four channel options of 325\,GHz.
@@
 
+\subsection{Uncertainty estimation}
+%
 \begin{figure}[!tb]
 	\centering
-	\includegraphics[height=85mm]{Channel_C34.png}
-	\caption{Deviation of AWS-34 measurements to noise free clear-sky
-		simulations before and after correction with QRNNs. Predictions from both three channel and four channel options for 325 GHz are shown. }
-	\label{fig:qrnn_C34:deviations}
-\end{figure}
-
-\begin{table}[!p]
-	\centering
-	\begin{tabular}[b]{c|c|c|c|c}
-	Dataset  		  &   bias &   std &   skewness & fraction  \\
-	&   [K]  &   [K] & [-] & rejected [\%]\\
-		\hline
-Noise                       &  0.003 & 0.641 &             -0.001 &      - \\
-uncorrected                 & -0.677 & 3.673 &            -10.321 &      - \\
-corrected (three-a) 		&  0.094 & 0.624 &             -0.629 &      2.750 \\
-corrected (three-b) 		&  0.100 & 0.652 &             -0.543 &      2.582 \\
-corrected (four)   			&  0.111 & 0.620 &             -0.659 &      2.985 \\
-		\hline
-	\end{tabular}
-	\caption{ Bias, standard deviation and measure of skewness for the error distributions of the dataset (AWS-34) shown in Figure~\ref{fig:qrnn_C34:deviations}}
-	\label{tab:qrnn:C34}
-\end{table}
-
-\begin{table}[!p]
-	\centering
-	\begin{tabular}[b]{c|c|c|c|c}
-	Dataset  		  &   bias &   std &   skewness & fraction  \\
-	&   [K]  &   [K] & [-] & rejected [\%]\\
-		\hline
-Noise                       & -0.004 & 0.450 &             -0.030 &      - \\
-uncorrected                 & -1.343 & 5.908 &             -7.484 &      - \\
-corrected (three-a)  		&  0.019 & 0.889 &             -3.519 &      4.906 \\	 
-corrected (three-b)  		& -0.008 & 0.850 &             -3.326 &      4.926 \\			
-corrected (four)    		& -0.011 & 0.878 &             -3.030 &      4.930 \\
-		\hline
-	\end{tabular}
-	\caption{ Same as Table~\ref{tab:qrnn:C34}, but for channel AWS-32.}
-	\label{tab:qrnn:C32}
-\end{table}
-
-\begin{table}[!p]
-	\centering
-	\begin{tabular}[b]{c|c|c|c|c}
-	Dataset  		  &   bias &   std &   skewness & fraction  \\
-	&   [K]  &   [K] & [-] & rejected [\%]\\
-		\hline
-Noise                       & -0.005 & 0.450 &             -0.004 &      - \\
-uncorrected                 & -0.982 & 4.703 &             -8.778 &      - \\
-corrected (three-a) 		&  0.088 & 0.583 &             -0.959 &      4.197 \\
-corrected (three-b)  		& -0.030 & 0.612 &             -0.756 &      4.205 \\
-corrected (four)            &  0.106 & 0.591 &             -1.006 &      4.212 \\
-		\hline
-
-	\end{tabular}
-	\caption{ Same as Table~\ref{tab:qrnn:C34}, but for channel AWS-33.}
-	\label{tab:qrnn:C33}
-\end{table}
-
-\begin{table}[!p]
-	\centering
-	\begin{tabular}[b]{c|c|c|c|c}
-	Dataset  		  &   bias &   std &   skewness & fraction  \\
-	&   [K]  &   [K] & [-] & rejected [\%]\\
-		\hline
-
-Noise                      &  0.003 & 0.626 &             -0.009 &      - \\
-uncorrected                & -0.428 & 2.653 &            -12.492 &      - \\
-corrected (three-a) 	   &  0.060 & 0.610 &             -0.281 &      1.439 \\
-corrected (three-b) 	   &  0.097 & 0.618 &              0.011 &      1.331 \\
-corrected (four)   		   &  0.042 & 0.591 &             -0.351 &      1.821 \\
-	\hline
-	\end{tabular}
-	\caption{ Same as Table~\ref{tab:qrnn:C34}, but for channel AWS-35.}
-	\label{tab:qrnn:C35}
-\end{table}
-
-\begin{table}[!p]
-	\centering
-	\begin{tabular}[b]{c|c|c|c|c}
-	Dataset  		  &   bias &   std &   skewness & fraction  \\
-	&   [K]  &   [K] & [-] & rejected [\%]\\
-		\hline
-Noise                       &  0.000 & 0.888  &              0.005 &      - \\
-uncorrected                 & -0.269 & 2.059 &            -11.899 &      - \\
-corrected (three-a) 		&  0.062 & 0.797 &             -0.139 &      1.279 \\
-corrected (three-b) 		&  0.092 & 0.770 &             -0.075 &      1.124 \\
-corrected (four)   			&  0.056 & 0.779 &             -0.172 &      1.156 \\
-
-		\hline
-	\end{tabular}
-	\caption{ Same as Table~\ref{tab:qrnn:C34}, but for channel AWS-36.}
-	\label{tab:qrnn:C36}
-\end{table}
-
-\subsection{Uncertainty estimation}
-%
+	\includegraphics[height=80mm]{prediction_uncertainty.png}
+	\caption{The prediction uncertainty in AWS-34 with respect to quantiles for randomly selected 2400 cases.
+The red line represents the uncertainty if underlying distribution is purely Gaussian with standard deviation 0.62\,K.
+}
+	\label{fig:prediction_uncertainty}
+\end{figure}
+
 Quantile regression can be used to construct a probability distribution of the predictions in comparison to simple regression models, which predict only a point estimate of the target.
@@
 
+The figure also shows that the uncertainties for all 1000 random cases are concentrated along a narrow width, thus suggesting that the case to case variability of the uncertainty is low.
+
+\dots
+
 A similar uncertainty quantification for other 183\,GHz channels also gives similar results.
 Thus, assuming the posterior distribution to be gaussian between $\pm 2 \sigma$, the median is the measure of mean of the gaussian distribution, and the estimated error with respect to the true-value gives the spread of the distribution.
+
+\subsection{QRNN using AWS-4X}
+%
 \begin{figure}[!tb]
 	\centering
-	\includegraphics[height=80mm]{prediction_uncertainty.png}
-	\caption{The prediction uncertainty in AWS-34 with respect to quantiles for randomly selected 2400 cases.
-The red line represents the uncertainty if underlying distribution is purely Gaussian with standard deviation 0.62\,K.
+	\includegraphics[height=80mm]{Channel_C32_C4X.png}
+	\caption{ Error distributions for measured and predicted AWS-32, when QRNN  model is trained with measurements from AWS-4X.
+The results from QRNN model trained with four channel 325\,GHz are also shown for comparison.
 }
-	\label{fig:prediction_uncertainty}
-\end{figure}
-
-\subsection{QRNN using AWS-4X}
-%
-\begin{figure}[!tb]
-	\centering
-	\includegraphics[height=80mm]{Channel_C32_C4X.png}
-	\caption{ }
 	\label{fig:qrnn_C32_C4X:deviations}
@@
 	\end{tabular}
-	\caption{ AWS-32 with AWS-4X}
+	\caption{Statistics for the error distributions of AWS-32 shown in Figure~\ref{fig:qrnn_C32_C4X:deviations}. The QRNN model is trained with measurements from AWS-4X and AWS-32.}
 	\label{tab:qrnn:C32:C4X}
@@
 
-\section{Sensitivity to different receiver noise temperatures}
-
-%
+The average deviation of the uncorrected measurements to noise-free clear-sky simulations is -1.343\,K and the standard deviation is 5.908\,K.
+When trained with AWS-4X, the predictions are not very successful in alleviating the cloud impact.
+Although, the error standard deviation of the predicted dataset is lower, a large negative skewness (-4.085\,K) indicates significantly high uncorrected cloud impact.
+On the other hand, QRNN predictions trained with 325\,GHz data are also not completely cloud free, but have a slightly better accuracy.
+The error standard deviation for the four channel option is 0.878\,K.
+
+Clearly, without additional information, QRNN cannot learn to predict cloud free values for AWS-32.
+As already seen in simple correction scheme, AWS-4X is not sufficient enough to characterize the effect of hydrometeors in AWS-32.
+
+\section{Sensitivity to different $T_r$}
+%
+In the previous section, we presented the results from QRNN trained using the three suggestions of 325\,GHz proposed in section~\ref{sec:channel:configurations}.
+The receiver noise ($T_r$) was assumed to be 1200\,K for all cases.
+In this section, we explore the sensitivity of QRNN to increasing noise level.
+The QRNN training is repeated for all three suggestions of 325\,GHz, but with $T_r$ = 1800\,K and $T_r$ = 2400\,K.
+QRNN is trained with identical structural and training parameters as described earlier.
+Tables showing the statistics for error distributions for each channel are provided.
+Table~\ref{tab:qrnn:C32:Trec:1800} - Table~\ref{tab:qrnn:C36:Trec:1800} show the statistics for AWS-32, AWS-33, AWS-34, AWS-35 and AWS-36 respectively, when $T_r$ = 1800\,K.
+Similarly Table~\ref{tab:qrnn:C32:Trec:2400} - Table~\ref{tab:qrnn:C36:Trec:2400} show the statistics when $T_r$ = 2400\,K.
+
+For all channels, increase in the measurement noise increases the standard deviation of the predictions.
+For example, for AWS-34 (four channel option), the error standard deviation is 0.620\,K, 0.630\,K and 0.643\,K for $T_r$ = 1200\,K, 1800\,K and 2400\,K respectively.
+It is difficult to gauge the impact of increasing noise through bias and skewness of the error distributions, as the distribution can have a large spread, but still be symmetric with low bias and skewness.
+It is interesting to note that even for 1800\,K, the error standard deviation for predicted values for channels AWS-34, AWS-35 and AWS-36 is smaller than noise.
+This is in agreement with the results seen for $T_r$ = 1200\,K.
+However, for $T_r$ = 2400\,K, only AWS-36 follows the trend.
+
+Overall, the results show that an increase in the measurement noise does not have a huge impact on on QRNN accuracy.
+For the four channel option, with a 100\% increase in noise, the change in standard deviation is less than 10\%.
+
 \begin{table}[!p]
@@
 	uncorrected                & -1.342 & 5.908 &             -7.479 &      - \\
-	corrected (three channela) & -0.009 & 0.893 &             -3.092 &      4.990 \\
-    corrected (three channelb) &  0.009 & 0.888 &             -3.197 &      4.902 \\	
+	corrected (three-a) 	   & -0.009 & 0.893 &             -3.092 &      4.990 \\
+    corrected (three-b) 	   &  0.009 & 0.888 &             -3.197 &      4.902 \\	
 	corrected (four channel)   &  0.006 & 0.860 &             -2.943 &      4.954 \\
@@
 	\end{tabular}
-	\caption{ AWS-32 , Trec = 1800}
-	\label{tab:qrnn:C36}
-\end{table}
-
-\begin{table}[!p]
-	\centering
-	\begin{tabular}[b]{c|c|c|c|c}
-		Dataset  		  &   bias &   std &   skewness & fraction  \\
-		&   [K]  &   [K] & [-] & rejected [\%]\\
-		\hline
-	Noise                      & -0.001 & 0.452 &              0.015 &      0.000 \\
-	uncorrected                & -0.975 & 4.703 &             -8.763 &      0.000 \\
-	corrected (three channela) &  0.085 & 0.587 &             -0.640 &      4.209 \\
-	corrected (three channelb) &  0.062 & 0.605 &             -0.845 &      4.205 \\
+	\caption{Error statistics for AWS-32, when the model is trained with $T_r$ = 1800\,K. The definitions of "three-a", "three-b" and "four" are same as described in Table~\ref{tab:qrnn:C34} }
+	\label{tab:qrnn:C32:Trec:1800}
+\end{table}
+
+\begin{table}[!p]
+	\centering
+	\begin{tabular}[b]{c|c|c|c|c}
+		Dataset  		  &   bias &   std &   skewness & fraction  \\
+		&   [K]  &   [K] & [-] & rejected [\%]\\
+		\hline
+	Noise                       & -0.001 & 0.452 &              0.015 &      - \\
+	uncorrected                 & -0.975 & 4.703 &             -8.763 &      - \\
+	corrected (three-a) 		&  0.085 & 0.587 &             -0.640 &      4.209 \\
+	corrected (three-b) 		&  0.062 & 0.605 &             -0.845 &      4.205 \\
 	corrected (four channel)    &  0.048 & 0.606 &             -1.112 &      4.264 \\
@@
 	\end{tabular}
-	\caption{ AWS-33, Trec = 1800 }
-	\label{tab:qrnn:C36}
-\end{table}
-
-\begin{table}[!p]
-	\centering
-	\begin{tabular}[b]{c|c|c|c|c}
-		Dataset  		  &   bias &   std &   skewness & fraction  \\
-		&   [K]  &   [K] & [-] & rejected [\%]\\
-		\hline
-	Noise                      &  0.001 & 0.632 &              0.021 &      0.000 \\
-	uncorrected                & -0.676 & 3.686 &            -10.301 &      0.000 \\
-	corrected (three channela) &  0.079 & 0.646 &             -0.344 &      2.730 \\
-    corrected (three channelb) &  0.090 & 0.639 &             -0.405 &      2.582 \\
+	\caption{ Same as Table~\ref{tab:qrnn:C32:Trec:1800}, but for AWS-33.}
+	\label{tab:qrnn:C33:Trec:1800}
+\end{table}
+
+\begin{table}[!p]
+	\centering
+	\begin{tabular}[b]{c|c|c|c|c}
+		Dataset  		  &   bias &   std &   skewness & fraction  \\
+		&   [K]  &   [K] & [-] & rejected [\%]\\
+		\hline
+	Noise                       &  0.001 & 0.632 &              0.021 &      - \\
+	uncorrected                 & -0.676 & 3.686 &            -10.301 &      - \\
+	corrected (three-a) 		&  0.079 & 0.646 &             -0.344 &      2.730 \\
+    corrected (three-b) 		&  0.090 & 0.639 &             -0.405 &      2.582 \\
 	corrected (four channel)    &  0.079 & 0.630 &             -0.399 &      2.981 \\
@@
 	\end{tabular}
-	\caption{ AWS-34, Trec = 1800 }
-	\label{tab:qrnn:C36}
-\end{table}
-
-\begin{table}[!p]
-	\centering
-	\begin{tabular}[b]{c|c|c|c|c}
-		Dataset  		  &   bias &   std &   skewness & fraction  \\
-		&   [K]  &   [K] & [-] & rejected [\%]\\
-		\hline
-Noise                       &  0.001 & 0.629 &              0.007 &      0.000 \\
-uncorrected                 & -0.417 & 2.654 &            -12.446 &      0.000 \\
-corrected (three channela)  &  0.045 & 0.636 &             -0.188 &      1.431 \\
-corrected (three channelb)  &  0.081 & 0.640 &             -0.458 &      1.299 \\
+	\caption{Same as Table~\ref{tab:qrnn:C32:Trec:1800}, but for AWS-34. }
+	\label{tab:qrnn:C34:Trec:1800}
+\end{table}
+
+\begin{table}[!p]
+	\centering
+	\begin{tabular}[b]{c|c|c|c|c}
+		Dataset  		  &   bias &   std &   skewness & fraction  \\
+		&   [K]  &   [K] & [-] & rejected [\%]\\
+		\hline
+Noise                       &  0.001 & 0.629 &              0.007 &      - \\
+uncorrected                 & -0.417 & 2.654 &            -12.446 &      - \\
+corrected (three-a)  		&  0.045 & 0.636 &             -0.188 &      1.431 \\
+corrected (three-b)  		&  0.081 & 0.640 &             -0.458 &      1.299 \\
 corrected (four channel)    &  0.058 & 0.617 &             -0.007 &      1.801 \\
@@
 	\end{tabular}
-	\caption{ AWS-35, Trec = 1800 }
-	\label{tab:qrnn:C36}
-\end{table}
-
-\begin{table}[!p]
-	\centering
-	\begin{tabular}[b]{c|c|c|c|c}
-		Dataset  		  &   bias &   std &   skewness & fraction  \\
-		&   [K]  &   [K] & [-] & rejected [\%]\\
-		\hline
-Noise                      &  0.002 & 0.882 &             -0.006 &      0.000 \\
-uncorrected                & -0.268 & 2.063 &            -12.003 &      0.000 \\
-corrected (three channela) &  0.075 & 0.831 &             -0.130 &      1.283 \\
-corrected (three channelb) &  0.105 & 0.807 &             -0.080 &      1.136 \\
+	\caption{Same as Table~\ref{tab:qrnn:C32:Trec:1800}, but for AWS-35. }
+	\label{tab:qrnn:C35:Trec:1800}
+\end{table}
+
+\begin{table}[!p]
+	\centering
+	\begin{tabular}[b]{c|c|c|c|c}
+		Dataset  		  &   bias &   std &   skewness & fraction  \\
+		&   [K]  &   [K] & [-] & rejected [\%]\\
+		\hline
+Noise                      &  0.002 & 0.882 &             -0.006 &      - \\
+uncorrected                & -0.268 & 2.063 &            -12.003 &      - \\
+corrected (three-a)        &  0.075 & 0.831 &             -0.130 &      1.283 \\
+corrected (three-b)        &  0.105 & 0.807 &             -0.080 &      1.136 \\
 corrected (four channel)   &  0.093 & 0.826 &             -0.175 &      1.120 \\
@@
 	\end{tabular}
-	\caption{ AWS-36, Trec = 1800 }
-	\label{tab:qrnn:C36}
-\end{table}
-
-%
-\begin{table}[!p]
-	\centering
-	\begin{tabular}[b]{c|c|c|c|c}
-		Dataset  		  &   bias &   std &   skewness & fraction  \\
-		&   [K]  &   [K] & [-] & rejected [\%]\\
-		\hline
-Noise                       &  0.002 & 0.454 &              0.003 &      0.000 \\
-uncorrected                 & -1.343 & 5.907 &             -7.483 &      0.000 \\
-corrected (three channela)  & -0.017 & 0.877 &             -3.381 &      4.934 \\
-corrected (three channelb)  & -0.015 & 0.882 &             -3.177 &      4.974 \\
+	\caption{ Same as Table~\ref{tab:qrnn:C32:Trec:1800}, but for AWS-36.}
+	\label{tab:qrnn:C36:Trec:1800}
+\end{table}
+
+%
+\begin{table}[!p]
+	\centering
+	\begin{tabular}[b]{c|c|c|c|c}
+		Dataset  		  &   bias &   std &   skewness & fraction  \\
+		&   [K]  &   [K] & [-] & rejected [\%]\\
+		\hline
+Noise                       &  0.002 & 0.454 &              0.003 &      - \\
+uncorrected                 & -1.343 & 5.907 &             -7.483 &      - \\
+corrected (three-a)  		& -0.017 & 0.877 &             -3.381 &      4.934 \\
+corrected (three-b)  		& -0.015 & 0.882 &             -3.177 &      4.974 \\
 corrected (four channel)    &  0.028 & 0.876 &             -3.638 &      4.978 \\
@@
 	\end{tabular}
-	\caption{ AWS-32, Trec = 2400 }
-	\label{tab:qrnn:C36}
-\end{table}
-
-\begin{table}[!p]
-	\centering
-	\begin{tabular}[b]{c|c|c|c|c}
-		Dataset  		  &   bias &   std &   skewness & fraction  \\
-		&   [K]  &   [K] & [-] & rejected [\%]\\
-		\hline
- Noise                     & -0.003 & 0.448 &              0.005 &      0.000 \\
-uncorrected                & -0.979 & 4.709 &             -8.762 &      0.000 \\
-corrected (three channela) &  0.057 & 0.628 &             -0.728 &      4.232 \\
-corrected (three channelb) &  0.040 & 0.614 &             -0.786 &      4.205 \\
+	\caption{ Error statistics for AWS-32, when the model is trained with $T_r$ = 1800\,K. The definitions of "three-a", "three-b" and "four" are same as described in Table~\ref{tab:qrnn:C34}  }
+	\label{tab:qrnn:C32:Trec:2400}
+\end{table}
+
+\begin{table}[!p]
+	\centering
+	\begin{tabular}[b]{c|c|c|c|c}
+		Dataset  		  &   bias &   std &   skewness & fraction  \\
+		&   [K]  &   [K] & [-] & rejected [\%]\\
+		\hline
+ Noise                     & -0.003 & 0.448 &              0.005 &      - \\
+uncorrected                & -0.979 & 4.709 &             -8.762 &      - \\
+corrected (three-a) &  0.057 & 0.628 &             -0.728 &      4.232 \\
+corrected (three-b) &  0.040 & 0.614 &             -0.786 &      4.205 \\
 corrected (four channel)   &  0.043 & 0.614 &             -0.798 &      4.232 \\
@@
 	\end{tabular}
-	\caption{ AWS-33, Trec = 2400  }
-	\label{tab:qrnn:C36}
-\end{table}
-
-\begin{table}[!p]
-	\centering
-	\begin{tabular}[b]{c|c|c|c|c}
-		Dataset  		  &   bias &   std &   skewness & fraction  \\
-		&   [K]  &   [K] & [-] & rejected [\%]\\
-		\hline
- Noise                      & -0.001 & 0.638 &              0.006 &      0.000 \\
-uncorrected                 & -0.676 & 3.688 &            -10.299 &      0.000 \\
- corrected (three channela) &  0.069 & 0.655 &             -0.396 &      2.666 \\
-corrected (three channelb)  &  0.090 & 0.648 &             -0.310 &      2.594 \\
+	\caption{ Same as Table~\ref{tab:qrnn:C32:Trec:2400}, but for AWS-33.  }
+	\label{tab:qrnn:C33:Trec:2400}
+\end{table}
+
+\begin{table}[!p]
+	\centering
+	\begin{tabular}[b]{c|c|c|c|c}
+		Dataset  		  &   bias &   std &   skewness & fraction  \\
+		&   [K]  &   [K] & [-] & rejected [\%]\\
+		\hline
+ Noise                      & -0.001 & 0.638 &              0.006 &      - \\
+uncorrected                 & -0.676 & 3.688 &            -10.299 &      - \\
+ corrected (three-a) &  0.069 & 0.655 &             -0.396 &      2.666 \\
+corrected (three-b)  &  0.090 & 0.648 &             -0.310 &      2.594 \\
 corrected (four channel)    &  0.059 & 0.643 &             -0.340 &      2.937 \\
@@
 	\end{tabular}
-	\caption{ AWS-34, Trec = 2400 }
-	\label{tab:qrnn:C36}
-\end{table}
-
-\begin{table}[!p]
-	\centering
-	\begin{tabular}[b]{c|c|c|c|c}
-		Dataset  		  &   bias &   std &   skewness & fraction  \\
-		&   [K]  &   [K] & [-] & rejected [\%]\\
-		\hline
-Noise                      & -0.004 & 0.633 &              0.021 &      0.000 \\
-uncorrected                & -0.420 & 2.654 &            -12.449 &      0.000 \\
-corrected (three channela) &  0.034 & 0.646 &             -0.389 &      1.479 \\
-corrected (three channelb) &  0.076 & 0.647 &             -0.148 &      1.291 \\
+	\caption{ Same as Table~\ref{tab:qrnn:C32:Trec:2400}, but for AWS-34.  }
+	\label{tab:qrnn:C34:Trec:2400}
+\end{table}
+
+\begin{table}[!p]
+	\centering
+	\begin{tabular}[b]{c|c|c|c|c}
+		Dataset  		  &   bias &   std &   skewness & fraction  \\
+		&   [K]  &   [K] & [-] & rejected [\%]\\
+		\hline
+Noise                      & -0.004 & 0.633 &              0.021 &      - \\
+uncorrected                & -0.420 & 2.654 &            -12.449 &      - \\
+corrected (three-a) &  0.034 & 0.646 &             -0.389 &      1.479 \\
+corrected (three-b) &  0.076 & 0.647 &             -0.148 &      1.291 \\
 corrected (four channel)   &  0.044 & 0.632 &             -0.188 &      1.809 \\
@@
 	\end{tabular}
-	\caption{ AWS-35, Trec = 2400}
-	\label{tab:qrnn:C36}
-\end{table}
-
-\begin{table}[!p]
-	\centering
-	\begin{tabular}[b]{c|c|c|c|c}
-		Dataset  		  &   bias &   std &   skewness & fraction  \\
-		&   [K]  &   [K] & [-] & rejected [\%]\\
-		\hline
-Noise                      &  0.005 & 0.884 &             -0.026 &      0.000 \\
-uncorrected                & -0.268 & 2.057 &            -11.977 &      0.000 \\
-corrected (three channela) &  0.039 & 0.854 &             -0.131 &      1.283 \\
-corrected (three channelb) &  0.090 & 0.839 &             -0.096 &      1.108 \\
+	\caption{ Same as Table~\ref{tab:qrnn:C32:Trec:2400}, but for AWS-35. }
+	\label{tab:qrnn:C35:Trec:2400}
+\end{table}
+
+\begin{table}[!p]
+	\centering
+	\begin{tabular}[b]{c|c|c|c|c}
+		Dataset  		  &   bias &   std &   skewness & fraction  \\
+		&   [K]  &   [K] & [-] & rejected [\%]\\
+		\hline
+Noise                      &  0.005 & 0.884 &             -0.026 &      - \\
+uncorrected                & -0.268 & 2.057 &            -11.977 &      - \\
+corrected (three-a) &  0.039 & 0.854 &             -0.131 &      1.283 \\
+corrected (three-b) &  0.090 & 0.839 &             -0.096 &      1.108 \\
 corrected (four channel)   &  0.059 & 0.850 &             -0.140 &      1.140 \\
@@
 	\end{tabular}
-	\caption{ AWS-36, Trec = 2400 }
-	\label{tab:qrnn:C36}
+	\caption{ Same as Table~\ref{tab:qrnn:C32:Trec:2400}, but for AWS-36.  }
+	\label{tab:qrnn:C36:Trec:2400}
 \end{table}
@@
 
-\subsection{Performance of QRNN}
-%
-\dots
+\subsubsection{Performance of QRNN}
+In section~\ref{} we use QRNN as a method for cloud correction based on 325\,GHz data.
+Measurements from all 325\,GHz channels and the the 183\,GHz channel to be predicted are used to train the QRNN model.
+
+The results demonstrate that QRNN is successful in predicting the clear-sky noise free data for AWS-33, AWS-32, AWS-35 and AWS-36.
+The error distributions for the predictions symmetric and have low bias and standard deviation.
+Among the two three channel options and the one four channel option of 325\,GHz, the performance of the three QRNN models is comparable.
+
+ the performance of none of the options can be considered as the best. For AWS-34
+
+QRNN is successful in learning to predcit the clear-sky noise-free values for 183\,GHz channels.
 

### 2020-06-17 Report/aws_325ghz_study.tex
new additions to Section 9

@@
 %
+\label{sec:qrnn}
 There are two main drawbacks of the simple scheme introduced in the previous
@@
 
-If $X$ is a random variable with cumulative distribution function $F(X)$, and $x_{\tau}$ is its $\tau$th quantile, the quantile loss function is defined as:
+If $x_{\tau}$ is the $\tau$th quantile of a cumulative distribution function $F(X)$, the quantile loss function is defined as:
 \begin{equation}
@@
 	\includegraphics[height=85mm]{quantile_loss.png}
-	\caption{The mean quantile loss with different configurations of layer width and hidden layers ($n_h$).}
+	\caption{The mean quantile loss with different configurations of layer width and hidden layers ($n_h$).
+Here QRNN is trained to predict clear-sky values for AWS-34 using four channels option of 325\,GHz}
 	\label{fig:quantile_loss}
 \end{figure}
-In this section, QRNNs are used to correct the cloud impact in each of 183\,GHz channels using TBs from all available channels of 325\,GHz.
+In this section, QRNNs are used to correct the cloud impact in each of 183\,GHz channels using TBs measurements from all available channels of 325\,GHz.
 A separate QRNN is used for each of the 183\,GHz channels.
@@
 Increasing both layer width and depth has a positive impact on performance of the network, however for four hidden layers, increasing the layer width leads to only small performance gains.
-On basis of these results, a neural network with four hidden layer and 128 neurons was chosen for training.
+On basis of these results, a neural network with four hidden layers and 128 neurons was chosen.
 For the training, we obtained the best performance when trained with a multiple learning rate schedule.
 We start the training process with a initial learning rate and after a certain number of epochs, the training is updated with a new initial learning rate.
-We chose the three training schedules with initial learning rates = 0.01, 0.001, 0.0001 respectively, updated after 20 epochs.
+We chose three training schedules with initial learning rates = 0.01, 0.001, 0.0001 respectively, updated after 20 epochs.
 
@@
 	\includegraphics[height=60mm]{distribution_predicted_C36}
-	\caption{ Probability distribution functions (PDFs) of predicted and observed noise free brightness temperatures for all 183\,GHz channels of AWS.  }
+	\caption{ Probability distribution functions (PDFs) of predicted and observed noise free brightness temperatures for all 183\,GHz channels of AWS.
+The results are based on QRNN trained with four channel option of 325\,GHz.}
 	\label{fig:pdf:qrnn}
@@
 The simulated clear-sky distributions are also plotted for reference.
-For these results, the four channel option was used to train the QRNN.
+These results are from four channel option.
 The distributions show that QRNN is overall successful in predicting the clear-sky cases.
@@
 Measurements with cases with $Tb2 - Tb1 > -15$\,K are assumed to be too-cloudy and are filtered out.
-Both the three channel and four channel QRNN model are successful in predicting the clear-sky noise-free value for AWS-34, and the resulting error distribution is symmetric.
+Here $Tb1$ denotes TBs from AWS-34 and and $Tb2$ is the paired counterpart from 325\,GHz, i.e., AWS-42.
+Both the three channels and four channels QRNN models are successful in predicting the clear-sky noise-free value for AWS-34, and the resulting error distribution is symmetric.
 The statistics corresponding to these distributions are provided in Table~\ref{tab:qrnn:C34}.
-.
 The fraction of cases rejected as "too-cloudy" is also provided under ``fraction rejected''.
 For AWS-34, average deviation in the predictions from all three QRNN models are comparable.
-The cloud impact in the uncorrected measurements is reflected in the high negative skewness (-10.32), however with QRNN the skewness is largely reduced and the symmetry in the distributions is reflected in the low skewness values.
+The cloud impact in the uncorrected measurements is reflected in the high negative skewness (-10.32), however the predictions have relatively symmetric error distributions as reflected by the low skewness values.
 Among the three set of predictions, option three-b has the most symmetric error distribution but with a relatively large spread.
 Predictions from option four have the lowest standard deviation (0.620\,K), which is interestingly smaller than the standard deviation of noise (0.641\,K).
-Though, all three options of 325\,GHz provide a full coverage to the hydrometer impact in AWS-34, predictions from four channel option are slightly more accurate.
+Though, all three options of 325\,GHz provide a full coverage to the hydrometer impact in AWS-34, predictions from four channel option have slightly better accuracy.
 
@@
 But a relatively high negative skewness in the predicted dataset indicates presence of uncorrected cloud impact.
+For AWS-32, option ``three-b'' has the lowest spread of errors, but the error distributions are more symmetric for option ``four''.
 
 Table~\ref{tab:qrnn:C33} shows the statistics for AWS-33.
-The standard deviation in the four channel option (0.591\,K) is slighly lower than three-b(0.612\,K), but the skewness in three-b in lower.
+The standard deviation in the four channel option (0.591\,K) is lower than ``three-b''(0.612\,K), but the skewness in three-b in lower.
 This indicates that with four channel option, the QRNN predictions are mostly closer to the simulations, but few cases with large cloud impact are under predicted.
 
-For AWS-35 (Table~\ref{tab:qrnn:C35}), the four channel option has the best performance.
+For AWS-35 (Table~\ref{tab:qrnn:C35}), the four channels option has the best performance.
 The average bias in QRNN predictions (four) is only 0.04\,K in comparsion to -0.42\,K for the measurements.
-Option three-b has lower skewness than option four, but the standard deviation is higher.
+Option ``three-b'' has lower skewness than option four, but the standard deviation is higher.
 It is interesting to note that the standard deviation in all three predicted datasets is always lower than noise.
 Similar results are also seen for AWS-36 (Table~\ref{tab:qrnn:C36}).
-The four channel combination reduces the average bias from -0.269\,K to 0.056\,K and the standard deviation from 2.059\,K to 0.779\,K.
+The four channels combination reduces the average bias from -0.269\,K to 0.056\,K and the standard deviation from 2.059\,K to 0.779\,K.
 Also for this channel, the spread of the predictions is narrower than noise.
@@
 	\caption{The prediction uncertainty in AWS-34 with respect to quantiles for randomly selected 2400 cases.
-The red line represents the uncertainty if underlying distribution is purely Gaussian with standard deviation 0.62\,K.
+The red line represents the uncertainty if underlying distribution is purely Gaussian with mean 270\,K and standard deviation 0.62\,K.
 }
@@
 If the posterior distribution from QRNN follow normal distribution, the uncertainty can be estimated as a gaussian distribution centered around the median and standard deviation equal to the estimated error.
-To inspect if the predictions follow a normal distribution we evaluate the length of confidence intervals with respect to the median.
-Figure~\ref{fig:prediction_uncertainty} shows the prediction uncertainty in AWS-34 (using four channel option).
+To inspect if the predictions follow a normal distribution we evaluate the length of confidence intervals from the median.
+Figure~\ref{fig:prediction_uncertainty} shows the prediction uncertainty in AWS-34 (four channel option).
 The uncertainty with respect to the median for 1000 randomly selected cases is shown.
@@
 If the underlying distribution is Gaussian, the prediction uncertainty should be symmetric around the median, and the uncertainties should be equally spaced for $1\sigma$, $2\sigma$ and so on.
-The predictions from our QRNN model seem to be symmetric around the median for the 95\% confidence interval ($\pm 2 \sigma$).
-In other words, around 95\% of the true cases lie in the confidence interval given by $\pm 2\sigma$, and only 6\% of predictions are either too low or too high than the true value.
-
+The predictions from our QRNN model seem to be symmetric around the median for the 94\% confidence interval ($\pm 2 \sigma$).
+In other words, around 94\% of the true cases lie in the confidence interval given by $\pm 2\sigma$, and only 6\% of predictions are either too low or too high than the true value.
 The figure also shows that the uncertainties for all 1000 random cases are concentrated along a narrow width, thus suggesting that the case to case variability of the uncertainty is low.
-
-\dots
 
@@
 	\includegraphics[height=80mm]{Channel_C32_C4X.png}
-	\caption{ Error distributions for measured and predicted AWS-32, when QRNN  model is trained with measurements from AWS-4X.
-The results from QRNN model trained with four channel 325\,GHz are also shown for comparison.
+	\caption{ Error distributions for measured and predicted AWS-32, when QRNN  model is trained with measurements from AWS-4X and AWS-32.
+The results from QRNN model trained with four channels 325\,GHz are also shown for comparison.
 }
@@
 \end{table} 
-We also tested the QRNN model to predict cloud-free TBs using AWS-4X.
+We also tested the QRNN model to predict cloud-free TBs by using measurements from AWS-4X and AWS-32 as input.
 In this case, we trained QRNN with measurements from AWS-32 and AWS-4X, to predict the clear-sky cloud free TBs for AWS-32.
-The model was trained as described in Section~\ref{sec:qrnn:training}, but the width of the network was chosen to be 256 neurons.
+The model was trained as described in Section~\ref{sec:qrnn:training}, but slightly better training results were obtained with width as 256 neurons.
 Other structural and training parameters remain unchanged.
@@
 On the other hand, QRNN predictions trained with 325\,GHz data are also not completely cloud free, but have a slightly better accuracy.
-The error standard deviation for the four channel option is 0.878\,K.
+The error standard deviation for the four channels option is 0.878\,K.
 
@@
 The receiver noise ($T_r$) was assumed to be 1200\,K for all cases.
-In this section, we explore the sensitivity of QRNN to increasing noise level.
+In this section, we explore the sensitivity of QRNN to a higher receiver noise.
 The QRNN training is repeated for all three suggestions of 325\,GHz, but with $T_r$ = 1800\,K and $T_r$ = 2400\,K.
@@
 	\end{tabular}
-	\caption{ Error statistics for AWS-32, when the model is trained with $T_r$ = 1800\,K. The definitions of "three-a", "three-b" and "four" are same as described in Table~\ref{tab:qrnn:C34}  }
+	\caption{ Error statistics for AWS-32, when the model is trained with $T_r$ = 2400\,K. The definitions of "three-a", "three-b" and "four" are same as described in Table~\ref{tab:qrnn:C34}  }
 	\label{tab:qrnn:C32:Trec:2400}
@@
 \subsubsection{Performance of QRNN}
-In section~\ref{} we use QRNN as a method for cloud correction based on 325\,GHz data.
-Measurements from all 325\,GHz channels and the the 183\,GHz channel to be predicted are used to train the QRNN model.
+In section~\ref{sec:qrnn} we use QRNN as a method for cloud correction based on 325\,GHz data.
+Measurements from all 325\,GHz channels and the 183\,GHz channel to be predicted are used to train the QRNN model.
 
@@
 The error distributions for the predictions symmetric and have low bias and standard deviation.
-Among the two three channel options and the one four channel option of 325\,GHz, the performance of the three QRNN models is comparable.
-
- the performance of none of the options can be considered as the best. For AWS-34
-
-QRNN is successful in learning to predcit the clear-sky noise-free values for 183\,GHz channels.
+Infact, for AWS-34, AWS-35 and AWS-36, the spread of errors is even smaller than the noise.
+QRNN seems to perform equally well with three configurations suggested for 325\,GHz channels.
+
+For AWS-32, the QRNN trained with 325\,GHz is only partially successful in reducing the impact of hyderometeors.
+The resulting error distributions have significantly lower spread than the measurements, but are still negatively skewed.
+Among the three combinations of 325\,GHz, the four channel option has slightly better performance.
+Since 325\,GHz cannot provide a full coverage for hydrometeor impact in AWS-32, QRNN cannot learn to predict cloud free values for instances which  lie outside the area of coverage.
+In order to compare the 229\,GHz channel with 325\,GHz, QRNN was also trained with AWS-4X to predict cloud free AWS-32 TBs.
+The performance of QRNN trained with AWS-4X is worse than training with 325\,GHz.
+The spread of error distributions is 1.5 times more than obtained with four channels option of 325\,GHz.
 

### 2020-06-18 Report/aws_325ghz_study.tex
A quick review of all existing text.

@@
 
+[* IK: Run spell check just before submitting * ]
+
 \setcounter{tocdepth}{1} 
@@
 radiometer. The exact channel configuration of AWS is not yet set. The main
-issue for this report is that AWS will have channels at 183\,GHz, but also one
+issue for this study is that AWS will have channels at 183\,GHz, but also one
 or several channels a higher frequencies. A number of channels around 325\,GHz
@@
 %
-To support the selection between 229 and 325\,GHz channels for AWS, this report
+To support the selection between 229 and 325\,GHz channels, this report
 investigates the possibility to use the later range in forming 183\,GHz data of
@@
 In \citet{rekha2012potential} the task was defined to screen out observations
-having a cloud impact exceeding 4\,K at 183$\pm$7\,GHz. Their final suggestion
+having a cloud impact exceeding 4\,K at 183\,$\pm$\,7\,GHz. Their final suggestion
 for screening does not involve data from any other channel than 229\,GHz, but
 requires radiative transfer calculations (as a ``B-O test'' is made). Only 
-screening of 183$\pm$7\,GHz was discussed.
+screening of 183\,$\pm$\,7\,GHz was discussed.
 
@@
 Results from \citet{rekha2012potential} will be used as reference. They did not
-suggest specific settings of their algorithm. The main consideration of the
+suggest specific settings of their algorithm. The main consideration of their
 scheme is a threshold value. We assume below 6\,K for
@@
 cases to 0.6\%, but increases the miss-classification for ``clear'' cases to 77\%.
-If 183$\pm$7\,GHz is classified as cloudy, we assume that also the data from
+If 183\,$\pm$7\,GHz is classified as cloudy, we assume that also the data from
 other 183\,GHz channels are rejected.
@@
 %
-The specifications of channels around 89, 166, 183 and 229\,GHz are assumed to
+The specifications of channels around 166, 183 and 229\,GHz are assumed to
 be fixed, with name, position and widths defined in Table~\ref{tab:fixed:chs}.
@@
     \hline
-    AWS-21  & \phantom{0}89.000 & 4000\\
     AWS-31  & 165.500 & 2800\\
@@
   \caption{Fixed channel position and widths. The left table covers channels of
-    AWS, with values taken from SoW. Channels AWS-21 to AWS-36 are at this
+    AWS, with values taken from SoW. Channels AWS-31 to AWS-36 are at this
     moment mandatory for AWS, while AWS-4X is so far tentative. The right table
@@
 Transfer System (ARTS, \citet{eriksson:arts2:11,buehler:artst:18}), version
-arts-2.3.????. Models and input used for absorption and hydrometeor properties
+arts-2.3.1284. Models and input used for absorption and hydrometeor properties
 are described below. Ocean/water and land emissivities are taken from
@@
 and RWC derived from CloudSat reflectivities and LWC from ERA-Interim were
-included. Both sets of calculations were were made by ARTS's interface to the
+included. Both sets of calculations were made by ARTS's interface to the
 RT4 solver \citep{evans1995microwavec}. This ``scattering solver'' was used
@@
 %
-Using the simulation setup described above, around 77000 cases were simulated
+Using the simulation setup described above, around 77000 cases [* Is this the
+correct final number? *] were simulated
 based on randomly selected CloudSat orbits during August 2015. The input data
@@
 
-The overall agreement is good for channels. For 183 GHz channels (Channels
+The overall agreement is good for all channels. For 183 GHz channels (Channels
 18-22), the simulations and observations have a good agreement for the part of
@@
 explain the deviation. As this region is well covered in the simulations
-reported in Fig.~7 of \citep{eriksson:towar:20}, the deviation of concern is
+reported in Fig.~7 of \citet{eriksson:towar:20}, the deviation of concern is
 presumably also a consequence of the neglected antenna pattern. In this study,
@@
 
+\subsection{Dataset formed}
+%
+[* Describe here briefly the final set of simulations used below. Number of
+cases, with and without thinng. Latiude range. If the full dataset was used for
+ATMS comparsion, switch place between 3.3 and 3.4. Probably easiest to say that
+all results below are for nadir. Otherwise this has to be clarified for the
+simple scehem. *]
+
 \section{Overview of the 183, 229 and 325\,GHz bands}
@@
 (Sec.~\ref{sec:fascod}), and performed with a fixed sensor viewing angle of
-25$^\circ$. No hydrometeors are included. For simpler interpretation of the
-results, the reflectivity is set to have no frequency variation, i.e.\ the same
-value is applied for all bands. The reflectivity is varied between 0 and 0.5
-(these fixed values are only applied in this section, the bulk simulations are
-using TESSEM and TELSEM for seting the surface properties).
-In the figures covering transmissivities and Jacobians, the specifications
-of ICI is applied for 325\,GHz channels (Table~\ref{tab:fixed:chs}).
+25$^\circ$ (deviation from nadir). No hydrometeors are included. For simpler
+interpretation of the results, the reflectivity is set to have no frequency
+variation, i.e.\ the same value is applied for all bands. The reflectivity is
+varied between 0 and 0.5 (these fixed values are only applied in this section,
+the bulk simulations are using TESSEM and TELSEM for seting the surface
+properties). In the figures covering transmissivities and Jacobians, the
+specifications of ICI is applied for 325\,GHz channels
+(Table~\ref{tab:fixed:chs}).
 
@@
 
-\begin{table}[!t]
-  \centering  
-  \begin{tabular}[c]{c|c|c|ccc}
-    Channel & Frequency   & Bandwidth & $T_r=1200$\,K
-    & $T_r=1800$\,K & $T_r=2400$\,K\\
-    name    & [GHz] &  [MHz] & [K]  & [K] & [K]\\
-    \hline
-    AWS-41  & 325.15$\pm$6.50 & 3000 & 0.58 & 0.82 & 1.06 \\
-    AWS-42  & 325.15$\pm$3.55 & 2500 & 0.64 & 0.90 & 1.16 \\
-    AWS-43  & 325.15$\pm$1.60 & 1200 & 0.92 & 1.30 & 1.68 \\
-    \hline
-  \end{tabular}
-  \caption{Tentative suggestion for a three 325\,GHz channels option. The
-    values in the three last columns is the 1$\sigma$ noise level according to
-    Eq.~\ref{eq:noise}, for $T_a=300$\,K and  $T_r$ }
-  \label{tab:chs:prel3}
-\end{table}
-
-\begin{table}[!t]
-  \centering  
-  \begin{tabular}[c]{c|c|c|ccc}
-    Channel & Frequency   & Bandwidth & $T_r=1200$\,K
-    & $T_r=1800$\,K & $T_r=2400$\,K\\
-    name    & [GHz] &  [MHz] & [K]  & [K] & [K]\\
-    \hline
-    AWS-41  & 325.15$\pm$6.60 & 2800 & 0.60 & 0.85 & 1.10 \\
-    AWS-42  & 325.15$\pm$4.10 & 1800 & 0.75 & 1.06 & 1.37 \\
-    AWS-43  & 325.15$\pm$2.40 & 1200 & 0.92 & 1.30 & 1.68 \\
-    AWS-44  & 325.15$\pm$1.20 & \phantom{0}800 & 1.12 & 1.59 & 2.06\\
-    \hline
-  \end{tabular}
-  \caption{Tentative suggestion for a four 325\,GHz channels option. Else as
-    Table~\ref{tab:chs:prel4}.}
-  \label{tab:chs:prel4}
-\end{table}
-
 \subsection{A four channel option}
@@
 
-\subsection{A second three channel option}
-%
-Relatively late in the study Omnisys informed us about that an IF of 1.7\,GHz
-should be avoided, as this frequency likely will be used for downlink of data.
-The four channel option needed just a marginal change to adopt to this
-constrain, while 1.7\,GHz is more or less at the centre of the three channel
-option. It was then decided to formulate second three channel option avoiding 
-1.7\,GHz, and the suggestion is found in Table~\ref{tab:chs:3b}.
-
-\begin{table}[!h]
+\begin{table}[!p]
   \centering  
@@
     \hline
+    AWS-41  & 325.15$\pm$6.50 & 3000 & 0.58 & 0.82 & 1.06 \\
+    AWS-42  & 325.15$\pm$3.55 & 2500 & 0.64 & 0.90 & 1.16 \\
+    AWS-43  & 325.15$\pm$1.60 & 1200 & 0.92 & 1.30 & 1.68 \\
+    \hline
+  \end{tabular}
+  \caption{Tentative suggestion for a three 325\,GHz channels option. The
+    values in the three last columns is the 1$\sigma$ noise level according to
+    Eq.~\ref{eq:noise}, for $T_a=300$\,K and stated $T_r$ }
+  \label{tab:chs:prel3}
+\end{table}
+
+\begin{table}[!p]
+  \centering  
+  \begin{tabular}[c]{c|c|c|ccc}
+    Channel & Frequency   & Bandwidth & $T_r=1200$\,K
+    & $T_r=1800$\,K & $T_r=2400$\,K\\
+    name    & [GHz] &  [MHz] & [K]  & [K] & [K]\\
+    \hline
+    AWS-41  & 325.15$\pm$6.60 & 2800 & 0.60 & 0.85 & 1.10 \\
+    AWS-42  & 325.15$\pm$4.10 & 1800 & 0.75 & 1.06 & 1.37 \\
+    AWS-43  & 325.15$\pm$2.40 & 1200 & 0.92 & 1.30 & 1.68 \\
+    AWS-44  & 325.15$\pm$1.20 & \phantom{0}800 & 1.12 & 1.59 & 2.06\\
+    \hline
+  \end{tabular}
+  \caption{Tentative suggestion for a four 325\,GHz channels option. Else as
+    Table~\ref{tab:chs:prel4}.}
+  \label{tab:chs:prel4}
+\end{table}
+
+\begin{table}[!p]
+  \centering  
+  \begin{tabular}[c]{c|c|c|ccc}
+    Channel & Frequency   & Bandwidth & $T_r=1200$\,K
+    & $T_r=1800$\,K & $T_r=2400$\,K\\
+    name    & [GHz] &  [MHz] & [K]  & [K] & [K]\\
+    \hline
     AWS-41  & 325.15$\pm$6.50 & 3000  & 0.58 & 0.82 & 1.06\\
@@
 
-AWS-41 is identical between the two three channel options. In this second
-option, AWS-43 is set to have the same limits as AWS-44 in the four channel
-option. AWS-42 was then allowed to fill the frequency range between the two
-other channels, but keeping a gap of 200\,MHz on each side.
-
-The resulting weighting functions are exemplified in Fig.~\ref{fig:3bch:prel}.
-As expected, there is now a somewhat poorer match to 183\,GHz, most importantly
-the weighting function of AWS-43 ends up between the ones of AWS-35 and 36. The
-weighting function of AWS-42 is slightly moved upwards compared to the first
-three channel option.
-
-\begin{figure}[!tb]
+\begin{figure}[!p]
   \centering
@@
 
+\subsection{A second three channel option}
+%
+Relatively late in the study Omnisys informed us about that an IF of 1.7\,GHz
+should be avoided, as this frequency likely will be used for downlink of data.
+The four channel option needed just a marginal change to adopt to this
+constrain, while 1.7\,GHz is more or less at the centre of the three channel
+option. It was then decided to formulate second three channel option avoiding 
+1.7\,GHz, and the suggestion is found in Table~\ref{tab:chs:3b}.
+
+AWS-41 is identical between the two three channel options. In this second
+option, AWS-43 is set to have the same limits as AWS-44 in the four channel
+option. AWS-42 was then allowed to fill the frequency range between the two
+other channels, but keeping a gap of 200\,MHz on each side.
+
+The resulting weighting functions are exemplified in Fig.~\ref{fig:3bch:prel}.
+As expected, there is now a somewhat poorer match to 183\,GHz, most importantly
+the weighting function of AWS-43 ends up between the ones of AWS-35 and 36. The
+weighting function of AWS-42 is slightly moved upwards compared to the first
+three channel option.
+
 \section{Cloud correction by a simple scheme}
@@
 %
-In this section, the 325\,GHz three channel option is evaluated for detection
+In this section, the (first) 325\,GHz three channel option is evaluated for detection
 and correction of cloud interference in 183\,GHz channels. Combinations of
@@
 
-The combinations of C1 and C2 are selected by matching their weighting
-functions as shown in Fig.~\ref{fig:3ch:prel}. Five 183\,GHz and 325\,GHz paired
-combinations are possible, for example one such paired combination is AWS-34
-and AWS-42.
+The combinations of C1 and C2 are selected by finding best match between
+weighting functions. Five 183\,GHz and 325\,GHz combinations are possible, for
+example one such paired combination is AWS-34 and AWS-42.
 
@@
 \begin{equation}
-x_{cs} = f_{cs}^{-1}(dtb_{cs}) 
+x_{cs} = f_{cs}^{-1}(dtb_{cs}).
 \label{eq:dtb}
@@
 measurements from C1 using data from C2. Without the availability of actual
-data, the simulation dataset but with noise added is used mimic the measurements. The
-noise for individual channels is calculated according to
+data, the simulation dataset but with noise added is used mimic the
+measurements. The noise for individual channels is calculated according to
 Equation~\ref{eq:noise}. As an example, the results from the channel
-combination AWS-34 and AWS-42 are shown. The error in the
-predicted measurements is assessed as the deviation to corresponding noise-free
-clear-sky value.
-The average bias, standard deviation and the measure of skewness, of the deviations are also calculated.
-Skewness gives a measure of asymmetry of the probability distribution of deviations around its mean.
+combination AWS-34 and AWS-42 are shown. The error in the predicted
+measurements is assessed as the deviation to corresponding noise-free clear-sky
+value. The average bias, standard deviation and the skewness of the
+deviations are calculated. Skewness gives a measure of asymmetry of the
+probability distribution of deviations around its mean.
 
@@
 	\centering
-	\includegraphics[height=85mm]{PDF_corrected_AWS-34_AWS-42_allfits}
+	\includegraphics[height=100mm]{PDF_corrected_AWS-34_AWS-42_allfits}
 	\caption{Deviation of AWS-34 measurements to noise free clear-sky
@@
 	\end{tabular}
-	\caption{Bias, standard deviation (std), and measure of skewness of error distributions
-		shown in Figure~\ref{fig:correction:c34-42:fit}.The fraction rejected describes the percentage of cases which are removed.
-Results from three different fit models are shown: linear, quadratic and cubic.}
+	\caption{Bias, standard deviation (std), and measure of skewness of error
+      distributions shown in Figure~\ref{fig:correction:c34-42:fit}. The
+      fraction rejected describes the percentage of cases which are removed.
+      Results from three different fit models are shown: linear, quadratic and
+      cubic.}
 	\label{tab:correction:stats:34:42:allfits}
@@
 \begin{figure}[!tb]
-	\centering
-	\includegraphics[height=85mm]{PDF_corrected_AWS-34_AWS-42_thinned}
+  \centering \includegraphics[height=100mm]{PDF_corrected_AWS-34_AWS-42_thinned}
 	\caption{Deviation of AWS-34 measurements to noise free clear-sky
@@
 %
-\begin{table}[!tb]
+\begin{table}[!p]
 	\centering
@@
 \end{tabular}
-\caption{Bias, standard deviation (std), and measure of skewness of the
-	error distributions of datasets shown in Figure~\ref{fig:correction:c34-42:thinned}.}
+\caption{Bias, standard deviation (std), and measure of skewness of the error
+  distributions of datasets shown in
+  Figure~\ref{fig:correction:c34-42:thinned}.}
 \label{tab:correction:stats:34:42:thinned}
@@
 \subsection{Application of correction scheme using AWS-4X}
-%
-\begin{figure}[!t]
-	\centering
-	\includegraphics[height=85mm]{PDF_corrected_AWS-32_AWS-4X_thinned}
-	\caption{Same as Fig.~\ref{fig:correction:c34-42:thinned}, but for channel combinations AWS-32 and AWS-4X. The dataset ``corrected 2$\sigma$'' is not shown.  }
-	\label{fig:correction:c32-4X:thinned}
-\end{figure}
 %
@@
 are corrected, the total bias increases to 0.88\,K. The unusually high fraction
-of cloudy cases and an increase in bias on correction suggests misclassification
-of clear cases as cloudy. Since, the weighting functions of AWS-32 and AWS-4X
-are poorly matched, their relationship is inadequate to estimate the cloud
-impact in AWS-32. Without any additional information, the regression approach
-can only provide a successful filtering in comparison to the original approach
-described by \citet{rekha2012potential}, although at the cost of high rejection
-fraction. Additional information e.g., TB from other channels, is necessary
-improve the accuracy of the correction.
-
-\begin{table}[!h]
+of cloudy cases and an increase in bias on correction suggests
+misclassification of clear cases as cloudy. Since, the weighting functions of
+AWS-32 and AWS-4X are poorly matched, their relationship is inadequate to
+estimate the cloud impact in AWS-32. Without any additional information, the
+regression approach can only provide a successful filtering in comparison to
+the original approach described by \citet{rekha2012potential}, although at the
+cost of high rejection fraction. Additional information seems necessary to improve
+the accuracy of the correction.
+
+\begin{figure}[!p]
+	\centering
+	\includegraphics[height=100mm]{PDF_corrected_AWS-32_AWS-4X_thinned}
+	\caption{Same as Fig.~\ref{fig:correction:c34-42:thinned}, but for channel combinations AWS-32 and AWS-4X. The dataset ``corrected 2$\sigma$'' is not shown.  }
+	\label{fig:correction:c32-4X:thinned}
+\end{figure}
+
+\begin{table}[!p]
 	\centering
@@
 	\end{tabular}
-	\caption{Same as Table~\ref{tab:correction:stats:34:42:thinned}, but for channel combinations: AWS-32 and AWS-4X.  }
+	\caption{Same as Table~\ref{tab:correction:stats:34:42:thinned}, but for
+      channel combinations: AWS-32 and AWS-4X. }
 	\label{tab:correction:stats:32:4X}
@@
 
-To develop the QRNN based correction scheme, we use the same dataset as in the simple scheme .
-Out of 125\,000 simulations, 90\% are used to train the model, while the rest 10\% is used to evaluate the model's performance during training.
-Presently we train QRNN for only nadir sensor viewing angle and the receiver noise $T_r$ = 1200\,K.
-In the training process, noise is added to the input according to Eqn~\ref{eq:noise}, every time the training data is exposed to the model.
-This ensures that the model is exposed to a new dataset on every iteration.
-Before training, the input data is normalized with mean and standard deviation.
-
-The structure of the QRNN is defined by various hyper-parameters which are tuned to achieve a high-performing model.
-These parameters determine the structure of the neural network and how the network is trained.
-We performed a grid search to determine structural parameters: depth (number of hidden layers) and width (number of neurons).
-The quantile loss on the validation set averaged over all predicted quantiles is used to compare the performance of different hyper-parameter configurations.
-Figure~\ref{fig:quantile_loss} shows the mean quantile loss when QRNN is trained for predicting clear-sky values for AWS-34 using four channel option.
-Increasing both layer width and depth has a positive impact on performance of the network, however for four hidden layers, increasing the layer width leads to only small performance gains.
-On basis of these results, a neural network with four hidden layers and 128 neurons was chosen.
-For the training, we obtained the best performance when trained with a multiple learning rate schedule.
-We start the training process with a initial learning rate and after a certain number of epochs, the training is updated with a new initial learning rate.
-We chose three training schedules with initial learning rates = 0.01, 0.001, 0.0001 respectively, updated after 20 epochs.
+To develop the QRNN based correction scheme, we use the same dataset as in the
+simple scheme . Out of 125\,000 simulations, 90\% are used to train the model,
+while the rest 10\% is used to evaluate the model's performance during
+training. Presently we train QRNN for only nadir sensor viewing angle and the
+receiver noise $T_r$ = 1200\,K. In the training process, noise is added to the
+input according to Eq.~\ref{eq:noise}, every time the training data are exposed
+to the model. This ensures that the model is exposed to a new dataset on every
+iteration. Before training, the input data is normalized with mean and standard
+deviation.
+
+The structure of the QRNN is defined by various hyper-parameters which are
+tuned to achieve a high-performing model. These parameters determine the
+structure of the neural network and how the network is trained. We performed a
+grid search to determine structural parameters: depth (number of hidden layers)
+and width (number of neurons). The quantile loss on the validation set averaged
+over all predicted quantiles is used to compare the performance of different
+hyper-parameter configurations. Figure~\ref{fig:quantile_loss} shows the mean
+quantile loss when QRNN is trained for predicting clear-sky values for AWS-34
+using four channel option. Increasing both layer width and depth has a positive
+impact on performance of the network, however for four hidden layers,
+increasing the layer width leads to only small performance gains. On basis of
+these results, a neural network with four hidden layers and 128 neurons was
+chosen. For the training, we obtained the best performance when trained with a
+multiple learning rate schedule. We start the training process with a initial
+learning rate and after a certain number of epochs, the training is updated
+with a new initial learning rate. We chose three training schedules with
+initial learning rates = 0.01, 0.001, 0.0001 respectively, updated after 20
+epochs.
 
@@
 Rectified Linear Unit (ReLU) was used as the activation function  and the batch size was set to 256 samples for all QRNN models.
-%
+
 \subsection{Prediction accuracy}
 %
+We train the QRNN to predict the quantiles $x_{\tau}$, for median, $\pm 1\sigma$, $\pm 2 \sigma$ and  $\pm 3 \sigma$ ($\tau$ = 0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998).
+The expectation value of the posterior distribution is assumed to be the best estimate for the predicted clear-sky value.
+To analyse the prediction accuracy, a testing dataset is constructed by randomly drawing 25\,000 cases from the simulation dataset.
+Noise is added to each simulation to mimic a new measurement dataset.
+
+The distributions of the predicted clear-sky noise-free values for each of the
+183\, GHz channels are shown in Figure~\ref{fig:pdf:qrnn}. The simulated
+clear-sky distributions are also plotted for reference. These results are from
+the four channel option. The distributions show that QRNN is overall successful in
+predicting the clear-sky cases. For all channels, the simulations and
+predictions have a good agreement for the main peak of the distribution.
+However, for AWS-32, AWS-33 and AWS-34, QRNN seems to predict slightly colder
+TBs. These results give an indication of the behavior of QRNN, but for a
+detailed analysis of the prediction accuracy, we make a quantitative assessment
+of the errors.
+
 \begin{figure}[!p]
@@
 \end{table}
-
-We train the QRNN to predict the quantiles $x_{\tau}$, for median, $\pm 1\sigma$, $\pm 2 \sigma$ and  $\pm 3 \sigma$ ($\tau$ = 0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998).
-The expectation value of the posterior distribution is assumed to be the best estimate for the predicted clear-sky value.
-To analyse the prediction accuracy, a testing dataset is constructed by randomly drawing 25\,000 cases from the simulation dataset.
-Noise is added to each simulation to mimic a new measurement dataset.
-
-The distributions of the predicted clear-sky noise-free values for each of the 183\, GHz channels are shown in Figure~\ref{fig:pdf:qrnn}.
-The simulated clear-sky distributions are also plotted for reference.
-These results are from four channel option.
-The distributions show that QRNN is overall successful in predicting the clear-sky cases.
-For all channels, the simulations and predictions have a good agreement for the main peak of the distribution.
-However, for AWS-32, AWS-33 and  AWS-34, QRNN seems to predict slightly colder TBs.
-These results give an indication of the behavior of QRNN, but for a detailed analysis of the prediction accuracy, we make a quantitative assessment of the errors.
 
@@
 Similar error statistics are also estimated for other 183\,GHz channels.
-Table~\ref{tab:qrnn:C32} provides the statistics for AWS-32.
-Before correction, the average bias and standard deviation with respect to noise free simulations is -1.343\,K and 5.908\,K respectively.
-However, after correction(four channel), the bias and standard deviation are -0.011\,K and 0.878\,K.
-The skewness in the error distributions is also reduced in the predictions (from -7.48 to -3.03).
-But a relatively high negative skewness in the predicted dataset indicates presence of uncorrected cloud impact.
-For AWS-32, option ``three-b'' has the lowest spread of errors, but the error distributions are more symmetric for option ``four''.
-
-Table~\ref{tab:qrnn:C33} shows the statistics for AWS-33.
-The standard deviation in the four channel option (0.591\,K) is lower than ``three-b''(0.612\,K), but the skewness in three-b in lower.
-This indicates that with four channel option, the QRNN predictions are mostly closer to the simulations, but few cases with large cloud impact are under predicted.
+Table~\ref{tab:qrnn:C32} provides the statistics for AWS-32. Before correction,
+the average bias and standard deviation with respect to noise free simulations
+is -1.343\,K and 5.908\,K respectively. However, after correction (four
+channel), the bias and standard deviation are -0.011\,K and 0.878\,K. The
+skewness in the error distributions is also reduced in the predictions (from
+-7.48 to -3.03). But a relatively high negative skewness in the predicted
+dataset indicates presence of uncorrected cloud impact. For AWS-32, option
+``three-b'' has the lowest spread of errors, but the error distributions are
+more symmetric for option ``four''.
+
+Table~\ref{tab:qrnn:C33} shows the statistics for AWS-33. The standard
+deviation in the four channel option (0.591\,K) is lower than
+``three-b''(0.612\,K), but the skewness in three-b in lower. This indicates
+that with four channel option, the QRNN predictions are mostly closer to the
+simulations, but few cases with large cloud impact are under-predicted.
 
@@
 
-Quantile regression can be used to construct a probability distribution of the predictions in comparison to simple regression models, which predict only a point estimate of the target.
-The outputs from QRNN model are subject to uncertainty which can be modeled by the prediction intervals.
-
-In our QRNN model, we estimate the conditional quantiles for  median, $\pm 1\sigma$, $\pm 2\sigma$, and $\pm 3\sigma$.
-The predictions for each quantile are used to construct the confidence intervals.
-The confidence interval for each point estimate is a way to quantify its uncertainty.
-For example, the predicted quantiles for $\pm 1 \sigma$ give 68\% probability that the true value will lie between the range.
-
-If the posterior distribution from QRNN follow normal distribution, the uncertainty can be estimated as a gaussian distribution centered around the median and standard deviation equal to the estimated error.
-To inspect if the predictions follow a normal distribution we evaluate the length of confidence intervals from the median.
-Figure~\ref{fig:prediction_uncertainty} shows the prediction uncertainty in AWS-34 (four channel option).
-The uncertainty with respect to the median for 1000 randomly selected cases is shown.
-The red line represents the uncertainty in a hypothetical Gaussian distribution  of $270\pm0.62$\,K.
-If the underlying distribution is Gaussian, the prediction uncertainty should be symmetric around the median, and the uncertainties should be equally spaced for $1\sigma$, $2\sigma$ and so on.
-The predictions from our QRNN model seem to be symmetric around the median for the 94\% confidence interval ($\pm 2 \sigma$).
-In other words, around 94\% of the true cases lie in the confidence interval given by $\pm 2\sigma$, and only 6\% of predictions are either too low or too high than the true value.
-The figure also shows that the uncertainties for all 1000 random cases are concentrated along a narrow width, thus suggesting that the case to case variability of the uncertainty is low.
-
-A similar uncertainty quantification for other 183\,GHz channels also gives similar results.
-Thus, assuming the posterior distribution to be gaussian between $\pm 2 \sigma$, the median is the measure of mean of the gaussian distribution, and the estimated error with respect to the true-value gives the spread of the distribution.
+Quantile regression can be used to construct a probability distribution of the
+predictions in contrast to simple regression models, which predict only a point
+estimate of the target. In our QRNN model, we estimate the conditional
+quantiles for median, $\pm 1\sigma$, $\pm 2\sigma$, and $\pm 3\sigma$. The
+predictions for each quantile are used to construct the confidence intervals.
+The confidence interval for each point estimate is a way to quantify its
+uncertainty. For example, the predicted quantiles for $\pm 1 \sigma$ give 68\%
+probability that the true value will lie between the range.
+
+To inspect if the predictions follow a normal distribution we evaluate the
+length of confidence intervals from the median.
+Figure~\ref{fig:prediction_uncertainty} shows the prediction uncertainty in
+AWS-34 (four channel option). The uncertainty with respect to the median for
+1000 randomly selected cases is shown. The red line represents the uncertainty
+in a hypothetical Gaussian distribution of $270\pm0.62$\,K. If the underlying
+distribution is Gaussian, the prediction uncertainty should be symmetric around
+the median, and the uncertainties should be equally spaced for $1\sigma$,
+$2\sigma$ and so on. The predictions from our QRNN model seem to be symmetric
+around the median for the 94\% confidence interval ($\pm 2 \sigma$). The figure
+also shows that the uncertainties for all 1000 random cases are concentrated
+along a narrow width, thus suggesting that the case to case variability of the
+uncertainty is low. A similar uncertainty quantification for other 183\,GHz
+channels also gives similar results.
 
@@
 \end{table} 
-We also tested the QRNN model to predict cloud-free TBs by using measurements from AWS-4X and AWS-32 as input.
-In this case, we trained QRNN with measurements from AWS-32 and AWS-4X, to predict the clear-sky cloud free TBs for AWS-32.
-The model was trained as described in Section~\ref{sec:qrnn:training}, but slightly better training results were obtained with width as 256 neurons.
-Other structural and training parameters remain unchanged.
-
-Figure~\ref{fig:qrnn_C32_C4X:deviations} shows the error distributions for the differences between the predicted values and clear-sky simulations for AWS-32.
-The corresponding statistics are shown in Table~\ref{tab:qrnn:C32:C4X}.
-The results from QRNN model trained with four channel option of 325\,GHz are also shown for comparison.
-
-The average deviation of the uncorrected measurements to noise-free clear-sky simulations is -1.343\,K and the standard deviation is 5.908\,K.
-When trained with AWS-4X, the predictions are not very successful in alleviating the cloud impact.
-Although, the error standard deviation of the predicted dataset is lower, a large negative skewness (-4.085\,K) indicates significantly high uncorrected cloud impact.
-On the other hand, QRNN predictions trained with 325\,GHz data are also not completely cloud free, but have a slightly better accuracy.
-The error standard deviation for the four channels option is 0.878\,K.
+We also tested the QRNN model to predict cloud-free TBs by using measurements
+from AWS-4X and AWS-32 as input. In this case, we trained QRNN with
+measurements from AWS-32 and AWS-4X, to predict the clear-sky cloud free TBs
+for AWS-32. The model was trained as described in
+Section~\ref{sec:qrnn:training}, but slightly better training results were
+obtained with width as 256 neurons. Other structural and training parameters
+remain unchanged.
+
+Figure~\ref{fig:qrnn_C32_C4X:deviations} shows the error distributions for the
+differences between the predicted values and clear-sky simulations for AWS-32.
+The corresponding statistics are shown in Table~\ref{tab:qrnn:C32:C4X}. The
+results from QRNN model trained with four channel option of 325\,GHz are also
+shown for comparison.
+
+The average deviation of the uncorrected measurements to noise-free clear-sky
+simulations is -1.343\,K and the standard deviation is 5.908\,K. When trained
+with AWS-4X, the predictions are not very successful in alleviating the cloud
+impact. Although, the error standard deviation of the predicted dataset is
+lower, a large negative skewness (-4.085) indicates significantly high
+uncorrected cloud impact. On the other hand, QRNN predictions trained with
+325\,GHz data are also not completely cloud free, but have a slightly better
+accuracy. The error standard deviation for the four channels option is
+0.878\,K.
 
@@
 \section{Sensitivity to different $T_r$}
+\label{sec:tr}
 %
@@
 
-For AWS-32, filtering based either AWS-4X or AWS-41 has a very high rejection rate, though the resulting dataset has low error.
-The high fraction of rejection can increase the probability of removing ``true'' clear cases.
-After correction, the error distributions are asymmetric and have large bias and standard deviation.
-Among the two combinations, the dataset corrected with AWS-41 has slightly better bias and standard deviation.
-As an exception to other 183\,GHz channels, the correction scheme for AWS-32 works better for $2\sigma$ threshold, as with a larger value of noise, relatively smaller number of cases are corrected.
-The effect of mismatch between weighting functions for AWS-32 and AWS-4X/41 is reflected in the performance of our correction scheme.
+For AWS-32, filtering based either AWS-4X or AWS-41 has a very high rejection
+rate, though the resulting dataset has low error. The high fraction of
+rejection can increase the probability of removing ``true'' clear cases. After
+correction, the error distributions are asymmetric and have large bias and
+standard deviation. Among the two combinations, the dataset corrected with
+AWS-41 has slightly better bias and standard deviation. As an exception to
+other 183\,GHz channels, the correction scheme for AWS-32 works better for
+$2\sigma$ threshold, as with a larger value of noise, relatively smaller number
+of cases are corrected. The effect of mismatch between weighting functions for
+AWS-32 and AWS-4X/41 is reflected in the performance of our correction scheme.
 
@@
 
-The results of \citet{rekha2012potential} is better than ours for AWS-32, while for the other 183\,GHz channels better results are obtained by using 325\,GHz data.
-However, when only pure-filtering is considered, our scheme performs better for AWS-32, albeit with a high rejection rate.
-For all later channels of 183\,GHz,  we reject only a small fraction of cases in comparison to \citet{rekha2012potential}, but the corrected datasets have symmetric error distributions with lower bias, standard deviations.
-Only for AWS-35 and AWS-36, the standard deviation and skewness of the corrected dataset is higher.
+The results of \citet{rekha2012potential} is better than ours for AWS-32, while
+for the other 183\,GHz channels better results are obtained by using 325\,GHz
+data. However, when only pure-filtering is considered, our scheme performs
+better for AWS-32, albeit with a high rejection rate. For all later channels of
+183\,GHz, we reject only a small fraction of cases in comparison to
+\citet{rekha2012potential}, but the corrected datasets have a more symmetric error
+distributions with lower bias and standard deviation. Only for AWS-35 and AWS-36,
+the standard deviation and skewness of the corrected dataset are higher.
 
@@
 \subsubsection{Performance of QRNN}
-In section~\ref{sec:qrnn} we use QRNN as a method for cloud correction based on 325\,GHz data.
-Measurements from all 325\,GHz channels and the 183\,GHz channel to be predicted are used to train the QRNN model.
-
-The results demonstrate that QRNN is successful in predicting the clear-sky noise free data for AWS-33, AWS-32, AWS-35 and AWS-36.
-The error distributions for the predictions symmetric and have low bias and standard deviation.
-Infact, for AWS-34, AWS-35 and AWS-36, the spread of errors is even smaller than the noise.
-QRNN seems to perform equally well with three configurations suggested for 325\,GHz channels.
-
-For AWS-32, the QRNN trained with 325\,GHz is only partially successful in reducing the impact of hyderometeors.
-The resulting error distributions have significantly lower spread than the measurements, but are still negatively skewed.
-Among the three combinations of 325\,GHz, the four channel option has slightly better performance.
-Since 325\,GHz cannot provide a full coverage for hydrometeor impact in AWS-32, QRNN cannot learn to predict cloud free values for instances which  lie outside the area of coverage.
-In order to compare the 229\,GHz channel with 325\,GHz, QRNN was also trained with AWS-4X to predict cloud free AWS-32 TBs.
-The performance of QRNN trained with AWS-4X is worse than training with 325\,GHz.
-The spread of error distributions is 1.5 times more than obtained with four channels option of 325\,GHz.
-
-\subsection{Technical implementation}
-
-\subsubsection{Shape of channel response functions}
-%
+In section~\ref{sec:qrnn} we use QRNN as a method for cloud correction based on
+325\,GHz data. Measurements from all 325\,GHz channels and the 183\,GHz channel
+to be predicted are used to train the QRNN model.
+
+The results demonstrate that QRNN is successful in predicting the clear-sky
+noise free data for AWS-33, AWS-32, AWS-35 and AWS-36. The error distributions
+for the predictions symmetric and have low bias and standard deviation. In
+fact, for AWS-34, AWS-35 and AWS-36, the spread of errors is even smaller than
+the noise. This is the case as a low fracion of the measurements have a
+significant cloud impact, and for clear sky situations the QRNN prediction can
+largely be seen as a weighted mean between the two channels. This averaging
+cancels out some of the noise in the two channels. QRNN seems to perform
+equally well with three configurations suggested for 325\,GHz channels.
+
+For AWS-32, the QRNN trained with 325\,GHz is only partially successful in
+reducing the impact of hyderometeors. The resulting error distributions have
+significantly lower spread than the measurements, but are still negatively
+skewed. Among the three combinations of 325\,GHz, the four channel option has
+slightly better performance. Since 325\,GHz cannot provide a full coverage for
+hydrometeor impact in AWS-32, QRNN cannot learn to predict cloud free values
+for instances which lie outside the area of coverage. In order to compare the
+229\,GHz channel with 325\,GHz, QRNN was also trained with AWS-4X to predict
+cloud free AWS-32 TBs. The performance of QRNN trained with AWS-4X is worse
+than training with 325\,GHz. The spread of error distributions is 1.5 times
+more than obtained with four channels option of 325\,GHz.
+
+\subsection{Technical recommendations}
+%
+
+\subsubsection{NE$\Delta$T requirement}
+%
+No critical dependency of the cloud correction to the 325\,GHz receiver noise
+temperature ($T_r$) was found (Sec.~\ref{sec:tr}). For example, for AWS-36 and
+the four channel option, the standard deviation only increased 0.85 from 0.7
+when increasing $T_r$ to 2400\,K from 1200\,K.
+
+ICI-5 has a width of 3\,GHz and has NE$\Delta$T requirement of 1.2\,K
+\citep{eriksson:towar:20}. From e.g.\ Table~\ref{tab:chs:3b} it can be
+understood that this scales to a requirement on $T_r$ of about 2700\,K (as
+3\,GHz bandwidth and $T_r=2400$\,K gives a noise of 1.06\,K).
+
+Combining the observations drawn in the two last paragraphs it seems reasonable
+to set the NE$\Delta$T requirements for AWS 325\,GHz channels to match a $T_r$
+of about 2400\,K. The resulting NE$\Delta$T values provide a sufficient basis
+for an accaptable cloud correction and they still represent a step forward
+compared to ICI. However, if the present ambition of Omnisys of $T_r=1200$\,K
+will be reached, AWS should provide much less noisy 325\,GHz observations than
+ICI.
+
+\subsubsection{Channel specifications}
+%
+We formed three tentative 325\,GHz channel options. All three options were
+considered only in the QRNN part as it is difficult to maintain the full
+information of all channels in a simple regression based scheme. None of the
+three options gave consistently best results, and it is not possible to give a
+clear recommendation. For this reason we did not see any value in testing
+further options.
+
+ICI has three 325\,GHz channels around 325.15\,GHz, but as AWS is a sounder and
+could have a cons
+
 The simulations have assumed rectangularly shaped response functions. This was
@@
 implementation, i.e.\ to decrease the demand on very sharp transitions from high
-to low response. We have assumed that 100\,MHz is sufficient in the lower end
-of the IF-range and 200\,MHz in the upper part. If found necessary we don't see
+to low response. ***** If found necessary we don't see
 any problem in increasing the gaps, beside that the bandwidth decreases and the

### 2020-06-21 Report/aws_325ghz_study.tex
revised statistics Sreerekha et al

@@
 
+\subsection{Dataset formed}
+%
+Using the simulation setup described in previous section, we simulated 125460 cases based on randomly selected CloudSat orbits during August 2015. The input data
+were restricted between $60^{\degree}$S to $60^{\degree}$N.
+We simulated both clear-sky and all-sky scenarios , and no differentiation was made between the observations over water and land.
+The simulations were generated for sensor viewing angles from $0^\circ$ to $45^\circ$, but all the results described in this report are based on nadir viewing angle.
+
+Since in this study, the cases with cloud impact are extremely important, we used ``clear-sky thinning'' to improve the representation of the cloudy cases in the dataset.
+Thinned dataset is a subset of the full dataset with 50\% of the clear-sky cases removed.
+The size of the thinned dataset is different for each channel.
+
 \subsection{Validation of simulations}
@@
 %
-Using the simulation setup described above, around 77000 cases [* Is this the
-correct final number? *] were simulated
-based on randomly selected CloudSat orbits during August 2015. The input data
-were restricted between $60^{\degree}$S to $60^{\degree}$N. No differentiation
-was made between the observations over water and land.
-
 \begin{figure}[p]
@@
 dataset will be considered in parallel below, to ensure that no fraction of the
-``cloudy'' cases is not underrepresentated in the results.
-
-\subsection{Dataset formed}
-%
-[* Describe here briefly the final set of simulations used below. Number of
-cases, with and without thinng. Latiude range. If the full dataset was used for
-ATMS comparsion, switch place between 3.3 and 3.4. Probably easiest to say that
-all results below are for nadir. Otherwise this has to be clarified for the
-simple scehem. *]
+``cloudy'' cases is not underrepresented in the results.
 
@@
 Figure~\ref{fig:correction:c34-42:thinned} shows the deviation of the uncorrected and
-corrected measurements to their noise-free clear-sky values for the thinned dataset. The results from
-\cite{rekha2012potential} are also shown as reference (see Sec.~\ref{sec:rekha}
+corrected measurements to their noise-free clear-sky values for the thinned dataset. The results from \cite{rekha2012potential} are also shown as reference (see Sec.~\ref{sec:rekha}
 for our assumptions). In order to allow a more direct comparison of our
@@
 	corrected($2\sigma$) 	&  -0.11 &  0.75 &              -0.69 &                4.99 \\
-	sreerekha et al   		&  -0.20 &  0.78 &              -1.00 &               45.36 \\			
+	sreerekha et al         &  -0.16 &  0.71 &              -0.46 &               46.37 \\			
 		\hline
@@
 skewness in the distribution is due to cloud impacts which pass through the
-clear-sky threshold. The higher skewness in ``Sreerekha et al'' is mainly
-beacuse their method only aims at removing cloud impacts above 4\,K.
-Their approach also leads to a high rejection fraction (45.36\%). The filtering
+clear-sky threshold.
+The skewness in ``Sreerekha et al'' is higher than our approach because their method only aims at removing cloud impacts above 4\,K.
+Their approach also leads to a high rejection fraction (46.37\%).
+The filtering
 method introduced here leads to a considerable lower rejection of data
@@
 from -2.25\,K to -0.21\,K, while with the approach from
-\citet{rekha2012potential} only 45.36\% of the data is rejected and the average
-bias reduces to -0.41\,K. When all the cloudy cases, except the ``too cloudy'',
+\citet{rekha2012potential} only 46.37\% of the data is rejected and the average
+bias reduces to -0.32\,K. When all the cloudy cases, except the ``too cloudy'',
 are corrected, the total bias increases to 0.88\,K. The unusually high fraction
@@
 corrected($2\sigma$) 	&   0.76 &  1.80 &              -1.07 &                5.35 \\
-sreerekha et al   		&  -0.41 &  1.00 &              -2.54 &               45.36 \\
+sreerekha et al   		&  -0.32 &  0.78 &              -1.94 &               46.37 \\
 		\hline
@@
 		corrected($2\sigma$) 	&   0.25 &  1.72 &             -13.86 &                7.93 \\
-		sreerekha et al   		&  -0.41 &  1.00 &              -2.54 &               45.36 \\
+		 sreerekha et al   		&  -0.32 &  0.78 &              -1.94 &               46.37 \\
 		\hline
@@
 		corrected($2\sigma$) 	&  -0.11 &  0.57 &              -1.17 &                6.88 \\
-		sreerekha et al   		&  -0.29 &  0.78 &              -2.22 &               45.36 \\
+		sreerekha et al         &  -0.23 &  0.65 &              -1.52 &               46.37 \\
 		\hline
@@
 		corrected($2\sigma$)  &  -0.09 &  0.83 &              -2.35 &                2.86 \\
-		sreerekha et al  	  &  -0.13 &  0.70 &              -0.54 &               45.36 \\
+		sreerekha et al       &  -0.11 &  0.67 &              -0.22 &               46.37 \\
 		\hline
@@
 		corrected($2\sigma$) &  -0.11 &  0.94 &              -0.19 &                2.50 \\
-		sreerekha et al 	 &  -0.09 &  0.91 &              -0.10 &               45.36 \\
+		sreerekha et al      &  -0.08 &  0.90 &              -0.02 &               46.37 \\
 		\hline
@@
 Table~\ref{tab:correction:stats:32:41} shows the statistics when AWS-32 is
-corrected using AWS-41. The statistics of the filtered dataset are better than
-the approach by \cite{rekha2012potential}, while the corrected data have poorer
+corrected using AWS-41. The bias and standard deviation of the filtered dataset are better than
+the approach by \cite{rekha2012potential}. However, the results from ``sreerekha et al'' have lower skewness. After correction, the corrected data have poorer
 statistics. This is not surprising as the weighting function match between

### 2020-06-22 DoF/DoF.py
DoF updated script

@@ -11,15 +11,25 @@ import os
 from TB_aws import TB_AWS
 
 channels = ['C21','C31', 'C32', 'C33', 'C34', 'C35', 'C36', 'C41', 'C42', 'C43']
-Y = TB_AWS(os.path.expanduser('~/Dendrite/Projects/AWS-325GHz/TB_AWS/TB_AWS_m60_p60.nc'),
-           inChannels = channels, option = "3a", T_rec = None)
+channels = ['C21','C31', 'C32', 'C33', 'C34', 'C35', 'C36', 'C41', 'C42', 'C43','C44']
+#channels = ['C21','C31', 'C32', 'C33', 'C34', 'C35', 'C36', 'C4X']
+Y = TB_AWS(os.path.expanduser('~/Dendrite/Projects/AWS-325GHz/TB_AWS/TB_AWS_m60_p60_four.nc'),
+           inChannels = channels, 
+           option     = "4", 
+           T_rec      = None, 
+           all_cases  = False,
+           cloudy     = False,
+           clear      = True)
 
-Y.get_cloudy()
+
 noise = Y.add_noise(Y)
+    
+#print (noise)
 U, S, V = Y.svd()
-S_l = Y.get_S_lambda( U, noise)
+S_l = Y.get_S_lambda(U, noise)
 
 S_y = Y.cov_mat()
 
 print(S_y.diagonal())
 print(S_l)
+

### 2020-06-22 Report/aws_325ghz_study.tex
tables for DoF

@@
     \hline
+    AWS-21  &  89.*** & 4000\\
     AWS-31  & 165.500 & 2800\\
@@
 
+\section{Degrees of freedom}
+%
+
+\begin{table}[!p]
+	\centering
+	\begin{tabular}[b]{c|c|c|c}
+		 325\,GHz & \multicolumn{3}{c}{DoF}   \\
+		 option &  $T_r = 1200 $\,K &   $T_r = 1800 $\,K &   $T_r = 2400$\,K \\
+		\hline
+		three-a &                8 &                7 &                7 \\
+		three-b &                8 &                8 &                6 \\
+		four    &                8 &                7 &                6 \\
+		\hline
+	\end{tabular}
+	\caption{The degrees of freedom for AWS with 325\,GHz channel. Both clear and cloudy cases are considered. Results for all three options of 325\,GHz and different $T_r$ are shown.    }
+	\label{tab:DoF:all}
+\end{table}
+
+\begin{table}[!p]
+	\centering
+	\begin{tabular}[b]{c|c|c|c}
+	325\,GHz & \multicolumn{3}{c}{DoF}   \\
+	option &  $T_r = 1200 $\,K &   $T_r = 1800 $\,K &   $T_r = 2400$\,K \\
+	\hline
+	three-a &                7 &                7 &                5 \\
+	three-b &                7 &                6 &                4 \\
+	four    &                6 &                5 &                4 \\
+	\hline
+\end{tabular}
+	\caption{Same as Table~\ref{tab:DoF:all}, but only for clear cases.}
+\label{tab:DoF:clear}
+\end{table}
+
+\begin{table}[!p]
+	\centering
+	\begin{tabular}[b]{c|c|c|c}
+	325\,GHz & \multicolumn{3}{c}{DoF}   \\
+	option &  $T_r = 1200 $\,K &   $T_r = 1800 $\,K &   $T_r = 2400$\,K \\
+		\hline
+		three-a &                8 &                8 &                8 \\
+		three-b &                8 &                8 &                8 \\
+		four    &                8 &                8 &                8 \\
+		\hline
+	\end{tabular}
+	\caption{Same as Table~\ref{tab:DoF:all}, but only for cloudy cases.  }
+	\label{tab:DoF:cloudy}
+\end{table}
+
+\begin{table}[!p]
+	\centering
+	\begin{tabular}[b]{c|c}
+		&   DoF \\
+		\hline
+		all    &      6        \\
+		clear  &      6        \\
+		cloudy &      6        \\
+		\hline
+	\end{tabular}
+	\caption{The degrees of freedom for AWS with 229\,GHz channel. }
+	\label{tab:DoF:4X}
+\end{table}
+
 \section{Discussion}

### 2020-06-24 Report/aws_325ghz_study.tex
added DoF section & Summary

@@
 %
-To be written \dots
+The main objective of this study is to demonstrate that channels around 325\,GHz can provide a basis for cloud filtering/correction of data measured around 183\,GHz.
+Previously, it was suggested that a channel at 229\,GHz to be used for cloud filtering.
+The 229\,GHz channel forms a part of the MicroWave Sounder (MWS) and  is used for cloud filtering of 183/,GHz.
+In this study, we investigate the possibility to use the 325\,GHz channels instead.
+The cloud impact of high altitude cirrus clouds is considerably higher in 325\,GHz.
+This makes it possible to estimate the low cloud impact at 183 GHz, even of the order of thermal noise and modelling uncertainties.
+
+On basis of the weighting functions of 183\,GHz, we suggest three specfications for 325\,GHz channels.
+The performance of all three options is evaluated.
+A channel specific simple regression was tested to estimate and correct the impact of hydrometeors in 183\,GHz channel.
+The advantage of this approach is that for each 183\,GHz the cloud adjustment can be quantified simply through a polynomial fit between the the cloud impact in 183\,GHz channel of concern  and brightness temperature differences between 183\,GHz and 325\,GHz.
+A similar regression scheme based on 229\,GHz, was also examined, but gave poor results.
+One drawback of the simple correction scheme is its channel specific approach, which cannot benefit from the other 325\,GHz channels available.
+In order to effectively use information from all 325\,GHz channels, we suggested a machine learning based approach for cloud correction.
+We used QRNN (Quantile Regression Neural Network ) to to correct the cloud impact in each 183\,GHz channel using measurements (noisy) from all available channels of 325\,GHz.
+All three options of 325\,GHz were evaluated, and the performance was comparable.
+For some channels, interestingly, the spread of errors was narrower than noise.
+Another advantage of using QRNN is that the cloud free values are predicted at different quantile levels, which helps in quantifying the case-specific uncertainty estimate.
+A similar QRNN model with 229\,GHz gave poor results.
+Also, no critical dependency to the 325\,GHz receiver noise temperature was observed.
+
+Ths study shows that combining measurements from 325\,GHz can provide a better cloud correction performance than 229\,GHz, and also with minimal rejection of data.
+The clear-sky predictions have error distributions which are symmetric with low bias and spread.
+Therefore, the NWP and standalone 1DVAR models that utilize the ``clear-sky'' data can greatly benefit from it.
+Also, in data assimilation systems, the case-specific uncertainty allows an effective selection of weights, thus significantly improving the impact of measurements.
+Another advantage of combining 183\,GHz and 325\,GHz for cloud correction is that NWP systems, which are not yet prepared for 325 GHz, could still benefit from the data early on.
 
@@
 To support the selection between 229 and 325\,GHz channels, this report
-investigates the possibility to use the later range in forming 183\,GHz data of
+investigates the possibility to use the latter range in forming 183\,GHz data of
 ``clear-sky'' character. That is, following \citet{rekha2012potential}, the
@@
 shape should be of no concern as long as the actual shape is well
-characterised.
+characterized.
 
@@
     \hline
-    AWS-21  &  89.*** & 4000\\
+    AWS-21  & \phantom{0}89.000 & 4000\\
     AWS-31  & 165.500 & 2800\\
@@
 hydrometeors, three habits are applied: Perpendicular 3-bullet rosette, Large
-plate aggregate and Large column aggregate. In the two later cases, the
+plate aggregate and Large column aggregate. In the last two cases, the
 aggregates are complemented with single crystal data to also cover smaller
@@
 Using the simulation setup described in previous section, we simulated 125460 cases based on randomly selected CloudSat orbits during August 2015. The input data
-were restricted between $60^{\degree}$S to $60^{\degree}$N.
-We simulated both clear-sky and all-sky scenarios , and no differentiation was made between the observations over water and land.
+were restricted between $60^{\degree}$S to $60^{\degree}$N, and surface is below 500\,m.
+Both clear-sky and all-sky scenarios were simulated, and no differentiation was made between the observations over water and land.
+24 monochromatic frequencies were used so that each channel could be represented with sufficient accuracy.
 The simulations were generated for sensor viewing angles from $0^\circ$ to $45^\circ$, but all the results described in this report are based on nadir viewing angle.
@@
 Since in this study, the cases with cloud impact are extremely important, we used ``clear-sky thinning'' to improve the representation of the cloudy cases in the dataset.
-Thinned dataset is a subset of the full dataset with 50\% of the clear-sky cases removed.
-The size of the thinned dataset is different for each channel.
+Thinned dataset is a subset of the full dataset with 50\% of the clear-sky cases removed (cloud impact $<$ 0.2\,K) The size of the thinned dataset is different for each channel.
 
@@
 %
+The information content analysis in the AWS is made by estimating the degrees of freedom (DoF) of the simulated measurements.
+The analysis is similar to the one described by  \citet{eriksson:towar:20} for ICI.
+
+Let $\mathbf{Y}$ be an ensemble of noise-free measurements, and $\textbf{E}$ and $\mathbf{\Lambda}$ be the corresponding eigenvectors and eigenvalues; then in the eigenvalue space, the covariance matrix $\mathbf{S_y}$ can be written as
+
+\begin{equation}
+\mathbf{S_y = E \Lambda E^T} 
+\end{equation}
+
+Similarly, the uncertainty due to thermal noise is
+\begin{equation}
+\mathbf{S_{\Lambda} = E S_{\epsilon} E^T }
+\end{equation}
+where, $\mathbf{S_{\epsilon}}$ is a diagonal matrix with NE$\Delta$T$^2$ as diagonal elements.
+The DoF is the number of diagonal elements of $\mathbf{\Lambda}$ greater than the $\mathbf{S_\Lambda}$.
+For further details see \citet{eriksson:towar:20}.
+
+To calculate the DoF, the ensemble of simulations from 89\,GHz, 166\,GHz, 183\,GHz are used along with 229\,GHz or 325\,GHz.
+All three options of 325\,GHz are considered.
+In order to compare the DoF for cloudy and clear cases, we divide the database into three parts: ``all'', ``clear'' and ``cloudy'.
+All cases with cloud impact greater than 1\,K in any of the 183\,GHz channels are classfied as ``cloudy'', otherwise they are classified as ``clear''.
+With this criteria, out of total 125460 cases, 12905 are classified as cloudy.
+
+Table~\ref{tab:DoF:all} shows the DoF with 325\,GHz when all cases are considered.
+For $T_r$ = 1200\,K, the DoF from all three options is 8, however, increase in receiver noise leads to a loss in the DoF.
+For $T_r$ = 2400\,K, the DoF for option three-a is 7, while for three-b and four, the DoF is 6.
+Table~\ref{tab:DoF:clear} and Table~\ref{tab:DoF:cloudy} show the DoF for clear-sky and cloudy cases respectively.
+For clear-sky situations, the DoF for option three-a and three-b is 7, while for option 4 it is 6.
+With increase in $T_r$, the weaker DoF are degraded.
+For $T_r$ = 2400\,K, we have only 5 DoF for option three-a and 4 for both option three-b and four.
+On the other hand, the presence of clouds increases the DoF significantly.
+For all three options, we have 8 DoF.
+Increase in noise has no effect on the DoF for cloudy cases.
+
+The channels of 325\,GHz are highly correlated with 183\,GHz for clear-sky conditions, thus there is a high redundancy in information between these two channels.
+Due to redundancy with 183\,GHz channel, we observe a reduction in the DoF for clear-sky conditions.
+However in cloudy situations, as the impact of clouds in 325\,GHz is higher, we observe a larger DoF.
+
+Table~\ref{tab:DoF:4X} gives the DoF, with 229\,GHz channel.
+The DoF is 6 for both clear and cloudy situations.
+This is consistent with the fact that 229\,GHz has no redundancy with the five 183\,GHz channels, but there exists some redundancy with the two window channels (89 and 166\,GHz).
 
@@
 fact, for AWS-34, AWS-35 and AWS-36, the spread of errors is even smaller than
-the noise. This is the case as a low fracion of the measurements have a
+the noise. This is the case as a low fraction of the measurements have a
 significant cloud impact, and for clear sky situations the QRNN prediction can
@@
 For AWS-32, the QRNN trained with 325\,GHz is only partially successful in
-reducing the impact of hyderometeors. The resulting error distributions have
+reducing the impact of hydrometeors. The resulting error distributions have
 significantly lower spread than the measurements, but are still negatively
@@
 of about 2400\,K. The resulting NE$\Delta$T values provide a sufficient basis
-for an accaptable cloud correction and they still represent a step forward
-compared to ICI. However, if the present ambition of Omnisys of $T_r=1200$\,K
+for an acceptable cloud correction and they still represent a step forward
+compared to IS However, if the present ambition of Omnisys of $T_r=1200$\,K
 will be reached, AWS should provide much less noisy 325\,GHz observations than
@@
 
-The simulations have assumed rectangularly shaped response functions. This was
+The simulations have assumed rectangular shaped response functions. This was
 done for simplicity and shall in no way be taken as an indication on that this
@@
 
-\subsubsection{Polarisation response}
-%
-Polarisation aspects have not been considered in full detail. Some polarisation
+\subsubsection{Polarization response}
+%
+Polarization aspects have not been considered in full detail. Some polarization
 is induced by the surface in the simulations, but hydrometeors are assumed to
-be totally randomly oriented and do not cause polarisation. To involve oriented
+be totally randomly oriented and do not cause polarization. To involve oriented
 particles was not possible due to the limited time allocated for the study.
 
-The basic recommendation would be to use the same polarisation response as far
+The basic recommendation would be to use the same polarization response as far
 as possible. If both quasi-horizontal and quasi-vertical bands must be applied,
-the recommendation prioritise to use the polarisation option for 183 and
-325\,GHz, to maintain a similar influence of polarisation between the bands.
+the recommendation prioritize to use the polarization option for 183 and
+325\,GHz, to maintain a similar influence of polarization between the bands.
 

### 2020-06-24 DoF/DoF.py

@@ -9,27 +9,69 @@ Created on Fri Jun 19 22:17:11 2020
 import numpy as np
 import os
 from TB_aws import TB_AWS
-
-channels = ['C21','C31', 'C32', 'C33', 'C34', 'C35', 'C36', 'C41', 'C42', 'C43']
-channels = ['C21','C31', 'C32', 'C33', 'C34', 'C35', 'C36', 'C41', 'C42', 'C43','C44']
-#channels = ['C21','C31', 'C32', 'C33', 'C34', 'C35', 'C36', 'C4X']
-Y = TB_AWS(os.path.expanduser('~/Dendrite/Projects/AWS-325GHz/TB_AWS/TB_AWS_m60_p60_four.nc'),
-           inChannels = channels, 
-           option     = "4", 
-           T_rec      = None, 
-           all_cases  = False,
-           cloudy     = False,
-           clear      = True)
+from tabulate import tabulate
 
 
-noise = Y.add_noise(Y)
+channels_3 =  ['C21','C31', 'C32', 'C33', 'C34', 'C35', 'C36', 'C41', 'C42', 'C43']
+channels_4 =  ['C21','C31', 'C32', 'C33', 'C34', 'C35', 'C36', 'C41', 'C42', 'C43', 'C44']
+channels_4X = ['C21','C31', 'C32', 'C33', 'C34', 'C35', 'C36', 'C4X']
+
+file_3a  = '~/Dendrite/Projects/AWS-325GHz/TB_AWS/TB_AWS_m60_p60.nc'
+file_3b  = '~/Dendrite/Projects/AWS-325GHz/TB_AWS/TB_AWS_m60_p60_three_b.nc'
+file_4  = '~/Dendrite/Projects/AWS-325GHz/TB_AWS/TB_AWS_m60_p60_four.nc'
+file_4X = '~/Dendrite/Projects/AWS-325GHz/TB_AWS/TB_AWS_m60_p60.nc'
+
+files    = [file_3a, file_3b,  file_4, file_4X]
+T_recs   = [None, 1, 2]
+channels = [channels_3, channels_3, channels_4, channels_4X]
+
+options = ["3a", "3b", "4", "3b"]
+
+
+all_cases = False
+cloudy    = True
+clear     = False
+
+DoF = np.zeros([4, 3])
+
+
+
+for i, (channel, file, option) in enumerate(zip(channels, files, options)):
+#    print (channel, file, option)
+    for j , T_rec in enumerate(T_recs):
+        
+ #       print (i, j,  T_rec)
[…]

### 2020-06-24 DoF/TB_aws.py

@@ -59,6 +59,7 @@ class TB_AWS():
         
         if clear:
             # subsets the vector Y, if only clear values are to be used
+            # a case is cloudy if cloud impact is greater than 1 K in any of 183GHz channels
             
             i_start = self.index_183[0]
             i_end   = self.index_183[-1]
@@ -75,8 +76,10 @@ class TB_AWS():
             
             i_start = self.index_183[0]
             i_end   = self.index_183[-1]
-            cloud_imp = np.abs(Y[1, i_start:i_end, :] - Y[0, i_start:i_end, :])
+            cloud_imp = np.abs(Y[1, i_start:i_end+1, :] - Y[0, i_start:i_end+1, :])
+
             icloud = cloud_imp >= 1.0
+ #           print(np.sum(icloud[:, :], axis = 1))
             icloud = np.any(icloud, axis = 0)
         
             self.Y = Y[1, :, icloud]
@@ -127,6 +130,7 @@ class TB_AWS():
 
         # for the channels we need        
         T_rec_subset = T_rec[self.index]
+        print(T_rec_subset)
 
         delta_f_subset = delta_f[self.index]
     
@@ -135,9 +139,15 @@ class TB_AWS():
             T_a = 250.0
             sigma = c * (T_rec_subset[ic] + T_a)/np.sqrt(delta_f_subset[ic] * delta_t)
 
-            noise.append(sigma ** 2)            
+            noise.append(sigma ** 2)        
+            
+        n = len(noise)
+        s_epsilon = np.zeros([n , n])
+        for i in range(n):
+            s_epsilon[i, i] = noise[i]
+        return s_epsilon   
 
-        return np.asarray(noise)          
+      
         
 
     def cov_mat(self):
@@ -171,7 +181,7 @@ class TB_AWS():
         """
         Y = self.Y - self.mean
 #        print (Y)
-        Y = np.transpose(Y)
+        Y = np.transpose(Y)/np.sqrt(self.n - 1)
         
         U, S, V = np.linalg.svd(Y, full_matrices = False)
         

### 2020-06-26 Report/aws_325ghz_study.tex
updated tables in DoF

@@
 A similar regression scheme based on 229\,GHz, was also examined, but gave poor results.
-One drawback of the simple correction scheme is its channel specific approach, which cannot benefit from the other 325\,GHz channels available.
+One drawback of the simple correction scheme is that channel specific approach limits the use of information from other 325\,GHz channels.
 In order to effectively use information from all 325\,GHz channels, we suggested a machine learning based approach for cloud correction.
@@
 \end{equation}
+
 where, $\mathbf{S_{\epsilon}}$ is a diagonal matrix with NE$\Delta$T$^2$ as diagonal elements.
@@
 All three options of 325\,GHz are considered.
+In this section, a new suggestion of option-3b is considered.
+The new option is mentioned in Table~\ref{tab:option3b:new}.
+
 In order to compare the DoF for cloudy and clear cases, we divide the database into three parts: ``all'', ``clear'' and ``cloudy'.
@@
 
+Fig~\ref{fig:DoF:clear:1200K} shows the ratio of $\Lambda/S_\Lambda$ with respect to the eigenvalue index for clear-sky cases.
+
 Table~\ref{tab:DoF:all} shows the DoF with 325\,GHz when all cases are considered.
-For $T_r$ = 1200\,K, the DoF from all three options is 8, however, increase in receiver noise leads to a loss in the DoF.
-For $T_r$ = 2400\,K, the DoF for option three-a is 7, while for three-b and four, the DoF is 6.
+For $T_r$ = 1200\,K, the DoF from all three options is around 8, however, increase in receiver noise leads to a loss in the DoF.
+For $T_r$ = 2400\,K, the DoF for option three-a is 7.8, while for three-b and four, the DoF is 7.7 and 6.2 respectively.
 Table~\ref{tab:DoF:clear} and Table~\ref{tab:DoF:cloudy} show the DoF for clear-sky and cloudy cases respectively.
-For clear-sky situations, the DoF for option three-a and three-b is 7, while for option 4 it is 6.
+For clear-sky situations, the DoF for option three-a and three-b is 7.3 and 7 respectively, while for option 4 it is 7.
 With increase in $T_r$, the weaker DoF are degraded.
-For $T_r$ = 2400\,K, we have only 5 DoF for option three-a and 4 for both option three-b and four.
+For $T_r$ = 2400\,K, we have only 5 DoF for option three-a and 4.8 for both option three-b and 4.9 for option four.
 On the other hand, the presence of clouds increases the DoF significantly.
-For all three options, we have 8 DoF.
-Increase in noise has no effect on the DoF for cloudy cases.
+For all three options, we have DoF around 8.
+Increase in noise has no significant effect on the DoF for cloudy cases.
 
@@
 Table~\ref{tab:DoF:4X} gives the DoF, with 229\,GHz channel.
-The DoF is 6 for both clear and cloudy situations.
+The DoF is 6.8 for both clear and cloudy situations.
 This is consistent with the fact that 229\,GHz has no redundancy with the five 183\,GHz channels, but there exists some redundancy with the two window channels (89 and 166\,GHz).
+
+\begin{figure}[!tb]
+	\centering
+	\includegraphics[height=80mm]{DoF.png}
+	\caption{ The ratio of $\Lambda/S_\Lambda$ with respect to the eigenvalue index for clear-sky cases. The black dotted line represents the level where the ratio is unity. }
+	\label{fig:DoF:clear:1200K}
+\end{figure}
 
@@
 		\hline
-		three-a &                8 &                7 &                7 \\
-		three-b &                8 &                8 &                6 \\
-		four    &                8 &                7 &                6 \\
+		three-a &              8.3 &              7.9 &              7.8 \\		
+		three-b &              8.5 &              8.2 &              7.7 \\		
+		four    &              8.2 &              7.8 &              6.2 \\
+
 		\hline
@@
 	\hline
-	three-a &                7 &                7 &                5 \\
-	three-b &                7 &                6 &                4 \\
-	four    &                6 &                5 &                4 \\
+		three-a &              7.3 &              7.1 &              5.0 \\		
+		three-b &              7.0 &              6.6 &              4.8 \\		
+		four    &              7.0 &              6.0 &              4.9 \\
+
 	\hline
@@
 		\hline
-		three-a &                8 &                8 &                8 \\
-		three-b &                8 &                8 &                8 \\
-		four    &                8 &                8 &                8 \\
+		three-a &              8.9 &              8.7 &              8.5 \\		
+		three-b &              8.9 &              8.8 &              8.7 \\		
+		four    &              8.7 &              8.5 &              8.3 \\
+
 		\hline
@@
 		\hline
-		all    &      6        \\
-		clear  &      6        \\
-		cloudy &      6        \\
+		all    &      6.8        \\
+		clear  &      6.8        \\
+		cloudy &      6.8        \\
 		\hline
@@
 
+\begin{table}[!p]
+	\centering
+	\begin{tabular}[b]{c|c|c|c|c}
+&	325\,GHz & \multicolumn{3}{c}{DoF}   \\
+&	option &  $T_r = 1200 $\,K &   $T_r = 1800 $\,K &   $T_r = 2400$\,K \\
+\hline
+			all &	four   &              8.2 &              7.8 &              6.2 \\
+				& four-a   &              8.3 &              8.0   &              6.1 \\
+
+\hline
+		clear  &	four  &                7.0 &              6.0 &              4.9 \\
+			   &   four-a &                7.0 &              6.4 &              4.9 \\
+
+\hline	
+		cloudy &	four  &              8.7 &              8.5 &              8.3 \\
+			   &   four-a &              8.8 &              8.6 &              8.4 \\
+\hline
+\end{tabular}
+\caption{The degrees of freedom for AWS with a 325GHz, new version .... }
+\label{tab:DoF:4X}
+\end{table}
 \section{Discussion}
@@
 
-\dots
+It is demonstrated that the 325\,GHz channels are capable of providing accurate cloud correction for 183\,GHz than the 229 \,GHz channel.
+The simple regression based approach is channel specific and involves only one of the 325\,GHz channel.
+
+In the second correction approach based on machine learning, QRNN is used to predict the clear-sky noise free values.
+The results show that QRNN are able to predict the clear-sky values with high accuracy.
+Another advantge of using QRNN is its ability to provide case-specific uncertainty estimates of predictions.
+In our study, the
 

### 2020-06-28 Report/aws_325ghz_study.tex
Started to extend summary

@@
 %
-The main objective of this study is to demonstrate that channels around 325\,GHz can provide a basis for cloud filtering/correction of data measured around 183\,GHz.
-Previously, it was suggested that a channel at 229\,GHz to be used for cloud filtering.
-The 229\,GHz channel forms a part of the MicroWave Sounder (MWS) and  is used for cloud filtering of 183/,GHz.
-In this study, we investigate the possibility to use the 325\,GHz channels instead.
-The cloud impact of high altitude cirrus clouds is considerably higher in 325\,GHz.
-This makes it possible to estimate the low cloud impact at 183 GHz, even of the order of thermal noise and modelling uncertainties.
-
-On basis of the weighting functions of 183\,GHz, we suggest three specfications for 325\,GHz channels.
-The performance of all three options is evaluated.
-A channel specific simple regression was tested to estimate and correct the impact of hydrometeors in 183\,GHz channel.
-The advantage of this approach is that for each 183\,GHz the cloud adjustment can be quantified simply through a polynomial fit between the the cloud impact in 183\,GHz channel of concern  and brightness temperature differences between 183\,GHz and 325\,GHz.
-A similar regression scheme based on 229\,GHz, was also examined, but gave poor results.
-One drawback of the simple correction scheme is that channel specific approach limits the use of information from other 325\,GHz channels.
-In order to effectively use information from all 325\,GHz channels, we suggested a machine learning based approach for cloud correction.
-We used QRNN (Quantile Regression Neural Network ) to to correct the cloud impact in each 183\,GHz channel using measurements (noisy) from all available channels of 325\,GHz.
-All three options of 325\,GHz were evaluated, and the performance was comparable.
-For some channels, interestingly, the spread of errors was narrower than noise.
-Another advantage of using QRNN is that the cloud free values are predicted at different quantile levels, which helps in quantifying the case-specific uncertainty estimate.
-A similar QRNN model with 229\,GHz gave poor results.
-Also, no critical dependency to the 325\,GHz receiver noise temperature was observed.
-
-Ths study shows that combining measurements from 325\,GHz can provide a better cloud correction performance than 229\,GHz, and also with minimal rejection of data.
-The clear-sky predictions have error distributions which are symmetric with low bias and spread.
-Therefore, the NWP and standalone 1DVAR models that utilize the ``clear-sky'' data can greatly benefit from it.
-Also, in data assimilation systems, the case-specific uncertainty allows an effective selection of weights, thus significantly improving the impact of measurements.
-Another advantage of combining 183\,GHz and 325\,GHz for cloud correction is that NWP systems, which are not yet prepared for 325 GHz, could still benefit from the data early on.
-
-[* IK: Run spell check just before submitting * ]
+The main objective of this study is to demonstrate that channels around
+325\,GHz can provide a basis for cloud filtering/correction of data measured
+around 183\,GHz. Previously, it was suggested that a channel at 229\,GHz to be
+used for cloud filtering. The 229\,GHz channel forms a part of the MicroWave
+Sounder (MWS) and will be used for cloud filtering of 183\,GHz insde that
+mission. In this study, we investigate the possibility to use the 325\,GHz
+channels instead. The cloud impact of high altitude cirrus clouds is
+considerably higher in 325\,GHz and this makes it possible to estimate the weak
+cloud impact at 183 GHz with relatively good accuracy.
+
+On basis of the weighting functions of 183\,GHz, three specfications for
+325\,GHz channels were suggested. A channel specific simple regression was
+tested to estimate and correct the impact of hydrometeors in 183\,GHz channel.
+The advantage of this approach is that for each 183\,GHz the cloud adjustment
+can be quantified simply through a polynomial fit between the the cloud impact
+in 183\,GHz channel of concern and brightness temperature differences between
+183\,GHz and 325\,GHz. A similar regression scheme based on 229\,GHz was also
+examined, but gave poor results. One drawback of the simple correction scheme
+is its channel specific approach, which cannot benefit from the other 325\,GHz
+channels available. In order to effectively use information from all 325\,GHz
+channels, we suggested a machine learning based approach for cloud correction.
+We used QRNN (Quantile Regression Neural Network) to to correct the cloud
+impact in each 183\,GHz channel using measurements from all available channels
+of 325\,GHz. All three options of 325\,GHz were evaluated, and the performance
+was comparable. For some channels, interestingly, the spread of errors was
+narrower than the noise of the target 183\,GHz channel. Another advantage of
+using QRNN is that the cloud free values are predicted at different quantile
+levels, which helps in quantifying the case-specific uncertainty estimate. A
+similar QRNN model with 229\,GHz gave poor results. No critical dependency to
+the 325\,GHz receiver noise temperature was observed.
+
+This study shows that combining measurements from 325\,GHz can provide a better
+cloud correction performance than 229\,GHz, and also with minimal rejection of
+data. The clear-sky predictions have error distributions which are symmetric
+with low bias and spread. Therefore, the NWP and standalone 1DVAR models that
+utilize the ``clear-sky'' data can greatly benefit from it. Also, in data
+assimilation systems, the case-specific uncertainty allows an effective
+selection of weights, thus significantly improving the impact of measurements.
+Another advantage of combining 183\,GHz and 325\,GHz for cloud correction is
+that NWP systems, which are not yet prepared for 325 GHz, could still benefit
+from the data early on.
+
+The cloud correction analysis did not give a clear value on the relative merit
+of the suggested channel options and also the measurements' degree of freedom
+(DOF) was assessed based on the performed simulations. The DoF can be seen as a
+measure of the effective number of channels. The DOF analysis gave further
+support for selecting 325\,GHz in favour of 229\,GHz. The DOF of the 325\,GHz
+options is higher or equal to the 229\,Ghz one already in clear-sky
+conditions, while  for cloud conditions 325\,GHz consistently gives two
+additional degrees of freedom. That is, 325\,GHz clearly gives more rich
+informaion in cloudy conditions than 229\,GHz.
 

### 2020-06-28 Report/aws_325ghz_study.tex
A first complete version!?

@@
 
-\thispagestyle{empty}
+% \thispagestyle{empty}
+\pagenumbering{roman}
+
 \noindent
@@
 used for cloud filtering. The 229\,GHz channel forms a part of the MicroWave
-Sounder (MWS) and will be used for cloud filtering of 183\,GHz insde that
+Sounder (MWS) and will be used for cloud filtering of 183\,GHz inside that
 mission. In this study, we investigate the possibility to use the 325\,GHz
@@
 
-On basis of the weighting functions of 183\,GHz, three specfications for
+On basis of the weighting functions of 183\,GHz, three specifications for
 325\,GHz channels were suggested. A channel specific simple regression was
@@
 with low bias and spread. Therefore, the NWP and standalone 1DVAR models that
-utilize the ``clear-sky'' data can greatly benefit from it. Also, in data
+utilise the ``clear-sky'' data can greatly benefit from it. Also, in data
 assimilation systems, the case-specific uncertainty allows an effective
@@
 of the suggested channel options and also the measurements' degree of freedom
-(DOF) was assessed based on the performed simulations. The DoF can be seen as a
-measure of the effective number of channels. The DOF analysis gave further
-support for selecting 325\,GHz in favour of 229\,GHz. The DOF of the 325\,GHz
-options is higher or equal to the 229\,Ghz one already in clear-sky
-conditions, while  for cloud conditions 325\,GHz consistently gives two
-additional degrees of freedom. That is, 325\,GHz clearly gives more rich
-informaion in cloudy conditions than 229\,GHz.
-
+(DoF) was assessed based on the performed simulations. The DoF can be seen as a
+measure of the effective number of channels. The DoF analysis gave further
+support for selecting 325\,GHz in favour of 229\,GHz. The DoF of the 325\,GHz
+options is higher or equal to the 229\,GHz one already in clear-sky conditions,
+while for cloud conditions 325\,GHz consistently gives two additional degrees
+of freedom. Some additional 325\,GHz channel versions were considered in the DoF
+analysis.
+
+With 325\,GHz as a better option confirmed, the next step is to establish
+requirements for these channels. The study considered this question to some
+extent. The cloud correction simulations gave no clear constraints on the
+requirements, while the DoF analysis at least gave some indications. By
+comparison to the NE$\Delta$D requirements for ICI and DoF values derived, it
+is suggested to set threshold, target and breakthrough for the 325\,GHz
+receiver noise temperature to 2400, 1800 and 1200\,K, respectively. Regarding
+number, position and widths of channels, the differences between considered
+options are relatively small and at this point it seems reasonable to let
+technical considerations guide the basic selection between having three or four
+channels. Later, when the technical constraints (such as the IF range
+available) are better known an updated assessment should be performed to set
+the final channel values.
+
+\vspace{10mm}
 \setcounter{tocdepth}{1} 
@@
 \newpage
+\pagenumbering{arabic}
 \setcounter{page}{1}
@@
 considered and versions involving ``B-O tests'' are left for possible future
-studies. On the other hand, cloud correction of all AWS 183\,GHz channels are
-investigated. Another important difference is that our simulations aim to be a
-random sample of real situations, while the simulations of
-\citet{rekha2012potential} have a strong over-representation of cloudy
-cases.
+studies.
+%On the other hand, cloud correction of all AWS 183\,GHz channels are
+%investigated. Another important difference is that our simulations aim to be a
+%random sample of real situations, while the simulations of
+%\citet{rekha2012potential} have a strong over-representation of cloudy
+%cases.
 
@@
 If 183\,$\pm$7\,GHz is classified as cloudy, we assume that also the data from
-other 183\,GHz channels are rejected.
+the other 183\,GHz channels are rejected.
 
@@
 shape should be of no concern as long as the actual shape is well
-characterized.
+characterised.
 
@@
 shown. This PDF gives a fair match in the intermediate region (but gives an
-even higher overrepresentation at more strong cloud impacts). This smaller
+even higher over-representation at more strong cloud impacts). This smaller
 dataset will be considered in parallel below, to ensure that no fraction of the
@@
 varied between 0 and 0.5 (these fixed values are only applied in this section,
-the bulk simulations are using TESSEM and TELSEM for seting the surface
+the bulk simulations are using TESSEM and TELSEM for setting the surface
 properties). In the figures covering transmissivities and Jacobians, the
@@
   \end{tabular}
-  \caption{Tentative suggestion for a three 325\,GHz channels option. The
+  \caption{Tentative suggestion for a three 325\,GHz channels option (three-a). The
     values in the three last columns is the 1$\sigma$ noise level according to
@@
   \end{tabular}
-  \caption{The second three channel suggestion.}
+  \caption{The second three channel suggestion (three-b).}
   \label{tab:chs:3b}
@@
 
-\begin{figure}[!tb]
+\begin{figure}[!b]
 	\centering
@@
 -15\,K are ``too-cloudy'' and are rejected.
-To analyse the sensitivity of our scheme to noise threhold, as discussed in the previous section, results from two different values of $dtb_{cs}$ are shown.
+To analyse the sensitivity of our scheme to noise threshold, as discussed in the previous section, results from two different values of $dtb_{cs}$ are shown.
 For both values of $dtb_{cs}$ the corresponding clear-sky cut-off
@@
 The neural network training is a process of learning to predict the outputs {$y_i$} from inputs {$x_i$} through a series of learnable transformations.
-While training, neural networks seek to minimize the model error through a loss function.
+While training, neural networks seek to minimise the model error through a loss function.
 The choice of the loss function depends on the predictive problem.
-When a neural network is trained to minimize the mean of the quantile loss function to predict the quantiles of the distribution, it is called a Quantile Regression Neural Network (QRNN).
+When a neural network is trained to minimise the mean of the quantile loss function to predict the quantiles of the distribution, it is called a Quantile Regression Neural Network (QRNN).
 
@@
 \end{figure}
-In this section, QRNNs are used to correct the cloud impact in each of 183\,GHz channels using TBs measurements from all available channels of 325\,GHz.
-A separate QRNN is used for each of the 183\,GHz channels.
-For example, to predict clear-sky TBs from AWS-34, the training data is measurements from all channels of 325\,GHz and measurements from the 183\,GHz to be predicted.
-We assess the performance of the scheme using both three channel and four channel options of 325\,GHz.
-Two suggestions for three channel option are described in Sec.~\ref{sec:channel:configurations}, and both have been used to train QRNN separately.
-Thus, for each channel of 183\,GHz, we have a set of three predictions: one from four channel option, and two from the old and new configurations of the three channel option.
-Further in the text, the old and new three channel configurations are labeled as "three-a" and "three-b".
-
-To develop the QRNN based correction scheme, we use the same dataset as in the
+In this section, QRNNs are used to correct the cloud impact in each of 183\,GHz
+channels using TBs measurements from all available channels of 325\,GHz. A
+separate QRNN is used for each of the 183\,GHz channels. For example, to
+predict clear-sky TBs from AWS-34, the training data is measurements from all
+channels of 325\,GHz and measurements from the 183\,GHz to be predicted. We
+assess the performance of the scheme using both three channel and four channel
+options of 325\,GHz. Two suggestions for three channel option are described in
+Sec.~\ref{sec:channel:configurations}, and both have been used to train QRNN
+separately. Thus, for each channel of 183\,GHz, we have a set of three
+predictions: one from four channel option, and two from the old and new
+configurations of the three channel option. Further in the text, the old and
+new three channel configurations are labelled as "three-a" and "three-b".
+
+To develop the QRNN scheme, we use the same dataset as in the
 simple scheme . Out of 125\,000 simulations, 90\% are used to train the model,
@@
 The grid search was also conducted for both three channel options, and an identical QRNN structure, as described for the four channel option, was found to have the best performance.
-For QRNN models presented here, we did not optimize the type of activation function and batch size.
+For QRNN models presented here, we did not optimise the type of activation function and batch size.
 Rectified Linear Unit (ReLU) was used as the activation function  and the batch size was set to 256 samples for all QRNN models.
@@
 However, for AWS-32, AWS-33 and AWS-34, QRNN seems to predict slightly colder
-TBs. These results give an indication of the behavior of QRNN, but for a
+TBs. These results give an indication of the behaviour of QRNN, but for a
 detailed analysis of the prediction accuracy, we make a quantitative assessment
@@
 For AWS-35 (Table~\ref{tab:qrnn:C35}), the four channels option has the best performance.
-The average bias in QRNN predictions (four) is only 0.04\,K in comparsion to -0.42\,K for the measurements.
+The average bias in QRNN predictions (four) is only 0.04\,K in comparison to -0.42\,K for the measurements.
 Option ``three-b'' has lower skewness than option four, but the standard deviation is higher.
@@
 
-The average deviation of the uncorrected measurements to noise-free clear-sky
-simulations is -1.343\,K and the standard deviation is 5.908\,K. When trained
-with AWS-4X, the predictions are not very successful in alleviating the cloud
-impact. Although, the error standard deviation of the predicted dataset is
-lower, a large negative skewness (-4.085) indicates significantly high
-uncorrected cloud impact. On the other hand, QRNN predictions trained with
-325\,GHz data are also not completely cloud free, but have a slightly better
-accuracy. The error standard deviation for the four channels option is
-0.878\,K.
-
-Clearly, without additional information, QRNN cannot learn to predict cloud free values for AWS-32.
-As already seen in simple correction scheme, AWS-4X is not sufficient enough to characterize the effect of hydrometeors in AWS-32.
+When trained with AWS-4X, the predictions are not very successful in
+alleviating the cloud impact. Although, the error standard deviation of the
+predicted dataset is lower, a large negative skewness (-4.085) indicates
+significantly high uncorrected cloud impact. On the other hand, QRNN
+predictions trained with 325\,GHz data are also not completely cloud free, but
+have a slightly better accuracy. The error standard deviation for the four
+channels option is 0.878\,K.
+Clearly, without additional information, QRNN cannot learn to predict cloud
+free values for AWS-32. As already seen in simple correction scheme, AWS-4X is
+not sufficient enough to characterise the effect of hydrometeors in AWS-32.
 
@@
 %
-In the previous section, we presented the results from QRNN trained using the three suggestions of 325\,GHz proposed in section~\ref{sec:channel:configurations}.
-The receiver noise ($T_r$) was assumed to be 1200\,K for all cases.
-In this section, we explore the sensitivity of QRNN to a higher receiver noise.
-The QRNN training is repeated for all three suggestions of 325\,GHz, but with $T_r$ = 1800\,K and $T_r$ = 2400\,K.
-QRNN is trained with identical structural and training parameters as described earlier.
-Tables showing the statistics for error distributions for each channel are provided.
-Table~\ref{tab:qrnn:C32:Trec:1800} - Table~\ref{tab:qrnn:C36:Trec:1800} show the statistics for AWS-32, AWS-33, AWS-34, AWS-35 and AWS-36 respectively, when $T_r$ = 1800\,K.
-Similarly Table~\ref{tab:qrnn:C32:Trec:2400} - Table~\ref{tab:qrnn:C36:Trec:2400} show the statistics when $T_r$ = 2400\,K.
-
-For all channels, increase in the measurement noise increases the standard deviation of the predictions.
-For example, for AWS-34 (four channel option), the error standard deviation is 0.620\,K, 0.630\,K and 0.643\,K for $T_r$ = 1200\,K, 1800\,K and 2400\,K respectively.
-It is difficult to gauge the impact of increasing noise through bias and skewness of the error distributions, as the distribution can have a large spread, but still be symmetric with low bias and skewness.
-It is interesting to note that even for 1800\,K, the error standard deviation for predicted values for channels AWS-34, AWS-35 and AWS-36 is smaller than noise.
-This is in agreement with the results seen for $T_r$ = 1200\,K.
-However, for $T_r$ = 2400\,K, only AWS-36 follows the trend.
+In the previous section, we presented the results from QRNN trained using the
+three suggestions of 325\,GHz proposed in
+section~\ref{sec:channel:configurations}. The receiver noise ($T_r$) was
+assumed to be 1200\,K for all cases. In this section, we explore the
+sensitivity of QRNN to a higher receiver noise. The QRNN training is repeated
+for all three suggestions of 325\,GHz, but with $T_r$ = 1800\,K and $T_r$ =
+2400\,K. QRNN is trained with identical structural and training parameters as
+described earlier. Tables showing the statistics for error distributions for
+each channel are provided. Table~\ref{tab:qrnn:C32:Trec:1800} -
+Table~\ref{tab:qrnn:C36:Trec:1800} show the statistics for AWS-32, AWS-33,
+AWS-34, AWS-35 and AWS-36 respectively, when $T_r$ = 1800\,K. Similarly
+Table~\ref{tab:qrnn:C32:Trec:2400} - Table~\ref{tab:qrnn:C36:Trec:2400} show
+the statistics when $T_r$ = 2400\,K.
+
+For all channels, increase in the measurement noise increases the standard
+deviation of the predictions. For example, for AWS-34 (four channel option),
+the error standard deviation is 0.620\,K, 0.630\,K and 0.643\,K for $T_r$ =
+1200\,K, 1800\,K and 2400\,K respectively. It is difficult to gauge the impact
+of increasing noise through bias and skewness of the error distributions, as
+the distribution can have a large spread, but still be symmetric with low bias
+and skewness. It is interesting to note that even for 1800\,K, the error
+standard deviation for predicted values for channels AWS-34, AWS-35 and AWS-36
+is smaller than noise. This is in agreement with the results seen for $T_r$ =
+1200\,K. However, for $T_r$ = 2400\,K, only AWS-36 follows the trend.
 
@@
 %
-The information content analysis in the AWS is made by estimating the degrees of freedom (DoF) of the simulated measurements.
-The analysis is similar to the one described by  \citet{eriksson:towar:20} for ICI.
-
-Let $\mathbf{Y}$ be an ensemble of noise-free measurements, and $\textbf{E}$ and $\mathbf{\Lambda}$ be the corresponding eigenvectors and eigenvalues; then in the eigenvalue space, the covariance matrix $\mathbf{S_y}$ can be written as
+An information content analysis is made by estimating the degrees of freedom
+(DoF) of the simulated measurements. The analysis is similar to the one
+described by \citet{eriksson:towar:20} for ICI.
+
+Let $\mathbf{Y}$ be an ensemble of noise-free measurements, and $\textbf{E}$
+and $\mathbf{\Lambda}$ be the corresponding eigenvectors and eigenvalues; then
+in the eigenvalue space, the covariance matrix $\mathbf{S_y}$ can be written as
 
@@
 \end{equation}
-
 Similarly, the uncertainty due to thermal noise is
@@
 \end{equation}
-
-where, $\mathbf{S_{\epsilon}}$ is a diagonal matrix with NE$\Delta$T$^2$ as diagonal elements.
-The DoF is the number of diagonal elements of $\mathbf{\Lambda}$ greater than the $\mathbf{S_\Lambda}$.
-For further details see \citet{eriksson:towar:20}.
-
-To calculate the DoF, the ensemble of simulations from 89\,GHz, 166\,GHz, 183\,GHz are used along with 229\,GHz or 325\,GHz.
-All three options of 325\,GHz are considered.
-In this section, a new suggestion of option-3b is considered.
-The new option is mentioned in Table~\ref{tab:option3b:new}.
-
-In order to compare the DoF for cloudy and clear cases, we divide the database into three parts: ``all'', ``clear'' and ``cloudy'.
-All cases with cloud impact greater than 1\,K in any of the 183\,GHz channels are classfied as ``cloudy'', otherwise they are classified as ``clear''.
-With this criteria, out of total 125460 cases, 12905 are classified as cloudy.
-
-Fig~\ref{fig:DoF:clear:1200K} shows the ratio of $\Lambda/S_\Lambda$ with respect to the eigenvalue index for clear-sky cases.
-
-Table~\ref{tab:DoF:all} shows the DoF with 325\,GHz when all cases are considered.
-For $T_r$ = 1200\,K, the DoF from all three options is around 8, however, increase in receiver noise leads to a loss in the DoF.
-For $T_r$ = 2400\,K, the DoF for option three-a is 7.8, while for three-b and four, the DoF is 7.7 and 6.2 respectively.
-Table~\ref{tab:DoF:clear} and Table~\ref{tab:DoF:cloudy} show the DoF for clear-sky and cloudy cases respectively.
-For clear-sky situations, the DoF for option three-a and three-b is 7.3 and 7 respectively, while for option 4 it is 7.
-With increase in $T_r$, the weaker DoF are degraded.
-For $T_r$ = 2400\,K, we have only 5 DoF for option three-a and 4.8 for both option three-b and 4.9 for option four.
-On the other hand, the presence of clouds increases the DoF significantly.
-For all three options, we have DoF around 8.
-Increase in noise has no significant effect on the DoF for cloudy cases.
-
-The channels of 325\,GHz are highly correlated with 183\,GHz for clear-sky conditions, thus there is a high redundancy in information between these two channels.
-Due to redundancy with 183\,GHz channel, we observe a reduction in the DoF for clear-sky conditions.
-However in cloudy situations, as the impact of clouds in 325\,GHz is higher, we observe a larger DoF.
-
-Table~\ref{tab:DoF:4X} gives the DoF, with 229\,GHz channel.
-The DoF is 6.8 for both clear and cloudy situations.
-This is consistent with the fact that 229\,GHz has no redundancy with the five 183\,GHz channels, but there exists some redundancy with the two window channels (89 and 166\,GHz).
+where, $\mathbf{S_{\epsilon}}$ is a diagonal matrix with NE$\Delta$T$^2$ as
+diagonal elements. The DoF is the number of diagonal elements of
+$\mathbf{\Lambda}$ greater than the $\mathbf{S_\Lambda}$. For further details
+see \citet{eriksson:towar:20}.
+
+To calculate the DoF, the ensemble of simulations from 89\,GHz, 166\,GHz,
+183\,GHz are used along with 229\,GHz or 325\,GHz. In order to compare the DoF
+for cloudy and clear cases, we divide the database into three parts: ``all'',
+``clear'' and ``cloudy'. All cases with cloud impact greater than 1\,K in any
+of the 183\,GHz channels are classified as ``cloudy'', otherwise they are
+classified as ``clear''. With this criteria, out of total 125460 cases, 12905
+are classified as cloudy.
+
+As example, Fig~\ref{fig:DoF:clear:1200K} shows the ratio of
+$\Lambda/S_\Lambda$ with respect to the eigenvalue index for clear-sky cases.
+The DoF below is an interpolation between the last index having a ratio above
+one and next index.
 
@@
 	\includegraphics[height=80mm]{DoF.png}
-	\caption{ The ratio of $\Lambda/S_\Lambda$ with respect to the eigenvalue index for clear-sky cases. The black dotted line represents the level where the ratio is unity. }
+	\caption{ The ratio of $\Lambda/S_\Lambda$ with respect to the eigenvalue
+      index for clear-sky cases. The black dotted line represents the level
+      where the ratio is unity. }
 	\label{fig:DoF:clear:1200K}
 \end{figure}
+
+\subsection{DoFs for nominal IF range}
+
+At this point we got feedback from Omnisys that also channel option 3b is
+technically challenging. In short, it is significantly more difficult to
+implement a 3\,GHz wide channel at an IF of 3.3\,GHz (AWS-42) than compared to
+at 6.5\,GHz (AWS-41). To decrease the ratio between channel widths and centre
+IF, a third three channel option was formulated (Table~\ref{tab:chs:3c}) that
+is below denoted as three c. This option uses the same IF range as the
+previously suggested ones.
+
+\begin{table}[!p]
+  \centering  
+  \begin{tabular}[c]{c|c|c|ccc}
+    Channel & Frequency   & Bandwidth & $T_r=1200$\,K
+    & $T_r=1800$\,K & $T_r=2400$\,K\\
+    name    & [GHz] &  [MHz] & [K]  & [K] & [K]\\
+    \hline
+    AWS-41  & 325.15$\pm$6.25 & 3500  & 0.54 & 0.76 & 0.98\\
+    AWS-42  & 325.15$\pm$3.05 & 2500  & 0.64 & 0.90 & 1.16\\
+    AWS-43  & 325.15$\pm$1.20 & \phantom{0}800 & 1.12 & 1.59 & 2.06\\
+    \hline
+  \end{tabular}
+  \caption{The third three channel suggestion (three-c).}
+  \label{tab:chs:3c}
+\end{table}
+
+Table~\ref{tab:DoF:all} shows the DoF with 325\,GHz when all cases are
+considered. For $T_r$ = 1200\,K, the DoF from all four options is around 8,
+however, increase in receiver noise leads to a loss in the DoF.
+Table~\ref{tab:DoF:clear} and Table~\ref{tab:DoF:cloudy} show the DoF for
+clear-sky and cloudy cases respectively. For clear-sky situations, the DoFs are
+about 77. With increase in $T_r$, the DoF are degraded. For $T_r$ = 2400\,K, we
+have only 5 DoF for option three-a and 4.8 for both option three-b/c and 4.9
+for option four. On the other hand, the presence of clouds increases the DoF
+significantly. For all three options, we have DoF close to 9. Increase in noise
+has a lower effect on the DoF for cloudy cases.
+
+The DoF values should not be interpreted to strongly. There appears to be some
+``noise'' in the DoF, especially for higher noise. For example, in
+Table~\ref{tab:DoF:all} all the options have fairly similar DoF for
+$T_r=1800$\,K while for $T_r=2400$\,K there are considerable differences. This
+shift when going $T_r=2400$\,K is not observed in the two other tables. Having
+this in mind, it seems that options three b and c give very similar DoF. If
+something, option three-c seems slightly better. The four channel option
+obtains somewhat lower DoF than the three channel ones.
+
+Table~\ref{tab:DoF:4X} gives the DoF, with 229\,GHz channel. The DoF is 6.8 for
+both clear and cloudy situations. This is consistent with the fact that
+229\,GHz has no redundancy with the five 183\,GHz channels, but there exists
+some redundancy with the two window channels (89 and 166\,GHz).
 
@@
 		three-a &              8.3 &              7.9 &              7.8 \\		
-		three-b &              8.5 &              8.2 &              7.7 \\		
+		three-b &              8.5 &              8.2 &              6.0 \\		
+		three-c &              8.5 &              8.2 &              7.7 \\		
 		four    &              8.2 &              7.8 &              6.2 \\
-
-		\hline
-	\end{tabular}
-	\caption{The degrees of freedom for AWS with 325\,GHz channel. Both clear and cloudy cases are considered. Results for all three options of 325\,GHz and different $T_r$ are shown.    }
+		\hline
+	\end{tabular}
+	\caption{The degrees of freedom for AWS with 325\,GHz channel. Both clear
+      and cloudy cases are considered. Results for all three options of
+      325\,GHz and different $T_r$ are shown. }
 	\label{tab:DoF:all}
@@
 		three-a &              7.3 &              7.1 &              5.0 \\		
-		three-b &              7.0 &              6.6 &              4.8 \\		
+		three-b &              7.0 &              6.7 &              4.8 \\		
+		three-c &              7.0 &              6.6 &              4.8 \\		
 		four    &              7.0 &              6.0 &              4.9 \\
-
 	\hline
@@
 		three-a &              8.9 &              8.7 &              8.5 \\		
-		three-b &              8.9 &              8.8 &              8.7 \\		
+		three-b &              8.9 &              8.7 &              8.6 \\		
+		three-c &              8.9 &              8.8 &              8.7 \\		
 		four    &              8.7 &              8.5 &              8.3 \\
-
 		\hline
@@
 
-\begin{table}[!p]
+\subsection{Impact of extending the IF range}
+%
+As a basic investigation of the impact of changing the width of the IF range, a
+version of the four channel option was considered, denoted as four-b. It was
+modified to cover 0.7 to 9.0 GHz (instead of 0.7 to 8.0 GHz). To focus on the
+extension, only the edge channels were changed. That is, the revised AWS-41 and
+have bandwidth of 3.8 and 0.9\,GHz, respectively. The DoFs obtained for four-b
+are found in Table~\ref{tab:DoF:4b}.
+
+As expected a slight improvement of the DoF can be seen for four-b. The
+exception ``all'' and $T_r=2400$\,K, again likely an indication on some noise
+in the DoFs coming out of the analysis.
+
+That is, a broader IF range should give slightly better performance. If a
+broader IF range is feasible, the position and width of all channels should be
+revised, bit this is out of the scope of this study and anyhow hardly motivated
+before it is known more exactly to what extent the IF range can be extended.
+
+\begin{table}[!bt]
 	\centering
@@
 \end{tabular}
-\caption{The degrees of freedom for AWS with a 325GHz, new version .... }
-\label{tab:DoF:4X}
+\caption{The degrees of freedom for channel option four-b. Values for option
+  four are repeated from Tables~\ref{tab:DoF:all}-\ref{tab:DoF:clear}. }
+\label{tab:DoF:4b}
 \end{table}
@@
 
-The results of \citet{rekha2012potential} is better than ours for AWS-32, while
+The results of \citet{rekha2012potential} are better than ours for AWS-32, while
 for the other 183\,GHz channels better results are obtained by using 325\,GHz
@@
 The results demonstrate that QRNN is successful in predicting the clear-sky
-noise free data for AWS-33, AWS-32, AWS-35 and AWS-36. The error distributions
-for the predictions symmetric and have low bias and standard deviation. In
+noise-free data for AWS-33, AWS-34, AWS-35 and AWS-36. The error distributions
+for the predictions are symmetric and have low bias and standard deviation. In
 fact, for AWS-34, AWS-35 and AWS-36, the spread of errors is even smaller than
@@
 %
+The cloud correction and filtering results gave no clear indications on the
+requirements of the channels, and as a complement also the measurements' degree
+of freedom (DoF) were assessed. The later analysis gave a bit clearer
+indications and the discussion in this section is mainly based on the DoF results.
 
@@
 the four channel option, the standard deviation only increased 0.85 from 0.7
-when increasing $T_r$ to 2400\,K from 1200\,K.
+when increasing $T_r$ to 2400\,K from 1200\,K. The DoF showed a higher
+sensitivity to $T_r$, especially when going from 1800\,K to 2400\,K and only
+considering clear cases (Table~\ref{tab:DoF:clear}).
 
@@
 Combining the observations drawn in the two last paragraphs it seems reasonable
-to set the NE$\Delta$T requirements for AWS 325\,GHz channels to match a $T_r$
-of about 2400\,K. The resulting NE$\Delta$T values provide a sufficient basis
-for an acceptable cloud correction and they still represent a step forward
-compared to IS However, if the present ambition of Omnisys of $T_r=1200$\,K
-will be reached, AWS should provide much less noisy 325\,GHz observations than
-ICI.
+to set the threshold, target and breakthrough for NE$\Delta$T of AWS 325\,GHz
+channels to match a $T_r$ of 2400, 1800 and 1200\,K, respectively. The
+threshold value provide a sufficient basis for an acceptable cloud correction
+and still represents a step forward compared to ICI. However, if the present
+ambition of Omnisys of $T_r=1200$\,K will be reached, AWS will provide much
+less noisy 325\,GHz observations than ICI, representing a breakthrough.
 
@@
 %
-We formed three tentative 325\,GHz channel options. All three options were
+We formed three first 325\,GHz channel options. All three options were
 considered only in the QRNN part as it is difficult to maintain the full
@@
 clear recommendation. For this reason we did not see any value in testing
-further options.
-
-ICI has three 325\,GHz channels around 325.15\,GHz, but as AWS is a sounder and
-could have a cons
-
-The simulations have assumed rectangular shaped response functions. This was
-done for simplicity and shall in no way be taken as an indication on that this
-shape is required.
-
-We have left some frequency gaps between the channels to simplify the technical
-implementation, i.e.\ to decrease the demand on very sharp transitions from high
-to low response. ***** If found necessary we don't see
-any problem in increasing the gaps, beside that the bandwidth decreases and the
-NE$\Delta$T of the channel will somewhat increase.
-
-\subsubsection{Polarization response}
-%
-Polarization aspects have not been considered in full detail. Some polarization
+further options in this part.
+
+Some further channel options were included on the DoF analysis. Staying inside
+0.8\,-\,8.0\,GHz in terms of IF, the option three-c was found to have the
+highest overall DoF, but the differences to three-b and four are relatively
+small. However, it could be challenging to implement any of the three channel
+options. Option three-a risks to be affected by interference of the downlink
+and in options three-b and c there is a high ratio between bandwidth and centre
+IF of AWS-42. This aspect also makes it hard to extend options three-b and c if
+it would turn out that the IF range can be extended. A brief analysis showed
+that a broader IF range gives some increase in DoF, that potentially could
+improve the merit of the four channel option.
+
+We don't see how these results can be boiled down to threshold, target and
+breakthrough requirements. Option 3c came out best here, but the full
+optimisation of the options was made and a modified or extended four channel
+version could reach the same performance. In any case, the differences between
+the options are small and it seems reasonable to allow that  the technically
+most simple option is selected (that in fact can be the four channel one).
+When this selection is done and the technical constraints are better known (IF
+range available, needed frequent gaps between channels), an iteration of DoF
+analysis should be made to see if some ``optimisation'' of the channel
+specifications can be achieved.
+
+Further, the simulations have assumed rectangular shaped response functions.
+This was done for simplicity and shall in no way be taken as an indication on
+that this shape is required. We have left some frequency gaps between the
+channels to simplify the technical implementation, i.e.\ to decrease the demand
+on very sharp transitions from high to low response.
+
+\subsubsection{Polarisation response}
+%
+Polarisation aspects have not been considered in full detail. Some polarisation
 is induced by the surface in the simulations, but hydrometeors are assumed to
-be totally randomly oriented and do not cause polarization. To involve oriented
+be totally randomly oriented and do not cause polarisation. To involve oriented
 particles was not possible due to the limited time allocated for the study.
 
-The basic recommendation would be to use the same polarization response as far
+The basic recommendation would be to use the same polarisation response as far
 as possible. If both quasi-horizontal and quasi-vertical bands must be applied,
-the recommendation prioritize to use the polarization option for 183 and
-325\,GHz, to maintain a similar influence of polarization between the bands.
+the recommendation prioritise to use the polarisation option for 183 and
+325\,GHz, to maintain a similar influence of polarisation between the bands.
 
@@
 
-It is demonstrated that the 325\,GHz channels are capable of providing accurate cloud correction for 183\,GHz than the 229 \,GHz channel.
-The simple regression based approach is channel specific and involves only one of the 325\,GHz channel.
-
-In the second correction approach based on machine learning, QRNN is used to predict the clear-sky noise free values.
-The results show that QRNN are able to predict the clear-sky values with high accuracy.
-Another advantge of using QRNN is its ability to provide case-specific uncertainty estimates of predictions.
-In our study, the
+It is demonstrated that the 325\,GHz channels are capable of providing a more
+accurate cloud correction for 183\,GHz than the 229 \,GHz channel. The simple
+regression based approach evaluated is channel specific and involves the
+325\,GHz channel one at the time. In the second correction approach based on
+machine learning, QRNN is used to predict the clear-sky noise-free values
+throughout using all 325\,GHz in parallel. This seems to be a very useful
+approach. The QRNN predictions result in error distributions with low skewness
+and widths. In some case the prediction uncertainty is even lower than the
+noise of the 183\,GHz channel targeted. This approach should be ideal for
+making use of AWS in assimilation systems of clear-sky type.
+
+No results gave strong constraints for defining threshold, target and
+breakthrough requirements, but a suggestion is still given with respect to
+receiver noise temperature. The three requirements levels are suggested to be
+placed at 2400, 1800 and 1200\,K. On the other hand, the differences found
+between the tested three and four channel options are too small to motivate any
+clear recommendation. It seems reasonable to instead select between having
+three or four channels based on the technical challenges associated with each
+option and later setting the exact channel specifications.
 

### 2020-06-28 Report/aws_325ghz_study.tex
A few changes after a reading of the newest sections.

@@
 Sounder (MWS) and will be used for cloud filtering of 183\,GHz inside that
-mission. In this study, we investigate the possibility to use the 325\,GHz
-channels instead. The cloud impact of high altitude cirrus clouds is
-considerably higher in 325\,GHz and this makes it possible to estimate the weak
-cloud impact at 183 GHz with relatively good accuracy.
+mission. In this study, we investigate the possibility to use some 325\,GHz
+channels instead.
 
@@
 however, increase in receiver noise leads to a loss in the DoF.
-Table~\ref{tab:DoF:clear} and Table~\ref{tab:DoF:cloudy} show the DoF for
+Tables~\ref{tab:DoF:clear} and \ref{tab:DoF:cloudy} show the DoF for
 clear-sky and cloudy cases respectively. For clear-sky situations, the DoFs are
-about 77. With increase in $T_r$, the DoF are degraded. For $T_r$ = 2400\,K, we
+about 7. With increase in $T_r$, the DoF are degraded. For $T_r$ = 2400\,K, we
 have only 5 DoF for option three-a and 4.8 for both option three-b/c and 4.9
@@
 modified to cover 0.7 to 9.0 GHz (instead of 0.7 to 8.0 GHz). To focus on the
-extension, only the edge channels were changed. That is, the revised AWS-41 and
+extension, only the edge channels were changed. That is, the revised AWS-41 and AWS-43
 have bandwidth of 3.8 and 0.9\,GHz, respectively. The DoFs obtained for four-b
@@
 broader IF range is feasible, the position and width of all channels should be
-revised, bit this is out of the scope of this study and anyhow hardly motivated
+revised, but this is out of the scope of this study and anyhow hardly motivated
 before it is known more exactly to what extent the IF range can be extended.
@@
 requirements of the channels, and as a complement also the measurements' degree
-of freedom (DoF) were assessed. The later analysis gave a bit clearer
+of freedom (DoF) was assessed. The later analysis gave a bit clearer
 indications and the discussion in this section is mainly based on the DoF results.
@@
 %
-We formed three first 325\,GHz channel options. All three options were
-considered only in the QRNN part as it is difficult to maintain the full
+We formed three 325\,GHz channel options. All three options were
+considered first in the QRNN part as it is difficult to maintain the full
 information of all channels in a simple regression based scheme. None of the
@@
 and in options three-b and c there is a high ratio between bandwidth and centre
-IF of AWS-42. This aspect also makes it hard to extend options three-b and c if
+IF of AWS-42. The later aspect also makes it hard to extend options three-b and c if
 it would turn out that the IF range can be extended. A brief analysis showed
@@
 We don't see how these results can be boiled down to threshold, target and
-breakthrough requirements. Option 3c came out best here, but the full
-optimisation of the options was made and a modified or extended four channel
-version could reach the same performance. In any case, the differences between
-the options are small and it seems reasonable to allow that  the technically
-most simple option is selected (that in fact can be the four channel one).
-When this selection is done and the technical constraints are better known (IF
-range available, needed frequent gaps between channels), an iteration of DoF
-analysis should be made to see if some ``optimisation'' of the channel
-specifications can be achieved.
+breakthrough requirements. Option 3c came out best here, but no full
+optimisation of the options was made, and a modified or extended four channel
+version could possibly reach the same performance. In any case, the differences
+between the options are small and it seems reasonable to allow that the
+technically most simple option is selected (that in fact can be the four
+channel one). When this selection is done and the technical constraints are
+better known (IF range available, needed frequent gaps between channels etc.), an
+iteration of DoF analysis should be made to see if some ``optimisation'' of the
+channel specifications can be achieved.
 
@@
 channels to simplify the technical implementation, i.e.\ to decrease the demand
-on very sharp transitions from high to low response.
+on very sharp transitions from high to low response, but if gaps of 200\,MHz
+actually are required or if some overlap of the responses can be tolerated is
+not known to us.
 
@@
 
+\newpage
 \section{Conclusion}

### 2020-06-28 DoF/TB_aws.py
scripts to calculate DoF

@@ -96,7 +96,7 @@ class TB_AWS():
         
         Returns:
             
-            
+        S_epsilon, diagonal array with NEDT **2 as diagonal elements    
         """
         c = 1.2
         delta_t = 0.003
@@ -122,9 +122,19 @@ class TB_AWS():
             
         if self.option == "3b":
             bandwidth_325 = np.array([3000, 3000, 800])* 1e6    
-            
+
+        if self.option == "3c":
+            bandwidth_325 = np.array([3500, 2500, 800])* 1e6    
+
+        if self.option == "3d":
+            bandwidth_325 = np.array([4000, 3000, 900])* 1e6                
+
         if self.option == "4":
             bandwidth_325 = np.array([2800, 1800, 1200, 800])*1e6
+            
+        if self.option == "4a":
+            bandwidth_325 = np.array([3800, 1800, 1200, 900])*1e6     
+            
         delta_f = np.concatenate([bandwidth_89, bandwidth_165, bandwidth_183,
                                   bandwidth_229, bandwidth_325])
 

### 2020-06-28 DoF/DoF.py
scripts to calculate DoF

@@ -10,34 +10,56 @@ import numpy as np
 import os
 from TB_aws import TB_AWS
 from tabulate import tabulate
+import matplotlib.pyplot as plt
+from interpolate import interpolate_DoF
+from matplotlib.ticker import (MultipleLocator, FormatStrFormatter,
+                               AutoMinorLocator)
 
+plt.rcParams.update({'font.size': 16})
 
 channels_3 =  ['C21','C31', 'C32', 'C33', 'C34', 'C35', 'C36', 'C41', 'C42', 'C43']
 channels_4 =  ['C21','C31', 'C32', 'C33', 'C34', 'C35', 'C36', 'C41', 'C42', 'C43', 'C44']
 channels_4X = ['C21','C31', 'C32', 'C33', 'C34', 'C35', 'C36', 'C4X']
+T_recs   = [None, 1, 2]
 
 file_3a  = '~/Dendrite/Projects/AWS-325GHz/TB_AWS/TB_AWS_m60_p60.nc'
 file_3b  = '~/Dendrite/Projects/AWS-325GHz/TB_AWS/TB_AWS_m60_p60_three_b.nc'
+file_3c  = '~/Dendrite/Projects/AWS-325GHz/TB_AWS/TB_AWS_m60_p60_three_c.nc'
+file_3d  = '~/Dendrite/Projects/AWS-325GHz/TB_AWS/TB_AWS_m60_p60_three_d.nc'
 file_4  = '~/Dendrite/Projects/AWS-325GHz/TB_AWS/TB_AWS_m60_p60_four.nc'
+file_4a  = '~/Dendrite/Projects/AWS-325GHz/TB_AWS/TB_AWS_m60_p60_four_a.nc'
 file_4X = '~/Dendrite/Projects/AWS-325GHz/TB_AWS/TB_AWS_m60_p60.nc'
 
-files    = [file_3a, file_3b,  file_4, file_4X]
-T_recs   = [None, 1, 2]
+#=============================================================
+#options 3a, 3b, 4, 4X
+files    = [file_3a, file_3c,  file_4, file_4X]
 channels = [channels_3, channels_3, channels_4, channels_4X]
+options = ["3a", "3c", "4", "3b"]
 
-options = ["3a", "3b", "4", "3b"]
+#=============================================================
+# options 3c and 3d
+#options = ["4", "4a"]
+#files    = [file_4, file_4a]
+#channels = [channels_4, channels_4]
+#=============================================================
 
-
+T_recs = [None]
[…]

### 2020-06-28 Report/aws_325ghz_study.tex
updated minor changes in sec9/10

@@
 
-On basis of the weighting functions of 183\,GHz, three specifications for
-325\,GHz channels were suggested. A channel specific simple regression was
-tested to estimate and correct the impact of hydrometeors in 183\,GHz channel.
+On basis of the relative humidity (RH) weighting functions of 183\,GHz, three specifications for 325\,GHz channels were suggested.
+A channel specific simple regression was tested to estimate and correct the impact of hydrometeors in 183\,GHz channel.
 The advantage of this approach is that for each 183\,GHz the cloud adjustment
@@
 examined, but gave poor results. One drawback of the simple correction scheme
-is its channel specific approach, which cannot benefit from the other 325\,GHz
+is it's channel specific approach, which cannot benefit from the other 325\,GHz
 channels available. In order to effectively use information from all 325\,GHz
 channels, we suggested a machine learning based approach for cloud correction.
-We used QRNN (Quantile Regression Neural Network) to to correct the cloud
+We used QRNN (Quantile Regression Neural Network) to correct the cloud
 impact in each 183\,GHz channel using measurements from all available channels
@@
 support for selecting 325\,GHz in favour of 229\,GHz. The DoF of the 325\,GHz
-options is higher or equal to the 229\,GHz one already in clear-sky conditions,
+options is higher or equal to the 229\,GHz one, already in clear-sky conditions,
 while for cloud conditions 325\,GHz consistently gives two additional degrees
@@
 requirements, while the DoF analysis at least gave some indications. By
-comparison to the NE$\Delta$D requirements for ICI and DoF values derived, it
+comparison to the NE$\Delta$T requirements for ICI and DoF values derived, it
 is suggested to set threshold, target and breakthrough for the 325\,GHz
@@
 number, position and widths of channels, the differences between considered
-options are relatively small and at this point it seems reasonable to let
+options are relatively small and at this point, it seems reasonable to let
 technical considerations guide the basic selection between having three or four
@@
 pressure, temperature and volume mixing ratio profiles of various atmospheric
-gases. Five climatoligies were used: tropical (TRO), mid-latitude summer (MLS),
+gases. Five climatologies were used: tropical (TRO), mid-latitude summer (MLS),
 mid-latitude winter (MLW), sub-arctic summer (SAS), and sub-arctic winter
@@
 Since in this study, the cases with cloud impact are extremely important, we used ``clear-sky thinning'' to improve the representation of the cloudy cases in the dataset.
-Thinned dataset is a subset of the full dataset with 50\% of the clear-sky cases removed (cloud impact $<$ 0.2\,K) The size of the thinned dataset is different for each channel.
+Thinned dataset is a subset of the full dataset with 50\% of the clear-sky cases removed (cloud impact $<$ 0.2\,K).
+The size of the thinned dataset is different for each channel.
 
@@
 simulated. The ATMS channel widths are considered, but as AWS is only covering
-the lower wing of the 183\,GHz transition the upper sideband of ATMS is not
+the lower wing of the 183\,GHz transition the upper side-band of ATMS is not
 included.
@@
 In the intermediate region, the simulations have a lower occurrence rate. The
-impact of hydrometeors should be somewhat higher in the upper sideband of ATMS,
+impact of hydrometeors should be somewhat higher in the upper side-band of ATMS,
 which is not reflected in the simulations, but this is not sufficient to
@@
 dataset will be considered in parallel below, to ensure that no fraction of the
-``cloudy'' cases is not underrepresented in the results.
+``cloudy'' cases is not under-represented in the results.
 
@@
 configurations of the three channel option. Further in the text, the old and
-new three channel configurations are labelled as "three-a" and "three-b".
+new three channel configurations are labelled as ``three-a'' and ``three-b''.
 
 To develop the QRNN scheme, we use the same dataset as in the
-simple scheme . Out of 125\,000 simulations, 90\% are used to train the model,
+simple scheme . Out of 125\,460 simulations, 90\% are used to train the model,
 while the rest 10\% is used to evaluate the model's performance during
@@
 The expectation value of the posterior distribution is assumed to be the best estimate for the predicted clear-sky value.
-To analyse the prediction accuracy, a testing dataset is constructed by randomly drawing 25\,000 cases from the simulation dataset.
-Noise is added to each simulation to mimic a new measurement dataset.
+To analyse the prediction accuracy, a testing dataset was constructed by randomly drawing 25\,000 cases from the simulation dataset.
+Noise was added to each simulation to mimic a new measurement dataset.
 
@@
 	\caption{ Bias, standard deviation and measure of skewness for the error distributions of the dataset (AWS-34) shown in Figure~\ref{fig:qrnn_C34:deviations}.
-The labels "three-a", "three-b" correspond to the old and new suggestions of three channels options of 325\,GHz, and the label "four" represents the four channels option.}
+The labels ``three-a'', ``three-b'' correspond to the old and new suggestions of three channels options of 325\,GHz, and the label ``four'' represents the four channels option.}
 	\label{tab:qrnn:C34}
@@
 
-In an analogy between the results from the simple correction scheme and QRNN, we perform a similar error distribution analysis as in Section~\ref{sec:simple}.
+In an analogy between the results from the simple correction scheme and QRNN, we perform a similar error distribution analysis as in Sec.~\ref{sec:simple}.
 Figure~\ref{fig:qrnn_C34:deviations} shows the error distributions of the measurements and predicted clear-sky TBs for AWS-34 using three (three-b) and four channel options of 325\,GHz.
@@
 The statistics corresponding to these distributions are provided in Table~\ref{tab:qrnn:C34}.
-The fraction of cases rejected as "too-cloudy" is also provided under ``fraction rejected''.
+The fraction of cases rejected as ``too-cloudy'' is also provided under ``fraction rejected''.
 For AWS-34, average deviation in the predictions from all three QRNN models are comparable.
@@
 
-To inspect if the predictions follow a normal distribution we evaluate the
+To inspect if the predictions follow a normal distribution, we evaluate the
 length of confidence intervals from the median.
@@
 for AWS-32. The model was trained as described in
-Section~\ref{sec:qrnn:training}, but slightly better training results were
+Sec.~\ref{sec:qrnn:training}, but slightly better training results were
 obtained with width as 256 neurons. Other structural and training parameters
@@
 three suggestions of 325\,GHz proposed in
-section~\ref{sec:channel:configurations}. The receiver noise ($T_r$) was
+Sec.~\ref{sec:channel:configurations}. The receiver noise ($T_r$) was
 assumed to be 1200\,K for all cases. In this section, we explore the
@@
 	\end{tabular}
-	\caption{Error statistics for AWS-32, when the model is trained with $T_r$ = 1800\,K. The definitions of "three-a", "three-b" and "four" are same as described in Table~\ref{tab:qrnn:C34} }
+	\caption{Error statistics for AWS-32, when the model is trained with $T_r$ = 1800\,K. The definitions of ``three-a'', ``three-b'' and ``four'' are same as described in Table~\ref{tab:qrnn:C34} }
 	\label{tab:qrnn:C32:Trec:1800}
@@
 	\end{tabular}
-	\caption{ Error statistics for AWS-32, when the model is trained with $T_r$ = 2400\,K. The definitions of "three-a", "three-b" and "four" are same as described in Table~\ref{tab:qrnn:C34}  }
+	\caption{ Error statistics for AWS-32, when the model is trained with $T_r$ = 2400\,K. The definitions of ``three-a'', ``three-b'' and ``four'' are same as described in Table~\ref{tab:qrnn:C34}  }
 	\label{tab:qrnn:C32:Trec:2400}
@@
 
-As example, Fig~\ref{fig:DoF:clear:1200K} shows the ratio of
+As an example, Fig~\ref{fig:DoF:clear:1200K} shows the ratio of
 $\Lambda/S_\Lambda$ with respect to the eigenvalue index for clear-sky cases.
-The DoF below is an interpolation between the last index having a ratio above
+The DoF in the section below, is an interpolation between the last index having a ratio above
 one and next index.
@@
 
-At this point we got feedback from Omnisys that also channel option 3b is
+At this point we got a feedback from Omnisys that also channel option three-b is
 technically challenging. In short, it is significantly more difficult to
@@
 IF, a third three channel option was formulated (Table~\ref{tab:chs:3c}) that
-is below denoted as three c. This option uses the same IF range as the
+is below denoted as three-c. This option uses the same IF range as the
 previously suggested ones.
@@
 modified to cover 0.7 to 9.0 GHz (instead of 0.7 to 8.0 GHz). To focus on the
-extension, only the edge channels were changed. That is, the revised AWS-41 and AWS-43
+extension, only the edge channels were changed. That is, the revised AWS-41 and AWS-44
 have bandwidth of 3.8 and 0.9\,GHz, respectively. The DoFs obtained for four-b
@@
 As expected a slight improvement of the DoF can be seen for four-b. The
-exception ``all'' and $T_r=2400$\,K, again likely an indication on some noise
+exception ``all'' and $T_r=2400$\,K, again is likely an indication on some noise
 in the DoFs coming out of the analysis.
 
-That is, a broader IF range should give slightly better performance. If a
-broader IF range is feasible, the position and width of all channels should be
-revised, but this is out of the scope of this study and anyhow hardly motivated
-before it is known more exactly to what extent the IF range can be extended.
+The results indicate that a broader IF range should give slightly better performance.
+If a broader IF range is feasible, the position and width of all channels should be revised, but this is out of the scope of this study, and anyhow hardly motivated before it is known more exactly to what extent the IF range can be extended.
 
@@
       all &	four   &              8.2 &              7.8 &              6.2 \\
-      & four-a   &              8.3 &              8.0   &              6.1 \\
+      & four-b   &              8.3 &              8.0   &              6.1 \\
 
@@
       clear  &	four  &                7.0 &              6.0 &              4.9 \\
-      &   four-a &                7.0 &              6.4 &              4.9 \\
+      &   four-b &                7.0 &              6.4 &              4.9 \\
 
@@
       cloudy &	four  &              8.7 &              8.5 &              8.3 \\
-      &   four-a &              8.8 &              8.6 &              8.4 \\
+      &   four-b &              8.8 &              8.6 &              8.4 \\
       \hline
@@
 \subsubsection{Performance of QRNN}
-In section~\ref{sec:qrnn} we use QRNN as a method for cloud correction based on
+In Sec.~\ref{sec:qrnn} we use QRNN as a method for cloud correction based on
 325\,GHz data. Measurements from all 325\,GHz channels and the 183\,GHz channel
@@
 229\,GHz channel with 325\,GHz, QRNN was also trained with AWS-4X to predict
-cloud free AWS-32 TBs. The performance of QRNN trained with AWS-4X is worse
+cloud free AWS-32. The performance of QRNN trained with AWS-4X is worse
 than training with 325\,GHz. The spread of error distributions is 1.5 times
@@
 The cloud correction and filtering results gave no clear indications on the
-requirements of the channels, and as a complement also the measurements' degree
-of freedom (DoF) was assessed. The later analysis gave a bit clearer
-indications and the discussion in this section is mainly based on the DoF results.
+requirements of the channels, and as a complement, the measurements' degree
+of freedom (DoF) was also assessed. The latter analysis gave a bit clearer
+indication and the discussion in this section is mainly based on the DoF results.
 
@@
 channels to match a $T_r$ of 2400, 1800 and 1200\,K, respectively. The
-threshold value provide a sufficient basis for an acceptable cloud correction
+threshold value provides a sufficient basis for an acceptable cloud correction
 and still represents a step forward compared to ICI. However, if the present
@@
 small. However, it could be challenging to implement any of the three channel
-options. Option three-a risks to be affected by interference of the downlink
-and in options three-b and c there is a high ratio between bandwidth and centre
-IF of AWS-42. The later aspect also makes it hard to extend options three-b and c if
-it would turn out that the IF range can be extended. A brief analysis showed
-that a broader IF range gives some increase in DoF, that potentially could
-improve the merit of the four channel option.
+options. The option three-a risks to be affected by interference of the downlink
+and in the options three-b and c there is a high ratio between bandwidth and centre IF of AWS-42.
+The latter aspect also makes it hard to extend options three-b and c, if it would turn out that the IF range can be extended.
+A brief analysis showed that a broader IF range gives some increase in DoF, that potentially could improve the merit of the four channel option.
 
 We don't see how these results can be boiled down to threshold, target and
-breakthrough requirements. Option 3c came out best here, but no full
-optimisation of the options was made, and a modified or extended four channel
+breakthrough requirements. Option three-c came out best here, but no full
+optimization of the options was made, and a modified or extended four channel
 version could possibly reach the same performance. In any case, the differences
-between the options are small and it seems reasonable to allow that the
+between the options are small, and it seems reasonable to allow that the
 technically most simple option is selected (that in fact can be the four
 channel one). When this selection is done and the technical constraints are
-better known (IF range available, needed frequent gaps between channels etc.), an
-iteration of DoF analysis should be made to see if some ``optimisation'' of the
-channel specifications can be achieved.
+better known (IF range available, needed frequent gaps between channels etc.), an iteration of DoF analysis should be made to see if some ``optimization'' of the channel specifications can be achieved.
 
@@
 as possible. If both quasi-horizontal and quasi-vertical bands must be applied,
-the recommendation prioritise to use the polarisation option for 183 and
+the recommendation prioritises to use the polarisation option for 183 and
 325\,GHz, to maintain a similar influence of polarisation between the bands.
@@
 accurate cloud correction for 183\,GHz than the 229 \,GHz channel. The simple
-regression based approach evaluated is channel specific and involves the
-325\,GHz channel one at the time. In the second correction approach based on
+regression based approach evaluated is channel specific, and involves the
+325\,GHz channel one at a time. In the second correction approach based on
 machine learning, QRNN is used to predict the clear-sky noise-free values
@@
 approach. The QRNN predictions result in error distributions with low skewness
-and widths. In some case the prediction uncertainty is even lower than the
+and widths. In some cases, the prediction uncertainty is even lower than the
 noise of the 183\,GHz channel targeted. This approach should be ideal for

### 2020-06-29 Report/aws_325ghz_study.tex
Version submitted June 26.

@@
 %
-The main objective of this study is to demonstrate that channels around
+The main objective of this study was to demonstrate that channels around
 325\,GHz can provide a basis for cloud filtering/correction of data measured
-around 183\,GHz. Previously, it was suggested that a channel at 229\,GHz to be
-used for cloud filtering. The 229\,GHz channel forms a part of the MicroWave
-Sounder (MWS) and will be used for cloud filtering of 183\,GHz inside that
-mission. In this study, we investigate the possibility to use some 325\,GHz
-channels instead.
-
-On basis of the relative humidity (RH) weighting functions of 183\,GHz, three specifications for 325\,GHz channels were suggested.
-A channel specific simple regression was tested to estimate and correct the impact of hydrometeors in 183\,GHz channel.
-The advantage of this approach is that for each 183\,GHz the cloud adjustment
-can be quantified simply through a polynomial fit between the the cloud impact
-in 183\,GHz channel of concern and brightness temperature differences between
-183\,GHz and 325\,GHz. A similar regression scheme based on 229\,GHz was also
-examined, but gave poor results. One drawback of the simple correction scheme
-is it's channel specific approach, which cannot benefit from the other 325\,GHz
-channels available. In order to effectively use information from all 325\,GHz
-channels, we suggested a machine learning based approach for cloud correction.
-We used QRNN (Quantile Regression Neural Network) to correct the cloud
-impact in each 183\,GHz channel using measurements from all available channels
-of 325\,GHz. All three options of 325\,GHz were evaluated, and the performance
-was comparable. For some channels, interestingly, the spread of errors was
-narrower than the noise of the target 183\,GHz channel. Another advantage of
-using QRNN is that the cloud free values are predicted at different quantile
-levels, which helps in quantifying the case-specific uncertainty estimate. A
-similar QRNN model with 229\,GHz gave poor results. No critical dependency to
-the 325\,GHz receiver noise temperature was observed.
+around 183\,GHz. Previously, it had been shown that a channel at 229\,GHz can
+be used for this cloud filtering and a 229\,GHz channel forms a part of the
+MicroWave Sounder (MWS). In this study, we investigate the possibility to use
+some 325\,GHz channels instead, more in line with the Ice Cloud Imager (ICI).
+
+On basis of the relative humidity (RH) weighting functions of 183\,GHz, three
+reference specifications for 325\,GHz channels were suggested. A channel
+specific simple regression was tested to estimate and correct the impact of
+hydrometeors in 183\,GHz channel. The advantage of this approach is that for
+each 183\,GHz the cloud adjustment can be quantified simply through a
+polynomial fit between the the cloud impact in 183\,GHz channel of concern and
+brightness temperature differences between 183\,GHz and 325\,GHz. A similar
+regression scheme based on 229\,GHz was also examined, but gave poor results.
+One drawback of the simple correction scheme is it's channel specific approach,
+which cannot benefit from the other 325\,GHz channels available. In order to
+effectively use information from all 325\,GHz channels, we suggested a machine
+learning based approach for cloud correction. We used QRNN (Quantile Regression
+Neural Network) to correct the cloud impact in each 183\,GHz channel using
+measurements from all available channels of 325\,GHz. All three options of
+325\,GHz were evaluated, and the performance was comparable. For some channels,
+interestingly, the spread of errors was narrower than the noise of the target
+183\,GHz channel. Another advantage of using QRNN is that the cloud free values
+are predicted at different quantile levels, which helps in quantifying the
+case-specific uncertainty estimate. A similar QRNN model with 229\,GHz gave
+poor results. No critical dependency to the 325\,GHz receiver noise temperature
+was observed.
 
@@
 with low bias and spread. Therefore, the NWP and standalone 1DVAR models that
-utilise the ``clear-sky'' data can greatly benefit from it. Also, in data
+utilise ``clear-sky'' data can greatly benefit from it. Also, in data
 assimilation systems, the case-specific uncertainty allows an effective
@@
 extent. The cloud correction simulations gave no clear constraints on the
-requirements, while the DoF analysis at least gave some indications. By
+requirements, while the DoF analysis gave some indications. By
 comparison to the NE$\Delta$T requirements for ICI and DoF values derived, it
@@
 
-\vspace{10mm}
+\vspace{20mm}
 \setcounter{tocdepth}{1} 
@@
 	\includegraphics[height=80mm]{DoF.png}
-	\caption{ The ratio of $\Lambda/S_\Lambda$ with respect to the eigenvalue
-      index for clear-sky cases. The black dotted line represents the level
-      where the ratio is unity. }
+	\caption{ The ratio of the diagonal elements of $\Lambda/S_\Lambda$ with
+      respect to the eigenvalue index for clear-sky cases. The black dashed
+      line represents the level where the ratio is unity. The crossing between
+      the coloured lines and the dashed line gives the DoF value reported.}
 	\label{fig:DoF:clear:1200K}
@@
 shift when going $T_r=2400$\,K is not observed in the two other tables. Having
-this in mind, it seems that options three b and c give very similar DoF. If
-something, option three-c seems slightly better. The four channel option
+this in mind, it seems that options three b and c give in overall similar DoF. If
+something, option three-c appears slightly better. The four channel option
 obtains somewhat lower DoF than the three channel ones.
@@
 
-The results indicate that a broader IF range should give slightly better performance.
-If a broader IF range is feasible, the position and width of all channels should be revised, but this is out of the scope of this study, and anyhow hardly motivated before it is known more exactly to what extent the IF range can be extended.
+The results indicate that a broader IF range should give slightly better
+performance. If a broader IF range is feasible, the position and width of all
+channels should be revised, but this is out of the scope of this study, and
+anyhow hardly motivated before it is known more exactly to what extent the IF
+range can be extended. Anyhow, as the three channel options already has a high
+ratio between bandwidth and centre IF for AWS-42, it seems difficult to make
+full use of an increased IF range for a those options and this is why this test
+was made using the four channel option.
 
@@
 %
-We formed three 325\,GHz channel options. All three options were
+We formed three reference 325\,GHz channel options. All three options were
 considered first in the QRNN part as it is difficult to maintain the full
@@
 small. However, it could be challenging to implement any of the three channel
-options. The option three-a risks to be affected by interference of the downlink
-and in the options three-b and c there is a high ratio between bandwidth and centre IF of AWS-42.
-The latter aspect also makes it hard to extend options three-b and c, if it would turn out that the IF range can be extended.
-A brief analysis showed that a broader IF range gives some increase in DoF, that potentially could improve the merit of the four channel option.
+options. The option three-a risks to be affected by interference of the
+downlink and in the options three-b and c there is a high ratio between
+bandwidth and centre IF of AWS-42. .A brief analysis showed that a broader IF
+range gives some increase in DoF, that at least could improve the merit of the
+four channel option.
 
@@
 channel one). When this selection is done and the technical constraints are
-better known (IF range available, needed frequent gaps between channels etc.), an iteration of DoF analysis should be made to see if some ``optimization'' of the channel specifications can be achieved.
+better known (IF range available, needed frequent gaps between channels etc.),
+an iteration of DoF analysis should be made to see if some ``optimization'' of
+the channel specifications can be achieved.
 
@@
 It is demonstrated that the 325\,GHz channels are capable of providing a more
-accurate cloud correction for 183\,GHz than the 229 \,GHz channel. The simple
+accurate overall cloud correction for 183\,GHz than a 229 \,GHz channel. The simple
 regression based approach evaluated is channel specific, and involves the
@@
 noise of the 183\,GHz channel targeted. This approach should be ideal for
-making use of AWS in assimilation systems of clear-sky type.
+making use of AWS in assimilation and retrieval systems of clear-sky type.
 

### 2020-06-30 Report/aws_325ghz_study.tex
updated with comments from Christophe

--- 2020-06-28 Report/aws_325ghz_study.tex
@@
 or several channels a higher frequencies. A number of channels around 325\,GHz
-was considered as the main option before AWS became an ESA/EUMETSAT mission,
+was considered as the main option before AWS became an ESA prototype mission,
 but it has now also been suggested to have a single channel at 229\,GHz. This
@@
 \citep{rekha2012potential}. For comparison, it can be mentioned that ICI (Ice
-Cloud Imager), another new Metop sensor, will include 325\,GHz channels.
+Cloud Imager), another new EPS-SG (EUMETSAT Polar System - Second Generation) sensor, will include 325\,GHz channels.
 
@@
 %
-A database of atmospheric cases was created based on data from CloudSat and
-ERA-Interim. The core idea of the approach is to use CloudSat reflectivities to
+A database of atmospheric cases was created based on data from CloudSat \citep{stephens2002bams} and
+ERA-Interim \citep{dee2011qjrms}. The core idea of the approach is to use CloudSat reflectivities to
 obtain as realistic vertical profiles of ice hydrometeors and rain as
@@
 For RWC the particle size distribution of \citet{abel2012improved} is applied.
-The PSD of IWC follows the basic formulation applied in DARDAR, using latest
+The PSD of IWC follows the basic formulation applied in DARDAR (\verb http://www.icare.univ-lille1.fr/projects/dardar), using latest
 parameter values (i.e.\ $\alpha$ and $\beta$) as given by
@@
 %
+
 \begin{figure}[p]
 	\centering
-	\includegraphics[height=60mm]{ATMS_C16_distribution}\hspace{5mm}% 
-	\includegraphics[height=60mm]{ATMS_C17_distribution}
-	\includegraphics[height=60mm]{ATMS_C18_distribution}\hspace{5mm}% 
-	\includegraphics[height=60mm]{ATMS_C19_distribution}
-	\includegraphics[height=60mm]{ATMS_C20_distribution}\hspace{5mm}% 
-	\includegraphics[height=60mm]{ATMS_C21_distribution}
-	\includegraphics[height=60mm]{ATMS_C22_distribution}
+	\includegraphics[height=57mm]{ATMS_C16_distribution}\hspace{5mm}% 
+	\includegraphics[height=57mm]{ATMS_C17_distribution}
+	\includegraphics[height=57mm]{ATMS_C18_distribution}\hspace{5mm}% 
+	\includegraphics[height=57mm]{ATMS_C19_distribution}
+	\includegraphics[height=57mm]{ATMS_C20_distribution}\hspace{5mm}% 
+	\includegraphics[height=57mm]{ATMS_C21_distribution}
+	\includegraphics[height=57mm]{ATMS_C22_distribution}
 	\caption{Probability distribution functions (PDFs) of simulated and
@@
 	\label{fig:pdf:c16-22}
+
 \end{figure}
@@
 ERA-Interim input data. The fraction of cloudy observations is lower in ATMS in
-comparison to simulations, for brightness temperatures below about 240\.K. This
+comparison to simulations, for brightness temperatures below about 240\,K. This
 is due to the fact that the antenna pattern is not considered in the
@@
 (transmissivity of $e^{-1}\approx0.37$) varies. The curves of the edge 183\,GHz
-channels (AWS-32 and 36) brackets the ones corresponding to the ICI 325\,GHZ
+channels (AWS-32 and 36) bracket the ones corresponding to the ICI 325\,GHZ
 channels. The later channels show a higher deviation from 1 at 150\,hPa, due to
@@
 suggestion uses the complete IF bandwidth as far as possible, that is
-technically possible.
+technically possible. Further in the text, this channel option is denoted as ``three-a''.
 
@@
 a IF range of 0.7 to 8.0\,GHz, and leaves 200\,MHz space between all the
-325\,GHz channels. Also this suggestion uses the complete IF bandwidth.
+325\,GHz channels. Also this suggestion uses the complete IF bandwidth. We will denote this channel option as ``four''.
 
@@
 constrain, while 1.7\,GHz is more or less at the centre of the three channel
-option. It was then decided to formulate second three channel option avoiding 
-1.7\,GHz, and the suggestion is found in Table~\ref{tab:chs:3b}.
+option. It was then decided to formulate a second three channel option, denoted as ``three-b'', avoiding 1.7\,GHz, and the suggestion is found in Table~\ref{tab:chs:3b}.
 
@@
 %
-In this section, the (first) 325\,GHz three channel option is evaluated for detection
+In this section, the (first) 325\,GHz three channel option (three-a) is evaluated for detection
 and correction of cloud interference in 183\,GHz channels. Combinations of
@@
 1$\sigma$ or 2$\sigma$ where $\sigma$ refers to the magnitude of measurement
-noise (Eq.~\ref{eq:noise}, often called NE$\Delta$T). We will use $1\sigma$ for
+noise (Eq.~\ref{eq:noise}, often called NE$\Delta$T (Noise Equivalent Delta Temperature)). We will use $1\sigma$ for
 the development of the scheme, however, the sensitivity of the scheme to
@@
 The filtering
-method introduced here leads to a considerable lower rejection of data
-(17.54\%).
+method introduced here, rejects only 17.54\% of the data.
 
@@
 separately. Thus, for each channel of 183\,GHz, we have a set of three
-predictions: one from four channel option, and two from the old and new
-configurations of the three channel option. Further in the text, the old and
-new three channel configurations are labelled as ``three-a'' and ``three-b''.
+predictions: one from four channel option, and two from the options ``three-a'' and ``three-b''.
 
@@
 IF, a third three channel option was formulated (Table~\ref{tab:chs:3c}) that
-is below denoted as three-c. This option uses the same IF range as the
+is below denoted as ``three-c''. This option uses the same IF range as the
 previously suggested ones.
@@
 As a basic investigation of the impact of changing the width of the IF range, a
-version of the four channel option was considered, denoted as four-b. It was
+version of the four channel option was considered, denoted as ``four-b''. It was
 modified to cover 0.7 to 9.0 GHz (instead of 0.7 to 8.0 GHz). To focus on the

### 2020-06-30 Report/aws_325ghz_study.tex
small changes after merge

--- 2020-06-30 Report/aws_325ghz_study.tex
@@
 
-On basis of the relative humidity (RH) weighting functions of 183\,GHz, three specifications for 325\,GHz channels were suggested.
-A channel specific simple regression was tested to estimate and correct the impact of hydrometeors in 183\,GHz channel.
+On basis of the relative humidity (RH) weighting functions of 183\,GHz, three
+ specifications for 325\,GHz channels were suggested. A channel specific simple regression was tested to estimate and correct the impact of hydrometeors in 183\,GHz channel.
 The advantage of this approach is that for each 183\,GHz the cloud adjustment
@@
 The basic shape of the Jacobian is similar for all 183 and 325\,GHz channels,
-but the peak altitude varies. Again the edge 183\,GHz channels brackets the
+but the peak altitude varies. Again the edge 183\,GHz channels bracket the
 325\,GHz ICI ones, as for transmissivity. These Jacobians are negative, meaning
@@
 \caption{Bias, standard deviation (std), and measure of skewness of the error
-  distributions of datasets shown in
+  distributions of datasets (AWS-34) shown in
   Figure~\ref{fig:correction:c34-42:thinned}.}
@@
 	\includegraphics[height=80mm]{DoF.png}
-	\caption{ The ratio of $\Lambda/S_\Lambda$ with respect to the eigenvalue
+	\caption{ The ratio of $\Lambda/S_\Lambda$ with
+ respect to the eigenvalue
       index for clear-sky cases. The black dotted line represents the level
-      where the ratio is unity. }
+      where the ratio is unity. 
+}
 	\label{fig:DoF:clear:1200K}
@@
 The latter aspect also makes it hard to extend options three-b and c, if it would turn out that the IF range can be extended.
-A brief analysis showed that a broader IF range gives some increase in DoF, that potentially could improve the merit of the four channel option.
+A brief analysis showed that a broader IF range gives some increase in DoF, that potentiallyacould improve the merit of the four channel option.
 

### 2020-08-27 Article/Article.tex
very first beginning of manuscript (AMT style)

%% Copernicus Publications Manuscript Preparation Template for LaTeX Submissions
%% ---------------------------------
%% This template should be used for copernicus.cls
%% The class file and some style files are bundled in the Copernicus Latex Package, which can be downloaded from the different journal webpages.
%% For further assistance please contact Copernicus Publications at: production@copernicus.org
%% https://publications.copernicus.org/for_authors/manuscript_preparation.html

%% Please use the following documentclass and journal abbreviations for preprints and final revised papers.

%% 2-column papers and preprints
\documentclass[amt, manuscript]{copernicus}

%% Journal abbreviations (please use the same for preprints and final revised papers)

%% \usepackage commands included in the copernicus.cls:
%\usepackage[german, english]{babel}
%\usepackage{tabularx}
%\usepackage{cancel}
%\usepackage{multirow}
%\usepackage{supertabular}
%\usepackage{algorithmic}
%\usepackage{algorithm}
%\usepackage{amsthm}
%\usepackage{float}
%\usepackage{subfig}
%\usepackage{rotating}

\begin{document}

\title{TEXT}

% \Author[affil]{given_name}{surname}

\Author[]{}{}
\Author[]{}{}
\Author[]{}{}

\affil[]{ADDRESS}
\affil[]{ADDRESS}

%% The [] brackets identify the author with the corresponding affiliation. 1, 2, 3, etc. should be inserted.

%% If an author is deceased, please mark the respective author name(s) with a dagger, e.g. "\Author[2,$\dag$]{Anton}{Aman}", and add a further "\affil[$\dag$]{deceased, 1 July 2019}".

%% If authors contributed equally, please mark the respective author names with an asterisk, e.g. "\Author[2,*]{Anton}{Aman}" and "\Author[3,*]{Bradley}{Bman}" and add a further affiliation: "\affil[*]{These authors contributed equally to this work.}".

\correspondence{NAME (EMAIL)}

\runningtitle{TEXT}

\runningauthor{TEXT}

\firstpage{1}

\maketitle

\begin{abstract}
TEXT
\end{abstract}

\copyrightstatement{TEXT}

\introduction  %% \introduction[modified heading if necessary]
TEXT
\section{Introduction}

\section{Data and methods}
\subsection{Ice Cloud Imager}

\subsection{ICI simulations}
%
The satellite observations for all ICI channels are simulated with the Atmospheric Radiative Transfer Simulator (ARTS).

\subsection{QRNN}

%
The neural network training is a process of learning to predict the outputs {$y_i$} from inputs {$x_i$} through a series of learnable transformations. While training, neural networks seek to minimise the model error through a loss function. The choice of the loss function depends on the predictive problem. When a neural network is trained to minimise the mean of the quantile loss function to predict the quantiles of the distribution, it is called a Quantile Regression Neural Network (QRNN).

\subsection{Training data}

Out of the 125\,000 simulations, 100\,000 are selected to form the training data. The remaining are used for testing. In the training data, 90\% of the data is randomly selected to form the training data, while the other 10\% form the \textit{testing-during-training} database.

The training sample combines measurements from all 183 GHz channels and the available sub-millimeter channels. For ICI, the training set combines data from 183\,GHz, 325 GHz, 448\,GHz and 664\,GHz to predict cloud corrected observations for the target 183 GHz. For each 183 GHz channel, QRNN needs to be trained separately with a new target value.

ARTS simulations are noise free, so to incorporate the satellite measurement uncertainties, gaussian noise is added to the input training data according to the channel NE$\Delta$T. The target training data is kept noise free. In order to build a robust learning network, random noise is added to the inputs at each training iteration. This exposes the model to a different datasets during the entire training process and avoids the memorisation of training samples. The input data is also normalized with mean and standard deviation.

\subsection{QRNN model selection}

A high performing QRNN model requires tuning of multiple hyperparameters. These parameters determine the structure and the training set-up of the neural network. Several of these hyper-parameters are non-learnable, and must be defined before beginning the training.

Among the structural parameters, a grid search was performed to determine the number of neurons (width) and hidden layers(depth). The quantile loss and CRPS on the validation set averaged over all predicted quantiles is used to compare the performance of different hyper-parameter configurations.

We did not optimise the type of activation function and batch size. Rectified Linear Unit (ReLU) was used as the activation function  and the batch size was set to 128 samples for all QRNN models.

The training process is optimized through different training parameters e.g. batch size, learning rate, number of epochs, momentum, decay. A customised  learning rate scheduler has been implemented to optimise SGD. The initial learning rate was revised after a certain number of epochs.  We started the training process with a initial learning rate of 0.1, and decreased it by a factor of 10 after 100 epochs. The best neural network performance was obtained when the network was trained three times with a new initial learning rate. For each training  if the validation loss remained unchanged till 6 training epochs, the learning rate was reduced by a factor of 2.

\begin{figure}[p]
	\centering
	\includegraphics[height=57mm]{Figures/CRPS.png} 
	\includegraphics[height=57mm]{Figures/quantile_loss.png}
	\caption{}
	\label{fig:}	
\end{figure}

\section{Results}
\subsection{Prediction results}

The prediction output from QRNN is in form of quantiles $x_{\tau}$, for median, $\pm 1\sigma$, $\pm 2 \sigma$ and  $\pm 3 \sigma$ ($\tau$ = 0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998). The expectation value of the posterior distribution is assumed to be the best estimate for the predicted clear-sky value.

\begin{figure}[p]
	\centering
	\includegraphics[height=57mm]{Figures/ICI_I1V.png} 
	\includegraphics[height=57mm]{Figures/ICI_I2V.png}
	\includegraphics[height=57mm]{Figures/ICI_I3V.png} 
	\caption{}
	\label{fig:}	
\end{figure}

\begin{table}[!p]
	\centering
	\begin{tabular}{lrrrr}
		\hline
		Dataset              &   bias &   std &   measure skewness &   rejected \\
		\hline
		Noise                &   0.00 &  0.80 &              -0.00 &       - \\
		uncorrected          &  -1.59 &  7.78 &              -8.88 &       - \\
		corrected (all)      &  -0.08 &  1.14 &               0.52 &       - \\
		corrected (filtered) &  -0.13 &  0.98 &              -0.34 &       5.50 \\
		\hline
	\end{tabular}
	\caption{I1V}
\end{table}

\begin{table}[!p]
	\centering
	\begin{tabular}{lrrrr}
		\hline
		Dataset              &   bias &   std &   measure skewness &   rejected \\
		\hline
		Noise                &  -0.01 &  0.80 &               0.02 &       - \\
		uncorrected          &   7.37 &  8.15 &              -7.80 &       - \\
		corrected (all)      &  -0.09 &  0.79 &               0.85 &       - \\
		corrected (filtered) &  -0.12 &  0.65 &               0.12 &       3.02 \\
		\hline
	\end{tabular}
	\caption{I2V}
\end{table}

\begin{table}[!p]
	\centering
	\begin{tabular}{lrrrr}
		\hline
		Dataset              &   bias &   std &   measure skewness &   rejected \\
		\hline
		Noise                &  0.00 & 0.80 &             -0.02 &      - \\
		uncorrected          & 14.64 & 8.66 &             -6.67 &      - \\
		corrected (all)      & -0.10 & 0.76 &              0.45 &      - \\
		corrected (filtered) & -0.11 & 0.64 &              0.20 &      1.57 \\
		\hline
	\end{tabular}
	\caption{I3V}
\end{table}

\begin{figure}[p]
	\centering
	\includegraphics[height=57mm]{Figures/prediction_uncertainty_I1V.png} 
	\includegraphics[height=57mm]{Figures/prediction_uncertainty_I2V.png}
	\includegraphics[height=57mm]{Figures/prediction_uncertainty_I3V.png} 
	\caption{}
	\label{fig:}	
\end{figure}
\subsection{Uncertainty quantification}

\section{Special case of using only 325\,GHz for cloud correction}

\subsection{Data}
24 monochromatic frequencies were used so that each channel could be represented
with sufficient accuracy. The simulations were generated for sensor viewing angles from
$0^{\circ}$ to $45^{\circ}$, but all the results described here are based on nadir viewing angle.

\subsection{Training}

\subsection{Prediction results}

\conclusions  %% \conclusions[modified heading if necessary]

%% The following commands are for the statements about the availability of data sets and/or software code corresponding to the manuscript.
%% It is strongly recommended to make use of these sections in case data sets and/or software code have been part of your research the article is based on.

\codeavailability{TEXT} %% use this section when having only software code available

\dataavailability{TEXT} %% use this section when having only data sets available

\codedataavailability{TEXT} %% use this section when having data sets and software code available

\sampleavailability{TEXT} %% use this section when having geoscientific samples available

\videosupplement{TEXT} %% use this section when having video supplements available

\appendix
\section{}    %% Appendix A

\subsection{}     %% Appendix A1, A2, etc.

\noappendix       %% use this to mark the end of the appendix section. Otherwise the figures might be numbered incorrectly (e.g. 10 instead of 1).

%% Regarding figures and tables in appendices, the following two options are possible depending on your general handling of figures and tables in the manuscript environment:

%% Option 1: If you sorted all figures and tables into the sections of the text, please also sort the appendix figures and appendix tables into the respective appendix sections.
%% They will be correctly named automatically.

%% Option 2: If you put all figures after the reference list, please insert appendix tables and figures after the normal tables and figures.
%% To rename them correctly to A1, A2, etc., please add the following commands in front of them:

\appendixfigures  %% needs to be added in front of appendix figures

\appendixtables   %% needs to be added in front of appendix tables

%% Please add \clearpage between each table and/or figure. Further guidelines on figures and tables can be found below.

\authorcontribution{TEXT} %% this section is mandatory

\competinginterests{TEXT} %% this section is mandatory even if you declare that no competing interests are present

\disclaimer{TEXT} %% optional section

\begin{acknowledgements}
TEXT
\end{acknowledgements}

%% REFERENCES

 \bibliographystyle{copernicus}
 \bibliography{example.bib}

\end{document}

### 2020-09-03 Article/Article.tex
added methods and results

@@
 \section{Data and methods}
-\subsection{Ice Cloud Imager}
+
+\subsection{ICI}
+%
+%t
+\begin{table*}[t]
+	\label{tab:QRNN_models}	
+	\caption{TEXT}
+	\begin{tabular}{lrrrr}
+		\tophline
+		Channel & Frequency 	& Bandwidth  	&NE$\Delta$T	&Polarisation\\
+		\middlehline
+		I1V&	183.31$\pm$7.00    & 2.0 			& 0.8 		& V\\
+		I2V&	183.31$\pm$3.40    & 1.5 			& 0.8 		& V\\
+		I3V&	183.31$\pm$2.00    & 1.5 			& 0.8 		& V\\
+		I4V&	243.20$\pm$2.50    & 3.0 			& 0.7 		& V\\
+		I4H&	243.20$\pm$2.50    & 3.0 			& 0.7 		& H\\
+		I5V&	325.15$\pm$9.50    & 3.0 			& 1.2 		& V\\
+		I6V&	325.15$\pm$3.50    & 2.4 			& 1.3 		& V\\
+		I6V&	325.15$\pm$1.50    & 1.6 			& 1.5 		& V\\
+		I8V&	448.00$\pm$7.20    & 3.0 			& 1.4 		& V\\
+		I9V&	448.00$\pm$3.00    & 2.0 			& 1.6 		& V\\
+		I10V&	448.00$\pm$1.40    & 1.2 			& 2.0 		& V\\
+		I11V&	664.00$\pm$4.20    & 5.0 			& 1.6 		& V\\
+		I11H&	664.00$\pm$4.20    & 5.0 			& 1.6 		& H\\		
+		\bottomhline
+	\end{tabular}
+	\begin{tabular}{lrrrr}
+		\tophline
+		Channel & Frequency 	& Bandwidth  	&NE$\Delta$T	&Polarisation\\
+		\middlehline
+		MWI-14&	183.31$\pm$7.00    & 2.0 			& 1.3 		& V\\
+		MWI-15&	183.31$\pm$6.10    & 1.5 			& 1.2 		& V\\
+		MWI-16&	183.31$\pm$4.90    & 1.5 			& 1.2 		& V\\
+		MWI-16&	183.31$\pm$3.40    & 1.5 			& 1.2 		& V\\
+		MWI-16&	183.31$\pm$2.00    & 1.5 			& 1.3 		& V\\	
+		\bottomhline
+	\end{tabular}
+	\belowtable{} % Table Footnotes
+\end{table*}
+Ice Cloud Imager (ICI) is a new EPS-SG (EUMETSAT Polar System - Second Generation) sensor that will observe  Earth using submillimeter-wave (sub-mm) frequency range.
+The main objective of ICI is measure ice cloud properties and improve the representation of clouds in regional and global models.
+ICI is a conically scanning millimetre/sub-millimetre radiometer which will measure 13 frequencies from 183 GHz up to 664 GHz.
+Channels with centre frequencies 183.31, 325.15 and 448.0\,GHz are centered on water vapor absorption lines, and measure vertical polarization.
+While other channels around 243.0 and 664.0\,GHz are ``window channels'' and receive both vertical and horizontal polarization.
+In addition to ICI, the EPS-SG satellite will also have Microwave Imager (MWI) onboard.
+MWI will measure frequencies from 18.7 GHz up to 183\,GHz and provide data continuity to the existing microwave imager measurements.
+The common 183\,GHz channels among the two instruments shall allow cross-calibration between the two instruments.
+The channel configurations for ICI and MWI (only 183\,GHz) are provided in Table~\ref{tab:ICI_MWI_configuration}.
 
@@
 %
-The satellite observations for all ICI channels are simulated with the Atmospheric Radiative Transfer Simulator (ARTS).
+**** Some parts copied directly from AWS report *****
+
+The satellite observations for all ICI channels are simulated with the Atmospheric Radiative Transfer Simulator (ARTS, (ARTS, \citet{eriksson:arts2:11,buehler:artst:18})version.
+The simulations include TB from five ICI channels around 183\,GHz, 243\,GHz, 325\,GHz, 448\,GHz and 664\,GHz.
+
+The absorption model takes into account the effect from nitrogen \citep{pwr:93}, oxygen \citep{pwr:93} and water vapour \citep{ellison2007permittivity}.
+LWC is taken from ERA-Interim and is assumed to be totally absorbing.
+In the
+mapping of CloudSat reflectivities to RWC and IWC a total separation between
+liquid and ice phase is assumed. All scattering hydrometeors at temperatures
+above 0$^\circ$C are assumed to be rain, and all below 0$^\circ$C are assumed
+to be ice hydrometeors.
+For RWC the particle size distribution of \citet{abel2012improved} is applied.
+The PSD of IWC follows the basic formulation applied in DARDAR (\verb http://www.icare.univ-lille1.fr/projects/dardar), using latest parameter values (i.e.\ $\alpha$ and $\beta$) as given by
+\citet{amt-12-2819-2019}. This PSD can be considered as a ``two moment''
+scheme, but is here applied in a one moment manner by setting $N_0^*$ (as a
+function of temperature) following Table~5 of \citet{delanoe2014normalized},
+and letting the radar reflectivity set the remaining moment.
+Single scattering data are taken from \citet{eriksson:agene:18}. For ice
+hydrometeors, three habits are applied: Perpendicular 3-bullet rosette, Large
+plate aggregate and Large column aggregate. In the last two cases, the
+aggregates are complemented with single crystal data to also cover smaller
+sizes. These data describe particles assumed to have a totally random
+orientation. To apply oriented particles is much more computationally costly
+and could not be accommodated inside the study.
+The land emissivity was taken from TELSEM \citep{aires2011tool} and the Ocean/water from TESSEM \citep{prigent2017sea}.
+For each atmopsheric case, both ''clear-sky'' and ``all-sky'' calculations were performed.
+In the former, all impact of all hydrometeors were set to zero, while in the latter, IWC and RWC derived from CloudSat reflectivities and LWC from ERA-Interim were taken into account.
+Both sets of calculations were made by ARTS's interface to the RT4 solver \citep{evans1995microwavec}.
+To avoid a possible bias between clear-sky and all-sky for insignificant hydrometeor contents, the same ``scattering solver'' was used for both calculations.
+The first two elements of the
+Stokes vector were calculated.
+
+\subsection{Simulation dataset}
+%
+Using the simulation setup described in previous section, Cloudsat profiles during August 2015 were randomly selected to generate 200\,000 cases for each ICI frequency.
+The input data were restricted between $60^{\degree}$S to $60^{\degree}$N, and surface is below 500\,m.
+Both clear-sky and all-sky scenarios were simulated, and no differentiation was made between the observations over ocean/sea and land.
+It is also assumed that all simulations are remapped to a common foorprint.
+
+**** show any comparsion to ATMS? or AWS channels ? ****
 
 \subsection{QRNN}
-
 %
@@
 
+\subsubsection{Model selection}
+%
+\label{model_selection}
+A high performing QRNN model requires tuning of multiple hyper-parameters.
+These parameters determine the structure and the training set-up of the neural network.
+Several of these hyper-parameters are non-learnable, and must be defined before beginning of every training.
+Grid search is one of the most often employed techniques for hyper-paramter tuning.
+In grid search, different combinations of hyperparamters are selected and for each, the model performance is evaluated.
+The model architecture with the best performance is selected.
+The model evaluation metrics employed in this article are described in the next section.
+
+For the structural parameters, the grid search is performed to determine the number of neurons (width) and hidden layers (depth).
+The model is trained for multiple values of layer widths and hidden layers, and the best configuration is selected by evaluating the predictions over the validation set.
+Similarly, the training process is optimized by performing a grid search different training parameters such as : batch size, learning rate, number of epochs, decay.
+The best performing hyperparameter configurations for a particular training set need not be same for other datasets.
+Therefore for each QRNN model used in this article the hyperparameters were tuned distinctly.
+
+\subsubsection{Evaluation metrics}
+
+Quantile loss function
+
+CRPS
+
+\section{Cloud correction in ICI 183 GHz channels}
+%
 \subsection{Training data}
-
-Out of the 125\,000 simulations, 100\,000 are selected to form the training data.
-The remaining are used for testing.
-In the training data, 90\% of the data is randomly selected to form the training data, while the other 10\% form the \textit{testing-during-training} database.
-
-The training sample combines measurements from all 183 GHz channels and the available sub-millimeter channels.
-For ICI, the training set combines data from 183\,GHz, 325 GHz, 448\,GHz and 664\,GHz to predict cloud corrected observations for the target 183 GHz.
-For each 183 GHz channel, QRNN needs to be trained separately with a new target value.
-
+%
+Out of the 200\,000 ICI channel simulations, 150\,000 cases are randomly picked to form the training set.
+The rest are used for testing.
+In the training set, 90\% of the data is randomly selected to form the training set, while the other 10\% form the \textit{testing-during-training} database.
 ARTS simulations are noise free, so to incorporate the satellite measurement uncertainties, gaussian noise is added to the input training data according to the channel NE$\Delta$T.
@@
 
-\subsection{QRNN model selection}
+\subsection{Training}
+%
+%t
+\begin{table}[t]
+\label{tab:QRNN_models}	
+\caption{TEXT}
+\begin{tabular}{lll}
+\tophline
+QRNN model & Training inputs & Target \\
+\middlehline
+QRNN-simple & I1V, I5V, I6V, I7V, I8V, I9V, I10V, I11V & I1V\\
+			& I2V, I5V, I6V, I7V, I8V, I9V, I10V, I11V & I2V\\
+			& I3V, I5V, I6V, I7V, I8V, I9V, I10V, I11V & I3V\\
+QRNN-all    & I1V, I2V, I3V, I5V, I6V, I7V, I8V, I9V, I10V, I11V & I1V\\	
+			& I1V, I2V, I3V, I5V, I6V, I7V, I8V, I9V, I10V, I11V & I2V\\	
+			& I1V, I2V, I3V, I5V, I6V, I7V, I8V, I9V, I10V, I11V & I3V\\
+QRNN-mwi	& MWI-15, I5V, I6V, I7V, I8V, I9V, I10V, I11V & MWI-15\\	
+			& MWI-16, I5V, I6V, I7V, I8V, I9V, I10V, I11V & MWI-16\\			
+\bottomhline
+\end{tabular}
+\belowtable{} % Table Footnotes
+\end{table}
+To investigate the performance of training inputs, two QRNN models with different set of training inputs are analysed.
+In both models, the training set combines data from 183\,GHz, 325 GHz, 448\,GHz and 664\,GHz to predict cloud corrected observations for the target 183\,GHz channel.
 
-A high performing QRNN model requires tuning of multiple hyperparameters.
-These parameters determine the structure and the training set-up of the neural network.
-Several of these hyper-parameters are non-learnable, and must be defined before beginning the training.
+In the first model, the training set includes the target 183\,GHz channel and the sub-mm channels.
+For example, to train for channel I1V, the input channels are I1V, I5V , I6V, I7V, I8V, I9V, I10V, I11V.
+A separate QRNN model is trained for each of the 183\,GHz channels.
+We shall refer this QRNN model as ``QRNN-simple''.
 
-Among the structural parameters, a grid search was performed to determine the number of neurons (width) and hidden layers(depth).
-The quantile loss and CRPS on the validation set averaged over all predicted quantiles is used to compare the performance of different hyper-parameter configurations.
+In the second QRNN model, we sugest to use all three 183\,GHz channels concurrently  with the other sub-mm channels.
+In this case, although the input training parameters are same for all channels, QRNN needs to be trained separately each 183\,GHz channel.
+Further in text, we refer this model as ``QRNN-all''.
+Table~\ref{tab:QRNN_models} summarises the two QRNN models.
 
-We did not optimise the type of activation function and batch size. Rectified Linear Unit (ReLU) was used as the activation function  and the batch size was set to 128 samples for all QRNN models.
+As described in section \ref{model_selection}, a grid search was implemented to select the best performing hyperparamters.
+The mean quantile loss and CRPS for different layer width and hidden layer configurations are shown in Fig\ref{fig:model_selection}.
+The results are for QRNN-simple with I3V as target channel.
+Increasing the complexity of the network by increasing the layer-width and depth has a positive impact on performance.
+However for four hidden layers, increasing the number of neurons beyond 128 has no significant impact on the performance.
+On basis of these results, a neural network with four hidden layers and 128 neurons in each layer was selected for QRNN-simple.
 
-The training process is optimized through different training parameters e.g.
-batch size, learning rate, number of epochs, momentum, decay.
-A customised  learning rate scheduler has been implemented to optimise SGD.
-The initial learning rate was revised after a certain number of epochs.
+For the optimising the training paramters, a customised  learning rate scheduler was implemented.
+The initial learning rate was reset after a certain number of epochs.
 We started the training process with a initial learning rate of 0.1, and decreased it by a factor of 10 after 100 epochs.
@@
 For each training  if the validation loss remained unchanged till 6 training epochs, the learning rate was reduced by a factor of 2.
+We did not optimise the type of activation function and batch size.
+Rectified Linear Unit (ReLU) was used as the activation function  and the batch size was set to 128 samples for all QRNN models.
+For QRNN-all a grid search (results not shown) over width and depth and learning rates resulted in similar performance, and an identical neural network was selected.
 
-\begin{figure}[p]
+\begin{figure}[t]
 	\centering
@@
 
-\section{Results}
 \subsection{Prediction results}
-
-The prediction output from QRNN is in form of quantiles $x_{\tau}$, for median, $\pm 1\sigma$, $\pm 2 \sigma$ and  $\pm 3 \sigma$ ($\tau$ = 0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998).
-The expectation value of the posterior distribution is assumed to be the best estimate for the predicted clear-sky value.
-
-\begin{figure}[p]
-	\centering
-	\includegraphics[height=57mm]{Figures/ICI_I1V.png} 
-	\includegraphics[height=57mm]{Figures/ICI_I2V.png}
-	\includegraphics[height=57mm]{Figures/ICI_I3V.png} 
-	\caption{}
-	\label{fig:}	
+%
+%f 
+\begin{figure}[t]
+	\includegraphics[height=57mm]{Figures/PDF_I1V_single.png} 
+	\includegraphics[height=57mm]{Figures/PDF_I2V_single.png}
+	\includegraphics[height=57mm]{Figures/PDF_I3V_single.png} 
+	\caption{PDF}
+	\label{fig:PDF_predictions}	
+\end{figure}
+%f 
+\begin{figure}[t]
+	\includegraphics[height=57mm]{Figures/ICI_I1V_single.png} 
+	\includegraphics[height=57mm]{Figures/ICI_I2V_single.png}
+	\includegraphics[height=57mm]{Figures/ICI_I3V_single.png} 
+	\caption{Error distributions}
+	\label{fig:error_distributions}	
 \end{figure}
 
-\begin{table}[!p]
-	\centering
-	\begin{tabular}{lrrrr}
-		\hline
-		Dataset              &   bias &   std &   measure skewness &   rejected \\
-		\hline
-		Noise                &   0.00 &  0.80 &              -0.00 &       - \\
-		uncorrected          &  -1.59 &  7.78 &              -8.88 &       - \\
-		corrected (all)      &  -0.08 &  1.14 &               0.52 &       - \\
-		corrected (filtered) &  -0.13 &  0.98 &              -0.34 &       5.50 \\
-		\hline
+%t
+\begin{table}[t]
+	\caption{I1V}
+	\label{tab:I1V_statistics}
+	\begin{tabular}{lrrrrrr}
+		\tophline
+		&&& \multicolumn{2}{c}{QRNN-simple} & \multicolumn{2}{c}{QRNN-all}\\
+		&   noise &   uncorrected &   corrected(all) &   corrected(filtered) & corrected(all) &   corrected(filtered) \\
+		\middlehline
+		bias     &   -0.00 &         -1.90 &           -0.03 &                 0.00 & -0.01 &                 0.01 \\
+		mae      &    0.64 &          2.35 &            0.69 &                 0.60 & 0.66 &                 0.58\\
+		std      &    0.80 &          8.92 &            1.05 &                 0.78 &  0.96 &                 0.75\\
+		skewness &   -0.01 &         -7.99 &           -1.24 &                -0.44 & -0.39 &                -0.32\\
+		rejected &    	 - &          - &            - &                 6.40 & - &                 6.42 \\
+		\bottomhline
 	\end{tabular}
-	\caption{I1V}
+	\belowtable{} % Table Footnotes
+\end{table}
+%t
+\begin{table}[t]
+	\caption{I2V}
+	\label{tab:I2V_statistics}
+	\begin{tabular}{lrrrrrr}
+		\tophline
+		&&& \multicolumn{2}{c}{QRNN-simple} & \multicolumn{2}{c}{QRNN-all}\\
+		&   noise &   uncorrected &   corrected(all) &   corrected(filtered) & corrected(all) &   corrected(filtered) \\
+		\middlehline
+		bias     &   -0.00 &         -1.05 &            0.02 &                 0.03&  0.02&   0.03\\
+		mae      &    0.64 &          1.54 &            0.56 &                 0.50&  0.46&   0.42\\
+		std      &    0.80 &          5.98 &            0.86 &                 0.64&  0.70&   0.53\\
+		skewness &    0.02 &        -10.64 &           -2.25 &                -0.22& -1.67&  -0.25\\
+		rejected &    - &          - &            - &                 3.70&  - &   3.67\\
+		\bottomhline
+	\end{tabular}
+	\belowtable{} % Table Footnotes
 \end{table}
 
-\begin{table}[!p]
-	\centering
-	\begin{tabular}{lrrrr}
-		\hline
-		Dataset              &   bias &   std &   measure skewness &   rejected \\
-		\hline
-		Noise                &  -0.01 &  0.80 &               0.02 &       - \\
-		uncorrected          &   7.37 &  8.15 &              -7.80 &       - \\
-		corrected (all)      &  -0.09 &  0.79 &               0.85 &       - \\
-		corrected (filtered) &  -0.12 &  0.65 &               0.12 &       3.02 \\
-		\hline
+%t
+\begin{table}[t]
+	\caption{I3V}
+	\label{tab:I3V_statistics}
+	\begin{tabular}{lrrrrrr}
+		\tophline
+		&&& \multicolumn{2}{c}{QRNN-simple} & \multicolumn{2}{c}{QRNN-all}\\
+		&   noise &   uncorrected &   corrected(all) &   corrected(filtered) & corrected(all) &   corrected(filtered) \\
+		\middlehline
+		bias     &   0.00 &         -0.63 &            0.02 &                 0.02& 0.04 &                 0.04 \\
+		mae      &    0.64 &          1.14 &            0.54 &                 0.50&0.48 &                 0.44 \\
+		std      &    0.80 &          4.26 &            0.80 &                 0.64&0.71 &                 0.56 \\
+		skewness &   0.00 &        -13.26 &           -1.40 &                -0.16&-1.41 &                -0.11 \\
+		rejected &    - &          - &           - &                 2.18&- &                 2.18 \\
+		\bottomhline
 	\end{tabular}
-	\caption{I2V}
+	\belowtable{} % Table Footnotes
 \end{table}
+QRNN predictions are estimates of the posterior distribution over different quantiles: $x_{\tau}$, for median, $\pm 1\sigma$, $\pm 2 \sigma$ and  $\pm 3 \sigma$ ($\tau$ = 0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998).
+The median of the posterior distribution is assumed to be the best estimate for the predicted clear-sky value.
+The prediction error is calculated as the deviation to the corresponding noise-free clear-sky value.
+We calculate the mean bias, mean absolute error and standard deviation of the errors.
+The asymmetry of the distributions around their mean is also calculated through the measure of skewness.
+In the following sections, we describe the performance of the two QRNN models.
 
-\begin{table}[!p]
-	\centering
-	\begin{tabular}{lrrrr}
-		\hline
-		Dataset              &   bias &   std &   measure skewness &   rejected \\
-		\hline
-		Noise                &  0.00 & 0.80 &             -0.02 &      - \\
-		uncorrected          & 14.64 & 8.66 &             -6.67 &      - \\
-		corrected (all)      & -0.10 & 0.76 &              0.45 &      - \\
-		corrected (filtered) & -0.11 & 0.64 &              0.20 &      1.57 \\
-		\hline
-	\end{tabular}
-	\caption{I3V}
-\end{table}
+The distributions of the predicted clear-sky values and the clear-sky simulations from QRNN-single are shown in Fig~\ref{fig:PDF_predictions}.
+The three figures correspond to channels: I1V, I2V and I3V.
+These results show that the clear-sky values predicted by QRNN-single have a very good match for the peak of the distributions, but a slight mismatch is evident towards the tails, where QRNN seems to predict slightly colder/warmer TBs.
 
-\begin{figure}[p]
-	\centering
-	\includegraphics[height=57mm]{Figures/prediction_uncertainty_I1V.png} 
-	\includegraphics[height=57mm]{Figures/prediction_uncertainty_I2V.png}
-	\includegraphics[height=57mm]{Figures/prediction_uncertainty_I3V.png} 
+Fig~\ref{fig:error_distributions} shows the error distributions of the uncorrected measurements and predicted clear-sky TBs for all three channels.
+Distribution of noise is also plotted for reference.
+The error metrics corresponding to these results are provided in Table~\ref{tab:I1V_statistics} - Table~\ref{tab:I3V_statistics}.
+Without any cloud impact, the error distributions should follow a Gaussian distribution, however the presence of clouds leads to a TB reduction, and introduces a high negative bias.
+Among the three channels, I1V has the highest cloud impact and I3V has the least.
+The bias in I1V measurements is -1.89\,K compared to only -0.55\,K in I3V.
+After correction, the cloud impact is reduced and the resulting error distributions are symmetric with low bias.
+The predictions and the observations have a good agreement for the main peak of the distribution, albeit the prediction errors have a sharper peak and a larger spread.
+The larger spread indicates few cases which are under-/over corrected.
+If all the cases with correction greater than 15\,K are excluded, only a fraction of the total cases are removed but the  the variability in predictions errors reduces significantly.
+This indicates low accuracy of QRNN predictions for cases with high cloud impact.
+
+Compared to channel I1V, the performance of QRNN model is slighly better for I2V and I3V.
+
+The error metrics from QRNN-all are also shown in the last columns of Table~\ref{tab:I1V_statistics} - Table~\ref{tab:I3V_statistics}.
+As expected, using additional 183\,GHz channels improves the accuracy of the predictions slightly.
+
+**** add QRNN-all results ****
+
+\subsection{Uncertainty quantification}
+%
+%f 
+\begin{figure}[t]
+	\includegraphics[height=57mm]{Figures/scatter_uncertainty_single_I1V.png} 
+	\includegraphics[height=57mm]{Figures/scatter_uncertainty_single_I2V.png}
+	\includegraphics[height=57mm]{Figures/scatter_uncertainty_single_I3V.png} \\
+	\includegraphics[height=57mm]{Figures/Frequency_uncertainty_bins_I1V_single.png} 
+	\includegraphics[height=57mm]{Figures/Frequency_uncertainty_bins_I2V_single.png}
+	\includegraphics[height=57mm]{Figures/Frequency_uncertainty_bins_I3V_single.png}
+	\\	
 	\caption{}
-	\label{fig:}	
+	\label{fig:error_distributions}	
 \end{figure}
-\subsection{Uncertainty quantification}
+The biggest advantage of using QRNN is estimation of case-specific uncertainties. The quantiles can be used to construct a probability distribution of the
+predictions in contrast to other correction approaches which give out only point estimates. In all QRNN models presented in this article, we estimate the conditional
+quantiles for median, $\pm 1\sigma$, $\pm 2\sigma$, and $\pm 3\sigma$. The
+predictions for each quantile are used to construct the confidence intervals.
+The confidence interval for each point estimate quantifies its uncertainty.
+For example, the predicted quantiles for $\pm 2 \sigma$ implies that there is  94\% probability that the true value will lie between the range.
+
+Fig~\ref{fig:uncertainty_scatter} shows the scatter plot between the error and uncertainty.
+The error distributions for all three channels are centered around zero, however the uncertainty in predictions for I1V and I2V are higher than I3V.
+An increase in the spread with increasing uncertainty is evident in all three.
+As the errors increase, the spread is mostly symmetric around x-axis but for high uncertainty values, negative errors occur more frequently.
+This suggests that predictions for cases high cloud impact are associated with high uncertainty.
+The lower panel in the same figure, shows the errors when plotted as distributions over different uncertainty bins.
+Apart from few individual variations, all three channels follow the trend of increasing uncertainty with decreasing accuracy, suggesting that QRNN is successful in providing well calibrated probabilistic predictions of the posterior distribution.
+
+%Fig~\ref{fig:uncertainty_estimate} shows the prediction uncertainties for randomly chosen 2000 cases. A large spread in the plot indicates a high case-to-case variability of the uncertainty.
+
+%To inspect if the predictions follow a normal distribution, we evaluate the length of confidence intervals from the median.
+Figure~\ref{fig:prediction_uncertainty} shows the prediction uncertainty in AWS-34 (four channel option).
+The uncertainty with respect to the median for 1000 randomly selected cases is shown.
+The red line represents the uncertainty in a hypothetical Gaussian distribution of $270\pm0.62$\,K.
+If the underlying distribution is Gaussian, the prediction uncertainty should be symmetric around the median, and the uncertainties should be equally spaced for $1\sigma$, $2\sigma$ and so on.
+The predictions from our QRNN model seem to be symmetric around the median for the 94\% confidence interval ($\pm 2 \sigma$).
+The figure also shows that the uncertainties for all 1000 random cases are concentrated along a narrow width, thus suggesting that the case to case variability of the uncertainty is low.
+A similar uncertainty quantification for other 183\,GHz channels also gives similar results.
+
+%f
+%\begin{figure}[t]
+%\includegraphics[height=57mm]{Figures/uncertainty_single_I1V.png} 
+%\includegraphics[height=57mm]{Figures/uncertainty_single_I2V.png}
+%\includegraphics[height=57mm]{Figures/uncertainty_single_I3V.png} 
+%\caption{}
+%\label{fig:}
+%\end{figure}
 

### 2020-09-03 ICI/PDF.py
updated scripts for ICI cloud correction

@@ -15,9 +15,12 @@ from read_ARTS_output import read_all_files
 import xarray
 from add_gaussian_noise import add_gaussian_noise
 from read_clear_allsky_pairs import read_clear_allsky_pairs, read_clear_allsky_pairs_MWI
-
+from get_IWP import get_IWP
+from ICI_channel_TB import ICI_channel_TB
+import random
 theta = 135.2
 
+#%%
 def calculate_histogram(TB, bins, channels):
         hist_arts = []
         for ic in range(channels):
@@ -26,36 +29,6 @@ def calculate_histogram(TB, bins, channels):
 
     
         return hist_arts
-#%%
-def ICI_channel_TB(TB, nchannels):
-    """
-    
-
-    Parameters
-    ----------
-    TB : TYPE
-        DESCRIPTION.
-    nchannels : TYPE
-        DESCRIPTION.
-
-    Returns
-    -------
-    TB_ICI : TYPE
-        DESCRIPTION.
-
-    """
-    n = int(nchannels/2)
-    TB_ICI = TB.copy(deep = True, data= None)[:, :,  0:n, :]
-
-    for ic in range(n):
-        print ('total_channels', ic, nchannels-ic-1)
-        ic1 = ic
-        ic2 = nchannels-ic-1
-        TB_ICI[:, :, ic, :]= (TB[:, :, ic1, :] + TB[:, :,  ic2, :])/2
-    return TB_ICI
-
-#%% 
-
 
 #%%  concatenate all ARTS simulations together         
 f_grid = np.concatenate([183.31 + np.array([-7.0, -3.4, -2.0, 2.0, 3.4, 7.0]),
@@ -64,35 +37,28 @@ f_grid = np.concatenate([183.31 + np.array([-7.0, -3.4, -2.0, 2.0, 3.4, 7.0]),
                                 448.00 + np.array([-7.2, -3.0, -1.4, 1.4, 3.0, 7.2]),
                                 664.00 + np.array([-4.2, 4.2])])
 
-f_grid_mwi = np.concatenate([183.31 + np.array([-7.0, -3.4, -2.0, 2.0, 3.4, 7.0]),
-                                243.20 + np.array([-2.5, 2.5]),
[…]

### 2020-09-03 ICI/ici.py

@@ -26,7 +26,8 @@ class iciData(Dataset):
 
         TB = self.file.variables["TB"][:]
         channels = self.file.variables["channels"][:]
-
+        
+        self.surface = self.file.variables["cases"][:]
         self.channels = inChannels       
         idx = []
         
@@ -122,6 +123,7 @@ class iciData(Dataset):
                           1.4, 1.6, 2.0, #448Ghz
                           1.6, 1.6])     #664Ghz
 
+        
         nedt_subset = nedt[index]
         size_TB = int(x.size/len(nedt_subset))
         x_noise = x.copy()

### 2020-09-03 ICI/get_IWP.py
new notebooks and scripts

@@ -1,0 +1,57 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Wed Aug 26 14:50:28 2020
+
+@author: inderpreet
+"""
+
+
+from data import Profiles
+import numpy as np
+import glob
+import os
+import xarray
+
+def get_IWP(files_cs):
+    Z = []
+    data = []
+    first_iteration = True
+    for file_clearsky in files_cs:
+
+        file_allsky  = file_clearsky.replace('_clearsky.nc', '.nc')
+#        print (file_clearsky, file_allsky)
+        
+        if os.path.isfile(file_allsky):
+
+            y = xarray.open_dataset(file_allsky)
+            y_ici_allsky = y.y_ici
+            
+            y = xarray.open_dataset(file_clearsky)
+    #        print(file_clearsky)
+            y_ici_clearsky = y.y_ici
+            
+            allsky       = y_ici_allsky.shape[0]
+            clearsky     = y_ici_clearsky.shape[0]
+            
+            cases = min(allsky, clearsky)
+            
+            file_mat = file_allsky.replace('ICI', 'Cases')
+            file_mat = file_mat.replace('.nc', '.mat')
+            print (file_mat)
+                
+            dataset = Profiles(file_mat)
+
+            for i in range(cases):
+                    dbz = dataset.get_y_cloudsat(i)
+                    data.append(list(dbz))
+
+#            if first_iteration:        
+#                Z = data
+#                first_iteration = False
+
+ #           else:
+ #               print (len(data))
+ #               Z.append(data)
+
+    return data

### 2020-09-03 ICI/statistics.py

@@ -1,0 +1,165 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Tue Sep  1 14:42:56 2020
+
+@author: inderpreet
+"""
+
+
+import matplotlib.pyplot as plt
+import numpy as np
+from scipy.stats import skew
+plt.rcParams.update({'font.size': 16})
+from matplotlib.ticker import (MultipleLocator, FormatStrFormatter,
+                               AutoMinorLocator)
+from scipy.stats import gaussian_kde
+
+quantiles = np.array([0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998])
+
+def predict(test_data, qrnn):
+    """
+    predict the posterior mean and median
+    """
+    x_noise = test_data.add_noise(test_data.x, test_data.index)
+    print (test_data.index)
+    x = (x_noise - test_data.mean)/test_data.std
+
+    y_pre = qrnn.predict(x.data)
+    y_prior = x_noise
+    y0 = test_data.y
+    y = test_data.y_noise
+    y_pos_mean = qrnn.posterior_mean(x.data)
+    
+    return y_pre, y_prior, y0, y, y_pos_mean
+    
+
+def calculate_pdf(y, y0, bins, im = None):
+
+    error = y - y0
+    if im is not None:
+        hist    = np.histogram(error[im], bins, density = True)
+    else:
+        hist    = np.histogram(error, bins, density = True)       
+    
+    return hist
+
+def calculate_bias(y_prior, y0, y, y_pos_mean, im, itarget): 
+    b0  = np.mean(y - y0)
+    b1  = np.mean(y_prior[:, itarget] - y0)
+    b2a = np.mean(y_pos_mean - y0) 
+    b2b = np.mean(y_pos_mean[im] - y0[im])
+    return b0, b1, b2a, b2b
+
+def calculate_std(y_prior, y0, y, y_pos_mean, im, itarget):  
+    std0  = np.std(y - y0)
+    std1  = np.std(y_prior[:, itarget] - y0)
+    std2a = np.std(y_pos_mean - y0)
+    std2b = np.std(y_pos_mean[im] - y0[im])
+    return std0, std1, std2a, std2b
+
+def calculate_mae(y_prior, y0, y, y_pos_mean, im, itarget): 
[…]

### 2020-09-09 Article/ici_submm_cloudcorr.tex
added references.bib and renamed Article.tex to ici_submm_cloudcorr.tex
new additions to the article; backing up

--- 2020-09-03 Article/Article.tex
@@
 \introduction  %% \introduction[modified heading if necessary]
-TEXT
-\section{Introduction}
 
@@
 
-\subsection{ICI}
+\subsection{Ice Cloud Imager}
 %
@@
 \begin{table*}[t]
-	\label{tab:QRNN_models}	
-	\caption{TEXT}
+	\label{tab:ICI_MWI_channels}	
+	\caption{Specifications of ICI and MWI channels. For MWI only 183\,GHz channels are shown.}
 	\begin{tabular}{lrrrr}
@@
 \subsection{ICI simulations}
+\label{sec:arts_simulations}
 %
+
 **** Some parts copied directly from AWS report *****
@@
 
-\section{Cloud correction in ICI 183 GHz channels}
+\section{Cloud correction in  183 GHz channels}
 %
@@
 %
-Out of the 200\,000 ICI channel simulations, 150\,000 cases are randomly picked to form the training set.
+Out of the 200\,000 ICI and MWI channel simulations, 150\,000 cases are randomly picked to form the training set.
 The rest are used for testing.
@@
 The input data is also normalized with mean and standard deviation.
-
+It is assumed for the simulations that the ICI and MWI channels are mapped to a common footprint and resolution.
+In such case, remapping reduces the noise in MWI channels from 1.2\,K at 10\,Km resolution to 0.8\,K at 15\,Km resolution.
 \subsection{Training}
@@
 \label{tab:QRNN_models}	
-\caption{TEXT}
+\caption{Summary of the different QRNN models used in the study.}
 \begin{tabular}{lll}
@@
 			& I3V, I5V, I6V, I7V, I8V, I9V, I10V, I11V 			 & I3V\\
+			& MWI-15, I5V, I6V, I7V, I8V, I9V, I10V, I11V 		 & MWI-15\\	
+			& MWI-16, I5V, I6V, I7V, I8V, I9V, I10V, I11V 		 & MWI-16\\
 QRNN-all    & I1V, I2V, I3V, I5V, I6V, I7V, I8V, I9V, I10V, I11V & I1V\\	
@@
 			& I1V, I2V, I3V, I5V, I6V, I7V, I8V, I9V, I10V, I11V & I3V\\
-QRNN-mwi	& MWI-15, I5V, I6V, I7V, I8V, I9V, I10V, I11V & MWI-15\\	
-			& MWI-16, I5V, I6V, I7V, I8V, I9V, I10V, I11V & MWI-16\\			
+
 \bottomhline
@@
 We shall refer this QRNN model as ``QRNN-simple''.
-
-In the second QRNN model, we sugest to use all three 183\,GHz channels concurrently  with the other sub-mm channels.
-In this case, although the input training parameters are same for all channels, QRNN needs to be trained separately each 183\,GHz channel.
+In the second QRNN model, we suggest to use all three 183\,GHz channels (from ICI) concurrently, along with sub-mm channels.
+In this case, although the input training parameters are identical for all channels, the target channel is different and QRNN has to be trained separately for each.
 Further in text, we refer this model as ``QRNN-all''.
 Table~\ref{tab:QRNN_models} summarises the two QRNN models.
+
+Apart from these two models, we also extend QRNN-simple to predict the clear-sky values for MWI channels.
+In this case, we combine the measurements from MWI-15(MWI-16) and the sub-mm channels to predict MWI-15(MWI-16).
+Since we assume that all channels are remapped to a common footprint, channels MWI-14, MWI-17 and MWI-18 are virtually identical to I1V, I2V and I3V, and thus results for them are not shown separately.
 
@@
 On basis of these results, a neural network with four hidden layers and 128 neurons in each layer was selected for QRNN-simple.
-
 For the optimising the training paramters, a customised  learning rate scheduler was implemented.
@@
 Rectified Linear Unit (ReLU) was used as the activation function  and the batch size was set to 128 samples for all QRNN models.
+
 For QRNN-all a grid search (results not shown) over width and depth and learning rates resulted in similar performance, and an identical neural network was selected.
@@
 	\centering
-	\includegraphics[height=57mm]{Figures/CRPS.png} 
-	\includegraphics[height=57mm]{Figures/quantile_loss.png}
-	\caption{}
+	\includegraphics[height=60mm]{Figures/CRPS.pdf} 
+	\caption{CRPS(left) and mean quantile loss(right) for different combinations of layer width and hidden layers ($n_h$). The results are from QRNN-simple for channel I2V.}
 	\label{fig:}	
@@
 
-\subsection{Prediction results}
+\subsection{Results}
 %
@@
 \begin{figure}[t]
-	\includegraphics[height=57mm]{Figures/PDF_I1V_single.png} 
-	\includegraphics[height=57mm]{Figures/PDF_I2V_single.png}
-	\includegraphics[height=57mm]{Figures/PDF_I3V_single.png} 
-	\caption{PDF}
+	\includegraphics[width=\textwidth]{Figures/PDF_predictions_ICI.pdf} 
+	\caption{Distributions of predicted clear-sky values from QRNN-simple for channels I1V, I2V and I3V. }
 	\label{fig:PDF_predictions}	
@@
 %f 
-\begin{figure}[t]
-	\includegraphics[height=57mm]{Figures/ICI_I1V_single.png} 
-	\includegraphics[height=57mm]{Figures/ICI_I2V_single.png}
-	\includegraphics[height=57mm]{Figures/ICI_I3V_single.png} 
-	\caption{Error distributions}
+\begin{figure}[t ]
+	\includegraphics[width=\textwidth]{Figures/error_distribution_QRNN-single.pdf} 
+	\caption{Error distributions for deviations of QRNN-simple predictions to clear-sky simulations for channels I1V, I2V and I3V.
+Label ``uncorrected'' represents the measurements, ``predicted'' denotes the entire dataset, while ``predicted(5\,K)'' refers to the dataset where cases with cloud correction greater than 5\,K are excluded.}
 	\label{fig:error_distributions}	
@@
 \begin{table}[t]
-	\caption{I1V}
-	\label{tab:I1V_statistics}
-	\begin{tabular}{lrrrrrr}
+	\caption{Bias, mean absolute error(MAE), standard deviation(STD), and measure of skewness(Skewness) for error distributions of predictions of I1V, I2V and I3V.
+Results from both QRNN-simple and QRNN-all are shown.
+The label ``All'' refers to the complete dataset, while in ``Filtered'', cases with cases with cloud correction greater than 5\,K(15\,K) are excluded from statistics.
+The fraction of cases removed by this filter are given in parentheses.}
+	\label{tab:error_statistics_ici}
+%	\tabcolsep=0.11cm
+	\begin{tabular}{llrr|rrr|rrr}
 		\tophline
-		&&& \multicolumn{2}{c}{QRNN-simple} & \multicolumn{2}{c}{QRNN-all}\\
-		&   noise &   uncorrected &   corrected(all) &   corrected(filtered) & corrected(all) &   corrected(filtered) \\
+		&&\multicolumn{2}{c|}{Simulations}& \multicolumn{3}{c|}{QRNN-simple} & \multicolumn{3}{c}{QRNN-all}\\
+		\cline{3-10}
+%		\hline
+		&&   Clear-sky &   All-sky &   All &   Filtered(5K) & Filtered(15K) & All &   Filtered(5K) & Filtered(15K) \\
 		\middlehline
-		bias     &   -0.00 &         -1.90 &           -0.03 &                 0.00 & -0.01 &                 0.01 \\
-		mae      &    0.64 &          2.35 &            0.69 &                 0.60 & 0.66 &                 0.58\\
-		std      &    0.80 &          8.92 &            1.05 &                 0.78 &  0.96 &                 0.75\\
-		skewness &   -0.01 &         -7.99 &           -1.24 &                -0.44 & -0.39 &                -0.32\\
-		rejected &    	 - &          - &            - &                 6.40 & - &                 6.42 \\
-		\bottomhline
-	\end{tabular}
-	\belowtable{} % Table Footnotes
-\end{table}
-%t
-\begin{table}[t]
-	\caption{I2V}
-	\label{tab:I2V_statistics}
-	\begin{tabular}{lrrrrrr}
-		\tophline
-		&&& \multicolumn{2}{c}{QRNN-simple} & \multicolumn{2}{c}{QRNN-all}\\
-		&   noise &   uncorrected &   corrected(all) &   corrected(filtered) & corrected(all) &   corrected(filtered) \\
+%		\multicolumn{7}{c}{Channel - I1V}\\
+
+Channel I1V &Bias     &   -0.00 &   -1.90&    -0.03 &      0.00(6.40\%) & 0.01(3.09\%)&-0.01 &0.01 (6.42\%)& 0.02(3.09\%) \\
+			&MAE      &    0.64 &    2.35&     0.69 &      0.60 & 0.63  &  0.65 & 0.62& 0.60\\
+			&STD      &    0.80 &    8.92&     1.05 &      0.78 &  0.84 &  0.97 & 0.84& 0.80\\
+			&Skewness &   -0.01 &   -7.99&    -1.24 &     -0.44 & -0.48 & -0.36 &-0.51&-0.34\\
 \middlehline
-		bias     &   -0.00 &         -1.05 &            0.02 &                 0.03&  0.02&   0.03\\
-		mae      &    0.64 &          1.54 &            0.56 &                 0.50&  0.46&   0.42\\
-		std      &    0.80 &          5.98 &            0.86 &                 0.64&  0.70&   0.53\\
-		skewness &    0.02 &        -10.64 &           -2.25 &                -0.22& -1.67&  -0.25\\
-		rejected &    - &          - &            - &                 3.70&  - &   3.67\\
+Channel I2V	&Bias     &   -0.00 &         -1.05 &    0.02 &      0.03(3.70\%)&0.02(1.60\%) &  0.02&   0.03(3.67\%)& 0.02(1.60\%)\\
+			&MAE      &    0.64 &          1.54 &    0.56 &      0.50&  	  0.52 &  0.46&   0.42 &  0.52\\
+			&STD      &    0.80 &          5.98 &    0.86 &      0.64&  	  0.69 &  0.70&   0.53 &  0.69\\
+			&Skewness &    0.02 &        -10.64 &   -2.25 &     -0.22& 		 -0.58 & -1.69& -0.25 &-0.56\\
+\middlehline	
+Channel I3V &Bias     &   0.00  &         -0.63 &    0.02 &      0.02(2.18\%)&0.03(0.92\%)&	 0.04 &  0.04(2.18\%) & 0.04(0.92\%) \\
+			&MAE      &   0.64  &          1.14 &    0.54 &      0.50		& 0.52&0.48 &    0.44 & 0.46\\
+			&STD      &   0.80  &          4.26 &    0.80 &      0.64		& 0.68&0.71 &     0.56 & 0.60\\
+			&Skewness &   0.00  &        -13.26 &   -1.40 &     -0.16		&-0.61&-1.41&   -0.11 & -0.77\\	
 		\bottomhline
@@
 \begin{table}[t]
-	\caption{I3V}
-	\label{tab:I3V_statistics}
-	\begin{tabular}{lrrrrrr}
+	\caption{Same as Table~\ref{tab:error_statistics_ici}, but for channels MWI-15 and MWI-16. Results are from QRNN-simple.}
+	\label{tab:statistics_mwi}
+	\begin{tabular}{llrr|rrr}
 		\tophline
-		&&& \multicolumn{2}{c}{QRNN-simple} & \multicolumn{2}{c}{QRNN-all}\\
-		&   noise &   uncorrected &   corrected(all) &   corrected(filtered) & corrected(all) &   corrected(filtered) \\
+		&&\multicolumn{2}{c|}{Simulations}& \multicolumn{3}{c}{QRNN-simple} \\
+		\cline{3-7}
+		%		\hline
+		&&   Clear-sky &   All-sky &   		 All &   Filtered(5\,K) & Filtered(15\,K) \\
 		\middlehline
-		bias     &   0.00 &         -0.63 &            0.02 &                 0.02& 0.04 &                 0.04 \\
-		mae      &    0.64 &          1.14 &            0.54 &                 0.50&0.48 &                 0.44 \\
-		std      &    0.80 &          4.26 &            0.80 &                 0.64&0.71 &                 0.56 \\
-		skewness &   0.00 &        -13.26 &           -1.40 &                -0.16&-1.41 &                -0.11 \\
-		rejected &    - &          - &           - &                 2.18&- &                 2.18 \\
+ MWI-15 		&Bias     &    0.00 &         -1.19 &           -0.02 &                -0.01(4.41\%) & -0.02(1.87\%)\\
+				&MAE      &    0.64 &          1.66 &            0.56 &                 0.49 		 &  0.52\\
+				&STD      &    0.80 &          6.21 &            0.84 &                 0.64 		 &  0.69\\
+				&Skewness &   -0.02 &         -9.87 &           -1.67 &                -0.29 		 & -0.47\\
+		\middlehline
+ MWI-16 		& Bias 	   &    0.00 &         -0.80 &           -0.04 &   -0.03(2.85\%) & -0.04(1.15\%)\\
+				& MAE      &    0.64 &          1.31 &            0.54 &     0.49		 & 0.51\\
+				& STD      &    0.80 &          5.01 &            0.82 &     0.63		 & 0.67\\
+				& Skewness &    0.01 &        -12.04 &           -1.94 &    -0.23		 &-0.81\\
 		\bottomhline			
@@
 QRNN predictions are estimates of the posterior distribution over different quantiles: $x_{\tau}$, for median, $\pm 1\sigma$, $\pm 2 \sigma$ and  $\pm 3 \sigma$ ($\tau$ = 0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998).
-The median of the posterior distribution is assumed to be the best estimate for the predicted clear-sky value.
-The prediction error is calculated as the deviation to the corresponding noise-free clear-sky value.
+To assess the accuracy of the predictions, the median of the posterior distribution is assumed to be the best estimate for the predicted clear-sky value.
+The prediction errors are calculated as the deviation of the predictions to their corresponding noise-free clear-sky values.
 We calculate the mean bias, mean absolute error and standard deviation of the errors.
-The asymmetry of the distributions around their mean is also calculated through the measure of skewness.
-In the following sections, we describe the performance of the two QRNN models.
+The asymmetry of error distributions around their mean is also calculated through the measure of skewness.
+In the next sections, we describe the performance of the two QRNN models for ICI and MWI channels.
 
-The distributions of the predicted clear-sky values and the clear-sky simulations from QRNN-single are shown in Fig~\ref{fig:PDF_predictions}.
+\subsection{Prediction accuracy}
+%
+The distributions of median value of clear-sky predictions from QRNN-single are shown in Fig~\ref{fig:PDF_predictions}.
+The distributions of corresponding clear-sky simulations are also plotted as reference.
 The three figures correspond to channels: I1V, I2V and I3V.
@@
 
-Fig~\ref{fig:error_distributions} shows the error distributions of the uncorrected measurements and predicted clear-sky TBs for all three channels.
-Distribution of noise is also plotted for reference.
-The error metrics corresponding to these results are provided in Table~\ref{tab:I1V_statistics} - Table~\ref{tab:I3V_statistics}.
-Without any cloud impact, the error distributions should follow a Gaussian distribution, however the presence of clouds leads to a TB reduction, and introduces a high negative bias.
-Among the three channels, I1V has the highest cloud impact and I3V has the least.
-The bias in I1V measurements is -1.89\,K compared to only -0.55\,K in I3V.
-After correction, the cloud impact is reduced and the resulting error distributions are symmetric with low bias.
+For a quantitative evaluation of how accurate the predictions are, the  deviations of the median values to the clear-sky simulations are computed.
+Fig~\ref{fig:error_distributions} shows the error distributions of predictions for all three channels.
+The distribution of noise is also plotted for reference.
+The error metrics corresponding to these results are provided in Table~\ref{tab:error_statistics_ici}.
+Without any cloud impact, the error distributions should follow a Gaussian distribution, however the presence of clouds leads to a TB reduction, and introduces a high negative bias among the deviations.
+Among the three channels, the highest cloud impact is seen in channel I1V.
+The average bias in channel I1V measurements is -1.89\,K, however the QRNN-single predictions successfully reduces the average deviation to -0.03\,K.
 The predictions and the observations have a good agreement for the main peak of the distribution, albeit the prediction errors have a sharper peak and a larger spread.
-The larger spread indicates few cases which are under-/over corrected.
-If all the cases with correction greater than 15\,K are excluded, only a fraction of the total cases are removed but the  the variability in predictions errors reduces significantly.
-This indicates low accuracy of QRNN predictions for cases with high cloud impact.
+The large spread is representative of the few cases which are either under/over predicted.
+If all the cases with correction greater than 5\,K are excluded, only a fraction of the total cases (6.42\%) are removed but the variability in predictions errors reduces significantly.
+This indicates that few cases with high cloud impact could be difficult to train and predict.
 
-Compared to channel I1V, the performance of QRNN model is slighly better for I2V and I3V.
+The performance of QRNN-single for I2V and I3V is analogous to I1V, though the accuracy seems to be higher for former.
+When all predictions are included, the average deviation for both I2V and I3V is -0.02\,K, but few cases with large errors increases the spread of the distributions.
+As observed for I1V, excluding cases with cloud correction greater than 5\,K removes the cases associated with low accuracy.
+Interestingly, the resulting spread of errors is also narrower than noise.
+After filtering, the error standard deviation for both I2V and I3V is 0.64\,K compared to 0.80\,K originating from measurement noise.
 
-The error metrics from QRNN-all are also shown in the last columns of Table~\ref{tab:I1V_statistics} - Table~\ref{tab:I3V_statistics}.
-As expected, using additional 183\,GHz channels improves the accuracy of the predictions slightly.
+The results QRNN-all are also shown in Table~\ref{tab:error_statistics_ici}.
+Using additional information from other 183\,GHz channels has a definite positive impact on the QRNN training.
+A marked impact is seen for channel I1V, where the low measure of skewness over the entire test set indicates that the resulting distributions are more symmetric than QRNN-simple.
+When cases with correction greater than 5\,K are excluded, the variability of errors is smaller than noise.
+A similar trend is observed for channels I2V and I3V.
 
-**** add QRNN-all results ****
+Table~\ref{tab:statistics_mwi} shows the metrics from error distributions for MWI-15 and MWI-16 predictions.
+Results from only QRNN-simple are shown.
+As shown above for ICI channels, the performance of QRNN-simple for the two MWI channels is consistent.
 
@@
 \begin{figure}[t]
-	\includegraphics[height=57mm]{Figures/scatter_uncertainty_single_I1V.png} 
-	\includegraphics[height=57mm]{Figures/scatter_uncertainty_single_I2V.png}
-	\includegraphics[height=57mm]{Figures/scatter_uncertainty_single_I3V.png} \\
-	\includegraphics[height=57mm]{Figures/Frequency_uncertainty_bins_I1V_single.png} 
-	\includegraphics[height=57mm]{Figures/Frequency_uncertainty_bins_I2V_single.png}
-	\includegraphics[height=57mm]{Figures/Frequency_uncertainty_bins_I3V_single.png}
-	\\	
+	\includegraphics[width=\textwidth]{Figures/PDF_uncertainty_bins_QRNN-single.pdf}	
+	\caption{Distribution of errors binned according to their uncertainty. Results are from QRNN-simple for channels I1V, I2V and I3V.}
+	\label{fig:error_distribution_uncertainty_bins_I1V}	
+\end{figure}
+\begin{figure}[t]
+	\includegraphics[height = 70mm]{Figures/calibration_QRNN_I2V.pdf}	
+	\caption{Calibration of the prediction intervals obtained from QRNN-simple and QRNN-all for channel I2V. }
+	\label{fig:calibration_I2V}	
+\end{figure}
+The biggest advantage of using QRNN is estimation of case-specific uncertainties.
+The quantiles can be used to construct a probability distribution of the predictions in contrast to other correction approaches which give out only point estimates.
+The predictions for each quantile can be used to construct the confidence intervals.
+The confidence interval for each point estimate quantifies it's uncertainty.
+For example, if $\tau_1$ and $\tau_2$ are two quantiles then there is $\tau_2-\tau_1$ probability that the true value will lie in between the range.
+
+To test if the uncertainty estimates given by QRNN are representative of prediction errors, we divided the $\pm2\sigma$ confidence interval into three bins and estimated the prediction error distribution for each.
+Figure~\ref{fig:error_distribution_uncertainty_bins_I1V} shows the prediction error distributions binned according to $2\sigma$ confidence interval for I1V, I2V and I3V.
+These results are from QRNN-simple.
+Similar results were also obtained for QRNN-all (figure not shown).
+Among the three channels the uncertainty in predictions for I1V and I2V are higher than I3V and an increase in the spread of errors with increasing uncertainty is evident in all three.
+As the errors increase, the spread is mostly symmetric around x-axis but among predictions associated with large uncertainties, high errors occur frequently.
+In other words, too-low/too-high QRNN predictions tend to be associated with high uncertainty.
+
+Figure~\ref{fig:calibration_I2V} shows the calibration of prediction intervals on the test dataset for channel I2V.
+Results from both QRNN-simple and QRNN-all are shown.
+The calibration of predictions with correction greater than 5\,K is also shown.
+For the entire test dataset, the calibration curves for QRNN-simple and QRNN-all are quite identical.
+If cases with cloud correction greater than 5\,K are considered, the calibration curve for QRNN-simple lies  below y=x line, implying that the prediction intervals are overly narrow.
+A similar behaviour is observed for channel I3V (figure not shown).
+However, for channel I1V, both QRNN-all and QRNN-simple fail to provide well calibrated predictions for cases associated with high cloud impact.
+
+These results show that both QRNN-simple and QRNN-all are successful in providing well calibrated probabilistic predictions of the posterior distributions except for few cases associated with high cloud impact.
+This is not unexpected, as such cases form a small subset of the training set and their priori distribution could be different from the the entire dataset.
+Since such cases form only a fraction of the training dataset, it can be hard to train the model to predict them accurately.
+A larger training dataset is needed to increase the representation of such cases in QRNN.
+\subsection{Discussion}
+
+\section{Special case of using only 325\,GHz for cloud correction}
+In this section, we investigate the possibility of using only channels around 325\,GHz for cloud correction at 183\,GHz.
+This special case of utilising only 325\,GHz channel can be relevant for smaller satellite missions like Artic Weather Satellite (AWS) where higher sub-mm channels are not available.
+
+\subsection{Data}
+\subsubsection{Artic Weather Satellite}
+The Arctic Weather Satellite (AWS) is a small satellite mission approved as ESA Earth Watch 
+Programme Element.
+It is a small platform carrying a single across-track scanning microwave radiometer.
+The main objective of AWS will be to improve representation of Artic and sub-Arctic weather in NWP models and improve the global weather forecasts.
+AWS will will have channels receiving frequencies around 89\,GHz, 165.5\,GHz, 183\,GHz, 229\,GHz and 325\,GHz.
+For a detailed description of the AWS channels see \citep{eriksson-etal_AWS_2020}, while a brief summary of AWS channels relevant to this study are provided in Table~\ref{tab:specifications_AWS}
+\begin{table*}[t]
+	\label{tab:ICI_MWI_channels}	
+	\caption{Specifications of AWS channels around 183\,GHz and 325\,GHz.}
+	\begin{tabular}{lrr}
+		\tophline
+		Channel & Frequency 	& Bandwidth  \\
+				& [GHz]			& [MHz]		\\
+		\middlehline
+		AWS-32	&	176.311    & 2000 		\\
+		AWS-33	&	178.811    & 2000 		\\
+		AWS-34	&	180.311    & 1000 		\\
+		AWS-35	&	181.511    & 1000 		 \\
+		AWS-36	&	182.311    & \phantom{0}500 	 \\
+	    AWS-41    & 325.15$\pm$6.60    & 2800 \\
+		AWS-42    & 325.15$\pm$4.10    & 1800  \\
+		AWS-43    & 325.15$\pm$2.40    & 1200 \\
+		AWS-44    & 325.15$\pm$1.20    & \phantom{0}800  \\
+			\bottomhline
+	\end{tabular}
+	\belowtable{} % Table Footnotes
+\end{table*}
+
+\subsubsection{AWS simulations}
+The satellite observations for AWS channels were simulated with ARTS.
+An similar ARTS set-up, as described for ICI (Section~\ref{sec:arts_simulations}) was followed, except that 24 monochromatic frequencies were used so that each channel could be represented with sufficient accuracy.
+All AWS sensor viewing angles (from $0^\circ$ to $45^\circ$) were simulated, but the results described in this section are based on nadir viewing angle.
+125\,000 cases based on randomly selected CloudSat orbits were simulated.
+\subsection{Training}
+%
+Out of the 125\,000 AWS simulations, 75\,000 cases are randomly picked to form the training set.
+The rest are used for testing.
+In the training set, 90\% of the data is randomly selected to form the training set, while the other 10\% form the \textit{testing-during-training} database.
+A similar data augmentation technique as described for ICI (Sec~\ref{sec:ici_training}) was followed to build a robust database and avoid memorisation of the samples.
+
+For each 183\,GHz channel from AWS, a training scheme similar to QRNN-simple is used. For example, to
+predict clear-sky TBs from AWS-34, the training data includes measurements AWS-34 and channels AWS-41, AWS-42, AWS-43, AWS-44.
+A grid search over the hyper-parameters was performed (results not shown) and the best performance over the validation set was obtained for 4 hidden layers with 128 neurons and batch size of 128 samples.
+Rectified Linear Unit (ReLU) was used as the activation function
+\subsection{Prediction accuracy}
+%f
+\begin{figure}[t]
+	\includegraphics[width = 80mm]{Figures/AWS-34_single.pdf}	
+	\caption{Error distributions for AWS-34 predictions.
+Label ``uncorrected'' represents the measurements, ``predicted'' denotes the entire dataset, while ``predicted(5\,K)'' and  ``predicted(15\,K)''  refers to the datasets where cases with cloud correction greater than 5\,K and 15\,K are excluded, respectively.}
+	\label{fig:qrnn_C34_deviations}	
+\end{figure}
+In an analogy between the results from ICI channels, we perform a similar error distribution analysis.
+Figure~\ref{fig:qrnn_C34_deviations} shows the error distributions of the measurements and predicted clear-sky TBs for AWS-34.
+The statistics corresponding to curves are illustrated in Table~\ref{tab:statistics_qrnn_aws}.
+The label ``Filtered'' represents the subset where all cases with correction greater than 5\,K(15\,K) are removed.
+The cloud impact in the uncorrected measurements is reflected in the high negative skewness (-10.30), however the  error distributions for the predictions are relatively symmetric.
+Removing cases with cloud correction greater than 5\,K, removes only 3.02\% of the data, but the errors reduce significantly.
+Infact, the standard deviation of predictions suggests that QRNN is successful in predicting the variability of noise-free simulations.
+
+Similar error statistics for other other 183\,GHz channels are also listed in Table~\ref{tab:statistics_qrnn_aws}.
+For channel AWS-32, the average bias and standard deviation in the prediction errors is is -1.34\,K and 5.91\,K respectively.
+However, after correction, the bias and standard deviation are -0.08\,K and 1.0\,K.
+A decrease in the skewness of error distributions is evident(from -7.48 to -1.52), but a relatively high values after prediction indicate presence of cases with partially-corrected cloud impact.
+For AWS-33, the predictions have slightly higher accuracy than AWS-32.
+The MAE in predictions is only 0.50\,K in comparison to 1.23\,K for the measurements.
+Similar results are also seen for AWS-35 and AWS-36.
+For both channels, the predictions are relatively more symmetric than the other channels.
+Also, it is worth to noting that when cases with 5\,K cloud correction are removed, the spread of predictions is narrower than noise.
+
+\begin{table}[t]
+	\caption{Bias, mean absolute error(MAE), standard deviation(STD), and measure of skewness(Skewness) for error distributions of predictions AWS channels.
+Results are from QRNN-simple.
+The label ``All'' refers to the complete dataset, while in ``Filtered'', cases with cases with cloud correction greater than 5\,K(15\,K) are excluded from statistics.
+The fraction of cases removed by this filter are given in parentheses.}
+	\label{tab:statistics_aws}
+	\begin{tabular}{llrr|rrr}
+		\tophline
+		&&\multicolumn{2}{c|}{Simulations}& \multicolumn{3}{c}{QRNN-simple} \\
+		\cline{3-7}
+		%		\hline
+		&&   Clear-sky &   All-sky &   		 All &   Filtered(5K)& Filtered(15K) \\
+		\middlehline
+AWS-32    &Bias     &   -0.00 &         -1.34 &           -0.08 &       		-0.07(5.30\%) & -0.08(2.50\%) \\
+          &MAE      &    0.36 &          1.58 &            0.62 &        		 0.53 		  &	0.57	\\
+          &STD      &    0.45 &          5.91 &            1.00 &        		 0.74 		  & 0.85\\
+          &Skewness &    0.02 &         -7.48 &           -1.52 &       		-1.63 		  & -2.01\\
+		\middlehline
+AWS-33	  &Bias     &   -0.00 &         -0.98 &            0.01 &                 0.00(4.08\%)& 0.00(1.75\%)\\
+		  &MAE      &    0.36 &          1.23 &            0.50 &                 0.43 	      & 0.46\\
+		  &STD      &    0.45 &          4.70 &            0.77 &                 0.57 	      & 0.64\\
+		  &Skewness &    0.01 &         -8.76 &           -0.40 &                -0.90  	  & -1.00\\
+
+		\middlehline
+AWS-34	  &Bias    &    0.00 &         -0.68 &            0.02 &                0.01(3.02\%)& 0.01(1.11\%) \\
+		  &MAE      &    0.50 &          1.08 &            0.53 &                 0.47 		 & 0.50\\
+		  &STD      &    0.63 &          3.69 &            0.78 &                 0.62 		 & 0.70\\
+		  &Skewness &    0.02 &        -10.30 &           -0.34 &                -0.49 		 &-0.76	\\
+		 \middlehline
+AWS-35	 & Bias     &    0.00 &         -0.42 &            0.01 &                 0.01(1.92\%) & 0.01(0.70\%) \\
+		 &MAE       &    0.50 &          0.83 &            0.50 &                 0.47 		   & 0.49\\
+		 &STD       &    0.63 &          2.65 &            0.71 &                 0.60         & 0.65\\
+		 &Skewness  &    0.01 &        -12.45 &           -0.15 &                -0.15         &-0.26\\
+		 \middlehline
+AWS-36   &Bias     &    0.00 &         -0.27 &            0.02 &                 0.02(1.30\%) & 0.02(0.31\%)\\
+		 &MAE      &    0.70 &          0.90 &            0.67 &                 0.64 		  & 0.06\\
+		 &STD      &    0.88 &          2.06 &            0.91 &                 0.81 		  &0.85\\
+		 &Skewness &   -0.01 &        -12.00 &           -0.51 &                -0.15 		  &-0.12\\	 
+		\bottomhline				
+	\end{tabular}
+	\belowtable{} % Table Footnotes
+\end{table}
+\subsubsection{Uncertainty quantification}
+%f
+\begin{figure}[t]
+	\includegraphics[width = 80mm]{Figures/prediction_uncertainty_aws-34.pdf}	
 	\caption{}
-	\label{fig:error_distributions}	
+	\label{fig:prediction_uncertainty_aws-34}	
 \end{figure}
-The biggest advantage of using QRNN is estimation of case-specific uncertainties. The quantiles can be used to construct a probability distribution of the
-predictions in contrast to other correction approaches which give out only point estimates. In all QRNN models presented in this article, we estimate the conditional
-quantiles for median, $\pm 1\sigma$, $\pm 2\sigma$, and $\pm 3\sigma$. The
-predictions for each quantile are used to construct the confidence intervals.
-The confidence interval for each point estimate quantifies its uncertainty.
-For example, the predicted quantiles for $\pm 2 \sigma$ implies that there is  94\% probability that the true value will lie between the range.
+\begin{figure}[t]
+	\includegraphics[width = 80mm]{Figures/cloud_impact_uncertainty_AWS.pdf}	
+	\caption{The average confidence intervals (2$\sigma$) plotted against the magnitude of cloud impact for all AWS channels.}
+	\label{fig:uncertainty_cloud_impact}	
+\end{figure}
 
-Fig~\ref{fig:uncertainty_scatter} shows the scatter plot between the error and uncertainty.
-The error distributions for all three channels are centered around zero, however the uncertainty in predictions for I1V and I2V are higher than I3V.
-An increase in the spread with increasing uncertainty is evident in all three.
-As the errors increase, the spread is mostly symmetric around x-axis but for high uncertainty values, negative errors occur more frequently.
-This suggests that predictions for cases high cloud impact are associated with high uncertainty.
-The lower panel in the same figure, shows the errors when plotted as distributions over different uncertainty bins.
-Apart from few individual variations, all three channels follow the trend of increasing uncertainty with decreasing accuracy, suggesting that QRNN is successful in providing well calibrated probabilistic predictions of the posterior distribution.
+%As the QRNN predictions are in form of quantiles, each prediction has an uncertainty estimate associated with it.
+Case specific uncertainty estimates can be quite useful but estimates of uncertainty fitted to a Gaussian model of random errors are potentially easier to implement in NWP models.
+To inspect if the predictions given by QRNN follow a normal distribution, we evaluated the length of confidence intervals from the median.
+Figure~\ref{fig:prediction_uncertainty_aws-34} shows the prediction uncertainty in AWS-34 for different quantiles.
+The red line represents the uncertainty in a hypothetical Gaussian distribution of $270\pm0.62$\,K.
+The high variability in the uncertainty estimates indicates that QRNN can successfully represent uncertainties for multiple types of cases in the individually, rather than having just a single summary measure of uncertainty about the whole scene.
 
-%Fig~\ref{fig:uncertainty_estimate} shows the prediction uncertainties for randomly chosen 2000 cases. A large spread in the plot indicates a high case-to-case variability of the uncertainty.
-
-%To inspect if the predictions follow a normal distribution, we evaluate the length of confidence intervals from the median.
-Figure~\ref{fig:prediction_uncertainty} shows the prediction uncertainty in AWS-34 (four channel option).
-The uncertainty with respect to the median for 1000 randomly selected cases is shown.
-The red line represents the uncertainty in a hypothetical Gaussian distribution of $270\pm0.62$\,K.
-If the underlying distribution is Gaussian, the prediction uncertainty should be symmetric around the median, and the uncertainties should be equally spaced for $1\sigma$, $2\sigma$ and so on.
-The predictions from our QRNN model seem to be symmetric around the median for the 94\% confidence interval ($\pm 2 \sigma$).
+%If the underlying distribution is Gaussian, the prediction uncertainties should be symmetric around the median, and equally spaced for $1\sigma$, $2\sigma$ and so on.
+The predictions around the median for the 94\% confidence interval ($\pm 2 \sigma$).
 The figure also shows that the uncertainties for all 1000 random cases are concentrated along a narrow width, thus suggesting that the case to case variability of the uncertainty is low.
@@
 
-%f
-%\begin{figure}[t]
-%\includegraphics[height=57mm]{Figures/uncertainty_single_I1V.png} 
-%\includegraphics[height=57mm]{Figures/uncertainty_single_I2V.png}
-%\includegraphics[height=57mm]{Figures/uncertainty_single_I3V.png} 
-%\caption{}
-%\label{fig:}
-%\end{figure}
+In order to analyse the performance of QRNN with task difficulty, the interrelation between the uncertainty estimates and cloud impact was investigated.
+Fig~\ref{fig:uncertainty_cloud_impact} displays the plot between mean uncertainty estimates for $2\sigma$ confidence interval and the cloud impact.
+For all five channels, the predictions with small or relatively low cloud signal have a low uncertainty or in other words have high sharpness.
+As fraction of cloud impact increases, the predictions are associated with high uncertainty.
+If we assume that higher cloud impact is representative of increase in task difficulty, the uncertainty of predictions increases with task difficulty.
 
-\section{Special case of using only 325\,GHz for cloud correction}
+%On the other hand, in order to examine if task difficulty also decreased the accuracy, we plotted the error distribution binned according to the cloud impact.
 
-\subsection{Data}
-24 monochromatic frequencies were used so that each channel could be represented
-with sufficient accuracy. The simulations were generated for sensor viewing angles from
-$0^{\circ}$ to $45^{\circ}$, but all the results described here are based on nadir viewing angle.
+\subsubsection{Discussion}
+%
+The results demonstrate that QRNN is successful in predicting the clear-sky
+noise-free data for AWS-33, AWS-34, AWS-35 and AWS-36 and partially for AWS-32.
+The prediction error distributions are symmetric with low bias and standard deviation.
+The cases with high error are mostly associated with high cloud impact and constitute only a small fraction of the total dataset.
+Excluding such cases decreases the variability in the predictions and in fact the spread of errors for AWS-34, AWS-35 and AWS-36 is smaller than noise.
+Removal of cases with high cloud impact, increases the representation of cases in cloud-free conditions, and for such cases, QRNN predictions can be seen as a weighted mean between the two ``super-channels''.
+Since the noise in the two channels are stationary and uncorrelated, the predictions benefit from the additional information, but the noise component tends to cancel out.
 
-\subsection{Training}
+For AWS-32, QRNN is only partially successful in reducing the impact of hydrometeors.
+The resulting error distributions have significantly lower spread than the measurements, but are still negatively skewed.
+Since 325\,GHz cannot provide a full coverage for hydrometeor impact in AWS-32, QRNN cannot learn to predict cloud free values for instances which lie outside the area of coverage.
 
-\subsection{Prediction results}
-
-\conclusions  %% \conclusions[modified heading if necessary]
+\section{Outlook and Conclusions}  %% \conclusions[modified heading if necessary]
 
@@
  \bibliographystyle{copernicus}
- \bibliography{example.bib}
+ \bibliography{references.bib}
 

### 2020-09-09 ICI/PDF_MWI.py
new scripts for article plots and analysis

@@ -15,11 +15,11 @@ from read_ARTS_output import read_all_files
 import xarray
 from add_gaussian_noise import add_gaussian_noise
 from read_clear_allsky_pairs import read_clear_allsky_pairs, read_clear_allsky_pairs_MWI
-from get_IWP import get_altitude, get_y_cloudsat
+from get_IWP import get_IWP
 from ICI_channel_TB import ICI_channel_TB
 import random
-theta = 135.2
 
+theta = 135.2
 #%%
 def calculate_histogram(TB, bins, channels):
         hist_arts = []
@@ -35,26 +35,22 @@ f_grid = np.concatenate([183.31 + np.array([-7.0, -3.4, -2.0, 2.0, 3.4, 7.0]),
                                 243.20 + np.array([-2.5, 2.5]),
                                 325.15 + np.array([-9.5, -3.5, -1.5, 1.5, 3.5, 9.5]),
                                 448.00 + np.array([-7.2, -3.0, -1.4, 1.4, 3.0, 7.2]),
-                                664.00 + np.array([-4.2, 4.2])])
+                                664.00 + np.array([-4.2, 4.2]),
+                                183.31 + np.array([-6.1, -4.9, 4.9, 6.1])]) # added two MWI channels
 
 nchannels = len(f_grid)
 nedt  = np.array([0.8, 0.8, 0.8, #183Ghz
+                  1.2, 1.2,      #183Ghz, MWI
                   0.7, 0.7,      #243Ghz
                   1.2, 1.3, 1.5, #325Ghz
                   1.4, 1.6, 2.0, #448Ghz
-                  1.6, 1.6
-                  ])      #664Ghz
-#                  1.2, 1.2])     #183Ghz, MWI
+                  1.6, 1.6,])    #664Ghz    
 
-files = glob.glob(os.path.expanduser('~/Dendrite/Projects/AWS-325GHz/\
-                                     ICI_m60_p60/c_**clearsky.nc'))
-#%% get dBZ and altitude 
 
-dBZ      = get_y_cloudsat(files[:])
-altitude = get_altitude(files[:])
[…]

### 2020-09-09 ICI/PDF_uncertainty.py

@@ -1,0 +1,102 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Fri Sep  4 22:54:58 2020
+
+@author: inderpreet
+
+plot error distributions in uncertainty bins
+"""
+
+import matplotlib.pyplot as plt
+import numpy as np
+import netCDF4
+import stats as S
+from ici import iciData
+plt.rcParams.update({'font.size': 32})
+from matplotlib.ticker import (MultipleLocator, FormatStrFormatter,
+                               AutoMinorLocator)
+
+from typhon.retrieval.qrnn import set_backend, QRNN
+set_backend("pytorch")
+
+#%%
+def PDF_uncertainty_bins(y_pre, y0, ulim):
+    dtb =(y_pre[:, 3] - y0)
+    uncertain = y_pre[:, 5] - y_pre[:, 1]
+ #I1V
+    #ulim = [3, 4] #I2V
+    #ulim = [1, 1.5 ]#I3V
+    
+    im = uncertain < ulim[0]
+    print (np.sum(im))
+    bins = np.arange(-12.5, 15., 0.8)
+    hist0 = np.histogram(dtb[im], bins, density = True)
+    
+    
+    im = np.logical_and((uncertain < ulim[1]), ( uncertain >= ulim[0]) )
+    hist1 = np.histogram(dtb[im], bins, density = True)
+    
+
+    
+    im = uncertain >=ulim[1]
+    hist2 = np.histogram(dtb[im], bins, density = True)
+    
+    
+    return hist0[0], hist1[0], hist2[0], bins
+#%%
+
+#%% input parameters
+depth     = 4
+width     = 128
+quantiles = np.array([0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998])
+batchSize = 128
+
+targets = ['I1V', 'I2V','I3V']
+
+binstep = 0.5
+bins = np.arange(-20, 15, binstep)
+iq = np.argwhere(quantiles == 0.5)[0,0]
+ulim = [3, 8]
+
+#%% 
+
+fig, ax = plt.subplots(1, 3, figsize = [30, 10])
+plt.subplots_adjust(wspace = 0.001)
+for i,target in enumerate(targets):
+    inChannels = np.array([target, 'I5V' , 'I6V', 'I7V', 'I8V', 'I9V', 'I10V', 'I11V'])
+    data = iciData("TB_ICI_test.nc", 
+                   inChannels, target, 
[…]

### 2020-09-09 ICI/calibration_plot.py

@@ -1,0 +1,156 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Mon Sep  7 20:46:41 2020
+
+@author: inderpreet
+"""
+import matplotlib.pyplot as plt
+import numpy as np
+import netCDF4
+
+from matplotlib.ticker import (MultipleLocator, FormatStrFormatter,
+                               AutoMinorLocator)
+from typhon.retrieval.qrnn import set_backend, QRNN
+set_backend("pytorch")
+import stats as S
+from ici import iciData
+plt.rcParams.update({'font.size': 26})
+#%% calibration plot
+def calibration(y_pre, y0, im, quantiles):
+
+    intervals = []
+    for i in range(1, 6):
+        intervals.append(quantiles[i] - quantiles[0] )
+    a0 = 0
+    a1 = 0
+    a2 = 0
+    a3 = 0
+    a4 = 0
+    a5 = 0
+    a6 = 0
+    for i in im:
+
+        if np.logical_and(y0[i] > y_pre[i, 0] ,  y0[i] <=y_pre[i, 1]):
+                   a1 += 1
+        if np.logical_and(y0[i] > y_pre[i, 0] ,  y0[i] <= y_pre[i, 2]):
+                   a2 += 1               
+        if np.logical_and(y0[i] > y_pre[i, 0] ,  y0[i] <= y_pre[i, 3]):
+                   a3 += 1
+        if np.logical_and(y0[i] > y_pre[i, 0] ,  y0[i] < y_pre[i, 4]):
+                   a4 += 1
+        if np.logical_and(y0[i] > y_pre[i, 0] ,  y0[i] < y_pre[i, 5]):
+                   a5 += 1
+        if np.logical_and(y0[i] > y_pre[i, 0] ,  y0[i] < y_pre[i, 6]):
+                   a6 += 1
+    return a1, a2, a3, a4, a5,a6, intervals 
+#%% input parameters
+depth     = 4
+width     = 128
+quantiles = np.array([0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998])
+batchSize = 128
+
+target = 'I1V'
+
+
+inChannels = np.array(['I1V', 'I2V', 'I3V', 'I5V' , 'I6V', 'I7V', 'I8V', 'I9V', 'I10V', 'I11V'])
[…]

### 2020-09-09 ICI/get_ICI.py

@@ -8,13 +8,10 @@ Created on Thu Aug 13 11:50:28 2020
 
 import os
 import numpy as np
-import matplotlib.pyplot as plt
 import glob
 from polarisation import calculate_polarisation
-from read_ARTS_output import read_all_files
 import xarray
-from add_gaussian_noise import add_gaussian_noise
-from read_clear_allsky_pairs import read_clear_allsky_pairs, read_clear_allsky_pairs_MWI
+from read_clear_allsky_pairs import read_clear_allsky_pairs
 from get_IWP import get_altitude, get_y_cloudsat
 from ICI_channel_TB import ICI_channel_TB
 import random

### 2020-09-09 ICI/ici.py

@@ -1,7 +1,6 @@
 import numpy as np
 import netCDF4
 import torch
-from add_gaussian_noise import add_gaussian_noise
 from torch.utils.data import Dataset
 
 class iciData(Dataset):

### 2020-09-09 ICI/stats.py

@@ -1,0 +1,186 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Tue Sep  1 14:42:56 2020
+
+@author: inderpreet
+"""
+
+
+import matplotlib.pyplot as plt
+import numpy as np
+from scipy.stats import skew
+plt.rcParams.update({'font.size': 16})
+from matplotlib.ticker import (MultipleLocator, FormatStrFormatter,
+                               AutoMinorLocator)
+from scipy.stats import gaussian_kde
+
+quantiles = np.array([0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998])
+
+def predict(test_data, qrnn, add_noise = False):
+    """
+    predict the posterior mean and median
+    """
+    if add_noise:
+        x_noise = test_data.add_noise(test_data.x, test_data.index)
+        x = (x_noise - test_data.mean)/test_data.std
+        y_prior = x_noise
+        y = test_data.y_noise
+        
+        y0 = test_data.y
+    else:
+        x = (test_data.x - test_data.mean)/test_data.std
+        y_prior = test_data.x
+        y = test_data.y
+        y0 = test_data.y0
+
+
+    y_pre = qrnn.predict(x.data)
+    y_pos_mean = qrnn.posterior_mean(x.data)
+    
+    return y_pre, y_prior, y0, y, y_pos_mean
+
+def calculate_all_histogram(y, y0, y_pre, y_prior, iq, bins, im, i183):
+    hist_noise  = calculate_pdf(y, y0, bins)
+    
+    hist_pre    = calculate_pdf(y_pre[:, iq], y0, bins)
+    
+    hist_prior  = calculate_pdf(y_prior[:, i183], y0, bins)
+    
+    hist_pos_mean    = calculate_pdf(y_pre[:, iq], y0, bins)
+    
+
+    hist_pos_mean_5  = calculate_pdf(y_pre[:, iq], y0, bins, im)
+    
+    return hist_noise, hist_pre, hist_prior, hist_pos_mean, hist_pos_mean_5    
+
+def calculate_pdf(y, y0, bins, im = None):
+
+    error = y - y0
+    if im is not None:
+        hist    = np.histogram(error[im], bins, density = True)
+    else:
[…]

### 2020-09-10 Article/ici_submm_cloudcorr.tex
Started on the Introduction in the article. Cleaning of references.

@@
 
+\newcommand{\todo}[1]{{\color{red} #1}}
+
 \begin{document}
 
-\title{TEXT}
+\title{An approach for cloud correction of operational humidity channels}
 
-% \Author[affil]{given_name}{surname}
+\Author[1]{Inderpreet}{Kaur}
+\Author[1]{Patrick}{Eriksson}
+\Author[1]{Simon}{Pfreundschuh}
 
-\Author[]{}{}
-\Author[]{}{}
-\Author[]{}{}
-
-\affil[]{ADDRESS}
-\affil[]{ADDRESS}
-
-%% The [] brackets identify the author with the corresponding affiliation. 1, 2, 3, etc. should be inserted.
-
-%% If an author is deceased, please mark the respective author name(s) with a dagger, e.g. "\Author[2,$\dag$]{Anton}{Aman}", and add a further "\affil[$\dag$]{deceased, 1 July 2019}".
+\affil[1]{Department of Space, Earth and Environment, Chalmers University of
+  Technology, Gothenburg, Sweden}
 
@@
 
-\correspondence{NAME (EMAIL)}
+\correspondence{Inderpreet Kaur <kauri@chalmers.se>}
 
-\runningtitle{TEXT}
+\runningtitle{A cloud correction approach}
 
-\runningauthor{TEXT}
+\runningauthor{Kaur et al.}
 
@@
 
-\introduction  %% \introduction[modified heading if necessary]
+\introduction
+%
+\todo{Add references and do a literature search on cloud filtering}
+
+Satellite observations of humidity inside the troposphere are mainly performed
+by downward-looking sensors. Among this class of observations, the frequency
+range around 183\,GHz has a special role. Water vapour has a noticeable
+transition at 22\,GHz, but it is relatively weak and only column values can be
+derived \citep[e.g.][]{schluessel1990atmospheric} for the observation geometry
+of concern. The first transition in the microwave region that can be used to
+derive altitude information, i.e.\ can be used for ``sounding'', is the one at
+183.31\,GHz \citep[e.g.][]{kakar1983retrieval}. On the other hand, at
+infrared wavelengths a high number of water vapour transitions are found,
+including some of high strength. As a consequence, infrared sounders can
+provide humidity profiles with high precision and good vertical resolution, but
+with strong limitions imposed by clouds. To be able to also sense humidity
+inside and below clouds weather satellites are since some time equipped with
+channels around 183\,GHz. Today such channels are part several sensors, such as
+MHS (Microwave Humidity Sounder) and ATMS (Advanced Technology Microwave
+Sounder ).
+
+Precipiation and most dense clouds, particularly if found at high altitude, can
+still afffect measured radiances around 183\,GHz. As the impact from the
+hydrometeors is then dominated by scattering, the complexity of the analysis of
+the data increases dramatically and there exists a need to identify such cases.
+This is normally denoted as cloud filtering, to obtain data of ``clear sky''
+character. Such filtering has been applied to derive climate records, and is
+also essentail in studies of the agreement between observations and
+simulations. Examples on cloud filtering methods used for these applicatons are
+\todo{(refs)}. These methods arebased on the 183\,GHz data alone and rules on
+the brightness temperatures of different channels, including the difference
+between channels, are applied to remove cloud affected data.
+
+The main motivation for introducing 183\,GHz channels in operational sensors is
+numerical weather prediction (NWP). Usage of microwave data in NWP by
+``all-sky'' assimilation is growing, but 183\,GHz data are still mainly used in
+a clear sky fashion. The later is particularly true in NWP of regional scope,
+all-sky assimilation of 183\,GHz at many national weather agencies will likely
+not be reached in many years. The cloud filtering in NWP differs between
+centres, but normally \dots
+
+All above filtering ...
 
@@
 
-The absorption model takes into account the effect from nitrogen \citep{pwr:93}, oxygen \citep{pwr:93} and water vapour \citep{ellison2007permittivity}.
-LWC is taken from ERA-Interim and is assumed to be totally absorbing.
-In the
-mapping of CloudSat reflectivities to RWC and IWC a total separation between
-liquid and ice phase is assumed. All scattering hydrometeors at temperatures
-above 0$^\circ$C are assumed to be rain, and all below 0$^\circ$C are assumed
-to be ice hydrometeors.
-For RWC the particle size distribution of \citet{abel2012improved} is applied.
-The PSD of IWC follows the basic formulation applied in DARDAR (\verb http://www.icare.univ-lille1.fr/projects/dardar), using latest parameter values (i.e.\ $\alpha$ and $\beta$) as given by
-\citet{amt-12-2819-2019}. This PSD can be considered as a ``two moment''
-scheme, but is here applied in a one moment manner by setting $N_0^*$ (as a
-function of temperature) following Table~5 of \citet{delanoe2014normalized},
-and letting the radar reflectivity set the remaining moment.
-Single scattering data are taken from \citet{eriksson:agene:18}. For ice
-hydrometeors, three habits are applied: Perpendicular 3-bullet rosette, Large
-plate aggregate and Large column aggregate. In the last two cases, the
-aggregates are complemented with single crystal data to also cover smaller
-sizes. These data describe particles assumed to have a totally random
-orientation. To apply oriented particles is much more computationally costly
-and could not be accommodated inside the study.
-The land emissivity was taken from TELSEM \citep{aires2011tool} and the Ocean/water from TESSEM \citep{prigent2017sea}.
-For each atmopsheric case, both ''clear-sky'' and ``all-sky'' calculations were performed.
-In the former, all impact of all hydrometeors were set to zero, while in the latter, IWC and RWC derived from CloudSat reflectivities and LWC from ERA-Interim were taken into account.
-Both sets of calculations were made by ARTS's interface to the RT4 solver \citep{evans1995microwavec}.
-To avoid a possible bias between clear-sky and all-sky for insignificant hydrometeor contents, the same ``scattering solver'' was used for both calculations.
-The first two elements of the
-Stokes vector were calculated.
+The absorption model takes into account the effect from nitrogen
+\citep{pwr:93}, oxygen \citep{pwr:93} and water vapour
+\citep{ellison2007permittivity}. LWC is taken from ERA-Interim and is assumed
+to be totally absorbing. In the mapping of CloudSat reflectivities to RWC and
+IWC a total separation between liquid and ice phase is assumed. All scattering
+hydrometeors at temperatures above 0$^\circ$C are assumed to be rain, and all
+below 0$^\circ$C are assumed to be ice hydrometeors. For RWC the particle size
+distribution of \citet{abel2012improved} is applied. The PSD of IWC follows the
+basic formulation applied in DARDAR (\verb
+ http://www.icare.univ-lille1.fr/projects/dardar), using latest parameter
+ values (i.e.\ $\alpha$ and $\beta$) as given by \citet{cazenave2019evolution}.
+ This PSD can be considered as a ``two moment'' scheme, but is here applied in
+ a one moment manner by setting $N_0^*$ (as a function of temperature)
+ following Table~5 of \citet{delanoe2014normalized}, and letting the radar
+ reflectivity set the remaining moment. Single scattering data are taken from
+ \citet{eriksson:agene:18}. For ice hydrometeors, three habits are applied:
+ Perpendicular 3-bullet rosette, Large plate aggregate and Large column
+ aggregate. In the last two cases, the aggregates are complemented with single
+ crystal data to also cover smaller sizes. These data describe particles
+ assumed to have a totally random orientation. To apply oriented particles is
+ much more computationally costly and could not be accommodated inside the
+ study. The land emissivity was taken from TELSEM \citep{aires2011tool} and the
+ Ocean/water from TESSEM \citep{prigent2017sea}. For each atmopsheric case,
+ both ''clear-sky'' and ``all-sky'' calculations were performed. In the former,
+ all impact of all hydrometeors were set to zero, while in the latter, IWC and
+ RWC derived from CloudSat reflectivities and LWC from ERA-Interim were taken
+ into account. Both sets of calculations were made by ARTS's interface to the
+ RT4 solver \citep{evans1995microwavec}. To avoid a possible bias between
+ clear-sky and all-sky for insignificant hydrometeor contents, the same
+ ``scattering solver'' was used for both calculations. The first two elements
+ of the Stokes vector were calculated.
 
@@
 
-These results show that both QRNN-simple and QRNN-all are successful in providing well calibrated probabilistic predictions of the posterior distributions except for few cases associated with high cloud impact.
-This is not unexpected, as such cases form a small subset of the training set and their priori distribution could be different from the the entire dataset.
-Since such cases form only a fraction of the training dataset, it can be hard to train the model to predict them accurately.
-A larger training dataset is needed to increase the representation of such cases in QRNN.
+These results show that both QRNN-simple and QRNN-all are successful in
+providing well calibrated probabilistic predictions of the posterior
+distributions except for few cases associated with high cloud impact. This is
+not unexpected, as such cases form a small subset of the training set and their
+priori distribution could be different from the the entire dataset. Since such
+cases form only a fraction of the training dataset, it can be hard to train the
+model to predict them accurately. A larger training dataset is needed to
+increase the representation of such cases in QRNN.
+
 \subsection{Discussion}
@@
 \section{Special case of using only 325\,GHz for cloud correction}
-In this section, we investigate the possibility of using only channels around 325\,GHz for cloud correction at 183\,GHz.
-This special case of utilising only 325\,GHz channel can be relevant for smaller satellite missions like Artic Weather Satellite (AWS) where higher sub-mm channels are not available.
+In this section, we investigate the possibility of using only channels around
+325\,GHz for cloud correction at 183\,GHz. This special case of utilising only
+325\,GHz channel can be relevant for smaller satellite missions like Artic
+Weather Satellite (AWS) where higher sub-mm channels are not available.
 
@@
 \subsubsection{Artic Weather Satellite}
-The Arctic Weather Satellite (AWS) is a small satellite mission approved as ESA Earth Watch 
-Programme Element.
-It is a small platform carrying a single across-track scanning microwave radiometer.
-The main objective of AWS will be to improve representation of Artic and sub-Arctic weather in NWP models and improve the global weather forecasts.
-AWS will will have channels receiving frequencies around 89\,GHz, 165.5\,GHz, 183\,GHz, 229\,GHz and 325\,GHz.
-For a detailed description of the AWS channels see \citep{eriksson-etal_AWS_2020}, while a brief summary of AWS channels relevant to this study are provided in Table~\ref{tab:specifications_AWS}
+The Arctic Weather Satellite (AWS) is a small satellite mission approved as ESA
+Earth Watch Programme Element. It is a small platform carrying a single
+across-track scanning microwave radiometer. The main objective of AWS will be
+to improve representation of Artic and sub-Arctic weather in NWP models and
+improve the global weather forecasts. AWS will will have channels receiving
+frequencies around 89\,GHz, 165.5\,GHz, 183\,GHz, 229\,GHz and 325\,GHz. For a
+detailed description of the AWS channels see \citep{eriksson2020study}, while a
+brief summary of AWS channels relevant to this study are provided in
+Table~\ref{tab:specifications_AWS}.
+
+% Let's try avoid citing the AWS report. If we do, we must put it on
+% research.chalmers.se
+
 \begin{table*}[t]

### 2020-09-10 Article/ici_submm_cloudcorr.tex
added new plots in AWS section

--- 2020-09-09 Article/ici_submm_cloudcorr.tex
@@
 
-%As the QRNN predictions are in form of quantiles, each prediction has an uncertainty estimate associated with it.
-Case specific uncertainty estimates can be quite useful but estimates of uncertainty fitted to a Gaussian model of random errors are potentially easier to implement in NWP models.
-To inspect if the predictions given by QRNN follow a normal distribution, we evaluated the length of confidence intervals from the median.
-Figure~\ref{fig:prediction_uncertainty_aws-34} shows the prediction uncertainty in AWS-34 for different quantiles.
-The red line represents the uncertainty in a hypothetical Gaussian distribution of $270\pm0.62$\,K.
-The high variability in the uncertainty estimates indicates that QRNN can successfully represent uncertainties for multiple types of cases in the individually, rather than having just a single summary measure of uncertainty about the whole scene.
-
-%If the underlying distribution is Gaussian, the prediction uncertainties should be symmetric around the median, and equally spaced for $1\sigma$, $2\sigma$ and so on.
-The predictions around the median for the 94\% confidence interval ($\pm 2 \sigma$).
-The figure also shows that the uncertainties for all 1000 random cases are concentrated along a narrow width, thus suggesting that the case to case variability of the uncertainty is low.
-A similar uncertainty quantification for other 183\,GHz channels also gives similar results.
+In this section, we analyse the uncertainty estimates obtained from QRNN.
+Figure~\ref{fig:prediction_uncertainty_aws-34} displays the prediction uncertainty in AWS-34 for different quantiles.
+The prediction uncertainty has been plotted as the deviation from the median value.
+The different lines represent 1500 randomly chosen cases.
+The red line represents the uncertainty in a hypothetical Gaussian distribution of $270\pm0.62$\,K, which is of the order of standard deviation of predictions for AWS-34 (see Table~\ref{tab:statistics_aws}).
+The high variability in the uncertainty estimates indicates that QRNN can successfully represent uncertainties for each case individually, rather than expressing them as a single measure for all cases.
+In the latter case, the uncertainty estimates would be concentrated along a narrow interval.
+Also, for majority of the cases, the prediction uncertainties are symmetric around the median, specially around  the 68\% ($\pm 1 \sigma$) and 94\% confidence interval ($\pm 2 \sigma$), suggesting that the posterior distribution follows a Gaussian distribution.
 
 In order to analyse the performance of QRNN with task difficulty, the interrelation between the uncertainty estimates and cloud impact was investigated.
+Here we assume that cloud impact is representative of task difficulty.
 Fig~\ref{fig:uncertainty_cloud_impact} displays the plot between mean uncertainty estimates for $2\sigma$ confidence interval and the cloud impact.
 For all five channels, the predictions with small or relatively low cloud signal have a low uncertainty or in other words have high sharpness.
-As fraction of cloud impact increases, the predictions are associated with high uncertainty.
-If we assume that higher cloud impact is representative of increase in task difficulty, the uncertainty of predictions increases with task difficulty.
-
-%On the other hand, in order to examine if task difficulty also decreased the accuracy, we plotted the error distribution binned according to the cloud impact.
+As fraction of cloud impact increases, the predictions become increasingly uncertain.
+However, this does not imply that the prediction accuracy is low.
+The calibration between prediction errors and measure of uncertainty should not be affected by task difficulty.
 
@@
 Since 325\,GHz cannot provide a full coverage for hydrometeor impact in AWS-32, QRNN cannot learn to predict cloud free values for instances which lie outside the area of coverage.
+
+%As the QRNN predictions are in form of quantiles, each prediction has an uncertainty estimate associated with it.
+Case specific uncertainty estimates can be quite useful but estimates of uncertainty fitted to a Gaussian model of random errors are potentially easier to implement in NWP models.
+To inspect if the predictions given by QRNN follow a normal distribution, we evaluated the length of confidence intervals from the median.
 

### 2020-09-10 Article/ici_submm_cloudcorr.tex
Changes in Sect. 4

@@
 \begin{table*}[t]	
+	\caption{Specifications of ICI and MWI channels. For MWI only 183\,GHz channels are shown.}
 	\label{tab:ICI_MWI_channels}
-	\caption{Specifications of ICI and MWI channels. For MWI only 183\,GHz channels are shown.}
 	\begin{tabular}{lrrrr}
@@
 The common 183\,GHz channels among the two instruments shall allow cross-calibration between the two instruments.
-The channel configurations for ICI and MWI (only 183\,GHz) are provided in Table~\ref{tab:ICI_MWI_configuration}.
+The channel configurations for ICI and MWI (only 183\,GHz) are provided in Table~\ref{tab:ICI_MWI_channels}.
 
@@
 The best performing hyperparameter configurations for a particular training set need not be same for other datasets.
-Therefore for each QRNN model used in this article the hyperparameters were tuned distinctly.
+Therefore for each QRNN model used in this article, the hyperparameters were tuned distinctly.
 
@@
 \subsection{Training}
-%
+\label{sec:ici_trainin}
 %t
 \begin{table}[t]
+\caption{Summary of the different QRNN models used in the study.}
 \label{tab:QRNN_models}
-\caption{Summary of the different QRNN models used in the study.}
 \begin{tabular}{lll}
@@
 To test if the uncertainty estimates given by QRNN are representative of prediction errors, we divided the $\pm2\sigma$ confidence interval into three bins and estimated the prediction error distribution for each.
-Figure~\ref{fig:error_distribution_uncertainty_bins_I1V} shows the prediction error distributions binned according to $2\sigma$ confidence interval for I1V, I2V and I3V.
+Fig.~\ref{fig:error_distribution_uncertainty_bins_I1V} shows the prediction error distributions binned according to $2\sigma$ confidence interval for I1V, I2V and I3V.
 These results are from QRNN-simple.
@@
 
-Figure~\ref{fig:calibration_I2V} shows the calibration of prediction intervals on the test dataset for channel I2V.
+Fig.~\ref{fig:calibration_I2V} shows the calibration of prediction intervals on the test dataset for channel I2V.
 Results from both QRNN-simple and QRNN-all are shown.
@@
 
-These results show that both QRNN-simple and QRNN-all are successful in
-providing well calibrated probabilistic predictions of the posterior
-distributions except for few cases associated with high cloud impact. This is
-not unexpected, as such cases form a small subset of the training set and their
-priori distribution could be different from the the entire dataset. Since such
-cases form only a fraction of the training dataset, it can be hard to train the
-model to predict them accurately. A larger training dataset is needed to
-increase the representation of such cases in QRNN.
-
-\subsection{Discussion}
+These results show that both QRNN-simple and QRNN-all are successful in providing well calibrated probabilistic predictions of the posterior distributions except for few cases associated with high cloud impact.
+This is not unexpected, as such cases form a small subset of the training set and their
+priori distribution could be different from the the entire dataset.
+Since such cases form only a fraction of the training dataset, it can be hard to train the model to predict them accurately.
+A larger training dataset would be required to increase the representation of such cases in QRNN.
 
@@
 \subsubsection{Artic Weather Satellite}
-The Arctic Weather Satellite (AWS) is a small satellite mission approved as ESA
-Earth Watch Programme Element. It is a small platform carrying a single
-across-track scanning microwave radiometer. The main objective of AWS will be
-to improve representation of Artic and sub-Arctic weather in NWP models and
-improve the global weather forecasts. AWS will will have channels receiving
-frequencies around 89\,GHz, 165.5\,GHz, 183\,GHz, 229\,GHz and 325\,GHz. For a
-detailed description of the AWS channels see \citep{eriksson2020study}, while a
-brief summary of AWS channels relevant to this study are provided in
-Table~\ref{tab:specifications_AWS}.
-
-% Let's try avoid citing the AWS report. If we do, we must put it on
-% research.chalmers.se
-
-\begin{table*}[t]
-	\label{tab:ICI_MWI_channels}	
+%t
+\begin{table}[t]
 	\caption{Specifications of AWS channels around 183\,GHz and 325\,GHz.}
+	\label{tab:specifications_AWS}	
 	\begin{tabular}{lrr}
@@
 	\belowtable{} % Table Footnotes
-\end{table*}
+\end{table}
+
+The Arctic Weather Satellite (AWS) is a small satellite mission approved as ESA
+Earth Watch Programme Element. It is a small platform carrying a single
+across-track scanning microwave radiometer. The main objective of AWS will be
+to improve representation of Artic and sub-Arctic weather in NWP models and
+improve the global weather forecasts. AWS will will have channels receiving
+frequencies around 89\,GHz, 165.5\,GHz, 183\,GHz, 229\,GHz and 325\,GHz. For a
+detailed description of the AWS channels see \citet{eriksson2020study}, while a
+brief summary of AWS channels relevant to this study are provided in
+Table~\ref{tab:specifications_AWS}.
+
+% Let's try avoid citing the AWS report. If we do, we must put it on
+% research.chalmers.se
 
@@
 The satellite observations for AWS channels were simulated with ARTS.
-An similar ARTS set-up, as described for ICI (Section~\ref{sec:arts_simulations}) was followed, except that 24 monochromatic frequencies were used so that each channel could be represented with sufficient accuracy.
+An similar ARTS set-up, as described for ICI (Sect.~\ref{sec:arts_simulations}) was followed, except that 24 monochromatic frequencies were used so that each channel could be represented with sufficient accuracy.
 All AWS sensor viewing angles (from $0^\circ$ to $45^\circ$) were simulated, but the results described in this section are based on nadir viewing angle.
@@
 In an analogy between the results from ICI channels, we perform a similar error distribution analysis.
-Figure~\ref{fig:qrnn_C34_deviations} shows the error distributions of the measurements and predicted clear-sky TBs for AWS-34.
-The statistics corresponding to curves are illustrated in Table~\ref{tab:statistics_qrnn_aws}.
+Fig.~\ref{fig:qrnn_C34_deviations} shows the error distributions of the measurements and predicted clear-sky TBs for AWS-34.
+The statistics corresponding to curves are provided in Table~\ref{tab:statistics_qrnn_aws}.
 The label ``Filtered'' represents the subset where all cases with correction greater than 5\,K(15\,K) are removed.
@@
 
+Overall the results demonstrate that QRNN is successful in predicting the clear-sky noise-free data for AWS-33, AWS-34, AWS-35 and AWS-36 and partially for AWS-32.
+The prediction error distributions are symmetric with low bias and standard deviation.
+The cases with high error are mostly associated with high cloud impact and constitute only a small fraction of the total dataset.
+Excluding such cases decreases the variability in the predictions and in fact the spread of errors for AWS-34, AWS-35 and AWS-36 is smaller than noise.
+Removal of cases with high cloud impact, increases the representation of cases in cloud-free conditions, and for such cases, QRNN predictions can be seen as a weighted mean between the two ``super-channels''.
+Since the noise in the two channels are stationary and uncorrelated, the predictions benefit from the additional information, but the noise component tends to cancel out.
+For AWS-32, QRNN is only partially successful in reducing the impact of hydrometeors.
+The prediction errors have significantly lower spread than the measurements, but cases with partially corrected cloud impact deteriorates the overall accuracy.
+Since 325\,GHz cannot provide a full coverage for hydrometeor impact in AWS-32, the testing data will inevitably contain cases for which QRNN has not trained for.
+Prediction for such \textit{out-of-distribution} cases would be inaccurate and highly uncertain.
+In such cases, the predictions should be used with caution.
+
 \begin{table}[t]
@@
 The fraction of cases removed by this filter are given in parentheses.}
-	\label{tab:statistics_aws}
+	\label{tab:statistics_qrnn_aws}
 	\begin{tabular}{llrr|rrr}
@@
 	\includegraphics[width = 80mm]{Figures/prediction_uncertainty_aws-34.pdf}	
-	\caption{}
+	\caption{The prediction uncertainty  for channel AWS-34  with respect to quantiles for randomly selected 1500 cases.
+The red line represents the uncertainty if underlying distribution is purely Gaussian with mean 270\,K and standard deviation 0.62\,K.}
 	\label{fig:prediction_uncertainty_aws-34}	
@@
 In this section, we analyse the uncertainty estimates obtained from QRNN.
-Figure~\ref{fig:prediction_uncertainty_aws-34} displays the prediction uncertainty in AWS-34 for different quantiles.
+Fig.~\ref{fig:prediction_uncertainty_aws-34} displays the prediction uncertainty in AWS-34 for different quantiles.
 The prediction uncertainty has been plotted as the deviation from the median value.
@@
 However, this does not imply that the prediction accuracy is low.
-The calibration between prediction errors and measure of uncertainty should not be affected by task difficulty.
-
-\subsubsection{Discussion}
-%
-The results demonstrate that QRNN is successful in predicting the clear-sky
-noise-free data for AWS-33, AWS-34, AWS-35 and AWS-36 and partially for AWS-32.
-The prediction error distributions are symmetric with low bias and standard deviation.
-The cases with high error are mostly associated with high cloud impact and constitute only a small fraction of the total dataset.
-Excluding such cases decreases the variability in the predictions and in fact the spread of errors for AWS-34, AWS-35 and AWS-36 is smaller than noise.
-Removal of cases with high cloud impact, increases the representation of cases in cloud-free conditions, and for such cases, QRNN predictions can be seen as a weighted mean between the two ``super-channels''.
-Since the noise in the two channels are stationary and uncorrelated, the predictions benefit from the additional information, but the noise component tends to cancel out.
-
-For AWS-32, QRNN is only partially successful in reducing the impact of hydrometeors.
-The resulting error distributions have significantly lower spread than the measurements, but are still negatively skewed.
-Since 325\,GHz cannot provide a full coverage for hydrometeor impact in AWS-32, QRNN cannot learn to predict cloud free values for instances which lie outside the area of coverage.
-
-%As the QRNN predictions are in form of quantiles, each prediction has an uncertainty estimate associated with it.
-Case specific uncertainty estimates can be quite useful but estimates of uncertainty fitted to a Gaussian model of random errors are potentially easier to implement in NWP models.
-To inspect if the predictions given by QRNN follow a normal distribution, we evaluated the length of confidence intervals from the median.
 

### 2020-09-10 Article/ici_submm_cloudcorr.tex
Added references to existing text in Introduction.

@@
 by downward-looking sensors. Among this class of observations, the frequency
-range around 183\,GHz has a special role. Water vapour has a noticeable
+range around 183\,GHz has a special position. Water vapour has a noticeable
 transition at 22\,GHz, but it is relatively weak and only column values can be
@@
 derive altitude information, i.e.\ can be used for ``sounding'', is the one at
-183.31\,GHz \citep[e.g.][]{kakar1983retrieval}. On the other hand, at
+183.31\,GHz \citep{kakar1983retrieval,wang1983profiling}. On the other hand, at
 infrared wavelengths a high number of water vapour transitions are found,
@@
 inside and below clouds weather satellites are since some time equipped with
-channels around 183\,GHz. Today such channels are part several sensors, such as
-MHS (Microwave Humidity Sounder) and ATMS (Advanced Technology Microwave
-Sounder ).
+channels around 183\,GHz. Today such channels are part of several sensors, such
+as ATMS (Advanced Technology Microwave Sounder, \citet{weng2012introduction}).
 
 Precipiation and most dense clouds, particularly if found at high altitude, can
-still afffect measured radiances around 183\,GHz. As the impact from the
-hydrometeors is then dominated by scattering, the complexity of the analysis of
-the data increases dramatically and there exists a need to identify such cases.
-This is normally denoted as cloud filtering, to obtain data of ``clear sky''
-character. Such filtering has been applied to derive climate records, and is
-also essentail in studies of the agreement between observations and
-simulations. Examples on cloud filtering methods used for these applicatons are
-\todo{(refs)}. These methods arebased on the 183\,GHz data alone and rules on
-the brightness temperatures of different channels, including the difference
-between channels, are applied to remove cloud affected data.
+still afffect measured radiances around 183\,GHz
+\citep[e.g.][]{bennartz2003sensitivity}. As the impact from the hydrometeors
+then is dominated by scattering, the complexity of the analysis of the data
+increases dramatically and there exists a need to identify the problematic
+cases. This is normally denoted as cloud filtering, to obtain data of ``clear
+sky'' character. Such filtering has been applied to derive climate records
+\citep{lang2020new} and is essentail in studies of the agreement between
+observations and simulations \citep{brogniez2016review} as well as 
+comparing observations of different instruments to validate their calibration
+\citep{john2013assessment,moradi:retri:15,berg2016intercalibration}. A commonly
+used cloud filtering methods for these applicatons is the one of
+\citet{buehler:aclou:07}. This method is based on the 183\,GHz data alone,
+involving rules on the brightness temperatures differences between channels. An
+older version is \citet{burns1997effects}.
 
 The main motivation for introducing 183\,GHz channels in operational sensors is
-numerical weather prediction (NWP). Usage of microwave data in NWP by
-``all-sky'' assimilation is growing, but 183\,GHz data are still mainly used in
-a clear sky fashion. The later is particularly true in NWP of regional scope,
-all-sky assimilation of 183\,GHz at many national weather agencies will likely
-not be reached in many years. The cloud filtering in NWP differs between
-centres, but normally \dots
+numerical weather prediction (NWP). Usage of microwave data by ``all-sky''
+assimilation is growing \citep{geer2017growing}, but 183\,GHz data are still
+mainly used in a clear sky fashion \citep{geer2018all}. The later is
+particularly true in NWP of regional scope, all-sky assimilation of 183\,GHz at
+many national weather agencies will likely not be reached in many years. The
+cloud filtering in NWP differs between centres. One approach is to make use of
+a ``scattering index'' \citep{bennartz2002precipitation}, based on the
+observations alone. Today likely more common is to use ``observation minus
+background'' (O-B), where the forecast model is used to obtain an estimate of
+the expected clear-sky value and the observation is rejected if the deviation
+exceeds some threshold (???). In both cases, the filtering typically involving
+observations around 89 and/or 150\,GHz.
+
+% favrichon2019detecting?
 

### 2020-09-11 Article/ici_submm_cloudcorr.tex
Article: sectioning outline and new text

@@
 
-\title{An approach for cloud correction of operational humidity channels}
+\title{An emerging approach for cloud correction and filtering of operational
+  microwave humidity radiances}
 
@@
 %
-\todo{Add references and do a literature search on cloud filtering}
-
 Satellite observations of humidity inside the troposphere are mainly performed
@@
 a ``scattering index'' \citep{bennartz2002precipitation}, based on the
-observations alone. Today likely more common is to use ``observation minus
+observations alone. Today, likely more common is to use ``observation minus
 background'' (O-B), where the forecast model is used to obtain an estimate of
@@
 
+Despite the broad usage these filtering methods have some drawbacks. For
+183\,GHz, the impact of hydrometeors systematically cause a decrease in the
+observed radiance (maybe with exceptions at extremely dry conditions), see
+e.g.\ \citet{barlakas:three:20} and below. This means that if any cloud
+contaminated is missed by the filtering this will cause a negative bias in mean
+radiance, compared to the true clear-sky mean. This bias will translate to
+a bias in humidity after the retrieval or assimilation. The alternative is to
+apply a very strict filtering, but this will result in that a high fraction of
+actually clear-sky values will be rejected \todo{(Reka or better reference)},
+i.e.\ an important loss of useful data. One for all. Same or lower frequency ...
+
 % favrichon2019detecting?
 
-All above filtering ...
+\newpage
 
+\section*{Outline of sectioning}
+
+2 Data and methods
+
+2.1 Satellite sensors
+
+2.1.1 Ice Cloud Imager (ICI)
+
+2.1.2 Microwave Imager (MWI)
+
+2.1.3 Arctic Weather Satellite (AWS)
+
+2.2 Quantile Regression Neural Network (QRNN)
+
+2.2.1 Theory
+
+2.2.2 Evaluation metrics
+
+2.3 Simulations
+
+2.3.1 Input data
+
+2.3.2 Simulation setup
+
+2.3.3 Produced dataset
+(If diifers between ICI, MWI and AWS, clarify this)
+
+\noindent 3 Results
+
+Short recap of aim of correction. We also use the correction as a filter, using
+a threshold on the correction. We use 5K (?) threshold as example.
+
+3.1 QRNN network configurations and training
+
+3.2 ICI
+
+3.2.1 Example results
+
+Show a few estimated posterior distributions (one figure) and distribution of
+predicted values (Fig 2)
+
+3.2.2 Error of best estimate
+
+3.2.3 Predicted uncertainty
+
+3.3 MWI
+
+3.3.1 MWI alone
+
+Just 183 GHz channels, original noise
+
+3.3.2 MWI and ICI
+
+As in present version
+
+3.4 AWS
+
+\noindent 4 Discussion
+
+\noindent 5 Conclusion
+
+\newpage
 \section{Data and methods}

### 2020-09-11 Article/ici_submm_cloudcorr.tex
A first complete, but raw, version of the Introduction.

@@
 %% 2-column papers and preprints
-\documentclass[amt, manuscript]{copernicus}
+\documentclass[amt]{copernicus}
 
@@
 
-\title{An emerging approach for cloud correction and filtering of operational
-  microwave humidity radiances}
+\title{Cloud correction and filtering of operational microwave humidity
+  radiances with case specific uncertainty estimation}
 
@@
 
-\runningtitle{A cloud correction approach}
+\runningtitle{Cloud correction with case specific uncertainty estimation}
 
@@
 provide humidity profiles with high precision and good vertical resolution, but
-with strong limitions imposed by clouds. To be able to also sense humidity
+with strong limitations imposed by clouds. To be able to also sense humidity
 inside and below clouds weather satellites are since some time equipped with
@@
 
-Precipiation and most dense clouds, particularly if found at high altitude, can
-still afffect measured radiances around 183\,GHz
+Precipitation and most dense clouds, particularly if found at high altitude, can
+still affect measured radiances around 183\,GHz
 \citep[e.g.][]{bennartz2003sensitivity}. As the impact from the hydrometeors
@@
 sky'' character. Such filtering has been applied to derive climate records
-\citep{lang2020new} and is essentail in studies of the agreement between
+\citep{lang2020new} and is essential in studies of the agreement between
 observations and simulations \citep{brogniez2016review} as well as 
@@
 \citep{john2013assessment,moradi:retri:15,berg2016intercalibration}. A commonly
-used cloud filtering methods for these applicatons is the one of
+used cloud filtering methods for these applications is the one of
 \citet{buehler:aclou:07}. This method is based on the 183\,GHz data alone,
@@
 the expected clear-sky value and the observation is rejected if the deviation
-exceeds some threshold (???). In both cases, the filtering typically involving
+exceeds some threshold (???). In both cases, the filtering typically involves
 observations around 89 and/or 150\,GHz.
@@
 Despite the broad usage these filtering methods have some drawbacks. For
-183\,GHz, the impact of hydrometeors systematically cause a decrease in the
+183\,GHz, the impact of hydrometeors systematically causes a decrease in the
 observed radiance (maybe with exceptions at extremely dry conditions), see
 e.g.\ \citet{barlakas:three:20} and below. This means that if any cloud
-contaminated is missed by the filtering this will cause a negative bias in mean
-radiance, compared to the true clear-sky mean. This bias will translate to
+contamination is missed by the filtering this will cause a negative bias in
+mean radiance, compared to the true clear-sky mean. This bias will translate to
 a bias in humidity after the retrieval or assimilation. The alternative is to
@@
 actually clear-sky values will be rejected \todo{(Reka or better reference)},
-i.e.\ an important loss of useful data. One for all. Same or lower frequency ...
+i.e.\ an important loss of useful data.
 
-% favrichon2019detecting?
+The filtering is normally done in a ``one for all'' manner, i.e.\ all 183\,GHz
+channels are either kept or rejected, while, as the channels differ in their
+altitude coverage, there could be cloud impact in some channels and still the
+others can be considered as clear-sky. To allow a channel specific filtering,
+data likely need to be combined in a more complex manner than simple
+differences, but it is unclear what type of regression that would be best. This
+points towards applying machine learning, as used by e.g.\
+\citet{favrichon2019detecting}.
+
+A maybe less obvious problem is the uncertainty to assign to the filtered
+values. To our best knowledge, in best case estimates of mean and worst case
+errors are provided. Some cases with relatively high cloud impact will likely be
+missed, while most cases are clear sky from start. As the remaining cloudy
+cases can cause significant biases, the likely solution is to apply a quite
+conservative (high) error estimate. However, this will unnecessary downgrade
+the value of the truly clear sky cases and the observations are used in a
+non-optimal manner.
+
+We are here approaching cloud filtering task from a new angle. The basic idea
+is to derive an estimate of the corresponding noise-free clear-sky (NFCS) value
+(i.e.\ the radiance that would have been measured in absence of noise and
+hydrometeors). This is done for each channel separately, only using
+measurements (no ``background'' data involved). Not only a best estimate is
+provided, but also a case specific uncertainty.
+
+This information can be used as a pure filter, by rejecting data where the
+correction exceeds some threshold value. This threshold value should be
+relatively low, to not introduce a bias in filtered dataset. However, even
+better is to replace the original value with the predicted NFSC value when
+forming the clear-sky dataset. This approach we denote as cloud correction. It
+is shown below that a basically bias free cloud correction can be obtained.
+This feature removes the need of threshold value, as long as the retrieval or
+assimilation system can incorporate the uncertainty of the corrected value. As
+also will be shown, the uncertainty for originally clear sky data is determined
+by noise, but the uncertainty increases with magnitude of correction.
+Accordingly, the cloud correction approach allows that the full weight of
+clear-sky data can be preserved.
+
+The estimation of NFSC values makes use of a special type of machine learning,
+denoted as Quantile Regression Neural Network (QRNN,
+\citet{pfreundschuh:aneur:18}). Unlike standard usage of machine learning where
+only some kind of best estimate is provided, QRNN works in a Bayesian fashion
+and instead gives a description of the posterior uncertainty. More precisely,
+QRNN outputs an user specified set of percentiles that gives a discrete
+description posterior distribution, that can be process to derive e.g.\ the
+expectation value.
+
+The approach is demonstrated on a combination of 183\,GHz channels (following
+\citet{buehler:aclou:07}), but we mainly explore the cloud correction (of
+183\,GHz data) that will be possible when sub-millimetre data will be at hand
+in some years. This wavelength region will be introduced by the Ice Cloud
+Imager (ICI, \citet{eriksson:towar:20}), but likely also be included in several
+smaller missions (such as AWS presented below). The focus on ICI is motivated
+by several reasons. The true potentail of the QRNN cloud correction approach is
+likely not revealed if tested on existing data and applying ICI data for cloud
+filtering has not earlier been discussed. It is also argued that the cloud
+correction makes it possible to make good use of ICI data already in clear-sky
+assimilation, a fact that should speed up the use of this novel data source.
 

### 2020-09-11 Article/ici_submm_cloudcorr.tex
added QRNN output example

--- 2020-09-11 Article/ici_submm_cloudcorr.tex
@@
 \documentclass[amt, manuscript]{copernicus}
+%\documentclass[amt]{copernicus}
 
@@
 	\end{tabular}
+
 	\belowtable{} % Table Footnotes
 \end{table*}
+
 Ice Cloud Imager (ICI) is a new EPS-SG (EUMETSAT Polar System - Second Generation) sensor that will observe  Earth using submillimeter-wave (sub-mm) frequency range.
@@
 While other channels around 243.0 and 664.0\,GHz are ``window channels'' and receive both vertical and horizontal polarization.
+
+\subsection{MicroWave Imager}
+%
 In addition to ICI, the EPS-SG satellite will also have Microwave Imager (MWI) onboard.
@@
 
-\subsection{ICI simulations}
+\subsection{Artic Weather Satellite}
+%
+\begin{table}[t]
+	\caption{Specifications of AWS channels around 183\,GHz and 325\,GHz.}
+	\label{tab:specifications_AWS}	
+	\begin{tabular}{lrr}
+		\tophline
+		Channel & Frequency 	& Bandwidth  \\
+		& [GHz]			& [MHz]		\\
+		\middlehline
+		AWS-32	&	176.311    & 2000 		\\
+		AWS-33	&	178.811    & 2000 		\\
+		AWS-34	&	180.311    & 1000 		\\
+		AWS-35	&	181.511    & 1000 		 \\
+		AWS-36	&	182.311    & \phantom{0}500 	 \\
+		AWS-41    & 325.15$\pm$6.60    & 2800 \\
+		AWS-42    & 325.15$\pm$4.10    & 1800  \\
+		AWS-43    & 325.15$\pm$2.40    & 1200 \\
+		AWS-44    & 325.15$\pm$1.20    & \phantom{0}800  \\
+		\bottomhline
+	\end{tabular}
+	\belowtable{} % Table Footnotes
+\end{table}
+
+The Arctic Weather Satellite (AWS) is a small satellite mission approved as ESA
+Earth Watch Programme Element. It is a small platform carrying a single
+across-track scanning microwave radiometer. The main objective of AWS will be
+to improve representation of Artic and sub-Arctic weather in NWP models and
+improve the global weather forecasts. AWS will will have channels receiving
+frequencies around 89\,GHz, 165.5\,GHz, 183\,GHz, 229\,GHz and 325\,GHz. For a
+detailed description of the AWS channels see \citet{eriksson2020study}, while a
+brief summary of AWS channels relevant to this study are provided in
+Table~\ref{tab:specifications_AWS}.
+
+\subsection{QRNN}
+%
+The neural network training is a process of learning to predict the outputs {$y_i$} from inputs {$x_i$} through a series of learnable transformations.
+While training, neural networks seek to minimise the model error through a loss function.
+The choice of the loss function depends on the predictive problem.
+When a neural network is trained to minimise the mean of the quantile loss function to predict the quantiles of the distribution, it is called a Quantile Regression Neural Network (QRNN).
+\subsubsection{Theory}
+
+\subsubsection{Evaluation metrics}
+
+Quantile loss function
+
+CRPS
+
+\subsection{Simulations}
 \label{sec:arts_simulations}
 %
-
+\subsubsection{Input data}
+\subsubsection{Simulation setup}
+\subsubsection{Produced dataset}
 **** Some parts copied directly from AWS report *****
@@
 
+The satellite observations for AWS channels were simulated with ARTS.
+An similar ARTS set-up, as described for ICI (Sect.~\ref{sec:arts_simulations}) was followed, except that 24 monochromatic frequencies were used so that each channel could be represented with sufficient accuracy.
+All AWS sensor viewing angles (from $0^\circ$ to $45^\circ$) were simulated, but the results described in this section are based on nadir viewing angle.
+125\,000 cases based on randomly selected CloudSat orbits were simulated.
+
 \subsection{Simulation dataset}
@@
 
-**** show any comparsion to ATMS? or AWS channels ? ****
+\section{Results}
 
-\subsection{QRNN}
-%
-The neural network training is a process of learning to predict the outputs {$y_i$} from inputs {$x_i$} through a series of learnable transformations.
-While training, neural networks seek to minimise the model error through a loss function.
-The choice of the loss function depends on the predictive problem.
-When a neural network is trained to minimise the mean of the quantile loss function to predict the quantiles of the distribution, it is called a Quantile Regression Neural Network (QRNN).
-
-\subsubsection{Model selection}
-%
-\label{model_selection}
-A high performing QRNN model requires tuning of multiple hyper-parameters.
-These parameters determine the structure and the training set-up of the neural network.
-Several of these hyper-parameters are non-learnable, and must be defined before beginning of every training.
-Grid search is one of the most often employed techniques for hyper-paramter tuning.
-In grid search, different combinations of hyperparamters are selected and for each, the model performance is evaluated.
-The model architecture with the best performance is selected.
-The model evaluation metrics employed in this article are described in the next section.
-
-For the structural parameters, the grid search is performed to determine the number of neurons (width) and hidden layers (depth).
-The model is trained for multiple values of layer widths and hidden layers, and the best configuration is selected by evaluating the predictions over the validation set.
-Similarly, the training process is optimized by performing a grid search different training parameters such as : batch size, learning rate, number of epochs, decay.
-The best performing hyperparameter configurations for a particular training set need not be same for other datasets.
-Therefore for each QRNN model used in this article, the hyperparameters were tuned distinctly.
-
-\subsubsection{Evaluation metrics}
-
-Quantile loss function
-
-CRPS
-
-\section{Cloud correction in  183 GHz channels}
-%
-\subsection{Training data}
-%
-Out of the 200\,000 ICI and MWI channel simulations, 150\,000 cases are randomly picked to form the training set.
-The rest are used for testing.
-In the training set, 90\% of the data is randomly selected to form the training set, while the other 10\% form the \textit{testing-during-training} database.
-ARTS simulations are noise free, so to incorporate the satellite measurement uncertainties, gaussian noise is added to the input training data according to the channel NE$\Delta$T.
-The target training data is kept noise free.
-In order to build a robust learning network, random noise is added to the inputs at each training iteration.
-This exposes the model to a different datasets during the entire training process and avoids the memorisation of training samples.
-The input data is also normalized with mean and standard deviation.
-It is assumed for the simulations that the ICI and MWI channels are mapped to a common footprint and resolution.
-In such case, remapping reduces the noise in MWI channels from 1.2\,K at 10\,Km resolution to 0.8\,K at 15\,Km resolution.
-\subsection{Training}
-\label{sec:ici_trainin}
-%t
 \begin{table}[t]
@@
 \end{table}
+
+\subsection{QRNN network configuration and training}
+%
+\label{model_selection}
+A high performing QRNN model requires tuning of multiple hyper-parameters.
+These parameters determine the structure and the training set-up of the neural network.
+Several of these hyper-parameters are non-learnable, and must be defined before beginning of every training.
+Grid search is one of the most often employed techniques for hyper-paramter tuning.
+In grid search, different combinations of hyperparamters are selected and for each, the model performance is evaluated.
+The model architecture with the best performance is selected.
+The model evaluation metrics employed in this article are described in the next section.
+
+For the structural parameters, the grid search is performed to determine the number of neurons (width) and hidden layers (depth).
+The model is trained for multiple values of layer widths and hidden layers, and the best configuration is selected by evaluating the predictions over the validation set.
+Similarly, the training process is optimized by performing a grid search different training parameters such as : batch size, learning rate, number of epochs, decay.
+The best performing hyperparameter configurations for a particular training set need not be same for other datasets.
+Therefore for each QRNN model used in this article, the hyperparameters were tuned distinctly.
+
 To investigate the performance of training inputs, two QRNN models with different set of training inputs are analysed.
@@
 Since we assume that all channels are remapped to a common footprint, channels MWI-14, MWI-17 and MWI-18 are virtually identical to I1V, I2V and I3V, and thus results for them are not shown separately.
+
+For each 183\,GHz channel from AWS, a training scheme similar to QRNN-simple is used. For example, to
+predict clear-sky TBs from AWS-34, the training data includes measurements AWS-34 and channels AWS-41, AWS-42, AWS-43, AWS-44.
+A grid search over the hyper-parameters was performed (results not shown) and the best performance over the validation set was obtained for 4 hidden layers with 128 neurons and batch size of 128 samples.
+Rectified Linear Unit (ReLU) was used as the activation function
 
@@
 
-\begin{figure}[t]
+\begin{figure*}[t]
 	\centering
@@
 	\label{fig:}	
+\end{figure*}
+
+\subsection{ICI}
+\subsubsection{Example results}
+%
+QRNN predictions are estimates of the posterior distribution over different quantiles.
+For this study we chose quantiles, $x_{\tau}$: median, $\pm 1\sigma$, $\pm 2 \sigma$ and  $\pm 3 \sigma$ ($\tau$ = 0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998).
+The quantiles are interpreted as probabilitic predictions and can be used to construct a probability distribution of the predictions.
+This is in sharp contrast to other correction approaches which give out only point estimates.
+Also, the probability distribution can be used to interpret the confidence intervals.
+For a given case, if two quantiles $\tau_1$ and $\tau_2$ are chosen, then there is $\tau_2 - \tau_1$ chance that the true value ($y_o$) shall lie in in range $[y_{\tau_2}, y_{\tau_1}]$.
+For example, in a 94\% confidence interval where, $\tau_1 = -2\sigma$ and $\tau_1 = +2\sigma$, there is 0.3\% probability that $y_\circ > y_{\tau_2}$, and 97\% probability that $y_\circ$ > $y_{\tau_1}$.
+
+As an example, Fig.~\ref{fig:posterior_distribution_I2V} shows the posterior distribution obtained from QRNN for three different cases.
+These results are from QRNN-single for channel I2V.
+The three cases shown in the figure have almost a similar median value but very different spread for other quantile levels.
+The spread of the distributions can also be expressed as the prediction interval.
+If $y_{\tau_2}, y_{\tau_1}$ are the predictions at two quantile levels $\tau_1$ and $\tau_2$ respectively, the interval $[y_{\tau_2}, y_{\tau_1}]$ is called the prediction interval.
+It is gives the range where the prediction could be located and its length is used as a measure of the reliability.
+The blue curve has shortest prediction interval indicating a sharp probabilistic prediction or more reliability.
+While the other two cases have longer intervals implying higher fluctuations, or low reliability.
+Thus, even if two point estimates are highly accurate, or have identical confidence level they could have different uncertainties.
+The uncertainty quantification is discussed in more detail in Sect.~\ref{sec:prediction_uncertainty}.
+
+%f
+\begin{figure}[t]
+	\centering
+	\includegraphics[height=60mm]{Figures/posterior_distribution_I2V.pdf} 
+	\caption{Posterior distribution obtained from QRNN-single (channel I2V) for three different cases. }
+	\label{fig:posterior_distribution_I2V}	
 \end{figure}
 
-\subsection{Results}
+\subsubsection{Error of best estimate}
 %
@@
 \end{table}
-QRNN predictions are estimates of the posterior distribution over different quantiles: $x_{\tau}$, for median, $\pm 1\sigma$, $\pm 2 \sigma$ and  $\pm 3 \sigma$ ($\tau$ = 0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998).
+
 To assess the accuracy of the predictions, the median of the posterior distribution is assumed to be the best estimate for the predicted clear-sky value.
@@
 
-\subsection{Prediction accuracy}
-%
 The distributions of median value of clear-sky predictions from QRNN-single are shown in Fig~\ref{fig:PDF_predictions}.
@@
 
-\subsection{Uncertainty quantification}
-%
+\subsubsection{Uncertainty quantification}
+\label{sec:prediction_uncertainty}
 %f 
@@
 The quantiles can be used to construct a probability distribution of the predictions in contrast to other correction approaches which give out only point estimates.
-The predictions for each quantile can be used to construct the confidence intervals.
-The confidence interval for each point estimate quantifies it's uncertainty.
-For example, if $\tau_1$ and $\tau_2$ are two quantiles then there is $\tau_2-\tau_1$ probability that the true value will lie in between the range.
+The different quantiles provide the measure of possible fluctuations in the prediction, also known as confidence interval.
+The
+predictions for each quantile are used to construct the confidence intervals.
+The confidence interval for each point estimate is a way to quantify its
+uncertainty. For example, the predicted quantiles for $\pm 1 \sigma$ give 68\%
+probability that the true value will lie between the range.
 
@@
 
-\section{Special case of using only 325\,GHz for cloud correction}
+\subsection{MWI}
+\subsubsection{MWI alone}
+\subsubsection{MWI and ICI}
+
+\subsection{AWS}
 In this section, we investigate the possibility of using only channels around
@@
 
-\subsection{Data}
-\subsubsection{Artic Weather Satellite}
-%t
-\begin{table}[t]
-	\caption{Specifications of AWS channels around 183\,GHz and 325\,GHz.}
-	\label{tab:specifications_AWS}	
-	\begin{tabular}{lrr}
-		\tophline
-		Channel & Frequency 	& Bandwidth  \\
-		& [GHz]			& [MHz]		\\
-		\middlehline
-		AWS-32	&	176.311    & 2000 		\\
-		AWS-33	&	178.811    & 2000 		\\
-		AWS-34	&	180.311    & 1000 		\\
-		AWS-35	&	181.511    & 1000 		 \\
-		AWS-36	&	182.311    & \phantom{0}500 	 \\
-		AWS-41    & 325.15$\pm$6.60    & 2800 \\
-		AWS-42    & 325.15$\pm$4.10    & 1800  \\
-		AWS-43    & 325.15$\pm$2.40    & 1200 \\
-		AWS-44    & 325.15$\pm$1.20    & \phantom{0}800  \\
-		\bottomhline
-	\end{tabular}
-	\belowtable{} % Table Footnotes
-\end{table}
-
-The Arctic Weather Satellite (AWS) is a small satellite mission approved as ESA
-Earth Watch Programme Element. It is a small platform carrying a single
-across-track scanning microwave radiometer. The main objective of AWS will be
-to improve representation of Artic and sub-Arctic weather in NWP models and
-improve the global weather forecasts. AWS will will have channels receiving
-frequencies around 89\,GHz, 165.5\,GHz, 183\,GHz, 229\,GHz and 325\,GHz. For a
-detailed description of the AWS channels see \citet{eriksson2020study}, while a
-brief summary of AWS channels relevant to this study are provided in
-Table~\ref{tab:specifications_AWS}.
-
-% Let's try avoid citing the AWS report. If we do, we must put it on
-% research.chalmers.se
-
-\subsubsection{AWS simulations}
-The satellite observations for AWS channels were simulated with ARTS.
-An similar ARTS set-up, as described for ICI (Sect.~\ref{sec:arts_simulations}) was followed, except that 24 monochromatic frequencies were used so that each channel could be represented with sufficient accuracy.
-All AWS sensor viewing angles (from $0^\circ$ to $45^\circ$) were simulated, but the results described in this section are based on nadir viewing angle.
-125\,000 cases based on randomly selected CloudSat orbits were simulated.
-\subsection{Training}
-%
 Out of the 125\,000 AWS simulations, 75\,000 cases are randomly picked to form the training set.
@@
 
-For each 183\,GHz channel from AWS, a training scheme similar to QRNN-simple is used. For example, to
-predict clear-sky TBs from AWS-34, the training data includes measurements AWS-34 and channels AWS-41, AWS-42, AWS-43, AWS-44.
-A grid search over the hyper-parameters was performed (results not shown) and the best performance over the validation set was obtained for 4 hidden layers with 128 neurons and batch size of 128 samples.
-Rectified Linear Unit (ReLU) was used as the activation function
 \subsection{Prediction accuracy}
+
 %f
@@
 \end{table}
-\subsubsection{Uncertainty quantification}
 %f
@@
 
-In this section, we analyse the uncertainty estimates obtained from QRNN.
+We analyse the uncertainty estimates obtained from QRNN.
 Fig.~\ref{fig:prediction_uncertainty_aws-34} displays the prediction uncertainty in AWS-34 for different quantiles.
@@
 
+\section{Discussion}
 \section{Outlook and Conclusions}  %% \conclusions[modified heading if necessary]

### 2020-09-11 ICI/plot_QRNN_output.py

@@ -1,0 +1,80 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Fri Sep  4 21:35:37 2020
+
+@author: inderpreet
+
+this code plots the output of QRNN for few selected cases
+"""
+
+
+import matplotlib.pyplot as plt
+import numpy as np
+import stats as S
+from ici_mwi import iciData
+plt.rcParams.update({'font.size': 26})
+from matplotlib.ticker import (MultipleLocator, FormatStrFormatter,
+                               AutoMinorLocator)
+
+from typhon.retrieval.qrnn import set_backend, QRNN
+set_backend("pytorch")
+
+#%% input parameters
+depth     = 4
+width     = 128
+quantiles = np.array([0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998])
+batchSize = 128
+
+targets = ['I2V']
+test_file = "TB_ICI_test.nc"
+
+iq = np.argwhere(quantiles == 0.5)[0,0]
+
+#%% Plot the output of QRNN, posteriori distribution
+
+fig, ax = plt.subplots(1, 1, figsize = [8, 8])
+
+for i,target in enumerate(targets):
+    inChannels = np.array([target, 'I5V' , 'I6V', 'I7V', 'I8V', 'I9V', 'I10V', 'I11V'])
+    data = iciData(test_file, 
+                   inChannels, target, 
+                   batch_size = batchSize)  
+
+    i183, = np.argwhere(inChannels == target)[0]
+
+# read QRNN    
+    file = 'qrnn_ici_%s_%s_%s_single.nc'%(depth, width, target)
+    print (file)
+    qrnn = QRNN.load(file)
+    y_pre, y_prior, y0, y, y_pos_mean = S.predict(data, qrnn, add_noise = True)
+    im = np.where(np.logical_and(((y_pre[:, 3]).astype(int) == 270), \
+                                 (np.abs(y_pre[:, 5] - y_pre[:, 1])> 10), 
+                  (np.abs(y_pre[:, 5] - y_pre[:, 1])< 20)))[0]  
+    for i in im[0:1]:
+        ax.plot(y_pre[i, :], quantiles,  '-ro',  linewidth = 2.5)
+        
+    im = np.where(np.logical_and(((y_pre[:, 3]).astype(int) == 270),\
+                                 (np.abs(y_pre[:, 5] - y_pre[:, 1])< 10)))[0]  
[…]

### 2020-09-14 Article/ici_submm_cloudcorr.tex

--- 2020-09-11 Article/ici_submm_cloudcorr.tex
@@
 %% 2-column papers and preprints
-\documentclass[amt]{copernicus}
+
+\documentclass[amt, manuscript]{copernicus}
+%\documentclass[amt]{copernicus}
+
+%\documentclass[amt]{copernicus}
 
@@
 
-\subsection{ICI simulations}
+\subsection{Artic Weather Satellite}
+%
+\begin{table*}[t]
+	\caption{Specifications of AWS channels around 183\,GHz and 325\,GHz.}
+	\label{tab:specifications_AWS}	
+	\begin{tabular}{lrr}
+		\tophline
+		Channel & Frequency 	& Bandwidth  \\
+		& [GHz]			& [MHz]		\\
+		\middlehline
+		AWS-32	&	176.311    & 2000 		\\
+		AWS-33	&	178.811    & 2000 		\\
+		AWS-34	&	180.311    & 1000 		\\
+		AWS-35	&	181.511    & 1000 		 \\
+		AWS-36	&	182.311    & \phantom{0}500 	 \\
+		AWS-41    & 325.15$\pm$6.60    & 2800 \\
+		AWS-42    & 325.15$\pm$4.10    & 1800  \\
+		AWS-43    & 325.15$\pm$2.40    & 1200 \\
+		AWS-44    & 325.15$\pm$1.20    & \phantom{0}800  \\
+		\bottomhline
+	\end{tabular}
+	\belowtable{} % Table Footnotes
+\end{table*}
+
+The Arctic Weather Satellite (AWS) is a small satellite mission approved as ESA
+Earth Watch Programme Element. It is a small platform carrying a single
+across-track scanning microwave radiometer. The main objective of AWS will be
+to improve representation of Artic and sub-Arctic weather in NWP models and
+improve the global weather forecasts. AWS will will have channels receiving
+frequencies around 89\,GHz, 165.5\,GHz, 183\,GHz, 229\,GHz and 325\,GHz. For a
+detailed description of the AWS channels see \citet{eriksson2020study}, while a
+brief summary of AWS channels relevant to this study are provided in
+Table~\ref{tab:specifications_AWS}.
+
+\subsection{QRNN}
+%
+The neural network training is a process of learning to predict the outputs {$y_i$} from inputs {$x_i$} through a series of learnable transformations.
+While training, neural networks seek to minimise the model error through a loss function.
+The choice of the loss function depends on the predictive problem.
+When a neural network is trained to minimise the mean of the quantile loss function to predict the quantiles of the distribution, it is called a Quantile Regression Neural Network (QRNN).
+\subsubsection{Theory}
+
+\subsubsection{Evaluation metrics}
+
+Quantile loss function
+
+CRPS
+
+\subsection{Simulations}
 \label{sec:arts_simulations}
 %
-
+\subsubsection{Input data}
+%
+\subsubsection{Simulation setup}
+%
 **** Some parts copied directly from AWS report *****
@@
 
-\subsection{Simulation dataset}
+\subsection{Produced dataset}
 %
-Using the simulation setup described in previous section, Cloudsat profiles during August 2015 were randomly selected to generate 200\,000 cases for each ICI frequency.
+Using the simulation setup described in previous section, Cloudsat profiles during August 2015 were randomly selected to generate 200\,000 cases for each ICI and MWI frequency.
 The input data were restricted between $60^{\degree}$S to $60^{\degree}$N, and surface is below 500\,m.
 Both clear-sky and all-sky scenarios were simulated, and no differentiation was made between the observations over ocean/sea and land.
-It is also assumed that all simulations are remapped to a common foorprint.
+It is also assumed that all simulations of ICI and MWI are remapped to a common foorprint.
 
-**** show any comparsion to ATMS? or AWS channels ? ****
+For AWS, 24 monochromatic frequencies were simulated so that each channel could be represented with sufficient accuracy.
+All AWS sensor viewing angles (from $0^\circ$ to $45^\circ$) were simulated, but the results described in this section are based on nadir viewing angle.
+130\,000 cases based on randomly selected CloudSat orbits were simulated.
 
-\subsection{QRNN}
+\begin{table*}[t]
+	\caption{Summary of the different QRNN models used in the study.}
+	\label{tab:QRNN_models}
+	\begin{tabular}{lllll}
+		\tophline
+		QRNN model & Sensor & Target & Input 183\,GHz channel &Other training inputs \\
+		\middlehline
+		QRNN-single &  ICI 	& I1V/I2V/I3V 	& I1V/I2V/I3V, & I5V, I6V, I7V, I8V, I9V, I10V, I11V\\
+		\cline{2-5}
+					&  MWI 	& MWI-15/MWI-16 & MWI-15/MWI-16	& I5V, I6V, I7V, I8V, I9V, I10V, I11V \\
+		\cline{2-5}
+					& AWS	& AWS-32/AWS-33/ &  AWS-32/AWS-33/ & AWS-41, AWS-42, AWS-43, AWS-44\\
+					&		& AWS-34/		 &	AWS-34/		   & \\
+					&		& AWS-35/AWS-36	 & AWS-35/AWS-36,  &\\
+		\cline{1-5}
+		QRNN-all &  ICI 	& I1V/I2V/I3V 	& I1V, I2V, I3V & I5V, I6V, I7V, I8V, I9V, I10V, I11V\\
+		\cline{1-5}
+		QRNN-mwi &  MWI		& MWI-14/MWI-15/ &  MWI-14, MWI-15, & None 	\\	
+				 &			& MWI-16/		 &  MWI-16, & \\
+				 &			& MWI-17/MWI-18	 &  MWI-17, MWI-18  &\\					
+	\bottomhline
+\end{tabular}
+\belowtable{} % Table Footnotes
+\end{table*}
+
+\subsection{Training data}
 %
-The neural network training is a process of learning to predict the outputs {$y_i$} from inputs {$x_i$} through a series of learnable transformations.
-While training, neural networks seek to minimise the model error through a loss function.
-The choice of the loss function depends on the predictive problem.
-When a neural network is trained to minimise the mean of the quantile loss function to predict the quantiles of the distribution, it is called a Quantile Regression Neural Network (QRNN).
+The QRNN models presented in this study are trained with simulated brightness temperature data to predict the noise-free clear-sky values for 183\,GHz channels.
+No other data was included in the training process, but the training set varied according to the QRNN-model (described further).
+Out of the 220\,000 simulations for ICI and MWI each, 175\,000 cases were randomly picked to form the training set.
+The rest were used for testing.
+For AWS a slightly smaller database was selected.
+Out of 130\,000 simulations, 100\,000 were used for training while the rest formed the testing set.
 
-\subsubsection{Model selection}
+In the training set for all three sensors, 90\% of the data was randomly selected to form the training set, while the other 10\% formed the \textit{testing-during-training} database.
+ARTS simulations are noise free, so to incorporate the satellite measurement uncertainties, gaussian noise was added to the input training data according to the channel NE$\Delta$T.
+The target training data was kept noise free.
+In order to build a robust learning network, random noise was added to the inputs at each training iteration.
+This exposes the model to a different datasets during the entire training process and avoids the memorisation of training samples.
+The input data was also normalized with mean and standard deviation.
+
+\subsection{QRNN model configurations}
 %
-\label{model_selection}
+\label{QRNN_models}
+Multiple QRNN models were trained with several combinations of the training input.
+For each combination, the target was always one of the available 183\,GHz channels, and this target channel was always included in the training set.
+The choice of other channels in the training set depended on the type of QRNN model chosen.
+Three main types of QRNN models were used in this study.
+
+In the first model, the training inputs always contained data from the target 183\,GHz channel, and one or more available sub-mm channels.
+No data from other 183\,GHz channels was included in training.
+We refer this model as ``QRNN-single''.
+For ICI and MWI, the available sub-mm channels are 325\,GHz, 448\,GHz and 664\,GHz, while for AWS only 325\,GHz is available.
+It should be noted that though MWI does not have any sub-mm channels,  sub-mm channels from ICI were used.
+It is assumed for the simulations that data from ICI and MWI channels are mapped to a common footprint and resolution.
+In such case, remapping reduces the noise in MWI channels from 1.2\,K at 10\,Km resolution to 0.8\,K at 15\,Km resolution.
+
+The second model was defined to investigate the  impact of using all 183\,GHz channels concurrently.
+This model is referred as ``QRNN-all''.
+In this model, the training set included data from all available 183\,GHz channels, along with other sub-mm channels.
+This model was applied only to ICI.
+It should be noted that although the training set was identical for I1V, I2V and I3V, a separate training was needed for each channel as target.
+
+The third model was  used only for MWI channels.
+In this case, all 183\,GHz channels were used concurrently in the training set.
+No other data from sub-mm channels was used.
+Further in the text, we shall refer this model as ``QRNN-mwi''.
+
+A summary of the three QRNN models described in this study is provided in Table~\ref{tab:QRNN_models}.
+
+\section{Results}
+\subsection{QRNN network structure}
+%
 A high performing QRNN model requires tuning of multiple hyper-parameters.
@@
 Several of these hyper-parameters are non-learnable, and must be defined before beginning of every training.
-Grid search is one of the most often employed techniques for hyper-paramter tuning.
-In grid search, different combinations of hyperparamters are selected and for each, the model performance is evaluated.
+Grid search is one of the most often employed techniques for hyper-parameter tuning.
+In grid search, different combinations of hyper-parameters are selected and for each, the model performance is evaluated.
 The model architecture with the best performance is selected.
-The model evaluation metrics employed in this article are described in the next section.
+We use quantile loss and CRPS for evaluation of the model performance.
 
-For the structural parameters, the grid search is performed to determine the number of neurons (width) and hidden layers (depth).
-The model is trained for multiple values of layer widths and hidden layers, and the best configuration is selected by evaluating the predictions over the validation set.
-Similarly, the training process is optimized by performing a grid search different training parameters such as : batch size, learning rate, number of epochs, decay.
-The best performing hyperparameter configurations for a particular training set need not be same for other datasets.
-Therefore for each QRNN model used in this article, the hyperparameters were tuned distinctly.
+For the structural parameters, the usually a grid search over the number of neurons (width) and hidden layers (depth) is performed.
+The model is trained for multiple values of layer widths and hidden layers, and the best configuration is selected by evaluating the predictions over validation dataset.
+Similarly, the training process is optimized by performing a grid search different training parameters such as : batch size, learning rate, number of epochs etc.
+In this study, all possible hyper-parameters were not tested.
+We investigated the performance of QRNN only to certain hyper-parameters like number of neurons, hidden layers, learning rate, convergence epochs and batch size.
+The others were chosen empirically.
 
-\subsubsection{Evaluation metrics}
-
-Quantile loss function
-
-CRPS
-
-\section{Cloud correction in  183 GHz channels}
-%
-\subsection{Training data}
-%
-Out of the 200\,000 ICI and MWI channel simulations, 150\,000 cases are randomly picked to form the training set.
-The rest are used for testing.
-In the training set, 90\% of the data is randomly selected to form the training set, while the other 10\% form the \textit{testing-during-training} database.
-ARTS simulations are noise free, so to incorporate the satellite measurement uncertainties, gaussian noise is added to the input training data according to the channel NE$\Delta$T.
-The target training data is kept noise free.
-In order to build a robust learning network, random noise is added to the inputs at each training iteration.
-This exposes the model to a different datasets during the entire training process and avoids the memorisation of training samples.
-The input data is also normalized with mean and standard deviation.
-It is assumed for the simulations that the ICI and MWI channels are mapped to a common footprint and resolution.
-In such case, remapping reduces the noise in MWI channels from 1.2\,K at 10\,Km resolution to 0.8\,K at 15\,Km resolution.
-\subsection{Training}
-\label{sec:ici_trainin}
-%t
-\begin{table}[t]
-\caption{Summary of the different QRNN models used in the study.}
-\label{tab:QRNN_models}
-\begin{tabular}{lll}
-\tophline
-QRNN model & Training inputs & Target \\
-\middlehline
-QRNN-simple & I1V, I5V, I6V, I7V, I8V, I9V, I10V, I11V 			 & I1V\\
-			& I2V, I5V, I6V, I7V, I8V, I9V, I10V, I11V 			 & I2V\\
-			& I3V, I5V, I6V, I7V, I8V, I9V, I10V, I11V 			 & I3V\\
-			& MWI-15, I5V, I6V, I7V, I8V, I9V, I10V, I11V 		 & MWI-15\\	
-			& MWI-16, I5V, I6V, I7V, I8V, I9V, I10V, I11V 		 & MWI-16\\
-QRNN-all    & I1V, I2V, I3V, I5V, I6V, I7V, I8V, I9V, I10V, I11V & I1V\\	
-			& I1V, I2V, I3V, I5V, I6V, I7V, I8V, I9V, I10V, I11V & I2V\\	
-			& I1V, I2V, I3V, I5V, I6V, I7V, I8V, I9V, I10V, I11V & I3V\\
-
-\bottomhline
-\end{tabular}
-\belowtable{} % Table Footnotes
-\end{table}
-To investigate the performance of training inputs, two QRNN models with different set of training inputs are analysed.
-In both models, the training set combines data from 183\,GHz, 325 GHz, 448\,GHz and 664\,GHz to predict cloud corrected observations for the target 183\,GHz channel.
-
-In the first model, the training set includes the target 183\,GHz channel and the sub-mm channels.
-For example, to train for channel I1V, the input channels are I1V, I5V , I6V, I7V, I8V, I9V, I10V, I11V.
-A separate QRNN model is trained for each of the 183\,GHz channels.
-We shall refer this QRNN model as ``QRNN-simple''.
-In the second QRNN model, we suggest to use all three 183\,GHz channels (from ICI) concurrently, along with sub-mm channels.
-In this case, although the input training parameters are identical for all channels, the target channel is different and QRNN has to be trained separately for each.
-Further in text, we refer this model as ``QRNN-all''.
-Table~\ref{tab:QRNN_models} summarises the two QRNN models.
-
-Apart from these two models, we also extend QRNN-simple to predict the clear-sky values for MWI channels.
-In this case, we combine the measurements from MWI-15(MWI-16) and the sub-mm channels to predict MWI-15(MWI-16).
-Since we assume that all channels are remapped to a common footprint, channels MWI-14, MWI-17 and MWI-18 are virtually identical to I1V, I2V and I3V, and thus results for them are not shown separately.
-
-As described in section \ref{model_selection}, a grid search was implemented to select the best performing hyperparamters.
-The mean quantile loss and CRPS for different layer width and hidden layer configurations are shown in Fig\ref{fig:model_selection}.
-The results are for QRNN-simple with I3V as target channel.
-Increasing the complexity of the network by increasing the layer-width and depth has a positive impact on performance.
+Firstly, we performed a grid search to select the size of the neural network.
+We evaluated the performance for three sizes of hiddden layers($n_h$ = 2, 3, 4), and layer widths of sizes in the set [8, 16, 32, 64, 128, 256, 512].
+The mean quantile loss and CRPS for different layer width and hidden layer configurations are shown in Fig\ref{fig:grid_search}.
+The results are for QRNN-single with I2V as target channel.
+Increasing the complexity of the network by increasing the layer width and depth has a positive impact on performance.
 However for four hidden layers, increasing the number of neurons beyond 128 has no significant impact on the performance.
-On basis of these results, a neural network with four hidden layers and 128 neurons in each layer was selected for QRNN-simple.
-For the optimising the training paramters, a customised  learning rate scheduler was implemented.
+On basis of these results, a neural network with four hidden layers and 128 neurons in each layer was selected for QRNN-single.
+For the optimising the training parameters, a customised  learning rate scheduler was implemented.
 The initial learning rate was reset after a certain number of epochs.
@@
 For each training  if the validation loss remained unchanged till 6 training epochs, the learning rate was reduced by a factor of 2.
-We did not optimise the type of activation function and batch size.
-Rectified Linear Unit (ReLU) was used as the activation function  and the batch size was set to 128 samples for all QRNN models.
+In order to select the batch size, we simply compared the performance for batch size = 128 and 256, and the former gave better results.
+Concerning number of maximum epochs, we obtained best results when the network was trained longer.
+Choosing a lower value of epochs (e.g.
+50), did not affect the accuracy of the median value, yet deteriorated the prediction uncertainty.
+We did not optimise the type of activation function and Rectified Linear Unit (ReLu) was used in all layers.
 
-For QRNN-all a grid search (results not shown) over width and depth and learning rates resulted in similar performance, and an identical neural network was selected.
+Though these set of hyper-parameters were selected for QRNN-single applied to I2V, they worked well for other channnels and QRNN-all/QRNN-mwi as well.
+In the end, all the results described in this study use an identical  hyper-parameter configuration.
 
-\begin{figure}[t]
+\begin{figure*}[t]
 	\centering
@@
 	\caption{CRPS(left) and mean quantile loss(right) for different combinations of layer width and hidden layers ($n_h$). The results are from QRNN-simple for channel I2V.}
-	\label{fig:}	
+	\label{fig:grid_search}	
+\end{figure*}
+
+\subsection{ICI}
+\subsubsection{Example results}
+%
+QRNN predictions are estimates of the posterior distribution over different quantiles.
+For this study we chose quantiles, $x_{\tau}$: median, $\pm 1\sigma$, $\pm 2 \sigma$ and  $\pm 3 \sigma$ ($\tau$ = 0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998).
+The quantiles are interpreted as probabilitic predictions and can be used to construct a probability distribution of the predictions.
+This is in sharp contrast to correction approaches which give out only point estimates.
+As an example, Fig.~\ref{fig:posterior_distribution_I2V} shows the posterior distribution obtained from QRNN for three different cases.
+These results are from QRNN-single for channel I2V.
+The three cases shown in the figure have almost a similar median value but very different spread.
+The spread of the distributions can also be expressed as the prediction interval.
+If $y_{\tau_2}, y_{\tau_1}$ are the predictions at two quantile levels $\tau_1$ and $\tau_2$ respectively, the interval $[y_{\tau_2}, y_{\tau_1}]$ is called the prediction interval.
+It is gives the range where the prediction could be located and its length is a measure of the reliability.
+Among the three cases shown in the figure, the blue curve has shortest prediction interval indicating a sharp probabilistic prediction or more reliability.
+While the other two cases have longer intervals implying higher fluctuations, or low reliability.
+
+The quantiles can also be used to  interpret the confidence intervals.
+For a given case, if two quantiles $\tau_1$ and $\tau_2$ are chosen, then there is $\tau_2 - \tau_1$ chance that the true value ($y_o$) shall lie in in range $[y_{\tau_1}, y_{\tau_2}]$.
+For example, in a 94\% confidence interval where, $\tau_1 = -2\sigma$ and $\tau_1 = +2\sigma$, there is 0.3\% probability that $y_\circ > y_{\tau_2}$, and 97\% probability that $y_\circ$ > $y_{\tau_1}$.
+
+%f
+\begin{figure}[t]
+	\centering
+	\includegraphics[height=60mm]{Figures/posterior_distribution_I2V.pdf} 
+	\caption{Posterior distribution obtained from QRNN-single (channel I2V) for three different cases. }
+	\label{fig:posterior_distribution_I2V}	
 \end{figure}
 
-\subsection{Results}
+\subsubsection{Error of best estimate}
 %
 %f
-\begin{figure}[t]
+\begin{figure*}[t]
 	\includegraphics[width=\textwidth]{Figures/PDF_predictions_ICI.pdf} 
@@
 	\label{fig:PDF_predictions}	
-\end{figure}
+\end{figure*}
 %f 
-\begin{figure}[t ]
+\begin{figure*}[t ]
 	\includegraphics[width=\textwidth]{Figures/error_distribution_QRNN-single.pdf} 
@@
 	\label{fig:error_distributions}	
-\end{figure}
+\end{figure*}
 
 %t
-\begin{table}[t]
+\begin{table*}[t]
 	\caption{Bias, mean absolute error(MAE), standard deviation(STD), and measure of skewness(Skewness) for error distributions of predictions of I1V, I2V and I3V.
@@
 		\tophline
-		&&\multicolumn{2}{c|}{Simulations}& \multicolumn{3}{c|}{QRNN-simple} & \multicolumn{3}{c}{QRNN-all}\\
+		&&\multicolumn{2}{c|}{Simulations}& \multicolumn{3}{c|}{QRNN-single} & \multicolumn{3}{c}{QRNN-all}\\
 		\cline{3-10}
 %		\hline
-		&&   Clear-sky &   All-sky &   All &   Filtered(5K) & Filtered(15K) & All &   Filtered(5K) & Filtered(15K) \\
+		&&   Clear-sky &   All-sky &  Filtered & Predicted & Predicted &   Filtered & Predicted & Predicted \\
+		&&&&							(5\,K) &(All)& (5\,K) & (5\,K)&(All)& (5\,K)\\
 		\middlehline
@@
 
-Channel I1V &Bias     &   -0.00 &   -1.90&    -0.03 &      0.00(6.40\%) & 0.01(3.09\%)&-0.01 &0.01 (6.42\%)& 0.02(3.09\%) \\
-			&MAE      &    0.64 &    2.35&     0.69 &      0.60 & 0.63  &  0.65 & 0.62& 0.60\\
-			&STD      &    0.80 &    8.92&     1.05 &      0.78 &  0.84 &  0.97 & 0.84& 0.80\\
-			&Skewness &   -0.01 &   -7.99&    -1.24 &     -0.44 & -0.48 & -0.36 &-0.51&-0.34\\
+Channel I1V& bias     &  0.00 & -1.88 & -0.32(6.1\%) & -0.06 & -0.04 & -0.31(6.1\%) & -0.06 & -0.04 \\
+			&mae      &  0.64 &  2.32 &  0.79 &  0.64 &  0.55 &  0.78 &  0.61 &  0.54 \\
+			&std      &  0.80 &  8.84 &  1.07 &  0.98 &  0.73 &  1.07 &  0.91 &  0.71 \\
+			&skewness & -0.01 & -8.10 & -1.53 & -1.53 & -0.75 & -1.52 & -1.07 & -0.55 \\
 \middlehline
-Channel I2V	&Bias     &   -0.00 &         -1.05 &    0.02 &      0.03(3.70\%)&0.02(1.60\%) &  0.02&   0.03(3.67\%)& 0.02(1.60\%)\\
-			&MAE      &    0.64 &          1.54 &    0.56 &      0.50&  	  0.52 &  0.46&   0.42 &  0.52\\
-			&STD      &    0.80 &          5.98 &    0.86 &      0.64&  	  0.69 &  0.70&   0.53 &  0.69\\
-			&Skewness &    0.02 &        -10.64 &   -2.25 &     -0.22& 		 -0.58 & -1.69& -0.25 &-0.56\\
+Channel I2V & bias     & -0.00 &  -1.04 & -0.24(3.7\%) & -0.01 & -0.00 & -0.24(3.6\%) & -0.05 & -0.03 \\
+			&mae      &  0.64 &   1.52 &  0.74 &  0.52 &  0.46 &  0.75 &  0.44 &  0.39 \\
+			&std      &  0.80 &   5.95 &  0.99 &  0.82 &  0.59 &  0.99 &  0.67 &  0.50 \\
+			&skewness &  0.00 & -10.80 & -1.10 & -2.17 & -0.27 & -1.05 & -2.22 & -0.27 \\
 \middlehline	
-Channel I3V &Bias     &   0.00  &         -0.63 &    0.02 &      0.02(2.18\%)&0.03(0.92\%)&	 0.04 &  0.04(2.18\%) & 0.04(0.92\%) \\
-			&MAE      &   0.64  &          1.14 &    0.54 &      0.50		& 0.52&0.48 &    0.44 & 0.46\\
-			&STD      &   0.80  &          4.26 &    0.80 &      0.64		& 0.68&0.71 &     0.56 & 0.60\\
-			&Skewness &   0.00  &        -13.26 &   -1.40 &     -0.16		&-0.61&-1.41&   -0.11 & -0.77\\	
+Channel I3V & bias     & -0.00 &  -0.63 & -0.18(2.3\%) &  0.01 &  0.02 & -0.19(2.2\%) & -0.03 & -0.03 \\
+			&mae      &  0.64 &   1.15 &  0.71 &  0.51 &  0.47 &  0.72 &  0.46 &  0.42 \\
+			&std      &  0.80 &   4.27 &  0.93 &  0.77 &  0.59 &  0.95 &  0.68 &  0.54 \\
+			&skewness & -0.00 & -13.41 & -0.86 & -1.75 & -0.11 & -0.93 & -1.53 & -0.14 \\
 		\bottomhline
@@
 	\belowtable{} % Table Footnotes
-\end{table}
+\end{table*}
 
+\begin{table*}[t]
+	\caption{A comparison of the error statistics from QRNN-single and QRNN-all, when only cases with cloud correction greater than 10\,K are included.
+The fraction of cases forming the dataset are included in the parenthesis}
+	\label{tab:error_statistics_ici_high_cloud_impact}
+	%	\tabcolsep=0.11cm
+	\begin{tabular}{lrr|rr|rr}
+		\tophline
+		&\multicolumn{2}{c|}{I1V}& \multicolumn{2}{c|}{I2V} & \multicolumn{2}{c}{I3V}\\
+		\cline{2-7}
+		&QRNN-single& QRNN-all & QRNN-single & QRNN-all  & QRNN-single & QRNN-all\\
+		\middlehline
+				    bias     & -0.53(4.02\%) & -0.38(4.07\%)  & -0.42(2.26\%) & -0.46(2.25\%) & -0.25(1.32\%) & -0.40(1.28\%) \\
+					mae      &  2.32 &  1.93  &  2.77 &  2.08 &  3.10 &  2.59 \\
+					std      &  3.13 &  2.63  &  3.65 &  2.85 &  4.03 &  3.47 \\
+		\bottomhline
+	\end{tabular}
+	\belowtable{} % Table Footnotes
+\end{table*}
+
+\begin{figure}[t]
+	\includegraphics[width=70mm]{Figures/different_filtering_thresholds.pdf} 
+	\caption{A comparison of the  average error bias when pure-filtering approach is applied with different thresholds (red curves).
+The corresponding fraction of cases rejected is also shown on the right y-axis(blue curves).
+}
+	\label{fig:filtering_thresholds}	
+\end{figure} 
+To assess the accuracy of QRNN predictions, a point estimate of the posterior distribution is required.
+Usually for Bayesian analysis, the posterior mean or posterior median are selected as point estimates.
+In this study, we assume the posterior median to be the best estimate for the predicted clear-sky value.
+
+The distributions of median value of clear-sky predictions from QRNN-single are shown in Fig.~\ref{fig:PDF_predictions}.
+The distributions of corresponding clear-sky simulations are also plotted as reference.
+The three figures correspond to channels: I1V, I2V and I3V.
+These results show that the clear-sky values predicted by QRNN-single have a very good match for the peak of the distributions, but a slight mismatch is evident towards the tails.
+The degree of mismatch is highest for I1V, which incidently also has the largest spread of brightness temperatures in the clear-sky conditions.
+For all three channels, the colder brightness temperatures are under-estimated by QRNN, while a tendency to over-estimate the warmer brightness temperatures is seen for I1V and I2V.
+
+For a quantitative evaluation of QRNN accuracy, the prediction errors are calculated as the deviation of the best estimate to its corresponding noise-free clear-sky values.
+We calculate the mean bias, mean absolute error and standard deviation of the errors.
+The asymmetry of error distributions around their mean is also calculated through the measure of skewness.
+Fisher-Pearson coefficient of skewness is used to calculate the measure of skewness:
+\begin{equation}
+g_1 = \frac{m_3}{m_2^{3/2}}, 
+\end{equation}
+where $m_2$ and $m_3$ are biased sample's second and third central moments.
+
+Fig~\ref{fig:error_distributions} shows the error distributions of predictions for all three channels from QRNN-single.
+The distribution of noise is also plotted for reference.
+Without any cloud impact, the error distributions should follow a Gaussian distribution, and the skewness should be close to zero.
+However the presence of clouds leads to a brightness temperature reduction, and introduces a high negative bias among the deviations.
+Among the three channels, I1V has the highest cloud impact, while I3V has the least.
+After correction of the cloud impact, the resulting error distributions are  symmetric with a sharper peak albeit with a large spread.
+The large spread is due to cases which end up with partial cloud correction and also due to cases where the predicted values are warmer than the simulations.
+For all three channels, quite similar behaviour is observed, though I1V has the highest number of cases with residual cloud impact.
+We assume that such cases are associated with high cloud impact.
+To validate our assumption, we implemented a pure-filtering approach.
+In the filtered subset, we removed all cases with QRNN cloud correction greater than 5\,K, and did not correct the remaining cases.
+This can be considered as a pure-filtering approach.
+The results from this subset are also displayed in the figure (red curve).
+For all three channels, the right side follows measurement noise, as expected, but the left side has substantial cases with small cloud impact which pass through the filter.
+However, since the spread of filtered dataset is smaller than the corrected one, it confirms our assumption that most of the partially corrected cases have high cloud impact.
+On the other hand, if all the predicted cases with correction less than 5\,K (Predicted (5\,K) in the figure) are considered, the resulting error distributions are quite close to the measurement noise, except for I1V, where few cases with residual cloud impact can still be seen.
+
+The error metrics corresponding to the error distributions described above are provided in Table~\ref{tab:error_statistics_ici}.
+The average bias in channel I1V measurements is -1.88\,K, which reduces to -0.32\,K with pure-filtering.
+However, when the complete dataset is corrected, the bias is only -0.06\,K and the standard deviation is only 0.98\,K in comparison to 8.84\,K in the measurements.
+The prediction accuracy of QRNN is further higher when filtering is made on the corrected data.
+In this case, the residual bias is only -0.04\,K, and the standard deviation is 0.73\,K, which is in fact of the order of measurement noise (0.80\,K).
+This high accuracy is achieved by filtering just 6.1\% of the data.
+This indicates that though a pure-filtering approach can prove as a reliable procedure for removing cases with high cloud impact, it is important to correct cases with relatively low cloud impact.
+
+Similar results are seen for channel I2V, though a better performance of QRNN is observed.
+In I2V, the measurement bias is -1.04\,K which reduces to -0.01\,K after correction.
+The mean absolute error also reduces from 1.52\,K to 0.52\,K.
+Removing cases with correction greater than 5\,K from the corrected dataset removes only 3.7\% of the data but reduces the absolute error to 0.46\,K and the bias to 0\,K.
+The standard deviation of the resulting dataset is only 0.59\,K as compared to 0.80\,K from noise.
+The reduction in the variability is also evident in the Fig~\ref{fig:error_distributions}, where the peak of the predicted distributions is sharper.
+
+In comparison to I1V and I2V, I3V has the lowest fraction of the measurements with significant cloud impact.
+The bias in the measurements is -0.63\,K in comparison to -1.88 in I1V.
+Pure-filtering removes 2.3\% of the total cases as cloudy, reduces the bias to 0.18\,K, and the standard deviation to 0.91\,K but nonetheless cannot provide a complete cloud filtering.
+After correction of all the cases in the test dataset, the bias reduces to 0.01\,K and the mean absolute error to 0.51\,K from 1.15\,K.
+Including correction along with filtering reduces the bias further down to 0.02\,K and standard deviation to 0.59\,K, which is again smaller than that of noise(0.80\,K).
+
+Overall for all three channels, the accuracy of the predicted dataset with correction greater than 5\,K removed, gives the best accuracy and lowest variability.
+Although similar results can also be achieved by selecting a lower filtering threshold, it comes at the cost of rejecting a high fraction of cases.
+Fig~\ref{fig:filtering_thresholds} shows the average bias obtained from different filtering thresholds and the corresponding percentage of data omitted (blue curve) for all three channels.
+Lowering the filtering threshold from 5\,K to 2.5\,K has only a small effect on improving the accuracy, however with further lower threshold values, accuracy of the order of ``predicted(5\,K)'' can be achieved, nonetheless with a high rejection.
+For example, for I1V, when all cases with cloud correction greater 0.5\,K are filtered, the average error bias of the subset is -0.06\,K, the mean absolute error is 0.59\,K and the standard deviation is 0.75\,K.
+Though, these values are comparable to predicted cases with 5\,K filter, they come at the cost of rejecting more than 30\% of the total cases.
+The unusually high rejection rate indicates that using lower filtering thresholds elevates the risk of erroneously removing clear-sky cases.
+
+Next, we describe the results from QRNN-all.
+In this model, all 183\,GHz channels along with other sub-mm channels were included while training.
+This model was designed to identify if other channels of the same frequency can provide auxiliary information in the training process.
+The results from QRNN-all all are also provided in the last columns of Table~\ref{tab:error_statistics_ici}.
+For channel I1V, using additional information from other two 183\,GHz channels has no impact on pure-filtering approach but a slight positive impact on the predictions.
+If predictions over the entire testing set are considered, the average bias in QRNN-all and QRNN-single is same, but the mean absolute errors in QRNN-all are almost 4.5\% less than QRNN-single, suggesting a lower spread in the errors.
+Having said that, in comparison to QRNN-single, the prediction accuracy has no significant improvement when all cases with correction larger than 5\,K are rejected.
+Thus, information from other 183\,GHz channels only assists in slightly improving the correctness of cases associated with high cloud impact in I1V.
+The accuracy of other cases remains unaltered.
+In order to quantify the positive effect on cases with high cloud impact, we computed the error statistics for all cases with correction greater than 15\,K.
+The results are shown in Table~\ref{tab:error_statistics_ici_high_cloud_impact}.
+For I1V, only 4\% of the cases have cloud correction greater than 10\,K, but have the lowest prediction accuracy.
+Using QRNN-all improves the overall error bias from -0.53\,K to -0.38\,K and the standard deviation from 3.13\% to 2.63\%,but still is unsuccessful in removing the cloud impact completely.
+Lower representation of cases with high cloud impact in the training set could be one of the reasons for this shortcoming.
+Due to low fraction of such cases, QRNN cannot learn to predict the clear-sky values accurately.
+
+For channel I2V, the predictions from QRNN-all have a slightly worse average error bias than QRNN-single, yet a significant improvement in the prediction accuracy is evident.
+For the complete testing set, the mean absolute error is 0.44\,K in comparison to 0.52\,K from QRNN-single, showing an improvement of almost 15\%.
+Similarly the standard deviation of the errors is only 0.67\,K, notably smaller than the measurement noise.
+Additionally, when the  corrected dataset is filtered with 5\,K threshold, the accuracy is even better.
+The mean absolute bias reduces to 0.39\,K and standard deviation to 0.50\,K.
+This implies that cases pertaining to clear-sky conditions and relatively low cloud impact benefit the most from the auxiliary information.
+This is in contrast to channel I1V, where accuracy of such cases remained unaffected.
+However, for cases with cloud impact greater than 10\,K a likewise improvement is observed (Table~\ref{tab:error_statistics_ici_high_cloud_impact}).
+Again both QRNN-all and QRNN-single are only partially successful in removing the cloud impact, but QRNN-all had a better performance among the two.
+For I2V, such cases form only 2.25\% of the testing dataset.
+Predictions from QRNN-all have slightly worse values for average error bias, but both mean absolute error and standard deviation improve by over 20\%.
+
+For channel I3V, the performance of QRNN-all is comparable to that for I2V.
+For I3V, the mean absolute bias in QRNN-all is 0.46\,K compared to 0.51\,K from QRNN-single, and the corresponding standard deviations are 0.68\,K and 0.77\,K.
+Removing the cases with cloud impact greater than 5\,K from the predicted dataset, leads to no change in the average bias, but the mean aboslute error and standard deviation reduce by almost  8\% and 20\% respectively.
+Again suggesting that cases with low/no cloud impact have a significant contribution in improving the accuracy of predictions.
+Cases with high cloud impact, though very low in number, also gained positively from the auxiliary information.
+
+\subsubsection{Uncertainty quantification}
+\label{sec:prediction_uncertainty}
+%f 
+\begin{figure}[t]
+	\includegraphics[width = 70mm]{Figures/prediction_uncertainty_I2V.pdf}	
+	\caption{The prediction uncertainty  for I2V  with respect to quantiles for randomly selected 1500 cases.
+The black line represents the uncertainty if underlying distribution is purely Gaussian with mean 270\,K and standard deviation 0.60\,K.}
+	\label{fig:prediction_uncertainty_I2V}	
+\end{figure}
+\begin{figure}[t]
+	\includegraphics[height = 70mm]{Figures/calibration_QRNN_I1V.pdf}	
+	\caption{Calibration of the prediction intervals obtained from QRNN-simple and QRNN-all for channel I1V. }
+	\label{fig:calibration_I1V}	
+\end{figure}
+\begin{figure*}[t]
+	\includegraphics[width=\textwidth]{Figures/PDF_uncertainty_bins_QRNN-single.pdf}	
+	\caption{Distribution of errors binned according to their uncertainty. Results are from QRNN-simple for channels I1V, I2V and I3V.}
+	\label{fig:error_distribution_uncertainty_bins}	
+\end{figure*}
+
+The biggest advantage of using QRNN is estimation of case-specific uncertainties.
+The quantiles can be used to construct a probability distribution of the predictions in contrast to other correction approaches which give out only point estimates.
+If median is chosen as the point estimate, the predictions at other quantiles provide a measure of the possible fluctuations in the point estimate.
+
+In order to understand, how QRNN predicted uncertainties behave, we calculated the deviations of predictions at different quantiles from the median value.
+Fig.~\ref{fig:prediction_uncertainty_I2V} displays the prediction uncertainty in I2V for different quantiles.
+The different lines represent 1500 randomly chosen cases, while the black line represents the uncertainty in a hypothetical Gaussian distribution of $270\pm0.60$\,K, which is of the order of standard deviation of predictions for I2V (see Table~\ref{tab:error_statistics_ici}).
+The uncertainties estimates from different cases shows a very high degree of variability.
+Among the cases associated with low uncertainty, the distribution is quite symmetric along the median value.
+Such cases are concentrated along a narrow interval and lie close to the black curve.
+For such cases, the uncertainties are also equally spaced for $1\sigma$, $2\sigma$ and so on, suggesting that a Gaussian distribution model could be used to express the underlying uncertainty of such cases.
+However, cases with high uncertainty have a larger spread, and are no longer equally spaced.
+For these cases, the prediction uncertainties have a larger spread over positive quantiles than negative quantiles.
+The high variability indicates that QRNN can successfully represent uncertainties for each case individually, rather than expressing them as a single measure for all cases.
+In the latter case, the uncertainty estimates for all cases would be concentrated along a narrow interval.
+
+For further analysis of the uncertainty estimates, we compare the distributions of the predictions from QRNN with the aprior distribution.
+In a model with high performance, the posterior distribution of the predictions should be similar to the a priori distribution of training dataset.
+A straightforward way to compare the two distribution is to plot the frequency of predictions and frequency of true value in different prediction intervals.
+This is also commonly known as calibration plot.
+Fig.~\ref{fig:calibration_I1V} shows the calibration of the prediction intervals on the test dataset for channel I1V.
+Results from both QRNN-single and QRNN-all are shown.
+The calibration of predictions with correction greater than 10\,K is also shown.
+For both QRNN models, the predictions for the complete test dataset are well calibrated and follow the y=x line.
+This shows that the training and test datasets come from the same a priori distribution.
+On the other hand, when cases with  cloud correction greater than 10\,K are considered, for both models, the predictions in all the intervals are poorly calibrated.
+In this case the calibration curve lies below the y=x line, indicating that the predicted intervals are too narrow, or the uncertainty is underestimated.
+In the test and training datasets, the clear-sky cases and cases with low cloud impact dominate the a priori distribution, and cases with high cloud impact fail to get an adequate representation.
+The a priori distribution of such cases is different from the clear-sky cases, thus the corresponding predictions had poor calibrations.
+We also plotted the calibration curves for I2V and I3V (figure not shown).
+For both these channels, predictions over complete dataset were well calibrated for both QRNN-single and QRNN-all, but for subset with threshold 10\,K, the slightly poor calibrations were observed in QRNN-single.
+This is in contrast with I1V, where both models had poor calibrations for cases with high cloud impact.
+
+Lastly, we investigated that if the uncertainty estimates given by QRNN are representative of prediction errors.
+We divided the 94\% confidence interval ($\pm2\sigma$ ) into three bins and estimated the prediction error distribution for each.
+Fig.~\ref{fig:error_distribution_uncertainty_bins} shows the prediction error distributions for I1V, I2V and I3V.
+These results are from QRNN-single.
+Similar results were also obtained for QRNN-all (figure not shown).
+For all three channels, an increase in the prediction errors with uncertainty is observed.
+The cases with high certainty have a narrow and sharp distribution, and the errors are mostly less than $\pm$2.5\,K.
+With increase in the uncertainty, frequency of cases with high accuracy decreases and the distributions spread out symmetrically to higher errors.
+Poor predictions occur more frequently when uncertainty is high, although cases with accurate predictions yet high uncertainty are also present.
+In spite of individual variations in the error distributions of each channel, predictions and their corresponding uncertainties followed the same relationship: This suggests that QRNN can reliably represent the quality of predictions through their uncertainty estimates.
+
+These three different types of analysis show that both QRNN-simple and QRNN-all are successful in providing well calibrated probabilistic predictions of the posterior distributions except for few cases associated with high cloud impact.
+This is not unexpected, as such cases form a small subset of the training set and their priori distribution could be different from the the entire dataset.
+Since such cases form only a fraction of the training dataset, it can be hard to train the model to predict them accurately.
+A larger training dataset would be required to increase the representation of such cases in QRNN.
+
+\subsection{MWI}
+\subsubsection{MWI alone}
+
+\subsubsection{MWI and ICI}
 %t
-\begin{table}[t]
+\begin{table*}[t]
 	\caption{Same as Table~\ref{tab:error_statistics_ici}, but for channels MWI-15 and MWI-16. Results are from QRNN-simple.}
@@
 	\end{tabular}
+
 	\belowtable{} % Table Footnotes
-\end{table}
-QRNN predictions are estimates of the posterior distribution over different quantiles: $x_{\tau}$, for median, $\pm 1\sigma$, $\pm 2 \sigma$ and  $\pm 3 \sigma$ ($\tau$ = 0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998).
-To assess the accuracy of the predictions, the median of the posterior distribution is assumed to be the best estimate for the predicted clear-sky value.
-The prediction errors are calculated as the deviation of the predictions to their corresponding noise-free clear-sky values.
-We calculate the mean bias, mean absolute error and standard deviation of the errors.
-The asymmetry of error distributions around their mean is also calculated through the measure of skewness.
-In the next sections, we describe the performance of the two QRNN models for ICI and MWI channels.
-
-\subsection{Prediction accuracy}
-%
-The distributions of median value of clear-sky predictions from QRNN-single are shown in Fig~\ref{fig:PDF_predictions}.
-The distributions of corresponding clear-sky simulations are also plotted as reference.
-The three figures correspond to channels: I1V, I2V and I3V.
-These results show that the clear-sky values predicted by QRNN-single have a very good match for the peak of the distributions, but a slight mismatch is evident towards the tails, where QRNN seems to predict slightly colder/warmer TBs.
-
-For a quantitative evaluation of how accurate the predictions are, the  deviations of the median values to the clear-sky simulations are computed.
-Fig~\ref{fig:error_distributions} shows the error distributions of predictions for all three channels.
-The distribution of noise is also plotted for reference.
-The error metrics corresponding to these results are provided in Table~\ref{tab:error_statistics_ici}.
-Without any cloud impact, the error distributions should follow a Gaussian distribution, however the presence of clouds leads to a TB reduction, and introduces a high negative bias among the deviations.
-Among the three channels, the highest cloud impact is seen in channel I1V.
-The average bias in channel I1V measurements is -1.89\,K, however the QRNN-single predictions successfully reduces the average deviation to -0.03\,K.
-The predictions and the observations have a good agreement for the main peak of the distribution, albeit the prediction errors have a sharper peak and a larger spread.
-The large spread is representative of the few cases which are either under/over predicted.
-If all the cases with correction greater than 5\,K are excluded, only a fraction of the total cases (6.42\%) are removed but the variability in predictions errors reduces significantly.
-This indicates that few cases with high cloud impact could be difficult to train and predict.
-
-The performance of QRNN-single for I2V and I3V is analogous to I1V, though the accuracy seems to be higher for former.
-When all predictions are included, the average deviation for both I2V and I3V is -0.02\,K, but few cases with large errors increases the spread of the distributions.
-As observed for I1V, excluding cases with cloud correction greater than 5\,K removes the cases associated with low accuracy.
-Interestingly, the resulting spread of errors is also narrower than noise.
-After filtering, the error standard deviation for both I2V and I3V is 0.64\,K compared to 0.80\,K originating from measurement noise.
-
-The results QRNN-all are also shown in Table~\ref{tab:error_statistics_ici}.
-Using additional information from other 183\,GHz channels has a definite positive impact on the QRNN training.
-A marked impact is seen for channel I1V, where the low measure of skewness over the entire test set indicates that the resulting distributions are more symmetric than QRNN-simple.
-When cases with correction greater than 5\,K are excluded, the variability of errors is smaller than noise.
-A similar trend is observed for channels I2V and I3V.
-
+\end{table*}
 Table~\ref{tab:statistics_mwi} shows the metrics from error distributions for MWI-15 and MWI-16 predictions.
@@
 
-\subsection{Uncertainty quantification}
-%
-%f 
-\begin{figure}[t]
-	\includegraphics[width=\textwidth]{Figures/PDF_uncertainty_bins_QRNN-single.pdf}	
-	\caption{Distribution of errors binned according to their uncertainty. Results are from QRNN-simple for channels I1V, I2V and I3V.}
-	\label{fig:error_distribution_uncertainty_bins_I1V}	
-\end{figure}
-\begin{figure}[t]
-	\includegraphics[height = 70mm]{Figures/calibration_QRNN_I2V.pdf}	
-	\caption{Calibration of the prediction intervals obtained from QRNN-simple and QRNN-all for channel I2V. }
-	\label{fig:calibration_I2V}	
-\end{figure}
-The biggest advantage of using QRNN is estimation of case-specific uncertainties.
-The quantiles can be used to construct a probability distribution of the predictions in contrast to other correction approaches which give out only point estimates.
-The predictions for each quantile can be used to construct the confidence intervals.
-The confidence interval for each point estimate quantifies it's uncertainty.
-For example, if $\tau_1$ and $\tau_2$ are two quantiles then there is $\tau_2-\tau_1$ probability that the true value will lie in between the range.
-
-To test if the uncertainty estimates given by QRNN are representative of prediction errors, we divided the $\pm2\sigma$ confidence interval into three bins and estimated the prediction error distribution for each.
-Fig.~\ref{fig:error_distribution_uncertainty_bins_I1V} shows the prediction error distributions binned according to $2\sigma$ confidence interval for I1V, I2V and I3V.
-These results are from QRNN-simple.
-Similar results were also obtained for QRNN-all (figure not shown).
-Among the three channels the uncertainty in predictions for I1V and I2V are higher than I3V and an increase in the spread of errors with increasing uncertainty is evident in all three.
-As the errors increase, the spread is mostly symmetric around x-axis but among predictions associated with large uncertainties, high errors occur frequently.
-In other words, too-low/too-high QRNN predictions tend to be associated with high uncertainty.
-
-Fig.~\ref{fig:calibration_I2V} shows the calibration of prediction intervals on the test dataset for channel I2V.
-Results from both QRNN-simple and QRNN-all are shown.
-The calibration of predictions with correction greater than 5\,K is also shown.
-For the entire test dataset, the calibration curves for QRNN-simple and QRNN-all are quite identical.
-If cases with cloud correction greater than 5\,K are considered, the calibration curve for QRNN-simple lies  below y=x line, implying that the prediction intervals are overly narrow.
-A similar behaviour is observed for channel I3V (figure not shown).
-However, for channel I1V, both QRNN-all and QRNN-simple fail to provide well calibrated predictions for cases associated with high cloud impact.
-
-These results show that both QRNN-simple and QRNN-all are successful in providing well calibrated probabilistic predictions of the posterior distributions except for few cases associated with high cloud impact.
-This is not unexpected, as such cases form a small subset of the training set and their
-priori distribution could be different from the the entire dataset.
-Since such cases form only a fraction of the training dataset, it can be hard to train the model to predict them accurately.
-A larger training dataset would be required to increase the representation of such cases in QRNN.
-
-\section{Special case of using only 325\,GHz for cloud correction}
+In this case, we combine the measurements from MWI-15(MWI-16) and the sub-mm channels to predict MWI-15(MWI-16).
+Since we assume that all channels are remapped to a common footprint, channels MWI-14, MWI-17 and MWI-18 are virtually identical to I1V, I2V and I3V, and thus results for them are not shown separately.
+\subsection{AWS}
 In this section, we investigate the possibility of using only channels around
@@
 
-\begin{table}[t]
+\begin{table*}[t]
 	\caption{Bias, mean absolute error(MAE), standard deviation(STD), and measure of skewness(Skewness) for error distributions of predictions AWS channels.
@@
 	\belowtable{} % Table Footnotes
-\end{table}
-\subsubsection{Uncertainty quantification}
+\end{table*}
 %f
-\begin{figure}[t]
-	\includegraphics[width = 80mm]{Figures/prediction_uncertainty_aws-34.pdf}	
-	\caption{The prediction uncertainty  for channel AWS-34  with respect to quantiles for randomly selected 1500 cases.
-The red line represents the uncertainty if underlying distribution is purely Gaussian with mean 270\,K and standard deviation 0.62\,K.}
-	\label{fig:prediction_uncertainty_aws-34}	
-\end{figure}
 \begin{figure}[t]
@@
 
-In this section, we analyse the uncertainty estimates obtained from QRNN.
-Fig.~\ref{fig:prediction_uncertainty_aws-34} displays the prediction uncertainty in AWS-34 for different quantiles.
-The prediction uncertainty has been plotted as the deviation from the median value.
-The different lines represent 1500 randomly chosen cases.
-The red line represents the uncertainty in a hypothetical Gaussian distribution of $270\pm0.62$\,K, which is of the order of standard deviation of predictions for AWS-34 (see Table~\ref{tab:statistics_aws}).
-The high variability in the uncertainty estimates indicates that QRNN can successfully represent uncertainties for each case individually, rather than expressing them as a single measure for all cases.
-In the latter case, the uncertainty estimates would be concentrated along a narrow interval.
-Also, for majority of the cases, the prediction uncertainties are symmetric around the median, specially around  the 68\% ($\pm 1 \sigma$) and 94\% confidence interval ($\pm 2 \sigma$), suggesting that the posterior distribution follows a Gaussian distribution.
+We analyse the uncertainty estimates obtained from QRNN.  F
 

### 2020-09-15 Article/ici_submm_cloudcorr.tex
added table for QRNN-mwi results, other minor changes

@@
 		Channel & Frequency 	& Bandwidth  	&NE$\Delta$T	&Polarisation\\
-		\middlehline
-		I1V&	183.31$\pm$7.00    & 2.0 			& 0.8 		& V\\
-		I2V&	183.31$\pm$3.40    & 1.5 			& 0.8 		& V\\
-		I3V&	183.31$\pm$2.00    & 1.5 			& 0.8 		& V\\
-		I4V&	243.20$\pm$2.50    & 3.0 			& 0.7 		& V\\
-		I4H&	243.20$\pm$2.50    & 3.0 			& 0.7 		& H\\
-		I5V&	325.15$\pm$9.50    & 3.0 			& 1.2 		& V\\
-		I6V&	325.15$\pm$3.50    & 2.4 			& 1.3 		& V\\
-		I6V&	325.15$\pm$1.50    & 1.6 			& 1.5 		& V\\
-		I8V&	448.00$\pm$7.20    & 3.0 			& 1.4 		& V\\
-		I9V&	448.00$\pm$3.00    & 2.0 			& 1.6 		& V\\
-		I10V&	448.00$\pm$1.40    & 1.2 			& 2.0 		& V\\
-		I11V&	664.00$\pm$4.20    & 5.0 			& 1.6 		& V\\
-		I11H&	664.00$\pm$4.20    & 5.0 			& 1.6 		& H\\		
+				& [GHz]			& [MHz]			& [K]			&\\
+		\middlehline
+		I1V&	183.31$\pm$7.00    & 2000 			& 0.8 		& V\\
+		I2V&	183.31$\pm$3.40    & 1500 			& 0.8 		& V\\
+		I3V&	183.31$\pm$2.00    & 1500			& 0.8 		& V\\
+		I4V&	243.20$\pm$2.50    & 3000			& 0.7 		& V\\
+		I4H&	243.20$\pm$2.50    & 3000			& 0.7 		& H\\
+		I5V&	325.15$\pm$9.50    & 3000			& 1.2 		& V\\
+		I6V&	325.15$\pm$3.50    & 2400			& 1.3 		& V\\
+		I6V&	325.15$\pm$1.50    & 1600			& 1.5 		& V\\
+		I8V&	448.00$\pm$7.20    & 3000			& 1.4 		& V\\
+		I9V&	448.00$\pm$3.00    & 2000			& 1.6 		& V\\
+		I10V&	448.00$\pm$1.40    & 1200			& 2.0 		& V\\
+		I11V&	664.00$\pm$4.20    & \phantom{0}500			& 1.6 		& V\\
+		I11H&	664.00$\pm$4.20    & \phantom{0}500 			& 1.6 		& H\\		
 		\bottomhline
@@
 		Channel & Frequency 	& Bandwidth  	&NE$\Delta$T	&Polarisation\\
-		\middlehline
-		MWI-14&	183.31$\pm$7.00    & 2.0 			& 1.3 		& V\\
-		MWI-15&	183.31$\pm$6.10    & 1.5 			& 1.2 		& V\\
-		MWI-16&	183.31$\pm$4.90    & 1.5 			& 1.2 		& V\\
-		MWI-16&	183.31$\pm$3.40    & 1.5 			& 1.2 		& V\\
-		MWI-16&	183.31$\pm$2.00    & 1.5 			& 1.3 		& V\\	
+				& [GHz]			& [MHz]			& [K]			&\\
+		\middlehline
+		MWI-14&	183.31$\pm$7.00    & 2000 			& 1.3 		& V\\
+		MWI-15&	183.31$\pm$6.10    & 1500			& 1.2 		& V\\
+		MWI-16&	183.31$\pm$4.90    & 1500			& 1.2 		& V\\
+		MWI-17&	183.31$\pm$3.40    & 1500			& 1.2 		& V\\
+		MWI-18&	183.31$\pm$2.00    & 1500			& 1.3 		& V\\	
 		\bottomhline
@@
 The common 183\,GHz channels among the two instruments shall allow cross-calibration between the two instruments.
-The channel configurations for ICI and MWI (only 183\,GHz) are provided in Table~\ref{tab:ICI_MWI_channels}.
+A brief summary of the MWI 183\,GHz channels is provided in Table~\ref{tab:ICI_MWI_channels}.
 
@@
 Earth Watch Programme Element. It is a small platform carrying a single
-across-track scanning microwave radiometer. The main objective of AWS will be
-to improve representation of Artic and sub-Arctic weather in NWP models and
-improve the global weather forecasts. AWS will will have channels receiving
-frequencies around 89\,GHz, 165.5\,GHz, 183\,GHz, 229\,GHz and 325\,GHz. For a
-detailed description of the AWS channels see \citet{eriksson2020study}, while a
-brief summary of AWS channels relevant to this study are provided in
-Table~\ref{tab:specifications_AWS}.
+across-track scanning microwave radiometer.
+It is planned as a small but cost-effective platform, which can supplement the information from other polar orbiting satellites.
+The main objective of AWS will be to improve representation of Artic and sub-Arctic weather in NWP models and improve the global weather forecasts.
+AWS will will have channels receiving frequencies around 89\,GHz, 165.5\,GHz, 183\,GHz, 229\,GHz and 325\,GHz.
+For a detailed description of the AWS channels see \citet{eriksson2020study}, while a brief summary of AWS channels relevant to this study are provided in
+Table~\ref{tab:specifications_AWS}. The first prototype mission is expected to be delivered around 2023.
 
@@
 %
-Using the simulation setup described in previous section, Cloudsat profiles during August 2015 were randomly selected to generate 200\,000 cases for each ICI and MWI frequency.
+Using the simulation setup described in previous section, Cloudsat profiles during August 2015 were randomly selected to generate 220\,000 cases for each ICI and MWI frequency.
 The input data were restricted between $60^{\degree}$S to $60^{\degree}$N, and surface is below 500\,m.
@@
 
-For AWS, 24 monochromatic frequencies were simulated so that each channel could be represented with sufficient accuracy.
+For AWS, 7 monochromatic frequencies were simulated each for 183\,GHz, 325\,GHz-upper amd 325\,GHz-lower, so that the channel brightness temperature for each could be represented with sufficient accuracy.
+The monochromatic frequencies were interpolated to a finer grid to get the channel temperatures.
 All AWS sensor viewing angles (from $0^\circ$ to $45^\circ$) were simulated, but the results described in this section are based on nadir viewing angle.
@@
 		\tophline
-		QRNN model & Sensor & Target & Input 183\,GHz channel &Other training inputs \\
+		QRNN model & Sensor & Target & Input 183\,GHz channel(s) &Other training inputs \\
 		\middlehline
@@
 %
-The QRNN models presented in this study are trained with simulated brightness temperature data to predict the noise-free clear-sky values for 183\,GHz channels.
+The QRNN models presented in this study are trained with simulated brightness temperature data to predict the NFSC values for 183\,GHz channels.
 No other data was included in the training process, but the training set varied according to the QRNN-model (described further).
@@
 For AWS a slightly smaller database was selected.
-Out of 130\,000 simulations, 100\,000 were used for training while the rest formed the testing set.
+We had 130\,000 available simulations and all were used for training.
+A testing dataset was constructed by randomly drawing 25\,000 cases from the training dataset and noise was added to each simulation to mimic a new measurement set.
 
@@
 \section{Results}
+%
+In this section, QRNN is used to predict the NFCS values for operational humidity channels.
+The main aim of this study is to demonstrate that sub-mm channels can be used to formulate the cloud filtering/correction of data measured around 183\,GHz.
+Different combinations of 183\,GHz channel and sub-mm channels are applied to QRNN and the results are compared.
+To determine the prediction performance of QRNN, the NFCS simulations are used as reference.
+Results from both pure-filtering and correction are described.
+Furthermore, the case specific uncertainties obtained from QRNN are also discussed.
+
 \subsection{QRNN network structure}
@@
 
-For the structural parameters, the usually a grid search over the number of neurons (width) and hidden layers (depth) is performed.
+For the structural parameters, usually a grid search over the number of neurons (width) and hidden layers (depth) is performed.
 The model is trained for multiple values of layer widths and hidden layers, and the best configuration is selected by evaluating the predictions over validation dataset.
@@
 For this study we chose quantiles, $x_{\tau}$: median, $\pm 1\sigma$, $\pm 2 \sigma$ and  $\pm 3 \sigma$ ($\tau$ = 0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998).
-The quantiles are interpreted as probabilitic predictions and can be used to construct a probability distribution of the predictions.
+The quantiles are interpreted as probabilistic predictions and can be used to construct a probability distribution of the predictions.
 This is in sharp contrast to correction approaches which give out only point estimates.
@@
 	\caption{Error distributions for deviations of QRNN-simple predictions to clear-sky simulations for channels I1V, I2V and I3V.
-Label ``uncorrected'' represents the measurements, ``predicted'' denotes the entire dataset, while ``predicted(5\,K)'' refers to the dataset where cases with cloud correction greater than 5\,K are excluded.}
+Label ``Uncorrected'' represents the measurements and ``Filtered(5\,K)'' represents the dataset when no correction is made but cases with cloud correction greater than 5\,K are omitted.
+`Predicted'' denotes the entire prediction dataset, while ``Predicted(5\,K)'' refers to the predicted dataset where cases with cloud correction greater than 5\,K are excluded.}
 	\label{fig:error_distributions}	
@@
 Results from both QRNN-simple and QRNN-all are shown.
-The label ``All'' refers to the complete dataset, while in ``Filtered'', cases with cases with cloud correction greater than 5\,K(15\,K) are excluded from statistics.
+The label ``Filtered'' refers to the dataset where cases with cloud correction greater than 5\,K are filtered out, and  no other correction is made.
+The label ``Predicted(All)'' refers to the complete predicted dataset, while in ``Predicted (5\,K)'', cases with cloud correction greater than 5\,K are removed from the predicted dataset.
 The fraction of cases removed by this filter are given in parentheses.}
@@
 
-Channel I1V& bias     &  0.00 & -1.88 & -0.32(6.1\%) & -0.06 & -0.04 & -0.31(6.1\%) & -0.06 & -0.04 \\
-			&mae      &  0.64 &  2.32 &  0.79 &  0.64 &  0.55 &  0.78 &  0.61 &  0.54 \\
-			&std      &  0.80 &  8.84 &  1.07 &  0.98 &  0.73 &  1.07 &  0.91 &  0.71 \\
-			&skewness & -0.01 & -8.10 & -1.53 & -1.53 & -0.75 & -1.52 & -1.07 & -0.55 \\
-\middlehline
-Channel I2V & bias     & -0.00 &  -1.04 & -0.24(3.7\%) & -0.01 & -0.00 & -0.24(3.6\%) & -0.05 & -0.03 \\
-			&mae      &  0.64 &   1.52 &  0.74 &  0.52 &  0.46 &  0.75 &  0.44 &  0.39 \\
-			&std      &  0.80 &   5.95 &  0.99 &  0.82 &  0.59 &  0.99 &  0.67 &  0.50 \\
-			&skewness &  0.00 & -10.80 & -1.10 & -2.17 & -0.27 & -1.05 & -2.22 & -0.27 \\
-\middlehline	
-Channel I3V & bias     & -0.00 &  -0.63 & -0.18(2.3\%) &  0.01 &  0.02 & -0.19(2.2\%) & -0.03 & -0.03 \\
-			&mae      &  0.64 &   1.15 &  0.71 &  0.51 &  0.47 &  0.72 &  0.46 &  0.42 \\
-			&std      &  0.80 &   4.27 &  0.93 &  0.77 &  0.59 &  0.95 &  0.68 &  0.54 \\
+Channel I1V& Bias     &  0.00 & -1.88 & -0.32(6.1\%) & -0.06 & -0.04 & -0.31(6.1\%) & -0.06 & -0.04 \\
+			&MAE      &  0.64 &  2.32 &  0.79 &  0.64 &  0.55 &  0.78 &  0.61 &  0.54 \\
+			&STD      &  0.80 &  8.84 &  1.07 &  0.98 &  0.73 &  1.07 &  0.91 &  0.71 \\
+			&Skewness & -0.01 & -8.10 & -1.53 & -1.53 & -0.75 & -1.52 & -1.07 & -0.55 \\
+\middlehline
+Channel I2V &Bias     & -0.00 &  -1.04 & -0.24(3.7\%) & -0.01 & -0.00 & -0.24(3.6\%) & -0.05 & -0.03 \\
+			&MAE      &  0.64 &   1.52 &  0.74 &  0.52 &  0.46 &  0.75 &  0.44 &  0.39 \\
+			&STD      &  0.80 &   5.95 &  0.99 &  0.82 &  0.59 &  0.99 &  0.67 &  0.50 \\
+			&Skewness &  0.00 & -10.80 & -1.10 & -2.17 & -0.27 & -1.05 & -2.22 & -0.27 \\
+\middlehline	
+Channel I3V &Bias     & -0.00 &  -0.63 & -0.18(2.3\%) &  0.01 &  0.02 & -0.19(2.2\%) & -0.03 & -0.03 \\
+			&MAE      &  0.64 &   1.15 &  0.71 &  0.51 &  0.47 &  0.72 &  0.46 &  0.42 \\
+			&STD      &  0.80 &   4.27 &  0.93 &  0.77 &  0.59 &  0.95 &  0.68 &  0.54 \\
 			&skewness & -0.00 & -13.41 & -0.86 & -1.75 & -0.11 & -0.93 & -1.53 & -0.14 \\
@@
 	\caption{A comparison of the error statistics from QRNN-single and QRNN-all, when only cases with cloud correction greater than 10\,K are included.
-The fraction of cases forming the dataset are included in the parenthesis}
+The fraction of cases forming the dataset are included in the parentheses}
 	\label{tab:error_statistics_ici_high_cloud_impact}
@@
 		\middlehline
-				    bias     & -0.53(4.02\%) & -0.38(4.07\%)  & -0.42(2.26\%) & -0.46(2.25\%) & -0.25(1.32\%) & -0.40(1.28\%) \\
-					mae      &  2.32 &  1.93  &  2.77 &  2.08 &  3.10 &  2.59 \\
-					std      &  3.13 &  2.63  &  3.65 &  2.85 &  4.03 &  3.47 \\
+				    Bias     & -0.53(4.02\%) & -0.38(4.07\%)  & -0.42(2.26\%) & -0.46(2.25\%) & -0.25(1.32\%) & -0.40(1.28\%) \\
+					MAE      &  2.32 &  1.93  &  2.77 &  2.08 &  3.10 &  2.59 \\
+					STD      &  3.13 &  2.63  &  3.65 &  2.85 &  4.03 &  3.47 \\
 		\bottomhline
@@
 	\includegraphics[width=70mm]{Figures/different_filtering_thresholds.pdf} 
-	\caption{A comparison of the  average error bias when pure-filtering approach is applied with different thresholds (red curves).
-The corresponding fraction of cases rejected is also shown on the right y-axis(blue curves).
-}
+	\caption{A comparison of the  average error bias when pure-filtering approach (QRNN-single) is applied with different thresholds (red curves).
+The corresponding fraction of cases rejected is also shown on the right y-axis(blue curves).}
 	\label{fig:filtering_thresholds}	
@@
 The distributions of median value of clear-sky predictions from QRNN-single are shown in Fig.~\ref{fig:PDF_predictions}.
-The distributions of corresponding clear-sky simulations are also plotted as reference.
+The distributions of corresponding NFCS simulations are also plotted as reference.
 The three figures correspond to channels: I1V, I2V and I3V.
@@
 
-For a quantitative evaluation of QRNN accuracy, the prediction errors are calculated as the deviation of the best estimate to its corresponding noise-free clear-sky values.
-We calculate the mean bias, mean absolute error and standard deviation of the errors.
+For a quantitative evaluation of QRNN accuracy, the prediction errors are calculated as the deviation of the best estimate to its corresponding NFCS values.
+We calculate the mean bias, MAE (mean absolute error) and standard deviation of the errors.
 The asymmetry of error distributions around their mean is also calculated through the measure of skewness.
@@
 The large spread is due to cases which end up with partial cloud correction and also due to cases where the predicted values are warmer than the simulations.
-For all three channels, quite similar behaviour is observed, though I1V has the highest number of cases with residual cloud impact.
+For all three channels quite similar behaviour is observed, though I1V has the highest number of cases with residual cloud impact.
 We assume that such cases are associated with high cloud impact.
@@
 In I2V, the measurement bias is -1.04\,K which reduces to -0.01\,K after correction.
-The mean absolute error also reduces from 1.52\,K to 0.52\,K.
+The MAE also reduces from 1.52\,K to 0.52\,K.
 Removing cases with correction greater than 5\,K from the corrected dataset removes only 3.7\% of the data but reduces the absolute error to 0.46\,K and the bias to 0\,K.
@@
 In comparison to I1V and I2V, I3V has the lowest fraction of the measurements with significant cloud impact.
-The bias in the measurements is -0.63\,K in comparison to -1.88 in I1V.
-Pure-filtering removes 2.3\% of the total cases as cloudy, reduces the bias to 0.18\,K, and the standard deviation to 0.91\,K but nonetheless cannot provide a complete cloud filtering.
-After correction of all the cases in the test dataset, the bias reduces to 0.01\,K and the mean absolute error to 0.51\,K from 1.15\,K.
+The bias in the measurements is only -0.63\,K in comparison to -1.88 in I1V.
+Pure-filtering removes 2.3\% of the total cases as cloudy, reduces the bias to 0.18\,K, and the standard deviation to 0.91\,K but nonetheless, cannot provide a complete cloud filtering.
+After correction of all the cases in the test dataset, the bias reduces to 0.01\,K and the MAE to 0.51\,K from 1.15\,K.
 Including correction along with filtering reduces the bias further down to 0.02\,K and standard deviation to 0.59\,K, which is again smaller than that of noise(0.80\,K).
@@
 Overall for all three channels, the accuracy of the predicted dataset with correction greater than 5\,K removed, gives the best accuracy and lowest variability.
-Although similar results can also be achieved by selecting a lower filtering threshold, it comes at the cost of rejecting a high fraction of cases.
-Fig~\ref{fig:filtering_thresholds} shows the average bias obtained from different filtering thresholds and the corresponding percentage of data omitted (blue curve) for all three channels.
+Although similar results can also be achieved by selecting a lower filtering threshold, it comes at the cost of rejecting higher fraction of cases.
+Fig~\ref{fig:filtering_thresholds} shows the average errors obtained from different filtering thresholds and the corresponding percentage of data omitted (blue curve) for all three channels.
 Lowering the filtering threshold from 5\,K to 2.5\,K has only a small effect on improving the accuracy, however with further lower threshold values, accuracy of the order of ``predicted(5\,K)'' can be achieved, nonetheless with a high rejection.
-For example, for I1V, when all cases with cloud correction greater 0.5\,K are filtered, the average error bias of the subset is -0.06\,K, the mean absolute error is 0.59\,K and the standard deviation is 0.75\,K.
+For example, for I1V, when all cases with cloud correction greater 0.5\,K are filtered, the average error bias of the subset is -0.06\,K, the MAE is 0.59\,K and the standard deviation is 0.75\,K.
 Though, these values are comparable to predicted cases with 5\,K filter, they come at the cost of rejecting more than 30\% of the total cases.
@@
 For channel I1V, using additional information from other two 183\,GHz channels has no impact on pure-filtering approach but a slight positive impact on the predictions.
-If predictions over the entire testing set are considered, the average bias in QRNN-all and QRNN-single is same, but the mean absolute errors in QRNN-all are almost 4.5\% less than QRNN-single, suggesting a lower spread in the errors.
+If predictions over the entire testing set are considered, the average bias in QRNN-all and QRNN-single is same, but the mean absolute errors in QRNN-all are almost 4.5\% less than QRNN-single, suggesting a lower spread of errors.
 Having said that, in comparison to QRNN-single, the prediction accuracy has no significant improvement when all cases with correction larger than 5\,K are rejected.
@@
 The results are shown in Table~\ref{tab:error_statistics_ici_high_cloud_impact}.
-For I1V, only 4\% of the cases have cloud correction greater than 10\,K, but have the lowest prediction accuracy.
+For I1V, only 4\% of the cases have cloud correction greater than 10\,K, but have lowest prediction accuracy.
 Using QRNN-all improves the overall error bias from -0.53\,K to -0.38\,K and the standard deviation from 3.13\% to 2.63\%,but still is unsuccessful in removing the cloud impact completely.
@@
 For channel I2V, the predictions from QRNN-all have a slightly worse average error bias than QRNN-single, yet a significant improvement in the prediction accuracy is evident.
-For the complete testing set, the mean absolute error is 0.44\,K in comparison to 0.52\,K from QRNN-single, showing an improvement of almost 15\%.
+For the complete testing set, the MAE is 0.44\,K in comparison to 0.52\,K from QRNN-single, showing an improvement of almost 15\%.
 Similarly the standard deviation of the errors is only 0.67\,K, notably smaller than the measurement noise.
@@
 For I2V, such cases form only 2.25\% of the testing dataset.
-Predictions from QRNN-all have slightly worse values for average error bias, but both mean absolute error and standard deviation improve by over 20\%.
+Predictions from QRNN-all have slightly worse values for average error bias, but both MAE and standard deviation improve by over 20\%.
 
@@
 For I3V, the mean absolute bias in QRNN-all is 0.46\,K compared to 0.51\,K from QRNN-single, and the corresponding standard deviations are 0.68\,K and 0.77\,K.
-Removing the cases with cloud impact greater than 5\,K from the predicted dataset, leads to no change in the average bias, but the mean aboslute error and standard deviation reduce by almost  8\% and 20\% respectively.
+Removing the cases with cloud impact greater than 5\,K from the predicted dataset, leads to no change in the average bias, but the mean absolute error and standard deviation reduce by almost  8\% and 20\% respectively.
 Again suggesting that cases with low/no cloud impact have a significant contribution in improving the accuracy of predictions.
@@
 	\caption{The prediction uncertainty  for I2V  with respect to quantiles for randomly selected 1500 cases.
-The black line represents the uncertainty if underlying distribution is purely Gaussian with mean 270\,K and standard deviation 0.60\,K.}
+The black line represents the uncertainty if underlying distribution is purely Gaussian with mean 270\,K and standard deviation 0.60\,K.
+The results are from QRNN-single.}
 	\label{fig:prediction_uncertainty_I2V}	
@@
 	\includegraphics[width=\textwidth]{Figures/PDF_uncertainty_bins_QRNN-single.pdf}	
-	\caption{Distribution of errors binned according to their uncertainty. Results are from QRNN-simple for channels I1V, I2V and I3V.}
+	\caption{Distribution of errors binned according to their uncertainty. Results are from QRNN-single for channels I1V, I2V and I3V.}
 	\label{fig:error_distribution_uncertainty_bins}	
@@
 
-In order to understand, how QRNN predicted uncertainties behave, we calculated the deviations of predictions at different quantiles from the median value.
+In order to understand how QRNN predicted uncertainties behave, we calculated the deviations of predictions at different quantiles from the median value.
 Fig.~\ref{fig:prediction_uncertainty_I2V} displays the prediction uncertainty in I2V for different quantiles.
-The different lines represent 1500 randomly chosen cases, while the black line represents the uncertainty in a hypothetical Gaussian distribution of $270\pm0.60$\,K, which is of the order of standard deviation of predictions for I2V (see Table~\ref{tab:error_statistics_ici}).
-The uncertainties estimates from different cases shows a very high degree of variability.
+The different lines represent 1500 randomly chosen cases, while the black line represents the uncertainty in a hypothetical Gaussian distribution of $270\pm0.60$\,K, which is of the order of standard deviation for I2V predictions (see Table~\ref{tab:error_statistics_ici}).
+The uncertainty estimates from different cases show a very high degree of variability.
 Among the cases associated with low uncertainty, the distribution is quite symmetric along the median value.
@@
 
-For further analysis of the uncertainty estimates, we compare the distributions of the predictions from QRNN with the aprior distribution.
+For further analysis of the uncertainty estimates, we compare the distributions of the predictions from QRNN with the a priori distribution.
 In a model with high performance, the posterior distribution of the predictions should be similar to the a priori distribution of training dataset.
@@
 
-These three different types of analysis show that both QRNN-simple and QRNN-all are successful in providing well calibrated probabilistic predictions of the posterior distributions except for few cases associated with high cloud impact.
-This is not unexpected, as such cases form a small subset of the training set and their priori distribution could be different from the the entire dataset.
+These three different types of analysis show that both QRNN-single and QRNN-all are successful in providing well calibrated probabilistic predictions of the posterior distributions except for few cases associated with high cloud impact.
+This is not unexpected, as such cases form a small subset of the training set and their priori distribution could be different from the entire dataset.
 Since such cases form only a fraction of the training dataset, it can be hard to train the model to predict them accurately.
@@
 \subsection{MWI}
+%
+In this section, we present results from QRNN when applied to MWI channels.
+Applicability and sensitivity of QRNN over different combinations of training datasets, is investigated.
+Firstly, we use combinations of data from all five 183\,GHz channels for ``self'' cloud filtering/correction (QRNN-mwi).
+No additional data is used.
+In the second model, we compare the performance of QRNN for MWI channels, if sub-mm channels from ICI are used.
+In this case, we assume that data from both channels is mapped to a common foorprint size.
 \subsubsection{MWI alone}
-
+%
+%t
+\begin{table*}[t]
+	\caption{Error statistics for predictions from QRNN-mwi.
+All channels of MWI are used to train for each 183\,GHz channel.
+The labels Filtered(5\,K), Predicted(All) and Predicted(5\,K) are same as described in Table~\ref{tab:error_statistics_ici}}
+	\label{tab:statistics_mwi-alone}
+	\begin{tabular}{llrr|rrr}
+		\tophline
+		&&\multicolumn{2}{c|}{Simulations}& \multicolumn{3}{c}{QRNN-single} \\
+		\cline{3-7}
+		%		\hline
+		&&   Clear-sky &   All-sky &  Filtered(5\,K) & Predicted & Predicted(5\,K) \\
+		\middlehline
+		MWI-14 		&bias     & 0.00 & -1.87 & -0.45 & -0.18 & -0.15 \\
+					&mae      & 0.64 &  2.31 &  0.91 &  0.96 &  0.80 \\
+					&std      & 0.81 &  8.97 &  1.54 &  1.73 &  1.29 \\
+					&skewness & 0.03 & -8.32 & -4.02 & -1.09 & -3.06 \\
+		\middlehline
+		MWI-15 		&Bias     & -0.01 & -1.23 & -0.36 & -0.16 & -0.13 \\
+					&MAE      &  0.64 &  1.70 &  0.85 &  0.62 &  0.53 \\
+					&STD      &  0.80 &  6.48 &  1.33 &  1.23 &  0.97 \\
+					&skewness &  0.01 & -9.96 & -3.32 & -3.06 & -4.17 \\
+		\middlehline	
+		MWI-16 		&Bias     & -0.00 &  -0.84 & -0.26 & -0.15 & -0.12 \\
+					&MAE      &  0.64 &   1.35 &  0.78 &  0.53 &  0.47 \\
+					&STD      &  0.80 &   5.31 &  1.15 &  1.03 &  0.80 \\
+					&skewness & -0.01 & -12.08 & -3.05 & -5.09 & -4.94 \\	
+		\middlehline			
+		MWI-17 		&Bias     & -0.00 &  -1.06 & -0.31 & -0.16 & -0.12 \\
+					&mae      &  0.64 &   1.54 &  0.80 &  0.62 &  0.54 \\
+					&std      &  0.80 &   6.22 &  1.22 &  1.12 &  0.90 \\
+					&skewness &  0.01 & -11.06 & -3.31 & -4.35 & -4.33 \\	
+		\middlehline			
+		MWI-18 		&Bias     & -0.00 &  -0.66 & -0.23 & -0.11 & -0.08 \\
+					&mae      &  0.64 &   1.17 &  0.76 &  0.62 &  0.57 \\
+					&std      &  0.80 &   4.57 &  1.13 &  1.08 &  0.88 \\
+					&skewness &  0.01 & -13.56 & -3.28 & -4.67 & -3.80 \\	
+		\bottomhline				
+	\end{tabular}	
+	\belowtable{} % Table Footnotes
+\end{table*}
+QRNN-mwi is designed to provide basis for a cloud correction approach applicable to current satellites, which lack the higher frequency channels.
+Table~\ref{tab:statistics_mwi-alone} shows the results for all 183\,GHz channels of MWI.
+For MWI-14, the predictions from QRNN-mwi are only partially successful in removing the cloudy impact.
+The prediction errors for the complete testing dataset are highly symmetric but with a large spread.
+The average error bias of measurements from NFCS values is -1.87\,K, and after correction, it reduces to -0.18\,K.
+The corresponding standard deviation values are 9.01\,K and 1.87\,K.
+When cases with 5\,K correction are filtered out from the predicted dataset, the bias reduced further to -0.16\,K and MAE from 1.13\,K to 0.97\,K.
+Though there is a small increase in the accuracy, the high errors indicate residual cloud impact.
+For MWI-15, a slightly better accuracy than MWI-14 is observed.
+For this channel, the average error bias in the measurements is -1.23\,K, which  reduces -0.15 after correction.
 \subsubsection{MWI and ICI}
@@
 \begin{table*}[t]
-	\caption{Same as Table~\ref{tab:error_statistics_ici}, but for channels MWI-15 and MWI-16. Results are from QRNN-simple.}
+	\caption{Same as Table~\ref{tab:error_statistics_ici}, but for channels MWI-15 and MWI-16. Results are from QRNN-single.}
 	\label{tab:statistics_mwi}
@@
 		\tophline
-		&&\multicolumn{2}{c|}{Simulations}& \multicolumn{3}{c}{QRNN-simple} \\
+				&&\multicolumn{2}{c|}{Simulations}& \multicolumn{3}{c}{QRNN-single} \\
 				\cline{3-7}
 				%		\hline
-		&&   Clear-sky &   All-sky &   		 All &   Filtered(5\,K) & Filtered(15\,K) \\
-		\middlehline
-		MWI-15 		&Bias     &    0.00 &         -1.19 &           -0.02 &                -0.01(4.41\%) & -0.02(1.87\%)\\
-		&MAE      &    0.64 &          1.66 &            0.56 &                 0.49 		 &  0.52\\
-		&STD      &    0.80 &          6.21 &            0.84 &                 0.64 		 &  0.69\\
-		&Skewness &   -0.02 &         -9.87 &           -1.67 &                -0.29 		 & -0.47\\
-		\middlehline
-		MWI-16 		& Bias 	   &    0.00 &         -0.80 &           -0.04 &   -0.03(2.85\%) & -0.04(1.15\%)\\
-		& MAE      &    0.64 &          1.31 &            0.54 &     0.49		 & 0.51\\
-		& STD      &    0.80 &          5.01 &            0.82 &     0.63		 & 0.67\\
-		& Skewness &    0.01 &        -12.04 &           -1.94 &    -0.23		 &-0.81\\
+				&&   Clear-sky &   All-sky &  Filtered(5\,K) & Predicted & Predicted(5\,K) \\
+		\middlehline
+		MWI-15  &Bias     &  0.00 & -1.23 & -0.26 & -0.04 & -0.03 \\
+				&MAE      &  0.64 &  1.70 &  0.76 &  0.56 &  0.50 \\
+				&STD      &  0.81 &  6.48 &  1.01 &  0.86 &  0.64 \\
+				&Skewness & -0.00 & -9.97 & -1.15 & -1.78 & -0.15 \\
+		\middlehline
+		MWI-16  &Bias     & 0.00 &  -0.85 & -0.22 & -0.06 & -0.05 \\
+				&MAE      & 0.64 &   1.34 &  0.73 &  0.55 &  0.50 \\
+				&STD      & 0.80 &   5.31 &  0.96 &  0.83 &  0.63 \\
+				&Skewness & 0.01 & -12.08 & -1.02 & -2.25 & -0.11 \\
 		\bottomhline			
 	\end{tabular}	
-
 	\belowtable{} % Table Footnotes
 \end{table*}
+In this section, we combine the measurements from MWI-15(MWI-16) and the ICI sub-mm channels to predict MWI-15(MWI-16).
+Since we assume that all channels are remapped to a common footprint, channels MWI-14, MWI-17 and MWI-18 are virtually identical to I1V, I2V and I3V, and thus results for them are not shown separately.
 Table~\ref{tab:statistics_mwi} shows the metrics from error distributions for MWI-15 and MWI-16 predictions.
-Results from only QRNN-simple are shown.
-As shown above for ICI channels, the performance of QRNN-simple for the two MWI channels is consistent.
-
-In this case, we combine the measurements from MWI-15(MWI-16) and the sub-mm channels to predict MWI-15(MWI-16).
-Since we assume that all channels are remapped to a common footprint, channels MWI-14, MWI-17 and MWI-18 are virtually identical to I1V, I2V and I3V, and thus results for them are not shown separately.
+Results from only QRNN-single are shown.
+
+For MWI-15, the average deviations of measurements from NFCS values is -1.23\,K, and the MAE is 1.70\,K.
+When all cases are corrected, the resulting average bias is -0.04\,K and the MAE reduces to 0.56\,K.
+If only pure-filtering is made, the average bias is -0.26\,K and MAE is 0.76\,K, suggesting that a significant number of cases non-zero cloud impact pass through.
+As seen for ICI, best results are obtained  when filtering is made on the corrected dataset.
+Similar accuracy is seen for MWI-16, although it has slightly lower cloud impact.
+
 \subsection{AWS}
-In this section, we investigate the possibility of using only channels around
-325\,GHz for cloud correction at 183\,GHz. This special case of utilising only
-325\,GHz channel can be relevant for smaller satellite missions like Artic
-Weather Satellite (AWS) where higher sub-mm channels are not available.
-
-Out of the 125\,000 AWS simulations, 75\,000 cases are randomly picked to form the training set.
-The rest are used for testing.
-In the training set, 90\% of the data is randomly selected to form the training set, while the other 10\% form the \textit{testing-during-training} database.
-A similar data augmentation technique as described for ICI (Sec~\ref{sec:ici_training}) was followed to build a robust database and avoid memorisation of the samples.
-
-\subsection{Prediction accuracy}
-
-%f
-\begin{figure}[t]
-	\includegraphics[width = 80mm]{Figures/AWS-34_single.pdf}	
-	\caption{Error distributions for AWS-34 predictions.
-Label ``uncorrected'' represents the measurements, ``predicted'' denotes the entire dataset, while ``predicted(5\,K)'' and  ``predicted(15\,K)''  refers to the datasets where cases with cloud correction greater than 5\,K and 15\,K are excluded, respectively.}
-	\label{fig:qrnn_C34_deviations}	
-\end{figure}
-In an analogy between the results from ICI channels, we perform a similar error distribution analysis.
-Fig.~\ref{fig:qrnn_C34_deviations} shows the error distributions of the measurements and predicted clear-sky TBs for AWS-34.
-The statistics corresponding to curves are provided in Table~\ref{tab:statistics_qrnn_aws}.
-The label ``Filtered'' represents the subset where all cases with correction greater than 5\,K(15\,K) are removed.
-The cloud impact in the uncorrected measurements is reflected in the high negative skewness (-10.30), however the  error distributions for the predictions are relatively symmetric.
-Removing cases with cloud correction greater than 5\,K, removes only 3.02\% of the data, but the errors reduce significantly.
-Infact, the standard deviation of predictions suggests that QRNN is successful in predicting the variability of noise-free simulations.
-
-Similar error statistics for other other 183\,GHz channels are also listed in Table~\ref{tab:statistics_qrnn_aws}.
+In this section, we investigate the possibility of using only channels around 325\,GHz for cloud correction at 183\,GHz.
+This special case of utilising only 325\,GHz channel can be relevant for smaller satellite missions like Artic Weather Satellite (AWS) where higher sub-mm channels are not available.
+
+In an analogy between the results from ICI channels, we perform a similar error distribution analysis 
+and the results are displayed in Table~\ref{tab:statistics_qrnn_aws}.
 For channel AWS-32, the average bias and standard deviation in the prediction errors is is -1.34\,K and 5.91\,K respectively.
@@
 
+In order to analyse the performance of QRNN with task difficulty, the interrelation between the uncertainty estimates and cloud impact was investigated.
+Here we assume that cloud impact is representative of task difficulty.
+Fig~\ref{fig:uncertainty_cloud_impact} displays the plot between mean uncertainty estimates for $2\sigma$ confidence interval and the cloud impact.
+For all five channels, the predictions with small or relatively low cloud signal have a low uncertainty or in other words have high sharpness.
+As fraction of cloud impact increases, the predictions become increasingly uncertain.
+However, this does not imply that the prediction accuracy is low.
+
 \begin{table*}[t]
 	\caption{Bias, mean absolute error(MAE), standard deviation(STD), and measure of skewness(Skewness) for error distributions of predictions AWS channels.
-Results are from QRNN-simple.
+Results are from QRNN-single.
 The label ``All'' refers to the complete dataset, while in ``Filtered'', cases with cases with cloud correction greater than 5\,K(15\,K) are excluded from statistics.
@@
 		\tophline
-		&&\multicolumn{2}{c|}{Simulations}& \multicolumn{3}{c}{QRNN-simple} \\
+		&&\multicolumn{2}{c|}{Simulations}& \multicolumn{3}{c}{QRNN-single} \\
 		\cline{3-7}
@@
 \end{figure}
-
-We analyse the uncertainty estimates obtained from QRNN.  F
-
-In order to analyse the performance of QRNN with task difficulty, the interrelation between the uncertainty estimates and cloud impact was investigated.
-Here we assume that cloud impact is representative of task difficulty.
-Fig~\ref{fig:uncertainty_cloud_impact} displays the plot between mean uncertainty estimates for $2\sigma$ confidence interval and the cloud impact.
-For all five channels, the predictions with small or relatively low cloud signal have a low uncertainty or in other words have high sharpness.
-As fraction of cloud impact increases, the predictions become increasingly uncertain.
-However, this does not imply that the prediction accuracy is low.
-
 \section{Discussion}

### 2020-09-18 Article/ici_submm_cloudcorr.tex
re-organised results, methods section, cleaned text

@@
 relatively low, to not introduce a bias in filtered dataset. However, even
-better is to replace the original value with the predicted NFSC value when
+better is to replace the original value with the predicted NFCS value when
 forming the clear-sky dataset. This approach we denote as cloud correction. It
@@
 
-\newpage
-
-\section*{Outline of sectioning}
-
-2 Data and methods
-
-2.1 Satellite sensors
-
-2.1.1 Ice Cloud Imager (ICI)
-
-2.1.2 Microwave Imager (MWI)
-
-2.1.3 Arctic Weather Satellite (AWS)
-
-2.2 Quantile Regression Neural Network (QRNN)
-
-2.2.1 Theory
-
-2.2.2 Evaluation metrics
-
-2.3 Simulations
-
-2.3.1 Input data
-
-2.3.2 Simulation setup
-
-2.3.3 Produced dataset
-(If diifers between ICI, MWI and AWS, clarify this)
-
-\noindent 3 Results
-
-Short recap of aim of correction. We also use the correction as a filter, using
-a threshold on the correction. We use 5K (?) threshold as example.
-
-3.1 QRNN network configurations and training
-
-3.2 ICI
-
-3.2.1 Example results
-
-Show a few estimated posterior distributions (one figure) and distribution of
-predicted values (Fig 2)
-
-3.2.2 Error of best estimate
-
-3.2.3 Predicted uncertainty
-
-3.3 MWI
-
-3.3.1 MWI alone
-
-Just 183 GHz channels, original noise
-
-3.3.2 MWI and ICI
-
-As in present version
-
-3.4 AWS
-
-\noindent 4 Discussion
-
-\noindent 5 Conclusion
-
-\newpage
 \section{Data and methods}
-
-\subsection{Ice Cloud Imager}
+%
+\subsection{Satellite Instruments}
+In this section, the different satellite instruments used in this study are described.
+\subsubsection{Ice Cloud Imager}
 %
@@
 \begin{table*}[t]	
-	\caption{Specifications of ICI and MWI channels. For MWI only 183\,GHz channels are shown.}
+	\caption{Specifications of ICI and MWI channels relevant to this study.}
 	\label{tab:ICI_MWI_channels}
-	\begin{tabular}{lrrrr}
+	\begin{tabular}{lrrr}
 		\tophline
-		Channel & Frequency 	& Bandwidth  	&NE$\Delta$T	&Polarisation\\
-				& [GHz]			& [MHz]			& [K]			&\\
-		\middlehline
-		I1V&	183.31$\pm$7.00    & 2000 			& 0.8 		& V\\
-		I2V&	183.31$\pm$3.40    & 1500 			& 0.8 		& V\\
-		I3V&	183.31$\pm$2.00    & 1500			& 0.8 		& V\\
-		I4V&	243.20$\pm$2.50    & 3000			& 0.7 		& V\\
-		I4H&	243.20$\pm$2.50    & 3000			& 0.7 		& H\\
-		I5V&	325.15$\pm$9.50    & 3000			& 1.2 		& V\\
-		I6V&	325.15$\pm$3.50    & 2400			& 1.3 		& V\\
-		I6V&	325.15$\pm$1.50    & 1600			& 1.5 		& V\\
-		I8V&	448.00$\pm$7.20    & 3000			& 1.4 		& V\\
-		I9V&	448.00$\pm$3.00    & 2000			& 1.6 		& V\\
-		I10V&	448.00$\pm$1.40    & 1200			& 2.0 		& V\\
-		I11V&	664.00$\pm$4.20    & \phantom{0}500			& 1.6 		& V\\
-		I11H&	664.00$\pm$4.20    & \phantom{0}500 			& 1.6 		& H\\		
+		Channel & Frequency 	& Bandwidth  	&NE$\Delta$T	\\
+				& [GHz]			& [MHz]			& [K]			\\
+		\middlehline
+		I1V&	183.31$\pm$7.00    & 2000 			& 0.8 		\\
+		I2V&	183.31$\pm$3.40    & 1500 			& 0.8 		\\
+		I3V&	183.31$\pm$2.00    & 1500			& 0.8 		\\
+		I5V&	325.15$\pm$9.50    & 3000			& 1.2 		\\
+		I6V&	325.15$\pm$3.50    & 2400			& 1.3 		\\
+		I6V&	325.15$\pm$1.50    & 1600			& 1.5 		\\
+		I8V&	448.00$\pm$7.20    & 3000			& 1.4 		\\
+		I9V&	448.00$\pm$3.00    & 2000			& 1.6 		\\
+		I10V&	448.00$\pm$1.40    & 1200			& 2.0 		\\
+		I11V&	664.00$\pm$4.20    & \phantom{0}500	& 1.6 		\\
+		I11H&	664.00$\pm$4.20    & \phantom{0}500 & 1.6 		\\		
 		\bottomhline
 	\end{tabular}
-	\begin{tabular}{lrrrr}
+	\begin{tabular}{lrrr}
 		\tophline
-		Channel & Frequency 	& Bandwidth  	&NE$\Delta$T	&Polarisation\\
-				& [GHz]			& [MHz]			& [K]			&\\
-		\middlehline
-		MWI-14&	183.31$\pm$7.00    & 2000 			& 1.3 		& V\\
-		MWI-15&	183.31$\pm$6.10    & 1500			& 1.2 		& V\\
-		MWI-16&	183.31$\pm$4.90    & 1500			& 1.2 		& V\\
-		MWI-17&	183.31$\pm$3.40    & 1500			& 1.2 		& V\\
-		MWI-18&	183.31$\pm$2.00    & 1500			& 1.3 		& V\\	
+		Channel & Frequency 	& Bandwidth  	&NE$\Delta$T	n\\
+				& [GHz]			& [MHz]			& [K]			\\
+		\middlehline
+		MWI-14&	183.31$\pm$7.00    & 2000 			& 1.3 		\\
+		MWI-15&	183.31$\pm$6.10    & 1500			& 1.2 		\\
+		MWI-16&	183.31$\pm$4.90    & 1500			& 1.2 		\\
+		MWI-17&	183.31$\pm$3.40    & 1500			& 1.2 		\\
+		MWI-18&	183.31$\pm$2.00    & 1500			& 1.3 		\\	
 		\bottomhline
@@
 
-Ice Cloud Imager (ICI) is a new EPS-SG (EUMETSAT Polar System - Second Generation) sensor that will observe  Earth using submillimeter-wave (sub-mm) frequency range.
-The main objective of ICI is measure ice cloud properties and improve the representation of clouds in regional and global models.
-ICI is a conically scanning millimetre/sub-millimetre radiometer which will measure 13 frequencies from 183 GHz up to 664 GHz.
-Channels with centre frequencies 183.31, 325.15 and 448.0\,GHz are centered on water vapor absorption lines, and measure vertical polarization.
-While other channels around 243.0 and 664.0\,GHz are ``window channels'' and receive both vertical and horizontal polarization.
-
-\subsection{MicroWave Imager}
-%
-In addition to ICI, the EPS-SG satellite will also have Microwave Imager (MWI) onboard.
-MWI will measure frequencies from 18.7 GHz up to 183\,GHz and provide data continuity to the existing microwave imager measurements.
-The common 183\,GHz channels among the two instruments shall allow cross-calibration between the two instruments.
-A brief summary of the MWI 183\,GHz channels is provided in Table~\ref{tab:ICI_MWI_channels}.
-
-\subsection{Artic Weather Satellite}
-%
-\begin{table*}[t]
-	\caption{Specifications of AWS channels around 183\,GHz and 325\,GHz.}
+Ice Cloud Imager (ICI) is a new instrument on board EPS-SG(EUMETSAT Polar System - Second Generation) satellite Metop-SG.
+Metop-SG is scheduled for launch in 2023, and will make ICI the first operational sensor observing Earth using sub-millimeter(sub-mm) wavelengths.
+ICI is a conically scanning radiometer that will measure 13 frequencies from 183 GHz up to 664 GHz.
+The main objective of ICI is to use high frequency channels for measuring ice cloud properties and improve the representation of ice clouds in regional and global Numerical Weather Prediction(NWP) models.
+ICI consists of channels receiving frequencies around 183.31\,GHz, 325.15\,GHz and 448.00\,GHz, measuring vertical polarization.
+While other channels around frequencies 243.20\,GHz and 664.00\,GHz are ``window channels'' and measure both vertical and horizontal polarization.
+The instrument will observe earth from a mean altitude of 832\,Km with sensor viewing angle 44.767$^\circ$(measured from nadir).
+For all the channels, the mean footprint size is about 15\,Km, but the exact geo-location of samples differs.
+Therefore a simultaneous utilization of data from different channels requires remapping to a common footprint \citep{eriksson:towar:20}.
+
+For this study, we conducted the forward simulations at frequencies: 183.31\,GHz, 325.15\,GHz, 448.00\,GHz and 664.00\,GHz(See Table~\ref{tab:ICI_MWI_channels}).
+For brevity, we assumed that all simulations were mapped to a common footprint.
+
+\subsubsection{MicroWave Imager}
+%
+\label{mwi_channels}
+In addition to ICI, the Metop-SG will also have Microwave Imager(MWI) on board.
+MWI is a conically scanning radiometer and will measure frequencies from 18 GHz up to 183\,GHz \todo{add ref}.
+All channels up to 89 GHz will receive both horizontal and vertical polarisation, while other frequencies will receive only vertical polarisation.
+A short summary of the MWI channels used in the study is provided in Table~\ref{tab:ICI_MWI_channels}.
+MWI also has three  183\,GHz frequencies in common with ICI.
+The overlapping frequencies shall allow cross-calibration between the two instruments, and provide microwave measurements from 18\,GHz to 664\,GHz on a common scale.
+The main objective of MWI is to provide data continuity to the existing microwave imager measurements for cloud and precipitation and support regional and global NWP models.
+
+For this study, forward simulations at frequencies around 183.31\,GHz were performed.
+When ICI and MWI simulations were used together, MWI channels were assumed to be mapped to ICI footprint and resolution.
+Remapping reduces the noise in MWI from 1.2\,K at 10\,Km resolution to 0.8\,K at 15\,Km resolution.
+
+\subsubsection{Artic Weather Satellite}
+%
+\begin{table}[t]
+	\caption{Specifications of AWS channels relevant to this study.}
 	\label{tab:specifications_AWS}	
-	\begin{tabular}{lrr}
+	\begin{tabular}{lrrr}
 		\tophline
-		Channel & Frequency 	& Bandwidth  \\
-		& [GHz]			& [MHz]		\\
-		\middlehline
-		AWS-32	&	176.311    & 2000 		\\
-		AWS-33	&	178.811    & 2000 		\\
-		AWS-34	&	180.311    & 1000 		\\
-		AWS-35	&	181.511    & 1000 		 \\
-		AWS-36	&	182.311    & \phantom{0}500 	 \\
-		AWS-41    & 325.15$\pm$6.60    & 2800 \\
-		AWS-42    & 325.15$\pm$4.10    & 1800  \\
-		AWS-43    & 325.15$\pm$2.40    & 1200 \\
-		AWS-44    & 325.15$\pm$1.20    & \phantom{0}800  \\
+		Channel & Frequency 	& Bandwidth & NE$\Delta$T \\
+				& [GHz]			& [MHz]		& [K]		\\
+		\middlehline
+		AWS-32	&	176.311    & 2000	&		\\
+		AWS-33	&	178.811    & 2000 	&	\\
+		AWS-34	&	180.311    & 1000 	&	\\
+		AWS-35	&	181.511    & 1000 	&	 \\
+		AWS-36	&	182.311    & \phantom{0}500  &	 \\
+		AWS-41  & 325.15$\pm$6.60    & 2800 	 &0.60\\
+		AWS-42  & 325.15$\pm$4.10    & 1800    &0.75	\\
+		AWS-43  & 325.15$\pm$2.40    & 1200    &0.92\\
+		AWS-44  & 325.15$\pm$1.20    & \phantom{0}800  &1.12  \\
 		\bottomhline
@@
 	\belowtable{} % Table Footnotes
-\end{table*}
-
+\end{table}
 The Arctic Weather Satellite (AWS) is a small satellite mission approved as ESA
-Earth Watch Programme Element. It is a small platform carrying a single
-across-track scanning microwave radiometer.
+Earth Watch Programme Element.
+It is a small platform carrying a single across-track scanning microwave radiometer.
 It is planned as a small but cost-effective platform, which can supplement the information from other polar orbiting satellites.
-The main objective of AWS will be to improve representation of Artic and sub-Arctic weather in NWP models and improve the global weather forecasts.
-AWS will will have channels receiving frequencies around 89\,GHz, 165.5\,GHz, 183\,GHz, 229\,GHz and 325\,GHz.
-For a detailed description of the AWS channels see \citet{eriksson2020study}, while a brief summary of AWS channels relevant to this study are provided in
-Table~\ref{tab:specifications_AWS}. The first prototype mission is expected to be delivered around 2023.
-
-\subsection{QRNN}
-%
-The neural network training is a process of learning to predict the outputs {$y_i$} from inputs {$x_i$} through a series of learnable transformations.
-While training, neural networks seek to minimise the model error through a loss function.
-The choice of the loss function depends on the predictive problem.
-When a neural network is trained to minimise the mean of the quantile loss function to predict the quantiles of the distribution, it is called a Quantile Regression Neural Network (QRNN).
-\subsubsection{Theory}
-
-\subsubsection{Evaluation metrics}
-
-Quantile loss function
-
-CRPS
+The first prototype mission is expected to be delivered around 2023.
+The main objective of AWS will be to improve the representation of Artic and sub-Arctic weather in NWP models and improve the global weather forecasts.
+AWS will will have channels receiving frequencies around 89.00\,GHz, 165.5\,GHz, 183.31\,GHz, 229.00\,GHz and 325.15\,GHz.
+For a detailed description of the AWS channels see \citet{eriksson2020study}.
+
+In this study, forward simulations at frequencies 183.31\,GHz and 325.15\,GHz were conducted. A brief summary of these channels is provided in Table~\ref{tab:specifications_AWS}.
+
+\subsubsection{Cloud Profiling Radar}
+%
+Cloud Profiling Radar(CPR) is the main instrument on sun-synchronous polar orbit satellite CloudSat (Cloud Satellite) \citep{Stephens2002cloudsat}.
+It was launched in 2006 and is part of the A-train constellation of four earth observation satellites.
+CPR is a nadir looking radar operating at 94.05\,GHz and measures the cloud backscatter as a function of distance from the radar, to provide vertical profiles of clouds and precipitation.
+
+In this study, CloudSat profiles were used only to perform the forward simulations for ICI, MWI and AWS.
 
@@
 %
+Cloudsat profiles during August 2015 were randomly selected for forward simulations.
+The input data were restricted between $60^{\degree}$S to $60^{\degree}$N, and surface is below 500\,m.
+Both clear-sky and all-sky scenarios were simulated, and no differentiation was made between the observations over ocean/sea and land.
 \subsubsection{Simulation setup}
@@
 
-\subsection{Produced dataset}
-%
-Using the simulation setup described in previous section, Cloudsat profiles during August 2015 were randomly selected to generate 220\,000 cases for each ICI and MWI frequency.
-The input data were restricted between $60^{\degree}$S to $60^{\degree}$N, and surface is below 500\,m.
-Both clear-sky and all-sky scenarios were simulated, and no differentiation was made between the observations over ocean/sea and land.
-It is also assumed that all simulations of ICI and MWI are remapped to a common foorprint.
-
-For AWS, 7 monochromatic frequencies were simulated each for 183\,GHz, 325\,GHz-upper amd 325\,GHz-lower, so that the channel brightness temperature for each could be represented with sufficient accuracy.
-The monochromatic frequencies were interpolated to a finer grid to get the channel temperatures.
-All AWS sensor viewing angles (from $0^\circ$ to $45^\circ$) were simulated, but the results described in this section are based on nadir viewing angle.
-130\,000 cases based on randomly selected CloudSat orbits were simulated.
+\subsubsection{Produced dataset}
+%
+Using the simulation setup described in previous section,  
+220\,000 cases for each ICI and MWI frequency were simulated, using randomly selected CloudSat profiles. For both instruments, the channel frequencies were simulated directly.  
+For AWS, 140\,000 cases were simulated.
+21 monochromatic frequencies were used and interpolated to a finer grid to get the channel brightness temperatures.
+All AWS sensor viewing angles (from $0^\circ$ to $45^\circ$) were simulated, but the results described in this study are based on nadir viewing angle.
+
+ARTS simulations are noise free, so to incorporate the measurement uncertainties, whenever needed, gaussian noise was added to according to the channel NE$\Delta$T (Table~\ref{tab:ICI_MWI_channels}, Table~\ref{tab:specifications_AWS}).
+For cases where MWI and ICI simulations were assumed to be remapped to a common footprint, the NE$\Delta$T for corresponding to ICI channels was used (See Sect.~\ref{mwi_channels}).
+
+The noise free simulations were divided into training and testing datasets.
+Out of the 220\,000 simulations for ICI and MWI each, 175\,000 cases were randomly picked to form the training set.
+The rest were used for testing.
+A smaller database was selected for AWS.
+120\,000 simulations were used for training and the
+remaining were used for testing.
+
+\subsection{QRNN}
+%
+The neural network training is a process of learning to predict the outputs {$y_i$} from inputs {$x_i$} through a series of learnable transformations.
+While training, neural networks seek to minimise the model error through a loss function.
+The choice of the loss function depends on the predictive problem.
+When a neural network is trained to minimise the mean of the quantile loss function to predict the quantiles of the distribution, it is called a Quantile Regression Neural Network (QRNN).
+
+\subsubsection{Theory}
+
+\subsubsection{Evaluation metrics}
+
+Quantile loss function
+
+CRPS
+
+\subsubsection{QRNN implementation}
+\label{sec:qrnn-implementation}
+
+The implementation of QRNN is based on PyTorch, an open source machine learning library \citep{paszke2017automatic}.
+It is developed and available as a part of \textit{typhon:tools for atmospheric research} software package [\todo{developer's version??}].
+
+For this study, we initialize the quantile loss function with quantile fractions $\tau$ = [0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998] to train the neural network to predict the corresponding quantiles $x_{\tau}$ = [$-3\sigma, -2\sigma, -1\sigma, median, 1\sigma, 2\sigma, 3\sigma $].
+QRNN is trained with simulated brightness temperatures from different channels, no other data is included.
+The input channels are variable and are determined by the type of QRNN model used.
+The different QRNN models are described in Sect.~\ref{QRNN_models}.
+
+A custom data augmentation scheme is implemented to build a robust learning network.
+At each training iteration, noise is added to the noise-free inputs according to the measurement uncertainty.
+The target training data is always kept noise free.
+This ensures that the model is exposed to different datasets during the entire training process, and avoids memorisation of training samples.
+The input data is normalized with mean and standard deviation.
+While training, 10\% of the training data is used for validation.
+
+The neural network is trained with an adaptive form of stochastic batch gradient descent.
+During the training process, at each iteration, the loss in the validation dataset in monitored.
+If the validation loss remains stagnant for a certain number of epochs, the training rate is reduced  by a given reduction factor.
+This process is continued till a minimum learning rate is achieved.
+
+A high performing QRNN model also requires tuning of multiple hyper-parameters.
+These parameters determine the structure and the training set-up of the neural network.
+Several of these hyper-parameters are non-learnable, and must be defined before beginning of every training.
+Grid search is one of the most often employed techniques for hyper-parameter tuning.
+In grid search, different combinations of hyper-parameters are selected and for each, the model performance is evaluated.
+The model architecture with the best performance is selected.
+For the structural parameters, usually a grid search over the number of neurons (width) and hidden layers (depth) is performed.
+The model is trained for multiple values of layer widths and hidden layers, and the best configuration is selected by evaluating the predictions over validation dataset.
+Similarly, the training process is optimized by performing a grid search different training parameters such as : batch size, learning rate, number of epochs etc.
+We use quantile loss and CRPS for evaluation of the model performance.
+
+\subsubsection{ QRNN model configurations}
+%
+\label{QRNN_models}
 
@@
 		\tophline
-		QRNN model & Sensor & Target & Input 183\,GHz channel(s) &Other training inputs \\
+		QRNN model & Instrument & Target & Input 183\,GHz channel(s) &Other training inputs \\
 		\middlehline
@@
 
-\subsection{Training data}
-%
-The QRNN models presented in this study are trained with simulated brightness temperature data to predict the NFSC values for 183\,GHz channels.
-No other data was included in the training process, but the training set varied according to the QRNN-model (described further).
-Out of the 220\,000 simulations for ICI and MWI each, 175\,000 cases were randomly picked to form the training set.
-The rest were used for testing.
-For AWS a slightly smaller database was selected.
-We had 130\,000 available simulations and all were used for training.
-A testing dataset was constructed by randomly drawing 25\,000 cases from the training dataset and noise was added to each simulation to mimic a new measurement set.
-
-In the training set for all three sensors, 90\% of the data was randomly selected to form the training set, while the other 10\% formed the \textit{testing-during-training} database.
-ARTS simulations are noise free, so to incorporate the satellite measurement uncertainties, gaussian noise was added to the input training data according to the channel NE$\Delta$T.
-The target training data was kept noise free.
-In order to build a robust learning network, random noise was added to the inputs at each training iteration.
-This exposes the model to a different datasets during the entire training process and avoids the memorisation of training samples.
-The input data was also normalized with mean and standard deviation.
-
-\subsection{QRNN model configurations}
-%
-\label{QRNN_models}
-Multiple QRNN models were trained with several combinations of the training input.
-For each combination, the target was always one of the available 183\,GHz channels, and this target channel was always included in the training set.
-The choice of other channels in the training set depended on the type of QRNN model chosen.
-Three main types of QRNN models were used in this study.
-
-In the first model, the training inputs always contained data from the target 183\,GHz channel, and one or more available sub-mm channels.
-No data from other 183\,GHz channels was included in training.
-We refer this model as ``QRNN-single''.
-For ICI and MWI, the available sub-mm channels are 325\,GHz, 448\,GHz and 664\,GHz, while for AWS only 325\,GHz is available.
-It should be noted that though MWI does not have any sub-mm channels,  sub-mm channels from ICI were used.
-It is assumed for the simulations that data from ICI and MWI channels are mapped to a common footprint and resolution.
-In such case, remapping reduces the noise in MWI channels from 1.2\,K at 10\,Km resolution to 0.8\,K at 15\,Km resolution.
-
-The second model was defined to investigate the  impact of using all 183\,GHz channels concurrently.
-This model is referred as ``QRNN-all''.
-In this model, the training set included data from all available 183\,GHz channels, along with other sub-mm channels.
-This model was applied only to ICI.
-It should be noted that although the training set was identical for I1V, I2V and I3V, a separate training was needed for each channel as target.
-
-The third model was used only for MWI channels.
-In this case, all 183\,GHz channels were used concurrently in the training set.
-No other data from sub-mm channels was used.
-Further in the text, we shall refer this model as ``QRNN-mwi''.
-
+In the study, three types of QRNN models are formulated.
+For each type, the target is always one of the available 183\,GHz channels, and this target channel is always included in the training set.
+The choice of other channels in the training set depends on the type of QRNN model chosen.
 A summary of the three QRNN models described in this study is provided in Table~\ref{tab:QRNN_models}.
+
+In the first model, ``QRNN-single'', the training inputs always contain data from the target 183\,GHz channel, and one or more available sub-mm channels.
+Other 183\,GHz channels are not included in the training.
+For ICI and MWI, 325\,GHz, 448\,GHz and 664\,GHz channels are used in the training, while for AWS only 325\,GHz is used.
+
+The second model, ``QRNN-all'', is defined to investigate the  impact of using all 183\,GHz channels concurrently.
+In this model, the training set includes data from all available 183\,GHz channels, along with other sub-mm channels.
+This model is applied only to ICI.
+It should be noted that although the training set is identical for I1V, I2V and I3V, a separate training is needed for each channel as target.
+
+The third model, ``QRNN-mwi'' is used only for MWI channels. In this case, all 183\,GHz channels are used concurrently in the training set. No other data from sub-mm channels is used.
 
@@
 The main aim of this study is to demonstrate that sub-mm channels can be used to formulate the cloud filtering/correction of data measured around 183\,GHz.
-Different combinations of 183\,GHz channel and sub-mm channels are applied to QRNN and the results are compared.
-To determine the prediction performance of QRNN, the NFCS simulations are used as reference.
+Different combinations of 183\,GHz channels and sub-mm channels are applied to QRNN and the results are compared.
+The impact of different hyper-parameters on QRNN performance is also discussed.
+NFCS simulations are used to analyse the prediction accuracy.
 Results from both pure-filtering and correction are described.
@@
 %
-A high performing QRNN model requires tuning of multiple hyper-parameters.
-These parameters determine the structure and the training set-up of the neural network.
-Several of these hyper-parameters are non-learnable, and must be defined before beginning of every training.
-Grid search is one of the most often employed techniques for hyper-parameter tuning.
-In grid search, different combinations of hyper-parameters are selected and for each, the model performance is evaluated.
-The model architecture with the best performance is selected.
-We use quantile loss and CRPS for evaluation of the model performance.
-
-For the structural parameters, usually a grid search over the number of neurons (width) and hidden layers (depth) is performed.
-The model is trained for multiple values of layer widths and hidden layers, and the best configuration is selected by evaluating the predictions over validation dataset.
-Similarly, the training process is optimized by performing a grid search different training parameters such as : batch size, learning rate, number of epochs etc.
-In this study, all possible hyper-parameters were not tested.
-We investigated the performance of QRNN only to certain hyper-parameters like number of neurons, hidden layers, learning rate, convergence epochs and batch size.
-The others were chosen empirically.
-
-Firstly, we performed a grid search to select the size of the neural network.
+\begin{figure*}[t]
+	\centering
+	\includegraphics[height=60mm]{Figures/CRPS.pdf} 
+	\caption{CRPS(left) and mean quantile loss(right) averaged over all predicted quantiles for different combinations of layer width and hidden layers ($n_h$).
+The results are from QRNN-single applied to I2V.}
+	\label{fig:grid_search}	
+\end{figure*}
+In this study, we investigated the performance of QRNN only to certain hyper-parameters like number of neurons, hidden layers, learning rate, convergence epochs and batch size.
+The optimization of other hyper-parameters was not performed and were chosen empirically.
+Firstly, we performed a grid search to define the structure of the neural network.
 We evaluated the performance for three sizes of hiddden layers($n_h$ = 2, 3, 4), and layer widths of sizes in the set [8, 16, 32, 64, 128, 256, 512].
-The mean quantile loss and CRPS for different layer width and hidden layer configurations are shown in Fig\ref{fig:grid_search}.
-The results are for QRNN-single with I2V as target channel.
+The mean quantile loss and CRPS over all predicted quantiles was computed for each configuration (Fig.~\ref{fig:grid_search}).
 Increasing the complexity of the network by increasing the layer width and depth has a positive impact on performance.
 However for four hidden layers, increasing the number of neurons beyond 128 has no significant impact on the performance.
-On basis of these results, a neural network with four hidden layers and 128 neurons in each layer was selected for QRNN-single.
-For the optimising the training parameters, a customised  learning rate scheduler was implemented.
+On basis of these results, a neural network with four hidden layers and 128 neurons in each layer was selected.
+For optimising the training parameters, a customised  learning rate scheduler was implemented.
 The initial learning rate was reset after a certain number of epochs.
@@
 The best neural network performance was obtained when the network was trained three times with a new initial learning rate.
-For each training  if the validation loss remained unchanged till 6 training epochs, the learning rate was reduced by a factor of 2.
-In order to select the batch size, we simply compared the performance for batch size = 128 and 256, and the former gave better results.
-Concerning number of maximum epochs, we obtained best results when the network was trained longer.
+For each training, if the validation loss remained unchanged till 6 training epochs, the learning rate was reduced by a factor of 2.
+In order to select the batch size, we simply compared the performance for for two batch sizes: 128 and 256, and the former gave better results.
+Concerning number of epochs, we obtained best results when the network was trained longer.
 Choosing a lower value of epochs (e.g.
@@
 
-Though these set of hyper-parameters were selected for QRNN-single applied to I2V, they worked well for other channnels and QRNN-all/QRNN-mwi as well.
-In the end, all the results described in this study use an identical hyper-parameter configuration.
-
-\begin{figure*}[t]
-	\centering
-	\includegraphics[height=60mm]{Figures/CRPS.pdf} 
-	\caption{CRPS(left) and mean quantile loss(right) for different combinations of layer width and hidden layers ($n_h$). The results are from QRNN-simple for channel I2V.}
-	\label{fig:grid_search}	
-\end{figure*}
+Though these set of hyper-parameters were selected for QRNN-single applied to I2V, they worked well for other channnels and other QRNN models as well.
+All the results described in this study used an identical hyper-parameter configuration.
 
@@
 %
+%f
+\begin{figure}[t]
+	\centering
+	\includegraphics[height=60mm]{Figures/posterior_distribution_I2V.pdf} 
+	\caption{Posterior distribution obtained from QRNN-single (I2V) for three different cases. }
+	\label{fig:posterior_distribution_I2V}	
+\end{figure}
+%f
+\begin{figure*}[t]
+	\includegraphics[width=\textwidth]{Figures/PDF_predictions_ICI.pdf} 
+	\caption{Distributions of point estimate NFCS from QRNN-single for channels I1V, I2V and I3V. The corresponding distributions for NFCS simulations are also shown.}
+	\label{fig:PDF_predictions}	
+\end{figure*}
 QRNN predictions are estimates of the posterior distribution over different quantiles.
-For this study we chose quantiles, $x_{\tau}$: median, $\pm 1\sigma$, $\pm 2 \sigma$ and  $\pm 3 \sigma$ ($\tau$ = 0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998).
+For this study we chose quantiles, $x_{\tau}$: median, $\pm 1\sigma$, $\pm 2 \sigma$ and  $\pm 3 \sigma$ (Sect.~\ref{sec:qrnn-implementation}).
 The quantiles are interpreted as probabilistic predictions and can be used to construct a probability distribution of the predictions.
-This is in sharp contrast to correction approaches which give out only point estimates.
-As an example, Fig.~\ref{fig:posterior_distribution_I2V} shows the posterior distribution obtained from QRNN for three different cases.
-These results are from QRNN-single for channel I2V.
-The three cases shown in the figure have almost a similar median value but very different spread.
+Fig.~\ref{fig:posterior_distribution_I2V} exemplifies the posterior distribution predicted by QRNN-single.
+The three cases shown in the figure have a similar median value but very different spread.
 The spread of the distributions can also be expressed as the prediction interval.
@@
 While the other two cases have longer intervals implying higher fluctuations, or low reliability.
-
 The quantiles can also be used to interpret the confidence intervals.
 For a given case, if two quantiles $\tau_1$ and $\tau_2$ are chosen, then there is $\tau_2 - \tau_1$ chance that the true value ($y_o$) shall lie in in range $[y_{\tau_1}, y_{\tau_2}]$.
-For example, in a 94\% confidence interval where, $\tau_1 = -2\sigma$ and $\tau_1 = +2\sigma$, there is 0.3\% probability that $y_\circ > y_{\tau_2}$, and 97\% probability that $y_\circ$ > $y_{\tau_1}$.
-
-%f
-\begin{figure}[t]
-	\centering
-	\includegraphics[height=60mm]{Figures/posterior_distribution_I2V.pdf} 
-	\caption{Posterior distribution obtained from QRNN-single (channel I2V) for three different cases. }
-	\label{fig:posterior_distribution_I2V}	
-\end{figure}
-
-\subsubsection{Error of best estimate}
-%
-%f
-\begin{figure*}[t]
-	\includegraphics[width=\textwidth]{Figures/PDF_predictions_ICI.pdf} 
-	\caption{Distributions of predicted clear-sky values from QRNN-simple for channels I1V, I2V and I3V. }
-	\label{fig:PDF_predictions}	
-\end{figure*}
+For example, in a 94\% confidence interval where, $\tau_1 = -2\sigma$ and $\tau_2 = +2\sigma$, there is 0.3\% probability that $y_\circ > y_{\tau_2}$, and 97\% probability that $y_\circ$ > $y_{\tau_1}$.
+More on confidence interval is discussed in Sect.~\ref{sec:prediction_uncertainty}.
+
+For an analysis of QRNN predictions, a point estimate of the posterior distribution is required.
+Usually for Bayesian analysis, the posterior mean or posterior median are selected as point estimates.
+In this study, we assume the posterior median to be the best estimate for the predicted NFCS value.
+The distribution of point estimates is shown in Fig.~\ref{fig:PDF_predictions}.
+For clear-sky conditions, I1V has the warmest brightness temperatures and I3V has the coldest.
+For all three channels, an excellent agreement between the predictions and simulations is observed, indicating that QRNN is successful in predicting NFCS values for majority of the cases.
+At lower brightness temperatures, the frequency of predictions is slightly smaller than simulations.
+This could be due to few QRNN predictions ending up with partially corrected cloud impact.
+
+\subsubsection{Analysis of cloud filtering}
+%
+\label{sec:cloud_filtering}
 %f 
@@
 	\includegraphics[width=\textwidth]{Figures/error_distribution_QRNN-single.pdf} 
-	\caption{Error distributions for deviations of QRNN-simple predictions to clear-sky simulations for channels I1V, I2V and I3V.
-Label ``Uncorrected'' represents the measurements and ``Filtered(5\,K)'' represents the dataset when no correction is made but cases with cloud correction greater than 5\,K are omitted.
-`Predicted'' denotes the entire prediction dataset, while ``Predicted(5\,K)'' refers to the predicted dataset where cases with cloud correction greater than 5\,K are excluded.}
+	\caption{Error distributions for deviations of filtered and predicted data to clear-sky simulations.
+The results are from QRNN-single and channels I1V, I2V and I3V.
+Noise for each channel is also plotted for reference.
+The label ``Uncorrected'' represents the measurement data and ``Filtered(5\,K)'' represents the dataset when no correction is made but cases with cloud correction greater than 5\,K are rejected.
+``Predicted(All)'' denotes the entire prediction dataset, while ``Predicted(5\,K)'' refers to the predicted dataset but where cases with cloud correction greater than 5\,K are excluded.}
 	\label{fig:error_distributions}	
 \end{figure*}
-
-%t
 \begin{table*}[t]
-	\caption{Bias, mean absolute error(MAE), standard deviation(STD), and measure of skewness(Skewness) for error distributions of predictions of I1V, I2V and I3V.
-Results from both QRNN-simple and QRNN-all are shown.
-The label ``Filtered'' refers to the dataset where cases with cloud correction greater than 5\,K are filtered out, and  no other correction is made.
-The label ``Predicted(All)'' refers to the complete predicted dataset, while in ``Predicted (5\,K)'', cases with cloud correction greater than 5\,K are removed from the predicted dataset.
-The fraction of cases removed by this filter are given in parentheses.}
+	\caption{ Error statistics for deviations of filtered and predicted data to NFCS simulations. 
+		The values for Bias, mean absolute error(MAE), standard deviation(STD), and measure of skewness(Skewness) are shown.
+Results are from both QRNN-single and QRNN-all for channels I1V, I2V and I3V.
+The number in parentheses is the percentage of cases removed by filtering.
+The label ``Filtered(5\,K)'' represents the dataset when no correction is made but cases with cloud correction greater than 5\,K are rejected, ``Predicted(All)'' refers to the complete predicted dataset, while ``Predicted (5\,K)'' denotes the prediction dataset but where cases with cloud correction greater than 5\,K are excluded.}
 	\label{tab:error_statistics_ici}
@@
 
-Channel I1V& Bias     &  0.00 & -1.88 & -0.32(6.1\%) & -0.06 & -0.04 & -0.31(6.1\%) & -0.06 & -0.04 \\
+		I1V& Bias     &  0.00 & -1.88 & -0.32(6.1\%) & -0.06 & -0.04 & -0.31(6.1\%) & -0.06 & -0.04 \\
 		&MAE      &  0.64 &  2.32 &  0.79 &  0.64 &  0.55 &  0.78 &  0.61 &  0.54 \\
@@
 		\middlehline
-Channel I2V &Bias     & -0.00 &  -1.04 & -0.24(3.7\%) & -0.01 & -0.00 & -0.24(3.6\%) & -0.05 & -0.03 \\
+		I2V &Bias     & -0.00 &  -1.04 & -0.24(3.7\%) & -0.01 & -0.00 & -0.24(3.6\%) & -0.05 & -0.03 \\
 		&MAE      &  0.64 &   1.52 &  0.74 &  0.52 &  0.46 &  0.75 &  0.44 &  0.39 \\
@@
 		\middlehline	
-Channel I3V &Bias     & -0.00 &  -0.63 & -0.18(2.3\%) &  0.01 &  0.02 & -0.19(2.2\%) & -0.03 & -0.03 \\
+		I3V &Bias     & -0.00 &  -0.63 & -0.18(2.3\%) &  0.01 &  0.02 & -0.19(2.2\%) & -0.03 & -0.03 \\
 		&MAE      &  0.64 &   1.15 &  0.71 &  0.51 &  0.47 &  0.72 &  0.46 &  0.42 \\
@@
 
+In this section, we use the point estimates to formulate a cloud filtering scheme.
+All cases with  cloud correction greater than a certain threshold are classified as cloudy and omitted from the dataset.
+Cloud correction is calculated as the difference of the point estimate and the corresponding measurement.
+Since this is a pure-filter, for the cases classified as clear-sky, the a priori values are used instead of the point estimates.
+
+To implement the cloud filtering scheme, we chose 5\,K cloud correction as the filtering threshold.
+All cases with correction greater than 5\,K were rejected.
+In order to analyse the performance of the filtering threshold, the deviations of the filtered measurements to the simulated NFCS values were calculated.
+Fig.~\ref{fig:error_distributions} shows the distribution of the deviations for filtered(red) and original datasets(green).
+Cloud contamination causes a reduction in the brightness temperatures, and introduces a large negative bias in the error distributions.
+Without any cloud impact, the error distributions must follow a Gaussian distribution with a narrow spread.
+When filtering is activated, and all cases with correction greater than 5\,K are rejected, the resulting distributions have a low but asymmetric spread.
+The right side of the distributions follows measurement noise, as expected, and the left side has a significantly smaller negative skewness than the measurements.
+This indicates that 5\,K filter can successfully remove cases associated with high cloud impact.
+However at the same time, the asymmetric error distribution indicates that cases with low cloud impact are erroneously classified as clear-sky.
+
+For a quantitative assessment of the performance achieved with cloud filtering, we calculated the average error bias, MAE (mean absolute error) and standard deviation of the errors.
+The asymmetry of error distributions around their mean is also calculated through the measure of skewness.
+Fisher-Pearson coefficient of skewness is used to calculate the measure of skewness:
+\begin{equation}
+g_1 = \frac{m_3}{m_2^{3/2}}, 
+\end{equation}
+where $m_2$ and $m_3$ are biased sample's second and third central moments.
+The error metrics corresponding to the error distributions described in Fig.~\ref{fig:error_distributions} are provided in Table~\ref{tab:error_statistics_ici} under label "Filtered(5\,K)".
+The average bias in I1V measurements is -1.88\,K, and rejecting around 6\% of the cases as cloudy reduces the bias to -0.32\,K.
+The standard deviation also reduces to 1.07\,K from 8.84\,K.
+Similarly for I2V, the average error bias in all sky measurements is -1.04\,K, that reduces to -0.24\,K after filtering.
+The corresponding improvement in MAE was almost 65\%.
+Only 3.7\% of the total cases were rejected to achieve this accuracy.
+For I3V, filtering classifies 2.3\% of the total cases as cloudy and reduces the bias to 0.18\,K from -0.63\,K and the standard deviation from 5.95\,K to 0.91\,K.
+The results from QRNN-all are also shown in the same table.
+Using all 183\,GHz channels concurrently has no notable impact on the cloud filtering.
+Almost similar statistics are obtained from QRNN-single and QRNN-all.
+Overall for all three channels, the notable decrease in the errors indicates that the cloud filter is effective in removing most of the cloudy cases, however few cases with low cloud impact still pass through the filter and deteriorate the performance.
+This indicates that though a pure-filtering approach can prove as a reliable procedure for removing cases with high cloud impact, additional measures are needed to remove cases with low cloud impact.
+
+A lower filtering threshold can help alleviate this problem to certain extent, however that can come at the cost of high rejection rate.
+We investigated the performance of cloud filtering with different threshold values.
+Fig.~\ref{fig:filtering_thresholds} shows the average errors obtained from different filtering thresholds and the corresponding percentage of data omitted.
+Lowering the filtering threshold from 5\,K to 2.5\,K has only a small effect on the filter performance.
+However, a further decrease in the filtering threshold decreases the average error bias significantly, albeit with a high rejection rate.
+For example, for I1V, when all cases with cloud correction greater 0.5\,K are filtered, the mean error bias of the subset is -0.06\,K, MAE is 0.59\,K and the standard deviation is 0.75\,K.
+Though, these values are comparable to the NFCS simulations, the high performance comes at the cost of rejecting more than 30\% of the total cases.
+The high fraction of rejection is a consequence of clear-sky cases being erroneously classified as cloudy.
+Since QRNN gives out NFCS values, choosing an unusually low correction threshold can also classify noisy clear-sky cases as cloudy.
+
+\begin{figure}[t]
+	\includegraphics[width=70mm]{Figures/different_filtering_thresholds.pdf} 
+	\caption{A comparison of the  average bias when pure-filtering approach (QRNN-single) is applied with different thresholds (red curves).
+The corresponding fraction of cases rejected is also shown on the right y-axis(blue curves).}
+	\label{fig:filtering_thresholds}	
+\end{figure}
+
+\subsubsection{Error of best estimate}  
+%
+%t
 \begin{table*}[t]
 	\caption{A comparison of the error statistics from QRNN-single and QRNN-all, when only cases with cloud correction greater than 10\,K are included.
-The fraction of cases forming the dataset are included in the parentheses}
+The number in the parentheses gives the fraction of cases included.}
 	\label{tab:error_statistics_ici_high_cloud_impact}
@@
 
-\begin{figure}[t]
-	\includegraphics[width=70mm]{Figures/different_filtering_thresholds.pdf} 
-	\caption{A comparison of the  average error bias when pure-filtering approach (QRNN-single) is applied with different thresholds (red curves).
-The corresponding fraction of cases rejected is also shown on the right y-axis(blue curves).}
-	\label{fig:filtering_thresholds}	
-\end{figure} 
-To assess the accuracy of QRNN predictions, a point estimate of the posterior distribution is required.
-Usually for Bayesian analysis, the posterior mean or posterior median are selected as point estimates.
-In this study, we assume the posterior median to be the best estimate for the predicted clear-sky value.
-
-The distributions of median value of clear-sky predictions from QRNN-single are shown in Fig.~\ref{fig:PDF_predictions}.
-The distributions of corresponding NFCS simulations are also plotted as reference.
-The three figures correspond to channels: I1V, I2V and I3V.
-These results show that the clear-sky values predicted by QRNN-single have a very good match for the peak of the distributions, but a slight mismatch is evident towards the tails.
-The degree of mismatch is highest for I1V, which incidently also has the largest spread of brightness temperatures in the clear-sky conditions.
-For all three channels, the colder brightness temperatures are under-estimated by QRNN, while a tendency to over-estimate the warmer brightness temperatures is seen for I1V and I2V.
-
-For a quantitative evaluation of QRNN accuracy, the prediction errors are calculated as the deviation of the best estimate to its corresponding NFCS values.
-We calculate the mean bias, MAE (mean absolute error) and standard deviation of the errors.
-The asymmetry of error distributions around their mean is also calculated through the measure of skewness.
-Fisher-Pearson coefficient of skewness is used to calculate the measure of skewness:
-\begin{equation}
-g_1 = \frac{m_3}{m_2^{3/2}}, 
-\end{equation}
-where $m_2$ and $m_3$ are biased sample's second and third central moments.
-
-Fig~\ref{fig:error_distributions} shows the error distributions of predictions for all three channels from QRNN-single.
-The distribution of noise is also plotted for reference.
-Without any cloud impact, the error distributions should follow a Gaussian distribution, and the skewness should be close to zero.
-However the presence of clouds leads to a brightness temperature reduction, and introduces a high negative bias among the deviations.
-Among the three channels, I1V has the highest cloud impact, while I3V has the least.
-After correction of the cloud impact, the resulting error distributions are  symmetric with a sharper peak albeit with a large spread.
-The large spread is due to cases which end up with partial cloud correction and also due to cases where the predicted values are warmer than the simulations.
-For all three channels quite similar behaviour is observed, though I1V has the highest number of cases with residual cloud impact.
-We assume that such cases are associated with high cloud impact.
-To validate our assumption, we implemented a pure-filtering approach.
-In the filtered subset, we removed all cases with QRNN cloud correction greater than 5\,K, and did not correct the remaining cases.
-This can be considered as a pure-filtering approach.
-The results from this subset are also displayed in the figure (red curve).
-For all three channels, the right side follows measurement noise, as expected, but the left side has substantial cases with small cloud impact which pass through the filter.
-However, since the spread of filtered dataset is smaller than the corrected one, it confirms our assumption that most of the partially corrected cases have high cloud impact.
-On the other hand, if all the predicted cases with correction less than 5\,K (Predicted (5\,K) in the figure) are considered, the resulting error distributions are quite close to the measurement noise, except for I1V, where few cases with residual cloud impact can still be seen.
-
-The error metrics corresponding to the error distributions described above are provided in Table~\ref{tab:error_statistics_ici}.
-The average bias in channel I1V measurements is -1.88\,K, which reduces to -0.32\,K with pure-filtering.
-However, when the complete dataset is corrected, the bias is only -0.06\,K and the standard deviation is only 0.98\,K in comparison to 8.84\,K in the measurements.
-The prediction accuracy of QRNN is further higher when filtering is made on the corrected data.
+The QRNN prediction accuracy is estimated by computing the deviation of the best estimate to its corresponding NFCS value (Fig.~\ref{fig:error_distributions}).
+The predicted values have a symmetric distributions albeit with a large spread.
+The large spread on the left is due to cases which end up with incomplete cloud correction, while spread on the right is from cases where the predicted values are warmer than the simulations.
+For all three channels, quite similar behaviour is observed, though I1V has the most cases with residual cloud impact.
+If the predicted cases with correction more than 5\,K are rejected, the resulting error distributions fit the measurement noise, except for I1V, where cases with residual cloud impact introduces a negative bias.
+
+For a quantitative assessment of the errors, we calculated the error metrics described in Sect.~\ref{sec:cloud_filtering} and the results are displayed in Table~\ref{tab:error_statistics_ici}.
+The average bias in I1V measurements is -1.88\,K, which reduces to -0.06\,K after cloud correction.
+The corresponding standard deviation is 0.98\,K in comparison to 8.84\,K in the measurements.
+The prediction accuracy of QRNN is further higher when filtering is made on the predictions.
 In this case, the residual bias is only -0.04\,K, and the standard deviation is 0.73\,K, which is in fact of the order of measurement noise (0.80\,K).
-This high accuracy is achieved by filtering just 6.1\% of the data.
-This indicates that though a pure-filtering approach can prove as a reliable procedure for removing cases with high cloud impact, it is important to correct cases with relatively low cloud impact.
-
-Similar results are seen for channel I2V, though a better performance of QRNN is observed.
+Similar results are seen for I2V, though a better performance of QRNN is observed.
 In I2V, the measurement bias is -1.04\,K which reduces to -0.01\,K after correction.
-The MAE also reduces from 1.52\,K to 0.52\,K.
-Removing cases with correction greater than 5\,K from the corrected dataset removes only 3.7\% of the data but reduces the absolute error to 0.46\,K and the bias to 0\,K.
+The MAE reduces from 1.52\,K to 0.52\,K.
+Removing cases with correction greater than 5\,K from the predictions removes 3.7\% of the data and reduces the absolute error to 0.46\,K and the bias to 0\,K.
 The standard deviation of the resulting dataset is only 0.59\,K as compared to 0.80\,K from noise.
 The reduction in the variability is also evident in the Fig~\ref{fig:error_distributions}, where the peak of the predicted distributions is sharper.
-
 In comparison to I1V and I2V, I3V has the lowest fraction of the measurements with significant cloud impact.
-The bias in the measurements is only -0.63\,K in comparison to -1.88 in I1V.
-Pure-filtering removes 2.3\% of the total cases as cloudy, reduces the bias to 0.18\,K, and the standard deviation to 0.91\,K but nonetheless, cannot provide a complete cloud filtering.
-After correction of all the cases in the test dataset, the bias reduces to 0.01\,K and the MAE to 0.51\,K from 1.15\,K.
-Including correction along with filtering reduces the bias further down to 0.02\,K and standard deviation to 0.59\,K, which is again smaller than that of noise(0.80\,K).
-
-Overall for all three channels, the accuracy of the predicted dataset with correction greater than 5\,K removed, gives the best accuracy and lowest variability.
-Although similar results can also be achieved by selecting a lower filtering threshold, it comes at the cost of rejecting higher fraction of cases.
-Fig~\ref{fig:filtering_thresholds} shows the average errors obtained from different filtering thresholds and the corresponding percentage of data omitted (blue curve) for all three channels.
-Lowering the filtering threshold from 5\,K to 2.5\,K has only a small effect on improving the accuracy, however with further lower threshold values, accuracy of the order of ``predicted(5\,K)'' can be achieved, nonetheless with a high rejection.
-For example, for I1V, when all cases with cloud correction greater 0.5\,K are filtered, the average error bias of the subset is -0.06\,K, the MAE is 0.59\,K and the standard deviation is 0.75\,K.
-Though, these values are comparable to predicted cases with 5\,K filter, they come at the cost of rejecting more than 30\% of the total cases.
-The unusually high rejection rate indicates that using lower filtering thresholds elevates the risk of erroneously removing clear-sky cases.
+In the predicted dataset, the bias is 0.01\,K and the MAE is 0.51\,K in comparison to 1.15\,K  in the measurements.
+Including correction along with filtering reduces the MAE further down to 0.47\,K and standard deviation to 0.59\,K, which is again smaller than that of noise(0.80\,K).
 
 Next, we describe the results from QRNN-all.
-In this model, all 183\,GHz channels along with other sub-mm channels were included while training.
-This model was designed to identify if other channels of the same frequency can provide auxiliary information in the training process.
-The results from QRNN-all all are also provided in the last columns of Table~\ref{tab:error_statistics_ici}.
-For channel I1V, using additional information from other two 183\,GHz channels has no impact on pure-filtering approach but a slight positive impact on the predictions.
-If predictions over the entire testing set are considered, the average bias in QRNN-all and QRNN-single is same, but the mean absolute errors in QRNN-all are almost 4.5\% less than QRNN-single, suggesting a lower spread of errors.
-Having said that, in comparison to QRNN-single, the prediction accuracy has no significant improvement when all cases with correction larger than 5\,K are rejected.
-Thus, information from other 183\,GHz channels only assists in slightly improving the correctness of cases associated with high cloud impact in I1V.
-The accuracy of other cases remains unaltered.
-In order to quantify the positive effect on cases with high cloud impact, we computed the error statistics for all cases with correction greater than 15\,K.
-The results are shown in Table~\ref{tab:error_statistics_ici_high_cloud_impact}.
-For I1V, only 4\% of the cases have cloud correction greater than 10\,K, but have lowest prediction accuracy.
-Using QRNN-all improves the overall error bias from -0.53\,K to -0.38\,K and the standard deviation from 3.13\% to 2.63\%,but still is unsuccessful in removing the cloud impact completely.
-Lower representation of cases with high cloud impact in the training set could be one of the reasons for this shortcoming.
-Due to low fraction of such cases, QRNN cannot learn to predict the clear-sky values accurately.
-
-For channel I2V, the predictions from QRNN-all have a slightly worse average error bias than QRNN-single, yet a significant improvement in the prediction accuracy is evident.
-For the complete testing set, the MAE is 0.44\,K in comparison to 0.52\,K from QRNN-single, showing an improvement of almost 15\%.
-Similarly the standard deviation of the errors is only 0.67\,K, notably smaller than the measurement noise.
-Additionally, when the  corrected dataset is filtered with 5\,K threshold, the accuracy is even better.
+In this model, all 183\,GHz channels along with other sub-mm channels are included while training.
+This model is designed to identify if other channels of the same frequency can provide auxiliary information in the training process.
+The results from QRNN-all all are provided in the last columns of Table~\ref{tab:error_statistics_ici}.
+For I1V, using additional information from other two 183\,GHz channels has only a slight positive impact on the predictions.
+In the prediction dataset, the average bias for QRNN-all and QRNN-single is identical, but the MAE in QRNN-all are almost 4.5\% less than QRNN-single.
+However when the predictions are filtered with 5\,K threshold, the performance of both models is quite similar.
+This indicates that information from other channels only assists in slightly improving the correctness of cases associated with high cloud impact in I1V.
+The predictions of cases with low cloud impact have no significant gain.
+For I2V, the predictions from QRNN-all have a slightly worse average error bias than QRNN-single, yet a significant improvement in the prediction accuracy is observed.
+When all predictions are considered, the MAE is 0.44\,K in comparison to 0.52\,K from QRNN-single, showing an improvement of almost 15\%.
+Similarly the standard deviation of the errors is only 0.67\,K, which is notably smaller than the measurement noise.
+Additionally, when the predicted dataset is filtered with 5\,K threshold, the accuracy is even better.
 The mean absolute bias reduces to 0.39\,K and standard deviation to 0.50\,K.
-This implies that cases pertaining to clear-sky conditions and relatively low cloud impact benefit the most from the auxiliary information.
-This is in contrast to channel I1V, where accuracy of such cases remained unaffected.
-However, for cases with cloud impact greater than 10\,K a likewise improvement is observed (Table~\ref{tab:error_statistics_ici_high_cloud_impact}).
-Again both QRNN-all and QRNN-single are only partially successful in removing the cloud impact, but QRNN-all had a better performance among the two.
+This implies that cases pertaining to clear-sky conditions and relatively low/no cloud impact benefit the most from the auxiliary information.
+This is in contrast to I1V, where accuracy of such cases remained unaffected.
+For I3V, the performance of QRNN-all is comparable to that for I2V.
+For I3V, the MAE in QRNN-all is 0.46\,K compared to 0.51\,K from QRNN-single, and the corresponding standard deviations are 0.68\,K and 0.77\,K.
+Removing the cases with cloud impact greater than 5\,K from the predictions, leads to no change in the average bias, but the MAE and standard deviation reduce by almost  8\% and 20\% respectively.
+This is again a consequence of improved prediction accuracy of cases with low/no cloud impact.
+
+In order to quantify the positive effect of QRNN-all on cases with high cloud impact, the error statistics for all cases with cloud correction greater than 10\,K were computed (Table~\ref{tab:error_statistics_ici_high_cloud_impact}).
+For I1V, only 4\% of the cases have cloud correction greater than 10\,K, but very high prediction errors.
+QRNN-all improves the overall error bias from -0.53\,K to -0.38\,K and the standard deviation from 3.13\% to 2.63\%, but is unsuccessful in removing the cloud impact completely.
+A likewise improvement is also observed for I2V.
+Despite both models being only partially successful in removing the cloud impact, QRNN-all has a better performance among the two.
 For I2V, such cases form only 2.25\% of the testing dataset.
 Predictions from QRNN-all have slightly worse values for average error bias, but both MAE and standard deviation improve by over 20\%.
-
-For channel I3V, the performance of QRNN-all is comparable to that for I2V.
-For I3V, the mean absolute bias in QRNN-all is 0.46\,K compared to 0.51\,K from QRNN-single, and the corresponding standard deviations are 0.68\,K and 0.77\,K.
-Removing the cases with cloud impact greater than 5\,K from the predicted dataset, leads to no change in the average bias, but the mean absolute error and standard deviation reduce by almost  8\% and 20\% respectively.
-Again suggesting that cases with low/no cloud impact have a significant contribution in improving the accuracy of predictions.
-Cases with high cloud impact, though very low in number, also gained positively from the auxiliary information.
+For I3V also, the cases with high cloud impact, though very low in number, also gained positively from the auxiliary information.
+
+The results show that both QRNN-single and QRNN-all are successful in predicting NFCS values for I2V, and I2V, and partially successful for I1V.
+The resulting error distributions are symmetric with low bias and standard deviation.
+For I2V and I3V, the variability of errors is even smaller than the noise.
+This is a consequence of predictions for cases associated with clear sky conditions.
+QRNN predictions are weighted mean of measurements between channels.
+For clear-sky conditions, the averaging of cases observed by multiple channels can cancel out the noise.
+The cancelling of noise is stronger in QRNN-all as all 183\,GHz channels are used concurrently.
+The lower prediction accuracy of I1V can be explained by the fact that it is the outermost 183\,GHz channel and the other sub-mm channels cannot provide a full coverage for the hydrometeor impact in I1V.
+Depending upon the atmospheric scenarios, there is always a portion of data detected by I1V, but never seen by any other channel.
+Though such cases are few, QRNN cannot learn to predict the clear-sky values accurately for cases which lie outside the coverage area.
+Besides this, lower representation of high cloud impact cases in the training set also affects QRNN accuracy.
 
@@
 	\caption{The prediction uncertainty  for I2V  with respect to quantiles for randomly selected 1500 cases.
-The black line represents the uncertainty if underlying distribution is purely Gaussian with mean 270\,K and standard deviation 0.60\,K.
+The black line represents a hypothetical Gaussian distribution of $270\pm0.60$\,K, which is of the order of standard deviation for I2V predictions (see Table~\ref{tab:error_statistics_ici}).
 The results are from QRNN-single.}
@@
 	\includegraphics[height = 70mm]{Figures/calibration_QRNN_I1V.pdf}	
-	\caption{Calibration of the prediction intervals obtained from QRNN-simple and QRNN-all for channel I1V. }
+	\caption{Calibration of the prediction intervals obtained from QRNN-single and QRNN-all for I1V. }
 	\label{fig:calibration_I1V}	
@@
 
-In order to understand how QRNN predicted uncertainties behave, we calculated the deviations of predictions at different quantiles from the median value.
-Fig.~\ref{fig:prediction_uncertainty_I2V} displays the prediction uncertainty in I2V for different quantiles.
-The different lines represent 1500 randomly chosen cases, while the black line represents the uncertainty in a hypothetical Gaussian distribution of $270\pm0.60$\,K, which is of the order of standard deviation for I2V predictions (see Table~\ref{tab:error_statistics_ici}).
-The uncertainty estimates from different cases show a very high degree of variability.
+In order to understand how QRNN predicted uncertainties behave, we calculated the deviations of predictions at different quantiles from the median value (Fig.~\ref{fig:prediction_uncertainty_I2V}).
+The large spread in the uncertainty estimates indicates that QRNN can successfully represent uncertainties for each case individually, rather than expressing them as a single measure for all cases.
+In the latter case, the uncertainty estimates for all cases would be concentrated along a narrow interval.
 Among the cases associated with low uncertainty, the distribution is quite symmetric along the median value.
-Such cases are concentrated along a narrow interval and lie close to the black curve.
-For such cases, the uncertainties are also equally spaced for $1\sigma$, $2\sigma$ and so on, suggesting that a Gaussian distribution model could be used to express the underlying uncertainty of such cases.
-However, cases with high uncertainty have a larger spread, and are no longer equally spaced.
-For these cases, the prediction uncertainties have a larger spread over positive quantiles than negative quantiles.
-The high variability indicates that QRNN can successfully represent uncertainties for each case individually, rather than expressing them as a single measure for all cases.
-In the latter case, the uncertainty estimates for all cases would be concentrated along a narrow interval.
-
-For further analysis of the uncertainty estimates, we compare the distributions of the predictions from QRNN with the a priori distribution.
+These cases are concentrated along a narrow interval and lie close to the black curve.
+For such cases, the uncertainties are also equally spaced for $1\sigma$, $2\sigma$ and $3\sigma$, suggesting that a Gaussian distribution model could be used to express their underlying uncertainty.
+However, the cases with high uncertainty are unequally spaced and have a larger spread over positive quantiles than negative quantiles.
+
+For further analysis, we compared the distribution of predictions from QRNN with the a priori distribution.
 In a model with high performance, the posterior distribution of the predictions should be similar to the a priori distribution of training dataset.
-A straightforward way to compare the two distribution is to plot the frequency of predictions and frequency of true value in different prediction intervals.
+A straightforward way to compare the two distribution is to plot the frequency of predictions and frequency of the true value in different prediction intervals.
 This is also commonly known as calibration plot.
-Fig.~\ref{fig:calibration_I1V} shows the calibration of the prediction intervals on the test dataset for channel I1V.
-Results from both QRNN-single and QRNN-all are shown.
-The calibration of predictions with correction greater than 10\,K is also shown.
+Fig.~\ref{fig:calibration_I1V} shows the calibration of the prediction intervals on the test dataset for I1V.
 For both QRNN models, the predictions for the complete test dataset are well calibrated and follow the y=x line.
 This shows that the training and test datasets come from the same a priori distribution.
-On the other hand, when cases with  cloud correction greater than 10\,K are considered, for both models, the predictions in all the intervals are poorly calibrated.
+On the other hand, when only the cases with  cloud correction greater than 10\,K are considered, for both models, the predictions in all the intervals are poorly calibrated.
 In this case the calibration curve lies below the y=x line, indicating that the predicted intervals are too narrow, or the uncertainty is underestimated.
-In the test and training datasets, the clear-sky cases and cases with low cloud impact dominate the a priori distribution, and cases with high cloud impact fail to get an adequate representation.
-The a priori distribution of such cases is different from the clear-sky cases, thus the corresponding predictions had poor calibrations.
+In the test and training datasets, the clear-sky cases and cases with low cloud impact dominate the a priori distribution.
+The a priori distribution of cloudy cases is significantly different to the clear-sky cases, thus leading to poorly calibrated predictions for former.
 We also plotted the calibration curves for I2V and I3V (figure not shown).
@@
 Lastly, we investigated that if the uncertainty estimates given by QRNN are representative of prediction errors.
-We divided the 94\% confidence interval ($\pm2\sigma$ ) into three bins and estimated the prediction error distribution for each.
-Fig.~\ref{fig:error_distribution_uncertainty_bins} shows the prediction error distributions for I1V, I2V and I3V.
-These results are from QRNN-single.
+We divided the 94\% confidence interval ($\pm2\sigma$ ) into three bins and estimated the prediction error distribution for each (Fig.~\ref{fig:error_distribution_uncertainty_bins}).
 Similar results were also obtained for QRNN-all (figure not shown).
@@
 With increase in the uncertainty, frequency of cases with high accuracy decreases and the distributions spread out symmetrically to higher errors.
-Poor predictions occur more frequently when uncertainty is high, although cases with accurate predictions yet high uncertainty are also present.
-In spite of individual variations in the error distributions of each channel, predictions and their corresponding uncertainties followed the same relationship: This suggests that QRNN can reliably represent the quality of predictions through their uncertainty estimates.
+Poor predictions occur more frequently when uncertainty is high.
+Cases with accurate predictions yet high uncertainty are also present.
+In spite of individual variations in the error distributions for each channel, predictions and their corresponding uncertainties followed the same relationship.
+This suggests that QRNN can reliably represent the quality of predictions through their uncertainty estimates.
 
@@
 In this section, we present results from QRNN when applied to MWI channels.
-Applicability and sensitivity of QRNN over different combinations of training datasets, is investigated.
-Firstly, we use combinations of data from all five 183\,GHz channels for ``self'' cloud filtering/correction (QRNN-mwi).
-No additional data is used.
-In the second model, we compare the performance of QRNN for MWI channels, if sub-mm channels from ICI are used.
-In this case, we assume that data from both channels is mapped to a common foorprint size.
+Firstly, we discuss results when all 183\,GHz MWI channels are used for ``self'' cloud filtering/correction (QRNN-mwi).
+We also describe the performance of QRNN when sub-mm channels from ICI are used to train MWI channels.
 \subsubsection{MWI alone}
@@
 \begin{table*}[t]
-	\caption{Error statistics for predictions from QRNN-mwi.
-All channels of MWI are used to train for each 183\,GHz channel.
-The labels Filtered(5\,K), Predicted(All) and Predicted(5\,K) are same as described in Table~\ref{tab:error_statistics_ici}}
+	\caption{Error statistics for predictions from QRNN-mwi. The labels Filtered(5\,K), Predicted(All) and Predicted(5\,K) are same as described in Table~\ref{tab:error_statistics_ici}}
 	\label{tab:statistics_mwi-alone}
@@
 %t
+\todo{Incomplete}
+
 \begin{table*}[t]
@@
 Since we assume that all channels are remapped to a common footprint, channels MWI-14, MWI-17 and MWI-18 are virtually identical to I1V, I2V and I3V, and thus results for them are not shown separately.
-Table~\ref{tab:statistics_mwi} shows the metrics from error distributions for MWI-15 and MWI-16 predictions.
-Results from only QRNN-single are shown.
-
+
+Table~\ref{tab:statistics_mwi} shows the error metrics of NFCS predictions from simulations.
 For MWI-15, the average deviations of measurements from NFCS values is -1.23\,K, and the MAE is 1.70\,K.
 When all cases are corrected, the resulting average bias is -0.04\,K and the MAE reduces to 0.56\,K.
-If only pure-filtering is made, the average bias is -0.26\,K and MAE is 0.76\,K, suggesting that a significant number of cases non-zero cloud impact pass through.
+If only pure-filtering is made, the average bias is -0.26\,K and MAE is 0.76\,K, suggesting that a significant number of cases with non-zero cloud impact pass through.
 As seen for ICI, best results are obtained  when filtering is made on the corrected dataset.
@@
 
+The uncertainty
+
+These results show that even though ICI and MWI are two different instruments, their channels can benefit from each other.
+Although re-mapping to a common footprint would slighly compromise the data quality, a high accuracy achieved with simulations suggests that the QRNN would work well even when actual measurements are available.
+
 \subsection{AWS}
+%
+%t
+\begin{table*}[t]
+	\caption{Same as Table~\ref{tab:error_statistics_ici}, but for channels AWS channels. Results are from QRNN-single. }
+	\label{tab:statistics_qrnn_aws}
+	\begin{tabular}{llrr|rrr}
+		\tophline
+		&&\multicolumn{2}{c|}{Simulations}& \multicolumn{3}{c}{QRNN-single} \\
+		\cline{3-7}
+		%		\hline
+		&&   Clear-sky &   All-sky &  Filtered(5\,K) & Predicted & Predicted(5\,K) \\
+		\middlehline
+		AWS-32  &Bias     & -0.00 & -1.34 & -0.29 & -0.04 & -0.03 \\
+		&MAE       &  0.36 &  1.58 &  0.54 &  0.62 &  0.53 \\
+		&STD      &  0.45 &  5.91 &  0.92 &  0.98 &  0.73 \\
+		&skewness & -0.03 & -7.48 & -3.80 & -1.49 & -1.59 \\
+		\middlehline
+		AWS-33	&Bias     & -0.01 & -0.98 & -0.25 & 0.02 &  0.01 \\
+		&MAE      &  0.36 &  1.23 &  0.51 & 0.49 &  0.42 \\
+		&STD      &  0.45 &  4.70 &  0.80 & 0.76 &  0.56 \\
+		&skewness & -0.00 & -8.78 & -2.92 & 0.04 & -0.79 \\
+
+		\middlehline
+		AWS-34	&Bias     &  0.00 &  -0.68 & -0.20 &  0.02 &  0.01 \\
+		&MAE      &  0.51 &   1.07 &  0.61 &  0.51 &  0.46 \\
+		&STD      &  0.64 &   3.67 &  0.84 &  0.75 &  0.60 \\
+		&skewness & -0.00 & -10.32 & -1.70 & -0.55 & -0.59 \\
+		\middlehline
+		AWS-35	&Bias     &  0.00 &  -0.43 & -0.15 & 0.01 &  0.00 \\
+		&MAE      &  0.50 &   0.84 &  0.57 & 0.48 &  0.44 \\
+		&STD      &  0.63 &   2.65 &  0.77 & 0.71 &  0.57 \\
+		&skewness & -0.01 & -12.49 & -1.34 & 0.40 & -0.29 \\
+		\middlehline
+		AWS-36  &Bias     & 0.00 &  -0.28 & -0.11 &  0.03 &  0.03 \\
+		&MAE      & 0.70 &   0.90 &  0.74 &  0.63 &  0.60 \\
+		&STD      & 0.88 &   2.06 &  0.96 &  0.86 &  0.76 \\
+		&skewness & 0.01 & -11.80 & -0.53 & -0.35 & -0.20 \\
+		\bottomhline				
+	\end{tabular}
+	\belowtable{} % Table Footnotes
+\end{table*}
+%f
+\begin{figure}[t]
+	\includegraphics[width = 80mm]{Figures/cloud_impact_uncertainty_AWS.pdf}	
+	\caption{The average confidence intervals (2$\sigma$) plotted against the magnitude of cloud impact for all AWS channels.}
+	\label{fig:uncertainty_cloud_impact}	
+\end{figure}
+
 In this section, we investigate the possibility of using only channels around 325\,GHz for cloud correction at 183\,GHz.
-This special case of utilising only 325\,GHz channel can be relevant for smaller satellite missions like Artic Weather Satellite (AWS) where higher sub-mm channels are not available.
+This special case of utilising only 325\,GHz channel can be relevant for smaller satellite missions like AWS where higher sub-mm channels are not available.
 
@@
 
-Overall the results demonstrate that QRNN is successful in predicting the clear-sky noise-free data for AWS-33, AWS-34, AWS-35 and AWS-36 and partially for AWS-32.
+Overall the results demonstrate that QRNN is successful in predicting the NFCS data for AWS-33, AWS-34, AWS-35 and AWS-36 and partially for AWS-32.
 The prediction error distributions are symmetric with low bias and standard deviation.
@@
 Excluding such cases decreases the variability in the predictions and in fact the spread of errors for AWS-34, AWS-35 and AWS-36 is smaller than noise.
-Removal of cases with high cloud impact, increases the representation of cases in cloud-free conditions, and for such cases, QRNN predictions can be seen as a weighted mean between the two ``super-channels''.
+Removal of cases with high cloud impact, increases the representation of cases in cloud-free conditions, and for such cases, QRNN predictions can be seen as a weighted mean between the two channels.
 Since the noise in the two channels are stationary and uncorrelated, the predictions benefit from the additional information, but the noise component tends to cancel out.
@@
 Since 325\,GHz cannot provide a full coverage for hydrometeor impact in AWS-32, the testing data will inevitably contain cases for which QRNN has not trained for.
-Prediction for such \textit{out-of-distribution} cases would be inaccurate and highly uncertain.
+Prediction for such cases would be inaccurate and highly uncertain.
 In such cases, the predictions should be used with caution.
 
-In order to analyse the performance of QRNN with task difficulty, the interrelation between the uncertainty estimates and cloud impact was investigated.
-Here we assume that cloud impact is representative of task difficulty.
+In order to analyse the performance of QRNN with respect to uncertainty, the interrelation between the uncertainty estimates and cloud impact was investigated.
 Fig~\ref{fig:uncertainty_cloud_impact} displays the plot between mean uncertainty estimates for $2\sigma$ confidence interval and the cloud impact.
@@
 
-\begin{table*}[t]
-	\caption{Bias, mean absolute error(MAE), standard deviation(STD), and measure of skewness(Skewness) for error distributions of predictions AWS channels.
-Results are from QRNN-single.
-The label ``All'' refers to the complete dataset, while in ``Filtered'', cases with cases with cloud correction greater than 5\,K(15\,K) are excluded from statistics.
-The fraction of cases removed by this filter are given in parentheses.}
-	\label{tab:statistics_qrnn_aws}
-	\begin{tabular}{llrr|rrr}
-		\tophline
-		&&\multicolumn{2}{c|}{Simulations}& \multicolumn{3}{c}{QRNN-single} \\
-		\cline{3-7}
-		%		\hline
-		&&   Clear-sky &   All-sky &   		 All &   Filtered(5K)& Filtered(15K) \\
-		\middlehline
-AWS-32    &Bias     &   -0.00 &         -1.34 &           -0.08 &       		-0.07(5.30\%) & -0.08(2.50\%) \\
-          &MAE      &    0.36 &          1.58 &            0.62 &        		 0.53 		  &	0.57	\\
-          &STD      &    0.45 &          5.91 &            1.00 &        		 0.74 		  & 0.85\\
-          &Skewness &    0.02 &         -7.48 &           -1.52 &       		-1.63 		  & -2.01\\
-		\middlehline
-AWS-33	  &Bias     &   -0.00 &         -0.98 &            0.01 &                 0.00(4.08\%)& 0.00(1.75\%)\\
-		  &MAE      &    0.36 &          1.23 &            0.50 &                 0.43 	      & 0.46\\
-		  &STD      &    0.45 &          4.70 &            0.77 &                 0.57 	      & 0.64\\
-		  &Skewness &    0.01 &         -8.76 &           -0.40 &                -0.90  	  & -1.00\\
-
-		\middlehline
-AWS-34	  &Bias    &    0.00 &         -0.68 &            0.02 &                0.01(3.02\%)& 0.01(1.11\%) \\
-		  &MAE      &    0.50 &          1.08 &            0.53 &                 0.47 		 & 0.50\\
-		  &STD      &    0.63 &          3.69 &            0.78 &                 0.62 		 & 0.70\\
-		  &Skewness &    0.02 &        -10.30 &           -0.34 &                -0.49 		 &-0.76	\\
-		 \middlehline
-AWS-35	 & Bias     &    0.00 &         -0.42 &            0.01 &                 0.01(1.92\%) & 0.01(0.70\%) \\
-		 &MAE       &    0.50 &          0.83 &            0.50 &                 0.47 		   & 0.49\\
-		 &STD       &    0.63 &          2.65 &            0.71 &                 0.60         & 0.65\\
-		 &Skewness  &    0.01 &        -12.45 &           -0.15 &                -0.15         &-0.26\\
-		 \middlehline
-AWS-36   &Bias     &    0.00 &         -0.27 &            0.02 &                 0.02(1.30\%) & 0.02(0.31\%)\\
-		 &MAE      &    0.70 &          0.90 &            0.67 &                 0.64 		  & 0.06\\
-		 &STD      &    0.88 &          2.06 &            0.91 &                 0.81 		  &0.85\\
-		 &Skewness &   -0.01 &        -12.00 &           -0.51 &                -0.15 		  &-0.12\\	 
-		\bottomhline				
-	\end{tabular}
-	\belowtable{} % Table Footnotes
-\end{table*}
-%f
-\begin{figure}[t]
-	\includegraphics[width = 80mm]{Figures/cloud_impact_uncertainty_AWS.pdf}	
-	\caption{The average confidence intervals (2$\sigma$) plotted against the magnitude of cloud impact for all AWS channels.}
-	\label{fig:uncertainty_cloud_impact}	
-\end{figure}
-\section{Discussion}
 \section{Outlook and Conclusions}  %% \conclusions[modified heading if necessary]
+
+\newpage
+
+\section*{Outline of sectioning}
+
+2 Data and methods
+
+2.1 Satellite sensors
+
+2.1.1 Ice Cloud Imager (ICI)
+
+2.1.2 Microwave Imager (MWI)
+
+2.1.3 Arctic Weather Satellite (AWS)
+
+2.2 Quantile Regression Neural Network (QRNN)
+
+2.2.1 Theory
+
+2.2.2 Evaluation metrics
+
+2.3 Simulations
+
+2.3.1 Input data
+
+2.3.2 Simulation setup
+
+2.3.3 Produced dataset
+(If diifers between ICI, MWI and AWS, clarify this)
+
+\noindent 3 Results
+
+Short recap of aim of correction. We also use the correction as a filter, using
+a threshold on the correction. We use 5K (?) threshold as example.
+
+3.1 QRNN network configurations and training
+
+3.2 ICI
+
+3.2.1 Example results
+
+Show a few estimated posterior distributions (one figure) and distribution of
+predicted values (Fig 2)
+
+3.2.2 Error of best estimate
+
+3.2.3 Predicted uncertainty
+
+3.3 MWI
+
+3.3.1 MWI alone
+
+Just 183 GHz channels, original noise
+
+3.3.2 MWI and ICI
+
+As in present version
+
+3.4 AWS
+
+\noindent 4 Discussion
+
+\noindent 5 Conclusion
+
+\newpage
 

### 2020-09-18 Article/ici_submm_cloudcorr.tex
Minor work on Introduction.

@@
 with strong limitations imposed by clouds. To be able to also sense humidity
-inside and below clouds weather satellites are since some time equipped with
+inside and below clouds, weather satellites are since some time equipped with
 channels around 183\,GHz. Today such channels are part of several sensors, such
@@
 The main motivation for introducing 183\,GHz channels in operational sensors is
-numerical weather prediction (NWP). Usage of microwave data by ``all-sky''
-assimilation is growing \citep{geer2017growing}, but 183\,GHz data are still
-mainly used in a clear sky fashion \citep{geer2018all}. The later is
-particularly true in NWP of regional scope, all-sky assimilation of 183\,GHz at
-many national weather agencies will likely not be reached in many years. The
-cloud filtering in NWP differs between centres. One approach is to make use of
-a ``scattering index'' \citep{bennartz2002precipitation}, based on the
+numerical weather prediction (NWP). Usage of passive microwave data by
+``all-sky'' assimilation in global NWP is growing in \citep{geer2017growing},
+but 183\,GHz data are still mainly used in a clear sky fashion
+\citep{geer2018all}. The later is particularly true in NWP of regional scope
+\citep{gustafsson2018survey}, all-sky assimilation of 183\,GHz at many national
+weather agencies will likely not be reached in many years. Anyhow, the cloud
+filtering applied differs between NWP centres. One approach is to make use of a
+``scattering index'' \citep{bennartz2002precipitation}, based on the
 observations alone. Today, likely more common is to use ``observation minus
@@
 apply a very strict filtering, but this will result in that a high fraction of
-actually clear-sky values will be rejected \todo{(Reka or better reference)},
-i.e.\ an important loss of useful data.
+actually clear-sky values will be rejected, i.e.\ an important loss of useful
+data.
 
@@
 A maybe less obvious problem is the uncertainty to assign to the filtered
-values. To our best knowledge, in best case estimates of mean and worst case
-errors are provided. Some cases with relatively high cloud impact will likely be
-missed, while most cases are clear sky from start. As the remaining cloudy
-cases can cause significant biases, the likely solution is to apply a quite
-conservative (high) error estimate. However, this will unnecessary downgrade
-the value of the truly clear sky cases and the observations are used in a
-non-optimal manner.
+values. To our best knowledge, so far only estimates of mean and worst case
+errors have been provided. Some cases with relatively high cloud impact will
+likely be missed, while most cases are clear sky from start. As the remaining
+cloudy cases can cause significant biases, the likely solution is to apply a
+quite conservative (high) error estimate. However, this will unnecessary
+downgrade the value of the truly clear sky cases and the observations are used
+in a non-optimal manner.
 
@@
 
-The estimation of NFSC values makes use of a special type of machine learning,
+The estimation of NFCS values makes use of a special type of machine learning,
 denoted as Quantile Regression Neural Network (QRNN,

### 2020-09-18 Article/ici_submm_cloudcorr.tex
Removed temporary outline of sections.

@@
 Imager (ICI, \citet{eriksson:towar:20}), but likely also be included in several
-smaller missions (such as AWS presented below). The focus on ICI is motivated
-by several reasons. The true potentail of the QRNN cloud correction approach is
-likely not revealed if tested on existing data and applying ICI data for cloud
-filtering has not earlier been discussed. It is also argued that the cloud
-correction makes it possible to make good use of ICI data already in clear-sky
-assimilation, a fact that should speed up the use of this novel data source.
+smaller missions (such as AWS, presented below). \todo{Explain what sub-mm can
+  do}.}
+
+The focus on ICI is motivated by several reasons. The true potentail of the
+QRNN cloud correction approach is likely not revealed if tested on existing
+data and applying ICI data for cloud filtering has not earlier been discussed.
+It is also argued that the cloud correction makes it possible to make good use
+of ICI data already in clear-sky assimilation, a fact that should speed up the
+use of this novel data source.
 
@@
 
-\section{Outlook and Conclusions}  %% \conclusions[modified heading if necessary]
-
-\newpage
-
-\section*{Outline of sectioning}
-
-2 Data and methods
-
-2.1 Satellite sensors
-
-2.1.1 Ice Cloud Imager (ICI)
-
-2.1.2 Microwave Imager (MWI)
-
-2.1.3 Arctic Weather Satellite (AWS)
-
-2.2 Quantile Regression Neural Network (QRNN)
-
-2.2.1 Theory
-
-2.2.2 Evaluation metrics
-
-2.3 Simulations
-
-2.3.1 Input data
-
-2.3.2 Simulation setup
-
-2.3.3 Produced dataset
-(If diifers between ICI, MWI and AWS, clarify this)
-
-\noindent 3 Results
-
-Short recap of aim of correction. We also use the correction as a filter, using
-a threshold on the correction. We use 5K (?) threshold as example.
-
-3.1 QRNN network configurations and training
-
-3.2 ICI
-
-3.2.1 Example results
-
-Show a few estimated posterior distributions (one figure) and distribution of
-predicted values (Fig 2)
-
-3.2.2 Error of best estimate
-
-3.2.3 Predicted uncertainty
-
-3.3 MWI
-
-3.3.1 MWI alone
-
-Just 183 GHz channels, original noise
-
-3.3.2 MWI and ICI
-
-As in present version
-
-3.4 AWS
-
-\noindent 4 Discussion
-
-\noindent 5 Conclusion
-
-\newpage
+\section{Conclusion and outlook}  %% \conclusions[modified heading if necessary]
+%
+To be written \dots
 

### 2020-09-19 Article/ici_submm_cloudcorr.tex
Work on Section 2.

@@
 \newcommand{\todo}[1]{{\color{red} #1}}
+\newcommand{\ynfcs}{$y_\text{NFCS}}
+\newcommand{\y}{\vec{y}}
 
@@
 smaller missions (such as AWS, presented below). \todo{Explain what sub-mm can
-  do}.}
+  do}.
 
@@
 
-\subsection{QRNN}
-%
-The neural network training is a process of learning to predict the outputs {$y_i$} from inputs {$x_i$} through a series of learnable transformations.
-While training, neural networks seek to minimise the model error through a loss function.
-The choice of the loss function depends on the predictive problem.
-When a neural network is trained to minimise the mean of the quantile loss function to predict the quantiles of the distribution, it is called a Quantile Regression Neural Network (QRNN).
-
-\subsubsection{Theory}
-
-\subsubsection{Evaluation metrics}
-
-Quantile loss function
-
-CRPS
-
-\subsubsection{QRNN implementation}
-\label{sec:qrnn-implementation}
-
-The implementation of QRNN is based on PyTorch, an open source machine learning library \citep{paszke2017automatic}.
-It is developed and available as a part of \textit{typhon:tools for atmospheric research} software package [\todo{developer's version??}].
-
-For this study, we initialize the quantile loss function with quantile fractions $\tau$ = [0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998] to train the neural network to predict the corresponding quantiles $x_{\tau}$ = [$-3\sigma, -2\sigma, -1\sigma, median, 1\sigma, 2\sigma, 3\sigma $].
-QRNN is trained with simulated brightness temperatures from different channels, no other data is included.
-The input channels are variable and are determined by the type of QRNN model used.
-The different QRNN models are described in Sect.~\ref{QRNN_models}.
-
-A custom data augmentation scheme is implemented to build a robust learning network.
-At each training iteration, noise is added to the noise-free inputs according to the measurement uncertainty.
-The target training data is always kept noise free.
-This ensures that the model is exposed to different datasets during the entire training process, and avoids memorisation of training samples.
-The input data is normalized with mean and standard deviation.
-While training, 10\% of the training data is used for validation.
-
-The neural network is trained with an adaptive form of stochastic batch gradient descent.
-During the training process, at each iteration, the loss in the validation dataset in monitored.
-If the validation loss remains stagnant for a certain number of epochs, the training rate is reduced  by a given reduction factor.
-This process is continued till a minimum learning rate is achieved.
-
-A high performing QRNN model also requires tuning of multiple hyper-parameters.
-These parameters determine the structure and the training set-up of the neural network.
-Several of these hyper-parameters are non-learnable, and must be defined before beginning of every training.
-Grid search is one of the most often employed techniques for hyper-parameter tuning.
-In grid search, different combinations of hyper-parameters are selected and for each, the model performance is evaluated.
-The model architecture with the best performance is selected.
-For the structural parameters, usually a grid search over the number of neurons (width) and hidden layers (depth) is performed.
-The model is trained for multiple values of layer widths and hidden layers, and the best configuration is selected by evaluating the predictions over validation dataset.
-Similarly, the training process is optimized by performing a grid search different training parameters such as : batch size, learning rate, number of epochs etc.
-We use quantile loss and CRPS for evaluation of the model performance.
-
+\subsection{Quantile regression neural networks}
+%
+The task that we aim to solve in this study is to predict the NFCS brightness
+temperatures $\ynfcs$ at a given $187\unit{GHz}$ channel from a vector of
+cloud-contaminated observations $\y$. Since the information-content of the
+cloud-contaminated observations is certainly too low to solve this problem
+exactly, a probabilistic formulation is appropriate here. The aim thus becomes
+to predict the conditional distribution $p(\ynfcs | \y)$ of the NFCS brightness
+temperatures $\ynfcs$ given the cloud-contaminated observations $\y$.
+
+As has been shown in \citet{pfreundschuh:aneur:18}, quantile regression neural
+networks (QRNN) can be used to solve these type of problems. Instead of a point
+prediction, as it is typically performed in regression problems, QRNNs learn to
+predict a vector of quantiles, which can be used to approximate the distribution
+of the predicted quantity conditional on the network inputs. Using QRNNs to
+perform probabilistic cloud correction thus not only allows deriving an estimate
+for $\ynfcs$ but also for the error of the corrected observations.
+
+For this application, the predicted percentiles are chosen to be
+$0.2\%, 3\%, 16\%, 50\%, 85\%, 97\%$ and $99.8\%$. For a Gaussian
+distribution with mean $\mu$ and standard deviation $\sigma$ the
+approximately corresponds to $\mu -3\sigma, \mu-2\sigma, \mu-\sigma
+, \mu, \mu + \sigma, \mu + 2\sigma, \mu + 3\sigma$ and thus allows
+estimating the $\pm 1, \pm 2$ and $\pm 3\sigma$ confidence intervals.
+The median is used as point estimate for the corrected $\ynfcs$.
+
+Fig.~\ref{fig:posterior_distribution_I2V} presents examples of the predicted
+quantiles for three different corrected observations of the ICI I1V channel. The
+three cases have a similar median value but very different spread of the
+remaining quantiles. These examples illustrate the case of very similar
+corrected observation values (the estimated median) but with different estimated
+observation errors.
+
+\begin{figure}[t]
+	\centering
+	\includegraphics[height=60mm]{Figures/posterior_distribution_I2V.pdf} 
+	\caption{Predicted quantiles of the conditional distribution of $\ynfcs$ for
+    the ICI I1C channel.}
+	\label{fig:posterior_distribution_I2V}	
+\end{figure}
+%
 \subsubsection{ QRNN model configurations}
@@
 
-In the study, three types of QRNN models are formulated.
-For each type, the target is always one of the available 183\,GHz channels, and this target channel is always included in the training set.
+In the study, three different QRNN cloud-correction models with different selections of input observations are
+investigated.
+All models ype, the target is always one of the available 183\,GHz channels, and this target channel is always included in the training set.
 The choice of other channels in the training set depends on the type of QRNN model chosen.
@@
 The third model, ``QRNN-mwi'' is used only for MWI channels. In this case, all 183\,GHz channels are used concurrently in the training set. No other data from sub-mm channels is used.
+
+\subsubsection{QRNN implementation}
+\label{sec:qrnn-implementation}
+
+The implementation of QRNN is based on PyTorch, an open source machine learning library \citep{paszke2017automatic}.
+It is developed and available as a part of \textit{typhon:tools for atmospheric research} software package [\todo{developer's version??}].
+
+For this study, we initialize the quantile loss function with quantile fractions $\tau$ = [0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998] to train the neural network to predict the corresponding quantiles $x_{\tau}$ = [$-3\sigma, -2\sigma, -1\sigma, median, 1\sigma, 2\sigma, 3\sigma $].
+QRNN is trained with simulated brightness temperatures from different channels, no other data is included.
+The input channels are variable and are determined by the type of QRNN model used.
+The different QRNN models are described in Sect.~\ref{QRNN_models}.
+
+A custom data augmentation scheme is implemented to build a robust learning network.
+At each training iteration, noise is added to the noise-free inputs according to the measurement uncertainty.
+The target training data is always kept noise free.
+This ensures that the model is exposed to different datasets during the entire training process, and avoids memorisation of training samples.
+The input data is normalized with mean and standard deviation.
+While training, 10\% of the training data is used for validation.
+
+The neural network is trained with an adaptive form of stochastic batch gradient descent.
+During the training process, at each iteration, the loss in the validation dataset in monitored.
+If the validation loss remains stagnant for a certain number of epochs, the training rate is reduced  by a given reduction factor.
+This process is continued till a minimum learning rate is achieved.
+
+A high performing QRNN model also requires tuning of multiple hyper-parameters.
+These parameters determine the structure and the training set-up of the neural network.
+Several of these hyper-parameters are non-learnable, and must be defined before beginning of every training.
+Grid search is one of the most often employed techniques for hyper-parameter tuning.
+In grid search, different combinations of hyper-parameters are selected and for each, the model performance is evaluated.
+The model architecture with the best performance is selected.
+For the structural parameters, usually a grid search over the number of neurons (width) and hidden layers (depth) is performed.
+The model is trained for multiple values of layer widths and hidden layers, and the best configuration is selected by evaluating the predictions over validation dataset.
+Similarly, the training process is optimized by performing a grid search different training parameters such as : batch size, learning rate, number of epochs etc.
+We use quantile loss and CRPS for evaluation of the model performance.
 
@@
 %f
-\begin{figure}[t]
-	\centering
-	\includegraphics[height=60mm]{Figures/posterior_distribution_I2V.pdf} 
-	\caption{Posterior distribution obtained from QRNN-single (I2V) for three different cases. }
-	\label{fig:posterior_distribution_I2V}	
-\end{figure}
-%f
 \begin{figure*}[t]
@@
 \end{figure*}
-QRNN predictions are estimates of the posterior distribution over different quantiles.
-For this study we chose quantiles, $x_{\tau}$: median, $\pm 1\sigma$, $\pm 2 \sigma$ and  $\pm 3 \sigma$ (Sect.~\ref{sec:qrnn-implementation}).
-The quantiles are interpreted as probabilistic predictions and can be used to construct a probability distribution of the predictions.
-Fig.~\ref{fig:posterior_distribution_I2V} exemplifies the posterior distribution predicted by QRNN-single.
-The three cases shown in the figure have a similar median value but very different spread.
-The spread of the distributions can also be expressed as the prediction interval.
-If $y_{\tau_2}, y_{\tau_1}$ are the predictions at two quantile levels $\tau_1$ and $\tau_2$ respectively, the interval $[y_{\tau_2}, y_{\tau_1}]$ is called the prediction interval.
-It is gives the range where the prediction could be located and its length is a measure of the reliability.
-Among the three cases shown in the figure, the blue curve has shortest prediction interval indicating a sharp probabilistic prediction or more reliability.
-While the other two cases have longer intervals implying higher fluctuations, or low reliability.
-The quantiles can also be used to interpret the confidence intervals.
-For a given case, if two quantiles $\tau_1$ and $\tau_2$ are chosen, then there is $\tau_2 - \tau_1$ chance that the true value ($y_o$) shall lie in in range $[y_{\tau_1}, y_{\tau_2}]$.
-For example, in a 94\% confidence interval where, $\tau_1 = -2\sigma$ and $\tau_2 = +2\sigma$, there is 0.3\% probability that $y_\circ > y_{\tau_2}$, and 97\% probability that $y_\circ$ > $y_{\tau_1}$.
-More on confidence interval is discussed in Sect.~\ref{sec:prediction_uncertainty}.
 

### 2020-09-21 Article/ici_submm_cloudcorr.tex
started writing sec 3.3.1

--- 2020-09-18 Article/ici_submm_cloudcorr.tex
@@
 with strong limitations imposed by clouds. To be able to also sense humidity
-inside and below clouds, weather satellites are since some time equipped with
+inside and below clouds weather satellites are since some time equipped with
 channels around 183\,GHz. Today such channels are part of several sensors, such
@@
 The main motivation for introducing 183\,GHz channels in operational sensors is
-numerical weather prediction (NWP). Usage of passive microwave data by
-``all-sky'' assimilation in global NWP is growing in \citep{geer2017growing},
-but 183\,GHz data are still mainly used in a clear sky fashion
-\citep{geer2018all}. The later is particularly true in NWP of regional scope
-\citep{gustafsson2018survey}, all-sky assimilation of 183\,GHz at many national
-weather agencies will likely not be reached in many years. Anyhow, the cloud
-filtering applied differs between NWP centres. One approach is to make use of a
-``scattering index'' \citep{bennartz2002precipitation}, based on the
+numerical weather prediction (NWP). Usage of microwave data by ``all-sky''
+assimilation is growing \citep{geer2017growing}, but 183\,GHz data are still
+mainly used in a clear sky fashion \citep{geer2018all}. The later is
+particularly true in NWP of regional scope, all-sky assimilation of 183\,GHz at
+many national weather agencies will likely not be reached in many years. The
+cloud filtering in NWP differs between centres. One approach is to make use of
+a ``scattering index'' \citep{bennartz2002precipitation}, based on the
 observations alone. Today, likely more common is to use ``observation minus
@@
 apply a very strict filtering, but this will result in that a high fraction of
-actually clear-sky values will be rejected, i.e.\ an important loss of useful
-data.
+actually clear-sky values will be rejected \todo{(Reka or better reference)},
+i.e.\ an important loss of useful data.
 
@@
 A maybe less obvious problem is the uncertainty to assign to the filtered
-values. To our best knowledge, so far only estimates of mean and worst case
-errors have been provided. Some cases with relatively high cloud impact will
-likely be missed, while most cases are clear sky from start. As the remaining
-cloudy cases can cause significant biases, the likely solution is to apply a
-quite conservative (high) error estimate. However, this will unnecessary
-downgrade the value of the truly clear sky cases and the observations are used
-in a non-optimal manner.
+values. To our best knowledge, in best case estimates of mean and worst case
+errors are provided. Some cases with relatively high cloud impact will likely be
+missed, while most cases are clear sky from start. As the remaining cloudy
+cases can cause significant biases, the likely solution is to apply a quite
+conservative (high) error estimate. However, this will unnecessary downgrade
+the value of the truly clear sky cases and the observations are used in a
+non-optimal manner.
 
@@
 
-The estimation of NFCS values makes use of a special type of machine learning,
+The estimation of NFSC values makes use of a special type of machine learning,
 denoted as Quantile Regression Neural Network (QRNN,
@@
 	\includegraphics[width = 70mm]{Figures/prediction_uncertainty_I2V.pdf}	
-	\caption{The prediction uncertainty  for I2V  with respect to quantiles for randomly selected 1500 cases.
-The black line represents a hypothetical Gaussian distribution of $270\pm0.60$\,K, which is of the order of standard deviation for I2V predictions (see Table~\ref{tab:error_statistics_ici}).
-The results are from QRNN-single.}
+	\caption{The prediction uncertainty  for QRNN-single(I2V) with respect to quantiles for randomly selected 1500 cases.
+The quantiles have been plotted at equidistant points.
+The black line represents a hypothetical Gaussian distribution of $270\pm0.60$\,K, which is of the order of standard deviation for I2V predictions (see Table~\ref{tab:error_statistics_ici}).}
 	\label{fig:prediction_uncertainty_I2V}	
@@
 \subsubsection{MWI alone}
+\todo {Incomplete}
+
 %
@@
 \begin{table*}[t]
-	\caption{Error statistics for predictions from QRNN-mwi. The labels Filtered(5\,K), Predicted(All) and Predicted(5\,K) are same as described in Table~\ref{tab:error_statistics_ici}}
+	\caption{Error statistics for predictions from QRNN-mwi. The labels Filtered(7.5\,K), Predicted(All) and Predicted(7.5\,K) are same as described in Table~\ref{tab:error_statistics_ici}}
 	\label{tab:statistics_mwi-alone}
@@
 		%		\hline
-		&&   Clear-sky &   All-sky &  Filtered(5\,K) & Predicted & Predicted(5\,K) \\
-		\middlehline
-		MWI-14 		&bias     & 0.00 & -1.87 & -0.45 & -0.18 & -0.15 \\
-					&mae      & 0.64 &  2.31 &  0.91 &  0.96 &  0.80 \\
-					&std      & 0.81 &  8.97 &  1.54 &  1.73 &  1.29 \\
-					&skewness & 0.03 & -8.32 & -4.02 & -1.09 & -3.06 \\
-		\middlehline
-		MWI-15 		&Bias     & -0.01 & -1.23 & -0.36 & -0.16 & -0.13 \\
-					&MAE      &  0.64 &  1.70 &  0.85 &  0.62 &  0.53 \\
-					&STD      &  0.80 &  6.48 &  1.33 &  1.23 &  0.97 \\
-					&skewness &  0.01 & -9.96 & -3.32 & -3.06 & -4.17 \\
-		\middlehline	
-		MWI-16 		&Bias     & -0.00 &  -0.84 & -0.26 & -0.15 & -0.12 \\
-					&MAE      &  0.64 &   1.35 &  0.78 &  0.53 &  0.47 \\
-					&STD      &  0.80 &   5.31 &  1.15 &  1.03 &  0.80 \\
-					&skewness & -0.01 & -12.08 & -3.05 & -5.09 & -4.94 \\	
-		\middlehline			
-		MWI-17 		&Bias     & -0.00 &  -1.06 & -0.31 & -0.16 & -0.12 \\
-					&mae      &  0.64 &   1.54 &  0.80 &  0.62 &  0.54 \\
-					&std      &  0.80 &   6.22 &  1.22 &  1.12 &  0.90 \\
-					&skewness &  0.01 & -11.06 & -3.31 & -4.35 & -4.33 \\	
-		\middlehline			
-		MWI-18 		&Bias     & -0.00 &  -0.66 & -0.23 & -0.11 & -0.08 \\
-					&mae      &  0.64 &   1.17 &  0.76 &  0.62 &  0.57 \\
-					&std      &  0.80 &   4.57 &  1.13 &  1.08 &  0.88 \\
-					&skewness &  0.01 & -13.56 & -3.28 & -4.67 & -3.80 \\	
+		&&   Clear-sky &   All-sky &  Filtered(5\,K) & Predicted & Predicted(7.5\,K) \\
+		\middlehline
+		MWI-14 		&bias     & -0.00 & -1.86 & -0.50(4.06\%) & -0.14 & -0.12 \\
+					&mae      &  0.96 &  2.58 &  1.25 &  1.12 &  1.00 \\
+					&std      &  1.20 &  9.00 &  1.94 &  1.86 &  1.52 \\
+					&skewness &  0.01 & -8.20 & -3.03 & -0.88 & -2.15 \\ 
+		\middlehline
+		MWI-15 		&bias     & 0.01 & -1.23 & -0.40(2.84\%) & -0.13 & -0.11 \\
+					&mae      & 0.95 &  1.99 &  1.18 &  0.74 &  0.66 \\
+					&std      & 1.20 &  6.55 &  1.73 &  1.32 &  1.11 \\
+					&skewness & 0.01 & -9.67 & -2.34 & -2.44 & -2.89 \\
+		\middlehline	
+		MWI-16 		&bias     & 0.00 &  -0.85 & -0.29(1.94\%) & -0.12 & -0.10 \\
+					&mae      & 0.96 &   1.64 &  1.10 &  0.68 &  0.63 \\
+					&std      & 1.20 &   5.39 &  1.54 &  1.15 &  0.96 \\
+					&skewness & 0.00 & -11.62 & -1.97 & -3.71 & -3.22 \\	
+		\middlehline			
+		MWI-17 		&bias     & -0.00 &  -1.04 & -0.32(2.41\%) & -0.13 & -0.11 \\
+					&mae      &  0.96 &   1.83 &  1.12 &  0.73 &  0.67 \\
+					&std      &  1.20 &   6.29 &  1.59 &  1.21 &  1.02 \\
+					&skewness & -0.01 & -10.69 & -2.13 & -3.45 & -3.23 \\	
+		\middlehline			
+		MWI-18 		&bias     &  0.01 &  -0.66 & -0.26(1.37\%) & -0.12 & -0.10 \\
+					&mae      &  0.96 &   1.47 &  1.08 &  0.80 &  0.76 \\
+					&std      &  1.20 &   4.66 &  1.51 &  1.23 &  1.08 \\
+					&skewness & -0.00 & -12.80 & -2.03 & -2.99 & -2.25 \\	
 		\bottomhline				
@@
 Table~\ref{tab:statistics_mwi-alone} shows the results for all 183\,GHz channels of MWI.
-For MWI-14, the predictions from QRNN-mwi are only partially successful in removing the cloudy impact.
-The prediction errors for the complete testing dataset are highly symmetric but with a large spread.
-The average error bias of measurements from NFCS values is -1.87\,K, and after correction, it reduces to -0.18\,K.
-The corresponding standard deviation values are 9.01\,K and 1.87\,K.
-When cases with 5\,K correction are filtered out from the predicted dataset, the bias reduced further to -0.16\,K and MAE from 1.13\,K to 0.97\,K.
-Though there is a small increase in the accuracy, the high errors indicate residual cloud impact.
-For MWI-15, a slightly better accuracy than MWI-14 is observed.
-For this channel, the average error bias in the measurements is -1.23\,K, which  reduces -0.15 after correction.
+
+MWI channels have a higher measurement uncertainty than ICI, so a higher filtering threshold is selected.
+All cases with cloud correction greater than 7.5\,K are considered as cloudy and filtered out.
+With pure-filtering, only 4\% of the cases are filtered out for MWI-14, but the bias reduces from -1.86\,K to -0.50\,K.
+For the predictions, the average bias is -0.14\,K.
+For both filtering and correction, a significant reduction in the errors is observed but the resulting values are still high and indicate only partial success of the method.
+For other channels also, a similar performance is observed.
+For MWI-15, cloud correction reduces the average erros from -1.23\,K to -0.13\,K  and the corresponding decrease in standard deviation is 6.55\,K to 1.32\,K.
+Filtering the predicted cases improves the bias and standard deviation further by 15\%.
+Interestingly, even with partial correction, the standard deviation is lower than the measurement noise.
+For MWI-16, the bias for predictions is -0.12\,K compared to -0.85\,K for the measurements.
+The corresponding standard deviation is  1.15\, which is again smaller than the measurement noise(1.20\,K).
+MWI-17 also has a similar performance.
+MWI-18 is least affected by cloud impact among the five channels.
+The average deviation of the measurement data to NFCS values is only -0.66\,K which reduces to -0.12\,K with QRNN.
+After filtering 1.37\% cases with high cloud impact, only a slight improvement in the accuracy is observed but the variability of errors decreases from 1.23\,K to 1.08\,K.
+
+The results from QRNN-mwi show that using 183\,GHz channels for self correction is only partially successful in removing the cloudy cases.
+Though most of the cases with high cloud impact can be removed, the high errors are mostly due to partially corrected and uncorrected cases with low cloud impact.
+Using a low threshold filter on the predicted data can improve the accuracy, but at the cost of excessive removal of clear-sky cases.
+The five channels are sensitive to different regions of the troposhere.
+The brightness temperature of same cloud measured at different frequencies can vary.
+This can be quite valuable information to train QRNN.
+However cloud impact from regions where the weighting functions match poorly cannot be represented adequately in QRNN.
+The partial correction is a consequence of cases which for which QRNN cannot train.
+
+In contrast to this, the noise reduction for the clear-sky cases is quite significant. The accurate prediction of NFCS values for noisy clear-sky values dominate sthe
+
 \subsubsection{MWI and ICI}
@@
 In this section, we combine the measurements from MWI-15(MWI-16) and the ICI sub-mm channels to predict MWI-15(MWI-16).
-Since we assume that all channels are remapped to a common footprint, channels MWI-14, MWI-17 and MWI-18 are virtually identical to I1V, I2V and I3V, and thus results for them are not shown separately.
+Since we assume that all channels are remapped to a common footprint, channels MWI-14, MWI-17 and MWI-18 are virtually identical to I1V, I2V and I3V, and results for them are not shown separately.
 
@@
 		\middlehline
-		AWS-32  &Bias     & -0.00 & -1.34 & -0.29 & -0.04 & -0.03 \\
-		&MAE       &  0.36 &  1.58 &  0.54 &  0.62 &  0.53 \\
-		&STD      &  0.45 &  5.91 &  0.92 &  0.98 &  0.73 \\
-		&skewness & -0.03 & -7.48 & -3.80 & -1.49 & -1.59 \\
+		AWS-32  &bias     & 0.00 & -1.32 & -0.26 & -0.03 & -0.02 \\
+				&mae      & 0.36 &  1.57 &  0.52 &  0.54 &  0.43 \\
+				&std      & 0.46 &  6.42 &  0.85 &  1.02 &  0.61 \\
+				&skewness & 0.01 & -8.43 & -3.65 & -0.07 & -1.98 \\
 		\middlehline

### 2020-09-22 Article/ici_submm_cloudcorr.tex
added comparison of predicted & observed errors

@@
 \newcommand{\todo}[1]{{\color{red} #1}}
-\newcommand{\ynfcs}{$y_\text{NFCS}}
+\newcommand{\ynfcs}{y_\text{NFCS}}
 \newcommand{\y}{\vec{y}}
@@
 
-The focus on ICI is motivated by several reasons. The true potentail of the
+The focus on ICI is motivated by several reasons. The true potential of the
 QRNN cloud correction approach is likely not revealed if tested on existing
@@
 \subsection{Satellite Instruments}
-In this section, the different satellite instruments used in this study are described.
 \subsubsection{Ice Cloud Imager}
@@
 Ice Cloud Imager (ICI) is a new instrument on board EPS-SG(EUMETSAT Polar System - Second Generation) satellite Metop-SG.
-Metop-SG is scheduled for launch in 2023, and will make ICI the first operational sensor observing Earth using sub-millimeter(sub-mm) wavelengths.
+Metop-SG is scheduled for launch in 2023, and it will make ICI the first operational sensor observing Earth using sub-millimeter(sub-mm) wavelengths.
 ICI is a conically scanning radiometer that will measure 13 frequencies from 183 GHz up to 664 GHz.
@@
 **** Some parts copied directly from AWS report *****
-
-The satellite observations for all ICI channels are simulated with the Atmospheric Radiative Transfer Simulator (ARTS, (ARTS, \citet{eriksson:arts2:11,buehler:artst:18})version.
-The simulations include TB from five ICI channels around 183\,GHz, 243\,GHz, 325\,GHz, 448\,GHz and 664\,GHz.
 
@@
 Using the simulation setup described in previous section,  
-220\,000 cases for each ICI and MWI frequency were simulated, using randomly selected CloudSat profiles. For both instruments, the channel frequencies were simulated directly.  
+220\,000 cases for each ICI and MWI frequency were simulated.
+For both instruments, the channel frequencies were simulated directly.
 For AWS, 140\,000 cases were simulated.
-21 monochromatic frequencies were used and interpolated to a finer grid to get the channel brightness temperatures.
+Forward simulations were performed for 21 monochromatic frequencies.
+These frequencies were interpolated to a finer grid to get the AWS channel brightness temperatures.
 All AWS sensor viewing angles (from $0^\circ$ to $45^\circ$) were simulated, but the results described in this study are based on nadir viewing angle.
 
-ARTS simulations are noise free, so to incorporate the measurement uncertainties, whenever needed, gaussian noise was added to according to the channel NE$\Delta$T (Table~\ref{tab:ICI_MWI_channels}, Table~\ref{tab:specifications_AWS}).
+ARTS simulations are noise free, so to incorporate the measurement uncertainties, whenever needed, gaussian noise was added to according to the channel NE$\Delta$T (Table~\ref{tab:ICI_MWI_channels},Table~\ref{tab:specifications_AWS}).
 For cases where MWI and ICI simulations were assumed to be remapped to a common footprint, the NE$\Delta$T for corresponding to ICI channels was used (See Sect.~\ref{mwi_channels}).
@@
 A smaller database was selected for AWS.
-120\,000 simulations were used for training and the
-remaining were used for testing.
+120\,000 simulations were used for training and the remaining were used for testing.
 
@@
 
-Fig.~\ref{fig:posterior_distribution_I2V} presents examples of the predicted
-quantiles for three different corrected observations of the ICI I1V channel. The
-three cases have a similar median value but very different spread of the
-remaining quantiles. These examples illustrate the case of very similar
-corrected observation values (the estimated median) but with different estimated
-observation errors.
-
-\begin{figure}[t]
-	\centering
-	\includegraphics[height=60mm]{Figures/posterior_distribution_I2V.pdf} 
-	\caption{Predicted quantiles of the conditional distribution of $\ynfcs$ for
-    the ICI I1C channel.}
-	\label{fig:posterior_distribution_I2V}	
-\end{figure}
-%
+%Fig.~\ref{fig:posterior_distribution_I2V} presents examples of the predicted quantiles for three different corrected observations of the ICI I1V channel.
+The three cases have a similar median value but very different spread of the remaining quantiles.
+These examples illustrate the case of very similar corrected observation values (the estimated median) but with different estimated observation errors.
+
 \subsubsection{ QRNN model configurations}
@@
 
-In the study, three different QRNN cloud-correction models with different selections of input observations are
-investigated.
-All models ype, the target is always one of the available 183\,GHz channels, and this target channel is always included in the training set.
-The choice of other channels in the training set depends on the type of QRNN model chosen.
-A summary of the three QRNN models described in this study is provided in Table~\ref{tab:QRNN_models}.
+In the study, three different QRNN cloud-correction models are formulated.
+The basic construction of all three models is to train for one of the available 183\,GHz channels, using certain input channels.
+The selection of input channels is categorized by the type of QRNN model chosen.
 
@@
 Other 183\,GHz channels are not included in the training.
-For ICI and MWI, 325\,GHz, 448\,GHz and 664\,GHz channels are used in the training, while for AWS only 325\,GHz is used.
+For ICI and MWI, 325\,GHz, 448\,GHz and 664\,GHz are used in the training, while for AWS only 325\,GHz is used.
 
@@
 This model is applied only to ICI.
-It should be noted that although the training set is identical for I1V, I2V and I3V, a separate training is needed for each channel as target.
 
 The third model, ``QRNN-mwi'' is used only for MWI channels. In this case, all 183\,GHz channels are used concurrently in the training set. No other data from sub-mm channels is used.
+
+For each model, multiple configurations are defined according to the satellite instrument.
+A summary of the three QRNN models and their different configurations used in this study is provided in Table~\ref{tab:QRNN_models}.
 
@@
 %f
+\begin{figure}[t]
+	\centering
+	\includegraphics[height=60mm]{Figures/posterior_distribution_I1V.pdf} 
+	\caption{Predicted quantiles of the conditional distribution of $\ynfcs$ for
+		the ICI I1V channel.}
+	\label{fig:posterior_distribution_I1V}	
+\end{figure}
+%f
 \begin{figure*}[t]
@@
 
+Fig.~\ref{fig:posterior_distribution_I2V} presents examples of the predicted quantiles for three different corrected observations of the ICI I1V channel.
+The three cases have a similar median value but very different spread of the remaining quantiles.
+These examples illustrate the case of very similar corrected observation values (the estimated median) but with different estimated observation errors.
 For an analysis of QRNN predictions, a point estimate of the posterior distribution is required.
@@
 The distribution of point estimates is shown in Fig.~\ref{fig:PDF_predictions}.
-For clear-sky conditions, I1V has the warmest brightness temperatures and I3V has the coldest.
-For all three channels, an excellent agreement between the predictions and simulations is observed, indicating that QRNN is successful in predicting NFCS values for majority of the cases.
+For all three channels, an excellent agreement between the predictions and simulations is observed.
+This indicates that QRNN is successful in predicting NFCS values for majority of the cases.
 At lower brightness temperatures, the frequency of predictions is slightly smaller than simulations.
@@
 \end{figure}
+\begin{figure*}[t]
+	\includegraphics[width=150mm]{Figures/deviation_posterior_samples_I2V.pdf}	
+	\caption{The distribution of predicted errors and observed errors for I2V as obtained from QRNN-single and QRNN-all for the test dataset.
+The predicted errors are estimated as deviation of random samples from posteriori distribution to corresponding median values.}
+	\label{fig:predicted_errors}	
+\end{figure*}
 \begin{figure}[t]
@@
 The quantiles can be used to construct a probability distribution of the predictions in contrast to other correction approaches which give out only point estimates.
-If median is chosen as the point estimate, the predictions at other quantiles provide a measure of the possible fluctuations in the point estimate.
-
-In order to understand how QRNN predicted uncertainties behave, we calculated the deviations of predictions at different quantiles from the median value (Fig.~\ref{fig:prediction_uncertainty_I2V}).
-The large spread in the uncertainty estimates indicates that QRNN can successfully represent uncertainties for each case individually, rather than expressing them as a single measure for all cases.
-In the latter case, the uncertainty estimates for all cases would be concentrated along a narrow interval.
+
+In order to analyse the prediction uncertainty, the deviations of predicted quantiles from its median value are estimated.
+Fig.~\ref{fig:prediction_uncertainty_I2V} shows the spread of prediction uncertainties over different quantiles for randomly chosen 1500 cases.
+The large spread in the predicted errors indicates that QRNN is successful in representing uncertainties for each case individually, rather than expressing them as a single measure for all cases.
+In the latter case, the uncertainty estimates would be concentrated along a narrow interval.
 Among the cases associated with low uncertainty, the distribution is quite symmetric along the median value.
 These cases are concentrated along a narrow interval and lie close to the black curve.
-For such cases, the uncertainties are also equally spaced for $1\sigma$, $2\sigma$ and $3\sigma$, suggesting that a Gaussian distribution model could be used to express their underlying uncertainty.
-However, the cases with high uncertainty are unequally spaced and have a larger spread over positive quantiles than negative quantiles.
+On the contrast, cases with high uncertainty are unequally spaced and have a larger spread over positive quantiles than negative quantiles.
+
+Fig.~\ref{fig:predicted_errors} shows the comparison of observed errors (prediction accuarcy) to predicted errors.
+The predicted dataset is constructed by drawing random samples from the posteriori distribution.
+We do derive any sample from outside $\pm3\sigma$.
+The predicted error is deviation of random sample to its median.
+For QRNN-single, the predicted and observed errors have good agreement for the peak of the distribution, but the predicted errors are spread out asymmetrically.
+For QRNN-all, the predicted and observed errors have a better agreement and their spread is symmetric.
+The results show that both QRNN-single and QRNN-all is not able to represent the left wings of the distribution.
+This could also be a sampling issue, as the high errors we try to predict form a very small fraction of the complete dataset.
 
@@
 %
-In this section, we present results from QRNN when applied to MWI channels.
-Firstly, we discuss results when all 183\,GHz MWI channels are used for ``self'' cloud filtering/correction (QRNN-mwi).
+In this section, we discuss results when all 183\,GHz MWI channels are used for ``self'' cloud filtering/correction (QRNN-mwi).
 We also describe the performance of QRNN when sub-mm channels from ICI are used to train MWI channels.
 \subsubsection{MWI alone}
-\todo {Incomplete}
-
 %
@@
 		%		\hline
-		&&   Clear-sky &   All-sky &  Filtered(5\,K) & Predicted & Predicted(7.5\,K) \\
+		&&   Clear-sky &   All-sky &  Filtered(7.5\,K) & Predicted & Predicted(7.5\,K) \\
 		\middlehline
@@
 \end{table*}
+\begin{figure}[t]
+	\includegraphics[width = 70mm]{Figures/cloud_impact_uncertainty_MWI.pdf}	
+	\caption{The average confidence intervals (2$\sigma$) plotted against the magnitude of cloud impact for all MWI channels.}
+	\label{fig:uncertainty_cloud_impact}	
+\end{figure}
 QRNN-mwi is designed to provide basis for a cloud correction approach applicable to current satellites, which lack the higher frequency channels.
+
 Table~\ref{tab:statistics_mwi-alone} shows the results for all 183\,GHz channels of MWI.
-
 MWI channels have a higher measurement uncertainty than ICI, so a higher filtering threshold is selected.
@@
 For other channels also, a similar performance is observed.
-For MWI-15, cloud correction reduces the average erros from -1.23\,K to -0.13\,K  and the corresponding decrease in standard deviation is 6.55\,K to 1.32\,K.
+For MWI-15, cloud correction reduces the average error from -1.23\,K to -0.13\,K  and the corresponding decrease in standard deviation is 6.55\,K to 1.32\,K.
 Filtering the predicted cases improves the bias and standard deviation further by 15\%.
@@
 For MWI-16, the bias for predictions is -0.12\,K compared to -0.85\,K for the measurements.
-The corresponding standard deviation is  1.15\, which is again smaller than the measurement noise(1.20\,K).
+The corresponding standard deviation is  1.15\,K, which is again smaller than the measurement noise(1.20\,K).
 MWI-17 also has a similar performance.
@@
 After filtering 1.37\% cases with high cloud impact, only a slight improvement in the accuracy is observed but the variability of errors decreases from 1.23\,K to 1.08\,K.
-
-The results from QRNN-mwi show that using 183\,GHz channels for self correction is only partially successful in removing the cloudy cases.
-Though most of the cases with high cloud impact can be removed, the high errors are mostly due to partially corrected and uncorrected cases with low cloud impact.
-Using a low threshold filter on the predicted data can improve the accuracy, but at the cost of excessive removal of clear-sky cases.
-The five channels are sensitive to different regions of the troposhere.
-The brightness temperature of same cloud measured at different frequencies can vary.
-This can be quite valuable information to train QRNN.
-However cloud impact from regions where the weighting functions match poorly cannot be represented adequately in QRNN.
-The partial correction is a consequence of cases which for which QRNN cannot train.
-
-In contrast to this, the noise reduction for the clear-sky cases is quite significant. The accurate prediction of NFCS values for noisy clear-sky values dominate sthe
+The results show that QRNN-mwi is partially successful in removing the cloud impact.
+A significant reduction in the deviation to NFCS values indicates that though most cases with high cloud impact can be removed/corrected, the cases with residual cloud impact and uncorrected cases deteriorate the performance.
+Using a low threshold filter can improve the accuracy, but at the cost of excessive removal of clear-sky cases.
+
+The five channels are sensitive to different regions of the troposphere so not all clouds get equal representation in each.
+The cloud impact from regions where the weighting functions match poorly cannot be represented adequately in QRNN.
+However,the brightness temperature of same cloud measured at different frequencies can be valuable to train QRNN.
+Similarly, the clear-sky measurements from different channels can effectively cancel out the noise.
+QRNN predictions can be interpreted as a weighted average between the multiple channels.
+As clear-sky cases occur more frequently, the averaging can cancel out noise.
+
+Finally, we investigate if uncertainty estimates from QRNN-mwi are representative of prediction errors.
+Fig.~\ref{fig:uncertainty_cloud_impact} displays the average prediction uncertainty in 97\% confidence interval for different cloud impacts.
+For all five channels, the predictions with small or relatively low cloud signal have a low uncertainty or in other words have high sharpness.
+As fraction of cloud impact increases, the predictions become increasingly uncertain.
+Most uncertain predictions occur for the outermost channels (MWI-14, MWI-15).
+These channels also have the lowest prediction accuracy.
 
@@
 %t
-\todo{Incomplete}
-
 \begin{table*}[t]
@@
 
-The uncertainty
-
 These results show that even though ICI and MWI are two different instruments, their channels can benefit from each other.
@@
 %f
-\begin{figure}[t]
-	\includegraphics[width = 80mm]{Figures/cloud_impact_uncertainty_AWS.pdf}	
-	\caption{The average confidence intervals (2$\sigma$) plotted against the magnitude of cloud impact for all AWS channels.}
-	\label{fig:uncertainty_cloud_impact}	
-\end{figure}
+%\begin{figure}[t]
+%	\includegraphics[width = 80mm]{Figures/cloud_impact_uncertainty_AWS.pdf}	
+%	\caption{The average confidence intervals (2$\sigma$) plotted against the magnitude of cloud impact for all AWS channels.}
+%	\label{fig:uncertainty_cloud_impact}	
+%\end{figure}
 
@@
 
-In order to analyse the performance of QRNN with respect to uncertainty, the interrelation between the uncertainty estimates and cloud impact was investigated.
+%In order to analyse the performance of QRNN with respect to uncertainty, the interrelation between the uncertainty estimates and cloud impact was investigated.
 Fig~\ref{fig:uncertainty_cloud_impact} displays the plot between mean uncertainty estimates for $2\sigma$ confidence interval and the cloud impact.

### 2020-09-22 Article/ici_submm_cloudcorr.tex
small changes in Sec 3

@@
 However for four hidden layers, increasing the number of neurons beyond 128 has no significant impact on the performance.
-On basis of these results, a neural network with four hidden layers and 128 neurons in each layer was selected.
+On basis of these results, a neural network with four hidden layers and 128 neurons in each layer is selected.
 For optimising the training parameters, a customised  learning rate scheduler was implemented.
@@
 We started the training process with a initial learning rate of 0.1, and decreased it by a factor of 10 after 100 epochs.
-The best neural network performance was obtained when the network was trained three times with a new initial learning rate.
+The best neural network performance was obtained when the network was trained three times.
+Each time with a new initial learning rate.
 For each training, if the validation loss remained unchanged till 6 training epochs, the learning rate was reduced by a factor of 2.
-In order to select the batch size, we simply compared the performance for for two batch sizes: 128 and 256, and the former gave better results.
+In order to select the batch size, we simply compared the performance for two batch sizes: 128 and 256, and the former gave better results.
 Concerning number of epochs, we obtained best results when the network was trained longer.
@@
 
-Though these set of hyper-parameters were selected for QRNN-single applied to I2V, they worked well for other channnels and other QRNN models as well.
-All the results described in this study used an identical hyper-parameter configuration.
+Though these set of hyper-parameters were selected for QRNN-single applied to I2V, they worked well for other QRNN models and their multiple configurations.
+All the results described in this study use an identical hyper-parameter configuration.
 
@@
 All cases with  cloud correction greater than a certain threshold are classified as cloudy and omitted from the dataset.
-Cloud correction is calculated as the difference of the point estimate and the corresponding measurement.
+Cloud correction is calculated as the difference of the point estimate to the corresponding measurement.
 Since this is a pure-filter, for the cases classified as clear-sky, the a priori values are used instead of the point estimates.
@@
 All cases with correction greater than 5\,K were rejected.
-In order to analyse the performance of the filtering threshold, the deviations of the filtered measurements to the simulated NFCS values were calculated.
+In order to analyse the performance of the filtering threshold, the deviations of the filtered measurements to the NFCS simulations were calculated.
 Fig.~\ref{fig:error_distributions} shows the distribution of the deviations for filtered(red) and original datasets(green).
@@
 Without any cloud impact, the error distributions must follow a Gaussian distribution with a narrow spread.
-When filtering is activated, and all cases with correction greater than 5\,K are rejected, the resulting distributions have a low but asymmetric spread.
-The right side of the distributions follows measurement noise, as expected, and the left side has a significantly smaller negative skewness than the measurements.
+When filtering is activated, the resulting distributions have a low but asymmetric spread.
+The right side of the distributions follows the measurement noise, as expected.
+The left side has a significantly smaller negative skewness than the measurements.
 This indicates that 5\,K filter can successfully remove cases associated with high cloud impact.
@@
 Similarly for I2V, the average error bias in all sky measurements is -1.04\,K, that reduces to -0.24\,K after filtering.
-The corresponding improvement in MAE was almost 65\%.
-Only 3.7\% of the total cases were rejected to achieve this accuracy.
+The corresponding improvement in MAE is almost 65\%.
+Only 3.7\% of the total cases are rejected to achieve this accuracy.
 For I3V, filtering classifies 2.3\% of the total cases as cloudy and reduces the bias to 0.18\,K from -0.63\,K and the standard deviation from 5.95\,K to 0.91\,K.
@@
 Overall for all three channels, the notable decrease in the errors indicates that the cloud filter is effective in removing most of the cloudy cases, however few cases with low cloud impact still pass through the filter and deteriorate the performance.
-This indicates that though a pure-filtering approach can prove as a reliable procedure for removing cases with high cloud impact, additional measures are needed to remove cases with low cloud impact.
+Thus pure-filtering approach can prove as a reliable procedure for removing cases with high cloud impact, but additional measures are needed to remove cases with low cloud impact.
 
@@
 However, a further decrease in the filtering threshold decreases the average error bias significantly, albeit with a high rejection rate.
-For example, for I1V, when all cases with cloud correction greater 0.5\,K are filtered, the mean error bias of the subset is -0.06\,K, MAE is 0.59\,K and the standard deviation is 0.75\,K.
+For example for I1V, when all cases with cloud correction greater 0.5\,K are filtered, the mean error bias of the subset is -0.06\,K, MAE is 0.59\,K and the standard deviation is 0.75\,K.
 Though, these values are comparable to the NFCS simulations, the high performance comes at the cost of rejecting more than 30\% of the total cases.
@@
 	\includegraphics[width=70mm]{Figures/different_filtering_thresholds.pdf} 
-	\caption{A comparison of the  average bias when pure-filtering approach (QRNN-single) is applied with different thresholds (red curves).
-The corresponding fraction of cases rejected is also shown on the right y-axis(blue curves).}
+	\caption{A comparison of the  average bias when pure-filtering approach is applied with different thresholds (red curves).
+The corresponding fraction of cases rejected is also shown on the right y-axis(blue curves).
+The results are from QRNN-single.
+}
 	\label{fig:filtering_thresholds}	
@@
 
-The QRNN prediction accuracy is estimated by computing the deviation of the best estimate to its corresponding NFCS value (Fig.~\ref{fig:error_distributions}).
-The predicted values have a symmetric distributions albeit with a large spread.
-The large spread on the left is due to cases which end up with incomplete cloud correction, while spread on the right is from cases where the predicted values are warmer than the simulations.
+The QRNN prediction accuracy is estimated by computing the deviation of the best estimate to its corresponding NFCS simulation(Fig.~\ref{fig:error_distributions}).
+The predicted values have symmetric error distributions albeit with a large spread.
+The large spread on the left is due to cases which end up with incomplete cloud correction, while the spread on the right is from cases where the predicted values are warmer than the simulations.
 For all three channels, quite similar behaviour is observed, though I1V has the most cases with residual cloud impact.
@@
 The corresponding standard deviation is 0.98\,K in comparison to 8.84\,K in the measurements.
-The prediction accuracy of QRNN is further higher when filtering is made on the predictions.
+The prediction accuracy of QRNN-single is further higher when filtering is made on the predictions.
 In this case, the residual bias is only -0.04\,K, and the standard deviation is 0.73\,K, which is in fact of the order of measurement noise (0.80\,K).
-Similar results are seen for I2V, though a better performance of QRNN is observed.
+Similar results are seen for I2V, though a better performance is observed.
 In I2V, the measurement bias is -1.04\,K which reduces to -0.01\,K after correction.
 The MAE reduces from 1.52\,K to 0.52\,K.
-Removing cases with correction greater than 5\,K from the predictions removes 3.7\% of the data and reduces the absolute error to 0.46\,K and the bias to 0\,K.
+Removing cases with correction greater than 5\,K from the predictions removes 3.7\% of the data and reduces the absolute error to 0.46\,K.
 The standard deviation of the resulting dataset is only 0.59\,K as compared to 0.80\,K from noise.
-The reduction in the variability is also evident in the Fig~\ref{fig:error_distributions}, where the peak of the predicted distributions is sharper.
+The reduction in the variability is also evident in the Fig~\ref{fig:error_distributions}, where the peak of distributions is sharper.
 In comparison to I1V and I2V, I3V has the lowest fraction of the measurements with significant cloud impact.
-In the predicted dataset, the bias is 0.01\,K and the MAE is 0.51\,K in comparison to 1.15\,K  in the measurements.
+In the predicted dataset, the bias is 0.01\,K and the MAE is 0.51\,K.
 Including correction along with filtering reduces the MAE further down to 0.47\,K and standard deviation to 0.59\,K, which is again smaller than that of noise(0.80\,K).
@@
 However when the predictions are filtered with 5\,K threshold, the performance of both models is quite similar.
-This indicates that information from other channels only assists in slightly improving the correctness of cases associated with high cloud impact in I1V.
-The predictions of cases with low cloud impact have no significant gain.
+This indicates that information from other channels is only slightly helpful in improving the correctness of cases associated with high cloud impact.
+The predictions for cases with low cloud impact have no significant gain.
 For I2V, the predictions from QRNN-all have a slightly worse average error bias than QRNN-single, yet a significant improvement in the prediction accuracy is observed.
@@
 Additionally, when the predicted dataset is filtered with 5\,K threshold, the accuracy is even better.
-The mean absolute bias reduces to 0.39\,K and standard deviation to 0.50\,K.
+The MAE reduces to 0.39\,K and standard deviation to 0.50\,K.
 This implies that cases pertaining to clear-sky conditions and relatively low/no cloud impact benefit the most from the auxiliary information.
@@
 In order to quantify the positive effect of QRNN-all on cases with high cloud impact, the error statistics for all cases with cloud correction greater than 10\,K were computed (Table~\ref{tab:error_statistics_ici_high_cloud_impact}).
-For I1V, only 4\% of the cases have cloud correction greater than 10\,K, but very high prediction errors.
+For I1V, only 4\% of the cases have cloud correction greater than 10\,K, but very low prediction accuracy.
 QRNN-all improves the overall error bias from -0.53\,K to -0.38\,K and the standard deviation from 3.13\% to 2.63\%, but is unsuccessful in removing the cloud impact completely.
@@
 Predictions from QRNN-all have slightly worse values for average error bias, but both MAE and standard deviation improve by over 20\%.
-For I3V also, the cases with high cloud impact, though very low in number, also gained positively from the auxiliary information.
-
-The results show that both QRNN-single and QRNN-all are successful in predicting NFCS values for I2V, and I2V, and partially successful for I1V.
+For I3V also, the cases with high cloud impact, though very low in number, also gain positively from the auxiliary information.
+
+The results show that both QRNN-single and QRNN-all are successful in predicting NFCS values for I2V, and I3V, and partially successful for I1V.
 The resulting error distributions are symmetric with low bias and standard deviation.
@@
 The cancelling of noise is stronger in QRNN-all as all 183\,GHz channels are used concurrently.
-The lower prediction accuracy of I1V can be explained by the fact that it is the outermost 183\,GHz channel and the other sub-mm channels cannot provide a full coverage for the hydrometeor impact in I1V.
+The lower prediction accuracy of I1V can be explained by the fact that it is the outermost 183\,GHz channel.
+The other sub-mm channels cannot provide a full coverage for the hydrometeor impact in I1V.
 Depending upon the atmospheric scenarios, there is always a portion of data detected by I1V, but never seen by any other channel.
@@
 
-Fig.~\ref{fig:predicted_errors} shows the comparison of observed errors (prediction accuarcy) to predicted errors.
+Fig.~\ref{fig:predicted_errors} shows the comparison of observed errors (prediction accuracy) to predicted errors.
 The predicted dataset is constructed by drawing random samples from the posteriori distribution.
@@
 For QRNN-single, the predicted and observed errors have good agreement for the peak of the distribution, but the predicted errors are spread out asymmetrically.
-For QRNN-all, the predicted and observed errors have a better agreement and their spread is symmetric.
-The results show that both QRNN-single and QRNN-all is not able to represent the left wings of the distribution.
+For QRNN-all, the predicted and observed errors have a better agreement and the spread is symmetric for the former.
+The results show that both QRNN-single and QRNN-all are not able to represent the left wings of the distribution.
 This could also be a sampling issue, as the high errors we try to predict form a very small fraction of the complete dataset.
@@
 For further analysis, we compared the distribution of predictions from QRNN with the a priori distribution.
-In a model with high performance, the posterior distribution of the predictions should be similar to the a priori distribution of training dataset.
+In a  high performing QRNN model, the posteriori distribution of the predictions should be similar to the a priori distribution of training dataset.
 A straightforward way to compare the two distribution is to plot the frequency of predictions and frequency of the true value in different prediction intervals.
@@
 In this case the calibration curve lies below the y=x line, indicating that the predicted intervals are too narrow, or the uncertainty is underestimated.
-In the test and training datasets, the clear-sky cases and cases with low cloud impact dominate the a priori distribution.
-The a priori distribution of cloudy cases is significantly different to the clear-sky cases, thus leading to poorly calibrated predictions for former.
+The clear-sky cases dominate the test/training dataset, thus the a priori distribution is representative of the same.
+The a priori distribution of cloudy cases is different to the clear-sky cases, therefore the predictions are poorly calibrated for the former.
 We also plotted the calibration curves for I2V and I3V (figure not shown).
-For both these channels, predictions over complete dataset were well calibrated for both QRNN-single and QRNN-all, but for subset with threshold 10\,K, the slightly poor calibrations were observed in QRNN-single.
+For both these channels, predictions over complete dataset were well calibrated for both QRNN-single and QRNN-all, but for subset with threshold 10\,K, slightly poor calibrations were observed in QRNN-single.
 This is in contrast with I1V, where both models had poor calibrations for cases with high cloud impact.
 
-Lastly, we investigated that if the uncertainty estimates given by QRNN are representative of prediction errors.
-We divided the 94\% confidence interval ($\pm2\sigma$ ) into three bins and estimated the prediction error distribution for each (Fig.~\ref{fig:error_distribution_uncertainty_bins}).
+Lastly, we investigated that if the uncertainty estimates given by QRNN are representative of prediction accuracy.
+Fig.~\ref{fig:error_distribution_uncertainty_bins} shows the errors of best estimate binned by their corresponding uncertainty in $\pm2\sigma$  confidence interval.
 Similar results were also obtained for QRNN-all (figure not shown).
-For all three channels, an increase in the prediction errors with uncertainty is observed.
+For all three channels, the spread of error distribution increases as the uncertainty about the accuracy of the trial increases.
 The cases with high certainty have a narrow and sharp distribution, and the errors are mostly less than $\pm$2.5\,K.
@@
 In spite of individual variations in the error distributions for each channel, predictions and their corresponding uncertainties followed the same relationship.
-This suggests that QRNN can reliably represent the quality of predictions through their uncertainty estimates.
-
-These three different types of analysis show that both QRNN-single and QRNN-all are successful in providing well calibrated probabilistic predictions of the posterior distributions except for few cases associated with high cloud impact.
-This is not unexpected, as such cases form a small subset of the training set and their priori distribution could be different from the entire dataset.
+
+The results show that both QRNN-single and QRNN-all are successful in providing well calibrated probabilistic predictions of the posterior distributions except for few cases associated with high cloud impact.
+This is not unexpected as such cases form a small subset of the training set and their priori distribution is different from the entire dataset.
 Since such cases form only a fraction of the training dataset, it can be hard to train the model to predict them accurately.

### 2020-09-22 Article/ici_submm_cloudcorr.tex
added missing Figures

@@
 
-Fig.~\ref{fig:posterior_distribution_I2V} presents examples of the predicted quantiles for three different corrected observations of the ICI I1V channel.
+Fig.~\ref{fig:posterior_distribution_I1V} presents examples of the predicted quantiles for three different corrected observations of the ICI I1V channel.
 The three cases have a similar median value but very different spread of the remaining quantiles.
@@
 The predicted dataset is constructed by drawing random samples from the posteriori distribution.
-We do derive any sample from outside $\pm3\sigma$.
+We do not derive any sample from outside $\pm3\sigma$.
 The predicted error is deviation of random sample to its median.
@@
 
-The five channels are sensitive to different regions of the troposphere so not all clouds get equal representation in each.
-The cloud impact from regions where the weighting functions match poorly cannot be represented adequately in QRNN.
-However,the brightness temperature of same cloud measured at different frequencies can be valuable to train QRNN.
-Similarly, the clear-sky measurements from different channels can effectively cancel out the noise.
-QRNN predictions can be interpreted as a weighted average between the multiple channels.
-As clear-sky cases occur more frequently, the averaging can cancel out noise.
-
-Finally, we investigate if uncertainty estimates from QRNN-mwi are representative of prediction errors.
-Fig.~\ref{fig:uncertainty_cloud_impact} displays the average prediction uncertainty in 97\% confidence interval for different cloud impacts.
+The five frequencies are sensitive to different regions of the troposphere so not all clouds are equally represented in all.
+The brightness temperature of same cloud measured at different frequencies can be valuable to train QRNN.
+However the hydrometeor impact from regions where the weighting functions match poorly cannot be represented adequately in QRNN.
+As a consequence, the predictions are poor.
+In constrast, the clear-sky measurements of the same scene from multiple channels, reinforces the QRNN predictions.
+The measurement noise in all channels is stationary and uncorrelated, thus the predictions benefit from the additional information, and averaging cancels out the noise component.
+As clear-sky cases occur more frequently, the effect is quite prominent.
+
+Further, we investigate if uncertainty estimates from QRNN-mwi are representative of prediction errors.
+Fig.~\ref{fig:uncertainty_cloud_impact} displays the average predicted errors in 94\% confidence interval, for different cloud impacts.
 For all five channels, the predictions with small or relatively low cloud signal have a low uncertainty or in other words have high sharpness.
@@
 These channels also have the lowest prediction accuracy.
+Thus, the QRNN predictions possess a multivariate representation of uncertainty.
+The uncertainty of cases with varying cloud impacts can be expressed individually.
 
@@
 These results show that even though ICI and MWI are two different instruments, their channels can benefit from each other.
-Although re-mapping to a common footprint would slighly compromise the data quality, a high accuracy achieved with simulations suggests that the QRNN would work well even when actual measurements are available.
+Although re-mapping to a common footprint would slighly compromise the data quality, a high accuracy achieved with simulations suggests that the QRNN would work well when actual measurements are available.
 
@@
 and the results are displayed in Table~\ref{tab:statistics_qrnn_aws}.
-For channel AWS-32, the average bias and standard deviation in the prediction errors is is -1.34\,K and 5.91\,K respectively.
+For channel AWS-32, the average bias and standard deviation in the prediction errors is -1.34\,K and 5.91\,K respectively.
 However, after correction, the bias and standard deviation are -0.08\,K and 1.0\,K.
-A decrease in the skewness of error distributions is evident(from -7.48 to -1.52), but a relatively high values after prediction indicate presence of cases with partially-corrected cloud impact.
+A decrease in the skewness of error distributions is evident, but a relatively high values after prediction indicate presence of cases with partially-corrected cloud impact.
 For AWS-33, the predictions have slightly higher accuracy than AWS-32.
@@
 Similar results are also seen for AWS-35 and AWS-36.
-For both channels, the predictions are relatively more symmetric than the other channels.
-Also, it is worth to noting that when cases with 5\,K cloud correction are removed, the spread of predictions is narrower than noise.
+For both channels, the error distributions are relatively more symmetric than the other channels.
+Also, it is worth to noting that when cases with 5\,K cloud correction are removed, the spread of prediction errors is narrower than noise.
 
@@
 The cases with high error are mostly associated with high cloud impact and constitute only a small fraction of the total dataset.
-Excluding such cases decreases the variability in the predictions and in fact the spread of errors for AWS-34, AWS-35 and AWS-36 is smaller than noise.
+Excluding such cases decreases the errors and in fact the spread of errors for AWS-34, AWS-35 and AWS-36 is smaller than noise.
 Removal of cases with high cloud impact, increases the representation of cases in cloud-free conditions, and for such cases, QRNN predictions can be seen as a weighted mean between the two channels.
-Since the noise in the two channels are stationary and uncorrelated, the predictions benefit from the additional information, but the noise component tends to cancel out.
 For AWS-32, QRNN is only partially successful in reducing the impact of hydrometeors.

### 2020-09-23 Article/ici_submm_cloudcorr.tex
added first version of abstract

@@
 \begin{abstract}
-TEXT
+
+This study presents a cloud filtering and correction method for microwave humidity radiances.
+The method is based on the postulation that sub-millimeter(sub-mm) frequencies can provide a basis for cloud filtering/correction of data measured around 183\,GHz.
+A quantile regression(QRNN) based approach is formulated to estimate the posterior distributions of noise free clear sky (NFCS) radiances.
+QRNNs are trained to correct the cloud impact for each 183\,GHz channel using measurements from the target channel and available sub-mm channels.
+The approach is demonstrated by application to Ice Cloud Imager(ICI) and MicroWave Imager (MWI).
+As a special case applicability to smaller satellite missions like Arctic Weather Satellite (AWS), with fewer sub-mm channels, is also evaluated.
+The performance of QRNN based cloud filtering is also investigated.
+The results are compared against the NFCS simulations.
+
+Pure-filtering approach is only partially successful in removing the cloud contamination.
+Though most of the cases with high cloud impact are drawn out, cases with low cloud impact are falsely classified as cloudy.
+This shortcoming is unacceptable in retrieval and assimilation applications and reinforces the necessity for cloud correction.
+The results from cloud correction show that QRNN is successful in alleviating the cloud contamination to a large extent.
+Few cases with residual cloud impact deteriorate the performance but filtering out such cases results in error distributions which are symmetric and have low bias and standard deviation.
+In some cases, the combination of 183\,GHz and sub-mm channels also results in a lower variability than noise.
+Another advantage of using QRNN is that predicted quantiles can be employed to quantify the case-specific uncertainty estimates.
+The results show that QRNN is successful in representing the uncertainty for most of scenes individually.
+Despite individual variations for each channel, it is observed that uncertainty consistently increases with the error in the performance.
+
+The results show that it can be highly recommended to use all available sub-mm frequencies to estimate the NFCS values of radiances/brightness temperatures.
+The strategy works well even when only one of the higher frequencies is available.
+This study uses simulated data, but we can expect to obtain similar performance when data fron the new sensors will be available.
+
 \end{abstract}
@@
 Among the cases associated with low uncertainty, the distribution is quite symmetric along the median value.
-These cases are concentrated along a narrow interval and lie close to the black curve.
+These cases are concentrated along a narrow interval and lie close to the black curve representing a Gaussian spread.
 On the contrast, cases with high uncertainty are unequally spaced and have a larger spread over positive quantiles than negative quantiles.
+Thus QRNN is capable of capturing non-Gaussian  error distributions as well.
 
@@
 The results show that both QRNN-single and QRNN-all are not able to represent the left wings of the distribution.
-This could also be a sampling issue, as the high errors we try to predict form a very small fraction of the complete dataset.
+This could also be a sampling issue, as the high errors we try to predict constitute a very small part of the complete dataset.
 

### 2020-09-24 Article/ici_submm_cloudcorr.tex
some minor changes

@@
 The approach is demonstrated by application to Ice Cloud Imager(ICI) and MicroWave Imager (MWI).
-As a special case applicability to smaller satellite missions like Arctic Weather Satellite (AWS), with fewer sub-mm channels, is also evaluated.
+As a special case, applicability to smaller satellite missions like Arctic Weather Satellite (AWS), with fewer sub-mm channels, is also evaluated.
 The performance of QRNN based cloud filtering is also investigated.
@@
 The strategy works well even when only one of the higher frequencies is available.
-This study uses simulated data, but we can expect to obtain similar performance when data fron the new sensors will be available.
+This study uses simulated data, but we can expect to obtain similar performance when data from the new sensors will be available.
 
@@
 	\includegraphics[width=\textwidth]{Figures/error_distribution_QRNN-single.pdf} 
-	\caption{Error distributions for deviations of filtered and predicted data to clear-sky simulations.
+	\caption{Error distributions for deviations of filtered and predicted data to NFCS simulations.
 The results are from QRNN-single and channels I1V, I2V and I3V.
@@
 		The values for Bias, mean absolute error(MAE), standard deviation(STD), and measure of skewness(Skewness) are shown.
-Results are from both QRNN-single and QRNN-all for channels I1V, I2V and I3V.
+Results are from both QRNN-single and QRNN-all and for channels I1V, I2V and I3V.
 The number in parentheses is the percentage of cases removed by filtering.
@@
 When filtering is activated, the resulting distributions have a low but asymmetric spread.
-The right side of the distributions follows the measurement noise, as expected.
-The left side has a significantly smaller negative skewness than the measurements.
+The right side of the distributions follows the measurement noise, as expected, but the left side has a significantly smaller negative skewness than the measurements.
 This indicates that 5\,K filter can successfully remove cases associated with high cloud impact.
-However at the same time, the asymmetric error distribution indicates that cases with low cloud impact are erroneously classified as clear-sky.
-
-For a quantitative assessment of the performance achieved with cloud filtering, we calculated the average error bias, MAE (mean absolute error) and standard deviation of the errors.
+However at the same time, the asymmetric error distribution is a result of cases erroneously classified as clear-sky.
+
+For a quantitative assessment of the performance achieved with cloud filtering, we calculated the average error bias, MAE (mean absolute error) and standard deviation of the deviations.
 The asymmetry of error distributions around their mean is also calculated through the measure of skewness.
@@
 The error metrics corresponding to the error distributions described in Fig.~\ref{fig:error_distributions} are provided in Table~\ref{tab:error_statistics_ici} under label "Filtered(5\,K)".
-The average bias in I1V measurements is -1.88\,K, and rejecting around 6\% of the cases as cloudy reduces the bias to -0.32\,K.
+The average bias in I1V measurements is -1.88\,K, and rejecting around 6\% of the cases as cloudy, reduces the bias to -0.32\,K.
 The standard deviation also reduces to 1.07\,K from 8.84\,K.
@@
 Using all 183\,GHz channels concurrently has no notable impact on the cloud filtering.
-Almost similar statistics are obtained from QRNN-single and QRNN-all.
+Almost similar statistics are obtained from both models.
+
 Overall for all three channels, the notable decrease in the errors indicates that the cloud filter is effective in removing most of the cloudy cases, however few cases with low cloud impact still pass through the filter and deteriorate the performance.

### 2020-09-24 Article/ici_submm_cloudcorr.tex
Added definitions of quantile loss and CRPS.

@@
 The task that we aim to solve in this study is to predict the NFCS brightness
-temperatures $\ynfcs$ at a given $187\unit{GHz}$ channel from a vector of
+temperature $\ynfcs$ at a given $187\unit{GHz}$ channel from a vector of
 cloud-contaminated observations $\y$. Since the information-content of the
@@
 The median is used as point estimate for the corrected $\ynfcs$.
+
+QRNN's are trained to minimize the mean of the quantile loss functions
+%
+\begin{align}
+  \mathcal{L}_\tau(y_\tau, y) &=
+  \begin{cases}
+    \tau|y - y_\tau|, & y_\tau < y \\ (1 - \tau)|y_\tau - y|, & \text{otherwise}
+    \\
+  \end{cases}
+\end{align}
+%
+for all predicted quantile fractions $\tau$, where $\y_\tau$ is the predicted
+quantile and $y$ the reference value from the training set. The quantile loss is
+used in this study as a performance criterion for the tuning of the hyper
+parameters of the QRNN. In addition to the quantile loss, also the Continuously
+Ranked Probability Score (CRPS) is considered. Given a predicted cumulative
+distribution function (CDF) $F$ and the reference value $y$, the CRPS is defined as
+%
+\begin{align}
+  \text{CRPS}(F, y) = \int_{-\infty}^{\infty} \left (F(y') - y\right )^2\: dy'.
+\end{align}
+%
+To compute the CRPS for a predictions from a QRNN, the predicted quantiles are
+used to derive a piece-wise linear approximation of the CDF of the predicted
+distribution and evaluate the above integral.
 
@@
 
-The implementation of QRNN is based on PyTorch, an open source machine learning library \citep{paszke2017automatic}.
-It is developed and available as a part of \textit{typhon:tools for atmospheric research} software package [\todo{developer's version??}].
+The implementation of QRNN is based on PyTorch, an open source machine learning
+library \citep{paszke2017automatic}. It is developed and available as a part of
+\textit{typhon:tools for atmospheric research} software package
+       [\todo{developer's version??}].
 

### 2020-09-24 setup.py

@@ -12,9 +12,9 @@ setup(
     long_description=long_description,
     long_description_content_type='text/markdown',  # Optional (see note above)
     url='https://github.com/simonpf/aws',  # Optional
-    author='Simon Pfreundschuh, Patrick Eriksson, Inderpreet Kaur',  # Optional
+    author='Simon Pfreundschuh'
     author_email='simon.pfreundschuh@chalmers.se',  # Optional
-    install_requires=["artssat"],
+    install_requires=["scikitimage", "requests", "appdirs"],
     packages=["aws"],
     python_requires='>=3.6',
     project_urls={  # Optional

### 2020-09-24 Article/ici_submm_cloudcorr.tex
started writing conclusions

--- 2020-09-24 Article/ici_submm_cloudcorr.tex
@@
 %
-To be written \dots
+
+In this study, quantile regression neural network is used for filtering and correction of cloud contamination in 183\,GHz channels.
+QRNN is a neural network which estimates the posterior distribution of target variable through quantiles.
+It is demonstrated that QRNN can combine data from 183\,GHz channels and the available sub-mm frequencies to provide channel specific NFCS predictions.
+Application of QRNN to data from three different satellite instruments is presented.
+
+QRNN based filtering is only partially successful in removing the cloudy data.
+The cloudy cases falsely classified as clear introduce a negative bias in the filtered data.
+This is not optimal solution, but in agreement with what can be achieved with the present instruments.
+
+Since the present sensors lack any sub-mm channels, to investigate the applicaibility to present sensors and also emphasize the benefit of high frequency channels, a QRNN model using only 183\,GHz data is also investigated.
+This allows us to
+
+The 183\,GHz channels and the sub-mm channels are sensitive to different parts of the troposphere.
+When all of them are considered together, the weighting functions of sub-mm channels can provide only a partially complete coverage to the hydrometeor impact.
+For the outermost 183\,GHz channels, there always exists a part of troposphere where hydrometeor impact cannot be covered.
+
+A slightly lower accuracy was observed for cases with high cloud impact.
+In few of such cases, the predicted NFCS values were not completely cloud free.
+This is expected as not all cases can be represented by the a priori distribution QRNN trains on.
+Predictions for \textit{out-of-distribution} cases is always a challenging task for deep learning algorithms and  shall always limit the performance.
+Improving the representation of such cases in the a priori distribution can help alleviate this problem.
+However since such cases are few, filtering them out results in highly accurate NFCS predictions with minimal reduction in data.
+
+The robustness of QRNN was also demonstrated by application to a smaller satellite missions AWS, where only one of the higher frequencies is available.
+The same approach was applicable in this case, and the results proved that only one sub-mm channel is also sufficient enough for cloud correction at 183\,GHz.
+
+The method is applied to channels from three different instruments : ICI, MWI and AWS.
 

### 2020-09-24 ICI/ICI_channel_TB.py
scripts for article Figures and Tables

@@ -1,0 +1,35 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Fri Aug 28 11:18:03 2020
+
+@author: inderpreet
+"""
+
+
+def ICI_channel_TB(TB, nchannels):
+    """
+    
+
+    Parameters
+    ----------
+    TB : TYPE
+        DESCRIPTION.
+    nchannels : TYPE
+        DESCRIPTION.
+
+    Returns
+    -------
+    TB_ICI : TYPE
+        DESCRIPTION.
+
+    """
+    n = int(nchannels/2)
+    TB_ICI = TB.copy(deep = True, data= None)[:, :,  0:n, :]
+
+    for ic in range(n):
+        print ('total_channels', ic, nchannels-ic-1)
+        ic1 = ic
+        ic2 = nchannels-ic-1
+        TB_ICI[:, :, ic, :]= (TB[:, :, ic1, :] + TB[:, :,  ic2, :])/2
+    return TB_ICI

### 2020-09-24 ICI/PDF_uncertainty.py

@@ -36,14 +36,16 @@ def PDF_uncertainty_bins(y_pre, y0, ulim):
     
     im = np.logical_and((uncertain < ulim[1]), ( uncertain >= ulim[0]) )
     hist1 = np.histogram(dtb[im], bins, density = True)
-    
+ 
+#    im = np.logical_and((uncertain < ulim[2]), ( uncertain >= ulim[1]) )
+#    hist2 = np.histogram(dtb[im], bins, density = True)
 
     
     im = uncertain >=ulim[1]
     hist2 = np.histogram(dtb[im], bins, density = True)
     
     
-    return hist0[0], hist1[0], hist2[0], bins
+    return hist0[0], hist1[0],  hist2[0], bins
 #%%
 
 #%% input parameters
@@ -82,6 +84,7 @@ for i,target in enumerate(targets):
     ax[i].plot(center, hist0, 'k', linewidth = 2.5)
     ax[i].plot(center, hist1, 'r', linewidth = 2.5)
     ax[i].plot(center, hist2, 'b', linewidth = 2.5)
+#    ax[i].plot(center, hist3, 'g', linewidth = 2.5)
     ax[i].xaxis.set_minor_locator(MultipleLocator(5))
     ax[i].grid(which = 'both', alpha = 0.4)
     
@@ -94,9 +97,11 @@ ax[2].set_yticklabels([])
 ax[1].legend([  '0 - ' + str(ulim[0]) + ' K',
             str(ulim[0]) +' - ' + str(ulim[1]) + ' K',
              '> ' + str(ulim[1]) + ' K' ], title = "uncertainty bins (2$\sigma$)", prop={'size': 24}, \
-             frameon = False, bbox_to_anchor=(1, 1.0), ncol=4)
+             frameon = False, bbox_to_anchor=(0.85, 1.0), ncol=2)
 
 
 
-fig.savefig('Figures/PDF_uncertainty_bins_QRNN-single.pdf')                               
+fig.savefig('Figures/PDF_uncertainty_bins_QRNN-single.pdf')    
+
+                           
                                 

### 2020-09-24 ICI/arts_output.py

@@ -1,0 +1,101 @@
+# -*- coding: utf-8 -*-
+import xarray
+import numpy as np
+
+class atms():
+    """
+    Defining a new `class` `arts_output` to read the output simulation data from ARTS
+
+    * The results are stored in NetCDF4 format. The siulated brightness temperatures together with the sensor position and viewing angles are stored in the variables y_atms, atms_position and atms_line_of_sight contained in the root of the file structure.
+
+    * The data can be read conveniently using the xarray package.
+
+    * In addition to the simulated brightness temperatures, the results contain the filename that the profile was taken from and the index of the profile in the `inputs` group of the file.
+
+    Dimensions :
+    * atms_channels: 6, atms_stokes_dim: 2, atms_views: 10
+    
+    Dimensions without coordinates:     
+    * atms_channels, atms_stokes_dim, atms_views, cases
+
+    Data variables:
+    * atms_position       (cases, atms_views) float32 ...    
+    * atms_line_of_sight  (cases, atms_views) float32 ...    
+    * y_atms              (cases, atms_views, atms_channels, atms_stokes_dim) float32 
+
+    """
+    
+    def __init__(self, fileName):
+        
+        simulation_results = xarray.open_dataset(fileName)
+        simulation_results
+        self.y_atms = simulation_results["y_atms"][:]
+        self.atms_position = simulation_results["atms_position"][:]
+        self.atms_line_of_sight = simulation_results["atms_line_of_sight"][:]
+            
+        self.input_data = xarray.open_dataset(fileName)    
+
+
+        
+class aws():
+    """
+    Defining a new `class` `arts_output` to read the output simulation data from ARTS
+
+    * The results are stored in NetCDF4 format. The siulated brightness temperatures together with the sensor position and viewing angles are stored in the variables y_atms, atms_position and atms_line_of_sight contained in the root of the file structure.
+
+    * The data can be read conveniently using the xarray package.
+
+    * In addition to the simulated brightness temperatures, the results contain the filename that the profile was taken from and the index of the profile in the `inputs` group of the file.
+
+    Dimensions :
+    * aws_channels: 18, atms_stokes_dim: 2, atms_views: 10
+    
+    Dimensions without coordinates:     
+    * aws_channels, aws_stokes_dim, aws_views, cases
+
+    Data variables:
+    * aws_position       (cases, atms_views) float32 ...    
+    * aws_line_of_sight  (cases, atms_views) float32 ...    
[…]

### 2020-09-24 ICI/calibration.py

@@ -1,0 +1,48 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Fri Sep 11 11:24:04 2020
+
+@author: inderpreet
+"""
+import numpy as np
+
+def calibration(y_pre, y0, im, quantiles):
+    """
+    
+
+    Parameters
+    ----------
+    y_pre : all predicted quantiles
+    y0 : noise free clear-sky simulations
+    im : array containing indices of all cases tobe used in calibration plot
+    quantiles : quantiles used
+
+    Returns
+    -------
+    frequencies (a) for all intervals 
+
+    """
+    intervals = []
+    for i in range(1, 6):
+        intervals.append(quantiles[i] - quantiles[0] )
+    a1 = 0
+    a2 = 0
+    a3 = 0
+    a4 = 0
+    a5 = 0
+    a6 = 0
+    for i in im:
+        if np.logical_and(y0[i] > y_pre[i, 0] ,  y0[i] <=y_pre[i, 1]):
+                   a1 += 1
+        if np.logical_and(y0[i] > y_pre[i, 0] ,  y0[i] <= y_pre[i, 2]):
+                   a2 += 1               
+        if np.logical_and(y0[i] > y_pre[i, 0] ,  y0[i] <= y_pre[i, 3]):
+                   a3 += 1
+        if np.logical_and(y0[i] > y_pre[i, 0] ,  y0[i] < y_pre[i, 4]):
+                   a4 += 1
+        if np.logical_and(y0[i] > y_pre[i, 0] ,  y0[i] < y_pre[i, 5]):
+                   a5 += 1
+        if np.logical_and(y0[i] > y_pre[i, 0] ,  y0[i] < y_pre[i, 6]):
+                   a6 += 1
+    return a1, a2, a3, a4, a5, a6, intervals 

### 2020-09-24 ICI/get_ICI.py

@@ -4,6 +4,9 @@
 Created on Thu Aug 13 11:50:28 2020
 
 @author: inderpreet
+
+Combines data from ARTS simulatons and writes the training and testing datasets
+for ICI 
 """
 
 import os
@@ -43,12 +46,11 @@ nedt  = np.array([0.8, 0.8, 0.8, #183Ghz
                   ])      #664Ghz
 #                  1.2, 1.2])     #183Ghz, MWI
 
-files = glob.glob(os.path.expanduser('~/Dendrite/Projects/AWS-325GHz/\
-                                     ICI_m60_p60/c_**clearsky.nc'))
+files = glob.glob(os.path.expanduser('~/Dendrite/Projects/AWS-325GHz/ICI_m60_p60/c_**clearsky.nc'))
 #%% get dBZ and altitude 
 
-dBZ      = get_y_cloudsat(files[:])
-altitude = get_altitude(files[:])
+# dBZ      = get_y_cloudsat(files[:])
+# altitude = get_altitude(files[:])
 
 #%%
 TB_cs, TB_as  = read_clear_allsky_pairs(files)
@@ -96,13 +98,13 @@ TB_ICI[:, randomList[175000:], :].to_netcdf('TB_ICI_test.nc', 'w')
 
 #%%save dBZ
 
-dBZ      = np.asarray(dBZ)
-altitude = np.asarray(altitude)
-np.save('dbz_train.npy', dBZ[randomList[:175000]])
-np.save('dbz_test.npy', dBZ[randomList[175000:]])
+# dBZ      = np.asarray(dBZ)
+# altitude = np.asarray(altitude)
+# np.save('dbz_train.npy', dBZ[randomList[:175000]])
+# np.save('dbz_test.npy', dBZ[randomList[175000:]])
 
-np.save('alt_train.npy', altitude[randomList[:175000]])
-np.save('alt_test.npy', altitude[randomList[175000:]])
+# np.save('alt_train.npy', altitude[randomList[:175000]])
+# np.save('alt_test.npy', altitude[randomList[175000:]])
 
 
 

### 2020-09-24 ICI/get_MWI.py

@@ -1,0 +1,102 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Thu Aug 13 11:50:28 2020
+
+@author: inderpreet
+
+Combines data from all ARTS simulations and writes the training and testing datasets
+for MWI channels
+"""
+
+
+import os
+import numpy as np
+import matplotlib.pyplot as plt
+import glob
+from polarisation import calculate_polarisation
+from read_ARTS_output import read_all_files
+import xarray
+from add_gaussian_noise import add_gaussian_noise
+from read_clear_allsky_pairs import read_clear_allsky_pairs, read_clear_allsky_pairs_MWI
+#from get_IWP import get_IWP
+from ICI_channel_TB import ICI_channel_TB
+import random
+
+theta = 135.2
+#%%
+def calculate_histogram(TB, bins, channels):
+        hist_arts = []
+        for ic in range(channels):
+            H = np.histogram(TB[:, ic], bins, density = True)
+            hist_arts.append(H[0])   
+
+    
+        return hist_arts
+
+#%%  concatenate all ARTS simulations together         
+f_grid = np.concatenate([183.31 + np.array([-7.0, -3.4, -2.0, 2.0, 3.4, 7.0]),
+                                243.20 + np.array([-2.5, 2.5]),
+                                325.15 + np.array([-9.5, -3.5, -1.5, 1.5, 3.5, 9.5]),
+                                448.00 + np.array([-7.2, -3.0, -1.4, 1.4, 3.0, 7.2]),
+                                664.00 + np.array([-4.2, 4.2]),
+                                183.31 + np.array([-6.1, -4.9, 4.9, 6.1])]) # added two MWI channels
+
+nchannels = len(f_grid)
+nedt  = np.array([0.8, 0.8, 0.8, #183Ghz
+                  1.2, 1.2,      #183Ghz, MWI
+                  0.7, 0.7,      #243Ghz
+                  1.2, 1.3, 1.5, #325Ghz
+                  1.4, 1.6, 2.0, #448Ghz
+                  1.6, 1.6,])    #664Ghz    
+
+
[…]

### 2020-09-24 ICI/ici_mwi.py

@@ -1,0 +1,151 @@
+import numpy as np
+import netCDF4
+import torch
+from add_gaussian_noise import add_gaussian_noise
+from torch.utils.data import Dataset
+
+class iciData(Dataset):
+    """
+    Pytorch dataset for the MWI training data mapped to ICI resolution
+
+    """
+    def __init__(self, path, inChannels, target, T_rec = None, batch_size = None):
+        """
+        Create instance of the dataset from a given file path.
+
+        Args:
+            path: Path to the NetCDF4 containing the data.
+            batch_size: If positive, data is provided in batches of this size
+
+        """
+        super().__init__()
+        
+        self.batch_size = batch_size
+
+        self.file = netCDF4.Dataset(path, mode = "r")
+
+        TB = self.file.variables["TB"][:]
+        channels = self.file.variables["channels"][:]
+        
+        self.surface = self.file.variables["cases"][:]
+        self.channels = inChannels       
+        idx = []
+        
+        for i in range(len(inChannels)):
+
+            idx.append(np.argwhere(channels == inChannels[i])[0][0]) 
+
+       
+        self.index = idx         
+        self.itarget = np.argwhere(np.array(channels) == target)[0]
+                                                                    
+                                
+       
+        C = []
+        
+        for i in range(len(inChannels)):
+            ic = self.index[i]
+            C.append(TB[1, :, ic])
+
+        self.x = np.float32(np.stack(C, axis = 1))
+        
+        #store mean and std to normalise data  
+        x_noise = self.add_noise(self.x, self.index)
+  
+        self.std = np.std(x_noise, axis = 0)
+        self.mean = np.mean(x_noise, axis = 0)   
+        
+        self.y = np.float32(TB[0, :, self.itarget[0]])
+   
+        self.y_noise = self.add_noise(self.y, self.itarget)     
+        self.x = self.x.data
+        self.y = self.y.data
+        self.y_noise = self.y_noise.data
+        
+
+
+    def __len__(self):
+        """
+        The number of entries in the training data. This is part of the
+        pytorch interface for datasets.
+
+        Return:
+            int: The number of samples in the data set
+        """
+        if self.batch_size is None:
+            return self.x.shape[0]
+        else:
+            return int(np.ceil(self.x.shape[0] / self.batch_size))
+
+    def __getitem__(self, i):
+        """
+        Return element from the dataset. This is part of the
+        pytorch interface for datasets.
+
+        Args:
[…]

### 2020-09-24 ICI/ici_mwi_alone.py

@@ -1,0 +1,151 @@
+import numpy as np
+import netCDF4
+import torch
+from add_gaussian_noise import add_gaussian_noise
+from torch.utils.data import Dataset
+
+class iciData(Dataset):
+    """
+    Pytorch dataset for the ICI training data.
+
+    """
+    def __init__(self, path, inChannels, target, T_rec = None, batch_size = None):
+        """
+        Create instance of the dataset from a given file path.
+
+        Args:
+            path: Path to the NetCDF4 containing the data.
+            batch_size: If positive, data is provided in batches of this size
+
+        """
+        super().__init__()
+        
+        self.batch_size = batch_size
+
+        self.file = netCDF4.Dataset(path, mode = "r")
+
+        TB = self.file.variables["TB"][:]
+        channels = self.file.variables["channels"][:]
+        
+        self.surface = self.file.variables["cases"][:]
+        self.channels = inChannels       
+        idx = []
+        
+        for i in range(len(inChannels)):
+
+            idx.append(np.argwhere(channels == inChannels[i])[0][0]) 
+
+       
+        self.index = idx         
+        self.itarget = np.argwhere(np.array(channels) == target)[0]
+                                                                    
+                                
+       
+        C = []
+        
+        for i in range(len(inChannels)):
+            ic = self.index[i]
+            C.append(TB[1, :, ic])
+
+        self.x = np.float32(np.stack(C, axis = 1))
+        
+        #store mean and std to normalise data  
+        x_noise = self.add_noise(self.x, self.index)
+  
+        self.std = np.std(x_noise, axis = 0)
+        self.mean = np.mean(x_noise, axis = 0)   
+        
+        self.y = np.float32(TB[0, :, self.itarget[0]])
+   
+        self.y_noise = self.add_noise(self.y, self.itarget)     
+        self.x = self.x.data
+        self.y = self.y.data
+        self.y_noise = self.y_noise.data
+        
+
+
+    def __len__(self):
+        """
+        The number of entries in the training data. This is part of the
+        pytorch interface for datasets.
+
+        Return:
+            int: The number of samples in the data set
+        """
+        if self.batch_size is None:
+            return self.x.shape[0]
+        else:
+            return int(np.ceil(self.x.shape[0] / self.batch_size))
+
+    def __getitem__(self, i):
+        """
+        Return element from the dataset. This is part of the
+        pytorch interface for datasets.
+
+        Args:
[…]

### 2020-09-24 ICI/plot_QRNN_output.py

@@ -26,15 +26,15 @@ width     = 128
 quantiles = np.array([0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998])
 batchSize = 128
 
-targets = ['I2V']
+targets = ['I1V']
 test_file = "TB_ICI_test.nc"
 
 iq = np.argwhere(quantiles == 0.5)[0,0]
 
 #%% Plot the output of QRNN, posteriori distribution
 
-fig, ax = plt.subplots(1, 1, figsize = [8, 8])
-
+fig, ax = plt.subplots(1, 1, figsize = [12, 8])
+x = np.arange(-3, 4, 1)
 for i,target in enumerate(targets):
     inChannels = np.array([target, 'I5V' , 'I6V', 'I7V', 'I8V', 'I9V', 'I10V', 'I11V'])
     data = iciData(test_file, 
@@ -52,29 +52,33 @@ for i,target in enumerate(targets):
                                  (np.abs(y_pre[:, 5] - y_pre[:, 1])> 10), 
                   (np.abs(y_pre[:, 5] - y_pre[:, 1])< 20)))[0]  
     for i in im[0:1]:
-        ax.plot(y_pre[i, :], quantiles,  '-ro',  linewidth = 2.5)
+        ax.plot(quantiles,  y_pre[i, :], '-ro',  linewidth = 2.5)
         
     im = np.where(np.logical_and(((y_pre[:, 3]).astype(int) == 270),\
                                  (np.abs(y_pre[:, 5] - y_pre[:, 1])< 10)))[0]  
     for i in im[0:1]:
-        ax.plot(y_pre[i, :], quantiles,  '-bo',  linewidth = 2.5)
+        ax.plot( quantiles, y_pre[i, :],  '-bo',  linewidth = 2.5)
         
     im = np.where(np.logical_and(((y_pre[:, 3]).astype(int) == 270),\
                                  (np.abs(y_pre[:, 5] - y_pre[:, 1])> 20)))[0]
    
     for i in im[0:1]:
-        ax.plot(y_pre[i, :], quantiles,  '-ko',  linewidth = 2.5)    
-ax.set_ylabel('Quantiles')
-ax.set_xlabel('TB[K]')
-y = np.arange(-3, 4, 1)
-#ax.set_yticks(y)
[…]

### 2020-09-24 ICI/plot_calibration.py

@@ -1,0 +1,119 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Mon Sep  7 20:46:41 2020
+
+@author: inderpreet
+This code plots the calibration curves for both QRNN-single and QRNN-all
+"""
+import matplotlib.pyplot as plt
+import numpy as np
+import netCDF4
+
+from matplotlib.ticker import (MultipleLocator, FormatStrFormatter,
+                               AutoMinorLocator)
+from typhon.retrieval.qrnn import set_backend, QRNN
+set_backend("pytorch")
+import stats as S
+from ici import iciData
+from calibration import calibration
+import random
+plt.rcParams.update({'font.size': 26})
+
+
+#%% input parameters
+depth     = 4
+width     = 128
+quantiles = np.array([0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998])
+batchSize = 128
+
+target = 'I3V'
+
+
+inChannels = np.array(['I1V', 'I2V', 'I3V', 'I5V' , 'I6V', 'I7V', 'I8V', 'I9V', 'I10V', 'I11V'])
+#inChannels = np.array(['I1V', 'I2V', 'I3V', 'MWI-15', 'MWI-16', 'I5V', 'I6V', 'I7V', 'I8V', 'I9V', 'I10V', 'I11V', 'I11H'])
+inChannels = np.array([target, 'I5V' , 'I6V', 'I7V', 'I8V', 'I9V', 'I10V', 'I11V'])
+i183, = np.argwhere(inChannels == target)[0]
+
+binstep = 0.5
+bins = np.arange(-20, 15, binstep)
+iq = np.argwhere(quantiles == 0.5)[0,0]
+
+#%% read input data
+data = iciData("TB_ICI_test.nc", 
+               inChannels, target, 
+               batch_size = batchSize)  
+
+file = 'qrnn_ici_%s_%s_%s_single.nc'%(depth, width, target)
+print (file)
+qrnn = QRNN.load(file)
+
+y_pre, y_prior, y0, y, y_pos_mean = S.predict(data, qrnn, add_noise = True)
+
+# calibration plot data with correction greater than 15K
+
+fig, ax = plt.subplots(1, 1, figsize = [8,8])   
+
+im = np.arange(0, y0.size, 1)
[…]

### 2020-09-24 ICI/plot_error_by_cloudimpact_mwi.py

@@ -1,0 +1,110 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Fri Sep  4 22:54:58 2020
+
+@author: inderpreet
+
+plot error distributions in different cloud impact bins
+"""
+
+import matplotlib.pyplot as plt
+import numpy as np
+import netCDF4
+import stats as S
+from ici import iciData
+plt.rcParams.update({'font.size': 32})
+from matplotlib.ticker import (MultipleLocator, FormatStrFormatter,
+                               AutoMinorLocator)
+
+from typhon.retrieval.qrnn import set_backend, QRNN
+set_backend("pytorch")
+
+#%%
+def PDF_uncertainty_bins(y_pre, y0, y_prior, ulim):
+    dtb =(y_pre[:, 3] - y0)
+    uncertain = np.abs(y_prior - y0)
+ #I1V
+    #ulim = [3, 4] #I2V
+    #ulim = [1, 1.5 ]#I3V
+    
+    im = uncertain < ulim[0]
+    print (np.sum(im))
+    bins = np.arange(-20.0, 10., 0.8)
+    hist0 = np.histogram(dtb[im], bins, density = True)
+    
+    
+    im = np.logical_and((uncertain < ulim[1]), ( uncertain >= ulim[0]) )
+    hist1 = np.histogram(dtb[im], bins, density = True)
+ 
+#    im = np.logical_and((uncertain < ulim[2]), ( uncertain >= ulim[1]) )
+#    hist2 = np.histogram(dtb[im], bins, density = True)
+
+    
+    im = uncertain >=ulim[1]
+    hist2 = np.histogram(dtb[im], bins, density = True)
+    
+    
+    return hist0[0], hist1[0],  hist2[0], bins
+#%%
+
+if __name__ == "__main__":
+#%% input parameters
+    depth     = 4
+    width     = 128
+    quantiles = np.array([0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998])
+    batchSize = 128
+    
+    targets = [ 'I1V', 'MWI-15', 'MWI-16', 'I2V', 'I3V',]
+    
+    binstep = 0.5
+    bins = np.arange(-20, 50, binstep)
+    iq = np.argwhere(quantiles == 0.5)[0,0]
+    ulim = [7.5, 20]
+    test_file = 'TB_ICI_mwi_test.nc'
+    #%% 
+    
+    fig, ax = plt.subplots(1, 5, figsize = [50, 10])
[…]

### 2020-09-24 ICI/plot_error_dist_ici.py

@@ -1,0 +1,89 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Fri Sep  4 21:35:37 2020
+
+@author: inderpreet
+
+this code plots the PDF of the predictions and errors of best estimate (median)
+ICI channels
+"""
+
+
+import matplotlib.pyplot as plt
+import numpy as np
+import stats as S
+from ici import iciData
+plt.rcParams.update({'font.size': 32})
+from matplotlib.ticker import (MultipleLocator, FormatStrFormatter,
+                               AutoMinorLocator)
+
+from typhon.retrieval.qrnn import set_backend, QRNN
+set_backend("pytorch")
+
+#%% input parameters
+depth     = 4
+width     = 128
+quantiles = np.array([0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998])
+batchSize = 128
+
+targets = ['I1V', 'I2V','I3V']
+test_file = "TB_ICI_test.nc"
+output_file = 'Figures/error_distribution_QRNN-single.pdf'
+
+binstep = 0.5
+bins = np.arange(-20, 15, binstep)
+iq = np.argwhere(quantiles == 0.5)[0,0]
+
+#%% Plot error of best estimate for all ICI channels
+
+fig, ax = plt.subplots(1, 3, figsize = [30, 10])
+plt.subplots_adjust(wspace = 0.001)
+for i,target in enumerate(targets):
+    inChannels = np.array([target, 'I5V' , 'I6V', 'I7V', 'I8V', 'I9V', 'I10V', 'I11V'])
+    data = iciData(test_file, 
+                   inChannels, target, 
+                   batch_size = batchSize)  
+
+    i183, = np.argwhere(inChannels == target)[0]
+
+# read QRNN    
+    file = 'qrnn_ici_%s_%s_%s_single.nc'%(depth, width, target)
+    print (file)
+    qrnn = QRNN.load(file)
+    y_pre, y_prior, y0, y, y_pos_mean = S.predict(data, qrnn, add_noise = True)
+    im = np.abs(y_pre[:, iq] - y_prior[:, i183]) < 5
+    hist_noise, hist_pre, hist_prior, hist_pos_mean, hist_pos_mean_5, hist_filter  = \
+        S.calculate_all_histogram(y, y0, y_pre, y_prior, iq, bins, im, i183)
+                                
+                                
+    center = (bins[:-1] + bins[1:]) / 2
+
[…]

### 2020-09-24 ICI/plot_error_dist_mwi.py

@@ -1,0 +1,92 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Fri Sep  4 21:35:37 2020
+
+@author: inderpreet
+
+this code plots the PDF of the predictions and errors of best estimate (median)
+MWI channels predicted using QRNN-mwi
+"""
+
+
+import matplotlib.pyplot as plt
+import numpy as np
+import stats as S
+from ici_mwi_alone import iciData
+plt.rcParams.update({'font.size': 32})
+from matplotlib.ticker import (MultipleLocator, FormatStrFormatter,
+                               AutoMinorLocator)
+from typhon.retrieval.qrnn import set_backend, QRNN
+set_backend("pytorch")
+
+#%% input parameters
+depth     = 4
+width     = 128
+quantiles = np.array([0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998])
+batchSize = 128
+
+targets = [ 'I1V', 'MWI-15', 'MWI-16', 'I2V', 'I3V',]
+targets_mwi = ['MWI-14', 'MWI-15', 'MWI-16', 'MWI-17', 'MWI-18'] 
+test_file = "TB_ICI_mwi_test.nc"
+output_file = 'Figures/error_distribution_MWI-alone.pdf'
+
+binstep = 0.5
+bins = np.arange(-20, 15, binstep)
+iq = np.argwhere(quantiles == 0.5)[0,0]
+
+
+#%% Plot error of best estimate for all ICI channels
+
+fig, ax = plt.subplots(1, 5, figsize = [50, 10])
+plt.subplots_adjust(wspace = 0.001)
+for i,target in enumerate(targets):
+    inChannels_single = np.array(['I1V', 'I2V', 'I3V', 'MWI-15', 'MWI-16'])
+    file_single = 'qrnn_ici_%s_%s_%s_mwi-alone.nc'%(depth, width, target)
+    data = iciData(test_file, 
+                   inChannels_single, target, 
+                   batch_size = batchSize)  
+
+    i183, = np.argwhere(inChannels_single == target)[0]
+
+# read QRNN    
+    file_single = 'qrnn_ici_%s_%s_%s_mwi-alone.nc'%(depth, width, target)
+    print (file_single)
+    qrnn = QRNN.load(file_single)
[…]

### 2020-09-24 ICI/plot_pdf_pred_ici.py

@@ -1,0 +1,119 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Fri Sep  4 21:35:37 2020
+
+@author: inderpreet
+
+this code plots the PDF of the predictions and errors of best estimate (median)
+ICI channels
+"""
+
+
+import matplotlib.pyplot as plt
+import numpy as np
+import stats as S
+from ici_mwi import iciData
+plt.rcParams.update({'font.size': 32})
+from matplotlib.ticker import (MultipleLocator, FormatStrFormatter,
+                               AutoMinorLocator)
+
+from typhon.retrieval.qrnn import set_backend, QRNN
+set_backend("pytorch")
+
+#%% input parameters
+depth     = 4
+width     = 128
+quantiles = np.array([0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998])
+batchSize = 128
+
+targets = ['I1V', 'I2V','I3V']
+test_file = "TB_ICI_test.nc"
+output_file = 'Figures/error_distribution_QRNN-single.pdf'
+
+binstep = 0.5
+bins = np.arange(-20, 15, binstep)
+iq = np.argwhere(quantiles == 0.5)[0,0]
+          
+                                
+#%% plot PDF of the predictions for ICI channels
+
+fig, ax = plt.subplots(1, 3, figsize = [30, 10])
+plt.subplots_adjust(wspace = 0.001)
+bins = np.arange(230, 300, 1)
+
+for i,target in enumerate(targets):
+    inChannels = np.array([target, 'I5V' , 'I6V', 'I7V', 'I8V', 'I9V', 'I10V', 'I11V'])
+    data = iciData(test_file, 
+                   inChannels, target, 
+                   batch_size = batchSize)  
+
+    i183, = np.argwhere(inChannels == target)[0]
+
+# read QRNN    
+    file = 'qrnn_ici_%s_%s_%s_single.nc'%(depth, width, target)
+    print (file)
+    qrnn = QRNN.load(file)
+    y_pre, y_prior, y0, y, y_pos_mean = S.predict(data, qrnn, add_noise = True)
+                               
+    h0 = np.histogram(y0, bins, density = True)
+    h_p = np.histogram(y_pre[:, iq], bins, density = True)
+    center = (bins[:-1] + bins[1:])/2
+
[…]

### 2020-09-24 ICI/plot_predicted_error.py

@@ -1,0 +1,185 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Fri Sep  4 21:35:37 2020
+
+@author: inderpreet
+
+this code plots the PDF of the predicted error and observed error (error  of best estimate (median))
+ICI channels
+"""
+
+
+import matplotlib.pyplot as plt
+import numpy as np
+import stats as S
+from ici import iciData
+plt.rcParams.update({'font.size': 32})
+from matplotlib.ticker import (MultipleLocator, FormatStrFormatter,
+                               AutoMinorLocator)
+
+from typhon.retrieval.qrnn import set_backend, QRNN
+set_backend("pytorch")
+
+#%%
+def sample_posterior(x, nn, y0, y_pre):
+    """
+    estimates histogram of predicted error (random samples drawn from posterior)
+
+    Parameters
+    ----------
+    x : input data for QRNN predictions
+    nn : number of samples required for each case
+    y0 : NFCS simulations
+    y_pre : predicted median
+
+    Returns
+    -------
+    hist_sample : frequency and bins of predicted errors
+    """
+    n = x.shape[0]
+    y_pos = []
+    for i in range(n):
+        y_pos.append(qrnn.sample_posterior(x[i, :], nn))
+    y_pos = np.array(y_pos)
+    
+    d = []
+    for j in range(nn):
+        
+        d.append(y_pos[:, j] - y_pre)
+    d = np.array(d).ravel()    
+    hist_sample = np.histogram(d, bins, density = True)
+    return hist_sample
+
+def predict(test_data, qrnn, add_noise = False):
+    """
+    predict the posterior mean and median
+    """
+    if add_noise:
+        x_noise = test_data.add_noise(test_data.x, test_data.index)
+        x = (x_noise - test_data.mean)/test_data.std
+        y_prior = x_noise
+        y = test_data.y_noise
+        
+        y0 = test_data.y
+    else:
+        x = (test_data.x - test_data.mean)/test_data.std
+        y_prior = test_data.x
+        y = test_data.y
+        y0 = test_data.y0
+
+
+    y_pre = qrnn.predict(x.data)
+    y_pos_mean = qrnn.posterior_mean(x.data)
+    
[…]

### 2020-09-24 ICI/plot_uncertainty.py

@@ -1,0 +1,94 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Sat Sep 12 22:09:27 2020
+
+@author: inderpreet
+
+PLot the uncertainties in randomly chosen cases
+"""
+import matplotlib.pyplot as plt
+import numpy as np
+import netCDF4
+
+from matplotlib.ticker import (MultipleLocator, FormatStrFormatter,
+                               AutoMinorLocator)
+from typhon.retrieval.qrnn import set_backend, QRNN
+set_backend("pytorch")
+import stats as S
+from ici import iciData
+from calibration import calibration
+import random
+plt.rcParams.update({'font.size': 26})
+
+
+#%% input parameters
+depth     = 4
+width     = 128
+quantiles = np.array([0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998])
+batchSize = 128
+
+target = 'I2V'
+
+
+inChannels = np.array(['I1V', 'I2V', 'I3V', 'I5V' , 'I6V', 'I7V', 'I8V', 'I9V', 'I10V', 'I11V'])
+#inChannels = np.array(['I1V', 'I2V', 'I3V', 'MWI-15', 'MWI-16', 'I5V', 'I6V', 'I7V', 'I8V', 'I9V', 'I10V', 'I11V', 'I11H'])
+inChannels = np.array([target, 'I5V' , 'I6V', 'I7V', 'I8V', 'I9V', 'I10V', 'I11V'])
+i183, = np.argwhere(inChannels == target)[0]
+
+binstep = 0.5
+bins = np.arange(-20, 15, binstep)
+iq = np.argwhere(quantiles == 0.5)[0,0]
+
+#%% Uncertainty plot
+plt.rcParams.update({'font.size': 26})
+inChannels = np.array([target, 'I5V' , 'I6V', 'I7V', 'I8V', 'I9V', 'I10V', 'I11V'])
+i183, = np.argwhere(inChannels == target)[0]
+data = iciData("TB_ICI_test.nc", 
+               inChannels, target, 
+               batch_size = batchSize)  
+
+file = 'qrnn_ici_%s_%s_%s_single.nc'%(depth, width, target)
+print (file)
+qrnn = QRNN.load(file)
+
[…]

### 2020-09-24 ICI/read_clear_allsky_pairs.py

@@ -9,8 +9,21 @@ import os
 import xarray
 
 def read_clear_allsky_pairs(files_clearsky):
+    """
+    find the pairs of clearsky and allsky cases from ARTS simulations 
+
+    Parameters
+    ----------
+    files_clearsky : list containing clearsky files
+
+    Returns
+    -------
+    y_ici_cs : TB for clearsky cases
+    y_ici_as : TB for all sky cases
+    """
 
     first_iteration = True
+    
     for file_clearsky in files_clearsky[:]:
         file_allsky = file_clearsky.replace('_clearsky.nc', '.nc')
         

### 2020-09-24 ICI/stats.py

@@ -51,8 +51,9 @@ def calculate_all_histogram(y, y0, y_pre, y_prior, iq, bins, im, i183):
     
 
     hist_pos_mean_5  = calculate_pdf(y_pre[:, iq], y0, bins, im)
+    hist_filter  = calculate_pdf(y_prior[:, i183], y0, bins, im)
     
-    return hist_noise, hist_pre, hist_prior, hist_pos_mean, hist_pos_mean_5    
+    return hist_noise, hist_pre, hist_prior, hist_pos_mean, hist_pos_mean_5, hist_filter    
 
 def calculate_pdf(y, y0, bins, im = None):
 
@@ -69,28 +70,32 @@ def calculate_bias(y_prior, y0, y, y_pos_mean, im, itarget):
     b1  = np.mean(y_prior[:, itarget] - y0)
     b2a = np.mean(y_pos_mean - y0) 
     b2b = np.mean(y_pos_mean[im] - y0[im])
-    return b0, b1, b2a, b2b
+    b1_filter = np.mean(y_prior[im, itarget] - y0[im])
+    return b0, b1, b2a, b2b, b1_filter
 
 def calculate_std(y_prior, y0, y, y_pos_mean, im, itarget):  
     std0  = np.std(y - y0)
     std1  = np.std(y_prior[:, itarget] - y0)
     std2a = np.std(y_pos_mean - y0)
     std2b = np.std(y_pos_mean[im] - y0[im])
-    return std0, std1, std2a, std2b
+    std1_filter  = np.std(y_prior[im, itarget] - y0[im])
+    return std0, std1, std2a, std2b, std1_filter
 
 def calculate_mae(y_prior, y0, y, y_pos_mean, im, itarget): 
     mae0  = np.mean(np.abs(y - y0))
     mae1  = np.mean(np.abs(y_prior[:, itarget] - y0))
     mae2a = np.mean(np.abs(y_pos_mean - y0)) 
     mae2b = np.mean(np.abs(y_pos_mean[im] - y0[im]))
-    return mae0, mae1, mae2a, mae2b
+    mae1_filter  = np.mean(np.abs(y_prior[im, itarget] - y0[im]))
+    return mae0, mae1, mae2a, mae2b, mae1_filter
 
 def calculate_skew(y_prior, y0, y, y_pos_mean, im, itarget):
     skew0  = skew(y - y0)
     skew1  = skew(y_prior[:, itarget] - y0)
     skew2a = skew(y_pos_mean - y0)
[…]

### 2020-09-24 ICI/tables_ici.py

@@ -1,0 +1,137 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Fri Sep 11 21:57:41 2020
+
+@author: inderpreet
+
+calculate statistics for ICI point estimates, the results are given in latex format
+"""
+
+
+import matplotlib.pyplot as plt
+import numpy as np
+import stats as S
+from ici import iciData
+plt.rcParams.update({'font.size': 26})
+from typhon.retrieval.qrnn import set_backend, QRNN
+set_backend("pytorch")
+import stats
+from tabulate import tabulate
+#%%
+def read_qrnn(file, inChannels, target):
+
+    data = iciData(test_file, 
+                   inChannels, target, 
+                   batch_size = batchSize)  
+
+
+
+# read QRNN    
+#    file = 'qrnn_ici_%s_%s_%s_single.nc'%(depth, width, target)
+#    print (file)
+    qrnn = QRNN.load(file)
+    y_pre, y_prior, y0, y, y_pos_mean = S.predict(data, qrnn, add_noise = True)
+    
+    return y_pre, y_prior, y0, y, y_pos_mean
+
+def correction(y_pre, y_prior, i183):    
+    bins = np.arange(-100, 30, 2)
+    im = np.abs(y_pre[:, 3] - y_prior[:, i183]) >= 0.0005
+    
+    cloud = y_prior[im, i183] - y0[im]
+    corr = y_prior[im, i183] - y_pre[im, 3]   
+    
+    hist= np.histogram(cloud, bins, density = True)
+    hist1 = np.histogram(corr, bins, density = True)
+    
+    return hist[0], hist1[0], bins
+
+#%% input parameters
+depth     = 4
+width     = 128
+quantiles = np.array([0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998])
+batchSize = 128
+
+targets = ['I1V', 'I2V', 'I3V']
+test_file = "TB_ICI_test.nc"
+
+iq = np.argwhere(quantiles == 0.5)[0,0]
+
+color = ['k', 'r', 'b']
+
+
+#%%
+fig, ax = plt.subplots(1,1)
+for i,target in enumerate(targets):
+    inChannels_single = np.array([target, 'I5V' , 'I6V', 'I7V', 'I8V', 'I9V', 'I10V', 'I11V'])
[…]

### 2020-09-24 ICI/tables_mwi-alone.py

@@ -1,0 +1,123 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Fri Sep 11 21:57:41 2020
+
+@author: inderpreet
+
+Calculate statistics for point estimates from QRNN-mwi
+"""
+
+
+import matplotlib.pyplot as plt
+import numpy as np
+import stats as S
+from ici_mwi_alone import iciData
+plt.rcParams.update({'font.size': 26})
+from typhon.retrieval.qrnn import set_backend, QRNN
+set_backend("pytorch")
+import stats
+from tabulate import tabulate
+#%%
+def read_qrnn(file, inChannels, target):
+
+    data = iciData(test_file, 
+                   inChannels, target, 
+                   batch_size = batchSize)  
+
+
+
+# read QRNN    
+#    file = 'qrnn_ici_%s_%s_%s_single.nc'%(depth, width, target)
+#    print (file)
+    qrnn = QRNN.load(file)
+    y_pre, y_prior, y0, y, y_pos_mean = S.predict(data, qrnn, add_noise = True)
+    
+    return y_pre, y_prior, y0, y, y_pos_mean
+#%%
+def correction(y_pre, y_prior, i183):    
+    bins = np.arange(-75, 10, 5)
+    im = np.abs(y_pre[:, 3] - y_prior[:, i183]) >=  20
+    
+    cloud = y_prior[im, i183] - y0[im]
+    corr = y_prior[im, i183] - y_pre[im, 3]   
+    
+    hist= np.histogram(cloud, bins, density = True)
+    hist1 = np.histogram(corr, bins, density = True)
+    
+    return hist[0], hist1[0], bins
+
+if __name__ == "__main__":
+
+    #%% input parameters
+    depth     = 4
+    width     = 128
+    quantiles = np.array([0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998])
+    batchSize = 128
+    
+    targets = [ 'I1V',  'MWI-15', 'MWI-16', 'I2V', 'I3V',]
+    #targets = [ 'I1V']
+    test_file = "TB_ICI_mwi_test.nc"
+    
+    iq = np.argwhere(quantiles == 0.5)[0,0]
+    
+    
+    color = ['k', 'b', 'r', 'g','c' ]
+    
+    #%%
+    fig, ax = plt.subplots(1,1)
+    for i,target in enumerate(targets):
[…]

### 2020-09-24 ICI/tables_mwi.py

@@ -1,0 +1,98 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Fri Sep 11 21:57:41 2020
+
+@author: inderpreet
+
+Tables for QRNN-single , MWI-15 and MWI-16
+"""
+
+
+import matplotlib.pyplot as plt
+import numpy as np
+import stats as S
+from ici_mwi import iciData
+plt.rcParams.update({'font.size': 26})
+from matplotlib.ticker import (MultipleLocator, FormatStrFormatter,
+                               AutoMinorLocator)
+
+from typhon.retrieval.qrnn import set_backend, QRNN
+set_backend("pytorch")
+import stats
+from tabulate import tabulate
+#%%
+def read_qrnn(file, inChannels, target):
+
+    data = iciData(test_file, 
+                   inChannels, target, 
+                   batch_size = batchSize)  
+
+
+
+# read QRNN    
+#    file = 'qrnn_ici_%s_%s_%s_single.nc'%(depth, width, target)
+#    print (file)
+    qrnn = QRNN.load(file)
+    y_pre, y_prior, y0, y, y_pos_mean = S.predict(data, qrnn, add_noise = True)
+    
+    return y_pre, y_prior, y0, y, y_pos_mean
+
+
+#%% input parameters
+depth     = 4
+width     = 128
+quantiles = np.array([0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998])
+batchSize = 128
+
+targets = [ 'MWI-15', 'MWI-16']
+test_file = "TB_ICI_mwi_test.nc"
+
+iq = np.argwhere(quantiles == 0.5)[0,0]
+
+#%%
+for i,target in enumerate(targets):
+    
+    inChannels_single = np.array([target, 'I5V' , 'I6V', 'I7V', 'I8V', 'I9V', 'I10V', 'I11V'])     
+    file_single = 'qrnn_ici_mwi_%s_%s_%s_single.nc'%(depth, width, target)
+    data = iciData(test_file, 
+                   inChannels_single, target, 
+                   batch_size = batchSize)  
+
+    i183, = np.argwhere(inChannels_single == target)[0]
+    y_pre, y_prior, y0, y, y_pos_mean = read_qrnn(file_single, inChannels_single, target )
+    im = np.abs(y_pre[:, 3] - y_prior[:, i183]) <= 5
+    print ((1 - np.sum(im)/im.size)* 100)
+    
+    
[…]

### 2020-09-28 Article/ici_submm_cloudcorr.tex
added results with filtering scheme from Buehler et al

@@
 	\label{tab:statistics_mwi-alone}
-	\begin{tabular}{llrr|rrr}
+	\begin{tabular}{llrr|rr|rr}
 		\tophline
-		&&\multicolumn{2}{c|}{Simulations}& \multicolumn{3}{c}{QRNN-single} \\
-		\cline{3-7}
+		&&\multicolumn{2}{c|}{Simulations}& &\multicolumn{3}{c}{QRNN-single} \\
+		\cline{3-4}
+		\cline{6-8}
 		%		\hline
-		&&   Clear-sky &   All-sky &  Filtered(7.5\,K) & Predicted & Predicted(7.5\,K) \\
-		\middlehline
-		MWI-14 		&bias     & -0.00 & -1.86 & -0.50(4.06\%) & -0.14 & -0.12 \\
-					&mae      &  0.96 &  2.58 &  1.25 &  1.12 &  1.00 \\
-					&std      &  1.20 &  9.00 &  1.94 &  1.86 &  1.52 \\
-					&skewness &  0.01 & -8.20 & -3.03 & -0.88 & -2.15 \\ 
-		\middlehline
-		MWI-15 		&bias     & 0.01 & -1.23 & -0.40(2.84\%) & -0.13 & -0.11 \\
-					&mae      & 0.95 &  1.99 &  1.18 &  0.74 &  0.66 \\
-					&std      & 1.20 &  6.55 &  1.73 &  1.32 &  1.11 \\
-					&skewness & 0.01 & -9.67 & -2.34 & -2.44 & -2.89 \\
-		\middlehline	
-		MWI-16 		&bias     & 0.00 &  -0.85 & -0.29(1.94\%) & -0.12 & -0.10 \\
-					&mae      & 0.96 &   1.64 &  1.10 &  0.68 &  0.63 \\
-					&std      & 1.20 &   5.39 &  1.54 &  1.15 &  0.96 \\
-					&skewness & 0.00 & -11.62 & -1.97 & -3.71 & -3.22 \\	
-		\middlehline			
-		MWI-17 		&bias     & -0.00 &  -1.04 & -0.32(2.41\%) & -0.13 & -0.11 \\
-					&mae      &  0.96 &   1.83 &  1.12 &  0.73 &  0.67 \\
-					&std      &  1.20 &   6.29 &  1.59 &  1.21 &  1.02 \\
-					&skewness & -0.01 & -10.69 & -2.13 & -3.45 & -3.23 \\	
-		\middlehline			
-		MWI-18 		&bias     &  0.01 &  -0.66 & -0.26(1.37\%) & -0.12 & -0.10 \\
-					&mae      &  0.96 &   1.47 &  1.08 &  0.80 &  0.76 \\
-					&std      &  1.20 &   4.66 &  1.51 &  1.23 &  1.08 \\
-					&skewness & -0.00 & -12.80 & -2.03 & -2.99 & -2.25 \\	
+		&&   Clear-sky &   All-sky & \multicolumn{2}{c}{Filtered} & \multicolumn{2}{c}{Predicted} \\
+		&&&&						(B183) & (7.5\,K)& (All) & (7.5\,K)\\
+		\middlehline
+		MWI-14 		&Bias     & 0.01 & -1.86 & -0.84(1.95\%) & -0.50(4.04\%) & -0.14 & -0.12 \\
+					&MAE      & 0.96 &  2.59 &  1.58 &  1.26 &  1.13 &  1.00 \\
+					&STD      & 1.20 &  9.02 &  3.27 &  1.96 &  1.87 &  1.53 \\
+					&Skewness & 0.00 & -8.21 & -5.13 & -3.00 & -0.74 & -2.14 \\
+		\middlehline
+		MWI-15 		&Bias     &  0.00 & -1.24 & -0.53(1.95\%) & -0.41(2.81\%) & -0.14 & -0.12 \\
+					&MAE      &  0.96 &  1.99 &  1.30 &  1.19 &  0.74 &  0.66 \\
+					&STD      &  1.20 &  6.55 &  2.15 &  1.74 &  1.32 &  1.12 \\
+					&Skewness & -0.01 & -9.68 & -3.67 & -2.41 & -2.42 & -2.94 \\
+		\middlehline	
+		MWI-16 		&Bias     &  0.00 &  -0.84 & -0.30(1.95\%) & -0.29(1.90\%) & -0.13 & -0.10 \\
+					&MAE      &  0.95 &   1.63 &  1.11 &  1.10 &  0.68 &  0.62 \\
+					&STD      &  1.20 &   5.39 &  1.60 &  1.54 &  1.15 &  0.96 \\
+					&Skewness & -0.02 & -11.62 & -2.55 & -2.00 & -3.87 & -3.35 \\	
+		\middlehline			
+		MWI-17 		&Bias     &  0.01 &  -1.06 & -0.40(1.95\%) & -0.34(2.36\%) & -0.13 & -0.11 \\
+					&MAE      &  0.95 &   1.83 &  1.18 &  1.13 &  0.73 &  0.67 \\
+					&STD      &  1.20 &   6.29 &  1.83 &  1.61 &  1.22 &  1.03 \\
+					&Skewness & -0.01 & -10.72 & -3.27 & -2.20 & -3.48 & -3.17 \\
+		\middlehline			
+		MWI-18 		&Bias     &  0.00 &  -0.65 & -0.22(1.95\%) & -0.25(1.39\%) & -0.11 & -0.09 \\
+					&MAE      &  0.96 &   1.47 &  1.06 &  1.08 &  0.80 &  0.75 \\
+					&STD      &  1.20 &   4.65 &  1.45 &  1.51 &  1.23 &  1.08 \\
+					&Skewness & -0.01 & -12.84 & -1.87 & -2.09 & -2.88 & -2.40 	\\
 		\bottomhline				
@@
 \end{figure}
-QRNN-mwi is designed to provide basis for a cloud correction approach applicable to current satellites, which lack the higher frequency channels.
-
+QRNN-mwi is designed to provide basis for a cloud correction approach applicable to current satellites, that lack the higher frequency channels.
 Table~\ref{tab:statistics_mwi-alone} shows the results for all 183\,GHz channels of MWI.
@@
 As a consequence, the predictions are poor.
-In constrast, the clear-sky measurements of the same scene from multiple channels, reinforces the QRNN predictions.
+In contrast, the clear-sky measurements of the same scene from multiple channels, reinforces the QRNN predictions.
 The measurement noise in all channels is stationary and uncorrelated, thus the predictions benefit from the additional information, and averaging cancels out the noise component.
@@
 		\middlehline
-		AWS-32  &bias     & 0.00 & -1.32 & -0.26 & -0.03 & -0.02 \\
-				&mae      & 0.36 &  1.57 &  0.52 &  0.54 &  0.43 \\
-				&std      & 0.46 &  6.42 &  0.85 &  1.02 &  0.61 \\
+		AWS-32  &Bias     & 0.00 & -1.32 & -0.26 & -0.03 & -0.02 \\
+				&MAE      & 0.36 &  1.57 &  0.52 &  0.54 &  0.43 \\
+				&STD      & 0.46 &  6.42 &  0.85 &  1.02 &  0.61 \\
 				&skewness & 0.01 & -8.43 & -3.65 & -0.07 & -1.98 \\
@@
 
+\todo{incomplete}
+
 In this study, quantile regression neural network is used for filtering and correction of cloud contamination in 183\,GHz channels.
@@
 This is not optimal solution, but in agreement with what can be achieved with the present instruments.
-
-Since the present sensors lack any sub-mm channels, to investigate the applicaibility to present sensors and also emphasize the benefit of high frequency channels, a QRNN model using only 183\,GHz data is also investigated.
-This allows us to
+The robustness of QRNN was also demonstrated by application to a smaller satellite missions AWS, where only one of the higher frequencies is available.
+The same approach was applicable in this case, and the results proved that even one sub-mm channel is sufficient enough for cloud correction at 183\,GHz.
+Since the present sensors lack any sub-mm channels, to investigate the applicability to present sensors and also emphasize the benefit of high frequency channels, a QRNN model using only 183\,GHz data is also investigated.
 
@@
 For the outermost 183\,GHz channels, there always exists a part of troposphere where hydrometeor impact cannot be covered.
-
 A slightly lower accuracy was observed for cases with high cloud impact.
@@
 
-The robustness of QRNN was also demonstrated by application to a smaller satellite missions AWS, where only one of the higher frequencies is available.
-The same approach was applicable in this case, and the results proved that only one sub-mm channel is also sufficient enough for cloud correction at 183\,GHz.
-
-The method is applied to channels from three different instruments : ICI, MWI and AWS.
-
 %% The following commands are for the statements about the availability of data sets and/or software code corresponding to the manuscript.

### 2020-09-28 ICI/tables_mwi-alone.py

@@ -18,6 +18,7 @@ from typhon.retrieval.qrnn import set_backend, QRNN
 set_backend("pytorch")
 import stats
 from tabulate import tabulate
+from filter_buehler import filter_buehler_19, filter_buehler_20
 #%%
 def read_qrnn(file, inChannels, target):
 
@@ -25,11 +26,6 @@ def read_qrnn(file, inChannels, target):
                    inChannels, target, 
                    batch_size = batchSize)  
 
-
-
-# read QRNN    
-#    file = 'qrnn_ici_%s_%s_%s_single.nc'%(depth, width, target)
-#    print (file)
     qrnn = QRNN.load(file)
     y_pre, y_prior, y0, y, y_pos_mean = S.predict(data, qrnn, add_noise = True)
     
@@ -47,16 +43,16 @@ def correction(y_pre, y_prior, i183):
     
     return hist[0], hist1[0], bins
 
+#%%
 if __name__ == "__main__":
-
-    #%% input parameters
+    # input parameters
     depth     = 4
     width     = 128
     quantiles = np.array([0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998])
     batchSize = 128
     
     targets = [ 'I1V',  'MWI-15', 'MWI-16', 'I2V', 'I3V',]
-    #targets = [ 'I1V']
+ #   targets = [ 'I1V']
     test_file = "TB_ICI_mwi_test.nc"
     
     iq = np.argwhere(quantiles == 0.5)[0,0]
@@ -65,33 +61,49 @@ if __name__ == "__main__":
     color = ['k', 'b', 'r', 'g','c' ]
     
     #%%
+    inChannels_single = np.array(['I1V', 'I2V', 'I3V', 'MWI-15', 'MWI-16'])
+    target = 'I1V'
+    data = iciData(test_file, 
+                   inChannels_single, target, 
+                   batch_size = batchSize)  
+    im_b = filter_buehler_19(data)
+ #   im_b = filter_buehler_20(data)
+    
     fig, ax = plt.subplots(1,1)
     for i,target in enumerate(targets):
+        print ('doing channel %s'%target)
         inChannels_single = np.array(['I1V', 'I2V', 'I3V', 'MWI-15', 'MWI-16'])
         file_single = 'qrnn_ici_%s_%s_%s_mwi-alone.nc'%(depth, width, target)
+
         print (file_single)
         i183, = np.argwhere(inChannels_single == target)[0]
[…]

### 2020-09-28 Article/ici_submm_cloudcorr.tex
added description of filtering with Buehler_etal

@@
 The lower prediction accuracy of I1V can be explained by the fact that it is the outermost 183\,GHz channel.
-The other sub-mm channels cannot provide a full coverage for the hydrometeor impact in I1V.
+Compared to other higher peaking channels, it has a higher concentration of cloudy cases or cases contaminated with surface effects.
+All the sub-mm channels collectively cannot provide a full coverage for the hydrometeor impact in I1V.
 Depending upon the atmospheric scenarios, there is always a portion of data detected by I1V, but never seen by any other channel.
 Though such cases are few, QRNN cannot learn to predict the clear-sky values accurately for cases which lie outside the coverage area.
-Besides this, lower representation of high cloud impact cases in the training set also affects QRNN accuracy.
+Besides this, lower representation of high cloud impact cases in the training set is another factor which affects QRNN accuracy.
 
@@
 In this section, we discuss results when all 183\,GHz MWI channels are used for ``self'' cloud filtering/correction (QRNN-mwi).
-We also describe the performance of QRNN when sub-mm channels from ICI are used to train MWI channels.
+QRNN-mwi is designed to provide basis for a cloud filtering/correction approach applicable to current satellites, that lack the higher frequency channels.
+A comparison to an existing cloud filtering scheme described by \citet{buehler:aclou:07} is also discussed.
+Furthermore the we extend the prediction approach to include ICI sub-mm channels for cloud correction of MWI channels.
 \subsubsection{MWI alone}
 %
+\paragraph{Comparison to \citet{buehler:aclou:07}}
+
 %t
 \begin{table*}[t]
-	\caption{Error statistics for predictions from QRNN-mwi. The labels Filtered(7.5\,K), Predicted(All) and Predicted(7.5\,K) are same as described in Table~\ref{tab:error_statistics_ici}}
+	\caption{Error statistics for predictions from QRNN-mwi.
+The results from filtering approach described by \citet{buehler:aclou:07} are listed under ``B183''.
+The labels Filtered(7.5\,K), Predicted(All) and Predicted(7.5\,K) are same as described in Table~\ref{tab:error_statistics_ici}}
 	\label{tab:statistics_mwi-alone}
@@
 		\tophline
-		&&\multicolumn{2}{c|}{Simulations}& &\multicolumn{3}{c}{QRNN-single} \\
+		&&\multicolumn{2}{c|}{Simulations}& &\multicolumn{3}{c}{QRNN-mwi} \\
 		\cline{3-4}
@@
 \end{table*}
+
+In the study by \citet{buehler:aclou:07}, they used brightness temperature based threshold to filter out cloudy cases, using Advanced Microwave Sounding Unit B (AMSU-B).
+They recommend to a viewing angle dependent brightness temperature threhold at $183.31\pm1.00$ \,GHz and brightness temperature difference between $183.31\pm3.00$ and $183.31\pm 1.00$ as a measure of cloud impact.
+Further in the text we refer this scheme as ``B183''.
+MWI lacks identical 183\,GHz channels as AMSU-B, so we chose the next nearest available frequencies.
+We use brightness temperatures from MWI-18 (TB-MWI18) is used as proxy for $183.31\pm1.00$ \,GHz and MWI-17 for $183.31\pm3.00$ (TB-MWI17).
+All cases with TB-MWI18 < 235.2\,K or TB-MWI17 - TB-MWI18 < 0 are classified as cloudy.
+The TB-MWI18 threshold is taken from Table 1 of \citet{buehler:aclou:07} for viewing angle $44.55^\circ$.
+This filter is not channel specific, thus same filter is applied to MWI 183\,GHz channels.
+Table~\ref{tab:statistics_mwi-alone} shows a comparison of results from B183 and QRNN based cloud filtering.
+Due to higher measurement uncertainty in MWI than ICI, a higher filtering threshold is selected.
+All cases with cloud correction greater than 7.5\,K are considered as cloudy and filtered out.
+
+The B183 filter classifies only 1.95\% of the total data as cloudy.
+For all five channels, rejecting these cases reduces the cloud impact significantly, but not fully.
+For the outermost channel MWI-14, QRNN filter rejects almost twice as more cloudy cases than B183 and the resulting bias is almost 40\% lower.
+Similarly the standard deviation is almost 1.6 times lower.
+For MWI-15, QRNN filter removes almost 2.81\% as cloudy, and the average bias is almost 30\% lower than B183.
+For MWI-16 both approaches remove almost similar number of cases, and the average error and MAE are comparable.
+But the resulting distribution from B183 has a slightly higher spread and skewness.
+For MWI-17 also, QRNN filter is successful in removing more cloudy cases than B183 and results in distributions with slighly better accuracy.
+However for MWI-18, the performance of B183 is better.
+For this channel, QRNN filter removes 28\% less cases than B183, but the overall accuracy of the two filters is not very different.
+The average bias after QRNN filter is -0.25\,K in comparison to -0.22\,K from B183.
+The corresponding difference in the standard deviation is 4\%.
+
+Both filtering schemes are only partially successful in removing the high cloud impact. However, the results indicate a  better performance of QRNN filter than B183 for all channels except for MWI-18.
+B183 filter is determined by the higher peaking channels, which when applied to other channels increases the risk of erroneous filtering.
+It could be possible that data in MWI-18 is cloudy but clear in MWI-14.
+QRNN with its channel specific approach has a clear advantage over B183.
+With only slighly higher rejection rate, QRNN filter can achieve data with lower bias and standard deviation.
+It should be noted that B183 involves AMSU-B brightness temperatures for the development of their scheme, and we do not adapt the filtering thresholds for MWI channels.
+This could affect the performance of B183 slightly.
+
+\paragraph{Cloud correction and uncertainty estimation}
+%
+%t
 \begin{figure}[t]
@@
 \end{figure}
-QRNN-mwi is designed to provide basis for a cloud correction approach applicable to current satellites, that lack the higher frequency channels.
-Table~\ref{tab:statistics_mwi-alone} shows the results for all 183\,GHz channels of MWI.
-MWI channels have a higher measurement uncertainty than ICI, so a higher filtering threshold is selected.
-All cases with cloud correction greater than 7.5\,K are considered as cloudy and filtered out.
-With pure-filtering, only 4\% of the cases are filtered out for MWI-14, but the bias reduces from -1.86\,K to -0.50\,K.
-For the predictions, the average bias is -0.14\,K.
-For both filtering and correction, a significant reduction in the errors is observed but the resulting values are still high and indicate only partial success of the method.
+
+In this section, we describe the accuracy of QRNN predictions in comparison to the NFCS simulations. We also analyse the corresponding uncertainties.
+
+Table~\ref{tab:statistics_mwi-alone} displays the different statistics quantifying the error of the best estimate.
+As seen the previous section, QRNN filter can only partially remove the cases with high cloud impact.
+With correction, a better accuracy is expected.
+For MWI-14, the average bias in the predicted dataset is -0.14\,K in comparison to -0.50\,K acheived by filtering alone.
 For other channels also, a similar performance is observed.
-For MWI-15, cloud correction reduces the average error from -1.23\,K to -0.13\,K  and the corresponding decrease in standard deviation is 6.55\,K to 1.32\,K.
+For MWI-15, cloud correction reduces the average bias to -0.14\,K, and the corresponding standard deviation is 1.32\,K.
 Filtering the predicted cases improves the bias and standard deviation further by 15\%.
 Interestingly, even with partial correction, the standard deviation is lower than the measurement noise.
-For MWI-16, the bias for predictions is -0.12\,K compared to -0.85\,K for the measurements.
+For MWI-16, the bias for predictions is -0.13\,K compared to -0.84\,K for the measurements.
 The corresponding standard deviation is  1.15\,K, which is again smaller than the measurement noise(1.20\,K).
@@
 MWI-18 is least affected by cloud impact among the five channels.
-The average deviation of the measurement data to NFCS values is only -0.66\,K which reduces to -0.12\,K with QRNN.
-After filtering 1.37\% cases with high cloud impact, only a slight improvement in the accuracy is observed but the variability of errors decreases from 1.23\,K to 1.08\,K.
-The results show that QRNN-mwi is partially successful in removing the cloud impact.
+The average deviation of the measurement data to NFCS values is only -0.65\,K which reduces to -0.11\,K with QRNN correction.
+After filtering 1.39\% cases with high cloud impact, only a slight improvement in the accuracy is observed but the variability of errors decreases from 1.23\,K to 1.08\,K.
+The results show that QRNN-mwi is partially successful in correcting the cloud impact.
 A significant reduction in the deviation to NFCS values indicates that though most cases with high cloud impact can be removed/corrected, the cases with residual cloud impact and uncorrected cases deteriorate the performance.
@@
 
+High quality cloud corrected radiances have great potential in the DA (data assimilation) systems.
+Most DA systems reject upto 80\% of the available observations due to cloud contamination.
+The loss is largest in mid-latitudes.
+Although all-sky microwave measurements are being successfully assimilated at most operational centres, cloud cleared microwave radiances offer forecast benefits without additional complexities.
+Assimilation of all-sky radiances calls for a complex radiative transfer and careful consideration of observational errors.
+
 %% The following commands are for the statements about the availability of data sets and/or software code corresponding to the manuscript.

### 2020-10-28 Article/ici_submm_cloudcorr.tex
restructured manuscript, WORK in PROGRESS

--- 2020-09-28 Article/ici_submm_cloudcorr.tex
@@
 \newcommand{\ynfcs}{y_\text{NFCS}}
+\newcommand{\yonfcs}{y^{o}_\text{NFCS}}
+\newcommand{\ynfcsi}{y_\text{NFCS, i}}
+\newcommand{\yonfcsi}{y^{o}_\text{NFCS, i}}
 \newcommand{\y}{\vec{y}}
@@
 
-\title{Cloud correction and filtering of operational microwave humidity
-  radiances with case specific uncertainty estimation}
+%\title{Cloud correction and filtering of operational microwave humidity radiances with case specific uncertainty estimation}
+
+\title{Estimation of cloud-corrected microwave humidity radiances with associated uncertainties}
+
+%\title{Cloud correction and uncertainty characterisation of operational microwave humidty channels}
 
@@
 
-This study presents a cloud filtering and correction method for microwave humidity radiances.
-The method is based on the postulation that sub-millimeter(sub-mm) frequencies can provide a basis for cloud filtering/correction of data measured around 183\,GHz.
+In this study, we present methodology to identify and correct the cloud impact in microwave humidity radiances.
 A quantile regression(QRNN) based approach is formulated to estimate the posterior distributions of noise free clear sky (NFCS) radiances.
-QRNNs are trained to correct the cloud impact for each 183\,GHz channel using measurements from the target channel and available sub-mm channels.
-The approach is demonstrated by application to Ice Cloud Imager(ICI) and MicroWave Imager (MWI).
-As a special case, applicability to smaller satellite missions like Arctic Weather Satellite (AWS), with fewer sub-mm channels, is also evaluated.
-The performance of QRNN based cloud filtering is also investigated.
+The applicability of the approach is demonstrated by application to current sensor MWHS-2.
+With the future outlook, the applicability to sub-millimeter (sub-mm) channels is also investigated.
 The results are compared against the NFCS simulations.
-
-Pure-filtering approach is only partially successful in removing the cloud contamination.
-Though most of the cases with high cloud impact are drawn out, cases with low cloud impact are falsely classified as cloudy.
-This shortcoming is unacceptable in retrieval and assimilation applications and reinforces the necessity for cloud correction.
-The results from cloud correction show that QRNN is successful in alleviating the cloud contamination to a large extent.
-Few cases with residual cloud impact deteriorate the performance but filtering out such cases results in error distributions which are symmetric and have low bias and standard deviation.
+With the present sensors, the approach is only partially successful in removing the cloud contamination.
+Though most of the cases with high cloud impact are corrected, cases with low cloud impact are only partially corrected.
+This is comparable to the level of accuracy achieved with operational cloud-filtering techniques.
+However with sub-mm channels, we are able to successfully correct most of the cases with cloud impact.
+The resulting error distributions are symmetric with very low spread.
 In some cases, the combination of 183\,GHz and sub-mm channels also results in a lower variability than noise.
+The methodology also works well even when only one of the higher frequencies is available.
 Another advantage of using QRNN is that predicted quantiles can be employed to quantify the case-specific uncertainty estimates.
-The results show that QRNN is successful in representing the uncertainty for most of scenes individually.
+The results show that QRNN is successful in representing the uncertainty for most of the scenes individually.
 Despite individual variations for each channel, it is observed that uncertainty consistently increases with the error in the performance.
-
-The results show that it can be highly recommended to use all available sub-mm frequencies to estimate the NFCS values of radiances/brightness temperatures.
-The strategy works well even when only one of the higher frequencies is available.
-This study uses simulated data, but we can expect to obtain similar performance when data from the new sensors will be available.
 
@@
 \subsection{Satellite Instruments}
+%
+\subsubsection{ MicroWave Humidity Sounder 2}
+%
+%t
+\begin{table}[t]
+	\caption{Specifications of MWHS-2 channels relevant to this study.}
+	\label{tab:specifications_MWHS2}	
+	\begin{tabular}{crrr}
+		\tophline
+		Channel & Frequency 	& Bandwidth & NE$\Delta$T \\
+		& [GHz]			& [MHz]		& [K]		\\
+		\middlehline
+		1	&	89.0   		  & 1500			&	1.0	\\
+		6	&	118.75±1.1    & \phantom{0}200 	&	1.6\\
+		7	&	118.75±2.5    & \phantom{0}200 	&	1.6\\
+		10	&	150.0         & 1500 			&	1.0 \\
+		11	&	183.31±1      & \phantom{0}500  &	1.0 \\
+		12  & 	183.31±1.8    & \phantom{0}700 	&   1.0\\
+		13  & 	183.31±3      & 1000    		&	1.0	\\
+		14  & 	183.31±4.5    & 2000    		&	1.0\\
+		15  & 	183.31±7      & 2000  			&	1.0  \\
+		\bottomhline
+	\end{tabular}
+	\belowtable{} % Table Footnotes
+\end{table}
+MicroWave Humidity Sounder 2 (MWHS-2) is an instrument onboard FengYun-3C (FY-3C).
+MWHS-2 is designed to observe the distribution of global atmospheric thermodynamics information, and monitor the severe convective systems.
+It is a cross track scanning microwave radiometer and measures 15 frequencies in the range 89-191\,GHz.
+89\,GHz and 150\,GHz are window channels, five humidity sounding channels are centered at 183.31\,GHz and eight temperature sounding channels centered at 118.75\,GHz oxygen absorption line.
+The five humidity sounding channels are similar to MWS (Micro Wave Sounder) and ATMS (Advanced Technology Microwave Sounder).
+As of December 2019, observations from MWHS-2 are routinely assimilated at ECMWF \citep{duncan2020MWHS}.
+The channels relevant to this study are described on Table~\ref{tab:specifications_MWHS2}.
+
+For this study, MWHS-2 simulations were sourced from ECMWF assimilation system. \todo{details?}
+
 \subsubsection{Ice Cloud Imager}
@@
 %t
-\begin{table*}[t]	
-	\caption{Specifications of ICI and MWI channels relevant to this study.}
+\begin{table}[t]	
+	\caption{Specifications of ICI channels relevant to this study.}
 	\label{tab:ICI_MWI_channels}
-	\begin{tabular}{lrrr}
+	\begin{tabular}{crrr}
 		\tophline
@@
 		I11V&	664.00$\pm$4.20    & \phantom{0}500	& 1.6 		\\		
-		I11H&	664.00$\pm$4.20    & \phantom{0}500 & 1.6 		\\		
 		\bottomhline
 	\end{tabular}
-	\begin{tabular}{lrrr}
-		\tophline
-		Channel & Frequency 	& Bandwidth  	&NE$\Delta$T	n\\
-				& [GHz]			& [MHz]			& [K]			\\
-		\middlehline
-		MWI-14&	183.31$\pm$7.00    & 2000 			& 1.3 		\\
-		MWI-15&	183.31$\pm$6.10    & 1500			& 1.2 		\\
-		MWI-16&	183.31$\pm$4.90    & 1500			& 1.2 		\\
-		MWI-17&	183.31$\pm$3.40    & 1500			& 1.2 		\\
-		MWI-18&	183.31$\pm$2.00    & 1500			& 1.3 		\\	
-		\bottomhline
-	\end{tabular}
-
 	\belowtable{} % Table Footnotes
-\end{table*}
+\end{table}
 
@@
 Metop-SG is scheduled for launch in 2023, and it will make ICI the first operational sensor observing Earth using sub-millimeter(sub-mm) wavelengths.
+The main objective of ICI is to use high frequency channels for measuring ice cloud properties and improve the representation of ice clouds in regional and global Numerical Weather Prediction(NWP) models.
 ICI is a conically scanning radiometer that will measure 13 frequencies from 183 GHz up to 664 GHz.
-The main objective of ICI is to use high frequency channels for measuring ice cloud properties and improve the representation of ice clouds in regional and global Numerical Weather Prediction(NWP) models.
 ICI consists of channels receiving frequencies around 183.31\,GHz, 325.15\,GHz and 448.00\,GHz, measuring vertical polarization.
@@
 For this study, we conducted the forward simulations at frequencies: 183.31\,GHz, 325.15\,GHz, 448.00\,GHz and 664.00\,GHz(See Table~\ref{tab:ICI_MWI_channels}).
-For brevity, we assumed that all simulations were mapped to a common footprint.
-
-\subsubsection{MicroWave Imager}
-%
-\label{mwi_channels}
-In addition to ICI, the Metop-SG will also have Microwave Imager(MWI) on board.
-MWI is a conically scanning radiometer and will measure frequencies from 18 GHz up to 183\,GHz \todo{add ref}.
-All channels up to 89 GHz will receive both horizontal and vertical polarisation, while other frequencies will receive only vertical polarisation.
-A short summary of the MWI channels used in the study is provided in Table~\ref{tab:ICI_MWI_channels}.
-MWI also has three  183\,GHz frequencies in common with ICI.
-The overlapping frequencies shall allow cross-calibration between the two instruments, and provide microwave measurements from 18\,GHz to 664\,GHz on a common scale.
-The main objective of MWI is to provide data continuity to the existing microwave imager measurements for cloud and precipitation and support regional and global NWP models.
-
-For this study, forward simulations at frequencies around 183.31\,GHz were performed.
-When ICI and MWI simulations were used together, MWI channels were assumed to be mapped to ICI footprint and resolution.
-Remapping reduces the noise in MWI from 1.2\,K at 10\,Km resolution to 0.8\,K at 15\,Km resolution.
+For brevity, we assume that all simulations are mapped to a common footprint.
 
@@
 
-\subsubsection{Cloud Profiling Radar}
-%
-Cloud Profiling Radar(CPR) is the main instrument on sun-synchronous polar orbit satellite CloudSat (Cloud Satellite) \citep{Stephens2002cloudsat}.
-It was launched in 2006 and is part of the A-train constellation of four earth observation satellites.
-CPR is a nadir looking radar operating at 94.05\,GHz and measures the cloud backscatter as a function of distance from the radar, to provide vertical profiles of clouds and precipitation.
-
-In this study, CloudSat profiles were used only to perform the forward simulations for ICI, MWI and AWS.
-
 \subsection{Simulations}
-\label{sec:arts_simulations}
-%
-\subsubsection{Input data}
-%
+%
+MWHS-2 simulated radiances are routinely calculated at ECMWF for their use in the ECMWF assimilation system.
+RTTOV and RTTOV-SCATT are used to calculate the radiances in the clear-sky and all-sky conditions respectively.
+For this study, MWHS-2 brightness temperatures for the period June-July 2020 were used.
+Out of all the available observations, we extracted data for latitudinal range $60^{\degree}$\,S to $60^{\degree}$\,N and satellite zenith angle less than $7.5^{\degree}$.
+With this filter we had 340\,000 cases for each frequency.
+
+ICI, AWS frequencies were simulated with ARTS.
+Cloudsat profiles during August 2015 were randomly selected for forward simulations.
+The input data were restricted between $60^{\degree}$S to $60^{\degree}$N, and surface was below 500\,m.
+Both clear-sky and all-sky scenarios were simulated.
+The complete simulation setup is described in Appendix \ref{appendix:ARTS_setup}.
+For each ICI frequency in Table~\ref{tab:ICI_MWI_channels}, 220\,000 cases were simulated.
+For both instruments, the channel frequencies were simulated directly.
+For AWS, 140\,000 cases were simulated.
+Forward simulations were performed for 21 monochromatic frequencies.
+These frequencies were interpolated to a finer grid to get the AWS channel brightness temperatures.
+All AWS sensor viewing angles (from $0^\circ$ to $45^\circ$) were simulated, but the results described in this study are based on nadir viewing angle.
+
+All simulations were noise free, so to incorporate the measurement uncertainties, whenever needed, gaussian noise was added to according to the channel NE$\Delta$T (Table~\ref{tab:specifications_MWHS2} - Table~\ref{tab:specifications_AWS}).
+
+The noise free simulations were split into training and testing datasets.
+The training dataset was used to train the machine learning model, while the testing dataset was used to evaluate the trained model.
+The construction and details of the model are described in Sect.~\ref{sec:QRNN}.
+For MWHS-2, 220\,000 simulations were randomly selected as training dataset, while 70\,000 were used for testing.
+For ICI, 175\,000 cases were randomly picked to form the training set.
+The remaining 45\,000 were used for testing.
+A smaller database was selected for AWS.
+120\,000 simulations were used for training and the rest were used for testing.
+
+\subsection{Quantile regression neural networks}
+\label{sec:QRNN}
+%
+The task that we aim to solve in this study is to predict the NFCS brightness
+temperature $\ynfcs$ at a given $183\unit{GHz}$ channel from a vector of
+cloud-contaminated observations $\y$. Since the information-content of the
+cloud-contaminated observations is certainly too low to solve this problem
+exactly, a probabilistic formulation is appropriate here. The aim thus becomes
+to predict the conditional distribution $p(\ynfcs | \y)$ of the NFCS brightness
+temperatures $\ynfcs$ given the cloud-contaminated observations $\y$.
+
+As has been shown in \citet{pfreundschuh:aneur:18}, quantile regression neural
+networks (QRNN) can be used to solve these type of problems. Instead of a point
+prediction, as it is typically performed in regression problems, QRNNs learn to
+predict a vector of quantiles, which can be used to approximate the distribution
+of the predicted quantity conditional on the network inputs. Using QRNNs to
+perform probabilistic cloud correction thus not only allows deriving an estimate
+for $\ynfcs$ but also for the error of the corrected observations.
+
+For this application, the predicted percentiles are chosen to be
+$0.2\%, 3\%, 16\%, 50\%, 85\%, 97\%$ and $99.8\%$. For a Gaussian
+distribution with mean $\mu$ and standard deviation $\sigma$ the
+approximately corresponds to $\mu -3\sigma, \mu-2\sigma, \mu-\sigma
+, \mu, \mu + \sigma, \mu + 2\sigma, \mu + 3\sigma$ and thus allows
+estimating the $\pm 1, \pm 2$ and $\pm 3\sigma$ confidence intervals.
+The median is used as point estimate for the corrected $\ynfcs$.
+
+QRNN's are trained to minimize the mean of the quantile loss functions
+%
+\begin{align}
+  \mathcal{L}_\tau(y_\tau, y) &=
+  \begin{cases}
+    \tau|y - y_\tau|, & y_\tau < y \\ (1 - \tau)|y_\tau - y|, & \text{otherwise}
+    \\
+  \end{cases}
+\end{align}
+%
+for all predicted quantile fractions $\tau$, where $\y_\tau$ is the predicted
+quantile and $y$ the reference value from the training set. The quantile loss is
+used in this study as a performance criterion for the tuning of the hyper
+parameters of the QRNN. In addition to the quantile loss, also the Continuously
+Ranked Probability Score (CRPS) is considered. Given a predicted cumulative
+distribution function (CDF) $F$ and the reference value $y$, the CRPS is defined as
+%
+\begin{align}
+  \text{CRPS}(F, y) = \int_{-\infty}^{\infty} \left (F(y') - y\right )^2\: dy'.
+\end{align}
+%
+To compute the CRPS for a predictions from a QRNN, the predicted quantiles are
+used to derive a piece-wise linear approximation of the CDF of the predicted
+distribution and evaluate the above integral.
+
+The implementation of QRNN is similar to one described in \citet{pfreundschuh:aneur:18}, except that instead of Kera python package, PyTorch, an open source machine learning
+library \citep{paszke2017automatic} is used.
+This version is developed and available as a part of \textit{typhon:tools for atmospheric research} software package [\todo{developer's version??}].
+The major challenge for implementing QRNN for the current application was to select high performing neural network architecture.
+This was obtained through grid search over different hyperparameter configurations.
+The details are described in Appendix~\ref{appendix:hyperparamter}
+
+\subsubsection{QRNN model configurations}
+%
+In the study, two QRNN configurations are formulated for cloud-correction.
+The basic construction of both is to train for each of the available 183\,GHz channels individually, using certain input training data.
+The input data is all-sky brightness temperatures from selected input channels and/or additional data like land/sea mask.
+The selection of input channels is sensor dependent and is described in detail when introduced.
+The output in both configurations is NFCS value for the target 183\,GHz channel.
+The two configurations differ only by the number of input 183\,GHz channels used in the training process:
+
+\begin{enumerate}
+	\item QRNN-single: In this configuration, the training input includes all-sky brightness temperatures from the target 183\,GHz channel and other non-humidity channels along with additional data, if relevant.
+No other 183\,GHz channel is included.
+
+	\item QRNN-all: In this configuration, all-sky brightness temperatures from all available 183\,GHz channels are included in the training input.
+Just like QRNN-single, data from other non-humidity channels and additional data are also taken into account, but the main difference is the concurrent utilisation of all 183\,GHz frequencies.
+\end{enumerate}
+
+For all three sensors described in this study, one or both of the above QRNN configurations are used.
+
+\subsection{Evaluation metrics}
+\label{sec:validation}
+\begin{figure}[t]
+	\centering
+	\includegraphics[height=45mm]{Figures/posterior_distribution_I1V.pdf} 
+	\caption{An example showing the predicted quantiles of the conditional distribution of $\ynfcs$ }
+	\label{fig:posterior_distribution_I1V}	
+\end{figure}
+QRNN predictions are posterior probability distribution of the NFCS values described over the selected quantiles.
+This is contrast with other conventional correction/filtering methods.
+In order to facilitate the interpretation of results, an example QRNN output is shown in Fig.~\ref{fig:posterior_distribution_I1V}.
+This examples illustrate the predicted quantiles for three different cases.
+For most analysis, usually a single point estimate is required.
+In Bayesian analysis, usually the posterior mean or posterior median are selected as point estimates.
+In this study, we assume the posterior median to be the best estimate for the predicted NFCS value ($\ynfcs$).
+To analyse the ability of QRNN in correctly predicting the point estimate, deviations of point estimates from the corresponding true value ($\yonfcs$) are evaluated using common performance indicators like bias, mean absolute error(MAE) and standard deviation (STD).
+The asymmetry of error distributions around their mean is also calculated through the measure of skewness.
+Fisher-Pearson coefficient of skewness is used to calculate the measure of skewness:
+\begin{equation}
+g_1 = \frac{m_3}{m_2^{3/2}}, 
+\end{equation}
+where $m_2$ and $m_3$ are biased sample's second and third central moments.
+
+For probabilistic predictions, accuracy of the point estimate is inadequate to gauge the complete performance.
+In a successful QRNN training, QRNN learns to predict not only an accurate point estimate but also correct underlying uncertainty.
+An ideal QRNN output should be sharp or in other words, concentrated in the vicinity of the point estimate.
+The predicted posterior distribution should also be well calibrated, that is, reflect the true probability distribution.
+A straightforward way to compare the two distribution is to plot the frequency of predictions and frequency of the true value in different prediction intervals.
+This is also commonly known as calibration plot.
+In a well-calibrated QRNN prediction, the calibration plot should follow the straight line y = x.
+Another way to assess how well the predicted posterior distribution reflects the observed errors is to compare predicted and observed errors.
+The predicted error is deviation of a random sample drawn from the posterior distribution to its median.
+In this study, we use both calibration plot and predicted errors to assess the correctness of predicted uncertainties.
+
+All evaluation results described in the study have been made on the testing data.
+
+\section{Correcting cloud affected data in MWHS-2}
+%
+In this section, we introduce the QRNN based cloud  correction in the context of current operational sensors.
+We use MWHS-2 to demonstrate the results.
+The choice is motivated by the fact that MWHS-2 has five complementary 183\,GHz channels as ATMS/MWS, along with additional 118\,GHz channel.
+In order to test the correction approach multiple QRNN experiments are performed and the results are compared for MWHS-2 channel 14.
+Later the methodology is expanded to other channels.
+Further, the estimates of case-specific uncertainties obtained from QRNN are also evaluated.
+
+\subsection{Experiments}
+%
+For MWHS-2, multiple experiments using both QRNN configurations are performed. The aim of the experiments is to delve into the sensitivity of the cloud correction to different input channels:
+
+\begin{enumerate}
+
+	\item In the first experiment, we examine the performance of QRNN cloud correction with MWHS-2 window channels: 89 and 150\,GHz.
+In ECMWF NWP system, the differences between the observations of these two window channels (Scattering Index) \citep{Lu2015FY3C} are used to identify the cloud affected data for ATMS, MHS and MWHS-2.
+To investigate the potential impact of window channels in QRNN based cloud correction, the configuration QRNN-single is applied to predict cloud free radiances.
+In this experiment, the training input includes all-sky brightness temperatures from target 183\,GHz channel, 89\,GHz and 150\,GHz.
+Both 89 and 150\,GHz are window channels so the land sea mask is also included as a training input.
+For example for channel 14, the training inputs are all-sky brightness temperatures from channels 14, 1, 10 and land/sea mask.
+This combination is referred as 89+150\,GHz in the text.
+
+	\item In the second experiment, we explore if few of low peaking channels of 118\,GHz could have any potential advantage in cloud correction.
+To explore their impact, QRNN-single is trained with data from target 183\,GHz, 89\,GHz, 150\,GHz, 118.75$\pm$1.1\,GHz (channel 6), 118.75$\pm$2.5\,GHz (channel 7) and land/sea mask.
+This combination is denoted as 89+150+118\,GHz
+
+	\item The third experiment is designed to assess the exclusive impact of 150\,GHz in cloud correction.
+In this experiment, QRNN-single is trained with brightness temperatures from 150\,GHz along with the target channel and land/sea mask.
+
+	\item The fourth experiment is based on the configuration QRNN-all.
+In this experiment, we use 89 and 150\,GHz channels along with all 183\,GHz channels to train QRNN.
+This experiment is motivated by the fact that in all-sky conditions, brightness temperatures between outer and inner humidity channels can be used as a criterion for cloud filtering\cite{buehler:aclou:07}.
+With QRNN-all, we investigate if additional humidity channels in the training process can improve the performance by providing auxiliary information.
+It should be noted that though the training inputs are same for each 183\,GHz channel, the output is the target 183\,GHz channel; thus each channel still needs to be trained separately.
+Land/sea mask is also included in the training.
+This combination is denoted as 89+150+183\,GHz
+\end{enumerate}
+
+\subsection{Prediction accuracy}
+
+\subsubsection{QRNN-single applied to MWHS-2 channel 14} 
+\begin{figure}[t]
+	\centering
+	\includegraphics[height=55mm]{Figures/QRNN_output_mwhs.pdf} 
+	\caption{Distributions of point estimate $\ynfcs$ obtained from QRNN-single 89+150\,GHz for MWHS-2 channel 14. The corresponding distribution for all-sky and clear-sky simulations are also shown.}
+	\label{fig:distribution_predicted_mwhs14}	
+\end{figure}
+\begin{table*}[t]
+	\caption{Error statistics for deviations of MWHS-2 NFSC predictions to simulations.
+Results are for different QRNN experiments for MWHS-2 channel 14.
+With configuration QRNN-single, the results are from combinations 89+150\,GHz, 89+150+118\,GHz and 150\,GHz.
+While with QRNN-all, only combination 89+150+183\,GHz is shown.
+The statistics for uncorrected all-sky simulations and NFCS simulations are also provided.
+The label ``All'' refers to entire predicted dataset, while Filtered(5\,K) denotes the subset where predictions with correction greater than 5\,K are omitted.
+The fraction of rejected cases is given in parentheses.
+}
+	\label{tab:error_statistics_mwhs_14}
+	\begin{tabular}{lrr|rr|rr|rr|rr}
+		\tophline
+		&\multicolumn{2}{c|}{Simulations}& \multicolumn{6}{c|}{QRNN-single} & \multicolumn{2}{c}{QRNN-all}\\
+		\cline{2-11}
+		%		\hline
+		&   Clear-sky &   All-sky &  \multicolumn{2}{c|}{89+150\,GHz} & \multicolumn{2}{c|}{89+150+118\,GHz} & \multicolumn{2}{c|}{150\,GHz} & \multicolumn{2}{c}{89+150+183\,GHz}\\
+		&			   &			& All & Filtered(5K) & All & Filtered(5K) & All & Filtered(5K)  & All & Filtered(5K)\\
+		\middlehline
+		bias     &  0.00 &  -0.84 & -0.09 & -0.08(3.3\%) & -0.04 & -0.03(3.4\%) & -0.09 & -0.09(3.2\%) & -0.09(3.3\%) & -0.08(3.3\%)  \\
+		mae      &  0.80 &   1.45 &  0.88 &  0.86 &  0.89 &  0.87 &  0.89 &  0.87 &  0.62 &  0.59\\
+		std      &  1.00 &   3.90 &  1.19 &  1.14 &  1.19 &  1.15 &  1.21 &  1.16 &  0.90 &  0.83\\
+		skewness & -0.00 & -14.34 & -1.11 & -0.93 & -1.00 & -0.84 & -0.88 & -0.98 & -1.58 & -1.62\\
+		\bottomhline
+	\end{tabular}
+\end{table*}
+Fig.~\ref{fig:distribution_predicted_mwhs14} shows the distribution of QRNN predictions obtained from QRNN.
+QRNN predictions are able to remove the extended mass concentration to the left is due hydrometeor impact, and overall a good match with the NFCS simulations is observed.
+QRNN is unable to predict the lowest clear-sky brightness temperatures, but cases with brightness temperatures around 260\,K occur frequently.
+Table~\ref{tab:error_statistics_mwhs_14} shows the error statistics for the predictions shown in Fig.~\ref{fig:distribution_predicted_mwhs14}.
+In the uncorrected data, cloud impact causes a large negative skewness(-14.34) in the error distribution and the corresponding bias is -0.84\,K.
+Training QRNN with 89 and 150\,GHz removes a part of the cloud impact and reduces the bias to -0.09\,K, and the skewness is -1.11.
+The MAE and STD are also reduced after correction, but are higher than noise.
+Including 118\,GHz in the training, gives comparable results as 89+150\,GHz.
+With 118\,GHz, the error distributions have lower bias and are more symmetric, but the MAE and STD remain unaltered.
+This indicates that the information from 118\,GHz channels can be beneficial in predicting few cases correctly, but the overall consequence is not exceptionally different from 89+150\,GHz.
+Similar is the case with using only 150\,GHz.
+In the latter, predictions have the most symmetric  error distributions, but the highest spread.
+
+Further we investigated that if filtering the predictions with large residual cloud impact could help in improving the prediction accuracy.
+For filtering such cases, we assume that predictions with cloud correction greater than 5\,K are cases associated with large deviations.
+In all three experiments, removing the cases with correction greater than 5\,K removes around 3\% of the data, but only a marginal positive impact on the accuracy is observed.
+With 5\,K thresold, though the cases with high errors are removed, the negative skewness conveys that some cases with low cloud impact are not completely corrected.
+Choosing a lower threshold can help in removing more partially corrected cases but at the cost of rejecting clear-sky cases.
+Since QRNN gives out NFCS values, choosing an unusually low correction threshold can also classify noisy clear-sky cases as cloudy.
+For example, for 89+150\,GHz, a threshold of 1.5\,K rejects almost 10\% of data, but the negative skewness is still not completely removed.
+
+The results are further compared with SI based cloud filtering. SI uses differences of brightness temperatures between 89 and 150\,GHz to identify cloud affected data:
+\begin{equation}
+\text{SI} = ((\text{TB}^{obs}_{90} - \text{TB}^{obs}_{150}) + (\text{TB}^{fg}_{90} - \text{TB}^{fg}_{150}))/2 
+\end{equation}
+
+where TB$^{obs}$ and TB$^{fg}$ are observation and model first guess brightness temperatures respectively.
+
+\todo{comparsion with SI}
+
+The three experiments were also performed for other four 183\,GHz channels, and a similar performance was obtained (Table not shown).
+The positive effect of 118\,GHz was slightly higher for MWHS-2 channel 15, but for others, no notable effect was observed.
+The results from combination 89+150\,GHz for these channels are provided in Sect.~\ref{sec:mwhs_others}
+
+\subsubsection{Comparison of QRNN-all and QRNN-single}
+%
+%f
+\begin{figure}[t]
+	\centering
+	\includegraphics[height=45mm]{Figures/correlation.pdf} 
+	\caption{ The triangular error correlation matrix obtained from QRNN-single and QRNN-all for MWHS-2. The label ``Clear'' represents cases with cloud impact less than 2\,K.}
+	\label{fig:correlations_mwhs}	
+\end{figure}
+To assess the differences between the capabilities of QRNN-all against QRNN-single, we  compare the error statistics obtained for 89+150\,GHz and 89+150+183\,GHz for channel 14.
+The last column of Table~\ref{tab:error_statistics_mwhs_14} displays the error statistics for the experiment QRNN-all.
+In comparison to QRNN-single, we obtain marginally lower error bias with QRNN-all, and the MAE and standard deviation reduce by almost 30\% and 25\% respectively.
+However the negative tail becomes more prominent.
+The low standard deviation, but strong negative tail indicates that the narrow spread is a consequence of correction of noise in clear-sky cases.
+Since a majority of the cases are clear-sky, their impact dominates the whole statistics.
+In order to quantify the positive effect of QRNN-all on cases with high and low cloud impact, a separate analysis of the high and low cloud impact cases is made.
+In both cases, QRNN-all has slightly better accuracy than QRNN-single, suggesting that concurrent use of all 183\,GHz channels can provide additional information on cloud structures to QRNN.
+
+Even though QRNN-all gives slightly better prediction accuracy, its inherent construction makes it crucial to examine the correlation between observed errors.
+Fig~\ref{fig:correlations_mwhs} illustrates the correlation matrix for both QRNN-all and QRNN-single.
+For clear cases, the observed errors (noise) in QRNN-single are uncorrelated between the five channels.
+However QRNN-all gives out highly correlated errors.
+The correlations are highest between adjacent channels, and drop out as the spacing between the channels increases.
+For cloudy cases, the observed errors obtained from QRNN-single are slightly correlated, but with QRNN-all a very strong correlation is observed(not shown).
+The residual cloud amount for different channels depends upon each other in a systematic way, but since QRNN-single does not have access to this information, only slightly higher correlations are observed.
+On the other hand, with QRNN-all, when all 183\,GHz channels are used simultaneously the predictions learn positively from the common information and also introduces high correlations between overlapping channels.
+Correlated errors can be undesirable for DA systems, so the configuration QRNN-all is avoided for further development.
+
+\subsubsection{QRNN-single applied to channel 11, 12, 13 and 15}
+\label{sec:mwhs_others}
+\begin{table*}[t]
+	\caption{ Error statisics for MWHS-2 channels 11, 12, 13 and 15 from QRNN-single experiment 89+150\,GHz.
+The labels ``All'' and ``Filtered(5\,K)' are as described in Table~\ref{tab:error_statistics_mwhs_14}.}
+	\label{tab:error_statistics_mwhs_others}
+	\begin{tabular}{lrrr|rr}
+		\tophline
+		&&\multicolumn{2}{c|}{Simulations}& \multicolumn{2}{c}{QRNN-single} \\
+		\cline{2-6}
+		%		\hline
+		& &  Clear-sky &   All-sky &  \multicolumn{2}{c}{89+150\,GHz}  \\
+		&	&		   &			& All & Filtered(5K)\\
+		\middlehline
+		Channel 11  &   bias     & 0.00 &  -0.16 & -0.03 & -0.03(0.2\%)  \\
+				    &	mae      & 0.80 &   0.89 &  0.79 &  0.79  \\
+					&	std      & 1.00 &   1.71 &  1.03 &  1.01  \\
+					&	skewness & 0.01 & -20.18 & -0.68 & -0.45  \\
+		\middlehline
+		Channel 12  & bias     & -0.00 &  -0.28 & -0.05 & -0.05(0.6\%)  \\
+					& mae      &  0.80 &   0.98 &  0.81 &  0.80  \\
+					& std      &  1.00 &   2.26 &  1.07 &  1.05  \\
+					& skewness &  0.00 & -20.72 & -0.91 & -0.70  \\
+		\middlehline
+		Channel 13  & bias     & -0.00 &  -0.52 & -0.08 & -0.07(1.6\%)  \\
+					& mae      &  0.80 &   1.17 &  0.84 &  0.83  \\
+					& std      &  1.00 &   3.04 &  1.13 &  1.10  \\
+					& skewness &  0.02 & -17.85 & -1.14 & -0.98 \\		
+		\middlehline
+		Channel 15  & bias     & -0.00 &  -1.28 & -0.07 & -0.06(5.6\%)  \\
+					& mae      &  0.80 &   1.87 &  0.97 &  0.92 \\
+					& std      &  1.00 &   5.08 &  1.35 &  1.25 \\
+					& skewness & -0.00 & -11.15 & -0.60 & -0.83  \\ 
+		\bottomhline
+	\end{tabular}
+\end{table*}
+In this section, we extend QRNN-single to predict NFCS values for MWHS-2 channels 11, 12, 13, and 15.
+The experiment QRNN-single with combination 89+150\,GHz is used and the results are displayed in  Table~\ref{tab:error_statistics_mwhs_others}.
+
+For channel 11, the error bias after correction is only -0.03\,K in comparison to 0.16\,K before correction.
+The strong negative tail is also diminishes after correction, but a non-zero negative skewness indicates presence of cases with cloud impact in the corrected dataset.
+Filtering the cases with high cloud impact has only a marginally positive impact.
+A similar performance is evident for channel 12.
+Correction reduces the bias by to -0.05\,K and the MAE is approximately 17\% less for the entire test dataset.
+However the effect of partially corrected cases is evident in the negative skewness.
+There is again only a partial correction evident for channels 13 and 15.
+The bias values are quite low indicating that QRNN is successful in removing a large fraction of the cloud impact, but relatively high skewness is a consequence of cases with low cloud impact which end up with inadequate correction.
+
+\todo{comparison with SI?}
+
+\subsection{Prediction uncertainty}
+
+\begin{figure}[t]
+	\includegraphics[width = 70mm]{Figures/prediction_uncertainty_MWHS_14.pdf}	
+	\caption{The prediction uncertainty for MWHS-2 channel 14 (QRNN-single) with respect to quantiles for randomly selected 1500 cases.
+The quantiles have been plotted at equidistant points.
+The red line represents a hypothetical Gaussian distribution of $270\pm1.0$\,K.}
+	\label{fig:prediction_uncertainty_mwhs}	
+\end{figure}
+\begin{figure}[t]
+	\includegraphics[height = 70mm]{Figures/calibration_QRNN_MWHS_14.pdf}	
+	\caption{Calibration of the prediction intervals obtained from QRNN-single for MWHS-2 channel 14. }
+	\label{fig:calibration_mwhs}	
+\end{figure}
+\begin{figure}[t]
+	\includegraphics[width=70mm]{Figures/deviation_posterior_mwhs_samples_14.pdf}	
+	\caption{The distribution of predicted errors and observed errors for MWHS-2 channel 14 as obtained from QRNN-single for the test dataset.
+The predicted errors are estimated as deviation of random samples from posteriori distribution to corresponding median values.}
+	\label{fig:predicted_errors_mwhs}	
+\end{figure}
+
+The quantiles given out by QRNN can be used to construct the probability distribution of the predictions in contrast to other correction approaches which give out only point estimates.
+
+An example of the uncertainties given out by QRNN is shown in Fig~\ref{fig:prediction_uncertainty_mwhs}.
+The predictions over quantiles $-3\sigma$, $-2\sigma$ and $-1\sigma$ are quite sharp and lie close to the median value.
+The spread over different cases is also quite narrow, with only few cases with high error.
+In contrast, the spread of predictions over quantiles $1\sigma$, $2\sigma$ and $3\sigma$ is wider.
+
+The calibration of the prediction intervals on the testing dataset is displayed in Fig~\ref{fig:calibration_mwhs}.
+For the entire testing dataset, the predictions are follow the y=x line, i.e.
+they are perfectly calibrated with the priori distribution.
+However for all cases with correction greater than 5\,K, the distribution is poorly calibrated.
+In this case, the calibration curve lies below the y=x line indicating that the prediction intervals are too narrow.
+
+Further we analysed if the  predicted errors obtained from QRNN are representative of observed errors.
+Fig~\ref{fig:predicted_errors_mwhs} illustrates the predicted and observed errors for MWHS-2 channel 14.
+The predicted errors are slightly overestimated for negative values, but overall the predicted errors from the QRNN posterior distribution have a good match with the observed errors.
+It should be noted that the density plot is curtailed at $10^{-4}$.
+With a test dataset of 70\,000 samples, we cannot represent the far wings of the distribution accurately.
+The high errors which we try to estimate are rare, and can not be fully represented by QRNN.
+
+For other humidity channels, the predicted uncertainties followed similar behaviour and the not shown.
+
+\section{Correcting cloud affected data using sub-mm frequencies}
+In this section, we demonstrate that sub-mm channels can be used to formulate the cloud correction of data measured around 183\,GHz.
+Results from different QRNN experiments with varying input conditions are described.
+The results are presented in context of different sensors.
+Furthermore, The case specific uncertainties predicted by QRNN are also discussed.
+
+\subsection{Experiments}
+%
+Two QRNN experiments are performed to investigate the efficacy of sub-mm channels in cloud correction: 
+\begin{enumerate}
+	\item In the first experiment, we follow the QRNN-single configuration to for cloud correction at three ICI humidity channels.
+In this case, the training data is the target 183\,GHz channel and all available ICI sub-mm frequencies (325\,GHz, 448\,GHz and 664\,GHz).
+No other data are included in the training process.
+The experiment is also channel specific, thus each 183\,GHz channel is trained separately.
+For example, to predict NFCS values for channel I1V, the input training dataset includes noisy all-sky simulations from channels I1V, I5V, I6V, I7V, I8V, I9V, I10V, and I11V and the target is NFCS simulations for channel I1V.
+
+	\item In the second experiment, we investigate the possibility of using only channels around 325\,GHz for cloud correction at 183\,GHz.
+This special case of utilising only 325\,GHz channel can be relevant for smaller satellite missions like AWS where higher sub-mm channels are not available.
+In this experiment, QRNN-single configuration is used and it is trained with all-sky simulations from all 325\,GHz frequencies from AWS and the target 183\,GHz channel.
+For example, for target AWS-32, the training inputs were AWS-32, AWS-41, AWS-42, AWS-43, AWS-44.
+QRNN was trained five times for each 183\,GHz channel as target.
+
+\end{enumerate}
+
+\subsection{Prediction accuracy}
+\subsubsection{ICI}
+%
+%f
+\begin{figure*}[t]
+	\includegraphics[width=\textwidth]{Figures/PDF_predictions_ICI.pdf} 
+	\caption{Distributions of point estimate NFCS from QRNN-single for channels I1V, I2V and I3V. The corresponding distributions for NFCS simulations are also shown.}
+	\label{fig:PDF_predictions}	
+\end{figure*}
+\begin{figure*}[t ]
+	\includegraphics[width=\textwidth]{Figures/error_distribution_QRNN-single.pdf} 
+	\caption{Error distributions for deviations predicted data to NFCS simulations.
+The results are from QRNN-ici and channels I1V, I2V and I3V.
+Noise for each channel is also plotted for reference.
+The label ``Uncorrected'' represents the measurement data, ``Predicted(All)'' denotes the entire prediction dataset, while ``Predicted(5\,K)'' refers to the predicted dataset but where cases with cloud correction greater than 5\,K are excluded.}
+	\label{fig:error_distributions}	
+\end{figure*}
+\begin{table*}[t]
+	\caption{ Error statistics for deviations predicted data to NFCS simulations. 
+		The values for Bias, mean absolute error(MAE), standard deviation(STD), and measure of skewness(Skewness) are shown.
+Results are for channels I1V, I2V and I3V.
+The number in parentheses is the percentage of cases removed by filtering.
+The label ``Predicted(All)'' refers to the complete predicted dataset, while ``Predicted (5\,K)'' denotes the prediction dataset but where cases with cloud correction greater than 5\,K are excluded.}
+	\label{tab:error_statistics_ici}
+	%	\tabcolsep=0.11cm
+	\begin{tabular}{llrr|rr}
+		\tophline
+		&&\multicolumn{2}{c|}{Simulations}& \multicolumn{2}{c}{QRNN-single} \\
+		\cline{3-6}
+		%		\hline
+		&&   Clear-sky &   All-sky &  \multicolumn{2}{c}{Predicted}  \\
+		&&			   &			&	(5\,K) & (All) \\
+		\middlehline
+		%		\multicolumn{7}{c}{Channel - I1V}\\
+
+		I1V&  bias     &  0.00 & -1.87 & -0.02 & -0.00  \\
+		&mae      &  0.64 &  2.32 &  0.70 &  0.60   \\
+		&std      &  0.80 &  8.84 &  1.06 &  0.79   \\
+		&skewness & -0.01 & -8.10 & -1.51 & -0.64  \\
+		\middlehline
+		I2V & bias     & 0.00 &  -1.04 &  0.00 &  0.01  \\
+		&mae      & 0.64 &   1.53 &  0.57 &  0.51 \\
+		&std      & 0.80 &   5.95 &  0.86 &  0.65 \\
+		&skewness & 0.00 & -10.79 & -1.85 & -0.22  \\
+		\middlehline	
+		I3V & bias     & 0.01 &  -0.63 &  0.02 &  0.02  \\
+		&mae      & 0.64 &   1.15 &  0.54 &  0.50  \\
+		&std      & 0.80 &   4.27 &  0.80 &  0.63  \\
+		&skewness & 0.01 & -13.37 & -1.51 & -0.13  \\
+		\bottomhline
+	\end{tabular}
+	\belowtable{} % Table Footnotes
+\end{table*}
+
+Fig.~\ref{fig:PDF_predictions} shows the distribution of point estimates given by QRNN.
+For all three channels, an excellent agreement between the predictions and simulations is observed.
+This indicates that QRNN is successful in predicting NFCS values for majority of the cases.
+At lower brightness temperatures, the frequency of predictions is slightly smaller than simulations.
+This could be due to few QRNN predictions ending up with partially corrected cloud impact.
+
+The QRNN prediction accuracy is estimated by computing the deviation of the best estimate to its corresponding NFCS simulation(Fig.~\ref{fig:error_distributions}).
+The predicted values have symmetric error distributions albeit with a large spread.
+The large spread on the left is due to cases which end up with incomplete cloud correction, while the spread on the right is from cases where the predicted values are warmer than the simulations.
+For all three channels, quite similar behaviour is observed, though I1V has the most cases with residual cloud impact.
+If the predicted cases with correction more than 5\,K are rejected, the resulting error distributions fit the measurement noise, except for I1V, where cases with residual cloud impact introduces a negative bias.
+
+For a quantitative assessment of the errors, we calculated the error metrics described in Sect.~\ref{sec:validation} and the results are displayed in Table~\ref{tab:error_statistics_ici}.
+The average bias in I1V measurements is -1.87\,K, which reduces to -0.02\,K after cloud correction.
+The corresponding standard deviation is 1.06\,K in comparison to 8.84\,K in the measurements.
+The prediction accuracy of QRNN is further higher when filtering is made on the predictions.
+In this case, the residual bias zero, and the standard deviation is 0.79\,K, which is in fact of the order of measurement noise (0.80\,K).
+Similar results are seen for I2V, though a better performance is observed.
+In I2V, the measurement bias is -1.04\,K which reduces to zero after correction and the MAE improves by almost 60\%.
+Removing cases with correction greater than 5\,K from the predictions removes only 3.7\% of the data and reduces the absolute error further by 10\%.
+The standard deviation of the resulting dataset is only 0.65\,K as compared to 0.80\,K from noise.
+The reduction in the variability is also evident in the Fig~\ref{fig:error_distributions}, where the peak of distributions is sharper.
+In comparison to I1V and I2V, I3V has the lowest fraction of the measurements with significant cloud impact.
+In the predicted dataset, the bias is 0.02\,K and the MAE is 0.54\,K.
+Including correction along with filtering reduces the MAE further down to 0.50\,K and standard deviation to 0.63\,K.
+
+\subsubsection{AWS}
+
+\begin{table*}[t]
+	\caption{Same as Table~\ref{tab:error_statistics_ici}, but for AWS channels. }
+	\label{tab:statistics_qrnn_aws}
+	\begin{tabular}{llrr|rr}
+		\tophline
+		&&\multicolumn{2}{c|}{Simulations}& \multicolumn{2}{c}{QRNN-single} \\
+		\cline{3-6}
+		%		\hline
+		&&   Clear-sky &   All-sky &   Predicted(All) & Predicted(5\,K) \\
+		\middlehline
+		AWS-32  &Bias     & 0.00 & -1.32 &  -0.03 & -0.02 \\
+		&MAE      & 0.36 &  1.57 &   0.54 &  0.43 \\
+		&STD      & 0.46 &  6.42 &   1.02 &  0.61 \\
+		&skewness & 0.01 & -8.43 &  -0.07 & -1.98 \\
+		\middlehline
+		AWS-33	&Bias     & -0.01 & -0.98 &  0.02 &  0.01 \\
+		&MAE      &  0.36 &  1.23 &  0.49 &  0.42 \\
+		&STD      &  0.45 &  4.70 &  0.76 &  0.56 \\
+		&skewness & -0.00 & -8.78 &  0.04 & -0.79 \\
+
+		\middlehline
+		AWS-34	&Bias     &  0.00 &  -0.68 &  0.02 &  0.01 \\
+		&MAE      &  0.51 &   1.07 &  0.51 &  0.46 \\
+		&STD      &  0.64 &   3.67 &  0.75 &  0.60 \\
+		&skewness & -0.00 & -10.32 & -0.55 & -0.59 \\
+		\middlehline
+		AWS-35	&Bias     &  0.00 &  -0.43 &  0.01 &  0.00 \\
+		&MAE      &  0.50 &   0.84 &  0.48 &  0.44 \\
+		&STD      &  0.63 &   2.65 &  0.71 &  0.57 \\
+		&skewness & -0.01 & -12.49 & -0.40 & -0.29 \\
+		\middlehline
+		AWS-36  &Bias     & 0.00 &  -0.28 &   0.03  &  0.03 \\
+		&MAE      & 0.70 &   0.90 &   0.63  &  0.60 \\
+		&STD      & 0.88 &   2.06 &   0.86  &  0.76 \\
+		&skewness & 0.01 & -11.80 &  -0.35  & -0.20 \\
+		\bottomhline				
+	\end{tabular}
+	\belowtable{} % Table Footnotes
+\end{table*}
+In an analogy between the results from ICI channels, we perform a similar error distribution analysis  and the results are displayed in Table~\ref{tab:statistics_qrnn_aws}.
+For channel AWS-32, the average bias and standard deviation in the uncorrected dataset is -1.32\,K and 6.42\,K respectively.
+However, after correction, the bias and standard deviation reduce to -0.03\,K and 1.02\,K.
+A decrease in the skewness of error distributions is evident, but a relatively high values after prediction indicate presence of cases with partially-corrected cloud impact.
+Filtering out cases with high cloud impact improves the statistics overall except for skewness, which increases.
+For AWS-33, the predictions have slightly higher accuracy than AWS-32.
+The MAE in predictions is only 0.49\,K in comparison to 1.23\,K for the measurements.
+Low skewness and bias values indicate that the error distribution is quite symmetric.
+Similar results are also seen for AWS-35 and AWS-36.
+For both channels, the error distributions are relatively more symmetric than the other channels.
+Also, it is worth to noting that when cases with 5\,K cloud correction are removed, the spread of prediction errors is narrower than noise.
+
+\subsection{Prediction Uncertainty}
+\label{sec:prediction_uncertainty}
+%f 
+\begin{figure}[t]
+	\includegraphics[width = 70mm]{Figures/prediction_uncertainty_I2V.pdf}	
+	\caption{The prediction uncertainty for I2V (QRNN-single) with respect to quantiles for randomly selected 1500 cases.
+The quantiles have been plotted at equidistant points.
+The black line represents a hypothetical Gaussian distribution of $270\pm0.60$\,K, which is of the order of standard deviation for I2V predictions (see Table~\ref{tab:error_statistics_ici}).}
+	\label{fig:prediction_uncertainty_I2V}	
+\end{figure}
+\begin{figure}[t]
+	\includegraphics[width=70mm]{Figures/deviation_posterior_samples_I2V.pdf}	
+	\caption{The distribution of predicted errors and observed errors for I2V as obtained from QRNN-single for the test dataset.
+The predicted errors are estimated as deviation of random samples from posteriori distribution to corresponding median values.}
+	\label{fig:predicted_errors}	
+\end{figure}
+\begin{figure}[t]
+	\includegraphics[height = 70mm]{Figures/calibration_QRNN_I2V.pdf}	
+	\caption{Calibration of the prediction intervals obtained from QRNN-single for I2V. }
+	\label{fig:calibration_I1V}	
+\end{figure}
+\begin{figure*}[t]
+	\includegraphics[width=\textwidth]{Figures/PDF_uncertainty_bins_QRNN-single.pdf}	
+	\caption{Distribution of errors binned according to their uncertainty. Results are from QRNN-single for channels I1V, I2V and I3V.}
+	\label{fig:error_distribution_uncertainty_bins}	
+\end{figure*}
+%f
+\begin{figure}[t]
+	\includegraphics[width = 80mm]{Figures/cloud_impact_uncertainty_AWS.pdf}	
+	\caption{The average confidence intervals (2$\sigma$) plotted against the magnitude of cloud impact for all AWS channels.}
+	\label{fig:uncertainty_cloud_impact}	
+\end{figure}
+
+In order to analyse the sharpness of the predictions, the deviations of predicted quantiles from its median value are estimated.
+Fig.~\ref{fig:prediction_uncertainty_I2V} shows the spread of prediction uncertainties over different quantiles for randomly chosen 1500 cases.
+The large spread in the predicted errors indicates that QRNN is successful in representing uncertainties for each case individually, rather than expressing them as a single measure for all cases.
+In the latter case, the uncertainty estimates would be concentrated along a narrow interval.
+Among the cases associated with low uncertainty, the distribution is quite symmetric along the median value.
+These cases are concentrated along a narrow interval and lie close to the black curve representing a Gaussian spread.
+On the contrast, cases with high uncertainty are unequally spaced and have a larger spread over positive quantiles than negative quantiles.
+Thus QRNN is capable of capturing non-Gaussian error distributions as well.
+
+Fig.~\ref{fig:predicted_errors} shows the comparison of observed errors (prediction accuracy) to predicted errors.
+The predicted and observed errors have good agreement for the peak of the distribution, but the predicted errors are spread out asymmetrically.
+QRNN is not able to represent the left wings of the distribution.
+This could also be a sampling issue, as the high errors we try to predict constitute a very small part of the complete dataset and we do not derive any sample from outside $\pm3\sigma$.
+
+Fig.~\ref{fig:calibration_I1V} shows the calibration of the prediction intervals on the test dataset for I1V.
+The predictions for the complete test dataset are well calibrated and follow the y=x line.
+This shows that the training and test datasets come from the same a priori distribution.
+On the other hand, when only the cases with  cloud correction greater than 10\,K are considered, the predictions in all the intervals are poorly calibrated.
+In this case the calibration curve lies below the y=x line, indicating that the predicted intervals are too narrow, or the uncertainty is underestimated.
+The calibration curves for I2V and I3V are also similar.
+
+Next we investigate if the uncertainty estimates given by QRNN are representative of prediction accuracy.
+Fig.~\ref{fig:error_distribution_uncertainty_bins} shows the errors of best estimate binned by their corresponding uncertainty in $\pm2\sigma$  confidence interval.
+For all three channels, the spread of error distribution increases as the uncertainty about the accuracy of the trial increases.
+The cases with high certainty have a narrow and sharp distribution, and the errors are mostly less than $\pm$2.5\,K.
+With increase in the uncertainty, frequency of cases with high accuracy decreases and the distributions spread out symmetrically to higher errors.
+Poor predictions occur more frequently when uncertainty is high.
+Cases with accurate predictions yet high uncertainty are also present.
+In spite of individual variations in the error distributions for each channel, predictions and their corresponding uncertainties followed the same relationship.
+
+With AWS, the behaviour of predicted uncertainties was observed to be similar as for ICI (not shown).
+The calibration plots and the predicted errors followed the same pattern as for ICI and are not shown.
+However, the relation between the mean uncertainty estimate and cloud impact is displayed in Fig~\ref{fig:uncertainty_cloud_impact}.
+For all five channels, the predictions with small or relatively low cloud signal have a low uncertainty or in other words have high sharpness.
+As fraction of cloud impact increases, the predictions become increasingly uncertain.
+The most uncertain predictions are for the lowest peaking channel AWS-32, which incidentally is also most affected by  hydrometeor impact.
+
+\section{Discussion}
+
+\subsection{Cloud correction with existing sensors}
+%
+The results from MWHS-2 show that QRNN based cloud correction is partially successful in correcting the cloud impact with existing sensors.
+The methodology can correctly address the large negative values in the all-sky and clear-sky deviations, but cases with low cloud impact end up with inadequate correction.
+The resulting error distributions are not completely symmetric but have a low bias and spread.
+Among several input channel combinations described for QRNN-single, the performance of combination 89+150\,GHz was observed to be optimal.
+The positive performance with 150\,GHz is not unexpected, as 150\,GHz is highly sensitive to ice hydrometeors and cloud water.
+But using 89\,GHz along with 150\,GHz gives a slightly better performance.
+The channel 89\,GHz is affected by surface emissivity and is relatively less sensitive to cloud water content, however its sensitivity to warm clouds in the lower troposphere could be important.
+We also investigated the impact of two temperature sounding channels (118....??).
+Both these channels provide complementary information to humidity channels in the lower troposphere.
+Including both these channels in the training process gave almost similar performance as with the combination 89+150\,GHz.
+Even though the cloud correction is partial, the performance is comparable to existing cloud filtering techniques like SI.
+SI is also a partial filter which identifies the contamination only due to precipitation and cloud ice.
+It removes most of the cases with high departures but the resulting error distributions are asymmetric.
+
+The partial performance of QRNN is due to incomplete orthogonal information to 183\,GHz humidity channels.
+The weighting functions of window channels 89 and 150\,GHz, and the two 118\,GHz channels peak in the lower troposphere.
+Among these four channels, 150\,GHz has the highest peaking function around 4\,Km \cite{chen2020mwhs}.
+These channels can only provide coverage to the humidity channels in lower and mid troposphere; nonetheless, the 183\,GHz channels are sensitive to hydrometeor content beyond 2\,Km.
+Due to missing complementary information from other channels in the upper troposphere, QRNN fails to train to predict these cases accurately.
+Additional information from other channels is necessary to help QRNN train better.
+Among the existing channels, the overlapping weighting functions of 183\,GHz can provide additional information to train QRNN.
+Though these channels can help in improving the training, the non-orthogonal information introduces highly correlated observational errors.
+This is undesirable in data assimilation for NWP, but in future if the operational centres progress with approaches dealing correlated observation errors, using the configuration QRNN-all for cloud correction could be beneficial.
+
+\todo{ uncertainty discussion}
+
+\subsection{Cloud correction with sub-mm frequencies }
+%
+In the ICI observations examined here, the results show that using sub-mm channels can successfully predict the NFCS values with very high accuracy for I2V, and I3V.
+The predicted values without any filter have an excellent match with the true values, and the departures are symmetrically distributed around zero mean.
+Few cases with high cloud impact do affect the accuracy and introduce a small negative bias, but such cases are easily filtered out with a simple correction threshold filter.
+For example, it is shown that filtering out cases with correction greater than 5\,K, results in variabilities of the order of noise with minimal reduction in data (2-4\%).
+For channel I1V, a slightly lower accuracy is observed due to relatively higher number of cases with residual cloud impact.
+The accuracy is improved by activating the correction filter, but some effect of residual cloud impact is apparent in the high negative skewness.
+Interestingly, reducing the correction threshold further has no significant effect on flagging these residual cases; in fact only the clear-sky cases are removed.
+This indicates that for I1V, QRNN is unsuccessful in accounting for few cases with low cloud impact.
+Compared to other two higher peaking channels, I1V is more sensitive to the effect of hydrometeors  and contamination from surface effects.
+The cases with surface contamination are also localized and seasonal.
+For QRNN to predict such cases accurately, QRNN should have access to complementary information from sub-mm channels.
+However, the weighting functions of sub-mm channels can provide only a partial coverage to the hydrometeor impact at I1V.
+A part of lower troposphere sensed by I1V has almost zero coverage from sub-mm channels.
+Though such cases are few, their lack of representation prevents QRNN from correctly learning to predict the clear-sky values accurately.
+
+A similar pattern of results is seen for when only 325\,GHz channel is used to correct cloud impact in AWS.
+QRNN is successful in predicting NFCS values for all channels except for the lowest peaking channel AWS-32.
+For AWS-32, the resulting error distributions have significantly lower spread than the measurements, but are still negatively skewed.
+This indicates that a single sub-mm channel like 325\,GHz is sufficient enough for cloud correction at 183\,GHz.
+This is an important result as smaller satellites are limited by their size to measure all sub-mm wavelengths.
+
+With ICI and AWS, for some channels the variability of errors smaller than measurement noise is achieved.
+This is a consequence of predictions for cases which lack cloud impact.
+QRNN predictions are weighted mean of measurements between channels.
+For clear-sky conditions, multiple observations of same scene from different channels can cancel out the noise.
+This effect is observed to be stronger in ICI observations than AWS, due to more number of input channels while training in the former.
+It should be noted that with satellite measurements, the spread of error distributions smaller than noise could be difficult to achieve due to other underlying uncertainties not considered here.
+However, symmetric error distributions with low spread could still be extremely important from the context of data assimilation.
+Most of the existing cloud filtering schemes eg.
+\cite{buehler:aclou:07} and SI \cite{} work well only at removing cases with high cloud impact.
+As a consequence of the residual cloud impact, the error distributions are highly skewed.
+This is not the optimal solution but the best which can be achieved with present sensors.
+To use these observations correctly data assimilation schemes often inflate their asymmetric error distributions at the cost of artificially suppressing the observational impact.
+
+The analysis of QRNN predicted errors and calibration plots show that QRNN is successful in providing well calibrated probabilistic predictions of the posterior distributions except for few cases associated with high cloud impact.
+This is not unexpected as such cases form a small subset of the training set and their priori distribution is different from the entire dataset.
+The clear-sky cases dominate the test/training dataset, thus the a priori distribution is representative of the same.
+The a priori distribution of cloudy cases is different to the clear-sky cases, therefore the predictions are poorly calibrated for the former.
+Predictions for textit{out-of-distribution} cases is always a challenging task for deep learning algorithms and  shall always limit the performance.
+Improving the representation of such cases in the a priori distribution can help alleviate this problem.
+A larger training dataset would also be required to increase the representation of such cases in QRNN.
+From data assimilation perspective, information on case-specific uncertainties is extremely useful.
+It allows for an effective selection of weights, thus significantly improving/deteriorating the impact of measurements.
+
+\section{Conclusion and outlook}  %% \conclusions[modified heading if necessary]
+%
+
+\todo {incomplete}
+
+In this study, a methodology based on quantile regression neural network (QRNN) is used for identifying and correcting the cloud contamination in 183\,GHz channels.
+QRNN is a neural network which trains on all-sky brightness temperatures from  channels containing orthogonal information to humidity channels, to estimate the noise free clear-sky (NFCS) radiances for humidity channels.
+The output is posterior distribution of the predictions over different quantiles.
+
+The applicability of QRNN based correction to current sensors is demonstrated with MHWS-2 and it is shown that QRNN  is partially successful in removing the cloud impact.
+This is not optimal solution, but it is in agreement with what can be achieved with the present instruments.
+Infact, for lower peaking humidity channels, our approach gives a better cloud cleared product with minimal rejection of data.
+
+The robustness of QRNN is  demonstrated by utlisation of sub-millimeter (sub-mm) channels.
+
+The smaller satellite missions AWS, where only one of the higher frequencies is available.
+The same approach was applicable in this case, and the results proved that even one sub-mm channel is sufficient enough for cloud correction at 183\,GHz.
+
+A slightly lower accuracy was observed for cases with high cloud impact.
+In few of such cases, the predicted NFCS values were not completely cloud free.
+This is expected as not all cases can be represented by the a priori distribution QRNN trains on.
+Predictions for \textit{out-of-distribution} cases is always a challenging task for deep learning algorithms and  shall always limit the performance.
+Improving the representation of such cases in the a priori distribution can help alleviate this problem.
+However since such cases are few, filtering them out results in highly accurate NFCS predictions with minimal reduction in data.
+
+High quality cloud corrected radiances have great potential in DA systems.
+Most DA systems reject upto 80\% of the available observations due to cloud contamination.
+The loss is largest in mid-latitudes.
+Although, NWP systems are gradually moving towards assimilating all-sky radiances but the use of data is overly cautious.
+Misrepresentation of clouds can deteriorate the model outputs.
+To improve the representivity of clouds in the models, the observational errors are inflated as a function of the cloud amount.
+Most NWP centres use a scattering index(SI) based on brightness temperatures of 89 and 150\,GHz channels as a measure of cloud amount or background departure check; however such approaches act only as a partial measure of cloud identification.
+On the contrary, cloud cleared microwave radiances offer forecast benefits without additional complexities.
+Another advantage of combining 183\,GHz and sub-mm for cloud correction is that NWP systems, which are not yet prepared for higher frequency channels, could still benefit from the data early on.
+
+%% The following commands are for the statements about the availability of data sets and/or software code corresponding to the manuscript.
+%% It is strongly recommended to make use of these sections in case data sets and/or software code have been part of your research the article is based on.
+
+\codeavailability{TEXT} %% use this section when having only software code available
+
+\dataavailability{TEXT} %% use this section when having only data sets available
+
+\codedataavailability{TEXT} %% use this section when having data sets and software code available
+
+\sampleavailability{TEXT} %% use this section when having geoscientific samples available
+
+\videosupplement{TEXT} %% use this section when having video supplements available
+
+\appendix
+\section{ARTS simulation setup}    %% Appendix A
+\label{appendix:ARTS_setup}
+%
+**** Some parts copied directly from AWS report *****
 Cloudsat profiles during August 2015 were randomly selected for forward simulations.
@@
 Both clear-sky and all-sky scenarios were simulated, and no differentiation was made between the observations over ocean/sea and land.
-\subsubsection{Simulation setup}
-%
-**** Some parts copied directly from AWS report *****
 
@@
 
-\subsubsection{Produced dataset}
-%
-Using the simulation setup described in previous section,  
-220\,000 cases for each ICI and MWI frequency were simulated.
-For both instruments, the channel frequencies were simulated directly.
-For AWS, 140\,000 cases were simulated.
-Forward simulations were performed for 21 monochromatic frequencies.
-These frequencies were interpolated to a finer grid to get the AWS channel brightness temperatures.
-All AWS sensor viewing angles (from $0^\circ$ to $45^\circ$) were simulated, but the results described in this study are based on nadir viewing angle.
-
-ARTS simulations are noise free, so to incorporate the measurement uncertainties, whenever needed, gaussian noise was added to according to the channel NE$\Delta$T (Table~\ref{tab:ICI_MWI_channels},Table~\ref{tab:specifications_AWS}).
-For cases where MWI and ICI simulations were assumed to be remapped to a common footprint, the NE$\Delta$T for corresponding to ICI channels was used (See Sect.~\ref{mwi_channels}).
-
-The noise free simulations were divided into training and testing datasets.
-Out of the 220\,000 simulations for ICI and MWI each, 175\,000 cases were randomly picked to form the training set.
-The rest were used for testing.
-A smaller database was selected for AWS.
-120\,000 simulations were used for training and the remaining were used for testing.
-
-\subsection{Quantile regression neural networks}
-%
-The task that we aim to solve in this study is to predict the NFCS brightness
-temperature $\ynfcs$ at a given $187\unit{GHz}$ channel from a vector of
-cloud-contaminated observations $\y$. Since the information-content of the
-cloud-contaminated observations is certainly too low to solve this problem
-exactly, a probabilistic formulation is appropriate here. The aim thus becomes
-to predict the conditional distribution $p(\ynfcs | \y)$ of the NFCS brightness
-temperatures $\ynfcs$ given the cloud-contaminated observations $\y$.
-
-As has been shown in \citet{pfreundschuh:aneur:18}, quantile regression neural
-networks (QRNN) can be used to solve these type of problems. Instead of a point
-prediction, as it is typically performed in regression problems, QRNNs learn to
-predict a vector of quantiles, which can be used to approximate the distribution
-of the predicted quantity conditional on the network inputs. Using QRNNs to
-perform probabilistic cloud correction thus not only allows deriving an estimate
-for $\ynfcs$ but also for the error of the corrected observations.
-
-For this application, the predicted percentiles are chosen to be
-$0.2\%, 3\%, 16\%, 50\%, 85\%, 97\%$ and $99.8\%$. For a Gaussian
-distribution with mean $\mu$ and standard deviation $\sigma$ the
-approximately corresponds to $\mu -3\sigma, \mu-2\sigma, \mu-\sigma
-, \mu, \mu + \sigma, \mu + 2\sigma, \mu + 3\sigma$ and thus allows
-estimating the $\pm 1, \pm 2$ and $\pm 3\sigma$ confidence intervals.
-The median is used as point estimate for the corrected $\ynfcs$.
-
-QRNN's are trained to minimize the mean of the quantile loss functions
-%
-\begin{align}
-  \mathcal{L}_\tau(y_\tau, y) &=
-  \begin{cases}
-    \tau|y - y_\tau|, & y_\tau < y \\ (1 - \tau)|y_\tau - y|, & \text{otherwise}
-    \\
-  \end{cases}
-\end{align}
-%
-for all predicted quantile fractions $\tau$, where $\y_\tau$ is the predicted
-quantile and $y$ the reference value from the training set. The quantile loss is
-used in this study as a performance criterion for the tuning of the hyper
-parameters of the QRNN. In addition to the quantile loss, also the Continuously
-Ranked Probability Score (CRPS) is considered. Given a predicted cumulative
-distribution function (CDF) $F$ and the reference value $y$, the CRPS is defined as
-%
-\begin{align}
-  \text{CRPS}(F, y) = \int_{-\infty}^{\infty} \left (F(y') - y\right )^2\: dy'.
-\end{align}
-%
-To compute the CRPS for a predictions from a QRNN, the predicted quantiles are
-used to derive a piece-wise linear approximation of the CDF of the predicted
-distribution and evaluate the above integral.
-
-%Fig.~\ref{fig:posterior_distribution_I2V} presents examples of the predicted quantiles for three different corrected observations of the ICI I1V channel.
-The three cases have a similar median value but very different spread of the remaining quantiles.
-These examples illustrate the case of very similar corrected observation values (the estimated median) but with different estimated observation errors.
-
-\subsubsection{ QRNN model configurations}
-%
-\label{QRNN_models}
-
-\begin{table*}[t]
-	\caption{Summary of the different QRNN models used in the study.}
-	\label{tab:QRNN_models}
-	\begin{tabular}{lllll}
-		\tophline
-		QRNN model & Instrument & Target & Input 183\,GHz channel(s) &Other training inputs \\
-		\middlehline
-		QRNN-single &  ICI 	& I1V/I2V/I3V 	& I1V/I2V/I3V, & I5V, I6V, I7V, I8V, I9V, I10V, I11V\\
-		\cline{2-5}
-		&  MWI 	& MWI-15/MWI-16 & MWI-15/MWI-16	& I5V, I6V, I7V, I8V, I9V, I10V, I11V \\
-		\cline{2-5}
-		& AWS	& AWS-32/AWS-33/ &  AWS-32/AWS-33/ & AWS-41, AWS-42, AWS-43, AWS-44\\
-		&		& AWS-34/		 &	AWS-34/		   & \\
-		&		& AWS-35/AWS-36	 & AWS-35/AWS-36,  &\\
-		\cline{1-5}
-		QRNN-all &  ICI 	& I1V/I2V/I3V 	& I1V, I2V, I3V & I5V, I6V, I7V, I8V, I9V, I10V, I11V\\
-		\cline{1-5}
-		QRNN-mwi &  MWI		& MWI-14/MWI-15/ &  MWI-14, MWI-15, & None 	\\	
-		&			& MWI-16/		 &  MWI-16, & \\
-		&			& MWI-17/MWI-18	 &  MWI-17, MWI-18  &\\					
-		\bottomhline
-	\end{tabular}
-	\belowtable{} % Table Footnotes
-\end{table*}
-
-In the study, three different QRNN cloud-correction models are formulated.
-The basic construction of all three models is to train for one of the available 183\,GHz channels, using certain input channels.
-The selection of input channels is categorized by the type of QRNN model chosen.
-
-In the first model, ``QRNN-single'', the training inputs always contain data from the target 183\,GHz channel, and one or more available sub-mm channels.
-Other 183\,GHz channels are not included in the training.
-For ICI and MWI, 325\,GHz, 448\,GHz and 664\,GHz are used in the training, while for AWS only 325\,GHz is used.
-
-The second model, ``QRNN-all'', is defined to investigate the  impact of using all 183\,GHz channels concurrently.
-In this model, the training set includes data from all available 183\,GHz channels, along with other sub-mm channels.
-This model is applied only to ICI.
-
-The third model, ``QRNN-mwi'' is used only for MWI channels. In this case, all 183\,GHz channels are used concurrently in the training set. No other data from sub-mm channels is used.
-
-For each model, multiple configurations are defined according to the satellite instrument.
-A summary of the three QRNN models and their different configurations used in this study is provided in Table~\ref{tab:QRNN_models}.
-
-\subsubsection{QRNN implementation}
-\label{sec:qrnn-implementation}
-
-The implementation of QRNN is based on PyTorch, an open source machine learning
-library \citep{paszke2017automatic}. It is developed and available as a part of
-\textit{typhon:tools for atmospheric research} software package
-       [\todo{developer's version??}].
-
-For this study, we initialize the quantile loss function with quantile fractions $\tau$ = [0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998] to train the neural network to predict the corresponding quantiles $x_{\tau}$ = [$-3\sigma, -2\sigma, -1\sigma, median, 1\sigma, 2\sigma, 3\sigma $].
-QRNN is trained with simulated brightness temperatures from different channels, no other data is included.
-The input channels are variable and are determined by the type of QRNN model used.
-The different QRNN models are described in Sect.~\ref{QRNN_models}.
-
-A custom data augmentation scheme is implemented to build a robust learning network.
-At each training iteration, noise is added to the noise-free inputs according to the measurement uncertainty.
-The target training data is always kept noise free.
-This ensures that the model is exposed to different datasets during the entire training process, and avoids memorisation of training samples.
-The input data is normalized with mean and standard deviation.
-While training, 10\% of the training data is used for validation.
-
-The neural network is trained with an adaptive form of stochastic batch gradient descent.
-During the training process, at each iteration, the loss in the validation dataset in monitored.
-If the validation loss remains stagnant for a certain number of epochs, the training rate is reduced  by a given reduction factor.
-This process is continued till a minimum learning rate is achieved.
-
+\subsection{QRNN network structure}
+\label{appendix:hyperparamter}
+%
+\begin{figure*}[t]
+	\centering
+	\includegraphics[height=60mm]{Figures/CRPS.pdf} 
+	\caption{CRPS(left) and mean quantile loss(right) averaged over all predicted quantiles for different combinations of layer width and hidden layers ($n_h$).
+The results are from QRNN-single applied to I2V.}
+	\label{fig:grid_search}	
+\end{figure*}
 A high performing QRNN model also requires tuning of multiple hyper-parameters.
@@
 
-\section{Results}
-%
-In this section, QRNN is used to predict the NFCS values for operational humidity channels.
-The main aim of this study is to demonstrate that sub-mm channels can be used to formulate the cloud filtering/correction of data measured around 183\,GHz.
-Different combinations of 183\,GHz channels and sub-mm channels are applied to QRNN and the results are compared.
-The impact of different hyper-parameters on QRNN performance is also discussed.
-NFCS simulations are used to analyse the prediction accuracy.
-Results from both pure-filtering and correction are described.
-Furthermore, the case specific uncertainties obtained from QRNN are also discussed.
-
-\subsection{QRNN network structure}
-%
-\begin{figure*}[t]
-	\centering
-	\includegraphics[height=60mm]{Figures/CRPS.pdf} 
-	\caption{CRPS(left) and mean quantile loss(right) averaged over all predicted quantiles for different combinations of layer width and hidden layers ($n_h$).
-The results are from QRNN-single applied to I2V.}
-	\label{fig:grid_search}	
-\end{figure*}
 In this study, we investigated the performance of QRNN only to certain hyper-parameters like number of neurons, hidden layers, learning rate, convergence epochs and batch size.
@@
 
-\subsection{ICI}
-\subsubsection{Example results}
-%
-%f
-\begin{figure}[t]
-	\centering
-	\includegraphics[height=60mm]{Figures/posterior_distribution_I1V.pdf} 
-	\caption{Predicted quantiles of the conditional distribution of $\ynfcs$ for
-		the ICI I1V channel.}
-	\label{fig:posterior_distribution_I1V}	
-\end{figure}
-%f
-\begin{figure*}[t]
-	\includegraphics[width=\textwidth]{Figures/PDF_predictions_ICI.pdf} 
-	\caption{Distributions of point estimate NFCS from QRNN-single for channels I1V, I2V and I3V. The corresponding distributions for NFCS simulations are also shown.}
-	\label{fig:PDF_predictions}	
-\end{figure*}
-
-Fig.~\ref{fig:posterior_distribution_I1V} presents examples of the predicted quantiles for three different corrected observations of the ICI I1V channel.
-The three cases have a similar median value but very different spread of the remaining quantiles.
-These examples illustrate the case of very similar corrected observation values (the estimated median) but with different estimated observation errors.
-For an analysis of QRNN predictions, a point estimate of the posterior distribution is required.
-Usually for Bayesian analysis, the posterior mean or posterior median are selected as point estimates.
-In this study, we assume the posterior median to be the best estimate for the predicted NFCS value.
-The distribution of point estimates is shown in Fig.~\ref{fig:PDF_predictions}.
-For all three channels, an excellent agreement between the predictions and simulations is observed.
-This indicates that QRNN is successful in predicting NFCS values for majority of the cases.
-At lower brightness temperatures, the frequency of predictions is slightly smaller than simulations.
-This could be due to few QRNN predictions ending up with partially corrected cloud impact.
-
-\subsubsection{Analysis of cloud filtering}
-%
-\label{sec:cloud_filtering}
-%f 
-\begin{figure*}[t ]
-	\includegraphics[width=\textwidth]{Figures/error_distribution_QRNN-single.pdf} 
-	\caption{Error distributions for deviations of filtered and predicted data to NFCS simulations.
-The results are from QRNN-single and channels I1V, I2V and I3V.
-Noise for each channel is also plotted for reference.
-The label ``Uncorrected'' represents the measurement data and ``Filtered(5\,K)'' represents the dataset when no correction is made but cases with cloud correction greater than 5\,K are rejected.
-``Predicted(All)'' denotes the entire prediction dataset, while ``Predicted(5\,K)'' refers to the predicted dataset but where cases with cloud correction greater than 5\,K are excluded.}
-	\label{fig:error_distributions}	
-\end{figure*}
-\begin{table*}[t]
-	\caption{ Error statistics for deviations of filtered and predicted data to NFCS simulations. 
-		The values for Bias, mean absolute error(MAE), standard deviation(STD), and measure of skewness(Skewness) are shown.
-Results are from both QRNN-single and QRNN-all and for channels I1V, I2V and I3V.
-The number in parentheses is the percentage of cases removed by filtering.
-The label ``Filtered(5\,K)'' represents the dataset when no correction is made but cases with cloud correction greater than 5\,K are rejected, ``Predicted(All)'' refers to the complete predicted dataset, while ``Predicted (5\,K)'' denotes the prediction dataset but where cases with cloud correction greater than 5\,K are excluded.}
-	\label{tab:error_statistics_ici}
-	%	\tabcolsep=0.11cm
-	\begin{tabular}{llrr|rrr|rrr}
-		\tophline
-		&&\multicolumn{2}{c|}{Simulations}& \multicolumn{3}{c|}{QRNN-single} & \multicolumn{3}{c}{QRNN-all}\\
-		\cline{3-10}
-		%		\hline
-		&&   Clear-sky &   All-sky &  Filtered & Predicted & Predicted &   Filtered & Predicted & Predicted \\
-		&&&&							(5\,K) &(All)& (5\,K) & (5\,K)&(All)& (5\,K)\\
-		\middlehline
-		%		\multicolumn{7}{c}{Channel - I1V}\\
-
-		I1V& Bias     &  0.00 & -1.88 & -0.32(6.1\%) & -0.06 & -0.04 & -0.31(6.1\%) & -0.06 & -0.04 \\
-		&MAE      &  0.64 &  2.32 &  0.79 &  0.64 &  0.55 &  0.78 &  0.61 &  0.54 \\
-		&STD      &  0.80 &  8.84 &  1.07 &  0.98 &  0.73 &  1.07 &  0.91 &  0.71 \\
-		&Skewness & -0.01 & -8.10 & -1.53 & -1.53 & -0.75 & -1.52 & -1.07 & -0.55 \\
-		\middlehline
-		I2V &Bias     & -0.00 &  -1.04 & -0.24(3.7\%) & -0.01 & -0.00 & -0.24(3.6\%) & -0.05 & -0.03 \\
-		&MAE      &  0.64 &   1.52 &  0.74 &  0.52 &  0.46 &  0.75 &  0.44 &  0.39 \\
-		&STD      &  0.80 &   5.95 &  0.99 &  0.82 &  0.59 &  0.99 &  0.67 &  0.50 \\
-		&Skewness &  0.00 & -10.80 & -1.10 & -2.17 & -0.27 & -1.05 & -2.22 & -0.27 \\
-		\middlehline	
-		I3V &Bias     & -0.00 &  -0.63 & -0.18(2.3\%) &  0.01 &  0.02 & -0.19(2.2\%) & -0.03 & -0.03 \\
-		&MAE      &  0.64 &   1.15 &  0.71 &  0.51 &  0.47 &  0.72 &  0.46 &  0.42 \\
-		&STD      &  0.80 &   4.27 &  0.93 &  0.77 &  0.59 &  0.95 &  0.68 &  0.54 \\
-		&skewness & -0.00 & -13.41 & -0.86 & -1.75 & -0.11 & -0.93 & -1.53 & -0.14 \\
-		\bottomhline
-	\end{tabular}
-	\belowtable{} % Table Footnotes
-\end{table*}
-
-In this section, we use the point estimates to formulate a cloud filtering scheme.
-All cases with  cloud correction greater than a certain threshold are classified as cloudy and omitted from the dataset.
-Cloud correction is calculated as the difference of the point estimate to the corresponding measurement.
-Since this is a pure-filter, for the cases classified as clear-sky, the a priori values are used instead of the point estimates.
-
-To implement the cloud filtering scheme, we chose 5\,K cloud correction as the filtering threshold.
-All cases with correction greater than 5\,K were rejected.
-In order to analyse the performance of the filtering threshold, the deviations of the filtered measurements to the NFCS simulations were calculated.
-Fig.~\ref{fig:error_distributions} shows the distribution of the deviations for filtered(red) and original datasets(green).
-Cloud contamination causes a reduction in the brightness temperatures, and introduces a large negative bias in the error distributions.
-Without any cloud impact, the error distributions must follow a Gaussian distribution with a narrow spread.
-When filtering is activated, the resulting distributions have a low but asymmetric spread.
-The right side of the distributions follows the measurement noise, as expected, but the left side has a significantly smaller negative skewness than the measurements.
-This indicates that 5\,K filter can successfully remove cases associated with high cloud impact.
-However at the same time, the asymmetric error distribution is a result of cases erroneously classified as clear-sky.
-
-For a quantitative assessment of the performance achieved with cloud filtering, we calculated the average error bias, MAE (mean absolute error) and standard deviation of the deviations.
-The asymmetry of error distributions around their mean is also calculated through the measure of skewness.
-Fisher-Pearson coefficient of skewness is used to calculate the measure of skewness:
-\begin{equation}
-g_1 = \frac{m_3}{m_2^{3/2}}, 
-\end{equation}
-where $m_2$ and $m_3$ are biased sample's second and third central moments.
-The error metrics corresponding to the error distributions described in Fig.~\ref{fig:error_distributions} are provided in Table~\ref{tab:error_statistics_ici} under label "Filtered(5\,K)".
-The average bias in I1V measurements is -1.88\,K, and rejecting around 6\% of the cases as cloudy, reduces the bias to -0.32\,K.
-The standard deviation also reduces to 1.07\,K from 8.84\,K.
-Similarly for I2V, the average error bias in all sky measurements is -1.04\,K, that reduces to -0.24\,K after filtering.
-The corresponding improvement in MAE is almost 65\%.
-Only 3.7\% of the total cases are rejected to achieve this accuracy.
-For I3V, filtering classifies 2.3\% of the total cases as cloudy and reduces the bias to 0.18\,K from -0.63\,K and the standard deviation from 5.95\,K to 0.91\,K.
-The results from QRNN-all are also shown in the same table.
-Using all 183\,GHz channels concurrently has no notable impact on the cloud filtering.
-Almost similar statistics are obtained from both models.
-
-Overall for all three channels, the notable decrease in the errors indicates that the cloud filter is effective in removing most of the cloudy cases, however few cases with low cloud impact still pass through the filter and deteriorate the performance.
-Thus pure-filtering approach can prove as a reliable procedure for removing cases with high cloud impact, but additional measures are needed to remove cases with low cloud impact.
-
-A lower filtering threshold can help alleviate this problem to certain extent, however that can come at the cost of high rejection rate.
-We investigated the performance of cloud filtering with different threshold values.
-Fig.~\ref{fig:filtering_thresholds} shows the average errors obtained from different filtering thresholds and the corresponding percentage of data omitted.
-Lowering the filtering threshold from 5\,K to 2.5\,K has only a small effect on the filter performance.
-However, a further decrease in the filtering threshold decreases the average error bias significantly, albeit with a high rejection rate.
-For example for I1V, when all cases with cloud correction greater 0.5\,K are filtered, the mean error bias of the subset is -0.06\,K, MAE is 0.59\,K and the standard deviation is 0.75\,K.
-Though, these values are comparable to the NFCS simulations, the high performance comes at the cost of rejecting more than 30\% of the total cases.
-The high fraction of rejection is a consequence of clear-sky cases being erroneously classified as cloudy.
-Since QRNN gives out NFCS values, choosing an unusually low correction threshold can also classify noisy clear-sky cases as cloudy.
-
-\begin{figure}[t]
-	\includegraphics[width=70mm]{Figures/different_filtering_thresholds.pdf} 
-	\caption{A comparison of the  average bias when pure-filtering approach is applied with different thresholds (red curves).
-The corresponding fraction of cases rejected is also shown on the right y-axis(blue curves).
-The results are from QRNN-single.
-}
-	\label{fig:filtering_thresholds}	
-\end{figure}
-
-\subsubsection{Error of best estimate}  
-%
-%t
-\begin{table*}[t]
-	\caption{A comparison of the error statistics from QRNN-single and QRNN-all, when only cases with cloud correction greater than 10\,K are included.
-The number in the parentheses gives the fraction of cases included.}
-	\label{tab:error_statistics_ici_high_cloud_impact}
-	%	\tabcolsep=0.11cm
-	\begin{tabular}{lrr|rr|rr}
-		\tophline
-		&\multicolumn{2}{c|}{I1V}& \multicolumn{2}{c|}{I2V} & \multicolumn{2}{c}{I3V}\\
-		\cline{2-7}
-		&QRNN-single& QRNN-all & QRNN-single & QRNN-all  & QRNN-single & QRNN-all\\
-		\middlehline
-		Bias     & -0.53(4.02\%) & -0.38(4.07\%)  & -0.42(2.26\%) & -0.46(2.25\%) & -0.25(1.32\%) & -0.40(1.28\%) \\
-		MAE      &  2.32 &  1.93  &  2.77 &  2.08 &  3.10 &  2.59 \\
-		STD      &  3.13 &  2.63  &  3.65 &  2.85 &  4.03 &  3.47 \\
-		\bottomhline
-	\end{tabular}
-	\belowtable{} % Table Footnotes
-\end{table*}
-
-The QRNN prediction accuracy is estimated by computing the deviation of the best estimate to its corresponding NFCS simulation(Fig.~\ref{fig:error_distributions}).
-The predicted values have symmetric error distributions albeit with a large spread.
-The large spread on the left is due to cases which end up with incomplete cloud correction, while the spread on the right is from cases where the predicted values are warmer than the simulations.
-For all three channels, quite similar behaviour is observed, though I1V has the most cases with residual cloud impact.
-If the predicted cases with correction more than 5\,K are rejected, the resulting error distributions fit the measurement noise, except for I1V, where cases with residual cloud impact introduces a negative bias.
-
-For a quantitative assessment of the errors, we calculated the error metrics described in Sect.~\ref{sec:cloud_filtering} and the results are displayed in Table~\ref{tab:error_statistics_ici}.
-The average bias in I1V measurements is -1.88\,K, which reduces to -0.06\,K after cloud correction.
-The corresponding standard deviation is 0.98\,K in comparison to 8.84\,K in the measurements.
-The prediction accuracy of QRNN-single is further higher when filtering is made on the predictions.
-In this case, the residual bias is only -0.04\,K, and the standard deviation is 0.73\,K, which is in fact of the order of measurement noise (0.80\,K).
-Similar results are seen for I2V, though a better performance is observed.
-In I2V, the measurement bias is -1.04\,K which reduces to -0.01\,K after correction.
-The MAE reduces from 1.52\,K to 0.52\,K.
-Removing cases with correction greater than 5\,K from the predictions removes 3.7\% of the data and reduces the absolute error to 0.46\,K.
-The standard deviation of the resulting dataset is only 0.59\,K as compared to 0.80\,K from noise.
-The reduction in the variability is also evident in the Fig~\ref{fig:error_distributions}, where the peak of distributions is sharper.
-In comparison to I1V and I2V, I3V has the lowest fraction of the measurements with significant cloud impact.
-In the predicted dataset, the bias is 0.01\,K and the MAE is 0.51\,K.
-Including correction along with filtering reduces the MAE further down to 0.47\,K and standard deviation to 0.59\,K, which is again smaller than that of noise(0.80\,K).
-
-Next, we describe the results from QRNN-all.
-In this model, all 183\,GHz channels along with other sub-mm channels are included while training.
-This model is designed to identify if other channels of the same frequency can provide auxiliary information in the training process.
-The results from QRNN-all all are provided in the last columns of Table~\ref{tab:error_statistics_ici}.
-For I1V, using additional information from other two 183\,GHz channels has only a slight positive impact on the predictions.
-In the prediction dataset, the average bias for QRNN-all and QRNN-single is identical, but the MAE in QRNN-all are almost 4.5\% less than QRNN-single.
-However when the predictions are filtered with 5\,K threshold, the performance of both models is quite similar.
-This indicates that information from other channels is only slightly helpful in improving the correctness of cases associated with high cloud impact.
-The predictions for cases with low cloud impact have no significant gain.
-For I2V, the predictions from QRNN-all have a slightly worse average error bias than QRNN-single, yet a significant improvement in the prediction accuracy is observed.
-When all predictions are considered, the MAE is 0.44\,K in comparison to 0.52\,K from QRNN-single, showing an improvement of almost 15\%.
-Similarly the standard deviation of the errors is only 0.67\,K, which is notably smaller than the measurement noise.
-Additionally, when the predicted dataset is filtered with 5\,K threshold, the accuracy is even better.
-The MAE reduces to 0.39\,K and standard deviation to 0.50\,K.
-This implies that cases pertaining to clear-sky conditions and relatively low/no cloud impact benefit the most from the auxiliary information.
-This is in contrast to I1V, where accuracy of such cases remained unaffected.
-For I3V, the performance of QRNN-all is comparable to that for I2V.
-For I3V, the MAE in QRNN-all is 0.46\,K compared to 0.51\,K from QRNN-single, and the corresponding standard deviations are 0.68\,K and 0.77\,K.
-Removing the cases with cloud impact greater than 5\,K from the predictions, leads to no change in the average bias, but the MAE and standard deviation reduce by almost  8\% and 20\% respectively.
-This is again a consequence of improved prediction accuracy of cases with low/no cloud impact.
-
-In order to quantify the positive effect of QRNN-all on cases with high cloud impact, the error statistics for all cases with cloud correction greater than 10\,K were computed (Table~\ref{tab:error_statistics_ici_high_cloud_impact}).
-For I1V, only 4\% of the cases have cloud correction greater than 10\,K, but very low prediction accuracy.
-QRNN-all improves the overall error bias from -0.53\,K to -0.38\,K and the standard deviation from 3.13\% to 2.63\%, but is unsuccessful in removing the cloud impact completely.
-A likewise improvement is also observed for I2V.
-Despite both models being only partially successful in removing the cloud impact, QRNN-all has a better performance among the two.
-For I2V, such cases form only 2.25\% of the testing dataset.
-Predictions from QRNN-all have slightly worse values for average error bias, but both MAE and standard deviation improve by over 20\%.
-For I3V also, the cases with high cloud impact, though very low in number, also gain positively from the auxiliary information.
-
-The results show that both QRNN-single and QRNN-all are successful in predicting NFCS values for I2V, and I3V, and partially successful for I1V.
-The resulting error distributions are symmetric with low bias and standard deviation.
-For I2V and I3V, the variability of errors is even smaller than the noise.
-This is a consequence of predictions for cases associated with clear sky conditions.
-QRNN predictions are weighted mean of measurements between channels.
-For clear-sky conditions, the averaging of cases observed by multiple channels can cancel out the noise.
-The cancelling of noise is stronger in QRNN-all as all 183\,GHz channels are used concurrently.
-The lower prediction accuracy of I1V can be explained by the fact that it is the outermost 183\,GHz channel.
-The other sub-mm channels cannot provide a full coverage for the hydrometeor impact in I1V.
-Depending upon the atmospheric scenarios, there is always a portion of data detected by I1V, but never seen by any other channel.
-Though such cases are few, QRNN cannot learn to predict the clear-sky values accurately for cases which lie outside the coverage area.
-Besides this, lower representation of high cloud impact cases in the training set also affects QRNN accuracy.
-
-\subsubsection{Uncertainty quantification}
-\label{sec:prediction_uncertainty}
-%f 
-\begin{figure}[t]
-	\includegraphics[width = 70mm]{Figures/prediction_uncertainty_I2V.pdf}	
-	\caption{The prediction uncertainty  for QRNN-single(I2V) with respect to quantiles for randomly selected 1500 cases.
-The quantiles have been plotted at equidistant points.
-The black line represents a hypothetical Gaussian distribution of $270\pm0.60$\,K, which is of the order of standard deviation for I2V predictions (see Table~\ref{tab:error_statistics_ici}).}
-	\label{fig:prediction_uncertainty_I2V}	
-\end{figure}
-\begin{figure*}[t]
-	\includegraphics[width=150mm]{Figures/deviation_posterior_samples_I2V.pdf}	
-	\caption{The distribution of predicted errors and observed errors for I2V as obtained from QRNN-single and QRNN-all for the test dataset.
-The predicted errors are estimated as deviation of random samples from posteriori distribution to corresponding median values.}
-	\label{fig:predicted_errors}	
-\end{figure*}
-\begin{figure}[t]
-	\includegraphics[height = 70mm]{Figures/calibration_QRNN_I1V.pdf}	
-	\caption{Calibration of the prediction intervals obtained from QRNN-single and QRNN-all for I1V. }
-	\label{fig:calibration_I1V}	
-\end{figure}
-\begin{figure*}[t]
-	\includegraphics[width=\textwidth]{Figures/PDF_uncertainty_bins_QRNN-single.pdf}	
-	\caption{Distribution of errors binned according to their uncertainty. Results are from QRNN-single for channels I1V, I2V and I3V.}
-	\label{fig:error_distribution_uncertainty_bins}	
-\end{figure*}
-
-The biggest advantage of using QRNN is estimation of case-specific uncertainties.
-The quantiles can be used to construct a probability distribution of the predictions in contrast to other correction approaches which give out only point estimates.
-
-In order to analyse the prediction uncertainty, the deviations of predicted quantiles from its median value are estimated.
-Fig.~\ref{fig:prediction_uncertainty_I2V} shows the spread of prediction uncertainties over different quantiles for randomly chosen 1500 cases.
-The large spread in the predicted errors indicates that QRNN is successful in representing uncertainties for each case individually, rather than expressing them as a single measure for all cases.
-In the latter case, the uncertainty estimates would be concentrated along a narrow interval.
-Among the cases associated with low uncertainty, the distribution is quite symmetric along the median value.
-These cases are concentrated along a narrow interval and lie close to the black curve representing a Gaussian spread.
-On the contrast, cases with high uncertainty are unequally spaced and have a larger spread over positive quantiles than negative quantiles.
-Thus QRNN is capable of capturing non-Gaussian  error distributions as well.
-
-Fig.~\ref{fig:predicted_errors} shows the comparison of observed errors (prediction accuracy) to predicted errors.
-The predicted dataset is constructed by drawing random samples from the posteriori distribution.
-We do not derive any sample from outside $\pm3\sigma$.
-The predicted error is deviation of random sample to its median.
-For QRNN-single, the predicted and observed errors have good agreement for the peak of the distribution, but the predicted errors are spread out asymmetrically.
-For QRNN-all, the predicted and observed errors have a better agreement and the spread is symmetric for the former.
-The results show that both QRNN-single and QRNN-all are not able to represent the left wings of the distribution.
-This could also be a sampling issue, as the high errors we try to predict constitute a very small part of the complete dataset.
-
-For further analysis, we compared the distribution of predictions from QRNN with the a priori distribution.
-In a  high performing QRNN model, the posteriori distribution of the predictions should be similar to the a priori distribution of training dataset.
-A straightforward way to compare the two distribution is to plot the frequency of predictions and frequency of the true value in different prediction intervals.
-This is also commonly known as calibration plot.
-Fig.~\ref{fig:calibration_I1V} shows the calibration of the prediction intervals on the test dataset for I1V.
-For both QRNN models, the predictions for the complete test dataset are well calibrated and follow the y=x line.
-This shows that the training and test datasets come from the same a priori distribution.
-On the other hand, when only the cases with  cloud correction greater than 10\,K are considered, for both models, the predictions in all the intervals are poorly calibrated.
-In this case the calibration curve lies below the y=x line, indicating that the predicted intervals are too narrow, or the uncertainty is underestimated.
-The clear-sky cases dominate the test/training dataset, thus the a priori distribution is representative of the same.
-The a priori distribution of cloudy cases is different to the clear-sky cases, therefore the predictions are poorly calibrated for the former.
-We also plotted the calibration curves for I2V and I3V (figure not shown).
-For both these channels, predictions over complete dataset were well calibrated for both QRNN-single and QRNN-all, but for subset with threshold 10\,K, slightly poor calibrations were observed in QRNN-single.
-This is in contrast with I1V, where both models had poor calibrations for cases with high cloud impact.
-
-Lastly, we investigated that if the uncertainty estimates given by QRNN are representative of prediction accuracy.
-Fig.~\ref{fig:error_distribution_uncertainty_bins} shows the errors of best estimate binned by their corresponding uncertainty in $\pm2\sigma$  confidence interval.
-Similar results were also obtained for QRNN-all (figure not shown).
-For all three channels, the spread of error distribution increases as the uncertainty about the accuracy of the trial increases.
-The cases with high certainty have a narrow and sharp distribution, and the errors are mostly less than $\pm$2.5\,K.
-With increase in the uncertainty, frequency of cases with high accuracy decreases and the distributions spread out symmetrically to higher errors.
-Poor predictions occur more frequently when uncertainty is high.
-Cases with accurate predictions yet high uncertainty are also present.
-In spite of individual variations in the error distributions for each channel, predictions and their corresponding uncertainties followed the same relationship.
-
-The results show that both QRNN-single and QRNN-all are successful in providing well calibrated probabilistic predictions of the posterior distributions except for few cases associated with high cloud impact.
-This is not unexpected as such cases form a small subset of the training set and their priori distribution is different from the entire dataset.
-Since such cases form only a fraction of the training dataset, it can be hard to train the model to predict them accurately.
-A larger training dataset would be required to increase the representation of such cases in QRNN.
-
-\subsection{MWI}
-%
-In this section, we discuss results when all 183\,GHz MWI channels are used for ``self'' cloud filtering/correction (QRNN-mwi).
-We also describe the performance of QRNN when sub-mm channels from ICI are used to train MWI channels.
-\subsubsection{MWI alone}
-%
-%t
-\begin{table*}[t]
-	\caption{Error statistics for predictions from QRNN-mwi. The labels Filtered(7.5\,K), Predicted(All) and Predicted(7.5\,K) are same as described in Table~\ref{tab:error_statistics_ici}}
-	\label{tab:statistics_mwi-alone}
-	\begin{tabular}{llrr|rr|rr}
-		\tophline
-		&&\multicolumn{2}{c|}{Simulations}& &\multicolumn{3}{c}{QRNN-single} \\
-		\cline{3-4}
-		\cline{6-8}
-		%		\hline
-		&&   Clear-sky &   All-sky & \multicolumn{2}{c}{Filtered} & \multicolumn{2}{c}{Predicted} \\
-		&&&&						(B183) & (7.5\,K)& (All) & (7.5\,K)\\
-		\middlehline
-		MWI-14 		&Bias     & 0.01 & -1.86 & -0.84(1.95\%) & -0.50(4.04\%) & -0.14 & -0.12 \\
-					&MAE      & 0.96 &  2.59 &  1.58 &  1.26 &  1.13 &  1.00 \\
-					&STD      & 1.20 &  9.02 &  3.27 &  1.96 &  1.87 &  1.53 \\
-					&Skewness & 0.00 & -8.21 & -5.13 & -3.00 & -0.74 & -2.14 \\
-		\middlehline
-		MWI-15 		&Bias     &  0.00 & -1.24 & -0.53(1.95\%) & -0.41(2.81\%) & -0.14 & -0.12 \\
-					&MAE      &  0.96 &  1.99 &  1.30 &  1.19 &  0.74 &  0.66 \\
-					&STD      &  1.20 &  6.55 &  2.15 &  1.74 &  1.32 &  1.12 \\
-					&Skewness & -0.01 & -9.68 & -3.67 & -2.41 & -2.42 & -2.94 \\
-		\middlehline	
-		MWI-16 		&Bias     &  0.00 &  -0.84 & -0.30(1.95\%) & -0.29(1.90\%) & -0.13 & -0.10 \\
-					&MAE      &  0.95 &   1.63 &  1.11 &  1.10 &  0.68 &  0.62 \\
-					&STD      &  1.20 &   5.39 &  1.60 &  1.54 &  1.15 &  0.96 \\
-					&Skewness & -0.02 & -11.62 & -2.55 & -2.00 & -3.87 & -3.35 \\	
-		\middlehline			
-		MWI-17 		&Bias     &  0.01 &  -1.06 & -0.40(1.95\%) & -0.34(2.36\%) & -0.13 & -0.11 \\
-					&MAE      &  0.95 &   1.83 &  1.18 &  1.13 &  0.73 &  0.67 \\
-					&STD      &  1.20 &   6.29 &  1.83 &  1.61 &  1.22 &  1.03 \\
-					&Skewness & -0.01 & -10.72 & -3.27 & -2.20 & -3.48 & -3.17 \\
-		\middlehline			
-		MWI-18 		&Bias     &  0.00 &  -0.65 & -0.22(1.95\%) & -0.25(1.39\%) & -0.11 & -0.09 \\
-					&MAE      &  0.96 &   1.47 &  1.06 &  1.08 &  0.80 &  0.75 \\
-					&STD      &  1.20 &   4.65 &  1.45 &  1.51 &  1.23 &  1.08 \\
-					&Skewness & -0.01 & -12.84 & -1.87 & -2.09 & -2.88 & -2.40 	\\
-		\bottomhline				
-	\end{tabular}	
-	\belowtable{} % Table Footnotes
-\end{table*}
-\begin{figure}[t]
-	\includegraphics[width = 70mm]{Figures/cloud_impact_uncertainty_MWI.pdf}	
-	\caption{The average confidence intervals (2$\sigma$) plotted against the magnitude of cloud impact for all MWI channels.}
-	\label{fig:uncertainty_cloud_impact}	
-\end{figure}
-QRNN-mwi is designed to provide basis for a cloud correction approach applicable to current satellites, that lack the higher frequency channels.
-Table~\ref{tab:statistics_mwi-alone} shows the results for all 183\,GHz channels of MWI.
-MWI channels have a higher measurement uncertainty than ICI, so a higher filtering threshold is selected.
-All cases with cloud correction greater than 7.5\,K are considered as cloudy and filtered out.
-With pure-filtering, only 4\% of the cases are filtered out for MWI-14, but the bias reduces from -1.86\,K to -0.50\,K.
-For the predictions, the average bias is -0.14\,K.
-For both filtering and correction, a significant reduction in the errors is observed but the resulting values are still high and indicate only partial success of the method.
-For other channels also, a similar performance is observed.
-For MWI-15, cloud correction reduces the average error from -1.23\,K to -0.13\,K  and the corresponding decrease in standard deviation is 6.55\,K to 1.32\,K.
-Filtering the predicted cases improves the bias and standard deviation further by 15\%.
-Interestingly, even with partial correction, the standard deviation is lower than the measurement noise.
-For MWI-16, the bias for predictions is -0.12\,K compared to -0.85\,K for the measurements.
-The corresponding standard deviation is  1.15\,K, which is again smaller than the measurement noise(1.20\,K).
-MWI-17 also has a similar performance.
-MWI-18 is least affected by cloud impact among the five channels.
-The average deviation of the measurement data to NFCS values is only -0.66\,K which reduces to -0.12\,K with QRNN.
-After filtering 1.37\% cases with high cloud impact, only a slight improvement in the accuracy is observed but the variability of errors decreases from 1.23\,K to 1.08\,K.
-The results show that QRNN-mwi is partially successful in removing the cloud impact.
-A significant reduction in the deviation to NFCS values indicates that though most cases with high cloud impact can be removed/corrected, the cases with residual cloud impact and uncorrected cases deteriorate the performance.
-Using a low threshold filter can improve the accuracy, but at the cost of excessive removal of clear-sky cases.
-
-The five frequencies are sensitive to different regions of the troposphere so not all clouds are equally represented in all.
-The brightness temperature of same cloud measured at different frequencies can be valuable to train QRNN.
-However the hydrometeor impact from regions where the weighting functions match poorly cannot be represented adequately in QRNN.
-As a consequence, the predictions are poor.
-In contrast, the clear-sky measurements of the same scene from multiple channels, reinforces the QRNN predictions.
-The measurement noise in all channels is stationary and uncorrelated, thus the predictions benefit from the additional information, and averaging cancels out the noise component.
-As clear-sky cases occur more frequently, the effect is quite prominent.
-
-Further, we investigate if uncertainty estimates from QRNN-mwi are representative of prediction errors.
-Fig.~\ref{fig:uncertainty_cloud_impact} displays the average predicted errors in 94\% confidence interval, for different cloud impacts.
-For all five channels, the predictions with small or relatively low cloud signal have a low uncertainty or in other words have high sharpness.
-As fraction of cloud impact increases, the predictions become increasingly uncertain.
-Most uncertain predictions occur for the outermost channels (MWI-14, MWI-15).
-These channels also have the lowest prediction accuracy.
-Thus, the QRNN predictions possess a multivariate representation of uncertainty.
-The uncertainty of cases with varying cloud impacts can be expressed individually.
-
-\subsubsection{MWI and ICI}
-%t
-\begin{table*}[t]
-	\caption{Same as Table~\ref{tab:error_statistics_ici}, but for channels MWI-15 and MWI-16. Results are from QRNN-single.}
-	\label{tab:statistics_mwi}
-	\begin{tabular}{llrr|rrr}
-		\tophline
-				&&\multicolumn{2}{c|}{Simulations}& \multicolumn{3}{c}{QRNN-single} \\
-				\cline{3-7}
-				%		\hline
-				&&   Clear-sky &   All-sky &  Filtered(5\,K) & Predicted & Predicted(5\,K) \\
-		\middlehline
-		MWI-15  &Bias     &  0.00 & -1.23 & -0.26 & -0.04 & -0.03 \\
-				&MAE      &  0.64 &  1.70 &  0.76 &  0.56 &  0.50 \\
-				&STD      &  0.81 &  6.48 &  1.01 &  0.86 &  0.64 \\
-				&Skewness & -0.00 & -9.97 & -1.15 & -1.78 & -0.15 \\
-		\middlehline
-		MWI-16  &Bias     & 0.00 &  -0.85 & -0.22 & -0.06 & -0.05 \\
-				&MAE      & 0.64 &   1.34 &  0.73 &  0.55 &  0.50 \\
-				&STD      & 0.80 &   5.31 &  0.96 &  0.83 &  0.63 \\
-				&Skewness & 0.01 & -12.08 & -1.02 & -2.25 & -0.11 \\
-		\bottomhline			
-	\end{tabular}	
-	\belowtable{} % Table Footnotes
-\end{table*}
-In this section, we combine the measurements from MWI-15(MWI-16) and the ICI sub-mm channels to predict MWI-15(MWI-16).
-Since we assume that all channels are remapped to a common footprint, channels MWI-14, MWI-17 and MWI-18 are virtually identical to I1V, I2V and I3V, and results for them are not shown separately.
-
-Table~\ref{tab:statistics_mwi} shows the error metrics of NFCS predictions from simulations.
-For MWI-15, the average deviations of measurements from NFCS values is -1.23\,K, and the MAE is 1.70\,K.
-When all cases are corrected, the resulting average bias is -0.04\,K and the MAE reduces to 0.56\,K.
-If only pure-filtering is made, the average bias is -0.26\,K and MAE is 0.76\,K, suggesting that a significant number of cases with non-zero cloud impact pass through.
-As seen for ICI, best results are obtained  when filtering is made on the corrected dataset.
-Similar accuracy is seen for MWI-16, although it has slightly lower cloud impact.
-
-These results show that even though ICI and MWI are two different instruments, their channels can benefit from each other.
-Although re-mapping to a common footprint would slighly compromise the data quality, a high accuracy achieved with simulations suggests that the QRNN would work well when actual measurements are available.
-
-\subsection{AWS}
-%
-%t
-\begin{table*}[t]
-	\caption{Same as Table~\ref{tab:error_statistics_ici}, but for channels AWS channels. Results are from QRNN-single. }
-	\label{tab:statistics_qrnn_aws}
-	\begin{tabular}{llrr|rrr}
-		\tophline
-		&&\multicolumn{2}{c|}{Simulations}& \multicolumn{3}{c}{QRNN-single} \\
-		\cline{3-7}
-		%		\hline
-		&&   Clear-sky &   All-sky &  Filtered(5\,K) & Predicted & Predicted(5\,K) \\
-		\middlehline
-		AWS-32  &Bias     & 0.00 & -1.32 & -0.26 & -0.03 & -0.02 \\
-				&MAE      & 0.36 &  1.57 &  0.52 &  0.54 &  0.43 \\
-				&STD      & 0.46 &  6.42 &  0.85 &  1.02 &  0.61 \\
-				&skewness & 0.01 & -8.43 & -3.65 & -0.07 & -1.98 \\
-		\middlehline
-		AWS-33	&Bias     & -0.01 & -0.98 & -0.25 & 0.02 &  0.01 \\
-				&MAE      &  0.36 &  1.23 &  0.51 & 0.49 &  0.42 \\
-				&STD      &  0.45 &  4.70 &  0.80 & 0.76 &  0.56 \\
-				&skewness & -0.00 & -8.78 & -2.92 & 0.04 & -0.79 \\
-
-		\middlehline
-		AWS-34	&Bias     &  0.00 &  -0.68 & -0.20 &  0.02 &  0.01 \\
-				&MAE      &  0.51 &   1.07 &  0.61 &  0.51 &  0.46 \\
-				&STD      &  0.64 &   3.67 &  0.84 &  0.75 &  0.60 \\
-				&skewness & -0.00 & -10.32 & -1.70 & -0.55 & -0.59 \\
-		\middlehline
-		AWS-35	&Bias     &  0.00 &  -0.43 & -0.15 & 0.01 &  0.00 \\
-				&MAE      &  0.50 &   0.84 &  0.57 & 0.48 &  0.44 \\
-				&STD      &  0.63 &   2.65 &  0.77 & 0.71 &  0.57 \\
-				&skewness & -0.01 & -12.49 & -1.34 & 0.40 & -0.29 \\
-		\middlehline
-		AWS-36  &Bias     & 0.00 &  -0.28 & -0.11 &  0.03 &  0.03 \\
-				&MAE      & 0.70 &   0.90 &  0.74 &  0.63 &  0.60 \\
-				&STD      & 0.88 &   2.06 &  0.96 &  0.86 &  0.76 \\
-				&skewness & 0.01 & -11.80 & -0.53 & -0.35 & -0.20 \\
-		\bottomhline				
-	\end{tabular}
-	\belowtable{} % Table Footnotes
-\end{table*}
-%f
-%\begin{figure}[t]
-%	\includegraphics[width = 80mm]{Figures/cloud_impact_uncertainty_AWS.pdf}	
-%	\caption{The average confidence intervals (2$\sigma$) plotted against the magnitude of cloud impact for all AWS channels.}
-%	\label{fig:uncertainty_cloud_impact}	
-%\end{figure}
-
-In this section, we investigate the possibility of using only channels around 325\,GHz for cloud correction at 183\,GHz.
-This special case of utilising only 325\,GHz channel can be relevant for smaller satellite missions like AWS where higher sub-mm channels are not available.
-
-In an analogy between the results from ICI channels, we perform a similar error distribution analysis 
-and the results are displayed in Table~\ref{tab:statistics_qrnn_aws}.
-For channel AWS-32, the average bias and standard deviation in the prediction errors is -1.34\,K and 5.91\,K respectively.
-However, after correction, the bias and standard deviation are -0.08\,K and 1.0\,K.
-A decrease in the skewness of error distributions is evident, but a relatively high values after prediction indicate presence of cases with partially-corrected cloud impact.
-For AWS-33, the predictions have slightly higher accuracy than AWS-32.
-The MAE in predictions is only 0.50\,K in comparison to 1.23\,K for the measurements.
-Similar results are also seen for AWS-35 and AWS-36.
-For both channels, the error distributions are relatively more symmetric than the other channels.
-Also, it is worth to noting that when cases with 5\,K cloud correction are removed, the spread of prediction errors is narrower than noise.
-
-Overall the results demonstrate that QRNN is successful in predicting the NFCS data for AWS-33, AWS-34, AWS-35 and AWS-36 and partially for AWS-32.
-The prediction error distributions are symmetric with low bias and standard deviation.
-The cases with high error are mostly associated with high cloud impact and constitute only a small fraction of the total dataset.
-Excluding such cases decreases the errors and in fact the spread of errors for AWS-34, AWS-35 and AWS-36 is smaller than noise.
-Removal of cases with high cloud impact, increases the representation of cases in cloud-free conditions, and for such cases, QRNN predictions can be seen as a weighted mean between the two channels.
-For AWS-32, QRNN is only partially successful in reducing the impact of hydrometeors.
-The prediction errors have significantly lower spread than the measurements, but cases with partially corrected cloud impact deteriorates the overall accuracy.
-Since 325\,GHz cannot provide a full coverage for hydrometeor impact in AWS-32, the testing data will inevitably contain cases for which QRNN has not trained for.
-Prediction for such cases would be inaccurate and highly uncertain.
-In such cases, the predictions should be used with caution.
-
-%In order to analyse the performance of QRNN with respect to uncertainty, the interrelation between the uncertainty estimates and cloud impact was investigated.
-Fig~\ref{fig:uncertainty_cloud_impact} displays the plot between mean uncertainty estimates for $2\sigma$ confidence interval and the cloud impact.
-For all five channels, the predictions with small or relatively low cloud signal have a low uncertainty or in other words have high sharpness.
-As fraction of cloud impact increases, the predictions become increasingly uncertain.
-However, this does not imply that the prediction accuracy is low.
-
-\section{Conclusion and outlook}  %% \conclusions[modified heading if necessary]
-%
-
-\todo{incomplete}
-
-In this study, quantile regression neural network is used for filtering and correction of cloud contamination in 183\,GHz channels.
-QRNN is a neural network which estimates the posterior distribution of target variable through quantiles.
-It is demonstrated that QRNN can combine data from 183\,GHz channels and the available sub-mm frequencies to provide channel specific NFCS predictions.
-Application of QRNN to data from three different satellite instruments is presented.
-
-QRNN based filtering is only partially successful in removing the cloudy data.
-The cloudy cases falsely classified as clear introduce a negative bias in the filtered data.
-This is not optimal solution, but in agreement with what can be achieved with the present instruments.
-The robustness of QRNN was also demonstrated by application to a smaller satellite missions AWS, where only one of the higher frequencies is available.
-The same approach was applicable in this case, and the results proved that even one sub-mm channel is sufficient enough for cloud correction at 183\,GHz.
-Since the present sensors lack any sub-mm channels, to investigate the applicability to present sensors and also emphasize the benefit of high frequency channels, a QRNN model using only 183\,GHz data is also investigated.
-
-The 183\,GHz channels and the sub-mm channels are sensitive to different parts of the troposphere.
-When all of them are considered together, the weighting functions of sub-mm channels can provide only a partially complete coverage to the hydrometeor impact.
-For the outermost 183\,GHz channels, there always exists a part of troposphere where hydrometeor impact cannot be covered.
-A slightly lower accuracy was observed for cases with high cloud impact.
-In few of such cases, the predicted NFCS values were not completely cloud free.
-This is expected as not all cases can be represented by the a priori distribution QRNN trains on.
-Predictions for \textit{out-of-distribution} cases is always a challenging task for deep learning algorithms and  shall always limit the performance.
-Improving the representation of such cases in the a priori distribution can help alleviate this problem.
-However since such cases are few, filtering them out results in highly accurate NFCS predictions with minimal reduction in data.
-
-%% The following commands are for the statements about the availability of data sets and/or software code corresponding to the manuscript.
-%% It is strongly recommended to make use of these sections in case data sets and/or software code have been part of your research the article is based on.
-
-\codeavailability{TEXT} %% use this section when having only software code available
-
-\dataavailability{TEXT} %% use this section when having only data sets available
-
-\codedataavailability{TEXT} %% use this section when having data sets and software code available
-
-\sampleavailability{TEXT} %% use this section when having geoscientific samples available
-
-\videosupplement{TEXT} %% use this section when having video supplements available
-
-\appendix
-\section{}    %% Appendix A
-
-\subsection{}     %% Appendix A1, A2, etc.
+     %% Appendix A1, A2, etc.
 

### 2020-10-28 MWHS/covariance_matrix.py
MWHS scripts

@@ -1,0 +1,152 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Fri Sep 11 21:57:41 2020
+
+@author: inderpreet
+
+calculate statistics for MWHS point estimates, the results are given in latex format
+"""
+
+import os
+import matplotlib.pyplot as plt
+import numpy as np
+import ICI.stats as S
+from read_qrnn import read_qrnn
+plt.rcParams.update({'font.size': 30})
+import seaborn as sns
+#%%
+
+def calculate_statistics(y_prior, y0, y, y_pre, im, i183):
+
+    bia      = S.calculate_bias(y_prior, y0, y, y_pre[:, 3], im, i183)
+    std      = S.calculate_std(y_prior, y0, y, y_pre[:, 3], im, i183)
+    ske      = S.calculate_skew(y_prior, y0, y, y_pre[:, 3], im, i183)
+    mae      = S.calculate_mae(y_prior, y0, y, y_pre[:, 3], im, i183)
+    
+    return bia, std, ske, mae
+
+def get_corr(im, Y_pre, Y):       
+
+    A = (Y_pre[im, :] - Y[im]).T    
+    cov = np.round(np.corrcoef(A), 2)
+    
+    return cov
+
+#%% input parameters
+depth     = 3
+width     = 128
+quantiles = np.array([0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998])
+batchSize = 128
+
+targets = [11, 12, 13, 14, 15]
+
+test_file = os.path.expanduser("~/Dendrite/Projects/AWS-325GHz/MWHS/data/TB_MWHS_test.nc")
+
+iq = np.argwhere(quantiles == 0.5)[0,0]
+
+qrnn_dir = "C89+150"
+#qrnn_dir = "C150"
+#qrnn_dir = "C150+118"
+     
+        
+d = {"C89+150" : [1, 10],
+     "C89+150+118" : [1, 10, 6, 7 ],
+     "C150" : [10],
+     "C89+150+183" : [1, 10, 11, 12, 13, 14, 15]           
+    } 
+
+
+qrnn_dirs = ["C89+150", "C89+150+183"]
+#qrnn_dirs = ["C89+150", "C89+150+118", "C150" ]
+
+
+#%%
+#%%
+# Set up the matplotlib figure
+fig, ax = plt.subplots(1, 2, figsize=(20, 10))
[…]

### 2020-10-28 MWHS/mwhs.py

@@ -8,7 +8,9 @@ class mwhsData(Dataset):
     Pytorch dataset for the MWHS training data.
 
     """
-    def __init__(self, path, inChannels, target, batch_size = None, ocean = True):
+    def __init__(self, path, inChannels, target, batch_size = None,
+                 ocean = True,
+                 test_data = False):
         """
         Create instance of the dataset from a given file path.
 
@@ -42,8 +44,8 @@ class mwhsData(Dataset):
         self.index = idx         
         self.itarget = np.argwhere(np.array(channels) == target)[0]
                                                                     
-                                
-       
+                                    
+        self.ocean = ocean
         C = []
         
         for ic in self.index:
@@ -56,14 +58,15 @@ class mwhsData(Dataset):
             for j in range(2):
                 im.append(TB.mask[j, i, :])
         im = np.stack(im, axis = 1)
-        print (im.shape, np.sum(im))
+#        print (im.shape, np.sum(im))
         im = np.logical_or.reduce(im, axis = 1)	
 	#store mean and std to normalise data
-        if ocean:
+        if self.ocean:
            il = self.lsm == 0
            im = np.logical_and(~im, il) 
         else:
             im = ~im
+            
         x_noise = self.add_noise(self.x[im, :], self.index)
   
         self.std = np.std(x_noise, axis = 0)
@@ -72,11 +75,33 @@ class mwhsData(Dataset):
         self.y = np.float32(TB[0, self.itarget[0], :])
    
         self.y_noise = self.add_noise(self.y, self.itarget) 
-        print ('y_noise', self.itarget)
+
         self.x = self.x.data[im, :]
         self.y = self.y.data[im]
-        self.y_noise = self.y_noise.data[im] - self.y
-        print (self.y.shape, self.x.shape)
+        self.y_noise = self.y_noise.data[im]
+        self.lsm = np.float32(self.lsm[im])
+        self.lsm = np.expand_dims(self.lsm, axis = 1)
+        self.im  = im
+        if test_data:
+            test_file_path = path.replace("test", "test_noisy_allsky")
+            test_file = netCDF4.Dataset(test_file_path, mode = "r")
+            TB_var = test_file.variables["TB_noise"]
+            TB_noise = TB_var[:]
+                                                                     
+            C = []
+            
+            for ic in self.index:
+                C.append(TB_noise[1, ic, :])
+    
[…]

### 2020-10-28 MWHS/plot_calibration.py

@@ -1,0 +1,122 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Mon Sep  7 20:46:41 2020
+
+@author: inderpreet
+This code plots the calibration curves for both QRNN-single and QRNN-all
+"""
+import matplotlib.pyplot as plt
+import numpy as np
+import netCDF4
+import os
+import ICI.stats as stats
+from matplotlib.ticker import (MultipleLocator, FormatStrFormatter,
+                               AutoMinorLocator)
+from typhon.retrieval.qrnn import set_backend, QRNN
+set_backend("pytorch")
+import ICI.stats as S
+
+from ICI.calibration import calibration
+from read_qrnn import read_qrnn
+import random
+plt.rcParams.update({'font.size': 26})
+
+
+#%% input parameters
+depth     = 3
+width     = 128
+quantiles = np.array([0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998])
+batchSize = 128
+
+targets = [11, 12, 13, 14, 15]
+test_file = os.path.expanduser("~/Dendrite/Projects/AWS-325GHz/MWHS/data/TB_MWHS_test.nc")
+
+iq = np.argwhere(quantiles == 0.5)[0,0]
+
+#qrnn_dir = "C89+150"
+#qrnn_dir = "C150"
+qrnn_dir = "C89+150"
+
+if qrnn_dir == "C89+150":
+    channels = [ 1, 10]
+  
+target = 14 
+
+#%% read input data
+        
+print(qrnn_dir, channels)
+
+qrnn_path = os.path.expanduser("~/Dendrite/Projects/AWS-325GHz/MWHS/qrnn_output/all_with_flag/%s/"%(qrnn_dir))
+
+inChannels = np.concatenate([[target], channels])
+
+print(qrnn_dir, channels, inChannels)
+    
+qrnn_file = os.path.join(qrnn_path, "qrnn_mwhs_%s.nc"%(target))
+
+print (qrnn_file)
+i183, = np.argwhere(inChannels == target)[0]
+
+y_pre, y_prior, y0, y, y_pos_mean = read_qrnn(qrnn_file, test_file, inChannels, target)
+
+# calibration plot data with correction greater than 15K
+
+fig, ax = plt.subplots(1, 1, figsize = [8,8])   
+
+im = np.arange(0, y0.size, 1)
[…]

### 2020-10-28 MWHS/plot_predicted_error.py

@@ -1,0 +1,170 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Fri Sep  4 21:35:37 2020
+
+@author: inderpreet
+
+this code plots the PDF of the predicted error and observed error (error  of best estimate (median))
+ICI channels
+"""
+import os
+from mwhs import mwhsData
+import matplotlib.pyplot as plt
+import numpy as np
+from typhon.retrieval.qrnn import set_backend, QRNN
+set_backend("pytorch")
+import ICI.stats as S
+plt.rcParams.update({'font.size': 32})
+from matplotlib.ticker import (MultipleLocator, FormatStrFormatter,
+                               AutoMinorLocator)
+
+from typhon.retrieval.qrnn import set_backend, QRNN
+set_backend("pytorch")
+
+#%%
+def sample_posterior(x, nn, y0, y_pre):
+    """
+    estimates histogram of predicted error (random samples drawn from posterior)
+
+    Parameters
+    ----------
+    x : input data for QRNN predictions
+    nn : number of samples required for each case
+    y0 : NFCS simulations
+    y_pre : predicted median
+
+    Returns
+    -------
+    hist_sample : frequency and bins of predicted errors
+    """
+    n = x.shape[0]
+    y_pos = []
+    for i in range(n):
+        y_pos.append(qrnn.sample_posterior(x[i, :], nn))
+    y_pos = np.array(y_pos)
+    
+    d = []
+    for j in range(nn):
+        
+        d.append( y_pre - y_pos[:, j] )
+    d = np.array(d).ravel()    
+    hist_sample = np.histogram(d, bins, density = True)
+    return hist_sample
+
+
+def predict(test_data, qrnn, add_noise = False):
+    """
+    predict the posterior mean and median
+    """
+    if add_noise:
+        x_noise = test_data.add_noise(test_data.x, test_data.index)
+        x = (x_noise - test_data.mean)/test_data.std
+        y_prior = x_noise
+        y = test_data.y_noise
+        
+        y0 = test_data.y
+    else:
+        x = (test_data.x - test_data.mean)/test_data.std
+        y_prior = test_data.x
+        y = test_data.y_noise
+        y0 = test_data.y
+        
+        if not test_data.ocean :
+        
+            x = np.concatenate((x, test_data.lsm ), axis = 1)
+
[…]

### 2020-10-28 MWHS/plot_uncertainty.py

@@ -1,0 +1,98 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Sat Sep 12 22:09:27 2020
+
+@author: inderpreet
+
+PLot the uncertainties in randomly chosen cases
+"""
+import os
+import matplotlib.pyplot as plt
+import numpy as np
+import netCDF4
+from read_qrnn import read_qrnn
+from matplotlib.ticker import (MultipleLocator, FormatStrFormatter,
+                               AutoMinorLocator)
+from typhon.retrieval.qrnn import set_backend, QRNN
+set_backend("pytorch")
+import random
+plt.rcParams.update({'font.size': 26})
+
+
+#%% input parameters
+depth     = 3
+width     = 128
+quantiles = np.array([0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998])
+batchSize = 128
+
+targets = [11, 12, 13, 14, 15]
+test_file = os.path.expanduser("~/Dendrite/Projects/AWS-325GHz/MWHS/data/TB_MWHS_test.nc")
+
+iq = np.argwhere(quantiles == 0.5)[0,0]
+
+#qrnn_dir = "C89+150"
+#qrnn_dir = "C150"
+qrnn_dir = "C89+150"
+
+if qrnn_dir == "C89+150":
+    channels = [ 1, 10]
+  
+target = 14 
+
+#%% read input data
+        
+print(qrnn_dir, channels)
+
+qrnn_path = os.path.expanduser("~/Dendrite/Projects/AWS-325GHz/MWHS/qrnn_output/all_with_flag/%s/"%(qrnn_dir))
+
+inChannels = np.concatenate([[target], channels])
+
+print(qrnn_dir, channels, inChannels)
+    
+qrnn_file = os.path.join(qrnn_path, "qrnn_mwhs_%s.nc"%(target))
+
+print (qrnn_file)
+i183, = np.argwhere(inChannels == target)[0]
+
+y_pre, y_prior, y0, y, y_pos_mean = read_qrnn(qrnn_file, test_file, inChannels, target)
+
+fig, ax = plt.subplots(1, 1, figsize = [8, 8])
+x = np.arange(-3, 4, 1)
+ii = 0
+
+randomList = random.sample(range(0, 50000), 1500)
+for i in randomList:
+    ii +=1
[…]

### 2020-10-28 MWHS/tables_mwhs.py

@@ -1,0 +1,148 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Fri Sep 11 21:57:41 2020
+
+@author: inderpreet
+
+calculate statistics for MWHS point estimates, the results are given in latex format
+"""
+
+import os
+import matplotlib.pyplot as plt
+import numpy as np
+import ICI.stats as S
+from read_qrnn import read_qrnn
+plt.rcParams.update({'font.size': 26})
+from tabulate import tabulate
+#%%
+
+def calculate_statistics(y_prior, y0, y, y_pre, im, i183):
+
+    bia      = S.calculate_bias(y_prior, y0, y, y_pre[:, 3], im, i183)
+    std      = S.calculate_std(y_prior, y0, y, y_pre[:, 3], im, i183)
+    ske      = S.calculate_skew(y_prior, y0, y, y_pre[:, 3], im, i183)
+    mae      = S.calculate_mae(y_prior, y0, y, y_pre[:, 3], im, i183)
+    
+    return bia, std, ske, mae
+#%% input parameters
+depth     = 3
+width     = 128
+quantiles = np.array([0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998])
+batchSize = 128
+
+targets = [11, 12, 13, 14, 15]
+targets = [14]
+test_file = os.path.expanduser("~/Dendrite/Projects/AWS-325GHz/MWHS/data/TB_MWHS_test.nc")
+
+iq = np.argwhere(quantiles == 0.5)[0,0]
+
+qrnn_dir = "C89+150"
+#qrnn_dir = "C150"
+#qrnn_dir = "C150+118"
+     
+        
+d = {"C89+150" : [1, 10],
+     "C89+150+118" : [1, 10, 6, 7 ],
+      "C89+150+118_v2" : [1, 10,  7, 8 ],
+     "C150" : [10],
+     "C89+150+183" : [1, 10, 11, 12, 13, 14, 15]           
+    } 
+
+Channels = [[1, 10], [1, 6, 7, 10]]
+#qrnn_dirs = ["C89+150", "C89+150+118", "C89+150+118_v2" ]
+qrnn_dirs = ["C89+150", "C89+150+118", "C150" ]
+
+
+
+#%%
+for target in targets:
+    BIA = []
+    MAE = []
+    STD = []
+    SKE = []
+    for qrnn_dir in qrnn_dirs:
+                
[…]

### 2020-10-29 Article/ici_submm_cloudcorr.tex
added SI results

@@
 
-\documentclass[amt, manuscript]{copernicus}
-%\documentclass[amt]{copernicus}
+%\documentclass[amt, manuscript]{copernicus}
+\documentclass[amt]{copernicus}
 
@@
 \Author[1]{Simon}{Pfreundschuh}
+\Author[2]{David}{Duncan}
 
@@
   Technology, Gothenburg, Sweden} 
+\affil[2]{European Centre for Medium Range Weather Forecasts, Reading, UK}
 
@@
 In this study, we present methodology to identify and correct the cloud impact in microwave humidity radiances.
-A quantile regression(QRNN) based approach is formulated to estimate the posterior distributions of noise free clear sky (NFCS) radiances.
+A channel specific quantile regression(QRNN) based approach is formulated to estimate the posterior distributions of noise free clear sky (NFCS) radiances.
 The applicability of the approach is demonstrated by application to current sensor MWHS-2.
@@
 Though most of the cases with high cloud impact are corrected, cases with low cloud impact are only partially corrected.
-This is comparable to the level of accuracy achieved with operational cloud-filtering techniques.
+This is comparable/better to the level of accuracy achieved with operational cloud-filtering techniques, like scattering index.
 However with sub-mm channels, we are able to successfully correct most of the cases with cloud impact.
 The resulting error distributions are symmetric with very low spread.
+The methodology also works well even when only one of the higher frequencies is available.
 In some cases, the combination of 183\,GHz and sub-mm channels also results in a lower variability than noise.
-The methodology also works well even when only one of the higher frequencies is available.
 Another advantage of using QRNN is that predicted quantiles can be employed to quantify the case-specific uncertainty estimates.
@@
 Despite individual variations for each channel, it is observed that uncertainty consistently increases with the error in the performance.
+
+\todo {write one line, why important for DA}
 
@@
 
-The results are further compared with SI based cloud filtering. SI uses differences of brightness temperatures between 89 and 150\,GHz to identify cloud affected data:
-\begin{equation}
-\text{SI} = ((\text{TB}^{obs}_{90} - \text{TB}^{obs}_{150}) + (\text{TB}^{fg}_{90} - \text{TB}^{fg}_{150}))/2 
-\end{equation}
-
-where TB$^{obs}$ and TB$^{fg}$ are observation and model first guess brightness temperatures respectively.
-
-\todo{comparsion with SI}
+In spite of the fact that QRNN only provides a partial cloud correction, the results are better to what scattering index (SI) based approach would give.
+SI uses the differences of brightness temperatures between 89 and 150\,GHz to identify cloud affected data \citep{geer2015scatteringindex}.
+With 5\,K SI threshold, almost 30\% of the data is rejected and the error distributions have bias, mae and standard deviation as -0.23\,K 0.92\,K and 1.40\,K respectively (Table~\ref{tab:SI_statistics}).
 
@@
 \end{table*}
+\begin{table}[t]
+	\caption{Error statistics obtained after filtering MWHS-2 humidity observations according to scattering index.  }
+	\label{tab:SI_statistics}
+	\begin{tabular}{lrrrrr}
+		\tophline
+		& Ch. 11 & Ch. 12 & Ch. 13 & Ch. 14 & Ch. 15\\
+			\cline{2-6}
+		bias     & -0.05&  -0.07 & -0.14 & -0.23 &  -0.34\\
+		mae      & 0.81 &   0.82 &  0.85 &  0.92 &  1.03\\
+		std      & 1.02 &   1.04 &  1.10 &  1.25 &  1.53\\
+		\bottomhline
+	\end{tabular}
+\end{table}
+
 In this section, we extend QRNN-single to predict NFCS values for MWHS-2 channels 11, 12, 13, and 15.
@@
 For channel 11, the error bias after correction is only -0.03\,K in comparison to 0.16\,K before correction.
-The strong negative tail is also diminishes after correction, but a non-zero negative skewness indicates presence of cases with cloud impact in the corrected dataset.
+The strong negative tail also diminishes after correction, but a non-zero negative skewness indicates presence of cases with cloud impact in the corrected dataset.
 Filtering the cases with high cloud impact has only a marginally positive impact.
 A similar performance is evident for channel 12.
-Correction reduces the bias by to -0.05\,K and the MAE is approximately 17\% less for the entire test dataset.
+Correction reduces the bias to -0.05\,K and the MAE is approximately 17\% lower for the entire test dataset.
 However the effect of partially corrected cases is evident in the negative skewness.
@@
 
-\todo{comparison with SI?}
+A comparison with SI based filtering is also made (Table~\ref{tab:SI_statistics}).
+For channels 11 and 12 the performance of QRNN is comparable to scattering index, albeit 30\% of the observations are rejected in the latter.
+For channels 13 and 15, the error statistics obtained with SI are slightly worse.
 
@@
 The calibration of the prediction intervals on the testing dataset is displayed in Fig~\ref{fig:calibration_mwhs}.
-For the entire testing dataset, the predictions are follow the y=x line, i.e.
+For the entire testing dataset, the predictions follow the y=x line, i.e.
 they are perfectly calibrated with the priori distribution.
@@
 In this case, the calibration curve lies below the y=x line indicating that the prediction intervals are too narrow.
+However since such cases are few and filtering them out results in well calibrated QRNN predictions.
 
@@
 The predicted errors are slightly overestimated for negative values, but overall the predicted errors from the QRNN posterior distribution have a good match with the observed errors.
+This is in agreement with the perfect calibration seen in Fig.~\ref{fig:calibration_mwhs}.
 It should be noted that the density plot is curtailed at $10^{-4}$.
@@
 The results are presented in context of different sensors.
-Furthermore, The case specific uncertainties predicted by QRNN are also discussed.
+Furthermore, the case specific uncertainties predicted by QRNN are also discussed.
 
@@
 QRNN was trained five times for each 183\,GHz channel as target.
-
 \end{enumerate}
@@
 
-\subsection{Prediction Uncertainty}
+\subsection{Prediction uncertainty}
 \label{sec:prediction_uncertainty}
@@
 The quantiles have been plotted at equidistant points.
-The black line represents a hypothetical Gaussian distribution of $270\pm0.60$\,K, which is of the order of standard deviation for I2V predictions (see Table~\ref{tab:error_statistics_ici}).}
+The red line represents a hypothetical Gaussian distribution of $270\pm0.60$\,K, which is of the order of standard deviation for I2V predictions (see Table~\ref{tab:error_statistics_ici}).}
 	\label{fig:prediction_uncertainty_I2V}	
@@
 \end{figure}
+\begin{figure}[t]
+	\includegraphics[width = 70mm]{Figures/cloud_impact_uncertainty_AWS.pdf}	
+	\caption{The average confidence intervals (2$\sigma$) plotted against the magnitude of cloud impact for all AWS channels.}
+	\label{fig:uncertainty_cloud_impact}	
+\end{figure}
 \begin{figure*}[t]
@@
 %f
-\begin{figure}[t]
-	\includegraphics[width = 80mm]{Figures/cloud_impact_uncertainty_AWS.pdf}	
-	\caption{The average confidence intervals (2$\sigma$) plotted against the magnitude of cloud impact for all AWS channels.}
-	\label{fig:uncertainty_cloud_impact}	
-\end{figure}
-
-In order to analyse the sharpness of the predictions, the deviations of predicted quantiles from its median value are estimated.
+
+Similar to evaluation of uncertainty estimates for MWHS-2(Sect.~\ref{sec:}), we analyse the spread of predicted quantiles, their calibration and distribution of predicted errors.
+
 Fig.~\ref{fig:prediction_uncertainty_I2V} shows the spread of prediction uncertainties over different quantiles for randomly chosen 1500 cases.
@@
 Among the cases associated with low uncertainty, the distribution is quite symmetric along the median value.
-These cases are concentrated along a narrow interval and lie close to the black curve representing a Gaussian spread.
+These cases are concentrated along a narrow interval and lie close to the red line representing a Gaussian spread.
 On the contrast, cases with high uncertainty are unequally spaced and have a larger spread over positive quantiles than negative quantiles.
-Thus QRNN is capable of capturing non-Gaussian error distributions as well.
+
+Fig.~\ref{fig:calibration_I1V} shows the calibration of the prediction intervals for I1V.
+The predictions for the complete test dataset are well calibrated and follow the y=x line.
+This shows that the training and test datasets come from the same a priori distribution.
+On the other hand, when only the cases with  cloud correction greater than 10\,K are considered, the predictions in all the intervals are poorly calibrated.
+In this case the calibration curve lies below the y=x line, indicating that the predicted intervals are too narrow, or the uncertainty is underestimated.
 
@@
 
-Fig.~\ref{fig:calibration_I1V} shows the calibration of the prediction intervals on the test dataset for I1V.
-The predictions for the complete test dataset are well calibrated and follow the y=x line.
-This shows that the training and test datasets come from the same a priori distribution.
-On the other hand, when only the cases with  cloud correction greater than 10\,K are considered, the predictions in all the intervals are poorly calibrated.
-In this case the calibration curve lies below the y=x line, indicating that the predicted intervals are too narrow, or the uncertainty is underestimated.
-The calibration curves for I2V and I3V are also similar.
-
-Next we investigate if the uncertainty estimates given by QRNN are representative of prediction accuracy.
+With AWS, the behaviour of predicted uncertainties is observed to be similar as for ICI (not shown).
+However, the relation between the mean uncertainty estimate and cloud impact is displayed in Fig~\ref{fig:uncertainty_cloud_impact}.
+For all five channels, the predictions with small or relatively low cloud signal have a low uncertainty or in other words have high sharpness.
+As fraction of cloud impact increases, the predictions become increasingly uncertain.
+The most uncertain predictions are for the lowest peaking channel AWS-32, which incidentally is also most affected by  hydrometeor impact.
+
+To conclude the results, we assessed if the uncertainty estimates given by QRNN are representative of prediction accuracy.
 Fig.~\ref{fig:error_distribution_uncertainty_bins} shows the errors of best estimate binned by their corresponding uncertainty in $\pm2\sigma$  confidence interval.
@@
 In spite of individual variations in the error distributions for each channel, predictions and their corresponding uncertainties followed the same relationship.
-
-With AWS, the behaviour of predicted uncertainties was observed to be similar as for ICI (not shown).
-The calibration plots and the predicted errors followed the same pattern as for ICI and are not shown.
-However, the relation between the mean uncertainty estimate and cloud impact is displayed in Fig~\ref{fig:uncertainty_cloud_impact}.
-For all five channels, the predictions with small or relatively low cloud signal have a low uncertainty or in other words have high sharpness.
-As fraction of cloud impact increases, the predictions become increasingly uncertain.
-The most uncertain predictions are for the lowest peaking channel AWS-32, which incidentally is also most affected by  hydrometeor impact.
+Similar results were also obtained with AWS(not shown).
 
@@
 The results from MWHS-2 show that QRNN based cloud correction is partially successful in correcting the cloud impact with existing sensors.
-The methodology can correctly address the large negative values in the all-sky and clear-sky deviations, but cases with low cloud impact end up with inadequate correction.
+The methodology can correctly address the large negative depatures owing to cloud impact, but cases with low cloud impact end up with inadequate correction.
 The resulting error distributions are not completely symmetric but have a low bias and spread.
-Among several input channel combinations described for QRNN-single, the performance of combination 89+150\,GHz was observed to be optimal.
+Among several input channel combinations described for QRNN-single, the performance of combination 89+150\,GHz is observed to be optimal.
 The positive performance with 150\,GHz is not unexpected, as 150\,GHz is highly sensitive to ice hydrometeors and cloud water.
@@
 The channel 89\,GHz is affected by surface emissivity and is relatively less sensitive to cloud water content, however its sensitivity to warm clouds in the lower troposphere could be important.
-We also investigated the impact of two temperature sounding channels (118....??).
+We also investigate the impact of two temperature sounding channels (MWHS-2 channel 6 and 7).
 Both these channels provide complementary information to humidity channels in the lower troposphere.
-Including both these channels in the training process gave almost similar performance as with the combination 89+150\,GHz.
-Even though the cloud correction is partial, the performance is comparable to existing cloud filtering techniques like SI.
+Including both these channels in the training process had no significant effect on the prediction accuracy.
+We obtain almost similar performance as with the combination 89+150\,GHz.
+
+Even though the cloud correction is partial, the performance is comparable or better to existing cloud filtering techniques like SI.
 SI is also a partial filter which identifies the contamination only due to precipitation and cloud ice.
-It removes most of the cases with high departures but the resulting error distributions are asymmetric.
+Note that SI is a one for all approach for all 183\,Ghz channels, thus is one observation is classfied as cloudy by SI, it is removed in all available humidity channels.
+This increases the probability of erroneously removing clear observations as cloudy.
+For high peaking channels of MWHS-2, both SI and QRNN give almost similar results, with however with almost 30\% rejection rate.
+On the other hand, for low peaking channels, the same rejection criteria gives less accurate results than QRNN.
+These channels have a stronger hydrometeor impact than channels 11 and 12.
+Clearly, a channel specific approach like QRNN is more appropriate and gives better performance.
 
@@
 Additional information from other channels is necessary to help QRNN train better.
-Among the existing channels, the overlapping weighting functions of 183\,GHz can provide additional information to train QRNN.
-Though these channels can help in improving the training, the non-orthogonal information introduces highly correlated observational errors.
+Among the other available channels, the overlapping weighting functions of 183\,GHz can provide additional information to train QRNN.
+Though these channels help in improving the training, the non-orthogonal information introduces highly correlated observational errors.
 This is undesirable in data assimilation for NWP, but in future if the operational centres progress with approaches dealing correlated observation errors, using the configuration QRNN-all for cloud correction could be beneficial.
 
-\todo{ uncertainty discussion}
+The biggest advantage of using QRNN is estimation of case-specific uncertainties.
+The predictions over chosen quantiles quantify the underlying uncertainty.
+The calibration plot and distribution of predicted errors show that  QRNN predictions are able to represent the a priori distribution.
+However we also observe that cases with high errors are poorly calibrated.
+The poor calibration predictions associated with low accuracy is a consequence of different underlying a priori distribution.
+Predictions with high error originate from cases with high cloud impact.
+Such cases have a significantly distinct a priori distribtion as compared to clear cases, which dominate the training dataset, and influence the a priori information.
+Additional information in form of more observational data or additional training inputs is required to improve QRNN prediction accuracy for such cases.
+However such cases are rare and can be filtered out with simple threshold as showing earlier.
+From data assimilation perspective, information on case-specific uncertainties is extremely useful.
+It allows for an effective selection of weights, thus significantly improving/deteriorating the impact of measurements.
 
@@
 Interestingly, reducing the correction threshold further has no significant effect on flagging these residual cases; in fact only the clear-sky cases are removed.
-This indicates that for I1V, QRNN is unsuccessful in accounting for few cases with low cloud impact.
+This indicates that for I1V, QRNN is unsuccessful in correcting these cases completely.
 Compared to other two higher peaking channels, I1V is more sensitive to the effect of hydrometeors  and contamination from surface effects.
@@
 For AWS-32, the resulting error distributions have significantly lower spread than the measurements, but are still negatively skewed.
-This indicates that a single sub-mm channel like 325\,GHz is sufficient enough for cloud correction at 183\,GHz.
+This indicates that a single sub-mm channel like 325\,GHz is also sufficient enough for cloud correction at 183\,GHz.
 This is an important result as smaller satellites are limited by their size to measure all sub-mm wavelengths.
@@
 Most of the existing cloud filtering schemes eg.
-\cite{buehler:aclou:07} and SI \cite{} work well only at removing cases with high cloud impact.
+\citet{buehler:aclou:07} and SI \cite{geer2015scatteringindex} work well only at removing cases with high cloud impact.
 As a consequence of the residual cloud impact, the error distributions are highly skewed.
@@
 This is not unexpected as such cases form a small subset of the training set and their priori distribution is different from the entire dataset.
-The clear-sky cases dominate the test/training dataset, thus the a priori distribution is representative of the same.
-The a priori distribution of cloudy cases is different to the clear-sky cases, therefore the predictions are poorly calibrated for the former.
-Predictions for textit{out-of-distribution} cases is always a challenging task for deep learning algorithms and  shall always limit the performance.
-Improving the representation of such cases in the a priori distribution can help alleviate this problem.
-A larger training dataset would also be required to increase the representation of such cases in QRNN.
-From data assimilation perspective, information on case-specific uncertainties is extremely useful.
-It allows for an effective selection of weights, thus significantly improving/deteriorating the impact of measurements.
 
@@
 
-\todo {incomplete}
-
-In this study, a methodology based on quantile regression neural network (QRNN) is used for identifying and correcting the cloud contamination in 183\,GHz channels.
+In this study, a methodology based on quantile regression neural network (QRNN) is used for identifying and correcting the cloud contamination in operational humidity channels.
 QRNN is a neural network which trains on all-sky brightness temperatures from  channels containing orthogonal information to humidity channels, to estimate the noise free clear-sky (NFCS) radiances for humidity channels.
 The output is posterior distribution of the predictions over different quantiles.
+QRNN is a channel specific approach, or in other words, QRNN is trained separately for each channel, and the cloud correction for each is independent of other channels.
 
@@
 This is not optimal solution, but it is in agreement with what can be achieved with the present instruments.
-Infact, for lower peaking humidity channels, our approach gives a better cloud cleared product with minimal rejection of data.
-
-The robustness of QRNN is  demonstrated by utlisation of sub-millimeter (sub-mm) channels.
-
-The smaller satellite missions AWS, where only one of the higher frequencies is available.
-The same approach was applicable in this case, and the results proved that even one sub-mm channel is sufficient enough for cloud correction at 183\,GHz.
-
-A slightly lower accuracy was observed for cases with high cloud impact.
-In few of such cases, the predicted NFCS values were not completely cloud free.
-This is expected as not all cases can be represented by the a priori distribution QRNN trains on.
-Predictions for \textit{out-of-distribution} cases is always a challenging task for deep learning algorithms and  shall always limit the performance.
-Improving the representation of such cases in the a priori distribution can help alleviate this problem.
-However since such cases are few, filtering them out results in highly accurate NFCS predictions with minimal reduction in data.
-
-High quality cloud corrected radiances have great potential in DA systems.
+As compared to existing clear-filtering approaches, QRNN gives comparable or better performance and with minimal rejection of data.
+In context of present sensors, the accuracy of QRNN is affected by one single limitation, that is, the prediction of ``out of distribution'' cases.
+Predictions for such cases is always a challenging task for deep learning algorithms and shall always limit their performance.
+Improving the representation of such cases in the a priori distribution can help alleviate this problem to a certain extent.
+However, improving their priori distribution is not trivial when the no additional source of orthogonal information is present.
+
+Based on the promising results from MWHS-2, and with future scope, we extend the study to include data from sub-millimeter (sub-mm) channels.
+The results show that with  sub-mm channels, QRNN is able to correctly predict most of the cloudy cases and can provide high quality cloud corrected radiances.
+The predicted radiances have symmetric and narrow error distributions and for some channels the spread is smaller than the measurement noise.
+This makes it highly suitable for application to data assimilation systems.
+The robustness of sub-mm channels in cloud correction is also demonstrated with use of only 325\,GHz for cloud correction.
+This is applicable to smaller satellite missions like AWS, where only one of the higher frequencies is available.
+The results indicate that utilisation of only 325\,GHz can also be beneficial when other channels are absent.
+In future when ICI would be available, the ICI sub-mm channels could also be used to cloud correct MWI humidity radiances.
+Although re-mapping to a common footprint would slighly compromise the data quality, the high accuracy achieved with ICI simulations suggests that the QRNN would work well even when actual measurements are available.
+
+The biggest advantge of QRNN compared to other regression based approached is that its probabilistic nature.
+The QRNN predictions over chosen quantiles are a measure of the accuracy at different probability levels.
+In comparison to deterministic correction approaches, the corrected radiances along with uncertainty estimates.
+\todo{incomplete}
+
+The high quality cloud corrected radiances have great potential in DA systems.
 Most DA systems reject upto 80\% of the available observations due to cloud contamination.
@@
 To improve the representivity of clouds in the models, the observational errors are inflated as a function of the cloud amount.
-Most NWP centres use a scattering index(SI) based on brightness temperatures of 89 and 150\,GHz channels as a measure of cloud amount or background departure check; however such approaches act only as a partial measure of cloud identification.
+Most NWP centres use partial cloud identification approaches.
 On the contrary, cloud cleared microwave radiances offer forecast benefits without additional complexities.
@@
 
-Though these set of hyper-parameters were selected for QRNN-single applied to I2V, they worked well for other QRNN models and their multiple configurations.
-All the results described in this study use an identical hyper-parameter configuration.
+Though these set of hyper-parameters were selected for QRNN-single applied to I2V, they worked well for both ICI and AWS QRNN experiments.
+However, for MWHS-2, an identical hyperparameter framework but three hidden layers gave best results.
 

### 2020-10-31 Article/ici_submm_cloudcorr.tex
some editing, and added table with SI and Buehler_etal filtering

@@
 
-%\documentclass[amt, manuscript]{copernicus}
-\documentclass[amt]{copernicus}
+\documentclass[amt, manuscript]{copernicus}
+%\documentclass[amt]{copernicus}
 
@@
 Despite individual variations for each channel, it is observed that uncertainty consistently increases with the error in the performance.
-
-\todo {write one line, why important for DA}
+From data assimilation perspective, high quality cloud cleared radiances with symmetric error distribution and case-specific uncertainties are extremely valuable.
 
@@
 It is a cross track scanning microwave radiometer and measures 15 frequencies in the range 89-191\,GHz.
-89\,GHz and 150\,GHz are window channels, five humidity sounding channels are centered at 183.31\,GHz and eight temperature sounding channels centered at 118.75\,GHz oxygen absorption line.
+89\,GHz and 150\,GHz are window channels, five humidity sounding channels are centered at 183.31\,GHz and eight temperature sounding channels are centered at 118.75\,GHz oxygen absorption line.
 The five humidity sounding channels are similar to MWS (Micro Wave Sounder) and ATMS (Advanced Technology Microwave Sounder).
@@
 The main objective of ICI is to use high frequency channels for measuring ice cloud properties and improve the representation of ice clouds in regional and global Numerical Weather Prediction(NWP) models.
-ICI is a conically scanning radiometer that will measure 13 frequencies from 183 GHz up to 664 GHz.
-ICI consists of channels receiving frequencies around 183.31\,GHz, 325.15\,GHz and 448.00\,GHz, measuring vertical polarization.
-While other channels around frequencies 243.20\,GHz and 664.00\,GHz are ``window channels'' and measure both vertical and horizontal polarization.
+ICI is a conically scanning radiometer that will measure 13 frequencies from 183\,GHz up to 664\, GHz.
+Among all available channels, 183.31\,GHz, 325.15\,GHz and 448.00\,GHz, will measure vertical polarization;  while other channels around frequencies 243.20\,GHz and 664.00\,GHz are ``window channels'' and will measure both vertical and horizontal polarization.
 The instrument will observe earth from a mean altitude of 832\,Km with sensor viewing angle 44.767$^\circ$(measured from nadir).
 For all the channels, the mean footprint size is about 15\,Km, but the exact geo-location of samples differs.
-Therefore a simultaneous utilization of data from different channels requires remapping to a common footprint \citep{eriksson:towar:20}.
+Therefore a simultaneous utilization of data from different channels shall require remapping to a common footprint \citep{eriksson:towar:20}.
 
@@
 %
-MWHS-2 simulated radiances are routinely calculated at ECMWF for their use in the ECMWF assimilation system.
-RTTOV and RTTOV-SCATT are used to calculate the radiances in the clear-sky and all-sky conditions respectively.
-For this study, MWHS-2 brightness temperatures for the period June-July 2020 were used.
-Out of all the available observations, we extracted data for latitudinal range $60^{\degree}$\,S to $60^{\degree}$\,N and satellite zenith angle less than $7.5^{\degree}$.
-With this filter we had 340\,000 cases for each frequency.
-
-ICI, AWS frequencies were simulated with ARTS.
-Cloudsat profiles during August 2015 were randomly selected for forward simulations.
-The input data were restricted between $60^{\degree}$S to $60^{\degree}$N, and surface was below 500\,m.
-Both clear-sky and all-sky scenarios were simulated.
+MWHS-2 simulated radiances are routinely calculated at ECMWF for their use in the ECMWF NWP system.
+RTTOV and RTTOV-SCATT are used to calculate the radiances in clear-sky and all-sky conditions, respectively.
+For this study, MWHS-2 brightness temperatures for the period June-July 2020 are used.
+Out of all the available observations, we use data for latitudinal range $60^{\degree}$\,S to $60^{\degree}$\,N and satellite zenith angle less than $7.5^{\degree}$.
+With this filter we have 340\,000 cases for each frequency.
+
+ICI and AWS frequencies are simulated with ARTS.
+Cloudsat profiles during August 2015 are randomly selected for forward simulations.
+The input data are restricted between $60^{\degree}$S to $60^{\degree}$N, and surface is below 500\,m.
+Both clear-sky and all-sky scenarios  are simulated.
 The complete simulation setup is described in Appendix \ref{appendix:ARTS_setup}.
-For each ICI frequency in Table~\ref{tab:ICI_MWI_channels}, 220\,000 cases were simulated.
-For both instruments, the channel frequencies were simulated directly.
-For AWS, 140\,000 cases were simulated.
-Forward simulations were performed for 21 monochromatic frequencies.
-These frequencies were interpolated to a finer grid to get the AWS channel brightness temperatures.
-All AWS sensor viewing angles (from $0^\circ$ to $45^\circ$) were simulated, but the results described in this study are based on nadir viewing angle.
-
-All simulations were noise free, so to incorporate the measurement uncertainties, whenever needed, gaussian noise was added to according to the channel NE$\Delta$T (Table~\ref{tab:specifications_MWHS2} - Table~\ref{tab:specifications_AWS}).
-
-The noise free simulations were split into training and testing datasets.
-The training dataset was used to train the machine learning model, while the testing dataset was used to evaluate the trained model.
+For each ICI frequency in Table~\ref{tab:ICI_MWI_channels}, 220\,000 cases are simulated.
+All ICI frequencies are simulated directly.
+For AWS, 140\,000 cases are simulated.
+Forward simulations are performed for 21 monochromatic frequencies, and later these frequencies are interpolated to a finer grid to get the AWS channel brightness temperatures.
+All AWS sensor viewing angles (from $0^\circ$ to $45^\circ$) are simulated, but the results described in this study are based on nadir viewing angle.
+Simulations for all three sensors are noise free, so to incorporate the measurement uncertainties, whenever needed, gaussian noise is added to according to the channel NE$\Delta$T (Table~\ref{tab:specifications_MWHS2} - Table~\ref{tab:specifications_AWS}).
+
+The noise free simulations are split into training and testing datasets.
+The training dataset is used to train the machine learning model, while the testing dataset is used to evaluate the trained model.
 The construction and details of the model are described in Sect.~\ref{sec:QRNN}.
-For MWHS-2, 220\,000 simulations were randomly selected as training dataset, while 70\,000 were used for testing.
-For ICI, 175\,000 cases were randomly picked to form the training set.
-The remaining 45\,000 were used for testing.
-A smaller database was selected for AWS.
-120\,000 simulations were used for training and the rest were used for testing.
+For MWHS-2, 220\,000 simulations are randomly selected as training dataset, while 70\,000 were used for testing.
+For ICI, 175\,000 cases are randomly picked to form the training set.
+The remaining 45\,000 are used for testing.
+A smaller database is selected for AWS.
+120\,000 simulations are used for training and the rest are used for testing.
 
@@
 $0.2\%, 3\%, 16\%, 50\%, 85\%, 97\%$ and $99.8\%$. For a Gaussian
-distribution with mean $\mu$ and standard deviation $\sigma$ the
-approximately corresponds to $\mu -3\sigma, \mu-2\sigma, \mu-\sigma
+distribution with mean $\mu$ and standard deviation $\sigma$, the quantiles
+approximately correspond to $\mu -3\sigma, \mu-2\sigma, \mu-\sigma
 , \mu, \mu + \sigma, \mu + 2\sigma, \mu + 3\sigma$ and thus allows
-estimating the $\pm 1, \pm 2$ and $\pm 3\sigma$ confidence intervals.
-The median is used as point estimate for the corrected $\ynfcs$.
+estimation of the $\pm 1, \pm 2$ and $\pm 3\sigma$ confidence intervals.
 
@@
 used in this study as a performance criterion for the tuning of the hyper
-parameters of the QRNN. In addition to the quantile loss, also the Continuously
+parameters of the QRNN (see Appendix~\ref{appendix:hyperparamter}). In addition to the quantile loss, also the Continuously
 Ranked Probability Score (CRPS) is considered. Given a predicted cumulative
@@
 
-The implementation of QRNN is similar to one described in \citet{pfreundschuh:aneur:18}, except that instead of Kera python package, PyTorch, an open source machine learning
+The implementation of QRNN is similar to one described in \citet{pfreundschuh:aneur:18}, except that instead of Keras python package, PyTorch, an open source machine learning
 library \citep{paszke2017automatic} is used.
@@
 %
+\label{sec:QRNN_configuration}
 In the study, two QRNN configurations are formulated for cloud-correction.
-The basic construction of both is to train for each of the available 183\,GHz channels individually, using certain input training data.
+The basic construction of both is to individually train for each of the available 183\,GHz channels, using certain input training data.
 The input data is all-sky brightness temperatures from selected input channels and/or additional data like land/sea mask.
-The selection of input channels is sensor dependent and is described in detail when introduced.
 The output in both configurations is NFCS value for the target 183\,GHz channel.
@@
 \begin{enumerate}
-	\item QRNN-single: In this configuration, the training input includes all-sky brightness temperatures from the target 183\,GHz channel and other non-humidity channels along with additional data, if relevant.
+	\item QRNN-single: In this configuration, the training input includes all-sky brightness temperatures from the target 183\,GHz channel and other non-humidity channels.
+Additional data is included, if relevant.
 No other 183\,GHz channel is included.
@@
 
-For all three sensors described in this study, one or both of the above QRNN configurations are used.
+For all three sensors described in this study, one or both of the above QRNN configurations are used. The selection of input channels is sensor dependent and is described in detail when introduced.
 
@@
 \end{figure}
-QRNN predictions are posterior probability distribution of the NFCS values described over the selected quantiles.
-This is contrast with other conventional correction/filtering methods.
+QRNN predictions are posterior probability distribution of the NFCS values described over the chosen quantiles.
 In order to facilitate the interpretation of results, an example QRNN output is shown in Fig.~\ref{fig:posterior_distribution_I1V}.
-This examples illustrate the predicted quantiles for three different cases.
-For most analysis, usually a single point estimate is required.
+This example illustrates the predicted quantiles for three different cases.
+This is in contrast with other conventional correction/filtering methods, which give out only point estimates.
+However, for most analysis, usually a single point estimate is required.
 In Bayesian analysis, usually the posterior mean or posterior median are selected as point estimates.
 In this study, we assume the posterior median to be the best estimate for the predicted NFCS value ($\ynfcs$).
-To analyse the ability of QRNN in correctly predicting the point estimate, deviations of point estimates from the corresponding true value ($\yonfcs$) are evaluated using common performance indicators like bias, mean absolute error(MAE) and standard deviation (STD).
+To analyse the ability of QRNN in correctly predicting the point estimate, deviation of the median value from the corresponding true value ($\yonfcs$) is evaluated using common performance indicators like bias, mean absolute error(MAE) and standard deviation (STD).
 The asymmetry of error distributions around their mean is also calculated through the measure of skewness.
-Fisher-Pearson coefficient of skewness is used to calculate the measure of skewness:
+For a univariate dataset of length $N$, the Fisher-Pearson coefficient of skewness is defined as:
 \begin{equation}
-g_1 = \frac{m_3}{m_2^{3/2}}, 
+g_1 = 	\frac{\sqrt{N(N-1)}}{N-2} \frac{\sum_{i = 1}^{N}(Y_i - \bar{Y})^3/N}{\sigma^3}
 \end{equation}
-where $m_2$ and $m_3$ are biased sample's second and third central moments.
+where $\bar{Y}$ and $\sigma$ are mean and standard deviation of the dataset, respectively.
 
 For probabilistic predictions, accuracy of the point estimate is inadequate to gauge the complete performance.
-In a successful QRNN training, QRNN learns to predict not only an accurate point estimate but also correct underlying uncertainty.
-An ideal QRNN output should be sharp or in other words, concentrated in the vicinity of the point estimate.
-The predicted posterior distribution should also be well calibrated, that is, reflect the true probability distribution.
-A straightforward way to compare the two distribution is to plot the frequency of predictions and frequency of the true value in different prediction intervals.
+In a successful QRNN training, QRNN learns to predict not only an accurate point estimate but also the correct underlying uncertainty.
+An ideal QRNN output should be sharp or in other words, all predicted quantiles should be concentrated in the vicinity of the point estimate.
+The predicted posterior distribution should also be well calibrated, that is, reflect the a priori probability distribution.
+A straightforward way to compare the two distributions is to plot the frequency of predictions and frequency of the true value in different prediction intervals.
 This is also commonly known as calibration plot.
-In a well-calibrated QRNN prediction, the calibration plot should follow the straight line y = x.
-Another way to assess how well the predicted posterior distribution reflects the observed errors is to compare predicted and observed errors.
+In a well-calibrated QRNN model, the calibration plot should follow the straight line y = x.
+Another way to assess how well the predicted posterior distribution reflects the observed errors is to compare the predicted and observed errors.
 The predicted error is deviation of a random sample drawn from the posterior distribution to its median.
-In this study, we use both calibration plot and predicted errors to assess the correctness of predicted uncertainties.
+In this study, we analyse both calibration plot and predicted errors to assess the correctness of predicted uncertainties.
 
@@
 The choice is motivated by the fact that MWHS-2 has five complementary 183\,GHz channels as ATMS/MWS, along with additional 118\,GHz channel.
-In order to test the correction approach multiple QRNN experiments are performed and the results are compared for MWHS-2 channel 14.
-Later the methodology is expanded to other channels.
+In order to formulate and test the correction approach, multiple QRNN experiments are performed for MWHS-2 channel 14.
+Later the methodology is expanded to other 183\,GHz channels.
+A brief comparison of the results is also made against existing cloud filtering methods.
 Further, the estimates of case-specific uncertainties obtained from QRNN are also evaluated.
@@
 %
-For MWHS-2, multiple experiments using both QRNN configurations are performed. The aim of the experiments is to delve into the sensitivity of the cloud correction to different input channels:
+For MWHS-2, multiple experiments using both QRNN configurations are performed. With different experiments we aim to delve into the sensitivity of the method to different input channels:
 
@@
 In ECMWF NWP system, the differences between the observations of these two window channels (Scattering Index) \citep{Lu2015FY3C} are used to identify the cloud affected data for ATMS, MHS and MWHS-2.
-To investigate the potential impact of window channels in QRNN based cloud correction, the configuration QRNN-single is applied to predict cloud free radiances.
+To investigate the potential impact of these two window channels in QRNN based cloud correction, the configuration QRNN-single is applied to predict cloud free radiances.
 In this experiment, the training input includes all-sky brightness temperatures from target 183\,GHz channel, 89\,GHz and 150\,GHz.
 Both 89 and 150\,GHz are window channels so the land sea mask is also included as a training input.
-For example for channel 14, the training inputs are all-sky brightness temperatures from channels 14, 1, 10 and land/sea mask.
+For example, for channel 14, the training inputs are all-sky brightness temperatures from channels 14, 1, 10 and land/sea mask.
 This combination is referred as 89+150\,GHz in the text.
@@
 	\item The third experiment is designed to assess the exclusive impact of 150\,GHz in cloud correction.
+This experiment is motivated by the fact that hydrometeor impact at 150\,GHz is stronger as compared to 89\,GHz, and is less affected by surface emissivity.
 In this experiment, QRNN-single is trained with brightness temperatures from 150\,GHz along with the target channel and land/sea mask.
@@
 In this experiment, we use 89 and 150\,GHz channels along with all 183\,GHz channels to train QRNN.
-This experiment is motivated by the fact that in all-sky conditions, brightness temperatures between outer and inner humidity channels can be used as a criterion for cloud filtering\cite{buehler:aclou:07}.
-With QRNN-all, we investigate if additional humidity channels in the training process can improve the performance by providing auxiliary information.
+The use of 183\,GHz channels for ``self'' cloud filtering has been studied by  \citet{buehler:aclou:07}.
+They show that brightness temperatures between outer and inner humidity channels can be used as a criterion for cloud filtering.
+With QRNN-all, we investigate if additional humidity channels in the training process can improve the performance.
 It should be noted that though the training inputs are same for each 183\,GHz channel, the output is the target 183\,GHz channel; thus each channel still needs to be trained separately.
@@
 	\includegraphics[height=55mm]{Figures/QRNN_output_mwhs.pdf} 
-	\caption{Distributions of point estimate $\ynfcs$ obtained from QRNN-single 89+150\,GHz for MWHS-2 channel 14. The corresponding distribution for all-sky and clear-sky simulations are also shown.}
+	\caption{Distribution of point estimate $\ynfcs$ obtained from QRNN-single 89+150\,GHz for MWHS-2 channel 14. The corresponding distributions for all-sky and clear-sky simulations are also shown.}
 	\label{fig:distribution_predicted_mwhs14}	
@@
 \begin{table*}[t]
-	\caption{Error statistics for deviations of MWHS-2 NFSC predictions to simulations.
+	\caption{Error statistics for deviations of NFCS predictions to simulations.
 Results are for different QRNN experiments for MWHS-2 channel 14.
-With configuration QRNN-single, the results are from combinations 89+150\,GHz, 89+150+118\,GHz and 150\,GHz.
+The results from input channel combinations 89+150\,GHz, 89+150+118\,GHz and 150\,GHz are with QRNN-single.
 While with QRNN-all, only combination 89+150+183\,GHz is shown.
@@
 \end{table*}
+
 Fig.~\ref{fig:distribution_predicted_mwhs14} shows the distribution of QRNN predictions obtained from QRNN.
-QRNN predictions are able to remove the extended mass concentration to the left is due hydrometeor impact, and overall a good match with the NFCS simulations is observed.
-QRNN is unable to predict the lowest clear-sky brightness temperatures, but cases with brightness temperatures around 260\,K occur frequently.
-Table~\ref{tab:error_statistics_mwhs_14} shows the error statistics for the predictions shown in Fig.~\ref{fig:distribution_predicted_mwhs14}.
+The predicted values are able to remove most of the low brightness temperature cases, and overall a good match with the NFCS simulations is observed.
+QRNN is unable to predict the lowest clear-sky brightness temperatures, and cases with brightness temperatures around 260\,K occur frequently.
+The corresponding error statistics(Sect.~\ref{sec:validation}) are displayed in  Table~\ref{tab:error_statistics_mwhs_14}.
 In the uncorrected data, cloud impact causes a large negative skewness(-14.34) in the error distribution and the corresponding bias is -0.84\,K.
 Training QRNN with 89 and 150\,GHz removes a part of the cloud impact and reduces the bias to -0.09\,K, and the skewness is -1.11.
-The MAE and STD are also reduced after correction, but are higher than noise.
+The MAE and STD are also reduced.
 Including 118\,GHz in the training, gives comparable results as 89+150\,GHz.
@@
 
-Further we investigated that if filtering the predictions with large residual cloud impact could help in improving the prediction accuracy.
+Further we investigated that if filtering the predictions with low accuracy could help in improving the error distribution.
 For filtering such cases, we assume that predictions with cloud correction greater than 5\,K are cases associated with large deviations.
 In all three experiments, removing the cases with correction greater than 5\,K removes around 3\% of the data, but only a marginal positive impact on the accuracy is observed.
-With 5\,K thresold, though the cases with high errors are removed, the negative skewness conveys that some cases with low cloud impact are not completely corrected.
+With 5\,K threshold though the cases with high errors are removed, the negative skewness indicates presence of cases with residual cloud impact.
 Choosing a lower threshold can help in removing more partially corrected cases but at the cost of rejecting clear-sky cases.
@@
 
-In spite of the fact that QRNN only provides a partial cloud correction, the results are better to what scattering index (SI) based approach would give.
-SI uses the differences of brightness temperatures between 89 and 150\,GHz to identify cloud affected data \citep{geer2015scatteringindex}.
-With 5\,K SI threshold, almost 30\% of the data is rejected and the error distributions have bias, mae and standard deviation as -0.23\,K 0.92\,K and 1.40\,K respectively (Table~\ref{tab:SI_statistics}).
+In spite of the fact that QRNN only provides a partial cloud correction, the results for  MWHS-2 channel 14 are comparable to what we achieve with existing cloud filtering techniques like scattering index (SI)  \citep{geer2015scatteringindex} and the filtering scheme by \citet{buehler:aclou:07}.
+SI uses the differences of brightness temperatures between 89 and 150\,GHz to identify cloud affected data.
+While in the study by \citet{buehler:aclou:07}, they use brightness temperature based threshold to filter out cloudy cases.
+They recommend a viewing angle dependent brightness temperature threshold at $183.31\pm1.00$ \,GHz and brightness temperature difference between $183.31\pm3.00$ and $183.31\pm 1.00$ as a measure of cloud impact.
+Further in the text we refer this scheme as ``B183''.
+The results obtained with SI and B183 are displayed in Table~\ref{tab:SI_statistics}.
+With SI threshold = 5\,K, almost 30\% of the data is rejected, yet the resulting error distributions are worse as compared to QRNN.
+Similar is the case with B183, where approximately 17\% of the data is rejected, but the filtering performance is inadequate.
 
@@
 In comparison to QRNN-single, we obtain marginally lower error bias with QRNN-all, and the MAE and standard deviation reduce by almost 30\% and 25\% respectively.
-However the negative tail becomes more prominent.
+However, the negative tail becomes more prominent.
 The low standard deviation, but strong negative tail indicates that the narrow spread is a consequence of correction of noise in clear-sky cases.
 Since a majority of the cases are clear-sky, their impact dominates the whole statistics.
-In order to quantify the positive effect of QRNN-all on cases with high and low cloud impact, a separate analysis of the high and low cloud impact cases is made.
-In both cases, QRNN-all has slightly better accuracy than QRNN-single, suggesting that concurrent use of all 183\,GHz channels can provide additional information on cloud structures to QRNN.
+In order to probe the positive effect of QRNN-all, we also estimated the errors for all cases with cloud correction greater than 5\,K.
+In comparison with QRNN-single, QRNN-all had slightly better accuracy.
+This suggests that concurrent use of all 183\,GHz channels can provide additional information on cloud structures to QRNN.
 
@@
 For cloudy cases, the observed errors obtained from QRNN-single are slightly correlated, but with QRNN-all a very strong correlation is observed(not shown).
-The residual cloud amount for different channels depends upon each other in a systematic way, but since QRNN-single does not have access to this information, only slightly higher correlations are observed.
-On the other hand, with QRNN-all, when all 183\,GHz channels are used simultaneously the predictions learn positively from the common information and also introduces high correlations between overlapping channels.
-Correlated errors can be undesirable for DA systems, so the configuration QRNN-all is avoided for further development.
 
@@
 \end{table*}
-\begin{table}[t]
-	\caption{Error statistics obtained after filtering MWHS-2 humidity observations according to scattering index.  }
+\begin{table*}[t]
+	\caption{Error statistics obtained after filtering MWHS-2 humidity observations according to scattering index (SI) and methodology described by \citet{buehler:aclou:07}.}
 	\label{tab:SI_statistics}
-	\begin{tabular}{lrrrrr}
+	\begin{tabular}{lrr|rr|rr|rr|rr}
 		\tophline
-		& Ch. 11 & Ch. 12 & Ch. 13 & Ch. 14 & Ch. 15\\
-			\cline{2-6}
-		bias     & -0.05&  -0.07 & -0.14 & -0.23 &  -0.34\\
-		mae      & 0.81 &   0.82 &  0.85 &  0.92 &  1.03\\
-		std      & 1.02 &   1.04 &  1.10 &  1.25 &  1.53\\
+		& \multicolumn{2}{c|}{Channel 11} & \multicolumn{2}{c|}{Channel 12} & \multicolumn{2}{c|}{Channel 13} & \multicolumn{2}{c|}{Channel 14} & \multicolumn{2}{c}{Channel 15}\\
+			\cline{2-11}
+		bias &-0.05	&-0.08	&-0.07&	-0.13&-0.14	&-0.24	&-0.23&	-0.4&-0.34&	-0.59\\
+		mae  & 0.81	&0.84	&0.82 &	0.88 &	0.85&0.95   &0.92 &	1.07&1.03 &	1.25\\
+		std  &1.02	&1.22	&1.04 &	1.52 &	1.1	& 2.0	&1.25 &	2.54&1.53&	3.25\\
 		\bottomhline		
 	\end{tabular}
-\end{table}
+\end{table*}
 
@@
 For channel 11, the error bias after correction is only -0.03\,K in comparison to 0.16\,K before correction.
-The strong negative tail also diminishes after correction, but a non-zero negative skewness indicates presence of cases with cloud impact in the corrected dataset.
-Filtering the cases with high cloud impact has only a marginally positive impact.
+The strong negative tail also diminishes after correction, but a non-zero negative skewness indicates presence of cases with residual cloud impact in the corrected dataset.
+Filtering the cases with high cloud impact has only a marginal positive effect.
 A similar performance is evident for channel 12.
-Correction reduces the bias to -0.05\,K and the MAE is approximately 17\% lower for the entire test dataset.
-However the effect of partially corrected cases is evident in the negative skewness.
-There is again only a partial correction evident for channels 13 and 15.
-The bias values are quite low indicating that QRNN is successful in removing a large fraction of the cloud impact, but relatively high skewness is a consequence of cases with low cloud impact which end up with inadequate correction.
-
-A comparison with SI based filtering is also made (Table~\ref{tab:SI_statistics}).
+Correction reduces the bias to -0.05\,K and standard deviation to 1.07\,K.
+The MAE is approximately 17\% lower after correction, but still the negative skewness is not removed completely.
+For channel 13 and 15 also a similar performance is seen.
+But in the latter, error distributions are most symmetric as compated to other four channels.
+The skewness is only -0.60.
+
+A comparison with SI based filtering and B183 is displayed in  Table~\ref{tab:SI_statistics}.
 For channels 11 and 12 the performance of QRNN is comparable to scattering index, albeit 30\% of the observations are rejected in the latter.
-For channels 13 and 15, the error statistics obtained with SI are slightly worse.
+For channels 13 and 15, the error statistics obtained with SI are slightly inferior.
+The filtering with B183 is also partial for all channels......\todo{can we say they are unsatisfactory?}
 
@@
 The quantiles given out by QRNN can be used to construct the probability distribution of the predictions in contrast to other correction approaches which give out only point estimates.
-
 An example of the uncertainties given out by QRNN is shown in Fig~\ref{fig:prediction_uncertainty_mwhs}.
@@
 
-Further we analysed if the  predicted errors obtained from QRNN are representative of observed errors.
+Further, we analyse if the  predicted errors obtained from QRNN are representative of observed errors.
 Fig~\ref{fig:predicted_errors_mwhs} illustrates the predicted and observed errors for MWHS-2 channel 14.
@@
 \begin{enumerate}
-	\item In the first experiment, we follow the QRNN-single configuration to for cloud correction at three ICI humidity channels.
+	\item In the first experiment, we apply QRNN-single configuration for cloud correction at three ICI humidity channels.
 In this case, the training data is the target 183\,GHz channel and all available ICI sub-mm frequencies (325\,GHz, 448\,GHz and 664\,GHz).
@@
 	\caption{Error distributions for deviations predicted data to NFCS simulations.
-The results are from QRNN-ici and channels I1V, I2V and I3V.
+The results are from QRNN-single and channels I1V, I2V and I3V.
 Noise for each channel is also plotted for reference.
@@
 		The values for Bias, mean absolute error(MAE), standard deviation(STD), and measure of skewness(Skewness) are shown.
-Results are for channels I1V, I2V and I3V.
+Results are from QRNN-single for channels I1V, I2V and I3V.
 The number in parentheses is the percentage of cases removed by filtering.
@@
 		%		\hline
-		&&   Clear-sky &   All-sky &  \multicolumn{2}{c}{Predicted}  \\
+		&&Clear-sky &   All-sky &  \multicolumn{2}{c}{Predicted}  \\
 		&&			   &			&	(5\,K) & (All) \\
@@
 
-		I1V&  bias     &  0.00 & -1.87 & -0.02 & -0.00  \\
+		I1V&  bias     &  0.00 & -1.87 & -0.02 & -0.00(6.1\%)  \\
 		&mae      &  0.64 &  2.32 &  0.70 &  0.60   \\
@@
 		\middlehline
-		I2V & bias     & 0.00 &  -1.04 &  0.00 &  0.01  \\
+		I2V & bias     & 0.00 &  -1.04 &  0.00 &  0.01(3.6\%)  \\
 		&mae      & 0.64 &   1.53 &  0.57 &  0.51 \\
@@
 		\middlehline	
-		I3V & bias     & 0.01 &  -0.63 &  0.02 &  0.02  \\
+		I3V & bias     & 0.01 &  -0.63 &  0.02 &  0.02(2.2\%)  \\
 		&mae      & 0.64 &   1.15 &  0.54 &  0.50  \\
@@
 
-For a quantitative assessment of the errors, we calculated the error metrics described in Sect.~\ref{sec:validation} and the results are displayed in Table~\ref{tab:error_statistics_ici}.
+For a quantitative assessment of the errors, the results from various error metrics described in  Sect.~\ref{sec:validation} are displayed in Table~\ref{tab:error_statistics_ici}.
 The average bias in I1V measurements is -1.87\,K, which reduces to -0.02\,K after cloud correction.
@@
 		\cline{3-6}
-		%		\hline
-		&&   Clear-sky &   All-sky &   Predicted(All) & Predicted(5\,K) \\
+		&&Clear-sky &   All-sky &  \multicolumn{2}{c}{Predicted}  \\
+		&&   &    &   (All) & (5\,K) \\
 		\middlehline
@@
 On the other hand, when only the cases with  cloud correction greater than 10\,K are considered, the predictions in all the intervals are poorly calibrated.
-In this case the calibration curve lies below the y=x line, indicating that the predicted intervals are too narrow, or the uncertainty is underestimated.
+In this case the calibration curve lies slightly below the y=x line, indicating that the predicted intervals are too narrow, or the uncertainty is underestimated.
 
@@
 The predicted and observed errors have good agreement for the peak of the distribution, but the predicted errors are spread out asymmetrically.
-QRNN is not able to represent the left wings of the distribution.
+QRNN is not able to completely represent the wings of the distribution.
 This could also be a sampling issue, as the high errors we try to predict constitute a very small part of the complete dataset and we do not derive any sample from outside $\pm3\sigma$.
@@
 The results from MWHS-2 show that QRNN based cloud correction is partially successful in correcting the cloud impact with existing sensors.
-The methodology can correctly address the large negative depatures owing to cloud impact, but cases with low cloud impact end up with inadequate correction.
+The methodology can correctly address the large negative depatures owing to cloud impact, but few cloudy cases end up with inadequate correction.
 The resulting error distributions are not completely symmetric but have a low bias and spread.
@@
 We also investigate the impact of two temperature sounding channels (MWHS-2 channel 6 and 7).
-Both these channels provide complementary information to humidity channels in the lower troposphere.
-Including both these channels in the training process had no significant effect on the prediction accuracy.
-We obtain almost similar performance as with the combination 89+150\,GHz.
-
-Even though the cloud correction is partial, the performance is comparable or better to existing cloud filtering techniques like SI.
-SI is also a partial filter which identifies the contamination only due to precipitation and cloud ice.
-Note that SI is a one for all approach for all 183\,Ghz channels, thus is one observation is classfied as cloudy by SI, it is removed in all available humidity channels.
-This increases the probability of erroneously removing clear observations as cloudy.
-For high peaking channels of MWHS-2, both SI and QRNN give almost similar results, with however with almost 30\% rejection rate.
-On the other hand, for low peaking channels, the same rejection criteria gives less accurate results than QRNN.
-These channels have a stronger hydrometeor impact than channels 11 and 12.
-Clearly, a channel specific approach like QRNN is more appropriate and gives better performance.
-
-The partial performance of QRNN is due to incomplete orthogonal information to 183\,GHz humidity channels.
+These channels provide complementary information to humidity channels in the lower troposphere.
+Including both these channels in the training process had no significant effect on the prediction accuracy and almost similar performance as with the combination 89+150\,GHz is obtained.
+
+The partial performance of QRNN is due to incomplete orthogonal information to 183\,GHz channels.
 The weighting functions of window channels 89 and 150\,GHz, and the two 118\,GHz channels peak in the lower troposphere.
 Among these four channels, 150\,GHz has the highest peaking function around 4\,Km \cite{chen2020mwhs}.
-These channels can only provide coverage to the humidity channels in lower and mid troposphere; nonetheless, the 183\,GHz channels are sensitive to hydrometeor content beyond 2\,Km.
-Due to missing complementary information from other channels in the upper troposphere, QRNN fails to train to predict these cases accurately.
-Additional information from other channels is necessary to help QRNN train better.
-Among the other available channels, the overlapping weighting functions of 183\,GHz can provide additional information to train QRNN.
-Though these channels help in improving the training, the non-orthogonal information introduces highly correlated observational errors.
-This is undesirable in data assimilation for NWP, but in future if the operational centres progress with approaches dealing correlated observation errors, using the configuration QRNN-all for cloud correction could be beneficial.
+These channels can only provide coverage to the humidity channels in lower and mid troposphere; nonetheless, the 183\,GHz channels are sensitive to hydrometeor content upto 2\,Km.
+Due to missing complementary information from other channels in the upper troposphere, QRNN fails at predicting these cases accurately.
+Such cases mostly represent the thin cirrus clouds, which have very small influence at 89 and 150\,GHz.
+Without additional information from other channels we cannot expect QRNN train better.
+Among the other available channels, the overlapping weighting functions of 183\,GHz can provide auxiliary information to train QRNN.
+Results show that these channels can help in improving the training, the non-orthogonal information introduces highly correlated observational errors.
+The residual cloud amount for different channels depends upon each other in a systematic way, but since QRNN-single does not have access to this information, the correlations are low.
+On the other hand, with QRNN-all, when all 183\,GHz channels are used simultaneously the predictions learn positively from the common information but also introduces high correlations between overlapping channels.
+Correlated errors can be undesirable for DA systems, but in future if the operational centres progress with approaches dealing with correlated observation errors, concurrent use of  89, 150 and 183\,GHz channels would give the best cloud correction performance.
+
+Even though the cloud correction is partial, the performance is comparable or better to existing cloud filtering techniques like SI and scheme by \cite{buehler:aclou:07}.
+Note that both these techniques are a one for all approach for each 183\,Ghz channel; thus if one observation is classified as cloudy by the filter, it is removed in all humidity channels.
+This increases the probability of erroneously removing clear observations.
+For high peaking channels of MWHS-2, both SI and QRNN give almost similar results, however with almost 30\% rejection rate.
+On the other hand, for low peaking channels, the same rejection criteria, SI gives less accurate results than QRNN, as these channels have a stronger hydrometeor impact than channels 11 and 12.
+This clearly indicates, that a channel specific approach like QRNN is more appropriate, and gives better performance.
 
@@
 Additional information in form of more observational data or additional training inputs is required to improve QRNN prediction accuracy for such cases.
-However such cases are rare and can be filtered out with simple threshold as showing earlier.
-From data assimilation perspective, information on case-specific uncertainties is extremely useful.
-It allows for an effective selection of weights, thus significantly improving/deteriorating the impact of measurements.
 
@@
 In context of present sensors, the accuracy of QRNN is affected by one single limitation, that is, the prediction of ``out of distribution'' cases.
-Predictions for such cases is always a challenging task for deep learning algorithms and shall always limit their performance.
+Correcting hydrometeor impact for cases where no complementary information is available is a challenge for QRNN and always limit its performance.
 Improving the representation of such cases in the a priori distribution can help alleviate this problem to a certain extent.

### 2020-11-02 Article/ici_submm_cloudcorr.tex
Final 1st draft

@@
 
-In this study, we present methodology to identify and correct the cloud impact in microwave humidity radiances.
-A channel specific quantile regression(QRNN) based approach is formulated to estimate the posterior distributions of noise free clear sky (NFCS) radiances.
-The applicability of the approach is demonstrated by application to current sensor MWHS-2.
+Identification of cloud affected observations is indispensable for both clear-sky and all-sky Numerical Weather Prediction (NWP) systems.
+In this study, we present a methodology to identify and correct the cloud impact in microwave humidity radiances.
+A channel specific quantile regression neural network (QRNN) based approach is formulated to estimate the posterior distributions of noise free clear sky (NFCS) radiances.
+The applicability of the approach is demonstrated by application to a present sensor: MWHS-2.
 With the future outlook, the applicability to sub-millimeter (sub-mm) channels is also investigated.
 The results are compared against the NFCS simulations.
-With the present sensors, the approach is only partially successful in removing the cloud contamination.
-Though most of the cases with high cloud impact are corrected, cases with low cloud impact are only partially corrected.
-This is comparable/better to the level of accuracy achieved with operational cloud-filtering techniques, like scattering index.
-However with sub-mm channels, we are able to successfully correct most of the cases with cloud impact.
-The resulting error distributions are symmetric with very low spread.
-The methodology also works well even when only one of the higher frequencies is available.
-In some cases, the combination of 183\,GHz and sub-mm channels also results in a lower variability than noise.
+With the present sensors, the approach is successful in correcting most of the cases with large negative departures, but a fraction cases end up with partial correction.
+In spite of the cases with residual cloud impact, the results from QRNN are better than what operational cloud filtering techniques like scattering index can achieve.
+On the other hand, when sub-mm observations from ICI are used to correct the cloud impact, QRNN can successfully correct most of the cases with cloud impact.
+Only 2-4\% of the cases are partially corrected and these can be easily removed by a simple filtering; and the resulting error distributions are almost symmetric with very low spread.
+The methodology also works well when only one of the higher frequencies (325\,GHz) is available.
+Except for the lowest peaking channel, using sub-mm observations results in error distributions with standard deviation less than the measurement noise.
 Another advantage of using QRNN is that predicted quantiles can be employed to quantify the case-specific uncertainty estimates.
-The results show that QRNN is successful in representing the uncertainty for most of the scenes individually.
-Despite individual variations for each channel, it is observed that uncertainty consistently increases with the error in the performance.
-From data assimilation perspective, high quality cloud cleared radiances with symmetric error distribution and case-specific uncertainties are extremely valuable.
+The results show that QRNN is successful in representing the uncertainty for each case individually.
+Despite individual variations for each channel, the predictions exhibit a higher uncertainty when the test data includes the ``out of distribution'' cases.
+In comparison to deterministic correction/filtering approaches, the high quality corrected radiances with uncertainty estimates have great potential to be used efficiently in assimilation systems.
 
@@
 
-Precipitation and most dense clouds, particularly if found at high altitude, can
+Although microwave channels are less affected by cloud contamination, precipitation and most dense clouds, particularly if found at high altitude, can
 still affect measured radiances around 183\,GHz
@@
 
-The main motivation for introducing 183\,GHz channels in operational sensors is
+Another motivation necessitating the need for cloud clearing is usage of 183\,GHz channels in 
 numerical weather prediction (NWP). Usage of passive microwave data by
@@
 but 183\,GHz data are still mainly used in a clear sky fashion
-\citep{geer2018all}. The later is particularly true in NWP of regional scope
+\citep{geer2018all}. The latter is particularly true in NWP of regional scope
 \citep{gustafsson2018survey}, all-sky assimilation of 183\,GHz at many national
-weather agencies will likely not be reached in many years. Anyhow, the cloud
-filtering applied differs between NWP centres. One approach is to make use of a
-``scattering index'' \citep{bennartz2002precipitation}, based on the
-observations alone. Today, likely more common is to use ``observation minus
-background'' (O-B), where the forecast model is used to obtain an estimate of
-the expected clear-sky value and the observation is rejected if the deviation
-exceeds some threshold (???). In both cases, the filtering typically involves
-observations around 89 and/or 150\,GHz.
-
-Despite the broad usage these filtering methods have some drawbacks. For
-183\,GHz, the impact of hydrometeors systematically causes a decrease in the
-observed radiance (maybe with exceptions at extremely dry conditions), see
-e.g.\ \citet{barlakas:three:20} and below. This means that if any cloud
-contamination is missed by the filtering this will cause a negative bias in
-mean radiance, compared to the true clear-sky mean. This bias will translate to
-a bias in humidity after the retrieval or assimilation. The alternative is to
-apply a very strict filtering, but this will result in that a high fraction of
-actually clear-sky values will be rejected, i.e.\ an important loss of useful
-data.
-
-The filtering is normally done in a ``one for all'' manner, i.e.\ all 183\,GHz
-channels are either kept or rejected, while, as the channels differ in their
-altitude coverage, there could be cloud impact in some channels and still the
-others can be considered as clear-sky. To allow a channel specific filtering,
-data likely need to be combined in a more complex manner than simple
-differences, but it is unclear what type of regression that would be best. This
-points towards applying machine learning, as used by e.g.\
-\citet{favrichon2019detecting}.
-
-A maybe less obvious problem is the uncertainty to assign to the filtered
-values. To our best knowledge, so far only estimates of mean and worst case
-errors have been provided. Some cases with relatively high cloud impact will
-likely be missed, while most cases are clear sky from start. As the remaining
-cloudy cases can cause significant biases, the likely solution is to apply a
-quite conservative (high) error estimate. However, this will unnecessary
-downgrade the value of the truly clear sky cases and the observations are used
-in a non-optimal manner.
+weather agencies will likely not be reached in many years.
+Anyhow, both clear-sky and all-sky assimilation require identification of cloud affected observations.
+``Scattering index'' \cite{geer2015scatteringindex} is one of the approaches used.
+It is based on brightness temperature differences between 89 and 150\,GHz.
+Another commonly used cloud filtering method is based on ``observation minus background'' (O-B), where the forecast model is used to obtain an estimate of the expected clear-sky value and the observation is rejected if the deviation exceeds some threshold \citep{English1999clouddetection}.
+
+Despite their broad usage, these filtering methods aim at partial removal of cloud contamination.
+The residual cloud impact can have some drawbacks.
+For 183\,GHz, the impact of hydrometeors systematically causes a decrease in the observed radiance (maybe with exceptions at extremely dry conditions), see
+e.g.\ \citet{barlakas:three:20} and below.
+This implies that if any cloud contamination is missed by the filtering this will cause a negative bias in mean radiance, compared to the true clear-sky mean.
+This bias will translate to a bias in humidity after the retrieval or assimilation.
+For NWP systems assimilating clear-sky observations, the effect of undetected clouds is overcome by inflating the observational errors.
+However this artificial suppression of observations diminishes the impact of observations.
+The alternative is to apply a very strict filtering, but this will result in that a high fraction of
+actually clear-sky values will be rejected, i.e.\ an important loss of useful data.
+Another limitation of existing clearing approaches is their ``one for all'' approach, i.e.\ observations in all 183\,GHz channels are either kept or rejected.
+This often rejects more observations than needed, as the channels differ in their altitude coverage.
+An observation could be cloudy in some channels and still the be clear-sky in others.
+To allow a channel specific filtering, data likely need to be combined in a more complex manner than simple differences, but it is unclear what type of regression that would be best.
+This points towards applying machine learning, as used by e.g.\ \citet{favrichon2019detecting}.
+A maybe less obvious problem is the uncertainty to assign to the filtered values.
+To our best knowledge, so far only estimates of mean and worst case errors have been provided.
+Some cases with relatively high cloud impact will likely be missed, while most cases are clear sky from start.
+As the remaining cloudy cases can cause significant biases, the likely solution is to apply a quite conservative (high) error estimate.
+However, this will unnecessary downgrade the value of the truly clear sky cases and the observations are used in a non-optimal manner.
 
@@
 measurements (no ``background'' data involved). Not only a best estimate is
-provided, but also a case specific uncertainty.
-
-This information can be used as a pure filter, by rejecting data where the
-correction exceeds some threshold value. This threshold value should be
+provided, but also a case specific uncertainty. This information can be used as a pure filter, by rejecting data where the correction exceeds some threshold value. This threshold value should be
 relatively low, to not introduce a bias in filtered dataset. However, even
 better is to replace the original value with the predicted NFCS value when
-forming the clear-sky dataset. This approach we denote as cloud correction. It
+forming the clear-sky dataset. We denote this approach as cloud correction. It
 is shown below that a basically bias free cloud correction can be obtained.
@@
 and instead gives a description of the posterior uncertainty. More precisely,
-QRNN outputs an user specified set of percentiles that gives a discrete
-description posterior distribution, that can be process to derive e.g.\ the
+QRNN outputs an user specified set of quantiles that gives a discrete
+description posterior distribution, that can be processed to derive e.g.\ the
 expectation value.
 
-The approach is demonstrated on a combination of 183\,GHz channels (following
-\citet{buehler:aclou:07}), but we mainly explore the cloud correction (of
+The approach is demonstrated with use of 89 and 150\,GHz channels (following
+\citet{geer2015scatteringindex}), but we mainly explore the cloud correction (of
 183\,GHz data) that will be possible when sub-millimetre data will be at hand
@@
 Imager (ICI, \citet{eriksson:towar:20}), but likely also be included in several
-smaller missions (such as AWS, presented below). \todo{Explain what sub-mm can
-  do}.
-
-The focus on ICI is motivated by several reasons. The true potential of the
-QRNN cloud correction approach is likely not revealed if tested on existing
+smaller missions (such as AWS, presented below).
+The focus on sub-mm channels is motivated by several reasons.
+Firstly, the higher frequencies have a higher sensitivity to scattering effects from smaller hydrometeors.
+For high altitude cirrus clouds, the these frequencies have a stronger signal than 183\,Ghz.
+In some cloudy situations it could be possible that the impact at 183 GHz is of the order of thermal noise and modelling uncertainties, while the impact at 325 GHz is significantly higher.
+Secondly, the true potential of the QRNN cloud correction approach is likely not revealed if tested on existing
 data and applying ICI data for cloud filtering has not earlier been discussed.
-It is also argued that the cloud correction makes it possible to make good use
-of ICI data already in clear-sky assimilation, a fact that should speed up the
-use of this novel data source.
-
+It is also argued that the cloud correction makes it possible to make good use of ICI data already in clear-sky assimilation, a fact that should speed up the use of this novel data source.
+
+A description of data and QRNN is provided in Sect.\ref{data_methods}.
+In Sect.~\ref{qrnn_mwhs} we demonstrate the applicabity of correction scheme to existing sensors, and later its application is extended to include sub-mm channels (Sect.\ref{qrnn_ici}).
+The results are discussed in Sect.~\ref{discussions}, and Sect.~\ref{conclusions} presents the conclusions from this work and the future outlook.
 \section{Data and methods}
+\label{data_methods}
 %
@@
 	\item QRNN-all: In this configuration, all-sky brightness temperatures from all available 183\,GHz channels are included in the training input.
-Just like QRNN-single, data from other non-humidity channels and additional data are also taken into account, but the main difference is the concurrent utilisation of all 183\,GHz frequencies.
+Just like QRNN-single, data from other non-humidity channels and additional data are also taken into account; but the main difference is the concurrent utilisation of all 183\,GHz frequencies.
 \end{enumerate}
 
-For all three sensors described in this study, one or both of the above QRNN configurations are used. The selection of input channels is sensor dependent and is described in detail when introduced.
+For all three sensors described in this study, one or both of the above QRNN configurations are used.
+The selection of input channels is sensor dependent and is described in detail when introduced later.
 
@@
 The predicted error is deviation of a random sample drawn from the posterior distribution to its median.
-In this study, we analyse both calibration plot and predicted errors to assess the correctness of predicted uncertainties.
+In this study, we analyse both the calibration plot and the predicted errors to assess the correctness of predicted uncertainties.
 
@@
 \section{Correcting cloud affected data in MWHS-2}
+\label{qrnn_mwhs}
 %
@@
 In order to formulate and test the correction approach, multiple QRNN experiments are performed for MWHS-2 channel 14.
-Later the methodology is expanded to other 183\,GHz channels.
+Later the methodology is extended to other 183\,GHz channels.
 A brief comparison of the results is also made against existing cloud filtering methods.
@@
 In ECMWF NWP system, the differences between the observations of these two window channels (Scattering Index) \citep{Lu2015FY3C} are used to identify the cloud affected data for ATMS, MHS and MWHS-2.
-To investigate the potential impact of these two window channels in QRNN based cloud correction, the configuration QRNN-single is applied to predict cloud free radiances.
-In this experiment, the training input includes all-sky brightness temperatures from target 183\,GHz channel, 89\,GHz and 150\,GHz.
+To investigate the potential impact of these two window channels in QRNN based cloud correction, the configuration QRNN-single is applied.
+In this experiment, the training inputs include all-sky brightness temperatures from target 183\,GHz channel, 89\,GHz and 150\,GHz.
 Both 89 and 150\,GHz are window channels so the land sea mask is also included as a training input.
@@
 	\item The third experiment is designed to assess the exclusive impact of 150\,GHz in cloud correction.
-This experiment is motivated by the fact that hydrometeor impact at 150\,GHz is stronger as compared to 89\,GHz, and is less affected by surface emissivity.
+This experiment is motivated by the fact that hydrometeor impact at 150\,GHz is strongest as compared to 89\,GHz and other 118\,GHz channels; and is less affected by surface emissivity.
 In this experiment, QRNN-single is trained with brightness temperatures from 150\,GHz along with the target channel and land/sea mask.
@@
 With QRNN-all, we investigate if additional humidity channels in the training process can improve the performance.
-It should be noted that though the training inputs are same for each 183\,GHz channel, the output is the target 183\,GHz channel; thus each channel still needs to be trained separately.
+Note that though the training inputs are same for each 183\,GHz channel, the output is the target 183\,GHz channel; thus each channel still needs to be trained separately.
 Land/sea mask is also included in the training.
@@
 		\middlehline
-		bias     &  0.00 &  -0.84 & -0.09 & -0.08(3.3\%) & -0.04 & -0.03(3.4\%) & -0.09 & -0.09(3.2\%) & -0.09(3.3\%) & -0.08(3.3\%)  \\
-		mae      &  0.80 &   1.45 &  0.88 &  0.86 &  0.89 &  0.87 &  0.89 &  0.87 &  0.62 &  0.59\\
-		std      &  1.00 &   3.90 &  1.19 &  1.14 &  1.19 &  1.15 &  1.21 &  1.16 &  0.90 &  0.83\\
+		Bias      &  0.00 &  -0.84 & -0.09 & -0.08(3.3\%) & -0.04 & -0.03(3.4\%) & -0.09 & -0.09(3.2\%) & -0.09(3.3\%) & -0.08(3.3\%)  \\
+		MAE       &  0.80 &   1.45 &  0.88 &  0.86 &  0.89 &  0.87 &  0.89 &  0.87 &  0.62 &  0.59\\
+		STD       &  1.00 &   3.90 &  1.19 &  1.14 &  1.19 &  1.15 &  1.21 &  1.16 &  0.90 &  0.83\\
 		skewness & -0.00 & -14.34 & -1.11 & -0.93 & -1.00 & -0.84 & -0.88 & -0.98 & -1.58 & -1.62\\
@@
 
-Fig.~\ref{fig:distribution_predicted_mwhs14} shows the distribution of QRNN predictions obtained from QRNN.
-The predicted values are able to remove most of the low brightness temperature cases, and overall a good match with the NFCS simulations is observed.
-QRNN is unable to predict the lowest clear-sky brightness temperatures, and cases with brightness temperatures around 260\,K occur frequently.
-The corresponding error statistics(Sect.~\ref{sec:validation}) are displayed in  Table~\ref{tab:error_statistics_mwhs_14}.
-In the uncorrected data, cloud impact causes a large negative skewness(-14.34) in the error distribution and the corresponding bias is -0.84\,K.
-Training QRNN with 89 and 150\,GHz removes a part of the cloud impact and reduces the bias to -0.09\,K, and the skewness is -1.11.
-The MAE and STD are also reduced.
+Fig.~\ref{fig:distribution_predicted_mwhs14} shows the distribution of point estimates obtained from QRNN.
+The predicted values are able to correct most of the low brightness temperature cases, and overall a good match with the NFCS simulations is observed.
+However, QRNN is unable to predict the lowest clear-sky brightness temperatures, and cases with brightness temperatures around 260\,K occur frequently.
+The corresponding error statistics(see Sect.~\ref{sec:validation}) are displayed in  Table~\ref{tab:error_statistics_mwhs_14}.
+In the uncorrected data, the negative departures due to cloud impact lead to a large negative skewness(-14.34) and high bias (-0.84\,K).
+Training QRNN with 89 and 150\,GHz successfully corrects a major portion of the cloud affected cases, and the bias is reduced to -0.09\,K.
+However, high skewness values indicate a negative tail or uncorrected departures.
 Including 118\,GHz in the training, gives comparable results as 89+150\,GHz.
@@
 
-Further we investigated that if filtering the predictions with low accuracy could help in improving the error distribution.
+Further we investigated that if filtering the predictions with low accuracy could help in improving the error distributions.
 For filtering such cases, we assume that predictions with cloud correction greater than 5\,K are cases associated with large deviations.
 In all three experiments, removing the cases with correction greater than 5\,K removes around 3\% of the data, but only a marginal positive impact on the accuracy is observed.
-With 5\,K threshold though the cases with high errors are removed, the negative skewness indicates presence of cases with residual cloud impact.
+With 5\,K threshold though the cases with high errors are removed, the persistent negative skewness indicates presence of cases with residual cloud impact.
 Choosing a lower threshold can help in removing more partially corrected cases but at the cost of rejecting clear-sky cases.
@@
 In spite of the fact that QRNN only provides a partial cloud correction, the results for  MWHS-2 channel 14 are comparable to what we achieve with existing cloud filtering techniques like scattering index (SI)  \citep{geer2015scatteringindex} and the filtering scheme by \citet{buehler:aclou:07}.
-SI uses the differences of brightness temperatures between 89 and 150\,GHz to identify cloud affected data.
-While in the study by \citet{buehler:aclou:07}, they use brightness temperature based threshold to filter out cloudy cases.
+SI uses the differences of brightness temperatures between 89 and 150\,GHz to identify cloud affected data, whilst in the study by \citet{buehler:aclou:07}, they use brightness temperature based threshold to filter out cloudy cases.
 They recommend a viewing angle dependent brightness temperature threshold at $183.31\pm1.00$ \,GHz and brightness temperature difference between $183.31\pm3.00$ and $183.31\pm 1.00$ as a measure of cloud impact.
-Further in the text we refer this scheme as ``B183''.
+Further in the text we refer this filter as ``B183''.
 The results obtained with SI and B183 are displayed in Table~\ref{tab:SI_statistics}.
@@
 Even though QRNN-all gives slightly better prediction accuracy, its inherent construction makes it crucial to examine the correlation between observed errors.
-Fig~\ref{fig:correlations_mwhs} illustrates the correlation matrix for both QRNN-all and QRNN-single.
+Fig.~\ref{fig:correlations_mwhs} illustrates the correlation matrix for both QRNN-all and QRNN-single.
 For clear cases, the observed errors (noise) in QRNN-single are uncorrelated between the five channels.
@@
 		\middlehline
-		Channel 11  &   bias     & 0.00 &  -0.16 & -0.03 & -0.03(0.2\%)  \\
-				    &	mae      & 0.80 &   0.89 &  0.79 &  0.79  \\
-					&	std      & 1.00 &   1.71 &  1.03 &  1.01  \\
+		Channel 11  &   Bias      & 0.00 &  -0.16 & -0.03 & -0.03(0.2\%)  \\
+				    &	MAE       & 0.80 &   0.89 &  0.79 &  0.79  \\
+					&	STD       & 1.00 &   1.71 &  1.03 &  1.01  \\
 					&	skewness & 0.01 & -20.18 & -0.68 & -0.45  \\
 		\middlehline
-		Channel 12  & bias     & -0.00 &  -0.28 & -0.05 & -0.05(0.6\%)  \\
-					& mae      &  0.80 &   0.98 &  0.81 &  0.80  \\
-					& std      &  1.00 &   2.26 &  1.07 &  1.05  \\
+		Channel 12  & Bias      & -0.00 &  -0.28 & -0.05 & -0.05(0.6\%)  \\
+					& MAE       &  0.80 &   0.98 &  0.81 &  0.80  \\
+					& STD       &  1.00 &   2.26 &  1.07 &  1.05  \\
 					& skewness &  0.00 & -20.72 & -0.91 & -0.70  \\
 		\middlehline
-		Channel 13  & bias     & -0.00 &  -0.52 & -0.08 & -0.07(1.6\%)  \\
-					& mae      &  0.80 &   1.17 &  0.84 &  0.83  \\
-					& std      &  1.00 &   3.04 &  1.13 &  1.10  \\
+		Channel 13  & Bias      & -0.00 &  -0.52 & -0.08 & -0.07(1.6\%)  \\
+					& MAE       &  0.80 &   1.17 &  0.84 &  0.83  \\
+					& STD       &  1.00 &   3.04 &  1.13 &  1.10  \\
 					& skewness &  0.02 & -17.85 & -1.14 & -0.98 \\		
 		\middlehline
-		Channel 15  & bias     & -0.00 &  -1.28 & -0.07 & -0.06(5.6\%)  \\
-					& mae      &  0.80 &   1.87 &  0.97 &  0.92 \\
-					& std      &  1.00 &   5.08 &  1.35 &  1.25 \\
+		Channel 15  & Bias      & -0.00 &  -1.28 & -0.07 & -0.06(5.6\%)  \\
+					& MAE       &  0.80 &   1.87 &  0.97 &  0.92 \\
+					& STD       &  1.00 &   5.08 &  1.35 &  1.25 \\
 					& skewness & -0.00 & -11.15 & -0.60 & -0.83  \\ 
@@
 			\cline{2-11}
-		bias &-0.05	&-0.08	&-0.07&	-0.13&-0.14	&-0.24	&-0.23&	-0.4&-0.34&	-0.59\\
-		mae  & 0.81	&0.84	&0.82 &	0.88 &	0.85&0.95   &0.92 &	1.07&1.03 &	1.25\\
-		std  &1.02	&1.22	&1.04 &	1.52 &	1.1	& 2.0	&1.25 &	2.54&1.53&	3.25\\
+		Bias &-0.05	&-0.08	&-0.07&	-0.13&-0.14	&-0.24	&-0.23&	-0.4&-0.34&	-0.59\\
+		MAE   & 0.81	&0.84	&0.82 &	0.88 &	0.85&0.95   &0.92 &	1.07&1.03 &	1.25\\
+		STD   &1.02	&1.22	&1.04 &	1.52 &	1.1	& 2.0	&1.25 &	2.54&1.53&	3.25\\
 		\bottomhline		
@@
 The MAE is approximately 17\% lower after correction, but still the negative skewness is not removed completely.
-For channel 13 and 15 also a similar performance is seen.
-But in the latter, error distributions are most symmetric as compated to other four channels.
-The skewness is only -0.60.
+For channel 13 and 15 also, a similar performance is seen.
+But in the latter, error distributions are most symmetric but with largest spread as compared to other four channels.
 
@@
 For channels 13 and 15, the error statistics obtained with SI are slightly inferior.
-The filtering with B183 is also partial for all channels......\todo{can we say they are unsatisfactory?}
+The filtering with B183 is also partial for all channels, but is poorer than SI.
 
 \subsection{Prediction uncertainty}
-
+\label{sec:uncertainty_mwhs}
 \begin{figure}[t]
@@
 The quantiles given out by QRNN can be used to construct the probability distribution of the predictions in contrast to other correction approaches which give out only point estimates.
-An example of the uncertainties given out by QRNN is shown in Fig~\ref{fig:prediction_uncertainty_mwhs}.
+An example of the uncertainties given out by QRNN is shown in Fig.~\ref{fig:prediction_uncertainty_mwhs}.
 The predictions over quantiles $-3\sigma$, $-2\sigma$ and $-1\sigma$ are quite sharp and lie close to the median value.
@@
 
-The calibration of the prediction intervals on the testing dataset is displayed in Fig~\ref{fig:calibration_mwhs}.
-For the entire testing dataset, the predictions follow the y=x line, i.e.
-they are perfectly calibrated with the priori distribution.
-However for all cases with correction greater than 5\,K, the distribution is poorly calibrated.
-In this case, the calibration curve lies below the y=x line indicating that the prediction intervals are too narrow.
-However since such cases are few and filtering them out results in well calibrated QRNN predictions.
+The calibration of the prediction intervals on the testing dataset is displayed in Fig.~\ref{fig:calibration_mwhs}.
+For the entire dataset, the predictions follow the y=x line, i.e.
+they are perfectly calibrated with the a priori distribution.
+However for the cases with correction greater than 5\,K, the distribution is poorly calibrated for higher quantiles.
+The curve lies below the y=x line indicating that the prediction intervals are too narrow.
+This is in agreement with the wide spread of predictions over the  higher quantiles (Fig.~\ref{fig:prediction_uncertainty_mwhs}).
+However such cases are few and filtering them results in well calibrated QRNN predictions.
 
 Further, we analyse if the  predicted errors obtained from QRNN are representative of observed errors.
-Fig~\ref{fig:predicted_errors_mwhs} illustrates the predicted and observed errors for MWHS-2 channel 14.
-The predicted errors are slightly overestimated for negative values, but overall the predicted errors from the QRNN posterior distribution have a good match with the observed errors.
+Fig.~\ref{fig:predicted_errors_mwhs} illustrates the predicted and observed errors for MWHS-2 channel 14.
+The predicted errors are slightly overestimated for negative values, but overall the predicted errors from the QRNN posterior distribution and the observed errors have a good match.
 This is in agreement with the perfect calibration seen in Fig.~\ref{fig:calibration_mwhs}.
@@
 \section{Correcting cloud affected data using sub-mm frequencies}
+\label{qrnn_ici}
 In this section, we demonstrate that sub-mm channels can be used to formulate the cloud correction of data measured around 183\,GHz.
@@
 The results are presented in context of different sensors.
-Furthermore, the case specific uncertainties predicted by QRNN are also discussed.
+Furthermore, the case specific uncertainties are also discussed.
 
@@
 	\item In the first experiment, we apply QRNN-single configuration for cloud correction at three ICI humidity channels.
-In this case, the training data is the target 183\,GHz channel and all available ICI sub-mm frequencies (325\,GHz, 448\,GHz and 664\,GHz).
+In this case, the training data is the target 183\,GHz channel and all available ICI sub-mm frequencies (325\,GHz, 448\,GHz and 664\,GHz) with vertical polarisation.
 No other data are included in the training process.
@@
 QRNN was trained five times for each 183\,GHz channel as target.
+Note that for this experiment, AWS was chosen due to availability of four 325\,GHz channels and five 183\,GHz channels.
 \end{enumerate}
@@
 	\includegraphics[width=\textwidth]{Figures/error_distribution_QRNN-single.pdf} 
-	\caption{Error distributions for deviations predicted data to NFCS simulations.
+	\caption{Error distributions for deviations of point estimates to NFCS simulations.
 The results are from QRNN-single and channels I1V, I2V and I3V.
@@
 \begin{table*}[t]
-	\caption{ Error statistics for deviations predicted data to NFCS simulations. 
+	\caption{ Error statistics for deviations of point estimates to NFCS simulations. 
 		The values for Bias, mean absolute error(MAE), standard deviation(STD), and measure of skewness(Skewness) are shown.
@@
 
-		I1V&  bias     &  0.00 & -1.87 & -0.02 & -0.00(6.1\%)  \\
-		&mae      &  0.64 &  2.32 &  0.70 &  0.60   \\
-		&std      &  0.80 &  8.84 &  1.06 &  0.79   \\
+		I1V&  Bias      &  0.00 & -1.87 & -0.02 & -0.00(6.1\%)  \\
+		&MAE       &  0.64 &  2.32 &  0.70 &  0.60   \\
+		&STD       &  0.80 &  8.84 &  1.06 &  0.79   \\
 		&skewness & -0.01 & -8.10 & -1.51 & -0.64  \\
 		\middlehline
-		I2V & bias     & 0.00 &  -1.04 &  0.00 &  0.01(3.6\%)  \\
-		&mae      & 0.64 &   1.53 &  0.57 &  0.51 \\
-		&std      & 0.80 &   5.95 &  0.86 &  0.65 \\
+		I2V & Bias      & 0.00 &  -1.04 &  0.00 &  0.01(3.6\%)  \\
+		&MAE       & 0.64 &   1.53 &  0.57 &  0.51 \\
+		&STD       & 0.80 &   5.95 &  0.86 &  0.65 \\
 		&skewness & 0.00 & -10.79 & -1.85 & -0.22  \\
 		\middlehline	
-		I3V & bias     & 0.01 &  -0.63 &  0.02 &  0.02(2.2\%)  \\
-		&mae      & 0.64 &   1.15 &  0.54 &  0.50  \\
-		&std      & 0.80 &   4.27 &  0.80 &  0.63  \\
+		I3V & Bias      & 0.01 &  -0.63 &  0.02 &  0.02(2.2\%)  \\
+		&MAE       & 0.64 &   1.15 &  0.54 &  0.50  \\
+		&STD       & 0.80 &   4.27 &  0.80 &  0.63  \\
 		&skewness & 0.01 & -13.37 & -1.51 & -0.13  \\
@@
 The standard deviation of the resulting dataset is only 0.65\,K as compared to 0.80\,K from noise.
-The reduction in the variability is also evident in the Fig~\ref{fig:error_distributions}, where the peak of distributions is sharper.
+The reduction in the standard deviation is also evident in the Fig.~\ref{fig:error_distributions}, where the peak of distributions is sharper.
 In comparison to I1V and I2V, I3V has the lowest fraction of the measurements with significant cloud impact.
@@
 
-Similar to evaluation of uncertainty estimates for MWHS-2(Sect.~\ref{sec:}), we analyse the spread of predicted quantiles, their calibration and distribution of predicted errors.
+Similar to evaluation of uncertainty estimates for MWHS-2 (Sect.~\ref{sec:uncertainty_mwhs}), we analyse the spread of predicted quantiles, their calibration and distribution of predicted errors.
 
 Fig.~\ref{fig:prediction_uncertainty_I2V} shows the spread of prediction uncertainties over different quantiles for randomly chosen 1500 cases.
-The large spread in the predicted errors indicates that QRNN is successful in representing uncertainties for each case individually, rather than expressing them as a single measure for all cases.
+The large spread in the predicted errors indicates that QRNN is successful in representing uncertainties for each case individually, rather than expressing them as a single measure.
 In the latter case, the uncertainty estimates would be concentrated along a narrow interval.
@@
 
-Fig.~\ref{fig:calibration_I1V} shows the calibration of the prediction intervals for I1V.
+Fig.~\ref{fig:calibration_I1V} shows the calibration of the prediction intervals for I2V.
 The predictions for the complete test dataset are well calibrated and follow the y=x line.
-This shows that the training and test datasets come from the same a priori distribution.
 On the other hand, when only the cases with  cloud correction greater than 10\,K are considered, the predictions in all the intervals are poorly calibrated.
-In this case the calibration curve lies slightly below the y=x line, indicating that the predicted intervals are too narrow, or the uncertainty is underestimated.
+In this case the calibration curve lies slightly below the y=x line for higher quantiles, indicating that the predicted intervals are too narrow, or the uncertainty is underestimated.
 
 Fig.~\ref{fig:predicted_errors} shows the comparison of observed errors (prediction accuracy) to predicted errors.
-The predicted and observed errors have good agreement for the peak of the distribution, but the predicted errors are spread out asymmetrically.
-QRNN is not able to completely represent the wings of the distribution.
-This could also be a sampling issue, as the high errors we try to predict constitute a very small part of the complete dataset and we do not derive any sample from outside $\pm3\sigma$.
+The predicted and observed errors mostly have a good agreement but the predicted errors are spread out more asymmetrically towards the negative departures.
+QRNN is also not able to completely represent the wings of the distribution.
+This could also be a sampling issue, as the high errors we try to predict constitute a very small part of the complete dataset.
+Note that since we do not derive any sample from outside $\pm3\sigma$, such cases could also belong to 0.003\% population not represented by the quantiles.
 
 With AWS, the behaviour of predicted uncertainties is observed to be similar as for ICI (not shown).
-However, the relation between the mean uncertainty estimate and cloud impact is displayed in Fig~\ref{fig:uncertainty_cloud_impact}.
+However, the relation between the mean uncertainty estimate and cloud impact is displayed in Fig.~\ref{fig:uncertainty_cloud_impact}.
 For all five channels, the predictions with small or relatively low cloud signal have a low uncertainty or in other words have high sharpness.
@@
 Cases with accurate predictions yet high uncertainty are also present.
-In spite of individual variations in the error distributions for each channel, predictions and their corresponding uncertainties followed the same relationship.
+In spite of individual variations in the error distributions for each channel, predictions and their corresponding uncertainties follow the same relationship.
 Similar results were also obtained with AWS(not shown).
@@
 \section{Discussion}
+\label{discussions}
 
@@
 Among several input channel combinations described for QRNN-single, the performance of combination 89+150\,GHz is observed to be optimal.
-The positive performance with 150\,GHz is not unexpected, as 150\,GHz is highly sensitive to ice hydrometeors and cloud water.
-But using 89\,GHz along with 150\,GHz gives a slightly better performance.
+The positive performance with 150\,GHz is not unexpected, as 150\,GHz is highly sensitive to ice hydrometeors and cloud water; but using 89\,GHz along with 150\,GHz gives a slightly better performance.
 The channel 89\,GHz is affected by surface emissivity and is relatively less sensitive to cloud water content, however its sensitivity to warm clouds in the lower troposphere could be important.
@@
 These channels provide complementary information to humidity channels in the lower troposphere.
-Including both these channels in the training process had no significant effect on the prediction accuracy and almost similar performance as with the combination 89+150\,GHz is obtained.
+Including both these channels in the training process had no additional effect on the prediction accuracy and almost similar performance as with the combination 89+150\,GHz is obtained.
+
+Even though the cloud correction is partial, the performance is comparable or better to existing cloud filtering techniques like SI and scheme by \cite{buehler:aclou:07}.
+Note that both these techniques are a one for all approach for each 183\,Ghz channel; thus if one observation is classified as cloudy by the filter, it is removed in all humidity channels.
+This increases the probability of erroneously removing clear observations.
+For high peaking channels of MWHS-2, both SI and QRNN give almost similar results, but with almost 30\% rejection rate.
+On the other hand, for low peaking channels, SI gives less accurate results than QRNN, as these channels have a stronger hydrometeor impact.
+This clearly indicates, that a channel specific approach like QRNN is more appropriate, and gives better performance.
 
@@
 Due to missing complementary information from other channels in the upper troposphere, QRNN fails at predicting these cases accurately.
-Such cases mostly represent the thin cirrus clouds, which have very small influence at 89 and 150\,GHz.
+Such cases are mostly associated with thin cirrus clouds, which have very small influence at 89 and 150\,GHz.
 Without additional information from other channels we cannot expect QRNN train better.
 Among the other available channels, the overlapping weighting functions of 183\,GHz can provide auxiliary information to train QRNN.
-Results show that these channels can help in improving the training, the non-orthogonal information introduces highly correlated observational errors.
-The residual cloud amount for different channels depends upon each other in a systematic way, but since QRNN-single does not have access to this information, the correlations are low.
-On the other hand, with QRNN-all, when all 183\,GHz channels are used simultaneously the predictions learn positively from the common information but also introduces high correlations between overlapping channels.
-Correlated errors can be undesirable for DA systems, but in future if the operational centres progress with approaches dealing with correlated observation errors, concurrent use of  89, 150 and 183\,GHz channels would give the best cloud correction performance.
-
-Even though the cloud correction is partial, the performance is comparable or better to existing cloud filtering techniques like SI and scheme by \cite{buehler:aclou:07}.
-Note that both these techniques are a one for all approach for each 183\,Ghz channel; thus if one observation is classified as cloudy by the filter, it is removed in all humidity channels.
-This increases the probability of erroneously removing clear observations.
-For high peaking channels of MWHS-2, both SI and QRNN give almost similar results, however with almost 30\% rejection rate.
-On the other hand, for low peaking channels, the same rejection criteria, SI gives less accurate results than QRNN, as these channels have a stronger hydrometeor impact than channels 11 and 12.
-This clearly indicates, that a channel specific approach like QRNN is more appropriate, and gives better performance.
+Results show that these channels indeed help in improving the training, yet the non-orthogonal information introduces highly correlated observational errors.
+The correlations for cloudy observations are not surprising as the cloud amount for different channels depends upon each other in a systematic way.
+However for clear-sky observations, the observational noise must be uncorrelated between the channels.
+This is observed to be true with QRNN-single, but QRNN-all fails at preserving the noise stochasticity.
+In the absence of hydrometeor impact, all 183\,GHz channels provide same information to the learning model, introducing redundancy.
+Redundant patterns in machine learning models often have undesirable effect on the predictive performance.
+In our application, redundant information does not affect the prediction accuracy, but introduces highly correlated noise between channels.
+Correlated errors are also undesirable for DA systems, but in future if the operational centres progress with approaches dealing with correlated observation errors, concurrent use of 89, 150 and 183\,GHz channels would give the best cloud correction performance.
 
@@
 The calibration plot and distribution of predicted errors show that  QRNN predictions are able to represent the a priori distribution.
-However we also observe that cases with high errors are poorly calibrated.
-The poor calibration predictions associated with low accuracy is a consequence of different underlying a priori distribution.
+However we also observe that cases with high errors are generally poorly calibrated.
+The poorly calibrated predictions are a consequence of a different underlying a priori distribution.
 Predictions with high error originate from cases with high cloud impact.
-Such cases have a significantly distinct a priori distribtion as compared to clear cases, which dominate the training dataset, and influence the a priori information.
+Such cases have a significantly distinct a priori distribtion as compared to clear cases, which dominate the training dataset and influence the a priori information.
 Additional information in form of more observational data or additional training inputs is required to improve QRNN prediction accuracy for such cases.
@@
 For channel I1V, a slightly lower accuracy is observed due to relatively higher number of cases with residual cloud impact.
-The accuracy is improved by activating the correction filter, but some effect of residual cloud impact is apparent in the high negative skewness.
-Interestingly, reducing the correction threshold further has no significant effect on flagging these residual cases; in fact only the clear-sky cases are removed.
-This indicates that for I1V, QRNN is unsuccessful in correcting these cases completely.
+The accuracy is improved by activating the correction filter, but some effect of residual cases is still apparent.
+Interestingly, reducing the correction threshold further has no significant effect on flagging these residual cases.
+In fact only the clear-sky cases are removed.
+This is a consequence of the correction being too low.
+Since such cases introduce a small negative bias and skewness, they are more appropriately related to low-cloud impact.
 Compared to other two higher peaking channels, I1V is more sensitive to the effect of hydrometeors  and contamination from surface effects.
 The cases with surface contamination are also localized and seasonal.
-For QRNN to predict such cases accurately, QRNN should have access to complementary information from sub-mm channels.
-However, the weighting functions of sub-mm channels can provide only a partial coverage to the hydrometeor impact at I1V.
+The weighting functions of sub-mm channels can provide only a partial coverage to the hydrometeor impact at I1V.
 A part of lower troposphere sensed by I1V has almost zero coverage from sub-mm channels.
@@
 For AWS-32, the resulting error distributions have significantly lower spread than the measurements, but are still negatively skewed.
-This indicates that a single sub-mm channel like 325\,GHz is also sufficient enough for cloud correction at 183\,GHz.
+In spite of the slightly inferior performance for AWS-32, the high accuracy for other channels indicates that a single sub-mm channel like 325\,GHz is also sufficient enough for cloud correction at 183\,GHz.
 This is an important result as smaller satellites are limited by their size to measure all sub-mm wavelengths.
@@
 For clear-sky conditions, multiple observations of same scene from different channels can cancel out the noise.
-This effect is observed to be stronger in ICI observations than AWS, due to more number of input channels while training in the former.
-It should be noted that with satellite measurements, the spread of error distributions smaller than noise could be difficult to achieve due to other underlying uncertainties not considered here.
-However, symmetric error distributions with low spread could still be extremely important from the context of data assimilation.
-Most of the existing cloud filtering schemes eg.
-\citet{buehler:aclou:07} and SI \cite{geer2015scatteringindex} work well only at removing cases with high cloud impact.
-As a consequence of the residual cloud impact, the error distributions are highly skewed.
+This effect is observed to be stronger in ICI observations than AWS; due to more number of training inputs in the former.
+Note that with actual satellite measurements, the spread of error distributions smaller than noise could be difficult to achieve due to other underlying uncertainties not considered here.
+
+The symmetric and low spread error distributions is an important results from the DA perspective.
+Most of the existing cloud filtering schemes work well only at removing cases with high cloud impact, and as a consequence, the error distributions are highly skewed.
+To use these observations correctly data assimilation schemes often inflate their asymmetric error distributions at the cost of artificially suppressing the observational impact.
 This is not the optimal solution but the best which can be achieved with present sensors.
-To use these observations correctly data assimilation schemes often inflate their asymmetric error distributions at the cost of artificially suppressing the observational impact.
+However, the symmetric error distributions obtained from QRNN allow us to effectively more than 95\% of the data without the need for error inflation.
 
@@
 \section{Conclusion and outlook}  %% \conclusions[modified heading if necessary]
+\label{conclusions}
 %
@@
 In this study, a methodology based on quantile regression neural network (QRNN) is used for identifying and correcting the cloud contamination in operational humidity channels.
-QRNN is a neural network which trains on all-sky brightness temperatures from  channels containing orthogonal information to humidity channels, to estimate the noise free clear-sky (NFCS) radiances for humidity channels.
-The output is posterior distribution of the predictions over different quantiles.
+QRNN is a neural network which trains on all-sky brightness temperatures from  channels containing orthogonal information to humidity channels, to estimate the noise free clear-sky (NFCS) radiances.
+The output is the posterior distribution of predictions over different quantiles.
 QRNN is a channel specific approach, or in other words, QRNN is trained separately for each channel, and the cloud correction for each is independent of other channels.
@@
 The applicability of QRNN based correction to current sensors is demonstrated with MHWS-2 and it is shown that QRNN is partially successful in removing the cloud impact.
-This is not optimal solution, but it is in agreement with what can be achieved with the present instruments.
-As compared to existing clear-filtering approaches, QRNN gives comparable or better performance and with minimal rejection of data.
-In context of present sensors, the accuracy of QRNN is affected by one single limitation, that is, the prediction of ``out of distribution'' cases.
+This is not  an optimal solution, but it is in agreement with what can be achieved with the present instruments.
+In comparison to existing clear-filtering approaches, QRNN gives comparable or better performance and with minimal rejection of data.
+The accuracy of QRNN is affected by one single limitation, that is, the prediction of ``out of distribution'' cases.
 Correcting hydrometeor impact for cases where no complementary information is available is a challenge for QRNN and always limit its performance.
@@
 The predicted radiances have symmetric and narrow error distributions and for some channels the spread is smaller than the measurement noise.
-This makes it highly suitable for application to data assimilation systems.
+This makes it highly suitable for application to data assimilation (DA) systems.
 The robustness of sub-mm channels in cloud correction is also demonstrated with use of only 325\,GHz for cloud correction.
@@
 
-The biggest advantge of QRNN compared to other regression based approached is that its probabilistic nature.
+The biggest advantge of QRNN compared to other regression based approached is its probabilistic nature.
 The QRNN predictions over chosen quantiles are a measure of the accuracy at different probability levels.
-In comparison to deterministic correction approaches, the corrected radiances along with uncertainty estimates.
-\todo{incomplete}
-
-The high quality cloud corrected radiances have great potential in DA systems.
-Most DA systems reject upto 80\% of the available observations due to cloud contamination.
+In this study, the predicted quantiles given by QRNN work well in representing the accuracy of the point estimate.
+The point estimates with low error have high certainty.
+On the other hand, the incorrect incorrect predictions on out-of-distribution cases have low confidence.
+In comparison to deterministic correction approaches, the corrected radiances along with uncertainty estimates give additional benefit for DA systems.
+The statistical structures of underlying uncertainty are extremely important for DA systems as they offer a measure of reliability and robustness of observations.
+
+The high quality cloud corrected radiances have great potential in both retrieval schemes and  NWP systems.
+Even with availability of new sensors and better observations, the problems posed by undetected cloud impact limit the complete usage of humidity observations.
+However, with the cloud correction methodology presented here, we can aim at resolving these limitations.
+This is specially true for clear-sky assimilation systems, which reject upto 80\% of the available observations due to cloud contamination.
 The loss is largest in mid-latitudes.
 Although, NWP systems are gradually moving towards assimilating all-sky radiances but the use of data is overly cautious.
-Misrepresentation of clouds can deteriorate the model outputs.
-To improve the representivity of clouds in the models, the observational errors are inflated as a function of the cloud amount.
-Most NWP centres use partial cloud identification approaches.
-On the contrary, cloud cleared microwave radiances offer forecast benefits without additional complexities.
+Infact, one of reasons for the positive performance of all-sky assimilation systems is also attributed to larger number of assimilated observations in comparison to clear-sky observations.
+If QRNN can provide the clear-sky NWP systems, cloud cleared microwave radiances with minimal rejection of data, we can reap forecast benefits without  additional complexities and inflation of errors.
+The all-sky assimilation systems could also benefit indirectly from cloud corrected radiances.
+To improve the representivity of clouds in the all-sky NWP models, the observational errors are inflated as a function of the cloud amount.
+QRNN could be employed here just to provide a measure of cloud impact.
 Another advantage of combining 183\,GHz and sub-mm for cloud correction is that NWP systems, which are not yet prepared for higher frequency channels, could still benefit from the data early on.
+
+In this study, we demonstrate the correction scheme with data from a limited period.
+The seasonal and latitudinal distributions are not taken into account.
+It remains to be  analysed for if QRNN shows any seasonal sensitivity or dependency on cloud types.
+Such analysis could also be important at improving the a priori distribution of rare cases.
 
@@
 %
-**** Some parts copied directly from AWS report *****
 Cloudsat profiles during August 2015 were randomly selected for forward simulations.

### 2020-11-06 Article/ici_submm_cloudcorr.tex
included suggestions from Patrick

@@
 %\documentclass[amt]{copernicus}
+
+\sloppy
 
@@
 
-Identification of cloud affected observations is indispensable for both clear-sky and all-sky Numerical Weather Prediction (NWP) systems.
+Identification of cloud affected observations is indispensable for both clear-sky and all-sky numerical weather prediction (NWP) systems.
 In this study, we present a methodology to identify and correct the cloud impact in microwave humidity radiances.
 A channel specific quantile regression neural network (QRNN) based approach is formulated to estimate the posterior distributions of noise free clear sky (NFCS) radiances.
-The applicability of the approach is demonstrated by application to a present sensor: MWHS-2.
+The applicability of the approach is demonstrated by application to a present sensor: MWHS-2 (MicroWave humidity sounder 2).
 With the future outlook, the applicability to sub-millimeter (sub-mm) channels is also investigated.
@@
 On the other hand, when sub-mm observations from ICI are used to correct the cloud impact, QRNN can successfully correct most of the cases with cloud impact.
-Only 2-4\% of the cases are partially corrected and these can be easily removed by a simple filtering; and the resulting error distributions are almost symmetric with very low spread.
+Only 2-4\% of the cases are partially corrected and these can be easily removed by a simple filtering.
+The resulting error distributions are almost symmetric with very low spread.
 The methodology also works well when only one of the higher frequencies (325\,GHz) is available.
-Except for the lowest peaking channel, using sub-mm observations results in error distributions with standard deviation less than the measurement noise.
+Except for the lowest peaking channel, using sub-mm observations also results in error distributions with standard deviation less than the measurement noise.
 Another advantage of using QRNN is that predicted quantiles can be employed to quantify the case-specific uncertainty estimates.
 The results show that QRNN is successful in representing the uncertainty for each case individually.
-Despite individual variations for each channel, the predictions exhibit a higher uncertainty when the test data includes the ``out of distribution'' cases.
+Despite individual variations for each channel, the predictions exhibit a higher uncertainty when cloudy cases lack orthogonal information from other channels.
 In comparison to deterministic correction/filtering approaches, the high quality corrected radiances with uncertainty estimates have great potential to be used efficiently in assimilation systems.
@@
 
-Despite their broad usage, these filtering methods aim at partial removal of cloud contamination.
+Despite their broad usage, these filtering methods aim at partial removal of cloud contamination originating from high ice clouds.
 The residual cloud impact can have some drawbacks.
@@
 However this artificial suppression of observations diminishes the impact of observations.
-The alternative is to apply a very strict filtering, but this will result in that a high fraction of
-actually clear-sky values will be rejected, i.e.\ an important loss of useful data.
+The alternative is to apply a very strict filtering, but this increases the rejection of clear-sky values, i.e.\ an important loss of useful data.
 Another limitation of existing clearing approaches is their ``one for all'' approach, i.e.\ observations in all 183\,GHz channels are either kept or rejected.
@@
 This points towards applying machine learning, as used by e.g.\ \citet{favrichon2019detecting}.
-A maybe less obvious problem is the uncertainty to assign to the filtered values.
+A maybe less obvious problem is the assignment of uncertainty to the filtered values.
 To our best knowledge, so far only estimates of mean and worst case errors have been provided.
@@
 Imager (ICI, \citet{eriksson:towar:20}), but likely also be included in several
-smaller missions (such as AWS, presented below).
+smaller missions (such as Artic Weather Satellite (AWS); presented below).
 The focus on sub-mm channels is motivated by several reasons.
 Firstly, the higher frequencies have a higher sensitivity to scattering effects from smaller hydrometeors.
-For high altitude cirrus clouds, the these frequencies have a stronger signal than 183\,Ghz.
+For high altitude cirrus clouds, these frequencies have a stronger signal than 183\,Ghz.
 In some cloudy situations it could be possible that the impact at 183 GHz is of the order of thermal noise and modelling uncertainties, while the impact at 325 GHz is significantly higher.
-Secondly, the true potential of the QRNN cloud correction approach is likely not revealed if tested on existing
-data and applying ICI data for cloud filtering has not earlier been discussed.
+Secondly, the true potential of the QRNN cloud correction approach is likely not revealed if tested on existing data and applying ICI data for cloud filtering has not earlier been discussed.
 It is also argued that the cloud correction makes it possible to make good use of ICI data already in clear-sky assimilation, a fact that should speed up the use of this novel data source.
@@
 A description of data and QRNN is provided in Sect.\ref{data_methods}.
-In Sect.~\ref{qrnn_mwhs} we demonstrate the applicabity of correction scheme to existing sensors, and later its application is extended to include sub-mm channels (Sect.\ref{qrnn_ici}).
+In Sect.~\ref{qrnn_mwhs} we demonstrate the applicability of correction scheme to existing sensors, and later its application is extended to include sub-mm channels (Sect.\ref{qrnn_ici}).
 The results are discussed in Sect.~\ref{discussions}, and Sect.~\ref{conclusions} presents the conclusions from this work and the future outlook.
+
 \section{Data and methods}
@@
 MicroWave Humidity Sounder 2 (MWHS-2) is an instrument onboard FengYun-3C (FY-3C).
-MWHS-2 is designed to observe the distribution of global atmospheric thermodynamics information, and monitor the severe convective systems.
-It is a cross track scanning microwave radiometer and measures 15 frequencies in the range 89-191\,GHz.
+MWHS-2 a cross track scanning microwave radiometer and measures 15 frequencies in the range 89-191\,GHz.
 89\,GHz and 150\,GHz are window channels, five humidity sounding channels are centered at 183.31\,GHz and eight temperature sounding channels are centered at 118.75\,GHz oxygen absorption line.
-The five humidity sounding channels are similar to MWS (Micro Wave Sounder) and ATMS (Advanced Technology Microwave Sounder).
-As of December 2019, observations from MWHS-2 are routinely assimilated at ECMWF \citep{duncan2020MWHS}.
+The five humidity sounding channels are similar to ATMS.
+As of December 2019, observations from MWHS-2 are routinely assimilated at European Centre for Medium-Range Weather Forecasts (ECMWF, \citet{duncan2020MWHS}).
 The channels relevant to this study are described on Table~\ref{tab:specifications_MWHS2}.
@@
 Metop-SG is scheduled for launch in 2023, and it will make ICI the first operational sensor observing Earth using sub-millimeter(sub-mm) wavelengths.
-The main objective of ICI is to use high frequency channels for measuring ice cloud properties and improve the representation of ice clouds in regional and global Numerical Weather Prediction(NWP) models.
+The main objective of ICI is to use high frequency channels for measuring ice cloud properties and improve the representation of ice clouds in regional and global NWP models.
 ICI is a conically scanning radiometer that will measure 13 frequencies from 183\,GHz up to 664\, GHz.
 Among all available channels, 183.31\,GHz, 325.15\,GHz and 448.00\,GHz, will measure vertical polarization;  while other channels around frequencies 243.20\,GHz and 664.00\,GHz are ``window channels'' and will measure both vertical and horizontal polarization.
-The instrument will observe earth from a mean altitude of 832\,Km with sensor viewing angle 44.767$^\circ$(measured from nadir).
-For all the channels, the mean footprint size is about 15\,Km, but the exact geo-location of samples differs.
+The instrument will observe earth from a mean altitude of 832\,km with sensor viewing angle 44.767$^\circ$(measured from nadir).
+For all the channels, the mean footprint size is about 15\,km, but the exact geo-location of samples differs.
 Therefore a simultaneous utilization of data from different channels shall require remapping to a common footprint \citep{eriksson:towar:20}.
@@
 \end{table}
-The Arctic Weather Satellite (AWS) is a small satellite mission approved as ESA
+The Arctic Weather Satellite (AWS) is a small satellite mission approved as European Space Agency (ESA)
 Earth Watch Programme Element.
@@
 The first prototype mission is expected to be delivered around 2023.
-The main objective of AWS will be to improve the representation of Artic and sub-Arctic weather in NWP models and improve the global weather forecasts.
-AWS will will have channels receiving frequencies around 89.00\,GHz, 165.5\,GHz, 183.31\,GHz, 229.00\,GHz and 325.15\,GHz.
-For a detailed description of the AWS channels see \citet{eriksson2020study}.
-
-In this study, forward simulations at frequencies 183.31\,GHz and 325.15\,GHz were conducted. A brief summary of these channels is provided in Table~\ref{tab:specifications_AWS}.
+The exact channels onboard AWS are not yet set, but five 183\,GHz and four 325\,GHz channels shall be included.
+A brief summary of these channels is provided in Table~\ref{tab:specifications_AWS}.
+
+In this study, forward simulations at frequencies 183.31\,GHz and 325.15\,GHz were conducted.
 
@@
 MWHS-2 simulated radiances are routinely calculated at ECMWF for their use in the ECMWF NWP system.
-RTTOV and RTTOV-SCATT are used to calculate the radiances in clear-sky and all-sky conditions, respectively.
+RTTOV (Radiative Transfer for TOVS, \citet{saunders2018update} and RTTOV-SCATT \citep{bauer2006rttovscat} are used to calculate the radiances in clear-sky and all-sky conditions, respectively.
 For this study, MWHS-2 brightness temperatures for the period June-July 2020 are used.
 Out of all the available observations, we use data for latitudinal range $60^{\degree}$\,S to $60^{\degree}$\,N and satellite zenith angle less than $7.5^{\degree}$.
-With this filter we have 340\,000 cases for each frequency.
-
-ICI and AWS frequencies are simulated with ARTS.
-Cloudsat profiles during August 2015 are randomly selected for forward simulations.
+With this filter we have 340\,000 cases.
+
+ICI and AWS frequencies are simulated with Atmospheric Radiative Transfer Simulator (ARTS, \citet{buehler:artst:18}).
+CloudSat\citep{Stephens2002cloudsat} profiles during August 2015 are randomly selected for forward simulations.
 The input data are restricted between $60^{\degree}$S to $60^{\degree}$N, and surface is below 500\,m.
@@
 The complete simulation setup is described in Appendix \ref{appendix:ARTS_setup}.
-For each ICI frequency in Table~\ref{tab:ICI_MWI_channels}, 220\,000 cases are simulated.
-All ICI frequencies are simulated directly.
-For AWS, 140\,000 cases are simulated.
-Forward simulations are performed for 21 monochromatic frequencies, and later these frequencies are interpolated to a finer grid to get the AWS channel brightness temperatures.
+For ICI and AWS, 220\,000 and 140\,000 cases are simulated, respectively.
 All AWS sensor viewing angles (from $0^\circ$ to $45^\circ$) are simulated, but the results described in this study are based on nadir viewing angle.
-Simulations for all three sensors are noise free, so to incorporate the measurement uncertainties, whenever needed, gaussian noise is added to according to the channel NE$\Delta$T (Table~\ref{tab:specifications_MWHS2} - Table~\ref{tab:specifications_AWS}).
-
-The noise free simulations are split into training and testing datasets.
+Simulations for all three sensors are noise free, so to incorporate the measurement uncertainties, whenever needed, gaussian noise is added to according to the channel NE$\Delta$T (see Table~\ref{tab:specifications_MWHS2} - Table~\ref{tab:specifications_AWS}).
+
+The simulations are split into training and testing datasets.
 The training dataset is used to train the machine learning model, while the testing dataset is used to evaluate the trained model.
@@
 The task that we aim to solve in this study is to predict the NFCS brightness
-temperature $\ynfcs$ at a given $183\unit{GHz}$ channel from a vector of
-cloud-contaminated observations $\y$. Since the information-content of the
+temperature \todo{$\ynfcs$, define it} at a given $183\unit{GHz}$ channel from a vector of
+all-sky observations $\y$. Since the information-content of the
 cloud-contaminated observations is certainly too low to solve this problem
@@
 
-As has been shown in \citet{pfreundschuh:aneur:18}, quantile regression neural
-networks (QRNN) can be used to solve these type of problems. Instead of a point
-prediction, as it is typically performed in regression problems, QRNNs learn to
+As has been shown in \citet{pfreundschuh:aneur:18}, QRNN can be used to solve these type of problems. Instead of a point prediction, as it is typically performed in regression problems, QRNNs learn to
 predict a vector of quantiles, which can be used to approximate the distribution
@@
 The major challenge for implementing QRNN for the current application was to select high performing neural network architecture.
-This was obtained through grid search over different hyperparameter configurations.
+This was obtained through grid search over different hyper-parameter configurations.
 The details are described in Appendix~\ref{appendix:hyperparamter}
@@
 The input data is all-sky brightness temperatures from selected input channels and/or additional data like land/sea mask.
-The output in both configurations is NFCS value for the target 183\,GHz channel.
+The output in both configurations is the posterior distribution of NFCS values for the target 183\,GHz channel.
 The two configurations differ only by the number of input 183\,GHz channels used in the training process:
@@
 \begin{enumerate}
-	\item QRNN-single: In this configuration, the training input includes all-sky brightness temperatures from the target 183\,GHz channel and other non-humidity channels.
+	\item QRNN-single: In this configuration, the training input comprises of  all-sky brightness temperatures from the target 183\,GHz channel and other channels.
 Additional data is included, if relevant.
@@
 
-	\item QRNN-all: In this configuration, all-sky brightness temperatures from all available 183\,GHz channels are included in the training input.
-Just like QRNN-single, data from other non-humidity channels and additional data are also taken into account; but the main difference is the concurrent utilisation of all 183\,GHz frequencies.
+	\item QRNN-all: Same as QRNN-single, but all available 183\,GHz frequencies are included.      
 \end{enumerate}
@@
 	\includegraphics[height=45mm]{Figures/posterior_distribution_I1V.pdf} 
-	\caption{An example showing the predicted quantiles of the conditional distribution of $\ynfcs$ }
+	\caption{Examples showing the predicted quantiles of the conditional distribution of $\ynfcs$ }
 	\label{fig:posterior_distribution_I1V}	
@@
 QRNN predictions are posterior probability distribution of the NFCS values described over the chosen quantiles.
-In order to facilitate the interpretation of results, an example QRNN output is shown in Fig.~\ref{fig:posterior_distribution_I1V}.
+In order to facilitate the interpretation of results, examples of QRNN outputs are shown in Fig.~\ref{fig:posterior_distribution_I1V}.
 This example illustrates the predicted quantiles for three different cases.
@@
 In this study, we assume the posterior median to be the best estimate for the predicted NFCS value ($\ynfcs$).
-To analyse the ability of QRNN in correctly predicting the point estimate, deviation of the median value from the corresponding true value ($\yonfcs$) is evaluated using common performance indicators like bias, mean absolute error(MAE) and standard deviation (STD).
+To analyse the ability of QRNN in correctly predicting the point estimate, deviation of the median value from the corresponding true value ($\yonfcs$) is evaluated using common performance indicators like bias, mean absolute error (MAE) and standard deviation (STD).
 The asymmetry of error distributions around their mean is also calculated through the measure of skewness.
@@
 \end{equation}
-where $\bar{Y}$ and $\sigma$ are mean and standard deviation of the dataset, respectively.
+where $\bar{Y}$ and $\sigma$ are mean and standard deviation of the deviations, respectively.
 
@@
 
-All evaluation results described in the study have been made on the testing data.
+All evaluation results described in the study have been made on the test dataset.
 
@@
 We use MWHS-2 to demonstrate the results.
-The choice is motivated by the fact that MWHS-2 has five complementary 183\,GHz channels as ATMS/MWS, along with additional 118\,GHz channel.
+The choice is motivated by the fact that MWHS-2 has five complementary 183\,GHz channels, along with additional 118\,GHz channel.
 In order to formulate and test the correction approach, multiple QRNN experiments are performed for MWHS-2 channel 14.
@@
 %
-For MWHS-2, multiple experiments using both QRNN configurations are performed. With different experiments we aim to delve into the sensitivity of the method to different input channels:
+\label{sec:QRNN_expt_MWHS}
+For MWHS-2, multiple experiments using both QRNN configurations are performed. With these we aim to delve into the sensitivity of the method to different input channels:
 
@@
 	\item In the first experiment, we examine the performance of QRNN cloud correction with MWHS-2 window channels: 89 and 150\,GHz.
-In ECMWF NWP system, the differences between the observations of these two window channels (Scattering Index) \citep{Lu2015FY3C} are used to identify the cloud affected data for ATMS, MHS and MWHS-2.
+In ECMWF NWP system, the differences between the observations of these two window channels are used to identify the cloud affected data for ATMS and MWHS-2 \citep{geer2015scatteringindex}.
 To investigate the potential impact of these two window channels in QRNN based cloud correction, the configuration QRNN-single is applied.
@@
 	\centering
-	\includegraphics[height=55mm]{Figures/QRNN_output_mwhs.pdf} 
+	\includegraphics[width = 70mm]{Figures/QRNN_output_mwhs.pdf} 
 	\caption{Distribution of point estimate $\ynfcs$ obtained from QRNN-single 89+150\,GHz for MWHS-2 channel 14. The corresponding distributions for all-sky and clear-sky simulations are also shown.}
@@
 \end{figure}
+\begin{figure}[t]
+	\centering
+	\includegraphics[width = 70mm]{Figures/MWHS_error_dist_14.pdf} 
+	\caption{Error distribution for deviations of point estimates to NFCS simulations.
+The results are from QRNN-single experiment 89+150\,GHz and MWHS-2 channel 14.
+Noise is also plotted for reference.
+The label ``All-sky'' represents the all-sky simulations, ``Predicted(All)'' denotes the predicted point estimates, while ``Predicted(5\,K)'' refers to the predicted point estimates but where cases with cloud correction greater than 5\,K are excluded.}
+	\label{fig:error_distribution_mwhs14}	
+\end{figure}
 \begin{table*}[t]
-	\caption{Error statistics for deviations of NFCS predictions to simulations.
-Results are for different QRNN experiments for MWHS-2 channel 14.
-The results from input channel combinations 89+150\,GHz, 89+150+118\,GHz and 150\,GHz are with QRNN-single.
-While with QRNN-all, only combination 89+150+183\,GHz is shown.
-The statistics for uncorrected all-sky simulations and NFCS simulations are also provided.
-The label ``All'' refers to entire predicted dataset, while Filtered(5\,K) denotes the subset where predictions with correction greater than 5\,K are omitted.
-The fraction of rejected cases is given in parentheses.
+	\caption{Error statistics for deviations of point estimates to NFCS simulations.
+Results are for different QRNN experiments for MWHS-2 channel 14 (see Sect.~\ref{sec:QRNN_expt_MWHS}).
+The statistics for all-sky and clear-sky simulations are also provided.
+The label ``All'' denotes the entire dataset of predicted point estimates, while ``Pred.(5\,K)'' refers to the predicted point estimates but where cases with cloud correction greater than 5\,K are excluded.
 }
@@
 		&   Clear-sky &   All-sky &  \multicolumn{2}{c|}{89+150\,GHz} & \multicolumn{2}{c|}{89+150+118\,GHz} & \multicolumn{2}{c|}{150\,GHz} & \multicolumn{2}{c}{89+150+183\,GHz}\\		
-		&			   &			& All & Filtered(5K) & All & Filtered(5K) & All & Filtered(5K)  & All & Filtered(5K)\\
+		&			   &			& All & Pred.(5\,K) & All & Pred.(5\,K) & All & Pred.(5\,K)  & All & Pred.(5\,K)\\
 		\middlehline
@@
 
-Fig.~\ref{fig:distribution_predicted_mwhs14} shows the distribution of point estimates obtained from QRNN.
+The posterior distribution of NFCS values obtained from experiment 89+150\,GHz is similar to one shown in Fig.~\ref{fig:posterior_distribution_I1V}.
+The median value is chosen as the point estimate (see Sect.~\ref{sec:validation}).
+The distribution of point estimates is displayed in Fig.~\ref{fig:distribution_predicted_mwhs14}.
 The predicted values are able to correct most of the low brightness temperature cases, and overall a good match with the NFCS simulations is observed.
 However, QRNN is unable to predict the lowest clear-sky brightness temperatures, and cases with brightness temperatures around 260\,K occur frequently.
-The corresponding error statistics(see Sect.~\ref{sec:validation}) are displayed in  Table~\ref{tab:error_statistics_mwhs_14}.
+The deviations of point estimates from NFCS simulations are shown in Fig.~\ref{fig:error_distribution_mwhs14}.
+The large negative deviations are corrected successfully with QRNN, but residual cloud impact is evident in the negative tail.
+Most of these residual cases have departures less than 10\,K.
+The corresponding error statistics(see Sect.~\ref{sec:validation}) are provided in  Table~\ref{tab:error_statistics_mwhs_14}.
 In the uncorrected data, the negative departures due to cloud impact lead to a large negative skewness(-14.34) and high bias (-0.84\,K).
@@
 
-In spite of the fact that QRNN only provides a partial cloud correction, the results for  MWHS-2 channel 14 are comparable to what we achieve with existing cloud filtering techniques like scattering index (SI)  \citep{geer2015scatteringindex} and the filtering scheme by \citet{buehler:aclou:07}.
+In spite of the fact that QRNN only provides a partial cloud correction, the results for  MWHS-2 channel 14 are comparable to what we achieve with existing cloud filtering techniques like scattering index (SI) and the filtering scheme by \citet{buehler:aclou:07}.
 SI uses the differences of brightness temperatures between 89 and 150\,GHz to identify cloud affected data, whilst in the study by \citet{buehler:aclou:07}, they use brightness temperature based threshold to filter out cloudy cases.
@@
 The results obtained with SI and B183 are displayed in Table~\ref{tab:SI_statistics}.
-With SI threshold = 5\,K, almost 30\% of the data is rejected, yet the resulting error distributions are worse as compared to QRNN.
-Similar is the case with B183, where approximately 17\% of the data is rejected, but the filtering performance is inadequate.
+With SI threshold = 5\,K, almost 30\% of the data is rejected, yet the resulting error distributions are poorer as compared to QRNN.
+The low bias and skewness values indicate that most of the high negative departures are removed, but cases with low cloud impact pass the filter as clear.
+Similar is the case with B183.
+Here only 3\% of the data is filtered out but the overall statistics are worse than both QRNN and SI.
+The results from the two filters are not surprising as both aim at removing only cases with high ice content.
+The thin cirrus clouds and other low hydrometeor impact cases remain unaltered.
 
@@
 	\caption{ Error statisics for MWHS-2 channels 11, 12, 13 and 15 from QRNN-single experiment 89+150\,GHz.
-The labels ``All'' and ``Filtered(5\,K)' are as described in Table~\ref{tab:error_statistics_mwhs_14}.}
+The labels ``All'' and ``Pred.(5\,K)' are same as described in Table~\ref{tab:error_statistics_mwhs_14}.}
 	\label{tab:error_statistics_mwhs_others}
@@
 		& &  Clear-sky &   All-sky &  \multicolumn{2}{c}{89+150\,GHz}  \\
-		&	&		   &			& All & Filtered(5K)\\
+		&	&		   &			& All & Pred.(5K)\\
 		\middlehline
@@
 \begin{table*}[t]
-	\caption{Error statistics obtained after filtering MWHS-2 humidity observations according to scattering index (SI) and methodology described by \citet{buehler:aclou:07}.}
+	\caption{Channel wise error statistics obtained after filtering MWHS-2 humidity observations  according to scattering index (SI) and filtering described by \citet{buehler:aclou:07}.
+The latter is denoted as  B183.
+}
 	\label{tab:SI_statistics}
@@
 		& \multicolumn{2}{c|}{Channel 11} & \multicolumn{2}{c|}{Channel 12} & \multicolumn{2}{c|}{Channel 13} & \multicolumn{2}{c|}{Channel 14} & \multicolumn{2}{c}{Channel 15}\\
+			& SI & B183 & SI & B183 & SI & B183 & SI & B183 & SI & B183\\
 			\cline{2-11}
-		Bias &-0.05	&-0.08	&-0.07&	-0.13&-0.14	&-0.24	&-0.23&	-0.4&-0.34&	-0.59\\
-		MAE   & 0.81	&0.84	&0.82 &	0.88 &	0.85&0.95   &0.92 &	1.07&1.03 &	1.25\\
-		STD   &1.02	&1.22	&1.04 &	1.52 &	1.1	& 2.0	&1.25 &	2.54&1.53&	3.25\\
+		Bias 	 &-0.04	& -0.05	& -0.07 &  -0.15 &  -0.14 & -0.29	&-0.23 &  -0.51 & -0.33 &  -0.81\\
+		MAE  	 & 0.81	&  0.81	&  0.82 &	0.86 &	 0.85 &  0.97   & 0.92 &   1.14 &  1.03 &	1.44\\
+		STD  	 &1.02	&  1.03	&  1.04 &	1.14 &	 1.1  &  1.39	& 1.26 &   1.83 &  1.53 &	2.64\\
+		Skewness &-0.12 & -0.24 & -0.38 & -0.86  &  -0.91 & -2.23   &-1.79 &  -3.45 & -2.85 &  -4.41\\
 		\bottomhline		
@@
 A comparison with SI based filtering and B183 is displayed in  Table~\ref{tab:SI_statistics}.
-For channels 11 and 12 the performance of QRNN is comparable to scattering index, albeit 30\% of the observations are rejected in the latter.
-For channels 13 and 15, the error statistics obtained with SI are slightly inferior.
-The filtering with B183 is also partial for all channels, but is poorer than SI.
+For channel 11 the performance of QRNN is comparable to both SI and B183.
+Similar is the case with channel 12, though the results from B183 are slightly poor.
+Both these channels are mostly transparent to hydrometeor impact, and the filtering schemes work well.
+The major caveat is the rejection of clear cases.
+With comparable accuracy, the fraction of rejection in SI is approx.
+30\% in comparison to approx.
+3\% in B183.
+For channels 13 and 15 the error statistics obtained with SI are slightly inferior in comparison to QRNN.
+The results with B183 are even worse.
+For all channels, the two filters succeed in removing the high ice cloud cases, but for lower peaking channels, the high negative skewness values indicate presence of cases with low cloud impact.
+Clearly the ``one for all'' approach of both filters is not adequate to cater for channel specific hydrometeor impact.
 
@@
 	\includegraphics[width = 70mm]{Figures/prediction_uncertainty_MWHS_14.pdf}	
-	\caption{The prediction uncertainty for MWHS-2 channel 14 (QRNN-single) with respect to quantiles for randomly selected 1500 cases.
+	\caption{Examples of prediction uncertainties obtained from QRNN-single (89+150\,GHz) for MWHS-2 channel 14.
+1500 randomly selected cases are shown.
 The quantiles have been plotted at equidistant points.
@@
 	\includegraphics[height = 70mm]{Figures/calibration_QRNN_MWHS_14.pdf}	
-	\caption{Calibration of the prediction intervals obtained from QRNN-single for MWHS-2 channel 14. }
+	\caption{Calibration of the prediction intervals obtained from QRNN-single (89+150\,GHz) for MWHS-2 channel 14.
+Plots for both the complete dataset and the subset with correction greater than 5\,K are shown.
+}
 	\label{fig:calibration_mwhs}	
@@
 	\includegraphics[width=70mm]{Figures/deviation_posterior_mwhs_samples_14.pdf}	
-	\caption{The distribution of predicted errors and observed errors for MWHS-2 channel 14 as obtained from QRNN-single for the test dataset.
+	\caption{The distribution of predicted errors and observed errors  obtained from QRNN-single (89+150\,GHz) for MWHS-2 channel 14.
 The predicted errors are estimated as deviation of random samples from posteriori distribution to corresponding median values.}
@@
 The quantiles given out by QRNN can be used to construct the probability distribution of the predictions in contrast to other correction approaches which give out only point estimates.
-An example of the uncertainties given out by QRNN is shown in Fig.~\ref{fig:prediction_uncertainty_mwhs}.
+Examples of the uncertainties given out by QRNN is shown in Fig.~\ref{fig:prediction_uncertainty_mwhs}.
+The spread of error distribution is asymmetric.
 The predictions over quantiles $-3\sigma$, $-2\sigma$ and $-1\sigma$ are quite sharp and lie close to the median value.
-The spread over different cases is also quite narrow, with only few cases with high error.
 In contrast, the spread of predictions over quantiles $1\sigma$, $2\sigma$ and $3\sigma$ is wider.
-
+Also, cases with very high uncertainty occur infrequently.
 The calibration of the prediction intervals on the testing dataset is displayed in Fig.~\ref{fig:calibration_mwhs}.
@@
 Fig.~\ref{fig:predicted_errors_mwhs} illustrates the predicted and observed errors for MWHS-2 channel 14.
+Both error distributions are asymmetric, and this is in fact covered by the percentile distribution  in Fig.~\ref{fig:prediction_uncertainty_mwhs}.
 The predicted errors are slightly overestimated for negative values, but overall the predicted errors from the QRNN posterior distribution and the observed errors have a good match.
@@
 With a test dataset of 70\,000 samples, we cannot represent the far wings of the distribution accurately.
-The high errors which we try to estimate are rare, and can not be fully represented by QRNN.
+The high errors which we try to estimate are rare, and cannot be fully represented by QRNN.
 
@@
 	\item In the first experiment, we apply QRNN-single configuration for cloud correction at three ICI humidity channels.
-In this case, the training data is the target 183\,GHz channel and all available ICI sub-mm frequencies (325\,GHz, 448\,GHz and 664\,GHz) with vertical polarisation.
-No other data are included in the training process.
-The experiment is also channel specific, thus each 183\,GHz channel is trained separately.
+In this case, the training data is the target 183\,GHz channel and from all frequencies  centered around 325\,GHz, 448\,GHz and 664\,GHz.
+For 664\,GHz only vertical polarisation is included.
+No other data are considered.
+The experiment is also channel specific.
 For example, to predict NFCS values for channel I1V, the input training dataset includes noisy all-sky simulations from channels I1V, I5V, I6V, I7V, I8V, I9V, I10V, and I11V and the target is NFCS simulations for channel I1V.
@@
 %
-%f
 \begin{figure*}[t]
-	\includegraphics[width=\textwidth]{Figures/PDF_predictions_ICI.pdf} 
-	\caption{Distributions of point estimate NFCS from QRNN-single for channels I1V, I2V and I3V. The corresponding distributions for NFCS simulations are also shown.}
-	\label{fig:PDF_predictions}	
-\end{figure*}
-\begin{figure*}[t ]
 	\includegraphics[width=\textwidth]{Figures/error_distribution_QRNN-single.pdf} 
-	\caption{Error distributions for deviations of point estimates to NFCS simulations.
-The results are from QRNN-single and channels I1V, I2V and I3V.
-Noise for each channel is also plotted for reference.
-The label ``Uncorrected'' represents the measurement data, ``Predicted(All)'' denotes the entire prediction dataset, while ``Predicted(5\,K)'' refers to the predicted dataset but where cases with cloud correction greater than 5\,K are excluded.}
+	\caption{Same as Fig.~\ref{fig:error_distribution_mwhs14}, but from QRNN-single experiment for ICI channels I1V, I2V and I3V.}
 	\label{fig:error_distributions}	
@@
 \begin{table*}[t]
-	\caption{ Error statistics for deviations of point estimates to NFCS simulations. 
-		The values for Bias, mean absolute error(MAE), standard deviation(STD), and measure of skewness(Skewness) are shown.
-Results are from QRNN-single for channels I1V, I2V and I3V.
-The number in parentheses is the percentage of cases removed by filtering.
-The label ``Predicted(All)'' refers to the complete predicted dataset, while ``Predicted (5\,K)'' denotes the prediction dataset but where cases with cloud correction greater than 5\,K are excluded.}
+	\caption{ Same as Table~\ref{tab:error_statistics_mwhs_others}, but from QRNN-single for ICI channels I1V, I2V and I3V.}
 	\label{tab:error_statistics_ici}
@@
 		&&Clear-sky &   All-sky &  \multicolumn{2}{c}{Predicted}  \\
-		&&			   &			&	(5\,K) & (All) \\
+		&&			   &			&	All & 5\,K \\
 		\middlehline
@@
 
-Fig.~\ref{fig:PDF_predictions} shows the distribution of point estimates given by QRNN.
-For all three channels, an excellent agreement between the predictions and simulations is observed.
-This indicates that QRNN is successful in predicting NFCS values for majority of the cases.
-At lower brightness temperatures, the frequency of predictions is slightly smaller than simulations.
-This could be due to few QRNN predictions ending up with partially corrected cloud impact.
-
-The QRNN prediction accuracy is estimated by computing the deviation of the best estimate to its corresponding NFCS simulation(Fig.~\ref{fig:error_distributions}).
+The error distributions of the point estimates obtained from QRNN are shown in Fig.~\ref{fig:error_distributions}.
 The predicted values have symmetric error distributions albeit with a large spread.
@@
 If the predicted cases with correction more than 5\,K are rejected, the resulting error distributions fit the measurement noise, except for I1V, where cases with residual cloud impact introduces a negative bias.
-
 For a quantitative assessment of the errors, the results from various error metrics described in  Sect.~\ref{sec:validation} are displayed in Table~\ref{tab:error_statistics_ici}.
@@
 \begin{table*}[t]
-	\caption{Same as Table~\ref{tab:error_statistics_ici}, but for AWS channels. }
+	\caption{Same as Table~\ref{tab:error_statistics_mwhs_others}, but from QRNN-single for AWS channels. }
 	\label{tab:statistics_qrnn_aws}
@@
 		\cline{3-6}
-		&&Clear-sky &   All-sky &  \multicolumn{2}{c}{Predicted}  \\
+		&&Clear-sky &   All-sky &  \multicolumn{2}{c}{Pred.}  \\
 		&&   &    &   (All) & (5\,K) \\
 		\middlehline
-		AWS-32  &Bias      & 0.00 & -1.32 &  -0.03 & -0.02 \\
+		AWS-32  &Bias      & 0.00 & -1.32 &  -0.03 & -0.02(4.77\%) \\
 				&MAE      & 0.36 &  1.57 &   0.54 &  0.43 \\
@@
 		\middlehline
-		AWS-33	&Bias      & -0.01 & -0.98 &  0.02 &  0.01 \\
+		AWS-33	&Bias      & -0.01 & -0.98 &  0.02 &  0.01(3.82\%) \\
 				&MAE      &  0.36 &  1.23 &  0.49 &  0.42 \\
@@
 		\middlehline
-		AWS-34	&Bias      &  0.00 &  -0.68 &  0.02 &  0.01 \\
+		AWS-34	&Bias      &  0.00 &  -0.68 &  0.02 &  0.01(2.89\%) \\
 				&MAE      &  0.51 &   1.07 &  0.51 &  0.46 \\
@@
 		\middlehline
-		AWS-35	&Bias      &  0.00 &  -0.43 &  0.01 &  0.00 \\
+		AWS-35	&Bias      &  0.00 &  -0.43 &  0.01 &  0.00(1.93\%) \\
 				&MAE      &  0.50 &   0.84 &  0.48 &  0.44 \\
@@
 		\middlehline
-		AWS-36  &Bias      & 0.00 &  -0.28 &   0.03  &  0.03 \\
+		AWS-36  &Bias      & 0.00 &  -0.28 &   0.03  &  0.03(1.27\%) \\
 				&MAE       & 0.70 &   0.90 &   0.63  &  0.60 \\
@@
 	\includegraphics[width = 70mm]{Figures/prediction_uncertainty_I2V.pdf}	
-	\caption{The prediction uncertainty for I2V (QRNN-single) with respect to quantiles for randomly selected 1500 cases.
-The quantiles have been plotted at equidistant points.
+	\caption{Same as Fig.~\ref{fig:prediction_uncertainty_mwhs}, but from QRNN-single for ICI channel I2V.
 The red line represents a hypothetical Gaussian distribution of $270\pm0.60$\,K, which is of the order of standard deviation for I2V predictions (see Table~\ref{tab:error_statistics_ici}).}
@@
 	\includegraphics[width=70mm]{Figures/deviation_posterior_samples_I2V.pdf}	
-	\caption{The distribution of predicted errors and observed errors for I2V as obtained from QRNN-single for the test dataset.
-The predicted errors are estimated as deviation of random samples from posteriori distribution to corresponding median values.}
+	\caption{Same as Fig.~\ref{fig:predicted_errors_mwhs}, but from QRNN-single for ICI channel I2V.}
 	\label{fig:predicted_errors}	
@@
 	\includegraphics[height = 70mm]{Figures/calibration_QRNN_I2V.pdf}	
-	\caption{Calibration of the prediction intervals obtained from QRNN-single for I2V. }
+	\caption{Same as Fig.~\ref{fig:calibration_mwhs}, but from QRNN-single for ICI channel I2V. }
 	\label{fig:calibration_I1V}	
@@
 The weighting functions of window channels 89 and 150\,GHz, and the two 118\,GHz channels peak in the lower troposphere.
-Among these four channels, 150\,GHz has the highest peaking function around 4\,Km \cite{chen2020mwhs}.
-These channels can only provide coverage to the humidity channels in lower and mid troposphere; nonetheless, the 183\,GHz channels are sensitive to hydrometeor content upto 2\,Km.
+Among these four channels, 150\,GHz has the highest peaking function around 4\,km \citep{chen2020mwhs}.
+These channels can only provide coverage to the humidity channels in lower and mid troposphere; nonetheless, the 183\,GHz channels are sensitive to hydrometeor content upto 2\,km.
 Due to missing complementary information from other channels in the upper troposphere, QRNN fails at predicting these cases accurately.
@@
 The correlations for cloudy observations are not surprising as the cloud amount for different channels depends upon each other in a systematic way.
-However for clear-sky observations, the observational noise must be uncorrelated between the channels.
+However for clear-sky observations, the correlations should preferably be close to zero.
 This is observed to be true with QRNN-single, but QRNN-all fails at preserving the noise stochasticity.
@@
 Correlated errors are also undesirable for DA systems, but in future if the operational centres progress with approaches dealing with correlated observation errors, concurrent use of 89, 150 and 183\,GHz channels would give the best cloud correction performance.
-
-The biggest advantage of using QRNN is estimation of case-specific uncertainties.
-The predictions over chosen quantiles quantify the underlying uncertainty.
-The calibration plot and distribution of predicted errors show that  QRNN predictions are able to represent the a priori distribution.
-However we also observe that cases with high errors are generally poorly calibrated.
-The poorly calibrated predictions are a consequence of a different underlying a priori distribution.
-Predictions with high error originate from cases with high cloud impact.
-Such cases have a significantly distinct a priori distribtion as compared to clear cases, which dominate the training dataset and influence the a priori information.
-Additional information in form of more observational data or additional training inputs is required to improve QRNN prediction accuracy for such cases.
 
@@
 For clear-sky conditions, multiple observations of same scene from different channels can cancel out the noise.
-This effect is observed to be stronger in ICI observations than AWS; due to more number of training inputs in the former.
+This effect is observed to be stronger in ICI than AWS, as the former has additional input channels giving same information.
 Note that with actual satellite measurements, the spread of error distributions smaller than noise could be difficult to achieve due to other underlying uncertainties not considered here.
 
-The symmetric and low spread error distributions is an important results from the DA perspective.
+\subsection{Prediction uncertainty and implications for DA}
+
+Another advantage of QRNN is estimation of case-specific uncertainties.
+The predictions over chosen quantiles quantify the underlying uncertainty.
+The analysis of QRNN predicted errors and calibration plots show that QRNN is successful in providing well calibrated probabilistic predictions of the posterior distributions except for few cases associated with high error.
+The poorly calibrated predictions are a consequence of cases with different underlying a priori distribution.
+Predictions with high error originate from cases with high cloud impact or cloudy cases with no orthogonal information.
+Such cases have a significantly distinct a priori distribution as compared to clear cases, which dominate the training dataset and influence the a priori information.
+Additional information in form of more observational data or additional training inputs is required to improve QRNN prediction accuracy for such cases.
+However the cases with low accuracy are associated with high uncertainty, and can be used with caution.
+
+The symmetric and low spread error distribution with uncertainty estimates is an important result from the DA perspective.
 Most of the existing cloud filtering schemes work well only at removing cases with high cloud impact, and as a consequence, the error distributions are highly skewed.
@@
 This is not the optimal solution but the best which can be achieved with present sensors.
-However, the symmetric error distributions obtained from QRNN allow us to effectively more than 95\% of the data without the need for error inflation.
-
-The analysis of QRNN predicted errors and calibration plots show that QRNN is successful in providing well calibrated probabilistic predictions of the posterior distributions except for few cases associated with high cloud impact.
-This is not unexpected as such cases form a small subset of the training set and their priori distribution is different from the entire dataset.
+However, the symmetric error distributions obtained from QRNN allow us to effectively utilize more than 95\% of the data without the need for error inflation.
 
@@
 In comparison to existing clear-filtering approaches, QRNN gives comparable or better performance and with minimal rejection of data.
-The accuracy of QRNN is affected by one single limitation, that is, the prediction of ``out of distribution'' cases.
-Correcting hydrometeor impact for cases where no complementary information is available is a challenge for QRNN and always limit its performance.
-Improving the representation of such cases in the a priori distribution can help alleviate this problem to a certain extent.
-However, improving their priori distribution is not trivial when the no additional source of orthogonal information is present.
+The accuracy of QRNN is affected by one single limitation, that is the prediction of ``out of distribution'' cases.
+Out of distribution cases are those which belong to a different a priori distribution than the one QRNN is trained on.
+Such cases can be the ones which occur infrequently, or those which lack any orthogonal information.
+The representation of the former can be improved with larger training datasets.
+However for the latter, improving their a priori distribution is not trivial.
+Correcting hydrometeor impact for cases without complete complementary information is a challenge for QRNN and always limit its performance.
 
@@
 The results indicate that utilisation of only 325\,GHz can also be beneficial when other channels are absent.
-In future when ICI would be available, the ICI sub-mm channels could also be used to cloud correct MWI humidity radiances.
+In future when ICI would be available, the ICI sub-mm channels could also be used to cloud correct MWI (MicroWave Imager) humidity radiances.
 Although re-mapping to a common footprint would slighly compromise the data quality, the high accuracy achieved with ICI simulations suggests that the QRNN would work well even when actual measurements are available.
@@
 The point estimates with low error have high certainty.
-On the other hand, the incorrect incorrect predictions on out-of-distribution cases have low confidence.
+On the other hand, the  incorrect predictions on out-of-distribution cases have low confidence.
 In comparison to deterministic correction approaches, the corrected radiances along with uncertainty estimates give additional benefit for DA systems.
@@
 \citep{pwr:93}, oxygen \citep{pwr:93} and water vapour 
-\citep{ellison2007permittivity}. LWC is taken from ERA-Interim and is assumed
-to be totally absorbing. In the mapping of CloudSat reflectivities to RWC and
-IWC a total separation between liquid and ice phase is assumed. All scattering
+\citep{ellison2007permittivity}. Liquid water content (LWC) is taken from ERA-Interim \citep{dee2011erainterim} and is assumed
+to be totally absorbing. In the mapping of CloudSat reflectivities to rain water content (RWC) and
+ice water content (IWC) a total separation between liquid and ice phase is assumed. All scattering
 hydrometeors at temperatures above 0$^\circ$C are assumed to be rain, and all
 below 0$^\circ$C are assumed to be ice hydrometeors. For RWC the particle size
-distribution of \citet{abel2012improved} is applied. The PSD of IWC follows the
-basic formulation applied in DARDAR (\verb
-http://www.icare.univ-lille1.fr/projects/dardar), using latest parameter
+distribution of \citet{abel2012improved} is applied. The particle size distribution (PSD) of IWC follows the basic formulation applied in DARDAR (\url{
+http://www.icare.univ-lille1.fr/projects/dardar}, \citet{delanoe2008variational}), using latest parameter
 values (i.e.\ $\alpha$ and $\beta$) as given by \citet{cazenave2019evolution}.
@@
 much more computationally costly and could not be accommodated inside the
-study. The land emissivity was taken from TELSEM \citep{aires2011tool} and the
-Ocean/water from TESSEM \citep{prigent2017sea}. For each atmopsheric case,
-both ''clear-sky'' and ``all-sky'' calculations were performed. In the former,
+study. The land emissivity was taken from TELSEM (Tool to Estimate Land‐Surface Emissivities at Microwave frequencies, \citet{aires2011tool}) and the
+Ocean/water from TESSEM (Tool to Estimate Sea‐Surface Emissivity from Microwaves to sub‐Millimeter waves , \citet{prigent2017sea}). For each atmospheric case,
+both ``clear-sky'' and ``all-sky'' calculations were performed. In the former,
 all impact of all hydrometeors were set to zero, while in the latter, IWC and
@@
 of the Stokes vector were calculated.
+For AWS, forward simulations were performed for 21 monochromatic frequencies, and later these frequencies were interpolated to a finer grid to get the AWS channel brightness temperatures.
 

### 2020-11-08 Article/ici_submm_cloudcorr_simon.tex
Added notes.

--- 2020-11-06 Article/ici_submm_cloudcorr.tex
@@
 \newcommand{\todo}[1]{{\color{red} #1}}
-\newcommand{\ynfcs}{y_\text{NFCS}}
-\newcommand{\yonfcs}{y^{o}_\text{NFCS}}
-\newcommand{\ynfcsi}{y_\text{NFCS, i}}
-\newcommand{\yonfcsi}{y^{o}_\text{NFCS, i}}
+\newcommand{\ynfcs}{\vec{y}_\text{NFCS}}
+\newcommand{\yonfcs}{\vec{y}^{o}_\text{NFCS}}
+\newcommand{\ynfcsi}{\vec{y}_\text{NFCS, i}}
+\newcommand{\yonfcsi}{\vec{y}^{o}_\text{NFCS, i}}
 \newcommand{\y}{\vec{y}}
@@
 
-The approach is demonstrated with use of 89 and 150\,GHz channels (following
-\citet{geer2015scatteringindex}), but we mainly explore the cloud correction (of
-183\,GHz data) that will be possible when sub-millimetre data will be at hand
-in some years. This wavelength region will be introduced by the Ice Cloud
-Imager (ICI, \citet{eriksson:towar:20}), but likely also be included in several
-smaller missions (such as Artic Weather Satellite (AWS); presented below).
-The focus on sub-mm channels is motivated by several reasons.
-Firstly, the higher frequencies have a higher sensitivity to scattering effects from smaller hydrometeors.
-For high altitude cirrus clouds, these frequencies have a stronger signal than 183\,Ghz.
-In some cloudy situations it could be possible that the impact at 183 GHz is of the order of thermal noise and modelling uncertainties, while the impact at 325 GHz is significantly higher.
-Secondly, the true potential of the QRNN cloud correction approach is likely not revealed if tested on existing data and applying ICI data for cloud filtering has not earlier been discussed.
-It is also argued that the cloud correction makes it possible to make good use of ICI data already in clear-sky assimilation, a fact that should speed up the use of this novel data source.
-
-A description of data and QRNN is provided in Sect.\ref{data_methods}.
-In Sect.~\ref{qrnn_mwhs} we demonstrate the applicability of correction scheme to existing sensors, and later its application is extended to include sub-mm channels (Sect.\ref{qrnn_ici}).
-The results are discussed in Sect.~\ref{discussions}, and Sect.~\ref{conclusions} presents the conclusions from this work and the future outlook.
+The proposed cloud correction scheme makes use of a Quantile Regression Neural
+Network (QRNN) to obtain a probabilistic prediction of the NFCS value. Unlike
+traditional neural networks techniques, which typically only provide a point
+estimate of the target variable, QRNNs are trained to predict an arbitrary set
+of quantiles of its Bayesian a posteriori distribution
+\citep{pfreundschuh:aneur:18}. The predicted a posteriori distribution 
+can then be used to derive an estimate of the NFCS value together with an estimate
+of the corresponding uncertainty.
+
+The main focus of this study is the potential of proposed cloud-correction
+method using sub-millimetre observations, which will become available
+operationally with the launch of the Ice Cloud Imager (ICI,
+\citet{eriksson:towar:20}) on board the next generation of polar orbiting
+meteorological satellites (MetOP-SG), but will likely also be included in
+several smaller missions (such as Artic Weather Satellite (AWS); presented
+below). Additionally, we demonstrate the feasibility of the approach based on
+observations at 89 and 150\ GHz channels (following
+\citet{geer2015scatteringindex}), which are available already today. The focus
+on sub-mm channels is motivated by several reasons. Firstly, the higher
+frequencies are more sensitive to scattering effects from smaller
+hydrometeors. For high altitude cirrus clouds, these frequencies have a stronger
+signal than 183\,Ghz. In some cloudy situations it could be possible that the
+impact at 183 GHz is of the order of thermal noise and modelling uncertainties,
+while the impact at 325 GHz is significantly higher. Secondly, the proposed
+cloud correction methods allows integrating ICI sub-mm observations in
+clear-sky data assimilation schemes and thus provides a simple
+way to make use this novel data source as soon as it becomes available.
+
+A description of the data used in this study and the QRNN approach is provided
+in Sect.\ref{data_methods}. In Sect.~\ref{qrnn_mwhs} we demonstrate the
+applicability of correction scheme to existing sensors, and later its
+application is extended to include sub-mm channels (Sect.\ref{qrnn_ici}). The
+results are discussed in Sect.~\ref{discussions}, and Sect.~\ref{conclusions}
+presents the conclusions from this work and the future outlook.
 
@@
 
-ICI and AWS frequencies are simulated with Atmospheric Radiative Transfer Simulator (ARTS, \citet{buehler:artst:18}).
-CloudSat\citep{Stephens2002cloudsat} profiles during August 2015 are randomly selected for forward simulations.
-The input data are restricted between $60^{\degree}$S to $60^{\degree}$N, and surface is below 500\,m.
-Both clear-sky and all-sky scenarios  are simulated.
-The complete simulation setup is described in Appendix \ref{appendix:ARTS_setup}.
-For ICI and AWS, 220\,000 and 140\,000 cases are simulated, respectively.
-All AWS sensor viewing angles (from $0^\circ$ to $45^\circ$) are simulated, but the results described in this study are based on nadir viewing angle.
-Simulations for all three sensors are noise free, so to incorporate the measurement uncertainties, whenever needed, gaussian noise is added to according to the channel NE$\Delta$T (see Table~\ref{tab:specifications_MWHS2} - Table~\ref{tab:specifications_AWS}).
+ICI and AWS frequencies are simulated with Atmospheric Radiative Transfer
+Simulator (ARTS, \citet{buehler:artst:18}). CloudSat
+\citep{Stephens2002cloudsat} profiles from August 2015 are randomly selected for
+forward simulations. The input data are restricted between $60\unit{^{\degree}}S$ to
+$60\unit{^{\degree}N}$, and surface is below 500\,m. Both clear-sky and all-sky
+scenarios are simulated. The complete simulation setup is described in Appendix
+\ref{appendix:ARTS_setup}. For ICI and AWS, 220\,000 and 140\,000 cases are
+simulated, respectively. All AWS sensor viewing angles (from $0^\circ$ to
+$45^\circ$) are simulated, but the results described in this study are based on
+nadir viewing angle. Simulations for all three sensors are noise free, so to
+incorporate the measurement uncertainties, whenever needed, gaussian noise is
+added to according to the channel NE$\Delta$T (see
+Table~\ref{tab:specifications_MWHS2} - Table~\ref{tab:specifications_AWS}).
 
@@
 
-As has been shown in \citet{pfreundschuh:aneur:18}, QRNN can be used to solve these type of problems. Instead of a point prediction, as it is typically performed in regression problems, QRNNs learn to
-predict a vector of quantiles, which can be used to approximate the distribution
-of the predicted quantity conditional on the network inputs. Using QRNNs to
-perform probabilistic cloud correction thus not only allows deriving an estimate
-for $\ynfcs$ but also for the error of the corrected observations.
+As has been shown in \citet{pfreundschuh:aneur:18}, QRNNs can be used to solve
+these type of problems. Instead of a point prediction, the QRNN is trained to
+predict a vector of quantiles of the distribution of the target variable
+conditional on the network input. Using these predicted quantiles, the cumulative
+distribution function (CDF) of the target variable can be estimated. QRNNs thus
+not only allow to predict a value $\ynfcs$ for the corrected brightness temperatures
+but also to estimate the uncertainty of the correction.
 
@@
 $0.2\%, 3\%, 16\%, 50\%, 85\%, 97\%$ and $99.8\%$. For a Gaussian
-distribution with mean $\mu$ and standard deviation $\sigma$, the quantiles
+distribution with mean $\mu$ and standard deviation $\sigma$, these quantiles
 approximately correspond to $\mu -3\sigma, \mu-2\sigma, \mu-\sigma
@@
 
-QRNN's are trained to minimize the mean of the quantile loss functions
+QRNN's are trained to minimize the mean of the sum of the quantile loss functions
 %
@@
 %
-for all predicted quantile fractions $\tau$, where $\y_\tau$ is the predicted
-quantile and $y$ the reference value from the training set. The quantile loss is
-used in this study as a performance criterion for the tuning of the hyper
-parameters of the QRNN (see Appendix~\ref{appendix:hyperparamter}). In addition to the quantile loss, also the Continuously
-Ranked Probability Score (CRPS) is considered. Given a predicted cumulative
-distribution function (CDF) $F$ and the reference value $y$, the CRPS is defined as
+for all selected quantile fractions $\tau$, where $y_\tau$ is the predicted
+quantile and $y$ the reference value from the training or test data . The
+quantile loss is used in this study as a performance criterion for the tuning of
+the hyper parameters of the QRNN (see Appendix~\ref{appendix:hyperparamter}). In
+addition to the quantile loss, also the Continuously Ranked Probability Score
+(CRPS) is considered. Given a predicted CDF
+$F$ and the reference value $y$, the CRPS is defined as
 %
@@
 %
-To compute the CRPS for a predictions from a QRNN, the predicted quantiles are
+To compute the CRPS for a prediction from a QRNN, the predicted quantiles are
 used to derive a piece-wise linear approximation of the CDF of the predicted
-distribution and evaluate the above integral.
-
-The implementation of QRNN is similar to one described in \citet{pfreundschuh:aneur:18}, except that instead of Keras python package, PyTorch, an open source machine learning
-library \citep{paszke2017automatic} is used.
-This version is developed and available as a part of \textit{typhon:tools for atmospheric research} software package [\todo{developer's version??}].
-The major challenge for implementing QRNN for the current application was to select high performing neural network architecture.
-This was obtained through grid search over different hyper-parameter configurations.
-The details are described in Appendix~\ref{appendix:hyperparamter}
+distribution.
+
+The implementation of QRNN is similar to the one described in
+\citet{pfreundschuh:aneur:18}, except that this version uses PyTorch
+\citep{paszke2017automatic} instead of Keras \citep{chollet2015keras} to
+implement the underlying neural network. The implementation is available as a
+part of version of the Typhon software package \citep{typhonv08}. The major
+challenge for implementing QRNN for the current application was to select high
+performing neural network architecture. This was obtained through grid search
+over different hyper-parameter configurations. The details are described in
+Appendix~\ref{appendix:hyperparamter}
 
@@
 \label{sec:QRNN_configuration}
-In the study, two QRNN configurations are formulated for cloud-correction.
-The basic construction of both is to individually train for each of the available 183\,GHz channels, using certain input training data.
-The input data is all-sky brightness temperatures from selected input channels and/or additional data like land/sea mask.
-The output in both configurations is the posterior distribution of NFCS values for the target 183\,GHz channel.
-The two configurations differ only by the number of input 183\,GHz channels used in the training process:
+In the study, two QRNN configurations are formulated for cloud-correction. The
+basic construction of both is that a separate network is trained for each
+183\,GHz channel to correct. The input data is all-sky brightness temperatures
+from selected input channels and/or additional data like land/sea mask. The
+output in both configurations is the posterior distribution of NFCS values for
+the target 183\,GHz channel. The two configurations differ only by the number of
+input 183\,GHz channels used in the training process:
 
@@
 \end{figure}
-QRNN predictions are posterior probability distribution of the NFCS values described over the chosen quantiles.
-In order to facilitate the interpretation of results, examples of QRNN outputs are shown in Fig.~\ref{fig:posterior_distribution_I1V}.
-This example illustrates the predicted quantiles for three different cases.
-This is in contrast with other conventional correction/filtering methods, which give out only point estimates.
-However, for most analysis, usually a single point estimate is required.
-In Bayesian analysis, usually the posterior mean or posterior median are selected as point estimates.
-In this study, we assume the posterior median to be the best estimate for the predicted NFCS value ($\ynfcs$).
-To analyse the ability of QRNN in correctly predicting the point estimate, deviation of the median value from the corresponding true value ($\yonfcs$) is evaluated using common performance indicators like bias, mean absolute error (MAE) and standard deviation (STD).
-The asymmetry of error distributions around their mean is also calculated through the measure of skewness.
-For a univariate dataset of length $N$, the Fisher-Pearson coefficient of skewness is defined as:
+QRNN predictions are posterior probability distribution of the NFCS values
+described over the chosen quantiles. In order to facilitate the interpretation
+of results, examples of QRNN outputs are shown in
+Fig.~\ref{fig:posterior_distribution_I1V}. This example illustrates the
+predicted quantiles for three different cases. This is in contrast with other
+conventional correction/filtering methods, which give out only point estimates.
+However, for most application only a single point estimate is required. In
+Bayesian analysis, usually the posterior mean or posterior median are selected
+as point estimates. In this study, we chose the posterior median as the point
+estimate for the predicted NFCS value ($\ynfcs$). To analyse the ability of QRNN
+in correctly predicting the point estimate, deviation of the median value from
+the corresponding true value ($\yonfcs$) is evaluated using common performance
+indicators like bias, mean absolute error (MAE) and standard deviation (STD).
+The asymmetry of error distributions around their mean is also calculated
+through the measure of skewness. For a univariate dataset of length $N$, the
+Fisher-Pearson coefficient of skewness is defined as:
 \begin{equation}
@@
 
-For probabilistic predictions, accuracy of the point estimate is inadequate to gauge the complete performance.
-In a successful QRNN training, QRNN learns to predict not only an accurate point estimate but also the correct underlying uncertainty.
-An ideal QRNN output should be sharp or in other words, all predicted quantiles should be concentrated in the vicinity of the point estimate.
-The predicted posterior distribution should also be well calibrated, that is, reflect the a priori probability distribution.
-A straightforward way to compare the two distributions is to plot the frequency of predictions and frequency of the true value in different prediction intervals.
-This is also commonly known as calibration plot.
-In a well-calibrated QRNN model, the calibration plot should follow the straight line y = x.
-Another way to assess how well the predicted posterior distribution reflects the observed errors is to compare the predicted and observed errors.
-The predicted error is deviation of a random sample drawn from the posterior distribution to its median.
-In this study, we analyse both the calibration plot and the predicted errors to assess the correctness of predicted uncertainties.
+For probabilistic predictions, accuracy of the point estimate is inadequate to
+gauge the complete performance. In a successful QRNN training, QRNN learns to
+predict not only an accurate point estimates but also the correct underlying
+uncertainty. An ideal QRNN output should be sharp or in other words, all
+predicted quantiles should be concentrated in the vicinity of the point
+estimate, but at the same time, the predicted posterior distribution should be
+well calibrated, that is, the predicted distribution should reflect actually
+observed frequencies. A straightforward way to compare the two distributions is
+to plot the frequency of predictions and frequency of the true value in
+different prediction intervals. This is also commonly known as calibration plot.
+In a well-calibrated QRNN model, the calibration plot should follow the straight
+line $y = x$. Another way to assess how well the predicted posterior distribution
+reflects the observed errors is to compare the predicted and observed errors.
+The predicted error is the deviation of a random sample drawn from the posterior
+distribution to its median. In this study, we analyse both the calibration plot
+and the predicted errors to assess the correctness of predicted uncertainties.
 
 All evaluation results described in the study have been made on the test dataset.
+\todo{Is this true for the hyper parameter tuning? Because if this is the
+  case, the evaluation should be redone on independent data.}
 
@@
 
-The posterior distribution of NFCS values obtained from experiment 89+150\,GHz is similar to one shown in Fig.~\ref{fig:posterior_distribution_I1V}.
-The median value is chosen as the point estimate (see Sect.~\ref{sec:validation}).
-The distribution of point estimates is displayed in Fig.~\ref{fig:distribution_predicted_mwhs14}.
-The predicted values are able to correct most of the low brightness temperature cases, and overall a good match with the NFCS simulations is observed.
-However, QRNN is unable to predict the lowest clear-sky brightness temperatures, and cases with brightness temperatures around 260\,K occur frequently.
-The deviations of point estimates from NFCS simulations are shown in Fig.~\ref{fig:error_distribution_mwhs14}.
-The large negative deviations are corrected successfully with QRNN, but residual cloud impact is evident in the negative tail.
-Most of these residual cases have departures less than 10\,K.
-The corresponding error statistics(see Sect.~\ref{sec:validation}) are provided in  Table~\ref{tab:error_statistics_mwhs_14}.
-In the uncorrected data, the negative departures due to cloud impact lead to a large negative skewness(-14.34) and high bias (-0.84\,K).
-Training QRNN with 89 and 150\,GHz successfully corrects a major portion of the cloud affected cases, and the bias is reduced to -0.09\,K.
-However, high skewness values indicate a negative tail or uncorrected departures.
-Including 118\,GHz in the training, gives comparable results as 89+150\,GHz.
-With 118\,GHz, the error distributions have lower bias and are more symmetric, but the MAE and STD remain unaltered.
-This indicates that the information from 118\,GHz channels can be beneficial in predicting few cases correctly, but the overall consequence is not exceptionally different from 89+150\,GHz.
-Similar is the case with using only 150\,GHz.
-In the latter, predictions have the most symmetric error distributions, but the highest spread.
+The posterior distribution of NFCS values obtained from experiment 89+150\,GHz
+is similar to the one shown in Fig.~\ref{fig:posterior_distribution_I1V}. The
+median value is chosen as the point estimate (see Sect.~\ref{sec:validation}).
+The distribution of point estimates is displayed in
+Fig.~\ref{fig:distribution_predicted_mwhs14}. The predicted values are able to
+correct most of the low brightness temperature cases, and overall a good match
+with the NFCS simulations is observed. However, QRNN is unable to predict the
+lowest clear-sky brightness temperatures, and cases with brightness temperatures
+around 260\,K occur frequently. The deviations of point estimates from NFCS
+simulations are shown in Fig.~\ref{fig:error_distribution_mwhs14}. The large
+negative deviations are corrected successfully with QRNN, but residual cloud
+impact is evident in the negative tail. Most of these residual cases have
+departures less than 10\,K. The corresponding error statistics(see
+Sect.~\ref{sec:validation}) are provided in
+Table~\ref{tab:error_statistics_mwhs_14}. In the uncorrected data, the negative
+departures due to cloud impact lead to a large negative skewness(-14.34) and
+high bias (-0.84\,K). Training QRNN with 89 and 150\,GHz successfully corrects a
+major portion of the cloud affected cases, and the bias is reduced to -0.09\,K.
+However, high skewness values indicate a negative tail or uncorrected
+departures. Including 118\,GHz in the training, gives comparable results as
+89+150\,GHz. With 118\,GHz, the error distributions have lower bias and are more
+symmetric, but the MAE and STD remain unaltered. This indicates that the
+information from 118\,GHz channels can be beneficial in predicting few cases
+correctly, but the overall consequence is not exceptionally different from
+89+150\,GHz. Similar is the case with using only 150\,GHz. In the latter,
+predictions have the most symmetric error distributions, but the highest spread.
 
@@
 
-The quantiles given out by QRNN can be used to construct the probability distribution of the predictions in contrast to other correction approaches which give out only point estimates.
-Examples of the uncertainties given out by QRNN is shown in Fig.~\ref{fig:prediction_uncertainty_mwhs}.
-The spread of error distribution is asymmetric.
-The predictions over quantiles $-3\sigma$, $-2\sigma$ and $-1\sigma$ are quite sharp and lie close to the median value.
-In contrast, the spread of predictions over quantiles $1\sigma$, $2\sigma$ and $3\sigma$ is wider.
-Also, cases with very high uncertainty occur infrequently.
-The calibration of the prediction intervals on the testing dataset is displayed in Fig.~\ref{fig:calibration_mwhs}.
-For the entire dataset, the predictions follow the y=x line, i.e.
-they are perfectly calibrated with the a priori distribution.
-However for the cases with correction greater than 5\,K, the distribution is poorly calibrated for higher quantiles.
-The curve lies below the y=x line indicating that the prediction intervals are too narrow.
-This is in agreement with the wide spread of predictions over the  higher quantiles (Fig.~\ref{fig:prediction_uncertainty_mwhs}).
-However such cases are few and filtering them results in well calibrated QRNN predictions.
+The quantiles given out by QRNN can be used to construct the probability
+distribution of the predictions in contrast to other correction approaches which
+give out only point estimates. Examples of the uncertainties given out by QRNN
+is shown in Fig.~\ref{fig:prediction_uncertainty_mwhs}. The spread of error
+distribution is asymmetric. The predictions over quantiles $-3\sigma$,
+$-2\sigma$ and $-1\sigma$ are quite sharp and lie close to the median value. In
+contrast, the spread of predictions over quantiles $1\sigma$, $2\sigma$ and
+$3\sigma$ is wider. Also, cases with very high uncertainty occur infrequently.
+The calibration of the prediction intervals on the testing dataset is displayed
+in Fig.~\ref{fig:calibration_mwhs}. For the entire dataset, the predictions
+follow the y=x line, i.e. the predicted uncertainties are perfectly calibrated
+with errors observed on the test data. However for the cases with correction
+greater than 5\,K, the distribution is poorly calibrated for higher quantiles.
+The curve lies below the y=x line indicating that the prediction intervals are
+too narrow. This is in agreement with the wide spread of predictions over the
+higher quantiles (Fig.~\ref{fig:prediction_uncertainty_mwhs}). However such
+cases are few and filtering them results in well calibrated QRNN predictions.
+\todo{This cannot be true. Filtering them, i.e. looking only at values with
+  correction < 5k will give predictions with too wide uncertainties, so that the
+  calibration will be above the diagonal. I don't think this information is particularly
+useful, so I'd suggest removing it.}
 
@@
 
-For other humidity channels, the predicted uncertainties followed similar behaviour and the not shown.
+For other humidity channels, the predicted uncertainties followed similar
+behaviour and are not shown.
 
@@
 However the cases with low accuracy are associated with high uncertainty, and can be used with caution.
+\todo{I could not follow the last sentence.}
 
@@
 Correcting hydrometeor impact for cases without complete complementary information is a challenge for QRNN and always limit its performance.
+\todo{Cases without orthogonal information are note what I understand as out-of-distribution samples.
+Moreover, rare cases are rather a matter of training set size.
+Nonetheless, it is of course essential that
+  the training set distribution reflects reality.}
 

### 2020-11-09 Article/ici_submm_cloudcorr_simon.tex
Updated comments.

@@
 \citep{Stephens2002cloudsat} profiles from August 2015 are randomly selected for
-forward simulations. The input data are restricted between $60\unit{^{\degree}}S$ to
+forward simulations. The input data are restricted between $60\unit{^{\degree}S}$ to
 $60\unit{^{\degree}N}$, and surface is below 500\,m. Both clear-sky and all-sky
@@
 conventional correction/filtering methods, which give out only point estimates.
-However, for most application only a single point estimate is required. In
+However, for most applications only a single point estimate is required. In
 Bayesian analysis, usually the posterior mean or posterior median are selected
@@
 All evaluation results described in the study have been made on the test dataset.
-\todo{Is this true for the hyper parameter tuning? Because if this is the
+\todo{Comment: Is this true for the hyper parameter tuning? Because if this is the
   case, the evaluation should be redone on independent data.}
@@
 \subsection{Experiments}
+\todo{Comment: I find the structure here confusing. You start with results from channel 14 but then have
+  an extra section on the accuracy for channel 14 and then another section considering the other
+  channel.}
 %
@@
 
-Further we investigated that if filtering the predictions with low accuracy could help in improving the error distributions.
-For filtering such cases, we assume that predictions with cloud correction greater than 5\,K are cases associated with large deviations.
-In all three experiments, removing the cases with correction greater than 5\,K removes around 3\% of the data, but only a marginal positive impact on the accuracy is observed.
-With 5\,K threshold though the cases with high errors are removed, the persistent negative skewness indicates presence of cases with residual cloud impact.
-Choosing a lower threshold can help in removing more partially corrected cases but at the cost of rejecting clear-sky cases.
-Since QRNN gives out NFCS values, choosing an unusually low correction threshold can also classify noisy clear-sky cases as cloudy.
-For example, for 89+150\,GHz, a threshold of 1.5\,K rejects almost 10\% of data, but the negative skewness is still not completely removed.
-
-In spite of the fact that QRNN only provides a partial cloud correction, the results for  MWHS-2 channel 14 are comparable to what we achieve with existing cloud filtering techniques like scattering index (SI) and the filtering scheme by \citet{buehler:aclou:07}.
-SI uses the differences of brightness temperatures between 89 and 150\,GHz to identify cloud affected data, whilst in the study by \citet{buehler:aclou:07}, they use brightness temperature based threshold to filter out cloudy cases.
-They recommend a viewing angle dependent brightness temperature threshold at $183.31\pm1.00$ \,GHz and brightness temperature difference between $183.31\pm3.00$ and $183.31\pm 1.00$ as a measure of cloud impact.
-Further in the text we refer this filter as ``B183''.
-The results obtained with SI and B183 are displayed in Table~\ref{tab:SI_statistics}.
-With SI threshold = 5\,K, almost 30\% of the data is rejected, yet the resulting error distributions are poorer as compared to QRNN.
-The low bias and skewness values indicate that most of the high negative departures are removed, but cases with low cloud impact pass the filter as clear.
-Similar is the case with B183.
-Here only 3\% of the data is filtered out but the overall statistics are worse than both QRNN and SI.
-The results from the two filters are not surprising as both aim at removing only cases with high ice content.
-The thin cirrus clouds and other low hydrometeor impact cases remain unaltered.
+Further we investigated whether filtering the predictions with low accuracy
+could help in improving the error distributions. For filtering such cases, we
+assume that predictions with cloud correction greater than 5\,K are cases
+associated with large deviations. In all three experiments, removing the cases
+with correction greater than 5\,K removes around 3\% of the data, but only a
+marginal positive impact on the accuracy is observed. With 5\,K threshold though
+the cases with high errors are removed, the persistent negative skewness
+indicates presence of cases with residual cloud impact. Choosing a lower
+threshold can help in removing more partially corrected cases but at the cost of
+rejecting clear-sky cases. Since QRNN gives out NFCS values, choosing an
+unusually low correction threshold can also classify noisy clear-sky cases as
+cloudy. For example, for 89+150\,GHz, a threshold of 1.5\,K rejects almost 10\%
+of data, but the negative skewness is still not completely removed.
+\todo{Comment: Did you try filtering based on predicted uncertainty?}
+
+In spite of the fact that QRNN only provides a partial cloud correction, the
+results for MWHS-2 channel 14 are comparable to what we achieve with existing
+cloud filtering techniques like scattering index (SI) and the filtering scheme
+by \citet{buehler:aclou:07}. SI uses the differences of brightness temperatures
+between 89 and 150\,GHz to identify cloud affected data, whilst in the study by
+\citet{buehler:aclou:07}, they use brightness temperature based threshold to
+filter out cloudy cases. They recommend a viewing angle dependent brightness
+temperature threshold at $183.31\pm1.00$ \,GHz and brightness temperature
+difference between $183.31\pm3.00$ and $183.31\pm 1.00$ as a measure of cloud
+impact. Further in the text we refer this filter as ``B183''. The results
+obtained with SI and B183 are displayed in Table~\ref{tab:SI_statistics}. With
+SI threshold = 5\,K, almost 30\% of the data is rejected, yet the resulting
+error distributions are poorer as compared to QRNN. The low bias and skewness
+values indicate that most of the high negative departures are removed, but cases
+with low cloud impact pass the filter as clear. Similar is the case with B183.
+Here only 3\% of the data is filtered out but the overall statistics are worse
+than both QRNN and SI. The results from the two filters are not surprising as
+both aim at removing only cases with high ice content. The thin cirrus clouds
+and other low hydrometeor impact cases remain unaltered.
 
@@
 The latter is denoted as  B183.
-}
+\todo{Comment: Did you consider combining this with Tab.
+5?
+If combined might be worth highlighting the best performing filtering method.
+Fraction of filtered cases should have its own column.}}
 	\label{tab:SI_statistics}
@@
 For channel 11 the performance of QRNN is comparable to both SI and B183.
-Similar is the case with channel 12, though the results from B183 are slightly poor.
+Similar is the case with channel 12, though the results from B183 are slightly poorer.
 Both these channels are mostly transparent to hydrometeor impact, and the filtering schemes work well.
@@
 The quantiles have been plotted at equidistant points.
-The red line represents a hypothetical Gaussian distribution of $270\pm1.0$\,K.}
+The red line represents a hypothetical Gaussian distribution of $270\pm1.0$\,K.
+\todo{Comment: I suggest adding boxes for each quantile to increase the amount of quantitative information in the plot.}}
 	\label{fig:prediction_uncertainty_mwhs}	
@@
 	\caption{The distribution of predicted errors and observed errors  obtained from QRNN-single (89+150\,GHz) for MWHS-2 channel 14.
-The predicted errors are estimated as deviation of random samples from posteriori distribution to corresponding median values.}
+The predicted errors are estimated as deviation of random samples from posteriori distribution to corresponding median values.
+\todo{Comment: I suggest different color for predicted}}
 	\label{fig:predicted_errors_mwhs}	
@@
 cases are few and filtering them results in well calibrated QRNN predictions.
-\todo{This cannot be true. Filtering them, i.e. looking only at values with
+\todo{Comment: This cannot be true. Filtering them, i.e. looking only at values with
   correction < 5k will give predictions with too wide uncertainties, so that the
-  calibration will be above the diagonal. I don't think this information is particularly
-useful, so I'd suggest removing it.}
+  calibration will be above the diagonal. This is because the two sets are complementary
+  and the cases must add up to give the good overall calibration shown above.
+  Although, It of course could be that this effect is less evident because the
+  number of cases < 5k is so much higher.}
 
@@
 	\includegraphics[width=\textwidth]{Figures/error_distribution_QRNN-single.pdf} 
-	\caption{Same as Fig.~\ref{fig:error_distribution_mwhs14}, but from QRNN-single experiment for ICI channels I1V, I2V and I3V.}
+	\caption{Same as Fig.~\ref{fig:error_distribution_mwhs14}, but from QRNN-single experiment for ICI channels I1V, I2V and I3V.
+    \todo{Comment: I might be worth adding  the calibration of error estimates based of B183 or SI with
+      a Gaussian error model. I don't think that the blue curve is so bad, actually, and adding these
+    values as reference might help to put the results into context.}}
 	\label{fig:error_distributions}	
@@
 The positive performance with 150\,GHz is not unexpected, as 150\,GHz is highly sensitive to ice hydrometeors and cloud water; but using 89\,GHz along with 150\,GHz gives a slightly better performance.
-The channel 89\,GHz is affected by surface emissivity and is relatively less sensitive to cloud water content, however its sensitivity to warm clouds in the lower troposphere could be important.
+The channel 89\,GHz is affected by surface emissivity and is less sensitive to cloud water content, however its sensitivity to warm clouds in the lower troposphere could be important.
 We also investigate the impact of two temperature sounding channels (MWHS-2 channel 6 and 7).
@@
 Such cases are mostly associated with thin cirrus clouds, which have very small influence at 89 and 150\,GHz.
-Without additional information from other channels we cannot expect QRNN train better.
+Without additional information from other channels we cannot expect QRNN to perform better.
 Among the other available channels, the overlapping weighting functions of 183\,GHz can provide auxiliary information to train QRNN.
@@
 Correlated errors are also undesirable for DA systems, but in future if the operational centres progress with approaches dealing with correlated observation errors, concurrent use of 89, 150 and 183\,GHz channels would give the best cloud correction performance.
+
+\todo{
+    The problem that QRNN faces is more than just incomplete orthogonal information. Even when the information
+    in 89 and 150 would be orthogonal it would still not be sufficient to do perfect cloud correction. The reason
+    is rather that the problem in general is ill-posed and thus at least under- but probably also over constrained
+    (the latter due to measurement noise). 
+  }
 
@@
 However the cases with low accuracy are associated with high uncertainty, and can be used with caution.
-\todo{I could not follow the last sentence.}
 
@@
 Correcting hydrometeor impact for cases without complete complementary information is a challenge for QRNN and always limit its performance.
-\todo{Cases without orthogonal information are note what I understand as out-of-distribution samples.
+\todo{Cases without orthogonal information are not what I understand as out-of-distribution samples.
 Moreover, rare cases are rather a matter of training set size.
@@
 The model is trained for multiple values of layer widths and hidden layers, and the best configuration is selected by evaluating the predictions over validation dataset.
-Similarly, the training process is optimized by performing a grid search different training parameters such as : batch size, learning rate, number of epochs etc.
+\todo{Comment: If I remember correctly you do not mention the validation set in Sect.
+2} Similarly, the training process is optimized by performing a grid search different training parameters such as : batch size, learning rate, number of epochs etc.
 We use quantile loss and CRPS for evaluation of the model performance.

### 2020-11-09 Article/ici_submm_cloudcorr.tex
merged table 5 and 6, addded Simon's suggestions

@@
 measurements (no ``background'' data involved). Not only a best estimate is
-provided, but also a case specific uncertainty. This information can be used as a pure filter, by rejecting data where the correction exceeds some threshold value. This threshold value should be
-relatively low, to not introduce a bias in filtered dataset. However, even
+provided, but also a case specific uncertainty. This information could be used as a pure filter, by rejecting data where the correction exceeds some threshold value. However, even
 better is to replace the original value with the predicted NFCS value when
@@
 is shown below that a basically bias free cloud correction can be obtained.
-This feature removes the need of threshold value, as long as the retrieval or
+This feature also removes the need of threshold value, as long as the retrieval or
 assimilation system can incorporate the uncertainty of the corrected value. As
@@
 ICI and AWS frequencies are simulated with Atmospheric Radiative Transfer Simulator (ARTS, \citet{buehler:artst:18}).
-CloudSat\citep{Stephens2002cloudsat} profiles during August 2015 are randomly selected for forward simulations.
-The input data are restricted between $60^{\degree}$S to $60^{\degree}$N, and surface is below 500\,m.
+CloudSat\citep{Stephens2002cloudsat} profiles from August 2015 are randomly selected for forward simulations.
+The input data are restricted between $60\unit{^{\degree}S}$ to
+$60\unit{^{\degree}N}$, and surface is below 500\,m.
 Both clear-sky and all-sky scenarios  are simulated.
@@
 \label{sec:QRNN_configuration}
-In the study, two QRNN configurations are formulated for cloud-correction.
-The basic construction of both is to individually train for each of the available 183\,GHz channels, using certain input training data.
-The input data is all-sky brightness temperatures from selected input channels and/or additional data like land/sea mask.
-The output in both configurations is the posterior distribution of NFCS values for the target 183\,GHz channel.
-The two configurations differ only by the number of input 183\,GHz channels used in the training process:
+In the study, two QRNN configurations are formulated for cloud-correction. The
+basic construction of both is that a separate network is trained for each
+183\,GHz channel to correct, using certain input data. The input data is all-sky brightness temperatures from selected input channels and/or additional data like land/sea mask. The
+output in both configurations is the posterior distribution of NFCS values for
+the target 183\,GHz channel. The two configurations differ only by the number of
+input 183\,GHz channels used in the training process:
 
@@
 This is in contrast with other conventional correction/filtering methods, which give out only point estimates.
-However, for most analysis, usually a single point estimate is required.
+However, for most applications only a single point estimate is required.
 In Bayesian analysis, usually the posterior mean or posterior median are selected as point estimates.
-In this study, we assume the posterior median to be the best estimate for the predicted NFCS value ($\ynfcs$).
+In this study, we chose the posterior median as the best estimate for the predicted NFCS value ($\ynfcs$).
 To analyse the ability of QRNN in correctly predicting the point estimate, deviation of the median value from the corresponding true value ($\yonfcs$) is evaluated using common performance indicators like bias, mean absolute error (MAE) and standard deviation (STD).
@@
 
-For probabilistic predictions, accuracy of the point estimate is inadequate to gauge the complete performance.
-In a successful QRNN training, QRNN learns to predict not only an accurate point estimate but also the correct underlying uncertainty.
-An ideal QRNN output should be sharp or in other words, all predicted quantiles should be concentrated in the vicinity of the point estimate.
-The predicted posterior distribution should also be well calibrated, that is, reflect the a priori probability distribution.
-A straightforward way to compare the two distributions is to plot the frequency of predictions and frequency of the true value in different prediction intervals.
-This is also commonly known as calibration plot.
-In a well-calibrated QRNN model, the calibration plot should follow the straight line y = x.
-Another way to assess how well the predicted posterior distribution reflects the observed errors is to compare the predicted and observed errors.
-The predicted error is deviation of a random sample drawn from the posterior distribution to its median.
-In this study, we analyse both the calibration plot and the predicted errors to assess the correctness of predicted uncertainties.
-
-All evaluation results described in the study have been made on the test dataset.
+For probabilistic predictions, accuracy of the point estimate is inadequate to
+gauge the complete performance. In a successful QRNN training, QRNN learns to
+predict not only an accurate point estimates but also the correct underlying
+uncertainty. An ideal QRNN output should be sharp or in other words, all
+predicted quantiles should be concentrated in the vicinity of the point
+estimate, but at the same time, the predicted posterior distribution should be
+well calibrated, that is, the predicted distribution should reflect actually
+observed frequencies. A straightforward way to compare the two distributions is
+to plot the frequency of predictions and frequency of the true value in
+different prediction intervals. This is also commonly known as calibration plot.
+In a well-calibrated QRNN model, the calibration plot should follow the straight
+line $y = x$. Another way to assess how well the predicted posterior distribution
+reflects the observed errors is to compare the predicted and observed errors.
+The predicted error is the deviation of a random sample drawn from the posterior
+distribution to its median. In this study, we analyse both the calibration plot
+and the predicted errors to assess the correctness of predicted uncertainties.
+
+All evaluation results except hyper-parameter tuning, described in the study have been made on the test dataset.
+Hyper-parameter tuning is made on the training dataset (see Appendix~\ref{appendix:hyperparamter}).
 
@@
 Noise is also plotted for reference.
-The label ``All-sky'' represents the all-sky simulations, ``Predicted(All)'' denotes the predicted point estimates, while ``Predicted(5\,K)'' refers to the predicted point estimates but where cases with cloud correction greater than 5\,K are excluded.}
+The label ``All-sky'' represents the all-sky simulations, ``Predicted(All)'' denotes the predicted point estimates.
+The error distribution achieved with scattering index (SI) filtering is also shown.
+}
 	\label{fig:error_distribution_mwhs14}	
@@
 	\label{tab:error_statistics_mwhs_14}
-	\begin{tabular}{lrr|rr|rr|rr|rr}
+	\setlength{\tabcolsep}{4pt}
+	\begin{tabular}{lrr|rr|rr|rr|rr|rr}
 		\tophline
-		&\multicolumn{2}{c|}{Simulations}& \multicolumn{6}{c|}{QRNN-single} & \multicolumn{2}{c}{QRNN-all}\\
-		\cline{2-11}
+		&\multicolumn{2}{c|}{Simulations}& \multicolumn{6}{c|}{QRNN-single} & \multicolumn{2}{c|}{QRNN-all} & \multicolumn{2}{c}{Pure filtering}\\
+		\cline{3-13}
 		%		\hline
-		&   Clear-sky &   All-sky &  \multicolumn{2}{c|}{89+150\,GHz} & \multicolumn{2}{c|}{89+150+118\,GHz} & \multicolumn{2}{c|}{150\,GHz} & \multicolumn{2}{c}{89+150+183\,GHz}\\		
-		&			   &			& All & Pred.(5\,K) & All & Pred.(5\,K) & All & Pred.(5\,K)  & All & Pred.(5\,K)\\
-		\middlehline
-		Bias      &  0.00 &  -0.84 & -0.09 & -0.08(3.3\%) & -0.04 & -0.03(3.4\%) & -0.09 & -0.09(3.2\%) & -0.09(3.3\%) & -0.08(3.3\%)  \\
-		MAE       &  0.80 &   1.45 &  0.88 &  0.86 &  0.89 &  0.87 &  0.89 &  0.87 &  0.62 &  0.59\\
-		STD       &  1.00 &   3.90 &  1.19 &  1.14 &  1.19 &  1.15 &  1.21 &  1.16 &  0.90 &  0.83\\
-		skewness & -0.00 & -14.34 & -1.11 & -0.93 & -1.00 & -0.84 & -0.88 & -0.98 & -1.58 & -1.62\\
+		&   Clear-sky &   All-sky &  \multicolumn{2}{c|}{89+150\,GHz} & \multicolumn{2}{c|}{89+150+118\,GHz} & \multicolumn{2}{c|}{150\,GHz} & \multicolumn{2}{c|}{89+150+183\,GHz}& SI & B183\\		
+		&			   &			& All & Pred.(5\,K) & All & Pred.(5\,K) & All & Pred.(5\,K)  & All & Pred.(5\,K)&&\\
+		\middlehline
+bias     & -0.00 &  -0.83 & -0.09 & -0.08 & -0.04 & -0.03 & -0.09 & -0.09 & -0.09 & -0.08 & -0.24 & -0.51\\
+mae      &  0.80 &   1.44 &  0.88 &  0.86 &  0.89 &  0.87 &  0.89 &  0.87 &  0.62 &  0.59 &  0.92 &  1.14\\
+std      &  1.00 &   3.89 &  1.19 &  1.14 &  1.19 &  1.15 &  1.21 &  1.16 &  0.90 &  0.83 &  1.26 &  1.83\\
+skewness &  0.01 & -14.40 & -1.11 & -0.96 & -1.02 & -0.86 & -0.89 & -1.02 & -1.61 & -1.58 & -1.79 & -3.45\\
+rejection&  -	 & - 	  & - 	  & 3.3\% & - 	  & 3.4\% & -     & 3.2\% & -     & 3.3\% & 28.1\%& 3.5\%\\
 \bottomhline
@@
 
-The posterior distribution of NFCS values obtained from experiment 89+150\,GHz is similar to one shown in Fig.~\ref{fig:posterior_distribution_I1V}.
+The posterior distribution of NFCS values obtained from experiment 89+150\,GHz is similar to the one shown in Fig.~\ref{fig:posterior_distribution_I1V}.
 The median value is chosen as the point estimate (see Sect.~\ref{sec:validation}).
@@
 
-Further we investigated that if filtering the predictions with low accuracy could help in improving the error distributions.
+Further we investigated whether filtering the predictions with low accuracy could help in improving the error distributions.
 For filtering such cases, we assume that predictions with cloud correction greater than 5\,K are cases associated with large deviations.
@@
 Further in the text we refer this filter as ``B183''.
-The results obtained with SI and B183 are displayed in Table~\ref{tab:SI_statistics}.
+The results obtained with SI and B183 are displayed in last two columns of Table~\ref{tab:error_statistics_mwhs_14}.
 With SI threshold = 5\,K, almost 30\% of the data is rejected, yet the resulting error distributions are poorer as compared to QRNN.
@@
 	\caption{ Error statisics for MWHS-2 channels 11, 12, 13 and 15 from QRNN-single experiment 89+150\,GHz.
-The labels ``All'' and ``Pred.(5\,K)' are same as described in Table~\ref{tab:error_statistics_mwhs_14}.}
+The labels ``All'' and ``Pred.(5\,K)' are same as described in Table~\ref{tab:error_statistics_mwhs_14}.
+The statistics from existing filtering approaches: scattering index (SI), and scheme by \citet{buehler:aclou:07} are also provided.
+The latter is denoted as ``B183''.}
 	\label{tab:error_statistics_mwhs_others}
-	\begin{tabular}{lrrr|rr}
+	\begin{tabular}{lrrr|rr|rr}
 		\tophline
-		&&\multicolumn{2}{c|}{Simulations}& \multicolumn{2}{c}{QRNN-single} \\
-		\cline{2-6}
+		&&\multicolumn{2}{c|}{Simulations}& \multicolumn{2}{c|}{QRNN-single} & \multicolumn{2}{c}{Pure filtering} \\
+		\cline{2-8}
 		%		\hline
-		& &  Clear-sky &   All-sky &  \multicolumn{2}{c}{89+150\,GHz}  \\
-		&	&		   &			& All & Pred.(5K)\\
-		\middlehline
-		Channel 11  &   Bias      & 0.00 &  -0.16 & -0.03 & -0.03(0.2\%)  \\
-				    &	MAE       & 0.80 &   0.89 &  0.79 &  0.79  \\
-					&	STD       & 1.00 &   1.71 &  1.03 &  1.01  \\
-					&	skewness & 0.01 & -20.18 & -0.68 & -0.45  \\
-		\middlehline
-		Channel 12  & Bias      & -0.00 &  -0.28 & -0.05 & -0.05(0.6\%)  \\
-					& MAE       &  0.80 &   0.98 &  0.81 &  0.80  \\
-					& STD       &  1.00 &   2.26 &  1.07 &  1.05  \\
-					& skewness &  0.00 & -20.72 & -0.91 & -0.70  \\
-		\middlehline
-		Channel 13  & Bias      & -0.00 &  -0.52 & -0.08 & -0.07(1.6\%)  \\
-					& MAE       &  0.80 &   1.17 &  0.84 &  0.83  \\
-					& STD       &  1.00 &   3.04 &  1.13 &  1.10  \\
-					& skewness &  0.02 & -17.85 & -1.14 & -0.98 \\		
-		\middlehline
-		Channel 15  & Bias      & -0.00 &  -1.28 & -0.07 & -0.06(5.6\%)  \\
-					& MAE       &  0.80 &   1.87 &  0.97 &  0.92 \\
-					& STD       &  1.00 &   5.08 &  1.35 &  1.25 \\
-					& skewness & -0.00 & -11.15 & -0.60 & -0.83  \\ 
-		\bottomhline
-	\end{tabular}
-\end{table*}
-\begin{table*}[t]
-	\caption{Channel wise error statistics obtained after filtering MWHS-2 humidity observations  according to scattering index (SI) and filtering described by \citet{buehler:aclou:07}.
-The latter is denoted as  B183.
-}
-	\label{tab:SI_statistics}
-	\begin{tabular}{lrr|rr|rr|rr|rr}
-		\tophline
-		& \multicolumn{2}{c|}{Channel 11} & \multicolumn{2}{c|}{Channel 12} & \multicolumn{2}{c|}{Channel 13} & \multicolumn{2}{c|}{Channel 14} & \multicolumn{2}{c}{Channel 15}\\
-			& SI & B183 & SI & B183 & SI & B183 & SI & B183 & SI & B183\\
-			\cline{2-11}
-		Bias 	 &-0.04	& -0.05	& -0.07 &  -0.15 &  -0.14 & -0.29	&-0.23 &  -0.51 & -0.33 &  -0.81\\
-		MAE  	 & 0.81	&  0.81	&  0.82 &	0.86 &	 0.85 &  0.97   & 0.92 &   1.14 &  1.03 &	1.44\\
-		STD  	 &1.02	&  1.03	&  1.04 &	1.14 &	 1.1  &  1.39	& 1.26 &   1.83 &  1.53 &	2.64\\
-		Skewness &-0.12 & -0.24 & -0.38 & -0.86  &  -0.91 & -2.23   &-1.79 &  -3.45 & -2.85 &  -4.41\\
+		& &  Clear-sky &   All-sky &  \multicolumn{2}{c|}{89+150\,GHz}    & SI & B183  \\
+		&	&		   &			& All & Pred.(5K) &&\\
+		\middlehline
+		Channel 11  &   Bias      & 0.00 &  -0.16 & -0.03 & -0.03		 &-0.04	& -0.05 \\
+				    &	MAE       & 0.80 &   0.89 &  0.79 &  0.79  		 & 0.81	&  0.81 \\
+					&	STD       & 1.00 &   1.71 &  1.03 &  1.01 		 & 1.02	&  1.03 \\
+					&	skewness  & 0.01 & -20.18 & -0.68 & -0.45 		 &-0.12 & -0.24 \\
+					& rejection   & -    & -      & -	  & 0.2\%        & 28.1\% & 3.5\%  \\
+		\middlehline
+		Channel 12  & Bias      & -0.00 &  -0.28 & -0.05 & -0.05		&  -0.07 & -0.15 \\
+					& MAE       &  0.80 &   0.98 &  0.81 &  0.80  		&   0.82 &	0.86 \\
+					& STD       &  1.00 &   2.26 &  1.07 &  1.05  		&  1.04  &  1.14 \\
+					& skewness  &  0.00 & -20.72 & -0.91 & -0.70  		&  -0.38 & -0.86 \\
+					& rejection & -    & -      & -	  & 0.6\%        & 28.1\% & 3.5\%  \\
+		\middlehline
+		Channel 13  & Bias      & -0.00 &  -0.52 & -0.08 & -0.07 		& -0.14  & -0.29 \\
+					& MAE       &  0.80 &   1.17 &  0.84 &  0.83  		&  0.86  &  0.97 \\
+					& STD       &  1.00 &   3.04 &  1.13 &  1.10  		&  112  &	1.39 \\
+					& skewness  &  0.02 & -17.85 & -1.14 & -0.98  		& -0.91  & -2.23 \\	
+					& rejection   & -    & -      & -	  & 1.6\%        & 28.1\% & 3.5\%  \\	
+		\middlehline
+		Channel 15  & Bias      & -0.00 &  -1.28 & -0.07 & -0.06        & -0.33 &  -0.81 \\
+					& MAE       &  0.80 &   1.87 &  0.97 &  0.92 		&  1.03 &	1.44 \\
+					& STD       &  1.00 &   5.08 &  1.35 &  1.25 		&  1.53 &	2.64 \\
+					& skewness  & -0.00 & -11.15 & -0.60 & -0.83 		& -2.85 &  -4.41 \\ 
+					& rejection & -     & -      & -	 & 5.6\%        & 28.1\% & 3.5\%  \\
 		\bottomhline
@@
 
-A comparison with SI based filtering and B183 is displayed in  Table~\ref{tab:SI_statistics}.
+A comparison with SI based filtering and B183 is displayed in last columns of Table~\ref{tab:error_statistics_mwhs_others}.
 For channel 11 the performance of QRNN is comparable to both SI and B183.
-Similar is the case with channel 12, though the results from B183 are slightly poor.
+Similar is the case with channel 12, though the results from B183 are slightly poorer.
 Both these channels are mostly transparent to hydrometeor impact, and the filtering schemes work well.
@@
 The calibration of the prediction intervals on the testing dataset is displayed in Fig.~\ref{fig:calibration_mwhs}.
-For the entire dataset, the predictions follow the y=x line, i.e.
-they are perfectly calibrated with the a priori distribution.
+For the entire dataset, the predictions follow the $y=x$ line, i.e.
+the predicted uncertainties are perfectly calibrated with the errors observed on the test data.
 However for the cases with correction greater than 5\,K, the distribution is poorly calibrated for higher quantiles.
-The curve lies below the y=x line indicating that the prediction intervals are too narrow.
+The curve lies below the$y =x$line indicating that the prediction intervals are too narrow.
 This is in agreement with the wide spread of predictions over the  higher quantiles (Fig.~\ref{fig:prediction_uncertainty_mwhs}).
-However such cases are few and filtering them results in well calibrated QRNN predictions.
+However such cases are less than 6\% of the dataset and filtering such cases does not affect the overall QRNN calibration.
 
@@
 
-For other humidity channels, the predicted uncertainties followed similar behaviour and the not shown.
+For other humidity channels, the predicted uncertainties followed similar behaviour and are not shown.
 
@@
 Fig.~\ref{fig:calibration_I1V} shows the calibration of the prediction intervals for I2V.
-The predictions for the complete test dataset are well calibrated and follow the y=x line.
+The predictions for the complete test dataset are well calibrated and follow the$y =x$line.
 On the other hand, when only the cases with  cloud correction greater than 10\,K are considered, the predictions in all the intervals are poorly calibrated.
-In this case the calibration curve lies slightly below the y=x line for higher quantiles, indicating that the predicted intervals are too narrow, or the uncertainty is underestimated.
+In this case the calibration curve lies slightly below the $y=x$ line for higher quantiles, indicating that the predicted intervals are too narrow, or the uncertainty is underestimated.
 
@@
 The poorly calibrated predictions are a consequence of cases with different underlying a priori distribution.
-Predictions with high error originate from cases with high cloud impact or cloudy cases with no orthogonal information.
+Predictions with high error originate from cases with high cloud impact or cases with no orthogonal information.
 Such cases have a significantly distinct a priori distribution as compared to clear cases, which dominate the training dataset and influence the a priori information.
-Additional information in form of more observational data or additional training inputs is required to improve QRNN prediction accuracy for such cases.
-However the cases with low accuracy are associated with high uncertainty, and can be used with caution.
+The distribution of rare cases can be improved by increasing the training dataset size, but lack of orthogonal information can only be balanced by including additional training inputs, e.g.
+brightness temperatures for other channels.
 
@@
 Most of the existing cloud filtering schemes work well only at removing cases with high cloud impact, and as a consequence, the error distributions are highly skewed.
-To use these observations correctly data assimilation schemes often inflate their asymmetric error distributions at the cost of artificially suppressing the observational impact.
+To use these observations correctly, data assimilation schemes often inflate their asymmetric error distributions at the cost of artificially suppressing the observational impact.
 This is not the optimal solution but the best which can be achieved with present sensors.
-However, the symmetric error distributions obtained from QRNN allow us to effectively utilize more than 95\% of the data without the need for error inflation.
+However, the symmetric error distributions obtained from QRNN allow us to effectively utilize more than 94\% of the data without the need for error inflation.
 
@@
 In comparison to existing clear-filtering approaches, QRNN gives comparable or better performance and with minimal rejection of data.
-The accuracy of QRNN is affected by one single limitation, that is the prediction of ``out of distribution'' cases.
-Out of distribution cases are those which belong to a different a priori distribution than the one QRNN is trained on.
-Such cases can be the ones which occur infrequently, or those which lack any orthogonal information.
-The representation of the former can be improved with larger training datasets.
+The accuracy of QRNN is affected by one single limitation, that is presence of cases which belong to a different a priori distribution than the one QRNN is trained on.
+Such cases can be either the ones which occur infrequently, or those which lack any orthogonal information.
+The representation of the former can be improved to represent reality by simply choosing larger training datasets.
 However for the latter, improving their a priori distribution is not trivial.
@@
 %
-Cloudsat profiles during August 2015 were randomly selected for forward simulations.
+CloudSat profiles during August 2015 were randomly selected for forward simulations.
 The input data were restricted between $60^{\degree}$S to $60^{\degree}$N, and surface is below 500\,m.

### 2020-11-10 Article/ici_submm_cloudcorr_simon.tex

@@
 clear-sky data can be preserved.
-
-The estimation of NFCS values makes use of a special type of machine learning,
-denoted as Quantile Regression Neural Network (QRNN,
-\citet{pfreundschuh:aneur:18}). Unlike standard usage of machine learning where
-only some kind of best estimate is provided, QRNN works in a Bayesian fashion
-and instead gives a description of the posterior uncertainty. More precisely,
-QRNN outputs an user specified set of quantiles that gives a discrete
-description posterior distribution, that can be processed to derive e.g.\ the
-expectation value.
 

### 2020-11-10 Article/ici_submm_cloudcorr.tex
some more editing, cleaned up text and ref

@@
 In this study, we present a methodology to identify and correct the cloud impact in microwave humidity radiances.
-A channel specific quantile regression neural network (QRNN) based approach is formulated to estimate the posterior distributions of noise free clear sky (NFCS) radiances.
-The applicability of the approach is demonstrated by application to a present sensor: MWHS-2 (MicroWave humidity sounder 2).
-With the future outlook, the applicability to sub-millimeter (sub-mm) channels is also investigated.
+A channel specific quantile regression neural network (QRNN) based approach is formulated to estimate the posterior distributions of noise free clear-sky (NFCS) radiances.
+The applicability of the approach is demonstrated by application to a present sensor: MicroWave Humidity Sounder-2 (MWHS-2).
+With the future outlook, the applicability to sub-millimeter (sub-mm) channels is also analysed.
 The results are compared against the NFCS simulations.
-With the present sensors, the approach is successful in correcting most of the cases with large negative departures, but a fraction cases end up with partial correction.
-In spite of the cases with residual cloud impact, the results from QRNN are better than what operational cloud filtering techniques like scattering index can achieve.
+With the present sensors, the approach is partially successful in correcting the negative departures.
+Almost all cases with high cloud impact are corrected, but thin cirrus clouds cannot be fully corrected.
+In spite of the partial performance, the results from QRNN are better than what operational cloud filtering techniques like scattering index can achieve.
 On the other hand, when sub-mm observations from ICI are used to correct the cloud impact, QRNN can successfully correct most of the cases with cloud impact.
-Only 2-4\% of the cases are partially corrected and these can be easily removed by a simple filtering.
-The resulting error distributions are almost symmetric with very low spread.
+Only 2-6\% of the cases are partially corrected and these can be easily removed by a simple filtering.
+The resulting error distributions are almost symmetric with a very low spread.
 The methodology also works well when only one of the higher frequencies (325\,GHz) is available.
@@
 numerical weather prediction (NWP). Usage of passive microwave data by
-``all-sky'' assimilation in global NWP is growing in \citep{geer2017growing},
-but 183\,GHz data are still mainly used in a clear sky fashion
+``all-sky'' assimilation in global NWP is growing \citep{geer2017growing},
+but 183\,GHz data are still mainly used in a clear-sky fashion
 \citep{geer2018all}. The latter is particularly true in NWP of regional scope
@@
 Anyhow, both clear-sky and all-sky assimilation require identification of cloud affected observations.
-``Scattering index'' \cite{geer2015scatteringindex} is one of the approaches used.
+``Scattering index'' \citep{geer2015scatteringindex} is one of the approaches used.
 It is based on brightness temperature differences between 89 and 150\,GHz.
@@
 To our best knowledge, so far only estimates of mean and worst case errors have been provided.
-Some cases with relatively high cloud impact will likely be missed, while most cases are clear sky from start.
+Some cases with relatively high cloud impact will likely be missed, while most cases are clear-sky from start.
 As the remaining cloudy cases can cause significant biases, the likely solution is to apply a quite conservative (high) error estimate.
-However, this will unnecessary downgrade the value of the truly clear sky cases and the observations are used in a non-optimal manner.
+However, this will unnecessary downgrade the value of the truly clear-sky cases and the observations are used in a non-optimal manner.
 
@@
 assimilation system can incorporate the uncertainty of the corrected value. As
-also will be shown, the uncertainty for originally clear sky data is determined
+also will be shown, the uncertainty for originally clear-sky data is determined
 by noise, but the uncertainty increases with magnitude of correction.
@@
 
-The estimation of NFCS values makes use of a special type of machine learning,
-denoted as Quantile Regression Neural Network (QRNN,
-\citet{pfreundschuh:aneur:18}). Unlike standard usage of machine learning where
-only some kind of best estimate is provided, QRNN works in a Bayesian fashion
-and instead gives a description of the posterior uncertainty. More precisely,
-QRNN outputs an user specified set of quantiles that gives a discrete
-description posterior distribution, that can be processed to derive e.g.\ the
-expectation value.
-
 The proposed cloud correction scheme makes use of a Quantile Regression Neural
-Network (QRNN) to obtain a probabilistic prediction of the NFCS value. Unlike
-traditional neural networks techniques, which typically only provide a point
+Network (QRNN, \citet{pfreundschuh:aneur:18}) to obtain a probabilistic prediction of the NFCS value. Unlike traditional neural networks techniques, which typically only provide a point
 estimate of the target variable, QRNNs are trained to predict an arbitrary set
@@
 The main focus of this study is the potential of proposed cloud-correction
-method using sub-millimetre observations, which will become available
+method using sub-millimetre (sub-mm) observations, which will become available
 operationally with the launch of the Ice Cloud Imager (ICI,
-\citet{eriksson:towar:20}) on board the next generation of polar orbiting
-meteorological satellites (MetOP-SG), but will likely also be included in
+\citet{eriksson:towar:20}) on board the next generation of EUMETSAT Polar System - Second Generation (EPS-SG), but will likely also be included in
 several smaller missions (such as Artic Weather Satellite (AWS); presented
@@
 hydrometeors. For high altitude cirrus clouds, these frequencies have a stronger
-signal than 183\,Ghz. In some cloudy situations it could be possible that the
-impact at 183 GHz is of the order of thermal noise and modelling uncertainties,
-while the impact at 325 GHz is significantly higher. Secondly, the proposed
+signal than 183\,GHz. In some cloudy situations it could be possible that the
+impact at 183\,GHz is of the order of thermal noise and modelling uncertainties,
+while the impact at 325\,GHz is significantly higher. Secondly, the proposed
 cloud correction methods allows integrating ICI sub-mm observations in
@@
 %
-\subsubsection{ MicroWave Humidity Sounder 2}
+\subsubsection{ MicroWave Humidity Sounder-2}
 %
@@
 MWHS-2 a cross track scanning microwave radiometer and measures 15 frequencies in the range 89-191\,GHz.
-89\,GHz and 150\,GHz are window channels, five humidity sounding channels are centered at 183.31\,GHz and eight temperature sounding channels are centered at 118.75\,GHz oxygen absorption line.
+89\,GHz and 150\,GHz are window channels, five humidity sounding channels are centered at 183.31\,GHz, and eight temperature sounding channels are centered at 118.75\,GHz oxygen absorption line.
 The five humidity sounding channels are similar to ATMS.
@@
 
-Ice Cloud Imager (ICI) is a new instrument on board EPS-SG(EUMETSAT Polar System - Second Generation) satellite Metop-SG.
-Metop-SG is scheduled for launch in 2023, and it will make ICI the first operational sensor observing Earth using sub-millimeter(sub-mm) wavelengths.
-The main objective of ICI is to use high frequency channels for measuring ice cloud properties and improve the representation of ice clouds in regional and global NWP models.
+Ice Cloud Imager (ICI) is a new instrument on board EPS-SG satellite MetOp-SG (Meteorological Operational - Second Generation).
+MetOp-SG is scheduled for launch in 2023, and it will make ICI the first operational sensor observing Earth using sub-mm wavelengths.
+The main objective of ICI is to use high frequency channels for measuring ice cloud properties, and improve the representation of ice clouds in regional and global NWP models.
 ICI is a conically scanning radiometer that will measure 13 frequencies from 183\,GHz up to 664\, GHz.
 Among all available channels, 183.31\,GHz, 325.15\,GHz and 448.00\,GHz, will measure vertical polarization;  while other channels around frequencies 243.20\,GHz and 664.00\,GHz are ``window channels'' and will measure both vertical and horizontal polarization.
-The instrument will observe earth from a mean altitude of 832\,km with sensor viewing angle 44.767$^\circ$(measured from nadir).
+The instrument will observe earth from a mean altitude of 832\,km with sensor viewing angle 44.767$^\unit{^{\degree}}$(measured from nadir).
 For all the channels, the mean footprint size is about 15\,km, but the exact geo-location of samples differs.
-Therefore a simultaneous utilization of data from different channels shall require remapping to a common footprint \citep{eriksson:towar:20}.
-
-For this study, we conducted the forward simulations at frequencies: 183.31\,GHz, 325.15\,GHz, 448.00\,GHz and 664.00\,GHz(See Table~\ref{tab:ICI_MWI_channels}).
+Therefore, a simultaneous utilization of data from different channels shall require remapping to a common footprint \citep{eriksson:towar:20}.
+
+For this study, we conducted the forward simulations at frequencies: 183.31\,GHz, 325.15\,GHz, 448.00\,GHz and 664.00\,GHz (See Table~\ref{tab:ICI_MWI_channels}).
 For brevity, we assume that all simulations are mapped to a common footprint.
@@
 		\middlehline
-		AWS-32	&	176.311    & 2000	&		\\
-		AWS-33	&	178.811    & 2000 	&	\\
-		AWS-34	&	180.311    & 1000 	&	\\
-		AWS-35	&	181.511    & 1000 	&	 \\
-		AWS-36	&	182.311    & \phantom{0}500  &	 \\
+		AWS-32	&	176.31    & 2000	&	0.45	\\
+		AWS-33	&	178.81    & 2000 	&	0.45\\
+		AWS-34	&	180.31    & 1000 	&	0.64\\
+		AWS-35	&	181.51    & 1000 	&	0.64 \\
+		AWS-36	&	182.31    & \phantom{0}500  &	0.88 \\
 		AWS-41  & 325.15$\pm$6.60    & 2800 	 &0.60\\
@@
 CloudSat\citep{Stephens2002cloudsat} profiles from August 2015 are randomly selected for forward simulations.
-The input data are restricted between $60\unit{^{\degree}S}$ to
-$60\unit{^{\degree}N}$, and surface is below 500\,m.
+The input data are restricted between $60\unit{^{\degree}S}$ to $60\unit{^{\degree}N}$, and surface is below 500\,m.
 Both clear-sky and all-sky scenarios  are simulated.
@@
 For ICI and AWS, 220\,000 and 140\,000 cases are simulated, respectively.
-All AWS sensor viewing angles (from $0^\circ$ to $45^\circ$) are simulated, but the results described in this study are based on nadir viewing angle.
+All AWS sensor viewing angles (from $0^{\degree}$ to $45^{\degree}$) are simulated, but the results described in this study are based on nadir viewing angle.
 Simulations for all three sensors are noise free, so to incorporate the measurement uncertainties, whenever needed, gaussian noise is added to according to the channel NE$\Delta$T (see Table~\ref{tab:specifications_MWHS2} - Table~\ref{tab:specifications_AWS}).
@@
 The task that we aim to solve in this study is to predict the NFCS brightness
-temperature \todo{$\ynfcs$, define it} at a given $183\unit{GHz}$ channel from a vector of
+temperature \todo{$\ynfcs$} at a given $183\unit{GHz}$ channel from a vector of
 all-sky observations $\y$. Since the information-content of the
@@
 quantile loss is used in this study as a performance criterion for the tuning of
-the hyper parameters of the QRNN (see Appendix~\ref{appendix:hyperparamter}). In
+the hyper-parameters of the QRNN (see Appendix~\ref{appendix:hyperparamter}). In
 addition to the quantile loss, also the Continuously Ranked Probability Score
@@
 183\,GHz channel to correct, using certain input data. The input data is all-sky brightness temperatures from selected input channels and/or additional data like land/sea mask. The
-output in both configurations is the posterior distribution of NFCS values for
+output in both configurations is the posterior distribution of $\ynfcs$ for
 the target 183\,GHz channel. The two configurations differ only by the number of
@@
 For all three sensors described in this study, one or both of the above QRNN configurations are used.
-The selection of input channels is sensor dependent and is described in detail when introduced later.
+The selection of input channels is sensor dependent, and is described in detail when introduced later.
 
@@
 \end{figure}
-QRNN predictions are posterior probability distribution of the NFCS values described over the chosen quantiles.
+QRNN predictions are posterior probability distribution of $\ynfcs$ described over the chosen quantiles.
 In order to facilitate the interpretation of results, examples of QRNN outputs are shown in Fig.~\ref{fig:posterior_distribution_I1V}.
-This example illustrates the predicted quantiles for three different cases.
+These examples illustrate the predicted quantiles for three different cases.
+The quantiles provide a quantification of the prediction uncertainty through a probabilistic upper and lower bound for each case.
 This is in contrast with other conventional correction/filtering methods, which give out only point estimates.
@@
 In Bayesian analysis, usually the posterior mean or posterior median are selected as point estimates.
-In this study, we chose the posterior median as the best estimate for the predicted NFCS value ($\ynfcs$).
+In this study, we chose the posterior median as the best estimate for $\ynfcs$.
 To analyse the ability of QRNN in correctly predicting the point estimate, deviation of the median value from the corresponding true value ($\yonfcs$) is evaluated using common performance indicators like bias, mean absolute error (MAE) and standard deviation (STD).
@@
 gauge the complete performance. In a successful QRNN training, QRNN learns to
-predict not only an accurate point estimates but also the correct underlying
+predict not only an accurate point estimate but also the correct underlying
 uncertainty. An ideal QRNN output should be sharp or in other words, all
 predicted quantiles should be concentrated in the vicinity of the point
-estimate, but at the same time, the predicted posterior distribution should be
+estimate. Nevertheless, the predicted posterior distribution should also be
 well calibrated, that is, the predicted distribution should reflect actually
@@
 
-All evaluation results except hyper-parameter tuning, described in the study have been made on the test dataset.
+All evaluation results except hyper-parameter tuning, described in the study, have been made on the test dataset.
 Hyper-parameter tuning is made on the training dataset (see Appendix~\ref{appendix:hyperparamter}).
@@
 We use MWHS-2 to demonstrate the results.
-The choice is motivated by the fact that MWHS-2 has five complementary 183\,GHz channels, along with additional 118\,GHz channel.
+The choice is motivated by the fact that MWHS-2 has five complementary 183\,GHz channels, along with additional 118\,GHz channels.
 In order to formulate and test the correction approach, multiple QRNN experiments are performed for MWHS-2 channel 14.
-Later the methodology is extended to other 183\,GHz channels.
+Later the optimal experiment is extended to other 183\,GHz channels.
 A brief comparison of the results is also made against existing cloud filtering methods.
@@
 The label ``All'' denotes the entire dataset of predicted point estimates, while ``Pred.(5\,K)'' refers to the predicted point estimates but where cases with cloud correction greater than 5\,K are excluded.
-}
+The last two columns show the statistics obatined after filtering cloudy cases according to scattering index (SI) and scheme by \citet{buehler:aclou:07} (B183).
+Bias, MAE, STD are in K, skewness in dimensionless.}
 	\label{tab:error_statistics_mwhs_14}
@@
 		&\multicolumn{2}{c|}{Simulations}& \multicolumn{6}{c|}{QRNN-single} & \multicolumn{2}{c|}{QRNN-all} & \multicolumn{2}{c}{Pure filtering}\\
-		\cline{3-13}
+		\cline{2-13}
 		%		\hline
@@
 		\middlehline
-bias     & -0.00 &  -0.83 & -0.09 & -0.08 & -0.04 & -0.03 & -0.09 & -0.09 & -0.09 & -0.08 & -0.24 & -0.51\\
-mae      &  0.80 &   1.44 &  0.88 &  0.86 &  0.89 &  0.87 &  0.89 &  0.87 &  0.62 &  0.59 &  0.92 &  1.14\\
-std      &  1.00 &   3.89 &  1.19 &  1.14 &  1.19 &  1.15 &  1.21 &  1.16 &  0.90 &  0.83 &  1.26 &  1.83\\
-skewness &  0.01 & -14.40 & -1.11 & -0.96 & -1.02 & -0.86 & -0.89 & -1.02 & -1.61 & -1.58 & -1.79 & -3.45\\
-rejection&  -	 & - 	  & - 	  & 3.3\% & - 	  & 3.4\% & -     & 3.2\% & -     & 3.3\% & 28.1\%& 3.5\%\\
+Bias     & -0.00 &  -0.83 & -0.09 & -0.08 & -0.04 & -0.03 & -0.09 & -0.09 & -0.09 & -0.08 & -0.24 & -0.51\\
+MAE      &  0.80 &   1.44 &  0.88 &  0.86 &  0.89 &  0.87 &  0.89 &  0.87 &  0.62 &  0.59 &  0.92 &  1.14\\
+STD      &  1.00 &   3.89 &  1.19 &  1.14 &  1.19 &  1.15 &  1.21 &  1.16 &  0.90 &  0.83 &  1.26 &  1.83\\
+Skewness &  0.01 & -14.40 & -1.11 & -0.96 & -1.02 & -0.86 & -0.89 & -1.02 & -1.61 & -1.58 & -1.79 & -3.45\\
+Rejection&  -	 & - 	  & - 	  & 3.3\% & - 	  & 3.4\% & -     & 3.2\% & -     & 3.3\% & 28.1\%& 3.5\%\\
 \bottomhline
@@
 
-The posterior distribution of NFCS values obtained from experiment 89+150\,GHz is similar to the one shown in Fig.~\ref{fig:posterior_distribution_I1V}.
+The posterior distribution of $\ynfcs$ obtained from experiment 89+150\,GHz is similar to the one shown in Fig.~\ref{fig:posterior_distribution_I1V}.
 The median value is chosen as the point estimate (see Sect.~\ref{sec:validation}).
@@
 However, QRNN is unable to predict the lowest clear-sky brightness temperatures, and cases with brightness temperatures around 260\,K occur frequently.
-The deviations of point estimates from NFCS simulations are shown in Fig.~\ref{fig:error_distribution_mwhs14}.
-The large negative deviations are corrected successfully with QRNN, but residual cloud impact is evident in the negative tail.
+The deviations of point estimates to NFCS simulations are shown in Fig.~\ref{fig:error_distribution_mwhs14}.
+The large negative deviations are corrected successfully with QRNN (blue curve), but residual cloud impact is evident in the negative tail.
 Most of these residual cases have departures less than 10\,K.
 The corresponding error statistics(see Sect.~\ref{sec:validation}) are provided in  Table~\ref{tab:error_statistics_mwhs_14}.
-In the uncorrected data, the negative departures due to cloud impact lead to a large negative skewness(-14.34) and high bias (-0.84\,K).
-Training QRNN with 89 and 150\,GHz successfully corrects a major portion of the cloud affected cases, and the bias is reduced to -0.09\,K.
+In the uncorrected all-sky simulations, the negative departures due to cloud impact lead to a large negative skewness(-14.34) and high bias (-0.84\,K).
+QRNN trained with 89 and 150\,GHz successfully corrects a major portion of the cloud affected cases, and the bias is reduced to -0.09\,K.
 However, high skewness values indicate a negative tail or uncorrected departures.
-Including 118\,GHz in the training, gives comparable results as 89+150\,GHz.
-With 118\,GHz, the error distributions have lower bias and are more symmetric, but the MAE and STD remain unaltered.
+Including 118\,GHz in the training gives comparable results as 89+150\,GHz.
+With 118\,GHz, the error distribution has lower bias and are more symmetric, but the MAE and STD remain unaltered.
 This indicates that the information from 118\,GHz channels can be beneficial in predicting few cases correctly, but the overall consequence is not exceptionally different from 89+150\,GHz.
@@
 
-Further we investigated whether filtering the predictions with low accuracy could help in improving the error distributions.
-For filtering such cases, we assume that predictions with cloud correction greater than 5\,K are cases associated with large deviations.
+Further, we investigated whether filtering the predictions with low accuracy could help in improving the error distributions.
+For filtering such cases, we assume that predictions with cloud correction greater than 5\,K are associated with large deviations.
 In all three experiments, removing the cases with correction greater than 5\,K removes around 3\% of the data, but only a marginal positive impact on the accuracy is observed.
-With 5\,K threshold though the cases with high errors are removed, the persistent negative skewness indicates presence of cases with residual cloud impact.
+With 5\,K threshold, though the cases with high errors are removed, the persistent negative skewness indicates presence of cases with residual cloud impact.
 Choosing a lower threshold can help in removing more partially corrected cases but at the cost of rejecting clear-sky cases.
@@
 The results obtained with SI and B183 are displayed in last two columns of Table~\ref{tab:error_statistics_mwhs_14}.
-With SI threshold = 5\,K, almost 30\% of the data is rejected, yet the resulting error distributions are poorer as compared to QRNN.
+With SI threshold = 5\,K, almost 28\% of the data is rejected, yet the resulting error distributions are poorer as compared to QRNN.
 The low bias and skewness values indicate that most of the high negative departures are removed, but cases with low cloud impact pass the filter as clear.
@@
 The positive effect of 118\,GHz was slightly higher for MWHS-2 channel 15, but for others, no notable effect was observed.
-The results from combination 89+150\,GHz for these channels are provided in Sect.~\ref{sec:mwhs_others}
+The results for these channels with combination 89+150\,GHz are provided in Sect.~\ref{sec:mwhs_others}
 
@@
 To assess the differences between the capabilities of QRNN-all against QRNN-single, we  compare the error statistics obtained for 89+150\,GHz and 89+150+183\,GHz for channel 14.
-The last column of Table~\ref{tab:error_statistics_mwhs_14} displays the error statistics for the experiment QRNN-all.
+Table~\ref{tab:error_statistics_mwhs_14} shows the error statistics for the experiment QRNN-all.
 In comparison to QRNN-single, we obtain marginally lower error bias with QRNN-all, and the MAE and standard deviation reduce by almost 30\% and 25\% respectively.
@@
 Since a majority of the cases are clear-sky, their impact dominates the whole statistics.
-In order to probe the positive effect of QRNN-all, we also estimated the errors for all cases with cloud correction greater than 5\,K.
-In comparison with QRNN-single, QRNN-all had slightly better accuracy.
+In order to probe the positive effect of QRNN-all, we also estimate the errors for all cases with cloud correction greater than 5\,K.
+In comparison with QRNN-single, QRNN-all has slightly better accuracy.
 This suggests that concurrent use of all 183\,GHz channels can provide additional information on cloud structures to QRNN.
@@
 The correlations are highest between adjacent channels, and drop out as the spacing between the channels increases.
-For cloudy cases, the observed errors obtained from QRNN-single are slightly correlated, but with QRNN-all a very strong correlation is observed(not shown).
+For cloudy cases, the observed errors obtained from QRNN-single are slightly correlated, but with QRNN-all a very strong correlation is observed (not shown).
 
@@
 The labels ``All'' and ``Pred.(5\,K)' are same as described in Table~\ref{tab:error_statistics_mwhs_14}.
-The statistics from existing filtering approaches: scattering index (SI), and scheme by \citet{buehler:aclou:07} are also provided.
-The latter is denoted as ``B183''.}
+The statistics from existing filtering approaches: scattering index (SI), and scheme by \citet{buehler:aclou:07} (B183) are also provided.}
 	\label{tab:error_statistics_mwhs_others}
@@
 					&	STD       & 1.00 &   1.71 &  1.03 &  1.01 		 & 1.02	&  1.03 \\
-					&	skewness  & 0.01 & -20.18 & -0.68 & -0.45 		 &-0.12 & -0.24 \\
-					& rejection   & -    & -      & -	  & 0.2\%        & 28.1\% & 3.5\%  \\
+					&	Skewness  & 0.01 & -20.18 & -0.68 & -0.45 		 &-0.12 & -0.24 \\
+					& Rejection   & -    & -      & -	  & 0.2\%        & 28.1\% & 3.5\%  \\
 		\middlehline
@@
 					& STD       &  1.00 &   2.26 &  1.07 &  1.05  		&  1.04  &  1.14 \\
-					& skewness  &  0.00 & -20.72 & -0.91 & -0.70  		&  -0.38 & -0.86 \\
-					& rejection & -    & -      & -	  & 0.6\%        & 28.1\% & 3.5\%  \\
+					& Skewness  &  0.00 & -20.72 & -0.91 & -0.70  		&  -0.38 & -0.86 \\
+					& Rejection & -    & -      & -	  & 0.6\%        & 28.1\% & 3.5\%  \\
 		\middlehline
@@
 					& STD       &  1.00 &   3.04 &  1.13 &  1.10  		&  112  &	1.39 \\
-					& skewness  &  0.02 & -17.85 & -1.14 & -0.98  		& -0.91  & -2.23 \\	
-					& rejection   & -    & -      & -	  & 1.6\%        & 28.1\% & 3.5\%  \\	
+					& Skewness  &  0.02 & -17.85 & -1.14 & -0.98  		& -0.91  & -2.23 \\	
+					& Rejection   & -    & -      & -	  & 1.6\%        & 28.1\% & 3.5\%  \\	
 		\middlehline
@@
 					& STD       &  1.00 &   5.08 &  1.35 &  1.25 		&  1.53 &	2.64 \\
-					& skewness  & -0.00 & -11.15 & -0.60 & -0.83 		& -2.85 &  -4.41 \\ 
-					& rejection & -     & -      & -	 & 5.6\%        & 28.1\% & 3.5\%  \\
+					& Skewness  & -0.00 & -11.15 & -0.60 & -0.83 		& -2.85 &  -4.41 \\ 
+					& Rejection & -     & -      & -	 & 5.6\%        & 28.1\% & 3.5\%  \\
 		\bottomhline
@@
 
-In this section, we extend QRNN-single to predict NFCS values for MWHS-2 channels 11, 12, 13, and 15.
+In this section, we extend QRNN-single to predict $\ynfcs$ for MWHS-2 channels 11, 12, 13, and 15.
 The experiment QRNN-single with combination 89+150\,GHz is used and the results are displayed in Table~\ref{tab:error_statistics_mwhs_others}.
@@
 With comparable accuracy, the fraction of rejection in SI is approx.
-30\% in comparison to approx.
+28\% in comparison to approx.
 3\% in B183.
@@
 The quantiles have been plotted at equidistant points.
-The red line represents a hypothetical Gaussian distribution of $270\pm1.0$\,K.}
+The blue line represents a hypothetical Gaussian distribution of $270\pm1.0$\,K.
+For each quantile, the sample variation is also shown as box plot.
+}
 	\label{fig:prediction_uncertainty_mwhs}	
@@
 The quantiles given out by QRNN can be used to construct the probability distribution of the predictions in contrast to other correction approaches which give out only point estimates.
-Examples of the uncertainties given out by QRNN is shown in Fig.~\ref{fig:prediction_uncertainty_mwhs}.
+Examples of the uncertainties given out by QRNN are shown in Fig.~\ref{fig:prediction_uncertainty_mwhs}.
 The spread of error distribution is asymmetric.
@@
 Also, cases with very high uncertainty occur infrequently.
-The calibration of the prediction intervals on the testing dataset is displayed in Fig.~\ref{fig:calibration_mwhs}.
+The box plots show that all the quantiles, except $3\sigma$ also follow the Gaussian distribution.
+
+The calibration of the prediction intervals is displayed in Fig.~\ref{fig:calibration_mwhs}.
 For the entire dataset, the predictions follow the $y=x$ line, i.e.
 the predicted uncertainties are perfectly calibrated with the errors observed on the test data.
-However for the cases with correction greater than 5\,K, the distribution is poorly calibrated for higher quantiles.
-The curve lies below the$y =x$line indicating that the prediction intervals are too narrow.
-This is in agreement with the wide spread of predictions over the  higher quantiles (Fig.~\ref{fig:prediction_uncertainty_mwhs}).
-However such cases are less than 6\% of the dataset and filtering such cases does not affect the overall QRNN calibration.
-
-Further, we analyse if the  predicted errors obtained from QRNN are representative of observed errors.
-Fig.~\ref{fig:predicted_errors_mwhs} illustrates the predicted and observed errors for MWHS-2 channel 14.
+However for the cases with correction greater than 5\,K, the distribution is poorly calibrated, and the curve lies below the $y =x$ line, indicating that the prediction intervals are too narrow.
+This is in agreement with the wider spread of predictions over the  higher quantiles (Fig.~\ref{fig:prediction_uncertainty_mwhs}).
+However such cases form less than 6\% of the dataset and filtering them has little effect on the overall calibration.
+
+Further, we analyse if the  predicted errors obtained from QRNN are representative of observed errors (Fig.~\ref{fig:predicted_errors_mwhs}).
 Both error distributions are asymmetric, and this is in fact covered by the percentile distribution  in Fig.~\ref{fig:prediction_uncertainty_mwhs}.
@@
 In this experiment, QRNN-single configuration is used and it is trained with all-sky simulations from all 325\,GHz frequencies from AWS and the target 183\,GHz channel.
-For example, for target AWS-32, the training inputs were AWS-32, AWS-41, AWS-42, AWS-43, AWS-44.
-QRNN was trained five times for each 183\,GHz channel as target.
-Note that for this experiment, AWS was chosen due to availability of four 325\,GHz channels and five 183\,GHz channels.
+For example, for target AWS-32, the training inputs are AWS-32, AWS-41, AWS-42, AWS-43, AWS-44.
+QRNN is trained five times for each 183\,GHz channel as target.
+Note that for this experiment, AWS was chosen due to availability of extra 325\,GHz and 183\,GHz channels.
 \end{enumerate}
@@
 	\includegraphics[width=\textwidth]{Figures/error_distribution_QRNN-single.pdf} 
-	\caption{Same as Fig.~\ref{fig:error_distribution_mwhs14}, but from QRNN-single experiment for ICI channels I1V, I2V and I3V.}
+	\caption{Same as Fig.~\ref{fig:error_distribution_mwhs14}, but from QRNN-single experiment for ICI channels I1V, I2V and I3V. }
 	\label{fig:error_distributions}	
@@
 \begin{table*}[t]
-	\caption{ Same as Table~\ref{tab:error_statistics_mwhs_others}, but from QRNN-single for ICI channels I1V, I2V and I3V.}
+	\caption{ Same as Table~\ref{tab:error_statistics_mwhs_others}, but from QRNN-single for ICI channels I1V, I2V and I3V. The fraction of rejected cases is given in parentheses.}
 	\label{tab:error_statistics_ici}
@@
 		&STD       		&  0.80 &  8.84 &  1.06 &  0.79   \\
-		&skewness 		& -0.01 & -8.10 & -1.51 & -0.64  \\
+		&Skewness 		& -0.01 & -8.10 & -1.51 & -0.64  \\
 		\middlehline
@@
 		&STD       		& 0.80 &   5.95 &  0.86 &  0.65 \\
-		&skewness 		& 0.00 & -10.79 & -1.85 & -0.22  \\
+		&Skewness 		& 0.00 & -10.79 & -1.85 & -0.22  \\
 		\middlehline	
@@
 		&STD       		& 0.80 &   4.27 &  0.80 &  0.63  \\
-		&skewness 		& 0.01 & -13.37 & -1.51 & -0.13  \\
+		&Skewness 		& 0.01 & -13.37 & -1.51 & -0.13  \\
 		\bottomhline
@@
 For all three channels, quite similar behaviour is observed, though I1V has the most cases with residual cloud impact.
-If the predicted cases with correction more than 5\,K are rejected, the resulting error distributions fit the measurement noise, except for I1V, where cases with residual cloud impact introduces a negative bias.
+If the predicted cases with correction more than 5\,K are rejected, the resulting error distributions fit the measurement noise, except for I1V, where cases with residual cloud impact introduce a negative bias.
 For a quantitative assessment of the errors, the results from various error metrics described in  Sect.~\ref{sec:validation} are displayed in Table~\ref{tab:error_statistics_ici}.
 The average bias in I1V measurements is -1.87\,K, which reduces to -0.02\,K after cloud correction.
-The corresponding standard deviation is 1.06\,K in comparison to 8.84\,K in the measurements.
-The prediction accuracy of QRNN is further higher when filtering is made on the predictions.
-In this case, the residual bias zero, and the standard deviation is 0.79\,K, which is in fact of the order of measurement noise (0.80\,K).
+The corresponding standard deviation is 1.06\,K in comparison to 8.84\,K in the all-sky simulations.
+The prediction accuracy of QRNN is further higher, when filtering is made on the predictions.
+In this case, the residual bias is zero, and the standard deviation is 0.79\,K, which is in fact of the order of measurement noise (0.80\,K).
 Similar results are seen for I2V, though a better performance is observed.
 In I2V, the measurement bias is -1.04\,K which reduces to zero after correction and the MAE improves by almost 60\%.
-Removing cases with correction greater than 5\,K from the predictions removes only 3.7\% of the data and reduces the absolute error further by 10\%.
+Removing cases with correction greater than 5\,K from the predictions removes only 3.6\% of the data and reduces the absolute error further by 10\%.
 The standard deviation of the resulting dataset is only 0.65\,K as compared to 0.80\,K from noise.
@@
 \begin{table*}[t]
-	\caption{Same as Table~\ref{tab:error_statistics_mwhs_others}, but from QRNN-single for AWS channels. }
+	\caption{Same as Table~\ref{tab:error_statistics_mwhs_others}, but from QRNN-single for AWS channels. The fraction of rejected cases is given in parentheses. }
 	\label{tab:statistics_qrnn_aws}
@@
 				&STD      & 0.46 &  6.42 &   1.02 &  0.61 \\
-				&skewness & 0.01 & -8.43 &  -0.07 & -1.98 \\
+				&Skewness & 0.01 & -8.43 &  -0.07 & -1.98 \\
 		\middlehline
@@
 				&STD      &  0.45 &  4.70 &  0.76 &  0.56 \\
-				&skewness & -0.00 & -8.78 &  0.04 & -0.79 \\
+				&Skewness & -0.00 & -8.78 &  0.04 & -0.79 \\
 
@@
 				&STD      &  0.64 &   3.67 &  0.75 &  0.60 \\
-				&skewness & -0.00 & -10.32 & -0.55 & -0.59 \\
+				&Skewness & -0.00 & -10.32 & -0.55 & -0.59 \\
 		\middlehline
@@
 				&STD      &  0.63 &   2.65 &  0.71 &  0.57 \\
-				&skewness & -0.01 & -12.49 & -0.40 & -0.29 \\
+				&Skewness & -0.01 & -12.49 & -0.40 & -0.29 \\
 		\middlehline
@@
 				&STD      & 0.88 &   2.06 &   0.86  &  0.76 \\
-				&skewness & 0.01 & -11.80 &  -0.35  & -0.20 \\
+				&Skewness & 0.01 & -11.80 &  -0.35  & -0.20 \\
 		\bottomhline				
@@
 However, after correction, the bias and standard deviation reduce to -0.03\,K and 1.02\,K.
-A decrease in the skewness of error distributions is evident, but a relatively high values after prediction indicate presence of cases with partially-corrected cloud impact.
-Filtering out cases with high cloud impact improves the statistics overall except for skewness, which increases.
+A decrease in the skewness of error distributions is evident, but a relatively high value after prediction indicates presence of cases with partially-corrected cloud impact.
+Filtering out cases with 5\,K correction improves the statistics except for skewness, which increases.
 For AWS-33, the predictions have slightly higher accuracy than AWS-32.
@@
 For both channels, the error distributions are relatively more symmetric than the other channels.
-Also, it is worth to noting that when cases with 5\,K cloud correction are removed, the spread of prediction errors is narrower than noise.
+Also, it is worth to noting that when cases with 5\,K cloud correction are removed, the spread of prediction errors is narrower than noise for AWS-34, AWS-35 and AWS-36.
 
@@
 	\caption{Same as Fig.~\ref{fig:prediction_uncertainty_mwhs}, but from QRNN-single for ICI channel I2V.
-The red line represents a hypothetical Gaussian distribution of $270\pm0.60$\,K, which is of the order of standard deviation for I2V predictions (see Table~\ref{tab:error_statistics_ici}).}
+The blue line represents a hypothetical Gaussian distribution of $270\pm0.60$\,K, which is of the order of standard deviation for I2V predictions (see Table~\ref{tab:error_statistics_ici}).}
 	\label{fig:prediction_uncertainty_I2V}	
+\end{figure}
+\begin{figure}[t]
+	\includegraphics[height = 70mm]{Figures/calibration_QRNN_I2V.pdf}	
+	\caption{Same as Fig.~\ref{fig:calibration_mwhs}, but from QRNN-single for ICI channel I2V. }
+	\label{fig:calibration_I1V}	
 \end{figure}
@@
 \end{figure}
-\begin{figure}[t]
-	\includegraphics[height = 70mm]{Figures/calibration_QRNN_I2V.pdf}	
-	\caption{Same as Fig.~\ref{fig:calibration_mwhs}, but from QRNN-single for ICI channel I2V. }
-	\label{fig:calibration_I1V}	
-\end{figure}
+
 \begin{figure}[t]
@@
 Among the cases associated with low uncertainty, the distribution is quite symmetric along the median value.
-These cases are concentrated along a narrow interval and lie close to the red line representing a Gaussian spread.
+These cases are concentrated along a narrow interval and lie close to the blue line representing a Gaussian spread.
 On the contrast, cases with high uncertainty are unequally spaced and have a larger spread over positive quantiles than negative quantiles.
+The narrow boxplots also indicate that the majority of the predictions are sharp.
+These are clear-cases which dominate the dataset, while cloudy cases have more spread out uncertainties.
 
 Fig.~\ref{fig:calibration_I1V} shows the calibration of the prediction intervals for I2V.
-The predictions for the complete test dataset are well calibrated and follow the$y =x$line.
+The predictions for the complete test dataset are well calibrated and follow the $y =x$ curve.
 On the other hand, when only the cases with  cloud correction greater than 10\,K are considered, the predictions in all the intervals are poorly calibrated.
-In this case the calibration curve lies slightly below the $y=x$ line for higher quantiles, indicating that the predicted intervals are too narrow, or the uncertainty is underestimated.
-
-Fig.~\ref{fig:predicted_errors} shows the comparison of observed errors (prediction accuracy) to predicted errors.
+In this case, the predicted intervals are too wide over lower quantiles and too wide over higher quantiles.
+
+Fig.~\ref{fig:predicted_errors} shows the comparison of observed errors to predicted errors.
 The predicted and observed errors mostly have a good agreement but the predicted errors are spread out more asymmetrically towards the negative departures.
@@
 
-To conclude the results, we assessed if the uncertainty estimates given by QRNN are representative of prediction accuracy.
-Fig.~\ref{fig:error_distribution_uncertainty_bins} shows the errors of best estimate binned by their corresponding uncertainty in $\pm2\sigma$  confidence interval.
+To conclude the results, we analyse if the uncertainty estimates given by QRNN are representative of prediction accuracy.
+Fig.~\ref{fig:error_distribution_uncertainty_bins} shows the observed errors binned by their corresponding uncertainty in $\pm2\sigma$  confidence interval.
 For all three channels, the spread of error distribution increases as the uncertainty about the accuracy of the trial increases.
@@
 In spite of individual variations in the error distributions for each channel, predictions and their corresponding uncertainties follow the same relationship.
-Similar results were also obtained with AWS(not shown).
+Similar results are also obtained with AWS (not shown).
 
@@
 Even though the cloud correction is partial, the performance is comparable or better to existing cloud filtering techniques like SI and scheme by \cite{buehler:aclou:07}.
-Note that both these techniques are a one for all approach for each 183\,Ghz channel; thus if one observation is classified as cloudy by the filter, it is removed in all humidity channels.
+Note that both these techniques are a one for all approach for each 183\,GHz channel; thus if one observation is classified as cloudy by the filter, it is removed in all humidity channels.
 This increases the probability of erroneously removing clear observations.
@@
 Redundant patterns in machine learning models often have undesirable effect on the predictive performance.
-In our application, redundant information does not affect the prediction accuracy, but introduces highly correlated noise between channels.
-Correlated errors are also undesirable for DA systems, but in future if the operational centres progress with approaches dealing with correlated observation errors, concurrent use of 89, 150 and 183\,GHz channels would give the best cloud correction performance.
+In our application, redundant information does not affect the prediction accuracy, but introduces highly correlated observational errors between channels.
+Correlated errors are also undesirable for DA systems, but in future, if the operational centres progress with approaches dealing with correlated observation errors, concurrent use of 89, 150 and 183\,GHz channels would give the best cloud correction performance.
 
@@
 Few cases with high cloud impact do affect the accuracy and introduce a small negative bias, but such cases are easily filtered out with a simple correction threshold filter.
-For example, it is shown that filtering out cases with correction greater than 5\,K, results in variabilities of the order of noise with minimal reduction in data (2-4\%).
+For example, it is shown that filtering out cases with correction greater than 5\,K, results in variabilities of the order of noise with minimal reduction in data (2-6\%).
 For channel I1V, a slightly lower accuracy is observed due to relatively higher number of cases with residual cloud impact.
@@
 In this study, a methodology based on quantile regression neural network (QRNN) is used for identifying and correcting the cloud contamination in operational humidity channels.
-QRNN is a neural network which trains on all-sky brightness temperatures from  channels containing orthogonal information to humidity channels, to estimate the noise free clear-sky (NFCS) radiances.
+QRNN is a neural network which trains on all-sky brightness temperatures from  channels containing orthogonal information to humidity channels, to estimate the noise free clear-sky (NFCS) brightness temperatures.
 The output is the posterior distribution of predictions over different quantiles.
@@
 
-The applicability of QRNN based correction to current sensors is demonstrated with MHWS-2 and it is shown that QRNN is partially successful in removing the cloud impact.
+The applicability of QRNN based correction to current sensors is demonstrated with MHWS-2 (MicroWave Humidity Sounder-2) and it is shown that QRNN is partially successful in removing the cloud impact.
 This is not  an optimal solution, but it is in agreement with what can be achieved with the present instruments.
@@
 However for the latter, improving their a priori distribution is not trivial.
-Correcting hydrometeor impact for cases without complete complementary information is a challenge for QRNN and always limit its performance.
+Correcting hydrometeor impact for cases without complete complementary information is a challenge for QRNN and always limits its performance.
 
@@
 The results indicate that utilisation of only 325\,GHz can also be beneficial when other channels are absent.
-In future when ICI would be available, the ICI sub-mm channels could also be used to cloud correct MWI (MicroWave Imager) humidity radiances.
+In future when Ice Cloud Imager (ICI) would be available, the ICI sub-mm channels could also be used to cloud correct MicroWave Imager (MWI) humidity radiances.
 Although re-mapping to a common footprint would slighly compromise the data quality, the high accuracy achieved with ICI simulations suggests that the QRNN would work well even when actual measurements are available.
@@
 The point estimates with low error have high certainty.
-On the other hand, the  incorrect predictions on out-of-distribution cases have low confidence.
+On the other hand, the  incorrect predictions have low confidence.
 In comparison to deterministic correction approaches, the corrected radiances along with uncertainty estimates give additional benefit for DA systems.
@@
 
-The high quality cloud corrected radiances have great potential in both retrieval schemes and  NWP systems.
+The high quality cloud corrected radiances have great potential in both retrieval schemes and numerical weather prediction (NWP) systems.
 Even with availability of new sensors and better observations, the problems posed by undetected cloud impact limit the complete usage of humidity observations.
@@
 
-\codeavailability{TEXT} %% use this section when having only software code available
+\codeavailability{QRNN is available as a part of the \textit{typhon: tools for atmospheric research},  https://doi.org/10.5281/zenodo.3626449.}
 
@@
 %
-CloudSat profiles during August 2015 were randomly selected for forward simulations.
-The input data were restricted between $60^{\degree}$S to $60^{\degree}$N, and surface is below 500\,m.
-Both clear-sky and all-sky scenarios were simulated, and no differentiation was made between the observations over ocean/sea and land.
+All radiative transfer forward simulations are made by the Atmospheric Radiative
+Transfer System (ARTS, \citet{eriksson:arts2:11,buehler:artst:18}), version
+arts-2.3.1.
+The absorption and hydrometeor properties are described below.
+For each atmospheric case, both ``all-sky'' and ``clear-sky'' calculations are performed.
+In the former, all hydrometeors contents are set to zero, while in the latter, ice water content (IWC) and rain water content (RWC) derived from CloudSat reflectivities and liquid water content (LWC) from ERA-Interim \citep{dee2011erainterim} are included.
+In order to avoid a possible bias between clear-sky and all-sky calculations for insignificant hydrometeor contents, both calculations are made by ARTS's interface to the RT4 solver \citep{evans1995microwavec}.
 
 The absorption model takes into account the effect from nitrogen
-\citep{pwr:93}, oxygen \citep{pwr:93} and water vapour 
-\citep{ellison2007permittivity}. Liquid water content (LWC) is taken from ERA-Interim \citep{dee2011erainterim} and is assumed
-to be totally absorbing. In the mapping of CloudSat reflectivities to rain water content (RWC) and
-ice water content (IWC) a total separation between liquid and ice phase is assumed. All scattering
-hydrometeors at temperatures above 0$^\circ$C are assumed to be rain, and all
-below 0$^\circ$C are assumed to be ice hydrometeors. For RWC the particle size
-distribution of \citet{abel2012improved} is applied. The particle size distribution (PSD) of IWC follows the basic formulation applied in DARDAR (\url{
+\citep{pwr:93}, oxygen \citep{pwr:93} and water vapour  \citep{ellison2007permittivity}.
+Liquid water content (LWC) is taken from ERA-Interim  and is assumed to be totally absorbing.
+In the mapping of CloudSat reflectivities to RWC and IWC, a total separation between liquid and ice phase is assumed.
+All scattering hydrometeors at temperatures above 0$^{\degree}$C and below 0$^{\degree}$C are assumed to be rain and ice hydrometeors, respectively.
+For RWC the particle size
+distribution (PSD) of \citet{abel2012improved} is applied. The PSD of IWC follows the basic formulation applied in DARDAR (\url{
 http://www.icare.univ-lille1.fr/projects/dardar}, \citet{delanoe2008variational}), using latest parameter
@@
 study. The land emissivity was taken from TELSEM (Tool to Estimate Land‐Surface Emissivities at Microwave frequencies, \citet{aires2011tool}) and the
-Ocean/water from TESSEM (Tool to Estimate Sea‐Surface Emissivity from Microwaves to sub‐Millimeter waves , \citet{prigent2017sea}). For each atmospheric case,
-both ``clear-sky'' and ``all-sky'' calculations were performed. In the former,
-all impact of all hydrometeors were set to zero, while in the latter, IWC and
-RWC derived from CloudSat reflectivities and LWC from ERA-Interim were taken
-into account. Both sets of calculations were made by ARTS's interface to the
-RT4 solver \citep{evans1995microwavec}. To avoid a possible bias between
-clear-sky and all-sky for insignificant hydrometeor contents, the same
-``scattering solver'' was used for both calculations. The first two elements
-of the Stokes vector were calculated.
-For AWS, forward simulations were performed for 21 monochromatic frequencies, and later these frequencies were interpolated to a finer grid to get the AWS channel brightness temperatures.
+Ocean/water from TESSEM (Tool to Estimate Sea‐Surface Emissivity from Microwaves to sub‐Millimeter waves , \citet{prigent2017sea}).
+
+Using the setup described above,  forward simulations are performed for ICI and AWS.
+The output from ARTS is first two elements of the Stokes vector,  which are converted to brightness temperatures for H- and V-polarisation.
+For AWS, forward simulations are performed for 21 monochromatic frequencies, and later these frequencies were interpolated to a finer grid to get the AWS channel brightness temperatures.
 

### 2020-11-11 Article/ici_submm_cloudcorr.tex
included Dave's changes

@@
 
-Identification of cloud affected observations is indispensable for both clear-sky and all-sky numerical weather prediction (NWP) systems.
-In this study, we present a methodology to identify and correct the cloud impact in microwave humidity radiances.
-A channel specific quantile regression neural network (QRNN) based approach is formulated to estimate the posterior distributions of noise free clear-sky (NFCS) radiances.
-The applicability of the approach is demonstrated by application to a present sensor: MicroWave Humidity Sounder-2 (MWHS-2).
-With the future outlook, the applicability to sub-millimeter (sub-mm) channels is also analysed.
-The results are compared against the NFCS simulations.
-With the present sensors, the approach is partially successful in correcting the negative departures.
-Almost all cases with high cloud impact are corrected, but thin cirrus clouds cannot be fully corrected.
-In spite of the partial performance, the results from QRNN are better than what operational cloud filtering techniques like scattering index can achieve.
-On the other hand, when sub-mm observations from ICI are used to correct the cloud impact, QRNN can successfully correct most of the cases with cloud impact.
-Only 2-6\% of the cases are partially corrected and these can be easily removed by a simple filtering.
-The resulting error distributions are almost symmetric with a very low spread.
-The methodology also works well when only one of the higher frequencies (325\,GHz) is available.
-Except for the lowest peaking channel, using sub-mm observations also results in error distributions with standard deviation less than the measurement noise.
-Another advantage of using QRNN is that predicted quantiles can be employed to quantify the case-specific uncertainty estimates.
-The results show that QRNN is successful in representing the uncertainty for each case individually.
-Despite individual variations for each channel, the predictions exhibit a higher uncertainty when cloudy cases lack orthogonal information from other channels.
-In comparison to deterministic correction/filtering approaches, the high quality corrected radiances with uncertainty estimates have great potential to be used efficiently in assimilation systems.
+A methodology based on quantile regression neural networks (QRNN) is presented that identifies and corrects the cloud impact on microwave humidity sounder radiances at 183GHz.
+This approach estimates the posterior distributions of noise free clear-sky (NFCS) radiances, providing nearly bias-free estimates of clear-sky radiances with a full posterior error distribution.
+It is first demonstrated by application to a present sensor, the MicroWave Humidity Sounder-2 (MWHS-2), then the applicability to sub-millimeter (sub-mm) sensors is also analysed.
+The QRNN results improve upon what operational cloud filtering techniques like a scattering index can achieve, but are ultimately imperfect due to limited information content on cirrus impact from traditional microwave channels---the negative departures associated with high cloud impact are successfully corrected, but thin cirrus clouds cannot be fully corrected.
+In contrast, when sub-mm observations are used, QRNN successfully corrects most cases with cloud impact, with only 2-6\% of cases left partially corrected.
+The methodology works well even if only one sub-mm channel (325\,GHz) is available.
+When using sub-mm observations, cloud correction usually results in error distributions with standard deviation less than typical channel noise values.
+Furthermore, QRNN outputs predicted quantiles for case-specific uncertainty estimates, successfully representing the uncertainty of cloud correction for each observation individually.
+In comparison to deterministic correction or filtering approaches, the corrected radiances and attendant uncertainty estimates have great potential to be used efficiently in assimilation systems due to being largely unbiased and adding little further uncertainty to the measurements.
 
@@
 \citep{geer2018all}. The latter is particularly true in NWP of regional scope
-\citep{gustafsson2018survey}, all-sky assimilation of 183\,GHz at many national
-weather agencies will likely not be reached in many years.
-Anyhow, both clear-sky and all-sky assimilation require identification of cloud affected observations.
+\citep{gustafsson2018survey}, with clear-sky assimilation of 183GHz radiances still commonplace.
+Regardless, both clear-sky and all-sky assimilation require identification of cloud affected observations, either to screen out these observations or to assign an appropriate observation error.
 ``Scattering index'' \citep{geer2015scatteringindex} is one of the approaches used.
@@
 
-Despite their broad usage, these filtering methods aim at partial removal of cloud contamination originating from high ice clouds.
-The residual cloud impact can have some drawbacks.
-For 183\,GHz, the impact of hydrometeors systematically causes a decrease in the observed radiance (maybe with exceptions at extremely dry conditions), see
-e.g.\ \citet{barlakas:three:20} and below.
-This implies that if any cloud contamination is missed by the filtering this will cause a negative bias in mean radiance, compared to the true clear-sky mean.
-This bias will translate to a bias in humidity after the retrieval or assimilation.
-For NWP systems assimilating clear-sky observations, the effect of undetected clouds is overcome by inflating the observational errors.
-However this artificial suppression of observations diminishes the impact of observations.
-The alternative is to apply a very strict filtering, but this increases the rejection of clear-sky values, i.e.\ an important loss of useful data.
+%Despite their broad usage, these filtering methods aim at partial removal of cloud contamination originating from high ice clouds. The residual cloud impact can have some drawbacks. 
+At 183\,GHz, the impact of hydrometeors typically causes a decrease in the observed radiance due to scattering from ice hydrometeors (e.g.\ \citet{barlakas:three:20}).
+This implies that if any cloud contamination is missed by the filtering, a negative bias in mean radiance will result compared to the true clear-sky mean, which may translate into a bias in humidity after the retrieval or assimilation.
+For NWP systems assimilating clear-sky observations, the effect of undetected clouds may be overcome by inflating the observational errors and diminishing the impact of observations.
+Furthermore, the mathematical assumptions of data assimilation are predicated on Gaussian errors with no mean bias, and residual cloud impacts that cause a net bias are not easily handled by variational bias correction.
+One solution is to apply a very strict filtering, but this increases the rejection of clear-sky values, i.e.\ an important loss of useful data.
 Another limitation of existing clearing approaches is their ``one for all'' approach, i.e.\ observations in all 183\,GHz channels are either kept or rejected.
@@
 An observation could be cloudy in some channels and still the be clear-sky in others.
-To allow a channel specific filtering, data likely need to be combined in a more complex manner than simple differences, but it is unclear what type of regression that would be best.
+To allow a channel specific filtering, data likely need to be combined in a more complex manner than simple differences, but it is unclear what type of regression would be best as the ideal solution would be scene-dependent.
 This points towards applying machine learning, as used by e.g.\ \citet{favrichon2019detecting}.
 A maybe less obvious problem is the assignment of uncertainty to the filtered values.
-To our best knowledge, so far only estimates of mean and worst case errors have been provided.
-Some cases with relatively high cloud impact will likely be missed, while most cases are clear-sky from start.
+To our best knowledge, so far only estimates of mean and worst case errors exist in the literature.
+Some cases with relatively high cloud impact will likely be missed, while most cases are clear-sky from the start.
 As the remaining cloudy cases can cause significant biases, the likely solution is to apply a quite conservative (high) error estimate.
-However, this will unnecessary downgrade the value of the truly clear-sky cases and the observations are used in a non-optimal manner.
-
-We are here approaching cloud filtering task from a new angle. The basic idea
+However, this will unnecessarily downgrade the value of the truly clear-sky cases and the observations are used in a non-optimal manner.
+
+In this study, we approach the cloud filtering task from a new angle. The basic idea
 is to derive an estimate of the corresponding noise-free clear-sky (NFCS) value
@@
 measurements (no ``background'' data involved). Not only a best estimate is
-provided, but also a case specific uncertainty. This information could be used as a pure filter, by rejecting data where the correction exceeds some threshold value. However, even
+provided, but also a case-specific uncertainty. This information could be used as a pure filter, by rejecting data where the correction exceeds some threshold value. However, even
 better is to replace the original value with the predicted NFCS value when
@@
 is shown below that a basically bias free cloud correction can be obtained.
-This feature also removes the need of threshold value, as long as the retrieval or
+This feature also removes the need for defining threshold values, as long as the retrieval or
 assimilation system can incorporate the uncertainty of the corrected value. As
@@
 by noise, but the uncertainty increases with magnitude of correction.
-Accordingly, the cloud correction approach allows that the full weight of
-clear-sky data can be preserved.
+Accordingly, the cloud correction approach permits the full weight of
+clear-sky data to be preserved.
 
@@
 
-The main focus of this study is the potential of proposed cloud-correction
+The main focus of this study is the potential of this cloud-correction
 method using sub-millimetre (sub-mm) observations, which will become available
@@
 observations at 89 and 150\ GHz channels (following
-\citet{geer2015scatteringindex}), which are available already today. The focus
-on sub-mm channels is motivated by several reasons. Firstly, the higher
+\citet{geer2015scatteringindex}), which are available on several sensors extant today. The focus
+on sub-mm channels is motivated by several reasons. First, the higher
 frequencies are more sensitive to scattering effects from smaller
-hydrometeors. For high altitude cirrus clouds, these frequencies have a stronger
-signal than 183\,GHz. In some cloudy situations it could be possible that the
-impact at 183\,GHz is of the order of thermal noise and modelling uncertainties,
-while the impact at 325\,GHz is significantly higher. Secondly, the proposed
-cloud correction methods allows integrating ICI sub-mm observations in
-clear-sky data assimilation schemes and thus provides a simple
+hydrometeors and are thus expected to provide greater sensitivity to high altitude cirrus clouds. For example, in some cloudy situations the
+cloud impact at 183\,GHz may be of the order of thermal noise and modelling uncertainties,
+while the impact at 325\,GHz is significant enough to provide sufficient signal to noise for identifying cloud. Second, the proposed
+cloud correction methods allow integration of ICI sub-mm observations in
+clear-sky data assimilation schemes with no further modifications, thus providing a simple
 way to make use this novel data source as soon as it becomes available.
@@
 \end{table}
-MicroWave Humidity Sounder 2 (MWHS-2) is an instrument onboard FengYun-3C (FY-3C).
+The MicroWave Humidity Sounder 2 (MWHS-2) is an instrument on two current satellites in the FengYun-3 series, FY-3C and FY-3D.
 MWHS-2 a cross track scanning microwave radiometer and measures 15 frequencies in the range 89-191\,GHz.
-89\,GHz and 150\,GHz are window channels, five humidity sounding channels are centered at 183.31\,GHz, and eight temperature sounding channels are centered at 118.75\,GHz oxygen absorption line.
+89\,GHz and 150\,GHz are window channels, five humidity sounding channels are centered at 183.31\,GHz, and eight temperature sounding channels are centered on the 118.75\,GHz oxygen absorption line.
 The five humidity sounding channels are similar to ATMS.
-As of December 2019, observations from MWHS-2 are routinely assimilated at European Centre for Medium-Range Weather Forecasts (ECMWF, \citet{duncan2020MWHS}).
-The channels relevant to this study are described on Table~\ref{tab:specifications_MWHS2}.
-
-For this study, MWHS-2 simulations were sourced from ECMWF assimilation system. \todo{details?}
+Observations from MWHS-2 are routinely assimilated in all-sky conditions at the European Centre for Medium-Range Weather Forecasts (ECMWF) with demonstrable positive impact on forecast performance \citep{duncan2020MWHS}.
+The channels relevant to this study are described in Table~\ref{tab:specifications_MWHS2}.
+
+For this study, MWHS-2 simulations were sourced from the operational ECMWF assimilation system.
 
@@
 %
-MWHS-2 simulated radiances are routinely calculated at ECMWF for their use in the ECMWF NWP system.
-RTTOV (Radiative Transfer for TOVS, \citet{saunders2018update} and RTTOV-SCATT \citep{bauer2006rttovscat} are used to calculate the radiances in clear-sky and all-sky conditions, respectively.
-For this study, MWHS-2 brightness temperatures for the period June-July 2020 are used.
-Out of all the available observations, we use data for latitudinal range $60^{\degree}$\,S to $60^{\degree}$\,N and satellite zenith angle less than $7.5^{\degree}$.
-With this filter we have 340\,000 cases.
+MWHS-2 simulated radiances during the period June-July 2020, are sourced from ECMWF.
+In the current version of the ECMWF Integrated Forecasting System (IFS), cycle 47R1 \citep{IFS47R1chap1}, clear-sky and all-sky radiative transfer are performed simultaneously for monitoring purposes, despite all humidity sounders being assimilated via all-sky exclusively.
+These side by side radiative transfer calculations on a large variety of model scenes from the IFS provides an ideal dataset for comparing radiances with and without cloud effects.
+Out of all the available observations during the period, we use data for latitudinal range $60^{\degree}$\,S to $60^{\degree}$\,N and satellite zenith angle less than $7.5^{\degree}$.
+With this filter we have approximately 290\,000 cases.
 
@@
 All evaluation results except hyper-parameter tuning, described in the study, have been made on the test dataset.
-Hyper-parameter tuning is made on the training dataset (see Appendix~\ref{appendix:hyperparamter}).
+Hyper-parameter tuning is made on the validation dataset (see Appendix~\ref{appendix:hyperparamter}).
+Validation dataset is part of the training dataset which is held back during the training process.
 
@@
 The choice is motivated by the fact that MWHS-2 has five complementary 183\,GHz channels, along with additional 118\,GHz channels.
-In order to formulate and test the correction approach, multiple QRNN experiments are performed for MWHS-2 channel 14.
+In order to formulate and test the correction approach, multiple QRNN experiments are performed for MWHS-2.
+However, for brevity we compare the comprehensive results only for channel 14.
 Later the optimal experiment is extended to other 183\,GHz channels.
@@
 	\item In the first experiment, we examine the performance of QRNN cloud correction with MWHS-2 window channels: 89 and 150\,GHz.
-In ECMWF NWP system, the differences between the observations of these two window channels are used to identify the cloud affected data for ATMS and MWHS-2 \citep{geer2015scatteringindex}.
+In ECMWF NWP system, the differences between the observations of these two window channels are used to identify the cloud affected data for humidity sounding channels \citep{geer2015scatteringindex}.
 To investigate the potential impact of these two window channels in QRNN based cloud correction, the configuration QRNN-single is applied.
@@
 	\includegraphics[width = 70mm]{Figures/QRNN_output_mwhs.pdf} 
-	\caption{Distribution of point estimate $\ynfcs$ obtained from QRNN-single 89+150\,GHz for MWHS-2 channel 14. The corresponding distributions for all-sky and clear-sky simulations are also shown.}
+	\caption{The distribution of point estimate $\ynfcs$ obtained from QRNN-single 89+150\,GHz for MWHS-2 channel 14.
+The corresponding distributions for all-sky and clear-sky simulations are also shown.}
 	\label{fig:distribution_predicted_mwhs14}	
@@
 	\includegraphics[width = 70mm]{Figures/MWHS_error_dist_14.pdf} 
-	\caption{Error distribution for deviations of point estimates to NFCS simulations.
+	\caption{The error distribution for deviations of point estimates to NFCS simulations.
 The results are from QRNN-single experiment 89+150\,GHz and MWHS-2 channel 14.
@@
 \begin{table*}[t]
-	\caption{Error statistics for deviations of point estimates to NFCS simulations.
+	\caption{The error statistics for deviations of point estimates to NFCS simulations.
 Results are for different QRNN experiments for MWHS-2 channel 14 (see Sect.~\ref{sec:QRNN_expt_MWHS}).
@@
 The label ``All'' denotes the entire dataset of predicted point estimates, while ``Pred.(5\,K)'' refers to the predicted point estimates but where cases with cloud correction greater than 5\,K are excluded.
-The last two columns show the statistics obatined after filtering cloudy cases according to scattering index (SI) and scheme by \citet{buehler:aclou:07} (B183).
+The last two columns show the statistics obtained after filtering cloudy cases according to scattering index (SI) and scheme by \citet{buehler:aclou:07} (B183).
 Bias, MAE, STD are in K, skewness in dimensionless.}
@@
 \begin{table*}[t]
-	\caption{ Error statisics for MWHS-2 channels 11, 12, 13 and 15 from QRNN-single experiment 89+150\,GHz.
+	\caption{ Error statistics for MWHS-2 channels 11, 12, 13 and 15 from QRNN-single experiment 89+150\,GHz.
 The labels ``All'' and ``Pred.(5\,K)' are same as described in Table~\ref{tab:error_statistics_mwhs_14}.
@@
 		& &  Clear-sky &   All-sky &  \multicolumn{2}{c|}{89+150\,GHz}    & SI & B183  \\
-		&	&		   &			& All & Pred.(5K) &&\\
+		&	&		   &			& All & Pred.(5\,K) &&\\
 		\middlehline
@@
 On the contrast, cases with high uncertainty are unequally spaced and have a larger spread over positive quantiles than negative quantiles.
-The narrow boxplots also indicate that the majority of the predictions are sharp.
+The narrow box plots also indicate that the majority of the predictions are sharp.
 These are clear-cases which dominate the dataset, while cloudy cases have more spread out uncertainties.
@@
 %
-The results from MWHS-2 show that QRNN based cloud correction is partially successful in correcting the cloud impact with existing sensors.
-The methodology can correctly address the large negative depatures owing to cloud impact, but few cloudy cases end up with inadequate correction.
+The results from MWHS-2 show that QRNN based cloud correction is partially successful in correcting the cloud impact with existing humidity sounding sensors.
+The methodology can correctly address the large negative departures owing to cloud impact, but few cloudy cases end up with inadequate correction.
 The resulting error distributions are not completely symmetric but have a low bias and spread.
 Among several input channel combinations described for QRNN-single, the performance of combination 89+150\,GHz is observed to be optimal.
-The positive performance with 150\,GHz is not unexpected, as 150\,GHz is highly sensitive to ice hydrometeors and cloud water; but using 89\,GHz along with 150\,GHz gives a slightly better performance.
-The channel 89\,GHz is affected by surface emissivity and is less sensitive to cloud water content, however its sensitivity to warm clouds in the lower troposphere could be important.
+The positive performance with 150\,GHz is not unexpected, as 150\,GHz is sensitive to ice hydrometeors and cloud water; but using 89\,GHz along with 150\,GHz gives a slightly better performance.
+The channel 89\,GHz is more affected by surface emission and is less sensitive to cloud water content, however its sensitivity to warm clouds in the lower troposphere could be important.
 We also investigate the impact of two temperature sounding channels (MWHS-2 channel 6 and 7).
@@
 Among these four channels, 150\,GHz has the highest peaking function around 4\,km \citep{chen2020mwhs}.
-These channels can only provide coverage to the humidity channels in lower and mid troposphere; nonetheless, the 183\,GHz channels are sensitive to hydrometeor content upto 2\,km.
+These channels can only provide coverage to the humidity channels in lower and mid troposphere; nonetheless, the 183\,GHz channels are sensitive to hydrometeor content up to 2\,km.
 Due to missing complementary information from other channels in the upper troposphere, QRNN fails at predicting these cases accurately.
@@
 In our application, redundant information does not affect the prediction accuracy, but introduces highly correlated observational errors between channels.
-Correlated errors are also undesirable for DA systems, but in future, if the operational centres progress with approaches dealing with correlated observation errors, concurrent use of 89, 150 and 183\,GHz channels would give the best cloud correction performance.
+Correlated errors are also undesirable for DA systems, but in future, if the operational centres progress with approaches dealing with correlated observation errors, for example as currently done for ATMS at ECMWF \citep{Weston2018eumATMS}, concurrent use of 89, 150 and 183\,GHz channels would give the best cloud correction performance.
 
@@
 Few cases with high cloud impact do affect the accuracy and introduce a small negative bias, but such cases are easily filtered out with a simple correction threshold filter.
-For example, it is shown that filtering out cases with correction greater than 5\,K, results in variabilities of the order of noise with minimal reduction in data (2-6\%).
+For example, it is shown that filtering out cases with correction greater than 5\,K, results in variabilities of the order of sensor noise with minimal reduction in data (2-6\%).
 For channel I1V, a slightly lower accuracy is observed due to relatively higher number of cases with residual cloud impact.
@@
 
-A similar pattern of results is seen for when only 325\,GHz channel is used to correct cloud impact in AWS.
+A similar pattern of results is seen for when only one 325\,GHz channel is used to correct cloud impact in AWS.
 QRNN is successful in predicting NFCS values for all channels except for the lowest peaking channel AWS-32.
@@
 In spite of the slightly inferior performance for AWS-32, the high accuracy for other channels indicates that a single sub-mm channel like 325\,GHz is also sufficient enough for cloud correction at 183\,GHz.
-This is an important result as smaller satellites are limited by their size to measure all sub-mm wavelengths.
+This is an important result as smaller satellites may be limited by their size to measure several sub-mm wavelengths.
 
@@
 This effect is observed to be stronger in ICI than AWS, as the former has additional input channels giving same information.
-Note that with actual satellite measurements, the spread of error distributions smaller than noise could be difficult to achieve due to other underlying uncertainties not considered here.
+Note that with actual satellite measurements, the spread of error distributions smaller than sensor noise could be difficult to achieve due to other underlying uncertainties not considered here.
 
@@
 To use these observations correctly, data assimilation schemes often inflate their asymmetric error distributions at the cost of artificially suppressing the observational impact.
-This is not the optimal solution but the best which can be achieved with present sensors.
-However, the symmetric error distributions obtained from QRNN allow us to effectively utilize more than 94\% of the data without the need for error inflation.
+However, the symmetric error distributions obtained from QRNN allow effective utilization more than 94\% of the data without the need for artificial error inflation.
 
@@
 The applicability of QRNN based correction to current sensors is demonstrated with MHWS-2 (MicroWave Humidity Sounder-2) and it is shown that QRNN is partially successful in removing the cloud impact.
-This is not  an optimal solution, but it is in agreement with what can be achieved with the present instruments.
 In comparison to existing clear-filtering approaches, QRNN gives comparable or better performance and with minimal rejection of data.
@@
 
-Based on the promising results from MWHS-2, and with future scope, we extend the study to include data from sub-millimeter (sub-mm) channels.
+Based on the promising results from MWHS-2, and with future scope, we extend the study to include data from sub-millimetre (sub-mm) channels.
 The results show that with  sub-mm channels, QRNN is able to correctly predict most of the cloudy cases and can provide high quality cloud corrected radiances.
@@
 The results indicate that utilisation of only 325\,GHz can also be beneficial when other channels are absent.
-In future when Ice Cloud Imager (ICI) would be available, the ICI sub-mm channels could also be used to cloud correct MicroWave Imager (MWI) humidity radiances.
-Although re-mapping to a common footprint would slighly compromise the data quality, the high accuracy achieved with ICI simulations suggests that the QRNN would work well even when actual measurements are available.
-
-The biggest advantge of QRNN compared to other regression based approached is its probabilistic nature.
+It's possible that the ICI sub-mm channels could also be used to cloud correct MicroWave Imager (MWI) humidity radiances.
+Although re-mapping to a common footprint would slightly compromise the data quality, the high accuracy achieved with ICI simulations suggests that the QRNN would work well even when actual measurements are available.
+
+The biggest advantage of QRNN compared to other regression based approaches is its probabilistic nature.
 The QRNN predictions over chosen quantiles are a measure of the accuracy at different probability levels.
 In this study, the predicted quantiles given by QRNN work well in representing the accuracy of the point estimate.
-The point estimates with low error have high certainty.
-On the other hand, the  incorrect predictions have low confidence.
+The point estimates with low error have high certainty and incorrect predictions have low confidence.
 In comparison to deterministic correction approaches, the corrected radiances along with uncertainty estimates give additional benefit for DA systems.
@@
 
-The high quality cloud corrected radiances have great potential in both retrieval schemes and numerical weather prediction (NWP) systems.
+The cloud corrected radiances have great potential in both retrieval schemes and numerical weather prediction (NWP) systems.
 Even with availability of new sensors and better observations, the problems posed by undetected cloud impact limit the complete usage of humidity observations.
 However, with the cloud correction methodology presented here, we can aim at resolving these limitations.
-This is specially true for clear-sky assimilation systems, which reject upto 80\% of the available observations due to cloud contamination.
-The loss is largest in mid-latitudes.
-Although, NWP systems are gradually moving towards assimilating all-sky radiances but the use of data is overly cautious.
-Infact, one of reasons for the positive performance of all-sky assimilation systems is also attributed to larger number of assimilated observations in comparison to clear-sky observations.
-If QRNN can provide the clear-sky NWP systems, cloud cleared microwave radiances with minimal rejection of data, we can reap forecast benefits without  additional complexities and inflation of errors.
-The all-sky assimilation systems could also benefit indirectly from cloud corrected radiances.
-To improve the representivity of clouds in the all-sky NWP models, the observational errors are inflated as a function of the cloud amount.
-QRNN could be employed here just to provide a measure of cloud impact.
+This is especially true for clear-sky assimilation systems, which reject up to 80\% of the available observations due to cloud contamination.
+One of reasons for the positive performance of all-sky assimilation systems is attributed to the larger number of assimilated observations in comparison to clear-sky observations.
+If QRNN can provide the clear-sky NWP systems with cloud cleared microwave radiances with minimal rejection of data, it may be possible to reap forecast benefits without additional complexities and computational cost of scattering calculations.
+The all-sky assimilation systems could also benefit indirectly from cloud corrected radiances, to provide a measure of cloud impact as a diagnostic field for analysing increments.
 Another advantage of combining 183\,GHz and sub-mm for cloud correction is that NWP systems, which are not yet prepared for higher frequency channels, could still benefit from the data early on.
@@
 In this study, we demonstrate the correction scheme with data from a limited period.
-The seasonal and latitudinal distributions are not taken into account.
-It remains to be  analysed for if QRNN shows any seasonal sensitivity or dependency on cloud types.
+The seasonal and latitudinal distributions are not taken into account, and more complex surfaces such as sea ice, snow, and high orography have not been considered.
+It remains to be seen whether QRNN shows any seasonal sensitivity or dependency on cloud types.
 Such analysis could also be important at improving the a priori distribution of rare cases.
@@
 These parameters determine the structure and the training set-up of the neural network.
-Several of these hyper-parameters are non-learnable, and must be defined before beginning of every training.
+Several of these hyper-parameters are non-learnable/, and must be defined before beginning of every training.
 Grid search is one of the most often employed techniques for hyper-parameter tuning.
@@
 For the structural parameters, usually a grid search over the number of neurons (width) and hidden layers (depth) is performed.
-The model is trained for multiple values of layer widths and hidden layers, and the best configuration is selected by evaluating the predictions over validation dataset.
+The model is trained for multiple values of layer widths and hidden layers, and the best configuration is selected by evaluating the predictions over validation data.
 Similarly, the training process is optimized by performing a grid search different training parameters such as : batch size, learning rate, number of epochs etc.
@@
 Firstly, we performed a grid search to define the structure of the neural network.
-We evaluated the performance for three sizes of hiddden layers($n_h$ = 2, 3, 4), and layer widths of sizes in the set [8, 16, 32, 64, 128, 256, 512].
+We evaluated the performance for three sizes of hidden layers($n_h$ = 2, 3, 4), and layer widths of sizes in the set [8, 16, 32, 64, 128, 256, 512].
 The mean quantile loss and CRPS over all predicted quantiles was computed for each configuration (Fig.~\ref{fig:grid_search}).
@@
 Though these set of hyper-parameters were selected for QRNN-single applied to I2V, they worked well for both ICI and AWS QRNN experiments.
-However, for MWHS-2, an identical hyperparameter framework but three hidden layers gave best results.
+However, for MWHS-2, an identical hyper-parameter framework but three hidden layers gave best results.
 

### 2020-11-11 MWHS/covariance_matrix.py
scripts for MWHS2 analysis

@@ -4,28 +4,16 @@
 Created on Fri Sep 11 21:57:41 2020
 
 @author: inderpreet
-
-calculate statistics for MWHS point estimates, the results are given in latex format
+Compute and plot the correlations between different channels 
 """
 
 import os
 import matplotlib.pyplot as plt
 import numpy as np
-import ICI.stats as S
 from read_qrnn import read_qrnn
 plt.rcParams.update({'font.size': 30})
 import seaborn as sns
 #%%
-
-def calculate_statistics(y_prior, y0, y, y_pre, im, i183):
-
-    bia      = S.calculate_bias(y_prior, y0, y, y_pre[:, 3], im, i183)
-    std      = S.calculate_std(y_prior, y0, y, y_pre[:, 3], im, i183)
-    ske      = S.calculate_skew(y_prior, y0, y, y_pre[:, 3], im, i183)
-    mae      = S.calculate_mae(y_prior, y0, y, y_pre[:, 3], im, i183)
-    
-    return bia, std, ske, mae
-
 def get_corr(im, Y_pre, Y):       
 
     A = (Y_pre[im, :] - Y[im]).T    
@@ -33,120 +21,119 @@ def get_corr(im, Y_pre, Y):
     
     return cov
 
-#%% input parameters
-depth     = 3
-width     = 128
-quantiles = np.array([0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998])
-batchSize = 128
+if __name__ == "__main__":
+    #%% input parameters
+    depth     = 3
+    width     = 128
+    quantiles = np.array([0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998])
+    batchSize = 128
+    
+    targets = [11, 12, 13, 14, 15]
+    
+    test_file = os.path.expanduser("~/Dendrite/Projects/AWS-325GHz/MWHS/data/TB_MWHS_test.nc")
+    
+    iq = np.argwhere(quantiles == 0.5)[0,0]
+    
+    qrnn_dir = "C89+150"
+    #qrnn_dir = "C150"
+    #qrnn_dir = "C150+118"
+         
+            
+    d = {"C89+150" : [1, 10],
+         "C89+150+118" : [1, 10, 6, 7 ],
+         "C150" : [10],
+         "C89+150+183" : [1, 10, 11, 12, 13, 14, 15]           
+        } 
+    
+    
[…]

### 2020-11-11 MWHS/mwhs.py

@@ -85,7 +85,9 @@ class mwhsData(Dataset):
         if test_data:
             test_file_path = path.replace("test", "test_noisy_allsky")
             test_file = netCDF4.Dataset(test_file_path, mode = "r")
-            TB_var = test_file.variables["TB_noise"]
+            print (test_file_path)
+            print (path)
+            TB_var = test_file.variables["TB"]
             TB_noise = TB_var[:]
                                                                      
             C = []

### 2020-11-11 MWHS/plot_calibration.py

@@ -8,20 +8,12 @@ This code plots the calibration curves for both QRNN-single and QRNN-all
 """
 import matplotlib.pyplot as plt
 import numpy as np
-import netCDF4
-import os
-import ICI.stats as stats
 from matplotlib.ticker import (MultipleLocator, FormatStrFormatter,
                                AutoMinorLocator)
-from typhon.retrieval.qrnn import set_backend, QRNN
-set_backend("pytorch")
-import ICI.stats as S
-
 from ICI.calibration import calibration
 from read_qrnn import read_qrnn
-import random
 plt.rcParams.update({'font.size': 26})
-
+import os
 
 #%% input parameters
 depth     = 3
@@ -42,7 +34,8 @@ if qrnn_dir == "C89+150":
     channels = [ 1, 10]
   
 target = 14 
-
+path = os.path.expanduser('~/Dendrite/Projects/AWS-325GHz/MWHS/data/')
+allChannels = np.arange(1, 16, 1)
 #%% read input data
         
 print(qrnn_dir, channels)
@@ -72,7 +65,7 @@ a1, a2, a3, a4, a5, a6, intervals  = calibration(y_pre, y0, im, quantiles)
                            a4/len(y0[:]), a5/len(y0[:]),
                           ], 'r.-', ms = 15, linewidth = 2.5))
 
-im = np.where(np.abs(y_pre[:, iq] - y_prior[:, i183]) >= 5)[0]
+im = np.where(np.abs(y_pre[:, iq] - y_prior[:, i183]) > 5)[0]
 a1, a2, a3, a4, a5, a6, intervals  = calibration(y_pre, y0, im, quantiles)     
 
 (ax.plot(intervals[:], [ a1/len(y0[im]), a2/len(y0[im]), a3/len(y0[im]), 
@@ -94,7 +87,7 @@ ax.xaxis.set_minor_locator(MultipleLocator(0.2))
 ax.grid(which = 'both', alpha = 0.2)
 fig.savefig('Figures/calibration_plot_%s'%target)
 
-(ax.legend(["All data", "correction > 10K"],
+(ax.legend(["All data", "correction > 5K"],
             prop={'size': 22}, frameon = False))  
 
 fig.savefig("Figures/calibration_QRNN_MWHS_%s.pdf"%target, bbox_inches = 'tight')
@@ -105,16 +98,18 @@ bin_center = (bins[:-1] + bins[1:]) / 2
[…]

### 2020-11-11 MWHS/plot_error_distribution.py

@@ -1,0 +1,163 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Fri Sep 11 21:57:41 2020
+
+@author: inderpreet
+
+plot the error distributions for MWHS-2
+"""
+
+import os
+import matplotlib.pyplot as plt
+import numpy as np
+import ICI.stats as S
+from read_qrnn import read_qrnn
+plt.rcParams.update({'font.size': 26})
+from matplotlib.ticker import (MultipleLocator, FormatStrFormatter,
+                               AutoMinorLocator)
+from tables_SI import get_SI_land, get_SI_ocean
+
+from mwhs import mwhsData
+#%%
+
+#%% input parameters
+depth     = 3
+width     = 128
+quantiles = np.array([0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998])
+batchSize = 128
+
+targets = [11, 12, 13, 14, 15]
+targets = [14]
+test_file = os.path.expanduser("~/Dendrite/Projects/AWS-325GHz/MWHS/data/TB_MWHS_test.nc")
+
+iq = np.argwhere(quantiles == 0.5)[0,0]
+
+qrnn_dir = "C89+150"
+#qrnn_dir = "C150"
+#qrnn_dir = "C150+118"
+     
+        
+d = {"C89+150" : [1, 10],
+     "C89+150+118" : [1, 10, 6, 7 ],
+      "C89+150+118_v2" : [1, 10,  7, 8 ],
+     "C150" : [10],
+     "C89+150+183" : [1, 10, 11, 12, 13, 14, 15]           
+    } 
+
+Channels = [[1, 10], [1, 6, 7, 10]]
+#qrnn_dirs = ["C89+150", "C89+150+118", "C89+150+118_v2" ]
+qrnn_dirs = ["C89+150"]
+
+bins = np.arange(-30, 10, 0.5)
+quantiles = np.array([0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998])
+iq = np.argwhere(quantiles == 0.5)[0,0]
+
+allChannels = np.arange(1, 16, 1)
+
+
+path = os.path.expanduser('~/Dendrite/Projects/AWS-325GHz/MWHS/data/')
+TB_ob = np.load(os.path.join(path, 'TB_obs.npy'))
+TB_fg = np.load(os.path.join(path, 'TB_fg.npy'))
[…]

### 2020-11-11 MWHS/plot_predicted_error.py

@@ -112,7 +112,7 @@ if __name__ == "__main__":
         fig, ax = plt.subplots(1, 1, figsize = [10, 10])
         print(qrnn_dir, channels)
         
-        qrnn_path = os.path.expanduser("~/Dendrite/Projects/AWS-325GHz/MWHS/qrnn_output/all_with_flag/%s/"%(qrnn_dir))
+        qrnn_path = os.path.expanduser("~/Dendrite/Projects/AWS-325GHz/MWHS/qrnn_output/new_data/%s/"%(qrnn_dir))
         
 
         inChannels = np.concatenate([[target], channels])
@@ -143,7 +143,7 @@ if __name__ == "__main__":
 
         ax.plot(center, hist_pre[0],'b', linewidth = 2.5)
     
-        ax.plot(center, hist_sample[0], 'b--', linewidth = 2.5)
+        ax.plot(center, hist_sample[0], 'r--', linewidth = 2.5)
 
         ax.xaxis.set_minor_locator(MultipleLocator(5))
         ax.yaxis.set_minor_locator(MultipleLocator(5))
@@ -159,7 +159,7 @@ if __name__ == "__main__":
         ax.set_ylabel('Occurence frequency [#/K]')
         ax.set_xlabel('Deviation to NFCS [K]')
 
-#        ax.set_ylim(0.0001, 1)                            
+        ax.set_ylim(0.0001, 1)                            
     #     ax.set_ylim(0.0001, 1)
         ax.legend([ "Observed", "Predicted", ],
                      prop={'size': 28}, frameon = False, )                                

### 2020-11-11 MWHS/plot_uncertainty.py

@@ -18,6 +18,10 @@ from typhon.retrieval.qrnn import set_backend, QRNN
 set_backend("pytorch")
 import random
 plt.rcParams.update({'font.size': 26})
+from matplotlib import colors as mcolors
+
+
+colors = dict(mcolors.BASE_COLORS, **mcolors.CSS4_COLORS)
 
 
 #%% input parameters
@@ -60,17 +64,31 @@ y_pre, y_prior, y0, y, y_pos_mean = read_qrnn(qrnn_file, test_file, inChannels, 
 fig, ax = plt.subplots(1, 1, figsize = [8, 8])
 x = np.arange(-3, 4, 1)
 ii = 0
-
-randomList = random.sample(range(0, 50000), 1500)
+y_all = []
+randomList = random.sample(range(0, 65000), 1500)
 for i in randomList:
     ii +=1
 #for i in ind:
     y1 = y_pre[i,  :] - y_pre[i, 3]
-    
-    ax.plot(x, y1,'b', alpha = 0.3)
+    y_all.append(y1)    
+    ax.plot(x, y1, color = colors["grey"], alpha = 0.4)
+
+
+#%% add box
+
+y_all = np.stack(y_all)
+box1 = ax.boxplot(y_all, positions = x, showfliers=False,  widths = 0.9)
+for item in ['boxes', 'whiskers', 'fliers', 'medians', 'caps']:
+        plt.setp(box1[item], color="darkred")
+
+#%%
+y_normal = np.random.normal(270, 1.0, 24000)
+q_normal = np.quantile(y_normal, quantiles , axis = 0)
+ax.plot( x, q_normal - q_normal[3], 'b', linewidth =2)
+ax.tick_params(axis='x', which='major', pad=10)
 
 ax.xaxis.set_minor_locator(MultipleLocator(5))
-ax.yaxis.set_minor_locator(MultipleLocator(5))
+ax.yaxis.set_minor_locator(MultipleLocator(2))
 ax.grid(which = 'both', alpha = 0.4)
 
 ax.set_xlabel("Quantiles")
@@ -85,14 +103,10 @@ q_prior = np.quantile(y_prior, quantiles, axis = 0)
 q0 = np.quantile(y0, quantiles, axis = 0)
 #ax.plot(x, q0 - q0[3])
 
-y_normal = np.random.normal(270, 1.0, 24000)
-q_normal = np.quantile(y_normal, quantiles , axis = 0)
[…]

### 2020-11-11 MWHS/tables_mwhs.py

@@ -25,124 +25,163 @@ def calculate_statistics(y_prior, y0, y, y_pre, im, i183):
     mae      = S.calculate_mae(y_prior, y0, y, y_pre[:, 3], im, i183)
     
     return bia, std, ske, mae
-#%% input parameters
-depth     = 3
-width     = 128
-quantiles = np.array([0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998])
-batchSize = 128
 
-targets = [11, 12, 13, 14, 15]
-targets = [14]
-test_file = os.path.expanduser("~/Dendrite/Projects/AWS-325GHz/MWHS/data/TB_MWHS_test.nc")
-
-iq = np.argwhere(quantiles == 0.5)[0,0]
-
-qrnn_dir = "C89+150"
-#qrnn_dir = "C150"
-#qrnn_dir = "C150+118"
-     
-        
-d = {"C89+150" : [1, 10],
-     "C89+150+118" : [1, 10, 6, 7 ],
-      "C89+150+118_v2" : [1, 10,  7, 8 ],
-     "C150" : [10],
-     "C89+150+183" : [1, 10, 11, 12, 13, 14, 15]           
-    } 
-
-Channels = [[1, 10], [1, 6, 7, 10]]
-#qrnn_dirs = ["C89+150", "C89+150+118", "C89+150+118_v2" ]
-qrnn_dirs = ["C89+150", "C89+150+118", "C150" ]
-
-
-
-#%%
-for target in targets:
-    BIA = []
-    MAE = []
-    STD = []
-    SKE = []
-    for qrnn_dir in qrnn_dirs:
-                
-        qrnn_path = os.path.expanduser("~/Dendrite/Projects/AWS-325GHz/MWHS/qrnn_output/all_with_flag/%s/"%(qrnn_dir))
-        
-        
-        channels = np.array(d[qrnn_dir])
-        
-        if target not in channels:
-            inChannels = np.concatenate([[target], channels])
-        else:
-            inChannels = channels
-        
-        print(qrnn_dir, channels, inChannels)
-            
-        qrnn_file = os.path.join(qrnn_path, "qrnn_mwhs_%s.nc"%(target))
-        
-        print (qrnn_file)
-        i183, = np.argwhere(inChannels == target)[0]
-        
-        y_pre, y_prior, y0, y, y_pos_mean = read_qrnn(qrnn_file, test_file, inChannels, target)
-        im = (np.abs(y_pre[:, 3] - y_prior[:, i183] )< 5) 
[…]

### 2020-11-13 Article/ici_submm_cloudcorr.tex
changes in Fig12, more details in AWS results

@@
 
-A methodology based on quantile regression neural networks (QRNN) is presented that identifies and corrects the cloud impact on microwave humidity sounder radiances at 183GHz.
+A methodology based on quantile regression neural networks (QRNN) is presented that identifies and corrects the cloud impact on microwave humidity sounder radiances at 183\,GHz.
 This approach estimates the posterior distributions of noise free clear-sky (NFCS) radiances, providing nearly bias-free estimates of clear-sky radiances with a full posterior error distribution.
@@
 The task that we aim to solve in this study is to predict the NFCS brightness
-temperature \todo{$\ynfcs$} at a given $183\unit{GHz}$ channel from a vector of
+temperature \todo{$\ynfcs$} at a given 183\,GHz channel from a vector of
 all-sky observations $\y$. Since the information-content of the
@@
 All evaluation results except hyper-parameter tuning, described in the study, have been made on the test dataset.
-Hyper-parameter tuning is made on the validation dataset (see Appendix~\ref{appendix:hyperparamter}).
-Validation dataset is part of the training dataset which is held back during the training process.
+The hyper-parameter tuning is made on the validation dataset (see Appendix~\ref{appendix:hyperparamter}).
+The validation dataset is part of the training dataset which is held back during the training process.
 
@@
 In order to formulate and test the correction approach, multiple QRNN experiments are performed for MWHS-2.
-However, for brevity we compare the comprehensive results only for channel 14.
+However, for brevity we show the comparison of the comprehensive results only for channel 14.
 Later the optimal experiment is extended to other 183\,GHz channels.
@@
 The last two columns show the statistics obtained after filtering cloudy cases according to scattering index (SI) and scheme by \citet{buehler:aclou:07} (B183).
-Bias, MAE, STD are in K, skewness in dimensionless.}
+Bias, MAE, STD are in K, skewness is dimensionless.}
 	\label{tab:error_statistics_mwhs_14}
@@
 		\middlehline
-Bias     & -0.00 &  -0.83 & -0.09 & -0.08 & -0.04 & -0.03 & -0.09 & -0.09 & -0.09 & -0.08 & -0.24 & -0.51\\
-MAE      &  0.80 &   1.44 &  0.88 &  0.86 &  0.89 &  0.87 &  0.89 &  0.87 &  0.62 &  0.59 &  0.92 &  1.14\\
-STD      &  1.00 &   3.89 &  1.19 &  1.14 &  1.19 &  1.15 &  1.21 &  1.16 &  0.90 &  0.83 &  1.26 &  1.83\\
-Skewness &  0.01 & -14.40 & -1.11 & -0.96 & -1.02 & -0.86 & -0.89 & -1.02 & -1.61 & -1.58 & -1.79 & -3.45\\
-Rejection&  -	 & - 	  & - 	  & 3.3\% & - 	  & 3.4\% & -     & 3.2\% & -     & 3.3\% & 28.1\%& 3.5\%\\
+Bias     &  0.00 &  -0.84 & -0.10 & -0.09 & -0.05 & -0.04 & -0.11 & -0.10 & -0.10 & -0.09 & 0.24  & -0.52\\
+MAE      &  0.80 &   1.45 &  0.89 &  0.87 &  0.90 &  0.88 &  0.90 &  0.88 &  0.62 &  0.60 & 0.92  & 1.15\\
+STD      &  1.00 &   3.73 &  1.20 &  1.16 &  1.21 &  1.16 &  1.22 &  1.18 &  0.91 &  0.85 & 1.26  & 1.86\\
+Skewness & -0.02 & -12.72 & -1.17 & -1.00 & -1.06 & -0.90 & -1.16 & -1.04 & -1.78 & -1.71 &-1.95  & -3.45\\
+Rejection&  -	 & - 	  & - 	  & 3.3\% & - 	  & 3.4\% & -     & 3.2\% & -     & 3.3\% & 28.8\%& 3.5\%\\
 \bottomhline
@@
 The corresponding error statistics(see Sect.~\ref{sec:validation}) are provided in  Table~\ref{tab:error_statistics_mwhs_14}.
-In the uncorrected all-sky simulations, the negative departures due to cloud impact lead to a large negative skewness(-14.34) and high bias (-0.84\,K).
-QRNN trained with 89 and 150\,GHz successfully corrects a major portion of the cloud affected cases, and the bias is reduced to -0.09\,K.
+In the uncorrected all-sky simulations, the negative departures due to cloud impact lead to a large negative skewness(-12.72) and high bias (-0.84\,K).
+QRNN trained with 89 and 150\,GHz successfully corrects a major portion of the cloud affected cases, and the bias is reduced to -0.10\,K.
 However, high skewness values indicate a negative tail or uncorrected departures.
@@
 Similar is the case with using only 150\,GHz.
-In the latter, predictions have the most symmetric error distributions, but the highest spread.
 
@@
 SI uses the differences of brightness temperatures between 89 and 150\,GHz to identify cloud affected data, whilst in the study by \citet{buehler:aclou:07}, they use brightness temperature based threshold to filter out cloudy cases.
-They recommend a viewing angle dependent brightness temperature threshold at $183.31\pm1.00$ \,GHz and brightness temperature difference between $183.31\pm3.00$ and $183.31\pm 1.00$ as a measure of cloud impact.
+They recommend a viewing angle dependent brightness temperature threshold at $183.31\pm1.00$ \,GHz and brightness temperature difference between $183.31\pm3.00$ \,GHz and $183.31\pm 1.00$ \,GHz as a measure of cloud impact.
 Further in the text we refer this filter as ``B183''.
@@
 Table~\ref{tab:error_statistics_mwhs_14} shows the error statistics for the experiment QRNN-all.
-In comparison to QRNN-single, we obtain marginally lower error bias with QRNN-all, and the MAE and standard deviation reduce by almost 30\% and 25\% respectively.
+In comparison to QRNN-single, we obtain almost similar error bias with QRNN-all, but the MAE and standard deviation reduce by almost 30\% and 24\% respectively.
 However, the negative tail becomes more prominent.
@@
 Even though QRNN-all gives slightly better prediction accuracy, its inherent construction makes it crucial to examine the correlation between observed errors.
-Fig.~\ref{fig:correlations_mwhs} illustrates the correlation matrix for both QRNN-all and QRNN-single.
+Figure~\ref{fig:correlations_mwhs} illustrates the correlation matrix for both QRNN-all and QRNN-single.
 For clear cases, the observed errors (noise) in QRNN-single are uncorrelated between the five channels.
@@
 		\middlehline
-		Channel 11  &   Bias      & 0.00 &  -0.16 & -0.03 & -0.03		 &-0.04	& -0.05 \\
-				    &	MAE       & 0.80 &   0.89 &  0.79 &  0.79  		 & 0.81	&  0.81 \\
-					&	STD       & 1.00 &   1.71 &  1.03 &  1.01 		 & 1.02	&  1.03 \\
-					&	Skewness  & 0.01 & -20.18 & -0.68 & -0.45 		 &-0.12 & -0.24 \\
-					& Rejection   & -    & -      & -	  & 0.2\%        & 28.1\% & 3.5\%  \\
-		\middlehline
-		Channel 12  & Bias      & -0.00 &  -0.28 & -0.05 & -0.05		&  -0.07 & -0.15 \\
-					& MAE       &  0.80 &   0.98 &  0.81 &  0.80  		&   0.82 &	0.86 \\
-					& STD       &  1.00 &   2.26 &  1.07 &  1.05  		&  1.04  &  1.14 \\
-					& Skewness  &  0.00 & -20.72 & -0.91 & -0.70  		&  -0.38 & -0.86 \\
-					& Rejection & -    & -      & -	  & 0.6\%        & 28.1\% & 3.5\%  \\
-		\middlehline
-		Channel 13  & Bias      & -0.00 &  -0.52 & -0.08 & -0.07 		& -0.14  & -0.29 \\
-					& MAE       &  0.80 &   1.17 &  0.84 &  0.83  		&  0.86  &  0.97 \\
-					& STD       &  1.00 &   3.04 &  1.13 &  1.10  		&  112  &	1.39 \\
-					& Skewness  &  0.02 & -17.85 & -1.14 & -0.98  		& -0.91  & -2.23 \\	
-					& Rejection   & -    & -      & -	  & 1.6\%        & 28.1\% & 3.5\%  \\	
-		\middlehline
-		Channel 15  & Bias      & -0.00 &  -1.28 & -0.07 & -0.06        & -0.33 &  -0.81 \\
-					& MAE       &  0.80 &   1.87 &  0.97 &  0.92 		&  1.03 &	1.44 \\
-					& STD       &  1.00 &   5.08 &  1.35 &  1.25 		&  1.53 &	2.64 \\
-					& Skewness  & -0.00 & -11.15 & -0.60 & -0.83 		& -2.85 &  -4.41 \\ 
-					& Rejection & -     & -      & -	 & 5.6\%        & 28.1\% & 3.5\%  \\
+		Channel 11  & Bias     & -0.00 &  -0.15 & -0.12 & -0.12 & -0.04 & -0.05\\
+					& MAE      &  0.80 &   0.88 &  0.80 &  0.80 &  0.81 & 0.81 \\
+					& STD      &  1.00 &   1.51 &  1.03 &  1.02 &  1.02 & 1.03 \\
+					& Skewness &  0.01 & -15.73 & -0.61 & -0.45 & -0.07 & -0.29\\
+					& Rejection   & -    & -      & -	  & 0.2\% & 28.8\% & 3.5\%  \\
+		\middlehline
+		Channel 12  &  Bias     & -0.01 &  -0.29 & -0.12 & -0.11  & -0.08 & -0.16\\
+					&  MAE      &  0.80 &   0.98 &  0.82 &  0.81  &  0.82 & 0.87\\
+					&  STD      &  1.00 &   2.02 &  1.08 &  1.06  &  1.04 & 1.15\\
+					&  Skewness & -0.01 & -17.27 & -0.96 & -0.79  &  -0.25 & -1.02 \\
+					& Rejection & -     & -      & -	 & 0.6\%  & 28.8\% & 3.5\%  \\
+		\middlehline
+		Channel 13  &Bias       & 0.00 &  -0.53 & -0.11 & -0.10 & -0.14 & -0.31\\
+					&MAE        & 0.80 &   1.18 &  0.85 &  0.84 &  0.86 & 0.98\\
+					&STD        & 1.00 &   2.83 &  1.15 &  1.12 &  1.12 & 1.41 \\
+					&Skewness   & 0.01 & -15.24 & -1.22 & -1.08 & -1.03 & -2.30\\  	
+					& Rejection & -     & -      & -	 & 1.6\%& 28.8\% & 3.5\%  \\	
+		\middlehline
+		Channel 15  &  Bias     & 0.00 &  -1.28 & -0.09 & -0.07 & -0.33 & -0.83\\
+					&  MAE      & 0.80 &   1.88 &  0.98 &  0.93 &  1.03 &  1.46\\
+					&  STD      & 1.00 &   4.97 &  1.36 &  1.27 &  1.52 &  2.69\\
+					&  Skewness & 0.00 & -10.11 & -0.69 & -0.82 & -2.87 &  -4.33 \\ 
+					& Rejection & -     & -      & -	 & 5.5\% & 28.8\%& 3.5\%  \\
 		\bottomhline
@@
 
-For channel 11, the error bias after correction is only -0.03\,K in comparison to 0.16\,K before correction.
+For channel 11, the error bias after correction is  -0.12\,K in comparison to 0.15\,K before correction.
 The strong negative tail also diminishes after correction, but a non-zero negative skewness indicates presence of cases with residual cloud impact in the corrected dataset.
@@
 A similar performance is evident for channel 12.
-Correction reduces the bias to -0.05\,K and standard deviation to 1.07\,K.
-The MAE is approximately 17\% lower after correction, but still the negative skewness is not removed completely.
+Correction reduces the bias to -0.12\,K and standard deviation to 1.08\,K.
+The MAE is approximately 16\% lower after correction, but still the negative skewness is not removed completely.
 For channel 13 and 15 also, a similar performance is seen.
-But in the latter, error distributions are most symmetric but with largest spread as compared to other four channels.
+But in the latter, error distributions are most skewed and have a larger spread as compared to other four channels.
+The impact of poor predictions is highest in channel 15 owing to its sensitivity to hydrometeor impact.
 
@@
 For channel 11 the performance of QRNN is comparable to both SI and B183.
-Similar is the case with channel 12, though the results from B183 are slightly poorer.
-Both these channels are mostly transparent to hydrometeor impact, and the filtering schemes work well.
+Similar is the case with channel 12 and channel 13, though the results from B183 are slightly poorer.
+The higher peaking channels are mostly transparent to hydrometeor impact, and the filtering schemes work well.
 The major caveat is the rejection of clear cases.
@@
 3\% in B183.
-For channels 13 and 15 the error statistics obtained with SI are slightly inferior in comparison to QRNN.
+For channel, 15 the error statistics obtained with SI are slightly inferior in comparison to QRNN.
 The results with B183 are even worse.
@@
 In contrast, the spread of predictions over quantiles $1\sigma$, $2\sigma$ and $3\sigma$ is wider.
-Also, cases with very high uncertainty occur infrequently.
-The box plots show that all the quantiles, except $3\sigma$ also follow the Gaussian distribution.
+The box plots indicate that cases with very high uncertainty occur infrequently.
+Also, all quantiles but  $3\sigma$, follow the Gaussian distribution.
 
@@
 However for the cases with correction greater than 5\,K, the distribution is poorly calibrated, and the curve lies below the $y =x$ line, indicating that the prediction intervals are too narrow.
-This is in agreement with the wider spread of predictions over the  higher quantiles (Fig.~\ref{fig:prediction_uncertainty_mwhs}).
+This is in agreement with the wider spread of uncertainties for cases with low accuracy (Fig.~\ref{fig:prediction_uncertainty_mwhs}).
 However such cases form less than 6\% of the dataset and filtering them has little effect on the overall calibration.
@@
 In this experiment, QRNN-single configuration is used and it is trained with all-sky simulations from all 325\,GHz frequencies from AWS and the target 183\,GHz channel.
-For example, for target AWS-32, the training inputs are AWS-32, AWS-41, AWS-42, AWS-43, AWS-44.
+For example, for the target AWS-32, the training inputs are AWS-32, AWS-41, AWS-42, AWS-43, AWS-44.
 QRNN is trained five times for each 183\,GHz channel as target.
@@
 		\middlehline
-		AWS-32  &Bias      & 0.00 & -1.32 &  -0.03 & -0.02(4.77\%) \\
-				&MAE      & 0.36 &  1.57 &   0.54 &  0.43 \\
-				&STD      & 0.46 &  6.42 &   1.02 &  0.61 \\
-				&Skewness & 0.01 & -8.43 &  -0.07 & -1.98 \\
-		\middlehline
-		AWS-33	&Bias      & -0.01 & -0.98 &  0.02 &  0.01(3.82\%) \\
-				&MAE      &  0.36 &  1.23 &  0.49 &  0.42 \\
-				&STD      &  0.45 &  4.70 &  0.76 &  0.56 \\
-				&Skewness & -0.00 & -8.78 &  0.04 & -0.79 \\
-
-		\middlehline
-		AWS-34	&Bias      &  0.00 &  -0.68 &  0.02 &  0.01(2.89\%) \\
-				&MAE      &  0.51 &   1.07 &  0.51 &  0.46 \\
-				&STD      &  0.64 &   3.67 &  0.75 &  0.60 \\
-				&Skewness & -0.00 & -10.32 & -0.55 & -0.59 \\
-		\middlehline
-		AWS-35	&Bias      &  0.00 &  -0.43 &  0.01 &  0.00(1.93\%) \\
-				&MAE      &  0.50 &   0.84 &  0.48 &  0.44 \\
-				&STD      &  0.63 &   2.65 &  0.71 &  0.57 \\
-				&Skewness & -0.01 & -12.49 & -0.40 & -0.29 \\
-		\middlehline
-		AWS-36  &Bias      & 0.00 &  -0.28 &   0.03  &  0.03(1.27\%) \\
-				&MAE       & 0.70 &   0.90 &   0.63  &  0.60 \\
-				&STD      & 0.88 &   2.06 &   0.86  &  0.76 \\
-				&Skewness & 0.01 & -11.80 &  -0.35  & -0.20 \\
+		AWS-32  &bias     & 0.00 & -1.32 & -0.04 & -0.02(4.71\%) \\
+				&mae      & 0.36 &  1.57 &  0.58 &  0.44 \\
+				&std      & 0.46 &  6.42 &  1.15 &  0.64 \\
+				&skewness & 0.01 & -8.43 & -1.09 & -2.29 \\
+		\middlehline
+		AWS-33	&bias     &  0.00 & -1.00 & -0.04 & -0.02(3.75\%)  \\
+				&mae      &  0.36 &  1.24 &  0.46 &  0.37  \\
+				&std      &  0.45 &  5.17 &  0.87 &  0.52  \\
+				&skewness & -0.01 & -9.59 & -3.25 & -1.26  \\
+
+		\middlehline
+		AWS-34	& bias    &  0.00 &  -0.71 & -0.06 & -0.04(2.86\%)  \\
+				&mae      &  0.50 &   1.10 &  0.47 &  0.41  \\
+				&std      &  0.63 &   4.05 &  0.82 &  0.56  \\
+				&skewness & -0.01 & -11.06 & -3.53 & -1.02  \\
+		\middlehline
+		AWS-35	& bias    & -0.00 &  -0.45 & -0.03 & -0.03(1.92\%)  \\
+				&mae      &  0.50 &   0.86 &  0.48 &  0.43  \\
+				&std      &  0.63 &   2.90 &  0.77 &  0.57  \\
+				&skewness &  0.00 & -13.43 & -2.46 & -0.62  \\
+		\middlehline
+		AWS-36  & bias    & -0.01 &  -0.29 & -0.04 & -0.04(1.23\%)  \\
+				&mae      &  0.71 &   0.90 &  0.63 &  0.60  \\
+				&std      &  0.89 &   2.17 &  0.88 &  0.77  \\
+				&skewness &  0.00 & -13.54 & -1.32 & -0.27  \\
 		\bottomhline				
@@
 For channel AWS-32, the average bias and standard deviation in the uncorrected dataset is -1.32\,K and 6.42\,K respectively.
-However, after correction, the bias and standard deviation reduce to -0.03\,K and 1.02\,K.
-A decrease in the skewness of error distributions is evident, but a relatively high value after prediction indicates presence of cases with partially-corrected cloud impact.
-Filtering out cases with 5\,K correction improves the statistics except for skewness, which increases.
+However, after correction, the bias and standard deviation reduce to -0.04\,K and 1.15\,K.
+A decrease in the skewness of error distributions is evident, but a relatively high value after correction indicates presence of cases with partially-corrected cloud impact.
+Filtering out cases with 5\,K correction improves the statistics but introduces asymmetry in the error distribution.
+This is most likely to due rejected cases suffering from over-estimation.
 For AWS-33, the predictions have slightly higher accuracy than AWS-32.
-The MAE in predictions is only 0.49\,K in comparison to 1.23\,K for the measurements.
-Low skewness and bias values indicate that the error distribution is quite symmetric.
-Similar results are also seen for AWS-35 and AWS-36.
-For both channels, the error distributions are relatively more symmetric than the other channels.
+The MAE in predictions is only 0.46\,K in comparison to 1.24\,K for the measurements.
+High skewness despite low bias is most likely due to presence of isolated cases with large negative deviations.
+Though, filtering such cases makes the distribution more symmetric.
+For AWS-34 and AWS-35, again a similar behaviour is seen, though the distributions are more symmetric in the latter.
+For AWS-36, we obtain the most symmetric and narrow distributions after correction owing to the low sensitivity of AWS-36 to hydrometeor impact.
 Also, it is worth to noting that when cases with 5\,K cloud correction are removed, the spread of prediction errors is narrower than noise for AWS-34, AWS-35 and AWS-36.
@@
 
-Fig.~\ref{fig:prediction_uncertainty_I2V} shows the spread of prediction uncertainties over different quantiles for randomly chosen 1500 cases.
+Figure~\ref{fig:prediction_uncertainty_I2V} shows the spread of prediction uncertainties over different quantiles for randomly chosen 1500 cases.
 The large spread in the predicted errors indicates that QRNN is successful in representing uncertainties for each case individually, rather than expressing them as a single measure.
@@
 
-Fig.~\ref{fig:calibration_I1V} shows the calibration of the prediction intervals for I2V.
+Figure~\ref{fig:calibration_I1V} shows the calibration of the prediction intervals for I2V.
 The predictions for the complete test dataset are well calibrated and follow the $y =x$ curve.
@@
 
-Fig.~\ref{fig:predicted_errors} shows the comparison of observed errors to predicted errors.
+Figure~\ref{fig:predicted_errors} shows the comparison of observed errors to predicted errors.
 The predicted and observed errors mostly have a good agreement but the predicted errors are spread out more asymmetrically towards the negative departures.
@@
 With AWS, the behaviour of predicted uncertainties is observed to be similar as for ICI (not shown).
-However, the relation between the mean uncertainty estimate and cloud impact is displayed in Fig.~\ref{fig:uncertainty_cloud_impact}.
+However, the relation between the mean uncertainty estimate ($\pm3\sigma$) and cloud impact is displayed in Fig.~\ref{fig:uncertainty_cloud_impact}.
 For all five channels, the predictions with small or relatively low cloud signal have a low uncertainty or in other words have high sharpness.
@@
 To use these observations correctly, data assimilation schemes often inflate their asymmetric error distributions at the cost of artificially suppressing the observational impact.
-However, the symmetric error distributions obtained from QRNN allow effective utilization more than 94\% of the data without the need for artificial error inflation.
+However, the symmetric error distributions obtained from QRNN allow effective utilization of almost complete data without the need for artificial error inflation.
+In fact for DA, filtering based on correction threshold would be needless as cases with low accuracy shall inevitably get inhibited due to high uncertainty.
 

### 2020-11-16 Article/ici_submm_cloudcorr.tex
added calibration plot ECMWF error model,  small modifications in text

@@
 \Author[1]{Simon}{Pfreundschuh}
-\Author[2]{David}{Duncan}
+\Author[2]{David Ian}{Duncan}
 
@@
 For NWP systems assimilating clear-sky observations, the effect of undetected clouds may be overcome by inflating the observational errors and diminishing the impact of observations.
-Furthermore, the mathematical assumptions of data assimilation are predicated on Gaussian errors with no mean bias, and residual cloud impacts that cause a net bias are not easily handled by variational bias correction.
+Furthermore, the mathematical assumptions of data assimilation (DA) are predicated on Gaussian errors with no mean bias, and residual cloud impacts that cause a net bias are not easily handled by variational bias correction.
 One solution is to apply a very strict filtering, but this increases the rejection of clear-sky values, i.e.\ an important loss of useful data.
@@
 cloud correction methods allow integration of ICI sub-mm observations in
-clear-sky data assimilation schemes with no further modifications, thus providing a simple
+clear-sky DA schemes with no further modifications, thus providing a simple
 way to make use this novel data source as soon as it becomes available.
@@
 		10	&	150.0         & 1500 			&	1.0 \\
-		11	&	183.31±1      & \phantom{0}500  &	1.0 \\
+		11	&	183.31±1.0      & \phantom{0}500  &	1.0 \\
 		12  & 	183.31±1.8    & \phantom{0}700 	&   1.0\\
-		13  & 	183.31±3      & 1000    		&	1.0	\\
+		13  & 	183.31±3.0      & 1000    		&	1.0	\\
 		14  & 	183.31±4.5    & 2000    		&	1.0\\
-		15  & 	183.31±7      & 2000  			&	1.0  \\
+		15  & 	183.31±7.0      & 2000  			&	1.0  \\
 		\bottomhline
@@
 		\middlehline
-		I1V&	183.31$\pm$7.00    & 2000 			& 0.8 		\\
-		I2V&	183.31$\pm$3.40    & 1500 			& 0.8 		\\
-		I3V&	183.31$\pm$2.00    & 1500			& 0.8 		\\
-		I5V&	325.15$\pm$9.50    & 3000			& 1.2 		\\
-		I6V&	325.15$\pm$3.50    & 2400			& 1.3 		\\
-		I6V&	325.15$\pm$1.50    & 1600			& 1.5 		\\
-		I8V&	448.00$\pm$7.20    & 3000			& 1.4 		\\
-		I9V&	448.00$\pm$3.00    & 2000			& 1.6 		\\
-		I10V&	448.00$\pm$1.40    & 1200			& 2.0 		\\
-		I11V&	664.00$\pm$4.20    & \phantom{0}500	& 1.6 		\\		
+		I1V&	183.31$\pm$7.0    & 2000 			& 0.8 		\\
+		I2V&	183.31$\pm$3.4    & 1500 			& 0.8 		\\
+		I3V&	183.31$\pm$2.0    & 1500			& 0.8 		\\
+		I5V&	325.15$\pm$9.5    & 3000			& 1.2 		\\
+		I6V&	325.15$\pm$3.5    & 2400			& 1.3 		\\
+		I6V&	325.15$\pm$1.5    & 1600			& 1.5 		\\
+		I8V&	448.00$\pm$7.2    & 3000			& 1.4 		\\
+		I9V&	448.00$\pm$3.0    & 2000			& 1.6 		\\
+		I10V&	448.00$\pm$1.4    & 1200			& 2.0 		\\
+		I11V&	664.00$\pm$4.2    & \phantom{0}500	& 1.6 		\\		
 		\bottomhline
@@
 
-Ice Cloud Imager (ICI) is a new instrument on board EPS-SG satellite MetOp-SG (Meteorological Operational - Second Generation).
+The Ice Cloud Imager (ICI) is a new instrument on board EPS-SG satellite MetOp-SG (Meteorological Operational - Second Generation).
 MetOp-SG is scheduled for launch in 2023, and it will make ICI the first operational sensor observing Earth using sub-mm wavelengths.
@@
 ICI and AWS frequencies are simulated with Atmospheric Radiative Transfer Simulator (ARTS, \citet{buehler:artst:18}).
-CloudSat\citep{Stephens2002cloudsat} profiles from August 2015 are randomly selected for forward simulations.
+CloudSat \citep{Stephens2002cloudsat} profiles during August 2015 are randomly selected for forward simulations.
 The input data are restricted between $60\unit{^{\degree}S}$ to $60\unit{^{\degree}N}$, and surface is below 500\,m.
@@
 The complete simulation setup is described in Appendix \ref{appendix:ARTS_setup}.
-For ICI and AWS, 220\,000 and 140\,000 cases are simulated, respectively.
+For ICI and AWS, 220\,000 and 143\,000 cases are simulated, respectively.
 All AWS sensor viewing angles (from $0^{\degree}$ to $45^{\degree}$) are simulated, but the results described in this study are based on nadir viewing angle.
@@
 The construction and details of the model are described in Sect.~\ref{sec:QRNN}.
-For MWHS-2, 220\,000 simulations are randomly selected as training dataset, while 70\,000 were used for testing.
+For MWHS-2, 220\,000 simulations are randomly selected as training dataset, while 70\,000 are used for testing.
 For ICI, 175\,000 cases are randomly picked to form the training set.
@@
 A smaller database is selected for AWS.
-120\,000 simulations are used for training and the rest are used for testing.
+120\,000 simulations are used for training and the rest for testing.
 
@@
 
-	\item QRNN-all: Same as QRNN-single, but all available 183\,GHz frequencies are included.      
+	\item QRNN-all: Same as QRNN-single, but all available 183\,GHz channels are included.      
 \end{enumerate}
@@
 The hyper-parameter tuning is made on the validation dataset (see Appendix~\ref{appendix:hyperparamter}).
-The validation dataset is part of the training dataset which is held back during the training process.
+The validation dataset is part of the training dataset which is held back during the training.
 
@@
 	\includegraphics[width = 70mm]{Figures/QRNN_output_mwhs.pdf} 
-	\caption{The distribution of point estimate $\ynfcs$ obtained from QRNN-single 89+150\,GHz for MWHS-2 channel 14.
-The corresponding distributions for all-sky and clear-sky simulations are also shown.}
+	\caption{The distribution of point estimate obtained from QRNN-single 89+150\,GHz for MWHS-2 channel 14. The corresponding distributions for all-sky and clear-sky simulations are also shown.}
 	\label{fig:distribution_predicted_mwhs14}	
@@
 The label ``All-sky'' represents the all-sky simulations, ``Predicted(All)'' denotes the predicted point estimates.
-The error distribution achieved with scattering index (SI) filtering is also shown.
+The error distribution achieved with scattering index (SI) filtering is also shown (Filtered(SI)).
 }
@@
 
-The posterior distribution of $\ynfcs$ obtained from experiment 89+150\,GHz is similar to the one shown in Fig.~\ref{fig:posterior_distribution_I1V}.
-The median value is chosen as the point estimate (see Sect.~\ref{sec:validation}).
-The distribution of point estimates is displayed in Fig.~\ref{fig:distribution_predicted_mwhs14}.
+The posterior distribution of $\ynfcs$ obtained from experiment 89+150\,GHz is similar to the one shown in Fig.~\ref{fig:posterior_distribution_I1V} and the distribution of point estimates is displayed in Fig.~\ref{fig:distribution_predicted_mwhs14}.
 The predicted values are able to correct most of the low brightness temperature cases, and overall a good match with the NFCS simulations is observed.
@@
 The deviations of point estimates to NFCS simulations are shown in Fig.~\ref{fig:error_distribution_mwhs14}.
-The large negative deviations are corrected successfully with QRNN (blue curve), but residual cloud impact is evident in the negative tail.
+The large negative deviations are removed (blue curve), but residual cloud impact is evident in the negative tail.
 Most of these residual cases have departures less than 10\,K.
+The appearance of a small positive tail also indicates overestimation in few cases.
 The corresponding error statistics(see Sect.~\ref{sec:validation}) are provided in  Table~\ref{tab:error_statistics_mwhs_14}.
@@
 QRNN trained with 89 and 150\,GHz successfully corrects a major portion of the cloud affected cases, and the bias is reduced to -0.10\,K.
-However, high skewness values indicate a negative tail or uncorrected departures.
+However, negative skewness indicates presence of  uncorrected departures.
 Including 118\,GHz in the training gives comparable results as 89+150\,GHz.
-With 118\,GHz, the error distribution has lower bias and are more symmetric, but the MAE and STD remain unaltered.
+The error distribution has lower bias and are more symmetric, but the MAE and standard deviation remain unaltered.
 This indicates that the information from 118\,GHz channels can be beneficial in predicting few cases correctly, but the overall consequence is not exceptionally different from 89+150\,GHz.
-Similar is the case with using only 150\,GHz.
-
-Further, we investigated whether filtering the predictions with low accuracy could help in improving the error distributions.
+Similar is the case with using only 150\,GHz---the differences between the three experiments are negligible.
+
+Further, we investigate whether filtering the predictions with low accuracy could help in improving the error distributions.
 For filtering such cases, we assume that predictions with cloud correction greater than 5\,K are associated with large deviations.
 In all three experiments, removing the cases with correction greater than 5\,K removes around 3\% of the data, but only a marginal positive impact on the accuracy is observed.
-With 5\,K threshold, though the cases with high errors are removed, the persistent negative skewness indicates presence of cases with residual cloud impact.
+The persistent negative skewness indicates presence of cases with residual cloud impact.
+Such cases are most likely to be associated with low cloud impact.
 Choosing a lower threshold can help in removing more partially corrected cases but at the cost of rejecting clear-sky cases.
@@
 Here only 3\% of the data is filtered out but the overall statistics are worse than both QRNN and SI.
-The results from the two filters are not surprising as both aim at removing only cases with high ice content.
-The thin cirrus clouds and other low hydrometeor impact cases remain unaltered.
+The results from the two filters are not surprising as both are partial filters and aim at removing only cases with high ice content.
+The low hydrometeor impact cases remain unaltered.
 
@@
 The positive effect of 118\,GHz was slightly higher for MWHS-2 channel 15, but for others, no notable effect was observed.
-The results for these channels with combination 89+150\,GHz are provided in Sect.~\ref{sec:mwhs_others}
+In view of negligible performance differences between the three experiments, we consider the combination 89+159\,GHz to be the optimal.
+The results for other channels with this experiment are provided in Sect.~\ref{sec:mwhs_others}
 
@@
 To assess the differences between the capabilities of QRNN-all against QRNN-single, we  compare the error statistics obtained for 89+150\,GHz and 89+150+183\,GHz for channel 14.
-Table~\ref{tab:error_statistics_mwhs_14} shows the error statistics for the experiment QRNN-all.
+Table~\ref{tab:error_statistics_mwhs_14} also shows the error statistics for the experiment QRNN-all.
 In comparison to QRNN-single, we obtain almost similar error bias with QRNN-all, but the MAE and standard deviation reduce by almost 30\% and 24\% respectively.
@@
 Since a majority of the cases are clear-sky, their impact dominates the whole statistics.
-In order to probe the positive effect of QRNN-all, we also estimate the errors for all cases with cloud correction greater than 5\,K.
-In comparison with QRNN-single, QRNN-all has slightly better accuracy.
-This suggests that concurrent use of all 183\,GHz channels can provide additional information on cloud structures to QRNN.
+In order to probe the positive effect of QRNN-all, we also estimate the errors for all cases with cloud correction greater than 5\,K (table not shown).
+For such cases,  QRNN-all has slightly better accuracy than QRNN-single.
+The bias in QRNN-all and standard deviation is -0.53\,K and 1.93\,K, respectively, in comparison to -0.61\,K and 2.04\,K as observed in QRNN-single.
+Thus, the concurrent use of all 183\,GHz channels can provide additional information on cloud structures to QRNN.
 
@@
 \begin{table*}[t]
-	\caption{ Error statistics for MWHS-2 channels 11, 12, 13 and 15 from QRNN-single experiment 89+150\,GHz.
-The labels ``All'' and ``Pred.(5\,K)' are same as described in Table~\ref{tab:error_statistics_mwhs_14}.
-The statistics from existing filtering approaches: scattering index (SI), and scheme by \citet{buehler:aclou:07} (B183) are also provided.}
+	\caption{ As Table~\ref{tab:error_statistics_mwhs_14}, but for MWHS-2 channels 11, 12, 13, 15, and experiment QRNN-single 89+150\,GHz.}
 	\label{tab:error_statistics_mwhs_others}
@@
 For channel 11, the error bias after correction is  -0.12\,K in comparison to 0.15\,K before correction.
-The strong negative tail also diminishes after correction, but a non-zero negative skewness indicates presence of cases with residual cloud impact in the corrected dataset.
+The decrease in bias is not significantly high but the strong negative tail  diminishes after correction, indicating removal of cases with large deviations.
+Nonetheless, the non-zero negative skewness also indicates presence of cases with residual cloud impact in the corrected dataset.
 Filtering the cases with high cloud impact has only a marginal positive effect.
 A similar performance is evident for channel 12.
-Correction reduces the bias to -0.12\,K and standard deviation to 1.08\,K.
+Correction reduces the bias to -0.12\,K from -0.29\,K and standard deviation to 1.08\,K from 2.02\.K.
 The MAE is approximately 16\% lower after correction, but still the negative skewness is not removed completely.
 For channel 13 and 15 also, a similar performance is seen.
-But in the latter, error distributions are most skewed and have a larger spread as compared to other four channels.
-The impact of poor predictions is highest in channel 15 owing to its sensitivity to hydrometeor impact.
+But in the latter, error distributions are most symmetric and have the largest spread as compared to other four channels.
+The effect of poor predictions is highest in channel 15 owing to its maximum sensitivity to hydrometeor impact.
 
@@
 The major caveat is the rejection of clear cases.
-With comparable accuracy, the fraction of rejection in SI is approx.
-28\% in comparison to approx.
-3\% in B183.
+With comparable accuracy, the fraction of rejection in SI is more than 28\% in comparison to only 3\% in B183.
 For channel, 15 the error statistics obtained with SI are slightly inferior in comparison to QRNN.
 The results with B183 are even worse.
-For all channels, the two filters succeed in removing the high ice cloud cases, but for lower peaking channels, the high negative skewness values indicate presence of cases with low cloud impact.
+For all channels, the two filters succeed in removing the high ice cloud cases, but for lower peaking channels, the high negative skewness values indicate presence of cases with low cloud impact, which pass the filter as ``clear''.
 Clearly the ``one for all'' approach of both filters is not adequate to cater for channel specific hydrometeor impact.
@@
 	\includegraphics[height = 70mm]{Figures/calibration_QRNN_MWHS_14.pdf}	
-	\caption{Calibration of the prediction intervals obtained from QRNN-single (89+150\,GHz) for MWHS-2 channel 14.
-Plots for both the complete dataset and the subset with correction greater than 5\,K are shown.
+	\caption{Calibration of the prediction intervals derived from QRNN-single (89+150\,GHz) for MWHS-2 channel 14, and prediction intervals derived from Gaussian error model for ECMWF NWP system (SI).
+For the former, the calibration for both the entire predicted dataset and the subset with correction greater than 5\,K are shown.
 }
@@
 The box plots indicate that cases with very high uncertainty occur infrequently.
+The highly uncertain predictions are mostly cloudy cases with low accuracy, but clear cases with high uncertainty could also be present.
 Also, all quantiles but  $3\sigma$, follow the Gaussian distribution.
 
-The calibration of the prediction intervals is displayed in Fig.~\ref{fig:calibration_mwhs}.
-For the entire dataset, the predictions follow the $y=x$ line, i.e.
+The calibration of the prediction intervals given out by QRNN is displayed in Fig.~\ref{fig:calibration_mwhs}.
+We also analyse the calibration of the observational error model used for MWHS-2 in ECMWF NWP system \citep{lawrence2018FY3C}.
+A gaussian error model is used to represent the distribution of the errors, and plotted under the label ``SI''.
+For the entire dataset, the predictions from QRNN follow the $y=x$ line, i.e.
 the predicted uncertainties are perfectly calibrated with the errors observed on the test data.
@@
 This is in agreement with the wider spread of uncertainties for cases with low accuracy (Fig.~\ref{fig:prediction_uncertainty_mwhs}).
-However such cases form less than 6\% of the dataset and filtering them has little effect on the overall calibration.
+However such cases form less than 6\% of the dataset.
+On the other hand, the calibration of ECMWF error model is above the diagonal for predicted probabilities above 0.2.
+This suggests that the true probability is higher than what is predicted on these intervals.
 
@@
 The high errors which we try to estimate are rare, and cannot be fully represented by QRNN.
+Note that since we do not derive any sample from outside $\pm3\sigma$, such cases could also belong to 0.003\% population not represented by the quantiles.
 
@@
 		%		\hline
-		&&Clear-sky &   All-sky &  \multicolumn{2}{c}{Predicted}  \\
-		&&			   &			&	All & 5\,K \\
+		&&Clear-sky &   All-sky &  \multicolumn{2}{c}{Pred.}  \\
+		&&			   &			&	(All) & (5\,K) \\
 		\middlehline
@@
 For all three channels, quite similar behaviour is observed, though I1V has the most cases with residual cloud impact.
-If the predicted cases with correction more than 5\,K are rejected, the resulting error distributions fit the measurement noise, except for I1V, where cases with residual cloud impact introduce a negative bias.
+If the predicted cases with correction more than 5\,K are rejected, the resulting error distributions fit the measurement noise, except for I1V, where cases with residual cloud impact introduce a small negative bias.
 For a quantitative assessment of the errors, the results from various error metrics described in  Sect.~\ref{sec:validation} are displayed in Table~\ref{tab:error_statistics_ici}.
@@
 In comparison to I1V and I2V, I3V has the lowest fraction of the measurements with significant cloud impact.
-In the predicted dataset, the bias is 0.02\,K and the MAE is 0.54\,K.
-Including correction along with filtering reduces the MAE further down to 0.50\,K and standard deviation to 0.63\,K.
+In the predicted dataset, the MAE is 0.54\,K  and standard deviation is 0.80\,K.
+Filtering the cases with large correction reduces the MAE to 0.50\,K and standard deviation to 0.63\,K.
+For all three channels, the correction threshold filter is successful in removing the cases with low accuracy.
+This is in contrast with results obtained with MWHS-2, where negative bias due to low cloudy cases is persistent even after filtering.
 
@@
 		\middlehline
-		AWS-32  &bias     & 0.00 & -1.32 & -0.04 & -0.02(4.71\%) \\
-				&mae      & 0.36 &  1.57 &  0.58 &  0.44 \\
-				&std      & 0.46 &  6.42 &  1.15 &  0.64 \\
-				&skewness & 0.01 & -8.43 & -1.09 & -2.29 \\
-		\middlehline
-		AWS-33	&bias     &  0.00 & -1.00 & -0.04 & -0.02(3.75\%)  \\
-				&mae      &  0.36 &  1.24 &  0.46 &  0.37  \\
-				&std      &  0.45 &  5.17 &  0.87 &  0.52  \\
-				&skewness & -0.01 & -9.59 & -3.25 & -1.26  \\
-
-		\middlehline
-		AWS-34	& bias    &  0.00 &  -0.71 & -0.06 & -0.04(2.86\%)  \\
-				&mae      &  0.50 &   1.10 &  0.47 &  0.41  \\
-				&std      &  0.63 &   4.05 &  0.82 &  0.56  \\
-				&skewness & -0.01 & -11.06 & -3.53 & -1.02  \\
-		\middlehline
-		AWS-35	& bias    & -0.00 &  -0.45 & -0.03 & -0.03(1.92\%)  \\
-				&mae      &  0.50 &   0.86 &  0.48 &  0.43  \\
-				&std      &  0.63 &   2.90 &  0.77 &  0.57  \\
-				&skewness &  0.00 & -13.43 & -2.46 & -0.62  \\
-		\middlehline
-		AWS-36  & bias    & -0.01 &  -0.29 & -0.04 & -0.04(1.23\%)  \\
-				&mae      &  0.71 &   0.90 &  0.63 &  0.60  \\
-				&std      &  0.89 &   2.17 &  0.88 &  0.77  \\
-				&skewness &  0.00 & -13.54 & -1.32 & -0.27  \\
+		AWS-32  &Bias     & 0.00 & -1.32 & -0.04 & -0.02(4.71\%) \\
+				&MAE      & 0.36 &  1.57 &  0.58 &  0.44 \\
+				&STD      & 0.46 &  6.42 &  1.15 &  0.64 \\
+				&Skewness & 0.01 & -8.43 & -1.09 & -2.29 \\
+		\middlehline
+		AWS-33	&Bias     &  0.00 & -1.00 & -0.04 & -0.02(3.75\%)  \\
+				&MAE      &  0.36 &  1.24 &  0.46 &  0.37  \\
+				&STD      &  0.45 &  5.17 &  0.87 &  0.52  \\
+				&Skewness & -0.01 & -9.59 & -3.25 & -1.26  \\
+
+		\middlehline
+		AWS-34	&Bias    &  0.00 &  -0.71 & -0.06 & -0.04(2.86\%)  \\
+				&MAE      &  0.50 &   1.10 &  0.47 &  0.41  \\
+				&STD      &  0.63 &   4.05 &  0.82 &  0.56  \\
+				&Skewness & -0.01 & -11.06 & -3.53 & -1.02  \\
+		\middlehline
+		AWS-35	&Bias    & -0.00 &  -0.45 & -0.03 & -0.03(1.92\%)  \\
+				&MAE      &  0.50 &   0.86 &  0.48 &  0.43  \\
+				&STD      &  0.63 &   2.90 &  0.77 &  0.57  \\
+				&Skewness &  0.00 & -13.43 & -2.46 & -0.62  \\
+		\middlehline
+		AWS-36  &Bias    & -0.01 &  -0.29 & -0.04 & -0.04(1.23\%)  \\
+				&MAE      &  0.71 &   0.90 &  0.63 &  0.60  \\
+				&STD      &  0.89 &   2.17 &  0.88 &  0.77  \\
+				&Skewness &  0.00 & -13.54 & -1.32 & -0.27  \\
 		\bottomhline				
@@
 Filtering out cases with 5\,K correction improves the statistics but introduces asymmetry in the error distribution.
-This is most likely to due rejected cases suffering from over-estimation.
+This is most likely due to rejection of cases affected by over-estimation.
 For AWS-33, the predictions have slightly higher accuracy than AWS-32.
 The MAE in predictions is only 0.46\,K in comparison to 1.24\,K for the measurements.
-High skewness despite low bias is most likely due to presence of isolated cases with large negative deviations.
-Though, filtering such cases makes the distribution more symmetric.
+High skewness despite low bias (0.04\,K) is most likely due to presence of isolated cases with large negative deviations.
+Nonetheless, filtering such cases makes the distribution more symmetric.
 For AWS-34 and AWS-35, again a similar behaviour is seen, though the distributions are more symmetric in the latter.
@@
 	\includegraphics[width = 70mm]{Figures/prediction_uncertainty_I2V.pdf}	
-	\caption{Same as Fig.~\ref{fig:prediction_uncertainty_mwhs}, but from QRNN-single for ICI channel I2V.
-The blue line represents a hypothetical Gaussian distribution of $270\pm0.60$\,K, which is of the order of standard deviation for I2V predictions (see Table~\ref{tab:error_statistics_ici}).}
+	\caption{Same as Fig.~\ref{fig:prediction_uncertainty_mwhs}, but from QRNN-single for ICI channel I2V. The blue line represents a hypothetical Gaussian distribution of $270\pm0.65$\,K.}
 	\label{fig:prediction_uncertainty_I2V}	
@@
 	\includegraphics[width = 70mm]{Figures/cloud_impact_uncertainty_AWS.pdf}	
-	\caption{The average confidence intervals (2$\sigma$) plotted against the magnitude of cloud impact for all AWS channels.}
+	\caption{The average confidence intervals (3$\sigma$) plotted against the magnitude of cloud impact for all AWS channels.}
 	\label{fig:uncertainty_cloud_impact}	
@@
 This could also be a sampling issue, as the high errors we try to predict constitute a very small part of the complete dataset.
-Note that since we do not derive any sample from outside $\pm3\sigma$, such cases could also belong to 0.003\% population not represented by the quantiles.
 
@@
 To conclude the results, we analyse if the uncertainty estimates given by QRNN are representative of prediction accuracy.
-Fig.~\ref{fig:error_distribution_uncertainty_bins} shows the observed errors binned by their corresponding uncertainty in $\pm2\sigma$  confidence interval.
+Figure~\ref{fig:error_distribution_uncertainty_bins} shows the observed errors binned by their corresponding uncertainty in $\pm2\sigma$  confidence interval.
 For all three channels, the spread of error distribution increases as the uncertainty about the accuracy of the trial increases.
@@
 This increases the probability of erroneously removing clear observations.
-For high peaking channels of MWHS-2, both SI and QRNN give almost similar results, but with almost 30\% rejection rate.
+For high peaking channels of MWHS-2, both SI and QRNN give almost similar results, but with almost 28\% rejection rate.
 On the other hand, for low peaking channels, SI gives less accurate results than QRNN, as these channels have a stronger hydrometeor impact.
@@
 
-\subsection{Prediction uncertainty and implications for DA}
+\subsection{Prediction uncertainty and implications for data assimilation}
 
@@
 Most of the existing cloud filtering schemes work well only at removing cases with high cloud impact, and as a consequence, the error distributions are highly skewed.
-To use these observations correctly, data assimilation schemes often inflate their asymmetric error distributions at the cost of artificially suppressing the observational impact.
+To use these observations correctly, DA schemes often inflate their asymmetric error distributions at the cost of artificially suppressing the observational impact.
 However, the symmetric error distributions obtained from QRNN allow effective utilization of almost complete data without the need for artificial error inflation.
@@
 This is especially true for clear-sky assimilation systems, which reject up to 80\% of the available observations due to cloud contamination.
-One of reasons for the positive performance of all-sky assimilation systems is attributed to the larger number of assimilated observations in comparison to clear-sky observations.
+In fact, one of reasons for the positive performance of all-sky assimilation systems is attributed to the larger number of assimilated observations in comparison to clear-sky observations.
 If QRNN can provide the clear-sky NWP systems with cloud cleared microwave radiances with minimal rejection of data, it may be possible to reap forecast benefits without additional complexities and computational cost of scattering calculations.
@@
 
-\codeavailability{QRNN is available as a part of the \textit{typhon: tools for atmospheric research},  https://doi.org/10.5281/zenodo.3626449.}
-
-\dataavailability{TEXT} %% use this section when having only data sets available
-
-\codedataavailability{TEXT} %% use this section when having data sets and software code available
-
-\sampleavailability{TEXT} %% use this section when having geoscientific samples available
-
-\videosupplement{TEXT} %% use this section when having video supplements available
+\codeavailability{QRNN is available as a part of the \textit{typhon: tools for atmospheric research},  https://doi.org/10.5281/zenodo.3626449.
+The source code for all the analysis presented in the article is available as git repository ( \todo{???} ) }
 
@@
 
-\authorcontribution{TEXT} %% this section is mandatory
-
-\competinginterests{TEXT} %% this section is mandatory even if you declare that no competing interests are present
-
-\disclaimer{TEXT} %% optional section
+\authorcontribution{The study was conceptualised and supervised by PE.
+The analysis, validation and visualisation of results was done IK.
+The QRNN package is made available by SP.
+IK wrote the original draft, with help from PE, SP and DID.
+DID also provided the data for MWHS-2.
+All authors contributed to the study with discussions and feedback.}
+
+\competinginterests{The authors declare no conflict of interest.}
 

### 2020-11-18 Article/ici_submm_cloudcorr.tex
updated with Patrick's latest comments

@@
 The Ice Cloud Imager (ICI) is a new instrument on board EPS-SG satellite MetOp-SG (Meteorological Operational - Second Generation).
-MetOp-SG is scheduled for launch in 2023, and it will make ICI the first operational sensor observing Earth using sub-mm wavelengths.
+MetOp-SG is scheduled for launch in 2024, and it will make ICI the first operational sensor observing Earth using sub-mm wavelengths.
 The main objective of ICI is to use high frequency channels for measuring ice cloud properties, and improve the representation of ice clouds in regional and global NWP models.
@@
 
-For this study, we conducted the forward simulations at frequencies: 183.31\,GHz, 325.15\,GHz, 448.00\,GHz and 664.00\,GHz (See Table~\ref{tab:ICI_MWI_channels}).
+For this study, we conducted the forward simulations of the channels around: 183.31\,GHz, 325.15\,GHz, 448.00\,GHz and 664.00\,GHz (Table~\ref{tab:ICI_MWI_channels}).
 For brevity, we assume that all simulations are mapped to a common footprint.
@@
 The first prototype mission is expected to be delivered around 2023.
-The exact channels onboard AWS are not yet set, but five 183\,GHz and four 325\,GHz channels shall be included.
+The exact channels onboard AWS are not yet set, but five 183\,GHz and four 325\,GHz channels are presently planned.
 A brief summary of these channels is provided in Table~\ref{tab:specifications_AWS}.
 
-In this study, forward simulations at frequencies 183.31\,GHz and 325.15\,GHz were conducted.
+In this study, forward simulations of the channels around 183.31\,GHz and 325.15\,GHz were conducted.
 
@@
 All AWS sensor viewing angles (from $0^{\degree}$ to $45^{\degree}$) are simulated, but the results described in this study are based on nadir viewing angle.
-Simulations for all three sensors are noise free, so to incorporate the measurement uncertainties, whenever needed, gaussian noise is added to according to the channel NE$\Delta$T (see Table~\ref{tab:specifications_MWHS2} - Table~\ref{tab:specifications_AWS}).
+Simulations for all three sensors are noise free, so to incorporate the measurement uncertainties, whenever needed, gaussian noise is added to according to the channel NE$\Delta$T (Table~\ref{tab:specifications_MWHS2} - Table~\ref{tab:specifications_AWS}).
 
@@
 The task that we aim to solve in this study is to predict the NFCS brightness
-temperature \todo{$\ynfcs$} at a given 183\,GHz channel from a vector of
+temperature $\ynfcs$ at a given 183\,GHz channel from a vector of
 all-sky observations $\y$. Since the information-content of the
@@
 for all selected quantile fractions $\tau$, where $y_\tau$ is the predicted
-quantile and $y$ the reference value from the training or test data . The
-quantile loss is used in this study as a performance criterion for the tuning of
+quantile and $y$ the reference value from the training or test data. The
+quantile loss is also used in this study as a performance criterion for the tuning of
 the hyper-parameters of the QRNN (see Appendix~\ref{appendix:hyperparamter}). In
@@
 used to derive a piece-wise linear approximation of the CDF of the predicted
-distribution.
+distribution. Note that CRPS is only used to evaluate hyper-parameter tuning.
 
@@
 
-The posterior distribution of $\ynfcs$ obtained from experiment 89+150\,GHz is similar to the one shown in Fig.~\ref{fig:posterior_distribution_I1V} and the distribution of point estimates is displayed in Fig.~\ref{fig:distribution_predicted_mwhs14}.
+Posterior distributions of $\ynfcs$ obtained from experiment 89+150\,GHz are similar to the ones shown in Fig.~\ref{fig:posterior_distribution_I1V} and the distribution of point estimates is displayed in Fig.~\ref{fig:distribution_predicted_mwhs14}.
 The predicted values are able to correct most of the low brightness temperature cases, and overall a good match with the NFCS simulations is observed.
-However, QRNN is unable to predict the lowest clear-sky brightness temperatures, and cases with brightness temperatures around 260\,K occur frequently.
+However, QRNN is unable to predict the lowest clear-sky brightness temperatures, and cases with brightness temperatures around 260\,K occur too frequently.
 The deviations of point estimates to NFCS simulations are shown in Fig.~\ref{fig:error_distribution_mwhs14}.
@@
 The appearance of a small positive tail also indicates overestimation in few cases.
-The corresponding error statistics(see Sect.~\ref{sec:validation}) are provided in  Table~\ref{tab:error_statistics_mwhs_14}.
+The corresponding error statistics (see Sect.~\ref{sec:validation}) are provided in  Table~\ref{tab:error_statistics_mwhs_14}.
 In the uncorrected all-sky simulations, the negative departures due to cloud impact lead to a large negative skewness(-12.72) and high bias (-0.84\,K).
@@
 However, negative skewness indicates presence of  uncorrected departures.
-Including 118\,GHz in the training gives comparable results as 89+150\,GHz.
+Including 118\,GHz in the training gives a small improvement compared to 89+150 GHz alone.
 The error distribution has lower bias and are more symmetric, but the MAE and standard deviation remain unaltered.
-This indicates that the information from 118\,GHz channels can be beneficial in predicting few cases correctly, but the overall consequence is not exceptionally different from 89+150\,GHz.
+This indicates that the information from 118\,GHz channels can be beneficial in predicting few cases correctly, but the overall performance is not exceptionally different from 89+150\,GHz.
 Similar is the case with using only 150\,GHz---the differences between the three experiments are negligible.
@@
 In all three experiments, removing the cases with correction greater than 5\,K removes around 3\% of the data, but only a marginal positive impact on the accuracy is observed.
-The persistent negative skewness indicates presence of cases with residual cloud impact.
-Such cases are most likely to be associated with low cloud impact.
+The persistent negative skewness, even after filtering, indicates presence of cases with residual cloud impact.
+Such cases are most likely to be associated with low or medium cloud impact.
 Choosing a lower threshold can help in removing more partially corrected cases but at the cost of rejecting clear-sky cases.
@@
 
-In spite of the fact that QRNN only provides a partial cloud correction, the results for  MWHS-2 channel 14 are comparable to what we achieve with existing cloud filtering techniques like scattering index (SI) and the filtering scheme by \citet{buehler:aclou:07}.
+In spite of the fact that QRNN only provides a partial cloud correction, the results for  MWHS-2 channel 14 are better than what we achieve with existing cloud filtering techniques like scattering index (SI) and the filtering scheme by \citet{buehler:aclou:07}.
 SI uses the differences of brightness temperatures between 89 and 150\,GHz to identify cloud affected data, whilst in the study by \citet{buehler:aclou:07}, they use brightness temperature based threshold to filter out cloudy cases.
@@
 
-The three experiments were also performed for other four 183\,GHz channels, and a similar performance was obtained (Table not shown).
+The three experiments were also performed for other four 183\,GHz channels, and a similar performance was obtained (not shown).
 The positive effect of 118\,GHz was slightly higher for MWHS-2 channel 15, but for others, no notable effect was observed.
@@
 For channel 13 and 15 also, a similar performance is seen.
-But in the latter, error distributions are most symmetric and have the largest spread as compared to other four channels.
+But in the latter, error distributions are more symmetric and have the largest spread as compared to other four channels.
 The effect of poor predictions is highest in channel 15 owing to its maximum sensitivity to hydrometeor impact.
@@
 The quantiles have been plotted at equidistant points.
-The blue line represents a hypothetical Gaussian distribution of $270\pm1.0$\,K.
+The blue line represents a Gaussian distribution with a standard deviation of $1.0$\,K.
 For each quantile, the sample variation is also shown as box plot.
@@
 	\includegraphics[width = 70mm]{Figures/prediction_uncertainty_I2V.pdf}	
-	\caption{Same as Fig.~\ref{fig:prediction_uncertainty_mwhs}, but from QRNN-single for ICI channel I2V. The blue line represents a hypothetical Gaussian distribution of $270\pm0.65$\,K.}
+	\caption{Same as Fig.~\ref{fig:prediction_uncertainty_mwhs}, but from QRNN-single for ICI channel I2V. The blue line represents a Gaussian distribution with a standard deviation of $0.65$\,K.}
 	\label{fig:prediction_uncertainty_I2V}	
@@
 	\caption{Same as Fig.~\ref{fig:calibration_mwhs}, but from QRNN-single for ICI channel I2V. }
-	\label{fig:calibration_I1V}	
+	\label{fig:calibration_I2V}	
 \end{figure}
@@
 	\includegraphics[width = 70mm]{Figures/cloud_impact_uncertainty_AWS.pdf}	
-	\caption{The average confidence intervals (3$\sigma$) plotted against the magnitude of cloud impact for all AWS channels.}
+	\caption{The average confidence intervals ($\pm3\sigma$) plotted against the magnitude of cloud impact for all AWS channels.}
 	\label{fig:uncertainty_cloud_impact}	
@@
 
-Figure~\ref{fig:calibration_I1V} shows the calibration of the prediction intervals for I2V.
+Figure~\ref{fig:calibration_I2V} shows the calibration of the prediction intervals for I2V.
 The predictions for the complete test dataset are well calibrated and follow the $y =x$ curve.
-On the other hand, when only the cases with  cloud correction greater than 10\,K are considered, the predictions in all the intervals are poorly calibrated.
-In this case, the predicted intervals are too wide over lower quantiles and too wide over higher quantiles.
+Similar is the case, when cases with correction greater than 5\,K are considered.
+On the other hand, when  the cases with cloud correction greater than 10\,K are considered, the calibration is only slightly worse.
+In spite of the fact that such cases are few (~2\%), the high calibration indicates that QRNN is also successful in predicting the uncertainties associated with rare cases.
+For other two channels also the predictions are well calibrated, except for cases with correction greater than 5\,K in channel I1V (not shown).
 
@@
 To conclude the results, we analyse if the uncertainty estimates given by QRNN are representative of prediction accuracy.
-Figure~\ref{fig:error_distribution_uncertainty_bins} shows the observed errors binned by their corresponding uncertainty in $\pm2\sigma$  confidence interval.
+Figure~\ref{fig:error_distribution_uncertainty_bins} shows the observed ICI errors binned by their corresponding uncertainty in $\pm2\sigma$  confidence interval.
 For all three channels, the spread of error distribution increases as the uncertainty about the accuracy of the trial increases.
@@
 This increases the probability of erroneously removing clear observations.
-For high peaking channels of MWHS-2, both SI and QRNN give almost similar results, but with almost 28\% rejection rate.
+For high peaking channels of MWHS-2, both SI and QRNN give almost similar results, but with almost 28\% rejection rate in the former.
 On the other hand, for low peaking channels, SI gives less accurate results than QRNN, as these channels have a stronger hydrometeor impact.
@@
 Among these four channels, 150\,GHz has the highest peaking function around 4\,km \citep{chen2020mwhs}.
-These channels can only provide coverage to the humidity channels in lower and mid troposphere; nonetheless, the 183\,GHz channels are sensitive to hydrometeor content up to 2\,km.
+These channels can only provide coverage to the humidity channels in lower and mid troposphere; nonetheless, the 183\,GHz channels are sensitive to hydrometeor content up to 10\,km.
 Due to missing complementary information from other channels in the upper troposphere, QRNN fails at predicting these cases accurately.
@@
 In the ICI observations examined here, the results show that using sub-mm channels can successfully predict the NFCS values with very high accuracy for I2V, and I3V.
-The predicted values without any filter have an excellent match with the true values, and the departures are symmetrically distributed around zero mean.
+The predicted values have an excellent match with the true values, and the departures are symmetrically distributed around zero mean.
 Few cases with high cloud impact do affect the accuracy and introduce a small negative bias, but such cases are easily filtered out with a simple correction threshold filter.
@@
 Interestingly, reducing the correction threshold further has no significant effect on flagging these residual cases.
-In fact only the clear-sky cases are removed.
+In fact only clear-sky cases are removed.
 This is a consequence of the correction being too low.
 Since such cases introduce a small negative bias and skewness, they are more appropriately related to low-cloud impact.
-Compared to other two higher peaking channels, I1V is more sensitive to the effect of hydrometeors  and contamination from surface effects.
+Compared to other two higher peaking channels, I1V is more sensitive to the effect of hydrometeors  and contamination from surface effects (Fig.4 of \citet{eriksson:towar:20}).
 The cases with surface contamination are also localized and seasonal.
@@
 QRNN predictions are weighted mean of measurements between channels.
-For clear-sky conditions, multiple observations of same scene from different channels can cancel out the noise.
-This effect is observed to be stronger in ICI than AWS, as the former has additional input channels giving same information.
+In the absence of clouds, also the sub-mm channels provide humidity information that is incorporated in the 183 GHz NFCS estimate and some compensation of noise can be achieved.
+This effect is observed to be stronger in ICI than AWS, as the former has a higher number of channels giving redundant information.
 Note that with actual satellite measurements, the spread of error distributions smaller than sensor noise could be difficult to achieve due to other underlying uncertainties not considered here.
@@
 
-Another advantage of QRNN is estimation of case-specific uncertainties.
-The predictions over chosen quantiles quantify the underlying uncertainty.
-The analysis of QRNN predicted errors and calibration plots show that QRNN is successful in providing well calibrated probabilistic predictions of the posterior distributions except for few cases associated with high error.
-The poorly calibrated predictions are a consequence of cases with different underlying a priori distribution.
-Predictions with high error originate from cases with high cloud impact or cases with no orthogonal information.
+Another advantage of QRNN is the estimation of case-specific uncertainties.
+That is, the predictions over chosen quantiles quantify the underlying uncertainty of the particular case, and not just represent some ensemble mean error.
+This has the consequence that a DA system can assign a proper weighting of each individual QRNN prediction.
+The analysis of QRNN predicted errors and calibration plots confirmed that QRNN is successful in providing
+well calibrated probabilistic predictions also in practice, except for few cases associated with high error.
+Poorly calibrated predictions are a consequence of cases with different underlying a priori distribution.
+Predictions with high error originate from cases which occur infrequently or cases with no orthogonal information.
 Such cases have a significantly distinct a priori distribution as compared to clear cases, which dominate the training dataset and influence the a priori information.
@@
 
-The symmetric and low spread error distribution with uncertainty estimates is an important result from the DA perspective.
+The symmetric and low spread error distribution with uncertainty estimates is also an important result from the DA perspective.
 Most of the existing cloud filtering schemes work well only at removing cases with high cloud impact, and as a consequence, the error distributions are highly skewed.
@@
 
-Based on the promising results from MWHS-2, and with future scope, we extend the study to include data from sub-millimetre (sub-mm) channels.
+Based on the promising results from MWHS-2, and with future scope, we extend the study to include data from Ice Cloud Imager (ICI) sub-millimetre (sub-mm) channels.
 The results show that with  sub-mm channels, QRNN is able to correctly predict most of the cloudy cases and can provide high quality cloud corrected radiances.
@@
 The results indicate that utilisation of only 325\,GHz can also be beneficial when other channels are absent.
-It's possible that the ICI sub-mm channels could also be used to cloud correct MicroWave Imager (MWI) humidity radiances.
+It's possible that the ICI sub-mm channels could also be used to cloud correct humidity radiances from MicroWave Imager (MWI)---another conically scanning radiometer onboard Metop-SG.
+MWI will measure frequencies from 18\,GHz to 183\,GHz.
+Both MWI and ICI have the same requirements for incidence angle and fore-view observations, but different footprints.
 Although re-mapping to a common footprint  would slightly compromise the data quality, the high accuracy achieved with ICI simulations suggests that the QRNN would work well even when actual measurements are available.
@@
 \codeavailability{QRNN is available as a part of the \textit{typhon: tools for atmospheric research},  https://doi.org/10.5281/zenodo.3626449.
-The source code for all the analysis presented in the article is available as git repository ( \todo{???} ) }
+The source code for all the analysis presented in the article is available as git repository (https://github.com/SEE-MOF/aws)}
 
@@
 arts-2.3.1.
-The absorption and hydrometeor properties are described below.
+All simulations are based on dBZ-based model system \citep{ekelund2020using}, i.e.
+CloudSat reflectivities are used as input and are converted to ice water path (IWP) fields using microphysical assumptions.
 For each atmospheric case, both ``all-sky'' and ``clear-sky'' calculations are performed.
@@
 The absorption model takes into account the effect from nitrogen
-\citep{pwr:93}, oxygen \citep{pwr:93} and water vapour  \citep{ellison2007permittivity}.
-Liquid water content (LWC) is taken from ERA-Interim  and is assumed to be totally absorbing.
+\citep{pwr:93}, oxygen \citep{pwr:93} and liquid water content (LWC, \citet{ellison2007permittivity}).
+LWC is taken from ERA-Interim  and is assumed to be totally absorbing.
 In the mapping of CloudSat reflectivities to RWC and IWC, a total separation between liquid and ice phase is assumed.
@@
 The output from ARTS is first two elements of the Stokes vector,  which are converted to brightness temperatures for H- and V-polarisation.
-For AWS, forward simulations are performed for 21 monochromatic frequencies, and later these frequencies were interpolated to a finer grid to get the AWS channel brightness temperatures.
-
-\subsection{QRNN network structure}
+
+\section{QRNN network structure}
 \label{appendix:hyperparamter}
@@
 The QRNN package is made available by SP.
-IK wrote the original draft, with help from PE, SP and DID.
+IK wrote the original draft, with contributions from PE, SP and DID.
 DID also provided the data for MWHS-2.
@@
 \begin{acknowledgements}
-TEXT
+The part associated with AWS was done with funding from EUMETSAT (contract  EUM/CO/20/4600002417/CJA), while remaining work was mainly funded by the Swedish National Space Agency (grants 166/18 and 154/19).
+David Duncan is supported by the EUMETSAT Fellowship Programme.
+This project would not had been possible without the contribution of all individuals behind the open source softwares used (ARTS, Python and PyTorch).
 \end{acknowledgements}

### 2020-11-20 Article/ici_submm_cloudcorr.tex
AMT format for figure names

@@
 
-\title{Estimation of cloud-corrected microwave humidity radiances with associated uncertainties}
-
-%\title{Cloud correction and uncertainty characterisation of operational microwave humidty channels}
+\title{Cloud correction of humidity radiances with case-specific uncertainty 
+	estimate}
 
@@
 	\centering
-	\includegraphics[height=45mm]{Figures/posterior_distribution_I1V.pdf} 
+	\includegraphics[height=45mm]{Figures/fig01.pdf} 
 	\caption{Examples showing the predicted quantiles of the conditional distribution of $\ynfcs$ }
@@
 	\centering
-	\includegraphics[width = 70mm]{Figures/QRNN_output_mwhs.pdf} 
+	\includegraphics[width = 70mm]{Figures/fig02.pdf} 
 	\caption{The distribution of point estimate obtained from QRNN-single 89+150\,GHz for MWHS-2 channel 14. The corresponding distributions for all-sky and clear-sky simulations are also shown.}
@@
 	\centering
-	\includegraphics[width = 70mm]{Figures/MWHS_error_dist_14.pdf} 
+	\includegraphics[width = 70mm]{Figures/fig03.pdf} 
 	\caption{The error distribution for deviations of point estimates to NFCS simulations.
@@
 	\centering
-	\includegraphics[height=45mm]{Figures/correlation.pdf} 
+	\includegraphics[height=45mm]{Figures/fig04.pdf} 
 	\caption{ The triangular error correlation matrix obtained from QRNN-single and QRNN-all for MWHS-2. The label ``Clear'' represents cases with cloud impact less than 2\,K.}
@@
 \begin{figure}[t]
-	\includegraphics[width = 70mm]{Figures/prediction_uncertainty_MWHS_14.pdf}	
+	\includegraphics[width = 70mm]{Figures/fig05.pdf}	
 	\caption{Examples of prediction uncertainties obtained from QRNN-single (89+150\,GHz) for MWHS-2 channel 14.
@@
 \begin{figure}[t]
-	\includegraphics[height = 70mm]{Figures/calibration_QRNN_MWHS_14.pdf}	
+	\includegraphics[height = 70mm]{Figures/fig06.pdf}	
 	\caption{Calibration of the prediction intervals derived from QRNN-single (89+150\,GHz) for MWHS-2 channel 14, and prediction intervals derived from Gaussian error model for ECMWF NWP system (SI).
@@
 \begin{figure}[t]
-	\includegraphics[width=70mm]{Figures/deviation_posterior_mwhs_samples_14.pdf}	
+	\includegraphics[width=70mm]{Figures/fig07.pdf}	
 	\caption{The distribution of predicted errors and observed errors  obtained from QRNN-single (89+150\,GHz) for MWHS-2 channel 14.
@@
 \begin{figure*}[t]
-	\includegraphics[width=\textwidth]{Figures/error_distribution_QRNN-single.pdf} 
+	\includegraphics[width=\textwidth]{Figures/fig08.pdf} 
 	\caption{Same as Fig.~\ref{fig:error_distribution_mwhs14}, but from QRNN-single experiment for ICI channels I1V, I2V and I3V. }
@@
 \begin{figure}[t]
-	\includegraphics[width = 70mm]{Figures/prediction_uncertainty_I2V.pdf}	
+	\includegraphics[width = 70mm]{Figures/fig09.pdf}	
 	\caption{Same as Fig.~\ref{fig:prediction_uncertainty_mwhs}, but from QRNN-single for ICI channel I2V. The blue line represents a Gaussian distribution with a standard deviation of $0.65$\,K.}
@@
 \begin{figure}[t]
-	\includegraphics[height = 70mm]{Figures/calibration_QRNN_I2V.pdf}	
+	\includegraphics[height = 70mm]{Figures/fig10.pdf}	
 	\caption{Same as Fig.~\ref{fig:calibration_mwhs}, but from QRNN-single for ICI channel I2V. }
@@
 \begin{figure}[t]
-	\includegraphics[width=70mm]{Figures/deviation_posterior_samples_I2V.pdf}	
+	\includegraphics[width=70mm]{Figures/fig11.pdf}	
 	\caption{Same as Fig.~\ref{fig:predicted_errors_mwhs}, but from QRNN-single for ICI channel I2V.}
@@
 \begin{figure}[t]
-	\includegraphics[width = 70mm]{Figures/cloud_impact_uncertainty_AWS.pdf}	
+	\includegraphics[width = 70mm]{Figures/fig12.pdf}	
 	\caption{The average confidence intervals ($\pm3\sigma$) plotted against the magnitude of cloud impact for all AWS channels.}
@@
 \begin{figure*}[t]
-	\includegraphics[width=\textwidth]{Figures/PDF_uncertainty_bins_QRNN-single.pdf}	
+	\includegraphics[width=\textwidth]{Figures/fig13.pdf}	
 	\caption{Distribution of errors binned according to their uncertainty. Results are from QRNN-single for channels I1V, I2V and I3V.}
@@
 	\centering
-	\includegraphics[height=60mm]{Figures/CRPS.pdf} 
+	\includegraphics[height=60mm]{Figures/figB1.pdf} 
 	\caption{CRPS(left) and mean quantile loss(right) averaged over all predicted quantiles for different combinations of layer width and hidden layers ($n_h$).
@@
 
+\begin{table*}[t]
+	\caption{ Same as Table~\ref{tab:error_statistics_mwhs_others}, but from QRNN-single for ICI channels I1V, I2V and I3V. The fraction of rejected cases is given in parentheses.}
+	\label{tab:error_statistics_ici}
+	%	\tabcolsep=0.11cm
+	\begin{tabular}{llrr|rr|rr}
+		\tophline
+		&&\multicolumn{2}{c|}{Simulations}& \multicolumn{2}{c|}{QRNN All sub-mm}&\multicolumn{2}{c}{QRNN only 325 GHz} \\
+		\cline{3-8}
+		%		\hline
+		&&Clear-sky &   All-sky &  \multicolumn{2}{c|}{Predicted}&  \multicolumn{2}{c}{Predicted}   \\
+		&&			   &			&	(All) & (5\,K) &	(All) & (5\,K)\\
+		\middlehline
+		%		\multicolumn{7}{c}{Channel - I1V}\\
+
+		I1V&  Bias      &  0.00 & -1.87 & -0.02 & -0.00(6.1\%) & -0.03 & -0.01(6.2\%) \\
+		&MAE       		&  0.64 &  2.32 &  0.70 &  0.60  &   0.73 &  0.61 \\
+		&STD       		&  0.80 &  8.84 &  1.06 &  0.79  &  1.14 &  0.81 \\
+		&Skewness 		& -0.01 & -8.10 & -1.51 & -0.64  & -1.26 & -0.70\\
+		\middlehline
+		I2V & Bias      & 0.00 &  -1.04 &  0.00 &  0.01(3.6\%) & -0.03 & -0.01(3.6\%)  \\
+		&MAE       		& 0.64 &   1.53 &  0.57 &  0.51 &  0.62 &  0.54\\
+		&STD       		& 0.80 &   5.95 &  0.86 &  0.65 &  0.99 &  0.70\\
+		&Skewness 		& 0.00 & -10.79 & -1.85 & -0.22 & -2.67 & -0.38 \\
+		\middlehline	
+		I3V & Bias      & 0.01 &  -0.63 &  0.02 &  0.02(2.2\%)&  0.02 &  0.03(2.2\%)  \\
+		&MAE       		& 0.64 &   1.15 &  0.54 &  0.50  &  0.60 &  0.55\\
+		&STD       		& 0.80 &   4.27 &  0.80 &  0.63  &  0.94 &  0.70\\
+		&Skewness 		& 0.01 & -13.37 & -1.51 & -0.13  & -3.28 & -0.22\\
+		\bottomhline
+	\end{tabular}
+	\belowtable{} % Table Footnotes
+\end{table*}
+
      %% Appendix A1, A2, etc.
@@
 \authorcontribution{The study was conceptualised and supervised by PE.
-The analysis, validation and visualisation of results was done IK.
+The analysis, validation and visualisation of results was done by IK.
 The QRNN package is made available by SP.
+ARTS bulk simulations were set up by SP, and MWHS-2 data was provided by DID.
 IK wrote the original draft, with contributions from PE, SP and DID.
-DID also provided the data for MWHS-2.
 All authors contributed to the study with discussions and feedback.}
@@
 David Duncan is supported by the EUMETSAT Fellowship Programme.
-This project would not had been possible without the contribution of all individuals behind the open source softwares used (ARTS, Python and PyTorch).
+This project would not had been possible without the contribution of all individuals behind the open source softwares used (ARTS, Python, PyTorch, Numpy and Matplotlib).
 \end{acknowledgements}

### 2020-11-23 Article/ici_submm_cloudcorr.tex
fixed type-setting errors, suggestions from Vasilis

@@
 \newcommand{\ynfcs}{y_\text{NFCS}}
-\newcommand{\yonfcs}{y^{o}_\text{NFCS}}
+\newcommand{\yonfcs}{y^{\circ}_\text{NFCS}}
 \newcommand{\ynfcsi}{y_\text{NFCS, i}}
-\newcommand{\yonfcsi}{y^{o}_\text{NFCS, i}}
+\newcommand{\yonfcsi}{y^{\circ}_\text{NFCS, i}}
 \newcommand{\y}{\vec{y}}
@@
   Technology, Gothenburg, Sweden} 
-\affil[2]{European Centre for Medium Range Weather Forecasts, Reading, UK}
+\affil[2]{European Centre for Medium Range Weather Forecasts, Reading, United Kingdom}
 
@@
 The QRNN results improve upon what operational cloud filtering techniques like a scattering index can achieve, but are ultimately imperfect due to limited information content on cirrus impact from traditional microwave channels---the negative departures associated with high cloud impact are successfully corrected, but thin cirrus clouds cannot be fully corrected.
-In contrast, when sub-mm observations are used, QRNN successfully corrects most cases with cloud impact, with only 2-6\% of cases left partially corrected.
+In contrast, when sub-mm observations are used, QRNN successfully corrects most cases with cloud impact, with only 2--6\% of the cases left partially corrected.
 The methodology works well even if only one sub-mm channel (325\,GHz) is available.
@@
 transition at 22\,GHz, but it is relatively weak and only column values can be
-derived \citep[e.g.][]{schluessel1990atmospheric} for the observation geometry
+derived \citep[e.g.,][]{schluessel1990atmospheric} for the observation geometry
 of concern. The first transition in the microwave region that can be used to
-derive altitude information, i.e.\ can be used for ``sounding'', is the one at
-183.31\,GHz \citep{kakar1983retrieval,wang1983profiling}. On the other hand, at
+derive altitude information, i.e.\ ``sounding'', is the one at
+183\,GHz \citep{kakar1983retrieval,wang1983profiling}. On the other hand, at
 infrared wavelengths a high number of water vapour transitions are found,
@@
 channels around 183\,GHz. Today such channels are part of several sensors, such
-as ATMS (Advanced Technology Microwave Sounder, \citet{weng2012introduction}).
+as ATMS \citep[Advanced Technology Microwave Sounder,][]{weng2012introduction}.
 
@@
 comparing observations of different instruments to validate their calibration
-\citep{john2013assessment,moradi:retri:15,berg2016intercalibration}. A commonly
-used cloud filtering methods for these applications is the one of
-\citet{buehler:aclou:07}. This method is based on the 183\,GHz data alone,
-involving rules on the brightness temperatures differences between channels. An
-older version is \citet{burns1997effects}.
+\citep{john2013assessment,moradi:retri:15,berg2016intercalibration}. Commonly
+used cloud filtering methods for these applications are based on 183\,GHz data alone, involving rules on the brightness temperatures differences between channels \citep{burns1997effects, buehler:aclou:07}.
 
@@
 numerical weather prediction (NWP). Usage of passive microwave data by
-``all-sky'' assimilation in global NWP is growing \citep{geer2017growing},
+all-sky assimilation in global NWP is growing \citep{geer2017growing},
 but 183\,GHz data are still mainly used in a clear-sky fashion
 \citep{geer2018all}. The latter is particularly true in NWP of regional scope
-\citep{gustafsson2018survey}, with clear-sky assimilation of 183GHz radiances still commonplace.
+\citep{gustafsson2018survey}, with clear-sky assimilation of 183\,GHz radiances still commonplace.
 Regardless, both clear-sky and all-sky assimilation require identification of cloud affected observations, either to screen out these observations or to assign an appropriate observation error.
-``Scattering index'' \citep{geer2015scatteringindex} is one of the approaches used.
-It is based on brightness temperature differences between 89 and 150\,GHz.
-Another commonly used cloud filtering method is based on ``observation minus background'' (O-B), where the forecast model is used to obtain an estimate of the expected clear-sky value and the observation is rejected if the deviation exceeds some threshold \citep{English1999clouddetection}.
-
-%Despite their broad usage, these filtering methods aim at partial removal of cloud contamination originating from high ice clouds. The residual cloud impact can have some drawbacks. 
-At 183\,GHz, the impact of hydrometeors typically causes a decrease in the observed radiance due to scattering from ice hydrometeors (e.g.\ \citet{barlakas:three:20}).
-This implies that if any cloud contamination is missed by the filtering, a negative bias in mean radiance will result compared to the true clear-sky mean, which may translate into a bias in humidity after the retrieval or assimilation.
+The most commonly used cloud filtering techniques are the ``Scattering index'' \citep{geer2015scatteringindex} and the ``observation minus background'' (O$-$B).
+The first one is based on brightness temperature differences between 89 and 150\,GHz.
+In the second one, the forecast model is used to obtain an estimate of the expected clear-sky value and the observation is rejected if the deviation exceeds some threshold \citep{English1999clouddetection}.
+
+At 183\,GHz, the impact of hydrometeors typically causes a decrease in the observed radiance due to scattering from ice hydrometeors \citep[e.g.,][]{barlakas:three:20}.
+This implies that if any cloud contamination is missed by the filtering, a negative bias in the mean radiance, compared to the true clear-sky mean, may translate into a bias in humidity after the retrieval or assimilation.
 For NWP systems assimilating clear-sky observations, the effect of undetected clouds may be overcome by inflating the observational errors and diminishing the impact of observations.
-Furthermore, the mathematical assumptions of data assimilation (DA) are predicated on Gaussian errors with no mean bias, and residual cloud impacts that cause a net bias are not easily handled by variational bias correction.
+Furthermore, the mathematical assumptions of data assimilation (DA) are predicated Gaussian errors with no mean bias, and residual cloud impacts that cause a net bias are not easily handled by variational bias correction.
 One solution is to apply a very strict filtering, but this increases the rejection of clear-sky values, i.e.\ an important loss of useful data.
-Another limitation of existing clearing approaches is their ``one for all'' approach, i.e.\ observations in all 183\,GHz channels are either kept or rejected.
+Another limitation of existing filtering approaches is their ``one for all'' approach, i.e.\ observations in all 183\,GHz channels are either kept or rejected.
 This often rejects more observations than needed, as the channels differ in their altitude coverage.
@@
 To allow a channel specific filtering, data likely need to be combined in a more complex manner than simple differences, but it is unclear what type of regression would be best as the ideal solution would be scene-dependent.
-This points towards applying machine learning, as used by e.g.\ \citet{favrichon2019detecting}.
+This points towards applying machine learning techniques \citep[e.g.,][]{favrichon2019detecting}.
 A maybe less obvious problem is the assignment of uncertainty to the filtered values.
@@
 method using sub-millimetre (sub-mm) observations, which will become available
-operationally with the launch of the Ice Cloud Imager (ICI,
-\citet{eriksson:towar:20}) on board the next generation of EUMETSAT Polar System - Second Generation (EPS-SG), but will likely also be included in
-several smaller missions (such as Artic Weather Satellite (AWS); presented
+operationally with the launch of the Ice Cloud Imager \citep[ICI,][]{eriksson:towar:20} on board the next generation of European Organisation for the Exploitation of Meteorological Satellites Polar System - Second Generation (EUMETSAT EPS-SG), but will likely also be included in
+several smaller missions (such as Arctic Weather Satellite (AWS); presented
 below). Additionally, we demonstrate the feasibility of the approach based on
-observations at 89 and 150\ GHz channels (following
-\citet{geer2015scatteringindex}), which are available on several sensors extant today. The focus
+89 and 150\ GHz channels \citep[following][]{geer2015scatteringindex}, which are available on several sensors extant today. The focus
 on sub-mm channels is motivated by several reasons. First, the higher
@@
 The MicroWave Humidity Sounder 2 (MWHS-2) is an instrument on two current satellites in the FengYun-3 series, FY-3C and FY-3D.
-MWHS-2 a cross track scanning microwave radiometer and measures 15 frequencies in the range 89-191\,GHz.
-89\,GHz and 150\,GHz are window channels, five humidity sounding channels are centered at 183.31\,GHz, and eight temperature sounding channels are centered on the 118.75\,GHz oxygen absorption line.
+MWHS-2 a cross track scanning microwave radiometer and measures 15 frequencies in the range 89--191\,GHz.
+89\,GHz and 150\,GHz are window channels, five humidity sounding channels are centered around 183\,GHz, and eight temperature sounding channels are centered on the 118.75\,GHz oxygen absorption line.
 The five humidity sounding channels are similar to ATMS.
@@
 
-The Ice Cloud Imager (ICI) is a new instrument on board EPS-SG satellite MetOp-SG (Meteorological Operational - Second Generation).
+The ICI is a new instrument on board EPS-SG satellite MetOp-SG (Meteorological Operational - Second Generation).
 MetOp-SG is scheduled for launch in 2024, and it will make ICI the first operational sensor observing Earth using sub-mm wavelengths.
 The main objective of ICI is to use high frequency channels for measuring ice cloud properties, and improve the representation of ice clouds in regional and global NWP models.
-ICI is a conically scanning radiometer that will measure 13 frequencies from 183\,GHz up to 664\, GHz.
-Among all available channels, 183.31\,GHz, 325.15\,GHz and 448.00\,GHz, will measure vertical polarization;  while other channels around frequencies 243.20\,GHz and 664.00\,GHz are ``window channels'' and will measure both vertical and horizontal polarization.
-The instrument will observe earth from a mean altitude of 832\,km with sensor viewing angle 44.767$^\unit{^{\degree}}$(measured from nadir).
+ICI is a conically scanning radiometer that will measure 13 frequencies from 183\,GHz up to 664\,GHz.
+Among all available channels, 183\,GHz, 325\,GHz and 448\,GHz, will measure vertical polarization;  while other channels around 243\,GHz and 664\,GHz are ``window channels'' and will measure both vertical and horizontal polarization.
+The instrument will observe Earth from a mean altitude of 832\,km with the sensor viewing angle 44.767$^\unit{^{\degree}}$(measured from nadir).
 For all the channels, the mean footprint size is about 15\,km, but the exact geo-location of samples differs.
@@
 
-For this study, we conducted the forward simulations of the channels around: 183.31\,GHz, 325.15\,GHz, 448.00\,GHz and 664.00\,GHz (Table~\ref{tab:ICI_MWI_channels}).
+For this study, we conducted the forward simulations of the channels around: 183\,GHz, 325\,GHz, 448\,GHz and 664\,GHz (Table~\ref{tab:ICI_MWI_channels}).
 For brevity, we assume that all simulations are mapped to a common footprint.
@@
 \end{table}
-The Arctic Weather Satellite (AWS) is a small satellite mission approved as European Space Agency (ESA)
-Earth Watch Programme Element.
+The AWS is a small satellite mission approved as European Space Agency (ESA) Earth Watch Programme Element.
 It is a small platform carrying a single across-track scanning microwave radiometer.
@@
 
-In this study, forward simulations of the channels around 183.31\,GHz and 325.15\,GHz were conducted.
+In this study, forward simulations of the channels around 183\,GHz and 325\,GHz were conducted.
 
@@
 %
-MWHS-2 simulated radiances during the period June-July 2020, are sourced from ECMWF.
+MWHS-2 simulated radiances during the period June--July 2020 are sourced from ECMWF.
 In the current version of the ECMWF Integrated Forecasting System (IFS), cycle 47R1 \citep{IFS47R1chap1}, clear-sky and all-sky radiative transfer are performed simultaneously for monitoring purposes, despite all humidity sounders being assimilated via all-sky exclusively.
-These side by side radiative transfer calculations on a large variety of model scenes from the IFS provides an ideal dataset for comparing radiances with and without cloud effects.
-Out of all the available observations during the period, we use data for latitudinal range $60^{\degree}$\,S to $60^{\degree}$\,N and satellite zenith angle less than $7.5^{\degree}$.
-With this filter we have approximately 290\,000 cases.
-
-ICI and AWS frequencies are simulated with Atmospheric Radiative Transfer Simulator (ARTS, \citet{buehler:artst:18}).
-CloudSat \citep{Stephens2002cloudsat} profiles during August 2015 are randomly selected for forward simulations.
+These side by side radiative transfer calculations on a large variety of model scenes provides an ideal dataset for comparing radiances with and without cloud effects.
+Out of all the available observations during the period, we use data for the latitudinal range: $60^{\degree}$\,S to $60^{\degree}$\,N and satellite zenith angle, less than $7.5^{\degree}$.
+With this filter, we have approximately 290\,000 cases.
+
+ICI and AWS frequencies are simulated with Atmospheric Radiative Transfer Simulator \citep[ARTS,][]{buehler:artst:18}.
+For the forward simulations, Cloud Satellite \citep[Cloudsat,][]{Stephens2002cloudsat} profiles during August 2015 are randomly selected.
 The input data are restricted between $60\unit{^{\degree}S}$ to $60\unit{^{\degree}N}$, and surface is below 500\,m.
@@
 All AWS sensor viewing angles (from $0^{\degree}$ to $45^{\degree}$) are simulated, but the results described in this study are based on nadir viewing angle.
-Simulations for all three sensors are noise free, so to incorporate the measurement uncertainties, whenever needed, gaussian noise is added to according to the channel NE$\Delta$T (Table~\ref{tab:specifications_MWHS2} - Table~\ref{tab:specifications_AWS}).
+Simulations for all three sensors are noise free, so to incorporate the measurement uncertainties, whenever needed, Gaussian noise is added according to the channel NE$\Delta$T (Table~\ref{tab:specifications_MWHS2} -- Table~\ref{tab:specifications_AWS}).
 
@@
 For this application, the predicted percentiles are chosen to be
-$0.2\%, 3\%, 16\%, 50\%, 85\%, 97\%$ and $99.8\%$. For a Gaussian
+$0.2\,\%, 3\,\%, 16\,\%, 50\,\%, 85\,\%, 97\,\%$ and $99.8\,\%$. For a Gaussian
 distribution with mean $\mu$ and standard deviation $\sigma$, these quantiles
@@
 , \mu, \mu + \sigma, \mu + 2\sigma, \mu + 3\sigma$ and thus allows
-estimation of the $\pm 1, \pm 2$ and $\pm 3\sigma$ confidence intervals.
-
-QRNN's are trained to minimize the mean of the sum of the quantile loss functions
+estimation of the $\pm\, 1, \pm\, 2$ and $\pm\, 3\sigma$ confidence intervals.
+
+QRNN's are trained to minimize the mean of the sum of the quantile loss functions,
 %
@@
 over different hyper-parameter configurations. The details are described in
-Appendix~\ref{appendix:hyperparamter}
+Appendix~\ref{appendix:hyperparamter}.
 
@@
 	\centering
-	\includegraphics[height=45mm]{Figures/fig01.pdf} 
+	\includegraphics[height=70mm]{Figures/fig01.pdf} 
 	\caption{Examples showing the predicted quantiles of the conditional distribution of $\ynfcs$ }
@@
 \begin{equation}
-g_1 = 	\frac{\sqrt{N(N-1)}}{N-2} \frac{\sum_{i = 1}^{N}(Y_i - \bar{Y})^3/N}{\sigma^3}
+g_1 = 	\frac{\sqrt{N(N-1)}}{N-2} \frac{\sum_{i = 1}^{N}(Y_i - \bar{Y})^3/N}{\sigma^3} \,,
 \end{equation}
@@
 To investigate the potential impact of these two window channels in QRNN based cloud correction, the configuration QRNN-single is applied.
-In this experiment, the training inputs include all-sky brightness temperatures from target 183\,GHz channel, 89\,GHz and 150\,GHz.
+The training inputs include all-sky brightness temperatures from target 183\,GHz channel, 89\,GHz and 150\,GHz.
 Both 89 and 150\,GHz are window channels so the land sea mask is also included as a training input.
@@
 
-	\item In the second experiment, we explore if few of low peaking channels of 118\,GHz could have any potential advantage in cloud correction.
+	\item In the second experiment, we explore if few of low peaking channels of 118\,GHz could have any potential in cloud correction.
 To explore their impact, QRNN-single is trained with data from target 183\,GHz, 89\,GHz, 150\,GHz, 118.75$\pm$1.1\,GHz (channel 6), 118.75$\pm$2.5\,GHz (channel 7) and land/sea mask.
-This combination is denoted as 89+150+118\,GHz
+This combination is denoted as 89+150+118\,GHz.
 
@@
 Land/sea mask is also included in the training.
-This combination is denoted as 89+150+183\,GHz
+This combination is denoted as 89+150+183\,GHz.
 \end{enumerate}
@@
 	\includegraphics[width = 70mm]{Figures/fig02.pdf} 
-	\caption{The distribution of point estimate obtained from QRNN-single 89+150\,GHz for MWHS-2 channel 14. The corresponding distributions for all-sky and clear-sky simulations are also shown.}
+	\caption{The distribution of point estimate (``Predicted'') obtained from QRNN-single 89+150\,GHz for MWHS-2 channel 14.
+The corresponding distributions for all-sky and clear-sky simulations are also shown.}
 	\label{fig:distribution_predicted_mwhs14}	
@@
 Noise is also plotted for reference.
-The label ``All-sky'' represents the all-sky simulations, ``Predicted(All)'' denotes the predicted point estimates.
-The error distribution achieved with scattering index (SI) filtering is also shown (Filtered(SI)).
+The label ``All-sky'' represents the all-sky simulations, ``Predicted (All)'' denotes the predicted point estimates.
+The error distribution achieved with scattering index (SI) filtering is also shown (Filtered (SI)).
 }
@@
 		\middlehline
-Bias     &  0.00 &  -0.84 & -0.10 & -0.09 & -0.05 & -0.04 & -0.11 & -0.10 & -0.10 & -0.09 & 0.24  & -0.52\\
+Bias     &  0.00 & $-$0.84 &$-$0.10 &$-$0.09 &$-$0.05 &$-$0.04 &$-$0.11 &$-$0.10 &$-$0.10 &$-$0.09 & 0.24  &$-$0.52\\
 MAE      &  0.80 &   1.45 &  0.89 &  0.87 &  0.90 &  0.88 &  0.90 &  0.88 &  0.62 &  0.60 & 0.92  & 1.15\\
 STD      &  1.00 &   3.73 &  1.20 &  1.16 &  1.21 &  1.16 &  1.22 &  1.18 &  0.91 &  0.85 & 1.26  & 1.86\\
-Skewness & -0.02 & -12.72 & -1.17 & -1.00 & -1.06 & -0.90 & -1.16 & -1.04 & -1.78 & -1.71 &-1.95  & -3.45\\
-Rejection&  -	 & - 	  & - 	  & 3.3\% & - 	  & 3.4\% & -     & 3.2\% & -     & 3.3\% & 28.8\%& 3.5\%\\
+Skewness &$-$0.02 &$-$12.72 &$-$1.17 &$-$1.00 &$-$1.06 &$-$0.90 &$-$1.16 &$-$1.04 &$-$1.78 &$-$1.71 &-1.95  &$-$3.45\\
+Rejection& -	 &- 	  &-	  & 3.3\,\% &- 	  & 3.4\,\% &-     & 3.2\,\% &-     & 3.3\,\% & 28.8\,\%& 3.5\,\%\\
 \bottomhline
@@
 The predicted values are able to correct most of the low brightness temperature cases, and overall a good match with the NFCS simulations is observed.
-However, QRNN is unable to predict the lowest clear-sky brightness temperatures, and cases with brightness temperatures around 260\,K occur too frequently.
+However, QRNN is unable to predict the lowest clear-sky brightness temperatures, and cases with brightness temperatures around 260\,K, occur too frequently.
 The deviations of point estimates to NFCS simulations are shown in Fig.~\ref{fig:error_distribution_mwhs14}.
@@
 The corresponding error statistics (see Sect.~\ref{sec:validation}) are provided in  Table~\ref{tab:error_statistics_mwhs_14}.
-In the uncorrected all-sky simulations, the negative departures due to cloud impact lead to a large negative skewness(-12.72) and high bias (-0.84\,K).
-QRNN trained with 89 and 150\,GHz successfully corrects a major portion of the cloud affected cases, and the bias is reduced to -0.10\,K.
+In the uncorrected all-sky simulations, the negative departures due to cloud impact lead to a large negative skewness ($-$12.72) and high bias ($-$0.84\,K).
+QRNN trained with 89 and 150\,GHz successfully corrects a major portion of the cloud affected cases, and the bias is reduced to $-$0.10\,K.
 However, negative skewness indicates presence of  uncorrected departures.
@@
 For filtering such cases, we assume that predictions with cloud correction greater than 5\,K are associated with large deviations.
-In all three experiments, removing the cases with correction greater than 5\,K removes around 3\% of the data, but only a marginal positive impact on the accuracy is observed.
+In all three experiments, removing the cases with correction greater than 5\,K removes around 3\,\% of the data, but only a marginal positive impact on the accuracy is observed.
 The persistent negative skewness, even after filtering, indicates presence of cases with residual cloud impact.
@@
 Since QRNN gives out NFCS values, choosing an unusually low correction threshold can also classify noisy clear-sky cases as cloudy.
-For example, for 89+150\,GHz, a threshold of 1.5\,K rejects almost 10\% of data, but the negative skewness is still not completely removed.
-
-In spite of the fact that QRNN only provides a partial cloud correction, the results for  MWHS-2 channel 14 are better than what we achieve with existing cloud filtering techniques like scattering index (SI) and the filtering scheme by \citet{buehler:aclou:07}.
-SI uses the differences of brightness temperatures between 89 and 150\,GHz to identify cloud affected data, whilst in the study by \citet{buehler:aclou:07}, they use brightness temperature based threshold to filter out cloudy cases.
-They recommend a viewing angle dependent brightness temperature threshold at $183.31\pm1.00$ \,GHz and brightness temperature difference between $183.31\pm3.00$ \,GHz and $183.31\pm 1.00$ \,GHz as a measure of cloud impact.
-Further in the text we refer this filter as ``B183''.
+For example, for 89+150\,GHz, a threshold of 1.5\,K rejects almost 10\,\% of data, but the negative skewness is still not completely removed.
+
+In spite the fact that QRNN only provides a partial cloud correction, the results for  MWHS-2 channel 14 are better than what we achieve with existing cloud filtering techniques like scattering index (SI) and the filtering scheme by \citet{buehler:aclou:07}, hereafter B183.
+SI uses the differences of brightness temperatures between 89 and 150\,GHz to identify cloud affected data, whilst in B183, they use brightness temperature based threshold to filter out cloudy cases.
+They recommend a viewing angle dependent brightness temperature threshold at $183.31\pm1.00$\,GHz and brightness temperature difference between $183.31\pm3.00$\,GHz and $183.31\pm 1.00$\,GHz as a measure of cloud impact.
 The results obtained with SI and B183 are displayed in last two columns of Table~\ref{tab:error_statistics_mwhs_14}.
-With SI threshold = 5\,K, almost 28\% of the data is rejected, yet the resulting error distributions are poorer as compared to QRNN.
+With SI threshold 5\,K, almost 28\,\% of the data is rejected, yet the resulting error distributions are poorer as compared to QRNN.
 The low bias and skewness values indicate that most of the high negative departures are removed, but cases with low cloud impact pass the filter as clear.
 Similar is the case with B183.
-Here only 3\% of the data is filtered out but the overall statistics are worse than both QRNN and SI.
+Here only 3\,\% of the data is filtered out but the overall statistics are worse than both QRNN and SI.
 The results from the two filters are not surprising as both are partial filters and aim at removing only cases with high ice content.
@@
 The positive effect of 118\,GHz was slightly higher for MWHS-2 channel 15, but for others, no notable effect was observed.
-In view of negligible performance differences between the three experiments, we consider the combination 89+159\,GHz to be the optimal.
-The results for other channels with this experiment are provided in Sect.~\ref{sec:mwhs_others}
+In view of negligible performance differences between the three experiments, we consider the combination 89+150\,GHz to be the optimal.
+The results for other channels with this experiment are provided in Sect.~\ref{sec:mwhs_others}.
 
@@
 %f
-\begin{figure}[t]
+\begin{figure*}[t]
 	\centering
-	\includegraphics[height=45mm]{Figures/fig04.pdf} 
-	\caption{ The triangular error correlation matrix obtained from QRNN-single and QRNN-all for MWHS-2. The label ``Clear'' represents cases with cloud impact less than 2\,K.}
+	\includegraphics[height = 55mm]{Figures/fig04.pdf} 
+	\caption{ The triangular error correlation matrix obtained from (a) QRNN-single and (b) QRNN-all for MWHS-2. The label ``Clear'' represents cases with cloud impact less than 2\,K.}
 	\label{fig:correlations_mwhs}	
-\end{figure}
+\end{figure*}
 To assess the differences between the capabilities of QRNN-all against QRNN-single, we  compare the error statistics obtained for 89+150\,GHz and 89+150+183\,GHz for channel 14.
 Table~\ref{tab:error_statistics_mwhs_14} also shows the error statistics for the experiment QRNN-all.
-In comparison to QRNN-single, we obtain almost similar error bias with QRNN-all, but the MAE and standard deviation reduce by almost 30\% and 24\% respectively.
+In comparison to QRNN-single, we obtain almost similar error bias with QRNN-all, but the MAE and standard deviation reduce by almost 30\,\% and 24\,\% respectively.
 However, the negative tail becomes more prominent.
@@
 For such cases,  QRNN-all has slightly better accuracy than QRNN-single.
-The bias in QRNN-all and standard deviation is -0.53\,K and 1.93\,K, respectively, in comparison to -0.61\,K and 2.04\,K as observed in QRNN-single.
+The bias in QRNN-all and standard deviation is $-$0.53\,K and 1.93\,K, respectively, in comparison to $-$0.61\,K and 2.04\,K as observed in QRNN-single.
 Thus, the concurrent use of all 183\,GHz channels can provide additional information on cloud structures to QRNN.
@@
 		\middlehline
-		Channel 11  & Bias     & -0.00 &  -0.15 & -0.12 & -0.12 & -0.04 & -0.05\\
+		Channel 11  & Bias     &$-$0.00 & $-$0.15 &$-$0.12 &$-$0.12 &$-$0.04 &$-$0.05\\
 					& MAE      &  0.80 &   0.88 &  0.80 &  0.80 &  0.81 & 0.81 \\
 					& STD      &  1.00 &   1.51 &  1.03 &  1.02 &  1.02 & 1.03 \\
-					& Skewness &  0.01 & -15.73 & -0.61 & -0.45 & -0.07 & -0.29\\
-					& Rejection   & -    & -      & -	  & 0.2\% & 28.8\% & 3.5\%  \\
-		\middlehline
-		Channel 12  &  Bias     & -0.01 &  -0.29 & -0.12 & -0.11  & -0.08 & -0.16\\
+					& Skewness &  0.01 &$-$15.73 &$-$0.61 &$-$0.45 &$-$0.07 &$-$0.29\\
+					& Rejection   & -    & -      & -	  & 0.2\,\% & 28.8\,\% & 3.5\,\%  \\
+		\middlehline
+		Channel 12  &  Bias     &$-$0.01 & $-$0.29 &$-$0.12 &$-$0.11  &$-$0.08 &$-$0.16\\
 					&  MAE      &  0.80 &   0.98 &  0.82 &  0.81  &  0.82 & 0.87\\
 					&  STD      &  1.00 &   2.02 &  1.08 &  1.06  &  1.04 & 1.15\\
-					&  Skewness & -0.01 & -17.27 & -0.96 & -0.79  &  -0.25 & -1.02 \\
-					& Rejection & -     & -      & -	 & 0.6\%  & 28.8\% & 3.5\%  \\
-		\middlehline
-		Channel 13  &Bias       & 0.00 &  -0.53 & -0.11 & -0.10 & -0.14 & -0.31\\
+					&  Skewness &$-$0.01 &$-$17.27 &$-$0.96 &$-$0.79  & $-$0.25 &$-$1.02 \\
+					& Rejection & -     & -      & -	 & 0.6\,\%  & 28.8\,\% & 3.5\,\%  \\
+		\middlehline
+		Channel 13  &Bias       & 0.00 & $-$0.53 &$-$0.11 &$-$0.10 &$-$0.14 &$-$0.31\\
 					&MAE        & 0.80 &   1.18 &  0.85 &  0.84 &  0.86 & 0.98\\
 					&STD        & 1.00 &   2.83 &  1.15 &  1.12 &  1.12 & 1.41 \\
-					&Skewness   & 0.01 & -15.24 & -1.22 & -1.08 & -1.03 & -2.30\\  	
-					& Rejection & -     & -      & -	 & 1.6\%& 28.8\% & 3.5\%  \\	
-		\middlehline
-		Channel 15  &  Bias     & 0.00 &  -1.28 & -0.09 & -0.07 & -0.33 & -0.83\\
+					&Skewness   & 0.01 &$-$15.24 &$-$1.22 &$-$1.08 &$-$1.03 &$-$2.30\\  	
+					& Rejection & -     & -      & -	 & 1.6\,\%& 28.8\,\% & 3.5\,\%  \\	
+		\middlehline
+		Channel 15  &  Bias     & 0.00 & $-$1.28 &$-$0.09 &$-$0.07 &$-$0.33 &$-$0.83\\
 					&  MAE      & 0.80 &   1.88 &  0.98 &  0.93 &  1.03 &  1.46\\
 					&  STD      & 1.00 &   4.97 &  1.36 &  1.27 &  1.52 &  2.69\\
-					&  Skewness & 0.00 & -10.11 & -0.69 & -0.82 & -2.87 &  -4.33 \\ 
-					& Rejection & -     & -      & -	 & 5.5\% & 28.8\%& 3.5\%  \\
+					&  Skewness & 0.00 &$-$10.11 &$-$0.69 &$-$0.82 &$-$2.87 & $-$4.33 \\ 
+					& Rejection & -     & -      & -	 & 5.5\,\% & 28.8\,\%& 3.5\,\%  \\
 		\bottomhline
@@
 
-For channel 11, the error bias after correction is  -0.12\,K in comparison to 0.15\,K before correction.
-The decrease in bias is not significantly high but the strong negative tail  diminishes after correction, indicating removal of cases with large deviations.
+For channel 11, the bias after correction is $-$0.12\,K in comparison to 0.15\,K in the all-sky simulations.
+The decrease in bias is not significantly high, but the strong negative tail  diminishes after correction, indicating removal of cases with large deviations.
 Nonetheless, the non-zero negative skewness also indicates presence of cases with residual cloud impact in the corrected dataset.
@@
 A similar performance is evident for channel 12.
-Correction reduces the bias to -0.12\,K from -0.29\,K and standard deviation to 1.08\,K from 2.02\.K.
-The MAE is approximately 16\% lower after correction, but still the negative skewness is not removed completely.
+Correction reduces the bias to $-$0.12\,K from $-$0.29\,K and standard deviation to 1.08\,K from 2.02\.K.
+The MAE is approximately 16\,\% lower after correction, but still the negative skewness is not removed completely.
 For channel 13 and 15 also, a similar performance is seen.
@@
 The major caveat is the rejection of clear cases.
-With comparable accuracy, the fraction of rejection in SI is more than 28\% in comparison to only 3\% in B183.
+With comparable accuracy, the fraction of rejection in SI is more than 28\,\% in comparison to only 3\,\% in B183.
 For channel, 15 the error statistics obtained with SI are slightly inferior in comparison to QRNN.
@@
 This is in agreement with the wider spread of uncertainties for cases with low accuracy (Fig.~\ref{fig:prediction_uncertainty_mwhs}).
-However such cases form less than 6\% of the dataset.
+However, such cases form less than 6\,\% of the dataset.
 On the other hand, the calibration of ECMWF error model is above the diagonal for predicted probabilities above 0.2.
@@
 
-Further, we analyse if the  predicted errors obtained from QRNN are representative of observed errors (Fig.~\ref{fig:predicted_errors_mwhs}).
+Further, we analyse, if the  predicted errors obtained from QRNN are representative of observed errors (Fig.~\ref{fig:predicted_errors_mwhs}).
 Both error distributions are asymmetric, and this is in fact covered by the percentile distribution  in Fig.~\ref{fig:prediction_uncertainty_mwhs}.
@@
 The high errors which we try to estimate are rare, and cannot be fully represented by QRNN.
-Note that since we do not derive any sample from outside $\pm3\sigma$, such cases could also belong to 0.003\% population not represented by the quantiles.
+Note that since we do not derive any sample from outside $\pm\,3\sigma$, such cases could also belong to 0.003\,\% population not represented by the quantiles.
 
@@
 	\includegraphics[width=\textwidth]{Figures/fig08.pdf} 
-	\caption{Same as Fig.~\ref{fig:error_distribution_mwhs14}, but from QRNN-single experiment for ICI channels I1V, I2V and I3V. }
+	\caption{Same as Fig.~\ref{fig:error_distribution_mwhs14}, but from QRNN-single experiment for ICI channels (a) I1V, (b) I2V and (c) I3V. }
 	\label{fig:error_distributions}	
@@
 		\middlehline
-		%		\multicolumn{7}{c}{Channel - I1V}\\
-
-		I1V&  Bias      &  0.00 & -1.87 & -0.02 & -0.00(6.1\%)  \\
+		%		\multicolumn{7}{c}{Channel$-$ I1V}\\
+
+		I1V&  Bias      &  0.00 &$-$1.87 &$-$0.02 &$-$0.00 (6.1\,\%)  \\
 		&MAE       		&  0.64 &  2.32 &  0.70 &  0.60   \\
 		&STD       		&  0.80 &  8.84 &  1.06 &  0.79   \\
-		&Skewness 		& -0.01 & -8.10 & -1.51 & -0.64  \\
-		\middlehline
-		I2V & Bias      & 0.00 &  -1.04 &  0.00 &  0.01(3.6\%)  \\
+		&Skewness 		&$-$0.01 &$-$8.10 &$-$1.51 &$-$0.64  \\
+		\middlehline
+		I2V & Bias      & 0.00 & $-$1.04 &  0.00 &  0.01 (3.6\,\%)  \\
 		&MAE       		& 0.64 &   1.53 &  0.57 &  0.51 \\
 		&STD       		& 0.80 &   5.95 &  0.86 &  0.65 \\
-		&Skewness 		& 0.00 & -10.79 & -1.85 & -0.22  \\
-		\middlehline	
-		I3V & Bias      & 0.01 &  -0.63 &  0.02 &  0.02(2.2\%)  \\
+		&Skewness 		& 0.00 &$-$10.79 &$-$1.85 &$-$0.22  \\
+		\middlehline	
+		I3V & Bias      & 0.01 & $-$0.63 &  0.02 &  0.02 (2.2\,\%)  \\
 		&MAE       		& 0.64 &   1.15 &  0.54 &  0.50  \\
 		&STD       		& 0.80 &   4.27 &  0.80 &  0.63  \\
-		&Skewness 		& 0.01 & -13.37 & -1.51 & -0.13  \\
+		&Skewness 		& 0.01 &$-$13.37 &$-$1.51 &$-$0.13  \\
 		\bottomhline
@@
 For a quantitative assessment of the errors, the results from various error metrics described in  Sect.~\ref{sec:validation} are displayed in Table~\ref{tab:error_statistics_ici}.
-The average bias in I1V measurements is -1.87\,K, which reduces to -0.02\,K after cloud correction.
+The average bias in I1V all-sky simulations is $-$1.87\,K, which reduces to $-$0.02\,K after cloud correction.
 The corresponding standard deviation is 1.06\,K in comparison to 8.84\,K in the all-sky simulations.
@@
 Similar results are seen for I2V, though a better performance is observed.
-In I2V, the measurement bias is -1.04\,K which reduces to zero after correction and the MAE improves by almost 60\%.
-Removing cases with correction greater than 5\,K from the predictions removes only 3.6\% of the data and reduces the absolute error further by 10\%.
+In I2V, the all-sky bias is $-$1.04\,K which reduces to zero after correction and the MAE improves by almost 60\,\%.
+Removing cases with correction greater than 5\,K from the predictions removes only 3.6\,\% of the data and reduces the absolute error further by 10\,\%.
 The standard deviation of the resulting dataset is only 0.65\,K as compared to 0.80\,K from noise.
 The reduction in the standard deviation is also evident in the Fig.~\ref{fig:error_distributions}, where the peak of distributions is sharper.
-In comparison to I1V and I2V, I3V has the lowest fraction of the measurements with significant cloud impact.
+In comparison to I1V and I2V, I3V has the lowest fraction of the cases with significant cloud impact.
 In the predicted dataset, the MAE is 0.54\,K  and standard deviation is 0.80\,K.
 Filtering the cases with large correction reduces the MAE to 0.50\,K and standard deviation to 0.63\,K.
-For all three channels, the correction threshold filter is successful in removing the cases with low accuracy.
+For all three channels, the correction threshold filter successfully removes the cases with low accuracy.
 This is in contrast with results obtained with MWHS-2, where negative bias due to low cloudy cases is persistent even after filtering.
@@
 		\middlehline
-		AWS-32  &Bias     & 0.00 & -1.32 & -0.04 & -0.02(4.71\%) \\
+		AWS-32  &Bias     & 0.00 &$-$1.32 &$-$0.04 &$-$0.02 (4.71\,\%) \\
 				&MAE      & 0.36 &  1.57 &  0.58 &  0.44 \\
 				&STD      & 0.46 &  6.42 &  1.15 &  0.64 \\
-				&Skewness & 0.01 & -8.43 & -1.09 & -2.29 \\
-		\middlehline
-		AWS-33	&Bias     &  0.00 & -1.00 & -0.04 & -0.02(3.75\%)  \\
+				&Skewness & 0.01 &$-$8.43 &$-$1.09 &$-$2.29 \\
+		\middlehline
+		AWS-33	&Bias     &  0.00 &$-$1.00 &$-$0.04 &$-$0.02 (3.75\,\%)  \\
 				&MAE      &  0.36 &  1.24 &  0.46 &  0.37  \\
 				&STD      &  0.45 &  5.17 &  0.87 &  0.52  \\
-				&Skewness & -0.01 & -9.59 & -3.25 & -1.26  \\
-
-		\middlehline
-		AWS-34	&Bias    &  0.00 &  -0.71 & -0.06 & -0.04(2.86\%)  \\
+				&Skewness &$-$0.01 &$-$9.59 &$-$3.25 &$-$1.26  \\
+
+		\middlehline
+		AWS-34	&Bias    &  0.00 & $-$0.71 &$-$0.06 &$-$0.04 (2.86\,\%)  \\
 				&MAE      &  0.50 &   1.10 &  0.47 &  0.41  \\
 				&STD      &  0.63 &   4.05 &  0.82 &  0.56  \\
-				&Skewness & -0.01 & -11.06 & -3.53 & -1.02  \\
-		\middlehline
-		AWS-35	&Bias    & -0.00 &  -0.45 & -0.03 & -0.03(1.92\%)  \\
+				&Skewness &$-$0.01 &$-$11.06 &$-$3.53 &$-$1.02  \\
+		\middlehline
+		AWS-35	&Bias    &$-$0.00 & $-$0.45 &$-$0.03 &$-$0.03 (1.92\%)  \\
 				&MAE      &  0.50 &   0.86 &  0.48 &  0.43  \\
 				&STD      &  0.63 &   2.90 &  0.77 &  0.57  \\
-				&Skewness &  0.00 & -13.43 & -2.46 & -0.62  \\
-		\middlehline
-		AWS-36  &Bias    & -0.01 &  -0.29 & -0.04 & -0.04(1.23\%)  \\
+				&Skewness &  0.00 &$-$13.43 &$-$2.46 &$-$0.62  \\
+		\middlehline
+		AWS-36  &Bias    &$-$0.01 & $-$0.29 &$-$0.04 &$-$0.04 (1.23\,\%)  \\
 				&MAE      &  0.71 &   0.90 &  0.63 &  0.60  \\
 				&STD      &  0.89 &   2.17 &  0.88 &  0.77  \\
-				&Skewness &  0.00 & -13.54 & -1.32 & -0.27  \\
+				&Skewness &  0.00 &$-$13.54 &$-$1.32 &$-$0.27  \\
 		\bottomhline				
@@
 In an analogy between the results from ICI channels, we perform a similar error distribution analysis  and the results are displayed in Table~\ref{tab:statistics_qrnn_aws}.
-For channel AWS-32, the average bias and standard deviation in the uncorrected dataset is -1.32\,K and 6.42\,K respectively.
-However, after correction, the bias and standard deviation reduce to -0.04\,K and 1.15\,K.
+For channel AWS-32, the average bias and standard deviation in the uncorrected dataset is $-$1.32\,K and 6.42\,K respectively.
+However, after correction, the bias and standard deviation reduce to $-$0.04\,K and 1.15\,K, respectively.
 A decrease in the skewness of error distributions is evident, but a relatively high value after correction indicates presence of cases with partially-corrected cloud impact.
@@
 For AWS-33, the predictions have slightly higher accuracy than AWS-32.
-The MAE in predictions is only 0.46\,K in comparison to 1.24\,K for the measurements.
+The MAE in predictions is only 0.46\,K in comparison to 1.24\,K for the all-sky simulations.
 High skewness despite low bias (0.04\,K) is most likely due to presence of isolated cases with large negative deviations.
@@
 \begin{figure}[t]
-	\includegraphics[height = 70mm]{Figures/fig10.pdf}	
+	\includegraphics[width = 70mm]{Figures/fig10.pdf}	
 	\caption{Same as Fig.~\ref{fig:calibration_mwhs}, but from QRNN-single for ICI channel I2V. }
@@
 On the other hand, when  the cases with cloud correction greater than 10\,K are considered, the calibration is only slightly worse.
-In spite of the fact that such cases are few (~2\%), the high calibration indicates that QRNN is also successful in predicting the uncertainties associated with rare cases.
+In spite of the fact that such cases are few (~2\,\%), the high calibration indicates that QRNN is also successful in predicting the uncertainties associated with rare cases.
 For other two channels also the predictions are well calibrated, except for cases with correction greater than 5\,K in channel I1V (not shown).
@@
 To conclude the results, we analyse if the uncertainty estimates given by QRNN are representative of prediction accuracy.
-Figure~\ref{fig:error_distribution_uncertainty_bins} shows the observed ICI errors binned by their corresponding uncertainty in $\pm2\sigma$  confidence interval.
-For all three channels, the spread of error distribution increases as the uncertainty about the accuracy of the trial increases.
-The cases with high certainty have a narrow and sharp distribution, and the errors are mostly less than $\pm$2.5\,K.
+Figure~\ref{fig:error_distribution_uncertainty_bins} shows the observed ICI errors binned by their corresponding uncertainty in $\pm\,2\sigma$  confidence interval.
+For all three channels, the spread of error distribution increases as the uncertainty about the accuracy of the prediction increases.
+The cases with high certainty have a narrow and sharp distribution, and the errors are mostly less than $\pm\,$2.5\,K.
 With increase in the uncertainty, frequency of cases with high accuracy decreases and the distributions spread out symmetrically to higher errors.
@@
 
-Even though the cloud correction is partial, the performance is comparable or better to existing cloud filtering techniques like SI and scheme by \cite{buehler:aclou:07}.
-Note that both these techniques are a one for all approach for each 183\,GHz channel; thus if one observation is classified as cloudy by the filter, it is removed in all humidity channels.
+Even though the cloud correction is partial, the performance is comparable or better to existing cloud filtering techniques like SI and B183.
+Note that both these techniques are a ``one for all'' approach for each 183\,GHz channel; thus if one observation is classified as cloudy by the filter, it is removed in all humidity channels.
 This increases the probability of erroneously removing clear observations.
-For high peaking channels of MWHS-2, both SI and QRNN give almost similar results, but with almost 28\% rejection rate in the former.
+For high peaking channels of MWHS-2, both SI and QRNN give almost similar results, but with almost 28\,\% rejection rate in the former.
 On the other hand, for low peaking channels, SI gives less accurate results than QRNN, as these channels have a stronger hydrometeor impact.
@@
 Among these four channels, 150\,GHz has the highest peaking function around 4\,km \citep{chen2020mwhs}.
-These channels can only provide coverage to the humidity channels in lower and mid troposphere; nonetheless, the 183\,GHz channels are sensitive to hydrometeor content up to 10\,km.
+These channels can only provide coverage to the humidity channels in, lower and mid troposphere; nonetheless, the 183\,GHz channels are sensitive to hydrometeor content up to 10\,km.
 Due to missing complementary information from other channels in the upper troposphere, QRNN fails at predicting these cases accurately.
@@
 Few cases with high cloud impact do affect the accuracy and introduce a small negative bias, but such cases are easily filtered out with a simple correction threshold filter.
-For example, it is shown that filtering out cases with correction greater than 5\,K, results in variabilities of the order of sensor noise with minimal reduction in data (2-6\%).
+For example, it is shown that filtering out cases with correction greater than 5\,K, results in variabilities of the order of sensor noise with minimal reduction in data (2--6\,\%).
 For channel I1V, a slightly lower accuracy is observed due to relatively higher number of cases with residual cloud impact.
@@
 Since such cases introduce a small negative bias and skewness, they are more appropriately related to low-cloud impact.
-Compared to other two higher peaking channels, I1V is more sensitive to the effect of hydrometeors  and contamination from surface effects (Fig.4 of \citet{eriksson:towar:20}).
+Compared to other two higher peaking channels, I1V is more sensitive to the effect of hydrometeors  and contamination from surface effects \citep[Fig.
+4 of][]{eriksson:towar:20}.
 The cases with surface contamination are also localized and seasonal.
@@
 
-A similar pattern of results is seen for when only one 325\,GHz channel is used to correct cloud impact in AWS.
+A similar pattern is seen when only one 325\,GHz channel is used to correct cloud impact in AWS.
 QRNN is successful in predicting NFCS values for all channels except for the lowest peaking channel AWS-32.
-For AWS-32, the resulting error distributions have significantly lower spread than the measurements, but are still negatively skewed.
+For AWS-32, the resulting error distributions have significantly lower spread than the all-sky simulations, but are still negatively skewed.
 In spite of the slightly inferior performance for AWS-32, the high accuracy for other channels indicates that a single sub-mm channel like 325\,GHz is also sufficient enough for cloud correction at 183\,GHz.
@@
 Predictions with high error originate from cases which occur infrequently or cases with no orthogonal information.
-Such cases have a significantly distinct a priori distribution as compared to clear cases, which dominate the training dataset and influence the a priori information.
+Such cases have a significantly distinct a priori distribution as compared to clear cases, which dominate the training dataset, and influence the a priori information.
 The distribution of rare cases can be improved by increasing the training dataset size, but lack of orthogonal information can only be balanced by including additional training inputs, e.g.
@@
 However, with the cloud correction methodology presented here, we can aim at resolving these limitations.
-This is especially true for clear-sky assimilation systems, which reject up to 80\% of the available observations due to cloud contamination.
+This is especially true for clear-sky assimilation systems, which reject up to 80\,\% of the available observations due to cloud contamination.
 In fact, one of reasons for the positive performance of all-sky assimilation systems is attributed to the larger number of assimilated observations in comparison to clear-sky observations.
@@
 \appendix
-\section{ARTS simulation setup}    %% Appendix A
+\section{ARTS setup}    %% Appendix A
 \label{appendix:ARTS_setup}
@@
 All radiative transfer forward simulations are made by the Atmospheric Radiative
-Transfer System (ARTS, \citet{eriksson:arts2:11,buehler:artst:18}), version
+Transfer System \citep[ARTS,][]{eriksson:arts2:11,buehler:artst:18}), version
 arts-2.3.1.
-All simulations are based on dBZ-based model system \citep{ekelund2020using}, i.e.
-CloudSat reflectivities are used as input and are converted to ice water path (IWP) fields using microphysical assumptions.
-For each atmospheric case, both ``all-sky'' and ``clear-sky'' calculations are performed.
+All simulations are based on dBZ-based model system \citep{ekelund2020using}, i.e., CloudSat reflectivities are used as input and are converted to ice water path (IWP) fields using microphysical assumptions.
+For each atmospheric case, both all-sky and clear-sky calculations are performed.
 In the former, all hydrometeors contents are set to zero, while in the latter, ice water content (IWC) and rain water content (RWC) derived from CloudSat reflectivities and liquid water content (LWC) from ERA-Interim \citep{dee2011erainterim} are included.
-In order to avoid a possible bias between clear-sky and all-sky calculations for insignificant hydrometeor contents, both calculations are made by ARTS's interface to the RT4 solver \citep{evans1995microwavec}.
+In order to avoid a possible bias between clear-sky and all-sky calculations for insignificant hydrometeor contents, both calculations are made by the RT4 solver \citep{evans1995microwavec}.
 
 The absorption model takes into account the effect from nitrogen
-\citep{pwr:93}, oxygen \citep{pwr:93} and liquid water content (LWC, \citet{ellison2007permittivity}).
+\citep{pwr:93}, oxygen \citep{pwr:93} and liquid water content \citep[LWC,][]{ellison2007permittivity}.
 LWC is taken from ERA-Interim  and is assumed to be totally absorbing.
 In the mapping of CloudSat reflectivities to RWC and IWC, a total separation between liquid and ice phase is assumed.
-All scattering hydrometeors at temperatures above 0$^{\degree}$C and below 0$^{\degree}$C are assumed to be rain and ice hydrometeors, respectively.
+All scattering hydrometeors at temperatures above 0$^{\degree}$C and below 0$^{\degree}$\,C are assumed to be rain and ice hydrometeors, respectively.
 For RWC the particle size
-distribution (PSD) of \citet{abel2012improved} is applied. The PSD of IWC follows the basic formulation applied in DARDAR (\url{
-http://www.icare.univ-lille1.fr/projects/dardar}, \citet{delanoe2008variational}), using latest parameter
-values (i.e.\ $\alpha$ and $\beta$) as given by \citet{cazenave2019evolution}.
+distribution (PSD) of \citet{abel2012improved} is applied. The PSD of IWC follows the basic formulation applied in the radio detection and ranging(radar)/light
+detection and ranging (lidar) \citep[DARDAR,][\url{
+	http://www.icare.univ-lille1.fr/projects/dardar}]{delanoe2008variational}, using latest parameter values (i.e.\ $\alpha$ and $\beta$) as given by \citet{cazenave2019evolution}.
 This PSD can be considered as a ``two moment'' scheme, but is here applied in
@@
 \citet{eriksson:agene:18}. For ice hydrometeors, three habits are applied:
-Perpendicular 3-bullet rosette, Large plate aggregate and Large column
+perpendicular 3-bullet rosette, large plate aggregate and large column
 aggregate. In the last two cases, the aggregates are complemented with single
@@
 much more computationally costly and could not be accommodated inside the
-study. The land emissivity was taken from TELSEM (Tool to Estimate Land‐Surface Emissivities at Microwave frequencies, \citet{aires2011tool}) and the
-Ocean/water from TESSEM (Tool to Estimate Sea‐Surface Emissivity from Microwaves to sub‐Millimeter waves , \citet{prigent2017sea}).
+study. The land emissivity was taken from Tool to Estimate Land‐Surface Emissivities at Microwave frequencies \citep[TELSEM,][]{aires2011tool} and the
+Ocean/water from Tool to Estimate Sea‐Surface Emissivity from Microwaves to sub‐Millimeter waves \citep[TESSEM,][]{prigent2017sea}.
 
@@
 	\centering
-	\includegraphics[height=60mm]{Figures/figB1.pdf} 
-	\caption{CRPS(left) and mean quantile loss(right) averaged over all predicted quantiles for different combinations of layer width and hidden layers ($n_h$).
+	\includegraphics[height = 65mm]{Figures/figB1.pdf} 
+	\caption{(a) CRPS  and (b) mean quantile loss averaged over all predicted quantiles for different combinations of layer width and hidden layers ($\mathrm{n_h}$).
 The results are from QRNN-single applied to I2V.}
@@
 Firstly, we performed a grid search to define the structure of the neural network.
-We evaluated the performance for three sizes of hidden layers($n_h$ = 2, 3, 4), and layer widths of sizes in the set [8, 16, 32, 64, 128, 256, 512].
+We evaluated the performance for three sizes of hidden layers ($\mathrm{n_h}$ = 2, 3, 4), and layer widths of sizes in the set [8, 16, 32, 64, 128, 256, 512].
 The mean quantile loss and CRPS over all predicted quantiles was computed for each configuration (Fig.~\ref{fig:grid_search}).
@@
 
-\begin{table*}[t]
-	\caption{ Same as Table~\ref{tab:error_statistics_mwhs_others}, but from QRNN-single for ICI channels I1V, I2V and I3V. The fraction of rejected cases is given in parentheses.}
-	\label{tab:error_statistics_ici}
-	%	\tabcolsep=0.11cm
-	\begin{tabular}{llrr|rr|rr}
-		\tophline
-		&&\multicolumn{2}{c|}{Simulations}& \multicolumn{2}{c|}{QRNN All sub-mm}&\multicolumn{2}{c}{QRNN only 325 GHz} \\
-		\cline{3-8}
-		%		\hline
-		&&Clear-sky &   All-sky &  \multicolumn{2}{c|}{Predicted}&  \multicolumn{2}{c}{Predicted}   \\
-		&&			   &			&	(All) & (5\,K) &	(All) & (5\,K)\\
-		\middlehline
-		%		\multicolumn{7}{c}{Channel - I1V}\\
-
-		I1V&  Bias      &  0.00 & -1.87 & -0.02 & -0.00(6.1\%) & -0.03 & -0.01(6.2\%) \\
-		&MAE       		&  0.64 &  2.32 &  0.70 &  0.60  &   0.73 &  0.61 \\
-		&STD       		&  0.80 &  8.84 &  1.06 &  0.79  &  1.14 &  0.81 \\
-		&Skewness 		& -0.01 & -8.10 & -1.51 & -0.64  & -1.26 & -0.70\\
-		\middlehline
-		I2V & Bias      & 0.00 &  -1.04 &  0.00 &  0.01(3.6\%) & -0.03 & -0.01(3.6\%)  \\
-		&MAE       		& 0.64 &   1.53 &  0.57 &  0.51 &  0.62 &  0.54\\
-		&STD       		& 0.80 &   5.95 &  0.86 &  0.65 &  0.99 &  0.70\\
-		&Skewness 		& 0.00 & -10.79 & -1.85 & -0.22 & -2.67 & -0.38 \\
-		\middlehline	
-		I3V & Bias      & 0.01 &  -0.63 &  0.02 &  0.02(2.2\%)&  0.02 &  0.03(2.2\%)  \\
-		&MAE       		& 0.64 &   1.15 &  0.54 &  0.50  &  0.60 &  0.55\\
-		&STD       		& 0.80 &   4.27 &  0.80 &  0.63  &  0.94 &  0.70\\
-		&Skewness 		& 0.01 & -13.37 & -1.51 & -0.13  & -3.28 & -0.22\\
-		\bottomhline
-	\end{tabular}
-	\belowtable{} % Table Footnotes
-\end{table*}
-
      %% Appendix A1, A2, etc.

### 2020-11-23 Article/ici_submm_cloudcorr_simon.tex
Added corrections.

--- 2020-11-08 Article/ici_submm_cloudcorr_simon.tex
@@
 \newcommand{\todo}[1]{{\color{red} #1}}
-\newcommand{\ynfcs}{\vec{y}_\text{NFCS}}
-\newcommand{\yonfcs}{\vec{y}^{o}_\text{NFCS}}
-\newcommand{\ynfcsi}{\vec{y}_\text{NFCS, i}}
-\newcommand{\yonfcsi}{\vec{y}^{o}_\text{NFCS, i}}
+\newcommand{\ynfcs}{y_\text{NFCS}}
+\newcommand{\yonfcs}{y^{o}_\text{NFCS}}
+\newcommand{\ynfcsi}{y_\text{NFCS, i}}
+\newcommand{\yonfcsi}{y^{o}_\text{NFCS, i}}
 \newcommand{\y}{\vec{y}}
@@
 
-Identification of cloud affected observations is indispensable for both clear-sky and all-sky numerical weather prediction (NWP) systems.
-In this study, we present a methodology to identify and correct the cloud impact in microwave humidity radiances.
-A channel specific quantile regression neural network (QRNN) based approach is formulated to estimate the posterior distributions of noise free clear sky (NFCS) radiances.
-The applicability of the approach is demonstrated by application to a present sensor: MWHS-2 (MicroWave humidity sounder 2).
-With the future outlook, the applicability to sub-millimeter (sub-mm) channels is also investigated.
-The results are compared against the NFCS simulations.
-With the present sensors, the approach is successful in correcting most of the cases with large negative departures, but a fraction cases end up with partial correction.
-In spite of the cases with residual cloud impact, the results from QRNN are better than what operational cloud filtering techniques like scattering index can achieve.
-On the other hand, when sub-mm observations from ICI are used to correct the cloud impact, QRNN can successfully correct most of the cases with cloud impact.
-Only 2-4\% of the cases are partially corrected and these can be easily removed by a simple filtering.
-The resulting error distributions are almost symmetric with very low spread.
-The methodology also works well when only one of the higher frequencies (325\,GHz) is available.
-Except for the lowest peaking channel, using sub-mm observations also results in error distributions with standard deviation less than the measurement noise.
-Another advantage of using QRNN is that predicted quantiles can be employed to quantify the case-specific uncertainty estimates.
-The results show that QRNN is successful in representing the uncertainty for each case individually.
-Despite individual variations for each channel, the predictions exhibit a higher uncertainty when cloudy cases lack orthogonal information from other channels.
-In comparison to deterministic correction/filtering approaches, the high quality corrected radiances with uncertainty estimates have great potential to be used efficiently in assimilation systems.
+A methodology based on quantile regression neural networks (QRNN) is presented that identifies and corrects the cloud impact on microwave humidity sounder radiances at 183\,GHz.
+This approach estimates the posterior distributions of noise free clear-sky (NFCS) radiances, providing nearly bias-free estimates of clear-sky radiances with a full posterior error distribution.
+It is first demonstrated by application to a present sensor, the MicroWave Humidity Sounder-2 (MWHS-2), then the applicability to sub-millimeter (sub-mm) sensors is also analysed.
+The QRNN results improve upon what operational cloud filtering techniques like a scattering index can achieve, but are ultimately imperfect due to limited information content on cirrus impact from traditional microwave channels---the negative departures associated with high cloud impact are successfully corrected, but thin cirrus clouds cannot be fully corrected.
+In contrast, when sub-mm observations are used, QRNN successfully corrects most cases with cloud impact, with only 2-6\% of cases left partially corrected.
+The methodology works well even if only one sub-mm channel (325\,GHz) is available.
+When using sub-mm observations, cloud correction usually results in error distributions with standard deviation less than typical channel noise values.
+Furthermore, QRNN outputs predicted quantiles for case-specific uncertainty estimates, successfully representing the uncertainty of cloud correction for each observation individually.
+In comparison to deterministic correction or filtering approaches, the corrected radiances and attendant uncertainty estimates have great potential to be used efficiently in assimilation systems due to being largely unbiased and adding little further uncertainty to the measurements.
 
@@
 \citet{buehler:aclou:07}. This method is based on the 183\,GHz data alone,
-involving rules on the brightness temperatures differences between channels. An
+involving rules on the brightness temperature differences between channels. An
 older version is \citet{burns1997effects}.
@@
 numerical weather prediction (NWP). Usage of passive microwave data by
-``all-sky'' assimilation in global NWP is growing in \citep{geer2017growing},
-but 183\,GHz data are still mainly used in a clear sky fashion
+``all-sky'' assimilation in global NWP is growing \citep{geer2017growing},
+but 183\,GHz data are still mainly used in a clear-sky fashion
 \citep{geer2018all}. The latter is particularly true in NWP of regional scope
-\citep{gustafsson2018survey}, all-sky assimilation of 183\,GHz at many national
-weather agencies will likely not be reached in many years.
-Anyhow, both clear-sky and all-sky assimilation require identification of cloud affected observations.
-``Scattering index'' \cite{geer2015scatteringindex} is one of the approaches used.
+\citep{gustafsson2018survey}, with clear-sky assimilation of 183\,GHz radiances still commonplace.
+Regardless, both clear-sky and all-sky assimilation require identification of cloud affected observations, either to screen out these observations or to assign an appropriate observation error.
+``Scattering index'' \citep{geer2015scatteringindex} is one of the approaches used.
 It is based on brightness temperature differences between 89 and 150\,GHz.
@@
 
-Despite their broad usage, these filtering methods aim at partial removal of cloud contamination originating from high ice clouds.
-The residual cloud impact can have some drawbacks.
-For 183\,GHz, the impact of hydrometeors systematically causes a decrease in the observed radiance (maybe with exceptions at extremely dry conditions), see
-e.g.\ \citet{barlakas:three:20} and below.
-This implies that if any cloud contamination is missed by the filtering this will cause a negative bias in mean radiance, compared to the true clear-sky mean.
-This bias will translate to a bias in humidity after the retrieval or assimilation.
-For NWP systems assimilating clear-sky observations, the effect of undetected clouds is overcome by inflating the observational errors.
-However this artificial suppression of observations diminishes the impact of observations.
-The alternative is to apply a very strict filtering, but this increases the rejection of clear-sky values, i.e.\ an important loss of useful data.
+%Despite their broad usage, these filtering methods aim at partial removal of cloud contamination originating from high ice clouds. The residual cloud impact can have some drawbacks. 
+At 183\,GHz, the impact of hydrometeors typically causes a decrease in the observed radiance due to scattering from ice hydrometeors (e.g.\ \citet{barlakas:three:20}).
+This implies that if any cloud contamination is missed by the filtering, a negative bias in mean radiance will result compared to the true clear-sky mean, which may translate into a bias in humidity after the retrieval or assimilation.
+For NWP systems assimilating clear-sky observations, the effect of undetected clouds may be overcome by inflating the observational errors and diminishing the impact of observations.
+Furthermore, the mathematical assumptions of data assimilation (DA) are predicated on Gaussian errors with no mean bias, and residual cloud impacts that cause a net bias are not easily handled by variational bias correction.
+One solution is to apply a very strict filtering, but this increases the rejection of clear-sky values, i.e.\ an important loss of useful data.
 Another limitation of existing clearing approaches is their ``one for all'' approach, i.e.\ observations in all 183\,GHz channels are either kept or rejected.
@@
 An observation could be cloudy in some channels and still the be clear-sky in others.
-To allow a channel specific filtering, data likely need to be combined in a more complex manner than simple differences, but it is unclear what type of regression that would be best.
+To allow a channel specific filtering, data likely need to be combined in a more complex manner than simple differences, but it is unclear what type of regression would be best as the ideal solution would be scene-dependent.
 This points towards applying machine learning, as used by e.g.\ \citet{favrichon2019detecting}.
 A maybe less obvious problem is the assignment of uncertainty to the filtered values.
-To our best knowledge, so far only estimates of mean and worst case errors have been provided.
-Some cases with relatively high cloud impact will likely be missed, while most cases are clear sky from start.
+To our best knowledge, so far only estimates of mean and worst case errors exist in the literature.
+Some cases with relatively high cloud impact will likely be missed, while most cases are clear-sky from the start.
 As the remaining cloudy cases can cause significant biases, the likely solution is to apply a quite conservative (high) error estimate.
-However, this will unnecessary downgrade the value of the truly clear sky cases and the observations are used in a non-optimal manner.
-
-We are here approaching cloud filtering task from a new angle. The basic idea
+However, this will unnecessarily downgrade the value of the truly clear-sky cases and the observations are used in a non-optimal manner.
+
+In this study, we approach the cloud filtering task from a new angle. The basic idea
 is to derive an estimate of the corresponding noise-free clear-sky (NFCS) value
@@
 measurements (no ``background'' data involved). Not only a best estimate is
-provided, but also a case specific uncertainty. This information can be used as a pure filter, by rejecting data where the correction exceeds some threshold value. This threshold value should be
-relatively low, to not introduce a bias in filtered dataset. However, even
+provided, but also a case-specific uncertainty. This information could be used as a pure filter, by rejecting data where the correction exceeds some threshold value. However, even
 better is to replace the original value with the predicted NFCS value when
@@
 is shown below that a basically bias free cloud correction can be obtained.
-This feature removes the need of threshold value, as long as the retrieval or
+This feature also removes the need for defining threshold values, as long as the retrieval or
 assimilation system can incorporate the uncertainty of the corrected value. As
-also will be shown, the uncertainty for originally clear sky data is determined
+also will be shown, the uncertainty for originally clear-sky data is determined
 by noise, but the uncertainty increases with magnitude of correction.
-Accordingly, the cloud correction approach allows that the full weight of
-clear-sky data can be preserved.
-
-The estimation of NFCS values makes use of a special type of machine learning,
-denoted as Quantile Regression Neural Network (QRNN,
-\citet{pfreundschuh:aneur:18}). Unlike standard usage of machine learning where
-only some kind of best estimate is provided, QRNN works in a Bayesian fashion
-and instead gives a description of the posterior uncertainty. More precisely,
-QRNN outputs an user specified set of quantiles that gives a discrete
-description posterior distribution, that can be processed to derive e.g.\ the
-expectation value.
+Accordingly, the cloud correction approach permits the full weight of
+clear-sky data to be preserved.
 
 The proposed cloud correction scheme makes use of a Quantile Regression Neural
-Network (QRNN) to obtain a probabilistic prediction of the NFCS value. Unlike
-traditional neural networks techniques, which typically only provide a point
+Network (QRNN, \citet{pfreundschuh:aneur:18}) to obtain a probabilistic prediction of the NFCS value. Unlike traditional neural networks techniques, which typically only provide a point
 estimate of the target variable, QRNNs are trained to predict an arbitrary set
@@
 
-The main focus of this study is the potential of proposed cloud-correction
-method using sub-millimetre observations, which will become available
+The main focus of this study is the potential of this cloud-correction
+method using sub-millimetre (sub-mm) observations, which will become available
 operationally with the launch of the Ice Cloud Imager (ICI,
-\citet{eriksson:towar:20}) on board the next generation of polar orbiting
-meteorological satellites (MetOP-SG), but will likely also be included in
+\citet{eriksson:towar:20}) on board the next generation of EUMETSAT Polar System - Second Generation (EPS-SG), but will likely also be included in
 several smaller missions (such as Artic Weather Satellite (AWS); presented
@@
 observations at 89 and 150\ GHz channels (following
-\citet{geer2015scatteringindex}), which are available already today. The focus
-on sub-mm channels is motivated by several reasons. Firstly, the higher
+\citet{geer2015scatteringindex}), which are available on several sensors extant today. The focus
+on sub-mm channels is motivated by several reasons. First, the higher
 frequencies are more sensitive to scattering effects from smaller
-hydrometeors. For high altitude cirrus clouds, these frequencies have a stronger
-signal than 183\,Ghz. In some cloudy situations it could be possible that the
-impact at 183 GHz is of the order of thermal noise and modelling uncertainties,
-while the impact at 325 GHz is significantly higher. Secondly, the proposed
-cloud correction methods allows integrating ICI sub-mm observations in
-clear-sky data assimilation schemes and thus provides a simple
+hydrometeors and are thus expected to provide greater sensitivity to high altitude cirrus clouds. For example, in some cloudy situations the
+cloud impact at 183\,GHz may be of the order of thermal noise and modelling uncertainties,
+while the impact at 325\,GHz is significant enough to provide sufficient signal to noise for identifying cloud. Second, the proposed
+cloud correction methods allow integration of ICI sub-mm observations in
+clear-sky DA schemes with no further modifications, thus providing a simple
 way to make use this novel data source as soon as it becomes available.
@@
 \end{table}
-MicroWave Humidity Sounder 2 (MWHS-2) is an instrument onboard FengYun-3C (FY-3C).
-MWHS-2 a cross track scanning microwave radiometer and measures 15 frequencies in the range 89-191\,GHz.
-89\,GHz and 150\,GHz are window channels, five humidity sounding channels are centered at 183.31\,GHz and eight temperature sounding channels are centered at 118.75\,GHz oxygen absorption line.
+The MicroWave Humidity Sounder 2 (MWHS-2) is an instrument on two current satellites in the FengYun-3 series, FY-3C and FY-3D.
+MWHS-2 is a cross track scanning microwave radiometer and measures 15 frequencies in the range 89-191\,GHz.
+89\,GHz and 150\,GHz are window channels, five humidity sounding channels are centered at 183.31\,GHz, and eight temperature sounding channels are centered on the 118.75\,GHz oxygen absorption line.
 The five humidity sounding channels are similar to ATMS.
-As of December 2019, observations from MWHS-2 are routinely assimilated at European Centre for Medium-Range Weather Forecasts (ECMWF, \citet{duncan2020MWHS}).
-The channels relevant to this study are described on Table~\ref{tab:specifications_MWHS2}.
-
-For this study, MWHS-2 simulations were sourced from ECMWF assimilation system. \todo{details?}
+Observations from MWHS-2 are routinely assimilated in all-sky conditions at the European Centre for Medium-Range Weather Forecasts (ECMWF) with demonstrable positive impact on forecast performance \citep{duncan2020MWHS}.
+The channels relevant to this study are described in Table~\ref{tab:specifications_MWHS2}.
+
+For this study, MWHS-2 simulations were sourced from the operational ECMWF assimilation system.
 
@@
 
-Ice Cloud Imager (ICI) is a new instrument on board EPS-SG(EUMETSAT Polar System - Second Generation) satellite Metop-SG.
-Metop-SG is scheduled for launch in 2023, and it will make ICI the first operational sensor observing Earth using sub-millimeter(sub-mm) wavelengths.
-The main objective of ICI is to use high frequency channels for measuring ice cloud properties and improve the representation of ice clouds in regional and global NWP models.
+The Ice Cloud Imager (ICI) is a new instrument on board EPS-SG satellite MetOp-SG (Meteorological Operational - Second Generation).
+MetOp-SG is scheduled for launch in 2024, and it will make ICI the first operational sensor observing Earth using sub-mm wavelengths.
+The main objective of ICI is to use high frequency channels for measuring ice cloud properties, and improve the representation of ice clouds in regional and global NWP models.
 ICI is a conically scanning radiometer that will measure 13 frequencies from 183\,GHz up to 664\, GHz.
 Among all available channels, 183.31\,GHz, 325.15\,GHz and 448.00\,GHz, will measure vertical polarization;  while other channels around frequencies 243.20\,GHz and 664.00\,GHz are ``window channels'' and will measure both vertical and horizontal polarization.
-The instrument will observe earth from a mean altitude of 832\,km with sensor viewing angle 44.767$^\circ$(measured from nadir).
+The instrument will observe earth from a mean altitude of 832\,km with sensor viewing angle 44.767$^\unit{^{\degree}}$(measured from nadir).
 For all the channels, the mean footprint size is about 15\,km, but the exact geo-location of samples differs.
-Therefore a simultaneous utilization of data from different channels shall require remapping to a common footprint \citep{eriksson:towar:20}.
-
-For this study, we conducted the forward simulations at frequencies: 183.31\,GHz, 325.15\,GHz, 448.00\,GHz and 664.00\,GHz(See Table~\ref{tab:ICI_MWI_channels}).
+Therefore, a simultaneous utilization of data from different channels shall require remapping to a common footprint \citep{eriksson:towar:20}.
+
+For this study, we conducted the forward simulations of the channels around: 183.31\,GHz, 325.15\,GHz, 448.00\,GHz and 664.00\,GHz (Table~\ref{tab:ICI_MWI_channels}).
 For brevity, we assume that all simulations are mapped to a common footprint.
@@
 %
-MWHS-2 simulated radiances are routinely calculated at ECMWF for their use in the ECMWF NWP system.
-RTTOV (Radiative Transfer for TOVS, \citet{saunders2018update} and RTTOV-SCATT \citep{bauer2006rttovscat} are used to calculate the radiances in clear-sky and all-sky conditions, respectively.
-For this study, MWHS-2 brightness temperatures for the period June-July 2020 are used.
-Out of all the available observations, we use data for latitudinal range $60^{\degree}$\,S to $60^{\degree}$\,N and satellite zenith angle less than $7.5^{\degree}$.
-With this filter we have 340\,000 cases.
-
-ICI and AWS frequencies are simulated with Atmospheric Radiative Transfer
-Simulator (ARTS, \citet{buehler:artst:18}). CloudSat
-\citep{Stephens2002cloudsat} profiles from August 2015 are randomly selected for
-forward simulations. The input data are restricted between $60\unit{^{\degree}}S$ to
-$60\unit{^{\degree}N}$, and surface is below 500\,m. Both clear-sky and all-sky
-scenarios are simulated. The complete simulation setup is described in Appendix
-\ref{appendix:ARTS_setup}. For ICI and AWS, 220\,000 and 140\,000 cases are
-simulated, respectively. All AWS sensor viewing angles (from $0^\circ$ to
-$45^\circ$) are simulated, but the results described in this study are based on
-nadir viewing angle. Simulations for all three sensors are noise free, so to
-incorporate the measurement uncertainties, whenever needed, gaussian noise is
-added to according to the channel NE$\Delta$T (see
-Table~\ref{tab:specifications_MWHS2} - Table~\ref{tab:specifications_AWS}).
+MWHS-2 simulated radiances during the period June-July 2020, are sourced from ECMWF.
+In the current version of the ECMWF Integrated Forecasting System (IFS), cycle 47R1 \citep{IFS47R1chap1}, clear-sky and all-sky radiative transfer are performed simultaneously for monitoring purposes, despite all humidity sounders being assimilated via all-sky exclusively.
+These side by side radiative transfer calculations on a large variety of model scenes from the IFS provides an ideal dataset for comparing radiances with and without cloud effects.
+Out of all the available observations during the period, we use data for latitudinal range $60^{\degree}$\,S to $60^{\degree}$\,N and satellite zenith angle less than $7.5^{\degree}$.
+With this filter we have approximately 290\,000 cases.
+
+ICI and AWS frequencies are simulated with Atmospheric Radiative Transfer Simulator (ARTS, \citet{buehler:artst:18}).
+CloudSat \citep{Stephens2002cloudsat} profiles during August 2015 are randomly selected for forward simulations.
+The input data are restricted between $60\unit{^{\degree}S}$ to $60\unit{^{\degree}N}$, and surface is below 500\,m.
+Both clear-sky and all-sky scenarios  are simulated.
+The complete simulation setup is described in Appendix \ref{appendix:ARTS_setup}.
+For ICI and AWS, 220\,000 and 143\,000 cases are simulated, respectively.
+All AWS sensor viewing angles (from $0^{\degree}$ to $45^{\degree}$) are simulated, but the results described in this study are based on nadir viewing angle.
+Simulations for all three sensors are noise free, so to incorporate the measurement uncertainties, whenever needed, gaussian noise is added to according to the channel NE$\Delta$T (Table~\ref{tab:specifications_MWHS2} - Table~\ref{tab:specifications_AWS}).
 
@@
 A smaller database is selected for AWS.
-120\,000 simulations are used for training and the rest are used for testing.
+120\,000 simulations are used for training and the remaining 23\,000 for testing.
 
@@
 The task that we aim to solve in this study is to predict the NFCS brightness
-temperature \todo{$\ynfcs$, define it} at a given $183\unit{GHz}$ channel from a vector of
+temperature $\ynfcs$ at a given 183\,GHz channel from a vector of
 all-sky observations $\y$. Since the information-content of the
@@
 for all selected quantile fractions $\tau$, where $y_\tau$ is the predicted
-quantile and $y$ the reference value from the training or test data . The
-quantile loss is used in this study as a performance criterion for the tuning of
-the hyper parameters of the QRNN (see Appendix~\ref{appendix:hyperparamter}). In
+quantile and $y$ the reference value from the training or test data. The
+quantile loss is also used in this study as a performance criterion for the tuning of
+the hyper-parameters of the QRNN (see Appendix~\ref{appendix:hyperparamter}). In
 addition to the quantile loss, also the Continuously Ranked Probability Score
@@
 basic construction of both is that a separate network is trained for each
-183\,GHz channel to correct. The input data is all-sky brightness temperatures
-from selected input channels and/or additional data like land/sea mask. The
-output in both configurations is the posterior distribution of NFCS values for
+183\,GHz channel to correct, using certain input data. The input data is all-sky brightness temperatures from selected input channels and/or additional data like land/sea mask. The
+output in both configurations is the posterior distribution of $\ynfcs$ for
 the target 183\,GHz channel. The two configurations differ only by the number of
@@
 \end{figure}
-QRNN predictions are posterior probability distribution of the NFCS values
-described over the chosen quantiles. In order to facilitate the interpretation
-of results, examples of QRNN outputs are shown in
-Fig.~\ref{fig:posterior_distribution_I1V}. This example illustrates the
-predicted quantiles for three different cases. This is in contrast with other
-conventional correction/filtering methods, which give out only point estimates.
-However, for most application only a single point estimate is required. In
-Bayesian analysis, usually the posterior mean or posterior median are selected
-as point estimates. In this study, we chose the posterior median as the point
-estimate for the predicted NFCS value ($\ynfcs$). To analyse the ability of QRNN
-in correctly predicting the point estimate, deviation of the median value from
-the corresponding true value ($\yonfcs$) is evaluated using common performance
-indicators like bias, mean absolute error (MAE) and standard deviation (STD).
-The asymmetry of error distributions around their mean is also calculated
-through the measure of skewness. For a univariate dataset of length $N$, the
-Fisher-Pearson coefficient of skewness is defined as:
+QRNN predictions are posterior probability distribution of $\ynfcs$ described over the chosen quantiles.
+In order to facilitate the interpretation of results, examples of QRNN outputs are shown in Fig.~\ref{fig:posterior_distribution_I1V}.
+These examples illustrate the predicted quantiles for three different cases.
+The quantiles provide a quantification of the prediction uncertainty through a probabilistic upper and lower bound for each case.
+This is in contrast with other conventional correction/filtering methods, which give out only point estimates.
+However, for most applications only a single point estimate is required.
+In Bayesian analysis, usually the posterior mean or posterior median are selected as point estimates.
+In this study, we chose the posterior median as the best estimate for $\ynfcs$.
+To analyse the ability of QRNN in correctly predicting the point estimate, deviation of the median value from the corresponding true value ($\yonfcs$) is evaluated using common performance indicators like bias, mean absolute error (MAE) and standard deviation (STD).
+The asymmetry of error distributions around their mean is also calculated through the measure of skewness.
+For a univariate dataset of length $N$, the Fisher-Pearson coefficient of skewness is defined as:
 \begin{equation}
@@
 
-All evaluation results described in the study have been made on the test dataset.
-\todo{Is this true for the hyper parameter tuning? Because if this is the
-  case, the evaluation should be redone on independent data.}
+All evaluation results except hyper-parameter tuning, described in the study, have been made on the test dataset.
+The hyper-parameter tuning is made on the validation dataset (see Appendix~\ref{appendix:hyperparamter}).
+The validation dataset is a separate part of the training dataset which is held back during the training.
 
@@
 We use MWHS-2 to demonstrate the results.
-The choice is motivated by the fact that MWHS-2 has five complementary 183\,GHz channels, along with additional 118\,GHz channel.
-In order to formulate and test the correction approach, multiple QRNN experiments are performed for MWHS-2 channel 14.
-Later the methodology is extended to other 183\,GHz channels.
+The choice is motivated by the fact that MWHS-2 has five complementary 183\,GHz channels, along with additional 118\,GHz channels.
+In order to formulate and test the correction approach, multiple QRNN experiments are performed for MWHS-2.
+However, for brevity we show the comparison of the comprehensive results only for channel 14.
+Later the optimal experiment is extended to other 183\,GHz channels.
 A brief comparison of the results is also made against existing cloud filtering methods.
@@
 	\centering
-	\includegraphics[width = 70mm]{Figures/QRNN_output_mwhs.pdf} 
-	\caption{Distribution of point estimate $\ynfcs$ obtained from QRNN-single 89+150\,GHz for MWHS-2 channel 14. The corresponding distributions for all-sky and clear-sky simulations are also shown.}
+	\includegraphics[width = 70mm]{Figures/fig02.pdf} 
+	\caption{The distribution of point estimates obtained from QRNN-single 89+150\,GHz for MWHS-2 channel 14. The corresponding distributions for all-sky and clear-sky simulations are also shown.}
 	\label{fig:distribution_predicted_mwhs14}	
@@
 	\centering
-	\includegraphics[width = 70mm]{Figures/MWHS_error_dist_14.pdf} 
-	\caption{Error distribution for deviations of point estimates to NFCS simulations.
+	\includegraphics[width = 70mm]{Figures/fig03.pdf} 
+	\caption{The error distribution for deviations of point estimates to NFCS simulations.
 The results are from QRNN-single experiment 89+150\,GHz and MWHS-2 channel 14.
 Noise is also plotted for reference.
-The label ``All-sky'' represents the all-sky simulations, ``Predicted(All)'' denotes the predicted point estimates, while ``Predicted(5\,K)'' refers to the predicted point estimates but where cases with cloud correction greater than 5\,K are excluded.}
+The label ``All-sky'' represents the all-sky simulations, ``Predicted (All)'' denotes the predicted point estimates.
+The error distribution achieved with scattering index (SI) filtering is also shown (Filtered (SI)).
+}
 	\label{fig:error_distribution_mwhs14}	
@@
 \begin{table*}[t]
-	\caption{Error statistics for deviations of point estimates to NFCS simulations.
+	\caption{The error statistics for deviations of point estimates to NFCS simulations.
 Results are for different QRNN experiments for MWHS-2 channel 14 (see Sect.~\ref{sec:QRNN_expt_MWHS}).
 The statistics for all-sky and clear-sky simulations are also provided.
-The label ``All'' denotes the entire dataset of predicted point estimates, while ``Pred.(5\,K)'' refers to the predicted point estimates but where cases with cloud correction greater than 5\,K are excluded.
-}
+The label ``All'' denotes the entire dataset of predicted point estimates, while ``Pred.
+(5\,K)'' refers to the predicted point estimates but where cases with cloud correction greater than 5\,K are excluded.
+The last two columns show the statistics obtained after filtering cloudy cases according to scattering index (SI) and scheme by \citet{buehler:aclou:07} (B183).
+Bias, MAE, STD are in K, skewness is dimensionless.}
 	\label{tab:error_statistics_mwhs_14}
-	\begin{tabular}{lrr|rr|rr|rr|rr}
+	\setlength{\tabcolsep}{4pt}
+	\begin{tabular}{lrr|rr|rr|rr|rr|rr}
 		\tophline
-		&\multicolumn{2}{c|}{Simulations}& \multicolumn{6}{c|}{QRNN-single} & \multicolumn{2}{c}{QRNN-all}\\
-		\cline{2-11}
+		&\multicolumn{2}{c|}{Simulations}& \multicolumn{6}{c|}{QRNN-single} & \multicolumn{2}{c|}{QRNN-all} & \multicolumn{2}{c}{Pure filtering}\\
+		\cline{2-13}
 		%		\hline
-		&   Clear-sky &   All-sky &  \multicolumn{2}{c|}{89+150\,GHz} & \multicolumn{2}{c|}{89+150+118\,GHz} & \multicolumn{2}{c|}{150\,GHz} & \multicolumn{2}{c}{89+150+183\,GHz}\\		
-		&			   &			& All & Pred.(5\,K) & All & Pred.(5\,K) & All & Pred.(5\,K)  & All & Pred.(5\,K)\\
-		\middlehline
-		Bias      &  0.00 &  -0.84 & -0.09 & -0.08(3.3\%) & -0.04 & -0.03(3.4\%) & -0.09 & -0.09(3.2\%) & -0.09(3.3\%) & -0.08(3.3\%)  \\
-		MAE       &  0.80 &   1.45 &  0.88 &  0.86 &  0.89 &  0.87 &  0.89 &  0.87 &  0.62 &  0.59\\
-		STD       &  1.00 &   3.90 &  1.19 &  1.14 &  1.19 &  1.15 &  1.21 &  1.16 &  0.90 &  0.83\\
-		skewness & -0.00 & -14.34 & -1.11 & -0.93 & -1.00 & -0.84 & -0.88 & -0.98 & -1.58 & -1.62\\
+		&   Clear-sky &   All-sky &  \multicolumn{2}{c|}{89+150\,GHz} & \multicolumn{2}{c|}{89+150+118\,GHz} & \multicolumn{2}{c|}{150\,GHz} & \multicolumn{2}{c|}{89+150+183\,GHz}& SI & B183\\		
+		&			   &			& All & Pred. (5\,K) & All & Pred. (5\,K) & All & Pred. (5\,K)  & All & Pred. (5\,K)&&\\
+		\middlehline
+Bias     &  0.00 &  -0.84 & -0.10 & -0.09 & -0.05 & -0.04 & -0.11 & -0.10 & -0.10 & -0.09 & 0.24  & -0.52\\
+MAE      &  0.80 &   1.45 &  0.89 &  0.87 &  0.90 &  0.88 &  0.90 &  0.88 &  0.62 &  0.60 & 0.92  & 1.15\\
+STD      &  1.00 &   3.73 &  1.20 &  1.16 &  1.21 &  1.16 &  1.22 &  1.18 &  0.91 &  0.85 & 1.26  & 1.86\\
+Skewness & -0.02 & -12.72 & -1.17 & -1.00 & -1.06 & -0.90 & -1.16 & -1.04 & -1.78 & -1.71 &-1.95  & -3.45\\
+Rejection&  -	 & - 	  & - 	  & 3.3\% & - 	  & 3.4\% & -     & 3.2\% & -     & 3.3\% & 28.8\%& 3.5\%\\
 \bottomhline
@@
 
-The posterior distribution of NFCS values obtained from experiment 89+150\,GHz
-is similar to the one shown in Fig.~\ref{fig:posterior_distribution_I1V}. The
-median value is chosen as the point estimate (see Sect.~\ref{sec:validation}).
-The distribution of point estimates is displayed in
-Fig.~\ref{fig:distribution_predicted_mwhs14}. The predicted values are able to
-correct most of the low brightness temperature cases, and overall a good match
-with the NFCS simulations is observed. However, QRNN is unable to predict the
-lowest clear-sky brightness temperatures, and cases with brightness temperatures
-around 260\,K occur frequently. The deviations of point estimates from NFCS
-simulations are shown in Fig.~\ref{fig:error_distribution_mwhs14}. The large
-negative deviations are corrected successfully with QRNN, but residual cloud
-impact is evident in the negative tail. Most of these residual cases have
-departures less than 10\,K. The corresponding error statistics(see
-Sect.~\ref{sec:validation}) are provided in
-Table~\ref{tab:error_statistics_mwhs_14}. In the uncorrected data, the negative
-departures due to cloud impact lead to a large negative skewness(-14.34) and
-high bias (-0.84\,K). Training QRNN with 89 and 150\,GHz successfully corrects a
-major portion of the cloud affected cases, and the bias is reduced to -0.09\,K.
-However, high skewness values indicate a negative tail or uncorrected
-departures. Including 118\,GHz in the training, gives comparable results as
-89+150\,GHz. With 118\,GHz, the error distributions have lower bias and are more
-symmetric, but the MAE and STD remain unaltered. This indicates that the
-information from 118\,GHz channels can be beneficial in predicting few cases
-correctly, but the overall consequence is not exceptionally different from
-89+150\,GHz. Similar is the case with using only 150\,GHz. In the latter,
-predictions have the most symmetric error distributions, but the highest spread.
-
-Further we investigated that if filtering the predictions with low accuracy could help in improving the error distributions.
-For filtering such cases, we assume that predictions with cloud correction greater than 5\,K are cases associated with large deviations.
+Posterior distributions of $\ynfcs$ obtained from experiment 89+150\,GHz are similar to the ones shown in Fig.~\ref{fig:posterior_distribution_I1V} and the distribution of point estimates is displayed in Fig.~\ref{fig:distribution_predicted_mwhs14}.
+The predicted values are able to correct most of the low brightness temperature cases, and overall a good match with the NFCS simulations is observed.
+However, QRNN is unable to predict the lowest clear-sky brightness temperatures, and cases with brightness temperatures around 260\,K occur too frequently.
+The deviations of point estimates from NFCS simulations are shown in Fig.~\ref{fig:error_distribution_mwhs14}.
+The large negative deviations are removed (blue curve), but residual cloud impact is evident in the negative tail.
+Most of these residual cases have departures less than 10\,K.
+The appearance of a small positive tail also indicates overestimation in few cases.
+The corresponding error statistics (see Sect.~\ref{sec:validation}) are provided in  Table~\ref{tab:error_statistics_mwhs_14}.
+In the uncorrected all-sky simulations, the negative departures due to cloud impact lead to a large negative skewness(-12.72) and high bias (-0.84\,K).
+QRNN trained with 89 and 150\,GHz successfully corrects a major portion of the cloud affected cases, and the bias is reduced to -0.10\,K.
+However, negative skewness indicates presence of  uncorrected departures.
+Including 118\,GHz in the training gives a small improvement compared to 89+150 GHz alone.
+The error distribution has lower bias and is more symmetric, but the MAE and standard deviation remain unaltered.
+This indicates that the information from 118\,GHz channels can be beneficial in predicting few cases correctly, but the overall performance is not exceptionally different from 89+150\,GHz.
+Similar is the case with using only 150\,GHz---the differences between the three experiments are negligible.
+
+Further, we investigate whether filtering the predictions with low accuracy could help in improving the error distributions.
+For filtering such cases, we assume that predictions with cloud correction greater than 5\,K are associated with large deviations.
 In all three experiments, removing the cases with correction greater than 5\,K removes around 3\% of the data, but only a marginal positive impact on the accuracy is observed.
-With 5\,K threshold though the cases with high errors are removed, the persistent negative skewness indicates presence of cases with residual cloud impact.
+The persistent negative skewness, even after filtering, indicates presence of cases with residual cloud impact.
+Such cases are most likely to be associated with low or medium cloud impact.
 Choosing a lower threshold can help in removing more partially corrected cases but at the cost of rejecting clear-sky cases.
@@
 
-In spite of the fact that QRNN only provides a partial cloud correction, the results for  MWHS-2 channel 14 are comparable to what we achieve with existing cloud filtering techniques like scattering index (SI) and the filtering scheme by \citet{buehler:aclou:07}.
+In spite of the fact that QRNN only provides a partial cloud correction, the results for  MWHS-2 channel 14 are better than what we achieve with existing cloud filtering techniques like scattering index (SI) and the filtering scheme by \citet{buehler:aclou:07}.
 SI uses the differences of brightness temperatures between 89 and 150\,GHz to identify cloud affected data, whilst in the study by \citet{buehler:aclou:07}, they use brightness temperature based threshold to filter out cloudy cases.
-They recommend a viewing angle dependent brightness temperature threshold at $183.31\pm1.00$ \,GHz and brightness temperature difference between $183.31\pm3.00$ and $183.31\pm 1.00$ as a measure of cloud impact.
+They recommend a viewing angle dependent brightness temperature threshold at $183.31\pm1.00$ \,GHz and brightness temperature difference between $183.31\pm3.00$ \,GHz and $183.31\pm 1.00$ \,GHz as a measure of cloud impact.
 Further in the text we refer this filter as ``B183''.
-The results obtained with SI and B183 are displayed in Table~\ref{tab:SI_statistics}.
-With SI threshold = 5\,K, almost 30\% of the data is rejected, yet the resulting error distributions are poorer as compared to QRNN.
+The results obtained with SI and B183 are displayed in last two columns of Table~\ref{tab:error_statistics_mwhs_14}.
+With SI threshold = 5\,K, almost 28\% of the data is rejected, yet the resulting error distributions are poorer as compared to QRNN.
 The low bias and skewness values indicate that most of the high negative departures are removed, but cases with low cloud impact pass the filter as clear.
@@
 Here only 3\% of the data is filtered out but the overall statistics are worse than both QRNN and SI.
-The results from the two filters are not surprising as both aim at removing only cases with high ice content.
-The thin cirrus clouds and other low hydrometeor impact cases remain unaltered.
-
-The three experiments were also performed for other four 183\,GHz channels, and a similar performance was obtained (Table not shown).
+The results from the two filters are not surprising as both are partial filters and aim at removing only cases with high ice content.
+The low hydrometeor impact cases remain unaltered.
+
+The three experiments were also performed for the other four 183\,GHz channels, and a similar performance was obtained (not shown).
 The positive effect of 118\,GHz was slightly higher for MWHS-2 channel 15, but for others, no notable effect was observed.
-The results from combination 89+150\,GHz for these channels are provided in Sect.~\ref{sec:mwhs_others}
+In view of negligible performance differences between the three experiments, we consider the combination 89+159\,GHz to be optimal.
+The results for other channels with this experiment are provided in Sect.~\ref{sec:mwhs_others}
 
@@
 To assess the differences between the capabilities of QRNN-all against QRNN-single, we  compare the error statistics obtained for 89+150\,GHz and 89+150+183\,GHz for channel 14.
-The last column of Table~\ref{tab:error_statistics_mwhs_14} displays the error statistics for the experiment QRNN-all.
-In comparison to QRNN-single, we obtain marginally lower error bias with QRNN-all, and the MAE and standard deviation reduce by almost 30\% and 25\% respectively.
+Table~\ref{tab:error_statistics_mwhs_14} also shows the error statistics for the experiment QRNN-all.
+In comparison to QRNN-single, we obtain almost similar error bias with QRNN-all, but the MAE and standard deviation reduce by almost 30\% and 24\% respectively.
 However, the negative tail becomes more prominent.
@@
 Since a majority of the cases are clear-sky, their impact dominates the whole statistics.
-In order to probe the positive effect of QRNN-all, we also estimated the errors for all cases with cloud correction greater than 5\,K.
-In comparison with QRNN-single, QRNN-all had slightly better accuracy.
-This suggests that concurrent use of all 183\,GHz channels can provide additional information on cloud structures to QRNN.
+In order to probe the positive effect of QRNN-all, we also estimate the errors for all cases with cloud correction greater than 5\,K (table not shown).
+For such cases,  QRNN-all has slightly better accuracy than QRNN-single.
+The bias in QRNN-all and standard deviation is -0.53\,K and 1.93\,K, respectively, in comparison to -0.61\,K and 2.04\,K as observed in QRNN-single.
+Thus, the concurrent use of all 183\,GHz channels can provide additional information on cloud structures to QRNN.
 
 Even though QRNN-all gives slightly better prediction accuracy, its inherent construction makes it crucial to examine the correlation between observed errors.
-Fig.~\ref{fig:correlations_mwhs} illustrates the correlation matrix for both QRNN-all and QRNN-single.
+Figure~\ref{fig:correlations_mwhs} illustrates the correlation matrix for both QRNN-all and QRNN-single.
 For clear cases, the observed errors (noise) in QRNN-single are uncorrelated between the five channels.
@@
 \begin{table*}[t]
-	\caption{ Error statisics for MWHS-2 channels 11, 12, 13 and 15 from QRNN-single experiment 89+150\,GHz.
-The labels ``All'' and ``Pred.(5\,K)' are same as described in Table~\ref{tab:error_statistics_mwhs_14}.}
+	\caption{ As Table~\ref{tab:error_statistics_mwhs_14}, but for MWHS-2 channels 11, 12, 13, 15, and experiment QRNN-single 89+150\,GHz.}
 	\label{tab:error_statistics_mwhs_others}
-	\begin{tabular}{lrrr|rr}
+	\begin{tabular}{lrrr|rr|rr}
 		\tophline
-		&&\multicolumn{2}{c|}{Simulations}& \multicolumn{2}{c}{QRNN-single} \\
-		\cline{2-6}
+		&&\multicolumn{2}{c|}{Simulations}& \multicolumn{2}{c|}{QRNN-single} & \multicolumn{2}{c}{Pure filtering} \\
+		\cline{2-8}
 		%		\hline
-		& &  Clear-sky &   All-sky &  \multicolumn{2}{c}{89+150\,GHz}  \\
-		&	&		   &			& All & Pred.(5K)\\
-		\middlehline
-		Channel 11  &   Bias      & 0.00 &  -0.16 & -0.03 & -0.03(0.2\%)  \\
-				    &	MAE       & 0.80 &   0.89 &  0.79 &  0.79  \\
-					&	STD       & 1.00 &   1.71 &  1.03 &  1.01  \\
-					&	skewness & 0.01 & -20.18 & -0.68 & -0.45  \\
-		\middlehline
-		Channel 12  & Bias      & -0.00 &  -0.28 & -0.05 & -0.05(0.6\%)  \\
-					& MAE       &  0.80 &   0.98 &  0.81 &  0.80  \\
-					& STD       &  1.00 &   2.26 &  1.07 &  1.05  \\
-					& skewness &  0.00 & -20.72 & -0.91 & -0.70  \\
-		\middlehline
-		Channel 13  & Bias      & -0.00 &  -0.52 & -0.08 & -0.07(1.6\%)  \\
-					& MAE       &  0.80 &   1.17 &  0.84 &  0.83  \\
-					& STD       &  1.00 &   3.04 &  1.13 &  1.10  \\
-					& skewness &  0.02 & -17.85 & -1.14 & -0.98 \\		
-		\middlehline
-		Channel 15  & Bias      & -0.00 &  -1.28 & -0.07 & -0.06(5.6\%)  \\
-					& MAE       &  0.80 &   1.87 &  0.97 &  0.92 \\
-					& STD       &  1.00 &   5.08 &  1.35 &  1.25 \\
-					& skewness & -0.00 & -11.15 & -0.60 & -0.83  \\ 
+		& &  Clear-sky &   All-sky &  \multicolumn{2}{c|}{89+150\,GHz}    & SI & B183  \\
+		&	&		   &			& All & Pred. (5\,K) &&\\
+		\middlehline
+		Channel 11  & Bias     & -0.00 &  -0.15 & -0.12 & -0.12 & -0.04 & -0.05\\
+					& MAE      &  0.80 &   0.88 &  0.80 &  0.80 &  0.81 & 0.81 \\
+					& STD      &  1.00 &   1.51 &  1.03 &  1.02 &  1.02 & 1.03 \\
+					& Skewness &  0.01 & -15.73 & -0.61 & -0.45 & -0.07 & -0.29\\
+					& Rejection   & -    & -      & -	  & 0.2\% & 28.8\% & 3.5\%  \\
+		\middlehline
+		Channel 12  &  Bias     & -0.01 &  -0.29 & -0.12 & -0.11  & -0.08 & -0.16\\
+					&  MAE      &  0.80 &   0.98 &  0.82 &  0.81  &  0.82 & 0.87\\
+					&  STD      &  1.00 &   2.02 &  1.08 &  1.06  &  1.04 & 1.15\\
+					&  Skewness & -0.01 & -17.27 & -0.96 & -0.79  &  -0.25 & -1.02 \\
+					& Rejection & -     & -      & -	 & 0.6\%  & 28.8\% & 3.5\%  \\
+		\middlehline
+		Channel 13  &Bias       & 0.00 &  -0.53 & -0.11 & -0.10 & -0.14 & -0.31\\
+					&MAE        & 0.80 &   1.18 &  0.85 &  0.84 &  0.86 & 0.98\\
+					&STD        & 1.00 &   2.83 &  1.15 &  1.12 &  1.12 & 1.41 \\
+					&Skewness   & 0.01 & -15.24 & -1.22 & -1.08 & -1.03 & -2.30\\  	
+					& Rejection & -     & -      & -	 & 1.6\%& 28.8\% & 3.5\%  \\	
+		\middlehline
+		Channel 15  &  Bias     & 0.00 &  -1.28 & -0.09 & -0.07 & -0.33 & -0.83\\
+					&  MAE      & 0.80 &   1.88 &  0.98 &  0.93 &  1.03 &  1.46\\
+					&  STD      & 1.00 &   4.97 &  1.36 &  1.27 &  1.52 &  2.69\\
+					&  Skewness & 0.00 & -10.11 & -0.69 & -0.82 & -2.87 &  -4.33 \\ 
+					& Rejection & -     & -      & -	 & 5.5\% & 28.8\%& 3.5\%  \\
 		\bottomhline
@@
 \end{table*}
-\begin{table*}[t]
-	\caption{Channel wise error statistics obtained after filtering MWHS-2 humidity observations  according to scattering index (SI) and filtering described by \citet{buehler:aclou:07}.
-The latter is denoted as  B183.
-}
-	\label{tab:SI_statistics}
-	\begin{tabular}{lrr|rr|rr|rr|rr}
-		\tophline
-		& \multicolumn{2}{c|}{Channel 11} & \multicolumn{2}{c|}{Channel 12} & \multicolumn{2}{c|}{Channel 13} & \multicolumn{2}{c|}{Channel 14} & \multicolumn{2}{c}{Channel 15}\\
-			& SI & B183 & SI & B183 & SI & B183 & SI & B183 & SI & B183\\
-			\cline{2-11}
-		Bias 	 &-0.04	& -0.05	& -0.07 &  -0.15 &  -0.14 & -0.29	&-0.23 &  -0.51 & -0.33 &  -0.81\\
-		MAE  	 & 0.81	&  0.81	&  0.82 &	0.86 &	 0.85 &  0.97   & 0.92 &   1.14 &  1.03 &	1.44\\
-		STD  	 &1.02	&  1.03	&  1.04 &	1.14 &	 1.1  &  1.39	& 1.26 &   1.83 &  1.53 &	2.64\\
-		Skewness &-0.12 & -0.24 & -0.38 & -0.86  &  -0.91 & -2.23   &-1.79 &  -3.45 & -2.85 &  -4.41\\
-		\bottomhline		
-	\end{tabular}
-\end{table*}
-
-In this section, we extend QRNN-single to predict NFCS values for MWHS-2 channels 11, 12, 13, and 15.
+
+In this section, we extend QRNN-single to predict $\ynfcs$ for MWHS-2 channels 11, 12, 13, and 15.
 The experiment QRNN-single with combination 89+150\,GHz is used and the results are displayed in Table~\ref{tab:error_statistics_mwhs_others}.
 
-For channel 11, the error bias after correction is only -0.03\,K in comparison to 0.16\,K before correction.
-The strong negative tail also diminishes after correction, but a non-zero negative skewness indicates presence of cases with residual cloud impact in the corrected dataset.
+For channel 11, the error bias after correction is  -0.12\,K in comparison to 0.15\,K before correction.
+The decrease in bias is not significantly high but the strong negative tail  diminishes after correction, indicating removal of cases with large deviations.
+Nonetheless, the non-zero negative skewness also indicates presence of cases with residual cloud impact in the corrected dataset.
 Filtering the cases with high cloud impact has only a marginal positive effect.
 A similar performance is evident for channel 12.
-Correction reduces the bias to -0.05\,K and standard deviation to 1.07\,K.
-The MAE is approximately 17\% lower after correction, but still the negative skewness is not removed completely.
+Correction reduces the bias to -0.12\,K from -0.29\,K and standard deviation to 1.08\,K from 2.02\.K.
+The MAE is approximately 16\% lower after correction, but still the negative skewness is not removed completely.
 For channel 13 and 15 also, a similar performance is seen.
-But in the latter, error distributions are most symmetric but with largest spread as compared to other four channels.
-
-A comparison with SI based filtering and B183 is displayed in  Table~\ref{tab:SI_statistics}.
+But in the latter, error distributions are more symmetric and have the largest spread as compared to other four channels.
+The effect of poor predictions is highest in channel 15 owing to its maximum sensitivity to hydrometeor impact.
+
+A comparison with SI based filtering and B183 is displayed in last columns of Table~\ref{tab:error_statistics_mwhs_others}.
 For channel 11 the performance of QRNN is comparable to both SI and B183.
-Similar is the case with channel 12, though the results from B183 are slightly poor.
-Both these channels are mostly transparent to hydrometeor impact, and the filtering schemes work well.
+Similar is the case with channel 12 and channel 13, though the results from B183 are slightly poorer.
+The higher peaking channels are mostly transparent to hydrometeor impact, and the filtering schemes work well.
 The major caveat is the rejection of clear cases.
-With comparable accuracy, the fraction of rejection in SI is approx.
-30\% in comparison to approx.
-3\% in B183.
-For channels 13 and 15 the error statistics obtained with SI are slightly inferior in comparison to QRNN.
+With comparable accuracy, the fraction of rejection in SI is more than 28\% in comparison to only 3\% in B183.
+For channel, 15 the error statistics obtained with SI are slightly inferior in comparison to QRNN.
 The results with B183 are even worse.
-For all channels, the two filters succeed in removing the high ice cloud cases, but for lower peaking channels, the high negative skewness values indicate presence of cases with low cloud impact.
+For all channels, the two filters succeed in removing the high ice cloud cases, but for lower peaking channels, the high negative skewness values indicate presence of cases with low cloud impact, which pass the filter as ``clear''.
 Clearly the ``one for all'' approach of both filters is not adequate to cater for channel specific hydrometeor impact.
@@
 The quantiles have been plotted at equidistant points.
-The red line represents a hypothetical Gaussian distribution of $270\pm1.0$\,K.}
+The blue line represents a Gaussian distribution with a standard deviation of $1.0$\,K.
+For each quantile, the sample variation is also shown as box plot.
+}
 	\label{fig:prediction_uncertainty_mwhs}	
@@
 \begin{figure}[t]
-	\includegraphics[height = 70mm]{Figures/calibration_QRNN_MWHS_14.pdf}	
-	\caption{Calibration of the prediction intervals obtained from QRNN-single (89+150\,GHz) for MWHS-2 channel 14.
-Plots for both the complete dataset and the subset with correction greater than 5\,K are shown.
+	\includegraphics[height = 70mm]{Figures/fig06.pdf}	
+	\caption{Calibration of the prediction intervals derived from QRNN-single (89+150\,GHz) for MWHS-2 channel 14, and prediction intervals derived from Gaussian error model for ECMWF NWP system (SI).
+For the former, the calibration for both the entire predicted dataset and the subset with correction greater than 5\,K are shown.
 }
@@
 \begin{figure}[t]
-	\includegraphics[width=70mm]{Figures/deviation_posterior_mwhs_samples_14.pdf}	
+	\includegraphics[width=70mm]{Figures/fig07.pdf}	
 	\caption{The distribution of predicted errors and observed errors  obtained from QRNN-single (89+150\,GHz) for MWHS-2 channel 14.
-The predicted errors are estimated as deviation of random samples from posteriori distribution to corresponding median values.}
+The predicted errors are estimated as deviation of random samples from a posteriori distribution to corresponding median values.}
 	\label{fig:predicted_errors_mwhs}	
@@
 
-The quantiles given out by QRNN can be used to construct the probability
-distribution of the predictions in contrast to other correction approaches which
-give out only point estimates. Examples of the uncertainties given out by QRNN
-is shown in Fig.~\ref{fig:prediction_uncertainty_mwhs}. The spread of error
-distribution is asymmetric. The predictions over quantiles $-3\sigma$,
-$-2\sigma$ and $-1\sigma$ are quite sharp and lie close to the median value. In
-contrast, the spread of predictions over quantiles $1\sigma$, $2\sigma$ and
-$3\sigma$ is wider. Also, cases with very high uncertainty occur infrequently.
-The calibration of the prediction intervals on the testing dataset is displayed
-in Fig.~\ref{fig:calibration_mwhs}. For the entire dataset, the predictions
-follow the y=x line, i.e. the predicted uncertainties are perfectly calibrated
-with errors observed on the test data. However for the cases with correction
-greater than 5\,K, the distribution is poorly calibrated for higher quantiles.
-The curve lies below the y=x line indicating that the prediction intervals are
-too narrow. This is in agreement with the wide spread of predictions over the
-higher quantiles (Fig.~\ref{fig:prediction_uncertainty_mwhs}). However such
-cases are few and filtering them results in well calibrated QRNN predictions.
-\todo{This cannot be true. Filtering them, i.e. looking only at values with
-  correction < 5k will give predictions with too wide uncertainties, so that the
-  calibration will be above the diagonal. I don't think this information is particularly
-useful, so I'd suggest removing it.}
-
-Further, we analyse if the  predicted errors obtained from QRNN are representative of observed errors.
-Fig.~\ref{fig:predicted_errors_mwhs} illustrates the predicted and observed errors for MWHS-2 channel 14.
+The quantiles given out by QRNN can be used to construct the probability distribution of the predictions in contrast to other correction approaches which give out only point estimates.
+Examples of the uncertainties given out by QRNN are shown in Fig.~\ref{fig:prediction_uncertainty_mwhs}.
+The spread of error distribution is asymmetric.
+The predictions over quantiles $-3\sigma$, $-2\sigma$ and $-1\sigma$ are quite sharp and lie close to the median value.
+In contrast, the spread of predictions over quantiles $1\sigma$, $2\sigma$ and $3\sigma$ is wider.
+The box plots indicate that cases with very high uncertainty occur infrequently.
+The highly uncertain predictions are mostly cloudy cases with low accuracy, but clear cases with high uncertainty could also be present.
+Also, all quantiles but  $3\sigma$, follow the Gaussian distribution.
+
+The calibration of the prediction intervals given out by QRNN is displayed in Fig.~\ref{fig:calibration_mwhs}.
+We also analyse the calibration of the observational error model used for MWHS-2 in ECMWF NWP system \citep{lawrence2018FY3C}.
+A gaussian error model is used to represent the distribution of the errors, and plotted under the label ``SI''.
+For the entire dataset, the predictions from QRNN follow the $y=x$ line, i.e.
+the predicted uncertainties are perfectly calibrated with the errors observed on the test data.
+However for the cases with correction greater than 5\,K, the distribution is poorly calibrated, and the curve lies below the $y =x$ line, indicating that the prediction intervals are too narrow.
+This is in agreement with the wider spread of uncertainties for cases with low accuracy (Fig.~\ref{fig:prediction_uncertainty_mwhs}).
+However such cases form less than 6\% of the dataset.
+On the other hand, the calibration of ECMWF error model is above the diagonal for predicted probabilities above 0.2.
+This suggests that the true probability is higher than what is predicted on these intervals.
+
+Further, we analyse if the  predicted errors obtained from QRNN are representative of observed errors (Fig.~\ref{fig:predicted_errors_mwhs}).
 Both error distributions are asymmetric, and this is in fact covered by the percentile distribution  in Fig.~\ref{fig:prediction_uncertainty_mwhs}.
@@
 The high errors which we try to estimate are rare, and cannot be fully represented by QRNN.
-
-For other humidity channels, the predicted uncertainties followed similar
-behaviour and are not shown.
+Note that since we do not derive any sample from outside $\pm3\sigma$, such cases could also belong to 0.003\% population not represented by the quantiles.
+
+For other humidity channels, the predicted uncertainties followed similar behaviour and are not shown.
 
@@
 	\item In the second experiment, we investigate the possibility of using only channels around 325\,GHz for cloud correction at 183\,GHz.
-This special case of utilising only 325\,GHz channel can be relevant for smaller satellite missions like AWS where higher sub-mm channels are not available.
+This special case of utilizing only 325\,GHz channels can be relevant for smaller satellite missions like AWS where higher sub-mm channels are not available.
 In this experiment, QRNN-single configuration is used and it is trained with all-sky simulations from all 325\,GHz frequencies from AWS and the target 183\,GHz channel.
-For example, for target AWS-32, the training inputs were AWS-32, AWS-41, AWS-42, AWS-43, AWS-44.
-QRNN was trained five times for each 183\,GHz channel as target.
-Note that for this experiment, AWS was chosen due to availability of four 325\,GHz channels and five 183\,GHz channels.
+For example, for the target AWS-32, the training inputs are AWS-32, AWS-41, AWS-42, AWS-43, AWS-44.
+QRNN is trained five times for each 183\,GHz channel as target.
+Note that for this experiment, AWS was chosen due to availability of extra 325\,GHz and 183\,GHz channels.
 \end{enumerate}
@@
 \begin{figure*}[t]
-	\includegraphics[width=\textwidth]{Figures/error_distribution_QRNN-single.pdf} 
-	\caption{Same as Fig.~\ref{fig:error_distribution_mwhs14}, but from QRNN-single experiment for ICI channels I1V, I2V and I3V.}
+	\includegraphics[width=\textwidth]{Figures/fig08.pdf} 
+	\caption{Same as Fig.~\ref{fig:error_distribution_mwhs14}, but from QRNN-single experiment for ICI channels I1V, I2V and I3V. }
 	\label{fig:error_distributions}	
@@
 		&STD       		&  0.80 &  8.84 &  1.06 &  0.79   \\
-		&skewness & -0.01 & -8.10 & -1.51 & -0.64  \\
+		&Skewness 		& -0.01 & -8.10 & -1.51 & -0.64  \\
 		\middlehline
@@
 		&STD       		& 0.80 &   5.95 &  0.86 &  0.65 \\
-		&skewness & 0.00 & -10.79 & -1.85 & -0.22  \\
+		&Skewness 		& 0.00 & -10.79 & -1.85 & -0.22  \\
 		\middlehline	
@@
 		&STD       		& 0.80 &   4.27 &  0.80 &  0.63  \\
-		&skewness & 0.01 & -13.37 & -1.51 & -0.13  \\
+		&Skewness 		& 0.01 & -13.37 & -1.51 & -0.13  \\
 		\bottomhline
@@
 For all three channels, quite similar behaviour is observed, though I1V has the most cases with residual cloud impact.
-If the predicted cases with correction more than 5\,K are rejected, the resulting error distributions fit the measurement noise, except for I1V, where cases with residual cloud impact introduces a negative bias.
+If the predicted cases with correction more than 5\,K are rejected, the resulting error distributions fit the measurement noise, except for I1V, where cases with residual cloud impact introduce a small negative bias.
 For a quantitative assessment of the errors, the results from various error metrics described in  Sect.~\ref{sec:validation} are displayed in Table~\ref{tab:error_statistics_ici}.
 The average bias in I1V measurements is -1.87\,K, which reduces to -0.02\,K after cloud correction.
-The corresponding standard deviation is 1.06\,K in comparison to 8.84\,K in the measurements.
-The prediction accuracy of QRNN is further higher when filtering is made on the predictions.
-In this case, the residual bias zero, and the standard deviation is 0.79\,K, which is in fact of the order of measurement noise (0.80\,K).
+The corresponding standard deviation is 1.06\,K in comparison to 8.84\,K in the all-sky simulations.
+The prediction accuracy of QRNN is further higher, when filtering is made on the predictions.
+In this case, the residual bias is zero, and the standard deviation is 0.79\,K, which is in fact of the order of measurement noise (0.80\,K).
 Similar results are seen for I2V, though a better performance is observed.
 In I2V, the measurement bias is -1.04\,K which reduces to zero after correction and the MAE improves by almost 60\%.
-Removing cases with correction greater than 5\,K from the predictions removes only 3.7\% of the data and reduces the absolute error further by 10\%.
+Removing cases with correction greater than 5\,K from the predictions removes only 3.6\% of the data and reduces the absolute error further by 10\%.
 The standard deviation of the resulting dataset is only 0.65\,K as compared to 0.80\,K from noise.
@@
 		\middlehline
-		AWS-32  &Bias      & 0.00 & -1.32 &  -0.03 & -0.02(4.77\%) \\
-				&MAE      & 0.36 &  1.57 &   0.54 &  0.43 \\
-				&STD      & 0.46 &  6.42 &   1.02 &  0.61 \\
-				&skewness & 0.01 & -8.43 &  -0.07 & -1.98 \\
-		\middlehline
-		AWS-33	&Bias      & -0.01 & -0.98 &  0.02 &  0.01(3.82\%) \\
-				&MAE      &  0.36 &  1.23 &  0.49 &  0.42 \\
-				&STD      &  0.45 &  4.70 &  0.76 &  0.56 \\
-				&skewness & -0.00 & -8.78 &  0.04 & -0.79 \\
-
-		\middlehline
-		AWS-34	&Bias      &  0.00 &  -0.68 &  0.02 &  0.01(2.89\%) \\
-				&MAE      &  0.51 &   1.07 &  0.51 &  0.46 \\
-				&STD      &  0.64 &   3.67 &  0.75 &  0.60 \\
-				&skewness & -0.00 & -10.32 & -0.55 & -0.59 \\
-		\middlehline
-		AWS-35	&Bias      &  0.00 &  -0.43 &  0.01 &  0.00(1.93\%) \\
-				&MAE      &  0.50 &   0.84 &  0.48 &  0.44 \\
-				&STD      &  0.63 &   2.65 &  0.71 &  0.57 \\
-				&skewness & -0.01 & -12.49 & -0.40 & -0.29 \\
-		\middlehline
-		AWS-36  &Bias      & 0.00 &  -0.28 &   0.03  &  0.03(1.27\%) \\
-				&MAE       & 0.70 &   0.90 &   0.63  &  0.60 \\
-				&STD      & 0.88 &   2.06 &   0.86  &  0.76 \\
-				&skewness & 0.01 & -11.80 &  -0.35  & -0.20 \\
+		AWS-32  &Bias     & 0.00 & -1.32 & -0.04 & -0.02(4.71\%) \\
+				&MAE      & 0.36 &  1.57 &  0.58 &  0.44 \\
+				&STD      & 0.46 &  6.42 &  1.15 &  0.64 \\
+				&Skewness & 0.01 & -8.43 & -1.09 & -2.29 \\
+		\middlehline
+		AWS-33	&Bias     &  0.00 & -1.00 & -0.04 & -0.02(3.75\%)  \\
+				&MAE      &  0.36 &  1.24 &  0.46 &  0.37  \\
+				&STD      &  0.45 &  5.17 &  0.87 &  0.52  \\
+				&Skewness & -0.01 & -9.59 & -3.25 & -1.26  \\
+
+		\middlehline
+		AWS-34	&Bias    &  0.00 &  -0.71 & -0.06 & -0.04(2.86\%)  \\
+				&MAE      &  0.50 &   1.10 &  0.47 &  0.41  \\
+				&STD      &  0.63 &   4.05 &  0.82 &  0.56  \\
+				&Skewness & -0.01 & -11.06 & -3.53 & -1.02  \\
+		\middlehline
+		AWS-35	&Bias    & -0.00 &  -0.45 & -0.03 & -0.03(1.92\%)  \\
+				&MAE      &  0.50 &   0.86 &  0.48 &  0.43  \\
+				&STD      &  0.63 &   2.90 &  0.77 &  0.57  \\
+				&Skewness &  0.00 & -13.43 & -2.46 & -0.62  \\
+		\middlehline
+		AWS-36  &Bias    & -0.01 &  -0.29 & -0.04 & -0.04(1.23\%)  \\
+				&MAE      &  0.71 &   0.90 &  0.63 &  0.60  \\
+				&STD      &  0.89 &   2.17 &  0.88 &  0.77  \\
+				&Skewness &  0.00 & -13.54 & -1.32 & -0.27  \\
 		\bottomhline				
@@
 \end{table*}
-In an analogy between the results from ICI channels, we perform a similar error distribution analysis  and the results are displayed in Table~\ref{tab:statistics_qrnn_aws}.
+In an analogy to the results from ICI channels, we perform a similar error distribution analysis  and the results are displayed in Table~\ref{tab:statistics_qrnn_aws}.
 For channel AWS-32, the average bias and standard deviation in the uncorrected dataset is -1.32\,K and 6.42\,K respectively.
-However, after correction, the bias and standard deviation reduce to -0.03\,K and 1.02\,K.
-A decrease in the skewness of error distributions is evident, but a relatively high values after prediction indicate presence of cases with partially-corrected cloud impact.
-Filtering out cases with high cloud impact improves the statistics overall except for skewness, which increases.
+However, after correction, the bias and standard deviation reduce to -0.04\,K and 1.15\,K.
+A decrease in the skewness of error distributions is evident, but a relatively high value after correction indicates presence of cases with partially-corrected cloud impact.
+Filtering out cases with 5\,K correction improves the statistics but introduces asymmetry in the error distribution.
+This is most likely due to rejection of cases affected by over-estimation.
 For AWS-33, the predictions have slightly higher accuracy than AWS-32.
-The MAE in predictions is only 0.49\,K in comparison to 1.23\,K for the measurements.
-Low skewness and bias values indicate that the error distribution is quite symmetric.
-Similar results are also seen for AWS-35 and AWS-36.
-For both channels, the error distributions are relatively more symmetric than the other channels.
-Also, it is worth to noting that when cases with 5\,K cloud correction are removed, the spread of prediction errors is narrower than noise.
+The MAE in predictions is only 0.46\,K in comparison to 1.24\,K for the measurements.
+High skewness despite low bias (0.04\,K) is most likely due to presence of isolated cases with large negative deviations.
+Nonetheless, filtering such cases makes the distribution more symmetric.
+For AWS-34 and AWS-35, again a similar behaviour is seen, though the distributions are more symmetric in the latter.
+For AWS-36, we obtain the most symmetric and narrow distributions after correction owing to the low sensitivity of AWS-36 to hydrometeor impact.
+Also, it is worth to noting that when cases with 5\,K cloud correction are removed, the spread of prediction errors is narrower than noise for AWS-34, AWS-35 and AWS-36.
 
@@
 \begin{figure}[t]
-	\includegraphics[width = 70mm]{Figures/prediction_uncertainty_I2V.pdf}	
-	\caption{Same as Fig.~\ref{fig:prediction_uncertainty_mwhs}, but from QRNN-single for ICI channel I2V.
-The red line represents a hypothetical Gaussian distribution of $270\pm0.60$\,K, which is of the order of standard deviation for I2V predictions (see Table~\ref{tab:error_statistics_ici}).}
+	\includegraphics[width = 70mm]{Figures/fig09.pdf}	
+	\caption{Same as Fig.~\ref{fig:prediction_uncertainty_mwhs}, but from QRNN-single for ICI channel I2V. The blue line represents a Gaussian distribution with a standard deviation of $0.65$\,K.}
 	\label{fig:prediction_uncertainty_I2V}	
@@
 \begin{figure}[t]
-	\includegraphics[width=70mm]{Figures/deviation_posterior_samples_I2V.pdf}	
+	\includegraphics[height = 70mm]{Figures/fig10.pdf}	
+	\caption{Same as Fig.~\ref{fig:calibration_mwhs}, but from QRNN-single for ICI channel I2V. }
+	\label{fig:calibration_I2V}	
+\end{figure}
+\begin{figure}[t]
+	\includegraphics[width=70mm]{Figures/fig11.pdf}	
 	\caption{Same as Fig.~\ref{fig:predicted_errors_mwhs}, but from QRNN-single for ICI channel I2V.}
@@
 \end{figure}
+
 \begin{figure}[t]
-	\includegraphics[height = 70mm]{Figures/calibration_QRNN_I2V.pdf}	
-	\caption{Same as Fig.~\ref{fig:calibration_mwhs}, but from QRNN-single for ICI channel I2V. }
-	\label{fig:calibration_I1V}	
-\end{figure}
-\begin{figure}[t]
-	\includegraphics[width = 70mm]{Figures/cloud_impact_uncertainty_AWS.pdf}	
-	\caption{The average confidence intervals (2$\sigma$) plotted against the magnitude of cloud impact for all AWS channels.}
+	\includegraphics[width = 70mm]{Figures/fig12.pdf}	
+	\caption{The average confidence intervals ($\pm3\sigma$) plotted against the magnitude of cloud impact for all AWS channels.}
 	\label{fig:uncertainty_cloud_impact}	
@@
 Among the cases associated with low uncertainty, the distribution is quite symmetric along the median value.
-These cases are concentrated along a narrow interval and lie close to the red line representing a Gaussian spread.
+These cases are concentrated along a narrow interval and lie close to the blue line representing a Gaussian spread.
 On the contrast, cases with high uncertainty are unequally spaced and have a larger spread over positive quantiles than negative quantiles.
-
-Fig.~\ref{fig:calibration_I1V} shows the calibration of the prediction intervals for I2V.
-The predictions for the complete test dataset are well calibrated and follow the y=x line.
-On the other hand, when only the cases with  cloud correction greater than 10\,K are considered, the predictions in all the intervals are poorly calibrated.
-In this case the calibration curve lies slightly below the y=x line for higher quantiles, indicating that the predicted intervals are too narrow, or the uncertainty is underestimated.
-
-Fig.~\ref{fig:predicted_errors} shows the comparison of observed errors (prediction accuracy) to predicted errors.
+The narrow box plots also indicate that the majority of the predictions are sharp.
+These are clear-cases which dominate the dataset, while cloudy cases have more spread out uncertainties.
+
+Figure~\ref{fig:calibration_I2V} shows the calibration of the prediction intervals for I2V.
+The predictions for the complete test dataset are well calibrated and follow the $y =x$ curve.
+Similar is the case, when cases with correction greater than 5\,K are considered.
+On the other hand, when  the cases with cloud correction greater than 10\,K are considered, the calibration is only slightly worse.
+In spite of the fact that such cases are few (~2\%), the high calibration indicates that QRNN is also successful in predicting the uncertainties associated with rare cases.
+For other two channels also the predictions are well calibrated, except for cases with correction greater than 5\,K in channel I1V (not shown).
+
+Figure~\ref{fig:predicted_errors} shows the comparison of observed errors to predicted errors.
 The predicted and observed errors mostly have a good agreement but the predicted errors are spread out more asymmetrically towards the negative departures.
@@
 This could also be a sampling issue, as the high errors we try to predict constitute a very small part of the complete dataset.
-Note that since we do not derive any sample from outside $\pm3\sigma$, such cases could also belong to 0.003\% population not represented by the quantiles.
 
 With AWS, the behaviour of predicted uncertainties is observed to be similar as for ICI (not shown).
-However, the relation between the mean uncertainty estimate and cloud impact is displayed in Fig.~\ref{fig:uncertainty_cloud_impact}.
+However, the relation between the mean uncertainty estimate ($\pm3\sigma$) and cloud impact is displayed in Fig.~\ref{fig:uncertainty_cloud_impact}.
 For all five channels, the predictions with small or relatively low cloud signal have a low uncertainty or in other words have high sharpness.
@@
 
-To conclude the results, we assessed if the uncertainty estimates given by QRNN are representative of prediction accuracy.
-Fig.~\ref{fig:error_distribution_uncertainty_bins} shows the errors of best estimate binned by their corresponding uncertainty in $\pm2\sigma$  confidence interval.
+To conclude the results, we analyse if the uncertainty estimates given by QRNN are representative of prediction accuracy.
+Figure~\ref{fig:error_distribution_uncertainty_bins} shows the observed ICI errors binned by their corresponding uncertainty in $\pm2\sigma$  confidence interval.
 For all three channels, the spread of error distribution increases as the uncertainty about the accuracy of the trial increases.
@@
 %
-The results from MWHS-2 show that QRNN based cloud correction is partially successful in correcting the cloud impact with existing sensors.
-The methodology can correctly address the large negative depatures owing to cloud impact, but few cloudy cases end up with inadequate correction.
+The results from MWHS-2 show that QRNN based cloud correction is partially successful in correcting the cloud impact with existing humidity sounding sensors.
+The methodology can correctly address the large negative departures owing to cloud impact, but few cloudy cases end up with inadequate correction.
 The resulting error distributions are not completely symmetric but have a low bias and spread.
 Among several input channel combinations described for QRNN-single, the performance of combination 89+150\,GHz is observed to be optimal.
-The positive performance with 150\,GHz is not unexpected, as 150\,GHz is highly sensitive to ice hydrometeors and cloud water; but using 89\,GHz along with 150\,GHz gives a slightly better performance.
-The channel 89\,GHz is affected by surface emissivity and is relatively less sensitive to cloud water content, however its sensitivity to warm clouds in the lower troposphere could be important.
+The positive performance with 150\,GHz is not unexpected, as 150\,GHz is sensitive to ice hydrometeors and cloud water; but using 89\,GHz along with 150\,GHz gives a slightly better performance.
+The channel 89\,GHz is more affected by surface emission and is less sensitive to cloud water content, however its sensitivity to warm clouds in the lower troposphere could be important.
 We also investigate the impact of two temperature sounding channels (MWHS-2 channel 6 and 7).
@@
 
-Even though the cloud correction is partial, the performance is comparable or better to existing cloud filtering techniques like SI and scheme by \cite{buehler:aclou:07}.
-Note that both these techniques are a one for all approach for each 183\,Ghz channel; thus if one observation is classified as cloudy by the filter, it is removed in all humidity channels.
+Even though the cloud correction is partial, the performance is comparable or better to existing cloud filtering techniques like SI and the scheme by \cite{buehler:aclou:07}.
+Note that both these techniques are a one for all approach for each 183\,GHz channel; thus if one observation is classified as cloudy by the filter, it is removed in all humidity channels.
 This increases the probability of erroneously removing clear observations.
-For high peaking channels of MWHS-2, both SI and QRNN give almost similar results, but with almost 30\% rejection rate.
+For high peaking channels of MWHS-2, both SI and QRNN give almost similar results, but with almost 28\% rejection rate in the former.
 On the other hand, for low peaking channels, SI gives less accurate results than QRNN, as these channels have a stronger hydrometeor impact.
@@
 Among these four channels, 150\,GHz has the highest peaking function around 4\,km \citep{chen2020mwhs}.
-These channels can only provide coverage to the humidity channels in lower and mid troposphere; nonetheless, the 183\,GHz channels are sensitive to hydrometeor content upto 2\,km.
+These channels can only provide coverage to the humidity channels in lower and mid troposphere; nonetheless, the 183\,GHz channels are sensitive to hydrometeor content up to 10\,km.
 Due to missing complementary information from other channels in the upper troposphere, QRNN fails at predicting these cases accurately.
 Such cases are mostly associated with thin cirrus clouds, which have very small influence at 89 and 150\,GHz.
-Without additional information from other channels we cannot expect QRNN train better.
+Without additional information from other channels we cannot expect QRNN to perform better.
 Among the other available channels, the overlapping weighting functions of 183\,GHz can provide auxiliary information to train QRNN.
@@
 Redundant patterns in machine learning models often have undesirable effect on the predictive performance.
-In our application, redundant information does not affect the prediction accuracy, but introduces highly correlated noise between channels.
-Correlated errors are also undesirable for DA systems, but in future if the operational centres progress with approaches dealing with correlated observation errors, concurrent use of 89, 150 and 183\,GHz channels would give the best cloud correction performance.
+In our application, redundant information does not affect the prediction accuracy, but introduces highly correlated observational errors between channels.
+Correlated errors are also undesirable for DA systems, but in future, if the operational centres progress with approaches dealing with correlated observation errors, for example as currently done for ATMS at ECMWF \citep{Weston2018eumATMS}, concurrent use of 89, 150 and 183\,GHz channels would give the best cloud correction performance.
 
@@
 In the ICI observations examined here, the results show that using sub-mm channels can successfully predict the NFCS values with very high accuracy for I2V, and I3V.
-The predicted values without any filter have an excellent match with the true values, and the departures are symmetrically distributed around zero mean.
+The predicted values have an excellent match with the true values, and the departures are symmetrically distributed around zero mean.
 Few cases with high cloud impact do affect the accuracy and introduce a small negative bias, but such cases are easily filtered out with a simple correction threshold filter.
-For example, it is shown that filtering out cases with correction greater than 5\,K, results in variabilities of the order of noise with minimal reduction in data (2-4\%).
+For example, it is shown that filtering out cases with correction greater than 5\,K, results in variabilities of the order of sensor noise with minimal reduction in data (2-6\%).
 For channel I1V, a slightly lower accuracy is observed due to relatively higher number of cases with residual cloud impact.
@@
 
-A similar pattern of results is seen for when only 325\,GHz channel is used to correct cloud impact in AWS.
+A similar pattern of results is seen for when only one 325\,GHz channel is used to correct cloud impact in AWS.
 QRNN is successful in predicting NFCS values for all channels except for the lowest peaking channel AWS-32.
 For AWS-32, the resulting error distributions have significantly lower spread than the measurements, but are still negatively skewed.
-In spite of the slightly inferior performance for AWS-32, the high accuracy for other channels indicates that a single sub-mm channel like 325\,GHz is also sufficient enough for cloud correction at 183\,GHz.
-This is an important result as smaller satellites are limited by their size to measure all sub-mm wavelengths.
+In spite of the slightly inferior performance for AWS-32, the high accuracy for other channels indicates that a single sub-mm channel like 325\,GHz is also sufficient for cloud correction at 183\,GHz.
+This is an important result as smaller satellites may be limited by their size to measure several sub-mm wavelengths.
 
@@
 QRNN predictions are weighted mean of measurements between channels.
-For clear-sky conditions, multiple observations of same scene from different channels can cancel out the noise.
-This effect is observed to be stronger in ICI than AWS, as the former has additional input channels giving same information.
-Note that with actual satellite measurements, the spread of error distributions smaller than noise could be difficult to achieve due to other underlying uncertainties not considered here.
-
-\subsection{Prediction uncertainty and implications for DA}
-
-Another advantage of QRNN is estimation of case-specific uncertainties.
-The predictions over chosen quantiles quantify the underlying uncertainty.
-The analysis of QRNN predicted errors and calibration plots show that QRNN is successful in providing well calibrated probabilistic predictions of the posterior distributions except for few cases associated with high error.
-The poorly calibrated predictions are a consequence of cases with different underlying a priori distribution.
-Predictions with high error originate from cases with high cloud impact or cloudy cases with no orthogonal information.
+In the absence of clouds, also the sub-mm channels provide humidity information that is incorporated in the 183 GHz NFCS estimate and some compensation of noise can be achieved.
+This effect is observed to be stronger in ICI than AWS, as the former has a higher number of channels giving redundant information.
+Note that with actual satellite measurements, the spread of error distributions smaller than sensor noise could be difficult to achieve due to other underlying uncertainties not considered here.
+
+\subsection{Prediction uncertainty and implications for data assimilation}
+
+Another advantage of QRNN is the estimation of case-specific uncertainties.
+That is, the predictions over chosen quantiles quantify the underlying uncertainty of the particular case, and not just represent some ensemble mean error.
+This has the consequence that a DA system can assign a proper weighting of each individual QRNN prediction.
+The analysis of QRNN predicted errors and calibration plots confirmed that QRNN is successful in providing
+well calibrated probabilistic predictions also in practice, except for few cases associated with high error.
+Poorly calibrated predictions are a consequence of cases with different underlying a priori distribution.
+Predictions with high error originate from cases which occur infrequently or cases with no orthogonal information.
 Such cases have a significantly distinct a priori distribution as compared to clear cases, which dominate the training dataset and influence the a priori information.
-Additional information in form of more observational data or additional training inputs is required to improve QRNN prediction accuracy for such cases.
-However the cases with low accuracy are associated with high uncertainty, and can be used with caution.
-\todo{I could not follow the last sentence.}
-
-The symmetric and low spread error distribution with uncertainty estimates is an important result from the DA perspective.
+The distribution of rare cases can be improved by increasing the training dataset size, but lack of orthogonal information can only be balanced by including additional training inputs, e.g.
+brightness temperatures for other channels.
+
+The symmetric and low spread error distribution with uncertainty estimates is also an important result from the DA perspective.
 Most of the existing cloud filtering schemes work well only at removing cases with high cloud impact, and as a consequence, the error distributions are highly skewed.
-To use these observations correctly data assimilation schemes often inflate their asymmetric error distributions at the cost of artificially suppressing the observational impact.
-This is not the optimal solution but the best which can be achieved with present sensors.
-However, the symmetric error distributions obtained from QRNN allow us to effectively utilize more than 95\% of the data without the need for error inflation.
+To use these observations correctly, DA schemes often inflate their asymmetric error distributions at the cost of artificially suppressing the observational impact.
+However, the symmetric error distributions obtained from QRNN allow effective utilization of almost complete data without the need for artificial error inflation.
+In fact for DA, filtering based on correction threshold would be needless as cases with low accuracy shall inevitably get inhibited due to high uncertainty.
 
@@
 
-The applicability of QRNN based correction to current sensors is demonstrated with MHWS-2 and it is shown that QRNN is partially successful in removing the cloud impact.
-This is not  an optimal solution, but it is in agreement with what can be achieved with the present instruments.
-In comparison to existing clear-filtering approaches, QRNN gives comparable or better performance and with minimal rejection of data.
-The accuracy of QRNN is affected by one single limitation, that is the prediction of ``out of distribution'' cases.
-Out of distribution cases are those which belong to a different a priori distribution than the one QRNN is trained on.
-Such cases can be the ones which occur infrequently, or those which lack any orthogonal information.
-The representation of the former can be improved with larger training datasets.
-However for the latter, improving their a priori distribution is not trivial.
-Correcting hydrometeor impact for cases without complete complementary information is a challenge for QRNN and always limit its performance.
-\todo{Cases without orthogonal information are note what I understand as out-of-distribution samples.
-Moreover, rare cases are rather a matter of training set size.
-Nonetheless, it is of course essential that
-  the training set distribution reflects reality.}
-
-Based on the promising results from MWHS-2, and with future scope, we extend the study to include data from sub-millimeter (sub-mm) channels.
+The applicability of QRNN based correction to current sensors is demonstrated
+with MHWS-2 (MicroWave Humidity Sounder-2) and it is shown that QRNN is
+partially successful in removing the cloud impact. In comparison to existing
+clear-filtering approaches, QRNN gives comparable or better performance with
+minimal rejection of data. Nonetheless, since cloud correction using a limited
+number of microwave channels is an ill-posed problem, a point-estimate-based
+correction using only microwave observations between 89 and 150\,GHz is
+inherently limited in its capability of correcting cloud-contaminated brightness
+temperatures.
+
+Based on the promising results from MWHS-2, and with future scope, we extend the study to include data from Ice Cloud Imager (ICI) sub-millimetre (sub-mm) channels.
 The results show that with  sub-mm channels, QRNN is able to correctly predict most of the cloudy cases and can provide high quality cloud corrected radiances.
@@
 The results indicate that utilisation of only 325\,GHz can also be beneficial when other channels are absent.
-In future when ICI would be available, the ICI sub-mm channels could also be used to cloud correct MWI (MicroWave Imager) humidity radiances.
-Although re-mapping to a common footprint would slighly compromise the data quality, the high accuracy achieved with ICI simulations suggests that the QRNN would work well even when actual measurements are available.
-
-The biggest advantge of QRNN compared to other regression based approached is its probabilistic nature.
+It's possible that the ICI sub-mm channels could also be used to cloud correct humidity radiances from MicroWave Imager (MWI)---another conically scanning radiometer onboard Metop-SG.
+MWI will measure frequencies from 18\,GHz to 183\,GHz.
+Both MWI and ICI have the same requirements for incidence angle and fore-view observations, but different footprints.
+Although re-mapping to a common footprint  would slightly compromise the data quality, the high accuracy achieved with ICI simulations suggests that the QRNN would work well even when actual measurements are available.
+
+The biggest advantage of QRNN compared to other regression based approaches is its probabilistic nature.
 The QRNN predictions over chosen quantiles are a measure of the accuracy at different probability levels.
 In this study, the predicted quantiles given by QRNN work well in representing the accuracy of the point estimate.
-The point estimates with low error have high certainty.
-On the other hand, the  incorrect predictions on out-of-distribution cases have low confidence.
+The point estimates with low error have high certainty and incorrect predictions have low confidence.
 In comparison to deterministic correction approaches, the corrected radiances along with uncertainty estimates give additional benefit for DA systems.
@@
 
-The high quality cloud corrected radiances have great potential in both retrieval schemes and  NWP systems.
+The cloud corrected radiances have great potential in both retrieval schemes and numerical weather prediction (NWP) systems.
 Even with availability of new sensors and better observations, the problems posed by undetected cloud impact limit the complete usage of humidity observations.
 However, with the cloud correction methodology presented here, we can aim at resolving these limitations.
-This is specially true for clear-sky assimilation systems, which reject upto 80\% of the available observations due to cloud contamination.
-The loss is largest in mid-latitudes.
-Although, NWP systems are gradually moving towards assimilating all-sky radiances but the use of data is overly cautious.
-Infact, one of reasons for the positive performance of all-sky assimilation systems is also attributed to larger number of assimilated observations in comparison to clear-sky observations.
-If QRNN can provide the clear-sky NWP systems, cloud cleared microwave radiances with minimal rejection of data, we can reap forecast benefits without  additional complexities and inflation of errors.
-The all-sky assimilation systems could also benefit indirectly from cloud corrected radiances.
-To improve the representivity of clouds in the all-sky NWP models, the observational errors are inflated as a function of the cloud amount.
-QRNN could be employed here just to provide a measure of cloud impact.
+This is especially true for clear-sky assimilation systems, which reject up to 80\% of the available observations due to cloud contamination.
+In fact, one of reasons for the positive performance of all-sky assimilation systems is attributed to the larger number of assimilated observations in comparison to clear-sky observations.
+If QRNN can provide the clear-sky NWP systems with cloud cleared microwave radiances with minimal rejection of data, it may be possible to reap forecast benefits without additional complexities and computational cost of scattering calculations.
+The all-sky assimilation systems could also benefit indirectly from cloud corrected radiances, to provide a measure of cloud impact as a diagnostic field for analysing increments.
 Another advantage of combining 183\,GHz and sub-mm for cloud correction is that NWP systems, which are not yet prepared for higher frequency channels, could still benefit from the data early on.
@@
 
-\codeavailability{TEXT} %% use this section when having only software code available
-
-\dataavailability{TEXT} %% use this section when having only data sets available
-
-\codedataavailability{TEXT} %% use this section when having data sets and software code available
-
-\sampleavailability{TEXT} %% use this section when having geoscientific samples available
-
-\videosupplement{TEXT} %% use this section when having video supplements available
+\codeavailability{QRNN is available as a part of the \textit{typhon: tools for atmospheric research},  https://doi.org/10.5281/zenodo.3626449.
+The source code for all the analysis presented in the article is available as git repository (https://github.com/SEE-MOF/aws)}
 
@@
 %
-Cloudsat profiles during August 2015 were randomly selected for forward simulations.
-The input data were restricted between $60^{\degree}$S to $60^{\degree}$N, and surface is below 500\,m.
-Both clear-sky and all-sky scenarios were simulated, and no differentiation was made between the observations over ocean/sea and land.
+All radiative transfer forward simulations are made by the Atmospheric Radiative
+Transfer System (ARTS, \citet{eriksson:arts2:11,buehler:artst:18}), version
+arts-2.3.1.
+All simulations are based on dBZ-based model system \citep{ekelund2020using}, i.e.
+CloudSat reflectivities are used as input and are converted to ice water path (IWP) fields using microphysical assumptions.
+For each atmospheric case, both ``all-sky'' and ``clear-sky'' calculations are performed.
+In the former, all hydrometeors contents are set to zero, while in the latter, ice water content (IWC) and rain water content (RWC) derived from CloudSat reflectivities and liquid water content (LWC) from ERA-Interim \citep{dee2011erainterim} are included.
+In order to avoid a possible bias between clear-sky and all-sky calculations for insignificant hydrometeor contents, both calculations are made by ARTS's interface to the RT4 solver \citep{evans1995microwavec}.
 
 The absorption model takes into account the effect from nitrogen
-\citep{pwr:93}, oxygen \citep{pwr:93} and water vapour 
-\citep{ellison2007permittivity}. Liquid water content (LWC) is taken from ERA-Interim \citep{dee2011erainterim} and is assumed
-to be totally absorbing. In the mapping of CloudSat reflectivities to rain water content (RWC) and
-ice water content (IWC) a total separation between liquid and ice phase is assumed. All scattering
-hydrometeors at temperatures above 0$^\circ$C are assumed to be rain, and all
-below 0$^\circ$C are assumed to be ice hydrometeors. For RWC the particle size
-distribution of \citet{abel2012improved} is applied. The particle size distribution (PSD) of IWC follows the basic formulation applied in DARDAR (\url{
+\citep{pwr:93}, oxygen \citep{pwr:93} and liquid water content (LWC, \citet{ellison2007permittivity}).
+LWC is taken from ERA-Interim  and is assumed to be totally absorbing.
+In the mapping of CloudSat reflectivities to RWC and IWC, a total separation between liquid and ice phase is assumed.
+All scattering hydrometeors at temperatures above 0$^{\degree}$C and below 0$^{\degree}$C are assumed to be rain and ice hydrometeors, respectively.
+For RWC the particle size
+distribution (PSD) of \citet{abel2012improved} is applied. The PSD of IWC follows the basic formulation applied in DARDAR (\url{
 http://www.icare.univ-lille1.fr/projects/dardar}, \citet{delanoe2008variational}), using latest parameter
@@
 study. The land emissivity was taken from TELSEM (Tool to Estimate Land‐Surface Emissivities at Microwave frequencies, \citet{aires2011tool}) and the
-Ocean/water from TESSEM (Tool to Estimate Sea‐Surface Emissivity from Microwaves to sub‐Millimeter waves , \citet{prigent2017sea}). For each atmospheric case,
-both ``clear-sky'' and ``all-sky'' calculations were performed. In the former,
-all impact of all hydrometeors were set to zero, while in the latter, IWC and
-RWC derived from CloudSat reflectivities and LWC from ERA-Interim were taken
-into account. Both sets of calculations were made by ARTS's interface to the
-RT4 solver \citep{evans1995microwavec}. To avoid a possible bias between
-clear-sky and all-sky for insignificant hydrometeor contents, the same
-``scattering solver'' was used for both calculations. The first two elements
-of the Stokes vector were calculated.
-For AWS, forward simulations were performed for 21 monochromatic frequencies, and later these frequencies were interpolated to a finer grid to get the AWS channel brightness temperatures.
-
-\subsection{QRNN network structure}
+Ocean/water from TESSEM (Tool to Estimate Sea‐Surface Emissivity from Microwaves to sub‐Millimeter waves , \citet{prigent2017sea}).
+
+Using the setup described above, forward simulations are performed for ICI and AWS.
+The output from ARTS is first two elements of the Stokes vector,  which are converted to brightness temperatures for H- and V-polarisation.
+
+\section{QRNN network structure}
 \label{appendix:hyperparamter}
@@
 	\centering
-	\includegraphics[height=60mm]{Figures/CRPS.pdf} 
-	\caption{CRPS(left) and mean quantile loss(right) averaged over all predicted quantiles for different combinations of layer width and hidden layers ($n_h$).
+	\includegraphics[height=60mm]{Figures/figB1.pdf} 
+	\caption{CRPS(left) and mean quantile loss (right) averaged over all predicted quantiles for different combinations of layer width and hidden layers ($n_h$).
 The results are from QRNN-single applied to I2V.}
@@
 Though these set of hyper-parameters were selected for QRNN-single applied to I2V, they worked well for both ICI and AWS QRNN experiments.
-However, for MWHS-2, an identical hyperparameter framework but three hidden layers gave best results.
+However, for MWHS-2, an identical hyper-parameter framework but three hidden layers gave best results.
+
+\begin{table*}[t]
+	\caption{ Same as Table~\ref{tab:error_statistics_mwhs_others}, but from QRNN-single for ICI channels I1V, I2V and I3V. The fraction of rejected cases is given in parentheses.}
+	\label{tab:error_statistics_ici}
+	%	\tabcolsep=0.11cm
+	\begin{tabular}{llrr|rr|rr}
+		\tophline
+		&&\multicolumn{2}{c|}{Simulations}& \multicolumn{2}{c|}{QRNN All sub-mm}&\multicolumn{2}{c}{QRNN only 325 GHz} \\
+		\cline{3-8}
+		%		\hline
+		&&Clear-sky &   All-sky &  \multicolumn{2}{c|}{Predicted}&  \multicolumn{2}{c}{Predicted}   \\
+		&&			   &			&	(All) & (5\,K) &	(All) & (5\,K)\\
+		\middlehline
+		%		\multicolumn{7}{c}{Channel - I1V}\\
+
+		I1V&  Bias      &  0.00 & -1.87 & -0.02 & -0.00(6.1\%) & -0.03 & -0.01(6.2\%) \\
+		&MAE       		&  0.64 &  2.32 &  0.70 &  0.60  &   0.73 &  0.61 \\
+		&STD       		&  0.80 &  8.84 &  1.06 &  0.79  &  1.14 &  0.81 \\
+		&Skewness 		& -0.01 & -8.10 & -1.51 & -0.64  & -1.26 & -0.70\\
+		\middlehline
+		I2V & Bias      & 0.00 &  -1.04 &  0.00 &  0.01(3.6\%) & -0.03 & -0.01(3.6\%)  \\
+		&MAE       		& 0.64 &   1.53 &  0.57 &  0.51 &  0.62 &  0.54\\
+		&STD       		& 0.80 &   5.95 &  0.86 &  0.65 &  0.99 &  0.70\\
+		&Skewness 		& 0.00 & -10.79 & -1.85 & -0.22 & -2.67 & -0.38 \\
+		\middlehline	
+		I3V & Bias      & 0.01 &  -0.63 &  0.02 &  0.02(2.2\%)&  0.02 &  0.03(2.2\%)  \\
+		&MAE       		& 0.64 &   1.15 &  0.54 &  0.50  &  0.60 &  0.55\\
+		&STD       		& 0.80 &   4.27 &  0.80 &  0.63  &  0.94 &  0.70\\
+		&Skewness 		& 0.01 & -13.37 & -1.51 & -0.13  & -3.28 & -0.22\\
+		\bottomhline
+	\end{tabular}
+	\belowtable{} % Table Footnotes
+\end{table*}
 
@@
 
-\authorcontribution{TEXT} %% this section is mandatory
-
-\competinginterests{TEXT} %% this section is mandatory even if you declare that no competing interests are present
-
-\disclaimer{TEXT} %% optional section
+\authorcontribution{The study was conceptualised and supervised by PE.
+The analysis, validation and visualisation of results was done by IK.
+The QRNN package is made available by SP.
+ARTS bulk simulations were set up by SP, and MWHS-2 data was provided by DID.
+IK wrote the original draft, with contributions from PE, SP and DID.
+All authors contributed to the study with discussions and feedback.}
+
+\competinginterests{The authors declare no conflict of interest.}
 
 \begin{acknowledgements}
-TEXT
+The part associated with AWS was done with funding from EUMETSAT (contract  EUM/CO/20/4600002417/CJA), while remaining work was mainly funded by the Swedish National Space Agency (grants 166/18 and 154/19).
+David Duncan is supported by the EUMETSAT Fellowship Programme.
+This project would not had been possible without the contribution of all individuals behind the open source softwares used (ARTS, Python, PyTorch, Numpy and Matplotlib).
 \end{acknowledgements}

### 2020-11-23 Article/ici_submm_cloudcorr.tex
added Simon's corrections

@@
 \citep{john2013assessment,moradi:retri:15,berg2016intercalibration}. Commonly
-used cloud filtering methods for these applications are based on 183\,GHz data alone, involving rules on the brightness temperatures differences between channels \citep{burns1997effects, buehler:aclou:07}.
+used cloud filtering methods for these applications are based on 183\,GHz data alone, involving rules on the brightness temperature differences between channels \citep{burns1997effects, buehler:aclou:07}.
 
@@
 The MicroWave Humidity Sounder 2 (MWHS-2) is an instrument on two current satellites in the FengYun-3 series, FY-3C and FY-3D.
-MWHS-2 a cross track scanning microwave radiometer and measures 15 frequencies in the range 89--191\,GHz.
+MWHS-2 is a cross track scanning microwave radiometer and measures 15 frequencies in the range 89--191\,GHz.
 89\,GHz and 150\,GHz are window channels, five humidity sounding channels are centered around 183\,GHz, and eight temperature sounding channels are centered on the 118.75\,GHz oxygen absorption line.
@@
 A smaller database is selected for AWS.
-120\,000 simulations are used for training and the rest for testing.
+120\,000 simulations are used for training and the remaining 23\,000 for testing.
 
@@
 The hyper-parameter tuning is made on the validation dataset (see Appendix~\ref{appendix:hyperparamter}).
-The validation dataset is part of the training dataset which is held back during the training.
+The validation dataset is a separate part of the training dataset which is held back during the training.
 
@@
 	\includegraphics[width = 70mm]{Figures/fig02.pdf} 
-	\caption{The distribution of point estimate (``Predicted'') obtained from QRNN-single 89+150\,GHz for MWHS-2 channel 14.
+	\caption{The distribution of point estimates (``Predicted'') obtained from QRNN-single 89+150\,GHz for MWHS-2 channel 14.
 The corresponding distributions for all-sky and clear-sky simulations are also shown.}
@@
 The statistics for all-sky and clear-sky simulations are also provided.
-The label ``All'' denotes the entire dataset of predicted point estimates, while ``Pred.(5\,K)'' refers to the predicted point estimates but where cases with cloud correction greater than 5\,K are excluded.
+The label ``All'' denotes the entire dataset of predicted point estimates, while ``Pred.
+(5\,K)'' refers to the predicted point estimates but where cases with cloud correction greater than 5\,K are excluded.
 The last two columns show the statistics obtained after filtering cloudy cases according to scattering index (SI) and scheme by \citet{buehler:aclou:07} (B183).
@@
 		&   Clear-sky &   All-sky &  \multicolumn{2}{c|}{89+150\,GHz} & \multicolumn{2}{c|}{89+150+118\,GHz} & \multicolumn{2}{c|}{150\,GHz} & \multicolumn{2}{c|}{89+150+183\,GHz}& SI & B183\\		
-		&			   &			& All & Pred.(5\,K) & All & Pred.(5\,K) & All & Pred.(5\,K)  & All & Pred.(5\,K)&&\\
+		&			   &			& All & Pred. (5\,K) & All & Pred. (5\,K) & All & Pred. (5\,K)  & All & Pred. (5\,K)&&\\
 		\middlehline
@@
 Including 118\,GHz in the training gives a small improvement compared to 89+150 GHz alone.
-The error distribution has lower bias and are more symmetric, but the MAE and standard deviation remain unaltered.
+The error distribution has lower bias and is more symmetric, but the MAE and standard deviation remain unaltered.
 This indicates that the information from 118\,GHz channels can be beneficial in predicting few cases correctly, but the overall performance is not exceptionally different from 89+150\,GHz.
@@
 
-The three experiments were also performed for other four 183\,GHz channels, and a similar performance was obtained (not shown).
+The three experiments were also performed for the other four 183\,GHz channels, and a similar performance was obtained (not shown).
 The positive effect of 118\,GHz was slightly higher for MWHS-2 channel 15, but for others, no notable effect was observed.
-In view of negligible performance differences between the three experiments, we consider the combination 89+150\,GHz to be the optimal.
+In view of negligible performance differences between the three experiments, we consider the combination 89+150\,GHz to be optimal.
 The results for other channels with this experiment are provided in Sect.~\ref{sec:mwhs_others}.
@@
 		& &  Clear-sky &   All-sky &  \multicolumn{2}{c|}{89+150\,GHz}    & SI & B183  \\
-		&	&		   &			& All & Pred.(5\,K) &&\\
+		&	&		   &			& All & Pred. (5\,K) &&\\
 		\middlehline
@@
 	\caption{The distribution of predicted errors and observed errors  obtained from QRNN-single (89+150\,GHz) for MWHS-2 channel 14.
-The predicted errors are estimated as deviation of random samples from posteriori distribution to corresponding median values.}
+The predicted errors are estimated as deviation of random samples from a posteriori distribution to corresponding median values.}
 	\label{fig:predicted_errors_mwhs}	
@@
 	\item In the second experiment, we investigate the possibility of using only channels around 325\,GHz for cloud correction at 183\,GHz.
-This special case of utilising only 325\,GHz channel can be relevant for smaller satellite missions like AWS where higher sub-mm channels are not available.
+This special case of utilizing only 325\,GHz channels can be relevant for smaller satellite missions like AWS where higher sub-mm channels are not available.
 In this experiment, QRNN-single configuration is used and it is trained with all-sky simulations from all 325\,GHz frequencies from AWS and the target 183\,GHz channel.
@@
 \end{table*}
-In an analogy between the results from ICI channels, we perform a similar error distribution analysis  and the results are displayed in Table~\ref{tab:statistics_qrnn_aws}.
+In an analogy to the results from ICI channels, we perform a similar error distribution analysis  and the results are displayed in Table~\ref{tab:statistics_qrnn_aws}.
 For channel AWS-32, the average bias and standard deviation in the uncorrected dataset is $-$1.32\,K and 6.42\,K respectively.
@@
 The predictions for the complete test dataset are well calibrated and follow the $y =x$ curve.
-Similar is the case, when cases with correction greater than 5\,K are considered.
-On the other hand, when  the cases with cloud correction greater than 10\,K are considered, the calibration is only slightly worse.
-In spite of the fact that such cases are few (~2\,\%), the high calibration indicates that QRNN is also successful in predicting the uncertainties associated with rare cases.
+Similar is the case, when cases with correction greater than 5\,K are considered (not shown).
+On the other hand, when  the cases with cloud correction greater than 10\,K are considered, the calibration is  slightly worse.
+In spite of the fact that such cases are few (2\,\%), the high calibration indicates that QRNN is also successful in predicting the uncertainties associated with rare cases.
 For other two channels also the predictions are well calibrated, except for cases with correction greater than 5\,K in channel I1V (not shown).
@@
 For AWS-32, the resulting error distributions have significantly lower spread than the all-sky simulations, but are still negatively skewed.
-In spite of the slightly inferior performance for AWS-32, the high accuracy for other channels indicates that a single sub-mm channel like 325\,GHz is also sufficient enough for cloud correction at 183\,GHz.
+In spite of the slightly inferior performance for AWS-32, the high accuracy for other channels indicates that a single sub-mm channel like 325\,GHz is also sufficient for cloud correction at 183\,GHz.
 This is an important result as smaller satellites may be limited by their size to measure several sub-mm wavelengths.
@@
 The applicability of QRNN based correction to current sensors is demonstrated with MHWS-2 (MicroWave Humidity Sounder-2) and it is shown that QRNN is partially successful in removing the cloud impact.
-In comparison to existing clear-filtering approaches, QRNN gives comparable or better performance and with minimal rejection of data.
+In comparison to existing clear-filtering approaches, QRNN gives comparable or better performance with minimal rejection of data.
+Nonetheless, since cloud correction
+using a limited number of microwave channels is an ill-posed problem, a point-estimate-based correction using only microwave observations between 89 and 150 GHz is inherently limited in its capability of correcting cloud-contaminated brightness temperatures.
+
 The accuracy of QRNN is affected by one single limitation, that is presence of cases which belong to a different a priori distribution than the one QRNN is trained on.

### 2020-11-24 Article/ici_submm_cloudcorr.tex
Updated with Dave's comments, New title

@@
 
-\title{Cloud correction of humidity radiances with case-specific uncertainty 
-	estimate}
+\title{Can machine learning correct microwave humidity radiances for the
+	influence of clouds?}
 
@@
 
-\runningtitle{Cloud correction with case specific uncertainty estimation}
+\runningtitle{Correcting cloud affected microwave radiances}
 
@@
 
-Another motivation necessitating the need for cloud clearing is usage of 183\,GHz channels in 
+Another motivation necessitating the need for cloud filtering is usage of 183\,GHz channels in 
 numerical weather prediction (NWP). Usage of passive microwave data by
@@
 	\includegraphics[width = 70mm]{Figures/fig03.pdf} 
-	\caption{The error distribution for deviations of point estimates to NFCS simulations.
+	\caption{The error distribution for deviations of point estimates from NFCS simulations.
 The results are from QRNN-single experiment 89+150\,GHz and MWHS-2 channel 14.
@@
 \begin{table*}[t]
-	\caption{The error statistics for deviations of point estimates to NFCS simulations.
+	\caption{The error statistics for deviations of point estimates from NFCS simulations.
 Results are for different QRNN experiments for MWHS-2 channel 14 (see Sect.~\ref{sec:QRNN_expt_MWHS}).
@@
 However, QRNN is unable to predict the lowest clear-sky brightness temperatures, and cases with brightness temperatures around 260\,K, occur too frequently.
-The deviations of point estimates to NFCS simulations are shown in Fig.~\ref{fig:error_distribution_mwhs14}.
+The deviations of point estimates from NFCS simulations are shown in Fig.~\ref{fig:error_distribution_mwhs14}.
 The large negative deviations are removed (blue curve), but residual cloud impact is evident in the negative tail.
@@
 	\centering
-	\includegraphics[height = 55mm]{Figures/fig04.pdf} 
+	\includegraphics[width=0.65\textwidth]{Figures/fig04.pdf} 
 	\caption{ The triangular error correlation matrix obtained from (a) QRNN-single and (b) QRNN-all for MWHS-2. The label ``Clear'' represents cases with cloud impact less than 2\,K.}
@@
 
-The partial performance of QRNN is due to incomplete orthogonal information to 183\,GHz channels.
+The partial performance of QRNN is due to incomplete complementary information to 183\,GHz channels.
 The weighting functions of window channels 89 and 150\,GHz, and the two 118\,GHz channels peak in the lower troposphere.
@@
 Without additional information from other channels we cannot expect QRNN to perform better.
-Among the other available channels, the overlapping weighting functions of 183\,GHz can provide auxiliary information to train QRNN.
-Results show that these channels indeed help in improving the training, yet the non-orthogonal information introduces highly correlated observational errors.
+Among the other available channels, the overlapping weighting functions of 183\,GHz can provide auxiliary information to train QRNN, but such information would be not be completely orthogonal or statistically uncorrelated.
+Results show that these channels indeed help in improving the training, yet non-orthogonality introduces highly correlated observational errors.
 The correlations for cloudy observations are not surprising as the cloud amount for different channels depends upon each other in a systematic way.
@@
 This has the consequence that a DA system can assign a proper weighting of each individual QRNN prediction.
-The analysis of QRNN predicted errors and calibration plots confirmed that QRNN is successful in providing
-well calibrated probabilistic predictions also in practice, except for few cases associated with high error.
-Poorly calibrated predictions are a consequence of cases with different underlying a priori distribution.
-Predictions with high error originate from cases which occur infrequently or cases with no orthogonal information.
-Such cases have a significantly distinct a priori distribution as compared to clear cases, which dominate the training dataset, and influence the a priori information.
-The distribution of rare cases can be improved by increasing the training dataset size, but lack of orthogonal information can only be balanced by including additional training inputs, e.g.
+The analysis of QRNN predicted errors and calibration plots confirmed that QRNN is successful in providing well calibrated probabilistic predictions also in practice, except for few cases associated with high error.
+Poorly calibrated predictions are a consequence of outliers which are not well represented in the training dataset.
+The a priori distribution of the training dataset is dominated by clear-sky cases, however, the cloudy cases which occur infrequently or lack independent complementary information cannot be represented by same a priori distribution.
+The distribution of rare cases can be improved by increasing the training dataset size, but lack of complementary information can only be balanced by including additional training inputs, e.g.
 brightness temperatures for other channels.
@@
 Most of the existing cloud filtering schemes work well only at removing cases with high cloud impact, and as a consequence, the error distributions are highly skewed.
-To use these observations correctly, DA schemes often inflate their asymmetric error distributions at the cost of artificially suppressing the observational impact.
+To use these observations correctly, DA schemes often inflate their assigned observation errors at the cost of artificially suppressing the observational impact.
 However, the symmetric error distributions obtained from QRNN allow effective utilization of almost complete data without the need for artificial error inflation.
-In fact for DA, filtering based on correction threshold would be needless as cases with low accuracy shall inevitably get inhibited due to high uncertainty.
+In fact for DA, filtering based on correction threshold would be needless as cases with low accuracy shall inevitably get down-weighted due to high uncertainty.
 
@@
 
-In this study, a methodology based on quantile regression neural network (QRNN) is used for identifying and correcting the cloud contamination in operational humidity channels.
+In this study, a methodology based on quantile regression neural network (QRNN) is used for identifying and correcting the cloud contamination in operational microwave humidity channels.
 QRNN is a neural network which trains on all-sky brightness temperatures from channels containing orthogonal information to humidity channels, to estimate the noise free clear-sky (NFCS) brightness temperatures.
@@
 using a limited number of microwave channels is an ill-posed problem, a point-estimate-based correction using only microwave observations between 89 and 150 GHz is inherently limited in its capability of correcting cloud-contaminated brightness temperatures.
-
-The accuracy of QRNN is affected by one single limitation, that is presence of cases which belong to a different a priori distribution than the one QRNN is trained on.
-Such cases can be either the ones which occur infrequently, or those which lack any orthogonal information.
-The representation of the former can be improved to represent reality by simply choosing larger training datasets.
-However for the latter, improving their a priori distribution is not trivial.
-Correcting hydrometeor impact for cases without complete complementary information is a challenge for QRNN and always limits its performance.
 

### 2020-11-26 Article/ici_submm_cloudcorr.tex
version submitted to AMT

@@
 The proposed cloud correction scheme makes use of a Quantile Regression Neural
-Network (QRNN, \citet{pfreundschuh:aneur:18}) to obtain a probabilistic prediction of the NFCS value. Unlike traditional neural networks techniques, which typically only provide a point
+Network \cite[QRNN,][]{pfreundschuh:aneur:18} to obtain a probabilistic prediction of the NFCS value. Unlike traditional neural networks techniques, which typically only provide a point
 estimate of the target variable, QRNNs are trained to predict an arbitrary set
@@
 A description of the data used in this study and the QRNN approach is provided
-in Sect.\ref{data_methods}. In Sect.~\ref{qrnn_mwhs} we demonstrate the
+in Sect.~\ref{data_methods}. In Sect.~\ref{qrnn_mwhs} we demonstrate the
 applicability of correction scheme to existing sensors, and later its
-application is extended to include sub-mm channels (Sect.\ref{qrnn_ici}). The
+application is extended to include sub-mm channels (Sect.~\ref{qrnn_ici}). The
 results are discussed in Sect.~\ref{discussions}, and Sect.~\ref{conclusions}
-presents the conclusions from this work and the future outlook.
+presents the conclusions from this work, and the future outlook.
 
@@
 MWHS-2 is a cross track scanning microwave radiometer and measures 15 frequencies in the range 89--191\,GHz.
-89\,GHz and 150\,GHz are window channels, five humidity sounding channels are centered around 183\,GHz, and eight temperature sounding channels are centered on the 118.75\,GHz oxygen absorption line.
+89\,GHz and 150\,GHz are window channels, five humidity sounding channels are centered around 183\,GHz, and eight temperature sounding channels are centered on the 118\,GHz oxygen absorption line.
 The five humidity sounding channels are similar to ATMS.
@@
 \end{table}
-The AWS is a small satellite mission approved as European Space Agency (ESA) Earth Watch Programme Element.
+The AWS is a small satellite mission suggested as an European Space Agency (ESA) Earth Watch Programme Element.
 It is a small platform carrying a single across-track scanning microwave radiometer.
@@
 In spite the fact that QRNN only provides a partial cloud correction, the results for  MWHS-2 channel 14 are better than what we achieve with existing cloud filtering techniques like scattering index (SI) and the filtering scheme by \citet{buehler:aclou:07}, hereafter B183.
-SI uses the differences of brightness temperatures between 89 and 150\,GHz to identify cloud affected data, whilst in B183, they use brightness temperature based threshold to filter out cloudy cases.
-They recommend a viewing angle dependent brightness temperature threshold at $183.31\pm1.00$\,GHz and brightness temperature difference between $183.31\pm3.00$\,GHz and $183.31\pm 1.00$\,GHz as a measure of cloud impact.
+SI uses the differences of brightness temperatures between 89 and 150\,GHz to identify cloud affected data; whilst in B183, they recommend a viewing angle dependent brightness temperature threshold at $183.31\pm1.00$\,GHz and brightness temperature difference between $183.31\pm3.00$\,GHz and $183.31\pm 1.00$\,GHz as a measure of cloud impact.
 The results obtained with SI and B183 are displayed in last two columns of Table~\ref{tab:error_statistics_mwhs_14}.
-With SI threshold 5\,K, almost 28\,\% of the data is rejected, yet the resulting error distributions are poorer as compared to QRNN.
+With SI threshold 5\,K, more than 28\,\% of the data is rejected, yet the resulting error distributions are poorer as compared to QRNN.
 The low bias and skewness values indicate that most of the high negative departures are removed, but cases with low cloud impact pass the filter as clear.
@@
 A gaussian error model is used to represent the distribution of the errors, and plotted under the label ``SI''.
-For the entire dataset, the predictions from QRNN follow the $y=x$ line, i.e.
-the predicted uncertainties are perfectly calibrated with the errors observed on the test data.
+For the entire dataset, the predictions from QRNN follow the $y=x$ line, i.e.\ the predicted uncertainties are perfectly calibrated with the errors observed on the test data.
 However for the cases with correction greater than 5\,K, the distribution is poorly calibrated, and the curve lies below the $y =x$ line, indicating that the prediction intervals are too narrow.
@@
 \begin{table*}[t]
-	\caption{ Same as Table~\ref{tab:error_statistics_mwhs_others}, but from QRNN-single for ICI channels I1V, I2V and I3V. The fraction of rejected cases is given in parentheses.}
+	\caption{ Same as Table~\ref{tab:error_statistics_mwhs_others}, but from QRNN-single for ICI channels I1V, I2V and I3V. The fraction of rejected cases are given in parentheses.}
 	\label{tab:error_statistics_ici}
@@
 \begin{figure}[t]
-	\includegraphics[width=70mm]{Figures/fig11.pdf}	
+	\includegraphics[width= 70mm]{Figures/fig11.pdf}	
 	\caption{Same as Fig.~\ref{fig:predicted_errors_mwhs}, but from QRNN-single for ICI channel I2V.}
@@
 
-\section{Conclusion and outlook}  %% \conclusions[modified heading if necessary]
+\section{Conclusion and outlook}  
 \label{conclusions}
@@
 
-%% The following commands are for the statements about the availability of data sets and/or software code corresponding to the manuscript.
-%% It is strongly recommended to make use of these sections in case data sets and/or software code have been part of your research the article is based on.
-
 \codeavailability{QRNN is available as a part of the \textit{typhon: tools for atmospheric research},  https://doi.org/10.5281/zenodo.3626449.
@@
 arts-2.3.1.
-All simulations are based on dBZ-based model system \citep{ekelund2020using}, i.e., CloudSat reflectivities are used as input and are converted to ice water path (IWP) fields using microphysical assumptions.
+All simulations are based on dBZ-based model system presented by \citet{ekelund2020using}, i.e.\ CloudSat reflectivities are used as input and are converted to ice water content (IWC) and rain water content (RWC) using microphysical assumptions.
 For each atmospheric case, both all-sky and clear-sky calculations are performed.
-In the former, all hydrometeors contents are set to zero, while in the latter, ice water content (IWC) and rain water content (RWC) derived from CloudSat reflectivities and liquid water content (LWC) from ERA-Interim \citep{dee2011erainterim} are included.
+In the former, all hydrometeors contents are set to zero, while in the latter, IWC and RWC derived from CloudSat reflectivities, and liquid water content (LWC) from ERA-Interim \citep{dee2011erainterim} are included.
 In order to avoid a possible bias between clear-sky and all-sky calculations for insignificant hydrometeor contents, both calculations are made by the RT4 solver \citep{evans1995microwavec}.
-
 The absorption model takes into account the effect from nitrogen
-\citep{pwr:93}, oxygen \citep{pwr:93} and liquid water content \citep[LWC,][]{ellison2007permittivity}.
-LWC is taken from ERA-Interim  and is assumed to be totally absorbing.
+\citep{pwr:93}, oxygen \citep{pwr:93}, liquid water content \citep[LWC,][]{ellison2007permittivity}, and water vapour.
+For water vapour, absorption model as  in RTTOV \citep[Radiative transfer for TOVS,][]{saunders2018update} is followed, but with few modifications \citep{turner2019amsutran}.
+LWC is assumed to be totally absorbing.
 In the mapping of CloudSat reflectivities to RWC and IWC, a total separation between liquid and ice phase is assumed.
 All scattering hydrometeors at temperatures above 0$^{\degree}$C and below 0$^{\degree}$\,C are assumed to be rain and ice hydrometeors, respectively.
-For RWC the particle size
-distribution (PSD) of \citet{abel2012improved} is applied. The PSD of IWC follows the basic formulation applied in the radio detection and ranging(radar)/light
-detection and ranging (lidar) \citep[DARDAR,][\url{
-	http://www.icare.univ-lille1.fr/projects/dardar}]{delanoe2008variational}, using latest parameter values (i.e.\ $\alpha$ and $\beta$) as given by \citet{cazenave2019evolution}.
+For RWC the particle size distribution (PSD) of \citet{abel2012improved} is applied.
+The PSD of IWC follows the basic formulation applied in DARDAR \citep[\url{
+	http://www.icare.univ-lille1.fr/projects/dardar}][]{delanoe2008variational}, using latest parameter values (i.e.\ $\alpha$ and $\beta$) as given by \citet{cazenave2019evolution}.
 This PSD can be considered as a ``two moment'' scheme, but is here applied in

### 2021-01-22 Article/ici_submm_cloudcorr.tex
change AWS --> SMS

@@
 method using sub-millimetre (sub-mm) observations, which will become available
-operationally with the launch of the Ice Cloud Imager \citep[ICI,][]{eriksson:towar:20} on board the next generation of European Organisation for the Exploitation of Meteorological Satellites Polar System - Second Generation (EUMETSAT EPS-SG), but will likely also be included in
-several smaller missions (such as Arctic Weather Satellite (AWS); presented
-below). Additionally, we demonstrate the feasibility of the approach based on
-89 and 150\ GHz channels \citep[following][]{geer2015scatteringindex}, which are available on several sensors extant today. The focus
+operationally with the launch of the Ice Cloud Imager \citep[ICI,][]{eriksson:towar:20} on board the next generation of European Organisation for the Exploitation of Meteorological Satellites Polar System - Second Generation (EUMETSAT EPS-SG).
+Additionally, we demonstrate the feasibility of the approach based on 89 and 150\ GHz channels \citep[following][]{geer2015scatteringindex}, which are available on several sensors extant today.
+The focus
 on sub-mm channels is motivated by several reasons. First, the higher
@@
 
-\subsubsection{Artic Weather Satellite}
+\subsubsection{Small Microwave Satellite}
 %
 \begin{table}[t]
-	\caption{Specifications of AWS channels relevant to this study.}
-	\label{tab:specifications_AWS}	
+	\caption{Specifications of SMS channels.}
+	\label{tab:specifications_SMS}	
 	\begin{tabular}{lrrr}
@@
 		\middlehline
-		AWS-32	&	176.31    & 2000	&	0.45	\\
-		AWS-33	&	178.81    & 2000 	&	0.45\\
-		AWS-34	&	180.31    & 1000 	&	0.64\\
-		AWS-35	&	181.51    & 1000 	&	0.64 \\
-		AWS-36	&	182.31    & \phantom{0}500  &	0.88 \\
-		AWS-41  & 325.15$\pm$6.60    & 2800 	 &0.60\\
-		AWS-42  & 325.15$\pm$4.10    & 1800    &0.75	\\
-		AWS-43  & 325.15$\pm$2.40    & 1200    &0.92\\
-		AWS-44  & 325.15$\pm$1.20    & \phantom{0}800  &1.12  \\
+		SMS-1	&	176.31    & 2000	&	0.45	\\
+		SMS-2	&	178.81    & 2000 	&	0.45\\
+		SMS-3	&	180.31    & 1000 	&	0.64\\
+		SMS-4	&	181.51    & 1000 	&	0.64 \\
+		SMS-5	&	182.31    & \phantom{0}500  &	0.88 \\
+		SMS-6  & 325.15$\pm$6.60    & 2800 	 &0.60\\
+		SMS-7  & 325.15$\pm$4.10    & 1800    &0.75	\\
+		SMS-8  & 325.15$\pm$2.40    & 1200    &0.92\\
+		SMS-9  & 325.15$\pm$1.20    & \phantom{0}800  &1.12  \\
 		\bottomhline
@@
 \end{table}
-The AWS is a small satellite mission suggested as an European Space Agency (ESA) Earth Watch Programme Element.
-It is a small platform carrying a single across-track scanning microwave radiometer.
-It is planned as a small but cost-effective platform, which can supplement the information from other polar orbiting satellites.
-The first prototype mission is expected to be delivered around 2023.
-The exact channels onboard AWS are not yet set, but five 183\,GHz and four 325\,GHz channels are presently planned.
-A brief summary of these channels is provided in Table~\ref{tab:specifications_AWS}.
-
-In this study, forward simulations of the channels around 183\,GHz and 325\,GHz were conducted.
+The Small Microwave Satellite (SMS) is a hypothetical satellite which we consider to represent the type of sensors currently being considered for future missions.
+We assume it to be a single across-track scanning microwave radiometer with five 183\,GHz channels and four 325\,GHz channels.
+A brief summary of the  channel specifications assumed is provided in Table~\ref{tab:specifications_SMS}.
 
@@
 
-ICI and AWS frequencies are simulated with Atmospheric Radiative Transfer Simulator \citep[ARTS,][]{buehler:artst:18}.
+ICI and SMS frequencies are simulated with Atmospheric Radiative Transfer Simulator \citep[ARTS,][]{buehler:artst:18}.
 For the forward simulations, Cloud Satellite \citep[Cloudsat,][]{Stephens2002cloudsat} profiles during August 2015 are randomly selected.
@@
 The complete simulation setup is described in Appendix \ref{appendix:ARTS_setup}.
-For ICI and AWS, 220\,000 and 143\,000 cases are simulated, respectively.
-All AWS sensor viewing angles (from $0^{\degree}$ to $45^{\degree}$) are simulated, but the results described in this study are based on nadir viewing angle.
-Simulations for all three sensors are noise free, so to incorporate the measurement uncertainties, whenever needed, Gaussian noise is added according to the channel NE$\Delta$T (Table~\ref{tab:specifications_MWHS2} -- Table~\ref{tab:specifications_AWS}).
+For ICI and SMS, 220\,000 and 143\,000 cases are simulated, respectively.
+For SMS, sensor viewing angles from $0\unit{^{\degree}S}$ to $45\unit{^{\degree}N}$ are simulated, but the results described in this study are based on nadir viewing angle.
+Simulations for all three sensors are noise free, so to incorporate the measurement uncertainties, whenever needed, Gaussian noise is added according to the channel NE$\Delta$T (Table~\ref{tab:specifications_MWHS2} -- Table~\ref{tab:specifications_SMS}).
 
@@
 The remaining 45\,000 are used for testing.
-A smaller database is selected for AWS.
+A smaller database is selected for SMS.
 120\,000 simulations are used for training and the remaining 23\,000 for testing.
@@
 	\item In the second experiment, we investigate the possibility of using only channels around 325\,GHz for cloud correction at 183\,GHz.
-This special case of utilizing only 325\,GHz channels can be relevant for smaller satellite missions like AWS where higher sub-mm channels are not available.
-In this experiment, QRNN-single configuration is used and it is trained with all-sky simulations from all 325\,GHz frequencies from AWS and the target 183\,GHz channel.
-For example, for the target AWS-32, the training inputs are AWS-32, AWS-41, AWS-42, AWS-43, AWS-44.
+This special case of utilizing only 325\,GHz channels can be relevant for smaller satellite missions, as represented by SMS, where higher sub-mm channels are not available.
+In this experiment, QRNN-single configuration is used and it is trained with all-sky simulations from all 325\,GHz frequencies from SMS and the target 183\,GHz channel.
+For example, for the target SMS-1, the training inputs are SMS-1, SMS-6, SMS-7, SMS-8, SMS-9.
 QRNN is trained five times for each 183\,GHz channel as target.
-Note that for this experiment, AWS was chosen due to availability of extra 325\,GHz and 183\,GHz channels.
+
 \end{enumerate}
@@
 
-\subsubsection{AWS}
+\subsubsection{SMS}
 
 \begin{table*}[t]
-	\caption{Same as Table~\ref{tab:error_statistics_mwhs_others}, but from QRNN-single for AWS channels. The fraction of rejected cases is given in parentheses. }
-	\label{tab:statistics_qrnn_aws}
+	\caption{Same as Table~\ref{tab:error_statistics_mwhs_others}, but from QRNN-single for SMS channels. The fraction of rejected cases is given in parentheses. }
+	\label{tab:statistics_qrnn_sms}
 	\begin{tabular}{llrr|rr}
@@
 		\middlehline
-		AWS-32  &Bias     & 0.00 &$-$1.32 &$-$0.04 &$-$0.02 (4.71\,\%) \\
+		SMS-1  &Bias     & 0.00 &$-$1.32 &$-$0.04 &$-$0.02 (4.71\,\%) \\
 				&MAE      & 0.36 &  1.57 &  0.58 &  0.44 \\
@@
 		\middlehline
-		AWS-33	&Bias     &  0.00 &$-$1.00 &$-$0.04 &$-$0.02 (3.75\,\%)  \\
+		SMS-2	&Bias     &  0.00 &$-$1.00 &$-$0.04 &$-$0.02 (3.75\,\%)  \\
 				&MAE      &  0.36 &  1.24 &  0.46 &  0.37  \\
@@
 		\middlehline
-		AWS-34	&Bias    &  0.00 & $-$0.71 &$-$0.06 &$-$0.04 (2.86\,\%)  \\
+		SMS-3	&Bias    &  0.00 & $-$0.71 &$-$0.06 &$-$0.04 (2.86\,\%)  \\
 				&MAE      &  0.50 &   1.10 &  0.47 &  0.41  \\
@@
 		\middlehline
-		AWS-35	&Bias    &$-$0.00 & $-$0.45 &$-$0.03 &$-$0.03 (1.92\%)  \\
+		SMS-4	&Bias    &$-$0.00 & $-$0.45 &$-$0.03 &$-$0.03 (1.92\%)  \\
 				&MAE      &  0.50 &   0.86 &  0.48 &  0.43  \\
@@
 		\middlehline
-		AWS-36  &Bias    &$-$0.01 & $-$0.29 &$-$0.04 &$-$0.04 (1.23\,\%)  \\
+		SMS-5  &Bias    &$-$0.01 & $-$0.29 &$-$0.04 &$-$0.04 (1.23\,\%)  \\
 				&MAE      &  0.71 &   0.90 &  0.63 &  0.60  \\
@@
 \end{table*}
-In an analogy to the results from ICI channels, we perform a similar error distribution analysis  and the results are displayed in Table~\ref{tab:statistics_qrnn_aws}.
-For channel AWS-32, the average bias and standard deviation in the uncorrected dataset is $-$1.32\,K and 6.42\,K respectively.
+In an analogy to the results from ICI channels, we perform a similar error distribution analysis  and the results are displayed in Table~\ref{tab:statistics_qrnn_sms}.
+For channel SMS-1, the average bias and standard deviation in the uncorrected dataset is $-$1.32\,K and 6.42\,K respectively.
 However, after correction, the bias and standard deviation reduce to $-$0.04\,K and 1.15\,K, respectively.
@@
 This is most likely due to rejection of cases affected by over-estimation.
-For AWS-33, the predictions have slightly higher accuracy than AWS-32.
+For SMS-2, the predictions have slightly higher accuracy than SMS-1.
 The MAE in predictions is only 0.46\,K in comparison to 1.24\,K for the all-sky simulations.
@@
 Nonetheless, filtering such cases makes the distribution more symmetric.
-For AWS-34 and AWS-35, again a similar behaviour is seen, though the distributions are more symmetric in the latter.
-For AWS-36, we obtain the most symmetric and narrow distributions after correction owing to the low sensitivity of AWS-36 to hydrometeor impact.
-Also, it is worth to noting that when cases with 5\,K cloud correction are removed, the spread of prediction errors is narrower than noise for AWS-34, AWS-35 and AWS-36.
+For SMS-3 and SMS-4, again a similar behaviour is seen, though the distributions are more symmetric in the latter.
+For SMS-5, we obtain the most symmetric and narrow distributions after correction owing to the low sensitivity of SMS-5 to hydrometeor impact.
+Also, it is worth to noting that when cases with 5\,K cloud correction are removed, the spread of prediction errors is narrower than noise for SMS-3, SMS-4 and SMS-5.
 
@@
 	\includegraphics[width = 70mm]{Figures/fig12.pdf}	
-	\caption{The average confidence intervals ($\pm3\sigma$) plotted against the magnitude of cloud impact for all AWS channels.}
+	\caption{The average confidence intervals ($\pm3\sigma$) plotted against the magnitude of cloud impact for all SMS channels.}
 	\label{fig:uncertainty_cloud_impact}	
@@
 
-With AWS, the behaviour of predicted uncertainties is observed to be similar as for ICI (not shown).
+With SMS, the behaviour of predicted uncertainties is observed to be similar as for ICI (not shown).
 However, the relation between the mean uncertainty estimate ($\pm3\sigma$) and cloud impact is displayed in Fig.~\ref{fig:uncertainty_cloud_impact}.
@@
 As fraction of cloud impact increases, the predictions become increasingly uncertain.
-The most uncertain predictions are for the lowest peaking channel AWS-32, which incidentally is also most affected by  hydrometeor impact.
+The most uncertain predictions are for the lowest peaking channel SMS-1, which incidentally is also most affected by  hydrometeor impact.
 
@@
 In spite of individual variations in the error distributions for each channel, predictions and their corresponding uncertainties follow the same relationship.
-Similar results are also obtained with AWS (not shown).
+Similar results are also obtained with SMS (not shown).
 
@@
 
-A similar pattern is seen when only one 325\,GHz channel is used to correct cloud impact in AWS.
-QRNN is successful in predicting NFCS values for all channels except for the lowest peaking channel AWS-32.
-For AWS-32, the resulting error distributions have significantly lower spread than the all-sky simulations, but are still negatively skewed.
-In spite of the slightly inferior performance for AWS-32, the high accuracy for other channels indicates that a single sub-mm channel like 325\,GHz is also sufficient for cloud correction at 183\,GHz.
+A similar pattern is seen when only one 325\,GHz channel is used to correct cloud impact in SMS.
+QRNN is successful in predicting NFCS values for all channels except for the lowest peaking channel SMS-1.
+For SMS-1, the resulting error distributions have significantly lower spread than the all-sky simulations, but are still negatively skewed.
+In spite of the slightly inferior performance for SMS-1, the high accuracy for other channels indicates that a single sub-mm channel like 325\,GHz is also sufficient for cloud correction at 183\,GHz.
 This is an important result as smaller satellites may be limited by their size to measure several sub-mm wavelengths.
 
-With ICI and AWS, for some channels the variability of errors smaller than measurement noise is achieved.
+With ICI and SMS, for some channels the variability of errors smaller than measurement noise is achieved.
 This is a consequence of predictions for cases which lack cloud impact.
@@
 In the absence of clouds, also the sub-mm channels provide humidity information that is incorporated in the 183 GHz NFCS estimate and some compensation of noise can be achieved.
-This effect is observed to be stronger in ICI than AWS, as the former has a higher number of channels giving redundant information.
+This effect is observed to be stronger in ICI than SMS, as the former has a higher number of channels giving redundant information.
 Note that with actual satellite measurements, the spread of error distributions smaller than sensor noise could be difficult to achieve due to other underlying uncertainties not considered here.
@@
 The robustness of sub-mm channels in cloud correction is also demonstrated with use of only 325\,GHz for cloud correction.
-This is applicable to smaller satellite missions like AWS, where only one of the higher frequencies is available.
+This is applicable to smaller satellite missions as represented by SMS, where only one of the higher frequencies is available.
 The results indicate that utilisation of only 325\,GHz can also be beneficial when other channels are absent.
@@
 In the mapping of CloudSat reflectivities to RWC and IWC, a total separation between liquid and ice phase is assumed.
-All scattering hydrometeors at temperatures above 0$^{\degree}$C and below 0$^{\degree}$\,C are assumed to be rain and ice hydrometeors, respectively.
-For RWC the particle size distribution (PSD) of \citet{abel2012improved} is applied.
+All scattering hydrometeors at temperatures above 0$^{\degree}$C  and below 0$^{\degree}$\,C are assumed to be rain and ice hydrometeors respectively.
+For RWC, the particle size distribution (PSD) of \citet{abel2012improved} is applied.
 The PSD of IWC follows the basic formulation applied in DARDAR \citep[\url{
 	http://www.icare.univ-lille1.fr/projects/dardar}][]{delanoe2008variational}, using latest parameter values (i.e.\ $\alpha$ and $\beta$) as given by \citet{cazenave2019evolution}.
-This PSD can be considered as a ``two moment'' scheme, but is here applied in
-a one moment manner by setting $N_0^*$ (as a function of temperature)
-following Table~5 of \citet{delanoe2014normalized}, and letting the radar
-reflectivity set the remaining moment. Single scattering data are taken from
+This PSD can be considered as a ``two moment'' scheme, but is here applied in a one moment manner by setting $N_0^*$ (as a function of temperature)
+following Table~5 of \citet{delanoe2014normalized}, and letting the radar reflectivity set the remaining moment. Single scattering data are taken from
 \citet{eriksson:agene:18}. For ice hydrometeors, three habits are applied:
 perpendicular 3-bullet rosette, large plate aggregate and large column
-aggregate. In the last two cases, the aggregates are complemented with single
-crystal data to also cover smaller sizes. These data describe particles
-assumed to have a totally random orientation. To apply oriented particles is
-much more computationally costly and could not be accommodated inside the
-study. The land emissivity was taken from Tool to Estimate Land‐Surface Emissivities at Microwave frequencies \citep[TELSEM,][]{aires2011tool} and the
+aggregate. In the last two cases, the aggregates are complemented with single crystal data to also cover smaller sizes. The particles are assumed to have a totally random orientation. 
+To apply oriented particles is much more computationally costly and could not be accommodated inside the study.
+The land emissivity was taken from Tool to Estimate Land‐Surface Emissivities at Microwave frequencies \citep[TELSEM,][]{aires2011tool} and the
 Ocean/water from Tool to Estimate Sea‐Surface Emissivity from Microwaves to sub‐Millimeter waves \citep[TESSEM,][]{prigent2017sea}.
 
-Using the setup described above, forward simulations are performed for ICI and AWS.
+Using the setup described above, forward simulations are performed for ICI and SMS.
 The output from ARTS is first two elements of the Stokes vector,  which are converted to brightness temperatures for H- and V-polarisation.
@@
 
-Though these set of hyper-parameters were selected for QRNN-single applied to I2V, they worked well for both ICI and AWS QRNN experiments.
+Though these set of hyper-parameters were selected for QRNN-single applied to I2V, they worked well for both ICI and SMS QRNN experiments.
 However, for MWHS-2, an identical hyper-parameter framework but three hidden layers gave best results.
@@
 \begin{acknowledgements}
-The part associated with AWS was done with funding from EUMETSAT (contract  EUM/CO/20/4600002417/CJA), while remaining work was mainly funded by the Swedish National Space Agency (grants 166/18 and 154/19).
+The part associated with SMS was done with funding from EUMETSAT (contract  EUM/CO/20/4600002417/CJA), while remaining work was mainly funded by the Swedish National Space Agency (grants 166/18 and 154/19).
 David Duncan is supported by the EUMETSAT Fellowship Programme.

### 2021-01-25 Article/ici_submm_cloudcorr.tex
updated sect 2.1.3, Patrick's suggestion

@@
 \end{table}
-The Small Microwave Satellite (SMS) is a hypothetical satellite which we consider to represent the type of sensors currently being considered for future missions.
-We assume it to be a single across-track scanning microwave radiometer with five 183\,GHz channels and four 325\,GHz channels.
-A brief summary of the  channel specifications assumed is provided in Table~\ref{tab:specifications_SMS}.
+
+The Small Microwave Satellite (SMS) is a hypothetical satellite which we 
+introduce to represent the type of sensors currently being considered 
+for future small missions carrying a single instrument. We assume it to 
+be a single across-track scanning microwave radiometer. In this study, we 
+assume five 183 GHz channels and four 325 GHz channels, and just ignore 
+if the mission has additional channels at lower frequencies or not. A brief summary of the  channel specifications assumed is provided in Table~\ref{tab:specifications_SMS}.
 

### 2021-02-10 Article/Review_1/response_reviewer_1.tex
started response to reviewer

\documentclass[11pt,a4paper,draft]{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{geometry}
\usepackage{xcolor}
%\usepackage{showframe} %This line can be used to clearly show the new margins

\newgeometry{vmargin={30mm}, hmargin={35mm,25mm}}

\begin{document}
\textbf{Response Reviewer 1}

\textbf{	Interactive comment on ``Can machine learning
	correct microwave humidity radiances for the
	influence of clouds?'' by Inderpreet Kaur et al.}

\begin{itemize}

\item 	precipitation and most dense clouds" I think the hydrometeor size is an important

\textcolor{blue}{Reply: We agree that the hydrometeor size is an important aspect, but when it comes to an overview of the contamination at 183\,GHz, precipitating clouds and clouds with large optical thickness have the strongest effect. Though a dense cloud could be composed of hydrometeors of different shapes and size. }

\item	L66: ``only using measurements (no background data involved)'' My understanding is
		that the method is in theory model-free, but for the demonstration in this study, sim-
		ulations (e.g. background simulated at MWHS2 frequency) are used. Am I correct?
		Maybe this should be stressed here. Why not try with real MWHS2 observation for the
		all sky dataset?

\textcolor{blue}{Reply: Yes, the demonstration of the entire concept is based on simulations. We do not try with the real MWHS-2 observations as for the training process we would still require the clear-sky simulations.}

\item
		L137 "Simulations for all three sensors are noise free, so to incorporate the measurement uncertainties, whenever needed, Gaussian noise is added according to the chan-
		nel NEDT (Table 1 ? Table 3)." Are the errors arising from the radiative transfer calculation accounted for?

\textcolor{red}{Reply: }

\item	
		L159: "for all selected quantile fractions " by quantile fraction, do you mean the n th
		amongst the 7 selected (from 0.2 to 99.8\%)? Also, 16, 50 and 85\% are not symmetric
		(rounding?)

\textcolor{blue}{Reply: Yes, the selected quantiles are the seven percentiles mentioned. We re-phrase some sentences here to make it more clear. 85\% is a typo, it should be 84\%. }

\item	
		L163: Pfreundschuh uses an indicator function I (=1 or 0) in the CRPS, the authors
		here use y, can they explain the difference?

\textcolor{blue}{Reply: In the study by Pfreundschuh et al., 2018, CRPS is defined as using an indicator function ($I$), however for QRNN the integral is evaluated only by approximation. To calculate the CRPS, we use a piece-wise linear fit to the approximate posterior CDF obtain from the predicted quantiles. This approximation is further used to calculate CRPS. }

\item	
		L173: " The input data is all-sky brightness temperature" the simulated one, even for
		MWHS2, right?

\textcolor{blue}{Reply: Yes, even for MWHS-2 we use simulated all-sky brightness temperatures.}

\item	L301: "0.15 K" should be -0.15

\textcolor{blue}{Reply: The correction is made.}

\item	
		L453: "Among these four channels, 150 GHz has the highest peaking function around 4
		C2km (Chen and Bennartz, 2020)" Could you please clarify what you mean here, 150GHz
		is neither the highest nor the lowest peaking channel nor it peaks at 4km. Channel 89,
		118+/-1.1, 118+/-2.5, and 150 GHz peak at 0.1, 9.6, 2.9, 1km, respectively (according
		to Chen and Bennartz, 2020), this can also be seen in Lawrence et al. (2018) Fig. 1
		through the Jacobians of channels 6 and 7.

\textcolor{blue}{Reply: The reviewer is correct. It was wrongly mentioned that 150 GHz is the highest peaking channel, at 4\,km. We have corrected the text and it now reads as:	
``The channels, 150\,GHz and 118.75$\pm$2.5 peak between surface and 4\,km. These channels can only provide coverage to the humidity channels in the lower and mid troposphere. However, the 183\,GHz channels are sensitive to hydrometeor content up to 10\,km. The channel 118.75$\pm$1.1 peaks around 10\,km, but such information is only partly relevant for the higher peaking channels of 183\,GHz.'' }

\item	L460: "but such information would be not be completely orthogonal" duplicate "be"

\textcolor{blue}{Reply: The duplicate word is removed. }

\item	
		Table 1: NEDT are constructor specifications, the real noise is lower, see
		Fig 5 Guo, Y., J. Y. He, S. Y. Gu, and N. M. Lu, 2019: Calibration and validation of
		Feng Yun-3-D microwave humidity sounder II. IEEE Geoscience and Remote Sensing
		Letters, doi:10.1109/LGRS.2019.2957403.	Tab 5 Carminati, F., Atkinson, N., Candy, B., Lu, Q.: Insights into the Microwave Instruments Onboard the Feng-Yun 3D Satellite: Data Quality and Assimilation in the Met Office NWP System. Adv. Atmos. Sci. (2020). https://doi.org/10.1007/s00376-020-0010-1

\textcolor{red}{Reply:  }

\end{itemize}

		\textbf{Questions:}
		\newline
\begin{itemize}

\item	
		Is this method applicable to IR e.g. to an ATOVS system?

\textcolor{blue}{Reply:  Yes, the method could potentially be applied to IR. The functioning and the performance of the cloud correction approach is based on the differences in cloud signatures over different frequencies in the same field of view. For IR, infact, this feature is regularly used to flag out cloud contamination. Most cloud flagging schemes for IR are based on brightness temperature threshold.
}

\item 		
		The authors explain that it could benefit the all-sky assimilation systems indirectly for
		the analysis increment. Instead (or in addition) could it be used to model the variable
		observation error (when and by how much to be inflated)? This would be, in my view,
		the most valuable.

\textcolor{blue}{Reply: }

\item	Could the uncertainty use for weak constraint 4dvar?

\textcolor{blue}{Reply:}

\item	
		What is the resource cost of this method (is this fast enough to be used in 1-h regional
		nwp with 30min window)?

\textcolor{blue}{Reply:}

\end{itemize}

\end{document}

### 2021-02-10 Article/Review_1/response_reviewer_2.tex
started response to reviewer

\documentclass[11pt,a4paper,draft]{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{geometry}
\usepackage{xcolor}
%\usepackage{showframe} %This line can be used to clearly show the new margins

\newgeometry{vmargin={30mm}, hmargin={35mm,25mm}}

\begin{document}
\textbf{Response Reviewer 2}

\textbf{
	Interactive comment on ``Can machine learning
	correct microwave humidity radiances for the
	influence of clouds?'' by Inderpreet Kaur et al.}

\begin{itemize}

\item 			
			As I understand it, this study uses only simulated measurements (either with or without hydrometeors included), even for MWHS-2 for which actual measurements are available. This should be made clearer, especially given line 66, which states that no``background'' data is required for the method. I'd also like to see a bit more discussion 	about whether the results you present should be expected to hold for real data. An assumption that you are making is that your forward model can represent real clouds with enough fidelity that a model trained on simulated data will still work on real-world data. Can you point to any evidence to back up this assumption? Have you tried comparing the histograms of model-simulated Tbs with real-world MWHS-2 Tbs?

\textcolor{blue}{Reply: }

\item  	
			What is the computational cost of the QRNN method compared to simpler cloud-
			clearing filters? Could it feasibly be implemented into existing NWP models given
			current computational constraints?

\textcolor{blue}{Reply:}

\item  
			Lines 135-143: Why the large difference in number of cases simulated for ICI (220,000)
			vs. AWS (143,000), if they are both coming from the same population of CloudSat
			profiles? For the training dataset, you use about 75\% of total cases for MWHS-2,
			about 80\% of cases for ICI, and about 84\% of cases for AWS. Why this difference in
			proportions?

\textcolor{blue}{Reply: Yes, both ICI and AWS simulations come from same population of Cloudsat. For SMS, we had access to a smaller database, which was used for a earlier study. Due to difference in sizes of the available obseravtions, maximum possible observations were incorporated to allow  representation to each cloud event. }

\item  
			Line 340: ``With a test dataset of 70 000 samples, we cannot represent the far wings of the distribution accurately.'' Couldn't one apply this same reasoning to Figures 2,3, or
			8, which have density values below $10^{-4}$ included?

\textcolor{blue}{Reply: Yes, the same reasoning applies to Figures 2, 3 and 8 as well. We do not curtail the plot at $10^{-4}$ in these figures, so that it can be shown that most of the cases with density less than $10^{-4}$ correspond to low accuracy, due to their incomplete representation.}

\item 
			Figure 13: I wonder if there might be an easier, more concise way to evaluate whether
			the uncertainty intervals are properly calibrated. Namely, could you simply calculate
			how often the true value falls within the $\pm2\sigma$ uncertainty range, for each of the un-
			certainty bins ($0 - 3$K, $3 - 8$K, $8 +$ K) that you've included on the plot? If this percentage
			is significantly less than 95\%, it would suggests that your uncertainties are too small,
			while if it were closer to 100\% it would suggest your uncertainties are too large. Even
			if you don't get rid of Fig. 13, I think this would be useful information to include in the paper.

\textcolor{blue}{Reply:}

\item  
			Lines 498-499: ``. . . other underlying uncertainties not considered here.'' Whether here or elsewhere in the paper, I think you should talk a bit more about what these other uncertainties are (radiative transfer model errors should certainly be discussed), and what effects they might have on your results.

\textcolor{blue}{Reply:}

\end{itemize}

\textbf{Typos}
\begin{itemize}

\item Line 26: The phrase ``weather satellites are since some time equipped'' is confusing to
me. I suggest ``weather satellites have for some time been equipped. . .''

\textcolor{blue}{Reply: The sentence is re-written as per suggestion.}

\item Line 51: I believe you are missing the word ``on'' between ``predicated'' and ``Gaussian.''

\textcolor{blue}{Reply: The typo is corrected.}

\item Line 154: Should 85\% be changed to 84\%? That would be +2 sigma for a normal
distribution.

\textcolor{blue}{Reply: Yes, the predicted percentile should be 84\% instead of 85\%. The typo is corrected.}

\item Line 455:``. . . provide coverage to the humidity channels in, lower and mid troposphere''
This is confusing - get rid of the comma and add the word ``the'' instead?

\textcolor{blue}{Reply: The comma is removed and the word ``the'' is added.}

\item Line 494:	``QRNN predictions are weighted mean. . .'' I think this should say, ``QRNN
predictions are the weighted mean. . .''

\textcolor{blue}{Reply: The word ``the'' is added.}

\item Line 508: Missing ``the'' before ``same''

\textcolor{blue}{Reply: The word ``the'' is added.}

\end{itemize}

\end{document}

### 2021-02-10 Article/ici_submm_cloudcorr_v1.1.tex
started response to reviewer

--- 2021-01-25 Article/ici_submm_cloudcorr.tex
@@
 with strong limitations imposed by clouds. To be able to also sense humidity
-inside and below clouds, weather satellites are since some time equipped with
+inside and below clouds, weather satellites have for sometime been equipped with
 channels around 183\,GHz. Today such channels are part of several sensors, such
@@
 For NWP systems assimilating clear-sky observations, the effect of undetected clouds may be overcome by inflating the observational errors and diminishing the impact of observations.
-Furthermore, the mathematical assumptions of data assimilation (DA) are predicated Gaussian errors with no mean bias, and residual cloud impacts that cause a net bias are not easily handled by variational bias correction.
+Furthermore, the mathematical assumptions of data assimilation (DA) are predicated on Gaussian errors with no mean bias, and residual cloud impacts that cause a net bias are not easily handled by variational bias correction.
 One solution is to apply a very strict filtering, but this increases the rejection of clear-sky values, i.e.\ an important loss of useful data.
@@
 
-For this application, the predicted percentiles are chosen to be
-$0.2\,\%, 3\,\%, 16\,\%, 50\,\%, 85\,\%, 97\,\%$ and $99.8\,\%$. For a Gaussian
+For this application, the quantile fractions $\tau$ are chosen as 
+$0.2\,\%, 3\,\%, 16\,\%, 50\,\%, 84\,\%, 97\,\%$ and $99.8\,\%$ percentiles. For a Gaussian
 distribution with mean $\mu$ and standard deviation $\sigma$, these quantiles
@@
 %
-for all selected quantile fractions $\tau$, where $y_\tau$ is the predicted
+for all selected quantile fractions, where $y_\tau$ is the predicted
 quantile and $y$ the reference value from the training or test data. The
@@
 
-For channel 11, the bias after correction is $-$0.12\,K in comparison to 0.15\,K in the all-sky simulations.
+For channel 11, the bias after correction is $-$0.12\,K in comparison to $-$0.15\,K in the all-sky simulations.
 The decrease in bias is not significantly high, but the strong negative tail  diminishes after correction, indicating removal of cases with large deviations.
@@
 The partial performance of QRNN is due to incomplete complementary information to 183\,GHz channels.
-The weighting functions of window channels 89 and 150\,GHz, and the two 118\,GHz channels peak in the lower troposphere.
-Among these four channels, 150\,GHz has the highest peaking function around 4\,km \citep{chen2020mwhs}.
-These channels can only provide coverage to the humidity channels in, lower and mid troposphere; nonetheless, the 183\,GHz channels are sensitive to hydrometeor content up to 10\,km.
+The weighting functions of window channels 89 and 150\,GHz, and 118$\pm$2.5\,GHz channels peak in the lower troposphere.
+The channels, 150\,GHz and 118.75$\pm$2.5 peak between surface and 4\,km.
+These channels can only provide coverage to the humidity channels in the lower and mid troposphere.
+However, the 183\,GHz channels are sensitive to hydrometeor content up to 10\,km.
+The channel 118.75$\pm$1.1 peaks around 10\,km, but such information is only partly relevant for the higher peaking channels of 183\,GHz.
 Due to missing complementary information from other channels in the upper troposphere, QRNN fails at predicting these cases accurately.
@@
 Without additional information from other channels we cannot expect QRNN to perform better.
-Among the other available channels, the overlapping weighting functions of 183\,GHz can provide auxiliary information to train QRNN, but such information would be not be completely orthogonal or statistically uncorrelated.
+Among the other available channels, the overlapping weighting functions of 183\,GHz can provide auxiliary information to train QRNN, but such information would not be completely orthogonal or statistically uncorrelated.
 Results show that these channels indeed help in improving the training, yet non-orthogonality introduces highly correlated observational errors.
@@
 This is observed to be true with QRNN-single, but QRNN-all fails at preserving the noise stochasticity.
-In the absence of hydrometeor impact, all 183\,GHz channels provide same information to the learning model, introducing redundancy.
+In the absence of hydrometeor impact, all 183\,GHz channels provide the same information to the learning model, introducing redundancy.
 Redundant patterns in machine learning models often have undesirable effect on the predictive performance.
@@
 This is a consequence of predictions for cases which lack cloud impact.
-QRNN predictions are weighted mean of measurements between channels.
+QRNN predictions are the weighted mean of measurements between channels.
 In the absence of clouds, also the sub-mm channels provide humidity information that is incorporated in the 183 GHz NFCS estimate and some compensation of noise can be achieved.
@@
 Poorly calibrated predictions are a consequence of outliers which are not well represented in the training dataset.
-The a priori distribution of the training dataset is dominated by clear-sky cases, however, the cloudy cases which occur infrequently or lack independent complementary information cannot be represented by same a priori distribution.
+The a priori distribution of the training dataset is dominated by clear-sky cases, however, the cloudy cases which occur infrequently or lack independent complementary information cannot be represented by the same a priori distribution.
 The distribution of rare cases can be improved by increasing the training dataset size, but lack of complementary information can only be balanced by including additional training inputs, e.g.

### 2021-02-11 Article/Review_1/response_reviewer_1.tex
working on replies

@@
 
-\textcolor{blue}{Reply: We agree that the hydrometeor size is an important aspect, but when it comes to an overview of the contamination at 183\,GHz, precipitating clouds and clouds with large optical thickness have the strongest effect.
-Though a dense cloud could be composed of hydrometeors of different shapes and size.
+\textcolor{blue}{Reply: We agree that the hydrometeor size is an important aspect, but when it comes to an overview of the cloud contamination at 183\,GHz, precipitating clouds and clouds with large optical thickness have the strongest effect, and a dense cloud could be composed of hydrometeors of different shapes and size.
 }
@@
 \textcolor{blue}{Reply: Yes, the demonstration of the entire concept is based on simulations.
-We do not try with the real MWHS-2 observations as for the training process we would still require the clear-sky simulations.}
+We do not try with the real MWHS-2 observations as the validation of the training process could only be performed against clear-sy simulations.
+To stress on the fact that only background MWHS-2 observations are used, we have added the following text to Sect.
+2.1.1:
+``\textit{For the demonstation of the study, MWHS-2 background observations or simulations are used.
+Actual measurements are not taken into account.
+The requisite data was obtained from ECMWF.
+More details are described in Sect.2.1.1}''}
 
@@
 		L137 "Simulations for all three sensors are noise free, so to incorporate the measurement uncertainties, whenever needed, Gaussian noise is added according to the chan-
-		nel NEDT (Table 1 ? Table 3)." Are the errors arising from the radiative transfer calculation accounted for?
+		nel NEDT (Table 1 - Table 3)." Are the errors arising from the radiative transfer calculation accounted for?
 
@@
 \textcolor{blue}{Reply:  Yes, the method could potentially be applied to IR.
-The functioning and the performance of the cloud correction approach is based on the differences in cloud signatures over different frequencies in the same field of view.
+The operation and  performance of the cloud correction approach is based on the fact that different frequencies have varying sensitivity to cloud signatures in the same field of view.
 For IR, infact, this feature is regularly used to flag out cloud contamination.
-Most cloud flagging schemes for IR are based on brightness temperature threshold.
+Most cloud flagging schemes for IR are based on brightness temperature thresholds.
 }
@@
 
-\textcolor{blue}{Reply:}
+\textcolor{blue}{Reply:  Yes, it would be feasible to implement the scheme into existing NWP models.
+In this study, QRNN was not optimized to get the maximum computational performance.
+However, with the modern computing architectures a much faster computation can be expected.
+}
 

### 2021-02-11 Article/Review_1/response_reviewer_2.tex
working on replies

@@
 
-\textcolor{blue}{Reply: }
+\textcolor{blue}{Reply: We agree with the reviewer, the line 66, can be confusing. We have rearranged the text to give clarity.
+Regarding the the discussion about simulations holding well for the real-data, we have added a new subsection () under Discussion.
+Also, MWHS-2 simulations used in the study are the background radiance simulated by ECMWF for their assimilation systems.
+Their observational error model is already described in literature e.g.
+Lawrence et al., 2015.
+}
 
@@
 
-\textcolor{blue}{Reply:}
+\textcolor{blue}{Reply: \textcolor{red}{add time} Yes, it would be feasible to implement the scheme into existing NWP models.
+It should be noted QRNN was not optimized to get the maximum computational performance.
+However, with the modern computing architectures a much faster computation can be expected.
+}
 
@@
 For SMS, we had access to a smaller database, which was used for a earlier study.
-Due to difference in sizes of the available obseravtions, maximum possible observations were incorporated to allow  representation to each cloud event.
-}
+Due to difference in sizes of the available observations, maximum possible observations were incorporated to allow  representation to each cloud event.
+Even with differences in the database sizes, the results show that the predicted quantiles are well calibrated for all three sensors.
+With a larger database, one could expect similar or even better performance.}
 
@@
 
-\textcolor{blue}{Reply: Yes, the same reasoning applies to Figures 2, 3 and 8 as well.
-We do not curtail the plot at $10^{-4}$ in these figures, so that it can be shown that most of the cases with density less than $10^{-4}$ correspond to low accuracy, due to their incomplete representation.}
+\textcolor{blue}{Reply: Yes one could apply the same reasoning to the Figures 2, 3, or 8, but we prefer to show the complete distribution to emphasize that the cases with large errors occur infrequently.
+\textcolor{red}{Shall we show the complete dist?}}
 
@@
 			the uncertainty intervals are properly calibrated. Namely, could you simply calculate
-			how often the true value falls within the $\pm2\sigma$ uncertainty range, for each of the un-
-			certainty bins ($0 - 3$K, $3 - 8$K, $8 +$ K) that you've included on the plot? If this percentage
-			is significantly less than 95\%, it would suggests that your uncertainties are too small,
-			while if it were closer to 100\% it would suggest your uncertainties are too large. Even
-			if you don't get rid of Fig. 13, I think this would be useful information to include in the paper.
+			how often the true value falls within the $\pm2\sigma$ uncertainty range, for each of the uncertainty bins ($0 - 3$K, $3 - 8$K, $8 +$ K) that you've included on the plot?
+If this percentage is significantly less than 95\%, it would suggests that your uncertainties are too small, while if it were closer to 100\% it would suggest your uncertainties are too large.
+Even if you don't get rid of Fig.
+13, I think this would be useful information to include in the paper.
 
-\textcolor{blue}{Reply:}
+\textcolor{blue}{Reply: As per suggestion of the reviewer, we have included the information highlighting how well calibrated the uncertainties are.
+We add this information in Fig.
+13.
+We provide the occurence percentage of true value for each uncertainty bin.
+We would also like to point out that Fig.6 and Fig.10 already show the calibration of uncertainty intervals, but this additional information reinforces the results further.}
 

### 2021-02-11 Article/ici_submm_cloudcorr_v1.1.tex
working on replies

@@
 (i.e.\ the radiance that would have been measured in absence of noise and
-hydrometeors). This is done for each channel separately, only using
-measurements (no ``background'' data involved). Not only a best estimate is
-provided, but also a case-specific uncertainty. This information could be used as a pure filter, by rejecting data where the correction exceeds some threshold value. However, even
-better is to replace the original value with the predicted NFCS value when
-forming the clear-sky dataset. We denote this approach as cloud correction. It
-is shown below that a basically bias free cloud correction can be obtained.
-This feature also removes the need for defining threshold values, as long as the retrieval or
-assimilation system can incorporate the uncertainty of the corrected value. As
-also will be shown, the uncertainty for originally clear-sky data is determined
+hydrometeors).
+Not only a best estimate is provided, but also a case-specific uncertainty.
+This information could be used as a pure filter, by rejecting data where the correction exceeds some threshold value.
+However, even better is to replace the original value with the predicted NFCS value when forming the clear-sky dataset.
+We denote this approach as cloud correction.
+This is done for each channel separately and by only using the measurements, although the scheme is demonstrated in the study by using simulated observations.
+It is shown below that a basically bias free cloud correction can be obtained.
+This feature also removes the need for defining threshold values, as long as the retrieval or assimilation system can incorporate the uncertainty of the corrected value.
+As also will be shown, the uncertainty for originally clear-sky data is determined
 by noise, but the uncertainty increases with magnitude of correction.
@@
 Observations from MWHS-2 are routinely assimilated in all-sky conditions at the European Centre for Medium-Range Weather Forecasts (ECMWF) with demonstrable positive impact on forecast performance \citep{duncan2020MWHS}.
-The channels relevant to this study are described in Table~\ref{tab:specifications_MWHS2}.
-
-For this study, MWHS-2 simulations were sourced from the operational ECMWF assimilation system.
+
+For the demonstation of the study, MWHS-2 background observations or simulations are used.
+Actual measurements are not taken into account.
+The requisite data was obtained from ECMWF.
+More details are described in Sect.~\ref{simulations}.
 
@@
 %
+\label{simulations}
 MWHS-2 simulated radiances during the period June--July 2020 are sourced from ECMWF.
@@
 	\includegraphics[width=\textwidth]{Figures/fig13.pdf}	
-	\caption{Distribution of errors binned according to their uncertainty. Results are from QRNN-single for channels I1V, I2V and I3V.}
+	\caption{Distribution of errors binned according to their uncertainty.
+The occurrence of true value in each uncertainty interval bin is given in the parentheses.
+Results are from QRNN-single for channels I1V, I2V and I3V.}
 	\label{fig:error_distribution_uncertainty_bins}	
@@
 In spite of individual variations in the error distributions for each channel, predictions and their corresponding uncertainties follow the same relationship.
-Similar results are also obtained with SMS (not shown).
+We also evaluated if the uncertainty intervals are properly calibrated  Similar results are also obtained with SMS (not shown).
 
@@
 \label{discussions}
+
+\subsection{Cloud impact in simulations}
+
+\todo{As mentioned in Sect.~{}, the MWHS-2 simulations are the background radiances simulated by ECMWF for their assimilation systems. The 
+For ICI and SMS, the incorporate cloud variability by randomly selecting between three habits.
+But with only one particle size distribution (PSD), the true hydrometeor variability will be underestimated.
+But the all-sky DA systems, still assume a single PSD and habit combination.
+This can cause some model uncertainty and the mapping of cloud information from sub-mm channels to 183\,GHz shall not be perfect.
+Nonetheless, the advantge of the our scheme is that it allows to incorporate multiple PSD and habit variations and adapt to the local conditions.}
 

### 2021-02-19 Article/Review_1/response_reviewer_1.tex
response to reviewer v1

@@
 \usepackage{xcolor}
+\usepackage{natbib}
 %\usepackage{showframe} %This line can be used to clearly show the new margins
 
-\newgeometry{vmargin={30mm}, hmargin={35mm,25mm}}
+\newgeometry{vmargin={30mm}, hmargin={25mm,25mm}} 
+\setlength{\topskip}{0mm}
 
 \begin{document}
-\textbf{Response Reviewer 1}
+	\title{\textbf{Response to Reviewer 1}}
+	\date{}
+	\maketitle
 
-\textbf{	Interactive comment on ``Can machine learning
-	correct microwave humidity radiances for the
-	influence of clouds?'' by Inderpreet Kaur et al.}
+The authors would like to thank the reviewer for his/her careful review and constructive comments, which we believe will help improve the content of the manuscript.
+Below, under each bullet point, we provide a point by point response to each comment/question.
+The author responses are given in blue, and textual changes are italicised.
+
+\section*{General comments}
 
@@
 
-\item 	precipitation and most dense clouds" I think the hydrometeor size is an important
+\item 	``precipitation and most dense clouds'' I think the hydrometeor size is an important.\\
 
-\textcolor{blue}{Reply: We agree that the hydrometeor size is an important aspect, but when it comes to an overview of the cloud contamination at 183\,GHz, precipitating clouds and clouds with large optical thickness have the strongest effect, and a dense cloud could be composed of hydrometeors of different shapes and size.
-}
+\textcolor{blue}{Reply: We agree that the hydrometeor size is an important aspect, but when it comes to an overview of the cloud contamination at 183\,GHz, precipitating clouds and clouds with large optical thickness have the strongest effect, and a dense cloud could be composed of hydrometeors of different shapes and sizes.
+}\\
 
 \item	L66: ``only using measurements (no background data involved)'' My understanding is
-		that the method is in theory model-free, but for the demonstration in this study, sim-
-		ulations (e.g. background simulated at MWHS2 frequency) are used. Am I correct?
+		that the method is in theory model-free, but for the demonstration in this study, simulations (e.g. background simulated at MWHS2 frequency) are used. Am I correct?
 		Maybe this should be stressed here. Why not try with real MWHS2 observation for the
-		all sky dataset?
+		all sky dataset?\\
 
@@
 To stress on the fact that only background MWHS-2 observations are used, we have added the following text to Sect.
-2.1.1:
-``\textit{For the demonstation of the study, MWHS-2 background observations or simulations are used.
+2.1.1:\\
+Pg 4, line 104:
+``\textit{For the demonstation of the study, MWHS-2 background or simulations are used.
 Actual measurements are not taken into account.
 The requisite data was obtained from ECMWF.
-More details are described in Sect.2.1.1}''}
+More details are described in Sect.2.1.1}.''} \\
 
 \item
-		L137 "Simulations for all three sensors are noise free, so to incorporate the measurement uncertainties, whenever needed, Gaussian noise is added according to the chan-
-		nel NEDT (Table 1 - Table 3)." Are the errors arising from the radiative transfer calculation accounted for?
+		L137 "Simulations for all three sensors are noise free, so to incorporate the measurement uncertainties, whenever needed, Gaussian noise is added according to the channel NEDT (Table 1 - Table 3)." Are the errors arising from the radiative transfer calculation accounted for?\\
 
-\textcolor{red}{Reply: }
+\textcolor{blue}{Reply: The most important errors arising from radiative transfer calculations, are related to representing the cloud microphysics.
+In this study, for ICI and SMS, we consider only one particle size distribution (PSD) and habit and this could underestimate the true cloud variability.
+Underestimation of scattering at higher frequencies can lead to some imperfections in mapping the cloud information from sub-mm and 183\,GHz.
+Other factors affecting the accuracy of simulations, but not considered due to brevity include neglected antenna pattern and limitations associated with input data, both Cloudsat and ERAInterim.
+For example, the simulations could have tendency to be biased towards the Cloudsat geographical sampling.
+The actual background departures and the corresponding bias correction shall only be revealed when data from ICI is available in future.\\
+We have added a short description these radiative transfer errors that could affect the simulations in Sect. 2.2.  } \\
 
@@
 		amongst the 7 selected (from 0.2 to 99.8\%)? Also, 16, 50 and 85\% are not symmetric
-		(rounding?)
+		(rounding?)\\
 
-\textcolor{blue}{Reply: Yes, the selected quantiles are the seven percentiles mentioned. We re-phrase some sentences here to make it more clear. 85\% is a typo, it should be 84\%. }
+\textcolor{blue}{Reply: Yes, the selected quantiles are the seven percentiles mentioned.
+We re-phrase some sentences here to make it more clear.
+85\% is a typo, it should be 84\%.
+It has been corrected.}\\
 
@@
 		L163: Pfreundschuh uses an indicator function I (=1 or 0) in the CRPS, the authors
-		here use y, can they explain the difference?
+		here use y, can they explain the difference?\\
 
-\textcolor{blue}{Reply: In the study by Pfreundschuh et al., 2018, CRPS is defined as using an indicator function ($I$), however for QRNN the integral is evaluated only by approximation.
+\textcolor{blue}{Reply: In the study by \citet{pfreundschuh:aneur:18}, CRPS is defined as using an indicator function ($I$), however for QRNN the integral is evaluated only by approximation.
 To calculate the CRPS, we use a piece-wise linear fit to the approximate posterior CDF obtain from the predicted quantiles.
-This approximation is further used to calculate CRPS.
-}
+This approximation is further used to calculate CRPS.}\\
 
@@
 		L173: " The input data is all-sky brightness temperature" the simulated one, even for
-		MWHS2, right?
+		MWHS2, right? \\
 
-\textcolor{blue}{Reply: Yes, even for MWHS-2 we use simulated all-sky brightness temperatures.}
+\textcolor{blue}{Reply: Yes, even for MWHS-2 we use simulated all-sky brightness temperatures.}\\
 
-\item	L301: "0.15 K" should be -0.15
+\item	L301: "0.15 K" should be -0.15 \\
 
-\textcolor{blue}{Reply: The correction is made.}
+\textcolor{blue}{Reply: The correction is made.} \\
 
@@
 		to Chen and Bennartz, 2020), this can also be seen in Lawrence et al. (2018) Fig. 1
-		through the Jacobians of channels 6 and 7.
+		through the Jacobians of channels 6 and 7.\\
 
-\textcolor{blue}{Reply: The reviewer is correct. It was wrongly mentioned that 150 GHz is the highest peaking channel, at 4\,km. We have corrected the text and it now reads as:	
-``The channels, 150\,GHz and 118.75$\pm$2.5 peak between surface and 4\,km.
+\textcolor{blue}{Reply: The reviewer is correct. It was wrongly mentioned that 150 GHz is the highest peaking channel, at 4\,km. We have corrected the text and it now reads as:	\\
+Pg 25, line 465:	
+``\textit{The channels, 150\,GHz and 118.75$\pm$2.5 peak between surface and 4\,km.
 These channels can only provide coverage to the humidity channels in the lower and mid troposphere.
 However, the 183\,GHz channels are sensitive to hydrometeor content up to 10\,km.
-The channel 118.75$\pm$1.1 peaks around 10\,km, but such information is only partly relevant for the higher peaking channels of 183\,GHz.'' }
+The channel 118.75$\pm$1.1 peaks around 10\,km, but such information is only partly relevant for the higher peaking channels of 183\,GHz.}'' }\\
 
@@
 
-\textcolor{blue}{Reply: The duplicate word is removed. }
+\textcolor{blue}{Reply: The duplicate word is removed. }\\
 
@@
 		Fig 5 Guo, Y., J. Y. He, S. Y. Gu, and N. M. Lu, 2019: Calibration and validation of
-		Feng Yun-3-D microwave humidity sounder II. IEEE Geoscience and Remote Sensing
-		Letters, doi:10.1109/LGRS.2019.2957403.	Tab 5 Carminati, F., Atkinson, N., Candy, B., Lu, Q.: Insights into the Microwave Instruments Onboard the Feng-Yun 3D Satellite: Data Quality and Assimilation in the Met Office NWP System.
+		Feng Yun-3-D microwave humidity sounder II. \\
+		IEEE Geoscience and Remote Sensing
+		Letters, doi:10.1109/LGRS.2019.2957403.
+		Tab 5 Carminati, F., Atkinson, N., Candy, B., Lu, Q.: Insights into the Microwave Instruments Onboard the Feng-Yun 3D Satellite: Data Quality and Assimilation in the Met Office NWP System.
 Adv.
@@
 (2020).
-https://doi.org/10.1007/s00376-020-0010-1
+https://doi.org/10.1007/s00376-020-0010-1 \\
 
-\textcolor{red}{Reply:  }
+\textcolor{blue}{Reply: The reviewer rightly mentions that the real noise is lower, however we add the sensor noise according to the constructor specifications.
+This can be viewed as a conservative estimate of the sensor noise to include other sources of error not accounted for in NEDT.
+For example in study \citet{Carminati-fy3d-2020} the authors describe radiation leak affecting the higher frequency channels.}
 
@@
 
-		\textbf{Questions:}
-		\newline
+\section*{Questions}
 \begin{itemize}
@@
 \item	
-		Is this method applicable to IR e.g. to an ATOVS system?
+		Is this method applicable to IR e.g. to an ATOVS system?\\
 
@@
 The operation and  performance of the cloud correction approach is based on the fact that different frequencies have varying sensitivity to cloud signatures in the same field of view.
-For IR, infact, this feature is regularly used to flag out cloud contamination.
+For IR, infact this feature is regularly used to flag out cloud contamination.
 Most cloud flagging schemes for IR are based on brightness temperature thresholds.
-}
+}\\
 
@@
 		observation error (when and by how much to be inflated)? This would be, in my view,
-		the most valuable.
+		the most valuable.	\\
 
-\textcolor{blue}{Reply: }
+\textcolor{blue}{Reply: The reviewer has a very good point.
+At ECMWF, the observational errors for MHS and MWHS-2 are defined as quadratic functions of symmetric cloud indicator \citep{geer2015scatteringindex}.
+The observational errors are higher in regions for cloud and vice-versa.
+Thus it could be potentially feasible to use the QRNN identified cloud impact to formulate the observational errors.
+This could probably be the best use of the QRNN technique for all-sky.
+Of course using QRNN to develop a full observational model, would require to characterize the performance of the scheme over upper latitudes, land and ocean.}\\
 
-\item	Could the uncertainty use for weak constraint 4dvar?
+\item	Could the uncertainty use for weak constraint 4dvar?\\
 
-\textcolor{blue}{Reply:}
+\textcolor{blue}{Reply: Although, the uncertainties obtained from QRNN do not have a direct application to weak constraint 4dvar, but they could still be considered as a diagnostic to help evaluate the weak constraint in the troposphere.
+For example, undiagnosed cirrus contamination in the upper troposphere might be associated with apparent model biases that are actually caused by systematic forward model errors.
+}\\
 
@@
 		What is the resource cost of this method (is this fast enough to be used in 1-h regional
-		nwp with 30min window)?
+		nwp with 30min window)?\\
 
@@
 In this study, QRNN was not optimized to get the maximum computational performance.
-However, with the modern computing architectures a much faster computation can be expected.
-}
+For each MWHS-2 channel, it took around 30 minutes to train the net on a  x86\_64, 8 CPU machine.
+However, with the modern computing architectures and parallel processing, a much faster computation can be expected.
+}\\
 
@@
 
+ \bibliographystyle{copernicus}
+ \bibliography{references}
+
 \end{document}

### 2021-02-19 Article/Review_1/response_reviewer_2.tex
response to reviewer v1

--- 2021-02-10 Article/Review_1/response_reviewer_2.tex
@@
-\documentclass[11pt,a4paper,draft]{article}
+\documentclass[11pt,a4paper]{article}
 \usepackage[latin1]{inputenc}
@@
 \usepackage{xcolor}
+
 %\usepackage{showframe} %This line can be used to clearly show the new margins
 
-\newgeometry{vmargin={30mm}, hmargin={35mm,25mm}}
+\newgeometry{vmargin={30mm}, hmargin={25mm,25mm}} 
+\setlength{\topskip}{0mm}
 
 \begin{document}
-\textbf{Response Reviewer 2}
+\title{\textbf{Response to Reviewer 2}}
+\date{}
+\maketitle
 
-\textbf{
-	Interactive comment on ``Can machine learning
-	correct microwave humidity radiances for the
-	influence of clouds?'' by Inderpreet Kaur et al.}
+The authors would like to thank the reviewer for his/her careful review and constructive comments, which we believe will help improve the content of the manuscript.
+Below, under each bullet point, we provide a point by point response to each comment/question.
+The author responses are given in blue, and textual changes are italicised.
 
+\section*{General Comments}
 \begin{itemize}
@@
 Can you point to any evidence to back up this assumption?
-Have you tried comparing the histograms of model-simulated Tbs with real-world MWHS-2 Tbs?
+Have you tried comparing the histograms of model-simulated Tbs with real-world MWHS-2 Tbs?\\
 
-\textcolor{blue}{Reply: }
+\textcolor{blue}{Reply: We agree with the reviewer, the line 66, can be confusing. We have re-written the sentence to:\\
+Pg 3, line 68:	``\textit{This is done for each channel separately and by only using the measurements, although the scheme is demonstrated in the study by using simulated observations.}''\\\\		
+Regarding the discussion about simulations holding well for the real-data, we agree with the reviewer that our assumption is a strong one and requires some evidence.
+For MWHS-2, we have added a new figure (Pg 6, Fig.
+1, also shown below) comparing the histograms of background and bias corrected observations for one of the lower peaking channels of 183 GHz channel.
+The main deviations in the distributions arise from the hydrometeor scattering.
+With limited scope of particle size and shape variation in current NWP microphysical schemes, the true cloud variability cannot be  described accurately, and a bias correction is necessary to be closer to the reality.
+Also, ECMWF has real time monitoring of many satellite sensors including FY-3D MWHS-2, thus it is possible to assess how well the system (and RTTOV-SCATT) is performing.
+\newline
+For ICI and SMS, though a qualitative assessment of the simulations is not possible, we expect underestimation of the cloud variability owing to only single PSD and habit assumption.
+However, it is important to consider that QRNN can easily adapt to changes in brightness temperatures introduced by PSD and habit variation.\\
+We have added this discussion in the revised manuscript in Sect 2.2. }\\
+\begin{figure}
+	\centering
+\includegraphics[width = 80mm]{fig00.pdf}
+\caption{Probability distribution functions (PDFs) of simulated and observed brightness temperatures for MWHS-2 channel 14.
+The data covers latitude range $60^{\circ}$\,S to $60^{\circ}$\,N, and satellite zenith angle less than $7.5^{\circ}$.}
+\end{figure}
 
@@
 			clearing filters? Could it feasibly be implemented into existing NWP models given
-			current computational constraints?
+			current computational constraints?\\
 
-\textcolor{blue}{Reply:}
+\textcolor{blue}{Reply: Yes, it would be feasible to implement the scheme into existing NWP models.
+In this study, QRNN was not optimized to get the maximum computational performance.
+For each MWHS-2 channel, it took around 30 minutes to train the net on a  x86\_64, 8 CPU machine.
+For ICI and SMS, with smaller training dataset, the time was lower.
+However, with the modern computing architectures and parallel processing, a much faster computation can be expected.
+}\\
 
 \item  
-			Lines 135-143: Why the large difference in number of cases simulated for ICI (220,000)
-			vs. AWS (143,000), if they are both coming from the same population of CloudSat
+			Lines 135-143: Why the large difference in number of cases simulated for ICI (220\,000)
+			vs. SMS (143\,000), if they are both coming from the same population of CloudSat
 			profiles? For the training dataset, you use about 75\% of total cases for MWHS-2,
-			about 80\% of cases for ICI, and about 84\% of cases for AWS. Why this difference in
-			proportions?
+			about 80\% of cases for ICI, and about 84\% of cases for SMS. Why this difference in
+			proportions?\\
 
-\textcolor{blue}{Reply: Yes, both ICI and AWS simulations come from same population of Cloudsat.
+\textcolor{blue}{Reply: Yes, both ICI and SMS simulations come from same population of Cloudsat.
 For SMS, we had access to a smaller database, which was used for a earlier study.
-Due to difference in sizes of the available obseravtions, maximum possible observations were incorporated to allow  representation to each cloud event.
-}
+Due to difference in sizes of the available observations, maximum possible observations were incorporated in the training data to allow cloud variability.
+Even with differences in the database sizes, the results show that the predicted quantiles are well calibrated for all three sensors.
+With a larger database, one could expect similar or even better performance.}\\
 
@@
 			Line 340: ``With a test dataset of 70 000 samples, we cannot represent the far wings of the distribution accurately.'' Couldn't one apply this same reasoning to Figures 2,3, or
-			8, which have density values below $10^{-4}$ included?
+			8, which have density values below $10^{-4}$ included?\\
 
-\textcolor{blue}{Reply: Yes, the same reasoning applies to Figures 2, 3 and 8 as well.
-We do not curtail the plot at $10^{-4}$ in these figures, so that it can be shown that most of the cases with density less than $10^{-4}$ correspond to low accuracy, due to their incomplete representation.}
+\textcolor{blue}{Reply: Yes one could apply the same reasoning to the Figures 2, 3, or 8, but we prefer to show the complete distribution to emphasize that the cases with large errors occur infrequently.}\\
 
@@
 			the uncertainty intervals are properly calibrated. Namely, could you simply calculate
-			how often the true value falls within the $\pm2\sigma$ uncertainty range, for each of the un-
-			certainty bins ($0 - 3$K, $3 - 8$K, $8 +$ K) that you've included on the plot? If this percentage
-			is significantly less than 95\%, it would suggests that your uncertainties are too small,
-			while if it were closer to 100\% it would suggest your uncertainties are too large. Even
-			if you don't get rid of Fig. 13, I think this would be useful information to include in the paper.
+			how often the true value falls within the $\pm2\sigma$ uncertainty range, for each of the uncertainty bins ($0 - 3$K, $3 - 8$K, $8 +$ K) that you've included on the plot?
+If this percentage is significantly less than 95\%, it would suggests that your uncertainties are too small, while if it were closer to 100\% it would suggest your uncertainties are too large.
+Even if you don't get rid of Fig.
+13, I think this would be useful information to include in the paper.\\
 
-\textcolor{blue}{Reply:}
-
+\textcolor{blue}{Reply: As per suggestion of the reviewer, we have included the information highlighting how well calibrated the uncertainties are.
+We provide the occurence percentage of true value for each uncertainty bin and add this information in Fig.
+13 (also shown above).
+For each bin considered, the true value falls in the range almost 94\% of the time, indicating that the uncertainties are well calibrated.
+Only for channel I3V and the outermost bin, occcurence percentage is 88\%.
+\\
+These results are in line with Fig.7 and Fig.11, which also indicate that the uncertainty intervals are well calibrated.} \\
+\begin{figure}
+	\centering
+	\includegraphics[width = 190mm]{fig13.pdf}
+	\caption{Distribution of errors binned according to their uncertainty.
+The occurrence of true value in each uncertainty interval bin is given in the parentheses.
+Results are from QRNN-single for channels I1V, I2V and I3V.}
+\end{figure}
 \item  
@@
 .
-other underlying uncertainties not considered here.'' Whether here or elsewhere in the paper, I think you should talk a bit more about what these other uncertainties are (radiative transfer model errors should certainly be discussed), and what effects they might have on your results.
+other underlying uncertainties not considered here.'' Whether here or elsewhere in the paper, I think you should talk a bit more about what these other uncertainties are (radiative transfer model errors should certainly be discussed), and what effects they might have on your results.\\
 
-\textcolor{blue}{Reply:}
+\textcolor{blue}{Reply: Among the errors which affect the radiative transfer calculations are underestimation of cloud variability due to limited particle size distribution (PSD) and habit variation.
+Other factors include neglected antenna pattern and the limitations associated with input data, both Cloudsat and ERAInterim.
+For example, the simulations could have tendency to be biased towards the Cloudsat geographical sampling.
+All these issues can contribute to mapping errors between 183\,GHz  and higher frequency channels.
+However, it is possible improve the cloud representation by incorporating PSD and habit variation, and QRNN based cloud correction can easily adapt to changes in brightness temperatures introduced by the local variability.
+This is not the case with all-sky data assimilation systems, which assume only single PSD and habit combination, and shall continue to do so in coming years.\\
+We have edited Sect 2.2 and Conclusions to describe these different errors and their implications.  }
 
@@
 
-\textbf{Typos}
+\section*{Typos}
 \begin{itemize}

### 2021-02-19 Article/ici_submm_cloudcorr_v1.1.tex
response to reviewer v1

--- 2021-02-10 Article/ici_submm_cloudcorr_v1.1.tex
@@
 Observations from MWHS-2 are routinely assimilated in all-sky conditions at the European Centre for Medium-Range Weather Forecasts (ECMWF) with demonstrable positive impact on forecast performance \citep{duncan2020MWHS}.
-The channels relevant to this study are described in Table~\ref{tab:specifications_MWHS2}.
-
-For this study, MWHS-2 simulations were sourced from the operational ECMWF assimilation system.
+
+For the demonstration of the study, MWHS-2 background observations or simulations are used.
+Actual measurements are not taken into account.
+The requisite data was obtained from ECMWF.
+More details are described in Sect.~\ref{simulations}.
 
@@
 %
+\begin{figure}[t]
+	\centering
+	\includegraphics[width = 70mm]{Figures/fig00.pdf} 
+	\caption{Probability distribution functions (PDFs) of simulated and observed brightness temperatures for MWHS-2 channel 14.
+The data covers latitude range $60^{\degree}$\,S to $60^{\degree}$\,N, and satellite zenith angle less than $7.5^{\degree}$.}
+	\label{fig:distribution_OB_mwhs14}	
+\end{figure}
+\label{simulations}
 MWHS-2 simulated radiances during the period June--July 2020 are sourced from ECMWF.
@@
 With this filter, we have approximately 290\,000 cases.
+Figure~\ref{fig:distribution_OB_mwhs14} shows the histogram of background and bias corrected observations for MWHS-2 channel 14.
+The part of the distribution matching clear-sky conditions shows a good agreement between the background and the observations.
+The main deviations in the distributions arise from the hydrometeor scattering.
+With limited scope of particle size and shape variation in current NWP microphysical schemes, the true cloud variability cannot be  described accurately, and a bias correction is necessary to be closer to reality.
 
@@
 Simulations for all three sensors are noise free, so to incorporate the measurement uncertainties, whenever needed, Gaussian noise is added according to the channel NE$\Delta$T (Table~\ref{tab:specifications_MWHS2} -- Table~\ref{tab:specifications_SMS}).
+
+For ICI and SMS, the cloud variability  is incorporated by randomly selecting between three habits and one particle size distribution (PSD) (see Appendix~\ref{appendix:ARTS_setup}).
+But with only one PSD, the true hydrometeor variability will be underestimated.
+Underestimation of scattering at higher frequencies can lead to some imperfections in mapping the cloud information from sub-mm and 183\,GHz.
+Other factors affecting the accuracy of simulations, but not considered due to brevity, include neglected antenna pattern and limitations associated with input data, both Cloudsat and ERAInterim.
+For example, the simulations could have tendency to be biased towards the Cloudsat geographical sampling.
+The actual background departures and the corresponding bias correction shall only be revealed when data from ICI is available in future.
 
@@
 Cases with accurate predictions yet high uncertainty are also present.
-In spite of individual variations in the error distributions for each channel, predictions and their corresponding uncertainties follow the same relationship.
+For each channel and bin, but last bin for I3V,  the occurrence of true value inside all three uncertainty bins is almost 94\%, indicating that uncertainties are well calibrated and are not concentrated in a narrow interval.
+Only for I3V, the uncertainties are slightly smaller in the last bin.
+In spite of individual variations in the error distributions for each channel, the predictions and their corresponding uncertainties follow the same relationship.
 Similar results are also obtained with SMS (not shown).
@@
 The all-sky assimilation systems could also benefit indirectly from cloud corrected radiances, to provide a measure of cloud impact as a diagnostic field for analysing increments.
+Also, it could be potentially feasible to use the QRNN identified cloud impact to formulate the observational errors.
+This could probably be the best use of the QRNN technique for all-sky.
 Another advantage of combining 183\,GHz and sub-mm for cloud correction is that NWP systems, which are not yet prepared for higher frequency channels, could still benefit from the data early on.
 
-In this study, we demonstrate the correction scheme with data from a limited period.
-The seasonal and latitudinal distributions are not taken into account, and more complex surfaces such as sea ice, snow, and high orography have not been considered.
+In this study, we demonstrate the correction scheme with data with limited cloud variability and also neglect the antenna pattern.
+With only one habit and PSD, the true variability of the hydrometeors could be underestimated and can introduce mapping errors between 183\,GHz and sub-mm channels.
+However, it is possible improve the cloud representation by incorporating PSD and habit variation, and QRNN based cloud correction can easily adapt to changes in TB introduced by the local variability.
+This is not the case with all-sky DA systems, which assume only single PSD and habit combination, and shall continue to do so in coming years.
+Additionally, in the limited period study, the seasonal and latitudinal distributions are also not taken into account, and more complex surfaces such as sea ice, snow, and high orography have not been considered.
 It remains to be seen whether QRNN shows any seasonal sensitivity or dependency on cloud types.
@@
 For water vapour, absorption model as  in RTTOV \citep[Radiative transfer for TOVS,][]{saunders2018update} is followed, but with few modifications \citep{turner2019amsutran}.
+For 22 and 183\,GHz transitions, some parameters are replaced.
+A small comparison with RTTOV shows an agreement of the order of 0.1\,K.
 LWC is assumed to be totally absorbing.
-In the mapping of CloudSat reflectivities to RWC and IWC, a total separation between liquid and ice phase is assumed.
-All scattering hydrometeors at temperatures above 0$^{\degree}$C  and below 0$^{\degree}$\,C are assumed to be rain and ice hydrometeors respectively.
+While mapping the CloudSat reflectivities to RWC and IWC, the liquid and ice phase are assumed to be totally separated.
+All scattering hydrometeors at temperatures above 0$^{\degree}$C are assumed to be rain and below 0$^{\degree}$\,C as ice hydrometeors.
 For RWC, the particle size distribution (PSD) of \citet{abel2012improved} is applied.
@@
 This PSD can be considered as a ``two moment'' scheme, but is here applied in a one moment manner by setting $N_0^*$ (as a function of temperature)
-following Table~5 of \citet{delanoe2014normalized}, and letting the radar reflectivity set the remaining moment. Single scattering data are taken from
+following Table~5 of \citet{delanoe2014normalized}. The remaining moment is set by the radar reflectivity. Single scattering data are taken from
 \citet{eriksson:agene:18}. For ice hydrometeors, three habits are applied:
@@
 aggregate. In the last two cases, the aggregates are complemented with single crystal data to also cover smaller sizes. The particles are assumed to have a totally random orientation. 
-To apply oriented particles is much more computationally costly and could not be accommodated inside the study.
+It is computationally much expensive to apply oriented particles and are not accommodated inside the study.
 The land emissivity was taken from Tool to Estimate Land‐Surface Emissivities at Microwave frequencies \citep[TELSEM,][]{aires2011tool} and the

### 2021-03-10 Article/Review_1/response_reviewer_1.tex
version submitted final upload

@@
 \usepackage{natbib}
+\usepackage[modulo]{lineno}
+\linenumbers
 %\usepackage{showframe} %This line can be used to clearly show the new margins
@@
 
-\item 	``precipitation and most dense clouds'' I think the hydrometeor size is an important.\\
+\item 	``precipitation and most dense clouds'' I think the hydrometeor size is an important factor.\\
 
@@
 Pg 4, line 104:
-``\textit{For the demonstation of the study, MWHS-2 background or simulations are used.
+``\textit{For the demonstration of the study, MWHS-2 simulations from the ECMWF model background are used.
 Actual measurements are not taken into account.
@@
 
-\textcolor{blue}{Reply: In the study by \citet{pfreundschuh:aneur:18}, CRPS is defined as using an indicator function ($I$), however for QRNN the integral is evaluated only by approximation.
-To calculate the CRPS, we use a piece-wise linear fit to the approximate posterior CDF obtain from the predicted quantiles.
-This approximation is further used to calculate CRPS.}\\
+\textcolor{blue}{Reply: The CRPS in the manuscript is incorrect. We thank the reviewer for highlighting it. We have corrected the equation in the revised manuscript.}\\
 
@@
 
-\textcolor{blue}{Reply: The reviewer rightly mentions that the real noise is lower, however we add the sensor noise according to the constructor specifications.
+\textcolor{blue}{Reply: The reviewer rightly mentions that the real noise is lower, however we add the sensor noise according to the pre-launch specifications.
 This can be viewed as a conservative estimate of the sensor noise to include other sources of error not accounted for in NEDT.
-For example in study \citet{Carminati-fy3d-2020} the authors describe radiation leak affecting the higher frequency channels.}
+For example in the study by \citet{Carminati-fy3d-2020} the authors describe radiation leak affecting the higher frequency channels.\\
+We clarify in the manuscript that pre-launch specification values are used.}
 
@@
 Most cloud flagging schemes for IR are based on brightness temperature thresholds.
+\\
+In the manuscript, without going into the details, we mention that ``\textit{The scheme could also be potentially extended to cloud correction at infra-red frequencies}''
 }\\
@@
 This could probably be the best use of the QRNN technique for all-sky.
-Of course using QRNN to develop a full observational model, would require to characterize the performance of the scheme over upper latitudes, land and ocean.}\\
+Of course using QRNN to develop a full observational model, would require to characterize the performance of the scheme over upper latitudes, land and ocean.\\
+We have included the following text in the manuscript:\\
+Pg 29, Line 577: ``\textit{Also, it could be feasible to use the QRNN identified cloud impact to formulate the observational errors.
+This may be the best use of the QRNN technique when it comes to all-sky assimilation.}''}\\
 
@@
 
-\textcolor{blue}{Reply:  Yes, it would be feasible to implement the scheme into existing NWP models.
-In this study, QRNN was not optimized to get the maximum computational performance.
-For each MWHS-2 channel, it took around 30 minutes to train the net on a  x86\_64, 8 CPU machine.
-However, with the modern computing architectures and parallel processing, a much faster computation can be expected.
-}\\
-
+\textcolor{blue}{Reply: The method is probably computationally more complex than other methods
+	based on, for example, a scattering index, we consider it unlikely that the
+	computational cost of the scheme would be an issue in an operational context.\\
+	The only demanding part of the scheme is the training process, but it is performed offline.
+Evaluating the network during operational processing  would require only a forward pass through the network.
+In the study, we employ a simple, fully-connected network architecture so that 	the complexity of a forward pass is dominated by a low number of matrix-vector multiplications (one for each layer the network).
+The matrix-vector
+	multiplications are typically combined into matrix-matrix multiplications to
+	evaluate the network for multiple observations in parallel. Due to the recent
+	popularity of neural networks, highly optimized implementations of these methods
+	are available for all common computing architectures. 
+	We have included the following information in the Conclusions section.
+Pg 29, Line 591: ``\textit{Due to its low computational cost, implementation of this scheme should be feasible in NWP models given their computational constraints.
+Although the method is probably computationally more complex than existing cloud clearing methods, the demanding part of the scheme, the training, is performed offline.
+The operational processing only requires a forward pass through the neural network, for which highly-optimized implementations are readily available on all common computing platforms.}''}
 \end{itemize}

### 2021-03-10 Article/Review_1/response_reviewer_2.tex
version submitted final upload

@@
 \usepackage{xcolor}
-
+\usepackage[modulo]{lineno}
+\linenumbers
 %\usepackage{showframe} %This line can be used to clearly show the new margins
@@
 \begin{document}
+
 \title{\textbf{Response to Reviewer 2}}
@@
 The main deviations in the distributions arise from the hydrometeor scattering.
-With limited scope of particle size and shape variation in current NWP microphysical schemes, the true cloud variability cannot be  described accurately, and a bias correction is necessary to be closer to the reality.
+With limited scope of particle size and shape variation in current NWP microphysical schemes, the true cloud variability in radiance space is likely underestimated, though this is but one factor among many when it comes to the challenge of modelling clouds.
 Also, ECMWF has real time monitoring of many satellite sensors including FY-3D MWHS-2, thus it is possible to assess how well the system (and RTTOV-SCATT) is performing.
@@
 
-\textcolor{blue}{Reply: Yes, it would be feasible to implement the scheme into existing NWP models.
-In this study, QRNN was not optimized to get the maximum computational performance.
-For each MWHS-2 channel, it took around 30 minutes to train the net on a  x86\_64, 8 CPU machine.
-For ICI and SMS, with smaller training dataset, the time was lower.
-However, with the modern computing architectures and parallel processing, a much faster computation can be expected.
-}\\
+\textcolor{blue}{Reply: Although the method is probably computationally more complex than other methods	based on, for example, a scattering index, we consider it unlikely that the
+	computational cost of the scheme would be an issue in an operational context.\\
+	 The only demanding part of the scheme is the training process, but it is performed offline.
+Evaluating the network during operational processing  would require only a forward pass through the network.
+In the study, we employ a simple, fully-connected network architecture so that 	the complexity of a forward pass is dominated by a low number of matrix-vector multiplications (one for each layer the network).
+The matrix-vector
+	multiplications are typically combined into matrix-matrix multiplications to
+	evaluate the network for multiple observations in parallel. Due to the recent
+	popularity of neural networks, highly optimized implementations of these methods
+	are available for all common computing architectures. 	We also include the following text to the Conclusions.\\
+	Pg 29, Line 591: ``\textit{Due to its low computational cost, implementation of this scheme should be feasible in NWP models given their computational constraints.
+Although the method is probably computationally more complex than existing cloud clearing methods, the demanding part of the scheme, the training, is performed offline.
+The operational processing only requires a forward pass through the neural network, for which highly-optimized implementations are readily available on all common computing platforms}.'' }\\
 
@@
 For SMS, we had access to a smaller database, which was used for a earlier study.
+Additionally, SMS has fewer channels involved so it can be handled by smaller databases.\\
 Due to difference in sizes of the available observations, maximum possible observations were incorporated in the training data to allow cloud variability.
@@
 We provide the occurence percentage of true value for each uncertainty bin and add this information in Fig.
-13 (also shown above).
-For each bin considered, the true value falls in the range almost 94\% of the time, indicating that the uncertainties are well calibrated.
+13 (also shown below, as Fig.2).
+For each bin considered, the true value falls in the  $\pm2\sigma$ uncertainty range almost 94\% of the time, indicating that the uncertainties are well calibrated.
 Only for channel I3V and the outermost bin, occcurence percentage is 88\%.
@@
 	\caption{Distribution of errors binned according to their uncertainty.
-The occurrence of true value in each uncertainty interval bin is given in the parentheses.
+The percentage values in the parenthesis represent the occurence of true value within the $\pm2\sigma$ uncertainty range, for each of the uncertainty bins.
 Results are from QRNN-single for channels I1V, I2V and I3V.}
@@
 However, it is possible improve the cloud representation by incorporating PSD and habit variation, and QRNN based cloud correction can easily adapt to changes in brightness temperatures introduced by the local variability.
-This is not the case with all-sky data assimilation systems, which assume only single PSD and habit combination, and shall continue to do so in coming years.\\
+This is not the case with all-sky data assimilation systems, which may assume only single PSD and habit combination.\\
 We have edited Sect 2.2 and Conclusions to describe these different errors and their implications.  }

### 2021-03-10 Article/ici_submm_cloudcorr_v1.1.tex
version submitted final upload

@@
 hydrometeors).
+This is done for each channel separately and by only using the measurements, although the scheme is demonstrated in the study by using simulated observations.
 Not only a best estimate is provided, but also a case-specific uncertainty.
@@
 We denote this approach as cloud correction.
-This is done for each channel separately and by only using the measurements, although the scheme is demonstrated in the study by using simulated observations.
 It is shown below that a basically bias free cloud correction can be obtained.
@@
 The main focus of this study is the potential of this cloud-correction
-method using sub-millimetre (sub-mm) observations, which will become available
+method using sub-millimeter (sub-mm) observations, which will become available
 operationally with the launch of the Ice Cloud Imager \citep[ICI,][]{eriksson:towar:20} on board the next generation of European Organisation for the Exploitation of Meteorological Satellites Polar System - Second Generation (EUMETSAT EPS-SG).
@@
 Observations from MWHS-2 are routinely assimilated in all-sky conditions at the European Centre for Medium-Range Weather Forecasts (ECMWF) with demonstrable positive impact on forecast performance \citep{duncan2020MWHS}.
-
-For the demonstration of the study, MWHS-2 background observations or simulations are used.
+The channels relevant to this study are described in Table 1.
+It should be noted that the NE$\Delta$T values in the table are according to pre-launch specifications and not measured NE$\Delta$T values.
+
+For the demonstration of the study, MWHS-2 simulations from the ECMWF model background are used.
 Actual measurements are not taken into account.
@@
 	\centering
-	\includegraphics[width = 70mm]{Figures/fig00.pdf} 
+	\includegraphics[width = 70mm]{Figures/fig01.pdf} 
 	\caption{Probability distribution functions (PDFs) of simulated and observed brightness temperatures for MWHS-2 channel 14.
@@
 The main deviations in the distributions arise from the hydrometeor scattering.
-With limited scope of particle size and shape variation in current NWP microphysical schemes, the true cloud variability cannot be  described accurately, and a bias correction is necessary to be closer to reality.
+With limited scope of particle size and shape variation in current NWP microphysical schemes, the true cloud variability in radiance space is likely underestimated, though this is but one factor among many when it comes to the challenge of modelling clouds.
 
@@
 The remaining 45\,000 are used for testing.
-A smaller database is selected for SMS.
+We select a smaller database for SMS.
 120\,000 simulations are used for training and the remaining 23\,000 for testing.
+We assume that SMS can be handled by smaller database due to lesser number of channels involved.
 
@@
 \begin{align}
-\text{CRPS}(F, y) = \int_{-\infty}^{\infty} \left (F(y') - y\right )^2\: dy'.
+\text{CRPS}(F, y) = \int_{-\infty}^{\infty} \left (F(y') - \mathbf{I}_{y \leq y'} \right)^2\: dy',
 \end{align}
 %
+where $\mathbf{I}_{y \leq y'}$ is the indicator function taking the value $1$ when the condition
+$y \leq y'$ is true and $0$ otherwise.
 To compute the CRPS for a prediction from a QRNN, the predicted quantiles are
@@
 	\centering
-	\includegraphics[height=70mm]{Figures/fig01.pdf} 
+	\includegraphics[height=70mm]{Figures/fig02.pdf} 
 	\caption{Examples showing the predicted quantiles of the conditional distribution of $\ynfcs$ }
@@
 	\centering
-	\includegraphics[width = 70mm]{Figures/fig02.pdf} 
+	\includegraphics[width = 70mm]{Figures/fig03.pdf} 
 	\caption{The distribution of point estimates (``Predicted'') obtained from QRNN-single 89+150\,GHz for MWHS-2 channel 14.
@@
 	\centering
-	\includegraphics[width = 70mm]{Figures/fig03.pdf} 
+	\includegraphics[width = 70mm]{Figures/fig04.pdf} 
 	\caption{The error distribution for deviations of point estimates from NFCS simulations.
@@
 In view of negligible performance differences between the three experiments, we consider the combination 89+150\,GHz to be optimal.
-The results for other channels with this experiment are provided in Sect.~\ref{sec:mwhs_others}.
+For other channels, the results with 89+150\,GHz experiment are provided in Sect.~\ref{sec:mwhs_others}.
 
@@
 	\centering
-	\includegraphics[width=0.65\textwidth]{Figures/fig04.pdf} 
+	\includegraphics[width=0.65\textwidth]{Figures/fig05.pdf} 
 	\caption{ The triangular error correlation matrix obtained from (a) QRNN-single and (b) QRNN-all for MWHS-2. The label ``Clear'' represents cases with cloud impact less than 2\,K.}
@@
 \begin{figure}[t]
-	\includegraphics[width = 70mm]{Figures/fig05.pdf}	
+	\includegraphics[width = 70mm]{Figures/fig06.pdf}	
 	\caption{Examples of prediction uncertainties obtained from QRNN-single (89+150\,GHz) for MWHS-2 channel 14.
@@
 \begin{figure}[t]
-	\includegraphics[height = 70mm]{Figures/fig06.pdf}	
+	\includegraphics[height = 70mm]{Figures/fig07.pdf}	
 	\caption{Calibration of the prediction intervals derived from QRNN-single (89+150\,GHz) for MWHS-2 channel 14, and prediction intervals derived from Gaussian error model for ECMWF NWP system (SI).
@@
 \begin{figure}[t]
-	\includegraphics[width=70mm]{Figures/fig07.pdf}	
+	\includegraphics[width=70mm]{Figures/fig08.pdf}	
 	\caption{The distribution of predicted errors and observed errors  obtained from QRNN-single (89+150\,GHz) for MWHS-2 channel 14.
@@
 \begin{figure*}[t]
-	\includegraphics[width=\textwidth]{Figures/fig08.pdf} 
+	\includegraphics[width=\textwidth]{Figures/fig09.pdf} 
 	\caption{Same as Fig.~\ref{fig:error_distribution_mwhs14}, but from QRNN-single experiment for ICI channels (a) I1V, (b) I2V and (c) I3V. }
@@
 \begin{figure}[t]
-	\includegraphics[width = 70mm]{Figures/fig09.pdf}	
+	\includegraphics[width = 70mm]{Figures/fig10.pdf}	
 	\caption{Same as Fig.~\ref{fig:prediction_uncertainty_mwhs}, but from QRNN-single for ICI channel I2V. The blue line represents a Gaussian distribution with a standard deviation of $0.65$\,K.}
@@
 \begin{figure}[t]
-	\includegraphics[width = 70mm]{Figures/fig10.pdf}	
+	\includegraphics[width = 70mm]{Figures/fig11.pdf}	
 	\caption{Same as Fig.~\ref{fig:calibration_mwhs}, but from QRNN-single for ICI channel I2V. }
@@
 \begin{figure}[t]
-	\includegraphics[width= 70mm]{Figures/fig11.pdf}	
+	\includegraphics[width= 70mm]{Figures/fig12.pdf}	
 	\caption{Same as Fig.~\ref{fig:predicted_errors_mwhs}, but from QRNN-single for ICI channel I2V.}
@@
 \begin{figure}[t]
-	\includegraphics[width = 70mm]{Figures/fig12.pdf}	
+	\includegraphics[width = 70mm]{Figures/fig13.pdf}	
 	\caption{The average confidence intervals ($\pm3\sigma$) plotted against the magnitude of cloud impact for all SMS channels.}
@@
 \begin{figure*}[t]
-	\includegraphics[width=\textwidth]{Figures/fig13.pdf}	
+	\includegraphics[width=\textwidth]{Figures/fig14.pdf}	
 	\caption{Distribution of errors binned according to their uncertainty.
-The occurrence of true value in each uncertainty interval bin is given in the parentheses.
+The percentage values in the parenthesis represent the occurence of true value within the $\pm2\sigma$ uncertainty range, for each of the uncertainty bins.
 Results are from QRNN-single for channels I1V, I2V and I3V.}
@@
 Cases with accurate predictions yet high uncertainty are also present.
-For each channel and bin, but last bin for I3V,  the occurrence of true value inside all three uncertainty bins is almost 94\%, indicating that uncertainties are well calibrated and are not concentrated in a narrow interval.
+For each channel and bin, but last bin for I3V, the occurrence of true value within the $\pm\,2\sigma$ uncertainty range is almost 94\%, indicating that uncertainties are well calibrated and are not concentrated in a narrow interval.
 Only for I3V, the uncertainties are slightly smaller in the last bin.
@@
 The weighting functions of window channels 89 and 150\,GHz, and 118$\pm$2.5\,GHz channels peak in the lower troposphere.
-The channels, 150\,GHz and 118.75$\pm$2.5 peak between surface and 4\,km.
+The channels, 150\,GHz and 118.75$\pm$2.5 peak between surface and 4\,km \citep{chen2020mwhs}.
 These channels can only provide coverage to the humidity channels in the lower and mid troposphere.
@@
 
-Based on the promising results from MWHS-2, and with future scope, we extend the study to include data from Ice Cloud Imager (ICI) sub-millimetre (sub-mm) channels.
+Based on the promising results from MWHS-2, and with future scope, we extend the study to include data from Ice Cloud Imager (ICI) sub-millimeter (sub-mm) channels.
 The results show that with  sub-mm channels, QRNN is able to correctly predict most of the cloudy cases and can provide high quality cloud corrected radiances.
@@
 
-The cloud corrected radiances have great potential in both retrieval schemes and numerical weather prediction (NWP) systems.
+The cloud corrected microwave radiances have great potential in both retrieval schemes and numerical weather prediction (NWP) systems.
 Even with availability of new sensors and better observations, the problems posed by undetected cloud impact limit the complete usage of humidity observations.
@@
 The all-sky assimilation systems could also benefit indirectly from cloud corrected radiances, to provide a measure of cloud impact as a diagnostic field for analysing increments.
-Also, it could be potentially feasible to use the QRNN identified cloud impact to formulate the observational errors.
-This could probably be the best use of the QRNN technique for all-sky.
+Also, it could be feasible to use the QRNN identified cloud impact to formulate the observational errors.
+This may be the best use of the QRNN technique when it comes to all-sky assimilation.
 Another advantage of combining 183\,GHz and sub-mm for cloud correction is that NWP systems, which are not yet prepared for higher frequency channels, could still benefit from the data early on.
+Furthermore, the scheme could also be potentially extended to cloud correction at infra-red frequencies.
 
@@
 However, it is possible improve the cloud representation by incorporating PSD and habit variation, and QRNN based cloud correction can easily adapt to changes in TB introduced by the local variability.
-This is not the case with all-sky DA systems, which assume only single PSD and habit combination, and shall continue to do so in coming years.
-Additionally, in the limited period study, the seasonal and latitudinal distributions are also not taken into account, and more complex surfaces such as sea ice, snow, and high orography have not been considered.
+This is not the case with all-sky DA systems, which may assume only a single PSD and habit combination.
+Besides, in the limited period study, the seasonal and latitudinal distributions are also not taken into account, and more complex surfaces such as sea ice, snow, and high orography have not been considered.
 It remains to be seen whether QRNN shows any seasonal sensitivity or dependency on cloud types.
 Such analysis could also be important at improving the a priori distribution of rare cases.
+
+Due to its low computational cost, implementation of this scheme should be feasible in NWP models given their computational constraints.
+Although the method is probably computationally more complex than existing cloud clearing methods, the demanding part of the scheme, the training, is performed offline.
+The operational processing only requires a forward pass through the neural network, for which highly-optimized implementations are readily available on all common computing platforms.
 
@@
 For 22 and 183\,GHz transitions, some parameters are replaced.
-A small comparison with RTTOV shows an agreement of the order of 0.1\,K.
+An ongoing inter-comparison study with RTTOV shows an agreement of the order of 0.1\,K for most ICI channels.
 LWC is assumed to be totally absorbing.
